### 2020-06-11 ExperimentalData/DIIID/169466/Results/Report/Report.tex
Improved neutral model

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{fullpage}
\usepackage{graphicx}
\allowdisplaybreaks

\title{\bf DIII-D Discharge 169466}
\date{}
\author{}

\begin{document}
\maketitle

\section{Llama Data}
Figure~\ref{fig1} shows the following fit to the Llama data:
\begin{equation}
n_n(R) = \frac{n_n}{1+(R-R_{\rm sep})^{\,2}/L^{\,2}},
\end{equation}
where $n_n = 1.4\times 10^{17}\,{\rm m}^{-3}$, $L= 0.015\,{\rm m}$, $R_{\rm sep}= 1.92\,{\rm m}$.

\begin{figure}[h]
\centering
\includegraphics[height=4in]{neutral.eps}
\caption{Fit to Llama data. Black: Data points. Red: Fit.}\label{fig1}
\end{figure}

\section{Natural Frequencies}
\begin{figure}
\centering
\includegraphics[height=4in]{3200.eps}
\caption{Natural frequencies at $t=3200$ ms. Red: Linear natural frequency. Blue: Nonlinear natural frequency. Black: ${\bf E}\times {\bf B}$ frequency.}\label{fig2}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=4in]{3600.eps}
\caption{Natural frequencies at $t=3600$ ms. Red: Linear natural frequency. Blue: Nonlinear natural frequency. Black: ${\bf E}\times {\bf B}$ frequency.}\label{fig3}
\end{figure}

\end{document}

### 2020-06-13 ExperimentalData/DIIID/169466/Results/Report/Report.tex
Minor changes

@@
 \begin{equation}
-n_n(R) = \frac{n_n}{1+(R-R_{\rm sep})^{\,2}/L^{\,2}},
+\langle n_n\rangle(R) = \frac{n_n}{1+(R-R_{\rm sep})^{\,2}/l_n^{\,2}},
 \end{equation}
-where $n_n = 1.4\times 10^{17}\,{\rm m}^{-3}$, $L= 0.015\,{\rm m}$, $R_{\rm sep}= 1.92\,{\rm m}$.
+where $n_n = 1.4\times 10^{17}\,{\rm m}^{-3}$, $l_n= 0.015\,{\rm m}$, $R_{\rm sep}= 1.92\,{\rm m}$.  The fit is not perfect. However, given
+the uncertainties in quantities such as the charge exchange cross-section and the poloidal asymmetry of the neutral distribution, it is probably adequate.
+The separatrix is identified with the peak in the neutral distribution.
+Another important neutral
+distribution parameter is the poloidal asymmetry parameter:
+\begin{equation}
+y_n = \frac{\langle n_n\rangle\langle B^{\,2}\rangle}{\langle n_n\,B^{\,2}\rangle}.
+\end{equation}
 
-\begin{figure}[h]
+\section{Natural Frequencies}
+Figures~\ref{fig2} and \ref{fig3} show the natural frequencies at the $n=3$ resonant surfaces for the baseline scenario
+at times $t=3200$ and 3600 ms, respectively. It can be seen that the zero crossing is pushed to lower ${\mit\Psi}_N$ values the later time. 
+However, the natural frequency at the 9/3 surface is actually smaller at the later time, which is not consistent with the later time
+corresponding to lack of ELM suppression.
+
+Figures~\ref{fig4} and \ref{fig5} show what happens to the baseline scenario when the neutral density is increased by a factor of
+10. It can be seen that the nonlinear natural frequency is pulled strongly in the electron direction.
+
+Figures~\ref{fig6} and \ref{fig7} show what happens to the baseline scenario when the neutral density is decreased by a factor of
+10. It can be seen that the nonlinear natural frequency is pulled somewhat in the ion direction.
+
+Figures~\ref{fig8} and \ref{fig9} show what happens to the baseline scenario when there is no poloidal asymmetry in the neutral distribution.
+It can be seen that the nonlinear natural frequency is pulled somewhat in the ion direction.
+In this case, the natural frequency at the 10/3 surface is smaller at the earlier time, which is consistent with the earlier time
+corresponding to  ELM suppression.
+
+\section{Conclusions}
+The only clear trend is that the zero crossing moves inwards in ${\mit\Psi}_N$ at the later time. However, it is not clear that this
+accounts for the lack of ELM suppression at the later time.
+
+\begin{figure}
 \centering
@@
 
-\section{Natural Frequencies}
 \begin{figure}
 \centering
-\includegraphics[height=4in]{3200.eps}
-\caption{Natural frequencies at $t=3200$ ms. Red: Linear natural frequency. Blue: Nonlinear natural frequency. Black: ${\bf E}\times {\bf B}$ frequency.}\label{fig2}
+\includegraphics[height=4in]{3200_sim1.eps}
+\caption{Natural frequencies at $t=3200$ ms.
+Neutral parameters: $n_n= 1.4\times 10^{17}\,{\rm m}^{-3}$, $l_n= 0.015\,{\rm m}$, $y_n=1.5$.
+Red: Linear natural frequency.
+Blue: Nonlinear natural frequency.
+Black: ${\bf E}\times {\bf B}$ frequency.
+The points correspond to the
+6/3, 7/3, 8/3, 9/3, 10/3, 11/3, 12/3, 13/3, and 14/3 rational surfaces in order from the left to the right.}\label{fig2}
 \end{figure}
@@
 \centering
-\includegraphics[height=4in]{3600.eps}
-\caption{Natural frequencies at $t=3600$ ms. Red: Linear natural frequency. Blue: Nonlinear natural frequency. Black: ${\bf E}\times {\bf B}$ frequency.}\label{fig3}
+\includegraphics[height=4in]{3600_sim1.eps}
+\caption{Natural frequencies at $t=3600$ ms.
+Neutral parameters: $n_n= 1.4\times 10^{17}\,{\rm m}^{-3}$, $l_n= 0.015\,{\rm m}$, $y_n=1.5$.
+Red: Linear natural frequency.
+Blue: Nonlinear natural frequency.
+Black: ${\bf E}\times {\bf B}$ frequency.
+The points correspond to the
+6/3, 7/3, 8/3, 9/3, 10/3, 11/3, 12/3, 13/3, and 14/3 rational surfaces in order from the left to the right.}\label{fig3}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[height=4in]{3200_sim2.eps}
+\caption{Natural frequencies at $t=3200$ ms.
+Neutral parameters: $n_n= 1.4\times 10^{18}\,{\rm m}^{-3}$, $l_n= 0.015\,{\rm m}$, $y_n=1.5$.
+Red: Linear natural frequency.
+Blue: Nonlinear natural frequency.
+Black: ${\bf E}\times {\bf B}$ frequency.
+The points correspond to the
+6/3, 7/3, 8/3, 9/3, 10/3, 11/3, 12/3, 13/3, and 14/3 rational surfaces in order from the left to the right.}\label{fig4}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[height=4in]{3600_sim2.eps}
+\caption{Natural frequencies at $t=3600$ ms.
+Neutral parameters: $n_n= 1.4\times 10^{18}\,{\rm m}^{-3}$, $l_n= 0.015\,{\rm m}$, $y_n=1.5$.
+Red: Linear natural frequency.
+Blue: Nonlinear natural frequency.
+Black: ${\bf E}\times {\bf B}$ frequency.
+The points correspond to the
+6/3, 7/3, 8/3, 9/3, 10/3, 11/3, 12/3, 13/3, and 14/3 rational surfaces in order from the left to the right.}\label{fig5}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[height=4in]{3200_sim3.eps}
+\caption{Natural frequencies at $t=3200$ ms.
+Neutral parameters: $n_n= 1.4\times 10^{16}\,{\rm m}^{-3}$, $l_n= 0.015\,{\rm m}$, $y_n=1.5$.
+Red: Linear natural frequency.
+Blue: Nonlinear natural frequency.
+Black: ${\bf E}\times {\bf B}$ frequency.
+The points correspond to the
+6/3, 7/3, 8/3, 9/3, 10/3, 11/3, 12/3, 13/3, and 14/3 rational surfaces in order from the left to the right.}\label{fig6}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[height=4in]{3600_sim3.eps}
+\caption{Natural frequencies at $t=3600$ ms.
+Neutral parameters: $n_n= 1.4\times 10^{16}\,{\rm m}^{-3}$, $l_n= 0.015\,{\rm m}$, $y_n=1.5$.
+Red: Linear natural frequency.
+Blue: Nonlinear natural frequency.
+Black: ${\bf E}\times {\bf B}$ frequency.
+The points correspond to the
+6/3, 7/3, 8/3, 9/3, 10/3, 11/3, 12/3, 13/3, and 14/3 rational surfaces in order from the left to the right.}\label{fig7}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[height=4in]{3200_sim4.eps}
+\caption{Natural frequencies at $t=3200$ ms.
+Neutral parameters: $n_n= 1.4\times 10^{17}\,{\rm m}^{-3}$, $l_n= 0.015\,{\rm m}$, $y_n=1.0$.
+Red: Linear natural frequency.
+Blue: Nonlinear natural frequency.
+Black: ${\bf E}\times {\bf B}$ frequency.
+The points correspond to the
+6/3, 7/3, 8/3, 9/3, 10/3, 11/3, 12/3, 13/3, and 14/3 rational surfaces in order from the left to the right.}\label{fig8}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[height=4in]{3600_sim4.eps}
+\caption{Natural frequencies at $t=3600$ ms.
+Neutral parameters: $n_n= 1.4\times 10^{17}\,{\rm m}^{-3}$, $l_n= 0.015\,{\rm m}$, $y_n=1.0$.
+Red: Linear natural frequency.
+Blue: Nonlinear natural frequency.
+Black: ${\bf E}\times {\bf B}$ frequency.
+The points correspond to the
+6/3, 7/3, 8/3, 9/3, 10/3, 11/3, 12/3, 13/3, and 14/3 rational surfaces in order from the left to the right.}\label{fig9}
 \end{figure}

### 2020-06-20 Neoclassical/Source/Neoclassical.cpp
Improved graphs

@@ -973,13 +973,13 @@ void Neoclassical::Get_Normalized ()
       printf ("m = %3d r = %10.3e q = %10.3e rho = %10.3e a = %10.3e S = %10.3e w0 = %10.3e tauM = %10.3e tauth = %10.3e del = %10.3e\n",
 	      mk (j), rk (j), qk (j), rhok (j), a/R_0, Sk, wk, tm, th, dk);
 
-      fprintf (file, "%d %d %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e\n",
+      fprintf (file, "%d %d %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e\n",
 	       mk (j), ntor, rk (j), qk (j), rhok (j), a /R_0, Sk, wk, tm, th, sqrt (qk (j)/gk (j)/sk (j)), dk, wkl, wke,
-	       dnedrk (j)/1.e19, dTedrk (j) /e/1.e3, Wcritnk (j), WcritTk (j), akk(j), gk(j), dPsidr(j));
+	       dnedrk (j)/1.e19, dTedrk (j) /e/1.e3, Wcritnk (j), WcritTk (j), akk(j), gk(j), dPsidr(j), PsiNk(j));
     }
    fclose (file);
 
-   if (INTP > 0 && TIME > 0.)
+   if (INTP != 0 && TIME > 0.)
      {
       char* filename = new char[MAXFILENAMELENGTH];
       sprintf (filename, "Outputs/nFiles/n.%d", int (TIME));
@@ -997,9 +997,9 @@ void Neoclassical::Get_Normalized ()
 	  double tm  = tau_Mk (j) /tau_A;
 	  double th  = tau_thk (j) /mu_00_i (j) /tau_A;
 	  
-	  fprintf (file, "%d %d %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e\n",
[…]

### 2020-07-01 ExperimentalData/DIIID/145380/Paper/paper.tex
Added DiiiD paper

\documentclass[12pt,prb,aps]{revtex4-1}
\usepackage{amsmath}
\pdfoutput=1 
\usepackage{graphicx}
\newcommand {\bomega}{\mbox{\boldmath$\omega$}}
\newcommand {\bpi}{\mbox{\boldmath$\pi$}}

\begin{document}

\title {Modelling $q_{95}$ Windows for the Suppression of Edge Localized Modes by Resonant Magnetic Perturbations in the DIII-D Tokamak}

\author{R.~Fitzpatrick}
\affiliation{Institute for Fusion Studies,  Department of Physics,  University of Texas at Austin,  Austin TX, 78712, USA}

\maketitle

\section{Introduction}
Tokamak discharges operating in high-confinement mode (H-mode)\,\cite{wagner} exhibit intermittent bursts of heat and particle transport, 
emanating from the outer regions of the plasma, that are known as ``type-I edge localized modes'' (ELMs). \cite{zohm}
It is estimated that the heat load that ELMs
will deliver to the tungsten plasma-facing components in a reactor-scale tokamak, such as ITER, will be large enough to cause
massive tungsten ion influx into the plasma core, and that the erosion associated with this process will 
unacceptably limit the lifetimes of these components. \cite{loarte} Consequently, the development of robust and effective
methods for ELM control is a high priority for the international magnetic fusion program.

The most promising method for the control of ELMs in H-mode tokamak discharges is via the application of static   ``resonant magnetic perturbations'' (RMPs). Complete RMP-induced ELM suppression was first demonstrated on the DIII-D tokamak.\cite{evans} Subsequently, either mitigation or compete suppression of
ELMs has been demonstrated on the JET,\cite{jet} ASDEX-U,\cite{asdex} KSTAR,\cite{kstar} MAST\,\cite{mast}, and EAST\,\cite{east} tokamaks.

The application of a static RMP, resonant in the pedestal region (i.e., the region of strong pressure and current density gradients characteristic of the edge region of an H-mode tokamak discharge), to an H-mode tokamak discharge is observed to give rise to  two distinct phenomena.\cite{schmitz, lanctot,paz1,d158115,paz} The first of these  is the so-called ``density pump-out'', which  is characterized by a reduction in the electron number density
in the pedestal region that varies smoothly with the amplitude of the applied RMP,  is (usually) accompanied by a similar, but significantly smaller, reduction
in the electron and ion temperatures, but  is not associated with ELM suppression. The second phenomenon is  ``ELM suppression'' itself, which 
 occurs when the amplitude of the applied RMP exceeds a certain threshold value. 
ELM suppression  is only observed to take place when $q_{95}$ (i.e., the safety-factor on the magnetic flux-surface that encloses 95\% of the poloidal flux enclosed by
the last closed flux-surface) takes values that lie in certain narrow windows. \cite{paz1,d158115}

Numerical simulations made using the cylindrical,  nonlinear, two-fluid, reduced-magneto\-hydro\-dynamical (MHD), initial-value code, TM1\,\cite{tm1,tm2,tm3} have shed considerable light on the hitherto poorly understood  physical mechanism that underlies RMP-induced ELM
suppression in H-mode tokamak discharges.\cite{hu} The simulations  in question make a plausible case  that the density  pump-out  phenomenon is associated with the formation of   locked (i.e., non-rotating) helical magnetic
island chains at the bottom of the pedestal, whereas the ELM suppression phenomenon is associated with the formation of a locked helical magnetic island chain at the
top of the pedestal. The prevailing hypothesis is that such an island chain suppresses ELMs by limiting the expansion of the
pedestal, and, thereby, preventing it from attaining a width sufficient to destabilize peeling-ballooning modes\,\cite{connor}  (which are thought to trigger ELMs).\cite{d3d}

Recently, a toroidal generalization of the 
cylindrical asymptotic matching model presented
in Ref.~\onlinecite{rf1} was formulated and
used to model  RMP-induced ELM suppression experiments performed on the DIII-D tokamak, \cite{rf2}
leading to similar conclusions to the aforementioned TM1
studies. The primary aim of this paper is to employ this
new model to try to account for the  $q_{95}$ ELM
suppression windows  that are apparent when the edge safety-factor is slowly ramped in
a particular DIII-D discharge in which an $n=3$
RMP is used to control ELMs.\cite{d3d,d3d2}

It is well-known that magnetic reconnection caused when a  (stable) tearing mode is driven by a static RMP that is resonant at a particular magnetic flux-surface in a tokamak plasma is
facilitated when the associated ``natural frequency'' is relatively small.\cite{rfa,rfb}  The natural frequency  of a  (stable) tearing mode is the
helical phase velocity that the mode would possess were it naturally unstable (in the absence of the RMP).  Driven magnetic reconnection leads to the
formation of a locked magnetic island chain at the resonant surface in question. 
Hence, the prevailing hypothesis is that a $q_{95}$ window for
RMP-induced ELM suppression occurs when $q_{95}$ is such that the natural frequency of a tearing mode resonant  at 
the top of the pedestal is close to zero. 
Unfortunately, there is currently some uncertainty in the fusion community regarding the form of the natural frequency.

According to
linear tearing mode theory, a tearing mode is essentially convected by
the local electron fluid at the resonant surface (see the discussion at the end of the Appendix).\cite{hender,cole} Hence, if the response of an H-mode tokamak plasma to an applied RMP
is governed by linear physics then we would expect the
natural frequency to take the form\,\cite{lin1,lin2,lin3}
\begin{equation}
\varpi_{\rm linear} = - n\,(\omega_E+\omega_{\ast\,e}),\label{e1}
\end{equation}
where
\begin{align}
\omega_E &= -\frac{d{\mit\Phi}}{d{\mit\Psi}_p},\\[0.5ex]
\omega_{\ast\,e} &=\frac{T_e}{e}\,\frac{d\ln p_e}{d{\mit\Psi}_p}.
\end{align}
Here, ${\mit\Psi}_p$ is the equilibrium poloidal magnetic
flux (divided by $2\pi$), ${\mit\Phi}({\mit\Psi}_p)$ the equilibrium scalar
electric potential, $p_e({\mit\Psi}_p)$ the equilibrium
electron pressure, $T_e({\mit\Psi}_p)$ the equilibrium
electron temperature, $e$ the magnitude of the electron
charge, and $n$ the toroidal mode number of the RMP. 
Moreover, the right-hand side of Eq.~(\ref{e1}) is evaluated
at the ``rational''  (i.e., resonant) magnetic flux-surface at which the
safety-factor
\begin{equation}
q({\mit\Psi}_p)= \frac{d{\mit\Psi}_t}{d{\mit\Psi}_p},
\end{equation}
takes the rational value $n/m$, where $m$ is a positive integer. Here, $m$ and $n$ are the numbers of poloidal and
toroidal periods, respectively, of the helical magnetic island chain driven at the rational surface.  Furthermore, ${\mit\Psi}_t({\mit\Psi}_p)$ is the equilibrium toroidal magnetic flux (divided by $2\pi$).

According to nonlinear tearing mode theory, a tearing mode is essentially convected by
the local ion fluid at the rational surface (again, see the discussion at the end of the Appendix).\cite{nl1,nl2,nl3}
In fact, if the response of an H-mode tokamak plasma to an applied RMP
is governed by nonlinear physics then we would expect the
natural frequency to take the form\,\cite{rf2}
\begin{equation}\label{e2}
\varpi_{\rm nonlinear} = -n\left(\omega_E +\left[1-L_{00}^{\,ii}+L_{01}^{\,ii}\left(\frac{\eta_i}{1+\eta_i}\right)\right]
\omega_{\ast\,i}
%\right.\nonumber\\[0.5ex]&\left.
-\left[L_{00}^{\,iI}- L_{01}^{\,iI}\left(\frac{\eta_I}{1+\eta_I}\right)\right]\omega_{\ast\,I}\right),
\end{equation}
where
\begin{align}
\omega_{\ast\,a}({\mit\Psi}_p) &=-\frac{T_a}{Z_a\,e}\,\frac{d\ln p_a}{d{\mit\Psi}_p},\\[0.5ex]
\eta_a({\mit\Psi}_p)&=\frac{d\ln T_a}{d\ln n_a},
\end{align}
for $a=i, I$. 
Here,  $Z_i$, $n_i({\mit\Psi}_p)$, $T_i({\mit\Psi}_p)$, and $p_i({\mit\Psi}_p)=n_i\,T_i$   are the charge number, equilibrium number density, 
equilibrium temperature, and equilibrium pressure
of the majority (thermal) ions, respectively,
whereas  $Z_I$, $n_I$, $T_I$, $p_I = n_I\,T_I$
are the corresponding quantities for the impurity ions.  
Furthermore, $L_{00}^{ii}({\mit\Psi}_p)$, $L_{01}^{ii}({\mit\Psi}_p)$,  $L_{00}^{II}({\mit\Psi}_p)$, and $L_{01}^{II}({\mit\Psi}_p)$ are neoclassical parameters that are defined
in Ref.~\onlinecite{rf2}. Note that these parameters are
affected by charge exchange  with neutrals. Finally,
as before, the right-hand side of Eq.~(\ref{e2}) is evaluated
at the rational magnetic flux-surface.

A third possibility is that a tearing mode is convected by the local guiding center fluid at the rational surface,\cite{heyn,paz1}
in which case we would expect the natural frequency to take the form 
\begin{equation}\label{e3}
\varpi_{EB} =-n\,\omega_E.
\end{equation}
As before, the right-hand side of Eq.~(\ref{e3}) is evaluated
at the rational magnetic flux-surface.

The secondary aim of this paper is to determine which of the three aforementioned choices for the natural frequency can best account for the   $q_{95}$ ELM
suppression windows  observed in DIII-D.

\section{Description of Theoretical Model}
The theoretical model of the response of a tokamak plasma to an externally applied RMP that is employed in this
paper is described in detail in Ref.~\onlinecite{rf2}. The model employs a standard asymptotic matching approch.\cite{fkr,am1,am2,am3}
According to this approach, the response of the plasma to the applied RMP is governed by a combination of flux-freezing and
perturbed force balance (this combination is often referred to as ``marginally-stable ideal-MHD", which is a misnomer because MHD {\em per se}\/ plays no
role) everywhere in the plasma apart from a number of relatively narrow (in the radial direction) regions in which the applied
perturbation resonates with the equilibrium magnetic field. Magnetic reconnection can take place within the resonant regions to
produce relatively thin magnetic islands. Within the resonant regions, the plasma response is governed by nonlinear,
as opposed to linear, two-fluid resistive MHD. This is the case because the widths of the magnetic island chains
driven at the resonant surfaces exceed the linear layer widths (which invalidates linear theory).\cite{rf1}
Thus, when employing the asymptotic matching approach, the equations of flux-freezing and perturbed force balance
are solved in the so-called ``outer region'' that comprises most of the plasma (and the surrounding vacuum), the equations of 
nonlinear two-fluid resistive-MHD are solved in the various resonant layers that constitute the so-called ``inner region'', and the two
sets of solutions are then asymptotically matched to one another.

A toroidal tokamak equilibrium exhibits two distinct types of response to an applied RMP.\cite{paz1,kink0,kink1}
The first of these is known as the ``tearing response''---this is a non-ideal-MHD response that is associated with the
formation of current sheets and magnetic island chains at various resonant surfaces within the plasma. The second
response type is known as the ``kink response''---this is an edge-localized ideal-MHD response that is associated
with coupling to a stable non-resonant kink mode. For the case of the tearing response, our model employs an
approximation in which the plasma response is assumed to be vacuum-like between the various resonant surfaces. On the other hand,
the kink response of the plasma is calculated using the {\tt GPEC} code.\cite{ipec,gpec}

Our model has been implemented in the {\tt EPEC} (Extended Perturbed Equilibrium Code) code. The name
of this code reflects the fact that the nonlinear evolution of tearing modes in a
tokamak plasma has far more in common with the $1\tfrac{1}{2}$-D
evolution of the global plasma equilibrium than it does with
conventional linear tearing mode physics. (See the discussion in the Appendix.) In particular, the Alfv\'{e}n time is
an irrelevant timescale in nonlinear tearing mode theory, and
is also  very much shorter than the timescales on which
physical quantities of interest actually evolve. (Note that all timescales are normalized to the Alfv\'{e}n time
in Ref.~\onlinecite{rf2}. However, this is just a matter of convention. With the benefit of hindsight, it would
have been better to normalize the timescales with respect to a diamagnetic timescale, in which case the Alfv\'{e}n time would have completely dropped
out of the final system of equations.)

\section{Modeling of DIII-D Discharge \#145380}

\section{Summary and Discussion}

\section*{Acknowledgements}
This research was funded by the U.S.\ Department of Energy under contract DE-FG02-04ER-54742.
The author would like to thank Q.M.~Hu and R.~Nazikian for providing the experimental data used in this paper.

\section*{References}
\begin{thebibliography}{99}\baselineskip 5ex

\bibitem{wagner} F.~Wagner, G.~Becker, K.~Behringer, D.~Campbell, A.~Eberhagen, W.~Engelhardt, G.~Fussmann, O.~Gehre, J.~Gernhardt, G.~v.~Gierke, {\it et al.}, 
Phys.\ Rev.\ Lett.\ {\bf 49}, 1408 (1982).

\bibitem{zohm} H.~Zohm, Plasma Phys.\ Control.\ Fusion {\bf 38}, 105 (1996).

\bibitem{loarte} A.~Loarte, G.~Saibene, R.~Sartori, M.~B\'{e}coulet, L.~Horton, T.~Eich, A.~Herrmann, M.~Laux, G.~Matthews, S.~Jachmich, {\it et al.},  
J.\ Nucl.\ Materials {\bf 313}--{\bf 316}, 962 (2003).

\bibitem{evans}  T.E.~Evans, R.A.~Moyer, J.G.~Watkins, P.R.~Thomas, T.H.~Osborne, J.A.~Boedo, M.E.~Fenstermacher, K.H.~Finken, R.J.~Groebner, M.~Groth, {\it et al.},  
Phys.\ Rev.\ Lett.\ {\bf 92}, 235003 (2004).

\bibitem{jet} Y.~Liang,  H.R.~Koslowski, P.R.~Thomas, E.~Nardon, B.~Alper, P.~Andrew, Y.~Andrew, G.~Arnoux,  Y.~Baranov, M.~B\'{e}coulet, {\it et al.},  
Phys.\ Rev.\ Lett.\ {\bf 98}, 265004 (2007).

\bibitem{asdex} W.~Suttrop,  T.~Eich, J.C.~Fuchs, S.~G\"{u}nter, A.~Janzer, A.~Herrmann, A.~Kallenbach, P.T.~Lang, T.~Lunt, M.~Maraschek, {\it et al.},   
Phys.\ Rev.\ Lett.\ {\bf 106}, 225004 (2011).

\bibitem{kstar} Y.M.~Jeon,  J.-K.~Park, S.W.~Yoon, W.H.~Ko, S.G.~Lee, K.D.~Lee, G.S.~Yun, Y.U.~Nam, W.C.~Kim, J.-G.~Kwak, K.S.~Lee, H.K.~Kim, and H.L.~Yang, {\it et al.}, 
Phys.\ Rev.\ Lett.\ {\bf 109}, 035004 (2012).

\bibitem{mast} A.~Kirk, I.T.~Chapman, Y.~Liu, P.~Cahyna, P.~Denner, G.~Fishpool, C.J.~Ham, J.R.~Harrison, Y.~Liang, E.~Nardon, S.~Saarelma, R.~Scannell, A.J.~Thornton, and  MAST Team, 
Nucl.\  Fusion {\bf 53}, 043007 (2013).

\bibitem{east} T.~Sun,  Y.~Liang, Y.Q.~Liu, S.~Gu, X.~Yang, W.~Guo, T.~Shi, M.~Jia, L.~Wang, B.~Lyu, {\it et al.},  
Phys.\ Rev.\ Lett.\  {\bf 117}, 115001 (2016).

\bibitem{schmitz} O.~Schmitz, T.E.~Evans, M.E.~Fenstermacher, M.~Lehnen, H.~Stoschus, E.A.~Unterberg, J.W.~Coenen, H.~Frerichs, M.W.~Jakubowski, R.~Laengner, {\em et al.}, 
Nucl.\ Fusion {\bf 52}, 043005 (2012).

\bibitem{lanctot} M.J.~Lanctot, R.J.~Buttery, J.S.~de\,Grassie, T.E.~Evans, N.M.~Ferraro, J.M.~Hanson, S.R.~Haskey,  R.A.~Moyer, R.~Nazikian, T.H.~Osborne, {\em et al.}, \\
Nucl.\ Fusion {\bf 53}, 083019 (2013).

\bibitem{paz} C.~Paz-Solden, R.~Nazikian, S.R.~Haskey, N.C.~Logan, E.J.~Strait, N.M.~Ferraro, J.M.~Hanson, J.D.~King, M.J.~Lanctot, R.A.~Moyer, {\it et al.}, 
Phys.\ Rev.\ Lett.\ {\bf 114}, 105001 (2015).

\bibitem{d158115} R.~Nazikian, C.~Paz-Soldan, J.D.~Callen,  J.S.~de\,Grassie, D.~Eldon, T.E.~Evans, N.M.~Ferraro,  B.A.~Grierson, R.J.~Groebner, S.R.~Haskey, {\em et al.}, 
Phys.\ Rev.\ Lett.\ {\bf 114}, 105002 (2015).

\bibitem{paz1} C.~Paz-Solden, R.~Nazikian, L.~Cui, B.C.~Lyons,  D.M.~Orlov, A.~Kirk, N.C.~Logan, T.H.~Osborne, W.~Suttrop, and D.B.~Weisberg, 
Nucl.\ Fusion {\bf 59}, 056012 (2019).

\bibitem{tm1} Q.~Yu, S.~G\"{u}nter,  and B.D.~Scott, Phys.\ Plasmas {\bf 10}, 797 (2003).

\bibitem{tm2} Q.~Yu, Nucl.\ Fusion {\bf 50}, 025014 (2010).

\bibitem{tm3} Q.~Yu, and S.~G\"unter,  Nucl.\ Fusion {\bf 51},  073030 (2011).

\bibitem{hu} Q.M.~Hu,  R.~Nazikian,  B.A.~Grierson,  N.C.~Logan,  J.-K.~Park,  C.~Paz-Soldan, and Q.~Yu,  Phys.\ Plasmas {\bf 26}, 120702 (2019).

\bibitem{connor} J.W.~Connor,  R.J.~Hastie, H.R.~Wilson, and R.L.~Miller, Phys.\ Plasmas  {\bf 5}, 2687 (1998).

 \bibitem{d3d} P.B.~Snyder, T.H.~Osboune, K.H.~Burrell, R.J.~Groebner, A.W.~Leonard, R.~Nazikian, D.M.~Orlov, O.~Schmitz, M.R.~Wade, and H.R.~Wilson, 
 Phys.\ Plasmas {\bf 19}, 056115 (2012).

\bibitem{rf1} R.~Fitzpatrick, Phys.\ Plasmas {\bf 27}, 042506 (2020).

\bibitem{rf2} R.~Fitzpatrick, and A.O.~Nelson, Phys.\ Plasmas {\bf 27}, 072501 (2020).

\bibitem{d3d2} Q.M.~Hu, R.~Nazikian, B.A.~Grierson, N.C.~Logan, D.M.~Orlov, C.~Paz-Solden, and Q.~Yu,
{\em The $q_{95}$ Windows of Edge-Localized-Mode Suppression using Resonant Magnetic Perturbations in the DIII-D Tokamak}, 
Phys.\ Rev.\ Lett., to appear (2020).

\bibitem{rfa} R.~Fitzpatrick, Nucl.\ Fusion {\bf 33}, 1049 (1993).

\bibitem{rfb} R.~Fitzpatrick, Phys.\ Plasmas {\bf 5}, 3325 (1998).

\bibitem{hender} R.~Fitzpatrick, and T.C.~Hender, Phys.\ Fluids B {\bf 3}, 644 (1991).

\bibitem{cole} A.~Cole, and R.~Fitzpatrick, Phys.\ Plasmas {\bf 13}, 032503 (2006).

\bibitem{lin1} M.~B\'{e}coulet, F.~Orain, P.~Maget, N.~Mellet, X.~Garbet, E.~Nardon, G.T.A.~Huysmans, T.~Caspar, A.~Loarte,  P.~Cayna, {\em et al.}, 
Nucl.\ Fusion {\bf 52}, 054003  (2012).

\bibitem{lin2} N.M.~Ferraro, Phys.\ Plasmas {\bf 19}, 056105  (2012).

\bibitem{lin3} F.~Orain, M.~B\'{e}coulet, G.~Dif-Pradalier, G.T.A.~Huysmans, S.~Pamela,   E.~Nardon, C.~Passeron, G.~Latu, V.~Grandgirard, A.~Fil, {\em et al.}, 
Phys.\ Plasmas {\bf 20}, 102510 (2013).

\bibitem{nl1} R. Fitzpatrick, and F.L. Waelbroeck, Phys.\ Plasmas {\bf 12}, 022307 (2005).

\bibitem{nl2} R. Fitzpatrick, Phys.\ Plasmas {\bf 25}, 042503 (2018).

\bibitem{nl3} R. Fitzpatrick, Phys.\ Plasmas {\bf 25}, 112505 (2018).

\bibitem{heyn} M.F.~Heyn, I.B.~Ivanov, S.V.~Kasilov, W.~Kernbichler, I.~Joseph, R.A.~Moyer,  and A.M.~Runov, Nucl.\ Fusion {\bf 48}, 024005 (2008).

\bibitem{fkr} H.P.~Furth,  J.~Killeen, and M.N.~Rosenbluth,  Phys.\ Fluids {\bf 6}, 459 (1963).

\bibitem{am1} R.~Fitzpatrick, R.J.~Hastie, T.J.~Martin, and C.M.~Roach, Nucl.\ Fusion {\bf 33}, 1533 (1993).

\bibitem{am2} A.H.~Glasser, Z.R.~Wang, anf J.-K.~Park, Phys.\ Plasmas {\bf 23}, 112506 (2016).

\bibitem{am3} R.~Fitzpatrick, Phys.\ Plasmas {\bf 24}, 072506 (2017).

\bibitem{kink0} S.R.~Haskey, M.J.~Lanctot, Y.Q.~Liu, C.~Paz-Soldan, J.D.~King, B.D.~Blackwell, and O.~Schmitz,  Plasma 
Phys.\ Control.\ Fusion {\bf 57}, 025015 (2015).

\bibitem{kink1} D.A.~Ryan,  Y.Q.~Liu, A.~Kirk, W.~Suttrop, B.~Dudson, M.~Dunne, R.~Fischer, J.C.~Fuchs, M.~Garcia-Munoz, B.~Kurzan, {\it et al.}, 
Plasma Phys.\ Control.\ Fusion {\bf 57}, 095008 (2015).

\bibitem{ipec} J.~K.~Park, M.J.~Schaffer, J.E.~Menard, and A.H.~Boozer, Phys.\ Rev.\ Lett.\ {\bf 99}, 195003 (2007).

\bibitem{gpec} J.K.~Park, and N.C.~Logan, Phys.\ Plasmas {\bf 24}, 032505 (2017).

\bibitem{transp} R.J.~Hawryluk, {\em Physics of Plasma Close to Thermonuclear Conditions: Vol.~1}. (Commission of the European Communities, Brussels, 1980.) 
Internal Document DUR-FU-BRU-XII/476180.

\bibitem{haz} R.D.~Hazeltine, and J.D.~Meiss, Rev.\ Mod.\ Phys.\ {\bf 121}, 1 (1985).

\bibitem{ruth} P.H.~Rutherford,  Phys.\ Fluids  {\bf 16}, 1903 (1973).

\bibitem{wesson} J.A.~Wesson, private communication (1993).

\bibitem{rffig} R.~Fitzpatrick, Phys.\ Plasmas {\bf 10}, 2304 (2003).

\bibitem{ara} G.~Ara,  B.~Basu, B.~Coppi, G.~Laval, M.N.~Rosenbluth, and B.V.~Waddell, Ann.\ Phys.\ (N.Y.) {\bf 112}, 443 (1978).

\bibitem{wat} R.~Fitzpatrick, P.G.~Watson, and F.L.~Waelbroeck, Phys.\ Plasmas {\bf 12}, 082510 (2005).

\end{thebibliography}

\appendix
\section{Linear Versus Nonlinear Tearing Mode Theory in Tokamak Plasmas}\label{appa}
The discussion in this Appendix outlines certain facts pertaining
to tearing modes in tokamak plasmas that ought to be common knowledge in the 
magnetic fusion community (but appear not to be).

Consider a conventional tokamak plasma equilibrium. To lowest order, the equilibrium is governed by force balance,
\begin{equation}\label{ea}
-\nabla p + {\bf j}\times {\bf B} \simeq {\bf 0},
\end{equation}
and
flux freezing,
\begin{equation}\label{eb}
{\bf E} + {\bf V}\times {\bf B} \simeq {\bf 0}.
\end{equation}
This is the case because the other terms in the plasma equation of motion,
(\ref{ea}), and the plasma Ohm's law, (\ref{eb}), are much
smaller in magnitude than the retained terms. (Here, $p$ is the
scalar pressure, ${\bf j}$ the current density, ${\bf B}$ the
magnetic field strength, ${\bf E}$ the electric field strength, and ${\bf V}$ the plasma velocity). If we average the full plasma equation of motion and the full Ohm's law, as well as the full continuity and energy evolution equations, over magnetic flux-surfaces
then the dominant terms in these equations are annihilated, and
we end up with a set of $1\tfrac{1}{2}$-D evolution equations,
according to which the magnetic field and plasma current
evolve on the relatively long resistive timescale, $\tau_R$,
whereas the density and temperature evolve on a somewhat
shorter transport timescale.\cite{transp}

A linear tearing mode is a helical instability of a tokamak plasma equilibrium that is related to a shear-Alfv\'{e}n wave.\cite{haz} The mode resonates with the plasma at
the so-called rational magnetic flux-surface at which the
shear-Alfv\'{e}n velocity is zero. If $q$ is the safety-factor, $m$ the poloidal mode number, and $n$ the
toroidal mode number, then the rational
flux-surface is characterized by $q=m/n$. A thin resistive layer forms
around the rational surface that permits the reconnection of magnetic flux on a much faster timescale than the global
resistive evolution timescale, $\tau_R$, resulting in the formation of a helical magnetic island chain. Let the Alfv\'{e}n time,
$\tau_A$, be the
typical timescale on which a (compressional) Alfv\'{e}n
wave traverses the plasma.
In conventional tokamak plasmas, $\tau_A\ll \tau_R$. In fact,
the magnetic Lundquist number, $S\equiv \tau_R/\tau_A$,  typically exceeds $10^{\,8}$ in present-day tokamak plasmas,
and will likely exceed $10^{\,10}$ in ITER plasmas.
 It turns out that the width of the resistive layer is typically a factor $S^{\,-2/5}$ smaller than the
plasma minor radius, whereas magnetic flux is reconnected on
the hybrid timescale $\tau_A\ll \tau_A^{2/5}\,\tau_R^{3/5}\ll \tau_R$.\cite{fkr} Note that  the
structure of the tearing mode  outside the resistive layer is simply governed by a combination of flux-freezing and perturbed force balance.

 Figure~\ref{fig14} sketches the typical plasma current and vorticity patterns in a linear tearing layer. Observe that there is
 no distinction between a magnetic X-point and a magnetic 
O-point. The reason for this is that the magnetic separatrix
of the reconnected magnetic island does not present an obstacle
to plasma motion because the linear layer is so thin that the
plasma can diffuse resistively across magnetic field-lines very rapidly. However, this is only the case as long
as the radial width of the magnetic island chain is less than the linear layer width. As soon as magnetic reconnection
at the rational surface has proceeded to such an extent that
the magnetic island width exceeds the layer width then we enter the nonlinear regime.

Figure~\ref{fig14} also sketches the
typical plasma current and vorticity patterns in the nonlinear regime. Observe that there is now a considerable distinction between an X-point and an O-point. The reason for this is that the island is sufficiently wide that the plasma cannot diffuse across it resistively sufficiently rapidly to
avoid being trapped inside the magnetic separatrix. Indeed, both the regions inside and outside the magnetic separatrix
are governed by a combination of flux-freezing and perturbed force balance, whereas the resistive
layer, within which the plasma can easily slip through the magnetic field,  is diverted onto the magnetic separatrix. Moreover, as
the island grows, the width of the separatrix layer becomes
increasing negligible with respect to the island width. It
turns out that the separatrix layer does not significantly affect the evolution of a nonlinear magnetic island chain. Indeed,
the celebrated Rutherford island width evolution equation,
which governs the evolution of the island width, is simply a
$1\tfrac{1}{2}$-D evolution equation for a helical magnetic
equilibrium localized around the rational surface.\cite{ruth}
The Alfv\'{e}n time plays no role in this evolution (any more
than it plays a role in the $1\tfrac{1}{2}$-D evolution of
the global magnetic field). Likewise, the equation that
determines the phase velocity of a nonlinear magnetic island chain (see Ref.~\onlinecite{nl2}, and references therein) is essentially an
expression of the $1\tfrac{1}{2}$-D evolution of the plasma
flow profiles across the island region. As before, the  Alfv\'{e}n time plays no role in this evolution (any more
than it plays a role in the $1\tfrac{1}{2}$-D evolution of
the global plasma flow profiles).

It follows, from the previous discussion, that the nonlinear evolution of a tearing mode in a tokamak plasma has far more in common with the $1\tfrac{1}{2}$-D
evolution of the global plasma equilibrium than it does with
conventional linear tearing mode physics. In particular, the Alfv\'{e}n time is
an irrelevant timescale in nonlinear tearing mode theory, and
is also  very much shorter than the timescales on which
physical quantities of interest actually evolve. It should be noted that linear tearing layers in present-day tokamak plasmas are sufficiently thin that by the time a tearing mode is detectable it is already in the nonlinear regime (i.e., the island width exceeds the linear layer width).\cite{wesson} It, therefore, makes very little sense to
attempt to model tearing mode evolution in tokamak plasmas using a toroidal nonlinear magnetohydrodynamical (MHD) code. The reason for this is obvious: employing  an MHD code necessarily introduces the very short Alfv\'{e}n time into the calculation,
but this timescale is actually irrelevant to the problem in hand. In fact, this is exactly the same reason that MHD codes are not usually used to reconstruct global plasma equilibria, or to model their time evolution.

The natural frequency of a (stable) tearing mode is
the helical phase velocity with which it would propagate
were it actually unstable.\cite{rfa} The natural frequency
is determined by the equilibrium plasma flow at the
rational surface. Now, a magnetic island is a helical
pattern in the magnetic field  generated by a helical current perturbation that is localized in the
vicinity of the rational surface.
Given that plasma current is predominately carried by the
electrons, it is natural to suppose that a magnetic
island chain (as well as the tearing mode perturbation
away from the rational surface)  is convected by the
electron fluid in the immediate vicinity of the rational
surface. This is indeed the case in the linear regime.\cite{ara} Of course, as a consequence of diamagnetic flows, if the island chain is
convected by the electron fluid at the rational surface then it propagates with respect to the local ion fluid. However, this is not a
problem because a linear layer is sufficiently thin that the magnetic field can diffuse through the plasma very rapidly, which implies that
the ion fluid is not tied to the magnetic structure of the island chain. The situation is very different in the nonlinear regime. 
As we have seen, the region inside the magnetic separatrix of a nonlinear magnetic island chain is governed by a combination of flux-freezing and perturbed force balance.
This implies that both the electron and the ion fluids are trapped inside the separatrix, and are, therefore,  forced to co-rotate with the island chain. There
is no such constraint outside the separatrix, so the electron and ion fluids rotate at different speeds in this region,
as a consequence of diamagnetism.  Consequently, one or other of the electron and the ion fluid rotation profiles must exhibit a strong gradient across
the separatrix. The island propagation velocity is determined by which of the two fluids is most resistant to the formation of such a gradient. 
Of course, it is the ion fluid which is more resistant because of its much greater perpendicular viscosity,\cite{nl1,wat} as well as its much larger 
neoclassical stress tensor.\cite{nl2} Hence, a nonlinear magnetic island chain is convected by the ion fluid in the vicinity of the rational
surface, because this choice of propagation speed minimizes the ion fluid velocity gradient across the separatrix.

\newpage

\begin{figure}
\includegraphics[height=5in]{fig1.pdf}
\caption{Overview of DIII-D discharge \#145380.
(a) Safety factor at  ${\mit\Psi}_N=0.95$. 
(b) $D_\alpha$ (i.e., Deuterium Balmer-alpha) signal, as well as $n=3$ current flowing in upper and lower sections of I-coil. 
(c) Pedestal (i.e., ${\mit\Psi}_N=0.94$)
electron pressure. (The red curve is the running average over 10 ms.) (d) Pedestal electron number density. The common vertical yellow bands indicate the ELM suppression windows.}\label{fig1}
\end{figure}

\begin{figure}
\includegraphics[height=5in]{fig2.pdf}
\caption{Left Panel: Contours of the equilibrium poloidal
magnetic flux in   DIII-D discharge \#145380 at time $t=2500$ ms. The scale major radius is $R_0=1.70\,{\rm m}$. The white dot indicates the magnetic axis, the white curve indicates the
last closed magnetic flux-surface, and the thick black line indicates the limiter. 
Upper-Right Panel: Safety-factor profile in DIII-D discharge \#145380 at time $t=2500$ ms. Lower-Right Panel:  Total plasma pressure profile in DIII-D discharge \#145380 at time $t=2500$ ms. } \label{fig2}
\end{figure}

\begin{figure}
\includegraphics[height=7in]{fig3.pdf}
\caption{Top Panel: The green, red, blue, and cyan curves show the electron number density ($10^{19}\,{\rm m}^{-3}$),
electron temperature (keV), (thermal) ion temperature (keV), and
 C-VI ion number density  ($10^{18}\,{\rm m}^{-3}$),  profiles, respectively,  in  DIII-D discharge \#145380 at time $t=2500$ ms. Middle Panel:  ${\bf E}\times {\bf B}$ frequency profile in  DIII-D discharge \#145380 at time $t=2500$. Bottom Panel: Perpendicular momentum diffusivity 
profile in  DIII-D discharge \#145380 at time $t=2500$ ms.
The   common vertical dotted lines indicate the location of the top
of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig3}
\end{figure}

\begin{figure}
\includegraphics[height=4in]{fig4.pdf}
\caption{Safety-factors as functions of time in  DIII-D discharge \#145380. The red, green, blue, and black curves show the safety-factors
at the magnetic axis (${\mit\Psi}_N=0.00$),
the $95\%$ flux surface (${\mit\Psi}_N=0.950$), the
effective plasma boundary for the GPEC and EPEC calculations
(${\mit\Psi}_N=0.997$), and the true plasma boundary (${\mit\Psi}_N=1.00$), respectively. The horizontal dotted lines indicate the safety-factors at the various $n=3$ rational surfaces. 
} \label{fig4}
\end{figure}

\begin{figure}
\includegraphics[height=6in]{fig5.pdf}
\caption{Top Panel: $n=3$ natural frequencies as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics.
Bottom Panel:  $n=3$ island frequencies as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics. The red, green, blue, yellow, cyan, magenta, brown, pink,
purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM suppression windows.} \label{fig5}
\end{figure}

\begin{figure}
\includegraphics[height=6in]{fig6.pdf}
\caption{Top Panel: Full  $n=3$ vacuum island widths as functions of time
in   DIII-D discharge \#145380.
Bottom Panel:  Full $n=3$ island widths as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics. The blue, yellow, cyan, magenta, brown, pink,
purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM suppression windows. The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig6}
\end{figure}

\begin{figure}
\includegraphics[height=6in]{fig7.pdf}
\caption{Top Panel: Density flattening widths associated with induced $n=3$ magnetic island  chains as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics.
Bottom Panel:  Electron temperature flattening widths associated with induced $n=3$ magnetic island chains as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics. The blue, yellow, cyan, magenta, brown, pink,
purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM suppression windows. The  horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig7}
\end{figure}

\begin{figure}
\includegraphics[height=6in]{fig8.pdf}
\caption{Top Panel: $n=3$ natural frequencies as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is coincident with the ${\bf E}\times {\bf B}$
frequency.
Bottom Panel:  $n=3$ island frequencies as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is  coincident with the ${\bf E}\times {\bf B}$
frequency. The red, green, blue, yellow, cyan, magenta, brown, pink,
purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM suppression windows.} \label{fig8}
\end{figure}

\begin{figure}
\includegraphics[height=6in]{fig9.pdf}
\caption{Top Panel: $n=3$ vacuum island widths as functions of time
in   DIII-D discharge \#145380.
Bottom Panel:  $n=3$ island widths as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is  coincident with the ${\bf E}\times {\bf B}$
frequency. The blue, yellow, cyan, magenta, brown, pink,
purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM suppression windows. The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig9}
\end{figure}

\begin{figure}
\includegraphics[height=6in]{fig10.pdf}
\caption{Top Panel: Density flattening widths associated with induced $n=3$ magnetic island  chains as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is  coincident with the ${\bf E}\times {\bf B}$
frequency.
Bottom Panel:  Electron temperature flattening widths associated with induced $n=3$ magnetic island chains as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is  coincident with the ${\bf E}\times {\bf B}$
frequency. The blue, yellow, cyan, magenta, brown, pink,
purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM suppression windows. The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$. } \label{fig10}
\end{figure}

\begin{figure}
\includegraphics[height=6in]{fig11.pdf}
\caption{Top Panel: $n=3$ natural frequencies as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics.
Bottom Panel:  $n=3$ island frequencies as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics. The black, red, green, blue, yellow, cyan, magenta,  brown, purple, and orange curves correspond to $m=4$, 5, 6, 7, 8, 9, 10,  11, 13, and 14, respectively. The yellow vertical bands indicate the ELM suppression windows. } \label{fig11}
\end{figure}

\begin{figure}
\includegraphics[height=6in]{fig12.pdf}
\caption{Top Panel: $n=3$ vacuum island widths as functions of time
in   DIII-D discharge \#145380.
Bottom Panel:  $n=3$ island widths as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics. The blue, yellow, cyan, magenta, brown, pink,
purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM suppression windows. The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig12}
\end{figure}

\begin{figure}
\includegraphics[height=6in]{fig13.pdf}
\caption{Top Panel: Density flattening widths associated with induced $n=3$ magnetic island  chains as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics.
Bottom Panel:  Electron temperature flattening widths associated with induced $n=3$ magnetic island chains as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics. The blue, yellow, cyan, magenta, brown, pink,
purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM suppression windows. The horizontal dotted lines indicate  the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig13}
\end{figure}

\begin{figure}
\includegraphics[height=4in]{fig14.pdf}
\caption{Schematic diagram showing the perturbed plasma current and vorticity patterns around the magnetic X- and O-points of a linear and a nonlinear tearing mode. The horizontal axis measures radial distance from the rational
surface, whereas the vertical axis measures distance along equilibrium magnetic field-lines. Red and blue
correspond to positive and negative current/vorticity values, respectively. (See Figs.~7 and 10 in 
Ref.~\onlinecite{rffig}.)}\label{fig14}
\end{figure}

\end{document}

### 2020-07-01 Phase/Source/Phase.h

@@ -3,7 +3,7 @@
 // #######################################################################
 // Class to calculate time evolution of magnetic island chains interacting
 // with resonant magnetic perturbation in toroidal tokamak plasma.
-// Read data from programs FLUX, NEOCLASSICAL, and GPEC.
+// Reads data from programs FLUX, NEOCLASSICAL, and GPEC.
 
 // Command line options:
 // -f INTF   - overrides INTF value from namelist file
@@ -32,7 +32,7 @@
 #define PHASE
 
 #define VERSION_MAJOR 1
-#define VERSION_MINOR 3
+#define VERSION_MINOR 4
 
 #include <stdio.h>
 #include <math.h>

### 2020-07-02 ExperimentalData/DIIID/145380/Paper/paper.tex
Updates to paper

@@
 suppression in H-mode tokamak discharges.\cite{hu} The simulations  in question make a plausible case  that the density  pump-out  phenomenon is associated with the formation of   locked (i.e., non-rotating) helical magnetic
-island chains at the bottom of the pedestal, whereas the ELM suppression phenomenon is associated with the formation of a locked helical magnetic island chain at the
+island chains at the bottom of the pedestal, whereas the ELM-suppression phenomenon is associated with the formation of a locked helical magnetic island chain at the
 top of the pedestal. The prevailing hypothesis is that such an island chain suppresses ELMs by limiting the expansion of the
@@
 in Ref.~\onlinecite{rf1} was formulated and
-used to model  RMP-induced ELM suppression experiments performed on the DIII-D tokamak, \cite{rf2}
+used to model  RMP-induced ELM-suppression experiments performed on the DIII-D tokamak, \cite{rf2}
 leading to similar conclusions to the aforementioned TM1
 studies. The primary aim of this paper is to employ this
-new model to try to account for the  $q_{95}$ ELM
-suppression windows  that are apparent when the edge safety-factor is slowly ramped in
+new model to try to account for the  $q_{95}$
+ELM-suppression windows  that are apparent when the edge safety-factor is slowly ramped in
 a particular DIII-D discharge in which an $n=3$
@@
 
-It is well-known that magnetic reconnection caused when a  (stable) tearing mode is driven by a static RMP that is resonant at a particular magnetic flux-surface in a tokamak plasma is
+It is well-known that magnetic reconnection driven when a  (stable) tearing mode interacts with a static RMP that is resonant at a particular magnetic flux-surface in a tokamak plasma is
 facilitated when the associated ``natural frequency'' is relatively small.\cite{rfa,rfb}  The natural frequency  of a  (stable) tearing mode is the
@@
 the top of the pedestal is close to zero. 
-Unfortunately, there is currently some uncertainty in the fusion community regarding the form of the natural frequency.
+However, there is currently some uncertainty in the fusion community regarding the form of the natural frequency.
 
@@
 linear tearing mode theory, a tearing mode is essentially convected by
-the local electron fluid at the resonant surface (see the discussion at the end of the Appendix).\cite{hender,cole} Hence, if the response of an H-mode tokamak plasma to an applied RMP
+the local electron fluid at the resonant surface (see the discussion in Sect.~\ref{natural}).\cite{hender,cole} Hence, if the response of an H-mode tokamak plasma to an applied RMP
 is governed by linear physics then we would expect the
@@
 According to nonlinear tearing mode theory, a tearing mode is essentially convected by
-the local ion fluid at the rational surface (again, see the discussion at the end of the Appendix).\cite{nl1,nl2,nl3}
+the local ion fluid at the rational surface (again, see the discussion in Sect.~\ref{natural}).\cite{nl1,nl2,nl3}
 In fact, if the response of an H-mode tokamak plasma to an applied RMP
@@
 
-The secondary aim of this paper is to determine which of the three aforementioned choices for the natural frequency can best account for the   $q_{95}$ ELM
-suppression windows  observed in DIII-D.
+The secondary aim of this paper is to determine which of the three aforementioned choices for the natural frequency can best account for the   $q_{95}$ 
+ELM-suppression windows  observed in DIII-D discharge \#145380.
 
 \section{Description of Theoretical Model}
-The theoretical model of the response of a tokamak plasma to an externally applied RMP that is employed in this
-paper is described in detail in Ref.~\onlinecite{rf2}. The model employs a standard asymptotic matching approch.\cite{fkr,am1,am2,am3}
+The theoretical model of the response of a tokamak plasma to an externally applied RMP that is used in this
+paper is described in detail in Ref.~\onlinecite{rf2}. The model employs a standard asymptotic matching approach.\cite{fkr,am1,am2,am3}
 According to this approach, the response of the plasma to the applied RMP is governed by a combination of flux-freezing and
@@
 approximation in which the plasma response is assumed to be vacuum-like between the various resonant surfaces. On the other hand,
-the kink response of the plasma is calculated using the {\tt GPEC} code.\cite{ipec,gpec}
+the kink response of the plasma is calculated exactly using the {\tt GPEC} code.\cite{ipec,gpec}
 
@@
 evolution of the global plasma equilibrium than it does with
-conventional linear tearing mode physics. (See the discussion in the Appendix.) In particular, the Alfv\'{e}n time is
+conventional linear tearing mode physics. (See the discussion in Sect.~\ref{general}.) In particular, the Alfv\'{e}n time is
 an irrelevant timescale in nonlinear tearing mode theory, and
@@
 \section{Modeling of DIII-D Discharge \#145380}
+\subsection{Plasma Equilibrium}
+DIII-D discharge \#145380 is an ITER Similar Shape (ISS), ELMing, H-mode discharge with a toroidal magnetic field $B_T=-1.9\,{\rm T}$ in which the
+plasma current $I_p$ is slowly ramped over a 2 s interval to scan the magnetic safety-factor.\cite{d3d,d3d2} The majority ions are Deuterium, whereas the
+minority ions are Carbon~VI.
+Figure~\ref{fig1} gives an overview of this discharge. Note that the pedestal density is relatively high ($n_{e\,{\rm ped}}\sim 3\times 10^{19}\,{\rm m}^{-3}$). 
+A static RMP is applied to the plasma by running steady $n=3$ currents through the I-coil system.\cite{icoil}
+Three windows of ELM suppression are evident: the first extends from $t=2840$--$2980$ ms; the
+second extends from $t=3320$--$3560$ ms; and the third extends from $t=3880$--$4200$ ms.
+
+Figure~\ref{fig2} shows the measured plasma equilibrium at the start of the current ramp ($t=2500$ ms). Likewise,
+Fig.~\ref{fig3} shows the measured plasma profiles at the start of the current ramp. Here, ${\mit\Psi}_N$ is a
+normalized poloidal magnetic flux defined such that the magnetic axis corresponds to ${\mit\Psi}_N=0$, 
+and the last closed magnetic flux-surface (LCFS) to ${\mit\Psi}_N=1$. The perpendicular
+diffusivity data comes from {\tt TRANSP} modelling.\cite{transp}
+
+Measured plasma equilibrium and
+plasma profile data is available every $50$ ms. The equilibrium and profile data at a given point in time is interpolated from
+the measured data. In fact, quantities that depend on the plasma equilibrium and profiles are recalculated every 1 ms.  Data from the
+{\tt GPEC} code is available every 100 ms. As before, the {\tt GPEC} data at a given point in time is interpolated from the
+available {\tt GPEC} data, and any quantity that depends on this data is recalculated every 1 ms. There is one major exception to
+the aforementioned scheme. The theoretical model used in this paper actually requires plasma equilibria and profiles that are unaffected
+by the applied RMP. However, there is clear evidence that the equilibria and the profiles (in particular) are significantly modified
+within the three ELM-suppression windows (presumably because wide magnetic island chains are driven in the pedestal). 
+Hence, we do not use the equilibrium, profile, or {\tt GPEC}, data within the three ELM-suppression windows. Instead, we
+interpolate across these windows using data taken on either side of the windows.
+
+Figure~\ref{fig4} shows the safety-factor in DIII-D discharge \#145380 as a function of time. It can be seen
+that $q_{95}\equiv q({\mit\Psi}_N=0.95)$ varies from about 4.1 at the start of the current ramp to about 3.3
+at the end. However, the safety-factor at the magnetic axis, $q_0 \equiv q({\mit\Psi}_N=0.0)$, remains approximately
+constant at about 1.0. For the sake of practicality,  the {\tt GPEC} and {\tt EPEC} calculations described in this paper ignore rational
+surfaces that lie very close to the LCFS: in other words,  surfaces that lie in the region $0.997 < {\mit\Psi}_N\leq 1.000$.
+
+Note that every quantity used in our theoretical model is derived from experimental measurements taken in DIII-D discharge \#145380, with one
+exception. The exception is the neutral particle data. Unfortunately, no neutral particle data is available for DIII-D discharge \#145380.
+Hence, we employ neutral particle data derived from a much earlier discharge (see Ref.~\onlinecite{rf2}).\cite{neutral}
+In future, data from the new {\tt LLAMA} (Lyman Alpha Measurement Apparatus) system will be available in DIII-D discharges.\cite{llama}
+Combining this data  with modeling from the SOLPS-ITER code\,\cite{solps} ought to generate sufficient information to fully determine the
+neutral particle parameters required by the {\tt EPEC} code.
+
+\subsection{Case 1: $\varpi=\varpi_{\rm nonlinear}$}
+This first case that we shall consider is that in which the natural frequency is determined by nonlinear
+tearing mode theory: in other words, the natural frequency is specified by Eq.~(\ref{e2}).
+
+The upper panel of Fig.~\ref{fig5} shows the natural frequencies of the various  $n=3$ tearing modes 
+ that are resonant in the pedestal. It can be seen that the natural frequency of the $m=11$ harmonic has its main zero crossing in the middle
+of the first ELM-suppression window. Likewise, the natural frequency of the $m=10$ harmonic has its main zero crossing in the middle of the
+second ELM-suppression window. However, the natural frequency of the $m=9$ harmonic has its main zero crossing slightly
+before the third ELM-suppression window. The lower panel of Fig.~\ref{fig5} shows the actual phase velocities of the various $n=3$
+tearing modes that are resonant in the pedestal. It can be seen that if the magnitude of the natural frequency falls below about
+$5\,{\rm krad/s}$ then the associated tearing mode locks to the RMP (i.e., its phase velocity becomes zero).
+
+\subsection{Case 2: $\varpi=\varpi_{EB}$}
+
+\subsection{Case 3: $\varpi=\varpi_{\rm linear}$}
 
@@
 
-\bibitem{nl1} R. Fitzpatrick, and F.L. Waelbroeck, Phys.\ Plasmas {\bf 12}, 022307 (2005).
+\bibitem{nl1} R.~Fitzpatrick, and F.L.~Waelbroeck, Phys.\ Plasmas {\bf 12}, 022307 (2005).
 
-\bibitem{nl2} R. Fitzpatrick, Phys.\ Plasmas {\bf 25}, 042503 (2018).
+\bibitem{nl2} R.~Fitzpatrick, Phys.\ Plasmas {\bf 25}, 042503 (2018).
 
-\bibitem{nl3} R. Fitzpatrick, Phys.\ Plasmas {\bf 25}, 112505 (2018).
+\bibitem{nl3} R.~Fitzpatrick, Phys.\ Plasmas {\bf 25}, 112505 (2018).
 
@@
 
+\bibitem{icoil} G.L.~Jackson, P.M.~Anderson, J.~Bialek, W.P.~Cary, G.L.~Campbell, A.M.~Garofalo,  R.~Hatcher, A.G.~Kellman, R.J.~La\,Haye, A.~Nagy, {\em et al.},  
+Proc.\ 30th EPS Conf.\ on Controlled Fusion and Plasma Physics. (St.\ Petersburg, Russia, 2003) CD-ROM, P-4.47.
+
 \bibitem{transp} R.J.~Hawryluk, {\em Physics of Plasma Close to Thermonuclear Conditions: Vol.~1}. (Commission of the European Communities, Brussels, 1980.) 
 Internal Document DUR-FU-BRU-XII/476180.
+
+\bibitem{neutral} P.~Monier-Garbet, K.H.~Burrell, F.L.~Hinton, J.~Kim, X.~Garbet, and R.J.~Groebner,   
+Nucl.\ Fusion  {\bf 37}, 403 (1997).
+
+\bibitem{llama} A.~Rosenthal, and F.M.~Laggner, private communication (2020).
+
+\bibitem{solps} S~Wiesen, D.~Reiter, V.~Kotov, M.~Baelmans, W.~Dekeyser, A.S.~Kukushkin, S.W.~Lisgo, R.A.~Pitts, V.~Rozhansky, G.~Saibene I.~Veselova, and S.~Voskoboynikov,
+J.\ Nucl.\ Mat.\ {\bf 468}, 480 (2015).
+
+\bibitem{gim} R.~Fitzpatrick, C.G.~Gimblett, and R.J.~Hastie, 
+Plasma Phys.\ Control.\ Fusion {\bf 34}, 161 (1992).
 
@@
 \section{Linear Versus Nonlinear Tearing Mode Theory in Tokamak Plasmas}\label{appa}
+\subsection{Introduction}
 The discussion in this Appendix outlines certain facts pertaining
@@
 
+\subsection{General Considerations}\label{general}
 Consider a conventional tokamak plasma equilibrium. To lowest order, the equilibrium is governed by force balance,
@@
 whereas the density and temperature evolve on a somewhat
-shorter transport timescale.\cite{transp}
+shorter transport timescale.\cite{transp,gim}
 
-A linear tearing mode is a helical instability of a tokamak plasma equilibrium that is related to a shear-Alfv\'{e}n wave.\cite{haz} The mode resonates with the plasma at
+A linear tearing mode is a helical instability of a tokamak plasma equilibrium that is related to a shear-Alfv\'{e}n wave.\cite{haz} The mode resonates with the equilibrium magnetic field at
 the so-called rational magnetic flux-surface at which the
@@
 Observe that there is now a considerable distinction between an X-point and an O-point.
-The reason for this is that the island is sufficiently wide that the plasma cannot diffuse across it resistively sufficiently rapidly to
+The reason for this is that the island is sufficiently wide that the plasma cannot diffuse across it resistively rapidly enough to
 avoid being trapped inside the magnetic separatrix. Indeed, both the regions inside and outside the magnetic separatrix
@@
 It should be noted that linear tearing layers in present-day tokamak plasmas are sufficiently thin that by the time a tearing mode is detectable it is already in the nonlinear regime (i.e., the island width exceeds the linear layer width).\cite{wesson} It, therefore, makes very little sense to
-attempt to model tearing mode evolution in tokamak plasmas using a toroidal nonlinear magnetohydrodynamical (MHD) code.
+attempt to model nonlinear tearing mode evolution in tokamak plasmas using a toroidal, nonlinear, MHD code.
 The reason for this is obvious: employing  an MHD code necessarily introduces the very short Alfv\'{e}n time into the calculation,
@@
 
+\subsection{Natural Frequency}\label{natural}
 The natural frequency of a (stable) tearing mode is
@@
 is no such constraint outside the separatrix, so the electron and ion fluids rotate at different speeds in this region,
-as a consequence of diamagnetism.  Consequently, one or other of the electron and the ion fluid rotation profiles must exhibit a strong gradient across
+as a consequence of diamagnetism.  It follows that one or other of the electron and the ion fluid rotation profiles must exhibit a strong gradient across
 the separatrix. The island propagation velocity is determined by which of the two fluids is most resistant to the formation of such a gradient. 
@@
 (c) Pedestal (i.e., ${\mit\Psi}_N=0.94$)
-electron pressure. (The red curve is the running average over 10 ms.) (d) Pedestal electron number density. The common vertical yellow bands indicate the ELM suppression windows.}\label{fig1}
+electron pressure. (The red curve is the running average over 10 ms.) (d) Pedestal electron number density. The common vertical yellow bands indicate the ELM-suppression windows.}\label{fig1}
 \end{figure}
@@
 effective plasma boundary for the GPEC and EPEC calculations
-(${\mit\Psi}_N=0.997$), and the true plasma boundary (${\mit\Psi}_N=1.00$), respectively. The horizontal dotted lines indicate the safety-factors at the various $n=3$ rational surfaces. 
+(${\mit\Psi}_N=0.997$), and the true plasma boundary (${\mit\Psi}_N=1.00$), respectively.
+The yellow vertical bands indicate the ELM-suppression windows.
+The horizontal dotted lines indicate the safety-factors at the various $n=3$ rational surfaces.
 } \label{fig4}
@@
 in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics. The red, green, blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM suppression windows.} \label{fig5}
+purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig5}
 \end{figure}
@@
 purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively.
-The yellow vertical bands indicate the ELM suppression windows.
+The yellow vertical bands indicate the ELM-suppression windows.
 The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig6}
@@
 purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively.
-The yellow vertical bands indicate the ELM suppression windows.
+The yellow vertical bands indicate the ELM-suppression windows.
 The  horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig7}
@@
 frequency. The red, green, blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM suppression windows.} \label{fig8}
+purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig8}
 \end{figure}
@@
 purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively.
-The yellow vertical bands indicate the ELM suppression windows.
+The yellow vertical bands indicate the ELM-suppression windows.
 The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig9}
@@
 purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively.
-The yellow vertical bands indicate the ELM suppression windows.
+The yellow vertical bands indicate the ELM-suppression windows.
 The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.
@@
 The black, red, green, blue, yellow, cyan, magenta,  brown, purple, and orange curves correspond to $m=4$, 5, 6, 7, 8, 9, 10,  11, 13, and 14, respectively.
-The yellow vertical bands indicate the ELM suppression windows.
+The yellow vertical bands indicate the ELM-suppression windows.
 } \label{fig11}
@@
 purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively.
-The yellow vertical bands indicate the ELM suppression windows.
+The yellow vertical bands indicate the ELM-suppression windows.
 The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig12}
@@
 purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively.
-The yellow vertical bands indicate the ELM suppression windows.
+The yellow vertical bands indicate the ELM-suppression windows.
 The horizontal dotted lines indicate  the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig13}

### 2020-07-05 ExperimentalData/DIIID/145380/Paper/paper.tex
First draft of 145380 paper

@@
 \documentclass[12pt,prb,aps]{revtex4-1}
-\usepackage{amsmath}
-\pdfoutput=1 
-\usepackage{graphicx}
+\usepackage {amsmath}
+\pdfoutput = 1 
+\usepackage {graphicx}
 \newcommand {\bomega}{\mbox{\boldmath$\omega$}}
@@
 
-\author{R.~Fitzpatrick}
+\author{R.~Fitzpatrick\,\footnote{rfitzp@farside.ph.utexas.edu}}
 \affiliation{Institute for Fusion Studies,  Department of Physics,  University of Texas at Austin,  Austin TX, 78712, USA}
+
+\begin{abstract}
+A toroidal asymptotic matching model of the response of a tokamak plasma to a static resonant magnetic perturbation (RMP) is used to simulate the $n=3$ RMP-induced 
+edge-localized-mode (ELM)-suppression
+windows in $q_{95}$ that are evident when the plasma current is slowly ramped in DIII-D discharge \#145380. All quantities employed in the simulation are
+derived from experimental measurements, apart from the neutral particle data. 
+Three cases are considered.
+In the first case, the natural frequencies of tearing modes resonant in the plasma are 
+determined by the ion flows at the corresponding rational surfaces, which is the prediction of nonlinear theory.
+In the second case, the natural frequencies are 
+determined by the guiding center flows at the rational surfaces.
+ In the third case, the natural frequencies   are 
+determined by the electron flows at the  rational surfaces, which is the prediction of linear theory.
+The second case gives  the best agreement between the simulations and the  experimental observations.   The third case gives the worst agreement between the simulations 
+and the  observations. The first case only leads to partial agreement between  the  simulations and the  observations. However, this lack of complete agreement
+may be a consequence of using an inaccurate guess for the neutral particle distribution in the pedestal.  
+\end{abstract}
 
@@
 Tokamak discharges operating in high-confinement mode (H-mode)\,\cite{wagner} exhibit intermittent bursts of heat and particle transport, 
-emanating from the outer regions of the plasma, that are known as ``type-I edge localized modes'' (ELMs). \cite{zohm}
+emanating from the outer regions of the plasma, that are known as  (type-I) ``edge localized modes'' (ELMs).\cite{zohm}
 It is estimated that the heat load that ELMs
@@
 massive tungsten ion influx into the plasma core, and that the erosion associated with this process will 
-unacceptably limit the lifetimes of these components. \cite{loarte} Consequently, the development of robust and effective
+unacceptably limit the lifetimes of these components.\cite{loarte} Consequently, the development of robust and effective
 methods for ELM control is a high priority for the international magnetic fusion program.
 
-The most promising method for the control of ELMs in H-mode tokamak discharges is via the application of static   ``resonant magnetic perturbations'' (RMPs).
-Complete RMP-induced ELM suppression was first demonstrated on the DIII-D tokamak.\cite{evans} Subsequently, either mitigation or compete suppression of
+The most promising method for the control of ELMs in H-mode tokamak discharges is via the application of static   ``resonant magnetic perturbations'' (RMPs). Complete RMP-induced 
+ELM suppression was first demonstrated on the DIII-D tokamak.\cite{evans} Subsequently, either mitigation or compete suppression of
 ELMs has been demonstrated on the JET,\cite{jet} ASDEX-U,\cite{asdex} KSTAR,\cite{kstar} MAST\,\cite{mast}, and EAST\,\cite{east} tokamaks.
 
-The application of a static RMP, resonant in the pedestal region (i.e., the region of strong pressure and current density gradients characteristic of the edge region of an H-mode tokamak discharge), to an H-mode tokamak discharge is observed to give rise to  two distinct phenomena.\cite{schmitz, lanctot,paz1,d158115,paz} The first of these  is the so-called ``density pump-out'', which  is characterized by a reduction in the electron number density
+The application of a static RMP, resonant in the pedestal region (i.e., the region of strong pressure and current density gradients characteristic of the edge region of an H-mode 
+tokamak discharge), to an H-mode tokamak discharge is observed to give rise to  two distinct phenomena.\cite{schmitz, lanctot,paz1,d158115,paz} The first of these  is the 
+so-called ``density pump-out'', which  is characterized by a reduction in the electron number density
 in the pedestal region that varies smoothly with the amplitude of the applied RMP,  is (usually) accompanied by a similar, but significantly smaller, reduction
@@
 
-Numerical simulations made using the cylindrical,  nonlinear, two-fluid, reduced-magneto\-hydro\-dynamical (MHD), initial-value code, TM1\,\cite{tm1,tm2,tm3} have shed considerable light on the hitherto poorly understood  physical mechanism that underlies RMP-induced ELM
-suppression in H-mode tokamak discharges.\cite{hu} The simulations  in question make a plausible case  that the density  pump-out  phenomenon is associated with the formation of   locked (i.e., non-rotating) helical magnetic
+Numerical simulations made using the cylindrical,  nonlinear, two-fluid, reduced-magneto\-hydro\-dynamical (MHD), initial-value code, TM1\,\cite{tm1,tm2,tm3} have shed considerable 
+light on the hitherto poorly understood  physical mechanism that underlies RMP-induced ELM
+suppression in H-mode tokamak discharges.\cite{hu} The simulations  in question make a plausible case  that the density  pump-out  phenomenon is associated with the formation of   
+locked (i.e., non-rotating) helical magnetic
 island chains at the bottom of the pedestal, whereas the ELM-suppression phenomenon is associated with the formation of a locked helical magnetic island chain at the
@@
 in Ref.~\onlinecite{rf1} was formulated and
-used to model  RMP-induced ELM-suppression experiments performed on the DIII-D tokamak, \cite{rf2}
+used to model  RMP-induced ELM-suppression experiments performed on the DIII-D tokamak,\cite{rf2}
 leading to similar conclusions to the aforementioned TM1
@@
 ELM-suppression windows  that are apparent when the edge safety-factor is slowly ramped in
-a particular DIII-D discharge in which an $n=3$
+a particular DIII-D discharge (\#145380) in which an $n=3$
 RMP is used to control ELMs.\cite{d3d,d3d2}
@@
 RMP-induced ELM suppression occurs when $q_{95}$ is such that the natural frequency of a tearing mode resonant  at 
-the top of the pedestal is close to zero. 
+the top of the pedestal is close to zero.\cite{d3d} 
 However, there is currently some uncertainty in the fusion community regarding the form of the natural frequency.
 
-According to
-linear tearing mode theory, a tearing mode is essentially convected by
-the local electron fluid at the resonant surface (see the discussion in Sect.~\ref{natural}).\cite{hender,cole} Hence, if the response of an H-mode tokamak plasma to an applied RMP
-is governed by linear physics then we would expect the
-natural frequency to take the form\,\cite{lin1,lin2,lin3}
-\begin{equation}
-\varpi_{\rm linear} = - n\,(\omega_E+\omega_{\ast\,e}),\label{e1}
+According to nonlinear tearing mode theory, a tearing mode is essentially convected by
+the local ion fluid at the rational surface (see the discussion in Sect.~\ref{natural}).\cite{nl1,nl2,nl3}
+In fact, if the response of an H-mode tokamak plasma to an applied RMP
+is governed by nonlinear physics then we would expect the
+natural frequency to take the form\,\cite{rf2}
+\begin{equation}\label{e2}
+\varpi_{\perp\,i} = -n\left(\omega_E +\left[1-L_{00}^{\,ii}+L_{01}^{\,ii}\left(\frac{\eta_i}{1+\eta_i}\right)\right]
+\omega_{\ast\,i}
+-\left[L_{00}^{\,iI}- L_{01}^{\,iI}\left(\frac{\eta_I}{1+\eta_I}\right)\right]\omega_{\ast\,I}\right),
 \end{equation}
@@
 \begin{align}
-\omega_E &= -\frac{d{\mit\Phi}}{d{\mit\Psi}_p},\\[0.5ex]
-\omega_{\ast\,e} &=\frac{T_e}{e}\,\frac{d\ln p_e}{d{\mit\Psi}_p}.
+\omega_E({\mit\Psi}_p) &= -\frac{d{\mit\Phi}}{d{\mit\Psi}_p},\\[0.5ex]
+\omega_{\ast\,a}({\mit\Psi}_p) &=-\frac{T_a}{Z_a\,e}\,\frac{d\ln p_a}{d{\mit\Psi}_p},\\[0.5ex]
+\eta_a({\mit\Psi}_p)&=\frac{d\ln T_a}{d\ln n_a},
 \end{align}
-Here, ${\mit\Psi}_p$ is the equilibrium poloidal magnetic
+for $a=i, I$. 
+Here,  $e$ is the magnitude of the electron charge, ${\mit\Psi}_p$  the equilibrium poloidal magnetic
 flux (divided by $2\pi$), ${\mit\Phi}({\mit\Psi}_p)$ the equilibrium scalar
-electric potential, $p_e({\mit\Psi}_p)$ the equilibrium
-electron pressure, $T_e({\mit\Psi}_p)$ the equilibrium
-electron temperature, $e$ the magnitude of the electron
-charge, and $n$ the toroidal mode number of the RMP. 
-Moreover, the right-hand side of Eq.~(\ref{e1}) is evaluated
+electric potential, and $n$ the toroidal mode number of the RMP.  Moreover, $Z_i$, $n_i({\mit\Psi}_p)$, $T_i({\mit\Psi}_p)$, and $p_i({\mit\Psi}_p)=n_i\,T_i$   are the charge number, 
+equilibrium number density, 
+equilibrium temperature, and equilibrium pressure
+of the majority (thermal) ions, respectively,
+whereas  $Z_I$, $n_I$, $T_I$, $p_I = n_I\,T_I$
+are the corresponding quantities for the impurity ions.  
+Furthermore, $L_{00}^{ii}({\mit\Psi}_p)$, $L_{01}^{ii}({\mit\Psi}_p)$,  $L_{00}^{II}({\mit\Psi}_p)$, and $L_{01}^{II}({\mit\Psi}_p)$ are neoclassical parameters that are defined
+in Sect.~B of Ref.~\onlinecite{rf2}. Note that these parameters are
+affected by charge exchange  with neutrals. 
+The right-hand side of Eq.~(\ref{e2}) is evaluated
 at the ``rational''  (i.e., resonant) magnetic flux-surface at which the
@@
 toroidal periods, respectively, of the helical magnetic island chain driven at the rational surface.
-Furthermore, ${\mit\Psi}_t({\mit\Psi}_p)$ is the equilibrium toroidal magnetic flux (divided by $2\pi$).
+Moreover, ${\mit\Psi}_t({\mit\Psi}_p)$ is the equilibrium toroidal magnetic flux (divided by $2\pi$).
 
-According to nonlinear tearing mode theory, a tearing mode is essentially convected by
-the local ion fluid at the rational surface (again, see the discussion in Sect.~\ref{natural}).\cite{nl1,nl2,nl3}
-In fact, if the response of an H-mode tokamak plasma to an applied RMP
-is governed by nonlinear physics then we would expect the
-natural frequency to take the form\,\cite{rf2}
-\begin{equation}\label{e2}
-\varpi_{\rm nonlinear} = -n\left(\omega_E +\left[1-L_{00}^{\,ii}+L_{01}^{\,ii}\left(\frac{\eta_i}{1+\eta_i}\right)\right]
-\omega_{\ast\,i}
-%\right.\nonumber\\[0.5ex]&\left.
--\left[L_{00}^{\,iI}- L_{01}^{\,iI}\left(\frac{\eta_I}{1+\eta_I}\right)\right]\omega_{\ast\,I}\right),
+A second possibility is that a tearing mode is convected by the local guiding center fluid at the rational surface,\cite{heyn,paz1}
+in which case we would expect the natural frequency to take the form 
+\begin{equation}\label{e3}
+\varpi_{\perp\, EB} =-n\,\omega_E.
+\end{equation}
+As before, the right-hand side of Eq.~(\ref{e3}) is evaluated
+at the rational magnetic flux-surface.
+
+Finally, according to
+linear tearing mode theory, a tearing mode is essentially convected by
+the local electron fluid at the resonant surface (again, see the discussion in Sect.~\ref{natural}).\cite{hender,cole} Hence, if the response of an H-mode tokamak plasma to an applied RMP
+is governed by linear physics then we would expect the
+natural frequency to take the form\,\cite{lin1,lin2,lin3}
+\begin{equation}
+\varpi_{\perp\,e} = - n\,(\omega_E+\omega_{\ast\,e}),\label{e1}
 \end{equation}
@@
 \begin{align}
-\omega_{\ast\,a}({\mit\Psi}_p) &=-\frac{T_a}{Z_a\,e}\,\frac{d\ln p_a}{d{\mit\Psi}_p},\\[0.5ex]
-\eta_a({\mit\Psi}_p)&=\frac{d\ln T_a}{d\ln n_a},
+\omega_{\ast\,e}({\mit\Psi}_p) &=\frac{T_e}{e}\,\frac{d\ln p_e}{d{\mit\Psi}_p}.
 \end{align}
-for $a=i, I$. 
-Here,  $Z_i$, $n_i({\mit\Psi}_p)$, $T_i({\mit\Psi}_p)$, and $p_i({\mit\Psi}_p)=n_i\,T_i$   are the charge number, equilibrium number density, 
-equilibrium temperature, and equilibrium pressure
-of the majority (thermal) ions, respectively,
-whereas  $Z_I$, $n_I$, $T_I$, $p_I = n_I\,T_I$
-are the corresponding quantities for the impurity ions.  
-Furthermore, $L_{00}^{ii}({\mit\Psi}_p)$, $L_{01}^{ii}({\mit\Psi}_p)$,  $L_{00}^{II}({\mit\Psi}_p)$, and $L_{01}^{II}({\mit\Psi}_p)$ are neoclassical parameters that are defined
-in Ref.~\onlinecite{rf2}. Note that these parameters are
-affected by charge exchange  with neutrals. Finally,
-as before, the right-hand side of Eq.~(\ref{e2}) is evaluated
-at the rational magnetic flux-surface.
-
-A third possibility is that a tearing mode is convected by the local guiding center fluid at the rational surface,\cite{heyn,paz1}
-in which case we would expect the natural frequency to take the form 
-\begin{equation}\label{e3}
-\varpi_{EB} =-n\,\omega_E.
-\end{equation}
-As before, the right-hand side of Eq.~(\ref{e3}) is evaluated
+ Here, $p_e({\mit\Psi}_p)$ is the equilibrium
+electron pressure, and $T_e({\mit\Psi}_p)$ the equilibrium
+electron temperature.
+Finally,
+as before, the right-hand side of Eq.~(\ref{e1}) is evaluated
 at the rational magnetic flux-surface.
@@
 produce relatively thin magnetic islands. Within the resonant regions, the plasma response is governed by nonlinear,
-as opposed to linear, two-fluid resistive MHD. This is the case because the widths of the magnetic island chains
+as opposed to linear, two-fluid resistive-MHD. This is the case because the widths of the magnetic island chains
 driven at the resonant surfaces exceed the linear layer widths (which invalidates linear theory).\cite{rf1}
@@
 approximation in which the plasma response is assumed to be vacuum-like between the various resonant surfaces. On the other hand,
-the kink response of the plasma is calculated exactly using the {\tt GPEC} code.\cite{ipec,gpec}
+the kink response of the plasma is calculated exactly using the {\tt GPEC} code.\cite{ipec,gpec} (See Sect.~A.8 of Ref.~\onlinecite{rf2}.)
 
@@
 have been better to normalize the timescales with respect to a diamagnetic timescale, in which case the Alfv\'{e}n time would have completely dropped
-out of the final system of equations.)
+out of the final system of equations. See Sect.~E in Ref.~\onlinecite{rf2}.)
 
-\section{Modeling of DIII-D Discharge \#145380}
+\section{EPEC Modeling of DIII-D Discharge \#145380}
 \subsection{Plasma Equilibrium}
-DIII-D discharge \#145380 is an ITER Similar Shape (ISS), ELMing, H-mode discharge with a toroidal magnetic field $B_T=-1.9\,{\rm T}$ in which the
-plasma current $I_p$ is slowly ramped over a 2 s interval to scan the magnetic safety-factor.\cite{d3d,d3d2} The majority ions are Deuterium, whereas the
+DIII-D discharge \#145380 is an ITER-Similar-Shape (ISS), ELMing, H-mode discharge, with a toroidal magnetic field $B_T=-1.9\,{\rm T}$, in which the
+plasma current, $I_p$, is slowly ramped over a 2 second interval in order to scan the magnetic safety-factor.\cite{d3d,d3d2} The majority ions are Deuterium, whereas the
 minority ions are Carbon~VI.
-Figure~\ref{fig1} gives an overview of this discharge. Note that the pedestal density is relatively high ($n_{e\,{\rm ped}}\sim 3\times 10^{19}\,{\rm m}^{-3}$). 
+Figure~\ref{fig1} gives an overview of DIII-D discharge \#145380. Note that the pedestal electron number density is relatively high ($n_{e\,{\rm ped}}\sim 3\times 10^{19}\,{\rm m}^{-3}$). 
 A static RMP is applied to the plasma by running steady $n=3$ currents through the I-coil system.\cite{icoil}
@@
 Fig.~\ref{fig3} shows the measured plasma profiles at the start of the current ramp. Here, ${\mit\Psi}_N$ is a
-normalized poloidal magnetic flux defined such that the magnetic axis corresponds to ${\mit\Psi}_N=0$, 
+normalized equilibrium poloidal magnetic flux defined such that the magnetic axis corresponds to ${\mit\Psi}_N=0$, 
 and the last closed magnetic flux-surface (LCFS) to ${\mit\Psi}_N=1$. The perpendicular
@@
 Measured plasma equilibrium and
-plasma profile data is available every $50$ ms. The equilibrium and profile data at a given point in time is interpolated from
-the measured data. In fact, quantities that depend on the plasma equilibrium and profiles are recalculated every 1 ms.  Data from the
-{\tt GPEC} code is available every 100 ms. As before, the {\tt GPEC} data at a given point in time is interpolated from the
-available {\tt GPEC} data, and any quantity that depends on this data is recalculated every 1 ms. There is one major exception to
+plasma profiles are available every $50$ ms. The equilibrium and profiles  at a given point in time are interpolated from
+the measured equilibria and profiles. In fact, all quantities that depend on the plasma equilibrium and profiles are recalculated every 1 ms.  Data values from the
+{\tt GPEC} code are available every 100 ms. As before, the {\tt GPEC} data values at a given point in time are interpolated from the
+available {\tt GPEC} data values, and any quantity that depends on these values is recalculated every 1 ms. There is one major exception to
 the aforementioned scheme. The theoretical model used in this paper actually requires plasma equilibria and profiles that are unaffected
 by the applied RMP. However, there is clear evidence that the equilibria and the profiles (in particular) are significantly modified
-within the three ELM-suppression windows (presumably because wide magnetic island chains are driven in the pedestal). 
+within the three ELM-suppression windows (presumably because wide magnetic island chains are driven in the pedestal). [See Fig.~1(c).]
 Hence, we do not use the equilibrium, profile, or {\tt GPEC}, data within the three ELM-suppression windows. Instead, we
@@
 at the end. However, the safety-factor at the magnetic axis, $q_0 \equiv q({\mit\Psi}_N=0.0)$, remains approximately
-constant at about 1.0. For the sake of practicality,  the {\tt GPEC} and {\tt EPEC} calculations described in this paper ignore rational
-surfaces that lie very close to the LCFS: in other words,  surfaces that lie in the region $0.997 < {\mit\Psi}_N\leq 1.000$.
+constant at about 1.0. For the sake of practicality,  the {\tt GPEC} and {\tt EPEC} calculations described in this paper ignore $n=3$ rational
+surfaces that lie very close to the LCFS: in other words,  surfaces that lie in the region $0.997 < {\mit\Psi}_N\leq 1.000$. The centers of the
+first, second, and third ELM-suppression windows correspond to $q_{95}\simeq 3.95$, 3.60, and 3.48, respectively.
 
-Note that every quantity used in our theoretical model is derived from experimental measurements taken in DIII-D discharge \#145380, with one
-exception. The exception is the neutral particle data. Unfortunately, no neutral particle data is available for DIII-D discharge \#145380.
-Hence, we employ neutral particle data derived from a much earlier discharge (see Ref.~\onlinecite{rf2}).\cite{neutral}
-In future, data from the new {\tt LLAMA} (Lyman Alpha Measurement Apparatus) system will be available in DIII-D discharges.\cite{llama}
+Note that all quantities used in our theoretical model are derived from experimental measurements taken in DIII-D discharge \#145380, with the exception of the neutral particle data. 
+Unfortunately, no neutral particle data is available for DIII-D discharge \#145380.
+Hence, we employ neutral particle data derived from a much earlier discharge (see Sect.~III.D of Ref.~\onlinecite{rf2}).\cite{neutral}
+In future, data from the new {\tt LLAMA} (Lyman Alpha Measurement Apparatus) system will be routinely available in DIII-D discharges.\cite{llama}
 Combining this data  with modeling from the SOLPS-ITER code\,\cite{solps} ought to generate sufficient information to fully determine the
-neutral particle parameters required by the {\tt EPEC} code.
+neutral particle data required by the {\tt EPEC} code.
 
-\subsection{Case 1: $\varpi=\varpi_{\rm nonlinear}$}
-This first case that we shall consider is that in which the natural frequency is determined by nonlinear
-tearing mode theory: in other words, the natural frequency is specified by Eq.~(\ref{e2}).
+\subsection{Case 1: $\varpi=\varpi_{\perp\,i}$}
+The first case that we shall consider is that in which the natural frequency is determined by the local ion fluid; 
+in other words, the natural frequency is specified by Eq.~(\ref{e2}).
 
-The upper panel of Fig.~\ref{fig5} shows the natural frequencies of the various  $n=3$ tearing modes 
- that are resonant in the pedestal. It can be seen that the natural frequency of the $m=11$ harmonic has its main zero crossing in the middle
-of the first ELM-suppression window. Likewise, the natural frequency of the $m=10$ harmonic has its main zero crossing in the middle of the
-second ELM-suppression window. However, the natural frequency of the $m=9$ harmonic has its main zero crossing slightly
-before the third ELM-suppression window. The lower panel of Fig.~\ref{fig5} shows the actual phase velocities of the various $n=3$
-tearing modes that are resonant in the pedestal. It can be seen that if the magnitude of the natural frequency falls below about
-$5\,{\rm krad/s}$ then the associated tearing mode locks to the RMP (i.e., its phase velocity becomes zero).
+The upper panel of Fig.~\ref{fig5} shows the natural frequencies, in the absence of the RMP, of the various  $n=3$ tearing modes 
+ that are resonant in the pedestal. It can be seen that the natural frequency of the $m=11$ (brown) tearing mode has its main zero-crossing in the middle
+of the first ELM-suppression window. Likewise, the natural frequency of the $m=10$ (magenta) tearing mode has its main zero-crossing in the middle of the
+second ELM-suppression window. However, the natural frequency of the $m=9$ (cyan) tearing mode  has its main zero-crossing slightly
+prior to the occurrence of the third ELM-suppression window. The lower panel of Fig.~\ref{fig5} shows the natural frequencies, in the presence of the RMP, of the various $n=3$
+tearing modes that are resonant in the pedestal. It is apparent that if the magnitude of the natural frequency in the absence of the RMP falls below about
+$5\,{\rm krad/s}$ then the associated tearing mode locks to the RMP (i.e., its true natural frequency becomes zero).
 
-\subsection{Case 2: $\varpi=\varpi_{EB}$}
+The upper panel of Fig.~\ref{fig6} shows the widths of the various vacuum magnetic island chains driven by the applied $n=3$ RMP in the pedestal region as functions of time.
+The vacuum island widths are the  expected island widths in the absence of any shielding of driven magnetic reconnection due to
+plasma flow; in other words, they are the  widths of the island chains that would be driven if all of the natural frequencies were zero. It can be seen that
+the driven magnetic island chains extend over most of the pedestal, implying a very significant degradation in pedestal energy and particle confinement due to the
+expected flattening of the density and temperature profiles across the chains. Moreover, the driven island chains at the
+bottom of the pedestal overlap, implying that the magnetic field in this region is rendered stochastic. The lower panel
+of Fig.~\ref{fig6} shows the actual widths of the various magnetic island chains driven by the applied $n=3$ RMP as functions of time. It is apparent 
+that the true island widths are generally much smaller than the vacuum island widths, as a consequence of the shielding of driven magnetic
+reconnection due to plasma flow. However, the shielding breaks down at various rational surfaces when the associated natural frequency is zero (see the lower panel of
+Fig.~\ref{fig5}). In this situation, the driven island width is similar to the vacuum island width.
 
-\subsection{Case 3: $\varpi=\varpi_{\rm linear}$}
+Figure~\ref{fig7} shows the widths of the regions of density and electron temperature flattening associated with the $n=3$ magnetic
+island chains driven by the RMP in the pedestal region as functions of time. (See Sect.~III.F in Ref.~\onlinecite{rf2}.) (The particle and energy perpendicular diffusivities are assumed to be the
+same as the momentum perpendicular diffusivity.) It can be seen that the driven magnetic island chains are generally too narrow
+to significantly flatten the density and electron temperature profiles,\cite{flat}  implying that there is actually very little degradation of the pedestal energy and particle confinement
+due to the applied RMP. 
+However, in those situations in which the shielding of driven
+magnetic reconnection due to plasma flow breaks down (i.e., the true natural frequency becomes zero), locked magnetic island chains are generated that are
+ wide enough to flatten both the density and the electron temperature profiles.
+
+ Ideally, in order to account for the
+ELM-suppression windows in DIII-D discharge \#145380, according to the standard
+hypothesis of how RMP-induced ELM-suppression operates, we require the major regions of density and temperature
+flattening to correspond to the intersections of the yellow vertical bands and the horizontal dotted lines in Fig.~\ref{fig7}. If this is the case then
+the density and temperature profiles are locally flattened at the top of the pedestal (which corresponds to
+the horizontal dotted lines) during the ELM-suppression windows (which correspond to the yellow vertical bands). It can be seen
+that the region of density and temperature flattening associated with the $m=11$ (brown) tearing mode driven by the RMP lines up fairly well with the
+first ELM-suppression window. The region of density and temperature flattening associated with the $m=10$ (magenta) tearing mode 
+lines up somewhat less well with the second ELM-suppression window. To be more exact, the region is located at the top of the pedestal,
+but occurs slightly too early. However, the 
+region of density and temperature flattening associated with the $m=9$ (cyan) tearing mode 
+lines up very poorly with the third ELM-suppression window. To be more exact, the region is not really located at the top of the pedestal, and occurs
+significantly too early. The ultimate reason for this poor alignment is that the major zero-crossing of the $m=9$ natural
+frequency in the upper panel of Fig.~\ref{fig5} does not take place within the third ELM-suppression window (unlike the
+major zero-crossings of the $m=11$ and $m=10$ natural frequencies, which do take place within the first and the second
+ELM-suppression windows, respectively).
+
+\subsection{Case 2: $\varpi=\varpi_{\perp\,EB}$}
+The second case that we shall consider is that in which the natural frequency is determined by the local guiding center fluid; 
+in other words, the natural frequency is specified by Eq.~(\ref{e3}).
+
+Figures~\ref{fig8}--\ref{fig10} show analogous data to Figs.~\ref{fig5}--\ref{fig7}, respectively. It can be seen from the
+upper panel of Fig.~\ref{fig8} that, in the absence of the RMP,  the natural frequency of the $m=11$ (brown), the $m=10$ (magenta), and the $m=9$ (cyan), tearing modes have their
+zero-crossings in the middles
+of the first, second, and third, ELM-suppression window, respectively. As before, it is clear from the lower panel of Fig.~\ref{fig8} that these tearing modes lock
+to the RMP when the magnitudes of their unperturbed natural frequencies fall below about 5 krad/s. 
+Likewise, it is apparent from Fig.~\ref{fig9} that the true island widths driven in the pedestal by the applied
+RMP are much smaller than the corresponding vacuum island widths, except when the islands lock to the RMP.
+Furthermore, according to Fig.~\ref{fig10}, the regions of density and temperature flattening associated
+with the $m=11$ (brown), the $m=10$ (magenta), and the $m=9$ (cyan), tearing modes driven by the RMP line up
+very well with the first, second, and third, ELM-suppression windows, respectively. To be more exact, the regions are located at
+the top of the pedestal, and also occur at about the correct times. Note that overlapping island chains
+are also driven at the bottom of the pedestal. We associate these chains with the density pump-out phenomenon.\cite{hu,rf2} The chains at the bottom of the pedestal are more apparent
+in this particular case than in the other two cases considered in this paper because the diamagnetic contributions to the natural frequencies at the bottom of the pedestal (which are absent
+in the present case) are comparatively large.
+
+\subsection{Case 3: $\varpi=\varpi_{\perp\,e}$}
+The final case that we shall consider is that in which the natural frequency is determined by the local electron fluid; 
+in other words, the natural frequency is specified by Eq.~(\ref{e1}).
+
+Figures~\ref{fig11}--\ref{fig13} show analogous data to Figs.~\ref{fig5}--\ref{fig7} and Figs.~\ref{fig8}--\ref{fig10}, respectively.  
+It can be seen from Fig~\ref{fig13} that there is very little correlation between the major regions of density and temperature flattening associated
+with the $n=3$ tearing modes driven by the RMP and the  ELM-suppression windows. To be more exact, the 
+regions  are not really located at the top of the pedestal, and occur at completely the wrong times.
 
 \section{Summary and Discussion}
+The toroidal asymptotic matching model of the response of a tokamak plasma to a static RMP that is described in Ref.~\onlinecite{rf2}
+has been implemented in the {\tt EPEC} code (Extended Perturbed Equilibrium Code). The {\tt EPEC} code has  been used to simulate the $n=3$ RMP-induced ELM-suppression
+windows in $q_{95}$ that are evident when the plasma current is slowly ramped in DIII-D discharge \#145380. All quantities employed in the simulation are
+derived from measurements taken in DIII-D discharge \#145380, apart from the neutral particle data (which is taken from a much earlier discharge).
+
+Three cases are considered. In the first case, the natural frequencies of (stable) $n=3$ tearing modes, resonant in the plasma, are assumed to be
+determined by the ion flows at the corresponding rational surfaces, which is the prediction of nonlinear tearing mode theory.\cite{nl1,nl2,nl3}
+In the second case, the natural frequencies of (stable) $n=3$ tearing modes, resonant in the plasma, are assumed to be
+determined by the guiding center flows at the corresponding rational surfaces.\cite{heyn,paz1} 
+In the third case, the natural frequencies of (stable) $n=3$ tearing modes, resonant in the plasma, are assumed to be
+determined by the electron flows at the corresponding rational surfaces, which is the prediction of linear tearing mode theory.\cite{lin1,lin2,lin3}
+
+The second case gives the best agreement between the {\tt EPEC} simulations and the  observations. To be more
+exact, the second case leads to the prediction that comparatively wide locked magnetic island chains, that locally flatten the density and temperature profiles, 
+ are present at the top of the pedestal during the ELM-suppression
+windows, and are absent otherwise. This prediction is in accordance with the prevailing hypothesis that ELM suppression is due to the appearance of locked
+magnetic island chains at the top of the pedestal that locally flatten the pressure profile, thereby preventing the pedestal width from growing and achieving a  
+large enough value to trigger peeling-ballooning modes.\cite{d3d}
+
+ The third case gives by far the worst agreement between the {\tt EPEC} simulations and the  observations. This lack of agreement is hardly surprising, given
+that we have no reason to suppose that the response of a tokamak plasma to an RMP is correctly described by linear tearing mode theory.\cite{rf1}
+
+The first case only leads to partial agreement between  the {\tt EPEC} simulations and the  observations. This lack of complete agreement is somewhat
+disappointing, given that the response of a tokamak plasma to an RMP ought to be correctly described by nonlinear tearing mode theory. However, according to
+nonlinear theory, the natural frequency of a tearing mode resonant close to the edge of a tokamak plasma is strongly affected by charge-exchange with neutrals.\cite{rf2}
+In particular, the frequency depends on the poloidal asymmetry of the neutrals. To be more exact, if the neutrals are concentrated close to the X-point then the
+natural frequency is pulled in the electron diamagnetic direction, and vice versa.\cite{rf2} (See Sect.~IV of Ref.~\onlinecite{rf2}.) Thus, given our comparative ignorance of the neutral particle
+distribution in DIII-D discharge \#145380, it would be premature to write-off the nonlinear prediction at this stage.
 
@@
 
-\bibitem{lanctot} M.J.~Lanctot, R.J.~Buttery, J.S.~de\,Grassie, T.E.~Evans, N.M.~Ferraro, J.M.~Hanson, S.R.~Haskey,  R.A.~Moyer, R.~Nazikian, T.H.~Osborne, {\em et al.}, \\
+\bibitem{lanctot} M.J.~Lanctot, R.J.~Buttery, J.S.~de\,Grassie, T.E.~Evans, N.M.~Ferraro, J.M.~Hanson, S.R.~Haskey,  R.A.~Moyer, R.~Nazikian, T.H.~Osborne, {\em et al.}, 
 Nucl.\ Fusion {\bf 53}, 083019 (2013).
@@
 
+\bibitem{nl1} R.~Fitzpatrick, and F.L.~Waelbroeck, Phys.\ Plasmas {\bf 12}, 022307 (2005).
+
+\bibitem{nl2} R.~Fitzpatrick, Phys.\ Plasmas {\bf 25}, 042503 (2018).
+
+\bibitem{nl3} R.~Fitzpatrick, Phys.\ Plasmas {\bf 25}, 112505 (2018).
+
+\bibitem{heyn} M.F.~Heyn, I.B.~Ivanov, S.V.~Kasilov, W.~Kernbichler, I.~Joseph, R.A.~Moyer,  and A.M.~Runov, Nucl.\ Fusion {\bf 48}, 024005 (2008).
+
 \bibitem{hender} R.~Fitzpatrick, and T.C.~Hender, Phys.\ Fluids B {\bf 3}, 644 (1991).
@@
 
-\bibitem{nl1} R.~Fitzpatrick, and F.L.~Waelbroeck, Phys.\ Plasmas {\bf 12}, 022307 (2005).
-
-\bibitem{nl2} R.~Fitzpatrick, Phys.\ Plasmas {\bf 25}, 042503 (2018).
-
-\bibitem{nl3} R.~Fitzpatrick, Phys.\ Plasmas {\bf 25}, 112505 (2018).
-
-\bibitem{heyn} M.F.~Heyn, I.B.~Ivanov, S.V.~Kasilov, W.~Kernbichler, I.~Joseph, R.A.~Moyer,  and A.M.~Runov, Nucl.\ Fusion {\bf 48}, 024005 (2008).
-
 \bibitem{fkr} H.P.~Furth,  J.~Killeen, and M.N.~Rosenbluth,  Phys.\ Fluids {\bf 6}, 459 (1963).
@@
 
-\bibitem{am2} A.H.~Glasser, Z.R.~Wang, anf J.-K.~Park, Phys.\ Plasmas {\bf 23}, 112506 (2016).
+\bibitem{am2} A.H.~Glasser, Z.R.~Wang, and J.-K.~Park, Phys.\ Plasmas {\bf 23}, 112506 (2016).
 
@@
 
+\bibitem{flat} R.~Fitzpatrick,  Phys.\ Plasmas {\bf 2}, 825 (1995).
+
 \bibitem{gim} R.~Fitzpatrick, C.G.~Gimblett, and R.J.~Hastie, 
@@
 
-\bibitem{rffig} R.~Fitzpatrick, Phys.\ Plasmas {\bf 10}, 2304 (2003).
-
 \bibitem{ara} G.~Ara,  B.~Basu, B.~Coppi, G.~Laval, M.N.~Rosenbluth, and B.V.~Waddell, Ann.\ Phys.\ (N.Y.) {\bf 112}, 443 (1978).
@@
 \bibitem{wat} R.~Fitzpatrick, P.G.~Watson, and F.L.~Waelbroeck, Phys.\ Plasmas {\bf 12}, 082510 (2005).
+
+\bibitem{rffig} R.~Fitzpatrick, Phys.\ Plasmas {\bf 10}, 2304 (2003).
 
@@
 It should be noted that linear tearing layers in present-day tokamak plasmas are sufficiently thin that by the time a tearing mode is detectable it is already in the nonlinear regime (i.e., the island width exceeds the linear layer width).\cite{wesson} It, therefore, makes very little sense to
-attempt to model nonlinear tearing mode evolution in tokamak plasmas using a toroidal, nonlinear, MHD code.
+attempt to model nonlinear tearing mode evolution in tokamak plasmas using a toroidal nonlinear MHD code.
 The reason for this is obvious: employing  an MHD code necessarily introduces the very short Alfv\'{e}n time into the calculation,
@@
 \includegraphics[height=7in]{fig3.pdf}
-\caption{Top Panel: The green, red, blue, and cyan curves show the electron number density ($10^{19}\,{\rm m}^{-3}$),
+\caption{Top Panel: The red, green, blue, and cyan curves show the electron number density ($10^{19}\,{\rm m}^{-3}$),
 electron temperature (keV), (thermal) ion temperature (keV), and
- C-VI ion number density  ($10^{18}\,{\rm m}^{-3}$),  profiles, respectively,  in  DIII-D discharge \#145380 at time $t=2500$ ms.
-Middle Panel:  ${\bf E}\times {\bf B}$ frequency profile in  DIII-D discharge \#145380 at time $t=2500$.
-Bottom Panel: Perpendicular momentum diffusivity
+ C-VI ion number density  ($10^{18}\,{\rm m}^{-3}$)  profiles, respectively,  in  DIII-D discharge \#145380 at time $t=2500$ ms. Middle Panel:  
+ ${\bf E}\times {\bf B}$ frequency profile in  DIII-D discharge \#145380 at time $t=2500$. Bottom Panel: Perpendicular momentum diffusivity 
 profile in  DIII-D discharge \#145380 at time $t=2500$ ms.
@@
 effective plasma boundary for the GPEC and EPEC calculations
-(${\mit\Psi}_N=0.997$), and the true plasma boundary (${\mit\Psi}_N=1.00$), respectively.
-The yellow vertical bands indicate the ELM-suppression windows.
-The horizontal dotted lines indicate the safety-factors at the various $n=3$ rational surfaces.
-} \label{fig4}
+(${\mit\Psi}_N=0.997$), and the true plasma boundary (${\mit\Psi}_N=1.00$), respectively. The yellow vertical bands indicate the ELM-suppression windows. 
+The horizontal dotted lines indicate the safety-factors at the various $n=3$ rational surfaces.} \label{fig4}
 \end{figure}
@@
 \includegraphics[height=6in]{fig5.pdf}
-\caption{Top Panel: $n=3$ natural frequencies as functions of time
+\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of time
 in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics.
-Bottom Panel:  $n=3$ island frequencies as functions of time
+Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
 in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics. The red, green, blue, yellow, cyan, magenta, brown, pink,
@@
 in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively.
-The yellow vertical bands indicate the ELM-suppression windows.
+purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
 The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig6}
@@
 in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively.
-The yellow vertical bands indicate the ELM-suppression windows.
+purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
 The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig7}
@@
 \includegraphics[height=6in]{fig8.pdf}
-\caption{Top Panel: $n=3$ natural frequencies as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is coincident with the ${\bf E}\times {\bf B}$
+\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of time
+in   DIII-D discharge \#145380, assuming that the natural frequency is determined by the ${\bf E}\times {\bf B}$
 frequency.
-Bottom Panel:  $n=3$ island frequencies as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is  coincident with the ${\bf E}\times {\bf B}$
+Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
+in   DIII-D discharge \#145380, assuming that the natural frequency is  determined by the ${\bf E}\times {\bf B}$
 frequency. The red, green, blue, yellow, cyan, magenta, brown, pink,
@@
 Bottom Panel:  $n=3$ island widths as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is  coincident with the ${\bf E}\times {\bf B}$
+in   DIII-D discharge \#145380, assuming that the natural frequency is  determined by the ${\bf E}\times {\bf B}$
 frequency. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively.
-The yellow vertical bands indicate the ELM-suppression windows.
+purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
 The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig9}
@@
 \caption{Top Panel: Density flattening widths associated with induced $n=3$ magnetic island  chains as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is  coincident with the ${\bf E}\times {\bf B}$
+in   DIII-D discharge \#145380, assuming that the natural frequency is  determined by the ${\bf E}\times {\bf B}$
 frequency.
 Bottom Panel:  Electron temperature flattening widths associated with induced $n=3$ magnetic island chains as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is  coincident with the ${\bf E}\times {\bf B}$
+in   DIII-D discharge \#145380, assuming that the natural frequency is determined by the ${\bf E}\times {\bf B}$
 frequency. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively.
-The yellow vertical bands indicate the ELM-suppression windows.
-The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.
-} \label{fig10}
+purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
+The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig10}
 \end{figure}
@@
 \includegraphics[height=6in]{fig11.pdf}
-\caption{Top Panel: $n=3$ natural frequencies as functions of time
+\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of time
 in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics.
-Bottom Panel:  $n=3$ island frequencies as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics.
-The black, red, green, blue, yellow, cyan, magenta,  brown, purple, and orange curves correspond to $m=4$, 5, 6, 7, 8, 9, 10,  11, 13, and 14, respectively.
-The yellow vertical bands indicate the ELM-suppression windows.
-} \label{fig11}
+Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
+in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics. The black, red, green, blue, yellow, cyan, magenta,  brown, 
+purple, and orange curves correspond to $m=4$, 5, 6, 7, 8, 9, 10,  11, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig11}
 \end{figure}
@@
 in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively.
-The yellow vertical bands indicate the ELM-suppression windows.
+purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
 The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig12}
@@
 in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively.
-The yellow vertical bands indicate the ELM-suppression windows.
+purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
 The horizontal dotted lines indicate  the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig13}

### 2020-07-11 ExperimentalData/DIIID/145380/Paper/paper.tex
First circulated version of paper
Version of paper submitted to GA

@@
 determined by the electron flows at the  rational surfaces, which is the prediction of linear theory.
-The second case gives  the best agreement between the simulations and the  experimental observations.   The third case gives the worst agreement between the simulations 
+The second case gives  the best agreement between the simulations and the  experimental observations.   The third case gives by far the worst agreement between the simulations 
 and the  observations. The first case only leads to partial agreement between  the  simulations and the  observations. However, this lack of complete agreement
@@
 Figure~\ref{fig7} shows the widths of the regions of density and electron temperature flattening associated with the $n=3$ magnetic
-island chains driven by the RMP in the pedestal region as functions of time. (See Sect.~III.F in Ref.~\onlinecite{rf2}.) (The particle and energy perpendicular diffusivities are assumed to be the
-same as the momentum perpendicular diffusivity.) It can be seen that the driven magnetic island chains are generally too narrow
-to significantly flatten the density and electron temperature profiles,\cite{flat}  implying that there is actually very little degradation of the pedestal energy and particle confinement
+island chains driven by the RMP in the pedestal region as functions of time.
+(See Sect.~III.F in Ref.~\onlinecite{rf2}.) (Note that the energy diffusivity shown in Fig.~\ref{fig3}  is used to calculate the
+critical island width for electron temperature flattening, whereas the corresponding particle diffusivity is used to calculate
+the critical island width for density flattening.\cite{flat}) It can be seen that the driven magnetic island chains are generally too narrow
+to significantly flatten the density and electron temperature profiles,  implying that there is actually very little degradation of the pedestal energy and particle confinement
 due to the applied RMP. 
@@
 the density and temperature profiles are locally flattened at the top of the pedestal (which corresponds to
-the horizontal dotted lines) during the ELM-suppression windows (which correspond to the yellow vertical bands). It can be seen
+the horizontal dotted lines) during the ELM-suppression windows (which correspond to the yellow vertical bands). (Note that the top of the pedestal
+is, somewhat arbitrarily, identified with the off-axis peak in the electron number density that is apparent in the top panel of Fig.~\ref{fig3}.) It can be seen
 that the region of density and temperature flattening associated with the $m=11$ (brown) tearing mode driven by the RMP lines up fairly well with the
@@
 This research was funded by the U.S.\ Department of Energy under contract DE-FG02-04ER-54742.
-The author would like to thank Q.M.~Hu and R.~Nazikian for providing the experimental data used in this paper.
+The author would like to thank Q.M.~Hu and R.~Nazikian for providing the experimental data used in this paper. The
+author would also like to thank J.-K.~Park and N.C.~Logan for providing guidance on how to run the {\tt GPEC} code.
+
+\section*{Data Availabity Statement}
+The data that support the findings of this study are available from the corresponding author upon reasonable request.
 
@@
 the island grows, the width of the separatrix layer becomes
-increasing negligible with respect to the island width. It
+increasing negligible with respect to the full island width. It
 turns out that the separatrix layer does not significantly affect the evolution of a nonlinear magnetic island chain. Indeed,
@@
  C-VI ion number density  ($10^{18}\,{\rm m}^{-3}$)  profiles, respectively,  in  DIII-D discharge \#145380 at time $t=2500$ ms. Middle Panel:  
- ${\bf E}\times {\bf B}$ frequency profile in  DIII-D discharge \#145380 at time $t=2500$. Bottom Panel: Perpendicular momentum diffusivity 
-profile in  DIII-D discharge \#145380 at time $t=2500$ ms.
+ ${\bf E}\times {\bf B}$ frequency profile in  DIII-D discharge \#145380 at time $t=2500$. Bottom Panel: The red, green, and blue curves show
+ the perpendicular momentum, energy, and particle diffusivity profiles, respectively, 
+ in  DIII-D discharge \#145380 at time $t=2500$ ms.
 The   common vertical dotted lines indicate the location of the top

### 2020-07-11 Neoclassical/Source/Neoclassical.h

@@ -27,6 +27,7 @@
 // 1.2 - Major rearrangement of input and output files
 // 1.3 - Added PsiNk to nFile
 // 1.4 - Added cFile and linear interpolation
+// 1.5 - Added chie and chin
 
 // ################################################################
 
@@ -34,7 +35,7 @@
 #define NEOCLASSICAL
 
 #define VERSION_MAJOR 1
-#define VERSION_MINOR 4
+#define VERSION_MINOR 5
 
 #include <stdio.h>
 #include <math.h>
@@ -146,6 +147,8 @@ class Neoclassical
 
   // Read from Inputs/cFile
   Field Chip; // Perpendicular momentum diffusivity
+  Field Chie; // Perpendicular energy   diffusivity
+  Field Chin; // Perpendicular particle diffusivity
 
   // Profile data interpolated onto equilibrium grid
   Array<double,1> n_e;    // Electron number density (m^-3)
@@ -166,6 +169,8 @@ class Neoclassical
   Array<double,1> Z_eff;  // Effective ion charge number
   Array<double,1> alpha;  // Impurity strength parameter
   Array<double,1> chip;   // Perpendicular momentum diffusivity (m^2 s^-1)
+  Array<double,1> chie;   // Perpendicular energy   diffusivity (m^2 s^-1)
+  Array<double,1> chin;   // Perpendicular particle diffusivity (m^2 s^-1)
 
   // ---------------------------
   // Rational surface parameters
@@ -210,6 +215,8 @@ class Neoclassical
   Array<double,1> rhok;       // Relative mass densities
   Array<double,1> NNk;        // Flux-surfaced-averaged majority neutral number densities
   Array<double,1> chipk;      // Perpendicular momentum diffusivities
+  Array<double,1> chiek;      // Perpendicular energy   diffusivities
+  Array<double,1> chink;      // Perpendicular particle diffusivities
 
   Array<double,1> v_T_ek;     // Electron thermal velocities
   Array<double,1> v_T_ik;     // Majority ion thermal velocities

### 2020-07-17 ExperimentalData/DIIID/145380/Paper/paper.tex
Modifications to paper

@@
 In the second case, the natural frequencies are 
-determined by the guiding center flows at the rational surfaces.
+determined by the guiding-center flows at the rational surfaces.
  In the third case, the natural frequencies   are 
@@
 
-A second possibility is that a tearing mode is convected by the local guiding center fluid at the rational surface,\cite{heyn,paz1}
+A second possibility is that a tearing mode is convected by the local guiding-center fluid at the rational surface  (again, see the discussion in Sect.~\ref{natural}),\cite{heyn,paz1}
 in which case we would expect the natural frequency to take the form 
@@
 constant at about 1.0. For the sake of practicality,  the {\tt GPEC} and {\tt EPEC} calculations described in this paper ignore $n=3$ rational
-surfaces that lie very close to the LCFS: in other words,  surfaces that lie in the region $0.997 < {\mit\Psi}_N\leq 1.000$. The centers of the
-first, second, and third ELM-suppression windows correspond to $q_{95}\simeq 3.95$, 3.60, and 3.48, respectively.
+surfaces that lie very close to the LCFS: in other words,  surfaces that lie in the region $0.997 < {\mit\Psi}_N\leq 1.000$. Let $\overline{q_{95}}\equiv 5.2060-0.4457\,t$ represent the
+least-squares linear fit to the $q_{95}$ versus time data shown in Fig.~\ref{fig4}. 
+It follows that the 
+first, second, and third ELM-suppression windows extend over the $\overline{q_{95}}$ ranges $3.88$--$3.94$, $3.62$--$3.73$,
+and $3.33$--$3.48$, respectively.
 
@@
 
-The upper panel of Fig.~\ref{fig6} shows the widths of the various vacuum magnetic island chains driven by the applied $n=3$ RMP in the pedestal region as functions of time.
+The upper panel of Fig.~\ref{fig6} shows the widths of the various vacuum magnetic island chains driven by the applied $n=3$ RMP in the pedestal region as functions of $
+\overline{q_{95}}$.
 The vacuum island widths are the  expected island widths in the absence of any shielding of driven magnetic reconnection due to
@@
 reconnection due to plasma flow. However, the shielding breaks down at various rational surfaces when the associated natural frequency is zero (see the lower panel of
-Fig.~\ref{fig5}). In this situation, the driven island width is similar to the vacuum island width.
+Fig.~\ref{fig5}). In this situation, the driven island width is similar to the vacuum island width. Note that Fig.~\ref{fig6} is similar in conception to
+Fig.~23 of Ref.~\onlinecite{wade}.
 
 Figure~\ref{fig7} shows the widths of the regions of density and electron temperature flattening associated with the $n=3$ magnetic
-island chains driven by the RMP in the pedestal region as functions of time.
-(See Sect.~III.F in Ref.~\onlinecite{rf2}.) (Note that the energy diffusivity shown in Fig.~\ref{fig3}  is used to calculate the
-critical island width for electron temperature flattening, whereas the corresponding particle diffusivity is used to calculate
+island chains driven by the RMP in the pedestal region as functions of $\overline{q_{95}}$ and time.
+(See Sect.~III.F in Ref.~\onlinecite{rf2}.) (Note that the energy diffusivity data shown in Fig.~\ref{fig3}  is used to calculate the
+critical island width for electron temperature flattening, whereas the corresponding particle diffusivity data is used to calculate
 the critical island width for density flattening.\cite{flat}) It can be seen that the driven magnetic island chains are generally too narrow
@@
 \subsection{Case 2: $\varpi=\varpi_{\perp\,EB}$}
-The second case that we shall consider is that in which the natural frequency is determined by the local guiding center fluid; 
+The second case that we shall consider is that in which the natural frequency is determined by the local guiding-center fluid; 
 in other words, the natural frequency is specified by Eq.~(\ref{e3}).
@@
 In the second case, the natural frequencies of (stable) $n=3$ tearing modes, resonant in the plasma, are assumed to be
-determined by the guiding center flows at the corresponding rational surfaces.\cite{heyn,paz1} 
+determined by the guiding-center flows at the corresponding rational surfaces.\cite{heyn,paz1} 
 In the third case, the natural frequencies of (stable) $n=3$ tearing modes, resonant in the plasma, are assumed to be
@@
 \section*{Acknowledgements}
-This research was funded by the U.S.\ Department of Energy under contract DE-FG02-04ER-54742.
 The author would like to thank Q.M.~Hu and R.~Nazikian for providing the experimental data used in this paper. The
 author would also like to thank J.-K.~Park and N.C.~Logan for providing guidance on how to run the {\tt GPEC} code.
+This research was directly funded by the U.S.\ Department of Energy, Office of Science, Office of Fusion Energy Sciences,  under contract DE-FG02-04ER54742, and
+incorporates work funded by the U.S.\ Department of Energy, Office of Science, Office of Fusion Energy Sciences, using the DIII-D National Fusion Facility, a DOE Office of Science user facility, under contract DE-FC02-04ER54698.
+
+\section*{Disclaimer} This report was prepared as an account of work sponsored by an agency of the United States Government.
+Neither the United States Government nor any agency thereof, nor any of their employees, makes any warranty, express or implied, or assumes any legal liability or responsibility for the accuracy, completeness, or usefulness of any information, apparatus, product, or process disclosed, or represents that its use would not infringe privately owned rights.
+Reference herein to any specific commercial product, process, or service by trade name, trademark, manufacturer, or otherwise does not necessarily constitute or imply its endorsement, recommendation, or favoring by the United States Government or any agency thereof.
+The views and opinions of authors expressed herein do not necessarily state or reflect those of the United States Government or any agency thereof.
 
@@
 J.\ Nucl.\ Mat.\ {\bf 468}, 480 (2015).
+
+\bibitem{wade} M.R.~Wade, R.~Nazikian, J.D.~de\,Grassie, T.E.~Evans, N.M.~Ferraro, R.A.~Moyer, D.M.~Orlov, 
+R.J.~Buttery, M.E.~Fenstermacher, A.M.~Garofalo, {\em et al.}, Nucl.\ Fusion {\bf 55}, 023002 (2015).
 
@@
 problem because a linear layer is sufficiently thin that the magnetic field can diffuse through the plasma very rapidly, which implies that
-the ion fluid is not tied to the magnetic structure of the island chain. The situation is very different in the nonlinear regime. 
+the ion fluid is not tied to the magnetic structure of the island chain.
+
+The situation is very different in the nonlinear regime. 
 As we have seen, the region inside the magnetic separatrix of a nonlinear magnetic island chain is governed by a combination of flux-freezing and perturbed force balance.
@@
 surface, because this choice of propagation speed minimizes the ion fluid velocity gradient across the separatrix.
+
+Finally, we could imagine that if the width of an island chain is neither much less than the linear layer width (which is the strict
+criterion for the validity of linear theory) nor much greater than the linear layer width (which is the strict criterion for
+the validity of nonlinear theory) then the chain lies in some sort of intermediate regime in which it is
+convected by the local guiding-center fluid (which is intermediate between the predictions of linear and nonlinear theory).
 
@@
 \includegraphics[height=6in]{fig5.pdf}
-\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of time
+\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
 in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics.
@@
 \includegraphics[height=6in]{fig6.pdf}
-\caption{Top Panel: Full  $n=3$ vacuum island widths as functions of time
+\caption{Top Panel: Full  $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time 
 in   DIII-D discharge \#145380.
@@
 \includegraphics[height=6in]{fig7.pdf}
-\caption{Top Panel: Density flattening widths associated with induced $n=3$ magnetic island  chains as functions of time
+\caption{Top Panel: Density flattening widths associated with induced $n=3$ magnetic island  chains as functions of the least-squares linear fit to $q_{95}$ versus time
 in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics.
@@
 \includegraphics[height=6in]{fig8.pdf}
-\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of time
+\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
 in   DIII-D discharge \#145380, assuming that the natural frequency is determined by the ${\bf E}\times {\bf B}$
@@
 \includegraphics[height=6in]{fig9.pdf}
-\caption{Top Panel: $n=3$ vacuum island widths as functions of time
+\caption{Top Panel: $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time
 in   DIII-D discharge \#145380.
@@
 \includegraphics[height=6in]{fig10.pdf}
-\caption{Top Panel: Density flattening widths associated with induced $n=3$ magnetic island  chains as functions of time
+\caption{Top Panel: Density flattening widths associated with induced $n=3$ magnetic island  chains as functions of the least-squares linear fit to $q_{95}$ versus time
 in   DIII-D discharge \#145380, assuming that the natural frequency is  determined by the ${\bf E}\times {\bf B}$
@@
 \includegraphics[height=6in]{fig11.pdf}
-\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of time
+\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
 in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics.
@@
 \includegraphics[height=6in]{fig12.pdf}
-\caption{Top Panel: $n=3$ vacuum island widths as functions of time
+\caption{Top Panel: $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time
 in   DIII-D discharge \#145380.
@@
 \includegraphics[height=6in]{fig13.pdf}
-\caption{Top Panel: Density flattening widths associated with induced $n=3$ magnetic island  chains as functions of time
+\caption{Top Panel: Density flattening widths associated with induced $n=3$ magnetic island  chains as functions of the least-squares linear fit to $q_{95}$ versus time
 in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics.

### 2020-07-22 ExperimentalData/DIIID/145380/Paper/paper.tex
Latest version of paper

@@
 and the  observations. The first case only leads to partial agreement between  the  simulations and the  observations. However, this lack of complete agreement
-may be a consequence of using an inaccurate guess for the neutral particle distribution in the pedestal.  
+may be a consequence of using an inaccurate assumption for the neutral particle distribution in the pedestal.  
 \end{abstract}
@@
 \end{equation}
-takes the rational value $n/m$, where $m$ is a positive integer. Here, $m$ and $n$ are the numbers of poloidal and
+takes the rational value $m/n$, where $m$ is a positive integer. Here, $m$ and $n$ are the numbers of poloidal and
 toroidal periods, respectively, of the helical magnetic island chain driven at the rational surface.
@@
 minority ions are Carbon~VI.
-Figure~\ref{fig1} gives an overview of DIII-D discharge \#145380. Note that the pedestal electron number density is relatively high ($n_{e\,{\rm ped}}\sim 3\times 10^{19}\,{\rm m}^{-3}$). 
+Figure~\ref{fig1} gives an overview of DIII-D discharge \#145380. 
 A static RMP is applied to the plasma by running steady $n=3$ currents through the I-coil system.\cite{icoil}
@@
 Measured plasma equilibrium and
-plasma profiles are available every $50$ ms. The equilibrium and profiles  at a given point in time are interpolated from
-the measured equilibria and profiles. In fact, all quantities that depend on the plasma equilibrium and profiles are recalculated every 1 ms.  Data values from the
-{\tt GPEC} code are available every 100 ms. As before, the {\tt GPEC} data values at a given point in time are interpolated from the
-available {\tt GPEC} data values, and any quantity that depends on these values is recalculated every 1 ms. There is one major exception to
+plasma profiles are reconstructed every $50$ ms. The equilibrium and profiles  at a given point in time are interpolated from
+the reconstructed equilibria and profiles. In fact, all quantities that depend on the plasma equilibrium and profiles are recalculated every 1 ms.  Data values from the
+{\tt GPEC} code are calculated every 100 ms. As before, the {\tt GPEC} data values at a given point in time are interpolated from the
+calculated {\tt GPEC} data values, and any quantity that depends on these values is recalculated every 1 ms. There is one major exception to
 the aforementioned scheme. The theoretical model used in this paper actually requires plasma equilibria and profiles that are unaffected
@@
 In future, data from the new {\tt LLAMA} (Lyman Alpha Measurement Apparatus) system will be routinely available in DIII-D discharges.\cite{llama}
-Combining this data  with modeling from the SOLPS-ITER code\,\cite{solps} ought to generate sufficient information to fully determine the
+Combining this data  with modeling from a neutral particle simulation code such as, for example, the  SOLPS-ITER code\,\cite{solps} ought to generate sufficient information to fully determine the
 neutral particle data required by the {\tt EPEC} code.
@@
 The author would like to thank Q.M.~Hu and R.~Nazikian for providing the experimental data used in this paper. The
-author would also like to thank J.-K.~Park and N.C.~Logan for providing guidance on how to run the {\tt GPEC} code.
+author would also like to thank J.-K.~Park and N.C.~Logan for providing guidance on how to run the {\tt GPEC} code. Finally, the
+author would like to thank C.~Paz-Solden and B.A.~Grierson for helpful comments during the preparation of this paper.
+
 This research was directly funded by the U.S.\ Department of Energy, Office of Science, Office of Fusion Energy Sciences,  under contract DE-FG02-04ER54742, and

### 2020-07-22 ExperimentalData/DIIID/145380/Chi/ReadData.cpp

@@ -11,127 +11,38 @@ int main ()
   double chi4[MAXSIZE];
   double chi5[MAXSIZE];
   double chi6[MAXSIZE];
-  double chi7[MAXSIZE];
 
-  printf ("Reading chiph.txt\n");
-  FILE* file = fopen ("chiph.txt", "r");
+  printf ("Reading coeff.txt\n");
+  FILE* file = fopen ("coeff.txt", "r");
 
   int I = 1;
-  while (fscanf (file, "%lf %lf %lf %lf %lf %lf %lf %lf",
+  while (fscanf (file, "%lf %lf %lf %lf %lf %lf %lf",
 		 &PsiN[I], &chi1[I], &chi2[I], &chi3[I],
-		 &chi4[I], &chi5[I], &chi6[I], &chi7[I]) == 8)
+		 &chi4[I], &chi5[I], &chi6[I]) == 7)
     {
       I++;
     }
 
   fclose (file);
-
-  for (int i = 1; i < I; i++)
-    printf ("PsiN = %11.4e  chi_perp = (%11.4e %11.4e %11.4e %11.4e %11.4e %11.4e %11.4e)\n",
-	    PsiN[i], chi1[i], chi2[i], chi3[i],
-	    chi4[i], chi5[i], chi6[i], chi7[i]);
-
-  double chi[MAXSIZE];
-  for (int i = 1; i < I; i++)
-    chi[i] = (chi1[i] + chi2[i] + chi3[i] + chi4[i] + chi5[i] + chi6[i] + chi7[i])/7.e4;
 
   PsiN[0] = 0.;
   double s0 = (PsiN[0] - PsiN[2]) * (PsiN[0] - PsiN[1]) /(PsiN[3] - PsiN[2]) /(PsiN[3] - PsiN[1]);
   double s1 = (PsiN[0] - PsiN[3]) * (PsiN[0] - PsiN[1]) /(PsiN[2] - PsiN[3]) /(PsiN[2] - PsiN[1]);
   double s2 = (PsiN[0] - PsiN[3]) * (PsiN[0] - PsiN[2]) /(PsiN[1] - PsiN[3]) /(PsiN[1] - PsiN[2]);
 
-  chi[0] = s0 * chi[3] + s1 * chi[2] + s2 * chi[1];
-  
-  PsiN[I] = 1.;
[…]

### 2020-08-12 ExperimentalData/DIIID/145380/Paper/paper.tex
Revisions to paper

@@
 The most promising method for the control of ELMs in H-mode tokamak discharges is via the application of static   ``resonant magnetic perturbations'' (RMPs). Complete RMP-induced 
-ELM suppression was first demonstrated on the DIII-D tokamak.\cite{evans} Subsequently, either mitigation or compete suppression of
+ELM suppression was first demonstrated on the DIII-D tokamak.\cite{evans} Subsequently, either mitigation or complete suppression of
 ELMs has been demonstrated on the JET,\cite{jet} ASDEX-U,\cite{asdex} KSTAR,\cite{kstar} MAST\,\cite{mast}, and EAST\,\cite{east} tokamaks.
@@
 island chains at the bottom of the pedestal, whereas the ELM-suppression phenomenon is associated with the formation of a locked helical magnetic island chain at the
-top of the pedestal. The prevailing hypothesis is that such an island chain suppresses ELMs by limiting the expansion of the
+top of the pedestal. The prevailing hypothesis is that such an island chain suppresses ELMs by limiting the radial expansion of the
 pedestal, and, thereby, preventing it from attaining a width sufficient to destabilize peeling-ballooning modes\,\cite{connor}  (which are thought to trigger ELMs).\cite{d3d}
@@
 
-Our model has been implemented in the {\tt EPEC} (Extended Perturbed Equilibrium Code) code. The name
+Our model has been implemented in the newly-developed {\tt EPEC} (Extended Perturbed Equilibrium Code) code. The name
 of this code reflects the fact that the nonlinear evolution of tearing modes in a
@@
 A static RMP is applied to the plasma by running steady $n=3$ currents through the I-coil system.\cite{icoil}
-Three windows of ELM suppression are evident: the first extends from $t=2840$--$2980$ ms; the
-second extends from $t=3320$--$3560$ ms; and the third extends from $t=3880$--$4200$ ms.
+Three windows of ELM suppression or mitigation are evident: the first (in which ELMs are mitigated, but not
+entirely suppressed) extends from $t=2840$--$2980$ ms; the
+second (in which ELM are entirely suppressed) extends from $t=3320$--$3560$ ms; and the third (in which ELMs are
+entirely suppressed) extends from $t=3880$--$4200$ ms.
 
@@
 by the applied RMP. However, there is clear evidence that the equilibria and the profiles (in particular) are significantly modified
-within the three ELM-suppression windows (presumably because wide magnetic island chains are driven in the pedestal). [See Fig.~1(c).]
-Hence, we do not use the equilibrium, profile, or {\tt GPEC}, data within the three ELM-suppression windows. Instead, we
+within the three ELM-suppression/mitigation windows (presumably because wide magnetic island chains are driven in the pedestal). [See Fig.~1(c).]
+Hence, we do not use the equilibrium, profile, or {\tt GPEC}, data within the three ELM-suppression/mitigation windows. Instead, we
 interpolate across these windows using data taken on either side of the windows.
@@
 It follows that the 
-first, second, and third ELM-suppression windows extend over the $\overline{q_{95}}$ ranges $3.88$--$3.94$, $3.62$--$3.73$,
+first, second, and third ELM-suppression/mitigation windows extend over the $\overline{q_{95}}$ ranges $3.88$--$3.94$, $3.62$--$3.73$,
 and $3.33$--$3.48$, respectively.
@@
  that are resonant in the pedestal. It can be seen that the natural frequency of the $m=11$ (brown) tearing mode has its main zero-crossing in the middle
-of the first ELM-suppression window. Likewise, the natural frequency of the $m=10$ (magenta) tearing mode has its main zero-crossing in the middle of the
-second ELM-suppression window. However, the natural frequency of the $m=9$ (cyan) tearing mode  has its main zero-crossing slightly
-prior to the occurrence of the third ELM-suppression window. The lower panel of Fig.~\ref{fig5} shows the natural frequencies, in the presence of the RMP, of the various $n=3$
+of the first ELM-suppression/mitigation window. Likewise, the natural frequency of the $m=10$ (magenta) tearing mode has its main zero-crossing in the middle of the
+second ELM-suppression/mitigation window. However, the natural frequency of the $m=9$ (cyan) tearing mode  has its main zero-crossing slightly
+prior to the occurrence of the third ELM-suppression/mitigation window. The lower panel of Fig.~\ref{fig5} shows the natural frequencies, in the presence of the RMP, of the various $n=3$
 tearing modes that are resonant in the pedestal. It is apparent that if the magnitude of the natural frequency in the absence of the RMP falls below about
@@
  Ideally, in order to account for the
-ELM-suppression windows in DIII-D discharge \#145380, according to the standard
+ELM-suppression/mitigation windows in DIII-D discharge \#145380, according to the standard
 hypothesis of how RMP-induced ELM-suppression operates, we require the major regions of density and temperature
@@
 the density and temperature profiles are locally flattened at the top of the pedestal (which corresponds to
-the horizontal dotted lines) during the ELM-suppression windows (which correspond to the yellow vertical bands). (Note that the top of the pedestal
+the horizontal dotted lines) during the ELM-suppression/mitigation windows (which correspond to the yellow vertical bands). (Note that the top of the pedestal
 is, somewhat arbitrarily, identified with the off-axis peak in the electron number density that is apparent in the top panel of Fig.~\ref{fig3}.) It can be seen
 that the region of density and temperature flattening associated with the $m=11$ (brown) tearing mode driven by the RMP lines up fairly well with the
-first ELM-suppression window. The region of density and temperature flattening associated with the $m=10$ (magenta) tearing mode 
-lines up somewhat less well with the second ELM-suppression window. To be more exact, the region is located at the top of the pedestal,
+first ELM-suppression/mitigation window. The region of density and temperature flattening associated with the $m=10$ (magenta) tearing mode 
+lines up somewhat less well with the second ELM-suppression/mitigation window. To be more exact, the region is located at the top of the pedestal,
 but occurs slightly too early. However, the 
 region of density and temperature flattening associated with the $m=9$ (cyan) tearing mode 
-lines up very poorly with the third ELM-suppression window. To be more exact, the region is not really located at the top of the pedestal, and occurs
+lines up very poorly with the third ELM-suppression/mitigation window. To be more exact, the region is not really located at the top of the pedestal, and occurs
 significantly too early. The ultimate reason for this poor alignment is that the major zero-crossing of the $m=9$ natural
-frequency in the upper panel of Fig.~\ref{fig5} does not take place within the third ELM-suppression window (unlike the
+frequency in the upper panel of Fig.~\ref{fig5} does not take place within the third ELM-suppression/mitigation window (unlike the
 major zero-crossings of the $m=11$ and $m=10$ natural frequencies, which do take place within the first and the second
-ELM-suppression windows, respectively).
+ELM-suppression/mitigation windows, respectively).
 
@@
 upper panel of Fig.~\ref{fig8} that, in the absence of the RMP,  the natural frequency of the $m=11$ (brown), the $m=10$ (magenta), and the $m=9$ (cyan), tearing modes have their
-zero-crossings in the middles
-of the first, second, and third, ELM-suppression window, respectively. As before, it is clear from the lower panel of Fig.~\ref{fig8} that these tearing modes lock
+zero-crossings in the  first, second, and third, ELM-suppression/mitigation window, respectively. As before, it is clear from the lower panel of Fig.~\ref{fig8} that these tearing modes lock
 to the RMP when the magnitudes of their unperturbed natural frequencies fall below about 5 krad/s. 
@@
 with the $m=11$ (brown), the $m=10$ (magenta), and the $m=9$ (cyan), tearing modes driven by the RMP line up
-very well with the first, second, and third, ELM-suppression windows, respectively. To be more exact, the regions are located at
+very well with the first, second, and third, ELM-suppression/mitigation windows, respectively. To be more exact, the regions are located at
 the top of the pedestal, and also occur at about the correct times. Note that overlapping island chains
@@
 It can be seen from Fig~\ref{fig13} that there is very little correlation between the major regions of density and temperature flattening associated
-with the $n=3$ tearing modes driven by the RMP and the  ELM-suppression windows. To be more exact, the 
+with the $n=3$ tearing modes driven by the RMP and the  ELM-suppression/mitigation windows. To be more exact, the 
 regions  are not really located at the top of the pedestal, and occur at completely the wrong times.
@@
 The toroidal asymptotic matching model of the response of a tokamak plasma to a static RMP that is described in Ref.~\onlinecite{rf2}
-has been implemented in the {\tt EPEC} code (Extended Perturbed Equilibrium Code). The {\tt EPEC} code has  been used to simulate the $n=3$ RMP-induced ELM-suppression
+has been implemented in the newly developed {\tt EPEC} code (Extended Perturbed Equilibrium Code). The {\tt EPEC} code has  been used to simulate the $n=3$ RMP-induced ELM-suppression/mitigation
 windows in $q_{95}$ that are evident when the plasma current is slowly ramped in DIII-D discharge \#145380. All quantities employed in the simulation are
@@
 exact, the second case leads to the prediction that comparatively wide locked magnetic island chains, that locally flatten the density and temperature profiles, 
- are present at the top of the pedestal during the ELM-suppression
+ are present at the top of the pedestal during the ELM-suppression/mitigation 
 windows, and are absent otherwise. This prediction is in accordance with the prevailing hypothesis that ELM suppression is due to the appearance of locked
-magnetic island chains at the top of the pedestal that locally flatten the pressure profile, thereby preventing the pedestal width from growing and achieving a  
+magnetic island chains at the top of the pedestal that locally flatten the pressure profile, thereby preventing the pedestal width from growing radially and achieving a  
 large enough value to trigger peeling-ballooning modes.\cite{d3d}
@@
 author would also like to thank J.-K.~Park and N.C.~Logan for providing guidance on how to run the {\tt GPEC} code. Finally, the
-author would like to thank C.~Paz-Solden and B.A.~Grierson for helpful comments during the preparation of this paper.
+author would like to thank C.~Paz-Solden, B.A.~Grierson, and W.M.~Solomon for helpful comments during the preparation of this paper.
 
@@
 \bibitem{d3d2} Q.M.~Hu, R.~Nazikian, B.A.~Grierson, N.C.~Logan, D.M.~Orlov, C.~Paz-Solden, and Q.~Yu, 
-{\em The $q_{95}$ Windows of Edge-Localized-Mode Suppression using Resonant Magnetic Perturbations in the DIII-D Tokamak}, 
-Phys.\ Rev.\ Lett., to appear (2020).
+Phys.\ Rev.\ Lett.\ {\bf 125}, 045001 (2020).
 
@@
 (c) Pedestal (i.e., ${\mit\Psi}_N=0.94$)
-electron pressure. (The red curve is the running average over 10 ms.) (d) Pedestal electron number density. The common vertical yellow bands indicate the ELM-suppression windows.}\label{fig1}
+electron pressure.
+(The red curve is the running average over 10 ms.) (d) Pedestal electron number density.
+The common vertical yellow bands indicate the ELM-suppression/mitigation windows.}\label{fig1}
 \end{figure}
@@
 The   common vertical dotted lines indicate the location of the top
-of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig3}
+of the pedestal, ${\mit\Psi}_N=0.925$. In all cases, the thickness of the curves indicate the uncertainties in the measurements.} \label{fig3}
 \end{figure}
@@
 effective plasma boundary for the GPEC and EPEC calculations
-(${\mit\Psi}_N=0.997$), and the true plasma boundary (${\mit\Psi}_N=1.00$), respectively. The yellow vertical bands indicate the ELM-suppression windows. 
+(${\mit\Psi}_N=0.997$), and the true plasma boundary (${\mit\Psi}_N=1.00$), respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
 The horizontal dotted lines indicate the safety-factors at the various $n=3$ rational surfaces.} \label{fig4}
@@
 in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
+purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
 The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig6}
@@
 in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
+purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
 The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig7}
@@
 frequency. The red, green, blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig8}
+purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows.} \label{fig8}
 \end{figure}
@@
 frequency. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
+purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
 The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig9}
@@
 frequency. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
+purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
 The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig10}
@@
 in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics. The black, red, green, blue, yellow, cyan, magenta,  brown, 
-purple, and orange curves correspond to $m=4$, 5, 6, 7, 8, 9, 10,  11, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig11}
+purple, and orange curves correspond to $m=4$, 5, 6, 7, 8, 9, 10,  11, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows.} \label{fig11}
 \end{figure}
@@
 in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
+purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
 The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig12}
@@
 in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
+purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
 The horizontal dotted lines indicate  the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig13}

### 2020-08-12 ExperimentalData/DIIID/145380/Equilibrium2500/Neoclassical/Plots/Stage3/Interpolate.cpp

@@ -1,0 +1,211 @@
+#include <stdio.h>
+#include <stdlib.h>
+
+double Interpolate        (int I, double* X, double* Y, double x, int order);
+double InterpolateCubic   (double* X, double* Y, double x, int i0, int i1, int i2, int order);
+double InterpolateQuartic (double* X, double* Y, double x, int i0, int i1, int i2, int i3, int order);
+
+int main ()
+{
+  FILE* file = fopen ("../../Outputs/Stage3/profiles.txt", "r");
+
+  int    I = 512;
+  double c;
+
+  double* psi = new double [I];
+  double* ne  = new double [I];
+  double* te  = new double [I];
+  double* ti  = new double [I];
+  double* ni  = new double [I];
+  double* we  = new double [I];
+
+  for (int i = 0; i < I; i++)
+    fscanf (file, "%lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf",
+	    &psi[i], &c, &ne[i], &c, &te[i], &c, &c, &c, &ti[i], &c, &ni[i], &c, &c, &c, &we[i], &c,
+	    &c, &c, &c, &c);
+  
+  fclose (file);
+
+  printf ("\nProfile data:\n\n");
+  
+  for (int i = 0; i < I; i++)
+    printf ("PsiN = %11.4e  n_e = %11.4e  T_e = %11.4e  T_i = %11.4e  n_I = %11.4e  w_E = %11.4e\n",
+	    psi[i], ne[i], te[i], ti[i], ni[i], we[i]);
+
+  file = fopen ("145380_2500_uncertainty.txt", "r");
+
+  int J = 401;
+
+  double* psi1 = new double [J];
+  double* ne1  = new double [J];
+  double* te1  = new double [J];
+  double* ti1  = new double [J];
+  double* ni1  = new double [J];
+  double* we1  = new double [J];
+
+  for (int j = 0; j < J; j++)
+    fscanf (file, "%lf %lf %lf %lf %lf %lf",
+	    &psi1[j],  &ne1[j], &te1[j], &ni1[j], &ti1[j], &we1[j]);
+  
+  fclose (file);
+
+  for (int j = 0; j < J; j++)
+    {
[…]

### 2020-08-12 ExperimentalData/DIIID/145380/Equilibrium2500/Neoclassical/Plots/Stage3/Interpolate1.cpp

@@ -1,0 +1,171 @@
+#include <stdio.h>
+#include <stdlib.h>
+
+double Interpolate        (int I, double* X, double* Y, double x, int order);
+double InterpolateCubic   (double* X, double* Y, double x, int i0, int i1, int i2, int order);
+double InterpolateQuartic (double* X, double* Y, double x, int i0, int i1, int i2, int i3, int order);
+
+int main ()
+{
+  FILE* file = fopen ("coeff.txt", "r");
+
+  int I = 50;
+
+  double* psi   = new double [I];
+  double* chin  = new double [I];
+  double* dchin = new double [I];
+  double* chie  = new double [I];
+  double* dchie = new double [I];
+  double* chip  = new double [I];
+  double* dchip = new double [I];
+
+  for (int i = 0; i < I; i++)
+    fscanf (file, "%lf %lf %lf %lf %lf %lf %lf",
+	    &psi[i], &chin[i], &dchin[i], &chie[i], &dchie[i], &chip[i], &dchip[i]);
+  
+  fclose (file);
+
+  printf ("\nProfile data:\n\n");
+  
+  for (int i = 0; i < I; i++)
+    printf ("PsiN = %11.4e  chi_n = %11.4e  chi_e = %11.4e  chi_p = %11.4e\n",
+	    psi[i], chin[i], chie[i], chip[i]);
+
+  int J = 512;
+
+  double* psi1    = new double [J];
+  double* chin_1  = new double [J];
+  double* dchin_1 = new double [J];
+  double* chie_1  = new double [J];
+  double* dchie_1 = new double [J];
+  double* chip_1  = new double [J];
+  double* dchip_1 = new double [J];
+
+  for (int j = 0; j < J; j++)
+    psi1[j] = double (j) /double (J-1);
+  
+  for (int j = 0; j < J; j++)
+    {
+      chin_1 [j] = Interpolate (I, psi, chin,  psi1[j], 0);
+      dchin_1[j] = Interpolate (I, psi, dchin, psi1[j], 0);
+      chie_1 [j] = Interpolate (I, psi, chie,  psi1[j], 0);
+      dchie_1[j] = Interpolate (I, psi, dchie, psi1[j], 0);
[…]

### 2020-08-29 Papers/Paper2/Paper.tex
Started no-slip relaxation paper

--- 2020-07-17 ExperimentalData/DIIID/145380/Paper/paper.tex
@@
 
-\title {Modelling $q_{95}$ Windows for the Suppression of Edge Localized Modes by Resonant Magnetic Perturbations in the DIII-D Tokamak}
+\title {Modelling $q_{95}$ Windows for the Suppression of Edge Localized Modes by Resonant Magnetic Perturbations in the DIII-D Tokamak: Relaxation of the No-Slip
+Constraint}
 
@@
 
-\begin{abstract}
-A toroidal asymptotic matching model of the response of a tokamak plasma to a static resonant magnetic perturbation (RMP) is used to simulate the $n=3$ RMP-induced 
-edge-localized-mode (ELM)-suppression
-windows in $q_{95}$ that are evident when the plasma current is slowly ramped in DIII-D discharge \#145380. All quantities employed in the simulation are
-derived from experimental measurements, apart from the neutral particle data. 
-Three cases are considered.
-In the first case, the natural frequencies of tearing modes resonant in the plasma are 
-determined by the ion flows at the corresponding rational surfaces, which is the prediction of nonlinear theory.
-In the second case, the natural frequencies are 
-determined by the guiding-center flows at the rational surfaces.
- In the third case, the natural frequencies   are 
-determined by the electron flows at the  rational surfaces, which is the prediction of linear theory.
-The second case gives  the best agreement between the simulations and the  experimental observations.   The third case gives by far the worst agreement between the simulations 
-and the  observations. The first case only leads to partial agreement between  the  simulations and the  observations. However, this lack of complete agreement
-may be a consequence of using an inaccurate guess for the neutral particle distribution in the pedestal.  
-\end{abstract}
+%\begin{abstract}
+
+%\end{abstract}
 
@@
 \section{Introduction}
-Tokamak discharges operating in high-confinement mode (H-mode)\,\cite{wagner} exhibit intermittent bursts of heat and particle transport, 
-emanating from the outer regions of the plasma, that are known as  (type-I) ``edge localized modes'' (ELMs).\cite{zohm}
-It is estimated that the heat load that ELMs
-will deliver to the tungsten plasma-facing components in a reactor-scale tokamak, such as ITER, will be large enough to cause
-massive tungsten ion influx into the plasma core, and that the erosion associated with this process will 
-unacceptably limit the lifetimes of these components.\cite{loarte} Consequently, the development of robust and effective
-methods for ELM control is a high priority for the international magnetic fusion program.
 
-The most promising method for the control of ELMs in H-mode tokamak discharges is via the application of static   ``resonant magnetic perturbations'' (RMPs). Complete RMP-induced 
-ELM suppression was first demonstrated on the DIII-D tokamak.\cite{evans} Subsequently, either mitigation or compete suppression of
-ELMs has been demonstrated on the JET,\cite{jet} ASDEX-U,\cite{asdex} KSTAR,\cite{kstar} MAST\,\cite{mast}, and EAST\,\cite{east} tokamaks.
+\section{Cylindrical Model}
 
-The application of a static RMP, resonant in the pedestal region (i.e., the region of strong pressure and current density gradients characteristic of the edge region of an H-mode 
-tokamak discharge), to an H-mode tokamak discharge is observed to give rise to  two distinct phenomena.\cite{schmitz, lanctot,paz1,d158115,paz} The first of these  is the 
-so-called ``density pump-out'', which  is characterized by a reduction in the electron number density
-in the pedestal region that varies smoothly with the amplitude of the applied RMP,  is (usually) accompanied by a similar, but significantly smaller, reduction
-in the electron and ion temperatures, but  is not associated with ELM suppression. The second phenomenon is  ``ELM suppression'' itself, which 
- occurs when the amplitude of the applied RMP exceeds a certain threshold value. 
-ELM suppression  is only observed to take place when $q_{95}$ (i.e., the safety-factor on the magnetic flux-surface that encloses 95\% of the poloidal flux enclosed by
-the last closed flux-surface) takes values that lie in certain narrow windows. \cite{paz1,d158115}
+\section{Toroidal Model}
 
-Numerical simulations made using the cylindrical,  nonlinear, two-fluid, reduced-magneto\-hydro\-dynamical (MHD), initial-value code, TM1\,\cite{tm1,tm2,tm3} have shed considerable 
-light on the hitherto poorly understood  physical mechanism that underlies RMP-induced ELM
-suppression in H-mode tokamak discharges.\cite{hu} The simulations  in question make a plausible case  that the density  pump-out  phenomenon is associated with the formation of   
-locked (i.e., non-rotating) helical magnetic
-island chains at the bottom of the pedestal, whereas the ELM-suppression phenomenon is associated with the formation of a locked helical magnetic island chain at the
-top of the pedestal. The prevailing hypothesis is that such an island chain suppresses ELMs by limiting the expansion of the
-pedestal, and, thereby, preventing it from attaining a width sufficient to destabilize peeling-ballooning modes\,\cite{connor}  (which are thought to trigger ELMs).\cite{d3d}
-
-Recently, a toroidal generalization of the 
-cylindrical asymptotic matching model presented
-in Ref.~\onlinecite{rf1} was formulated and
-used to model  RMP-induced ELM-suppression experiments performed on the DIII-D tokamak,\cite{rf2}
-leading to similar conclusions to the aforementioned TM1
-studies. The primary aim of this paper is to employ this
-new model to try to account for the  $q_{95}$
-ELM-suppression windows  that are apparent when the edge safety-factor is slowly ramped in
-a particular DIII-D discharge (\#145380) in which an $n=3$
-RMP is used to control ELMs.\cite{d3d,d3d2}
-
-It is well-known that magnetic reconnection driven when a  (stable) tearing mode interacts with a static RMP that is resonant at a particular magnetic flux-surface in a tokamak plasma is
-facilitated when the associated ``natural frequency'' is relatively small.\cite{rfa,rfb}  The natural frequency  of a  (stable) tearing mode is the
-helical phase velocity that the mode would possess were it naturally unstable (in the absence of the RMP).  Driven magnetic reconnection leads to the
-formation of a locked magnetic island chain at the resonant surface in question. 
-Hence, the prevailing hypothesis is that a $q_{95}$ window for
-RMP-induced ELM suppression occurs when $q_{95}$ is such that the natural frequency of a tearing mode resonant  at 
-the top of the pedestal is close to zero.\cite{d3d} 
-However, there is currently some uncertainty in the fusion community regarding the form of the natural frequency.
-
-According to nonlinear tearing mode theory, a tearing mode is essentially convected by
-the local ion fluid at the rational surface (see the discussion in Sect.~\ref{natural}).\cite{nl1,nl2,nl3}
-In fact, if the response of an H-mode tokamak plasma to an applied RMP
-is governed by nonlinear physics then we would expect the
-natural frequency to take the form\,\cite{rf2}
-\begin{equation}\label{e2}
-\varpi_{\perp\,i} = -n\left(\omega_E +\left[1-L_{00}^{\,ii}+L_{01}^{\,ii}\left(\frac{\eta_i}{1+\eta_i}\right)\right]
-\omega_{\ast\,i}
--\left[L_{00}^{\,iI}- L_{01}^{\,iI}\left(\frac{\eta_I}{1+\eta_I}\right)\right]\omega_{\ast\,I}\right),
-\end{equation}
-where
-\begin{align}
-\omega_E({\mit\Psi}_p) &= -\frac{d{\mit\Phi}}{d{\mit\Psi}_p},\\[0.5ex]
-\omega_{\ast\,a}({\mit\Psi}_p) &=-\frac{T_a}{Z_a\,e}\,\frac{d\ln p_a}{d{\mit\Psi}_p},\\[0.5ex]
-\eta_a({\mit\Psi}_p)&=\frac{d\ln T_a}{d\ln n_a},
-\end{align}
-for $a=i, I$. 
-Here,  $e$ is the magnitude of the electron charge, ${\mit\Psi}_p$  the equilibrium poloidal magnetic
-flux (divided by $2\pi$), ${\mit\Phi}({\mit\Psi}_p)$ the equilibrium scalar
-electric potential, and $n$ the toroidal mode number of the RMP.  Moreover, $Z_i$, $n_i({\mit\Psi}_p)$, $T_i({\mit\Psi}_p)$, and $p_i({\mit\Psi}_p)=n_i\,T_i$   are the charge number, 
-equilibrium number density, 
-equilibrium temperature, and equilibrium pressure
-of the majority (thermal) ions, respectively,
-whereas  $Z_I$, $n_I$, $T_I$, $p_I = n_I\,T_I$
-are the corresponding quantities for the impurity ions.  
-Furthermore, $L_{00}^{ii}({\mit\Psi}_p)$, $L_{01}^{ii}({\mit\Psi}_p)$,  $L_{00}^{II}({\mit\Psi}_p)$, and $L_{01}^{II}({\mit\Psi}_p)$ are neoclassical parameters that are defined
-in Sect.~B of Ref.~\onlinecite{rf2}. Note that these parameters are
-affected by charge exchange  with neutrals. 
-The right-hand side of Eq.~(\ref{e2}) is evaluated
-at the ``rational''  (i.e., resonant) magnetic flux-surface at which the
-safety-factor
-\begin{equation}
-q({\mit\Psi}_p)= \frac{d{\mit\Psi}_t}{d{\mit\Psi}_p},
-\end{equation}
-takes the rational value $n/m$, where $m$ is a positive integer. Here, $m$ and $n$ are the numbers of poloidal and
-toroidal periods, respectively, of the helical magnetic island chain driven at the rational surface.
-Moreover, ${\mit\Psi}_t({\mit\Psi}_p)$ is the equilibrium toroidal magnetic flux (divided by $2\pi$).
-
-A second possibility is that a tearing mode is convected by the local guiding-center fluid at the rational surface  (again, see the discussion in Sect.~\ref{natural}),\cite{heyn,paz1}
-in which case we would expect the natural frequency to take the form 
-\begin{equation}\label{e3}
-\varpi_{\perp\, EB} =-n\,\omega_E.
-\end{equation}
-As before, the right-hand side of Eq.~(\ref{e3}) is evaluated
-at the rational magnetic flux-surface.
-
-Finally, according to
-linear tearing mode theory, a tearing mode is essentially convected by
-the local electron fluid at the resonant surface (again, see the discussion in Sect.~\ref{natural}).\cite{hender,cole} Hence, if the response of an H-mode tokamak plasma to an applied RMP
-is governed by linear physics then we would expect the
-natural frequency to take the form\,\cite{lin1,lin2,lin3}
-\begin{equation}
-\varpi_{\perp\,e} = - n\,(\omega_E+\omega_{\ast\,e}),\label{e1}
-\end{equation}
-where
-\begin{align}
-\omega_{\ast\,e}({\mit\Psi}_p) &=\frac{T_e}{e}\,\frac{d\ln p_e}{d{\mit\Psi}_p}.
-\end{align}
- Here, $p_e({\mit\Psi}_p)$ is the equilibrium
-electron pressure, and $T_e({\mit\Psi}_p)$ the equilibrium
-electron temperature.
-Finally,
-as before, the right-hand side of Eq.~(\ref{e1}) is evaluated
-at the rational magnetic flux-surface.
-
-The secondary aim of this paper is to determine which of the three aforementioned choices for the natural frequency can best account for the   $q_{95}$ 
-ELM-suppression windows  observed in DIII-D discharge \#145380.
-
-\section{Description of Theoretical Model}
-The theoretical model of the response of a tokamak plasma to an externally applied RMP that is used in this
-paper is described in detail in Ref.~\onlinecite{rf2}. The model employs a standard asymptotic matching approach.\cite{fkr,am1,am2,am3}
-According to this approach, the response of the plasma to the applied RMP is governed by a combination of flux-freezing and
-perturbed force balance (this combination is often referred to as ``marginally-stable ideal-MHD", which is a misnomer because MHD {\em per se}\/ plays no
-role) everywhere in the plasma apart from a number of relatively narrow (in the radial direction) regions in which the applied
-perturbation resonates with the equilibrium magnetic field. Magnetic reconnection can take place within the resonant regions to
-produce relatively thin magnetic islands. Within the resonant regions, the plasma response is governed by nonlinear,
-as opposed to linear, two-fluid resistive-MHD. This is the case because the widths of the magnetic island chains
-driven at the resonant surfaces exceed the linear layer widths (which invalidates linear theory).\cite{rf1}
-Thus, when employing the asymptotic matching approach, the equations of flux-freezing and perturbed force balance
-are solved in the so-called ``outer region'' that comprises most of the plasma (and the surrounding vacuum), the equations of 
-nonlinear two-fluid resistive-MHD are solved in the various resonant layers that constitute the so-called ``inner region'', and the two
-sets of solutions are then asymptotically matched to one another.
-
-A toroidal tokamak equilibrium exhibits two distinct types of response to an applied RMP.\cite{paz1,kink0,kink1}
-The first of these is known as the ``tearing response''---this is a non-ideal-MHD response that is associated with the
-formation of current sheets and magnetic island chains at various resonant surfaces within the plasma. The second
-response type is known as the ``kink response''---this is an edge-localized ideal-MHD response that is associated
-with coupling to a stable non-resonant kink mode. For the case of the tearing response, our model employs an
-approximation in which the plasma response is assumed to be vacuum-like between the various resonant surfaces. On the other hand,
-the kink response of the plasma is calculated exactly using the {\tt GPEC} code.\cite{ipec,gpec} (See Sect.~A.8 of Ref.~\onlinecite{rf2}.)
-
-Our model has been implemented in the {\tt EPEC} (Extended Perturbed Equilibrium Code) code. The name
-of this code reflects the fact that the nonlinear evolution of tearing modes in a
-tokamak plasma has far more in common with the $1\tfrac{1}{2}$-D
-evolution of the global plasma equilibrium than it does with
-conventional linear tearing mode physics. (See the discussion in Sect.~\ref{general}.) In particular, the Alfv\'{e}n time is
-an irrelevant timescale in nonlinear tearing mode theory, and
-is also  very much shorter than the timescales on which
-physical quantities of interest actually evolve. (Note that all timescales are normalized to the Alfv\'{e}n time
-in Ref.~\onlinecite{rf2}. However, this is just a matter of convention. With the benefit of hindsight, it would
-have been better to normalize the timescales with respect to a diamagnetic timescale, in which case the Alfv\'{e}n time would have completely dropped
-out of the final system of equations. See Sect.~E in Ref.~\onlinecite{rf2}.)
-
-\section{EPEC Modeling of DIII-D Discharge \#145380}
-\subsection{Plasma Equilibrium}
-DIII-D discharge \#145380 is an ITER-Similar-Shape (ISS), ELMing, H-mode discharge, with a toroidal magnetic field $B_T=-1.9\,{\rm T}$, in which the
-plasma current, $I_p$, is slowly ramped over a 2 second interval in order to scan the magnetic safety-factor.\cite{d3d,d3d2} The majority ions are Deuterium, whereas the
-minority ions are Carbon~VI.
-Figure~\ref{fig1} gives an overview of DIII-D discharge \#145380. Note that the pedestal electron number density is relatively high ($n_{e\,{\rm ped}}\sim 3\times 10^{19}\,{\rm m}^{-3}$). 
-A static RMP is applied to the plasma by running steady $n=3$ currents through the I-coil system.\cite{icoil}
-Three windows of ELM suppression are evident: the first extends from $t=2840$--$2980$ ms; the
-second extends from $t=3320$--$3560$ ms; and the third extends from $t=3880$--$4200$ ms.
-
-Figure~\ref{fig2} shows the measured plasma equilibrium at the start of the current ramp ($t=2500$ ms). Likewise,
-Fig.~\ref{fig3} shows the measured plasma profiles at the start of the current ramp. Here, ${\mit\Psi}_N$ is a
-normalized equilibrium poloidal magnetic flux defined such that the magnetic axis corresponds to ${\mit\Psi}_N=0$, 
-and the last closed magnetic flux-surface (LCFS) to ${\mit\Psi}_N=1$. The perpendicular
-diffusivity data comes from {\tt TRANSP} modelling.\cite{transp}
-
-Measured plasma equilibrium and
-plasma profiles are available every $50$ ms. The equilibrium and profiles  at a given point in time are interpolated from
-the measured equilibria and profiles. In fact, all quantities that depend on the plasma equilibrium and profiles are recalculated every 1 ms.  Data values from the
-{\tt GPEC} code are available every 100 ms. As before, the {\tt GPEC} data values at a given point in time are interpolated from the
-available {\tt GPEC} data values, and any quantity that depends on these values is recalculated every 1 ms. There is one major exception to
-the aforementioned scheme. The theoretical model used in this paper actually requires plasma equilibria and profiles that are unaffected
-by the applied RMP. However, there is clear evidence that the equilibria and the profiles (in particular) are significantly modified
-within the three ELM-suppression windows (presumably because wide magnetic island chains are driven in the pedestal). [See Fig.~1(c).]
-Hence, we do not use the equilibrium, profile, or {\tt GPEC}, data within the three ELM-suppression windows. Instead, we
-interpolate across these windows using data taken on either side of the windows.
-
-Figure~\ref{fig4} shows the safety-factor in DIII-D discharge \#145380 as a function of time. It can be seen
-that $q_{95}\equiv q({\mit\Psi}_N=0.95)$ varies from about 4.1 at the start of the current ramp to about 3.3
-at the end. However, the safety-factor at the magnetic axis, $q_0 \equiv q({\mit\Psi}_N=0.0)$, remains approximately
-constant at about 1.0. For the sake of practicality,  the {\tt GPEC} and {\tt EPEC} calculations described in this paper ignore $n=3$ rational
-surfaces that lie very close to the LCFS: in other words,  surfaces that lie in the region $0.997 < {\mit\Psi}_N\leq 1.000$. Let $\overline{q_{95}}\equiv 5.2060-0.4457\,t$ represent the
-least-squares linear fit to the $q_{95}$ versus time data shown in Fig.~\ref{fig4}. 
-It follows that the 
-first, second, and third ELM-suppression windows extend over the $\overline{q_{95}}$ ranges $3.88$--$3.94$, $3.62$--$3.73$,
-and $3.33$--$3.48$, respectively.
-
-Note that all quantities used in our theoretical model are derived from experimental measurements taken in DIII-D discharge \#145380, with the exception of the neutral particle data. 
-Unfortunately, no neutral particle data is available for DIII-D discharge \#145380.
-Hence, we employ neutral particle data derived from a much earlier discharge (see Sect.~III.D of Ref.~\onlinecite{rf2}).\cite{neutral}
-In future, data from the new {\tt LLAMA} (Lyman Alpha Measurement Apparatus) system will be routinely available in DIII-D discharges.\cite{llama}
-Combining this data  with modeling from the SOLPS-ITER code\,\cite{solps} ought to generate sufficient information to fully determine the
-neutral particle data required by the {\tt EPEC} code.
-
-\subsection{Case 1: $\varpi=\varpi_{\perp\,i}$}
-The first case that we shall consider is that in which the natural frequency is determined by the local ion fluid; 
-in other words, the natural frequency is specified by Eq.~(\ref{e2}).
-
-The upper panel of Fig.~\ref{fig5} shows the natural frequencies, in the absence of the RMP, of the various  $n=3$ tearing modes 
- that are resonant in the pedestal. It can be seen that the natural frequency of the $m=11$ (brown) tearing mode has its main zero-crossing in the middle
-of the first ELM-suppression window. Likewise, the natural frequency of the $m=10$ (magenta) tearing mode has its main zero-crossing in the middle of the
-second ELM-suppression window. However, the natural frequency of the $m=9$ (cyan) tearing mode  has its main zero-crossing slightly
-prior to the occurrence of the third ELM-suppression window. The lower panel of Fig.~\ref{fig5} shows the natural frequencies, in the presence of the RMP, of the various $n=3$
-tearing modes that are resonant in the pedestal. It is apparent that if the magnitude of the natural frequency in the absence of the RMP falls below about
-$5\,{\rm krad/s}$ then the associated tearing mode locks to the RMP (i.e., its true natural frequency becomes zero).
-
-The upper panel of Fig.~\ref{fig6} shows the widths of the various vacuum magnetic island chains driven by the applied $n=3$ RMP in the pedestal region as functions of $
-\overline{q_{95}}$.
-The vacuum island widths are the  expected island widths in the absence of any shielding of driven magnetic reconnection due to
-plasma flow; in other words, they are the  widths of the island chains that would be driven if all of the natural frequencies were zero. It can be seen that
-the driven magnetic island chains extend over most of the pedestal, implying a very significant degradation in pedestal energy and particle confinement due to the
-expected flattening of the density and temperature profiles across the chains. Moreover, the driven island chains at the
-bottom of the pedestal overlap, implying that the magnetic field in this region is rendered stochastic. The lower panel
-of Fig.~\ref{fig6} shows the actual widths of the various magnetic island chains driven by the applied $n=3$ RMP as functions of time. It is apparent 
-that the true island widths are generally much smaller than the vacuum island widths, as a consequence of the shielding of driven magnetic
-reconnection due to plasma flow. However, the shielding breaks down at various rational surfaces when the associated natural frequency is zero (see the lower panel of
-Fig.~\ref{fig5}). In this situation, the driven island width is similar to the vacuum island width. Note that Fig.~\ref{fig6} is similar in conception to
-Fig.~23 of Ref.~\onlinecite{wade}.
-
-Figure~\ref{fig7} shows the widths of the regions of density and electron temperature flattening associated with the $n=3$ magnetic
-island chains driven by the RMP in the pedestal region as functions of $\overline{q_{95}}$ and time.
-(See Sect.~III.F in Ref.~\onlinecite{rf2}.) (Note that the energy diffusivity data shown in Fig.~\ref{fig3}  is used to calculate the
-critical island width for electron temperature flattening, whereas the corresponding particle diffusivity data is used to calculate
-the critical island width for density flattening.\cite{flat}) It can be seen that the driven magnetic island chains are generally too narrow
-to significantly flatten the density and electron temperature profiles,  implying that there is actually very little degradation of the pedestal energy and particle confinement
-due to the applied RMP. 
-However, in those situations in which the shielding of driven
-magnetic reconnection due to plasma flow breaks down (i.e., the true natural frequency becomes zero), locked magnetic island chains are generated that are
- wide enough to flatten both the density and the electron temperature profiles.
-
- Ideally, in order to account for the
-ELM-suppression windows in DIII-D discharge \#145380, according to the standard
-hypothesis of how RMP-induced ELM-suppression operates, we require the major regions of density and temperature
-flattening to correspond to the intersections of the yellow vertical bands and the horizontal dotted lines in Fig.~\ref{fig7}. If this is the case then
-the density and temperature profiles are locally flattened at the top of the pedestal (which corresponds to
-the horizontal dotted lines) during the ELM-suppression windows (which correspond to the yellow vertical bands). (Note that the top of the pedestal
-is, somewhat arbitrarily, identified with the off-axis peak in the electron number density that is apparent in the top panel of Fig.~\ref{fig3}.) It can be seen
-that the region of density and temperature flattening associated with the $m=11$ (brown) tearing mode driven by the RMP lines up fairly well with the
-first ELM-suppression window. The region of density and temperature flattening associated with the $m=10$ (magenta) tearing mode 
-lines up somewhat less well with the second ELM-suppression window. To be more exact, the region is located at the top of the pedestal,
-but occurs slightly too early. However, the 
-region of density and temperature flattening associated with the $m=9$ (cyan) tearing mode 
-lines up very poorly with the third ELM-suppression window. To be more exact, the region is not really located at the top of the pedestal, and occurs
-significantly too early. The ultimate reason for this poor alignment is that the major zero-crossing of the $m=9$ natural
-frequency in the upper panel of Fig.~\ref{fig5} does not take place within the third ELM-suppression window (unlike the
-major zero-crossings of the $m=11$ and $m=10$ natural frequencies, which do take place within the first and the second
-ELM-suppression windows, respectively).
-
-\subsection{Case 2: $\varpi=\varpi_{\perp\,EB}$}
-The second case that we shall consider is that in which the natural frequency is determined by the local guiding-center fluid; 
-in other words, the natural frequency is specified by Eq.~(\ref{e3}).
-
-Figures~\ref{fig8}--\ref{fig10} show analogous data to Figs.~\ref{fig5}--\ref{fig7}, respectively. It can be seen from the
-upper panel of Fig.~\ref{fig8} that, in the absence of the RMP,  the natural frequency of the $m=11$ (brown), the $m=10$ (magenta), and the $m=9$ (cyan), tearing modes have their
-zero-crossings in the middles
-of the first, second, and third, ELM-suppression window, respectively. As before, it is clear from the lower panel of Fig.~\ref{fig8} that these tearing modes lock
-to the RMP when the magnitudes of their unperturbed natural frequencies fall below about 5 krad/s. 
-Likewise, it is apparent from Fig.~\ref{fig9} that the true island widths driven in the pedestal by the applied
-RMP are much smaller than the corresponding vacuum island widths, except when the islands lock to the RMP.
-Furthermore, according to Fig.~\ref{fig10}, the regions of density and temperature flattening associated
-with the $m=11$ (brown), the $m=10$ (magenta), and the $m=9$ (cyan), tearing modes driven by the RMP line up
-very well with the first, second, and third, ELM-suppression windows, respectively. To be more exact, the regions are located at
-the top of the pedestal, and also occur at about the correct times. Note that overlapping island chains
-are also driven at the bottom of the pedestal. We associate these chains with the density pump-out phenomenon.\cite{hu,rf2} The chains at the bottom of the pedestal are more apparent
-in this particular case than in the other two cases considered in this paper because the diamagnetic contributions to the natural frequencies at the bottom of the pedestal (which are absent
-in the present case) are comparatively large.
-
-\subsection{Case 3: $\varpi=\varpi_{\perp\,e}$}
-The final case that we shall consider is that in which the natural frequency is determined by the local electron fluid; 
-in other words, the natural frequency is specified by Eq.~(\ref{e1}).
-
-Figures~\ref{fig11}--\ref{fig13} show analogous data to Figs.~\ref{fig5}--\ref{fig7} and Figs.~\ref{fig8}--\ref{fig10}, respectively.  
-It can be seen from Fig~\ref{fig13} that there is very little correlation between the major regions of density and temperature flattening associated
-with the $n=3$ tearing modes driven by the RMP and the  ELM-suppression windows. To be more exact, the 
-regions  are not really located at the top of the pedestal, and occur at completely the wrong times.
-
-\section{Summary and Discussion}
-The toroidal asymptotic matching model of the response of a tokamak plasma to a static RMP that is described in Ref.~\onlinecite{rf2}
-has been implemented in the {\tt EPEC} code (Extended Perturbed Equilibrium Code). The {\tt EPEC} code has  been used to simulate the $n=3$ RMP-induced ELM-suppression
-windows in $q_{95}$ that are evident when the plasma current is slowly ramped in DIII-D discharge \#145380. All quantities employed in the simulation are
-derived from measurements taken in DIII-D discharge \#145380, apart from the neutral particle data (which is taken from a much earlier discharge).
-
-Three cases are considered. In the first case, the natural frequencies of (stable) $n=3$ tearing modes, resonant in the plasma, are assumed to be
-determined by the ion flows at the corresponding rational surfaces, which is the prediction of nonlinear tearing mode theory.\cite{nl1,nl2,nl3}
-In the second case, the natural frequencies of (stable) $n=3$ tearing modes, resonant in the plasma, are assumed to be
-determined by the guiding-center flows at the corresponding rational surfaces.\cite{heyn,paz1} 
-In the third case, the natural frequencies of (stable) $n=3$ tearing modes, resonant in the plasma, are assumed to be
-determined by the electron flows at the corresponding rational surfaces, which is the prediction of linear tearing mode theory.\cite{lin1,lin2,lin3}
-
-The second case gives the best agreement between the {\tt EPEC} simulations and the  observations. To be more
-exact, the second case leads to the prediction that comparatively wide locked magnetic island chains, that locally flatten the density and temperature profiles, 
- are present at the top of the pedestal during the ELM-suppression
-windows, and are absent otherwise. This prediction is in accordance with the prevailing hypothesis that ELM suppression is due to the appearance of locked
-magnetic island chains at the top of the pedestal that locally flatten the pressure profile, thereby preventing the pedestal width from growing and achieving a  
-large enough value to trigger peeling-ballooning modes.\cite{d3d}
-
- The third case gives by far the worst agreement between the {\tt EPEC} simulations and the  observations. This lack of agreement is hardly surprising, given
-that we have no reason to suppose that the response of a tokamak plasma to an RMP is correctly described by linear tearing mode theory.\cite{rf1}
-
-The first case only leads to partial agreement between  the {\tt EPEC} simulations and the  observations. This lack of complete agreement is somewhat
-disappointing, given that the response of a tokamak plasma to an RMP ought to be correctly described by nonlinear tearing mode theory. However, according to
-nonlinear theory, the natural frequency of a tearing mode resonant close to the edge of a tokamak plasma is strongly affected by charge-exchange with neutrals.\cite{rf2}
-In particular, the frequency depends on the poloidal asymmetry of the neutrals. To be more exact, if the neutrals are concentrated close to the X-point then the
-natural frequency is pulled in the electron diamagnetic direction, and vice versa.\cite{rf2} (See Sect.~IV of Ref.~\onlinecite{rf2}.) Thus, given our comparative ignorance of the neutral particle
-distribution in DIII-D discharge \#145380, it would be premature to write-off the nonlinear prediction at this stage.
+\section{Discussion and Conclusions}
 
 \section*{Acknowledgements}
-The author would like to thank Q.M.~Hu and R.~Nazikian for providing the experimental data used in this paper. The
-author would also like to thank J.-K.~Park and N.C.~Logan for providing guidance on how to run the {\tt GPEC} code.
 This research was directly funded by the U.S.\ Department of Energy, Office of Science, Office of Fusion Energy Sciences,  under contract DE-FG02-04ER54742, and
@@
 
-\bibitem{wagner} F.~Wagner, G.~Becker, K.~Behringer, D.~Campbell, A.~Eberhagen, W.~Engelhardt, G.~Fussmann, O.~Gehre, J.~Gernhardt, G.~v.~Gierke, {\it et al.}, 
-Phys.\ Rev.\ Lett.\ {\bf 49}, 1408 (1982).
+%\bibitem{rf1} R.~Fitzpatrick, Phys.\ Plasmas {\bf 27}, 042506 (2020).
 
-\bibitem{zohm} H.~Zohm, Plasma Phys.\ Control.\ Fusion {\bf 38}, 105 (1996).
-
-\bibitem{loarte} A.~Loarte, G.~Saibene, R.~Sartori, M.~B\'{e}coulet, L.~Horton, T.~Eich, A.~Herrmann, M.~Laux, G.~Matthews, S.~Jachmich, {\it et al.},  
-J.\ Nucl.\ Materials {\bf 313}--{\bf 316}, 962 (2003).
-
-\bibitem{evans}  T.E.~Evans, R.A.~Moyer, J.G.~Watkins, P.R.~Thomas, T.H.~Osborne, J.A.~Boedo, M.E.~Fenstermacher, K.H.~Finken, R.J.~Groebner, M.~Groth, {\it et al.},  
-Phys.\ Rev.\ Lett.\ {\bf 92}, 235003 (2004).
-
-\bibitem{jet} Y.~Liang,  H.R.~Koslowski, P.R.~Thomas, E.~Nardon, B.~Alper, P.~Andrew, Y.~Andrew, G.~Arnoux,  Y.~Baranov, M.~B\'{e}coulet, {\it et al.},  
-Phys.\ Rev.\ Lett.\ {\bf 98}, 265004 (2007).
-
-\bibitem{asdex} W.~Suttrop,  T.~Eich, J.C.~Fuchs, S.~G\"{u}nter, A.~Janzer, A.~Herrmann, A.~Kallenbach, P.T.~Lang, T.~Lunt, M.~Maraschek, {\it et al.},   
-Phys.\ Rev.\ Lett.\ {\bf 106}, 225004 (2011).
-
-\bibitem{kstar} Y.M.~Jeon,  J.-K.~Park, S.W.~Yoon, W.H.~Ko, S.G.~Lee, K.D.~Lee, G.S.~Yun, Y.U.~Nam, W.C.~Kim, J.-G.~Kwak, K.S.~Lee, H.K.~Kim, and H.L.~Yang, {\it et al.}, 
-Phys.\ Rev.\ Lett.\ {\bf 109}, 035004 (2012).
-
-\bibitem{mast} A.~Kirk, I.T.~Chapman, Y.~Liu, P.~Cahyna, P.~Denner, G.~Fishpool, C.J.~Ham, J.R.~Harrison, Y.~Liang, E.~Nardon, S.~Saarelma, R.~Scannell, A.J.~Thornton, and  MAST Team, 
-Nucl.\  Fusion {\bf 53}, 043007 (2013).
-
-\bibitem{east} T.~Sun,  Y.~Liang, Y.Q.~Liu, S.~Gu, X.~Yang, W.~Guo, T.~Shi, M.~Jia, L.~Wang, B.~Lyu, {\it et al.},  
-Phys.\ Rev.\ Lett.\  {\bf 117}, 115001 (2016).
-
-\bibitem{schmitz} O.~Schmitz, T.E.~Evans, M.E.~Fenstermacher, M.~Lehnen, H.~Stoschus, E.A.~Unterberg, J.W.~Coenen, H.~Frerichs, M.W.~Jakubowski, R.~Laengner, {\em et al.}, 
-Nucl.\ Fusion {\bf 52}, 043005 (2012).
-
-\bibitem{lanctot} M.J.~Lanctot, R.J.~Buttery, J.S.~de\,Grassie, T.E.~Evans, N.M.~Ferraro, J.M.~Hanson, S.R.~Haskey,  R.A.~Moyer, R.~Nazikian, T.H.~Osborne, {\em et al.}, 
-Nucl.\ Fusion {\bf 53}, 083019 (2013).
-
-\bibitem{paz} C.~Paz-Solden, R.~Nazikian, S.R.~Haskey, N.C.~Logan, E.J.~Strait, N.M.~Ferraro, J.M.~Hanson, J.D.~King, M.J.~Lanctot, R.A.~Moyer, {\it et al.}, 
-Phys.\ Rev.\ Lett.\ {\bf 114}, 105001 (2015).
-
-\bibitem{d158115} R.~Nazikian, C.~Paz-Soldan, J.D.~Callen,  J.S.~de\,Grassie, D.~Eldon, T.E.~Evans, N.M.~Ferraro,  B.A.~Grierson, R.J.~Groebner, S.R.~Haskey, {\em et al.}, 
-Phys.\ Rev.\ Lett.\ {\bf 114}, 105002 (2015).
-
-\bibitem{paz1} C.~Paz-Solden, R.~Nazikian, L.~Cui, B.C.~Lyons,  D.M.~Orlov, A.~Kirk, N.C.~Logan, T.H.~Osborne, W.~Suttrop, and D.B.~Weisberg, 
-Nucl.\ Fusion {\bf 59}, 056012 (2019).
-
-\bibitem{tm1} Q.~Yu, S.~G\"{u}nter,  and B.D.~Scott, Phys.\ Plasmas {\bf 10}, 797 (2003).
-
-\bibitem{tm2} Q.~Yu, Nucl.\ Fusion {\bf 50}, 025014 (2010).
-
-\bibitem{tm3} Q.~Yu, and S.~G\"unter,  Nucl.\ Fusion {\bf 51},  073030 (2011).
-
-\bibitem{hu} Q.M.~Hu,  R.~Nazikian,  B.A.~Grierson,  N.C.~Logan,  J.-K.~Park,  C.~Paz-Soldan, and Q.~Yu,  Phys.\ Plasmas {\bf 26}, 120702 (2019).
-
-\bibitem{connor} J.W.~Connor,  R.J.~Hastie, H.R.~Wilson, and R.L.~Miller, Phys.\ Plasmas  {\bf 5}, 2687 (1998).
-
- \bibitem{d3d} P.B.~Snyder, T.H.~Osboune, K.H.~Burrell, R.J.~Groebner, A.W.~Leonard, R.~Nazikian, D.M.~Orlov, O.~Schmitz, M.R.~Wade, and H.R.~Wilson, 
- Phys.\ Plasmas {\bf 19}, 056115 (2012).
-
-\bibitem{rf1} R.~Fitzpatrick, Phys.\ Plasmas {\bf 27}, 042506 (2020).
-
-\bibitem{rf2} R.~Fitzpatrick, and A.O.~Nelson, Phys.\ Plasmas {\bf 27}, 072501 (2020).
-
-\bibitem{d3d2} Q.M.~Hu, R.~Nazikian, B.A.~Grierson, N.C.~Logan, D.M.~Orlov, C.~Paz-Solden, and Q.~Yu,
-{\em The $q_{95}$ Windows of Edge-Localized-Mode Suppression using Resonant Magnetic Perturbations in the DIII-D Tokamak}, 
-Phys.\ Rev.\ Lett., to appear (2020).
+%\bibitem{rf2} R.~Fitzpatrick, and A.O.~Nelson, Phys.\ Plasmas {\bf 27}, 072501 (2020).
 
@@
 
-\bibitem{rfb} R.~Fitzpatrick, Phys.\ Plasmas {\bf 5}, 3325 (1998).
+%\bibitem{rfb} R.~Fitzpatrick, Phys.\ Plasmas {\bf 5}, 3325 (1998).
 
-\bibitem{nl1} R.~Fitzpatrick, and F.L.~Waelbroeck, Phys.\ Plasmas {\bf 12}, 022307 (2005).
+%\bibitem{nl1} R.~Fitzpatrick, and F.L.~Waelbroeck, Phys.\ Plasmas {\bf 12}, 022307 (2005).
 
-\bibitem{nl2} R.~Fitzpatrick, Phys.\ Plasmas {\bf 25}, 042503 (2018).
+%\bibitem{nl2} R.~Fitzpatrick, Phys.\ Plasmas {\bf 25}, 042503 (2018).
 
-\bibitem{nl3} R.~Fitzpatrick, Phys.\ Plasmas {\bf 25}, 112505 (2018).
+%\bibitem{nl3} R.~Fitzpatrick, Phys.\ Plasmas {\bf 25}, 112505 (2018).
 
-\bibitem{heyn} M.F.~Heyn, I.B.~Ivanov, S.V.~Kasilov, W.~Kernbichler, I.~Joseph, R.A.~Moyer,  and A.M.~Runov, Nucl.\ Fusion {\bf 48}, 024005 (2008).
+%\bibitem{hender} R.~Fitzpatrick, and T.C.~Hender, Phys.\ Fluids B {\bf 3}, 644 (1991).
 
-\bibitem{hender} R.~Fitzpatrick, and T.C.~Hender, Phys.\ Fluids B {\bf 3}, 644 (1991).
-
-\bibitem{cole} A.~Cole, and R.~Fitzpatrick, Phys.\ Plasmas {\bf 13}, 032503 (2006).
-
-\bibitem{lin1} M.~B\'{e}coulet, F.~Orain, P.~Maget, N.~Mellet, X.~Garbet, E.~Nardon, G.T.A.~Huysmans, T.~Caspar, A.~Loarte,  P.~Cayna, {\em et al.}, 
-Nucl.\ Fusion {\bf 52}, 054003  (2012).
-
-\bibitem{lin2} N.M.~Ferraro, Phys.\ Plasmas {\bf 19}, 056105  (2012).
-
-\bibitem{lin3} F.~Orain, M.~B\'{e}coulet, G.~Dif-Pradalier, G.T.A.~Huysmans, S.~Pamela,   E.~Nardon, C.~Passeron, G.~Latu, V.~Grandgirard, A.~Fil, {\em et al.}, 
-Phys.\ Plasmas {\bf 20}, 102510 (2013).
+%\bibitem{cole} A.~Cole, and R.~Fitzpatrick, Phys.\ Plasmas {\bf 13}, 032503 (2006).
 
@@
 
-\bibitem{am1} R.~Fitzpatrick, R.J.~Hastie, T.J.~Martin, and C.M.~Roach, Nucl.\ Fusion {\bf 33}, 1533 (1993).
+%\bibitem{am1} R.~Fitzpatrick, R.J.~Hastie, T.J.~Martin, and C.M.~Roach, Nucl.\ Fusion {\bf 33}, 1533 (1993).
 
-\bibitem{am2} A.H.~Glasser, Z.R.~Wang, and J.-K.~Park, Phys.\ Plasmas {\bf 23}, 112506 (2016).
+%\bibitem{am3} R.~Fitzpatrick, Phys.\ Plasmas {\bf 24}, 072506 (2017).
 
-\bibitem{am3} R.~Fitzpatrick, Phys.\ Plasmas {\bf 24}, 072506 (2017).
-
-\bibitem{kink0} S.R.~Haskey, M.J.~Lanctot, Y.Q.~Liu, C.~Paz-Soldan, J.D.~King, B.D.~Blackwell, and O.~Schmitz,  Plasma 
-Phys.\ Control.\ Fusion {\bf 57}, 025015 (2015).
-
-\bibitem{kink1} D.A.~Ryan,  Y.Q.~Liu, A.~Kirk, W.~Suttrop, B.~Dudson, M.~Dunne, R.~Fischer, J.C.~Fuchs, M.~Garcia-Munoz, B.~Kurzan, {\it et al.}, 
-Plasma Phys.\ Control.\ Fusion {\bf 57}, 095008 (2015).
-
-\bibitem{ipec} J.~K.~Park, M.J.~Schaffer, J.E.~Menard, and A.H.~Boozer, Phys.\ Rev.\ Lett.\ {\bf 99}, 195003 (2007).
-
-\bibitem{gpec} J.K.~Park, and N.C.~Logan, Phys.\ Plasmas {\bf 24}, 032505 (2017).
-
-\bibitem{icoil} G.L.~Jackson, P.M.~Anderson, J.~Bialek, W.P.~Cary, G.L.~Campbell, A.M.~Garofalo,  R.~Hatcher, A.G.~Kellman, R.J.~La\,Haye, A.~Nagy, {\em et al.},  
-Proc.\ 30th EPS Conf.\ on Controlled Fusion and Plasma Physics. (St.\ Petersburg, Russia, 2003) CD-ROM, P-4.47.
-
-\bibitem{transp} R.J.~Hawryluk, {\em Physics of Plasma Close to Thermonuclear Conditions: Vol.~1}. (Commission of the European Communities, Brussels, 1980.) 
-Internal Document DUR-FU-BRU-XII/476180.
-
-\bibitem{neutral} P.~Monier-Garbet, K.H.~Burrell, F.L.~Hinton, J.~Kim, X.~Garbet, and R.J.~Groebner,   
-Nucl.\ Fusion  {\bf 37}, 403 (1997).
-
-\bibitem{llama} A.~Rosenthal, and F.M.~Laggner, private communication (2020).
-
-\bibitem{solps} S~Wiesen, D.~Reiter, V.~Kotov, M.~Baelmans, W.~Dekeyser, A.S.~Kukushkin, S.W.~Lisgo, R.A.~Pitts, V.~Rozhansky, G.~Saibene I.~Veselova, and S.~Voskoboynikov,
-J.\ Nucl.\ Mat.\ {\bf 468}, 480 (2015).
-
-\bibitem{wade} M.R.~Wade, R.~Nazikian, J.D.~de\,Grassie, T.E.~Evans, N.M.~Ferraro, R.A.~Moyer, D.M.~Orlov, 
-R.J.~Buttery, M.E.~Fenstermacher, A.M.~Garofalo, {\em et al.}, Nucl.\ Fusion {\bf 55}, 023002 (2015).
-
-\bibitem{flat} R.~Fitzpatrick,  Phys.\ Plasmas {\bf 2}, 825 (1995).
-
-\bibitem{gim} R.~Fitzpatrick, C.G.~Gimblett, and R.J.~Hastie, 
-Plasma Phys.\ Control.\ Fusion {\bf 34}, 161 (1992).
-
-\bibitem{haz} R.D.~Hazeltine, and J.D.~Meiss, Rev.\ Mod.\ Phys.\ {\bf 121}, 1 (1985).
+%\bibitem{flat} R.~Fitzpatrick,  Phys.\ Plasmas {\bf 2}, 825 (1995).
 
@@
 
-\bibitem{wesson} J.A.~Wesson, private communication (1993).
+%\bibitem{ara} G.~Ara,  B.~Basu, B.~Coppi, G.~Laval, M.N.~Rosenbluth, and B.V.~Waddell, Ann.\ Phys.\ (N.Y.) {\bf 112}, 443 (1978).
 
-\bibitem{ara} G.~Ara,  B.~Basu, B.~Coppi, G.~Laval, M.N.~Rosenbluth, and B.V.~Waddell, Ann.\ Phys.\ (N.Y.) {\bf 112}, 443 (1978).
+%\bibitem{wat} R.~Fitzpatrick, P.G.~Watson, and F.L.~Waelbroeck, Phys.\ Plasmas {\bf 12}, 082510 (2005).
 
-\bibitem{wat} R.~Fitzpatrick, P.G.~Watson, and F.L.~Waelbroeck, Phys.\ Plasmas {\bf 12}, 082510 (2005).
-
-\bibitem{rffig} R.~Fitzpatrick, Phys.\ Plasmas {\bf 10}, 2304 (2003).
+%\bibitem{rffig} R.~Fitzpatrick, Phys.\ Plasmas {\bf 10}, 2304 (2003).
 
@@
 
-\appendix
-\section{Linear Versus Nonlinear Tearing Mode Theory in Tokamak Plasmas}\label{appa}
-\subsection{Introduction}
-The discussion in this Appendix outlines certain facts pertaining
-to tearing modes in tokamak plasmas that ought to be common knowledge in the 
-magnetic fusion community (but appear not to be).
-
-\subsection{General Considerations}\label{general}
-Consider a conventional tokamak plasma equilibrium. To lowest order, the equilibrium is governed by force balance,
-\begin{equation}\label{ea}
--\nabla p + {\bf j}\times {\bf B} \simeq {\bf 0},
-\end{equation}
-and
-flux freezing,
-\begin{equation}\label{eb}
-{\bf E} + {\bf V}\times {\bf B} \simeq {\bf 0}.
-\end{equation}
-This is the case because the other terms in the plasma equation of motion,
-(\ref{ea}), and the plasma Ohm's law, (\ref{eb}), are much
-smaller in magnitude than the retained terms. (Here, $p$ is the
-scalar pressure, ${\bf j}$ the current density, ${\bf B}$ the
-magnetic field strength, ${\bf E}$ the electric field strength, and ${\bf V}$ the plasma velocity).
-If we average the full plasma equation of motion and the full Ohm's law, as well as the full continuity and energy evolution equations, over magnetic flux-surfaces
-then the dominant terms in these equations are annihilated, and
-we end up with a set of $1\tfrac{1}{2}$-D evolution equations,
-according to which the magnetic field and plasma current
-evolve on the relatively long resistive timescale, $\tau_R$,
-whereas the density and temperature evolve on a somewhat
-shorter transport timescale.\cite{transp,gim}
-
-A linear tearing mode is a helical instability of a tokamak plasma equilibrium that is related to a shear-Alfv\'{e}n wave.\cite{haz} The mode resonates with the equilibrium magnetic field at
-the so-called rational magnetic flux-surface at which the
-shear-Alfv\'{e}n velocity is zero. If $q$ is the safety-factor, $m$ the poloidal mode number, and $n$ the
-toroidal mode number, then the rational
-flux-surface is characterized by $q=m/n$. A thin resistive layer forms
-around the rational surface that permits the reconnection of magnetic flux on a much faster timescale than the global
-resistive evolution timescale, $\tau_R$, resulting in the formation of a helical magnetic island chain. Let the Alfv\'{e}n time,
-$\tau_A$, be the
-typical timescale on which a (compressional) Alfv\'{e}n
-wave traverses the plasma.
-In conventional tokamak plasmas, $\tau_A\ll \tau_R$. In fact,
-the magnetic Lundquist number, $S\equiv \tau_R/\tau_A$,  typically exceeds $10^{\,8}$ in present-day tokamak plasmas,
-and will likely exceed $10^{\,10}$ in ITER plasmas.
- It turns out that the width of the resistive layer is typically a factor $S^{\,-2/5}$ smaller than the
-plasma minor radius, whereas magnetic flux is reconnected on
-the hybrid timescale $\tau_A\ll \tau_A^{2/5}\,\tau_R^{3/5}\ll \tau_R$.\cite{fkr} Note that  the
-structure of the tearing mode  outside the resistive layer is simply governed by a combination of flux-freezing and perturbed force balance.
-
- Figure~\ref{fig14} sketches the typical plasma current and vorticity patterns in a linear tearing layer. Observe that there is
- no distinction between a magnetic X-point and a magnetic 
-O-point. The reason for this is that the magnetic separatrix
-of the reconnected magnetic island does not present an obstacle
-to plasma motion because the linear layer is so thin that the
-plasma can diffuse resistively across magnetic field-lines very rapidly. However, this is only the case as long
-as the radial width of the magnetic island chain is less than the linear layer width. As soon as magnetic reconnection
-at the rational surface has proceeded to such an extent that
-the magnetic island width exceeds the layer width then we enter the nonlinear regime.
-
-Figure~\ref{fig14} also sketches the
-typical plasma current and vorticity patterns in the nonlinear regime.
-Observe that there is now a considerable distinction between an X-point and an O-point.
-The reason for this is that the island is sufficiently wide that the plasma cannot diffuse across it resistively rapidly enough to
-avoid being trapped inside the magnetic separatrix. Indeed, both the regions inside and outside the magnetic separatrix
-are governed by a combination of flux-freezing and perturbed force balance, whereas the resistive
-layer, within which the plasma can easily slip through the magnetic field,  is diverted onto the magnetic separatrix. Moreover, as
-the island grows, the width of the separatrix layer becomes
-increasing negligible with respect to the full island width. It
-turns out that the separatrix layer does not significantly affect the evolution of a nonlinear magnetic island chain. Indeed,
-the celebrated Rutherford island width evolution equation,
-which governs the evolution of the island width, is simply a
-$1\tfrac{1}{2}$-D evolution equation for a helical magnetic
-equilibrium localized around the rational surface.\cite{ruth}
-The Alfv\'{e}n time plays no role in this evolution (any more
-than it plays a role in the $1\tfrac{1}{2}$-D evolution of
-the global magnetic field). Likewise, the equation that
-determines the phase velocity of a nonlinear magnetic island chain (see Ref.~\onlinecite{nl2}, and references therein) is essentially an
-expression of the $1\tfrac{1}{2}$-D evolution of the plasma
-flow profiles across the island region. As before, the  Alfv\'{e}n time plays no role in this evolution (any more
-than it plays a role in the $1\tfrac{1}{2}$-D evolution of
-the global plasma flow profiles).
-
-It follows, from the previous discussion, that the nonlinear evolution of a tearing mode in a tokamak plasma has far more in common with the $1\tfrac{1}{2}$-D
-evolution of the global plasma equilibrium than it does with
-conventional linear tearing mode physics. In particular, the Alfv\'{e}n time is
-an irrelevant timescale in nonlinear tearing mode theory, and
-is also  very much shorter than the timescales on which
-physical quantities of interest actually evolve.
-It should be noted that linear tearing layers in present-day tokamak plasmas are sufficiently thin that by the time a tearing mode is detectable it is already in the nonlinear regime (i.e., the island width exceeds the linear layer width).\cite{wesson} It, therefore, makes very little sense to
-attempt to model nonlinear tearing mode evolution in tokamak plasmas using a toroidal nonlinear MHD code.
-The reason for this is obvious: employing  an MHD code necessarily introduces the very short Alfv\'{e}n time into the calculation,
-but this timescale is actually irrelevant to the problem in hand.
-In fact, this is exactly the same reason that MHD codes are not usually used to reconstruct global plasma equilibria, or to model their time evolution.
-
-\subsection{Natural Frequency}\label{natural}
-The natural frequency of a (stable) tearing mode is
-the helical phase velocity with which it would propagate
-were it actually unstable.\cite{rfa} The natural frequency
-is determined by the equilibrium plasma flow at the
-rational surface. Now, a magnetic island is a helical
-pattern in the magnetic field  generated by a helical current perturbation that is localized in the
-vicinity of the rational surface.
-Given that plasma current is predominately carried by the
-electrons, it is natural to suppose that a magnetic
-island chain (as well as the tearing mode perturbation
-away from the rational surface)  is convected by the
-electron fluid in the immediate vicinity of the rational
-surface. This is indeed the case in the linear regime.\cite{ara} Of course, as a consequence of diamagnetic flows, if the island chain is
-convected by the electron fluid at the rational surface then it propagates with respect to the local ion fluid. However, this is not a
-problem because a linear layer is sufficiently thin that the magnetic field can diffuse through the plasma very rapidly, which implies that
-the ion fluid is not tied to the magnetic structure of the island chain.
-
-The situation is very different in the nonlinear regime. 
-As we have seen, the region inside the magnetic separatrix of a nonlinear magnetic island chain is governed by a combination of flux-freezing and perturbed force balance.
-This implies that both the electron and the ion fluids are trapped inside the separatrix, and are, therefore,  forced to co-rotate with the island chain. There
-is no such constraint outside the separatrix, so the electron and ion fluids rotate at different speeds in this region,
-as a consequence of diamagnetism.  It follows that one or other of the electron and the ion fluid rotation profiles must exhibit a strong gradient across
-the separatrix. The island propagation velocity is determined by which of the two fluids is most resistant to the formation of such a gradient. 
-Of course, it is the ion fluid which is more resistant because of its much greater perpendicular viscosity,\cite{nl1,wat} as well as its much larger 
-neoclassical stress tensor.\cite{nl2} Hence, a nonlinear magnetic island chain is convected by the ion fluid in the vicinity of the rational
-surface, because this choice of propagation speed minimizes the ion fluid velocity gradient across the separatrix.
-
-Finally, we could imagine that if the width of an island chain is neither much less than the linear layer width (which is the strict
-criterion for the validity of linear theory) nor much greater than the linear layer width (which is the strict criterion for
-the validity of nonlinear theory) then the chain lies in some sort of intermediate regime in which it is
-convected by the local guiding-center fluid (which is intermediate between the predictions of linear and nonlinear theory).
-
-\newpage
-
-\begin{figure}
-\includegraphics[height=5in]{fig1.pdf}
-\caption{Overview of DIII-D discharge \#145380.
-(a) Safety factor at  ${\mit\Psi}_N=0.95$. 
-(b) $D_\alpha$ (i.e., Deuterium Balmer-alpha) signal, as well as $n=3$ current flowing in upper and lower sections of I-coil. 
-(c) Pedestal (i.e., ${\mit\Psi}_N=0.94$)
-electron pressure. (The red curve is the running average over 10 ms.) (d) Pedestal electron number density. The common vertical yellow bands indicate the ELM-suppression windows.}\label{fig1}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=5in]{fig2.pdf}
-\caption{Left Panel: Contours of the equilibrium poloidal
-magnetic flux in   DIII-D discharge \#145380 at time $t=2500$ ms. The scale major radius is $R_0=1.70\,{\rm m}$. The white dot indicates the magnetic axis, the white curve indicates the
-last closed magnetic flux-surface, and the thick black line indicates the limiter. 
-Upper-Right Panel: Safety-factor profile in DIII-D discharge \#145380 at time $t=2500$ ms.
-Lower-Right Panel:  Total plasma pressure profile in DIII-D discharge \#145380 at time $t=2500$ ms.
-} \label{fig2}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=7in]{fig3.pdf}
-\caption{Top Panel: The red, green, blue, and cyan curves show the electron number density ($10^{19}\,{\rm m}^{-3}$),
-electron temperature (keV), (thermal) ion temperature (keV), and
- C-VI ion number density  ($10^{18}\,{\rm m}^{-3}$)  profiles, respectively,  in  DIII-D discharge \#145380 at time $t=2500$ ms. Middle Panel:  
- ${\bf E}\times {\bf B}$ frequency profile in  DIII-D discharge \#145380 at time $t=2500$. Bottom Panel: The red, green, and blue curves show
- the perpendicular momentum, energy, and particle diffusivity profiles, respectively, 
- in  DIII-D discharge \#145380 at time $t=2500$ ms.
-The   common vertical dotted lines indicate the location of the top
-of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig3}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=4in]{fig4.pdf}
-\caption{Safety-factors as functions of time in  DIII-D discharge \#145380. The red, green, blue, and black curves show the safety-factors
-at the magnetic axis (${\mit\Psi}_N=0.00$),
-the $95\%$ flux surface (${\mit\Psi}_N=0.950$), the
-effective plasma boundary for the GPEC and EPEC calculations
-(${\mit\Psi}_N=0.997$), and the true plasma boundary (${\mit\Psi}_N=1.00$), respectively. The yellow vertical bands indicate the ELM-suppression windows. 
-The horizontal dotted lines indicate the safety-factors at the various $n=3$ rational surfaces.} \label{fig4}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=6in]{fig5.pdf}
-\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics.
-Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics. The red, green, blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig5}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=6in]{fig6.pdf}
-\caption{Top Panel: Full  $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time 
-in   DIII-D discharge \#145380.
-Bottom Panel:  Full $n=3$ island widths as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
-The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig6}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=6in]{fig7.pdf}
-\caption{Top Panel: Density flattening widths associated with induced $n=3$ magnetic island  chains as functions of the least-squares linear fit to $q_{95}$ versus time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics.
-Bottom Panel:  Electron temperature flattening widths associated with induced $n=3$ magnetic island chains as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
-The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig7}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=6in]{fig8.pdf}
-\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by the ${\bf E}\times {\bf B}$
-frequency.
-Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is  determined by the ${\bf E}\times {\bf B}$
-frequency. The red, green, blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig8}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=6in]{fig9.pdf}
-\caption{Top Panel: $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time
-in   DIII-D discharge \#145380.
-Bottom Panel:  $n=3$ island widths as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is  determined by the ${\bf E}\times {\bf B}$
-frequency. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
-The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig9}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=6in]{fig10.pdf}
-\caption{Top Panel: Density flattening widths associated with induced $n=3$ magnetic island  chains as functions of the least-squares linear fit to $q_{95}$ versus time
-in   DIII-D discharge \#145380, assuming that the natural frequency is  determined by the ${\bf E}\times {\bf B}$
-frequency.
-Bottom Panel:  Electron temperature flattening widths associated with induced $n=3$ magnetic island chains as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by the ${\bf E}\times {\bf B}$
-frequency. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
-The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig10}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=6in]{fig11.pdf}
-\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics.
-Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics. The black, red, green, blue, yellow, cyan, magenta,  brown, 
-purple, and orange curves correspond to $m=4$, 5, 6, 7, 8, 9, 10,  11, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig11}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=6in]{fig12.pdf}
-\caption{Top Panel: $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time
-in   DIII-D discharge \#145380.
-Bottom Panel:  $n=3$ island widths as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
-The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig12}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=6in]{fig13.pdf}
-\caption{Top Panel: Density flattening widths associated with induced $n=3$ magnetic island  chains as functions of the least-squares linear fit to $q_{95}$ versus time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics.
-Bottom Panel:  Electron temperature flattening widths associated with induced $n=3$ magnetic island chains as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
-The horizontal dotted lines indicate  the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig13}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=4in]{fig14.pdf}
-\caption{Schematic diagram showing the perturbed plasma current and vorticity patterns around the magnetic X- and O-points of a linear and a nonlinear tearing mode. 
-The horizontal axis measures radial distance from the rational
-surface, whereas the vertical axis measures distance along equilibrium magnetic field-lines. Red and blue
-correspond to positive and negative current/vorticity values, respectively. (See Figs.~7 and 10 in 
-Ref.~\onlinecite{rffig}.)}\label{fig14}
-\end{figure}
+%\begin{figure}
+%\includegraphics[height=5in]{fig1.pdf}
+%\caption{Overview of DIII-D discharge \#145380.
+%(a) Safety factor at  ${\mit\Psi}_N=0.95$. 
+%(b) $D_\alpha$ (i.e., Deuterium Balmer-alpha) signal, as well as $n=3$ current flowing in upper and lower sections of I-coil. 
+%(c) Pedestal (i.e., ${\mit\Psi}_N=0.94$)
+%electron pressure.
+(The red curve is the running average over 10 ms.) (d) Pedestal electron number density.
+The common vertical yellow bands indicate the ELM-suppression/mitigation windows.}\label{fig1}
+%\end{figure}
 

### 2020-09-01 Papers/Paper2/Paper.tex
Added SCALE input option

@@
 %\begin{abstract}
-
 %\end{abstract}
-
-\maketitle
 
@@
 
-\section{Cylindrical Model}
+\section{Cylindrical RMP Response Model}\label{s2}
+\subsection{Plasma Equilibrium}
+Consider a large aspect-ratio, low-$\beta$, tokamak plasma whose magnetic flux surfaces map out (almost)
+concentric circles in the poloidal plane.
+Such a plasma is well approximated as a periodic cylinder.  Suppose that the minor radius of the plasma
+is $a$. Standard cylindrical coordinates ($r$, $\theta$, $z$) are adopted. The system is assumed to
+be periodic in the $z$-direction, with periodicity length $2\pi\,R_0$, where $R_0\gg a$ is the simulated
+plasma major radius. It is convenient to define the simulated toroidal angle $\phi=z/R_0$.
 
-\section{Toroidal Model}
+The equilibrium magnetic field is written ${\bf B} = [0,B_\theta(r), B_\phi]$. The associated equilibrium
+plasma current density takes the form ${\bf j} =[0,0,j_\phi(r)]$, where $\mu_0\,j_\phi= (1/r)\,d(r\,B_\theta)/dr$. The
+so-called {\em safety-factor}, $q(r)=r\,B_\phi/(R_0\,B_\theta)$, parameterizes the helical pitches of equilibrium magnetic
+field-lines.
+
+\subsection{Plasma Response to RMP}
+Consider the response of the plasma to an externally generated, static, helical, resonant magnetic perturbation (RMP). 
+Suppose that the RMP has $m$ periods in the poloidal direction, and $n$ periods in the toroidal direction.
+It is convenient to express the perturbed magnetic field and the perturbed plasma current density in
+terms of a perturbed poloidal magnetic flux, $\psi(r,\theta,\phi,t)$. In fact, $\delta{\bf B} = \nabla\psi\times \nabla z$, 
+and $\mu_0\,\delta {\bf j} = - \nabla^2\psi\,\nabla z$,
+where $\psi(r,\theta,\phi,t) = \hat{\psi}(r,t)\,\exp[{\rm i}\,(m\,\theta-n\,\phi)]$, and $\hat{\psi}$ is real. This particular representation
+is valid provided that $m/n\gg a/R_0$.\cite{rfa}
+
+The response of the plasma to the RMP is governed by the equations of marginally stable, ideal-MHD everywhere in the
+plasma, apart from a relatively narrow (in $r$) region in the vicinity of the so-called {\em rational surface}, minor radius $r_s$, 
+at which $q(r_s)=m/n$.\cite{rfa}
+
+It is convenient to parameterize the RMP in terms of the so-called {\em vacuum magnetic flux}, ${\mit\Psi}_v(t) = |{\mit\Psi}_v|\,{\rm e}^{-{\rm i}\,\varphi_v}$,
+which is defined to be the value of $\hat{\psi}(r,t)$ at radius $r_s$ in the presence of the RMP, but in the absence of plasma. Here,
+$\varphi_v$ is the helical phase of the RMP. Likewise, the response of the plasma in the vicinity of the rational
+surface is parameterized in terms of the so-called {\em reconnected magnetic flux}, ${\mit\Psi}_s(t)=|{\mit\Psi}_s|\,{\rm e}^{\,{\rm i}\,\varphi_s}$, 
+which is the actual value of $\hat{\psi}(r,t)$ at radius $r_s$. Here, $\varphi_s$ is the helical phase of
+the reconnected magnetic flux.
+
+The intrinsic stability of the $m$, $n$ tearing mode is governed by the dimensionless parameter
+$E_{ss}= [d\hat{\psi}_s/d\ln r]_{r_{s-}}^{r_{s+}}$, where $\hat{\psi}_s(r)$
+is a solution of the marginally stable, ideal-MHD equations, for the case of an $m$, $n$ helical
+perturbation, that satisfies physical boundary conditions at $r=0$ and $r=a$, in the absence of the
+RMP, and is such that $\hat{\psi}_s(r_s)=1$.\cite{fkr,am1} According to resistive-MHD theory,\cite{fkr,ruth}
+if $E_{ss}>0$ then the $m$, $n$ tearing mode spontaneously reconnects magnetic flux at the rational
+surface to form a helical magnetic island chain. In this paper, it is assumed that $E_{ss}<0$, so that the
+$m$, $n$ tearing mode is intrinsically stable. In this case, any magnetic reconnection that takes place
+at the rational surface is due solely to the action of the RMP.
+
+The ideal-MHD response of the plasma to the RMP is governed by the dimensionless parameter
+$E_{sv}= [d\hat{\psi}_v/d\ln r]_{r_{s-}}^{r_{s+}}$, where $\hat{\psi}_v(r)$
+is a solution of the marginally stable, ideal-MHD equations, for the case of an $m$, $n$ helical
+perturbation, that satisfies physical boundary conditions at $r=0$ and $r=a$, in the presence of the
+RMP, and is such that $\hat{\psi}_v(r_s)=0$.\cite{am1}
+
+\subsection{Linear Response Regime}
+In the linear response regime, the reconnected magnetic flux induced by the RMP at the
+rational surface is governed by\,\cite{rfa,rfb,rfc}
+\begin{equation}\label{e1}
+\frac{\delta_s}{r_s}\,\tau_R\left(\frac{d}{dt}+{\rm i}\,\omega_s\right){\mit\Psi}_s= E_{ss}\,{\mit\Psi}_s+E_{sv}\,{\mit\Psi}_v,
+\end{equation}
+where $\delta_s$ is the linear layer width, $\tau_R=\mu_0\,r_s^{\,2}\,\sigma(r_s)$ the global resistive diffusion timescale,
+ and
+\begin{equation}
+\omega_s (t)=m\,{\mit\Omega}_\theta(r_s,t)-n\,{\mit\Omega}_\phi(r_s,t).
+\end{equation}
+Here, $\sigma(r)$, ${\mit\Omega}_\theta(r,t)$, and ${\mit\Omega}_\phi(r,t)$ are the 
+plasma conductivity, poloidal angular velocity, and toroidal angular velocity profiles, respectively. 
+Note that, in this paper, we are assuming that the constant-$\psi$ approximation\,\cite{fkr} holds at the rational surface. (It is demonstrated in
+Ref.~\onlinecite{rf1} that the appropriate linear response regime for an RMP resonant in the pedestal of a typical DIII-D H-mode discharge
+is the so-called  {\em first semi-collisional regime}, which is indeed a constant-$\psi$ response regime. Moreover, if the appropriate linear response regime
+is constant-$\psi$ then so is the appropriate nonlinear response regime, because the constant-$\psi$ constraint is
+easier to satisfy in the nonlinear regime than in the linear regime.\cite{rfb,rffig})
+
+Equation~(\ref{e1}) can be rewritten as an {\em amplitude evolution equation},
+\begin{equation}\label{e3}
+\frac{\delta_s}{r_s}\,\tau_R\,\frac{d|{\mit\Psi}_s|}{dt}= E_{ss}\,|{\mit\Psi}_s| + E_{sv}\,|{\mit\Psi}_v|\,\cos(\varphi_s-\varphi_v),
+\end{equation}
+combined with a {\em phase evolution equation}, 
+\begin{equation}\label{e4}
+\frac{d\varphi_s}{dt} = \omega_s - \frac{E_{sv}}{\tau_R}\,\frac{r_s}{\delta_s}\,\frac{|{\mit\Psi}_v|}{|{\mit\Psi}_s|}\,\sin(\varphi_s-\varphi_v).
+\end{equation}
+The final term on the right-hand side of Eq.~(\ref{e4}) is termed the {\em slip frequency}, and is the difference between the helical phase velocity of
+the reconnected magnetic flux and that expected on the  assumption that the flux is convected by the plasma flow at the
+rational surface (i.e., $d\varphi_s/dt=\omega_s$). In general, the slip frequency is non-zero because the plasma in the vicinity of the rational surface is capable of diffusing resistively 
+through the linear layer structure.
+
+\subsection{Nonlinear Response Regime}
+In the nonlinear response regime, Eq.~(\ref{e3}) generalizes to the {\em Rutherford island width evolution equation}:\,\cite{ruth,ruth1}
+\begin{equation}\label{e5}
+\frac{({\cal I}/2)\,W_s}{r_s}\,\tau_R\,\frac{d|{\mit\Psi}_s|}{dt} = E_{ss}\,|{\mit\Psi}_s| + E_{sv}\,|{\mit\Psi}_v|\,\cos(\varphi_s-\varphi_v),
+\end{equation}
+where
+\begin{equation}
+W_s = 4\left(\frac{|{\mit\Psi}_s|}{s_s\,r_s\,B_\theta(r_s)}\right)^{1/2} r_s
+\end{equation}
+is the full radial width of the magnetic island chain, ${\cal I} = 0.8227$, $s(r) = d\ln q/d\ln r$, and $s_s=s(r_s)$. The
+nonlinear regime holds when $W_s\gg \delta_s$, whereas the linear regime holds when $\delta_s\ll W_s$.
+
+Equation~(\ref{e5}) is usually coupled with the so-called {\em no-slip constraint}:\,\cite{rfa}
+\begin{equation}\label{e6}
+\frac{d\varphi_s}{dt} = \omega_s.
+\end{equation}
+The reasoning behind the imposition of this constraint is that the plasma is trapped inside the
+magnetic separatrix of the magnetic island chain that forms in the vicinity of the rational surface,
+which forces the chain to co-rotate with the local plasma flow. However, in reality, the plasma
+is able to diffuse resistively across the separatrix to some extent. Hence, by analogy with Eqs.~(\ref{e3}), (\ref{e4}), and (\ref{e5}), and 
+in accordance with Refs.~\onlinecite{slip1} and \onlinecite{slip2}, in this paper we shall modify Eq.~(\ref{e6}) such that
+\begin{equation}\label{e7}
+\frac{d\varphi_s}{dt} = \omega_s - \frac{E_{sv}}{\tau_R}\,\frac{r_s}{({\cal I}/2)\,W_s}\,\frac{|{\mit\Psi}_v|}{|{\mit\Psi}_s|}\,\sin(\varphi_s-\varphi_v).
+\end{equation}
+The final term on the right-hand side of the previous equation is the {\em nonlinear slip frequency}. In general,
+we would expect this frequency to be relatively small (because it is generally the case that $|\omega_s|\,\tau_R\,(W_s/r_s)\gg 1$
+for fully-developed magnetic islands in high-temperature tokamak plasmas\,\cite{rf1,slip2}). Nevertheless, the
+nonlinear slip frequency may be non-negligible for developing island chains, which is why we are including it in our analysis.
+(Note that the nonlinear slip frequency does not appear in rigorous island calculations, such as
+that described in Ref.~\onlinecite{rfisland}, and references therein, because such calculations depend crucially on
+complicated hierarchical ordering assumptions, according to which the nonlinear slip frequency is negligible.)
+
+\subsection{Composite Model}
+We can combine Eqs.~(\ref{e3}), (\ref{e4}), (\ref{e5}), and (\ref{e7}) to give the following
+composite resonant response model that interpolates between the linear and the nonlinear
+regimes:
+\begin{align}\label{e9}
+\left(\frac{({\cal I}/2)\,W_s+\delta_s}{r_s}\right)\tau_R\,\frac{d|{\mit\Psi}_s|}{dt} &= E_{ss}\,|{\mit\Psi}_s| + E_{sv}\,|{\mit\Psi}_v|\,\cos(\varphi_s-\varphi_v),\\[0.5ex]
+\frac{d\varphi_s}{dt}& = \omega_s - \frac{E_{sv}}{\tau_R}\left(\frac{r_s}{({\cal I}/2)\,W_s+\delta_s}\right)\frac{|{\mit\Psi}_v|}{|{\mit\Psi}_s|}\,\sin(\varphi_s-\varphi_v).\label{e10}
+\end{align}
+If we define $X_s = |{\mit\Psi}_s|\,\cos\varphi_s$, $Y_s = |{\mit\Psi}_s|\,\sin\varphi_s$, $X_v = |{\mit\Psi}_v|\,\cos\varphi_v$, and $Y_v = |{\mit\Psi}_v|\,\sin\varphi_v$ 
+then the previous two equations are more conveniently written in the nonsingular (when $|{\mit\Psi}_s|=0$) forms:\,\cite{slip1,slip2,slip3}
+\begin{align}\label{e11}
+\left(\frac{({\cal I}/2)\,W_s+\delta_s}{r_s}\right)\tau_R\left(\frac{dX_s}{dt}+\omega_s\,Y_s\right)&= E_{ss}\,X_s + E_{sv}\,X_v,\\[0.5ex]
+\left(\frac{({\cal I}/2)\,W_s+\delta_s}{r_s}\right)\tau_R\left(\frac{dY_s}{dt}-\omega_s\,X_s\right)& = E_{ss}\,Y_s + E_{sv}\,Y_v,\label{e12}
+\end{align}
+where
+\begin{equation}
+W_s = 4\left(\frac{\sqrt{X_s^{\,2}+Y_s^{\,2}}}{s_s\,r_s\,B_\theta(r_s)}\right)^{1/2} r_s.
+\end{equation}
+With the benefit of hindsight, Eqs.~(\ref{e11}) and (\ref{e12}) could have been derived more directly from the
+following heuristic generalization of Eq.~(\ref{e1}):\,\cite{slip2}
+\begin{equation}
+\left(\frac{({\cal I}/2)\,W_s+\delta_s}{r_s}\right)\tau_R\left(\frac{d}{dt}+{\rm i}\,\omega_s\right){\mit\Psi}_s= E_{ss}\,{\mit\Psi}_s+E_{sv}\,{\mit\Psi}_v.
+\end{equation}
+
+\section{Modified Toroidal RMP Response Model}
+Our toroidal model of the response of a tokamak plasma to a static, externally generated, RMP is described in
+detail in Ref.~\onlinecite{rftor}. In the light of the composite model developed in Sect.~\ref{s2}, we shall
+modify the resonant plasma response component of our  toroidal response model; this component is described in Appendix~D of Ref.~\onlinecite{rftor}.
+
+Equations~(D1) and (D2) in Ref.~\onlinecite{rftor} are modified such that 
+\begin{align}\label{e15}
+\left(\hat{W}_k + \hat{\delta}_k\right){\cal S}_k\,\frac{d\hat{\mit\Psi}_k}{d\hat{t}} &= \sum_{k'=1,K}\hat{E}_{kk'}\hat{\mit\Psi}_{k'}\,\cos(\varphi_k-\varphi_{k'}-\xi_{kk'})
++\hat{E}_{kk}\,\hat{\chi}_k\,\cos(\varphi_k-\zeta_k),\\[0.5ex]
+{\cal S}_k&=\frac{\tau_R(\hat{r}_k)}{\tau_A},
+\end{align}
+respectively. Here, 
+\begin{align}
+\hat{W}_k &=\frac{2\,{\cal I}}{\hat{a}\,\hat{r}_k}\left(\frac{q}{g\,s}\right)_{\hat{r}_k} |\hat{\mit\Psi}_k|^{\,1/2},\\[0.5ex]
+\hat{\delta}_k &= \frac{\delta_{\rm SC}(\hat{r}_k)}{R_0\,\hat{a}\,\hat{r}_k},
+\end{align}
+where $\delta_{\rm SC}(\hat{r})$ is the semi-collisional linear layer width specified in Ref.~\onlinecite{rf1}.
+
+In the previous expressions, $R_0$ is the major radius of the magnetic axis, $r$ is a magnetic flux surface label with dimensions of length (which, roughly speaking, is the average minor radius of the
+flux surface), $q(r)$ is the safety-factor profile, $s(r)=d\ln q/d\ln r$, 
+$g(r)\,B_0$ is the toroidal magnetic field-strength at major radius $R_0$, $B_0$ is the vacuum
+toroidal magnetic field-strength on the magnetic axis, $a$ is the value of $r$ on the last closed magnetic-flux surface, $r_k$ is the value of $r$ on the $k$th rational
+surface (resonant with poloidal mode number $m_k$, and toroidal mode number $n$), $\hat{a}=a/R_0$, $\hat{r}=r/a$, and $\hat{r}_k=r_k/a$. 
+Furthermore, $\tau_R(\hat{r})= \mu_0\,r^{\,2}\,\sigma_{ee}\,Q_{00}^{\,ee}$, where $\sigma_{ee}$ is the classical plasma parallel electrical conductivity, and
+$Q_{00}^{\,ee}$ describes the corrections to this conductivity due to neoclassical effects and the presence of plasma impurities. Also, $\tau_A$ is a convenient
+scale time, and $\hat{t}=t/\tau_A$. Finally, ${\mit\Psi}_k = B_0\,R_0\,\hat{\mit\Psi}_k\,{\rm e}^{-{\rm i}\,\varphi_k}$ is the reconnected magnetic flux
+at the $k$th rational surface, ${\mit\chi}_k = B_0\,R_0\,\hat{\mit\chi}_k\,{\rm e}^{-{\rm i}\,\zeta_k}$ is a measure of the vacuum magnetic flux at the $k$th
+rational surface (in fact, $\hat{E}_{kk}\,\chi_k$ is equivalent to $E_{sv}\,{\mit\Psi}_v$ in Sect.~\ref{s2}), and $E_{kk'} =\hat{E}_{kk'}\,{\rm e}^{-{\rm i}\,\xi_{kk'}}$ is the toroidal tearing stability matrix.\cite{am1} Here, $\hat{\mit\Psi}_k>0$, $\varphi_k$, $\hat{\chi}_k>0$,
+$\zeta_k$, $\hat{E}_{kk'}>0$, and $\xi_{kk'}$ are all real quantities.
+
+Equation~(\ref{e15}) represents a minor improvement to Eq.~(D1) of Ref.~\onlinecite{rftor} in which the interpolation between the
+linear and nonlinear regimes is performed in a more systematic manner.
+
+Equation~(D6) of Ref.~\onlinecite{rftor} is modified such that
+\begin{align}\label{e19}
+\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{d\varphi_k}{d\hat{t}}-\hat{\varpi}_k\right)&=
+- \sum_{k'=1,K}\hat{E}_{kk'}\,\hat{\mit\Psi}_{k'}\,\sin(\varphi_k-\varphi_{k'}-\xi_{kk'})-\hat{E}_{kk}\,\hat{\chi}_k\,\sin(\varphi_k-\zeta_k),
+\end{align}
+where
+\begin{equation}
+\hat{\varpi}_k= m_k\,\hat{\mit\Omega}_\theta(\hat{r}_k,\hat{t})-n\,\hat{\mit\Omega}_\phi(\hat{r}_k,\hat{t}),
+\end{equation}
+and $\hat{\mit\Omega}_\theta= {\mit\Omega}_\theta\,\tau_A$, $\hat{\mit\Omega}_\phi= {\mit\Omega}_\phi\,\tau_A$. Equation~(\ref{e19}) represents
+a major improvement to Eq.~(D6) that takes into  account the finite slip frequencies of the magnetic island chains induced at
+the various rational surfaces in the plasma.
+
+If we define $X_k = \hat{\mit\Psi}_k\,\cos\varphi_k$ and $Y_k=\hat{\mit\Psi}_k\,\sin\varphi_k$ then Eqs.~(\ref{e15}) and (\ref{e19}) are
+more conveniently written in the nonsingular (when $\hat{\mit\Psi}_k=0$) forms
+\begin{align}\label{e21}
+\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{dX_k}{d\hat{t}} 
++\hat{\varpi}_k\,Y_k\right)= \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,X_{k'}  -\sin\xi_{kk'}\,Y_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\cos\zeta_k,\\[0.5ex]
+\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{dY_k}{d\hat{t}} -\hat{\varpi}_k\,X_k\right)
+= \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,Y_{k'}
++\sin\xi_{kk'}\,X_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\sin\zeta_k.\label{e22}
+\end{align}
+Equations (\ref{e15}), (\ref{e19}), (\ref{e21}), and (\ref{e22}) are the toroidal generalizations of Eqs.~(\ref{e9}), (\ref{e10}), (\ref{e11}), and (\ref{e12}), respectively.
 
@@
 
-%\bibitem{rf1} R.~Fitzpatrick, Phys.\ Plasmas {\bf 27}, 042506 (2020).
-
-%\bibitem{rf2} R.~Fitzpatrick, and A.O.~Nelson, Phys.\ Plasmas {\bf 27}, 072501 (2020).
-
 \bibitem{rfa} R.~Fitzpatrick, Nucl.\ Fusion {\bf 33}, 1049 (1993).
-
-%\bibitem{rfb} R.~Fitzpatrick, Phys.\ Plasmas {\bf 5}, 3325 (1998).
-
-%\bibitem{nl1} R.~Fitzpatrick, and F.L.~Waelbroeck, Phys.\ Plasmas {\bf 12}, 022307 (2005).
-
-%\bibitem{nl2} R.~Fitzpatrick, Phys.\ Plasmas {\bf 25}, 042503 (2018).
-
-%\bibitem{nl3} R.~Fitzpatrick, Phys.\ Plasmas {\bf 25}, 112505 (2018).
-
-%\bibitem{hender} R.~Fitzpatrick, and T.C.~Hender, Phys.\ Fluids B {\bf 3}, 644 (1991).
-
-%\bibitem{cole} A.~Cole, and R.~Fitzpatrick, Phys.\ Plasmas {\bf 13}, 032503 (2006).
 
@@
 
-%\bibitem{am1} R.~Fitzpatrick, R.J.~Hastie, T.J.~Martin, and C.M.~Roach, Nucl.\ Fusion {\bf 33}, 1533 (1993).
-
-%\bibitem{am3} R.~Fitzpatrick, Phys.\ Plasmas {\bf 24}, 072506 (2017).
-
-%\bibitem{flat} R.~Fitzpatrick,  Phys.\ Plasmas {\bf 2}, 825 (1995).
+\bibitem{am1} R.~Fitzpatrick, R.J.~Hastie, T.J.~Martin, and C.M.~Roach, Nucl.\ Fusion {\bf 33}, 1533 (1993).
 
@@
 
-%\bibitem{ara} G.~Ara,  B.~Basu, B.~Coppi, G.~Laval, M.N.~Rosenbluth, and B.V.~Waddell, Ann.\ Phys.\ (N.Y.) {\bf 112}, 443 (1978).
+\bibitem{rfb} R.~Fitzpatrick, Phys.\ Plasmas {\bf 5}, 3325 (1998).
 
-%\bibitem{wat} R.~Fitzpatrick, P.G.~Watson, and F.L.~Waelbroeck, Phys.\ Plasmas {\bf 12}, 082510 (2005).
+\bibitem{rfc} R.~Fitzpatrick, Phys.\ Plasmas {\bf 21}, 092513 (2014).
 
-%\bibitem{rffig} R.~Fitzpatrick, Phys.\ Plasmas {\bf 10}, 2304 (2003).
+\bibitem{rf1} R.~Fitzpatrick, Phys.\ Plasmas {\bf 27}, 042506 (2020).
+
+\bibitem{rffig} R.~Fitzpatrick, Phys.\ Plasmas {\bf 10}, 2304 (2003).
+
+\bibitem{ruth1} P.H.~Rutherford, in  {\it Basic Physical Processes of
+Toroidal Fusion Plasmas}, Proc.\ Course and Workshop, Varenna, 1985. (Commission of the European Communities, Brussels, 1985.) Vol.~2, p.~531.
+
+\bibitem{slip1} L.G.~Eliseev, N.V.~Ivanov, A.M.~Kakurin, A.V.~Melnikov, and S.V.~Perfilov, Phys.\ Plasmas {\bf 22}, 052504 (2015).
+
+\bibitem{slip2} W.~Huang, and P.~Zhu, Phys.\ Plasmas {\bf 27}, 022514 (2020).
+
+\bibitem{rfisland} R.~Fitzpatrick, Phys.\ Plasmas {\bf 25}, 082513 (2018);
+
+\bibitem{slip3} A.N.~Chudnovskiy, Y.V.~Gvozdkov, N.V.~Ivanov, A.M.~Kakurin,
+A.A.~Medvedev, I.I.~Orlovskiy, Y.D.~Pavlov, V.V.~Piterskiy, V.D.~Pustovitov,
+M.B.~Safonova, V.V.~Volkov, and the T-10 Team, Nucl.\ Fusion {\bf 43} 681 (2003).
+
+\bibitem{rftor} R.~Fitzpatrick, and A.O.~Nelson, Phys.\ Plasmas {\bf 27}, 072501 (2020).
 

### 2020-09-01 Phase-2.x/Source/Phase.h

@@ -12,6 +12,7 @@
 // -o OLD    - overrides OLD value from namelist file
 // -F FREQ   - overrides FREQ value from namelist file
 // -s STAGE5 - overrides STAGE5 value from namelist file
+// -S SCALE  - overrides SCALE value from namelist file
 // -t TIME   - sets experimental time
 
 // Stage 4 - Class reads FLUX/NEOCLASSICAL/GPEC data and plots error-field
@@ -26,8 +27,13 @@
 // 1.2 - Major rearrangement of input and output files
 // 1.3 - Added PsiN and island width in PsiN to Stage6 output files
 // 1.4 - Added linear iterpolation
+// 1.5 - Added wnl
+// 1.6 - Redefined Sk. Corrected composite factor in Rutherford equation.
+// 1.7 - Added SCALE as input value
 
 // 2.0 - Relaxed no-slip constraint
+// 2.1 - Redefined Sk. Corrected composite factor in Rutherford equation.
+// 2.2 - Added SCALE as input value
 
 // #######################################################################
 
@@ -35,7 +41,7 @@
 #define PHASE
 
 #define VERSION_MAJOR 2
-#define VERSION_MINOR 0
+#define VERSION_MINOR 2
 
 #include <stdio.h>
 #include <math.h>
@@ -58,7 +64,7 @@
 using namespace blitz;
 
 // Namelist funtion
-extern "C" void NameListRead (int* NFLOW, int* STAGE2, int* INTF, int* INTN, int* INTU, int* OLD, int* FREQ, double* DT, double* TIME,
+extern "C" void NameListRead (int* NFLOW, int* STAGE2, int* INTF, int* INTN, int* INTU, int* OLD, int* FREQ, double* DT, double* TIME, double* SCALE, 
 			      int* NCTRL, double* TCTRL, double* ICTRL, double* PCTRL);
 
 // ############
@@ -82,6 +88,7 @@ class Phase
   int      INTU;   // If != 0 then use interpolated uFile and lFiles
   int      OLD;    // If != 0 then initialize new calculation
   int      FREQ;   // If != 0 then use island width dependent natural frequency
+  double   SCALE;  // GPEC scalefactor
   
   int      NCTRL;  // Number of control points
   double*  TCTRL;  // Control times (s)
@@ -126,7 +133,7 @@ class Phase
   Array<double,1> rk;      // Normalized minor radii of resonant surfaces
   Array<double,1> qk;      // Safety-factors at resonant surfaces
[…]

### 2020-09-01 Phase-2.x/Source/main.cpp

@@ -29,10 +29,10 @@ int main (int argc, char** argv)
   int c;
   char* tvalue = NULL; char* svalue = NULL; char* fvalue = NULL; 
   char* nvalue = NULL; char* uvalue = NULL; char* ovalue = NULL;
-  char* Fvalue = NULL;
+  char* Fvalue = NULL; char* Svalue = NULL;
   opterr = 0;
   
-  while ((c = getopt (argc, argv, "f:hn:o:s:t:u:F:")) != -1)
+  while ((c = getopt (argc, argv, "f:hn:o:s:t:u:F:S:")) != -1)
     switch (c)
       {
       case 'f':
@@ -48,6 +48,7 @@ int main (int argc, char** argv)
 	printf ("-t TIME   - set experimental time to TIME\n");
 	printf ("-u INTU   - set interpolation flag INTU\n");
 	printf ("-F FREQ   - set frequency flag FREQ\n");
+	printf ("-S SCALE  - set GPEC scalefactor SCALE\n");
 	exit (0);
       case 'n':
 	nvalue = optarg;
@@ -67,8 +68,11 @@ int main (int argc, char** argv)
       case 'F':
 	Fvalue = optarg;
  	break;
+      case 'S':
+	Svalue = optarg;
+ 	break;
       case '?':
-	if (optopt == 't' || optopt == 's' || optopt == 'f' || optopt == 'o'|| optopt == 'n' || optopt == 'u' || optopt == 'F')
+	if (optopt == 't' || optopt == 's' || optopt == 'f' || optopt == 'o'|| optopt == 'n' || optopt == 'u' || optopt == 'F' || optopt == 'S')
 	  printf ("Option = %c requires an argument\n", optopt);
 	  else if (isprint (optopt))
 	    printf ("Unknown option '-%c'\n", optopt);
@@ -79,8 +83,9 @@ int main (int argc, char** argv)
 	abort ();
       }
 
-  int _STAGE5 = -1; int _INTF = -1; int    _OLD  = -1;    int _FREQ = -1;
-  int _INTN   = -1; int _INTU = -1; double _TIME = -1.e6; float  __TIME; 
+  int    _STAGE5 = -1;    int   _INTF = -1; int    _OLD  = -1;    int _FREQ = -1;
+  int    _INTN   = -1;    int   _INTU = -1; double _TIME = -1.e6; float  __TIME;
+  double _SCALE  = -1.e6; float __SCALE;
   
[…]

### 2020-09-05 Phase-2.x/Source/NamelistRead.f90
Phase version 2.3

@@ -29,19 +29,23 @@ subroutine NameListRead (NFLOW, STAGE5, INTF, INTN, INTU, OLD, FREQ, DT, TIME, S
   integer          :: i
   double precision :: pi
  
-  namelist /PHASE_CONTROL/  STAGE5, NFLOW, INTF, INTN, INTU, OLD, FREQ, DT, TIME, SCALE, NCTRL
-  namelist /PHASE_WAVEFORM/ TCTRL, ICTRL, PCTRL
+  namelist /PHASE_CONTROL/   STAGE5, NFLOW, INTF, INTN, INTU, OLD, FREQ, DT, TIME, SCALE
+  namelist /PHASE_WAVEFORM/  NCTRL
+  namelist /PHASE_WAVEFORM1/ TCTRL, ICTRL, PCTRL
   
   open  (unit = 100, file = 'Inputs/Phase.in', status = 'old')
   read  (unit = 100, nml  = PHASE_CONTROL) 
   close (unit = 100)
   
+  open  (unit = 100, file = 'Inputs/Waveform.in', status = 'old')
+  read  (unit = 100, nml  = PHASE_WAVEFORM)
+
   allocate (TCTRL (NCTRL))
   allocate (ICTRL (NCTRL))
   allocate (PCTRL (NCTRL))
 
-  open  (unit = 100, file = 'Inputs/Phase.in', status = 'old')
-  read  (unit = 100, nml  = PHASE_WAVEFORM) 
+  read  (unit = 100, nml  = PHASE_WAVEFORM1)
+
   close (unit = 100)
   
   pi = 4.*atan(1.)

### 2020-09-05 Phase-2.x/Source/Phase.cpp

@@ -1,29 +1,33 @@
 // Phase.cpp
 
+// #####################
 // PROGRAM ORGANIZATION:
-// 
-//       Phase:: Phase          ()
-// void  Phase:: Solve          (int _STAGE2, int _INTF, int _INTN, int _INTU, int _OLD, int _FREQ, double _TIME, double _SCALE)
-// void  Phase:: Read_Data      (int _STAGE2, int _INTF, int _INTN, int _INTU, int _OLD, int _FREQ, double _TIME, double _SCALE)
-// void  Phase:: Scan_Shift     ()
-// void  Phase:: Calc_Velocity  ()
-// void  Phase:: Initialize     ()
-// void  Phase:: Save           ()
-// void  Phase:: IslandDynamics ()
-// void  Phase:: CalcRMP        (double t)
-// void  Phase:: CalcChiZeta    (double t)
-// void  Phase:: Pack           (Array<double,1> y)
-// void  Phase:: Unpack         (Array<double,1> y)
-// void  Phase:: PackRhs        (Array<double,1> XkRHS, Array<double,1> YkRHS,
-//		                 Array<double,2> alphakpRHS, Array<double,2> betakpRHS, Array<double,1> dydt)
-// void  Phase:: Rhs            (double t, Array<double,1>& y, Array<double,1>& dydt)
-// void  Phase:: RK4Adaptive    (double& x, Array<double,1>& y, double& h, 
-//			         double& t_err, double acc, double S, int& rept,
-//			         int maxrept, double h_min, double h_max, int flag, int diag, FILE* file)
-// void  Phase:: RK4Fixed       (double& x, Array<double,1>& y, double h)
-// FILE* Phase:: OpenFilew      (char* filename)
-// FILE* Phase:: OpenFilew      (char* filename)
-// FILE* Phase:: OpenFilea      (char* filename)
+// $####################
+
+//        Phase:: Phase               ()
+// void   Phase:: Solve               (int _STAGE2, int _INTF, int _INTN, int _INTU, int _OLD, int _FREQ, double _TIME, double _SCALE)
[…]

### 2020-09-07 Papers/Paper2/Paper.tex
Phase version 2.3
Added PHASE_LIN flag

@@
 \section{Introduction}
+In the context of tokamak plasmas, a resonant magnetic perturbation (RMP) refers to an externally
+generated, (usually) static, helical magnetic perturbation that resonates at
+one or more rational surfaces within the plasma. Resonant magnetic perturbations have been successfully
+employed to compensate error fields (i.e., accidentally produced RMP), and, thereby,  to prevent the formation of
+locked modes in a wide variety of different types of tokamak discharge. \cite{error1,error2,error3} RMPs have also been used to either control or
+mitigate edge-localized-modes (ELMs) in H-mode tokamak discharges.\cite{elm1,elm2,elm3,elm4,elm5,elm6}
 
-\section{Cylindrical RMP Response Model}\label{s2}
+By far the most efficient manner in which to model the response of a tokamak plasma to an RMP is
+to employ an ``asymptotic matching'' approach.\cite{fkr,rfa, am1,am2,am3} 
+According to such an approach, the response of the plasma to the applied RMP is governed by a combination of flux-freezing and
+perturbed force balance---this combination is usually referred to as ``marginally-stable ideal-magnetohydrodynamics (MHD)", which is a misnomer because MHD {\em per se}\/ plays no
+role---everywhere in the plasma apart from a number of relatively narrow (in the radial direction) regions in which the applied
+perturbation resonates with the equilibrium magnetic field. Magnetic reconnection can take place within the resonant regions to
+produce relatively thin magnetic island chains. Within the resonant regions, the plasma response is governed by  linear or nonlinear 
+ two-fluid resistive-MHD, depending on whether the induced magnetic island widths are smaller or larger than the corresponding linear layer widths. 
+ Thus, when employing the asymptotic matching approach, the equations of marginally-stable ideal-MHD
+are solved in the so-called ``outer region'' that comprises most of the plasma (and the surrounding vacuum), the equations of 
+linear/nonlinear two-fluid resistive-MHD are solved in the various resonant layers that constitute the so-called ``inner region'', and the two
+sets of solutions are then asymptotically matched to one another.
+
+In the nonlinear resonant response regime, the evolution of the island width in a given resonant layer is governed by the familiar Rutherford island width evolution equation.\cite{ruth,ruth1}
+On the other hand, the phase evolution of the island chain is conventionally governed by the well-known no-slip constraint.\cite{rfa} According to this constraint,  plasma is trapped inside the
+magnetic separatrix of the magnetic island chain,
+which forces the chain to co-rotate with the local plasma flow. In reality, however, the plasma
+is able to diffuse resistively across the separatrix to some extent.\cite{slip1,slip2}
+
+The primary aim of this paper is to investigate 
+what happens when the no-slip constraint is relaxed in a recently-developed model of  RMP-induced
+suppression of ELMs in H-mode tokamak discharges.\cite{rftor} The secondary aim is to examine what happens when an improvement is made to the manner in which the resonant
+plasma response component of the model interpolates between the linear and the nonlinear regime.
+
+This paper is organized as follows. In Sect.~\ref{s2}, we develop a cylindrical version of
+our new resonant plasma response model. In Sect.~\ref{s3},  we use this cylindrical version as a guide for producing a toroidal
+version of the model.
+
+\section{Cylindrical Resonant Response Model}\label{s2}
 \subsection{Plasma Equilibrium}
@@
 plasma current density takes the form ${\bf j} =[0,0,j_\phi(r)]$, where $\mu_0\,j_\phi= (1/r)\,d(r\,B_\theta)/dr$. The
-so-called {\em safety-factor}, $q(r)=r\,B_\phi/(R_0\,B_\theta)$, parameterizes the helical pitches of equilibrium magnetic
+so-called ``safety-factor'', $q(r)=r\,B_\phi/(R_0\,B_\theta)$, parameterizes the helical pitches of equilibrium magnetic
 field-lines.
@@
 \subsection{Plasma Response to RMP}
-Consider the response of the plasma to an externally generated, static, helical, resonant magnetic perturbation (RMP). 
+Consider the response of the plasma to an externally generated, static, helical, RMP. 
 Suppose that the RMP has $m$ periods in the poloidal direction, and $n$ periods in the toroidal direction.
@@
 
-The response of the plasma to the RMP is governed by the equations of marginally stable, ideal-MHD everywhere in the
-plasma, apart from a relatively narrow (in $r$) region in the vicinity of the so-called {\em rational surface}, minor radius $r_s$, 
+The response of the plasma to the RMP is governed by the equations of marginally-stable, ideal-MHD everywhere in the
+plasma, apart from a relatively narrow (in $r$) region in the vicinity of the so-called  ``rational surface'', minor radius $r_s$, 
 at which $q(r_s)=m/n$.\cite{rfa}
 
-It is convenient to parameterize the RMP in terms of the so-called {\em vacuum magnetic flux}, ${\mit\Psi}_v(t) = |{\mit\Psi}_v|\,{\rm e}^{-{\rm i}\,\varphi_v}$,
+It is convenient to parameterize the RMP in terms of the so-called ``vacuum magnetic flux'', ${\mit\Psi}_v(t) = |{\mit\Psi}_v|\,{\rm e}^{-{\rm i}\,\varphi_v}$,
 which is defined to be the value of $\hat{\psi}(r,t)$ at radius $r_s$ in the presence of the RMP, but in the absence of plasma. Here,
 $\varphi_v$ is the helical phase of the RMP. Likewise, the response of the plasma in the vicinity of the rational
-surface is parameterized in terms of the so-called {\em reconnected magnetic flux}, ${\mit\Psi}_s(t)=|{\mit\Psi}_s|\,{\rm e}^{\,{\rm i}\,\varphi_s}$, 
+surface is parameterized in terms of the so-called ``reconnected magnetic flux'', ${\mit\Psi}_s(t)=|{\mit\Psi}_s|\,{\rm e}^{\,{\rm i}\,\varphi_s}$, 
 which is the actual value of $\hat{\psi}(r,t)$ at radius $r_s$. Here, $\varphi_s$ is the helical phase of
@@
 $E_{ss}= [d\hat{\psi}_s/d\ln r]_{r_{s-}}^{r_{s+}}$, where $\hat{\psi}_s(r)$
-is a solution of the marginally stable, ideal-MHD equations, for the case of an $m$, $n$ helical
+is a solution of the marginally-stable, ideal-MHD equations, for the case of an $m$, $n$ helical
 perturbation, that satisfies physical boundary conditions at $r=0$ and $r=a$, in the absence of the
@@
 $E_{sv}= [d\hat{\psi}_v/d\ln r]_{r_{s-}}^{r_{s+}}$, where $\hat{\psi}_v(r)$
-is a solution of the marginally stable, ideal-MHD equations, for the case of an $m$, $n$ helical
+is a solution of the marginally-stable, ideal-MHD equations, for the case of an $m$, $n$ helical
 perturbation, that satisfies physical boundary conditions at $r=0$ and $r=a$, in the presence of the
@@
 Ref.~\onlinecite{rf1} that the appropriate linear response regime for an RMP resonant in the pedestal of a typical DIII-D H-mode discharge
-is the so-called  {\em first semi-collisional regime}, which is indeed a constant-$\psi$ response regime. Moreover, if the appropriate linear response regime
+is the so-called  ``first semi-collisional regime'', which is indeed a constant-$\psi$ response regime. Moreover, if the appropriate linear response regime
 is constant-$\psi$ then so is the appropriate nonlinear response regime, because the constant-$\psi$ constraint is
@@
 
-Equation~(\ref{e1}) can be rewritten as an {\em amplitude evolution equation},
+Equation~(\ref{e1}) can be rewritten as an ``amplitude evolution equation'',
 \begin{equation}\label{e3}
@@
 \end{equation}
-combined with a {\em phase evolution equation}, 
+combined with a ``phase evolution equation'', 
 \begin{equation}\label{e4}
@@
 \end{equation}
-The final term on the right-hand side of Eq.~(\ref{e4}) is termed the {\em slip frequency}, and is the difference between the helical phase velocity of
+The final term on the right-hand side of Eq.~(\ref{e4}) is termed the ``slip-frequency'', and is the difference between the helical phase velocity of
 the reconnected magnetic flux and that expected on the  assumption that the flux is convected by the plasma flow at the
-rational surface (i.e., $d\varphi_s/dt=\omega_s$). In general, the slip frequency is non-zero because the plasma in the vicinity of the rational surface is capable of diffusing resistively 
+rational surface (i.e., $d\varphi_s/dt=\omega_s$). In general, the slip-frequency is non-zero because the plasma in the vicinity of the rational surface is capable of diffusing resistively 
 through the linear layer structure.
@@
 \subsection{Nonlinear Response Regime}
-In the nonlinear response regime, Eq.~(\ref{e3}) generalizes to the {\em Rutherford island width evolution equation}:\,\cite{ruth,ruth1}
+In the nonlinear response regime, Eq.~(\ref{e3}) generalizes to the ``Rutherford island width evolution equation'':\,\cite{ruth,ruth1}
 \begin{equation}\label{e5}
@@
 
-Equation~(\ref{e5}) is usually coupled with the so-called {\em no-slip constraint}:\,\cite{rfa}
+Equation~(\ref{e5}) is usually coupled with the so-called ``no-slip constraint'':\,\cite{rfa}
 \begin{equation}\label{e6}
@@
 \end{equation}
-The final term on the right-hand side of the previous equation is the {\em nonlinear slip frequency}. In general,
+The final term on the right-hand side of the previous equation is the ``nonlinear slip-frequency''. In general,
 we would expect this frequency to be relatively small (because it is generally the case that $|\omega_s|\,\tau_R\,(W_s/r_s)\gg 1$
 for fully-developed magnetic islands in high-temperature tokamak plasmas\,\cite{rf1,slip2}). Nevertheless, the
-nonlinear slip frequency may be non-negligible for developing island chains, which is why we are including it in our analysis.
-(Note that the nonlinear slip frequency does not appear in rigorous island calculations, such as
+nonlinear slip-frequency may be non-negligible for developing island chains, which is why we are including it in our analysis.
+(Note that the nonlinear slip-frequency does not appear in rigorous island calculations, such as
 that described in Ref.~\onlinecite{rfisland}, and references therein, because such calculations depend crucially on
-complicated hierarchical ordering assumptions, according to which the nonlinear slip frequency is negligible.)
+complicated hierarchical ordering assumptions, according to which the nonlinear slip-frequency is negligible.)
 
@@
 where
-\begin{equation}
+\begin{equation}\label{e23x}
 W_s = 4\left(\frac{\sqrt{X_s^{\,2}+Y_s^{\,2}}}{s_s\,r_s\,B_\theta(r_s)}\right)^{1/2} r_s.
@@
 
-\section{Modified Toroidal RMP Response Model}
+\section{Modified Toroidal Resonant Response Model}\label{s3}
 Our toroidal model of the response of a tokamak plasma to a static, externally generated, RMP is described in
-detail in Ref.~\onlinecite{rftor}. In the light of the composite model developed in Sect.~\ref{s2}, we shall
-modify the resonant plasma response component of our  toroidal response model; this component is described in Appendix~D of Ref.~\onlinecite{rftor}.
+detail in Ref.~\onlinecite{rftor}. In the light of the composite cylindrical resonant response model developed in Sect.~\ref{s2}, we shall
+modify the resonant  response component of the aforementioned toroidal  model; this component is described in Appendix~D of Ref.~\onlinecite{rftor}.
 
@@
 \begin{align}
-\hat{W}_k &=\frac{2\,{\cal I}}{\hat{a}\,\hat{r}_k}\left(\frac{q}{g\,s}\right)_{\hat{r}_k} |\hat{\mit\Psi}_k|^{\,1/2},\\[0.5ex]
+\hat{W}_k &=\frac{2\,{\cal I}}{\hat{a}\,\hat{r}_k}\left(\frac{q}{g\,s}\right)_{\hat{r}_k}^{1/2} |\hat{\mit\Psi}_k|^{\,1/2},\\[0.5ex]
 \hat{\delta}_k &= \frac{\delta_{\rm SC}(\hat{r}_k)}{R_0\,\hat{a}\,\hat{r}_k},
@@
 \begin{equation}
-\hat{\varpi}_k= m_k\,\hat{\mit\Omega}_\theta(\hat{r}_k,\hat{t})-n\,\hat{\mit\Omega}_\phi(\hat{r}_k,\hat{t}),
+\hat{\varpi}_k= \hat{\varpi}_{k0}+m_k\,{\mit\Delta}\hat{\mit\Omega}_\theta(\hat{r}_k,\hat{t})-n\,{\mit\Delta}\hat{\mit\Omega}_\phi(\hat{r}_k,\hat{t}),
 \end{equation}
-and $\hat{\mit\Omega}_\theta= {\mit\Omega}_\theta\,\tau_A$, $\hat{\mit\Omega}_\phi= {\mit\Omega}_\phi\,\tau_A$. Equation~(\ref{e19}) represents
-a major improvement to Eq.~(D6) that takes into  account the finite slip frequencies of the magnetic island chains induced at
-the various rational surfaces in the plasma.
+and $\hat{\varpi}_{k0}= \varpi_{k0}\,\tau_A$, $\hat{\mit\Omega}_\theta= {\mit\Delta}{\mit\Omega}_\theta\,\tau_A$, and $\hat{\mit\Omega}_\phi= {\mit\Delta}{\mit\Omega}_\phi\,\tau_A$.
+Here, $\varpi_{k0}$
+is the so-called ``natural frequency'' at the $k$th rational surface; this quantity is defined as the helical phase velocity of a naturally unstable island chain, resonant at the surface, in the
+absence of an RMP (or any other island chains). On the other hand,  ${\mit\Delta}{\mit\Omega}_\theta$ and ${\mit\Delta}{\mit\Omega}_\phi$ are the changes in the plasma
+poloidal and toroidal velocity profiles, respectively, induced by the electromagnetic torques that develop in the vicinities of the various rational surfaces in the plasma.
+Equation~(\ref{e19}) represents
+a major improvement to Eq.~(D6) that takes into  account the finite slip-frequencies of the magnetic island chains induced at
+the various rational surfaces in the plasma. In the absence of a finite slip-frequency, the right-hand side of Eq.~(\ref{e19}) would be zero.
 
@@
 = \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,Y_{k'}
-+\sin\xi_{kk'}\,X_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\sin\zeta_k.\label{e22}
++\sin\xi_{kk'}\,X_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\sin\zeta_k,\label{e22}
 \end{align}
-Equations (\ref{e15}), (\ref{e19}), (\ref{e21}), and (\ref{e22}) are the toroidal generalizations of Eqs.~(\ref{e9}), (\ref{e10}), (\ref{e11}), and (\ref{e12}), respectively.
+where
+\begin{equation}\label{e23}
+\hat{W}_k =\frac{2\,{\cal I}}{\hat{a}\,\hat{r}_k}\left(\frac{q}{g\,s}\right)^{1/2}_{\hat{r}_k} (X_k^{\,2} + Y_k^{\,2})^{\,1/4}.
+\end{equation}
+Equations (\ref{e15}), (\ref{e19}), (\ref{e21}), (\ref{e22}) and (\ref{e23}) are the toroidal generalizations of Eqs.~(\ref{e9}), (\ref{e10}), (\ref{e11}), (\ref{e12}), and (\ref{e23x}), respectively.
 
@@
 
-\bibitem{rfa} R.~Fitzpatrick, Nucl.\ Fusion {\bf 33}, 1049 (1993).
+\bibitem{error1} J.T.~Scoville, and R.J.~La\,Haye, Nucl.\ Fusion {\bf 43}, 250 (2003).
+
+\bibitem{error2}  J.-K.~Park, M.J.~Schaffer, J.E.~Menard, and A.H.~Boozer  Phys.\  Rev.\  Lett.\  {\bf 99}, 195003 (2007).
+
+\bibitem{error3} N.M.~Ferraro, J.-K.~Park, C.E.~Myers, A.~Brooks, S.P.~Gerhardt, J.E.~Menard, S.~Munaretto, and M.L.~Reinke, Nucl.\ Fusion {\bf 59}, 086021 (2019).
+
+\bibitem{elm1}  T.E.~Evans, R.A.~Moyer, J.G.~Watkins, P.R.~Thomas, T.H.~Osborne, J.A.~Boedo, M.E.~Fenstermacher, K.H.~Finken, R.J.~Groebner, M.~Groth, {\it et al.},  
+Phys.\ Rev.\ Lett.\ {\bf 92}, 235003 (2004).
+
+\bibitem{elm2} Y.~Liang,  H.R.~Koslowski, P.R.~Thomas, E.~Nardon, B.~Alper, P.~Andrew, Y.~Andrew, G.~Arnoux,  Y.~Baranov, M.~B\'{e}coulet, {\it et al.},  
+Phys.\ Rev.\ Lett.\ {\bf 98}, 265004 (2007).
+
+\bibitem{elm3} W.~Suttrop,  T.~Eich, J.C.~Fuchs, S.~G\"{u}nter, A.~Janzer, A.~Herrmann, A.~Kallenbach, P.T.~Lang, T.~Lunt, M.~Maraschek, {\it et al.},   
+Phys.\ Rev.\ Lett.\ {\bf 106}, 225004 (2011).
+
+\bibitem{elm4} Y.M.~Jeon,  J.-K.~Park, S.W.~Yoon, W.H.~Ko, S.G.~Lee, K.D.~Lee, G.S.~Yun, Y.U.~Nam, W.C.~Kim, J.-G.~Kwak, K.S.~Lee, H.K.~Kim, and H.L.~Yang, {\it et al.}, 
+Phys.\ Rev.\ Lett.\ {\bf 109}, 035004 (2012).
+
+\bibitem{elm5} A.~Kirk, I.T.~Chapman, Y.~Liu, P.~Cahyna, P.~Denner, G.~Fishpool, C.J.~Ham, J.R.~Harrison, Y.~Liang, E.~Nardon, S.~Saarelma, R.~Scannell, A.J.~Thornton, and  MAST Team, 
+Nucl.\  Fusion {\bf 53}, 043007 (2013).
+
+\bibitem{elm6} T.~Sun,  Y.~Liang, Y.Q.~Liu, S.~Gu, X.~Yang, W.~Guo, T.~Shi, M.~Jia, L.~Wang, B.~Lyu, {\it et al.},  
+Phys.\ Rev.\ Lett.\  {\bf 117}, 115001 (2016).
 
@@
 
+\bibitem{rfa} R.~Fitzpatrick, Nucl.\ Fusion {\bf 33}, 1049 (1993).
+
 \bibitem{am1} R.~Fitzpatrick, R.J.~Hastie, T.J.~Martin, and C.M.~Roach, Nucl.\ Fusion {\bf 33}, 1533 (1993).
 
+\bibitem{am2} A.H.~Glasser, Z.R.~Wang, and J.-K.~Park, Phys.\ Plasmas {\bf 23}, 112506 (2016).
+
+\bibitem{am3} R.~Fitzpatrick, Phys.\ Plasmas {\bf 24}, 072506 (2017).
+
 \bibitem{ruth} P.H.~Rutherford,  Phys.\ Fluids  {\bf 16}, 1903 (1973).
+
+\bibitem{ruth1} P.H.~Rutherford, in  {\it Basic Physical Processes of
+Toroidal Fusion Plasmas}, Proc.\ Course and Workshop, Varenna, 1985. (Commission of the European Communities, Brussels, 1985.) Vol.~2, p.~531.
+
+\bibitem{slip1} L.G.~Eliseev, N.V.~Ivanov, A.M.~Kakurin, A.V.~Melnikov, and S.V.~Perfilov, Phys.\ Plasmas {\bf 22}, 052504 (2015).
+
+\bibitem{slip2} W.~Huang, and P.~Zhu, Phys.\ Plasmas {\bf 27}, 022514 (2020).
+
+\bibitem{rftor} R.~Fitzpatrick, and A.O.~Nelson, Phys.\ Plasmas {\bf 27}, 072501 (2020).
+
+\bibitem{rftor1} R.~Fitzpatrick,  ``Modelling $q_{95}$ Windows for the Suppression of Edge Localized
+Modes by Resonant Magnetic Perturbations in the DIII-D Tokamak", submitted to Physics of Plasmas (2020).
 
@@
 
-\bibitem{ruth1} P.H.~Rutherford, in  {\it Basic Physical Processes of
-Toroidal Fusion Plasmas}, Proc.\ Course and Workshop, Varenna, 1985. (Commission of the European Communities, Brussels, 1985.) Vol.~2, p.~531.
-
-\bibitem{slip1} L.G.~Eliseev, N.V.~Ivanov, A.M.~Kakurin, A.V.~Melnikov, and S.V.~Perfilov, Phys.\ Plasmas {\bf 22}, 052504 (2015).
-
-\bibitem{slip2} W.~Huang, and P.~Zhu, Phys.\ Plasmas {\bf 27}, 022514 (2020).
-
-\bibitem{rfisland} R.~Fitzpatrick, Phys.\ Plasmas {\bf 25}, 082513 (2018);
+\bibitem{rfisland} R.~Fitzpatrick, Phys.\ Plasmas {\bf 25}, 082513 (2018).
 
@@
 M.B.~Safonova, V.V.~Volkov, and the T-10 Team, Nucl.\ Fusion {\bf 43} 681 (2003).
-
-\bibitem{rftor} R.~Fitzpatrick, and A.O.~Nelson, Phys.\ Plasmas {\bf 27}, 072501 (2020).
-
 \end{thebibliography}

### 2020-09-07 Phase-2.x/Source/NamelistRead.f90

@@ -1,6 +1,6 @@
 ! Function to read PHASE namelist
 
-subroutine NameListRead (NFLOW, STAGE5, INTF, INTN, INTU, OLD, FREQ, DT, TIME, SCALE, NCTRL, xTCTRL, xICTRL, xPCTRL) &
+subroutine NameListRead (NFLOW, STAGE5, INTF, INTN, INTU, OLD, FREQ, LIN, DT, TIME, SCALE, NCTRL, xTCTRL, xICTRL, xPCTRL) &
      bind (c, name = 'NameListRead')
 
   use, intrinsic :: iso_c_binding, only: c_int, c_double
@@ -13,6 +13,7 @@ subroutine NameListRead (NFLOW, STAGE5, INTF, INTN, INTU, OLD, FREQ, DT, TIME, S
   integer (kind = c_int),    intent (inout) :: INTU
   integer (kind = c_int),    intent (inout) :: OLD
   integer (kind = c_int),    intent (inout) :: FREQ
+  integer (kind = c_int),    intent (inout) :: LIN
   real    (kind = c_double), intent (inout) :: DT
   real    (kind = c_double), intent (inout) :: TIME
   real    (kind = c_double), intent (inout) :: SCALE
@@ -29,7 +30,7 @@ subroutine NameListRead (NFLOW, STAGE5, INTF, INTN, INTU, OLD, FREQ, DT, TIME, S
   integer          :: i
   double precision :: pi
  
-  namelist /PHASE_CONTROL/   STAGE5, NFLOW, INTF, INTN, INTU, OLD, FREQ, DT, TIME, SCALE
+  namelist /PHASE_CONTROL/   STAGE5, NFLOW, INTF, INTN, INTU, OLD, FREQ, LIN, DT, TIME, SCALE
   namelist /PHASE_WAVEFORM/  NCTRL
   namelist /PHASE_WAVEFORM1/ TCTRL, ICTRL, PCTRL
   

### 2020-09-09 Papers/Paper2/Paper.tex
First draft of Paper2

@@
 
-\title {Modelling $q_{95}$ Windows for the Suppression of Edge Localized Modes by Resonant Magnetic Perturbations in the DIII-D Tokamak: Relaxation of the No-Slip
-Constraint}
+\title {Further Modeling of $q_{95}$ Windows for the Suppression of Edge Localized Modes by Resonant Magnetic Perturbations in the DIII-D Tokamak}
 
@@
 
-%\begin{abstract}
-%\end{abstract}
+\begin{abstract}
+An improved resonant plasma response model that describes the interaction between a tokamak plasma and a resonant magnetic perturbation  (RMP) is developed. 
+The model interpolates between the linear and the nonlinear response regimes, and takes into account the fact that the slip-frequency
+is non-zero in the nonlinear regime. The improved model is incorporated into the {\tt EPEC} toroidal asymptotic matching code.
+The modified {\tt EPEC} code is used to model RMP-induced edge-localized-modr mitigation/suppression in DIII-D H-mode discharge \#145380. 
+Allowing for a finite slip-frequency (i.e., relaxing the so-called no-slip constraint) is found to slightly facilitate the locking of
+driven magnetic island chains to the RMP. The previously obtained conclusion 
+that the response of a typical H-mode tokamak plasma to an RMP cannot be accurately modeled by linear theory is confirmed.
+The previously obtained conclusion that the best agreement between theory and observations is achieved by assuming that the
+natural frequencies of tearing modes, in the absence of the RMP, are determined by the local equilibrium ${\bf E}\times{\bf B}$ frequency is also confirmed.
+\end{abstract}
+
+\maketitle
 
@@
 generated, (usually) static, helical magnetic perturbation that resonates at
-one or more rational surfaces within the plasma. Resonant magnetic perturbations have been successfully
-employed to compensate error fields (i.e., accidentally produced RMP), and, thereby,  to prevent the formation of
-locked modes in a wide variety of different types of tokamak discharge. \cite{error1,error2,error3} RMPs have also been used to either control or
-mitigate edge-localized-modes (ELMs) in H-mode tokamak discharges.\cite{elm1,elm2,elm3,elm4,elm5,elm6}
+one or more ``rational'' magnetic flux surfaces within the plasma. Resonant magnetic perturbations have been successfully
+employed to compensate error fields (i.e., accidentally produced RMPs), and, thereby,  to prevent the associated formation of
+locked modes, in a wide variety of different types of tokamak discharge. \cite{error1,error2,error3} RMPs have also been  successfully used to either  
+mitigate or completely suppress  edge-localized-modes (ELMs) in H-mode tokamak discharges.\cite{elm1,elm2,elm3,elm4,elm5,elm6}
 
-By far the most efficient manner in which to model the response of a tokamak plasma to an RMP is
-to employ an ``asymptotic matching'' approach.\cite{fkr,rfa, am1,am2,am3} 
-According to such an approach, the response of the plasma to the applied RMP is governed by a combination of flux-freezing and
-perturbed force balance---this combination is usually referred to as ``marginally-stable ideal-magnetohydrodynamics (MHD)", which is a misnomer because MHD {\em per se}\/ plays no
-role---everywhere in the plasma apart from a number of relatively narrow (in the radial direction) regions in which the applied
+``Asymptotic matching'' is by far the most efficient method for modeling the response of a tokamak plasma to an RMP.\cite{fkr,rfa, am1,am2,am3} 
+According to the asymptotic matching approach, the response of the plasma to the applied RMP is governed by a combination of flux-freezing and
+perturbed force balance---this combination is usually referred to as ``marginally-stable ideal-magnetohydrodynamics (MHD)"---everywhere in the plasma apart from a number of relatively narrow (in the radial direction) regions in which the applied
 perturbation resonates with the equilibrium magnetic field. Magnetic reconnection can take place within the resonant regions to
-produce relatively thin magnetic island chains. Within the resonant regions, the plasma response is governed by  linear or nonlinear 
- two-fluid resistive-MHD, depending on whether the induced magnetic island widths are smaller or larger than the corresponding linear layer widths. 
+produce relatively narrow magnetic island chains. Within the resonant regions, the plasma response is governed by  linear or nonlinear 
+ two-fluid resistive-MHD, depending on whether the induced magnetic island widths are smaller or larger, respectively, than the corresponding linear layer widths. 
  Thus, when employing the asymptotic matching approach, the equations of marginally-stable ideal-MHD
@@
 
-In the nonlinear resonant response regime, the evolution of the island width in a given resonant layer is governed by the familiar Rutherford island width evolution equation.\cite{ruth,ruth1}
-On the other hand, the phase evolution of the island chain is conventionally governed by the well-known no-slip constraint.\cite{rfa} According to this constraint,  plasma is trapped inside the
-magnetic separatrix of the magnetic island chain,
+In the nonlinear resonant response regime, the evolution of the island chain width in a given resonant layer is governed by the familiar ``Rutherford island width evolution equation''.\cite{ruth,ruth1}
+On the other hand, the phase evolution of the island chain is conventionally governed by the well-known ``no-slip constraint''.\cite{rfa} According to this constraint,  plasma is trapped inside the
+magnetic separatrix of the island chain,
 which forces the chain to co-rotate with the local plasma flow. In reality, however, the plasma
@@
 
-The primary aim of this paper is to investigate 
-what happens when the no-slip constraint is relaxed in a recently-developed model of  RMP-induced
-suppression of ELMs in H-mode tokamak discharges.\cite{rftor} The secondary aim is to examine what happens when an improvement is made to the manner in which the resonant
-plasma response component of the model interpolates between the linear and the nonlinear regime.
-
-This paper is organized as follows. In Sect.~\ref{s2}, we develop a cylindrical version of
-our new resonant plasma response model. In Sect.~\ref{s3},  we use this cylindrical version as a guide for producing a toroidal
-version of the model.
+The recently developed, toroidal, asymptotic matching code {\tt EPEC} has been used to simulate 
+RMP-induced ELM mitigation/suppression in DIII-D H-mode plasmas.\cite{rftor,rftor1}
+The original {\tt EPEC} model incorporates the no-slip constraint.
+The first aim of this paper is to investigate 
+what happens when the no-slip constraint is relaxed in the aforementioned {\tt EPEC} simulations.
+ The second aim is to examine what happens when an improvement is made to the manner in which the resonant
+plasma response component of the {\tt EPEC} model interpolates between the linear and the nonlinear regimes.
 
 \section{Cylindrical Resonant Response Model}\label{s2}
+\subsection{Introduction}
+For the sake of simplicity, and also to make a better connection with previous research, let us commence our investigation by discussing
+the resonant response of a tokamak plasma to an RMP in cylindrical geometry.
+
 \subsection{Plasma Equilibrium}
@@
 The reasoning behind the imposition of this constraint is that the plasma is trapped inside the
-magnetic separatrix of the magnetic island chain that forms in the vicinity of the rational surface,
+magnetic separatrix of the  island chain that forms in the vicinity of the rational surface,
 which forces the chain to co-rotate with the local plasma flow. However, in reality, the plasma
@@
 If we define $X_s = |{\mit\Psi}_s|\,\cos\varphi_s$, $Y_s = |{\mit\Psi}_s|\,\sin\varphi_s$, $X_v = |{\mit\Psi}_v|\,\cos\varphi_v$, and $Y_v = |{\mit\Psi}_v|\,\sin\varphi_v$ 
-then the previous two equations are more conveniently written in the nonsingular (when $|{\mit\Psi}_s|=0$) forms:\,\cite{slip1,slip2,slip3}
+then the previous two equations are more conveniently written in the non-singular (when $|{\mit\Psi}_s|=0$) forms:\,\cite{slip1,slip2,slip3}
 \begin{align}\label{e11}
@@
 \section{Modified Toroidal Resonant Response Model}\label{s3}
-Our toroidal model of the response of a tokamak plasma to a static, externally generated, RMP is described in
-detail in Ref.~\onlinecite{rftor}. In the light of the composite cylindrical resonant response model developed in Sect.~\ref{s2}, we shall
-modify the resonant  response component of the aforementioned toroidal  model; this component is described in Appendix~D of Ref.~\onlinecite{rftor}.
+Let us now generalize our investigation to toroidal geometry.
+
+The toroidal model of the response of a tokamak plasma to a static, externally generated, RMP that is implemented in the {\tt EPEC} code\,\cite{rftor1} is described in
+detail in Ref.~\onlinecite{rftor}. In the light of the composite cylindrical resonant response model developed in Sect.~\ref{s2}, we propose to 
+modify the resonant  response component of the {\tt EPEC} model (this component is described in Appendix~D of Ref.~\onlinecite{rftor}).
 
@@
 \begin{align}\label{e15}
-\left(\hat{W}_k + \hat{\delta}_k\right){\cal S}_k\,\frac{d\hat{\mit\Psi}_k}{d\hat{t}} &= \sum_{k'=1,K}\hat{E}_{kk'}\hat{\mit\Psi}_{k'}\,\cos(\varphi_k-\varphi_{k'}-\xi_{kk'})
+\left(\hat{W}_k + \hat{\delta}_k\right){\cal S}_k\,\frac{d\hat{\mit\Psi}_k}{d\hat{t}} &= \sum_{k'=1,K}\hat{E}_{kk'}\,\hat{\mit\Psi}_{k'}\,\cos(\varphi_k-\varphi_{k'}-\xi_{kk'})
 +\hat{E}_{kk}\,\hat{\chi}_k\,\cos(\varphi_k-\zeta_k),\\[0.5ex]
@@
 \begin{equation}
-\hat{\varpi}_k= \hat{\varpi}_{k0}+m_k\,{\mit\Delta}\hat{\mit\Omega}_\theta(\hat{r}_k,\hat{t})-n\,{\mit\Delta}\hat{\mit\Omega}_\phi(\hat{r}_k,\hat{t}),
+\hat{\varpi}_k= \hat{\varpi}_{k\,0}+m_k\,{\mit\Delta}\hat{\mit\Omega}_\theta(\hat{r}_k,\hat{t})-n\,{\mit\Delta}\hat{\mit\Omega}_\phi(\hat{r}_k,\hat{t}),
 \end{equation}
-and $\hat{\varpi}_{k0}= \varpi_{k0}\,\tau_A$, $\hat{\mit\Omega}_\theta= {\mit\Delta}{\mit\Omega}_\theta\,\tau_A$, and $\hat{\mit\Omega}_\phi= {\mit\Delta}{\mit\Omega}_\phi\,\tau_A$.
-Here, $\varpi_{k0}$
+and $\hat{\varpi}_{k\,0}= \varpi_{k\,0}\,\tau_A$, $\hat{\mit\Omega}_\theta= {\mit\Delta}{\mit\Omega}_\theta\,\tau_A$, and $\hat{\mit\Omega}_\phi= {\mit\Delta}{\mit\Omega}_\phi\,\tau_A$.
+Here, $\varpi_{k\,0}$
 is the so-called ``natural frequency'' at the $k$th rational surface; this quantity is defined as the helical phase velocity of a naturally unstable island chain, resonant at the surface, in the
@@
 If we define $X_k = \hat{\mit\Psi}_k\,\cos\varphi_k$ and $Y_k=\hat{\mit\Psi}_k\,\sin\varphi_k$ then Eqs.~(\ref{e15}) and (\ref{e19}) are
-more conveniently written in the nonsingular (when $\hat{\mit\Psi}_k=0$) forms
+more conveniently written in the non-singular (when $\hat{\mit\Psi}_k=0$) forms
 \begin{align}\label{e21}
@@
 
+\section{EPEC Modeling of DIII-D Discharge \#145380}\label{s4}
+\subsection{Introduction}
+DIII-D discharge \#145380 is an ITER-Similar-Shape (ISS), ELMing, H-mode discharge, with a toroidal magnetic field $B_T=-1.9\,{\rm T}$, in which the
+plasma current, $I_p$, is slowly ramped over a 2 second interval in order to scan the magnetic safety-factor.\cite{d3d,d3d2} The majority ions are Deuterium, whereas the
+minority ions are Carbon~VI.
+Figure~\ref{fig1} gives an overview of this discharge. ${\mit\Psi}_N$ is the conventional normalized poloidal magnetic flux.
+A static RMP is applied to the plasma by running steady $n=3$ currents through the I-coil system.\cite{icoil}
+Three windows of ELM suppression or mitigation are evident: the first (in which ELMs are mitigated, but not
+entirely suppressed) extends from $t=2840$--$2980$ ms; the
+second (in which ELM are entirely suppressed) extends from $t=3320$--$3560$ ms; and the third (in which ELMs are
+entirely suppressed) extends from $t=3880$--$4200$ ms. The 
+first, second, and third ELM-suppression/mitigation windows extend over the $\overline{q_{95}}$ ranges $3.88$--$3.94$, $3.62$--$3.73$,
+and $3.33$--$3.48$, respectively. Here, $\overline{q_{95}}$ is least-squares linear fit to the variation of the safety-factor at the ${\mit\Psi}_N = 0.95$ flux surface with time.
+
+\subsection{Relaxation of No-Slip Constraint}\label{s4a}
+As is discussed in Ref.~\onlinecite{rftor1}, the best agreement between the predictions of the {\tt EPEC} code and experimental observations is
+obtained by assuming that the natural frequencies at the various rational surfaces in the plasma are determined by the
+local equilibrium ${\bf E}\times {\bf B}$ frequencies. In other words, 
+\begin{equation}\label{e24}
+\varpi_{k\,0} =-n\,\omega_E({\mit\Psi}_{p\,k}),
+\end{equation}
+where 
+\begin{equation}
+\omega_E({\mit\Psi}_p) = -\frac{d{\mit\Phi}}{d{\mit\Psi}_p}.
+\end{equation}
+Here, ${\mit\Phi}({\mit\Psi}_p)$ is the equilibrium scalar electric potential, ${\mit\Psi}_p$ the equilibrium poloidal magnetic flux (divided by $2\pi$), 
+and ${\mit\Psi}_{p\,k}$  the value of ${\mit\Psi}_p$ at the $k$th rational surface.  Equation~(\ref{e24}) holds at
+every rational surface in all of the simulations discussed in Sect.~\ref{s4a}.
+
+\subsubsection{No-Slip Constraint Imposed}
+In our first simulation, the no-slip constraint is imposed at all rational surfaces in the plasma. This implies that the resonant response
+model at the $k$th rational surface consists of Eq.~(\ref{e15}) and Eq.~(\ref{e19}), with the right-hand side of the latter equation
+set to zero; in other words,  the slip-frequency is set to zero at the $k$th rational surface.
+
+The upper panel of Fig.~\ref{fig2} shows the natural frequencies, in the absence of the RMP, of the various  $n=3$ tearing modes 
+ that are resonant in the pedestal of DIII-D discharge \#145380. It can be seen that 
+the natural frequencies of the $m=11$ (brown), the $m=10$ (magenta), and the $m=9$ (cyan), tearing modes have their
+zero-crossings in the  first, second, and third, ELM-suppression/mitigation window, respectively. 
+  The lower panel of Fig.~\ref{fig2} shows the natural frequencies, in the presence of the RMP, of the various $n=3$
+tearing modes that are resonant in the pedestal. It is apparent that if the magnitude of the natural frequency in the absence of the RMP falls below about
+$3\,{\rm krad/s}$ then the associated tearing mode locks to the RMP (i.e., its true natural frequency becomes zero).
+
+The upper panel of Fig.~\ref{fig3} shows the widths of the various vacuum magnetic island chains driven by the applied $n=3$ RMP in the pedestal region as functions of $
+\overline{q_{95}}$.
+The vacuum island widths are the  expected island widths in the absence of any shielding of driven magnetic reconnection due to
+plasma flow; in other words, they are the  widths of the island chains that would be driven if all of the natural frequencies were zero. It can be seen that
+the driven magnetic island chains extend over most of the pedestal, implying a very significant degradation in pedestal energy and particle confinement due to the
+expected flattening of the density and temperature profiles across the chains.\cite{flat} Moreover, the driven island chains at the
+bottom of the pedestal overlap, implying that the magnetic field in this region is rendered stochastic. The lower panel
+of Fig.~\ref{fig3} shows the actual widths of the various magnetic island chains driven by the applied $n=3$ RMP as functions of time. It is apparent 
+that the true island widths are generally much smaller than the vacuum island widths, as a consequence of the shielding of driven magnetic
+reconnection due to plasma flow. However, the shielding breaks down at various rational surfaces when the associated natural frequency is zero (see the lower panel of
+Fig.~\ref{fig3}). In this situation, the driven island width is similar to the vacuum island width.
+
+According to the prevailing hypothesis, RMP-induced ELM mitigation/suppression in an H-mode tokamak discharge occurs when a comparatively wide, locked, magnetic
+island chain is generated at the top of the pedestal.\cite{hu} The temperature and density flattening associated with the chain
+is presumed to limit the radial expansion of the
+pedestal, and, thereby, prevent it from attaining a width sufficient to destabilize peeling-ballooning modes\,\cite{connor}  (which are thought to trigger ELMs).\cite{d3d}
+It has also been suggested that  the well-known ``density pump-out" phenomenon, which is often observed when RMPs are applied
+to H-mode tokamak plasmas, is associated with the formation of overlapping island chains
+at the bottom of the pedestal.\cite{hu}
+
+According to Fig.~\ref{fig3},  
+ the comparatively wide, $m=11$ (brown),  $m=10$ (magenta), and  $m=9$ (cyan), locked magnetic island chains which are predicted to be driven by the RMP in the pedestal of DIII-D discharge \#145380 line up
+fairly well with the first, second, and third, ELM-suppression/mitigation windows, respectively. To be more exact, the island chains are located at
+the top of the pedestal (i.e., ${\mit\Psi}_N=0.925$), and also occur in roughly the correct time intervals. This is consistent with the hypothesis that the formation of locked
+magnetic island chains at the top of the pedestal causes ELM mitigation/suppression. 
+Note that overlapping island chains
+are also driven at the bottom of the pedestal; as has already been mentioned, such island chains are associated with the density pump-out phenomenon.
+
+In principle, the calculation shown in Figs.~\ref{fig2} and \ref{fig3} is a repeat of one performed in Ref.~\onlinecite{rftor1}. In practice, there is a slight difference between
+the two calculations because the expression for the linear layer width used in Eq.~(D1) of Ref.~\onlinecite{rftor} (which specifies the island width evolution
+equation employed in Ref.~\onlinecite{rftor1}), which was only intended to be approximate,  is slightly inaccurate [because it contains a spurious factor of ($2\,{\cal I}/\hat{a})\,(q/g\,s)^{1/2}_{\hat{r}_k}$].
+This accounts for the very minor differences between Figs.~\ref{fig2} and \ref{fig3} in this
+paper, and Figs.~8 and 9 in Ref.~\onlinecite{rftor1}.
+
+\subsubsection{No-Slip Constraint Relaxed}
+In our second simulation, the no-slip constraint is relaxed at all rational surfaces in the plasma. This implies that the resonant response
+model at the $k$th rational surface consists of Eqs.~(\ref{e21}) and (\ref{e22}). Figures~\ref{fig4} and \ref{fig5} show analogous 
+data to Figs.~\ref{fig2} and \ref{fig3}, respectively. Figure~\ref{fig6} shows details of the bottom panels of Figs.~\ref{fig2} and \ref{fig4},
+in order to better illustrate the island chain dynamics when the  RMP-modified natural frequencies of the various $n=3$ tearing modes in  plasma
+are comparatively small.
+
+A comparison of Figs.~\ref{fig2} and \ref{fig4}, as well as an examination of Fig.~\ref{fig6}, reveals that the relaxation of the
+no-slip constraint facilitates the locking of magnetic island chains to the RMP to a relatively modest degree. (Here, by locking, we mean a reduction in the
+RMP-modified natural frequency to a value close to zero.) 
+This is not surprising, since
+relaxation of the no-slip constraint clearly weakens the coupling between a given magnetic island chain and the local plasma flow (which is ultimately responsible
+for the shielding of driven magnetic reconnection). 
+It can be seen from Fig.~\ref{fig6} that if the no-slip constraint is imposed then the RMP-modified natural frequencies of locked magnetic
+island chains are exactly zero. On the other hand, if the no-slip constraint is relaxed then locked magnetic island chains possess
+ small but finite RMP-modified natural frequencies, because the local plasma flow is able to slip through the  chains to some
+ extent. However, the degree of slippage for a fully developed locked magnetic island chain is comparatively small (i.e., no more than
+ $0.5\,{\rm krad/s}$), which helps explain
+ why the no-slip constraint can be used to accurately predict the dynamics of wide magnetic island chains in tokamaks and reversed field pinches.\cite{rfp}
+
+It is remarkable that the results shown in Figs.~\ref{fig2}--\ref{fig4} are so similar, given that the relaxation of the no-slip constraint leads to a
+radical modification of the dynamics of non-locked magnetic island chains. When the no-slip constraint is imposed, the widths of magnetic island chains that are
+unable to lock to the RMP are forced to pulsate, periodically falling to zero, because the helical phases of the chains are forced to
+continuously increase (or decrease) by their non-zero natural frequencies.\cite{rfb,rfc,rfisland,rf1,pulse} On the other hand, when the no-slip
+constraint is relaxed, the widths of magnetic island chains that are unable to lock to the RMP have steady values, because the  chains can
+slip with respect to the local plasma flow, which means that they can have fixed helical phases despite the fact that their natural
+frequencies are non-zero.
+
+\subsection{Improved Interpolation between Linear and Nonlinear Resonant Response Regimes}\label{s4b}
+According to linear tearing mode theory, in the absence of the RMP, the natural frequency of the tearing mode resonant at the $k$th rational surface is given by\,\cite{ara,lin1,lin2,lin3}
+\begin{equation}\label{elin}
+\varpi_{k\,0} = \varpi_{{\rm ln}\,k} \equiv - n\,(\omega_E+\omega_{\ast\,e})_{{\mit\Psi}_{p\,k}},
+\end{equation}
+where
+\begin{align}
+\omega_{\ast\,e}({\mit\Psi}_p) &=\frac{T_e}{e}\,\frac{d\ln p_e}{d{\mit\Psi}_p}.
+\end{align}
+ Here,  $e$ is the magnitude of the electron charge,  $p_e({\mit\Psi}_p)$  the equilibrium
+electron pressure, and $T_e({\mit\Psi}_p)$ the equilibrium
+electron temperature.
+
+According to nonlinear tearing mode theory, in the absence of the RMP, 
+the natural frequency of the tearing mode resonant at the $k$th rational surface is given by\,\cite{rftor}
+\begin{equation}
+\varpi_{k\,0} = \varpi_{{\rm nl}\,k}\equiv  -n\left(\omega_E +\left[1-L_{00}^{\,ii}+L_{01}^{\,ii}\left(\frac{\eta_i}{1+\eta_i}\right)\right]
+\omega_{\ast\,i}
+-\left[L_{00}^{\,iI}- L_{01}^{\,iI}\left(\frac{\eta_I}{1+\eta_I}\right)\right]\omega_{\ast\,I}\right)_{{\mit\Psi}_{p\,k}},
+\end{equation}
+where
+\begin{align}
+\omega_{\ast\,a}({\mit\Psi}_p) &=-\frac{T_a}{Z_a\,e}\,\frac{d\ln p_a}{d{\mit\Psi}_p},\\[0.5ex]
+\eta_a({\mit\Psi}_p)&=\frac{d\ln T_a}{d\ln n_a},
+\end{align}
+for $a=i, I$. 
+Here, $Z_i$, $n_i({\mit\Psi}_p)$, $T_i({\mit\Psi}_p)$, and $p_i({\mit\Psi}_p)=n_i\,T_i$   are the charge number, 
+equilibrium number density, 
+equilibrium temperature, and equilibrium pressure
+of the majority (thermal) ions, respectively,
+whereas  $Z_I$, $n_I$, $T_I$, $p_I = n_I\,T_I$
+are the corresponding quantities for the impurity ions.  
+Furthermore, $L_{00}^{ii}({\mit\Psi}_p)$, $L_{01}^{ii}({\mit\Psi}_p)$,  $L_{00}^{II}({\mit\Psi}_p)$, and $L_{01}^{II}({\mit\Psi}_p)$ are neoclassical parameters that are defined
+in Sect.~B of Ref.~\onlinecite{rftor}.
+
+Finally, the best agreement between theory and experiment is obtained by assuming that, in the absence of the RMP, the 
+ natural frequency of the tearing mode resonant at the $k$th rational surface is given by\,\cite{rftor1}
+\begin{equation}\label{eeb}
+\varpi_{k\,0} = \varpi_{{\rm eb}\,k}\equiv -n\,(\omega_E)_{{\mit\Psi}_{p\,k}}.
+\end{equation}
+
+\subsubsection{Linear Calculation}
+For the sake of comparison, we shall first perform a purely linear calculation. Thus, the
+resonant plasma response model at the $k$th rational surface consists of Eqs.~(\ref{e21}) and (\ref{e22}), with
+$\hat{W}_k$ set to zero. Moreover, in the absence of the RMP, the natural frequency at the $k$th rational surface is specified by Eq.~(\ref{elin}).
+Figures~\ref{fig7} and \ref{fig8} show the natural frequencies in the absence, and in the presence, of the RMP, as well as the vacuum
+islands widths and the actual island widths.
+
+\subsubsection{Composite Linear/Nonlinear Calculation}
+In our composite linear/nonlinear calculation, the resonant plasma response model at the $k$th rational surface consists of Eqs.~(\ref{e21}) and (\ref{e22}).
+Moreover, in the absence of the RMP, the natural frequency at the $k$th rational surface is specified
+by 
+\begin{equation}\label{ecomp}
+\varpi_{k\,0} = \frac{\varpi_{{\rm ln}\,k} +(\varpi_{{\rm eb}\,k} -\varpi_{{\rm ln}\,k}-\varpi_{{\rm nl}\,k})\,x_k + \varpi_{{\rm nl}\,k}\,x_k^{\,2}}{1-x_k +x_k^{\,2}},
+\end{equation}
+where $x_k = \hat{W}_k/\hat{\delta}_k$.
+It follows that $\varpi_{k\,0}=\varpi_{{\rm ln}\,k}$ in the linear regime, $x_k\ll 1$;  $\varpi_{k\,0}=\varpi_{{\rm nl}\,k}$ in the nonlinear regime, $x_k\gg 1$;
+and $\varpi_{k\,0}=\varpi_{{\rm eb}\,k}$  when $x_k=1$.
+(Note that $\varpi_{{\rm eb}\,k}$ generally lies between $\varpi_{{\rm ln}\,k}$ and $\varpi_{{\rm nl}\,k}$.) Figures~\ref{fig9} and \ref{fig10} show the natural frequencies in the absence, and in the presence, of the RMP, as well as the vacuum
+islands widths and the actual island widths.
+
+It can be seen, by a comparison of Figs.~\ref{fig7}--\ref{fig10}, that the linear calculation very significantly overestimates how easy it is for magnetic
+island chains to lock to the RMP. The reason for this is that the linear slip-frequency is comparatively high, because the linear layer width is
+comparatively narrow. The true slip-frequency becomes less than the linear slip-frequency as soon as the island width exceeds the
+linear layer width. [See Eq.~(\ref{e10}).] The fact that that linear calculation is highly inaccurate confirms the conclusion reached in Ref.~\onlinecite{rf1}
+that the response of a typical H-mode tokamak plasma to an RMP is not governed by linear theory, because the driven
+island widths exceed the very narrow linear layer widths, even when driven reconnection is strongly suppressed by plasma flow.
+
+Intriguingly, the composite linear/nonlinear model fairly accurately predicts the temporal extends of the three ELM mitigation/suppression windows (assuming that the
+windows correspond to the formation of wide locked magnetic island chains at the top of the pedestal). 
+However, the windows do not occur at the correct times. We conclude that Eq.~(\ref{eeb}) gives a more accurate prediction for the
+natural frequencies, in the absence of the RMP, than Eq.~(\ref{ecomp}). However, the reason for this is, as yet, unclear.
+
 \section{Discussion and Conclusions}
+We have developed an improved resonant plasma response model that describes the interaction between a tokamak plasma and an RMP. 
+The model interpolates between the linear and the nonlinear response regimes, and takes into account the fact that the slip-frequency
+is non-zero in the nonlinear regime. Our improved model has been incorporated into the {\tt EPEC} toroidal asymptotic matching code.\cite{rftor1}
+The moidifed {\tt EPEC} code is used to model RMP-induced ELM mitigation/suppression in DIII-D discharge \#145380.
+
+We find that allowing for a finite slip-frequency (i.e., relaxing the so-called no-slip constraint) slightly facilitates the locking of
+driven magnetic island chains to the RMP. (Here, by locking, we mean the reduction of the true natural frequency of a given chain to
+a value that is very close to zero.) In fact, there is surprisingly little difference between {\tt EPEC} simulations that impose the
+no-slip constraint at the various rational surfaces in the plasma and those in which the constraint is relaxed. This is true despite
+the fact that the nature of non-locked island solutions is radically different in the two cases (in the first case, the widths of the island
+chains driven at the rational surfaces pulsate, in the second they remain steady).
+
+Our calculations  confirm the conclusion reached in Ref.~\onlinecite{rf1}
+that the response of a typical H-mode tokamak plasma to an RMP cannot be accurately modeled by linear theory. Our calculations also
+confirm the conclusion reached in Ref.~\onlinecite{rftor1} that the best agreement between theory and observations is obtained by assuming that the
+natural frequencies of tearing modes, in the absence of the RMP, are determined by the local ${\bf E}\times{\bf B}$ frequency.
 
@@
 M.B.~Safonova, V.V.~Volkov, and the T-10 Team, Nucl.\ Fusion {\bf 43} 681 (2003).
+
+\bibitem{d3d} P.B.~Snyder, T.H.~Osboune, K.H.~Burrell, R.J.~Groebner, A.W.~Leonard, R.~Nazikian, D.M.~Orlov, O.~Schmitz, M.R.~Wade, and H.R.~Wilson, 
+ Phys.\ Plasmas {\bf 19}, 056115 (2012).
+
+\bibitem{d3d2} Q.M.~Hu, R.~Nazikian, B.A.~Grierson, N.C.~Logan, D.M.~Orlov, C.~Paz-Solden, and Q.~Yu, 
+Phys.\ Rev.\ Lett.\ {\bf 125}, 045001 (2020).
+
+\bibitem{icoil} G.L.~Jackson, P.M.~Anderson, J.~Bialek, W.P.~Cary, G.L.~Campbell, A.M.~Garofalo,  R.~Hatcher, A.G.~Kellman, R.J.~La\,Haye, A.~Nagy, {\em et al.},  
+Proc.\ 30th EPS Conf.\ on Controlled Fusion and Plasma Physics. (St.\ Petersburg, Russia, 2003) CD-ROM, P-4.47.
+
+\bibitem{hu} Q.M.~Hu,  R.~Nazikian,  B.A.~Grierson,  N.C.~Logan,  J.-K.~Park,  C.~Paz-Soldan, and Q.~Yu, Phys.\ Rev.\ Lett.\ {\bf 125}, 045001 (2020).
+
+\bibitem{flat} R.~Fitzpatrick, Phys.\ Plasmas {\bf 2}, 825 (1995).
+
+\bibitem{connor} J.W.~Connor,  R.J.~Hastie, H.R.~Wilson, and R.L.~Miller, Phys.\ Plasmas  {\bf 5}, 2687 (1998).
+
+\bibitem{rfp} B.E.~Chapman, R.~Fitzpatrick, D.~Craig, P.~Martin, and G.~Spizzo, Phys.\ Plasmas {\bf 11}, 2156 (2004).
+
+\bibitem{pulse} R.~Fitzpatrick, Phys.\ Plasmas {\bf 25}, 112505 (2018).
+
+\bibitem{ara} G.~Ara,  B.~Basu, B.~Coppi, G.~Laval, M.N.~Rosenbluth, and B.V.~Waddell, Ann.\ Phys.\ (N.Y.) {\bf 112}, 443 (1978).
+
+\bibitem{lin1} M.~B\'{e}coulet, F.~Orain, P.~Maget, N.~Mellet, X.~Garbet, E.~Nardon, G.T.A.~Huysmans, T.~Caspar, A.~Loarte,  P.~Cayna, {\em et al.}, 
+Nucl.\ Fusion {\bf 52}, 054003  (2012).
+
+\bibitem{lin2} N.M.~Ferraro, Phys.\ Plasmas {\bf 19}, 056105  (2012).
+
+\bibitem{lin3} F.~Orain, M.~B\'{e}coulet, G.~Dif-Pradalier, G.T.A.~Huysmans, S.~Pamela,   E.~Nardon, C.~Passeron, G.~Latu, V.~Grandgirard, A.~Fil, {\em et al.}, 
+Phys.\ Plasmas {\bf 20}, 102510 (2013).
+
 \end{thebibliography}
 
-%\begin{figure}
-%\includegraphics[height=5in]{fig1.pdf}
-%\caption{Overview of DIII-D discharge \#145380.
-%(a) Safety factor at  ${\mit\Psi}_N=0.95$. 
-%(b) $D_\alpha$ (i.e., Deuterium Balmer-alpha) signal, as well as $n=3$ current flowing in upper and lower sections of I-coil. 
-%(c) Pedestal (i.e., ${\mit\Psi}_N=0.94$)
-%electron pressure.
+\newpage
+
+\begin{figure}
+\includegraphics[height=5in]{fig1.pdf}
+\caption{Overview of DIII-D discharge \#145380.
+(a) Safety factor at  ${\mit\Psi}_N=0.95$. 
+(b) $D_\alpha$ (i.e., Deuterium Balmer-alpha) signal, as well as $n=3$ current flowing in upper and lower sections of I-coil. 
+(c) Pedestal (i.e., ${\mit\Psi}_N=0.94$)
+electron pressure.
 (The red curve is the running average over 10 ms.) (d) Pedestal electron number density.
 The common vertical yellow bands indicate the ELM-suppression/mitigation windows.}\label{fig1}
-%\end{figure}
+\end{figure}
 
+\begin{figure}
+\includegraphics[height=6in]{fig2.pdf}
+\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
+in   DIII-D discharge \#145380, assuming that the natural frequency is determined by the ${\bf E}\times {\bf B}$
+frequency.
+Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
+in   DIII-D discharge \#145380, assuming that the natural frequency is determined by the ${\bf E}\times {\bf B}$
+frequency. The red, green, blue, yellow, cyan, magenta, brown, pink,
+purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig2}
+\end{figure}
+
+\begin{figure}
+\includegraphics[height=6in]{fig3.pdf}
+\caption{Top Panel: Full  $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time 
+in   DIII-D discharge \#145380.
+Bottom Panel:  Full $n=3$ island widths as functions of time
+in   DIII-D discharge \#145380, assuming that the natural frequency is determined by  the ${\bf E}\times {\bf B}$
+frequency. The blue, yellow, cyan, magenta, brown, pink,
+purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
+The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig3}
+\end{figure}
+
+\begin{figure}
+\includegraphics[height=6in]{fig4.pdf}
+\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
+in   DIII-D discharge \#145380, assuming that the natural frequency is determined by the ${\bf E}\times {\bf B}$
+frequency.
+Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
+in   DIII-D discharge \#145380, assuming that the natural frequency is determined by the ${\bf E}\times {\bf B}$
+frequency. The red, green, blue, yellow, cyan, magenta, brown, pink,
+purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig4}
+\end{figure}
+
+\begin{figure}
+\includegraphics[height=6in]{fig5.pdf}
+\caption{Top Panel: Full  $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time 
+in   DIII-D discharge \#145380.
+Bottom Panel:  Full $n=3$ island widths as functions of time
+in   DIII-D discharge \#145380, assuming that the natural frequency is determined by the ${\bf E}\times {\bf B}$
+frequency. The blue, yellow, cyan, magenta, brown, pink,
+purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
+The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig5}
+\end{figure}
+
+\begin{figure}
+\includegraphics[height=6in]{fig6.pdf}
+\caption{Top Panel: Detail of the bottom panel of Fig.~\ref{fig2}. Bottom Panel: Detail of the bottom panel of Fig.~\ref{fig4}. } \label{fig6}
+\end{figure}
+
+\begin{figure}
+\includegraphics[height=6in]{fig7.pdf}
+\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
+in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear theory.
+Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
+in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear theory. The red, green, blue, yellow, cyan, magenta, brown, pink,
+purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig7}
+\end{figure}
+
+\begin{figure}
+\includegraphics[height=6in]{fig8.pdf}
+\caption{Top Panel: Full  $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time 
+in   DIII-D discharge \#145380.
+Bottom Panel:  Full $n=3$ island widths as functions of time
+in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear theory. The blue, yellow, cyan, magenta, brown, pink,
+purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
+The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig8}
+\end{figure}
+
+\begin{figure}
+\includegraphics[height=6in]{fig9.pdf}
+\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
+in   DIII-D discharge \#145380, assuming that the natural frequency is determined by composite linear/nonlinear theory.
+Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
+in   DIII-D discharge \#145380, assuming that the natural frequency is determined by composite linear/nonlinear theory. The red, green, blue, yellow, cyan, magenta, brown, pink,
+purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig9}
+\end{figure}
+
+\begin{figure}
+\includegraphics[height=6in]{fig10.pdf}
+\caption{Top Panel: Full  $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time 
+in   DIII-D discharge \#145380.
+Bottom Panel:  Full $n=3$ island widths as functions of time
+in   DIII-D discharge \#145380, assuming that the natural frequency is determined by composite linear/nonlinear theory. The blue, yellow, cyan, magenta, brown, pink,
+purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
+The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig10}
+\end{figure}
 \end{document}

### 2020-09-09 Papers/Paper2/Paper.tex
Paper2 ready for informal distruibution

@@
 is non-zero in the nonlinear regime. The improved model is incorporated into the {\tt EPEC} toroidal asymptotic matching code.
-The modified {\tt EPEC} code is used to model RMP-induced edge-localized-modr mitigation/suppression in DIII-D H-mode discharge \#145380. 
+The modified {\tt EPEC} code is used to investigate RMP-induced edge-localized-mode (ELM) mitigation/suppression in DIII-D H-mode discharge \#145380. 
 Allowing for a finite slip-frequency (i.e., relaxing the so-called no-slip constraint) is found to slightly facilitate the locking of
-driven magnetic island chains to the RMP. The previously obtained conclusion 
+driven magnetic island chains to the RMP, and, hence, to slightly facilitate RMP-induced ELM mitigation/suppression.  The previously obtained conclusion 
 that the response of a typical H-mode tokamak plasma to an RMP cannot be accurately modeled by linear theory is confirmed.
@@
 generated, (usually) static, helical magnetic perturbation that resonates at
-one or more ``rational'' magnetic flux surfaces within the plasma. Resonant magnetic perturbations have been successfully
+one or more ``rational'' magnetic flux-surfaces within the plasma. Resonant magnetic perturbations have been successfully
 employed to compensate error fields (i.e., accidentally produced RMPs), and, thereby,  to prevent the associated formation of
@@
 
-The recently developed, toroidal, asymptotic matching code {\tt EPEC} has been used to simulate 
+The recently developed, toroidal, asymptotic matching code {\tt EPEC} (Extended Perturbed Equilibrium Code) has been used to simulate 
 RMP-induced ELM mitigation/suppression in DIII-D H-mode plasmas.\cite{rftor,rftor1}
@@
 \subsection{Plasma Equilibrium}
-Consider a large aspect-ratio, low-$\beta$, tokamak plasma whose magnetic flux surfaces map out (almost)
+Consider a large aspect-ratio, low-$\beta$, tokamak plasma whose magnetic flux-surfaces map out (almost)
 concentric circles in the poloidal plane.
@@
 It is convenient to express the perturbed magnetic field and the perturbed plasma current density in
-terms of a perturbed poloidal magnetic flux, $\psi(r,\theta,\phi,t)$. In fact, $\delta{\bf B} = \nabla\psi\times \nabla z$, 
+terms of a perturbed poloidal magnetic flux (divided by $2\pi\,R_0$), $\psi(r,\theta,\phi,t)$. In fact, $\delta{\bf B} = \nabla\psi\times \nabla z$, 
 and $\mu_0\,\delta {\bf j} = - \nabla^2\psi\,\nabla z$,
@@
 The final term on the right-hand side of the previous equation is the ``nonlinear slip-frequency''. In general,
-we would expect this frequency to be relatively small (because it is generally the case that $|\omega_s|\,\tau_R\,(W_s/r_s)\gg 1$
+we would expect this frequency to be relatively small (because it is usually the case that $|\omega_s|\,\tau_R\,(W_s/r_s)\gg 1$
 for fully-developed magnetic islands in high-temperature tokamak plasmas\,\cite{rf1,slip2}). Nevertheless, the
@@
 
-In the previous expressions, $R_0$ is the major radius of the magnetic axis, $r$ is a magnetic flux surface label with dimensions of length (which, roughly speaking, is the average minor radius of the
-flux surface), $q(r)$ is the safety-factor profile, $s(r)=d\ln q/d\ln r$, 
+In the previous expressions, $R_0$ is the major radius of the magnetic axis, $r$ is a magnetic flux-surface label with dimensions of length (which, roughly speaking, is the average minor radius of the
+flux-surface), $q(r)$ is the safety-factor profile, $s(r)=d\ln q/d\ln r$, 
 $g(r)\,B_0$ is the toroidal magnetic field-strength at major radius $R_0$, $B_0$ is the vacuum
-toroidal magnetic field-strength on the magnetic axis, $a$ is the value of $r$ on the last closed magnetic-flux surface, $r_k$ is the value of $r$ on the $k$th rational
+toroidal magnetic field-strength on the magnetic axis, $a$ is the value of $r$ on the last closed magnetic flux-surface, $r_k$ is the value of $r$ on the $k$th rational
 surface (resonant with poloidal mode number $m_k$, and toroidal mode number $n$), $\hat{a}=a/R_0$, $\hat{r}=r/a$, and $\hat{r}_k=r_k/a$. 
@@
 Equation~(\ref{e15}) represents a minor improvement to Eq.~(D1) of Ref.~\onlinecite{rftor} in which the interpolation between the
-linear and nonlinear regimes is performed in a more systematic manner.
+linear and nonlinear regimes is performed in a slightly more accurate manner.
 
@@
 absence of an RMP (or any other island chains). On the other hand,  ${\mit\Delta}{\mit\Omega}_\theta$ and ${\mit\Delta}{\mit\Omega}_\phi$ are the changes in the plasma
-poloidal and toroidal velocity profiles, respectively, induced by the electromagnetic torques that develop in the vicinities of the various rational surfaces in the plasma.
+poloidal and toroidal velocity profiles, respectively, induced by the electromagnetic torques that develop in the vicinities of the various rational surfaces in the plasma in response to the RMP.
 Equation~(\ref{e19}) represents
-a major improvement to Eq.~(D6) that takes into  account the finite slip-frequencies of the magnetic island chains induced at
+a major improvement to Eq.~(D6) of Ref.~\onlinecite{rftor} that takes into  account the finite slip-frequencies of the magnetic island chains induced at
 the various rational surfaces in the plasma. In the absence of a finite slip-frequency, the right-hand side of Eq.~(\ref{e19}) would be zero.
@@
 
-\section{EPEC Modeling of DIII-D Discharge \#145380}\label{s4}
+\section{{\tt EPEC} Modeling of DIII-D Discharge \#145380}\label{s4}
 \subsection{Introduction}
@@
 first, second, and third ELM-suppression/mitigation windows extend over the $\overline{q_{95}}$ ranges $3.88$--$3.94$, $3.62$--$3.73$,
-and $3.33$--$3.48$, respectively. Here, $\overline{q_{95}}$ is least-squares linear fit to the variation of the safety-factor at the ${\mit\Psi}_N = 0.95$ flux surface with time.
+and $3.33$--$3.48$, respectively. Here, $\overline{q_{95}}$ is least-squares linear fit to the variation of the safety-factor at the ${\mit\Psi}_N = 0.95$ flux-surface with time.
 
@@
 comparatively narrow. The true slip-frequency becomes less than the linear slip-frequency as soon as the island width exceeds the
-linear layer width. [See Eq.~(\ref{e10}).] The fact that that linear calculation is highly inaccurate confirms the conclusion reached in Ref.~\onlinecite{rf1}
+linear layer width. [See Eq.~(\ref{e10}).] The fact that the linear calculation is highly inaccurate confirms the conclusion reached in Ref.~\onlinecite{rf1}
 that the response of a typical H-mode tokamak plasma to an RMP is not governed by linear theory, because the driven
@@
 windows correspond to the formation of wide locked magnetic island chains at the top of the pedestal). 
-However, the windows do not occur at the correct times. We conclude that Eq.~(\ref{eeb}) gives a more accurate prediction for the
+However, the windows do not occur in the correct time intervals. We conclude that Eq.~(\ref{eeb}) gives a more accurate prediction for the
 natural frequencies, in the absence of the RMP, than Eq.~(\ref{ecomp}). However, the reason for this is, as yet, unclear.
 
-\section{Discussion and Conclusions}
+\section{Summary}
 We have developed an improved resonant plasma response model that describes the interaction between a tokamak plasma and an RMP. 
@@
 is non-zero in the nonlinear regime. Our improved model has been incorporated into the {\tt EPEC} toroidal asymptotic matching code.\cite{rftor1}
-The moidifed {\tt EPEC} code is used to model RMP-induced ELM mitigation/suppression in DIII-D discharge \#145380.
+The modified {\tt EPEC} code is used to model RMP-induced ELM mitigation/suppression in DIII-D H-mode discharge \#145380.
 
@@
 
-\bibitem{rftor1} R.~Fitzpatrick,  ``Modelling $q_{95}$ Windows for the Suppression of Edge Localized
+\bibitem{rftor1} R.~Fitzpatrick,  ``Modeling $q_{95}$ Windows for the Suppression of Edge Localized
 Modes by Resonant Magnetic Perturbations in the DIII-D Tokamak", submitted to Physics of Plasmas (2020).
@@
 \includegraphics[height=6in]{fig2.pdf}
-\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by the ${\bf E}\times {\bf B}$
+\caption{Composite linear/nonlinear calculation with the no-slip constraint imposed at all rational surfaces, and the natural frequencies
+in the absence of the RMP determined by the local  ${\bf E}\times {\bf B}$
 frequency.
-Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by the ${\bf E}\times {\bf B}$
-frequency. The red, green, blue, yellow, cyan, magenta, brown, pink,
+Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
+in   DIII-D discharge \#145380. Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
+in   DIII-D discharge \#145380. The red, green, blue, yellow, cyan, magenta, brown, pink,
 purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig2}
@@
 \includegraphics[height=6in]{fig3.pdf}
-\caption{Top Panel: Full  $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time 
+\caption{Composite linear/nonlinear calculation with the no-slip constraint imposed at all rational surfaces, and the natural frequencies
+in the absence of the RMP determined by the local  ${\bf E}\times {\bf B}$
+frequency. Top Panel: Full  $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time 
 in   DIII-D discharge \#145380.
 Bottom Panel:  Full $n=3$ island widths as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by  the ${\bf E}\times {\bf B}$
-frequency. The blue, yellow, cyan, magenta, brown, pink,
+in   DIII-D discharge \#145380. The blue, yellow, cyan, magenta, brown, pink,
 purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
@@
 \includegraphics[height=6in]{fig4.pdf}
-\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by the ${\bf E}\times {\bf B}$
+\caption{Composite linear/nonlinear calculation with the no-slip constraint relaxed at all rational surfaces, and the natural frequencies
+in the absence of the RMP determined by the local  ${\bf E}\times {\bf B}$
 frequency.
+Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
+in   DIII-D discharge \#145380.
 Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by the ${\bf E}\times {\bf B}$
-frequency. The red, green, blue, yellow, cyan, magenta, brown, pink,
+in   DIII-D discharge \#145380. The red, green, blue, yellow, cyan, magenta, brown, pink,
 purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig4}
@@
 \includegraphics[height=6in]{fig5.pdf}
-\caption{Top Panel: Full  $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time 
+\caption{Composite linear/nonlinear calculation with the no-slip constraint relaxed at all rational surfaces, and the natural frequencies
+in the absence of the RMP determined by the local  ${\bf E}\times {\bf B}$
+frequency. Top Panel: Full  $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time 
 in   DIII-D discharge \#145380.
 Bottom Panel:  Full $n=3$ island widths as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by the ${\bf E}\times {\bf B}$
-frequency. The blue, yellow, cyan, magenta, brown, pink,
+in   DIII-D discharge \#145380. The blue, yellow, cyan, magenta, brown, pink,
 purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
@@
 \includegraphics[height=6in]{fig7.pdf}
-\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear theory.
+\caption{Linear calculation with the no-slip constraint relaxed at all rational surfaces, and  the natural frequencies
+in the absence of the RMP determined by linear theory. 
+ Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
+in   DIII-D discharge \#145380.
 Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear theory. The red, green, blue, yellow, cyan, magenta, brown, pink,
+in   DIII-D discharge \#145380. The red, green, blue, yellow, cyan, magenta, brown, pink,
 purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig7}
@@
 \includegraphics[height=6in]{fig8.pdf}
-\caption{Top Panel: Full  $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time 
+\caption{Linear calculation with the no-slip constraint relaxed at all rational surfaces, and  the natural frequencies
+in the absence of the RMP determined by linear theory. Top Panel: Full  $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time 
 in   DIII-D discharge \#145380.
 Bottom Panel:  Full $n=3$ island widths as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear theory. The blue, yellow, cyan, magenta, brown, pink,
+in   DIII-D discharge \#145380. The blue, yellow, cyan, magenta, brown, pink,
 purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
@@
 \includegraphics[height=6in]{fig9.pdf}
-\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by composite linear/nonlinear theory.
+\caption{Composite linear/nonlinear calculation with the no-slip constraint relaxed at all rational surfaces, and  the natural frequencies
+in the absence of the RMP determined by composite linear/nonlinear theory. Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
+in   DIII-D discharge \#145380.
 Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by composite linear/nonlinear theory. The red, green, blue, yellow, cyan, magenta, brown, pink,
+in   DIII-D discharge \#145380. The red, green, blue, yellow, cyan, magenta, brown, pink,
 purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig9}
@@
 \includegraphics[height=6in]{fig10.pdf}
-\caption{Top Panel: Full  $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time 
+\caption{Composite linear/nonlinear calculation with the no-slip constraint relaxed at all rational surfaces, and  the natural frequencies
+in the absence of the RMP determined by composite linear/nonlinear theory. Top Panel: Full  $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time 
 in   DIII-D discharge \#145380.
 Bottom Panel:  Full $n=3$ island widths as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by composite linear/nonlinear theory. The blue, yellow, cyan, magenta, brown, pink,
+in   DIII-D discharge \#145380. The blue, yellow, cyan, magenta, brown, pink,
 purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 

### 2020-09-10 Papers/Paper2/Paper.tex
Minor corrections to Paper2

@@
 \end{equation}
-The reasoning behind the imposition of this constraint is that the plasma is trapped inside the
+The reasoning behind the imposition of this constraint is that  plasma is trapped inside the
 magnetic separatrix of the  island chain that forms in the vicinity of the rational surface,
@@
 Here, $\varpi_{k\,0}$
-is the so-called ``natural frequency'' at the $k$th rational surface; this quantity is defined as the helical phase velocity of a naturally unstable island chain, resonant at the surface, in the
+is the so-called ``natural frequency''  (in the absence of the RMP) at the $k$th rational surface; this quantity is defined as the helical phase velocity of a naturally unstable island chain, resonant at the surface, in the
 absence of an RMP (or any other island chains). On the other hand,  ${\mit\Delta}{\mit\Omega}_\theta$ and ${\mit\Delta}{\mit\Omega}_\phi$ are the changes in the plasma
@@
 As is discussed in Ref.~\onlinecite{rftor1}, the best agreement between the predictions of the {\tt EPEC} code and experimental observations is
-obtained by assuming that the natural frequencies at the various rational surfaces in the plasma are determined by the
+obtained by assuming that the unperturbed natural frequencies at the various rational surfaces in the plasma are determined by the
 local equilibrium ${\bf E}\times {\bf B}$ frequencies. In other words, 
@@
 \end{equation}
-Here, ${\mit\Phi}({\mit\Psi}_p)$ is the equilibrium scalar electric potential, ${\mit\Psi}_p$ the equilibrium poloidal magnetic flux (divided by $2\pi$), 
+Here, ${\mit\Phi}({\mit\Psi}_p)$ is the equilibrium scalar electric potential (in the absence of the RMP), ${\mit\Psi}_p$ the equilibrium poloidal magnetic flux (divided by $2\pi$), 
 and ${\mit\Psi}_{p\,k}$  the value of ${\mit\Psi}_p$ at the $k$th rational surface.  Equation~(\ref{e24}) holds at
@@
 island chains are exactly zero. On the other hand, if the no-slip constraint is relaxed then locked magnetic island chains possess
- small but finite RMP-modified natural frequencies, because the local plasma flow is able to slip through the  chains to some
+ small but finite RMP-modified natural frequencies, because the local plasma flow is able to slip through the  stationary chains to some
  extent. However, the degree of slippage for a fully developed locked magnetic island chain is comparatively small (i.e., no more than
@@
 \end{align}
- Here,  $e$ is the magnitude of the electron charge,  $p_e({\mit\Psi}_p)$  the equilibrium
+ Here,  $e$ is the magnitude of the electron charge,  $p_e({\mit\Psi}_p)$  the equilibrium (i.e., in the absence of the RMP)
 electron pressure, and $T_e({\mit\Psi}_p)$ the equilibrium

### 2020-09-19 ExperimentalData/DIIID/145380/Paper/Reply.tex
Revised version of Paper1

\documentclass{article}[12pt]
\usepackage{fullpage}

\begin{document}
\begin{center}
{\em Modeling $q_{95}$ Windows for the Suppression of Edge Localized Modes by Resonant Magnetic}\\[0.5ex]
{\em Perturbations in the DIII-D tokamak}\\[1ex]
by Richard Fitzpatrick\\[1ex]
{\bf Reply to Referees' Comments}
\end{center}

First, let me thanks both referees for their careful reading of the paper, and their helpful comments. In response to these 
comments, I have made the following major changes to the paper.
\begin{enumerate}
\item I have taken the material in the Appendix relating to the natural frequency, and have converted it into a
preliminary section in the main text. The remainder of the Appendix has been discarded, because it was
not germane to the argument of the paper. The new section allows me to state the first and second aims of
the paper right next to one another (at the end of the Introduction), and also helps to frame the discussion of the three calculations 
that are described in the paper. 
\item I have improved the figures, in that  I have  make the axes labels larger, and
have added legends to Figs.~4--13. 
\item I have added the neutral particle profile to Fig.~3.
\item I have added a summary figure (Fig.~14) that helps to compare and
contrast the results of the three calculations that are described in the paper.
\item The new summary figure makes it apparent that the results of the calculation with the linear natural frequency are
not as bad as I had originally thought. Hence, I have amended the discussion in the paper relating to this calculation.
\item I have tried to make it clear throughout the paper that, in the absence of the RMP,  the  {\tt EPEC} code uses profile information to reconstruct the natural frequencies
of tearing modes that are unmodified by RMP-induced electromagnetic torques in the plasma. In the presence of the RMP, the {\tt EPEC} code
calculates how these frequencies are modified by the torques. 
 Because it is clear, from a comparison of {\tt EPEC} simulations made with and without the RMP, that
the natural frequencies are not appreciably modified by the torques, except in those relatively short time intervals
in which a mode locks to the RMP, it is not unreasonable to use the profiles outside these intervals as inputs to the code. 
\end{enumerate}

The following gives responses to specific queries from Referee 1 that are not covered by the previous discussion (all reference numbers refer to references in the
original manuscript):
\begin{enumerate}
\item p.~3: I have made it clear that the maximum practical currents that can be driven in RMP coils render
the coils incapable of locking tearing modes except when the natural frequencies of the modes are
comparatively small (i.e., 5 krad/s, instead of the usual 100 krad/s, in DIII-D).
\item p.~4: I have replaced references to the ``guiding-center fluid" by references to the ${\bf E}\times {\bf B}$ velocity.
\item p.~4: I have add the Lyons (2017) reference. 
\item p.~5: I have added more asymptotic matching references. 
\item p.~5: I have made it clear that the observation that the driven widths of non-locked magnetic
island chains exceed the linear layer widths actually applies to DIII-D discharge 158115, and have argued
that it is not unreasonable to assume that the same holds true in discharge 145380. I have also explained
why I think that this state of affairs will persist in ITER.
\item p.~5: I did mean Ref.~12 instead of 14.
\item  p.~7: If the density pump-out modifies profiles in a manner that is not associated with the generation of
electromagnetic torques at the various rational surfaces in the plasma then the pump-out modified 
profiles would be the appropriate profiles to use as the starting point of the calculation. 
\item p.~7: {\tt EPEC} does not modify the plasma equilibrium. 
\item p.~8: I have replaced ``actual widths" by ``shielded widths". 
\item p.~9: The 1/3 power is correct in Ref.~22. If you read the final section of Ref.~49 you will see that
when you take into account the fact that parallel transport in high-temperature tokamak plasmas is
convective, rather than conductive, then the critical island width scales as $\chi_\perp^{1/3}$, rather than
$\chi_\perp^{1/4}$. I have added an additional reference to make this clear. I have also made it clear that the
generic $\chi_\perp$ used in Ref.~22 has been replaced by separate diffusivities for momentum, energy, and particles
in the present paper. 
\item p.~10: Because the $m=11$ ELM suppression window only differs from the other two windows by the presence of
a single ELM in the middle of the window, I do not think that it makes sense to make a significant distinction between the $m=11$
window and the other two. 
\item p.~12: Unfortunately, I do not know how to run the {\tt EPED} model. 
\item Fig.~1: The thin grey line seems to be a ``feature'' of the interaction of obsolete versions of Powerpoint and the Mac operating system.
Because the line does not actually occur in the figure, I cannot delete it. (I also cannot redraw the figure, because I did not generate it in the first place. I think that it is a pretty old figure.) I can only hope that the line does not appear in the published version of the paper. 
\end{enumerate}

The following gives responses to specific queries from Referee 2 that are not covered by the previous discussion:
\begin{enumerate}
\item {\tt EPEC}, like {\tt GPEC}, uses a flux-coordinate system, and is essentially spectral in the poloidal and toroidal directions. Thus,
{\tt EPEC} cannot treat an X-point exactly, but it can get asymptotically close to an X-point by making the cutoff surface arbitrarily close to
the LCFS. 
\end{enumerate}
\end{document}

### 2020-09-19 ExperimentalData/DIIID/145380/Paper/paper1.tex
Revised version of Paper1

--- 2020-08-12 ExperimentalData/DIIID/145380/Paper/paper.tex
@@
 
-\title {Modelling $q_{95}$ Windows for the Suppression of Edge Localized Modes by Resonant Magnetic Perturbations in the DIII-D Tokamak}
+\title {Modeling $q_{95}$ Windows for the Suppression of Edge Localized Modes by Resonant Magnetic Perturbations in the DIII-D Tokamak}
 
@@
 In the first case, the natural frequencies of tearing modes resonant in the plasma are 
-determined by the ion flows at the corresponding rational surfaces, which is the prediction of nonlinear theory.
+determined by the ion flows at the corresponding resonant surfaces, which is the prediction of nonlinear tearing mode theory.
 In the second case, the natural frequencies are 
-determined by the guiding-center flows at the rational surfaces.
+determined by the local ${\bf E}\times {\bf B}$ velocities at the resonant surfaces.
  In the third case, the natural frequencies   are 
-determined by the electron flows at the  rational surfaces, which is the prediction of linear theory.
-The second case gives  the best agreement between the simulations and the  experimental observations.   The third case gives by far the worst agreement between the simulations 
-and the  observations. The first case only leads to partial agreement between  the  simulations and the  observations. However, this lack of complete agreement
-may be a consequence of using an inaccurate assumption for the neutral particle distribution in the pedestal.  
+determined by the electron flows at the  resonant surfaces, which is the prediction of linear tearing mode theory.
+The second case gives  the best agreement between the simulations and the  experimental observations.
+The first and third cases only leads to partial agreement between  the  simulations and the  observations.
+In the first case, the lack of complete agreement
+may be a consequence of using an inaccurate assumption for the neutral particle distribution in the pedestal.  In the third case, the lack of complete agreement is probably
+due to the fact that the response of a tokamak plasma to an RMP is not accurately described by linear tearing mode theory.
 \end{abstract}
@@
 The application of a static RMP, resonant in the pedestal region (i.e., the region of strong pressure and current density gradients characteristic of the edge region of an H-mode 
-tokamak discharge), to an H-mode tokamak discharge is observed to give rise to  two distinct phenomena.\cite{schmitz, lanctot,paz1,d158115,paz} The first of these  is the 
+tokamak discharge), to an H-mode tokamak discharge is observed to give rise to  two distinct phenomena.\cite{schmitz, lanctot,paz1,d158115,lyons,paz} The first of these  is the 
 so-called ``density pump-out'', which  is characterized by a reduction in the electron number density
@@
 leading to similar conclusions to the aforementioned TM1
-studies. The primary aim of this paper is to employ this
+studies. The first aim of this paper is to employ this
 new model to try to account for the  $q_{95}$
-ELM-suppression windows  that are apparent when the edge safety-factor is slowly ramped in
+ELM-suppression/mitigation windows  that are apparent when the edge safety-factor is slowly ramped in
 a particular DIII-D discharge (\#145380) in which an $n=3$
-RMP is used to control ELMs.\cite{d3d,d3d2}
+RMP is used to control ELMs.\cite{d3d,d3d2} The second aim is to determine  which choice for the so-called ``natural frequency''  of tearing modes can best account for the   $q_{95}$ 
+ELM-suppression/mitigation windows  observed in DIII-D discharge \#145380.
 
+\section{Natural Frequency}
+\subsection{Introduction}
 It is well-known that magnetic reconnection driven when a  (stable) tearing mode interacts with a static RMP that is resonant at a particular magnetic flux-surface in a tokamak plasma is
-facilitated when the associated ``natural frequency'' is relatively small.\cite{rfa,rfb}  The natural frequency  of a  (stable) tearing mode is the
-helical phase velocity that the mode would possess were it naturally unstable (in the absence of the RMP).  Driven magnetic reconnection leads to the
+facilitated when the associated natural frequency, in the absence of the RMP,  is relatively small.\cite{rfa,rfb}  The natural frequency  of a  (stable) tearing mode is the
+helical phase velocity that the mode would possess were it naturally unstable.  (It should be noted that the maximum practical currents
+that can be driven in edge-resonant RMP coils severely limit the ability of such coils to modify the rotation
+frequencies of tearing modes resonant in the pedestals of present-day tokamaks.  For example, in the DIII-D tokamak, as will become clear later on in the paper,
+the RMP coils are only capable of arresting the rotation of edge-resonant tearing modes when the magnitude of the helical
+phase velocities of such modes fall below about 5 krad/s. A typical phase velocity is 100 krad/s.) Driven magnetic reconnection leads to the
 formation of a locked magnetic island chain at the resonant surface in question. 
@@
 the top of the pedestal is close to zero.\cite{d3d} 
-However, there is currently some uncertainty in the fusion community regarding the form of the natural frequency.
+However, there is currently some debate in the fusion community regarding the appropriate choice for the natural frequency.
 
-According to nonlinear tearing mode theory, a tearing mode is essentially convected by
-the local ion fluid at the rational surface (see the discussion in Sect.~\ref{natural}).\cite{nl1,nl2,nl3}
+ The natural frequency of a tearing mode 
+is determined by the equilibrium plasma flow at the
+resonant surface. Now, a magnetic island chain is a helical
+pattern in the magnetic field  generated by a helical current perturbation that is localized in the
+vicinity of the resonant surface.
+Given that plasma current is predominately carried by the
+electrons, it is natural to suppose that a magnetic
+island chain (as well as the tearing mode perturbation
+away from the resonant surface)  is convected by the
+electron fluid in the immediate vicinity of the resonant
+surface. This is indeed the case in the linear regime.\cite{ara} Of course, as a consequence of diamagnetic flows, if the island chain is
+convected by the electron fluid at the resonant surface then it propagates with respect to the local ion fluid. However, this is not a
+problem because a linear layer is sufficiently thin that the magnetic field can diffuse through the plasma very rapidly, which implies that
+the ion fluid is not tied to the magnetic structure of the island chain.
+
+The situation is very different in the nonlinear regime. 
+The region inside the magnetic separatrix of a nonlinear magnetic island chain is governed by a combination of flux-freezing and perturbed force balance.
+This implies that both the electron and the ion fluids are trapped inside the separatrix, and are, therefore,  forced to co-rotate with the island chain. There
+is no such constraint outside the separatrix, so the electron and ion fluids rotate at different speeds in this region,
+as a consequence of diamagnetism.  It follows that one or other of the electron and the ion fluid rotation profiles must exhibit a strong gradient across
+the separatrix. The island propagation velocity is determined by which of the two fluids is most resistant to the formation of such a gradient. 
+Of course, it is the ion fluid which is more resistant because of its much greater perpendicular viscosity,\cite{nl1,wat} as well as its much larger 
+neoclassical stress tensor.\cite{nl2} Hence, a nonlinear magnetic island chain is convected by the ion fluid in the vicinity of the resonant 
+surface, because this choice of propagation speed minimizes the ion fluid velocity gradient across the separatrix.
+
+Finally, we could imagine that if the width of an island chain is neither much less than the linear layer width (which is the strict
+criterion for the validity of linear theory) nor much greater than the linear layer width (which is the strict criterion for
+the validity of nonlinear theory) then the chain lies in some sort of intermediate regime in which it is
+convected at the local ${\bf E}\times {\bf B}$ velocity (this prediction is generally intermediate between the predictions of linear and nonlinear theory).
+
+It is clear, from the preceding discussion,  that there are three main choices for the natural frequency of a given tearing mode in a tokamak plasma.
+
+\subsection{Case 1}
+As we have already mentioned, according to nonlinear tearing mode theory, a tearing mode is essentially convected by
+the local ion fluid at the resonant surface.\cite{nl1,nl2,nl3}
 In fact, if the response of an H-mode tokamak plasma to an applied RMP
@@
 at the ``rational''  (i.e., resonant) magnetic flux-surface at which the
-safety-factor
+safety-factor, 
 \begin{equation}
@@
 toroidal periods, respectively, of the helical magnetic island chain driven at the rational surface.
-Moreover, ${\mit\Psi}_t({\mit\Psi}_p)$ is the equilibrium toroidal magnetic flux (divided by $2\pi$).
+Moreover, ${\mit\Psi}_t({\mit\Psi}_p)$ is the equilibrium toroidal (poloidal) magnetic flux (divided by $2\pi$).
 
-A second possibility is that a tearing mode is convected by the local guiding-center fluid at the rational surface  (again, see the discussion in Sect.~\ref{natural}),\cite{heyn,paz1}
+\subsection{Case 2}
+A second possibility is that a tearing mode is convected at the local ${\bf E}\times{\bf B}$ velocity at the resonant surface,\cite{heyn,lyons,paz1}
 in which case we would expect the natural frequency to take the form 
@@
 
+\subsection{Case 3}
 Finally, according to
 linear tearing mode theory, a tearing mode is essentially convected by
-the local electron fluid at the resonant surface (again, see the discussion in Sect.~\ref{natural}).\cite{hender,cole} Hence, if the response of an H-mode tokamak plasma to an applied RMP
+the local electron fluid at the resonant surface.\cite{hender,cole} Hence, if the response of an H-mode tokamak plasma to an applied RMP
 is governed by linear physics then we would expect the
@@
 
-The secondary aim of this paper is to determine which of the three aforementioned choices for the natural frequency can best account for the   $q_{95}$ 
-ELM-suppression windows  observed in DIII-D discharge \#145380.
-
-\section{Description of Theoretical Model}
+\section{EPEC Modeling of DIII-D Discharge \#145380}
+\subsection{EPEC Code}
 The theoretical model of the response of a tokamak plasma to an externally applied RMP that is used in this
-paper is described in detail in Ref.~\onlinecite{rf2}. The model employs a standard asymptotic matching approach.\cite{fkr,am1,am2,am3}
+paper is described in detail in Ref.~\onlinecite{rf2}. The model employs a standard asymptotic matching approach.\cite{fkr,coppi,ruth,ara,pletz,am1,pletz1,tokuda,brennan,fura,am2,am3}
 According to this approach, the response of the plasma to the applied RMP is governed by a combination of flux-freezing and
-perturbed force balance (this combination is often referred to as ``marginally-stable ideal-MHD", which is a misnomer because MHD {\em per se}\/ plays no
-role) everywhere in the plasma apart from a number of relatively narrow (in the radial direction) regions in which the applied
+perturbed force balance (this combination is often referred to as ``marginally-stable ideal-MHD") everywhere in the plasma apart from a number of relatively narrow (in the radial direction) regions in which the applied
 perturbation resonates with the equilibrium magnetic field. Magnetic reconnection can take place within the resonant regions to
@@
 as opposed to linear, two-fluid resistive-MHD. This is the case because the widths of the magnetic island chains
-driven at the resonant surfaces exceed the linear layer widths (which invalidates linear theory).\cite{rf1}
+driven at the resonant surfaces (in DIII-D discharge 158115,\cite{rf1} which is similar to DIII-D discharge 145380) exceed the linear layer widths (which invalidates linear theory).
+(This state of affairs can be expected to persist in future tokamaks, such as ITER, because such tokamaks will operate with much higher values of the
+Lundquist number than present-day tokamaks, leading to a reduction in the linear layer widths.)
 Thus, when employing the asymptotic matching approach, the equations of flux-freezing and perturbed force balance
@@
 
-A toroidal tokamak equilibrium exhibits two distinct types of response to an applied RMP.\cite{paz1,kink0,kink1}
+A toroidal tokamak equilibrium exhibits two distinct types of response to an applied RMP.\cite{paz,kink0,kink1}
 The first of these is known as the ``tearing response''---this is a non-ideal-MHD response that is associated with the
@@
 evolution of the global plasma equilibrium than it does with
-conventional linear tearing mode physics. (See the discussion in Sect.~\ref{general}.) In particular, the Alfv\'{e}n time is
+conventional linear tearing mode physics. In particular, the Alfv\'{e}n time is
 an irrelevant  timescale in nonlinear tearing mode theory, and
@@
 
-\section{EPEC Modeling of DIII-D Discharge \#145380}
 \subsection{Plasma Equilibrium}
@@
 and the last closed magnetic flux-surface (LCFS) to ${\mit\Psi}_N=1$. The perpendicular
-diffusivity data comes from {\tt TRANSP} modelling.\cite{transp}
+diffusivity data comes from {\tt TRANSP} modeling.\cite{transp}
 
@@
 calculated {\tt GPEC} data values, and any quantity that depends on these values is recalculated every 1 ms. There is one major exception to
-the aforementioned scheme. The theoretical model used in this paper actually requires plasma equilibria and profiles that are unaffected
-by the applied RMP. However, there is clear evidence that the equilibria and the profiles (in particular) are significantly modified
+the aforementioned scheme. The theoretical model implemented in the {\tt EPEC} code actually requires  profiles that are unaffected
+by the applied RMP (to be more exact, it requires sufficient information to reconstruct  natural frequencies that are unmodified by the electromagnetic
+torques that develop in the plasma in response to the RMP). However, there is clear evidence that the  profiles  are significantly modified
 within the three ELM-suppression/mitigation windows (presumably because wide magnetic island chains are driven in the pedestal). [See Fig.~1(c).]
-Hence, we do not use the equilibrium, profile, or {\tt GPEC}, data within the three ELM-suppression/mitigation windows. Instead, we
-interpolate across these windows using data taken on either side of the windows.
+Hence, we do not use the  profile (or {\tt GPEC}) data within the three ELM-suppression/mitigation windows. Instead, we
+interpolate across these windows using data taken on either side of the windows. The ultimate justification for this approach is the fact that, as can be seen from Figs.~\ref{fig5}, \ref{fig8}, and
+\ref{fig11}, {\tt EPEC} simulations performed in the absence of the RMP (i.e., in the absence of RMP-generated electromagnetic torques) give very similar natural frequencies to simulations performed in the presence of the RMP, except
+in time intervals in which one or more tearing modes lock to the RMP (of course, we are identifying such intervals with the ELM suppression/mitigation windows).
 
@@
 constant at about 1.0. For the sake of practicality,  the {\tt GPEC} and {\tt EPEC} calculations described in this paper ignore $n=3$ rational
-surfaces that lie very close to the LCFS: in other words,  surfaces that lie in the region $0.997 < {\mit\Psi}_N\leq 1.000$. Let $\overline{q_{95}}\equiv 5.2060-0.4457\,t$ represent the
+surfaces that lie very close to the LCFS; in other words,  surfaces that lie in the region $0.997 < {\mit\Psi}_N\leq 1.000$. (It should be
+noted that {\tt EPEC}, like {\tt GPEC}, employs a straight field-line flux coordinate system, and is effectively
+spectral in the poloidal and toroidal directions.)  $\overline{q_{95}}\equiv 5.2060-0.4457\,t$ is the
 least-squares linear fit to the $q_{95}$ versus time data shown in Fig.~\ref{fig4}. 
@@
 In future, data from the new {\tt LLAMA} (Lyman Alpha Measurement Apparatus) system will be routinely available in DIII-D discharges.\cite{llama}
-Combining this data  with modeling from a neutral particle simulation code such as, for example, the  SOLPS-ITER code\,\cite{solps} ought to generate sufficient information to fully determine the
+Combining this data  with modeling from a neutral particle simulation code, such as, for example, the  SOLPS-ITER code,\cite{solps} ought to generate sufficient information to fully determine the
 neutral particle data required by the {\tt EPEC} code.
@@
 
-The upper panel of Fig.~\ref{fig5} shows the natural frequencies, in the absence of the RMP, of the various  $n=3$ tearing modes 
+The upper panel of Fig.~\ref{fig5} shows the natural frequencies, reconstructed by {\tt EPEC} from profile data, in the absence of the RMP (i.e., in the absence of
+any RMP-induced electromagnetic torques in the plasma), of the various  $n=3$ tearing modes 
  that are resonant in the pedestal. It can be seen that the natural frequency of the $m=11$ (brown) tearing mode has its main zero-crossing in the middle
@@
 second ELM-suppression/mitigation window. However, the natural frequency of the $m=9$ (cyan) tearing mode  has its main zero-crossing slightly
-prior to the occurrence of the third ELM-suppression/mitigation window. The lower panel of Fig.~\ref{fig5} shows the natural frequencies, in the presence of the RMP, of the various $n=3$
+prior to the occurrence of the third ELM-suppression/mitigation window.
+The lower panel of Fig.~\ref{fig5} shows the natural frequencies, reconstructed by {\tt EPEC} from profile data, in the presence of the RMP (i.e., modified by the electromagnetic torques that develop in the plasma in response to the RMP), of the various $n=3$
 tearing modes that are resonant in the pedestal. It is apparent that if the magnitude of the natural frequency in the absence of the RMP falls below about
@@
 
-The upper panel of Fig.~\ref{fig6} shows the widths of the various vacuum magnetic island chains driven by the applied $n=3$ RMP in the pedestal region as functions of $
+The upper panel of Fig.~\ref{fig6} shows the predicted widths of the various vacuum magnetic island chains driven by the applied $n=3$ RMP in the pedestal region as functions of $
 \overline{q_{95}}$.
@@
 bottom of the pedestal overlap, implying that the magnetic field in this region is rendered stochastic. The lower panel
-of Fig.~\ref{fig6} shows the actual widths of the various magnetic island chains driven by the applied $n=3$ RMP as functions of time. It is apparent 
-that the true island widths are generally much smaller than the vacuum island widths, as a consequence of the shielding of driven magnetic
-reconnection due to plasma flow. However, the shielding breaks down at various rational surfaces when the associated natural frequency is zero (see the lower panel of
+of Fig.~\ref{fig6} shows the predicted widths of the various magnetic island chains driven by the applied $n=3$ RMP as functions of time, taking into
+account the shielding of driven magnetic reconnection by plasma flow. It is apparent 
+that the shielded island widths are generally much smaller than the vacuum island widths.
+However, the shielding breaks down at various resonant surfaces when the associated natural frequency is zero (see the lower panel of
 Fig.~\ref{fig5}). In this situation, the driven island width is similar to the vacuum island width. Note that Fig.~\ref{fig6} is similar in conception to
@@
 Figure~\ref{fig7} shows the widths of the regions of density and electron temperature flattening associated with the $n=3$ magnetic
-island chains driven by the RMP in the pedestal region as functions of $\overline{q_{95}}$ and time.
-(See Sect.~III.F in Ref.~\onlinecite{rf2}.) (Note that the energy diffusivity data shown in Fig.~\ref{fig3}  is used to calculate the
+island chains driven by the RMP in the pedestal region as functions of $\overline{q_{95}}$ and time. (See Sect.~III.F in Ref.~\onlinecite{rf2}, as well as
+Refs.~\onlinecite{flat} and \onlinecite{flat1}.) (Note that the energy diffusivity data shown in Fig.~\ref{fig3}  is used to calculate the
 critical island width for electron temperature flattening, whereas the corresponding particle diffusivity data is used to calculate
-the critical island width for density flattening.\cite{flat}) It can be seen that the driven magnetic island chains are generally too narrow
+the critical island width for density flattening.\cite{flat} This distinction was not made in Ref.~\onlinecite{rf2}, which just used a
+generic perpendicular diffusivity for momentum, energy, and particles.) It can be seen that the driven magnetic island chains that do not lock to the RMP are generally too narrow
 to significantly flatten the density and electron temperature profiles,  implying that there is actually very little degradation of the pedestal energy and particle confinement
-due to the applied RMP. 
+due to the applied RMP from such island chains. 
 However, in those situations in which the shielding of driven
-magnetic reconnection due to plasma flow breaks down (i.e., the true natural frequency becomes zero), locked magnetic island chains are generated that are
+magnetic reconnection due to plasma flow breaks down at a given resonant surface (i.e., the true natural frequency becomes zero), a locked magnetic island chain is generated that is
  wide enough to flatten both the density and the electron temperature profiles.
@@
 \subsection{Case 2: $\varpi=\varpi_{\perp\,EB}$}
-The second case that we shall consider is that in which the natural frequency is determined by the local guiding-center fluid; 
+The second case that we shall consider is that in which the natural frequency is determined by the local ${\bf E}\times {\bf B}$ velocity; 
 in other words, the natural frequency is specified by Eq.~(\ref{e3}).
@@
 to the RMP when the magnitudes of their unperturbed natural frequencies fall below about 5 krad/s. 
-Likewise, it is apparent from Fig.~\ref{fig9} that the true island widths driven in the pedestal by the applied
+Likewise, it is apparent from Fig.~\ref{fig9} that the shielded island widths driven in the pedestal by the applied
 RMP are much smaller than the corresponding vacuum island widths, except when the islands lock to the RMP.
@@
 very well with the first, second, and third, ELM-suppression/mitigation windows, respectively. To be more exact, the regions are located at
-the top of the pedestal, and also occur at about the correct times. Note that overlapping island chains
+the top of the pedestal, and also occur in approximately the correct time intervals. Note that overlapping island chains
 are also driven at the bottom of the pedestal. We associate these chains with the density pump-out phenomenon.\cite{hu,rf2} The chains at the bottom of the pedestal are more apparent
@@
 Figures~\ref{fig11}--\ref{fig13} show analogous data to Figs.~\ref{fig5}--\ref{fig7} and Figs.~\ref{fig8}--\ref{fig10}, respectively.  
-It can be seen from Fig~\ref{fig13} that there is very little correlation between the major regions of density and temperature flattening associated
-with the $n=3$ tearing modes driven by the RMP and the  ELM-suppression/mitigation windows. To be more exact, the 
-regions  are not really located at the top of the pedestal, and occur at completely the wrong times.
+It can be seen from Fig~\ref{fig13} that there is no ELM suppression/mitigation window associated with the $m=11$ mode.  
+However, the  ELM suppression/mitigation windows associated with the $m=10$ and $m=9$ modes occur in approximately the correct
+time intervals.
 
@@
 The toroidal asymptotic matching model of the response of a tokamak plasma to a static RMP that is described in Ref.~\onlinecite{rf2}
-has been implemented in the newly developed {\tt EPEC} code (Extended Perturbed Equilibrium Code). The {\tt EPEC} code has  been used to simulate the $n=3$ RMP-induced ELM-suppression/mitigation
+has been implemented in the newly developed {\tt EPEC} code (Extended Perturbed Equilibrium Code). The {\tt EPEC} code has  been used to simulate the three $n=3$ RMP-induced ELM-suppression/mitigation
 windows in $q_{95}$ that are evident when the plasma current is slowly ramped in DIII-D discharge \#145380. All quantities employed in the simulation are
@@
 
-Three cases are considered. In the first case, the natural frequencies of (stable) $n=3$ tearing modes, resonant in the plasma, are assumed to be
-determined by the ion flows at the corresponding rational surfaces, which is the prediction of nonlinear tearing mode theory.\cite{nl1,nl2,nl3}
+Three cases are considered. These cases are summarized in Fig.~\ref{fig14}. (In this figure, the ELM/mitigation suppression windows are defined as the intersection of the regions
+of density flattening and the top of the pedestal in Figs.~\ref{fig7}, \ref{fig10}, and \ref{fig13}.) In the first case, the natural frequencies of (stable) $n=3$ tearing modes, resonant in the plasma, are assumed to be
+determined by the ion flows at the corresponding resonant surfaces, which is the prediction of nonlinear tearing mode theory.\cite{nl1,nl2,nl3}
 In the second case, the natural frequencies of (stable) $n=3$ tearing modes, resonant in the plasma, are assumed to be
-determined by the guiding-center flows at the corresponding rational surfaces.\cite{heyn,paz1} 
+determined by the ${\bf E}\times {\bf B}$ velocities at the corresponding resonant surfaces.\cite{heyn,paz1} 
 In the third case, the natural frequencies of (stable) $n=3$ tearing modes, resonant in the plasma, are assumed to be
-determined by the electron flows at the corresponding rational surfaces, which is the prediction of linear tearing mode theory.\cite{lin1,lin2,lin3}
+determined by the electron flows at the corresponding resonant surfaces, which is the prediction of linear tearing mode theory.\cite{lin1,lin2,lin3}
+
+The first case only leads to partial agreement between  the {\tt EPEC} simulations and the  observations; in that, the first ELM suppression/mitigation window is
+missing.  This lack of complete agreement is somewhat
+disappointing, given that the response of a tokamak plasma to an RMP ought to be correctly described by nonlinear tearing mode theory. However, according to
+nonlinear theory, the natural frequency of a tearing mode resonant close to the edge of a tokamak plasma is strongly affected by charge-exchange with neutrals.\cite{rf2}
+In particular, the frequency depends on the poloidal asymmetry of the neutrals. To be more exact, if the neutrals are concentrated close to the X-point then the
+natural frequency is pulled in the electron diamagnetic direction, and vice versa.\cite{rf2} (See Sect.~IV of Ref.~\onlinecite{rf2}.) Thus, given our comparative ignorance of the neutral particle
+distribution in DIII-D discharge \#145380, it would be premature to write-off the nonlinear prediction at this stage.
 
@@
 
- The third case gives by far the worst agreement between the {\tt EPEC} simulations and the  observations. This lack of agreement is hardly surprising, given
-that we have no reason to suppose that the response of a tokamak plasma to an RMP is correctly described by linear tearing mode theory.\cite{rf1}
-
-The first case only leads to partial agreement between  the {\tt EPEC} simulations and the  observations. This lack of complete agreement is somewhat
-disappointing, given that the response of a tokamak plasma to an RMP ought to be correctly described by nonlinear tearing mode theory. However, according to
-nonlinear theory, the natural frequency of a tearing mode resonant close to the edge of a tokamak plasma is strongly affected by charge-exchange with neutrals.\cite{rf2}
-In particular, the frequency depends on the poloidal asymmetry of the neutrals. To be more exact, if the neutrals are concentrated close to the X-point then the
-natural frequency is pulled in the electron diamagnetic direction, and vice versa.\cite{rf2} (See Sect.~IV of Ref.~\onlinecite{rf2}.) Thus, given our comparative ignorance of the neutral particle
-distribution in DIII-D discharge \#145380, it would be premature to write-off the nonlinear prediction at this stage.
+ The third case only leads to partial agreement between  the {\tt EPEC} simulations and the  observations; in that, the third ELM suppression/mitigation window is
+missing. This lack of agreement is probably due to that fact that the response of a tokamak plasma to an RMP is not accurately described by linear tearing mode theory.\cite{rf1}
 
@@
 
+\bibitem{lyons} B.C.~Lyons, N.M.~Ferraro, C.~Paz-Solden, R.~Nazikian, and A.~Wingen, Plasma Phys.\ Contol.\ Fusion {\bf 59}, 044001(2017).
+
 \bibitem{paz1} C.~Paz-Solden, R.~Nazikian, L.~Cui, B.C.~Lyons,  D.M.~Orlov, A.~Kirk, N.C.~Logan, T.H.~Osborne, W.~Suttrop, and D.B.~Weisberg, 
@@
 
+\bibitem{ara} G.~Ara,  B.~Basu, B.~Coppi, G.~Laval, M.N.~Rosenbluth, and B.V.~Waddell, Ann.\ Phys.\ (N.Y.) {\bf 112}, 443 (1978).
+
 \bibitem{nl1} R.~Fitzpatrick, and F.L.~Waelbroeck, Phys.\ Plasmas {\bf 12}, 022307 (2005).
+
+\bibitem{wat} R.~Fitzpatrick, P.G.~Watson, and F.L.~Waelbroeck, Phys.\ Plasmas {\bf 12}, 082510 (2005).
 
@@
 
+\bibitem{coppi} B.~Coppi, J.M.~Greene, and J.L.~Johnson, Nucl.\ Fusion {\bf 6}, 101 (1966).
+
+\bibitem{ruth} P.H.~Rutherford,  Phys.\ Fluids  {\bf 16}, 1903 (1973).
+
+\bibitem{pletz} A.~Pletzer, and R.L.~Dewar, J.\ Plasma Physics {\bf 45}, 427 (1991).
+
 \bibitem{am1} R.~Fitzpatrick, R.J.~Hastie, T.J.~Martin, and C.M.~Roach, Nucl.\ Fusion {\bf 33}, 1533 (1993).
+
+\bibitem{pletz1} A.~Pletzer, A.~Bondeson, and R.L.~Dewar, J.\ Comp.\ Phys.\ {\bf 115}, 530 (1994).
+
+\bibitem{tokuda} S.~Tokuda, Nucl.\ Fusion {\bf 41}, 1037 (2001).
+
+\bibitem{brennan} D.P.~Brennan, R.J.~La Haye, A.D.~Turnbull, M.S.~Chu, T.H.~Jensen, L.L.~Lao, T.C.~Luce, P.A.~Politzer, and E.J.~Strait,
+Phys.\ Plasmas {\bf 10}, 1643 (2003).
+
+\bibitem{fura} M.~Furukawa, and S.~Tokuda, Phys.\ Plasmas {\bf 19}, 102511 (2012).
 
@@
 
-\bibitem{gim} R.~Fitzpatrick, C.G.~Gimblett, and R.J.~Hastie, 
-Plasma Phys.\ Control.\ Fusion {\bf 34}, 161 (1992).
-
-\bibitem{haz} R.D.~Hazeltine, and J.D.~Meiss, Rev.\ Mod.\ Phys.\ {\bf 121}, 1 (1985).
-
-\bibitem{ruth} P.H.~Rutherford,  Phys.\ Fluids  {\bf 16}, 1903 (1973).
-
-\bibitem{wesson} J.A.~Wesson, private communication (1993).
-
-\bibitem{ara} G.~Ara,  B.~Basu, B.~Coppi, G.~Laval, M.N.~Rosenbluth, and B.V.~Waddell, Ann.\ Phys.\ (N.Y.) {\bf 112}, 443 (1978).
-
-\bibitem{wat} R.~Fitzpatrick, P.G.~Watson, and F.L.~Waelbroeck, Phys.\ Plasmas {\bf 12}, 082510 (2005).
-
-\bibitem{rffig} R.~Fitzpatrick, Phys.\ Plasmas {\bf 10}, 2304 (2003).
+\bibitem{flat1} N.N.~Gorelenkov, R.V.~Budny, Z.~Chang, M.V.~Gorelenkova, and L.E.~Zakharov, Phys.\ Plasmas {\bf 3}, 3379 (1996).
 
 \end{thebibliography}
-
-\appendix
-\section{Linear Versus Nonlinear Tearing Mode Theory in Tokamak Plasmas}\label{appa}
-\subsection{Introduction}
-The discussion in this Appendix outlines certain facts pertaining
-to tearing modes in tokamak plasmas that ought to be common knowledge in the 
-magnetic fusion community (but appear not to be).
-
-\subsection{General Considerations}\label{general}
-Consider a conventional tokamak plasma equilibrium. To lowest order, the equilibrium is governed by force balance,
-\begin{equation}\label{ea}
--\nabla p + {\bf j}\times {\bf B} \simeq {\bf 0},
-\end{equation}
-and
-flux freezing,
-\begin{equation}\label{eb}
-{\bf E} + {\bf V}\times {\bf B} \simeq {\bf 0}.
-\end{equation}
-This is the case because the other terms in the plasma equation of motion,
-(\ref{ea}), and the plasma Ohm's law, (\ref{eb}), are much
-smaller in magnitude than the retained terms. (Here, $p$ is the
-scalar pressure, ${\bf j}$ the current density, ${\bf B}$ the
-magnetic field strength, ${\bf E}$ the electric field strength, and ${\bf V}$ the plasma velocity).
-If we average the full plasma equation of motion and the full Ohm's law, as well as the full continuity and energy evolution equations, over magnetic flux-surfaces
-then the dominant terms in these equations are annihilated, and
-we end up with a set of $1\tfrac{1}{2}$-D evolution equations,
-according to which the magnetic field and plasma current
-evolve on the relatively long resistive timescale, $\tau_R$,
-whereas the density and temperature evolve on a somewhat
-shorter transport timescale.\cite{transp,gim}
-
-A linear tearing mode is a helical instability of a tokamak plasma equilibrium that is related to a shear-Alfv\'{e}n wave.\cite{haz} The mode resonates with the equilibrium magnetic field at
-the so-called rational magnetic flux-surface at which the
-shear-Alfv\'{e}n velocity is zero. If $q$ is the safety-factor, $m$ the poloidal mode number, and $n$ the
-toroidal mode number, then the rational
-flux-surface is characterized by $q=m/n$. A thin resistive layer forms
-around the rational surface that permits the reconnection of magnetic flux on a much faster timescale than the global
-resistive evolution timescale, $\tau_R$, resulting in the formation of a helical magnetic island chain. Let the Alfv\'{e}n time,
-$\tau_A$, be the
-typical timescale on which a (compressional) Alfv\'{e}n
-wave traverses the plasma.
-In conventional tokamak plasmas, $\tau_A\ll \tau_R$. In fact,
-the magnetic Lundquist number, $S\equiv \tau_R/\tau_A$,  typically exceeds $10^{\,8}$ in present-day tokamak plasmas,
-and will likely exceed $10^{\,10}$ in ITER plasmas.
- It turns out that the width of the resistive layer is typically a factor $S^{\,-2/5}$ smaller than the
-plasma minor radius, whereas magnetic flux is reconnected on
-the hybrid timescale $\tau_A\ll \tau_A^{2/5}\,\tau_R^{3/5}\ll \tau_R$.\cite{fkr} Note that  the
-structure of the tearing mode  outside the resistive layer is simply governed by a combination of flux-freezing and perturbed force balance.
-
- Figure~\ref{fig14} sketches the typical plasma current and vorticity patterns in a linear tearing layer. Observe that there is
- no distinction between a magnetic X-point and a magnetic 
-O-point. The reason for this is that the magnetic separatrix
-of the reconnected magnetic island does not present an obstacle
-to plasma motion because the linear layer is so thin that the
-plasma can diffuse resistively across magnetic field-lines very rapidly. However, this is only the case as long
-as the radial width of the magnetic island chain is less than the linear layer width. As soon as magnetic reconnection
-at the rational surface has proceeded to such an extent that
-the magnetic island width exceeds the layer width then we enter the nonlinear regime.
-
-Figure~\ref{fig14} also sketches the
-typical plasma current and vorticity patterns in the nonlinear regime.
-Observe that there is now a considerable distinction between an X-point and an O-point.
-The reason for this is that the island is sufficiently wide that the plasma cannot diffuse across it resistively rapidly enough to
-avoid being trapped inside the magnetic separatrix. Indeed, both the regions inside and outside the magnetic separatrix
-are governed by a combination of flux-freezing and perturbed force balance, whereas the resistive
-layer, within which the plasma can easily slip through the magnetic field,  is diverted onto the magnetic separatrix. Moreover, as
-the island grows, the width of the separatrix layer becomes
-increasing negligible with respect to the full island width. It
-turns out that the separatrix layer does not significantly affect the evolution of a nonlinear magnetic island chain. Indeed,
-the celebrated Rutherford island width evolution equation,
-which governs the evolution of the island width, is simply a
-$1\tfrac{1}{2}$-D evolution equation for a helical magnetic
-equilibrium localized around the rational surface.\cite{ruth}
-The Alfv\'{e}n time plays no role in this evolution (any more
-than it plays a role in the $1\tfrac{1}{2}$-D evolution of
-the global magnetic field). Likewise, the equation that
-determines the phase velocity of a nonlinear magnetic island chain (see Ref.~\onlinecite{nl2}, and references therein) is essentially an
-expression of the $1\tfrac{1}{2}$-D evolution of the plasma
-flow profiles across the island region. As before, the  Alfv\'{e}n time plays no role in this evolution (any more
-than it plays a role in the $1\tfrac{1}{2}$-D evolution of
-the global plasma flow profiles).
-
-It follows, from the previous discussion, that the nonlinear evolution of a tearing mode in a tokamak plasma has far more in common with the $1\tfrac{1}{2}$-D
-evolution of the global plasma equilibrium than it does with
-conventional linear tearing mode physics. In particular, the Alfv\'{e}n time is
-an irrelevant timescale in nonlinear tearing mode theory, and
-is also  very much shorter than the timescales on which
-physical quantities of interest actually evolve.
-It should be noted that linear tearing layers in present-day tokamak plasmas are sufficiently thin that by the time a tearing mode is detectable it is already in the nonlinear regime (i.e., the island width exceeds the linear layer width).\cite{wesson} It, therefore, makes very little sense to
-attempt to model nonlinear tearing mode evolution in tokamak plasmas using a toroidal nonlinear MHD code.
-The reason for this is obvious: employing  an MHD code necessarily introduces the very short Alfv\'{e}n time into the calculation,
-but this timescale is actually irrelevant to the problem in hand.
-In fact, this is exactly the same reason that MHD codes are not usually used to reconstruct global plasma equilibria, or to model their time evolution.
-
-\subsection{Natural Frequency}\label{natural}
-The natural frequency of a (stable) tearing mode is
-the helical phase velocity with which it would propagate
-were it actually unstable.\cite{rfa} The natural frequency
-is determined by the equilibrium plasma flow at the
-rational surface. Now, a magnetic island is a helical
-pattern in the magnetic field  generated by a helical current perturbation that is localized in the
-vicinity of the rational surface.
-Given that plasma current is predominately carried by the
-electrons, it is natural to suppose that a magnetic
-island chain (as well as the tearing mode perturbation
-away from the rational surface)  is convected by the
-electron fluid in the immediate vicinity of the rational
-surface. This is indeed the case in the linear regime.\cite{ara} Of course, as a consequence of diamagnetic flows, if the island chain is
-convected by the electron fluid at the rational surface then it propagates with respect to the local ion fluid. However, this is not a
-problem because a linear layer is sufficiently thin that the magnetic field can diffuse through the plasma very rapidly, which implies that
-the ion fluid is not tied to the magnetic structure of the island chain.
-
-The situation is very different in the nonlinear regime. 
-As we have seen, the region inside the magnetic separatrix of a nonlinear magnetic island chain is governed by a combination of flux-freezing and perturbed force balance.
-This implies that both the electron and the ion fluids are trapped inside the separatrix, and are, therefore,  forced to co-rotate with the island chain. There
-is no such constraint outside the separatrix, so the electron and ion fluids rotate at different speeds in this region,
-as a consequence of diamagnetism.  It follows that one or other of the electron and the ion fluid rotation profiles must exhibit a strong gradient across
-the separatrix. The island propagation velocity is determined by which of the two fluids is most resistant to the formation of such a gradient. 
-Of course, it is the ion fluid which is more resistant because of its much greater perpendicular viscosity,\cite{nl1,wat} as well as its much larger 
-neoclassical stress tensor.\cite{nl2} Hence, a nonlinear magnetic island chain is convected by the ion fluid in the vicinity of the rational
-surface, because this choice of propagation speed minimizes the ion fluid velocity gradient across the separatrix.
-
-Finally, we could imagine that if the width of an island chain is neither much less than the linear layer width (which is the strict
-criterion for the validity of linear theory) nor much greater than the linear layer width (which is the strict criterion for
-the validity of nonlinear theory) then the chain lies in some sort of intermediate regime in which it is
-convected by the local guiding-center fluid (which is intermediate between the predictions of linear and nonlinear theory).
 
@@
 \includegraphics[height=7in]{fig3.pdf}
-\caption{Top Panel: The red, green, blue, and cyan curves show the electron number density ($10^{19}\,{\rm m}^{-3}$),
-electron temperature (keV), (thermal) ion temperature (keV), and
- C-VI ion number density  ($10^{18}\,{\rm m}^{-3}$)  profiles, respectively,  in  DIII-D discharge \#145380 at time $t=2500$ ms. Middle Panel:  
+\caption{Top Panel: The red, green, blue,  cyan, and magenta curves show the electron number density ($10^{19}\,{\rm m}^{-3}$),
+electron temperature (keV), (thermal) ion temperature (keV), 
+ C-VI ion number density  ($10^{18}\,{\rm m}^{-3}$), and flux-surface averaged neutral density ($10^{17}\,{\rm m}^{-3}$)   profiles, respectively,  in  DIII-D discharge \#145380 at time $t=2500$ ms.
+Middle Panel:
  ${\bf E}\times {\bf B}$ frequency profile in  DIII-D discharge \#145380 at time $t=2500$. Bottom Panel: The red, green, and blue curves show
- the perpendicular momentum, energy, and particle diffusivity profiles, respectively, 
+ the perpendicular momentum ($\chi_\phi$), energy ($\chi_E$), and particle ($D_\perp$) diffusivity profiles, respectively, 
  in  DIII-D discharge \#145380 at time $t=2500$ ms.
@@
 the $95\%$ flux surface (${\mit\Psi}_N=0.950$), the
-effective plasma boundary for the GPEC and EPEC calculations
+effective plasma boundary for the {\tt GPEC} and {\tt EPEC} calculations
 (${\mit\Psi}_N=0.997$), and the true plasma boundary (${\mit\Psi}_N=1.00$), respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
@@
 \begin{figure}
-\includegraphics[height=6in]{fig5.pdf}
+\includegraphics[height=7in]{fig5.pdf}
 \caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
@@
 \begin{figure}
-\includegraphics[height=6in]{fig6.pdf}
+\includegraphics[height=7in]{fig6.pdf}
 \caption{Top Panel: Full  $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time 
@@
 Bottom Panel:  Full $n=3$ island widths as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
+in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics. The yellow, cyan, magenta, brown, pink,
+purple, and orange  areas correspond to $m=8$, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
 The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig6}
@@
 \begin{figure}
-\includegraphics[height=6in]{fig7.pdf}
+\includegraphics[height=7in]{fig7.pdf}
 \caption{Top Panel: Density flattening widths associated with induced $n=3$ magnetic island  chains as functions of the least-squares linear fit to $q_{95}$ versus time
@@
 Bottom Panel:  Electron temperature flattening widths associated with induced $n=3$ magnetic island chains as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
+in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics. The yellow, cyan, magenta, brown, pink,
+purple, and orange  areas correspond to $m=8$, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
 The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig7}
@@
 \begin{figure}
-\includegraphics[height=6in]{fig8.pdf}
+\includegraphics[height=7in]{fig8.pdf}
 \caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by the ${\bf E}\times {\bf B}$
-frequency.
+in   DIII-D discharge \#145380, assuming that the natural frequency is determined by the local ${\bf E}\times {\bf B}$
+velocity.
 Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is  determined by the ${\bf E}\times {\bf B}$
-frequency. The red, green, blue, yellow, cyan, magenta, brown, pink,
+in   DIII-D discharge \#145380, assuming that the natural frequency is  determined by the local ${\bf E}\times {\bf B}$
+velocity. The red, green, blue, yellow, cyan, magenta, brown, pink,
 purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows.} \label{fig8}
@@
 \begin{figure}
-\includegraphics[height=6in]{fig9.pdf}
+\includegraphics[height=7in]{fig9.pdf}
 \caption{Top Panel: $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time
@@
 Bottom Panel:  $n=3$ island widths as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is  determined by the ${\bf E}\times {\bf B}$
-frequency. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
+in   DIII-D discharge \#145380, assuming that the natural frequency is  determined by the local ${\bf E}\times {\bf B}$
+velocity. The yellow, cyan, magenta, brown, pink,
+purple, and orange  areas correspond to $m=8$, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
 The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig9}
@@
 \begin{figure}
-\includegraphics[height=6in]{fig10.pdf}
+\includegraphics[height=7in]{fig10.pdf}
 \caption{Top Panel: Density flattening widths associated with induced $n=3$ magnetic island  chains as functions of the least-squares linear fit to $q_{95}$ versus time
-in   DIII-D discharge \#145380, assuming that the natural frequency is  determined by the ${\bf E}\times {\bf B}$
-frequency.
+in   DIII-D discharge \#145380, assuming that the natural frequency is  determined by the local ${\bf E}\times {\bf B}$
+velocity.
 Bottom Panel:  Electron temperature flattening widths associated with induced $n=3$ magnetic island chains as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by the ${\bf E}\times {\bf B}$
-frequency. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
+in   DIII-D discharge \#145380, assuming that the natural frequency is determined by the local ${\bf E}\times {\bf B}$
+velocity. The yellow, cyan, magenta, brown, pink,
+purple, and orange  areas correspond to $m=8$, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
 The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig10}
@@
 \begin{figure}
-\includegraphics[height=6in]{fig11.pdf}
+\includegraphics[height=7in]{fig11.pdf}
 \caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
@@
 \begin{figure}
-\includegraphics[height=6in]{fig12.pdf}
+\includegraphics[height=7in]{fig12.pdf}
 \caption{Top Panel: $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time
@@
 Bottom Panel:  $n=3$ island widths as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
+in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics. The yellow, cyan, magenta, brown, pink,
+purple, and orange  areas correspond to $m=8$,  9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
 The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig12}
@@
 \begin{figure}
-\includegraphics[height=6in]{fig13.pdf}
+\includegraphics[height=7in]{fig13.pdf}
 \caption{Top Panel: Density flattening widths associated with induced $n=3$ magnetic island  chains as functions of the least-squares linear fit to $q_{95}$ versus time
@@
 Bottom Panel:  Electron temperature flattening widths associated with induced $n=3$ magnetic island chains as functions of time
-in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
+in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics. The yellow, cyan, magenta, brown, pink,
+purple, and orange  areas correspond to $m=8$, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
 The horizontal dotted lines indicate  the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig13}
@@
 \begin{figure}
-\includegraphics[height=4in]{fig14.pdf}
-\caption{Schematic diagram showing the perturbed plasma current and vorticity patterns around the magnetic X- and O-points of a linear and a nonlinear tearing mode. 
-The horizontal axis measures radial distance from the rational
-surface, whereas the vertical axis measures distance along equilibrium magnetic field-lines. Red and blue
-correspond to positive and negative current/vorticity values, respectively. (See Figs.~7 and 10 in 
-Ref.~\onlinecite{rffig}.)}\label{fig14}
+\includegraphics[height=3in]{fig14.pdf}
+\caption{Summary of results.
+The yellow vertical bands indicate the experimental $n=3$ ELM-suppression/mitigation windows in DIII-D discharge \#145380, as functions  of the least-squares linear fit to $q_{95}$ versus time.
+The brown, magenta, and cyan bars show the  ELM suppression/mitigation windows predicted by the {\tt EPEC} code that are associated with locked $m=11/n=3$, $10/3$, and $9/3$, magnetic island chains, respectively,
+driven at the top of the pedestal. The three cases considered are such that the natural frequency at a given resonant surface is determined by:
+1) the local ion flow; 2) the local ${\bf E}\times {\bf B}$ velocity; 3) the local electron flow.}\label{fig14}
 \end{figure}

### 2020-10-31 Papers/Paper2/Paper.tex
Lastest version

@@
 
-``Asymptotic matching'' is by far the most efficient method for modeling the response of a tokamak plasma to an RMP.\cite{fkr,rfa, am1,am2,am3} 
+``Asymptotic matching'' is by far the most efficient method for modeling the response of a tokamak plasma to an RMP.\cite{fkr,coppi,ruth,ara,pletz,rfa, am1,tokuda,brennan,am2,am3} 
 According to the asymptotic matching approach, the response of the plasma to the applied RMP is governed by a combination of flux-freezing and
@@
 Here, $\sigma(r)$, ${\mit\Omega}_\theta(r,t)$, and ${\mit\Omega}_\phi(r,t)$ are the 
-plasma conductivity, poloidal angular velocity, and toroidal angular velocity profiles, respectively. 
+plasma electrical conductivity, poloidal angular velocity, and toroidal angular velocity profiles, respectively. 
 Note that, in this paper, we are assuming that the constant-$\psi$ approximation\,\cite{fkr} holds at the rational surface. (It is demonstrated in
@@
 bottom of the pedestal overlap, implying that the magnetic field in this region is rendered stochastic. The lower panel
-of Fig.~\ref{fig3} shows the actual widths of the various magnetic island chains driven by the applied $n=3$ RMP as functions of time. It is apparent 
-that the true island widths are generally much smaller than the vacuum island widths, as a consequence of the shielding of driven magnetic
+of Fig.~\ref{fig3} shows the predicted widths of the various magnetic island chains driven by the applied $n=3$ RMP as functions of time. It is apparent 
+that the predicted island widths are generally much smaller than the vacuum island widths, as a consequence of the shielding of driven magnetic
 reconnection due to plasma flow. However, the shielding breaks down at various rational surfaces when the associated natural frequency is zero (see the lower panel of
@@
 Finally, the best agreement between theory and experiment is obtained by assuming that, in the absence of the RMP, the 
- natural frequency of the tearing mode resonant at the $k$th rational surface is given by\,\cite{rftor1}
+ natural frequency of the tearing mode resonant at the $k$th rational surface is given by\,\cite{rftor1,heyn}
 \begin{equation}\label{eeb}
@@
 
+\bibitem{coppi} B.~Coppi, J.M.~Greene, and J.L.~Johnson, Nucl.\ Fusion {\bf 6}, 101 (1966).
+
+\bibitem{ruth} P.H.~Rutherford,  Phys.\ Fluids  {\bf 16}, 1903 (1973).
+
+\bibitem{ara} G.~Ara,  B.~Basu, B.~Coppi, G.~Laval, M.N.~Rosenbluth, and B.V.~Waddell, Ann.\ Phys.\ (N.Y.) {\bf 112}, 443 (1978).
+
+\bibitem{pletz} A.~Pletzer, and R.L.~Dewar, J.\ Plasma Physics {\bf 45}, 427 (1991).
+
 \bibitem{rfa} R.~Fitzpatrick, Nucl.\ Fusion {\bf 33}, 1049 (1993).
@@
 
+\bibitem{tokuda} S.~Tokuda, Nucl.\ Fusion {\bf 41}, 1037 (2001).
+
+\bibitem{brennan} D.P.~Brennan, R.J.~La Haye, A.D.~Turnbull, M.S.~Chu, T.H.~Jensen, L.L.~Lao, T.C.~Luce, P.A.~Politzer, and E.J.~Strait,
+Phys.\ Plasmas {\bf 10}, 1643 (2003).
+
 \bibitem{am2} A.H.~Glasser, Z.R.~Wang, and J.-K.~Park, Phys.\ Plasmas {\bf 23}, 112506 (2016).
@@
 \bibitem{am3} R.~Fitzpatrick, Phys.\ Plasmas {\bf 24}, 072506 (2017).
-
-\bibitem{ruth} P.H.~Rutherford,  Phys.\ Fluids  {\bf 16}, 1903 (1973).
 
@@
 
-\bibitem{rftor1} R.~Fitzpatrick,  ``Modeling $q_{95}$ Windows for the Suppression of Edge Localized
-Modes by Resonant Magnetic Perturbations in the DIII-D Tokamak", submitted to Physics of Plasmas (2020).
+\bibitem{rftor1} R.~Fitzpatrick,  Phys.\ Plasmas {\bf 27}, 102511 (2020).
 
@@
 
-\bibitem{ara} G.~Ara,  B.~Basu, B.~Coppi, G.~Laval, M.N.~Rosenbluth, and B.V.~Waddell, Ann.\ Phys.\ (N.Y.) {\bf 112}, 443 (1978).
-
 \bibitem{lin1} M.~B\'{e}coulet, F.~Orain, P.~Maget, N.~Mellet, X.~Garbet, E.~Nardon, G.T.A.~Huysmans, T.~Caspar, A.~Loarte,  P.~Cayna, {\em et al.}, 
@@
 Phys.\ Plasmas {\bf 20}, 102510 (2013).
+
+\bibitem{heyn} M.F.~Heyn, I.B.~Ivanov, S.V.~Kasilov, W.~Kernbichler, I.~Joseph, R.A.~Moyer,  and A.M.~Runov, Nucl.\ Fusion {\bf 48}, 024005 (2008).
 
@@
 Bottom Panel:  Full $n=3$ island widths as functions of time
-in   DIII-D discharge \#145380. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
+in   DIII-D discharge \#145380. The yellow, cyan, magenta, brown, pink,
+purple, and orange  areas correspond to $m=8$, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
 The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig3}
@@
 Bottom Panel:  Full $n=3$ island widths as functions of time
-in   DIII-D discharge \#145380. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
+in   DIII-D discharge \#145380. The yellow, cyan, magenta, brown, pink,
+purple, and orange  areas correspond to $m=8$, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
 The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig5}
@@
 Bottom Panel:  Full $n=3$ island widths as functions of time
-in   DIII-D discharge \#145380. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
+in   DIII-D discharge \#145380. The yellow, cyan, magenta, brown, pink,
+purple, and orange  areas correspond to $m=8$, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
 The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig8}
@@
 Bottom Panel:  Full $n=3$ island widths as functions of time
-in   DIII-D discharge \#145380. The blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
+in   DIII-D discharge \#145380. The yellow, cyan, magenta, brown, pink,
+purple, and orange  areas correspond to $m=8$, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
 The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig10}

### 2020-11-05 Papers/Paper2/Submit/Paper.tex
Lastest version of paper2

--- 2020-10-31 Papers/Paper2/Paper.tex
@@
 is non-zero in the nonlinear regime. The improved model is incorporated into the {\tt EPEC} toroidal asymptotic matching code.
-The modified {\tt EPEC} code is used to investigate RMP-induced edge-localized-mode (ELM) mitigation/suppression in DIII-D H-mode discharge \#145380. 
-Allowing for a finite slip-frequency (i.e., relaxing the so-called no-slip constraint) is found to slightly facilitate the locking of
-driven magnetic island chains to the RMP, and, hence, to slightly facilitate RMP-induced ELM mitigation/suppression.  The previously obtained conclusion 
+The modified {\tt EPEC} code is used to investigate RMP-induced edge-localized-mode (ELM) suppression in DIII-D H-mode discharge \#145380. 
+Somewhat surprisingly, allowing for a finite slip-frequency (i.e., relaxing the so-called no-slip constraint) is found to only slightly facilitate the locking of
+driven magnetic island chains to the RMP, and, hence, to only slightly facilitate RMP-induced ELM suppression.  The previously obtained conclusion 
 that the response of a typical H-mode tokamak plasma to an RMP cannot be accurately modeled by linear theory is confirmed.
@@
 The recently developed, toroidal, asymptotic matching code {\tt EPEC} (Extended Perturbed Equilibrium Code) has been used to simulate 
-RMP-induced ELM mitigation/suppression in DIII-D H-mode plasmas.\cite{rftor,rftor1}
+RMP-induced ELM suppression in DIII-D H-mode plasmas.\cite{rftor,rftor1}
 The original {\tt EPEC} model incorporates the no-slip constraint.
@@
 \subsection{Plasma Equilibrium}
-Consider a large aspect-ratio, low-$\beta$, tokamak plasma whose magnetic flux-surfaces map out (almost)
-concentric circles in the poloidal plane.
+Consider a large aspect-ratio, low-$\beta$, circular cross-section, tokamak plasma.
 Such a plasma is well approximated as a periodic cylinder.  Suppose that the minor radius of the plasma
@@
 plasma major radius. It is convenient to define the simulated toroidal angle $\phi=z/R_0$. 
-
-The equilibrium magnetic field is written ${\bf B} = [0,B_\theta(r), B_\phi]$. The associated equilibrium
-plasma current density takes the form ${\bf j} =[0,0,j_\phi(r)]$, where $\mu_0\,j_\phi= (1/r)\,d(r\,B_\theta)/dr$. The
+The equilibrium magnetic field is written ${\bf B} = [0,B_\theta(r), B_\phi]$.  The
 so-called ``safety-factor'', $q(r)=r\,B_\phi/(R_0\,B_\theta)$, parameterizes the helical pitches of equilibrium magnetic
@@
 terms of a perturbed poloidal magnetic flux (divided by $2\pi\,R_0$), $\psi(r,\theta,\phi,t)$. In fact, $\delta{\bf B} = \nabla\psi\times \nabla z$, 
-and $\mu_0\,\delta {\bf j} = - \nabla^2\psi\,\nabla z$,
 where $\psi(r,\theta,\phi,t) = \hat{\psi}(r,t)\,\exp[{\rm i}\,(m\,\theta-n\,\phi)]$, and $\hat{\psi}$ is real. This particular representation
@@
 nonlinear slip-frequency may be non-negligible for developing island chains, which is why we are including it in our analysis.
-(Note that the nonlinear slip-frequency does not appear in rigorous island calculations, such as
-that described in Ref.~\onlinecite{rfisland}, and references therein, because such calculations depend crucially on
-complicated hierarchical ordering assumptions, according to which the nonlinear slip-frequency is negligible.)
 
 \subsection{Composite Model}
-We can combine Eqs.~(\ref{e3}), (\ref{e4}), (\ref{e5}), and (\ref{e7}) to give the following
+If we define $X_s = |{\mit\Psi}_s|\,\cos\varphi_s$, $Y_s = |{\mit\Psi}_s|\,\sin\varphi_s$, $X_v = |{\mit\Psi}_v|\,\cos\varphi_v$, and $Y_v = |{\mit\Psi}_v|\,\sin\varphi_v$ 
+then we can combine Eqs.~(\ref{e3}), (\ref{e4}), (\ref{e5}), and (\ref{e7}) to give the following
 composite resonant response model that interpolates between the linear and the nonlinear
-regimes:
-\begin{align}\label{e9}
-\left(\frac{({\cal I}/2)\,W_s+\delta_s}{r_s}\right)\tau_R\,\frac{d|{\mit\Psi}_s|}{dt} &= E_{ss}\,|{\mit\Psi}_s| + E_{sv}\,|{\mit\Psi}_v|\,\cos(\varphi_s-\varphi_v),\\[0.5ex]
-\frac{d\varphi_s}{dt}& = \omega_s - \frac{E_{sv}}{\tau_R}\left(\frac{r_s}{({\cal I}/2)\,W_s+\delta_s}\right)\frac{|{\mit\Psi}_v|}{|{\mit\Psi}_s|}\,\sin(\varphi_s-\varphi_v).\label{e10}
-\end{align}
-If we define $X_s = |{\mit\Psi}_s|\,\cos\varphi_s$, $Y_s = |{\mit\Psi}_s|\,\sin\varphi_s$, $X_v = |{\mit\Psi}_v|\,\cos\varphi_v$, and $Y_v = |{\mit\Psi}_v|\,\sin\varphi_v$ 
-then the previous two equations are more conveniently written in the non-singular (when $|{\mit\Psi}_s|=0$) forms:\,\cite{slip1,slip2,slip3}
+regimes:\,\cite{slip1,slip2,slip3}
 \begin{align}\label{e11}
@@
 
-Equation~(\ref{e15}) represents a minor improvement to Eq.~(D1) of Ref.~\onlinecite{rftor} in which the interpolation between the
+Equation~(\ref{e15}) represents a {\em minor}\/ improvement to Eq.~(D1) of Ref.~\onlinecite{rftor} in which the interpolation between the
 linear and nonlinear regimes is performed in a slightly more accurate manner.
@@
 poloidal and toroidal velocity profiles, respectively, induced by the electromagnetic torques that develop in the vicinities of the various rational surfaces in the plasma in response to the RMP.
+
 Equation~(\ref{e19}) represents
-a major improvement to Eq.~(D6) of Ref.~\onlinecite{rftor} that takes into  account the finite slip-frequencies of the magnetic island chains induced at
+a {\em major}\/ improvement to Eq.~(D6) of Ref.~\onlinecite{rftor} that takes into  account the finite slip-frequencies of the magnetic island chains induced at
 the various rational surfaces in the plasma. In the absence of a finite slip-frequency, the right-hand side of Eq.~(\ref{e19}) would be zero.
@@
 \end{equation}
-Equations (\ref{e15}), (\ref{e19}), (\ref{e21}), (\ref{e22}) and (\ref{e23}) are the toroidal generalizations of Eqs.~(\ref{e9}), (\ref{e10}), (\ref{e11}), (\ref{e12}), and (\ref{e23x}), respectively.
+Equationsv (\ref{e21}), (\ref{e22}) and (\ref{e23}) are the toroidal generalizations of Eqs.~(\ref{e11}), (\ref{e12}), and (\ref{e23x}), respectively.
 
@@
 \subsection{Introduction}
-DIII-D discharge \#145380 is an ITER-Similar-Shape (ISS), ELMing, H-mode discharge, with a toroidal magnetic field $B_T=-1.9\,{\rm T}$, in which the
-plasma current, $I_p$, is slowly ramped over a 2 second interval in order to scan the magnetic safety-factor.\cite{d3d,d3d2} The majority ions are Deuterium, whereas the
-minority ions are Carbon~VI.
-Figure~\ref{fig1} gives an overview of this discharge. ${\mit\Psi}_N$ is the conventional normalized poloidal magnetic flux.
+DIII-D discharge \#145380 is an ITER-Similar-Shape (ISS), ELMing, H-mode discharge in which the
+plasma current is slowly ramped in order to scan the magnetic safety-factor.\cite{d3d,d3d2} This discharge is described in more detail in Sect.~III.B of Ref.~\onlinecite{rftor1}.
 A static RMP is applied to the plasma by running steady $n=3$ currents through the I-coil system.\cite{icoil}
-Three windows of ELM suppression or mitigation are evident: the first (in which ELMs are mitigated, but not
-entirely suppressed) extends from $t=2840$--$2980$ ms; the
-second (in which ELM are entirely suppressed) extends from $t=3320$--$3560$ ms; and the third (in which ELMs are
-entirely suppressed) extends from $t=3880$--$4200$ ms. The 
-first, second, and third ELM-suppression/mitigation windows extend over the $\overline{q_{95}}$ ranges $3.88$--$3.94$, $3.62$--$3.73$,
-and $3.33$--$3.48$, respectively. Here, $\overline{q_{95}}$ is least-squares linear fit to the variation of the safety-factor at the ${\mit\Psi}_N = 0.95$ flux-surface with time.
+Three windows of ELM suppression  are evident: the first occurs when $t\simeq 2900$ ms and $q_{95}\simeq 3.91$; the
+second occurs when $t=3400$ ms and $q_{95}\simeq 3.66$; and the third occurs when $t\simeq 4000$ ms and $q_{95}\simeq 3.41$.  Here, $q_{95}$ is the safety-factor at the 95\% flux-surface.
 
@@
 where 
-\begin{equation}
-\omega_E({\mit\Psi}_p) = -\frac{d{\mit\Phi}}{d{\mit\Psi}_p}.
-\end{equation}
+$\omega_E({\mit\Psi}_p) = -d{\mit\Phi}/d{\mit\Psi}_p$.
 Here, ${\mit\Phi}({\mit\Psi}_p)$ is the equilibrium scalar electric potential (in the absence of the RMP), ${\mit\Psi}_p$ the equilibrium poloidal magnetic flux (divided by $2\pi$), 
@@
 The upper panel of Fig.~\ref{fig2} shows the natural frequencies, in the absence of the RMP, of the various  $n=3$ tearing modes 
- that are resonant in the pedestal of DIII-D discharge \#145380. It can be seen that 
-the natural frequencies of the $m=11$ (brown), the $m=10$ (magenta), and the $m=9$ (cyan), tearing modes have their
-zero-crossings in the  first, second, and third, ELM-suppression/mitigation window, respectively. 
-  The lower panel of Fig.~\ref{fig2} shows the natural frequencies, in the presence of the RMP, of the various $n=3$
-tearing modes that are resonant in the pedestal. It is apparent that if the magnitude of the natural frequency in the absence of the RMP falls below about
+ that are resonant in the pedestal of DIII-D discharge \#145380, whereas  
+  the lower panel of Fig.~\ref{fig2} shows the same frequencies  in the presence of the RMP.
+   It is apparent that if the magnitude of the natural frequency in the absence of the RMP falls below about
 $3\,{\rm krad/s}$ then the associated tearing mode locks to the RMP (i.e., its true natural frequency becomes zero).
 
-The upper panel of Fig.~\ref{fig3} shows the widths of the various vacuum magnetic island chains driven by the applied $n=3$ RMP in the pedestal region as functions of $
-\overline{q_{95}}$.
-The vacuum island widths are the  expected island widths in the absence of any shielding of driven magnetic reconnection due to
-plasma flow; in other words, they are the  widths of the island chains that would be driven if all of the natural frequencies were zero. It can be seen that
-the driven magnetic island chains extend over most of the pedestal, implying a very significant degradation in pedestal energy and particle confinement due to the
-expected flattening of the density and temperature profiles across the chains.\cite{flat} Moreover, the driven island chains at the
-bottom of the pedestal overlap, implying that the magnetic field in this region is rendered stochastic. The lower panel
-of Fig.~\ref{fig3} shows the predicted widths of the various magnetic island chains driven by the applied $n=3$ RMP as functions of time. It is apparent 
-that the predicted island widths are generally much smaller than the vacuum island widths, as a consequence of the shielding of driven magnetic
-reconnection due to plasma flow. However, the shielding breaks down at various rational surfaces when the associated natural frequency is zero (see the lower panel of
+The upper panel of Fig.~\ref{fig3} shows the widths of the various  magnetic island chains driven by the applied $n=3$ RMP in the
+absence of shielding due to plasma flow, whereas the lower panel
+shows the same widths in the presence of shielding. It is apparent 
+that the predicted island widths are generally much smaller than the ``vacuum'' island widths (i.e., the widths in the absence of shielding), as a consequence of the shielding of driven magnetic
+reconnection by plasma flow. However, this shielding breaks down at various rational surfaces when the associated natural frequency is zero (see the lower panel of
 Fig.~\ref{fig3}). In this situation, the driven island width is similar to the vacuum island width.
@@
 pedestal, and, thereby, prevent it from attaining a width sufficient to destabilize peeling-ballooning modes\,\cite{connor}  (which are thought to trigger ELMs).\cite{d3d}
-It has also been suggested that  the well-known ``density pump-out" phenomenon, which is often observed when RMPs are applied
-to H-mode tokamak plasmas, is associated with the formation of overlapping island chains
-at the bottom of the pedestal.\cite{hu}
 
@@
  the comparatively wide, $m=11$ (brown),  $m=10$ (magenta), and  $m=9$ (cyan), locked magnetic island chains which are predicted to be driven by the RMP in the pedestal of DIII-D discharge \#145380 line up
-fairly well with the first, second, and third, ELM-suppression/mitigation windows, respectively. To be more exact, the island chains are located at
+fairly well with the first, second, and third, ELM-suppression windows, respectively. To be more exact, the island chains are located at
 the top of the pedestal (i.e., ${\mit\Psi}_N=0.925$), and also occur in roughly the correct time intervals. This is consistent with the hypothesis that the formation of locked
 magnetic island chains at the top of the pedestal causes ELM mitigation/suppression.
-Note that overlapping island chains
-are also driven at the bottom of the pedestal; as has already been mentioned, such island chains are associated with the density pump-out phenomenon.
 
@@
 RMP-modified natural frequency to a value close to zero.) 
-This is not surprising, since
+This is not surprising, because 
 relaxation of the no-slip constraint clearly weakens the coupling between a given magnetic island chain and the local plasma flow (which is ultimately responsible
@@
 It is remarkable that the results shown in Figs.~\ref{fig2}--\ref{fig4} are so similar, given that the relaxation of the no-slip constraint leads to a
-radical modification of the dynamics of non-locked magnetic island chains. When the no-slip constraint is imposed, the widths of magnetic island chains that are
+{\em radical}\/ modification of the dynamics of non-locked magnetic island chains. When the no-slip constraint is imposed, the widths of magnetic island chains that are
 unable to lock to the RMP are forced to pulsate, periodically falling to zero, because the helical phases of the chains are forced to
-continuously increase (or decrease) by their non-zero natural frequencies.\cite{rfb,rfc,rfisland,rf1,pulse} On the other hand, when the no-slip
+continuously increase (or decrease) by their non-zero natural frequencies.\cite{rfb,rfc,rf1,pulse} On the other hand, when the no-slip
 constraint is relaxed, the widths of magnetic island chains that are unable to lock to the RMP have steady values, because the  chains can
@@
 where
-\begin{align}
-\omega_{\ast\,e}({\mit\Psi}_p) &=\frac{T_e}{e}\,\frac{d\ln p_e}{d{\mit\Psi}_p}.
-\end{align}
+$\omega_{\ast\,e}({\mit\Psi}_p)=(T_e/e)\,d\ln p_e/d{\mit\Psi}_p$.
  Here,  $e$ is the magnitude of the electron charge,  $p_e({\mit\Psi}_p)$  the equilibrium (i.e., in the absence of the RMP)
@@
 where
-\begin{align}
-\omega_{\ast\,a}({\mit\Psi}_p) &=-\frac{T_a}{Z_a\,e}\,\frac{d\ln p_a}{d{\mit\Psi}_p},\\[0.5ex]
-\eta_a({\mit\Psi}_p)&=\frac{d\ln T_a}{d\ln n_a},
-\end{align}
+$\omega_{\ast\,a}({\mit\Psi}_p) =-(T_a/Z_a\,e)\,d\ln p_a/d{\mit\Psi}_p$,
+$\eta_a({\mit\Psi}_p)=d\ln T_a/d\ln n_a$,
 for $a=i, I$. 
@@
 Finally, the best agreement between theory and experiment is obtained by assuming that, in the absence of the RMP, the 
- natural frequency of the tearing mode resonant at the $k$th rational surface is given by\,\cite{rftor1,heyn}
-\begin{equation}\label{eeb}
-\varpi_{k\,0} = \varpi_{{\rm eb}\,k}\equiv -n\,(\omega_E)_{{\mit\Psi}_{p\,k}}.
-\end{equation}
+ natural frequency of the tearing mode resonant at the $k$th rational surface is given by Eq.~(\ref{e24}).\cite{rftor1,heyn}
 
@@
 comparatively narrow. The true slip-frequency becomes less than the linear slip-frequency as soon as the island width exceeds the
-linear layer width. [See Eq.~(\ref{e10}).] The fact that the linear calculation is highly inaccurate confirms the conclusion reached in Ref.~\onlinecite{rf1}
+linear layer width. The fact that the linear calculation is highly inaccurate confirms the conclusion reached in Ref.~\onlinecite{rf1}
 that the response of a typical H-mode tokamak plasma to an RMP is not governed by linear theory, because the driven
@@
 windows correspond to the formation of wide locked magnetic island chains at the top of the pedestal). 
-However, the windows do not occur in the correct time intervals. We conclude that Eq.~(\ref{eeb}) gives a more accurate prediction for the
+However, the windows do not occur in the correct time intervals. We conclude that Eq.~(\ref{e24}) gives a more accurate prediction for the
 natural frequencies, in the absence of the RMP, than Eq.~(\ref{ecomp}). However, the reason for this is, as yet, unclear.
@@
 no-slip constraint at the various rational surfaces in the plasma and those in which the constraint is relaxed. This is true despite
-the fact that the nature of non-locked island solutions is radically different in the two cases (in the first case, the widths of the island
+the fact that the nature of non-locked island solutions is {\em radically}\/ different in the two cases (in the first case, the widths of the island
 chains driven at the rational surfaces pulsate, in the second they remain steady).
@@
 
-\section*{Data Availabity Statement}
+\section*{Data Availability Statement}
 The data that support the findings of this study are available from the corresponding author upon reasonable request.
@@
 
-\bibitem{rfisland} R.~Fitzpatrick, Phys.\ Plasmas {\bf 25}, 082513 (2018).
+%\bibitem{rfisland} R.~Fitzpatrick, Phys.\ Plasmas {\bf 25}, 082513 (2018).
 
@@
 
-\bibitem{hu} Q.M.~Hu,  R.~Nazikian,  B.A.~Grierson,  N.C.~Logan,  J.-K.~Park,  C.~Paz-Soldan, and Q.~Yu, Phys.\ Rev.\ Lett.\ {\bf 125}, 045001 (2020).
+\bibitem{hu} Q.M.~Hu,  R.~Nazikian,  B.A.~Grierson,  N.C.~Logan,  J.-K.~Park,  C.~Paz-Soldan, and Q.~Yu, Phys.\ Plasmas {\bf 26}, 120702 (2019).
 
-\bibitem{flat} R.~Fitzpatrick, Phys.\ Plasmas {\bf 2}, 825 (1995).
+%\bibitem{flat} R.~Fitzpatrick, Phys.\ Plasmas {\bf 2}, 825 (1995).
 
@@
 
-\begin{figure}
-\includegraphics[height=5in]{fig1.pdf}
-\caption{Overview of DIII-D discharge \#145380.
-(a) Safety factor at  ${\mit\Psi}_N=0.95$. 
-(b) $D_\alpha$ (i.e., Deuterium Balmer-alpha) signal, as well as $n=3$ current flowing in upper and lower sections of I-coil. 
-(c) Pedestal (i.e., ${\mit\Psi}_N=0.94$)
-electron pressure.
+%\begin{figure}
+%\includegraphics[height=5in]{fig1.pdf}
+%\caption{Overview of DIII-D discharge \#145380.
+%(a) Safety factor at  ${\mit\Psi}_N=0.95$. 
+%(b) $D_\alpha$ (i.e., Deuterium Balmer-alpha) signal, as well as $n=3$ current flowing in upper and lower sections of I-coil. 
+%(c) Pedestal (i.e., ${\mit\Psi}_N=0.94$)
+%electron pressure.
 (The red curve is the running average over 10 ms.) (d) Pedestal electron number density.
 The common vertical yellow bands indicate the ELM-suppression/mitigation windows.}\label{fig1}
-\end{figure}
+%\end{figure}
 
@@
 in   DIII-D discharge \#145380. The yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=8$, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
+purple, and orange  areas correspond to $m=8$, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
 The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig5}
@@
 in   DIII-D discharge \#145380. The yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=8$, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
+purple, and orange  areas correspond to $m=8$, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
 The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig8}
@@
 in   DIII-D discharge \#145380. The yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=8$, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
+purple, and orange  areas correspond to $m=8$, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
 The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig10}

### 2020-11-05 Papers/Paper2/Submit/Reply.tex
Lastest version of paper2

\documentclass{article}[12pt]
\usepackage{fullpage}

\begin{document}
\begin{center}
{\em Further Modeling $q_{95}$ Windows for the Suppression of Edge Localized Modes by Resonant Magnetic}\\[0.5ex]
{\em Perturbations in the DIII-D tokamak}\\[1ex]
by Richard Fitzpatrick\\[1ex]
{\bf Reply to Editor's Comments}
\end{center}

I have modified the paper to remove material that appeared in earlier papers. I have also tried to make it more
clear why it is somewhat surprising that the relaxation of the no-slip constraint makes so little difference to
the calculation.
\end{document}

### 2020-11-14 Flux/Source/Flux.h
Flux version 1.5

@@ -38,6 +38,7 @@
 // 1.2 - Improved gFile indexing
 // 1.3 - Major rearrangement of input and output files
 // 1.4 - Added linear interpolation
+// 1.5 - Added RP1, Bt, Bt1, Bp., Bp1, and B2v
 
 // ############################################################################
 
@@ -45,7 +46,7 @@
 #define FLUX
 
 #define VERSION_MAJOR 1
-#define VERSION_MINOR 4
+#define VERSION_MINOR 5
 
 #include <stdio.h>
 #include <math.h>
@@ -143,12 +144,13 @@ class Flux
   double  Raxis;       // R coordinate of magnetic axis
   double  Zaxis;       // Z coordinate of magnetic axis
   double  Rbound;      // R coordinate of plasma boundary on inboard midplane
-  int     ia;          // R grid index of inboard plasma boundary at Z=Z_axis
+  double  Rbound1;     // R coordinate of plasma boundary on outboard midplane
+  int     ia;          // R grid index of inboard plasma boundary at Z = Z_axis
   int     ic;          // R grid index of magnetic axis
   int     jc;          // Z grid index of magnetic axis
   int     L;           // Number of points in Psi(R,Zaxis) array
   double* s;           // Array of s = sqrt[1 - Psi(R,Zaxis)] values
-  double* Rs;          // Array of R(s) values
+  double* Rs;          // Array of R(s) values, where R is major radius on inboard midplane
   double  q95;         // Safety-factor on 95% flux surface
   double  r95;         // Radial coordinate of 95% flux surface
   double  qlim;        // Safety-factor at PsiN = PSILIM flux surface
@@ -158,8 +160,14 @@ class Flux
   double  qgp, qgp1;
 
   // Stage2 profile parameters
-  double* P ;          // Psi array
-  double* RP;          // R(Psi)
+  double* P;           // Psi array
+  double* RP;          // R(Psi) on inboard midplane
+  double* RP1;         // R(Psi) on outboard midplane 
+  double* Bt;          // B_toroidal(Psi) on inboard midplane
+  double* Bt1;         // B_toroidal(Psi) on outboard midplane
+  double* Bp;          // B_poloidal(Psi) on inboard midplane
+  double* Bp1;         // B_poloidal(Psi) on outboard midplane
+  double* B2v;         // <B^2>(Psi) (normalized) 
   double* rP;          // r(Psi)
   double* GP;          // g(Psi)
   double* QGP;         // q(Psi)/g(Psi) 

### 2020-11-14 Neoclassical/Source/Neoclassical.cpp

@@ -59,7 +59,7 @@ void Neoclassical::Solve (int _NEUTRAL, int _IMPURITY, int _FREQ, int _INTP, int
   // Read discharge parameters
   Read_Parameters (_NEUTRAL, _IMPURITY, _FREQ, _INTP, _INTF, _INTC, _NTYPE, _NN, _LN, _YN, _TIME);
   
-  // Read equilibirum data
+  // Read equilibrium data
   Read_Equilibrium ();
 
   // Read profile data

### 2020-12-05 Neoclassical/Source/Neoclassical.cpp
Fixed error in Neoclassical

@@ -161,6 +161,11 @@ void Neoclassical::Read_Parameters (int _NEUTRAL, int _IMPURITY, int _FREQ, int 
        printf ("NEOCLASSICAL::Read_Parameters: Error invalid NTYPE value\n");
        exit (1);
      }
+  if (abs (FREQ) > 3 || FREQ == 0)
+    {
+      printf ("NEOCLASSICAL::Read_Parameters: Error invalid FREQ value\n");
+      exit (1);
+    }
 
   // Output input parameters
   printf ("Git Hash     = "); printf (GIT_HASH);     printf ("\n");
@@ -620,6 +625,7 @@ void Neoclassical::Get_Derived ()
       chiek  (j) = Interpolate (NPSI, rr, chie,   rk (j), 0);
       chink  (j) = Interpolate (NPSI, rr, chin,   rk (j), 0);
       rhok   (j) = (AI * (nik (j) + nbk (j)) + AII * nIk (j)) * m_p /rho0;
+
       if (NTYPE == 0)
 	NNk (j) = NN * exp ((rk(j) - 1.) /(LN /a));
       else if (NTYPE == 1)
@@ -849,6 +855,7 @@ void Neoclassical::Get_Parameters ()
   L_Ii_01.resize (nres);
   L_II_00.resize (nres);
   L_II_01.resize (nres);
+  G_ii_00.resize (nres);
   Q_00.resize    (nres); 
  
   // ........................
@@ -958,6 +965,7 @@ void Neoclassical::Get_Parameters ()
       L_Ii_01 (j) = gsl_matrix_get (L, 2, 1);
       L_II_00 (j) = gsl_matrix_get (L, 2, 2);
       L_II_01 (j) = gsl_matrix_get (L, 2, 3);
+      G_ii_00 (j) = gsl_matrix_get (invH, 0, 0) * SVN * NNk (j) /nu_iik (j);
             
       gsl_matrix_free      (H);
       gsl_matrix_free      (G);
@@ -988,16 +996,16 @@ void Neoclassical::Get_Parameters ()
       gsl_matrix_free (Q);
       gsl_permutation_free (pp);
       
[…]

### 2020-12-08 Flux/Source/Flux.h
Updating README.md file

@@ -19,10 +19,10 @@
 // theta > 0 above midplane.
 
 // Command line options:
-// -g INTG   - override INTG value from namelist
-// -n NTOR   - override NTOR value from namelist
-// -m MMIN   - override MMIN value from namelist
-// -M MMAX   - override MMAX value from namelist
+// -g INTG   - override INTG   value from namelist
+// -n NTOR   - override NTOR   value from namelist
+// -m MMIN   - override MMIN   value from namelist
+// -M MMAX   - override MMAX   value from namelist
 // -p PSILIM - override PSILIM value from namelist
 // -t TIME   - sets experimental time
 
@@ -80,10 +80,10 @@ extern "C" void NameListRead (int* INTG, int* NPSI, int* NTHETA, int* NNC, int* 
 extern "C" void gFileRead ();
 
 // gFile interpolation functions
-extern "C" void gFileInterpolateLinear ();
+extern "C" void gFileInterpolateLinear    ();
 extern "C" void gFileInterpolateQuadratic ();
-extern "C" void gFileInterpolateCubic ();
-extern "C" void gFileInterpolateQuartic ();
+extern "C" void gFileInterpolateCubic     ();
+extern "C" void gFileInterpolateQuartic   ();
 
 // ############
 // Class header
@@ -93,26 +93,26 @@ class Flux
  private:
   
   // Control parameters read from Inputs/Flux.in
-  int    NPSI;         // Number of points in PsiN grid
-  int    NTHETA;       // Number of points in theta grid
-  int    NNC;          // Number of neoclassical harmonics
-  int    QFLG;         // QFLG = 0 - use q95 from gFile
-                       // QFLG = 1 - rescale q95 to Q95 by adding constant to gg'
-  double Q95;          // Target Q95 (QFLG = 1)
-  int    NTOR;         // Toroidal mode number
-  int    MMIN;         // Minimum poloidal mode number
-  int    MMAX;         // Maximum poloidal mode number
-  double PSILIM;       // Maximum PsiN for rational surface
-  double H0;           // Initial integration step-length for equilibirum flux surface integrals 
-  double ACC;          // Integration accuracy for equilibrium flux surface integrals
-  double ETA;          // Regularization factor for Green's function
-  double DR;           // Discritization parameter for simulated Mirnov data
-  double TIME;         // Experimental time
-  int    INTG;         // If != 0 then use interpolated gFile
[…]

### 2020-12-10 Flux/Source/Stage2.cpp
Improved FLUX rational surface search

@@ -697,14 +697,24 @@ void Flux::Stage2FindRational ()
 	}
 
       // Correct rres values
+      /*
       for (int ii = 0; ii < 4; ii++)
 	{
 	  double qqq = Interpolate (NPSI, rP, QP, rres[i], 0);
-	  rres[i]   += (double (mres[i]) /double (NTOR) /qqq - 1.) * rres[i] /sres[i];
+	  rres[i]   += (qres[i]/qqq - 1.) * rres[i] /sres[i];
 	  sres[i]    = rres[i] /Interpolate (NPSI, QP, rP, qres[i], 1) /qres[i];
 	}
+      */
+      for (int ii = 0; ii < 4; ii++)
+	{
+	  double qqq = Interpolate (NPSI, rP, QP, rres[i], 0);
+	  double qqp = Interpolate (NPSI, rP, QP, rres[i], 1);
+	  double qpp = Interpolate (NPSI, rP, QP, rres[i], 2);
+	  rres[i] += (- qqp + sqrt (qqp*qqp - 2.*qpp * (qqq - qres[i]))) /qpp;
+	}
+      
       gmres[i] = Interpolate (NPSI, rP, QP, rres[i], 0) - qres[i];
-
+      sres[i]    = rres[i] /Interpolate (NPSI, QP, rP, qres[i], 1) /qres[i];
       gres[i]    = Interpolate (NPSI, rP, GP,  rres[i], 0);
       Rres[i]    = Interpolate (NPSI, rP, RP,  rres[i], 0);
       Rres1[i]   = Interpolate (NPSI, rP, RP1, rres[i], 0);

### 2020-12-10 Flux/Source/gFileRead.f90

@@ -128,6 +128,7 @@ subroutine gFileRead () bind (c, name = 'gFileRead')
 
   read (100, '(5e16.9)') (RBOUND (i), ZBOUND (i), i = 1, NBOUND)
   read (100, '(5e16.9)') (RLIM   (i), ZLIM   (i), i = 1, NLIM)
+  close (unit = 100)
 
   open  (unit = 101, file = 'Outputs/Stage1/Boundary.txt')
   write (101, '(2e17.9)') (RBOUND (i)/R0, ZBOUND (i)/R0, i = 1, NBOUND)
@@ -147,7 +148,5 @@ subroutine gFileRead () bind (c, name = 'gFileRead')
   deallocate (ZBOUND)
   deallocate (RLIM)
   deallocate (ZLIM)
-  
-  close (unit = 100)
 
 endsubroutine gFileRead

### 2020-12-19 Neoclassical/Source/Neoclassical.cpp
Corrected nFile interpolation. Corrected Phase6 plots

@@ -996,7 +996,7 @@ void Neoclassical::Get_Parameters ()
       gsl_matrix_free (Q);
       gsl_permutation_free (pp);
       
-     printf ("m = %3d  L_ii = (%10.3e, %10.3e)  L_iI = (%10.3e, %10.3e)  L_Ii = (%10.3e, %10.3e)  L_II = (%10.3e, %10.3e)  G_ii = %10.3e  zasQ_00 = %10.3e\n",
+     printf ("m = %3d  L_ii = (%10.3e, %10.3e)  L_iI = (%10.3e, %10.3e)  L_Ii = (%10.3e, %10.3e)  L_II = (%10.3e, %10.3e)  G_ii = %10.3e  Q_00 = %10.3e\n",
 	     mk (j), L_ii_00 (j),  L_ii_01 (j),  L_iI_00 (j),  L_iI_01 (j),  L_Ii_00 (j),  L_Ii_01 (j),  L_II_00 (j), L_II_01 (j), G_ii_00 (j), Q_00 (j));
     }
 

### 2020-12-19 Phase-2.x/Source/Phase.cpp

@@ -1264,7 +1264,7 @@ void Phase::IslandDynamics ()
 	  fprintf (file13, "\n"); fprintf (file14, "\n"); fprintf (file15, "\n"); fprintf (file16, "\n");
 	  fprintf (file17, "\n"); fprintf (file18, "\n");
 
-	  if (cnt%100 == 0)
+	  if (cnt%10 == 0)
 	    printf ("t = %11.4e  irmp = %11.4e  prmp/pi = %11.4e\n", t*tau_A, irmp, prmp /M_PI);
 	  cnt++;
 	  
@@ -1291,23 +1291,59 @@ void Phase::IslandDynamics ()
 
   FILE* filex = OpenFilea ((char*) "../IslandDynamics/Outputs/Stage6/omega0.txt");
   for (int j = 0; j < nres; j++)
-    fprintf (filex, "%3d %16.9e %16.9e %16.9e %16.9e %16.9e\n",
+    fprintf (filex, "%3d %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e\n",
 	     mk (j), rk (j), wkl (j) /tau_A/1.e3, wke (j) /tau_A/1.e3, wkn (j) /tau_A/1.e3, GetNaturalFrequency (j) /tau_A/1.e3, TIME);
   fclose (filex);
 
   FILE* filew = OpenFilea ((char*) "../IslandDynamics/Outputs/Stage6/omega.txt");
   for (int j = 0; j < nres; j++)
     {
-      double Wk = 4. * R_0 * fack (j) * sqrt (fabs (Psik (j)));
+      double Wk = 4. * fack (j) * sqrt (fabs (Psik (j))) * dPsiNdr (j);
 
-      if (j == 0 && Wk/2. > rk (j))
-	Wk = 2. * rk (j);
-      if (j > 0 && Wk/2. > rk (j) - rk (j-1))
-	Wk = 2. * (rk (j) - rk (j-1));
-      if (j < nres-1 && Wk/2. > rk (j+1) - rk (j))
-	Wk = 2. * (rk (j+1) - rk (j));
-      if (j == nres-1 && Wk/2. > 1. - rk (j))
-	Wk = 2. * (1. - rk (j));
+      if (j == 0)
+	{
+	  double Pminus = PsiN (j);
+	  double Pplus  = PsiN (j+1) - PsiN (j);
+	  double dP;
+
[…]

### 2020-12-23 Flux/Source/Flux.cpp
Improved calculation of island widths

@@ -44,10 +44,9 @@ void Flux::SetParameters (int _INTG, int _NTOR, int _MMIN, int _MMAX, double _TI
   // Set default values of input parameters
   INTG   = 0;
   NPSI   = 256;
+  PACK   = 1.;
   NTHETA = 512;
   NNC    = 10;
-  QFLG   = 0;
-  Q95    = 2.5;
   NTOR   = 2;
   MMIN   = 2;
   MMAX   = 20;
@@ -60,7 +59,7 @@ void Flux::SetParameters (int _INTG, int _NTOR, int _MMIN, int _MMAX, double _TI
   DR     = 1.e-2;
  
   // Read namelist file Inputs/Flux.in
-  NameListRead (&INTG, &NPSI, &NTHETA, &NNC, &NTOR, &QFLG, &Q95, &H0, &ACC, &ETA, &DR, &MMIN, &MMAX, &PSILIM, &TIME);
+  NameListRead (&INTG, &NPSI, &PACK, &NTHETA, &NNC, &NTOR, &H0, &ACC, &ETA, &DR, &MMIN, &MMAX, &PSILIM, &TIME);
 
   // Override namelist values with command line options
   if (_NTOR > 0)
@@ -122,21 +121,14 @@ void Flux::SetParameters (int _INTG, int _NTOR, int _MMIN, int _MMAX, double _TI
       printf ("FLUX::SetParameters: Error - PSILIM must lie between 0 and 1\n");
       exit (1);
     }
-  if (QFLG && Q95 <= 0.)
-    {
-      printf ("FLUX::SetParameters: Error - Q95 must be positive\n");
-      exit (1);
-    }
-  
+ 
   // Output calculation parameters
   printf ("Git Hash     = "); printf (GIT_HASH);     printf ("\n");
   printf ("Compile time = "); printf (COMPILE_TIME); printf ("\n");
   printf ("Git Branch   = "); printf (GIT_BRANCH);   printf ("\n\n");
   printf ("Input Parameters (from Inputs/Flux.in and command line options):\n");
-  printf ("NPSI = %4d         NTHETA = %4d         NNC  = %3d\n",
-	  NPSI, NTHETA, NNC);
-  printf ("Q95  = %11.4e  QFLG   = %2d\n",
-	  Q95, QFLG, NTOR);
[…]

### 2020-12-23 Neoclassical/Source/Neoclassical.cpp

@@ -302,8 +302,8 @@ void Neoclassical::Read_Equilibrium ()
 
   for (int j = 0; j < nres; j++)
     {
-      if (fscanf (file, "%d %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf",
-		  &mk (j), &rk (j), &sk (j), &gk (j), &gmk (j), &Ktk (j), &Kastk (j), &fck (j), &akk (j), &PsiNk (j), &dPsidr (j), &Kthek (j)) != 12)
+      if (fscanf (file, "%d %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf",
+		  &mk (j), &rk (j), &sk (j), &gk (j), &gmk (j), &Ktk (j), &Kastk (j), &fck (j), &akk (j), &PsiNk (j), &dPsidr (j), &Kthek (j), &in, &in, &in) != 15)
 	{
 	  printf ("NEOCLASSICAL:Read_Equilibrium: Error reading fFile (3)\n");
 	  exit (1);

### 2020-12-23 Neoclassical/Source/Neoclassical.h

@@ -34,6 +34,7 @@
 // 1.9  - Minor changes for KSTAR data
 // 1.10 - Changed operation of FREQ switch
 // 1.11 - Added missing extra term associated with chanrge exchange
+// 1.12 - Updated fFile input for additonal terms
 
 // ################################################################
 
@@ -41,7 +42,7 @@
 #define NEOCLASSICAL
 
 #define VERSION_MAJOR 1
-#define VERSION_MINOR 11
+#define VERSION_MINOR 12
 
 #include <stdio.h>
 #include <math.h>

### 2020-12-23 Phase-2.x/Source/IslandRoot.cpp

@@ -1,0 +1,131 @@
+// IslandRoot.cpp
+
+#include "Phase.h"
+
+// ############################################################
+// Function to find full width in PsiN of magnetic island chain
+// ############################################################
+double Phase::GetIslandWidth (double A1, double A2, double A3, double Psi)
+{
+  double Xminus, Xplus;
+
+  GetIslandLimits (A1, A2, A3, Psi, Xminus, Xplus);
+
+  return Xplus - Xminus;
+}
+
+// ########################################################################################
+// Function to find offset from rational surface in PsiN of center of magnetic island chain
+// ########################################################################################
+double Phase::GetIslandOffset (double A1, double A2, double A3, double Psi)
+{
+  double Xminus, Xplus;
+
+  GetIslandLimits (A1, A2, A3, Psi, Xminus, Xplus);
+
+  return (Xplus + Xminus) /2.;
+}
+
+// ########################################################
+// Function to find limits in PsiN of magnetic island chain 
+// ########################################################
+void Phase::GetIslandLimits (double A1, double A2, double A3, double Psi, double& Xminus, double& Xplus)
+{
+  if (fabs (Psi) < 1.e-15)
+    {
+      Xminus = 0.;
+      Xplus  = 0.;
+
+      return;
+    }
+  
+  double LARGE = 1.e6;
+
+  // Calculate basis island width
+  double W0 = 4. * sqrt (A1 * fabs (Psi));
+  double c = W0*W0/4.;
+  
+  // Find maximum allowed value of c
+  double CMAX = LARGE;
+  double cmax = CMAX; 
+  if (9.*A2*A2 - 32.*A3 > 0.)
+    {
+      double xp = (- 3.*A2 + sqrt (9.*A2*A2 - 32.*A3)) /8./A3;
+      double xm = (- 3.*A2 - sqrt (9.*A2*A2 - 32.*A3)) /8./A3;
+
+      double fxxp = 2. + 6.*A2*xp + 12.*A3*xp*xp;
+      double fxxm = 2. + 6.*A2*xm + 12.*A3*xm*xm;
+
+      double fp, fm;
+      if (fxxp < 0.)
[…]

### 2020-12-28 Flux/Source/Integrate.cpp
Bug fixes

@@ -323,7 +323,7 @@ int Flux::Rhs2 (double r, const double y[], double dydr[], void*)
 {
   // y[0] - (rP)^2    
 
-  double qg = Interpolate (NPSI, S, QGP, 1.-r*r, 0);
+  double qg = Interpolate (NPSI, PsiN, QGP, 1.-r, 0);
 
   dydr[0] = 2.*fabs(Psic) * qg;
 

### 2020-12-28 IslandDynamics/Source/IslandDynamics.cpp

@@ -29,8 +29,8 @@
 #define MAXCOMMANDLINELENGTH 500
 
 extern "C" void NameListRead (int* FLUX_NTOR, int* FLUX_MMIN, int* FLUX_MMAX,
-			      int* NEO_INTF, int* NEO_IMPURITY, int* NEO_NEUTRAL, int* NEO_FREQ, int* NEO_NTYPE, double* NEO_NN, double* NEO_LN, double* NEO_YN,
-			      int* PHASE, int* PHASE_MID, int* PHASE_INTN, int* PHASE_STAGE2, int* PHASE_OLD, int* PHASE_VER2, int* PHASE_FREQ, int* PHASE_LIN, double* PHASE_SCALE, 
+			      int* NEO_INTP, int* NEO_INTF, int* NEO_IMPURITY, int* NEO_NEUTRAL, int* NEO_FREQ, int* NEO_NTYPE, double* NEO_NN, double* NEO_LN, double* NEO_YN,
+			      int* PHASE, int* PHASE_MID, int* PHASE_INTN, int* PHASE_INTU, int* PHASE_STAGE2, int* PHASE_OLD, int* PHASE_VER2, int* PHASE_FREQ, int* PHASE_LIN, double* PHASE_SCALE, 
 			      int* RESTART, double* TSTART, double* TEND, double* DT); 
 
 void IslandDynamics ();
@@ -66,7 +66,7 @@ void IslandDynamics ()
   int    FLUX_NTOR;      // Set toroidal mode number in FLUX
   int    FLUX_MMIN;      // Set minimum poloidal mode number in FLUX
   int	 FLUX_MMAX;      // Set maximum poloidal mode number in FLUX
-  int    NEO_INTP = 1;   // If != 0 then interpolate pFiles in NEOCLASSICAL
+  int    NEO_INTP;       // If != 0 then interpolate pFiles in NEOCLASSICAL
   int	 NEO_INTF;       // If != 0 then interpolate fFiles in NEOCLASSICAL
[…]

### 2020-12-28 Neoclassical/Source/Neoclassical.cpp

@@ -77,7 +77,7 @@ void Neoclassical::Solve (int _NEUTRAL, int _IMPURITY, int _FREQ, int _INTP, int
   // Calculcate neoclassical frequencies at rational surfaces
   Get_Frequencies ();
 
-  // Calculate normalized quantites at rational surface
+  // Calculate normalized quantites at rational surface and output nFile
   Get_Normalized ();
 }
 
@@ -130,6 +130,14 @@ void Neoclassical::Read_Parameters (int _NEUTRAL, int _IMPURITY, int _FREQ, int 
   if (_INTC > -1)
     INTC = _INTC;
 
+  // Output input parameters
+  printf ("Git Hash     = "); printf (GIT_HASH);     printf ("\n");
+  printf ("Compile time = "); printf (COMPILE_TIME); printf ("\n");
+  printf ("Git Branch   = "); printf (GIT_BRANCH);   printf ("\n\n");
+  printf ("Input parameters (from Inputs/Neoclassical.in and command line options):\n");
+  printf ("IMPURITY = %2d NEUTRAL = %2d FREQ = %2d INTP = %2d INTF = %2d INTC = %2d NTYPE = %2d NN = %11.4e LN = %11.4e SVN = %11.4e YN = %11.4e EN = %11.4e TIME = %11.4e\n",
+	  IMPURITY, NEUTRAL, FREQ, INTP, INTF, INTC, NTYPE, NN, LN, SVN, YN, EN, TIME);
+
   // Sanity check
   if (YN < 0.)
     {
@@ -166,14 +174,6 @@ void Neoclassical::Read_Parameters (int _NEUTRAL, int _IMPURITY, int _FREQ, int 
       printf ("NEOCLASSICAL::Read_Parameters: Error invalid FREQ value\n");
       exit (1);
     }
-
-  // Output input parameters
-  printf ("Git Hash     = "); printf (GIT_HASH);     printf ("\n");
-  printf ("Compile time = "); printf (COMPILE_TIME); printf ("\n");
-  printf ("Git Branch   = "); printf (GIT_BRANCH);   printf ("\n\n");
-  printf ("Input parameters (from Inputs/Neoclassical.in and command line options):\n");
[…]

### 2020-12-28 Neoclassical/Source/Neoclassical.h

@@ -16,7 +16,7 @@
 // -y YN       - override YN value from namelist file
 // -N NN       - override NN value from namelist file
 // -l LN       - override LN value from namelist file
-// -t TIME     - sets experimental time
+// -t TIME     - sets experimental time (ms)
 
 // Intermediate data in folder Outputs/Stage3
 // Final data passed to program PHASE in file Outputs/nFile
@@ -35,6 +35,7 @@
 // 1.10 - Changed operation of FREQ switch
 // 1.11 - Added missing extra term associated with chanrge exchange
 // 1.12 - Updated fFile input for additonal terms
+// 1.13 - Corrected error in fFile interpolation. Improved system calls.
 
 // ################################################################
 
@@ -42,7 +43,7 @@
 #define NEOCLASSICAL
 
 #define VERSION_MAJOR 1
-#define VERSION_MINOR 12
+#define VERSION_MINOR 13
 
 #include <stdio.h>
 #include <math.h>
@@ -100,7 +101,7 @@ class Neoclassical
   double SVN;      // Majority ion/neutral charge exchange rate constant (m^3 /s)
   double YN;       // Majority neutral peaking factor on flux-surfaces
   double EN;       // Ratio of majority neutral to ion temperatures
-  double TIME;     // Experimental time
+  double TIME;     // Experimental time (ms)
  
   // ------------------
   // Physical constants
@@ -420,6 +421,8 @@ class Neoclassical
   FILE* OpenFilew (char* filename);
   // Open file for appending
   FILE* OpenFilea (char* filename);
+  // Call operating system 
+  void CallSystem (char* command);
 };
 
 #endif //NEOCLASSICAL

### 2020-12-28 Phase-2.x/Source/IslandRoot.cpp

@@ -31,18 +31,18 @@ double Phase::GetIslandOffset (double A1, double A2, double A3, double Psi)
 // ########################################################
 void Phase::GetIslandLimits (double A1, double A2, double A3, double Psi, double& Xminus, double& Xplus)
 {
-  if (fabs (Psi) < 1.e-15)
-    {
-      Xminus = 0.;
-      Xplus  = 0.;
-
-      return;
-    }
-  
   double LARGE = 1.e6;
+  double SMALL = 1.e-15;
 
   // Calculate basis island width
   double W0 = 4. * sqrt (A1 * fabs (Psi));
+  if (W0 < 1.e-4)
+    {
+      Xminus = - sqrt (W0) /2.;
+      Xplus  = + sqrt (W0) /2.;
+
+      return;
+    }
   double c = W0*W0/4.;
   
   // Find maximum allowed value of c
@@ -78,12 +78,20 @@ void Phase::GetIslandLimits (double A1, double A2, double A3, double Psi, double
     c = 0.99*cmax;
 
   // Solve polynomial equation
+  int    status;
   double a[5] = {-c, 0., 1., A2, A3};
   double z[8];
 
   gsl_poly_complex_workspace* w = gsl_poly_complex_workspace_alloc (5);
 
-  gsl_poly_complex_solve (a, 5, w, z);
+  gsl_set_error_handler_off ();
+ 
+  status = gsl_poly_complex_solve (a, 5, w, z);
+  if (status != 0)
+    {
+      printf ("FLUX::IslandRoot: Warning: gsl_poly_complex_solve lack of convergence - Psi = %10.3e A1 = %10.3e A2 = %10.3e A3 = %10.3e W0 = %10.3e c = %10.3e cmax = %10.3e status = %2d\n",
+	      Psi, A1, A2, A3, W0, c, cmax, status);
+    }
 
   gsl_poly_complex_workspace_free (w);
 
@@ -92,18 +100,23 @@ void Phase::GetIslandLimits (double A1, double A2, double A3, double Psi, double
   double x[4];
 
   for (int i = 0; i < 4; i++)
-    if (fabs (z[2*i+1]) < 1.e-15)
+    if (fabs (z[2*i+1]) < SMALL)
       {
-	x[i] = z[2*i];
+	x[nroot] = z[2*i];
 	nroot++;
[…]

### 2020-12-28 Phase-2.x/Source/NamelistRead.f90

@@ -1,6 +1,6 @@
 ! Function to read PHASE namelist
 
-subroutine NameListRead (NFLOW, STAGE5, INTF, INTN, INTU, OLD, FREQ, LIN, MID, DT, TIME, SCALE, PMAX,&
+subroutine NameListRead (NFLOW, STAGE5, INTF, INTN, INTU, OLD, FREQ, LIN, MID, DT, TSTART, TEND, SCALE, PMAX,&
      NCTRL, xTCTRL, xICTRL, xPCTRL) bind (c, name = 'NameListRead')
 
   use, intrinsic :: iso_c_binding, only: c_int, c_double
@@ -16,7 +16,8 @@ subroutine NameListRead (NFLOW, STAGE5, INTF, INTN, INTU, OLD, FREQ, LIN, MID, D
   integer (kind = c_int),    intent (inout) :: LIN
   integer (kind = c_int),    intent (inout) :: MID
   real    (kind = c_double), intent (inout) :: DT
-  real    (kind = c_double), intent (inout) :: TIME
+  real    (kind = c_double), intent (inout) :: TSTART
+  real    (kind = c_double), intent (inout) :: TEND
   real    (kind = c_double), intent (inout) :: SCALE
   real    (kind = c_double), intent (inout) :: PMAX
   integer (kind = c_int),    intent (inout) :: NCTRL
@@ -32,7 +33,7 @@ subroutine NameListRead (NFLOW, STAGE5, INTF, INTN, INTU, OLD, FREQ, LIN, MID, D
   integer          :: i
   double precision :: pi
  
-  namelist /PHASE_CONTROL/   STAGE5, NFLOW, INTF, INTN, INTU, OLD, FREQ, LIN, MID, DT, TIME, SCALE, PMAX
+  namelist /PHASE_CONTROL/   STAGE5, NFLOW, INTF, INTN, INTU, OLD, FREQ, LIN, MID, DT, TSTART, TEND, SCALE, PMAX
   namelist /PHASE_WAVEFORM/  NCTRL
   namelist /PHASE_WAVEFORM1/ TCTRL, ICTRL, PCTRL
   

### 2020-12-28 Phase-2.x/Source/Phase.h

@@ -5,6 +5,9 @@
 // with resonant magnetic perturbation in toroidal tokamak plasma.
 // Reads data from programs FLUX, NEOCLASSICAL, and GPEC.
 
+// Simulation start time is lesser of 0, TSTART, and TCTRL (0)
+// Simulation end time is lesser of TEND and TCTRL (NCTRL-1)
+
 // Command line options:
 // -f INTF   - overrides INTF value from namelist file
 // -n INTN   - overrides INTN value from namelist file
@@ -14,7 +17,8 @@
 // -s STAGE5 - overrides STAGE5 value from namelist file
 // -S SCALE  - overrides SCALE value from namelist file
 // -m MID    - overrides MID value from namelist file
-// -t TIME   - sets experimental time
+// -t TSTART - sets simulation start time (s)
+// -T TEND   - sets simulation end time (s)
 
 // Stage 4 - Class reads FLUX/NEOCLASSICAL/GPEC data and plots error-field
 //           drive versus relative phases of RMP coil currents for 1kA currents
@@ -41,6 +45,7 @@
 // 2.5 - Added middle coil set
 // 2.6 - Limited island width to stop them extending beyond neighbouring rational surfaces
 // 2.7 - Improved calculation of island widths
+// 2.8 - Replaced TIME by TSTART and TEND
 
 // #######################################################################
 
@@ -48,7 +53,7 @@
 #define PHASE
 
 #define VERSION_MAJOR 2
-#define VERSION_MINOR 7
+#define VERSION_MINOR 8
 
 #include <stdio.h>
 #include <math.h>
@@ -64,6 +69,7 @@
 #include <gsl/gsl_sf_bessel.h>
 #include <gsl/gsl_const_mksa.h>
 #include <gsl/gsl_poly.h>
+#include <gsl/gsl_errno.h>
 
 #define MAXFILENAMELENGTH 500
 #define MAXCONTROLPOINTNUMBER 500
@@ -72,8 +78,8 @@
 using namespace blitz;
 
 // Namelist funtion
-extern "C" void NameListRead (int* NFLOW, int* STAGE2, int* INTF, int* INTN, int* INTU, int* OLD, int* FREQ, int* LIN, int* MID, double* DT, double* TIME, double* SCALE, 
-			      double* PMAX, int* NCTRL, double* TCTRL, double* ICTRL, double* PCTRL);
[…]

### 2020-12-28 Phase-2.x/Source/lFileInterpolate.cpp

@@ -225,6 +225,11 @@ void Phase::lFileInterpolateLinear (char* lFile1, double time1, char* lFile, dou
 
   printf ("lFile Interpolation:\n");
   printf ("%s %11.4e\n", lFile1, weight1);
+
+  FILE* monitor = OpenFilea ((char*) "../IslandDynamics/Outputs/monitor.txt");
+  fprintf (monitor, "lFile Interpolation:\n");
+  fprintf (monitor, "%s %11.4e\n", lFile1, weight1);
+  fclose (monitor);
  
   // ........
   // Clean up
@@ -397,6 +402,12 @@ void Phase::lFileInterpolateQuadratic (char* lFile1, double time1, char* lFile2,
   printf ("lFile Interpolation:\n");
   printf ("%s %11.4e\n", lFile1, weight1);
   printf ("%s %11.4e\n", lFile2, weight2);
+
+  FILE* monitor = OpenFilea ((char*) "../IslandDynamics/Outputs/monitor.txt");
+  fprintf (monitor, "lFile Interpolation:\n");
+  fprintf (monitor, "%s %11.4e\n", lFile1, weight1);
+  fprintf (monitor, "%s %11.4e\n", lFile2, weight2);
+  fclose (monitor);
  
   // ........
   // Clean up
@@ -632,6 +643,13 @@ void Phase::lFileInterpolateCubic (char* lFile1, double time1, char* lFile2, dou
   printf ("%s %11.4e\n", lFile1, weight1);
   printf ("%s %11.4e\n", lFile2, weight2);
   printf ("%s %11.4e\n", lFile3, weight3);
+
+  FILE* monitor = OpenFilea ((char*) "../IslandDynamics/Outputs/monitor.txt");
+  fprintf (monitor, "lFile Interpolation:\n");
+  fprintf (monitor, "%s %11.4e\n", lFile1, weight1);
+  fprintf (monitor, "%s %11.4e\n", lFile2, weight2);
+  fprintf (monitor, "%s %11.4e\n", lFile3, weight3);
+  fclose (monitor);
   
   // ........
   // Clean up
@@ -925,6 +943,14 @@ void Phase::lFileInterpolateQuartic (char* lFile1, double time1, char* lFile2, d
   printf ("%s %11.4e\n", lFile2, weight2);
   printf ("%s %11.4e\n", lFile3, weight3);
   printf ("%s %11.4e\n", lFile4, weight4);
+
[…]

### 2020-12-31 Flux/Source/Stage2.cpp
Major reorganization. New island width calculation

@@ -69,8 +69,8 @@ void Flux::Stage2 ()
     fprintf (file, "%16.9e %16.9e %16.9e\n",
 	     1. - P[j], rP[j] /ra, - ra * Interpolate (NPSI, rP, P, rP[j], 1));
   for (int i = 0; i < nres; i++)
-    fprintf (file, "%d %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e\n",
-	     mres[i], rres[i]/ra, sres[i], gres[i], gmres[i], Ktres[i], Kares[i], fcres[i], ajj[i], PsiNres[i], dPsidr[i], Khres[i], A1res[i], A2res[i], A3res[i]);
+    fprintf (file, "%d %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e\n",
+	     mres[i], rres[i]/ra, sres[i], gres[i], gmres[i], Ktres[i], Kares[i], fcres[i], ajj[i], PsiNres[i], dPsidr[i], Khres[i], A1res[i]);
   for (int i = 0; i < nres; i++)
     for (int j = 0; j < nres; j++)
       fprintf (file, "%d %d %16.9e %16.9e\n", mres[i], mres[j],
@@ -96,8 +96,8 @@ void Flux::Stage2 ()
 	fprintf (file, "%16.9e %16.9e %16.9e\n",
 		 1. - P[j], rP[j] /ra, - ra * Interpolate (NPSI, rP, P, rP[j], 1));
       for (int i = 0; i < nres; i++)
-	fprintf (file, "%d %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e\n",
-		 mres[i], rres[i]/ra, sres[i], gres[i], gmres[i], Ktres[i], Kares[i], fcres[i], ajj[i], PsiNres[i], dPsidr[i], Khres[i], A1res[i], A2res[i], A3res[i]);
+	fprintf (file, "%d %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e\n",
[…]

### 2020-12-31 Flux/Source/gFileInterpolate.f90

@@ -2,6 +2,7 @@
 
 ! PROGRAM ORGANIZATION:
 
+! subroutine gFileWrite
 ! subroutine gFileInterpolateLinear
 ! subroutine gFileInterpolateQuadratic
 ! subroutine gFileInterpolateCubic

### 2020-12-31 IslandDynamics/Source/IslandDynamics.cpp

@@ -30,7 +30,7 @@
 
 extern "C" void NameListRead (int* FLUX_NTOR, int* FLUX_MMIN, int* FLUX_MMAX,
 			      int* NEO_INTP, int* NEO_INTF, int* NEO_IMPURITY, int* NEO_NEUTRAL, int* NEO_FREQ, int* NEO_NTYPE, double* NEO_NN, double* NEO_LN, double* NEO_YN,
-			      int* PHASE, int* PHASE_MID, int* PHASE_INTN, int* PHASE_INTU, int* PHASE_STAGE2, int* PHASE_OLD, int* PHASE_VER2, int* PHASE_FREQ, int* PHASE_LIN, double* PHASE_SCALE, 
+			      int* PHASE, int* PHASE_MID, int* PHASE_INTN, int* PHASE_INTU, int* PHASE_STAGE5, int* PHASE_OLD, int* PHASE_FREQ, int* PHASE_LIN, double* PHASE_SCALE, 
 			      int* RESTART, double* TSTART, double* TEND, double* DT); 
 
 void IslandDynamics ();
@@ -82,7 +82,6 @@ void IslandDynamics ()
   int	 PHASE_INTU;     // If != 0 then interpolate uFiles/mFiles/lFiles in PHASE
   int	 PHASE_STAGE5;   // If != 0 then Stage5 PHASE calculation enabled
   int	 PHASE_OLD;      // If != 0 then restart PHASE calculations from previous run
-  int    PHASE_VER2;     // If != 0 then call Phase-2.x, else call Phase-1.x
   int    PHASE_FREQ;     // If != 0 then use island width dependent natural frequency (only applies to Phase-2.x, overrides NEO_FREQ)
   int    PHASE_LIN ;     // If != 0 then perform purely linear calculation (only applies to Phase-2.x)
   double PHASE_SCALE;    // GPEC scalefactor
@@ -93,18 +92,18 @@ void IslandDynamics ()
 
   NameListRead (&FLUX_NTOR, &FLUX_MMIN, &FLUX_MMAX,
[…]

### 2021-02-12 Flux/Source/Smoothing.cpp
Added improved transport model

@@ -8,11 +8,12 @@
 void Flux::Smoothing (int N, double *y)
 {
   double* w = new double[N];
+  double* weights = new double[5];
 
   for (int i = 0; i < N; i++)
     w[i] = y[i];
 
-  double* weights = new double[5];
+  /* 
   for (int i = 0; i < N; i++)
     {
       int j;
@@ -70,6 +71,19 @@ void Flux::Smoothing (int N, double *y)
 
       y[i] = (weights[0] * w[j-2] + weights[1] * w[j-1] + weights[2] * w[j] + weights[3] * w[j+1] + weights[4] * w[j+2]) /35.;
     }
+  */
+
+  for (int i = 2; i < N-2; i++)
+    {
+      weights[0] = -3.;
+      weights[1] = +12.;
+      weights[2] = +17.;
+      weights[3] = +12.;
+      weights[4] = -3.;
+
+      y[i] = (weights[0] * w[i-2] + weights[1] * w[i-1] + weights[2] * w[i] + weights[3] * w[i+1] + weights[4] * w[i+2]) /35.;
+    }
 
   delete[] w;
+  delete[] weights;
 }

### 2021-02-12 Flux/Source/gFileInterpolate.f90

@@ -233,7 +233,6 @@ subroutine gFileInterpolateQuadratic () bind (c, name = 'gFileInterpolateQuadrat
   double precision, dimension (:),    allocatable :: RBOUND,  ZBOUND,   RLIM,    ZLIM    
   double precision, dimension (:, :), allocatable :: PSI
 
-  
   ! -----------------------
   ! Read file and time data
   ! -----------------------

### 2021-02-12 Neoclassical/Source/NamelistRead.f90

@@ -4,7 +4,7 @@
 ! Function to read NEOCLASSICAL namelist
 ! ######################################
 
-subroutine NameListRead (IMPURITY, NEUTRAL, FREQ, INTP, INTF, INTC, NTYPE, NN, LN, SVN, YN, EN, TIME, COULOMB) &
+subroutine NameListRead (IMPURITY, NEUTRAL, FREQ, INTP, INTF, INTC, NTYPE, NN, LN, SVN, YN, EN, TIME, COULOMB, NSMOOTH) &
      bind (c, name = 'NameListRead')
   
   use, intrinsic :: iso_c_binding, only: c_int, c_double
@@ -17,6 +17,7 @@ subroutine NameListRead (IMPURITY, NEUTRAL, FREQ, INTP, INTF, INTC, NTYPE, NN, L
   integer (kind = c_int),    intent (inout) :: INTF
   integer (kind = c_int),    intent (inout) :: INTC
   integer (kind = c_int),    intent (inout) :: NTYPE
+  integer (kind = c_int),    intent (inout) :: NSMOOTH
   real    (kind = c_double), intent (inout) :: NN
   real    (kind = c_double), intent (inout) :: LN
   real    (kind = c_double), intent (inout) :: SVN
@@ -25,7 +26,7 @@ subroutine NameListRead (IMPURITY, NEUTRAL, FREQ, INTP, INTF, INTC, NTYPE, NN, L
   real    (kind = c_double), intent (inout) :: TIME
   real    (kind = c_double), intent (inout) :: COULOMB
   
-  namelist /NEOCLASSICAL_CONTROL/ IMPURITY, NEUTRAL, FREQ, INTP, INTF, INTC, NTYPE, NN, LN, SVN, YN, EN, TIME, COULOMB
+  namelist /NEOCLASSICAL_CONTROL/ IMPURITY, NEUTRAL, FREQ, INTP, INTF, INTC, NTYPE, NN, LN, SVN, YN, EN, TIME, COULOMB, NSMOOTH
   
   open  (unit = 100, file = 'Inputs/Neoclassical.nml', status = 'old')
   read  (unit = 100, nml = NEOCLASSICAL_CONTROL) 

### 2021-02-12 Phase/Source/IslandRoot.cpp

@@ -9,7 +9,7 @@ double Phase::GetIslandWidth (int j)
 {
   double Xminus, Xplus;
 
-  GetIslandLimits (j, Psik (j), 1., Xminus, Xplus);
+  GetIslandLimits (j, Psik (j), Xminus, Xplus);
 
   return Xplus - Xminus;
 }
@@ -21,7 +21,7 @@ double Phase::GetVacuumIslandWidth (int j)
 {
   double Xminus, Xplus;
 
-  GetIslandLimits (j, chi (j), CHIR, Xminus, Xplus);
+  GetIslandLimits (j, chi (j), Xminus, Xplus);
 
   return Xplus - Xminus;
 }
@@ -29,10 +29,10 @@ double Phase::GetVacuumIslandWidth (int j)
 // ########################################################
 // Function to find limits in PsiN of magnetic island chain 
 // ########################################################
-void Phase::GetIslandLimits (int j, double Psi, double chir, double& Xminus, double& Xplus)
+void Phase::GetIslandLimits (int j, double Psi, double& Xminus, double& Xplus)
 {
-  double cplus  = chir*chir * 2. * A1 (j) * fabs (Psi) /Deltakp (j)/Deltakp (j);
-  double cminus = chir*chir * 2. * A1 (j) * fabs (Psi) /Deltakm (j)/Deltakm (j);
+  double cplus  = 2. * A1 (j) * fabs (Psi) /Deltakp (j)/Deltakp (j);
+  double cminus = 2. * A1 (j) * fabs (Psi) /Deltakm (j)/Deltakm (j);
   
   Xplus  = + Deltakp (j) * GetIslandRoot (cplus);
   Xminus = - Deltakm (j) * GetIslandRoot (cminus);

### 2021-02-12 Phase/Source/NamelistRead.f90

@@ -1,7 +1,7 @@
 ! Function to read PHASE namelist
 
 subroutine NameListRead (NFLOW, STAGE5, INTF, INTN, INTU, OLD, FREQ, LIN, MID, DT, TSTART, TEND, SCALE, PMAX,&
-     CHIR, NCTRL, xTCTRL, xICTRL, xPCTRL) bind (c, name = 'NameListRead')
+     CHIR, HIGH, NCTRL, xTCTRL, xICTRL, xPCTRL) bind (c, name = 'NameListRead')
 
   use, intrinsic :: iso_c_binding, only: c_int, c_double
   implicit none
@@ -15,14 +15,15 @@ subroutine NameListRead (NFLOW, STAGE5, INTF, INTN, INTU, OLD, FREQ, LIN, MID, D
   integer (kind = c_int),    intent (inout) :: FREQ
   integer (kind = c_int),    intent (inout) :: LIN
   integer (kind = c_int),    intent (inout) :: MID
+  integer (kind = c_int),    intent (inout) :: NCTRL
+  integer (kind = c_int),    intent (inout) :: HIGH
   real    (kind = c_double), intent (inout) :: DT
   real    (kind = c_double), intent (inout) :: TSTART
   real    (kind = c_double), intent (inout) :: TEND
   real    (kind = c_double), intent (inout) :: SCALE
   real    (kind = c_double), intent (inout) :: PMAX
   real    (kind = c_double), intent (inout) :: CHIR
- integer (kind = c_int),    intent (inout) :: NCTRL
-  
+
   real (kind = c_double), dimension (*), intent (inout) :: xTCTRL 
   real (kind = c_double), dimension (*), intent (inout) :: xICTRL 
   real (kind = c_double), dimension (*), intent (inout) :: xPCTRL
@@ -34,7 +35,7 @@ subroutine NameListRead (NFLOW, STAGE5, INTF, INTN, INTU, OLD, FREQ, LIN, MID, D
   integer          :: i
   double precision :: pi
  
-  namelist /PHASE_CONTROL/   STAGE5, NFLOW, INTF, INTN, INTU, OLD, FREQ, LIN, MID, DT, TSTART, TEND, SCALE, PMAX, CHIR
[…]

### 2021-02-12 Phase/Source/Phase.cpp

@@ -114,6 +114,7 @@ void Phase::Read_Data (int _STAGE5, int _INTF, int _INTN, int _INTU, int _OLD, i
   SCALE  = 2.;
   PMAX   = 4.;
   CHIR   = 1.;
+  HIGH   = 1;
   IFLA   = 0;
   IRMP   = -1.e6;
 
@@ -126,7 +127,7 @@ void Phase::Read_Data (int _STAGE5, int _INTF, int _INTN, int _INTU, int _OLD, i
   ICTRL = new double[MAXCONTROLPOINTNUMBER];
   PCTRL = new double[MAXCONTROLPOINTNUMBER];
 
-  NameListRead (&NFLOW, &STAGE5, &INTF, &INTN, &INTU, &OLD, &FREQ, &LIN, &MID, &DT, &TSTART, &TEND, &SCALE, &PMAX, &CHIR, &NCTRL, TCTRL, ICTRL, PCTRL);
+  NameListRead (&NFLOW, &STAGE5, &INTF, &INTN, &INTU, &OLD, &FREQ, &LIN, &MID, &DT, &TSTART, &TEND, &SCALE, &PMAX, &CHIR, &HIGH, &NCTRL, TCTRL, ICTRL, PCTRL);
 
   TT.resize (NCTRL);
   
@@ -164,8 +165,8 @@ void Phase::Read_Data (int _STAGE5, int _INTF, int _INTN, int _INTU, int _OLD, i
   // .............................
   // Output calculation parameters
   // .............................
-  printf ("NFLOW = %4d STAGE5 = %2d INTF = %2d INTN = %2d INTU = %2d OLD = %2d FREQ = %2d LIN = %2d MID = %2d DT = %11.4e TSTART = %11.4e TEND = %11.4e SCALE = %11.4e PMAX = %11.4e CHIR = %11.4e NCTRL = %4d IRMP = %11.4e\n",
-	  NFLOW, STAGE5, INTF, INTN, INTU, OLD, FREQ, LIN, MID, DT, TSTART, TEND, SCALE, PMAX, CHIR, NCTRL, IRMP);
+  printf ("NFLOW = %4d STAGE5 = %2d INTF = %2d INTN = %2d INTU = %2d OLD = %2d FREQ = %2d LIN = %2d MID = %2d HIGH = %2d DT = %11.4e TSTART = %11.4e TEND = %11.4e SCALE = %11.4e PMAX = %11.4e CHIR = %11.4e NCTRL = %4d IRMP = %11.4e\n",
[…]

### 2021-02-26 IslandDynamics/Source/NamelistRead.f90
Added coil phase optimization

@@ -6,8 +6,8 @@
 
 subroutine NameListRead (FLUX_NTOR, FLUX_MMIN, FLUX_MMAX,&
      NEO_INTP, NEO_INTF, NEO_IMPURITY, NEO_NEUTRAL, NEO_FREQ, NEO_NTYPE, NEO_NN, NEO_LN, NEO_YN,&
-     PHASE, PHASE_MID, PHASE_INTN, PHASE_INTU, PHASE_STAGE5, PHASE_OLD, PHASE_FREQ, PHASE_LIN, PHASE_HIGH,& 
-     PHASE_RATS, PHASE_SCALE, PHASE_CHIR, RESTART, TSTART, TEND, DT)&
+     PHASE, PHASE_MID, PHASE_COPT, PHASE_INTN, PHASE_INTU, PHASE_STAGE5, PHASE_OLD, PHASE_FREQ, PHASE_LIN,&
+     PHASE_HIGH, PHASE_RATS, PHASE_SCALE, PHASE_CHIR, RESTART, TSTART, TEND, DT)&
      bind (c, name = 'NameListRead')
 
   use, intrinsic :: iso_c_binding, only: c_int, c_double
@@ -27,6 +27,7 @@ subroutine NameListRead (FLUX_NTOR, FLUX_MMIN, FLUX_MMAX,&
   real    (kind = c_double), intent (inout) :: NEO_YN
   integer (kind = c_int),    intent (inout) :: PHASE
   integer (kind = c_int),    intent (inout) :: PHASE_MID
+  integer (kind = c_int),    intent (inout) :: PHASE_COPT
   integer (kind = c_int),    intent (inout) :: PHASE_STAGE5
   integer (kind = c_int),    intent (inout) :: PHASE_INTN
   integer (kind = c_int),    intent (inout) :: PHASE_INTU
@@ -44,7 +45,7 @@ subroutine NameListRead (FLUX_NTOR, FLUX_MMIN, FLUX_MMAX,&
   
   namelist /ISLANDDYNAMICS_CONTROL/ FLUX_NTOR, FLUX_MMIN, FLUX_MMAX,&
        NEO_INTP, NEO_INTF, NEO_IMPURITY, NEO_NEUTRAL, NEO_FREQ, NEO_NTYPE, NEO_NN, NEO_LN, NEO_YN,&
[…]

### 2021-02-26 Phase/Source/main.cpp

@@ -32,9 +32,10 @@ int main (int argc, char** argv)
   char* Fvalue = NULL; char* Svalue = NULL; char* lvalue = NULL;
   char* mvalue = NULL; char* Tvalue = NULL; char* cvalue = NULL;
   char* ivalue = NULL; char* rvalue = NULL; char* Hvalue = NULL;
+  char* Cvalue = NULL;
   opterr = 0;
   
-  while ((c = getopt (argc, argv, "f:hn:o:s:t:u:F:S:l:m:T:c:i:r:H:")) != -1)
+  while ((c = getopt (argc, argv, "f:hn:o:s:t:u:F:S:l:m:T:c:i:r:H:C:")) != -1)
     switch (c)
       {
       case 'f':
@@ -54,6 +55,7 @@ int main (int argc, char** argv)
 	printf ("-s STAGE5 - set Stage5 caculation enabling flag STAGE5\n");
 	printf ("-t TSTART - set simulation start time (s) to TSTART\n");
 	printf ("-u INTU   - set uFile/mFile/lFile interpolation enabling flag INTU\n");
+	printf ("-C COPT   - set coil current optimization flag COPT\n");
 	printf ("-F FREQ   - set island frequency choice flag FREQ\n");
 	printf ("-H HIGH   - set higher orddr transport calculation enabling flag HIGH\n");
 	printf ("-S SCALE  - set GPEC scalefactor SCALE\n");	
@@ -101,10 +103,13 @@ int main (int argc, char** argv)
       case 'H':
 	Hvalue = optarg;
  	break;
+      case 'C':
+	Cvalue = optarg;
+ 	break;
       case '?':
 	if (optopt == 't' || optopt == 's' || optopt == 'f' || optopt == 'o'|| optopt == 'n' || optopt == 'u'
 	    || optopt == 'F' || optopt == 'S' || optopt == 'l' || optopt == 'm' || optopt == 'T' || optopt == 'c'
-	    || optopt == 'i' || optopt == 'r' || optopt == 'H')
+	    || optopt == 'i' || optopt == 'r' || optopt == 'H' || optopt == 'C')
 	  printf ("Option = %c requires an argument\n", optopt);
 	  else if (isprint (optopt))
 	    printf ("Unknown option '-%c'\n", optopt);
@@ -120,6 +125,7 @@ int main (int argc, char** argv)
[…]

### 2021-03-09 Phase/Source/main.cpp
Added more coil optimization

@@ -32,10 +32,10 @@ int main (int argc, char** argv)
   char* Fvalue = NULL; char* Svalue = NULL; char* lvalue = NULL;
   char* mvalue = NULL; char* Tvalue = NULL; char* cvalue = NULL;
   char* ivalue = NULL; char* rvalue = NULL; char* Hvalue = NULL;
-  char* Cvalue = NULL;
+  char* Cvalue = NULL; char* Dvalue = NULL;
   opterr = 0;
   
-  while ((c = getopt (argc, argv, "f:hn:o:s:t:u:F:S:l:m:T:c:i:r:H:C:")) != -1)
+  while ((c = getopt (argc, argv, "f:hn:o:s:t:u:F:S:l:m:T:c:i:r:H:C:D:")) != -1)
     switch (c)
       {
       case 'f':
@@ -56,6 +56,7 @@ int main (int argc, char** argv)
 	printf ("-t TSTART - set simulation start time (s) to TSTART\n");
 	printf ("-u INTU   - set uFile/mFile/lFile interpolation enabling flag INTU\n");
 	printf ("-C COPT   - set coil current optimization flag COPT\n");
+	printf ("-D CORE   - set core minimization factor CORE\n");
 	printf ("-F FREQ   - set island frequency choice flag FREQ\n");
 	printf ("-H HIGH   - set higher orddr transport calculation enabling flag HIGH\n");
 	printf ("-S SCALE  - set GPEC scalefactor SCALE\n");	
@@ -106,10 +107,13 @@ int main (int argc, char** argv)
       case 'C':
 	Cvalue = optarg;
  	break;
+      case 'D':
+	Dvalue = optarg;
+ 	break;
       case '?':
 	if (optopt == 't' || optopt == 's' || optopt == 'f' || optopt == 'o'|| optopt == 'n' || optopt == 'u'
 	    || optopt == 'F' || optopt == 'S' || optopt == 'l' || optopt == 'm' || optopt == 'T' || optopt == 'c'
-	    || optopt == 'i' || optopt == 'r' || optopt == 'H' || optopt == 'C')
+	    || optopt == 'i' || optopt == 'r' || optopt == 'H' || optopt == 'C' || optopt == 'D')
 	  printf ("Option = %c requires an argument\n", optopt);
 	  else if (isprint (optopt))
 	    printf ("Unknown option '-%c'\n", optopt);
[…]

### 2021-04-09 Flux/Source/Flux.cpp
Added many flags

@@ -3,8 +3,8 @@
 // PROGRAM ORGANIZATION:
 //
 //       Flux:: Flux          ()       
-// void  Flux:: Solve         (int _INTP, int _NTOR, int _MMIN, int _MMAX, double _TIME)
-// void  Flux:: SetParameters (int _INTG, int _NTOR, int _MMIN, int _MMAX, double _TIME)
+// void  Flux:: Solve         (int _INTP, int _NTOR, int _MMIN, int _MMAX, double _TIME, double _PSILIM, double _PSIPED, double _PSIRAT)
+// void  Flux:: SetParameters (int _INTG, int _NTOR, int _MMIN, int _MMAX, double _TIME, double _PSILIM, double _PSIPED, double _PSIRAT)
 // FILE* Flux:: OpenFilew     (char* filename)
 // FILE* Flux:: OpenFiler     (char* filename)
 // FILE* Flux:: OpenFilea     (char* filename)
@@ -21,10 +21,10 @@ Flux::Flux ()
 // #########################
 // Function to solve problem
 // #########################
-void Flux::Solve (int _INTP, int _NTOR, int _MMIN, int _MMAX, double _TIME, double _PSILIM)
+void Flux::Solve (int _INTP, int _NTOR, int _MMIN, int _MMAX, double _TIME, double _PSILIM, double _PSIPED, double _PSIRAT)
 {
   // Set global parameters
-  SetParameters (_INTP, _NTOR, _MMIN, _MMAX, _TIME, _PSILIM);
+  SetParameters (_INTP, _NTOR, _MMIN, _MMAX, _TIME, _PSILIM, _PSIPED, _PSIRAT);
 
   // Input gFile data and output Stage1 data.
   // Stage1 data output to directory Outputs/Stage1.
@@ -39,29 +39,34 @@ void Flux::Solve (int _INTP, int _NTOR, int _MMIN, int _MMAX, double _TIME, doub
 // #################################
 // Function to set global parameters
 // #################################
-void Flux::SetParameters (int _INTG, int _NTOR, int _MMIN, int _MMAX, double _TIME, double _PSILIM)
[…]

### 2021-04-09 Flux/Source/gFileRead.f90

@@ -25,7 +25,7 @@ subroutine gFileRead () bind (c, name = 'gFileRead')
   
   character (len = 100) :: string
   integer               :: i,       j,        i3,      NRBOX,   NZBOX, NBOUND, NLIM
-  double precision      :: RBOXLEN, ZBOXLEN,  R0,      RBOXLFT, zero,  RMAX
+  double precision      :: RBOXLEN, ZBOXLEN,  R0,      RBOXLFT, zero,  ZOFF,   RMAX
   double precision      :: RAXIS,   ZAXIS,    B0,      MU0,     ZMAX
   double precision      :: RLEFT,   RRIGHT,   ZLOW,    ZHIGH
   double precision      :: PSIAXIS, PSIBOUND, CURRENT
@@ -36,10 +36,13 @@ subroutine gFileRead () bind (c, name = 'gFileRead')
 
   MU0 = 16. * atan(1.0) * 1.e-7
 
+  ! ----------
+  ! Read gFile
+  ! ----------
   open (unit = 100, file = 'Inputs/gFile', status = 'old')
   
   read (100, '(a48, 3i4)') string,  i3,      NRBOX,   NZBOX
-  read (100, '(5e16.9  )') RBOXLEN, ZBOXLEN, R0,      RBOXLFT,  zero
+  read (100, '(5e16.9  )') RBOXLEN, ZBOXLEN, R0,      RBOXLFT,  ZOFF
   read (100, '(5e16.9  )') RAXIS,   ZAXIS,   PSIAXIS, PSIBOUND, B0
   read (100, '(5e16.9  )') CURRENT, zero,    zero,    zero,     zero
   read (100, '(5e16.9  )') zero,    zero,    zero,    zero,     zero
@@ -50,15 +53,39 @@ subroutine gFileRead () bind (c, name = 'gFileRead')
   allocate (Pp  (NRBOX))
   allocate (Q   (NRBOX))
   allocate (Psi (NRBOX, NZBOX))
+
+  read (100, '(5e16.9)') (T   (i), i = 1, NRBOX)
+  read (100, '(5e16.9)') (P   (i), i = 1, NRBOX)
+  read (100, '(5e16.9)') (TTp (i), i = 1, NRBOX)
+  read (100, '(5e16.9)') (Pp  (i), i = 1, NRBOX)
   
[…]

### 2021-04-09 IslandDynamics/Source/IslandDynamics.cpp

@@ -24,6 +24,9 @@
 // 1.8  - Added IRMP
 // 1.9  - Added COPT flag
 // 1.10 - Added more copt options
+// 1.11 - Added PSIPED
+// 1.12 - Removed PHASE_FREQ flag
+// 1.13 - Greatly simplified such that only calls PHASE
 
 // ##############################################################
 
@@ -34,15 +37,12 @@
 #include <time.h>
 
 #define VERSION_MAJOR 1
-#define VERSION_MINOR 10
+#define VERSION_MINOR 13
 
 #define MAXCOMMANDLINELENGTH 500
 
-extern "C" void NameListRead (int* FLUX_NTOR, int* FLUX_MMIN, int* FLUX_MMAX,
-			      int* NEO_INTP, int* NEO_INTF, int* NEO_IMPURITY, int* NEO_NEUTRAL, int* NEO_FREQ, int* NEO_NTYPE, double* NEO_NN, double* NEO_LN,
-			      double* NEO_YN, int* PHASE, int* PHASE_MID, int* PHASE_COPT, double* PHASE_CORE, int* PHASE_INTN, int* PHASE_INTU, int* PHASE_STAGE5, int* PHASE_OLD,
-			      int* PHASE_FREQ, int* PHASE_LIN, int* PHASE_HIGH, int* PHASE_RATS, double* PHASE_SCALE, double* PHASE_CHIR, int* RESTART,
-			      double* TSTART, double* TEND, double* DT); 
+extern "C" void NameListRead (int* PHASE_MID, int* PHASE_COPT, double* PHASE_CORE, int* PHASE_LIN, int* PHASE_FREQ, int* PHASE_HIGH, int* PHASE_RATS,
+			      int* PHASE_NATS, double* PHASE_SCALE, double* PHASE_CHIR, int* RESTART, double* TSTART, double* TEND, double* DT); 
 
 void IslandDynamics (double IRMP);
 
@@ -122,53 +122,38 @@ void IslandDynamics (double IRMP)
   // .............
   // Read namelist
   // .............
-  int    FLUX_INTG = 1;  // If != 0 then interpolate gFiles in FLUX
[…]

### 2021-04-09 Neoclassical/Source/cFileInterpolate.cpp

@@ -36,6 +36,27 @@ void Neoclassical::cFileInterp (vector<string> cFileName, vector<double> cFileTi
 
       cFileInterpolateQuadratic (file1, cFileTime[0], file2, cFileTime[1], cFile, time);
     }
+  else if (CATS)
+    {
+      int index;
+
+      if (time < cFileTime[0])
+	index = 0;
+      else if (time >= cFileTime[cFileNumber-1])
+	index = cFileNumber - 2;
+      else
+	{
+	  for (int i = 0; i < cFileNumber - 1; i++)
+	    if (time >= cFileTime[i] && time < cFileTime[i+1])
+	      index = i;
+	}
+      
+      char* cFile = "Inputs/cFile";
+      char* file1 = (char*) cFileName[index  ].c_str();
+      char* file2 = (char*) cFileName[index+1].c_str();
+
+      cFileInterpolateQuadratic (file1, cFileTime[index], file2, cFileTime[index+1], cFile, time);
+    }
   else if (cFileNumber == 3)
     {
       char* cFile = "Inputs/cFile";
@@ -121,12 +142,12 @@ void Neoclassical::cFileInterp (vector<string> cFileName, vector<double> cFileTi
 void Neoclassical::cFileInterpolateLinear (char* cFile1, double time1, char* cFile, double time)
 {
   int    n;
-  double x, y, dydx;
+  double x, y1, y2, y3, y4, dydx;
 
   // ################
   // Read first cFile
   // ################
-  Field Chip_1;        
+  Field Chip_1, Chie_1, Chin_1, Chii_1;        
 
   FILE* file = OpenFiler (cFile1);
 
@@ -138,10 +159,13 @@ void Neoclassical::cFileInterpolateLinear (char* cFile1, double time1, char* cFi
     }
 
   Chip_1.resize (n);
+  Chie_1.resize (n);
+  Chin_1.resize (n);
+  Chii_1.resize (n);
 
   for (int i = 0; i < n; i++)
     {
-      if (fscanf (file, "%lf %lf", &x, &y) != 2)
+      if (fscanf (file, "%lf %lf %lf %lf %lf", &x, &y1, &y2, &y3, &y4) != 5)
 	{
 	  printf ("NEOCLASSICAL::cFileInterpolateLinear: Error reading cFile_1 (2)\n");
[…]

### 2021-04-09 Neoclassical/Source/main.cpp

@@ -26,10 +26,10 @@ int main (int argc, char** argv)
   int c;
   char* nvalue = NULL; char* Ivalue = NULL; char* fvalue = NULL; char* tvalue = NULL;
   char* yvalue = NULL; char* pvalue = NULL; char* evalue = NULL; char* lvalue = NULL;
-  char* Nvalue = NULL; char* Tvalue = NULL; char* cvalue = NULL; 
+  char* Nvalue = NULL; char* Tvalue = NULL; char* cvalue = NULL; char* Cvalue = NULL; 
   opterr = 0;
   
-  while ((c = getopt (argc, argv, "c:e:f:hp:n:t:y:I:l:N:T:")) != -1)
+  while ((c = getopt (argc, argv, "c:e:f:hp:n:t:y:I:l:N:T:C:")) != -1)
     switch (c)
       {
       case 'c':
@@ -43,18 +43,19 @@ int main (int argc, char** argv)
 	break;
       case 'h':
 	printf ("Options:\n");
-	printf ("-c INTC     - set interpolation flag INTC\n");
-	printf ("-e INTF     - set interpolation flag INTF\n");
-	printf ("-f FREQ     - set frequency flag FREQ\n");
+	printf ("-c INTC     - set interpolation flag to INTC\n");
+	printf ("-e INTF     - set interpolation flag to INTF\n");
+	printf ("-f EXB      - set ExB frequency flag to EXB\n");
 	printf ("-h          - list options\n");
-	printf ("-l LN       - set neutral density distribution scalelength LN\n");
-	printf ("-n NEUTRAL  - set neutral flag NEUTRAL\n");
-	printf ("-p INTP     - set interpolation flag INTP\n");
+	printf ("-l LN       - set neutral density distribution scalelength to LN\n");
+	printf ("-n NEUTRAL  - set neutral flag to NEUTRAL\n");
+	printf ("-p INTP     - set interpolation flag to INTP\n");
 	printf ("-t TIME     - set experimental time to TIME\n");
-	printf ("-y YN       - set neutral poloidal peaking factor YN\n");
-	printf ("-I IMPURITY - set impurity flag IMPURITY\n");
-	printf ("-N NN       - set boundary neutral density NN\n");
-	printf ("-T NTYPE    - set neutral density distribution type NTYPE\n");
[…]

### 2021-04-09 Phase/Source/NamelistRead.f90

@@ -1,6 +1,6 @@
 ! Function to read PHASE namelist
 
-subroutine NameListRead (NFLOW, STAGE5, INTF, INTN, INTU, OLD, FREQ, LIN, MID, COPT, DT, TSTART, TEND, SCALE, PMAX,&
+subroutine NameListRead (NFLOW, STAGE5, INTF, INTN, INTU, NATS, OLD, FREQ, LIN, MID, COPT, DT, TSTART, TEND, SCALE, PMAX,&
      CHIR, HIGH, RATS, CORE, NCTRL, xTCTRL, xICTRL, xPCTRL) bind (c, name = 'NameListRead')
 
   use, intrinsic :: iso_c_binding, only: c_int, c_double
@@ -11,6 +11,7 @@ subroutine NameListRead (NFLOW, STAGE5, INTF, INTN, INTU, OLD, FREQ, LIN, MID, C
   integer (kind = c_int),    intent (inout) :: INTF
   integer (kind = c_int),    intent (inout) :: INTN
   integer (kind = c_int),    intent (inout) :: INTU
+  integer (kind = c_int),    intent (inout) :: NATS
   integer (kind = c_int),    intent (inout) :: OLD
   integer (kind = c_int),    intent (inout) :: FREQ
   integer (kind = c_int),    intent (inout) :: LIN 
@@ -38,7 +39,7 @@ subroutine NameListRead (NFLOW, STAGE5, INTF, INTN, INTU, OLD, FREQ, LIN, MID, C
   integer          :: i
   double precision :: pi
  
-  namelist /PHASE_CONTROL/   STAGE5, NFLOW, INTF, INTN, INTU, OLD, FREQ, LIN, MID, COPT, DT, TSTART, TEND, SCALE,&
+  namelist /PHASE_CONTROL/ STAGE5, NFLOW, INTF, INTN, INTU, NATS, OLD, FREQ, LIN, MID, COPT, DT, TSTART, TEND, SCALE,&
        PMAX, CHIR, HIGH, RATS, CORE
   namelist /PHASE_WAVEFORM/  NCTRL
   namelist /PHASE_WAVEFORM1/ TCTRL, ICTRL, PCTRL

### 2021-04-09 Phase/Source/nFileInterpolate.cpp

@@ -36,6 +36,27 @@ void Phase::nFileInterp (vector<string> nFileName, vector<double> nFileTime, int
 
       nFileInterpolateQuadratic (file1, nFileTime[0], file2, nFileTime[1], nFile, time);
     }
+  else if (NATS)
+    {
+      int index;
+
+      if (time < nFileTime[0])
+	index = 0;
+      else if (time >= nFileTime[nFileNumber-1])
+	index = nFileNumber - 2;
+      else
+	{
+	  for (int i = 0; i < nFileNumber - 1; i++)
+	    if (time >= nFileTime[i] && time < nFileTime[i+1])
+	      index = i;
+	}
+      
+      char* nFile = "Inputs/nFile";
+      char* file1 = (char*) nFileName[index  ].c_str();
+      char* file2 = (char*) nFileName[index+1].c_str();
+
+      nFileInterpolateQuadratic (file1, nFileTime[index], file2, nFileTime[index+1], nFile, time);
+    }
   else if (nFileNumber == 3)
     {
       char* nFile = "Inputs/nFile";
@@ -145,7 +166,7 @@ void Phase::nFileInterpolateLinear (char* nFile1, double time1, char* nFile, dou
  
   if (fscanf (file, "%d %lf %lf", &nres_1, &taua_1, &P0_1) != 3)
     {
-      printf ("PHASE::nFileInterpolateLinear:Error reading nFile_1 (1)\n");
+      printf ("PHASE::nFileInterpolateLinear: Error reading nFile_1 (1)\n");
       exit (1);
     }
   
@@ -157,11 +178,11 @@ void Phase::nFileInterpolateLinear (char* nFile1, double time1, char* nFile, dou
   u21_1.resize  (nres_1); u22_1.resize  (nres_1); u23_1.resize  (nres_1); u24_1.resize  (nres_1); u25_1.resize  (nres_1);
   u26_1.resize  (nres_1); u27_1.resize  (nres_1); u28_1.resize  (nres_1); u29_1.resize  (nres_1); u30_1.resize  (nres_1);
[…]

### 2021-04-09 WindowFind/Source/WindowFind.cpp

@@ -158,7 +158,7 @@ void WindowFind ()
   // ..............
   double IRMP = ISTART;
   char   ISLANDstring[MAXCOMMANDLINELENGTH];
-  double a, b, c, Q[5000], P[5000];
+  double a, b, c, d, Q[5000], P[5000];
 
   do
     {
@@ -179,7 +179,7 @@ void WindowFind ()
       // Extract RMP window data
       FILE* file = fopen ("../IslandDynamics/Outputs/Stage6/deltap.txt", "r");
       int i = -1;
-      while (fscanf (file, "%lf %lf %lf", &a, &b, &c) == 3)
+      while (fscanf (file, "%lf %lf %lf %lf", &a, &b, &c, &d) == 4)
 	{
 	  i++;
 	  Q[i] = b;

### 2021-04-18 Neoclassical/Source/Neoclassical.cpp
Improvements to poloidal equation of motion and linear layer theory

@@ -79,6 +79,9 @@ void Neoclassical::Solve (int _NEUTRAL, int _IMPURITY, int _EXB, int _INTP, int 
   // Calculcate neoclassical frequencies at rational surfaces
   Get_Frequencies ();
 
+  // Calculcate linear layer widths at rational surfaces
+  Get_LayerWidths ();
+
   // Calculate normalized quantites at rational surface and output nFile
   Get_Normalized ();
 }
@@ -90,7 +93,7 @@ void Neoclassical::Read_Parameters (int _NEUTRAL, int _IMPURITY, int _EXB, int _
 				    int _INTC, int _NTYPE, double _NN, double _LN, double _YN, double _TIME, int _CATS)
 {
   // Set default values of control parameters
-  EXB     = 0;
+  EXB      = 0;
 
   INTP     = 0;
   INTF     = 0;
@@ -312,18 +315,19 @@ void Neoclassical::Read_Equilibrium ()
   PsiNk.resize  (nres);
   dPsidr.resize (nres);
   A2.resize     (nres);
+  q_hat.resize  (nres);
 
   for (int j = 0; j < nres; j++)
     {
-      if (fscanf (file, "%d %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf",
-		  &mk (j), &rk (j), &sk (j), &gk (j), &gmk (j), &Ktk (j), &Kastk (j), &fck (j), &akk (j), &PsiNk (j), &dPsidr (j), &Kthek (j), &in, &A2 (j)) != 14)
+      if (fscanf (file, "%d %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf",
+		  &mk (j), &rk (j), &sk (j), &gk (j), &gmk (j), &Ktk (j), &Kastk (j), &fck (j), &akk (j), &PsiNk (j), &dPsidr (j), &Kthek (j), &in, &A2 (j), &q_hat (j)) != 15)
 	{
 	  printf ("NEOCLASSICAL:Read_Equilibrium: Error reading fFile (3)\n");
 	  exit (1);
 	}
       qk (j) = double (mk (j)) /double (ntor);
-      printf ("m = %3d  r = %11.4e  s = %11.4e  g = %11.4e  gm = %11.4e  Kt = %11.4e  Kast = %11.4e  Kthe = %11.4e  fc = %11.4e  akk = %11.4e  PsiN = %11.4e\n",
[…]

### 2021-04-18 Neoclassical/Source/Neoclassical.h

@@ -60,6 +60,8 @@
 // 1.18 - Added L_Ii_00 correction
 // 1.19 - Added Chii. Changed FREQ flag to EXB flag.
 // 1.20 - Added CATS flag
+// 1.21 - Use more accurate expression for neoclassical flow damping time
+// 1.22 - Added more accurate calculation of linear layer width
 
 // ################################################################
 
@@ -67,7 +69,7 @@
 #define NEOCLASSICAL
 
 #define VERSION_MAJOR 1
-#define VERSION_MINOR 20
+#define VERSION_MINOR 22
 
 #include <stdio.h>
 #include <math.h>
@@ -75,6 +77,8 @@
 #include <unistd.h>
 #include <vector>
 #include <blitz/array.h>
+#include <gsl/gsl_complex.h>
+#include <gsl/gsl_complex_math.h>
 #include <gsl/gsl_const_mksa.h>
 #include <gsl/gsl_sf_erf.h>
 #include <gsl/gsl_linalg.h>
@@ -150,6 +154,8 @@ class Neoclassical
   double hmin;     // Minimum step-length
   double hmax;     // Maximum step-length
   int    maxrept;  // Maximum number of step recalculations
+  int    flag;     // Flag for selecting right-hand sides of differential equations
+  int    jres;     // Flag for selecting resonant surface
 
   // .......................
   // Plasma equilibrium data
@@ -253,7 +259,7 @@ class Neoclassical
   int             ntor;   // Toroidal mode number
   int             nres;   // Number of resonant surfaces
   Array<int,1>    mk;     // Poloidal mode numbers
-  Array<double,1> rk;     // Minor radii /r_a
+  Array<double,1> rk;     // Minor radii /a
   Array<double,1> PsiNk;  // Normalized poloidal fluxes 
   Array<double,1> qk;     // Safety factors
   Array<double,1> sk;     // Magnetic shears (dlnq/dlnr)
@@ -266,6 +272,7 @@ class Neoclassical
   Array<double,1> akk;    // Metric elements
   Array<double,1> dPsidr; // R_0 dPsiN/dr
   Array<double,1> A2;     // A2
+  Array<double,1> q_hat;  // q_hat
 
   // Derived from profiles
   double rho0;                // Central mass density (kg/m^-3)
@@ -343,6 +350,16 @@ class Neoclassical
   Array<double,1> tau_Mk;     // Momentum confinement timescales (s)
   Array<double,1> tau_thk;    // Poloidal flow damping timescales (s)
 
[…]

### 2021-04-22 Phase/Source/NamelistRead.f90
Improvements to layer theory and poloidal e.o.m.

@@ -1,7 +1,8 @@
 ! Function to read PHASE namelist
 
-subroutine NameListRead (NFLOW, STAGE5, INTF, INTN, INTU, NATS, OLD, FREQ, LIN, MID, COPT, DT, TSTART, TEND, SCALE, PMAX,&
-     CHIR, HIGH, RATS, CORE, FFAC, NCTRL, xTCTRL, xICTRL, xPCTRL) bind (c, name = 'NameListRead')
+subroutine NameListRead (NFLOW, STAGE5, INTF, INTN, INTU, NATS, OLD, FREQ, LIN, MID, COPT,&
+     DT, TSTART, TEND, SCALE, PMAX, CHIR, HIGH, RATS, CORE, FFAC, NCTRL,&
+     xTCTRL, xICTRL, xPCTRL) bind (c, name = 'NameListRead')
 
   use, intrinsic :: iso_c_binding, only: c_int, c_double
   implicit none
@@ -40,8 +41,8 @@ subroutine NameListRead (NFLOW, STAGE5, INTF, INTN, INTU, NATS, OLD, FREQ, LIN, 
   integer          :: i
   double precision :: pi
  
-  namelist /PHASE_CONTROL/ STAGE5, NFLOW, INTF, INTN, INTU, NATS, OLD, FREQ, FFAC, LIN, MID, COPT, DT, TSTART, TEND, SCALE,&
-       PMAX, CHIR, HIGH, RATS, CORE
+  namelist /PHASE_CONTROL/ STAGE5, NFLOW, INTF, INTN, INTU, NATS, OLD, FREQ, FFAC, LIN, MID, COPT, DT,&
+       TSTART, TEND, SCALE, PMAX, CHIR, HIGH, RATS, CORE
   namelist /PHASE_WAVEFORM/  NCTRL
   namelist /PHASE_WAVEFORM1/ TCTRL, ICTRL, PCTRL
   

### 2021-04-22 Phase/Source/fFileInterpolate.cpp

@@ -171,7 +171,7 @@ void Phase::fFileInterpolateLinear (char* fFile1, double time1, char* fFile, dou
   u4_1.resize   (nres_1); u5_1.resize  (nres_1); u6_1.resize  (nres_1);
   u7_1.resize   (nres_1); u8_1.resize  (nres_1); u9_1.resize  (nres_1);
   u10_1.resize  (nres_1); u11_1.resize (nres_1); u12_1.resize (nres_1);
-  u13_1.resize  (nres_1);
+  u13_1.resize  (nres_1); u14_1.resize (nres_1);
 
   for (int j = 0; j < nres_1; j++)
     {
@@ -230,14 +230,17 @@ void Phase::fFileInterpolateLinear (char* fFile1, double time1, char* fFile, dou
   nres_0 = nres_1;
 
   v1_0.resize     (NPSI_0); v2_0.resize  (NPSI_0); v3_0.resize  (NPSI_0);
+
   mres_0.resize   (nres_0);
   u1_0.resize     (nres_0); u2_0.resize  (nres_0); u3_0.resize  (nres_0);
   u4_0.resize     (nres_0); u5_0.resize  (nres_0); u6_0.resize  (nres_0);
   u7_0.resize     (nres_0); u8_0.resize  (nres_0); u9_0.resize  (nres_0);
   u10_0.resize    (nres_0); u11_0.resize (nres_0); u12_0.resize (nres_0);
-  u13_0.resize    (nres_0);
+  u13_0.resize    (nres_0); u14_0.resize (nres_0);
+
   Freal_0.resize  (nres_0, nres_0); Fimag_0.resize  (nres_0, nres_0);
   Ereal_0.resize  (nres_0, nres_0); Eimag_0.resize  (nres_0, nres_0);
+
   EIreal_0.resize (nres_0); EIimag_0.resize (nres_0);
   EOreal_0.resize (nres_0); EOimag_0.resize (nres_0);
 
@@ -393,7 +396,7 @@ void Phase::fFileInterpolateQuadratic (char* fFile1, double time1, char* fFile2,
   u4_1.resize   (nres_1); u5_1.resize  (nres_1); u6_1.resize  (nres_1);
   u7_1.resize   (nres_1); u8_1.resize  (nres_1); u9_1.resize  (nres_1);
   u10_1.resize  (nres_1); u11_1.resize (nres_1); u12_1.resize (nres_1);
[…]

### 2021-06-28 Documentation/EPEC_Model.tex
Added charge exchange damping

\documentclass[12pt,prb,aps]{revtex4-2}
\usepackage {amsmath}
\pdfoutput = 1 
\usepackage {graphicx}
\allowdisplaybreaks

\begin{document}
\title{\bf The EPEC Model}
\author{R.~Fitzpatrick\,\footnote{rfitzp@utexas.edu}}
\affiliation{Institute for Fusion Studies,  Department of Physics,  University of Texas at Austin,  Austin TX 78712, USA}

\maketitle

\section{Plasma Response in Outer Region}
\subsection{Coordinates}\label{a1}
Let $R$, $\phi$, and $Z$ be right-handed cylindrical coordinates whose symmetry axis corresponds to
the toroidal symmetry axis of the plasma. Let $r$, $\theta$, and $\phi$ be right-handed flux coordinates
whose Jacobian is ${\cal J}\equiv (\nabla r \times \nabla\theta\cdot\nabla\phi)^{-1}=r\,R^{\,2}/R_0$. 
Here, $R_0$ is a convenient scale major radius, $r$ is a magnetic flux-surface label with dimensions of length,
and $\theta$ is an axisymmetric angular coordinate that increases by $2\pi$ radians for every poloidal circuit of the magnetic axis.
Let $r=0$ correspond to the magnetic axis, and let $r=r_{100}$ correspond to the LCFS. 
Let $\theta=0$ correspond to the inboard midplane, and let $0<\theta<\pi$ correspond to the region above the midplane.

\subsection{Equilibrium Magnetic Field}\label{a2}
The equilibrium magnetic field is written
${\bf B} = R_0\,B_0\left[f(r)\,\nabla\phi\times \nabla r + g(r)\,\nabla\phi\right]$, 
where $B_0$ is a convenient scale toroidal magnetic field-strength, and
$q(r) = r\,g/(R_0\,f)$
is the safety-factor profile. The equilibrium poloidal magnetic flux (divided by $2\pi$), ${\mit\Psi}_p(r)$,
satisfies $d{\mit\Psi}_p/dr = R_0\,B_0\,f(r)$, where, by convention, ${\mit\Psi}_p(r_{100})=0$. The
normalized poloidal magnetic flux, ${\mit\Psi}_N(r)$, is defined such that
${\mit\Psi}_N(r) = 1-{\mit\Psi}_p(r)/{\mit\Psi}_p(0)$. Hence, ${\mit\Psi}_N(0)=0$ and
${\mit\Psi}_N(r_{100})=1$. Finally, if ${\mit\Psi}_N(r_{95})=0.95$ then $q_{95}\equiv q(r_{95})$.

\subsection{Perturbed Magnetic Field}
Consider the response of the plasma to an RMP with $n>0$ periods in the toroidal direction.
We can write the components of the perturbed magnetic field in the form
\begin{align}
\frac{r\,R^{\,2}\,\delta{\bf B}\cdot\nabla r}{R_0^{\,2}}&= {\rm i}\sum_j \psi_j(r)\,{\rm e}^{\,{\rm i}\,(m_j\theta-n\,\phi)},\\[0.5ex]
{\cal J} \,\delta{\bf B}\cdot\nabla\phi\times \nabla r &= -\sum_j{\mit\Xi}_j(r)\,{\rm e}^{\,{\rm i}\,(m_j\theta-n\,\phi)},\\[0.5ex]
R^{\,2}\,\delta{\bf B}\cdot\nabla\phi&= n\sum_j \frac{{\mit\Xi}_j(r)}{m_j}\,{\rm e}^{\,{\rm i}\,(m_j\,\theta-n\,\phi)},
\end{align}
where the sum is over all relevant poloidal harmonics of the perturbed magnetic field.

Let there be $K$ resonant magnetic flux-surfaces in the plasma, labelled $1$ through $K$.
Consider the $k$th resonant surface, $r=r_k$, at which $n\,q(r_k)= m_k$, where $m_k$ is a positive integer. Let
${\mit\Psi}_k = \psi_k(r_k)/m_k$, and 
${\mit\Delta\Psi}_k=[{\mit\Xi}_k]_{r_{k-}}^{r_{k+}}$.
Here, ${\mit\Psi}_k$ is the (complex) reconnected helical magnetic flux (divided by $2\pi\,R_0$) at the $k$th resonant surface, whereas ${\mit\Delta\Psi}_k$ (which has the same dimensions as ${\mit\Psi}_k$) is a (complex) 
measure of the strength of the current sheet (consisting of filaments running parallel to the local equilibrium magnetic
field) at the same resonant surface.

\subsection{Toroidal Tearing Mode Dispersion Relation}\label{tear}
In the presence of the RMP, the ${\mit\Psi}_k$ and the ${\mit\Delta\Psi}_k$ values are related according to the inhomogeneous 
toroidal tearing mode dispersion relation, which takes the form
\begin{equation}\label{dispersion}
{\mit\Delta\Psi}_k = \sum_{k'=1,K} E_{kk'}\,{\mit\Psi}_{k'} + |E_{kk}|\,\chi_k.
\end{equation}
Here, $E_{kk'}$  (for $k$, $k'= 1$, $K$) is the dimensionless, Hermitian, toroidal tearing mode stability matrix, whereas the $\chi_k$ (for $k=1,K$) parameterize the current sheets driven at the various
resonant surfaces when the plasma responds  to the applied RMP in accordance with the equations of linearized, marginally-stable, ideal-MHD.

The EPEC model determines the elements of the $E_{kk'}$ matrix using a high-$q$ approximation. In fact, if $F_{kk'}$ is the inverse of the $E_{kk'}$ matrix then
\begin{equation}\label{e56}
F_{kk'} = \oint\oint 
G(R_k,Z_k;R_{k'},Z_{k'})\,{\rm e}^{-{\rm i}\,(m_k\,\theta_k-m_{k'}\,\theta_{k'})}\,\frac{d\theta_k}{2\pi}\,\frac{d\theta_{k'}}{2\pi},
\end{equation}
and
\begin{align}
 G(R_k,Z_k;R_{k'},Z_{k'})&= \frac{(-1)^{\,n}\,\pi^{\,2}\,R_k\,R_{k'}/R_0}{2\,\Gamma(1/2)\,\Gamma(n+1/2)}
\left[\frac{\cosh\eta_{kk'}}{R_k^{\,2}+R_{k'}^{\,2}+(Z_k-Z_{k'})^{\,2}}\right]^{1/2}\nonumber\\[0.5ex]
&\times\left[(n-1/2)\,P_{-1/2}^{\,n-1}(\cosh\eta_{kk'})+
\frac{P_{-1/2}^{\,n+1}(\cosh\eta_{kk'})}{n+1/2}\right],
\end{align}
with
\begin{equation}
\eta_{kk'} = \tanh^{-1}\left[\frac{2\,R_k\,R_{k'}}{R_k^{\,2}+R_{k'}^{\,2}+(Z_k-Z_{k'})^{\,2}}\right].
\end{equation}
Here, the double integral in Eq.~(\ref{e56}) is taken around the
$k$th resonant surface (cylindrical coordinates $R_k$, $0$, $Z_k$;
flux coordinates $r_k$, $\theta_k$, $0$, with $r_k$ constant; resonant poloidal mode number $m_k$) and the $k'$th resonant surface (cylindrical coordinates $R_{k'}$, $0$, $Z_{k'}$;
flux coordinates $r_{k'}$, $\theta_{k'}$, $0$, with $r_{k'}$ constant; resonant poloidal mode number $m_{k'}$). Finally, the $\Gamma(z)$ and $P_\mu^{\,\nu}(z)$ are Gamma functions and associated Legendre functions, respectively.

The (complex) $\chi_k$ parameters are determined from the GPEC code.
To be more exact, the GPEC code calculates the (complex) dimensionless ${\mit\Delta}_{m_k\,n}$ parameters which measure the strengths of the ideal current sheets that develop
at the various resonant magnetic flux-surfaces in the plasma in response to the applied RMP.  The ${\mit\Delta}_{m_k\,n}$ parameters are related to the $\chi_k$ parameters according to
\begin{equation}\label{a8}
\frac{\chi_k}{R_0\,B_0} = -{\rm i} \,\frac{{\mit\Delta}_{m_k\,n}}{|E_{kk}|}\left(\frac{r_k}{R_0}\right)^2
\frac{g(r_k)}{m_k\,[a_{kk}(r_k)+ (r_k/R_0\,q_k)^{\,2}]},
\end{equation}
where $q_k= m_k/n$, and $a_{kk}(r) = \oint |\nabla r|^{-2}\,d\theta/(2\pi)$.

\section{Neoclassical Physics}\label{appb}
\subsection{Plasma Species}\label{a3}
The plasma is assumed to consist of three (charged) species; namely,  electrons ($e$), majority ions ($i$), and impurity ions
($I$).  The charges of the  three species are $e_e=-e$, $e_i= e$, and $e_I=Z_I\,e$, respectively, where
$e$ is the magnitude of the electron charge. 
Quasi-neutrality demands that
$n_e= n_i+ Z_I\,n_I$, where $n_a(r)$ is the species-$a$ number density. 
 Let 
$\alpha_I(r) =Z_I\,(Z_{\rm eff}-1)/(Z_I-Z_{\rm eff})$,
where 
$Z_{\rm eff}(r) = (n_i+Z_I^{\,2}\,n_I)/n_e$
is the effective ion charge number. It follows that
$n_i/n_e = (Z_I-Z_{\rm eff})/(Z_I-1)$
and
$n_I/n_e= (Z_{\rm eff}-1)/[Z_I\,(Z_I-1)]$.

\subsection{Collisionality Parameters}
Consider an equilibrium magnetic flux-surface whose label is $r$. 
Let
\begin{equation}
\frac{1}{\gamma(r)} =\frac{q}{g}\oint\frac{ B\,R^{\,2}}{B_0\,R_0^{\,2}}\,\frac{d\theta}{2\pi},
\end{equation}
where $B=|{\bf B}|$. 
It is helpful to define a new poloidal angle ${\mit\Theta}$ such that
\begin{equation}
\frac{d{\mit\Theta}}{d\theta} = \frac{\gamma\,q}{g}\,\frac{B\,R^{\,2}}{B_0\,R_0^{\,2}}.
\end{equation}
Let
\begin{align}
I_1 &=\oint \frac{B_0}{B}\,\frac{d{\mit\Theta}}{2\pi},\\[0.5ex]
I_2 &=\oint \frac{B}{B_0}\,\frac{d{\mit\Theta}}{2\pi},\\[0.5ex]
I_3 &=\oint\left(\frac{\partial B}{\partial{\mit\Theta}}\right)^2\frac{1}{B_0\,B}\,\frac{d{\mit\Theta}}{2\pi},\\[0.5ex]
I_{4,j}&= \sqrt{2\,j}\oint\frac{\cos(j\,{\mit\Theta})}{B/B_0}\,\frac{d{\mit\Theta}}{2\pi},\\[0.5ex]
I_{5,j} &= \sqrt{2\,j}\oint\frac{\cos(j\,{\mit\Theta})}{2\,(B/B_0)^{\,2}}\,\frac{d{\mit\Theta}}{2\pi},\\[0.5ex]
I_6(\lambda) &=\oint \frac{\sqrt{1-\lambda\,B/B_{\rm max}}}{B/B_0}\,\frac{d{\mit\Theta}}{2\pi},
\end{align}
where $B_{\rm max}$ is the maximum value of $B$ on the magnetic
flux-surface, and $j$ a positive integer. 
The species-$a$ transit frequency is written
$\omega_{t\,a}(r)= K_t\,\gamma\,v_{T\,a}$,
where 
\begin{equation}\label{cdef}
K_t(r) = \frac{I_1^{\,2}\,I_3}{I_2^{\,2}\,\sum_{j=1,\infty} I_{4,j}\,I_{5,j}},
\end{equation}
and $v_{T\,a} = \sqrt{2\,T_a/m_a}$.  Here, $m_a$ is the
species-$a$ mass, and $T_a(r)$ the species-$a$ temperature (in energy units). The fraction of circulating particles 
is
\begin{equation}
f_c(r) = \frac{3\,I_2}{4}\,\frac{B_0^{\,2}}{B_{\rm max}^{\,2}}
\int_0^1 \frac{\lambda\,d\lambda}{I_6(\lambda)}.
\end{equation}
Finally, the dimensionless species-$a$ collisionality parameter
is written
$\nu_{\ast\,a} (r)= K_\ast\,g_t/(\omega_{t\,a}\,\tau_{aa})$,
where 
$g_t(r) =f_c/(1-f_c)$,
\begin{align}
K_\ast(r) &= \frac{3}{8\pi}\,\frac{I_2}{I_3}\,K_t^{\,2},\\[0.5ex]
\frac{1}{\tau_{aa}(r)}&= \frac{4}{3\sqrt{\pi}}\,\frac{4\pi\,n_a\,e_a^{\,4}\,\ln{\mit\Lambda}}{(4\pi\,\epsilon_0)^{\,2}\,m_a^{\,2}\,v_{T\,a}^{\,3}}.
\end{align}
Here, the Coulomb logarithm, $\ln{\mit\Lambda}$, is assumed to take the same large constant value (i.e., $\ln{\mit\Lambda}\simeq 17$), 
independent of species.

\subsection{Collisional Friction Matrices}
Let $x_{ab}=v_{T\,b}/v_{T\,a}$. In the following,
all quantities that are of order $(m_e/m_i)^{\,1/2}$, $(m_e/m_I)^{\,1/2}$, or smaller, are neglected with respect to unity.
The  $2\times 2$ dimensionless ion collisional friction matrices, $[F^{\,ii}](r)$, $[F^{\,iI}](r)$, $[F^{\,Ii}](r)$, and $[F^{\,II}](r)$, are defined to have the following elements:
\begin{align}
F^{\,ii}_{\,00} &= \frac{\alpha_I\,(1+m_i/m_I)}{(1+x_{iI}^{\,2})^{\,3/2}},\\[0.5ex]
F^{\,ii}_{\,01}&=\frac{3}{2}\,\frac{\alpha_I\,(1+m_i/m_I)}{(1+x_{iI}^{\,2})^{\,5/2}},\\[0.5ex]
F^{\,ii}_{\,11}& =\sqrt{2}+ \frac{\alpha_I\,[13/4+4\,x_{iI}^{\,2}+(15/2)\,x_{iI}^{\,4}]}{(1+x_{iI}^{\,2})^{\,5/2}},\\[0.5ex]
F^{\,iI}_{\,01}&=\frac{3}{2}\,\frac{T_i}{T_I}\,\frac{\alpha_I\,(1+m_I/m_i)}{x_{iI}\,(1+x_{Ii}^{\,2})^{\,5/2}},\\[0.5ex]
F^{\,iI}_{\,11}& =\frac{27}{4}\,\frac{T_i}{T_I}\,\frac{\alpha_I\,x_{iI}^{\,2}}{(1+x_{iI}^{\,2})^{\,5/2}},\\[0.5ex]
F^{\,Ii}_{\,11}& =\frac{27}{4}\,\frac{\alpha_I\,x_{iI}^{\,2}}{(1+x_{iI}^{\,2})^{\,5/2}},\\[0.5ex]
F^{\,II}_{\,11}& =\frac{T_i}{T_I}\left\{\sqrt{2}\,\alpha_I^{\,2}\,x_{Ii} + \frac{\alpha_I\,[
15/2+4\,x_{iI}^{\,2}+(13/4)\,x_{iI}^{\,4}]}{(1+x_{iI}^{\,2})^{\,5/2}}\right\},
\end{align}
 $F^{\,ii}_{\,10}=F^{\,ii}_{\,01}$, $F^{\,iI}_{\,00} =F^{\,ii}_{\,00}$, $F^{\,iI}_{\,10}=F^{\,ii}_{01}$, $F^{\,Ii}_{\,00} =F^{\,ii}_{\,00}$,
$F^{\,Ii}_{\,01}=F^{\,ii}_{01}$, 
$F^{\,Ii}_{\,10}=F^{\,iI}_{01}$, $F^{\,II}_{\,00} =F^{\,ii}_{00}$,
$F^{\,II}_{\,01}=F^{\,iI}_{01}$, 
$F^{\,II}_{\,10}=F^{\,iI}_{01}$.

The $2\times 2$ dimensionless electron collisional friction matrix, $[F^{\,ee}](r)$,   is defined to have the following elements:
$F^{\,ee}_{00} = Z_{\rm eff}$,
$F^{\,ee}_{01} = (3/2)\,Z_{\rm eff}$,
$F^{\,ee}_{10} = F^{\,ee}_{01}$,
$F^{\,ee}_{11}= \sqrt{2} + (13/4)\,Z_{\rm eff}$.

\subsection{Neoclassical Viscosity Matrices}\label{vmatrix}
The $2\times 2$ dimensionless species-$a$ neoclassical viscosity matrix, $[\mu^{\,a}](r)$,  is defined to have the following elements:
$\mu_{00}^{\,a} = K_{00}^{\,a}$, $\mu_{01}^{\,a}= (5/2)\,K_{00}^{\,a}- K_{01}^{\,a}$,
$\mu_{10}^{\,a}= \mu_{01}^{\,a}$,
$\mu_{11}^{\,a} = K_{11}^{\,a} - 5\,K_{01}^{\,a}+(25/4)\,K_{00}^{\,a}$.
Here,
\begin{align}
 K_{jk}^{\,e} &= g_t\,\frac{4}{3\sqrt{\pi}}\int_0^\infty
\frac{e^{-x}\,x^{\,4+j+k}\,\nu_D^{\,e}(x)\,dx}{[x^{\,2}+\nu_{\ast\,e}\,\nu_D^{\,e}(x)]\,[x^{\,2}+(5\pi/8)\,(\omega_{t\,e}\,\tau_{ee})^{\,-1}\,\nu_T^{\,e}(x)]},\\[0.5ex]
\nu_D^{\,e}&= \frac{3\sqrt{\pi}}{4}\left[\left(1-\frac{1}{2\,x}\right)\psi(x)+\psi'(x)\right]+\frac{3\sqrt{\pi}}{4}\,Z_{\rm eff},\\[0.5ex]
\nu_\epsilon^{\,e}&= \frac{3\sqrt{\pi}}{2}\left[\psi(x)-\psi'(x)\right],\\[0.5ex]
\nu_T^{\,a}(x) &= 3\,\nu_D^{\,a}(x)+\nu_{\epsilon}^{\,a}(x),
\end{align}
and
\begin{align}
\psi(x) &= \frac{2}{\sqrt{\pi}}\int_0^x{\rm e}^{-t^{\,2}}\,dt -\frac{2}{\sqrt{\pi}}\,x\,{\rm e}^{-x^{\,2}},\\[0.5ex]
\psi'(x)&= \frac{2}{\sqrt{\pi}}\,x\,{\rm e}^{-x^{\,2}}.
\end{align}
Furthermore, 
\begin{align}
 K_{jk}^{\,i} &=g_t\,\frac{4}{3\sqrt{\pi}}\int_0^\infty
\frac{e^{-x}\,x^{\,2+j+k}\,\nu_D^{\,i}(x)\,dx}{[x+\nu_{\ast\,i}\,\nu_D^{\,i}(x)]\,[x+(5\pi/8)\,(\omega_{t\,i}\,\tau_{ii})^{\,-1}\,\nu_T^{\,i}(x)]},\\[0.5ex]
 \nu_D^{\,i}&= \frac{3\sqrt{\pi}}{4}\left[\left(1-\frac{1}{2\,x}\right)\psi(x)+\psi'(x)\right]\frac{1}{x}\nonumber\\[0.5ex]\phantom{===}
&\phantom{=}+\frac{3\sqrt{\pi}}{4}\,\alpha_I\left[\left(1-\frac{x_{iI}}{2\,x}\right)\psi\!\left(\frac{x}{x_{iI}}\right)
+\psi'\!\left(\frac{x}{x_{iI}}\right)\right]\frac{1}{x},\\[0.5ex]
 \nu_\epsilon^{\,i}&=\frac{3\sqrt{\pi}}{2}\left[\psi(x)-\psi'(x)\right]\frac{1}{x}\nonumber\\[0.5ex]\phantom{===}
&\phantom{=}+\frac{3\sqrt{\pi}}{2}\,\alpha_I\left[\frac{m_i}{m_I}\,\psi\!\left(\frac{x}{x_{iI}}\right)
-\psi'\!\left(\frac{x}{x_{iI}}\right)\right]\frac{1}{x},
\end{align}
and, finally, 
\begin{align}
 K_{jk}^{\,I} &= g_t\,\frac{4}{3\sqrt{\pi}}\int_0^\infty
\frac{e^{-x}\,x^{\,2+j+k}\,\nu_D^{\,I}(x)\,dx}{[x+\nu_{\ast\,I}\,\nu_D^{\,I}(x)]\,[x+(5\pi/8)\,(\omega_{t\,I}\,\tau_{II})^{\,-1}\,\nu_T^{\,I}(x)]},\\[0.5ex]
 \nu_D^{\,I}&= \frac{3\sqrt{\pi}}{4}\left[\left(1-\frac{1}{2\,x}\right)\psi(x)+\psi'(x)\right]\frac{1}{x}\nonumber\\[0.5ex]\phantom{===}
&\phantom{=}+\frac{3\sqrt{\pi}}{4}\,\frac{1}{\alpha_I}\left[\left(1-\frac{x_{Ii}}{2\,x}\right)\psi\!\left(\frac{x}{x_{Ii}}\right)
+\psi'\!\left(\frac{x}{x_{Ii}}\right)\right]\frac{1}{x},\\[0.5ex]
 \nu_\epsilon^{\,I}&= \frac{3\sqrt{\pi}}{2}\left[\psi(x)-\psi'(x)\right]\frac{1}{x}\nonumber\\[0.5ex]\phantom{===}
&\phantom{=}+\frac{3\sqrt{\pi}}{2}\,\frac{1}{\alpha_I}\left[\frac{m_I}{m_i}\,\psi\!\left(\frac{x}{x_{Ii}}\right)
-\psi'\!\left(\frac{x}{x_{Ii}}\right)\right]\frac{1}{x}.
\end{align}
Note that our expressions for the neoclassical viscosity
matrices interpolate in the most accurate manner possible
between the three standard neoclassical collisionality
regimes (i.e., the banana, plateau, and Pfirsch-Sch\"{u}ter
regimes).

\subsection{Parallel Force and Heat Balance}\label{sbalance}
Let
$[\tilde{\mu}^{\,I}] =\alpha_I^{\,2}\,(T_i/T_I)\,x_{Ii}\,[\mu^{\,I}]$.
The requirement of equilibrium force and heat balance parallel to the magnetic field leads us to define
four $2\times 2$  dimensionless ion matrices, $[L^{\,ii}](r)$, $[L^{\,iI}](r)$, $[L^{\,Ii}](r)$, and $[L^{\,II}](r)$,
where
\begin{align}
\left(\begin{array}{cc} [L^{\,ii}], & [L^{\,iI}]\\[0.5ex] [L^{\,Ii}],& [L^{\,II}]\end{array}\right)=
\left(\begin{array}{cc}[F^{\,ii}+\mu^{\,i}+ Y^{\,in}/y_n], & -[F^{\,iI}]\\[0.5ex] -[F^{\,Ii}], & [F^{\,II}+\tilde{\mu}^{\,I}]\end{array}\right)^{-1}
\left(\begin{array}{cc} [F^{\,ii}+Y^{\,in}], & -[F^{\,iI}]\\[0.5ex] -[F^{\,Ii}], & [F^{\,II}]\end{array}\right),
\end{align}
the additional  four $2\times 2$  dimensionless ion matrices, $[G^{\,ii}](r)$, $[G^{\,iI}](r)$, $[G^{\,Ii}](r)$, and $[G^{\,II}](r)$,
where
\begin{align}
\left(\begin{array}{cc} [G^{\,ii}], & [G^{\,iI}]\\[0.5ex] [G^{\,Ii}],& [G^{\,II}]\end{array}\right)=\tau_{ii}\,\langle \sigma\,v\rangle_i^{\,\rm cx}
\,\langle n_n\rangle
\left(\begin{array}{cc}[F^{\,ii}+\mu^{\,i}+ Y^{\,in}/y_n], & -[F^{\,iI}]\\[0.5ex] -[F^{\,Ii}], & [F^{\,II}+\tilde{\mu}^{\,I}]\end{array}\right)^{-1},
\end{align}
and the $2\times 2$ dimensionless electron matrix, $[Q^{\,ee}](r)$, 
where
$[Q^{\,ee}]= [F^{\,ee}+\mu^{\,e}]^{\,-1}$.
Here,
\begin{align}
[Y^{\,in}] &= \tau_{ii}\,\langle \sigma\,v\rangle_i^{\,\rm cx}
\,\langle n_n\rangle\left[
\begin{array}{cc} 1,& 0\\[0.5ex]0,&E_n/T_i\end{array}
\right],\\[0.5ex]
y_n &= \frac{\langle n_n\rangle\,\langle B^{\,2}\rangle}{\langle
n_n\,B^{\,2}\rangle},
\end{align}
where
\begin{equation}
\langle A\rangle (r) \equiv\left.\oint \frac{A(r,{\mit\Theta})\,d{\mit\Theta}}{B(r,{\mit\Theta})}\right/\oint \frac{d{\mit\Theta}}{B(r,{\mit\Theta})}.
\end{equation}
Moreover, $\langle \sigma\,v\rangle_i^{\,\rm cx}$ is the flux-surface
averaged rate constant for charge exchange reactions between neutrals and majority ions, $n_n(r,{\mit\Theta})$  the
neutral particle number density, and $E_n/T_i$ the ratio of the incoming neutral energy to the majority ion energy. The parameter
$y_n$ takes into account the fact that the incoming neutrals at the
edge of an H-mode tokamak plasma are usually
concentrated at the X-point (i.e., $y_n>1$).

\subsection{Impurity Ion Angular Rotation Velocities}\label{srotation}
Let
\begin{align}
\omega_{\theta\,I}(r)&=\frac{{\bf V}^{\,I}\cdot\nabla\theta}{{\bf B}\cdot\nabla\theta}\,\frac{R_0\,B_0\,g}{R^{\,2}},\\[0.5ex]
\omega_{\phi\,I}(r) &= {\bf V}^{\,I}\cdot\nabla\phi,
\end{align}
where ${\bf V}^{\,I}$ is the impurity ion fluid velocity, and the right-hand sides are evaluated on the outboard mid-plane. According to neoclassical theory
\begin{align}
\omega_{\theta\,I} &= K_\theta\,\omega_{{\rm nc}\,I},\\[0.5ex]
\omega_{\phi\,I} &= \omega_E+\omega_{\ast\,I} + \omega_{\theta\,I},
\end{align}
where
\begin{equation}
K_\theta(r) = \frac{R_0^{\,2}\,B_0^{\,2}\,g^{\,2}}{R^{\,2}\,\langle B^{\,2}\rangle},
\end{equation}
\begin{align}
\omega_E(r) &=-\frac{d{\mit\Phi}}{d{\mit\Psi}_p},\\[0.5ex]
\omega_{\ast\,a}(r) &= -\frac{T_a}{e_a}\,\frac{d\ln p_a}{d{\mit\Psi}_p},\\[0.5ex]
\eta_a(r) &= \frac{d\ln T_a}{d\ln n_a}.
\end{align}
and 
\begin{align}\label{a53}
\omega_{{\rm nc}\,I}(r)&=-G_{00}^{\,Ii}\,\omega_E -\left[L^{\,II}_{00}-L^{\,II}_{01}\left(\frac{\eta_I}{1+\eta_I}\right)\right]\omega_{\ast\,I}-
\left[L^{\,Ii}_{00}-L^{\,Ii}_{01}\left(\frac{\eta_i}{1+\eta_i}\right)\right]\omega_{\ast\,i}.
\end{align}
Here, $p_a(r)=n_a\,T_a$, and ${\mit\Phi}(r)$ is the equilibrium electric scalar potential.

\section{Plasma Response in Inner Region}
\subsection{Evolution Equations}
Let ${\mit\Psi}_k= R_0\,B_0\,\hat{\mit\Psi}_k\,{\rm e}^{-{\rm i}\,\varphi_k}$, ${\mit\chi}_k= R_0\,B_0\,\hat{\chi}_k\,{\rm e}^{-{\rm i}\,\zeta_k}$, and $E_{kk'}=\hat{E}_{kk'}\,{\rm e}^{-{\rm i}\,\xi_{kk'}}$,
where $\hat{\mit\Psi}_k>0$, $\varphi_k$, $\hat{\chi}_k>0$, $\zeta_k$, $\hat{E}_{kk}'>0$, and $\xi_{kk'}$ are all real quantities. Furthermore,
let $X_k= \hat{\mit\Psi}_k\,\cos\varphi_k$ and $Y_k= \hat{\mit\Psi}_k\,\sin\varphi_k$. The resonant plasma response model at the 
$k$th resonant surface takes the form
\begin{align}\label{e21}
\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{dX_k}{d\hat{t}} 
+\hat{\varpi}_k\,Y_k\right)= \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,X_{k'}  -\sin\xi_{kk'}\,Y_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\cos\zeta_k,\\[0.5ex]
\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{dY_k}{d\hat{t}} -\hat{\varpi}_k\,X_k\right)
= \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,Y_{k'}
+\sin\xi_{kk'}\,X_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\sin\zeta_k,\label{e22}
\end{align}
where
\begin{align}\label{e23}
{\cal S}_k&=\frac{\tau_R(r_k)}{\tau_A},\\[0.5ex]
\tau_A &= \left[\frac{\mu_0\,\rho(0)\,r_{100}^{\,2}}{B_0^{\,2}}\right]^{1/2},\\[0.5ex]
\tau_R(r) &= \mu_0\,r^{\,2}\,\sigma_{ee}\,Q_{00}^{ee},\\[0.5ex]
\sigma_{ee}(r) &=\frac{n_e\,e^{\,2}\,\tau_{ee}}{m_e},\\[0.5ex]
\hat{W}_k &=\frac{2\,{\cal I}}{\epsilon_{100}\,\hat{r}_k}\left(\frac{q}{g\,s}\right)^{1/2}_{r_k} (X_k^{\,2} + Y_k^{\,2})^{\,1/4},\\[0.5ex]
s(r) &= \frac{d\ln q}{d\ln r},\\[0.5ex]
\hat{\delta}_k &= \frac{\delta_{\rm linear}(r_k)}{R_0\,\epsilon_{100}\,\hat{r}_k}.
\end{align}
Here, ${\cal I}=0.8227$, $\epsilon_{100}=r_{100}/R_0$, $\hat{r}=r/r_{100}$, $\hat{r}_k=r_k/r_{100}$, and $\hat{t}=t/\tau_A$. Furthermore, $\delta_{\rm linear}(r)$ is the linear layer width, whereas $\rho(r)$ is the plasma
mass density profile.

The EPEC resonant plasma response model interpolates smoothly
between the linear regime and the
nonlinear Rutherford regime. The linear regime corresponds to $\hat{W}_k\ll\hat{\delta}_k$, whereas the nonlinear
region corresponds to $\hat{W}_k\gg\hat{\delta}_k$.

\subsection{Linear Layer Width}\label{linear}
Let
\begin{align}
\tau_H(r) &= \frac{R_0}{B_0\,g}\,\frac{\sqrt{\mu_0\,\rho}}{n\,s},\\[0.5ex]
\tau_E(r) &= \frac{r^{\,2}}{D_\perp + (2/3)\,\chi_e},\\[0.5ex]
\tau_M(r) &= \frac{R_0^{\,2}\,q^{\,2}}{\chi_\phi},\\[0.5ex]
\rho_s (r)&= \frac{\sqrt{m_i\,T_e}}{e\,B_0\,g},\\[0.5ex]
\tau(r)& = -\frac{\omega_{\ast\,i}}{\omega_{\ast\,e}},\\[0.5ex]
S(r) &= \frac{\tau_R}{\tau_H},\\[0.5ex]
P_M(r) &= \frac{\tau_R}{\tau_M},\\[0.5ex]
P_E(r) &= \frac{\tau_R}{\tau_E},\\[0.5ex]
D(r)&= \frac{5}{3}\,S^{\,1/3}\,\frac{\rho_s}{r},\\[0.5ex]
Q_E(r)&= S^{\,1/3}\,n\,\omega_E\,\tau_H,\\[0.5ex]
Q_{e,i}(r)&= -S^{\,1/3}\,n\,\omega_{\ast\,e,i}\,\tau_H
\end{align}
Here, $\chi_{e}(r)$ and $D_\perp(r)$ are the perpendicular electron energy and particle diffusivity profiles, respectively. 
The constant-$\psi$ linear layer width is determined from the solution of
\begin{equation}
\frac{d^{\,2}\,Y}{dp^{\,2}} -\left[\frac{-Q_E\,(Q_E-Q_i)+{\rm i}\,(Q_E-Q_i)\,(P_M+P_E)\,p^{\,2}+
P_M\,P_E\,p^{\,4}}
{{\rm i}\,(Q_E-Q_e) +\{P_E + {\rm i}\,(Q_E-Q_i)\,D^{\,2}\}\,p^{\,2}+(1+\tau)\,P_M\,D^{\,2}\,p^{\,4}}
\right] p^{\,2}\, Y = 0.
\end{equation}
If the small-$p$ behavior of solution of the previous equation that is well-behaved as $p\rightarrow \infty$ is
\begin{equation}
Y(p) = Y_0\left[1 - c\,p+{\cal O}(p^{\,2})\right].
\end{equation}
then the 
linear layer width is 
\begin{equation}
\frac{\delta_{\rm linear}}{r} = \frac{\pi\,|c|}{S^{\,1/3}}.
\end{equation}

\section{Plasma Angular Velocity Evolution}\label{a4}
\subsection{Evolution Equations}
The quantity $\hat{\varpi}_k$ that appears in Eqs.~(\ref{e21}) and (\ref{e22}) evolves in time according to
\begin{equation}\label{e19a}
\hat{\varpi}_k(\hat{t})= \hat{\varpi}_{k\,0}-\sum_{k'=1,K}^{p=1,\infty} \frac{m_k}{m_{k'}}\,\frac{y_p(\hat{r}_k)}{y_p(\hat{r}_{k'})}\,\alpha_{k',p}(\hat{t})-\sum_{k'=1,K}^{p=1,\infty}\frac{z_p(\hat{r}_k)}{z_p(\hat{r}_{k'})}\,\beta_{k',p}(\hat{t}),
\end{equation}
Here, $\hat{\varpi}_{k\,0}= \varpi_{k\,0}\,\tau_A$, $y_p(\hat{r})=J_1(j_{1,p}\,\hat{r})/\hat{r}$, and $z_p(\hat{r})=J_0(j_{0,p}\,\hat{r})$. Moreover, $\varpi_{k\,0}$
is the so-called ``natural frequency''  (in the absence of the RMP) at the $k$th resonant surface; this quantity is defined as the helical phase velocity of a naturally unstable island chain, resonant at the surface, in the
absence of an RMP (or any other island chains). Furthermore, $J_m(z)$ is a standard Bessel function, and $j_{m,p}$ denotes the $p$th zero of this function. 
The time evolution equations for the $\alpha_{k,p}$ and $\beta_{k,p}$ parameters specify how the
plasma poloidal and toroidal angular velocity profiles are modified by the electromagnetic torques that develop within the plasma, in response to the applied
RMP, and how these modifications affect the natural frequencies. The evolution equations take the form
\begin{align}
(1+2\,Q_k^{\,2})\,\frac{d\alpha_{k,p}}{d\hat{t}}+ \left(\frac{j_{1,p}^{\,2}}{\hat{\tau}_{M\,k}}+\frac{1}{\hat{\tau}_{\theta\,k}}+\frac{1}{\hat{\tau}_{{\rm cx}\,k}}\right)\alpha_{k,p}&=
\frac{m_k^{\,2}\,[y_p(\hat{r}_k)]^{\,2}}{\hat{\rho}_k\,\epsilon_{100}^{\,2}\,[J_2(j_{1,p})]^{\,2}}\,\delta\hat{T}_k,\\[0.5ex]
\frac{d\beta_{k,p}}{d\hat{t}}+ \left(\frac{j_{0,p}^{\,2}}{\hat{\tau}_{M\,k}}+\frac{1}{\hat{\tau}_{{\rm cx}\,k}}\right)\beta_{k,p}&=
\frac{n^{\,2}\,[z_p(\hat{r}_k)]^{\,2}}{\hat{\rho}_k\,[J_1(j_{0,p})]^{\,2}}\,\delta\hat{T}_k,
\end{align}
where
\begin{equation}\label{e24a}
\delta \hat{T}_k=\sum_{k'=1,K}\hat{E}_{kk'}\,\hat{\mit\Psi}_k\,\hat{\mit\Psi}_{k'}\,\sin(\varphi_k-\varphi_{k'}-\xi_{kk'})+\hat{E}_{kk}\,\hat{\mit\Psi}_k\,\hat{\chi}_k\,\sin(\varphi_k-\zeta_k).
\end{equation}
Here, $Q_k = Q(r_k)$, $\hat{\rho}_k=\rho(r_k)/\rho(0)$, $\hat{\tau}_{M\,k}= r_{100}^{\,2}/[\chi_\phi(r_k)\,\tau_A]$,  $\hat{\tau}_{\theta\,k}=\tau_\theta(r_k)/\tau_A$, $\hat{\tau}_{{\rm cx}\,k} =\tau_{{\rm cx}}(r_k)/\tau_A$. 
Moreover, $\chi_\phi(r)$ is the perpendicular toroidal momentum diffusivity profile, whereas
\begin{equation}\label{a70}
\tau_\theta(r) = \left. \frac{\tau_{ii}}{\mu_{00}^i}\right/\left(1+\frac{q^{\,2}\,R_0^{\,2}}{r^{\,2}\,a_{kk}}\right).
\end{equation}
is the poloidal flow damping timescale, 
and
\begin{equation}
\tau_{\rm cx}(r)=\frac{1}{\langle n_n\rangle\,\langle \sigma\,v\rangle_i^{\rm cx}}
\end{equation}
is the charge exchange damping timescale. 
Furthermore,
\begin{equation}\label{a71}
Q^{\,2}(r) =\frac{q^{\,2}\,R_0^{\,2}}{2\,r^{\,2}}\left.\left(\left\langle\frac{1}{R^{\,2}}\right\rangle-\frac{1}{\langle R^{\,2}\rangle}\right)\right/\left\langle \frac{|\nabla r|^{\,2}}{R^{\,2}}\right\rangle.
\end{equation}

\subsection{Natural Frequencies}
According to linear tearing mode theory, in the absence of the RMP, the natural frequency of the tearing mode resonant at the $k$th resonant surface is given by
\begin{equation}\label{elin}
 \varpi_{{\rm linear}\,k} = - n\,(\omega_E+\omega_{\ast\,e})_{r_k}.
\end{equation}
According to nonlinear tearing mode theory, in the absence of the RMP, 
the natural frequency of the tearing mode resonant at the $k$th resonant surface is given by
\begin{equation}\label{e28y}
 \varpi_{{\rm nonlinear}\,k}=  -n\,(\omega_E+\omega_{\ast\,i}+\omega_{{\rm nc}\,i})_{r_k},
 \end{equation}
where
\begin{equation}\label{a74}
\omega_{{\rm nc}\,i}(r)= -G^{\,ii}_{00}\,\omega_E-\left[L^{\,ii}_{00}-L^{\,ii}_{01}\left(\frac{\eta_i}{1+\eta_i}\right)\right]\omega_{\ast\,i}-
\left[L^{\,iI}_{00}-L^{\,iI}_{01}\left(\frac{\eta_I}{1+\eta_I}\right)\right]\omega_{\ast\,I}.
\end{equation}

Given that our resonant plasma response model interpolates smoothly between the linear regime ($\hat{W}_k\ll \hat{\delta}_k$) and the nonlinear
regime ($\hat{W}_k\gg \hat{\delta}_k$), it makes sense to adopt a model for the natural frequency that does the same. Hence, the EPEC model for the natural frequency is
\begin{equation}\label{ecomp}
\varpi_{k\,0} = \frac{\hat{\delta}_k\,\varpi_{{\rm linear}\,k} +\hat{W}_k\,\varpi_{{\rm nonlinear}\,k}}{\hat{\delta}_k+\hat{W}_k}.
\end{equation}

\section{Pedestal Pressure Reduction} \label{a5}
The full width (in ${\mit\Psi}_N$)  of the magnetic separatrix of the island chain induced at the $k$th resonant surface is
\begin{equation}
W_k = 4\left[\frac{\hat{\mit\Psi}_k}{\sigma_k\,|\hat{{\mit\Psi}}_p(0)|}\right]^{1/2},
\end{equation}
where $\sigma_k=\sigma(r_k)$, $\sigma(r) = d\ln q/d{\mit\Psi}_N$, and $\hat{\mit\Psi}_p(r) = {\mit\Psi}_p/(R_0^{\,2}\,B_0)$.  
However, the halfway point between the inner and outer extremities of the separatrix is located at the flux-surface where ${\mit\Psi}_N = {\mit\Psi}_N(r_k) - A_k\,W_k^{\,2}/8$ and $A_k = [(1/3)\,(d^{\,2}q/d{\mit\Psi}_N^{\,2})/(dq/d{\mit\Psi}_N)]_{r_k}$.
On average, the presence of a magnetic island chain of full width $W_k$ at the $k$th resonant surface
causes the electron temperature, ion temperature,  and electron number density profiles to be flattened in  annular regions, centered on the
halfway points between the inner and outer radii of the island separatrices, of widths (in ${\mit\Psi}_N$)
\begin{align}
\delta_{T_e\,k}& = \frac{2}{\pi}\,W_k\,\tanh\left(\frac{W_k}{W_{T_e\,k}}\right),\\[0.5ex]
\delta_{T_i\,k}& = \frac{2}{\pi}\,W_k\,\tanh\left(\frac{W_k}{W_{T_i\,k}}\right),\\[0.5ex]
\delta_{n_e\,k}& = \frac{2}{\pi}\,W_k\,\tanh\left(\frac{W_k}{W_{n_e\,k}}\right),
\end{align}
respectively, where
\begin{align}
W_{T_e\,k} &= \left(\frac{\chi_{e}}{v_{T\,e}\,R_0}\,\frac{f^{\,2}}{n\,\sigma\,|\hat{\mit\Psi}_p(0)|^{\,2}}\right)^{1/3}_{r_k},\\[0.5ex]
W_{T_i\,k} &= \left(\frac{\chi_{i}}{v_{T\,i}\,R_0}\,\frac{f^{\,2}}{n\,\sigma\,|\hat{\mit\Psi}_p(0)|^{\,2}}\right)^{1/3}_{r_k},\\[0.5ex]
W_{n_e\,k} &= \left(\frac{D_\perp}{v_{T\,i}\,R_0}\,\frac{f^{\,2}}{n\,\sigma\,|\hat{\mit\Psi}_p(0)|^{\,2}}\right)^{1/3}_{r_k}.
\end{align}
Here, $\chi_i(r)$ is the perpendicular  ion energy diffusivity profile.

The total change in the plasma pressure interior to the innermost resonant surface due to the temperature and
density flattening at the various resonant surfaces (assuming that the pressure at the LCFS is fixed) is
\begin{align}
{\mit\Delta}P &=\sum_{k=1,K} 
\left\{\left[\delta_{n_e\,k}\,\frac{dn_e}{d{\mit\Psi}_N}\,T_e- \delta_{n_e\,k}\,W_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+\frac{d^{\,2}n_e}{d{\mit\Psi}_n^{\,2}}\,T_e\right)
+ \delta_{n_e\,k}^{\,3}\,\frac{d^{\,3}n_e}{d{\mit\Psi}_N^{\,3}}\,\frac{T_e}{24}\right]\right.
\nonumber\\[0.5ex]
&\phantom{++++}+\left[\delta_{T_e\,k}\,n_e\,\frac{dT_e}{d{\mit\Psi}_N}- \delta_{T_e\,k}\,W_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+
 n_e\,\frac{d^{\,2}T_e}{d{\mit\Psi}_n^{\,2}}\right)
+ \delta_{T_e\,k}^{\,3}\,\frac{n_e}{24}\,\frac{d^{\,3}T_e}{d{\mit\Psi}_N^{\,3}}\right]\nonumber\\[0.5ex]
&\phantom{++++}+\left[\delta_{n_e\,k}\,\frac{dn_i}{d{\mit\Psi}_N}\,T_i- \delta_{n_e\,k}\,W_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}n_i}{d{\mit\Psi}_n^{\,2}}
\,T_i\right)+ \delta_{n_e\,k}^{\,3}\,\frac{d^{\,3}n_i}{d{\mit\Psi}_N^{\,3}}\,\frac{T_i}{24}\right]
\nonumber\\[0.5ex]
&\phantom{++++}\left.+\left[\delta_{T_i\,k}\,n_i\,\frac{dT_i}{d{\mit\Psi}_N}- \delta_{T_i\,k}\,W_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+n_i\,\frac{d^{\,2}T_i}{d{\mit\Psi}_n^{\,2}}\right)
+ \delta_{T_i\,k}^{\,3}\,\frac{n_i}{24}\,\frac{d^{\,3}T_i}{d{\mit\Psi}_N^{\,3}}\right]\right\}_{r_k}.
\end{align}
where
we have neglected the impurity ion pressure.

\end{document}

### 2021-06-28 Neoclassical/Source/Neoclassical.h

@@ -63,6 +63,7 @@
 // 1.21 - Use more accurate expression for neoclassical flow damping time
 // 1.22 - Added more accurate calculation of linear layer width
 // 1.23 - Added C1 and C2
+// 1.24 - Added change exchange to angular velocity evolution equations
 
 // ################################################################
 
@@ -70,7 +71,7 @@
 #define NEOCLASSICAL
 
 #define VERSION_MAJOR 1
-#define VERSION_MINOR 23
+#define VERSION_MINOR 24
 
 #include <stdio.h>
 #include <math.h>
@@ -354,6 +355,7 @@ class Neoclassical
   Array<double,1> tau_Rk;     // Classical resistive timescales (s)
   Array<double,1> tau_Mk;     // Momentum confinement timescales (s)
   Array<double,1> tau_thk;    // Poloidal flow damping timescales (s)
+  Array<double,1> tau_cxk;    // Charge exchange damping timescales (s)
 
   Array<double,1> Sk;         // Lundquist number   
   Array<double,1> tauk;       // Ratio of diamagnetic frequencies

### 2021-06-29 Flux/Source/Flux.h
Trying to add E, F, H to FLUX

@@ -213,6 +213,7 @@ class Flux
   double* PPP;         // dP/dPsi
   double* S;           // sqrt(1 - Psi)
   double* QX;          // q(Psi) from gFile
+  double* J0;          // GGJ integral
 
   double* PsiN;        // PsiN array
   double* QPN;         // dQ/dPsiN array
@@ -254,6 +255,7 @@ class Flux
   gsl_matrix* Znc;     // Z versus Theta on rational surfaces
   gsl_matrix* Bnc;     // B versus Theta on rational surfaces
   gsl_matrix* Cnc;     // dB/dTheta versus Theta on rational surfaces
+  gsl_matrix* Pnc;     // |Grad psi|^2 versus Theta on rational surfaces 
 
   // Neoclassical parameter data
   double*     I1;      // Neoclassical integral
@@ -264,6 +266,17 @@ class Flux
   gsl_matrix* I6;      // Neoclassical integrals
   double*     I7;      // Neoclassical integral
   double*     I8;      // Neoclassical integral
+
+  // Glasser-Greene-Johnson data
+  double* J1;          // GGJ integral
+  double* J2;          // GGJ integral
+  double* J3;          // GGJ integral
+  double* J4;          // GGJ integral
+  double* J5;          // GGJ integral
+  double* J6;          // GGJ integral
+  double* E;           // GGJ index
+  double* F;           // GGJ index
+  double* H;           // GGJ index
 
   // Perturbed equilibrium data
   gsl_matrix_complex* FF;  // F-matrix

### 2021-06-29 Neoclassical/Source/Neoclassical.cpp

@@ -994,7 +994,7 @@ void Neoclassical::Get_Parameters ()
   L_ii_00.resize (nres); L_ii_01.resize (nres); L_iI_00.resize (nres);
   L_iI_01.resize (nres); L_Ii_00.resize (nres); L_Ii_01.resize (nres);
   L_II_00.resize (nres); L_II_01.resize (nres); G_ii_00.resize (nres);
-  G_Ii_00.resize (nres); Q_00.resize    (nres); P_ei_00.resize (nres);
+  G_Ii_00.resize (nres); Q_00.resize    (nres); G_ei_00.resize (nres);
   L_ee_00.resize (nres); L_ee_01.resize (nres); L_ei_00.resize (nres);
   L_ei_01.resize (nres); L_eI_00.resize (nres); L_eI_01.resize (nres);
  
@@ -1128,7 +1128,7 @@ void Neoclassical::Get_Parameters ()
       gsl_matrix* Fee = gsl_matrix_alloc (2, 2);
       gsl_matrix* Fei = gsl_matrix_alloc (2, 2);
       gsl_matrix* FeI = gsl_matrix_alloc (2, 2);
-      gsl_matrix* Pei = gsl_matrix_alloc (2, 2);
+      gsl_matrix* Gei = gsl_matrix_alloc (2, 2);
       gsl_matrix* Lee = gsl_matrix_alloc (2, 2);
       gsl_matrix* Lei = gsl_matrix_alloc (2, 2);
       gsl_matrix* LeI = gsl_matrix_alloc (2, 2);
@@ -1170,7 +1170,7 @@ void Neoclassical::Get_Parameters ()
       Matrix_Mult (Fei,   Gii,   Temp1, 2);
       Matrix_Mult (FeI,   GIi,   Temp2, 2);
       Matrix_Add  (Temp1, Temp2, Temp3, 2);
-      Matrix_Mult (Q,     Temp3, Pei,   2);
+      Matrix_Mult (Q,     Temp3, Gei,   2);
 
       Matrix_Mult (Q, Fee, Lee, 2);
 
@@ -1186,7 +1186,7 @@ void Neoclassical::Get_Parameters ()
       Matrix_Add  (Temp2, Temp3, Temp1, 2);
       Matrix_Mult (Q,     Temp1, LeI,   2);
 
[…]

### 2021-07-11 Documentation/EPEC_Model.tex
Updated FLUX documentation
Added bootstrap terms

@@
-\documentclass[12pt,prb,aps]{revtex4-2}
+\documentclass[notitlepage,12pt,prb,aps]{revtex4-1}
 \usepackage {amsmath}
@@
 \affiliation{Institute for Fusion Studies,  Department of Physics,  University of Texas at Austin,  Austin TX 78712, USA}
-
+\date{\today}
 \maketitle
@@
 \begin{align}
- G(R_k,Z_k;R_{k'},Z_{k'})&= \frac{(-1)^{\,n}\,\pi^{\,2}\,R_k\,R_{k'}/R_0}{2\,\Gamma(1/2)\,\Gamma(n+1/2)}
+ G(R_k,Z_k;R_{k'},Z_{k'})&= \frac{(-1)^{\,n}\,\pi^{\,2}\,R_k\,R_{k'}/R_0}{2\,{\mit\Gamma}(1/2)\,{\mit\Gamma}(n+1/2)}
 \left[\frac{\cosh\eta_{kk'}}{R_k^{\,2}+R_{k'}^{\,2}+(Z_k-Z_{k'})^{\,2}}\right]^{1/2}\nonumber\\[0.5ex]
@@
 flux coordinates $r_{k'}$, $\theta_{k'}$, $0$, with $r_{k'}$ constant; resonant poloidal mode number $m_{k'}$).
-Finally, the $\Gamma(z)$ and $P_\mu^{\,\nu}(z)$ are Gamma functions and associated Legendre functions, respectively.
+Finally, the ${\mit\Gamma}(z)$ and $P_\mu^{\,\nu}(z)$ are gamma functions and associated Legendre functions, respectively.
 
@@
 and
-$n_I/n_e= (Z_{\rm eff}-1)/[Z_I\,(Z_I-1)]$.
+$n_I/n_e= (Z_{\rm eff}-1)/[Z_I\,(Z_I-1)]$. Finally, let $Z_{{\rm eff}\,i}= (Z_I-Z_{\rm eff})/(Z_I-1)$, and
+$Z_{{\rm eff}\,I}=Z_I\,(Z_{\rm eff}-1)/(Z_I-1)$. Note that $Z_{\rm eff}= Z_{{\rm eff}\,i}+ Z_{{\rm eff}\,I}$.
 
@@
 
-The $2\times 2$ dimensionless electron collisional friction matrix, $[F^{\,ee}](r)$,   is defined to have the following elements:
+The $2\times 2$ dimensionless electron collisional friction matrices, $[F^{\,ee}](r)$,   $[F^{\,ei}](r)$, and
+$[F^{\,eI}](r)$, are defined to have the following elements:
 $F^{\,ee}_{00} = Z_{\rm eff}$,
@@
 $F^{\,ee}_{10} = F^{\,ee}_{01}$,
-$F^{\,ee}_{11}= \sqrt{2} + (13/4)\,Z_{\rm eff}$.
+$F^{\,ee}_{11}= \sqrt{2} + (13/4)\,Z_{\rm eff}$, $F^{\,ei}_{00} = Z_{{\rm eff}\,i}$,
+$F^{\,ei}_{01} =F^{\,ei}_{11}=0$, $F^{\,ei}_{10}=(3/2)\,Z_{{\rm eff}\,i}$,  $F^{\,eI}_{00} = Z_{{\rm eff}\,I}$,
+$F^{\,eI}_{01} =F^{\,eI}_{11}=0$, $F^{\,eI}_{10}=(3/2)\,Z_{{\rm eff}\,I}$.
 
@@
 \end{align}
-and the $2\times 2$ dimensionless electron matrix, $[Q^{\,ee}](r)$, 
+and the $2\times 2$ dimensionless electron matrices, $[Q^{\,ee}](r)$, $[G^{\,ei}](r)$, $[L^{\,ee}](r)$, $[L^{\,ei}](r)$, 
+and $[L^{\,eI}](r)$, 
 where
-$[Q^{\,ee}]= [F^{\,ee}+\mu^{\,e}]^{\,-1}$.
+\begin{align}
+[Q^{\,ee}]&= [F^{\,ee}+\mu^{\,e}]^{\,-1},\\[0.5ex]
+[G^{\,ei}] &= [Q^{\,ee}]\,([F^{\,ei}]\,[G^{\,ii}]+ [F^{\,eI}]\,[G^{\,Ii}]),\\[0.5ex]
+[L^{\,ee}] &= [Q^{\,ee}]\,[F^{\,ee}],\\[0.5ex]
+[L^{\,ei}] &= [Q^{\,ee}]\left\{[F^{\,ei}\,]\,[L^{\,ii}]-[F^{\,ei}]+[F^{\,eI}]\,[L^{\,Ii}]\right\},\\[0.5ex]
+[L^{\,eI}] &= [Q^{\,ee}]\left\{[F^{\,eI}]\,[L^{\,II}]-[F^{\,eI}]+[F^{\,ei}]\,[L^{\,iI}]\right\}.
+\end{align}
 Here,
@@
 
+\subsection{Neoclassical Frequencies}
+The neoclassical frequencies of the three plasma species have the following definitions:
+\begin{align}
+\omega_{{\rm nc}\,i}(r)&=-G_{00}^{\,ii}\,\omega_E -\left[L^{\,ii}_{00}-L^{\,ii}_{01}\left(\frac{\eta_i}{1+\eta_i}\right)\right]\omega_{\ast\,i}-
+\left[L^{\,iI}_{00}-L^{\,iI}_{01}\left(\frac{\eta_I}{1+\eta_I}\right)\right]\omega_{\ast\,I},\\[0.5ex]
+\omega_{{\rm nc}\,I}(r)&=-G_{00}^{\,Ii}\,\omega_E -\left[L^{\,II}_{00}-L^{\,II}_{01}\left(\frac{\eta_I}{1+\eta_I}\right)\right]\omega_{\ast\,I}-
+\left[L^{\,Ii}_{00}-L^{\,Ii}_{01}\left(\frac{\eta_i}{1+\eta_i}\right)\right]\omega_{\ast\,i},\\[0.5ex]
+\omega_{{\rm nc}\,e}(r)&=-G_{00}^{\,ei}\,\omega_E -\left[L^{\,ee}_{00}-L^{\,ee}_{01}\left(\frac{\eta_e}{1+\eta_e}\right)\right]\omega_{\ast\,e}-
+\left[L^{\,ei}_{00}-L^{\,ei}_{01}\left(\frac{\eta_i}{1+\eta_i}\right)\right]\omega_{\ast\,i}\nonumber\\[0.5ex]
+&\phantom{=}-
+\left[L^{\,eI}_{00}-L^{\,eI}_{01}\left(\frac{\eta_I}{1+\eta_I}\right)\right]\omega_{\ast\,I}.
+\end{align}
+Here,
+\begin{align}
+\omega_E(r) &=-\frac{d{\mit\Phi}}{d{\mit\Psi}_p},\\[0.5ex]
+\omega_{\ast\,a}(r) &= -\frac{T_a}{e_a}\,\frac{d\ln p_a}{d{\mit\Psi}_p},\\[0.5ex]
+\eta_a(r) &= \frac{d\ln T_a}{d\ln n_a}.
+\end{align}
+Moreover, $p_a(r)=n_a\,T_a$, and ${\mit\Phi}(r)$ is the equilibrium electric scalar potential.
+
 \subsection{Impurity Ion Angular Rotation Velocities}\label{srotation}
@@
 \end{align}
-where ${\bf V}^{\,I}$ is the impurity ion fluid velocity, and the right-hand sides are evaluated on the outboard mid-plane. According to neoclassical theory
+where ${\bf V}^{\,I}$ is the impurity ion fluid velocity, and the right-hand sides are evaluated on the outboard mid-plane. According to neoclassical theory,
 \begin{align}
@@
 \begin{equation}
-K_\theta(r) = \frac{R_0^{\,2}\,B_0^{\,2}\,g^{\,2}}{R^{\,2}\,\langle B^{\,2}\rangle},
+K_\theta(r) = \frac{R_0^{\,2}\,B_0^{\,2}\,g^{\,2}}{R^{\,2}\,\langle B^{\,2}\rangle}.
 \end{equation}
-\begin{align}
-\omega_E(r) &=-\frac{d{\mit\Phi}}{d{\mit\Psi}_p},\\[0.5ex]
-\omega_{\ast\,a}(r) &= -\frac{T_a}{e_a}\,\frac{d\ln p_a}{d{\mit\Psi}_p},\\[0.5ex]
-\eta_a(r) &= \frac{d\ln T_a}{d\ln n_a}.
-\end{align}
-and 
-\begin{align}\label{a53}
-\omega_{{\rm nc}\,I}(r)&=-G_{00}^{\,Ii}\,\omega_E -\left[L^{\,II}_{00}-L^{\,II}_{01}\left(\frac{\eta_I}{1+\eta_I}\right)\right]\omega_{\ast\,I}-
-\left[L^{\,Ii}_{00}-L^{\,Ii}_{01}\left(\frac{\eta_i}{1+\eta_i}\right)\right]\omega_{\ast\,i}.
-\end{align}
-Here, $p_a(r)=n_a\,T_a$, and ${\mit\Phi}(r)$ is the equilibrium electric scalar potential.
 
@@
 \begin{align}\label{e21}
-\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{dX_k}{d\hat{t}} 
-+\hat{\varpi}_k\,Y_k\right)= \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,X_{k'}  -\sin\xi_{kk'}\,Y_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\cos\zeta_k,\\[0.5ex]
-\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{dY_k}{d\hat{t}} -\hat{\varpi}_k\,X_k\right)
+&\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{dX_k}{d\hat{t}} 
++\hat{\varpi}_k\,Y_k\right)= \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,X_{k'}  -\sin\xi_{kk'}\,Y_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\cos\zeta_k\nonumber\\[0.5ex]&\phantom{=====} +\frac{\alpha_{b\,e\,k}}{\hat{W}_k}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_{e}\,k}\,\hat{W}_{n_e\,k}+\hat{\rho}_{\theta_e}^{\,2}+W_k^{\,2}}\right)X_k+\frac{\alpha_{b\,i\,k}}{\hat{W}_k}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_{i}\,k}\,\hat{W}_{n_e\,k}+\hat{\rho}_{\theta_i}^{\,2}+\hat{W}_k^{\,2}}\right)X_k\nonumber\\[0.5ex]
+&\phantom{=====}+\frac{\alpha_{c\,k}}{\hat{W}_k}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{n_e\,k}^{\,2}+\hat{W}_k^{\,2}}\right)X_k+\frac{\alpha_{p\,k}}{\hat{W}_k^{\,3}}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_{i}\,k}\,\hat{W}_{n_e\,k}+\hat{W}_k^{\,2}}\right)^2 X_k,\\[0.5ex]
+&\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{dY_k}{d\hat{t}} -\hat{\varpi}_k\,X_k\right)
 = \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,Y_{k'}
-+\sin\xi_{kk'}\,X_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\sin\zeta_k,\label{e22}
++\sin\xi_{kk'}\,X_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\sin\zeta_k\nonumber\\[0.5ex]&\phantom{=====} +\frac{\alpha_{b\,e\,k}}{\hat{W}_k}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_{e}\,k}\,\hat{W}_{n_e\,k}+\hat{\rho}_{\theta_e}^{\,2}+\hat{W}_k^{\,2}}\right)Y_k+\frac{\alpha_{b\,i\,k}}{\hat{W}_k}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_{i}\,k}\,\hat{W}_{n_e\,k}+\hat{\rho}_{\theta_i}^{\,2}+\hat{W}_k^{\,2}}\right)Y_k\nonumber\\[0.5ex]
+&\phantom{=====}+\frac{\alpha_{c\,k}}{\hat{W}_k}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{n_e\,k}^{\,2}+\hat{W}_k^{\,2}}\right)Y_k+\frac{\alpha_{p\,k}}{\hat{W}_k^{\,3}}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_{i}\,k}\,\hat{W}_{n_e\,k}+\hat{W}_k^{\,2}}\right)^2 Y_k,\label{e22}
 \end{align}
@@
 \hat{W}_k &=\frac{2\,{\cal I}}{\epsilon_{100}\,\hat{r}_k}\left(\frac{q}{g\,s}\right)^{1/2}_{r_k} (X_k^{\,2} + Y_k^{\,2})^{\,1/4},\\[0.5ex]
+\hat{W}_{T_e\,k} &= 2\,{\cal I}\left(\frac{\chi_e\,R_0}{v_{T\,e}\,r^{\,2}\,s\,n}\right)^{1/3}_{r_k},\\[0.5ex]
+\hat{W}_{T_i\,k} &= 2\,{\cal I}\left(\frac{\chi_i\,R_0}{v_{T\,e}\,r^{\,2}\,s\,n}\right)^{1/3}_{r_k},\\[0.5ex]
+\hat{W}_{n_e\,k} &= 2\,{\cal I}\left(\frac{D_\perp\,R_0}{v_{T\,e}\,r^{\,2}\,s\,n}\right)^{1/3}_{r_k},\\[0.5ex]
 s(r) &= \frac{d\ln q}{d\ln r},\\[0.5ex]
-\hat{\delta}_k &= \frac{\delta_{\rm linear}(r_k)}{R_0\,\epsilon_{100}\,\hat{r}_k}.
+\hat{\rho}_{\theta\,e} &= \left(\frac{2\,{\cal I}\,v_{T\,e}\,m_e\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},\\[0.5ex]
+\hat{\rho}_{\theta\,i} &= \left(\frac{2\,{\cal I}\,v_{T\,i}\,m_i\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},\\[0.5ex]
+\hat{\delta}_k &= \frac{\delta_{\rm linear}(r_k)}{R_0\,\epsilon_{100}\,\hat{r}_k},\\[0.5ex]
+\alpha_{b\,e\,k} &= -2\,{\cal I}\,I_g\left(\frac{\omega_{\ast\,e}+\omega_{{\rm nc}\,e}}{\omega_\beta}\right)_{r_k},\\[0.5ex]
+\alpha_{b\,i\,k} &= 2\,{\cal I}\,I_g\left[\frac{(n_i/n_e)\left(\omega_{\ast\,i}+\omega_{{\rm nc}\,i}\right)+(Z_I\,n_I/n_e)\left(\omega_{\ast\,I}+\omega_{{\rm nc}\,I}\right)}{\omega_\beta}\right]_{r_k},\\[0.5ex]
+\alpha_{c\,k} &= 2\,{\cal I}\,I_g\,D_R(r_k),\\[0.5ex]
+\alpha_{p\,k} &= 8\,{\cal I}^{\,3}\, I_p\left[\frac{(\omega_{\ast\,i}+\omega_{{\rm nc}\,i})\,\omega_{{\rm nc}\,i}}{\omega_\beta\,\omega_{\mit\Omega}}\right]_{r_k},\\[0.5ex]
+\omega_{\beta}(r)&= \frac{s\,g\,B_0}{\mu_0\,n_e\,e\,R_0^{\,2}\,q},\\[0.5ex]
+\omega_{\mit\Omega}(r)&= \frac{e\,g\,B_0\,s\,q}{m_i}.
 \end{align}
-Here, ${\cal I}=0.8227$, $\epsilon_{100}=r_{100}/R_0$, $\hat{r}=r/r_{100}$, $\hat{r}_k=r_k/r_{100}$, and $\hat{t}=t/\tau_A$.
+Here, ${\cal I}=0.8227$, $I_g=1.58$, $I_p=1.38$, $\epsilon_{100}=r_{100}/R_0$, $\hat{r}=r/r_{100}$, $\hat{r}_k=r_k/r_{100}$, and $\hat{t}=t/\tau_A$.
 Furthermore, $\delta_{\rm linear}(r)$ is the linear layer width, whereas $\rho(r)$ is the plasma
-mass density profile.
+mass density profile. Moreover, $\chi_e(r)$, $\chi_i(r)$, and $D_\perp(r)$ are the perpendicular electron
+energy, ion energy, and particle diffusivity profile, respectively.
 
@@
 \end{align}
-Here, $\chi_{e}(r)$ and $D_\perp(r)$ are the perpendicular electron energy and particle diffusivity profiles, respectively. 
 The constant-$\psi$ linear layer width is determined from the solution of
@@
 \begin{equation}\label{e28y}
- \varpi_{{\rm nonlinear}\,k}=  -n\,(\omega_E+\omega_{\ast\,i}+\omega_{{\rm nc}\,i})_{r_k},
- \end{equation}
-where
-\begin{equation}\label{a74}
-\omega_{{\rm nc}\,i}(r)= -G^{\,ii}_{00}\,\omega_E-\left[L^{\,ii}_{00}-L^{\,ii}_{01}\left(\frac{\eta_i}{1+\eta_i}\right)\right]\omega_{\ast\,i}-
-\left[L^{\,iI}_{00}-L^{\,iI}_{01}\left(\frac{\eta_I}{1+\eta_I}\right)\right]\omega_{\ast\,I}.
+ \varpi_{{\rm nonlinear}\,k}=  -n\,(\omega_E+\omega_{\ast\,i}+\omega_{{\rm nc}\,i})_{r_k}.
  \end{equation}
@@
 
-\section{Pedestal Pressure Reduction} \label{a5}
+\section{Pressure Reduction} \label{a5}
 The full width (in ${\mit\Psi}_N$)  of the magnetic separatrix of the island chain induced at the $k$th resonant surface is
@@
 \end{align}
-Here, $\chi_i(r)$ is the perpendicular  ion energy diffusivity profile.
 
-The total change in the plasma pressure interior to the innermost resonant surface due to the temperature and
+The total change in the plasma pressure interior to the $j$th resonant surface due to the temperature and
 density flattening at the various resonant surfaces (assuming that the pressure at the LCFS is fixed) is
 \begin{align}
-{\mit\Delta}P &=\sum_{k=1,K} 
+{\mit\Delta}P_j &=\sum_{k=j,K} 
 \left\{\left[\delta_{n_e\,k}\,\frac{dn_e}{d{\mit\Psi}_N}\,T_e- \delta_{n_e\,k}\,W_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+\frac{d^{\,2}n_e}{d{\mit\Psi}_n^{\,2}}\,T_e\right)
@@
 \nonumber\\[0.5ex]
-&\phantom{++++}+\left[\delta_{T_e\,k}\,n_e\,\frac{dT_e}{d{\mit\Psi}_N}- \delta_{T_e\,k}\,W_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+
+&\phantom{++}+\left[\delta_{T_e\,k}\,n_e\,\frac{dT_e}{d{\mit\Psi}_N}- \delta_{T_e\,k}\,W_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+
  n_e\,\frac{d^{\,2}T_e}{d{\mit\Psi}_n^{\,2}}\right)
 + \delta_{T_e\,k}^{\,3}\,\frac{n_e}{24}\,\frac{d^{\,3}T_e}{d{\mit\Psi}_N^{\,3}}\right]\nonumber\\[0.5ex]
-&\phantom{++++}+\left[\delta_{n_e\,k}\,\frac{dn_i}{d{\mit\Psi}_N}\,T_i- \delta_{n_e\,k}\,W_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}n_i}{d{\mit\Psi}_n^{\,2}}
+&\phantom{++}+\left[\delta_{n_e\,k}\,\frac{dn_i}{d{\mit\Psi}_N}\,T_i- \delta_{n_e\,k}\,W_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}n_i}{d{\mit\Psi}_n^{\,2}}
 \,T_i\right)+ \delta_{n_e\,k}^{\,3}\,\frac{d^{\,3}n_i}{d{\mit\Psi}_N^{\,3}}\,\frac{T_i}{24}\right]
 \nonumber\\[0.5ex]
-&\phantom{++++}\left.+\left[\delta_{T_i\,k}\,n_i\,\frac{dT_i}{d{\mit\Psi}_N}- \delta_{T_i\,k}\,W_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+n_i\,\frac{d^{\,2}T_i}{d{\mit\Psi}_n^{\,2}}\right)
+&\phantom{++}\left.+\left[\delta_{T_i\,k}\,n_i\,\frac{dT_i}{d{\mit\Psi}_N}- \delta_{T_i\,k}\,W_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+n_i\,\frac{d^{\,2}T_i}{d{\mit\Psi}_n^{\,2}}\right)
 + \delta_{T_i\,k}^{\,3}\,\frac{n_i}{24}\,\frac{d^{\,3}T_i}{d{\mit\Psi}_N^{\,3}}\right]\right\}_{r_k}.

### 2021-07-11 Flux/Source/Stage2.cpp

@@ -103,7 +103,7 @@ void Flux::Stage2 ()
 		 1. - P[j], rP[j] /ra, - ra * Interpolate (NPSI, rP, P, rP[j], 1));
       for (int i = 0; i < nres; i++)
 	fprintf (file, "%d %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e\n",
-		 mres[i], rres[i]/ra, sres[i], gres[i], gmres[i], Ktres[i], Kares[i], fcres[i], ajj[i], PsiNres[i], dPsidr[i], Khres[i], A1res[i], A2res[i], q_hat[i], C1res[i], C2res[i], E[i]+F[i]+H[i]*H[i]);
+		 mres[i], rres[i]/ra, sres[i], gres[i], gmres[i], Ktres[i], Kares[i], fcres[i], ajj[i], PsiNres[i], dPsidr[i], Khres[i], A1res[i], A2res[i], q_hat[i], C1res[i], C2res[i], E[i]+F[i]);
       for (int i = 0; i < nres; i++)
 	for (int j = 0; j < nres; j++)
 	  fprintf (file, "%d %d %16.9e %16.9e\n", i, j,
@@ -813,8 +813,8 @@ void Flux::Stage2CalcGGJ ()
     }
 
   for (int i = 0; i < nres; i++)
-    printf ("mpol = %3d J1 = %10.3e J2 = %10.3e J3 = %10.3e J4 = %10.4e J5 = %10.4e J6 = %10.4e E = %10.4e F = %10.4e H = %10.4e DI = %10.4e DR = %10.4e\n",
-	    mres[i], J1[i], J2[i], J3[i], J4[i], J5[i], J6[i], E[i], F[i], H[i], E[i]+F[i]+H[i]-0.25, E[i]+F[i]+H[i]*H[i]);
+    printf ("mpol = %3d J1 = %10.3e J2 = %10.3e J3 = %10.3e J4 = %10.4e J5 = %10.4e J6 = %10.4e E = %10.4e F = %10.4e H = %10.4e DI = %10.4e DR_ln = %10.4e DR_nl = %10.4e\n",
[…]

### 2021-07-11 IslandDynamics/Source/NamelistRead.f90

@@ -6,7 +6,8 @@
 
 subroutine NameListRead (PHASE_MID, PHASE_COPT, PHASE_CORE, PHASE_LIN,&
      PHASE_FREQ, PHASE_FFAC, PHASE_HIGH, PHASE_RATS, PHASE_NATS, PHASE_SCALE,&
-     PHASE_CHIR, PHASE_CXD, PHASE_BSC, RESTART, TSTART, TEND, DT)&
+     PHASE_CHIR, PHASE_CXD, PHASE_BOOT, PHASE_CURV, PHASE_POLZ,&
+     RESTART, TSTART, TEND, DT)&
      bind (c, name = 'NameListRead')
 
   use, intrinsic :: iso_c_binding, only: c_int, c_double
@@ -20,7 +21,9 @@ subroutine NameListRead (PHASE_MID, PHASE_COPT, PHASE_CORE, PHASE_LIN,&
   integer (kind = c_int),    intent (inout) :: PHASE_RATS
   integer (kind = c_int),    intent (inout) :: PHASE_NATS
   integer (kind = c_int),    intent (inout) :: PHASE_CXD
-  integer (kind = c_int),    intent (inout) :: PHASE_BSC
+  integer (kind = c_int),    intent (inout) :: PHASE_BOOT
+  integer (kind = c_int),    intent (inout) :: PHASE_CURV
+  integer (kind = c_int),    intent (inout) :: PHASE_POLZ
   real    (kind = c_double), intent (inout) :: PHASE_FFAC
   real    (kind = c_double), intent (inout) :: PHASE_SCALE
   real    (kind = c_double), intent (inout) :: PHASE_CHIR
@@ -32,7 +35,8 @@ subroutine NameListRead (PHASE_MID, PHASE_COPT, PHASE_CORE, PHASE_LIN,&
   
   namelist /ISLANDDYNAMICS_CONTROL/ PHASE_MID, PHASE_COPT, PHASE_CORE, PHASE_LIN,&
        PHASE_FREQ, PHASE_FFAC, PHASE_HIGH, PHASE_RATS, PHASE_NATS, PHASE_SCALE,&
-       PHASE_CHIR, PHASE_CXD, PHASE_BSC, RESTART, TSTART, TEND, DT
+       PHASE_CHIR, PHASE_CXD, PHASE_BOOT, PHASE_CURV, PHASE_POLZ,&
+       RESTART, TSTART, TEND, DT
   
[…]

### 2021-07-21 Phase/Source/Phase.cpp
Minor improvements

@@ -803,7 +803,9 @@ void Phase::Read_Data (int _STAGE5, int _INTF, int _INTN, int _INTU, int _NATS, 
   printf ("Reading data from program GPEC:\n");
   printf ("...............................\n");
   
-  char    line[MAXULFILELINELENGTH]; char line1[MAXULFILELINELENGTH];
+  char    line[MAXULFILELINELENGTH];
+  char    line1[MAXULFILELINELENGTH];
+  char    line0[MAXULFILELINELENGTH];
   double  v1, v2, v3, v4, v5, v6, v7, v8, v9, v10, v11, v12;
   double* QIN = new double[nres];
   double* PSI = new double[nres];
@@ -826,8 +828,9 @@ void Phase::Read_Data (int _STAGE5, int _INTF, int _INTN, int _INTU, int _NATS, 
     {
       printf ("Middle coil:\n");
       file = OpenFiler ((char*) "Inputs/mFile");
-      
-      for (int i = 0; i < 5; i++)
+
+      fgets (line0, MAXULFILELINELENGTH, file);
+      for (int i = 0; i < 4; i++)
 	fgets (line, MAXULFILELINELENGTH, file);
       fgets (line1, MAXULFILELINELENGTH, file);
       for (int i = 0; i < 2; i++)
@@ -864,9 +867,17 @@ void Phase::Read_Data (int _STAGE5, int _INTF, int _INTN, int _INTU, int _NATS, 
 	    DRE[i] = v9;
 	    DIM[i] = v10;
 	    WWW[i] = 2.*v11;
-	    
-	    DRE[i] /= 2.*M_PI * qk (i) /SCALEFACTOR/SCALEFACTOR;
-	    DIM[i] /= 2.*M_PI * qk (i) /SCALEFACTOR/SCALEFACTOR;
+
+	    if (strstr (line0, "GPEC") != NULL)
+	      {
+		DRE[i] /= 2.*M_PI * qk(i) /SCALEFACTOR/SCALEFACTOR;
+		DIM[i] /= 2.*M_PI * qk(i) /SCALEFACTOR/SCALEFACTOR;
+	      }
+	    else
+	      {
[…]

### 2021-08-18 Flux/Plots/Stage1Equilibrium.py
Streamlining NEOCLASSICAL for OMFIT

@@ -28,6 +28,7 @@ zhi = para[5]
 rax = para[6]
 zax = para[7]
 pax = para[8]
+pab = para[9]
 
 aspect = (zhi - zlow) / (rrgt - rlft)
 
@@ -36,7 +37,7 @@ fig.canvas.manager.set_window_title("FLUX: Stage1 Equilibrium")
 
 XX, YY = np.meshgrid(r, z, indexing='ij')
 ZZ = np.asarray(psi)
-levels = np.linspace(pax, 0.0, 40)
+levels = np.linspace(pax, pab, 40)
 
 plt.contour(XX, YY, ZZ, levels)
 

### 2021-08-18 Flux/Source/gFileRead.f90

@@ -40,11 +40,11 @@ subroutine gFileRead () bind (c, name = 'gFileRead')
   character (len = *), parameter :: file = "Outputs/Stage1.nc"
 
   integer          :: err = 0, file_id
-  integer          :: para_d_id, para_id, NPARA = 9, bound_d_id, rbound_id, zbound_id
+  integer          :: para_d_id, para_id, NPARA = 10, bound_d_id, rbound_id, zbound_id
   integer          :: lim_d_id, rlim_id, zlim_id, R_d_id, R_id, Z_d_id, Z_id
   integer          :: PS_d_id (2), PS_id, PN_id, T_id, P_id, TTp_id, Pp_id, Q_id, C_id
   integer          :: xt_id, xp_id, xttp_id, xpp_id, xq_id, xc_id
-  double precision :: para (9)
+  double precision :: para (10)
 
   MU0 = 16. * atan(1.0) * 1.e-7
 
@@ -66,15 +66,16 @@ subroutine gFileRead () bind (c, name = 'gFileRead')
   RAXIS  = RAXIS                  /R0
   ZAXIS  = ZAXIS                  /R0
    
-  para (1) = R0
-  para (2) = dabs(B0)
-  para (3) = RLEFT
-  para (4) = RRIGHT
-  para (5) = ZLOW
-  para (6) = ZHIGH
-  para (7) = RAXIS
-  para (8) = ZAXIS 
-  para (9) = PSIAXIS /R0/R0/dabs(B0)
+  para (1)  = R0
+  para (2)  = dabs(B0)
+  para (3)  = RLEFT
+  para (4)  = RRIGHT
+  para (5)  = ZLOW
+  para (6)  = ZHIGH
+  para (7)  = RAXIS
+  para (8)  = ZAXIS 
+  para (9)  = PSIAXIS /R0/R0/dabs(B0)
+  para (10) = PSIBOUND /R0/R0/dabs(B0)
 
   allocate (R (NRBOX))
   allocate (Z (NZBOX))

### 2021-08-18 Neoclassical/Source/Neoclassical.cpp

@@ -4,9 +4,9 @@
 // 
 //        Neoclassical:: Neoclassical         ()
 // void   Neoclassical:: Solve                (int _NEUTRAL, int _IMPURITY, int _EXB, int _INTP, int _INTF,
-//			                        int _INTC, int _NTYPE, double _NN, double _LN, double _YN, double _TIME, int _CATS, int _OMFIT)
+//			                        int _INTC, int _NTYPE, double _NN, double _LN, double _YN, double _TIME, int _CATS)
 // void   Neoclassical:: Read_Parameters      (int _NEUTRAL, int _IMPURITY, int _EXB, int _INTP, int _INTF,
-// 				                int _INTC, int _NTYPE, double _NN, double _LN, double _YN, double _TIME, int _CATS, int _OMFIT)
+// 				                int _INTC, int _NTYPE, double _NN, double _LN, double _YN, double _TIME, int _CATS)
 // void   Neoclassical:: Read_Equilibrium     ()
 // void   Neoclassical:: Read_Profiles        ()
 // void   Neoclassical:: Get_Derived          ()
@@ -14,8 +14,7 @@
 // void   Neoclassical:: Get_Parameters       ()
 // void   Neoclassical:: Get_Frequencies      ()
 // void   Neoclassical:: Get_LayerWidths      ()
-// void   Neoclassical:: WriteStage2Netcdfcpp ()
-// void   Neoclassical:: WriteStage2Netcdfc   ()
+// void   Neoclassical:: WriteStage3Netcdfc   ()
 // void   Neoclassical:: Get_Normalized       ()
 // double Neoclassical:: psi_fun              (double x)
 // double Neoclassical:: psi_fun_p            (double x)
@@ -62,13 +61,13 @@ Neoclassical::Neoclassical ()
 // Solve problem
 // ##############
 void Neoclassical::Solve (int _NEUTRAL, int _IMPURITY, int _EXB, int _INTP, int _INTF,
[…]

### 2021-08-18 Documentation/EPEC_Model.tex
Streamlining NEOCLASSICAL for OMFIT
Improved documentation

@@
-\documentclass[notitlepage,12pt,prb,aps]{revtex4-1}
+\documentclass[notitlepage,12pt]{article}
 \usepackage {amsmath}
@@
 \usepackage {graphicx}
+\usepackage{fullpage}
 \allowdisplaybreaks
@@
 \title{\bf The EPEC Model}
-\author{R.~Fitzpatrick\,\footnote{rfitzp@utexas.edu}}
-\affiliation{Institute for Fusion Studies,  Department of Physics,  University of Texas at Austin,  Austin TX 78712, USA}
-\date{\today}
+\author{R.~Fitzpatrick\,\footnote{rfitzp@utexas.edu}\\
+Institute for Fusion Studies,\\  Department of Physics,\\  University of Texas at Austin,\\  Austin TX 78712, USA}
 \maketitle
@@
 \section{Plasma Response in Inner Region}
+\subsection{Island Widths}
+Let ${\mit\Psi}_k= R_0\,B_0\,\hat{\mit\Psi}_k\,{\rm e}^{-{\rm i}\,\varphi_k}$, where $\hat{\mit\Psi}_k>0$  and $\varphi_k$ are both real quantities.
+The full width (in $r$) of the magnetic island chain at the
+$k$th resonant surface is
+\begin{equation}
+W_k = 4\,R_0\left(\frac{q\,}{g\,s}\right)^{1/2}_{r_k}\hat{\mit\Psi}_k^{\,1/2},
+\end{equation}
+where 
+\begin{equation}
+s(r) = \frac{d\ln q}{d\ln r}.
+\end{equation}
+
+\subsection{Critical Island Widths}
+The critical full island width (in $r$) which must be exceeded before the electron temperature is flattened within the
+magnetic separatrix of the magnetic island chain at the $k$th resonant surface is
+\begin{equation}\label{e64g}
+\frac{W_{T_e\,k} }{r_k}= 5.07\left(\frac{\chi_e}{\chi_{\parallel\,e}}\right)^{1/4}_{r_k}\left(\frac{1}{\epsilon\,s\,n}\right)^{1/2}_{r_k},
+\end{equation}
+where $\chi_e(r)$ is the perpendicular electron energy diffusivity profile, $\epsilon =r/R_0$, 
+\begin{align}
+\chi_{\parallel\,e}&= \frac{\chi_{\parallel\,e}^{\rm brag}\,\chi_{\parallel\,e}^{\rm max}}{\chi_{\parallel\,e}^{\rm brag}+\chi_{\parallel\,e}^{\rm max}},\\[0.5ex]
+\chi_{\parallel\,e}^{\rm brag} &= 1.13\,\tau_{ee}\,v_{T\,e}^{\,2},\\[0.5ex]
+\chi_{\parallel\,e}^{\rm max} &= \frac{2\,R_0\,v_{T\,e}}{n\,s}\,\frac{r_k}{W_{T_e\,k}}.
+\end{align}
+Equation~(\ref{e64g}) must be solved iteratively for $W_{T_e\,k}/r_k$.
+
+The critical full island width (in $r$) which must be exceeded before the ion temperature is flattened within the
+magnetic separatrix of the magnetic island chain at the $k$th resonant surface is
+\begin{equation}\label{e64gg}
+\frac{W_{T_i\,k} }{r_k}= 5.07\left(\frac{\chi_i}{\chi_{\parallel\,i}}\right)^{1/4}_{r_k}\left(\frac{1}{\epsilon\,s\,n}\right)^{1/2}_{r_k},
+\end{equation}
+where $\chi_i(r)$ is the perpendicular ion energy diffusivity profile, 
+\begin{align}
+\chi_{\parallel\,i}&= \frac{\chi_{\parallel\,i}^{\rm brag}\,\chi_{\parallel\,i}^{\rm max}}{\chi_{\parallel\,i}^{\rm brag}+\chi_{\parallel\,i}^{\rm max}},\\[0.5ex]
+\chi_{\parallel\,i}^{\rm brag} &= 1.95\,\tau_{ii}\,v_{T\,i}^{\,2},\\[0.5ex]
+\chi_{\parallel\,i}^{\rm max} &= \frac{2\,R_0\,v_{T\,i}}{n\,s}\,\frac{r_k}{W_{T_i\,k}}.
+\end{align}
+Equation~(\ref{e64gg}) must be solved iteratively for $W_{T_i\,k}/r_k$.
+
+The critical full island width (in $r$) which must be exceeded before the electron density is flattened within the
+magnetic separatrix of the magnetic island chain at the $k$th resonant surface is
+\begin{equation}\label{e64ggg}
+\frac{W_{n_e\,k} }{r_k}= 5.07\left(\frac{D_\perp}{\chi_{\parallel\,i}}\right)^{1/4}_{r_k}\left(\frac{1}{\epsilon\,s\,n}\right)^{1/2}_{r_k},
+\end{equation}
+where $D_\perp(r)$ is the perpendicular particle diffusivity profile, 
+\begin{align}
+\chi_{\parallel\,i}&= \frac{\chi_{\parallel\,i}^{\rm brag}\,\chi_{\parallel\,i}^{\rm max}}{\chi_{\parallel\,i}^{\rm brag}+\chi_{\parallel\,i}^{\rm max}},\\[0.5ex]
+\chi_{\parallel\,i}^{\rm brag} &= 1.95\,\tau_{ii}\,v_{T\,i}^{\,2},\\[0.5ex]
+\chi_{\parallel\,i}^{\rm max} &= \frac{2\,R_0\,v_{T\,i}}{n\,s}\,\frac{r_k}{W_{n_e\,k}}.
+\end{align}
+Equation~(\ref{e64ggg}) must be solved iteratively for $W_{n_e\,k}/r_k$.
+
 \subsection{Evolution Equations}
-Let ${\mit\Psi}_k= R_0\,B_0\,\hat{\mit\Psi}_k\,{\rm e}^{-{\rm i}\,\varphi_k}$, ${\mit\chi}_k= R_0\,B_0\,\hat{\chi}_k\,{\rm e}^{-{\rm i}\,\zeta_k}$, and $E_{kk'}=\hat{E}_{kk'}\,{\rm e}^{-{\rm i}\,\xi_{kk'}}$,
-where $\hat{\mit\Psi}_k>0$, $\varphi_k$, $\hat{\chi}_k>0$, $\zeta_k$, $\hat{E}_{kk}'>0$, and $\xi_{kk'}$ are all real quantities. Furthermore,
+Let ${\mit\chi}_k= R_0\,B_0\,\hat{\chi}_k\,{\rm e}^{-{\rm i}\,\zeta_k}$, and $E_{kk'}=\hat{E}_{kk'}\,{\rm e}^{-{\rm i}\,\xi_{kk'}}$,
+where  $\hat{\chi}_k>0$, $\zeta_k$, $\hat{E}_{kk}'>0$, and $\xi_{kk'}$ are all real quantities. Furthermore,
 let $X_k= \hat{\mit\Psi}_k\,\cos\varphi_k$ and $Y_k= \hat{\mit\Psi}_k\,\sin\varphi_k$. The resonant plasma response model at the 
@@
 \sigma_{ee}(r) &=\frac{n_e\,e^{\,2}\,\tau_{ee}}{m_e},\\[0.5ex]
-\hat{W}_k &=\frac{2\,{\cal I}}{\epsilon_{100}\,\hat{r}_k}\left(\frac{q}{g\,s}\right)^{1/2}_{r_k} (X_k^{\,2} + Y_k^{\,2})^{\,1/4},\\[0.5ex]
-\hat{W}_{T_e\,k} &= 2\,{\cal I}\left(\frac{\chi_e\,R_0}{v_{T\,e}\,r^{\,2}\,s\,n}\right)^{1/3}_{r_k},\\[0.5ex]
-\hat{W}_{T_i\,k} &= 2\,{\cal I}\left(\frac{\chi_i\,R_0}{v_{T\,e}\,r^{\,2}\,s\,n}\right)^{1/3}_{r_k},\\[0.5ex]
-\hat{W}_{n_e\,k} &= 2\,{\cal I}\left(\frac{D_\perp\,R_0}{v_{T\,e}\,r^{\,2}\,s\,n}\right)^{1/3}_{r_k},\\[0.5ex]
-s(r) &= \frac{d\ln q}{d\ln r},\\[0.5ex]
-\hat{\rho}_{\theta\,e} &= \left(\frac{2\,{\cal I}\,v_{T\,e}\,m_e\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},\\[0.5ex]
-\hat{\rho}_{\theta\,i} &= \left(\frac{2\,{\cal I}\,v_{T\,i}\,m_i\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},\\[0.5ex]
+\hat{W}_k &=\frac{{\cal I}\,W_k}{2\,r_k}=\frac{2\,{\cal I}}{\epsilon_{100}\,\hat{r}_k}\left(\frac{q}{g\,s}\right)^{1/2}_{r_k} (X_k^{\,2} + Y_k^{\,2})^{\,1/4},\\[0.5ex]
+\hat{W}_{T_e\,k} &=\frac{{\cal I}\,W_{T_e\,k}}{2\,r_k} ,\\[0.5ex]
+\hat{W}_{T_i\,k} &= \frac{{\cal I}\,W_{T_i\,k}}{2\,r_k},\\[0.5ex]
+\hat{W}_{n_e\,k} &= \frac{{\cal I}\,W_{n_e\,k}}{2\,r_k},\\[0.5ex]
+\hat{\rho}_{\theta\,e} &=  \left(\frac{{\cal I}\,\rho_{\theta\,e}}{2\,r}\right)_{r_k}=\left(\frac{2\,{\cal I}\,v_{T\,e}\,m_e\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},\\[0.5ex]
+\hat{\rho}_{\theta\,i} &=  \left(\frac{{\cal I}\,\rho_{\theta\,i}}{2\,r}\right)_{r_k}= \left(\frac{2\,{\cal I}\,v_{T\,i}\,m_i\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},\\[0.5ex]
 \hat{\delta}_k &= \frac{\delta_{\rm linear}(r_k)}{R_0\,\epsilon_{100}\,\hat{r}_k},\\[0.5ex]
@@
 Furthermore, $\delta_{\rm linear}(r)$ is the linear layer width, whereas $\rho(r)$ is the plasma
-mass density profile. Moreover, $\chi_e(r)$, $\chi_i(r)$, and $D_\perp(r)$ are the perpendicular electron
-energy, ion energy, and particle diffusivity profile, respectively.
+mass density profile.
 
@@
 \begin{equation}
-W_k = 4\left[\frac{\hat{\mit\Psi}_k}{\sigma_k\,|\hat{{\mit\Psi}}_p(0)|}\right]^{1/2},
+\overline{W}_k = \left(\frac{d{\mit\Psi}_N}{dr}\right)_{r_k}\,W_k=4\left[\frac{\hat{\mit\Psi}_k}{\sigma_k\,|\hat{{\mit\Psi}}_p(0)|}\right]^{1/2},
 \end{equation}
-where $\sigma_k=\sigma(r_k)$, $\sigma(r) = d\ln q/d{\mit\Psi}_N$, and $\hat{\mit\Psi}_p(r) = {\mit\Psi}_p/(R_0^{\,2}\,B_0)$.  
+where 
+\begin{equation}
+\frac{d{\mit\Psi}_N}{dr} = \frac{r\,g}{R_0^{\,2}\,q\,|\hat{\mit\Psi}_p(0)|},
+\end{equation}
+$\sigma_k=\sigma(r_k)$, $\sigma(r) = d\ln q/d{\mit\Psi}_N$, and $\hat{\mit\Psi}_p(r) = {\mit\Psi}_p/(R_0^{\,2}\,B_0)$.  
 However, the halfway point between the inner and outer extremities of the separatrix is located at the flux-surface where ${\mit\Psi}_N = {\mit\Psi}_N(r_k) - A_k\,W_k^{\,2}/8$ and $A_k = [(1/3)\,(d^{\,2}q/d{\mit\Psi}_N^{\,2})/(dq/d{\mit\Psi}_N)]_{r_k}$.
@@
 \begin{align}
-\delta_{T_e\,k}& = \frac{2}{\pi}\,W_k\,\tanh\left(\frac{W_k}{W_{T_e\,k}}\right),\\[0.5ex]
-\delta_{T_i\,k}& = \frac{2}{\pi}\,W_k\,\tanh\left(\frac{W_k}{W_{T_i\,k}}\right),\\[0.5ex]
-\delta_{n_e\,k}& = \frac{2}{\pi}\,W_k\,\tanh\left(\frac{W_k}{W_{n_e\,k}}\right),
+\delta_{T_e\,k}& = \frac{2}{\pi}\,\overline{W}_k\,\tanh\left(\frac{\overline{W}_k}{\overline{W}_{T_e\,k}}\right),\\[0.5ex]
+\delta_{T_i\,k}& = \frac{2}{\pi}\,\overline{W}_k\,\tanh\left(\frac{\overline{W}_k}{\overline{W}_{T_i\,k}}\right),\\[0.5ex]
+\delta_{n_e\,k}& = \frac{2}{\pi}\,\overline{W}_k\,\tanh\left(\frac{\overline{W}_k}{\overline{W}_{n_e\,k}}\right),
 \end{align}
@@
 \begin{align}
-W_{T_e\,k} &= \left(\frac{\chi_{e}}{v_{T\,e}\,R_0}\,\frac{f^{\,2}}{n\,\sigma\,|\hat{\mit\Psi}_p(0)|^{\,2}}\right)^{1/3}_{r_k},\\[0.5ex]
-W_{T_i\,k} &= \left(\frac{\chi_{i}}{v_{T\,i}\,R_0}\,\frac{f^{\,2}}{n\,\sigma\,|\hat{\mit\Psi}_p(0)|^{\,2}}\right)^{1/3}_{r_k},\\[0.5ex]
-W_{n_e\,k} &= \left(\frac{D_\perp}{v_{T\,i}\,R_0}\,\frac{f^{\,2}}{n\,\sigma\,|\hat{\mit\Psi}_p(0)|^{\,2}}\right)^{1/3}_{r_k}.
+\overline{W}_{T_e\,k} &=  \left(\frac{d{\mit\Psi}_N}{dr}\right)_{r_k}\,W_{T_e\,k},\\[0.5ex]
+\overline{W}_{T_i\,k} &= \left(\frac{d{\mit\Psi}_N}{dr}\right)_{r_k}\,W_{T_i\,k},\\[0.5ex]
+\overline{W}_{n_e\,k} &= \left(\frac{d{\mit\Psi}_N}{dr}\right)_{r_k}\,W_{n_e\,k}.
 \end{align}
@@
 {\mit\Delta}P_j &=\sum_{k=j,K} 
-\left\{\left[\delta_{n_e\,k}\,\frac{dn_e}{d{\mit\Psi}_N}\,T_e- \delta_{n_e\,k}\,W_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+\frac{d^{\,2}n_e}{d{\mit\Psi}_n^{\,2}}\,T_e\right)
+\left\{\left[\delta_{n_e\,k}\,\frac{dn_e}{d{\mit\Psi}_N}\,T_e- \delta_{n_e\,k}\,\overline{W}_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+\frac{d^{\,2}n_e}{d{\mit\Psi}_n^{\,2}}\,T_e\right)
 + \delta_{n_e\,k}^{\,3}\,\frac{d^{\,3}n_e}{d{\mit\Psi}_N^{\,3}}\,\frac{T_e}{24}\right]\right.
 \nonumber\\[0.5ex]
-&\phantom{++}+\left[\delta_{T_e\,k}\,n_e\,\frac{dT_e}{d{\mit\Psi}_N}- \delta_{T_e\,k}\,W_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+
+&\phantom{++}+\left[\delta_{T_e\,k}\,n_e\,\frac{dT_e}{d{\mit\Psi}_N}- \delta_{T_e\,k}\,\overline{W}_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+
  n_e\,\frac{d^{\,2}T_e}{d{\mit\Psi}_n^{\,2}}\right)
 + \delta_{T_e\,k}^{\,3}\,\frac{n_e}{24}\,\frac{d^{\,3}T_e}{d{\mit\Psi}_N^{\,3}}\right]\nonumber\\[0.5ex]
-&\phantom{++}+\left[\delta_{n_e\,k}\,\frac{dn_i}{d{\mit\Psi}_N}\,T_i- \delta_{n_e\,k}\,W_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}n_i}{d{\mit\Psi}_n^{\,2}}
+&\phantom{++}+\left[\delta_{n_e\,k}\,\frac{dn_i}{d{\mit\Psi}_N}\,T_i- \delta_{n_e\,k}\,\overline{W}_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}n_i}{d{\mit\Psi}_n^{\,2}}
 \,T_i\right)+ \delta_{n_e\,k}^{\,3}\,\frac{d^{\,3}n_i}{d{\mit\Psi}_N^{\,3}}\,\frac{T_i}{24}\right]
 \nonumber\\[0.5ex]
-&\phantom{++}\left.+\left[\delta_{T_i\,k}\,n_i\,\frac{dT_i}{d{\mit\Psi}_N}- \delta_{T_i\,k}\,W_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+n_i\,\frac{d^{\,2}T_i}{d{\mit\Psi}_n^{\,2}}\right)
+&\phantom{++}\left.+\left[\delta_{T_i\,k}\,n_i\,\frac{dT_i}{d{\mit\Psi}_N}- \delta_{T_i\,k}\,\overline{W}_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+n_i\,\frac{d^{\,2}T_i}{d{\mit\Psi}_n^{\,2}}\right)
 + \delta_{T_i\,k}^{\,3}\,\frac{n_i}{24}\,\frac{d^{\,3}T_i}{d{\mit\Psi}_N^{\,3}}\right]\right\}_{r_k}.

### 2021-08-20 Documentation/EPEC_Model.tex
Improved documentation

@@
 \hat{W}_{n_e\,k} &= \frac{{\cal I}\,W_{n_e\,k}}{2\,r_k},\\[0.5ex]
-\hat{\rho}_{\theta\,e} &=  \left(\frac{{\cal I}\,\rho_{\theta\,e}}{2\,r}\right)_{r_k}=\left(\frac{2\,{\cal I}\,v_{T\,e}\,m_e\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},\\[0.5ex]
-\hat{\rho}_{\theta\,i} &=  \left(\frac{{\cal I}\,\rho_{\theta\,i}}{2\,r}\right)_{r_k}= \left(\frac{2\,{\cal I}\,v_{T\,i}\,m_i\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},\\[0.5ex]
+\hat{\rho}_{\theta\,e} &= \frac{2\,{\cal I}\,\rho_{\theta\,e}}{r}= \left(\frac{{\cal I}\,\rho_{\theta\,e}}{2\,r}\right)_{r_k}=\left(\frac{2\,{\cal I}\,v_{T\,e}\,m_e\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},\\[0.5ex]
+\hat{\rho}_{\theta\,i} &=  \frac{2\,{\cal I}\,\rho_{\theta\,i}}{r}= \left(\frac{{\cal I}\,\rho_{\theta\,i}}{2\,r}\right)_{r_k}= \left(\frac{2\,{\cal I}\,v_{T\,i}\,m_i\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},\\[0.5ex]
 \hat{\delta}_k &= \frac{\delta_{\rm linear}(r_k)}{R_0\,\epsilon_{100}\,\hat{r}_k},\\[0.5ex]
@@
 \begin{equation}
-\overline{W}_k = \left(\frac{d{\mit\Psi}_N}{dr}\right)_{r_k}\,W_k=4\left[\frac{\hat{\mit\Psi}_k}{\sigma_k\,|\hat{{\mit\Psi}}_p(0)|}\right]^{1/2},
+\overline{W}_k = \left(\frac{d{\mit\Psi}_N}{dr}\right)_{r_k}\,W_k=4\left(A_{i\,k}\,\hat{\mit\Psi}_k\right)^{1/2},
 \end{equation}
@@
 \end{equation}
-$\sigma_k=\sigma(r_k)$, $\sigma(r) = d\ln q/d{\mit\Psi}_N$, and $\hat{\mit\Psi}_p(r) = {\mit\Psi}_p/(R_0^{\,2}\,B_0)$.  
-However, the halfway point between the inner and outer extremities of the separatrix is located at the flux-surface where ${\mit\Psi}_N = {\mit\Psi}_N(r_k) - A_k\,W_k^{\,2}/8$ and $A_k = [(1/3)\,(d^{\,2}q/d{\mit\Psi}_N^{\,2})/(dq/d{\mit\Psi}_N)]_{r_k}$.
+$A_{1\,k}=A_1(r_k)$, $A_1 = 1/(\sigma\,|\hat{\mit\Psi}_p(0)|)$,  $\sigma(r) = d\ln q/d{\mit\Psi}_N$, and $\hat{\mit\Psi}_p(r) = {\mit\Psi}_p/(R_0^{\,2}\,B_0)$.  
+However, the halfway point between the inner and outer extremities of the separatrix is located at the flux-surface where ${\mit\Psi}_N = {\mit\Psi}_N(r_k) - A_2{\,k}\,W_k^{\,2}/8$ and $A_{2\,k} = [(1/3)\,(d^{\,2}q/d{\mit\Psi}_N^{\,2})/(dq/d{\mit\Psi}_N)]_{r_k}$.
 On average, the presence of a magnetic island chain of full width $W_k$ at the $k$th resonant surface
@@
 \nonumber\\[0.5ex]
-&\phantom{++}+\left[\delta_{T_e\,k}\,n_e\,\frac{dT_e}{d{\mit\Psi}_N}- \delta_{T_e\,k}\,\overline{W}_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+
+&\phantom{++}+\left[\delta_{T_e\,k}\,n_e\,\frac{dT_e}{d{\mit\Psi}_N}- \delta_{T_e\,k}\,\overline{W}_k^{\,2}\,\frac{A_{2\,k}}{8}\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+
  n_e\,\frac{d^{\,2}T_e}{d{\mit\Psi}_n^{\,2}}\right)
 + \delta_{T_e\,k}^{\,3}\,\frac{n_e}{24}\,\frac{d^{\,3}T_e}{d{\mit\Psi}_N^{\,3}}\right]\nonumber\\[0.5ex]
-&\phantom{++}+\left[\delta_{n_e\,k}\,\frac{dn_i}{d{\mit\Psi}_N}\,T_i- \delta_{n_e\,k}\,\overline{W}_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}n_i}{d{\mit\Psi}_n^{\,2}}
+&\phantom{++}+\left[\delta_{n_e\,k}\,\frac{dn_i}{d{\mit\Psi}_N}\,T_i- \delta_{n_e\,k}\,\overline{W}_k^{\,2}\,\frac{A_{2\,k}}{8}\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}n_i}{d{\mit\Psi}_n^{\,2}}
 \,T_i\right)+ \delta_{n_e\,k}^{\,3}\,\frac{d^{\,3}n_i}{d{\mit\Psi}_N^{\,3}}\,\frac{T_i}{24}\right]
 \nonumber\\[0.5ex]
-&\phantom{++}\left.+\left[\delta_{T_i\,k}\,n_i\,\frac{dT_i}{d{\mit\Psi}_N}- \delta_{T_i\,k}\,\overline{W}_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+n_i\,\frac{d^{\,2}T_i}{d{\mit\Psi}_n^{\,2}}\right)
+&\phantom{++}\left.+\left[\delta_{T_i\,k}\,n_i\,\frac{dT_i}{d{\mit\Psi}_N}- \delta_{T_i\,k}\,\overline{W}_k^{\,2}\,\frac{A_{2\,k}}{8}\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+n_i\,\frac{d^{\,2}T_i}{d{\mit\Psi}_n^{\,2}}\right)
 + \delta_{T_i\,k}^{\,3}\,\frac{n_i}{24}\,\frac{d^{\,3}T_i}{d{\mit\Psi}_N^{\,3}}\right]\right\}_{r_k}.

### 2021-08-20 Neoclassical/Plots/Stage3Lundquist.py

@@ -7,7 +7,7 @@ import netCDF4 as nc
 import matplotlib.pyplot as plt
 import numpy as np
 
-fn = root['OUTPUTS']['NEOCLASSICAL']['Stage3']
+fn = root['NEOCLASSICAL']['OUTPUTS']['Stage3']
 ds = nc.Dataset(fn)
 
 psin = ds['PsiN_k']

### 2021-08-20 Neoclassical/Plots/Stage3Profiles.py

@@ -6,7 +6,7 @@
 import netCDF4 as nc
 import matplotlib.pyplot as plt
 
-fn = root['OUTPUTS']['NEOCLASSICAL']['Stage3']
+fn = root['NEOCLASSICAL']['OUTPUTS']['Stage3']
 ds = nc.Dataset(fn)
 
 psin = ds['PsiN']

### 2021-08-20 Phase/Plots/Stage5RmpWaveform.py

@@ -7,7 +7,7 @@ import netCDF4 as nc
 import numpy as np
 import matplotlib.pyplot as plt
 
-fn = root['OUTPUTS']['PHASE']['Stage5']
+fn = root['PHASE']['OUTPUTS']['Stage5']
 ds = nc.Dataset(fn)
 
 time = ds['time']

### 2021-08-21 Documentation/EPEC_Model.tex

--- 2021-08-18 Documentation/EPEC_Model.tex
@@
 \begin{equation}
-\overline{W}_k = \left(\frac{d{\mit\Psi}_N}{dr}\right)_{r_k}\,W_k=4\left[\frac{\hat{\mit\Psi}_k}{\sigma_k\,|\hat{{\mit\Psi}}_p(0)|}\right]^{1/2},
+\overline{W}_k = \left(\frac{d{\mit\Psi}_N}{dr}\right)_{r_k}\,W_k=4\left(A_{1\,k}\,\hat{\mit\Psi}_k\right)^{1/2},
 \end{equation}
@@
 \end{equation}
-$\sigma_k=\sigma(r_k)$, $\sigma(r) = d\ln q/d{\mit\Psi}_N$, and $\hat{\mit\Psi}_p(r) = {\mit\Psi}_p/(R_0^{\,2}\,B_0)$.  
-However, the halfway point between the inner and outer extremities of the separatrix is located at the flux-surface where ${\mit\Psi}_N = {\mit\Psi}_N(r_k) - A_k\,W_k^{\,2}/8$ and $A_k = [(1/3)\,(d^{\,2}q/d{\mit\Psi}_N^{\,2})/(dq/d{\mit\Psi}_N)]_{r_k}$.
+$A_{1\,k}=A_1(r_k)$, $A_1 = 1/(\sigma\,|\hat{\mit\Psi}_p(0)|)$,  $\sigma(r) = d\ln q/d{\mit\Psi}_N$, and $\hat{\mit\Psi}_p(r) = {\mit\Psi}_p/(R_0^{\,2}\,B_0)$.  
+However, the halfway point between the inner and outer extremities of the separatrix is located at the flux-surface where ${\mit\Psi}_N = {\mit\Psi}_N(r_k) - A_{2\,k}\,W_k^{\,2}/8$ and $A_{2\,k} = [(1/3)\,(d^{\,2}q/d{\mit\Psi}_N^{\,2})/(dq/d{\mit\Psi}_N)]_{r_k}$.
 On average, the presence of a magnetic island chain of full width $W_k$ at the $k$th resonant surface
@@
 {\mit\Delta}P_j &=\sum_{k=j,K} 
-\left\{\left[\delta_{n_e\,k}\,\frac{dn_e}{d{\mit\Psi}_N}\,T_e- \delta_{n_e\,k}\,\overline{W}_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+\frac{d^{\,2}n_e}{d{\mit\Psi}_n^{\,2}}\,T_e\right)
-+ \delta_{n_e\,k}^{\,3}\,\frac{d^{\,3}n_e}{d{\mit\Psi}_N^{\,3}}\,\frac{T_e}{24}\right]\right.
-\nonumber\\[0.5ex]
-&\phantom{++}+\left[\delta_{T_e\,k}\,n_e\,\frac{dT_e}{d{\mit\Psi}_N}- \delta_{T_e\,k}\,\overline{W}_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+
- n_e\,\frac{d^{\,2}T_e}{d{\mit\Psi}_n^{\,2}}\right)
-+ \delta_{T_e\,k}^{\,3}\,\frac{n_e}{24}\,\frac{d^{\,3}T_e}{d{\mit\Psi}_N^{\,3}}\right]\nonumber\\[0.5ex]
-&\phantom{++}+\left[\delta_{n_e\,k}\,\frac{dn_i}{d{\mit\Psi}_N}\,T_i- \delta_{n_e\,k}\,\overline{W}_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}n_i}{d{\mit\Psi}_n^{\,2}}
-\,T_i\right)+ \delta_{n_e\,k}^{\,3}\,\frac{d^{\,3}n_i}{d{\mit\Psi}_N^{\,3}}\,\frac{T_i}{24}\right]
-\nonumber\\[0.5ex]
-&\phantom{++}\left.+\left[\delta_{T_i\,k}\,n_i\,\frac{dT_i}{d{\mit\Psi}_N}- \delta_{T_i\,k}\,\overline{W}_k^{\,2}\,\frac{A_k}{8}\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+n_i\,\frac{d^{\,2}T_i}{d{\mit\Psi}_n^{\,2}}\right)
-+ \delta_{T_i\,k}^{\,3}\,\frac{n_i}{24}\,\frac{d^{\,3}T_i}{d{\mit\Psi}_N^{\,3}}\right]\right\}_{r_k}.
+\left\{(F_1+F_3)\,\delta_{n_e\,k}+ F_2\,\delta_{T_e\,k}+F_4\,\delta_{T_i\,k} + (F_5+F_7)\,\delta_{n_e\,k}\,\overline{W}_k^{\,2}
+\right.\nonumber\\[0.5ex]
+&\phantom{++}\left.+F_6\, \delta_{T_e\,k}\,\overline{W}_k^{\,2}+ F_8\,\delta_{T_i\,k}\,\overline{W}_k^{\,2}+ (F_9+F_{11})\,\delta_{n_e\,k}^{\,3}
++ F_{10}\,\delta_{T_e\,k}^{\,3}+ F_{12}\,\delta_{T_i\,k}^{\,3}\right\}_{r_k},
 \end{align}
 where
-we have neglected the impurity ion pressure.
+\begin{align}
+F_1 &=\frac{dn_e}{d{\mit\Psi}_N}\,T_e,\\[0.5ex]
+F_2 &=\frac{dT_e}{d{\mit\Psi}_N}\,n_e,\\[0.5ex]
+F_3 &=\frac{dn_i}{d{\mit\Psi}_N}\,T_i,\\[0.5ex]
+F_4 &=\frac{dT_i}{d{\mit\Psi}_N}\,n_i,\\[0.5ex]
+F_5& -\frac{A_2}{8}\,\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+\frac{d^{\,2}n_e}{d{\mit\Psi}_n^{\,2}}\,T_e\right),\\[0.5ex]
+F_6& -\frac{A_2}{8}\,\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+\frac{d^{\,2}T_e}{d{\mit\Psi}_n^{\,2}}\,n_e\right),\\[0.5ex]
+F_7& -\frac{A_2}{8}\,\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}n_i}{d{\mit\Psi}_n^{\,2}}\,T_i\right),\\[0.5ex]
+F_8& -\frac{A_2}{8}\,\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}T_i}{d{\mit\Psi}_n^{\,2}}\,n_i\right),\\[0.5ex]
+F_9&=\frac{T_e}{24}\,\frac{d^{\,3}n_e}{d{\mit\Psi}_N^{\,3}},\\[0.5ex]
+F_{10}&=\frac{n_e}{24}\,\frac{d^{\,3}T_e}{d{\mit\Psi}_N^{\,3}},\\[0.5ex]
+F_{11}&=\frac{T_i}{24}\,\frac{d^{\,3}n_i}{d{\mit\Psi}_N^{\,3}},\\[0.5ex]
+F_{12}&=\frac{n_i}{24}\,\frac{d^{\,3}T_i}{d{\mit\Psi}_N^{\,3}},
+\end{align} 
+and we have neglected the impurity ion pressure.
 

### 2021-08-23 Documentation/EPEC_Model.tex
Improved documentation

@@
 \chi_{\parallel\,e}&= \frac{\chi_{\parallel\,e}^{\rm brag}\,\chi_{\parallel\,e}^{\rm max}}{\chi_{\parallel\,e}^{\rm brag}+\chi_{\parallel\,e}^{\rm max}},\\[0.5ex]
-\chi_{\parallel\,e}^{\rm brag} &= 1.13\,\tau_{ee}\,v_{T\,e}^{\,2},\\[0.5ex]
+\chi_{\parallel\,e}^{\rm brag} &= \frac{1.55\,\tau_{ee}\,v_{T\,e}^{\,2}}{1+0.38\,Z_{\rm eff}},\\[0.5ex]
 \chi_{\parallel\,e}^{\rm max} &= \frac{2\,R_0\,v_{T\,e}}{n\,s}\,\frac{r_k}{W_{T_e\,k}}.
@@
 $A_{1\,k}=A_1(r_k)$, $A_1 = 1/(\sigma\,|\hat{\mit\Psi}_p(0)|)$,  $\sigma(r) = d\ln q/d{\mit\Psi}_N$, and $\hat{\mit\Psi}_p(r) = {\mit\Psi}_p/(R_0^{\,2}\,B_0)$.  
-However, the halfway point between the inner and outer extremities of the separatrix is located at the flux-surface where ${\mit\Psi}_N = {\mit\Psi}_N(r_k) - A_{2\,k}\,W_k^{\,2}/8$ and $A_{2\,k} = [(1/3)\,(d^{\,2}q/d{\mit\Psi}_N^{\,2})/(dq/d{\mit\Psi}_N)]_{r_k}$.
+However, the halfway point between the inner and outer extremities of the separatrix is located at the flux-surface where ${\mit\Psi}_N = {\mit\Psi}_N(r_k) - A_{2\,k}\,W_k^{\,2}/8$, $A_{2\,k}=A_2(r_k)$, and $A_{2\,k} = [(1/3)\,(d^{\,2}q/d{\mit\Psi}_N^{\,2})/(dq/d{\mit\Psi}_N)]_{r_k}$.
 On average, the presence of a magnetic island chain of full width $W_k$ at the $k$th resonant surface
@@
 F_4 &=\frac{dT_i}{d{\mit\Psi}_N}\,n_i,\\[0.5ex]
-F_5& -\frac{A_2}{8}\,\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+\frac{d^{\,2}n_e}{d{\mit\Psi}_n^{\,2}}\,T_e\right),\\[0.5ex]
-F_6& -\frac{A_2}{8}\,\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+\frac{d^{\,2}T_e}{d{\mit\Psi}_n^{\,2}}\,n_e\right),\\[0.5ex]
-F_7& -\frac{A_2}{8}\,\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}n_i}{d{\mit\Psi}_n^{\,2}}\,T_i\right),\\[0.5ex]
-F_8& -\frac{A_2}{8}\,\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}T_i}{d{\mit\Psi}_n^{\,2}}\,n_i\right),\\[0.5ex]
+F_5&= -\frac{A_2}{8}\,\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+\frac{d^{\,2}n_e}{d{\mit\Psi}_n^{\,2}}\,T_e\right),\\[0.5ex]
+F_6&= -\frac{A_2}{8}\,\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+\frac{d^{\,2}T_e}{d{\mit\Psi}_n^{\,2}}\,n_e\right),\\[0.5ex]
+F_7& =-\frac{A_2}{8}\,\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}n_i}{d{\mit\Psi}_n^{\,2}}\,T_i\right),\\[0.5ex]
+F_8& =-\frac{A_2}{8}\,\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}T_i}{d{\mit\Psi}_n^{\,2}}\,n_i\right),\\[0.5ex]
 F_9&=\frac{T_e}{24}\,\frac{d^{\,3}n_e}{d{\mit\Psi}_N^{\,3}},\\[0.5ex]

### 2021-08-28 Documentation/EPEC_Model.tex
Added Poem terms

@@
 &\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{dX_k}{d\hat{t}} 
-+\hat{\varpi}_k\,Y_k\right)= \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,X_{k'}  -\sin\xi_{kk'}\,Y_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\cos\zeta_k\nonumber\\[0.5ex]&\phantom{=====} +\frac{\alpha_{b\,e\,k}}{\hat{W}_k}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_{e}\,k}\,\hat{W}_{n_e\,k}+\hat{\rho}_{\theta_e}^{\,2}+W_k^{\,2}}\right)X_k+\frac{\alpha_{b\,i\,k}}{\hat{W}_k}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_{i}\,k}\,\hat{W}_{n_e\,k}+\hat{\rho}_{\theta_i}^{\,2}+\hat{W}_k^{\,2}}\right)X_k\nonumber\\[0.5ex]
-&\phantom{=====}+\frac{\alpha_{c\,k}}{\hat{W}_k}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{n_e\,k}^{\,2}+\hat{W}_k^{\,2}}\right)X_k+\frac{\alpha_{p\,k}}{\hat{W}_k^{\,3}}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_{i}\,k}\,\hat{W}_{n_e\,k}+\hat{W}_k^{\,2}}\right)^2 X_k,\\[0.5ex]
++\hat{\varpi}_k\,Y_k\right)= \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,X_{k'}  -\sin\xi_{kk'}\,Y_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\cos\zeta_k\nonumber\\[0.5ex]&\phantom{=====}+\left(f_{b\,k} +f_{c\,k}+f_{p\,k}-f_{s\,k}\right)X_k,\\[0.5ex]
 &\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{dY_k}{d\hat{t}} -\hat{\varpi}_k\,X_k\right)
 = \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,Y_{k'}
-+\sin\xi_{kk'}\,X_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\sin\zeta_k\nonumber\\[0.5ex]&\phantom{=====} +\frac{\alpha_{b\,e\,k}}{\hat{W}_k}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_{e}\,k}\,\hat{W}_{n_e\,k}+\hat{\rho}_{\theta_e}^{\,2}+\hat{W}_k^{\,2}}\right)Y_k+\frac{\alpha_{b\,i\,k}}{\hat{W}_k}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_{i}\,k}\,\hat{W}_{n_e\,k}+\hat{\rho}_{\theta_i}^{\,2}+\hat{W}_k^{\,2}}\right)Y_k\nonumber\\[0.5ex]
-&\phantom{=====}+\frac{\alpha_{c\,k}}{\hat{W}_k}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{n_e\,k}^{\,2}+\hat{W}_k^{\,2}}\right)Y_k+\frac{\alpha_{p\,k}}{\hat{W}_k^{\,3}}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_{i}\,k}\,\hat{W}_{n_e\,k}+\hat{W}_k^{\,2}}\right)^2 Y_k,\label{e22}
++\sin\xi_{kk'}\,X_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\sin\zeta_k\nonumber\\[0.5ex]&\phantom{=====}+\left(
+f_{b\,k} +f_{c\,k}+f_{p\,k}-f_{s\,k}\right)Y_k,\label{e22}
 \end{align}
@@
 \sigma_{ee}(r) &=\frac{n_e\,e^{\,2}\,\tau_{ee}}{m_e},\\[0.5ex]
+f_{b\,k} &= f_{b\,e\,k}+f_{b\,i\,k},\\[0.5ex]
+f_{b\,e\,k} &= \alpha_{b\,e\,k}\left(f_{b\,T_e\,k} + f_{b\,n_e\,k}\right),\\[0.5ex]
+f_{b\,i\,k} &= \alpha_{b\,i\,k}\left(f_{b\,T_i\,k} + f_{b\,n_i\,k}\right),\\[0.5ex]
+f_{b\,T_e\,k}&=\left(\frac{\eta_e}{1+\eta_e}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{T_e\,k}^{\,2}+\hat{\rho}_{\theta\,e\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
+f_{b\,n_e\,k}&=\left(\frac{1}{1+\eta_e}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{n_e\,k}^{\,2}+\hat{\rho}_{\theta\,e\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
+f_{b\,T_i\,k}&=\left(\frac{\eta_i}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{T_i\,k}^{\,2}+\hat{\rho}_{\theta\,i\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
+f_{b\,n_i\,k}&=\left(\frac{1}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{n_e\,k}^{\,2}+\hat{\rho}_{\theta\,i\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
+f_{c\,k} &= \alpha_{c\,k}\left(f_{c\,T_e\,k} + f_{c\,n_e\,k} + f_{c\,T_i\,k} + f_{c\,n_i\,k}\right),\\[0.5ex]
+f_{c\,T_e\,k}&=\left(\frac{n_e}{n_e+n_i}\,\frac{\eta_e}{1+\eta_e}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{T_e\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
+f_{c\,n_e\,k}&=\left(\frac{n_e}{n_e+n_i}\,\frac{1}{1+\eta_e}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{n_e\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
+f_{c\,T_i\,k}&=\left(\frac{n_i}{n_e+n_i}\,\frac{\eta_i}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{T_i\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
+f_{c\,n_i\,k}&=\left(\frac{n_i}{n_e+n_i}\,\frac{1}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{n_e\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
+f_{p\,k} &= \alpha_{p\,k}\left(f_{p\,T_i\,k} + f_{p\,n_i\,k}\right),\\[0.5ex]
+f_{p\,T_i\,k}&=\left(\frac{\eta_i}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k}{(\hat{W}_{T_i\,k}^{\,2}+\hat{W}_k^{\,2})^{\,2}},\\[0.5ex]
+f_{p\,n_i\,k}&=\left(\frac{1}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k}{(\hat{W}_{n_e\,k}^{\,2}+\hat{W}_k^{\,2})^{\,2}},\\[0.5ex]
 \hat{W}_k &=\frac{{\cal I}\,W_k}{2\,r_k}=\frac{2\,{\cal I}}{\epsilon_{100}\,\hat{r}_k}\left(\frac{q}{g\,s}\right)^{1/2}_{r_k} (X_k^{\,2} + Y_k^{\,2})^{\,1/4},\\[0.5ex]
@@
 \hat{W}_{n_e\,k} &= \frac{{\cal I}\,W_{n_e\,k}}{2\,r_k},\\[0.5ex]
-\hat{\rho}_{\theta\,e} &= \left(\frac{{\cal I}\,\rho_{\theta\,e}}{2\,r}\right)_{r_k}=\left(\frac{2\,{\cal I}\,v_{T\,e}\,m_e\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},\\[0.5ex]
-\hat{\rho}_{\theta\,i} &= \left(\frac{{\cal I}\,\rho_{\theta\,i}}{2\,r}\right)_{r_k}= \left(\frac{2\,{\cal I}\,v_{T\,i}\,m_i\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},\\[0.5ex]
+\hat{\rho}_{\theta\,e\, k} &= \left(\frac{{\cal I}\,\rho_{\theta\,e}}{2\,r}\right)_{r_k}=\left(\frac{2\,{\cal I}\,v_{T\,e}\,m_e\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},\\[0.5ex]
+\hat{\rho}_{\theta\,i\,k} &= \left(\frac{{\cal I}\,\rho_{\theta\,i}}{2\,r}\right)_{r_k}= \left(\frac{2\,{\cal I}\,v_{T\,i}\,m_i\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},\\[0.5ex]
 \hat{\delta}_k &= \frac{\delta_{\rm linear}(r_k)}{R_0\,\epsilon_{100}\,\hat{r}_k},\\[0.5ex]
@@
 \omega_{\beta}(r)&= \frac{s\,g\,B_0}{\mu_0\,n_e\,e\,R_0^{\,2}\,q},\\[0.5ex]
-\omega_{\mit\Omega}(r)&= \frac{e\,g\,B_0\,s\,q}{m_i}.
+\omega_{\mit\Omega}(r)&= \frac{e\,g\,B_0\,s\,q}{m_i},\\[0.5ex]
+f_{s\,k} &=\frac{f_{s\,1\,k} \,\hat{W}_{T_e\,k}^{\,2}+ f_{s\,2\,k} \,\hat{W}_k^{\,2}}{\hat{W}_{T_e\,k}^{\,2}+ \hat{W}_k^{\,2}},\\[0.5ex]
+f_{s\,1\,k} &= P_{1\,k}\,\frac{W_k}{r_k}\,\ln\left(\frac{r_k}{W_k}\right)+ P_{2\,k}\,\frac{W_k}{r_k},\\[0.5ex]
+f_{s\,2\,k} &= P_{3\,k}\,\frac{W_k}{r_k},\\[0.5ex]
+P_{1\,k} &= 0.41\,A_k^{\,2},\\[0.5ex]
+P_{2\,k} &= 0.41\left(A_k^{\,2}\left[\ln\left(\frac{1}{r_k}\right)+4.85\right] - \frac{{\mit\Sigma}_k'\,A_k}{2} - B_k - 0.44\,A_k\right),\\[0.5ex]
+P_{3\,k} &= 0.8\,A_k^{\,2} - 0.27\,B_k-0.09\,A_k,\\[0.5ex]
+A_k &= -\left(\frac{r\,q\,\hat{J}_\phi'}{s}\right)_{r_k},\\[0.5ex]
+B_k &= -\left(\frac{r^{\,2}\,q\,\hat{J}_\phi''}{s}\right)_{r_k}.
 \end{align}
@@
 Furthermore, $\delta_{\rm linear}(r)$ is the linear layer width, whereas $\rho(r)$ is the plasma
-mass density profile.
+mass density profile. Finally,
+\begin{equation}
+\hat{J}_\phi(r) = - \frac{\mu_0\,R_0\,R}{B_0}\,\frac{dP}{d{\mit\Psi}_p} - R_0^{\,2}\,B_0\,g\,\frac{dg}{d{\mit\Psi}_p},
+\end{equation}
+where $P({\mit\Psi}_p)$ is the total plasma pressure,  the previous expression is evaluated on the outboard mid-plane, and
+$\hat{J}_\phi'\equiv d\hat{J}_\phi/dr$, $\hat{J}_\phi''\equiv d^{\,2}\hat{J}_\phi/dr^{\,2}$.
 
-The EPEC resonant plasma response model interpolates smoothly
+The quantity ${\mit\Sigma}_k'$ is
+defined as
+\begin{equation}
+{\mit\Sigma}_k' = \lim_{\delta\rightarrow 0}\left[\left.\frac{r\,\psi'}{\psi}\right|_{r_k-\delta}+ \left.\frac{r\,\psi'}{\psi}\right|_{r_k+\delta}
+-2\,A_k\,(1+\ln\delta)\right],
+\end{equation}
+where $\psi(r)$ is the solution of 
+\begin{equation}
+\frac{d^{\,2}\psi}{dr^{\,2}}+ \frac{1}{r}\,\frac{d\psi}{dr}-\frac{m^{\,2}}{r^{\,2}}\,\psi - \frac{\hat{J}_\phi'\,\psi}{r\,(1/q-n/m_k)}=0
+\end{equation}
+that is well=behaved at $r=0$, and satisfies $r\,\psi'/\psi = -m$ at $r=r_{100}$. Here, $\psi'\equiv d\psi/dr$.
+
+Note that the EPEC resonant plasma response model interpolates smoothly
 between the linear regime and the
@@
 \begin{equation}\label{elin}
- \varpi_{{\rm linear}\,k} = - n\,(\omega_E+\omega_{\ast\,e})_{r_k}.
+ \varpi_{e,k} = - n\,(\omega_E+\omega_{\ast\,e})_{r_k}.
 \end{equation}
@@
 \begin{equation}\label{e28y}
- \varpi_{{\rm nonlinear}\,k}=  -n\,(\omega_E+\omega_{\ast\,i}+\omega_{{\rm nc}\,i})_{r_k}.
+ \varpi_{i\,k}=  -n\,(\omega_E+\omega_{\ast\,i}+\omega_{{\rm nc}\,i})_{r_k}.
+ \end{equation}
+ It is also helpful to define
+ \begin{equation}
+ \varpi_{E\,k}=  -n\,(\omega_E)_{r_k}.
  \end{equation}
 
-Given that our resonant plasma response model interpolates smoothly between the linear regime ($\hat{W}_k\ll \hat{\delta}_k$) and the nonlinear
-regime ($\hat{W}_k\gg \hat{\delta}_k$), it makes sense to adopt a model for the natural frequency that does the same. Hence, the EPEC model for the natural frequency is
+The EPEC model for the natural frequency is
 \begin{equation}\label{ecomp}
-\varpi_{k\,0} = \frac{\hat{\delta}_k\,\varpi_{{\rm linear}\,k} +\hat{W}_k\,\varpi_{{\rm nonlinear}\,k}}{\hat{\delta}_k+\hat{W}_k}.
+\varpi_{k\,0} = \varpi_{E\,k} + (\varpi_{e\,k} - \varpi_{E\,k})\,f_{e\,k} + (\varpi_{i\,k} - \varpi_{E\,k})\,f_{i\,k},
 \end{equation}
+where
+\begin{align}
+f_{e\,k}&= f_{T_e\,k}+ f_{n_e\,k},\\[0.5ex]
+f_{i\,k}&= f_{T_i\,k}+ f_{n_i\,k},\\[0.5ex]
+f_{T_e\,k}&=\left(\frac{\eta_e}{1+\eta_e}\right)_{r_k}\,\frac{\hat{W}_{T_e\,k}^{\,2}}{\hat{W}_{T_e\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
+f_{n_e\,k}&=\left(\frac{1}{1+\eta_e}\right)_{r_k}\,\frac{\hat{W}_{n_e\,k}^{\,2}}{\hat{W}_{n_e\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
+f_{T_i\,k}&=\left(\frac{\eta_i}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_i\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
+f_{n_i\,k}&=\left(\frac{1}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k^{\,2}}{\hat{W}_{n_e\,k}^{\,2}+\hat{W}_k^{\,2}}.
+\end{align}
 

### 2021-08-28 Neoclassical/Source/Neoclassical.cpp

@@ -342,19 +342,23 @@ void Neoclassical::Read_Equilibrium ()
   C1.resize     (nres);
   C2.resize     (nres);
   DR.resize     (nres);
+  Poem1.resize  (nres);
+  Poem2.resize  (nres);
+  Poem3.resize  (nres);
 
   for (int j = 0; j < nres; j++)
     {
-      if (fscanf (file, "%d %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf",
+      if (fscanf (file, "%d %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf",
 		  &mk (j), &rk (j), &sk (j), &gk (j), &gmk (j), &Ktk (j), &Kastk (j), &fck (j), &akk (j), &PsiNk (j),
-		  &dPsidr (j), &Kthek (j), &in, &A2 (j), &q_hat (j), &C1 (j), &C2 (j), &DR (j)) != 18)
+		  &dPsidr (j), &Kthek (j), &in, &A2 (j), &q_hat (j), &C1 (j), &C2 (j), &DR (j), &Poem1 (j), &Poem2 (j), &Poem3 (j)) != 21)
 	{
 	  printf ("NEOCLASSICAL:Read_Equilibrium: Error reading fFile (3)\n");
 	  exit (1);
 	}
       qk (j) = double (mk (j)) /double (ntor);
-      printf ("m = %3d  r = %11.4e  s = %11.4e  g = %11.4e  gm = %11.4e  Kt = %11.4e  Kast = %11.4e  Kthe = %11.4e  fc = %11.4e  akk = %11.4e  PsiN = %11.4e  q_hat = %11.4e  DR = %11.4e\n",
-	      mk (j), rk (j), sk (j), gk (j), gmk (j), Ktk (j), Kastk (j), Kthek (j), fck (j), akk (j), PsiNk (j), q_hat (j), DR (j));
+      printf ("m = %3d  r = %9.2e  s = %9.2e  g = %9.2e  gm = %9.2e  Kt = %9.2e  Kast = %9.2e  Kthe = %9.2e  fc = %9.2e  akk = %9.2e  PsiN = %9.2e  q_hat = %9.2e  DR = %9.2e  Poem1 = %9.2e  Poem2 = %9.2e  Poem3 = %9.2e\n",
[…]

### 2021-08-28 Neoclassical/Source/Neoclassical.h

@@ -68,7 +68,8 @@
 // 1.26 - Added calculation of alpha_b(e,i), alpha_c, and alpha_p
 // 1.27 - Added NETCDF output. Adapted ti run with OMFIT.
 
-// 2.1  - Compeltely went over to OMFIT mode
+// 2.0  - Completely went over to OMFIT mode
+// 2.1  - Added POEM terms in Rutherford equation
 
 // ################################################################
 
@@ -290,6 +291,9 @@ class Neoclassical
   Array<double,1> C1;     // C1
   Array<double,1> C2;     // C2
   Array<double,1> DR;     // GGJ stability parameter
+  Array<double,1> Poem1;  // Poem terms for right-hand side of Rutherford equations
+  Array<double,1> Poem2;  // Poem terms for right-hand side of Rutherford equations
+  Array<double,1> Poem3;  // Poem terms for right-hand side of Rutherford equations
 
   Array<double,2> EEh;    // Moduli of E-maxtrix elements 
 
@@ -324,25 +328,25 @@ class Neoclassical
   Array<double,1> chiek;      // Perpendicular electron energy diffusivities from cFile (m^2/s)
   Array<double,1> chink;      // Perpendicular particle diffusivities from cFile (m^2/s)
   Array<double,1> chiik;      // Perpendicular ion energy diffusivities from cFile (m^2/s)
-  Array<double,1> alpbek;     // Bootstrap current parameter
-  Array<double,1> alpbik;     // Bootstrap current parameter
-  Array<double,1> alpck;      // Curvature parameter
-  Array<double,1> alppk;      // Polarization current parameter
-  Array<double,1> rhothek;    // Electron poloidal gyroradius (m)
-  Array<double,1> rhothik;    // Majority ion poloidal gyroradius (m)
+  Array<double,1> alpbek;     // Bootstrap current parameters
+  Array<double,1> alpbik;     // Bootstrap current parameters
+  Array<double,1> alpck;      // Curvature parameters
+  Array<double,1> alppk;      // Polarization current parameters
+  Array<double,1> rhothek;    // Electron poloidal gyroradii (m)
+  Array<double,1> rhothik;    // Majority ion poloidal gyroradii (m)
 
-  Array<double,1> dnedP1k;    // Electron number density 1st derivative wrt PsiN (m^-3)
[…]

### 2021-08-28 Phase/Source/Phase.cpp

@@ -383,10 +383,14 @@ void Phase::Read_Data (int _STAGE5, int _INTF, int _INTN, int _INTU, int _NATS, 
   qhatk.resize (nres);
   C1k.resize   (nres);
   C2k.resize   (nres);
+  Poem1.resize (nres);
+  Poem2.resize (nres);
+  Poem3.resize (nres);
   for (int j = 0; j < nres; j++)
     {
-      if (fscanf (file, "%d %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf",
-		  &ini, &inr, &inr, &inr, &inr, &inr, &inr, &inr, &inr, &inr, &inr, &inr, &A1(j), &inr, &qhatk(j), &C1k(j), &C2k(j), &inr) != 18)
+      if (fscanf (file, "%d %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf",
+		  &ini, &inr, &inr, &inr, &inr, &inr, &inr, &inr, &inr, &inr, &inr, &inr, &A1(j), &inr, &qhatk(j), &C1k(j), &C2k(j), &inr,
+		  &Poem1(j), &Poem2(j), &Poem3(j)) != 21)
 	{
 	  printf ("NEOCLASSICAL: Error reading fFile (3)\n");
 	  exit (1);
@@ -533,10 +537,10 @@ void Phase::Read_Data (int _STAGE5, int _INTF, int _INTN, int _INTU, int _NATS, 
   Factor5.resize (nres); Factor6.resize  (nres); Factor7.resize  (nres); Factor8.resize  (nres);
   Factor9.resize (nres); Factor10.resize (nres); Factor11.resize (nres); Factor12.resize (nres);
   alphabe.resize (nres); alphabi.resize  (nres); alphac.resize   (nres); alphap.resize   (nres);
-  rhothe.resize  (nres); rhothi.resize   (nres); etae.resize     (nres);
+  rhothe.resize  (nres); rhothi.resize   (nres); etae.resize     (nres); etai.resize     (nres);
 
   for (int j = 0; j < nres; j++)
[…]

### 2021-08-28 Phase/Source/fFileInterpolate.cpp

@@ -7,7 +7,7 @@
 // void Phase:: fFileInterpolateQuadratic (char* fFile1, double time1, char* fFile2, double time2, char* fFile,      double time)
 // void Phase:: fFileInterpolateCubic     (char* fFile1, double time1, char* fFile2, double time2, char* fFile3,     double time3, char* fFile, double time)
 // void Phase:: fFileInterpolateQuartic   (char* fFile1, double time1, char* fFile2, double time2, char* fFile3,     double time3,
-//				                  char* fFile4, double time4, char* fFile,  double time)
+//				           char* fFile4, double time4, char* fFile,  double time)
 
 #include "Phase.h"
 
@@ -131,14 +131,14 @@ void Phase::fFileInterpolateLinear (char* fFile1, double time1, char* fFile, dou
   int             NPSI_1, NTOR_1, nres_1;
   Array<double,1> v1_1, v2_1, v3_1;
   Array<int, 1>   mres_1;
-  Array<double,1> u1_1, u2_1, u3_1, u4_1, u5_1, u6_1, u7_1, u8_1, u9_1, u10_1, u11_1, u12_1, u13_1, u14_1, u15_1, u16_1, u17_1;
+  Array<double,1> u1_1, u2_1, u3_1, u4_1, u5_1, u6_1, u7_1, u8_1, u9_1, u10_1, u11_1, u12_1, u13_1, u14_1, u15_1, u16_1, u17_1, u18_1, u19_1, u20_1;
   Array<double,2> Freal_1, Fimag_1, Ereal_1, Eimag_1;
   
   double          r1_0, r2_0, r3_0, r4_0, r5_0, r6_0, r7_0, r8_0, r9_0, r10_0, r11_0, r12_0, r13_0;
   int             NPSI_0, NTOR_0, nres_0;
   Array<double,1> v1_0, v2_0, v3_0;
   Array<int, 1>   mres_0;
-  Array<double,1> u1_0, u2_0, u3_0, u4_0, u5_0, u6_0, u7_0, u8_0, u9_0, u10_0, u11_0, u12_0, u13_0, u14_0, u15_0, u16_0, u17_0;
[…]

### 2021-08-29 Documentation/EPEC_Model.tex
Fully operational non-interpolating OMFIT version

@@
 \end{equation}
-that is well=behaved at $r=0$, and satisfies $r\,\psi'/\psi = -m$ at $r=r_{100}$. Here, $\psi'\equiv d\psi/dr$.
+that is well-behaved at $r=0$, and satisfies $r\,\psi'/\psi = -m$ at $r=r_{100}$. Here, $\psi'\equiv d\psi/dr$.
 
@@
 F_4 &=\frac{dT_i}{d{\mit\Psi}_N}\,n_i,\\[0.5ex]
-F_5&= -\frac{A_2}{8}\,\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+\frac{d^{\,2}n_e}{d{\mit\Psi}_n^{\,2}}\,T_e\right),\\[0.5ex]
-F_6&= -\frac{A_2}{8}\,\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+\frac{d^{\,2}T_e}{d{\mit\Psi}_n^{\,2}}\,n_e\right),\\[0.5ex]
-F_7& =-\frac{A_2}{8}\,\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}n_i}{d{\mit\Psi}_n^{\,2}}\,T_i\right),\\[0.5ex]
-F_8& =-\frac{A_2}{8}\,\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}T_i}{d{\mit\Psi}_n^{\,2}}\,n_i\right),\\[0.5ex]
+F_5&= -\frac{A_2}{8}\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+\frac{d^{\,2}n_e}{d{\mit\Psi}_n^{\,2}}\,T_e\right),\\[0.5ex]
+F_6&= -\frac{A_2}{8}\left(\frac{dn_e}{d{\mit\Psi}_N}\,\frac{dT_e}{d{\mit\Psi}_N}+\frac{d^{\,2}T_e}{d{\mit\Psi}_n^{\,2}}\,n_e\right),\\[0.5ex]
+F_7& =-\frac{A_2}{8}\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}n_i}{d{\mit\Psi}_n^{\,2}}\,T_i\right),\\[0.5ex]
+F_8& =-\frac{A_2}{8}\left(\frac{dn_i}{d{\mit\Psi}_N}\,\frac{dT_i}{d{\mit\Psi}_N}+\frac{d^{\,2}T_i}{d{\mit\Psi}_n^{\,2}}\,n_i\right),\\[0.5ex]
 F_9&=\frac{T_e}{24}\,\frac{d^{\,3}n_e}{d{\mit\Psi}_N^{\,3}},\\[0.5ex]

### 2021-09-13 Rescale/Source/Function_Defs_0.f90
Fist attempts to update Rescale

@@ -1,9 +1,9 @@
 Module Function_Defs_0
 
   interface
-     subroutine NameListRead (SCALE, q_95_new, OPOINT, XPOINT) 
+     subroutine NameListRead (q_95_new, OPOINT, XPOINT) 
 
-       integer          :: SCALE, OPOINT, XPOINT
+       integer          :: OPOINT, XPOINT
        double precision :: q_95_new
   
  
@@ -11,14 +11,14 @@ Module Function_Defs_0
   end interface   
 
   interface
-     subroutine ReadgFile (string, i3, NRBOX, NZBOX, RBOXLEN, ZBOXLEN, R0, RBOXLFT, RAXIS, ZAXIS, PSIAXIS, PSIBOUND,&
+     subroutine ReadgFile (string, i3, NRBOX, NZBOX, RBOXLEN, ZBOXLEN, R0, RBOXLFT, ZOFF, RAXIS, ZAXIS, PSIAXIS, PSIBOUND,&
           B0, CURRENT, T, P, TTp, Pp, Q, Psi, NBOUND, NLIM, RBOUND, ZBOUND, RLIM, ZLIM)
        
        character (len = 100) :: string
        
        integer :: i3, NRBOX, NZBOX, NBOUND, NLIM
        
-       double precision :: RBOXLEN, ZBOXLEN, R0, RBOXLFT, zero, RAXIS, ZAXIS, B0, PSIAXIS, PSIBOUND, CURRENT
+       double precision :: RBOXLEN, ZBOXLEN, R0, RBOXLFT, ZOFF, zero, RAXIS, ZAXIS, B0, PSIAXIS, PSIBOUND, CURRENT
        
        double precision, dimension (:), allocatable :: T, P, TTp, Pp, Q, RBOUND, ZBOUND, RLIM, ZLIM
        
@@ -28,14 +28,14 @@ Module Function_Defs_0
   end interface
 
   interface
-     subroutine WritegFile (string, i3, NRBOX, NZBOX, RBOXLEN, ZBOXLEN, R0, RBOXLFT, RAXIS, ZAXIS, PSIAXIS, PSIBOUND,&
+     subroutine WritegFile (string, i3, NRBOX, NZBOX, RBOXLEN, ZBOXLEN, R0, RBOXLFT, ZOFF, RAXIS, ZAXIS, PSIAXIS, PSIBOUND,&
[…]

### 2021-09-25 Documentation/EPEC_Model.tex
Improved documentation

@@
 where $q_k= m_k/n$, and $a_{kk}(r) = \oint |\nabla r|^{-2}\,d\theta/(2\pi)$.
+
+\subsection{Cylindrical Tearing Mode Equation}
+The cylindrical tearing mode equation for the eigenfunction, $\psi(r)$,  of the $m_k$, $n$ tearing mode takes the form
+\begin{equation}
+\frac{d^{\,2}\psi}{dr^{\,2}}+ \frac{1}{r}\,\frac{d\psi}{dr}-\frac{m_k^{\,2}}{r^{\,2}}\,\psi - \frac{\hat{J}_\phi'\,\psi}{r\,(1/q-n/m_k)}=0.
+\end{equation}
+Here, 
+\begin{equation}
+\hat{J}_\phi(r) = - \frac{\mu_0\,R_0\,R}{B_0}\,\frac{dP}{d{\mit\Psi}_p} - R_0^{\,2}\,B_0\,g\,\frac{dg}{d{\mit\Psi}_p},
+\end{equation}
+where $P({\mit\Psi}_p)$ is the total plasma pressure,  the previous expression is evaluated on the outboard mid-plane, and
+$\hat{J}_\phi'\equiv d\hat{J}_\phi/dr$.
+
+Suppose that the plasma is surrounded by a thin resistive wall of time constant
+$\tau_w$, located at $r=r_w>r_{100}$. The quantities ${\mit\Delta}_k^{nw}$ and ${\mit\Sigma}_k^{nw}$
+are defined as 
+\begin{align}
+{\mit\Delta}_k^{nw}&= \lim_{\delta\rightarrow 0}
+\left[\left.\frac{r\,\psi'_{nw}}{\psi_{nw}}\right|_{r_k+\delta}
+- \left.\frac{r\,\psi'_{nw}}{\psi_{nw}}\right|_{r_k-\delta}\right],\\[0.5ex]
+{\mit\Sigma}_k^{nw} &= \lim_{\delta\rightarrow 0}\left[\left.\frac{r\,\psi'_{nw}}{\psi_{nw}}\right|_{r_k+\delta}+ \left.\frac{r\,\psi'_{nw}}{\psi_{nw}}\right|_{r_k-\delta}
+-2\,A_k\,(1+\ln\delta)\right],
+\end{align}
+where 
+\begin{align}
+A_k &= -\left(\frac{r\,q\,\hat{J}_\phi'}{s}\right)_{r_k},\\[0.5ex]
+s(r) &= \frac{d\ln q}{d\ln r}.
+\end{align}
+Here, $\psi_{nw}(r)$ is a solution of the cylindrical tearing mode equation that is well-behaved at $r=0$,
+continuous at $r=r_k$, and satisfies 
+\begin{equation}
+\left.\frac{r\,\psi'_{nw}}{\psi_{nw}}\right|_{r_{100}} = -m.
+\end{equation}
+ Moreover, $\psi'\equiv d\psi/dr$.
+
+The quantities ${\mit\Delta}_k^{pw}$ and ${\mit\Sigma}_k^{\,pw}$
+are defined as 
+\begin{align}
+{\mit\Delta}_k^{nw}&= \lim_{\delta\rightarrow 0}
+\left[\left.\frac{r\,\psi'_{pw}}{\psi_{pw}}\right|_{r_k+\delta}
+- \left.\frac{r\,\psi'_{pw}}{\psi_{pw}}\right|_{r_k-\delta}\right],\\[0.5ex]
+{\mit\Sigma}_k^{\,pw} &= \lim_{\delta\rightarrow 0}\left[\left.\frac{r\,\psi'_{pw}}{\psi_{pw}}\right|_{r_k+\delta}+ \left.\frac{r\,\psi'_{pw}}{\psi_{pw}}\right|_{r_k-\delta}
+-2\,A_k\,(1+\ln\delta)\right].
+\end{align}
+Here, $\psi_{pw}(r)$ is a solution of the cylindrical tearing mode equation that is well-behaved at $r=0$,
+continuous at $r=r_k$, and satisfies 
+\begin{equation}
+\left.\frac{r\,\psi'_{pw}}{\psi_{pw}}\right|_{r_{100}} = -m\left[\frac{1+(r_{100}/r_w)^{\,2m}}{1-(r_{100}/r_w)^{\,2m}}\right].
+\end{equation}
+It is also helpful to define
+\begin{align}
+{\mit\Sigma}_{kw} &= \frac{2m\,(r_{100}/r_w)^{\,m}}{1-(r_{100}/r_w)^{\,2m}}\,\frac{\psi_{pw}(r_{100})}{\psi_{pw}(r_k)},\\[0.5ex]
+{\mit\Delta}_{kw} &= -\frac{{\mit\Sigma}_{kw}^{\,2}}{{\mit\Delta}^{nw}_k-{\mit\Delta}^{pw}_k},\\[0.5ex]
+B_k &= -\left(\frac{r^{\,2}\,q\,\hat{J}_\phi''}{s}\right)_{r_k},
+\end{align}
+where $\hat{J}_\phi'' \equiv d^2\hat{J}_\phi/dr^{\,2}$.
 
@@
 \section{Plasma Response in Inner Region}
+\subsection{Linear Layer Widths}\label{linear}
+Let
+\begin{align}
+\tau_R(r) &= \mu_0\,r^{\,2}\,\sigma_{ee}\,Q_{00}^{ee},\\[0.5ex]
+\sigma_{ee}(r) &=\frac{n_e\,e^{\,2}\,\tau_{ee}}{m_e},\\[0.5ex]
+\tau_H(r) &= \frac{R_0}{B_0\,g}\,\frac{\sqrt{\mu_0\,\rho}}{n\,s},\\[0.5ex]
+\tau_E(r) &= \frac{r^{\,2}}{D_\perp + (2/3)\,\chi_e},\\[0.5ex]
+\tau_M(r) &= \frac{R_0^{\,2}\,q^{\,2}}{\chi_\phi},\\[0.5ex]
+\rho_s (r)&= \frac{\sqrt{m_i\,T_e}}{e\,B_0\,g},\\[0.5ex]
+\tau(r)& = -\frac{\omega_{\ast\,i}}{\omega_{\ast\,e}},\\[0.5ex]
+S(r) &= \frac{\tau_R}{\tau_H},\\[0.5ex]
+P_M(r) &= \frac{\tau_R}{\tau_M},\\[0.5ex]
+P_E(r) &= \frac{\tau_R}{\tau_E},\\[0.5ex]
+D(r)&= \frac{5}{3}\,S^{\,1/3}\,\frac{\rho_s}{r},\\[0.5ex]
+Q_E(r)&= S^{\,1/3}\,n\,\omega_E\,\tau_H,\\[0.5ex]
+Q_{e,i}(r)&= -S^{\,1/3}\,n\,\omega_{\ast\,e,i}\,\tau_H
+\end{align}
+Here, $\chi_e(r)$, $D_\perp(r)$, and $\chi_\phi(r)$ are the perpendicular electron energy, particle,
+and toroidal momentum diffusivity profiles, respectively. 
+The constant-$\psi$ linear layer width is determined from the solution of
+\begin{equation}\label{e87}
+\frac{d^{\,2}\,Y}{dp^{\,2}} -\left[\frac{-Q_E\,(Q_E-Q_i)+{\rm i}\,(Q_E-Q_i)\,(P_M+P_E)\,p^{\,2}+
+P_M\,P_E\,p^{\,4}}
+{{\rm i}\,(Q_E-Q_e) +\{P_E + {\rm i}\,(Q_E-Q_i)\,D^{\,2}\}\,p^{\,2}+(1+\tau)\,P_M\,D^{\,2}\,p^{\,4}}
+\right] p^{\,2}\, Y = 0.
+\end{equation}
+If the small-$p$ behavior of solution of the previous equation that is well-behaved as $p\rightarrow \infty$ is
+\begin{equation}
+Y(p) = Y_0\left[1 - c\,p+{\cal O}(p^{\,2})\right].
+\end{equation}
+then the 
+linear layer width is 
+\begin{equation}
+\delta_{\rm linear}(r) = \frac{\pi\,|c|\,r}{S^{\,1/3}}.
+\end{equation}
+Note that Eq.~(\ref{e87}) can only be solved when $1+\tau>0$.
+
 \subsection{Island Widths}
@@
 \begin{equation}
-W_k = 4\,R_0\left(\frac{q\,}{g\,s}\right)^{1/2}_{r_k}\hat{\mit\Psi}_k^{\,1/2},
-\end{equation}
-where 
-\begin{equation}
-s(r) = \frac{d\ln q}{d\ln r}.
+W_k = 4\,R_0\left(\frac{q\,}{g\,s}\right)^{1/2}_{r_k}\hat{\mit\Psi}_k^{\,1/2}.
 \end{equation}
@@
 \begin{equation}\label{e64g}
-\frac{W_{T_e\,k} }{r_k}= 5.07\left(\frac{\chi_e}{\chi_{\parallel\,e}}\right)^{1/4}_{r_k}\left(\frac{1}{\epsilon\,s\,n}\right)^{1/2}_{r_k},
+W_{T_e\,k} = 5.07\left(\frac{\chi_e}{\chi_{\parallel\,e}}\right)^{1/4}_{r_k}\left(\frac{1}{\epsilon\,s\,n}\right)^{1/2}_{r_k}r_k,
 \end{equation}
-where $\chi_e(r)$ is the perpendicular electron energy diffusivity profile, $\epsilon =r/R_0$, 
+where $\epsilon =r/R_0$, and 
 \begin{align}
@@
 \begin{equation}\label{e64gg}
-\frac{W_{T_i\,k} }{r_k}= 5.07\left(\frac{\chi_i}{\chi_{\parallel\,i}}\right)^{1/4}_{r_k}\left(\frac{1}{\epsilon\,s\,n}\right)^{1/2}_{r_k},
+W_{T_i\,k}= 5.07\left(\frac{\chi_i}{\chi_{\parallel\,i}}\right)^{1/4}_{r_k}\left(\frac{1}{\epsilon\,s\,n}\right)^{1/2}_{r_k}r_k,
 \end{equation}
@@
 \begin{equation}\label{e64ggg}
-\frac{W_{n_e\,k} }{r_k}= 5.07\left(\frac{D_\perp}{\chi_{\parallel\,i}}\right)^{1/4}_{r_k}\left(\frac{1}{\epsilon\,s\,n}\right)^{1/2}_{r_k},
+W_{n_e\,k}= 5.07\left(\frac{D_\perp}{\chi_{\parallel\,i}}\right)^{1/4}_{r_k}\left(\frac{1}{\epsilon\,s\,n}\right)^{1/2}_{r_k}r_k,
 \end{equation}
-where $D_\perp(r)$ is the perpendicular particle diffusivity profile, 
+where 
 \begin{align}
@@
 
-\subsection{Evolution Equations}
+\subsection{Resonant Plasma Response Model}
 Let ${\mit\chi}_k= R_0\,B_0\,\hat{\chi}_k\,{\rm e}^{-{\rm i}\,\zeta_k}$, and $E_{kk'}=\hat{E}_{kk'}\,{\rm e}^{-{\rm i}\,\xi_{kk'}}$,
@@
 \begin{align}\label{e21}
-&\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{dX_k}{d\hat{t}} 
-+\hat{\varpi}_k\,Y_k\right)= \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,X_{k'}  -\sin\xi_{kk'}\,Y_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\cos\zeta_k\nonumber\\[0.5ex]&\phantom{=====}+\left(f_{b\,k} +f_{c\,k}+f_{p\,k}-f_{s\,k}\right)X_k,\\[0.5ex]
-&\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{dY_k}{d\hat{t}} -\hat{\varpi}_k\,X_k\right)
-= \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,Y_{k'}
-+\sin\xi_{kk'}\,X_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\sin\zeta_k\nonumber\\[0.5ex]&\phantom{=====}+\left(
-f_{b\,k} +f_{c\,k}+f_{p\,k}-f_{s\,k}\right)Y_k,\label{e22}
+\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{dX_k}{d\hat{t}} 
++\hat{\varpi}_k\,Y_k\right)&= f_k\,X_k+ \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,X_{k'}  -\sin\xi_{kk'}\,Y_{k'})\nonumber\\[0.5ex] &\phantom{=}+ {\mit\Sigma}_{kw}\,U_k + \hat{E}_{kk}\,\hat{\chi}_k\,\cos\zeta_k,\\[0.5ex]
+\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{dY_k}{d\hat{t}} -\hat{\varpi}_k\,X_k\right)
+&= f_k\,Y_k + \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,Y_{k'}
++\sin\xi_{kk'}\,X_{k'}) \nonumber\\[0.5ex]
+&\phantom{=}+ {\mit\Sigma}_{kw}\,V_k+ \hat{E}_{kk}\,\hat{\chi}_k\,\sin\zeta_k,\label{e22}\\[0.5ex]
+\hat{\tau}_w\,\frac{dU_k}{d\hat{t}} &={\mit\Delta}_{kw}\, U_k+ {\mit\Sigma}_{kw}\,X_k,\\[0.5ex]
+\hat{\tau}_w\,\frac{dV_k}{d\hat{t}} &={\mit\Delta}_{kw}\, V_k+ {\mit\Sigma}_{kw}\,Y_k,
 \end{align}
@@
 \begin{align}\label{e23}
+\hat{W}_k &=\frac{{\cal I}\,W_k}{2\,r_k}=\frac{2\,{\cal I}}{\epsilon_{100}\,\hat{r}_k}\left(\frac{q}{g\,s}\right)^{1/2}_{r_k} (X_k^{\,2} + Y_k^{\,2})^{\,1/4},\\[0.5ex]
+\hat{\delta}_k &= \frac{\delta_{\rm linear}(r_k)}{R_0\,\epsilon_{100}\,\hat{r}_k},\\[0.5ex]
 {\cal S}_k&=\frac{\tau_R(r_k)}{\tau_A},\\[0.5ex]
 \tau_A &= \left[\frac{\mu_0\,\rho(0)\,r_{100}^{\,2}}{B_0^{\,2}}\right]^{1/2},\\[0.5ex]
-\tau_R(r) &= \mu_0\,r^{\,2}\,\sigma_{ee}\,Q_{00}^{ee},\\[0.5ex]
-\sigma_{ee}(r) &=\frac{n_e\,e^{\,2}\,\tau_{ee}}{m_e},\\[0.5ex]
+\hat{\tau}_w &= \frac{\tau_w}{\tau_A},\\[0.5ex]
+f_k &=f_{b\,k}+f_{c\,k} + f_{p\,k} + f_{w\,k} + f_{s\,k},
+\end{align}
+Here, ${\cal I} = 0.8227$, $\epsilon_{100}=r_{100}/R_0$, $\hat{r}=r/r_{100}$, $\hat{r}_k=r_k/r_{100}$, $\hat{t}=t/\tau_A$, and $\rho(r)$ is the plasma
+mass density profile.
+
+The perturbed bootstrap current terms take the form
+\begin{align}
 f_{b\,k} &= f_{b\,e\,k}+f_{b\,i\,k},\\[0.5ex]
@@
 f_{b\,T_i\,k}&=\left(\frac{\eta_i}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{T_i\,k}^{\,2}+\hat{\rho}_{\theta\,i\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
-f_{b\,n_i\,k}&=\left(\frac{1}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{n_e\,k}^{\,2}+\hat{\rho}_{\theta\,i\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
+f_{b\,n_i\,k}&=\left(\frac{1}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{n_e\,k}^{\,2}+\hat{\rho}_{\theta\,i\,k}^{\,2}+\hat{W}_k^{\,2}},
+\end{align}
+where
+\begin{align}
+\alpha_{b\,e\,k} &= -2\,{\cal I}\,I_g\left(\frac{\omega_{\ast\,e}+\omega_{{\rm nc}\,e}}{\omega_\beta}\right)_{r_k},\\[0.5ex]
+\alpha_{b\,i\,k} &= 2\,{\cal I}\,I_g\left[\frac{(n_i/n_e)\left(\omega_{\ast\,i}+\omega_{{\rm nc}\,i}\right)+(Z_I\,n_I/n_e)\left(\omega_{\ast\,I}+\omega_{{\rm nc}\,I}\right)}{\omega_\beta}\right]_{r_k},\\[0.5ex]
+\omega_{\beta}(r)&= \frac{s\,g\,B_0}{\mu_0\,n_e\,e\,R_0^{\,2}\,q},\\[0.5ex]
+\hat{W}_{T_e\,k} &=\frac{{\cal I}\,W_{T_e\,k}}{2\,r_k} ,\\[0.5ex]
+\hat{W}_{T_i\,k} &= \frac{{\cal I}\,W_{T_i\,k}}{2\,r_k},\\[0.5ex]
+\hat{W}_{n_e\,k} &= \frac{{\cal I}\,W_{n_e\,k}}{2\,r_k},\\[0.5ex]
+\hat{\rho}_{\theta\,e\, k} &= \left(\frac{{\cal I}\,\rho_{\theta\,e}}{2\,r}\right)_{r_k}=\left(\frac{2\,{\cal I}\,v_{T\,e}\,m_e\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},\\[0.5ex]
+\hat{\rho}_{\theta\,i\,k} &= \left(\frac{{\cal I}\,\rho_{\theta\,i}}{2\,r}\right)_{r_k}= \left(\frac{2\,{\cal I}\,v_{T\,i}\,m_i\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},
+\end{align}
+and $I_g = 1.58$.
+
+The curvature terms take the form
+\begin{align}
 f_{c\,k} &= \alpha_{c\,k}\left(f_{c\,T_e\,k} + f_{c\,n_e\,k} + f_{c\,T_i\,k} + f_{c\,n_i\,k}\right),\\[0.5ex]
@@
 f_{c\,T_i\,k}&=\left(\frac{n_i}{n_e+n_i}\,\frac{\eta_i}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{T_i\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
-f_{c\,n_i\,k}&=\left(\frac{n_i}{n_e+n_i}\,\frac{1}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{n_e\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
+f_{c\,n_i\,k}&=\left(\frac{n_i}{n_e+n_i}\,\frac{1}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{n_e\,k}^{\,2}+\hat{W}_k^{\,2}},
+\end{align}
+where
+\begin{align}
+\alpha_{c\,k} &= 2\,{\cal I}\,I_g\,D_R(r_k).
+\end{align}
+Here, $D_R(r)$ is the Glasser-Greene-Johnson resistive interchange stability parameter.
+
+The ion polarization terms take the form
+\begin{align}
 f_{p\,k} &= \alpha_{p\,k}\left(f_{p\,T_i\,k} + f_{p\,n_i\,k}\right),\\[0.5ex]
 f_{p\,T_i\,k}&=\left(\frac{\eta_i}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k}{(\hat{W}_{T_i\,k}^{\,2}+\hat{W}_k^{\,2})^{\,2}},\\[0.5ex]
-f_{p\,n_i\,k}&=\left(\frac{1}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k}{(\hat{W}_{n_e\,k}^{\,2}+\hat{W}_k^{\,2})^{\,2}},\\[0.5ex]
-\hat{W}_k &=\frac{{\cal I}\,W_k}{2\,r_k}=\frac{2\,{\cal I}}{\epsilon_{100}\,\hat{r}_k}\left(\frac{q}{g\,s}\right)^{1/2}_{r_k} (X_k^{\,2} + Y_k^{\,2})^{\,1/4},\\[0.5ex]
-\hat{W}_{T_e\,k} &=\frac{{\cal I}\,W_{T_e\,k}}{2\,r_k} ,\\[0.5ex]
-\hat{W}_{T_i\,k} &= \frac{{\cal I}\,W_{T_i\,k}}{2\,r_k},\\[0.5ex]
-\hat{W}_{n_e\,k} &= \frac{{\cal I}\,W_{n_e\,k}}{2\,r_k},\\[0.5ex]
-\hat{\rho}_{\theta\,e\, k} &= \left(\frac{{\cal I}\,\rho_{\theta\,e}}{2\,r}\right)_{r_k}=\left(\frac{2\,{\cal I}\,v_{T\,e}\,m_e\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},\\[0.5ex]
-\hat{\rho}_{\theta\,i\,k} &= \left(\frac{{\cal I}\,\rho_{\theta\,i}}{2\,r}\right)_{r_k}= \left(\frac{2\,{\cal I}\,v_{T\,i}\,m_i\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},\\[0.5ex]
-\hat{\delta}_k &= \frac{\delta_{\rm linear}(r_k)}{R_0\,\epsilon_{100}\,\hat{r}_k},\\[0.5ex]
-\alpha_{b\,e\,k} &= -2\,{\cal I}\,I_g\left(\frac{\omega_{\ast\,e}+\omega_{{\rm nc}\,e}}{\omega_\beta}\right)_{r_k},\\[0.5ex]
-\alpha_{b\,i\,k} &= 2\,{\cal I}\,I_g\left[\frac{(n_i/n_e)\left(\omega_{\ast\,i}+\omega_{{\rm nc}\,i}\right)+(Z_I\,n_I/n_e)\left(\omega_{\ast\,I}+\omega_{{\rm nc}\,I}\right)}{\omega_\beta}\right]_{r_k},\\[0.5ex]
-\alpha_{c\,k} &= 2\,{\cal I}\,I_g\,D_R(r_k),\\[0.5ex]
+f_{p\,n_i\,k}&=\left(\frac{1}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k}{(\hat{W}_{n_e\,k}^{\,2}+\hat{W}_k^{\,2})^{\,2}},
+\end{align}
+where
+\begin{align}
 \alpha_{p\,k} &= 8\,{\cal I}^{\,3}\, I_p\left[\frac{(\omega_{\ast\,i}+\omega_{{\rm nc}\,i})\,\omega_{{\rm nc}\,i}}{\omega_\beta\,\omega_{\mit\Omega}}\right]_{r_k},\\[0.5ex]
-\omega_{\beta}(r)&= \frac{s\,g\,B_0}{\mu_0\,n_e\,e\,R_0^{\,2}\,q},\\[0.5ex]
-\omega_{\mit\Omega}(r)&= \frac{e\,g\,B_0\,s\,q}{m_i},\\[0.5ex]
-f_{s\,k} &=\frac{f_{s\,1\,k} \,\hat{W}_{T_e\,k}^{\,2}+ f_{s\,2\,k} \,\hat{W}_k^{\,2}}{\hat{W}_{T_e\,k}^{\,2}+ \hat{W}_k^{\,2}},\\[0.5ex]
+\omega_{\mit\Omega}(r)&= \frac{e\,g\,B_0\,s\,q}{m_i}
+\end{align}
+where $I_=1.38$.
+
+The wall stabilization terms take the form
+\begin{equation}
+f_{w\,k} = \frac{{\mit\Sigma}_{kw}^{\,2}}{{\mit\Delta}_{kw}}.
+\end{equation}
+
+Finally, the island saturation terms take the form 
+\begin{align}
+f_{s\,k} &=-\left(\frac{f_{s\,1\,k} \,\hat{W}_{T_e\,k}^{\,2}+ f_{s\,2\,k} \,\hat{W}_k^{\,2}}{\hat{W}_{T_e\,k}^{\,2}+ \hat{W}_k^{\,2}}\right),\\[0.5ex]
 f_{s\,1\,k} &= P_{1\,k}\,\frac{W_k}{r_k}\,\ln\left(\frac{r_k}{W_k}\right)+ P_{2\,k}\,\frac{W_k}{r_k},\\[0.5ex]
@@
 P_{1\,k} &= 0.41\,A_k^{\,2},\\[0.5ex]
-P_{2\,k} &= 0.41\left(A_k^{\,2}\left[\ln\left(\frac{1}{r_k}\right)+4.85\right] - \frac{{\mit\Sigma}_k'\,A_k}{2} - B_k - 0.44\,A_k\right),\\[0.5ex]
-P_{3\,k} &= 0.8\,A_k^{\,2} - 0.27\,B_k-0.09\,A_k,\\[0.5ex]
-A_k &= -\left(\frac{r\,q\,\hat{J}_\phi'}{s}\right)_{r_k},\\[0.5ex]
-B_k &= -\left(\frac{r^{\,2}\,q\,\hat{J}_\phi''}{s}\right)_{r_k}.
+P_{2\,k} &= 0.41\left(A_k^{\,2}\left[\ln\left(\frac{1}{r_k}\right)+4.85\right] - \frac{{\mit\Sigma}_k^{nw}\,A_k}{2} - B_k - 0.44\,A_k\right),\\[0.5ex]
+P_{3\,k} &= 0.8\,A_k^{\,2} - 0.27\,B_k-0.09\,A_k.
 \end{align}
-Here, ${\cal I}=0.8227$, $I_g=1.58$, $I_p=1.38$, $\epsilon_{100}=r_{100}/R_0$, $\hat{r}=r/r_{100}$, $\hat{r}_k=r_k/r_{100}$, and $\hat{t}=t/\tau_A$.
-Furthermore, $\delta_{\rm linear}(r)$ is the linear layer width, whereas $\rho(r)$ is the plasma
-mass density profile. Finally,
-\begin{equation}
-\hat{J}_\phi(r) = - \frac{\mu_0\,R_0\,R}{B_0}\,\frac{dP}{d{\mit\Psi}_p} - R_0^{\,2}\,B_0\,g\,\frac{dg}{d{\mit\Psi}_p},
-\end{equation}
-where $P({\mit\Psi}_p)$ is the total plasma pressure,  the previous expression is evaluated on the outboard mid-plane, and
-$\hat{J}_\phi'\equiv d\hat{J}_\phi/dr$, $\hat{J}_\phi''\equiv d^{\,2}\hat{J}_\phi/dr^{\,2}$.
-
-The quantity ${\mit\Sigma}_k'$ is
-defined as
-\begin{equation}
-{\mit\Sigma}_k' = \lim_{\delta\rightarrow 0}\left[\left.\frac{r\,\psi'}{\psi}\right|_{r_k-\delta}+ \left.\frac{r\,\psi'}{\psi}\right|_{r_k+\delta}
--2\,A_k\,(1+\ln\delta)\right],
-\end{equation}
-where $\psi(r)$ is the solution of 
-\begin{equation}
-\frac{d^{\,2}\psi}{dr^{\,2}}+ \frac{1}{r}\,\frac{d\psi}{dr}-\frac{m^{\,2}}{r^{\,2}}\,\psi - \frac{\hat{J}_\phi'\,\psi}{r\,(1/q-n/m_k)}=0
-\end{equation}
-that is well-behaved at $r=0$, and satisfies $r\,\psi'/\psi = -m$ at $r=r_{100}$. Here, $\psi'\equiv d\psi/dr$.
 
@@
 region corresponds to $\hat{W}_k\gg\hat{\delta}_k$.
-
-\subsection{Linear Layer Width}\label{linear}
-Let
-\begin{align}
-\tau_H(r) &= \frac{R_0}{B_0\,g}\,\frac{\sqrt{\mu_0\,\rho}}{n\,s},\\[0.5ex]
-\tau_E(r) &= \frac{r^{\,2}}{D_\perp + (2/3)\,\chi_e},\\[0.5ex]
-\tau_M(r) &= \frac{R_0^{\,2}\,q^{\,2}}{\chi_\phi},\\[0.5ex]
-\rho_s (r)&= \frac{\sqrt{m_i\,T_e}}{e\,B_0\,g},\\[0.5ex]
-\tau(r)& = -\frac{\omega_{\ast\,i}}{\omega_{\ast\,e}},\\[0.5ex]
-S(r) &= \frac{\tau_R}{\tau_H},\\[0.5ex]
-P_M(r) &= \frac{\tau_R}{\tau_M},\\[0.5ex]
-P_E(r) &= \frac{\tau_R}{\tau_E},\\[0.5ex]
-D(r)&= \frac{5}{3}\,S^{\,1/3}\,\frac{\rho_s}{r},\\[0.5ex]
-Q_E(r)&= S^{\,1/3}\,n\,\omega_E\,\tau_H,\\[0.5ex]
-Q_{e,i}(r)&= -S^{\,1/3}\,n\,\omega_{\ast\,e,i}\,\tau_H
-\end{align}
-The constant-$\psi$ linear layer width is determined from the solution of
-\begin{equation}
-\frac{d^{\,2}\,Y}{dp^{\,2}} -\left[\frac{-Q_E\,(Q_E-Q_i)+{\rm i}\,(Q_E-Q_i)\,(P_M+P_E)\,p^{\,2}+
-P_M\,P_E\,p^{\,4}}
-{{\rm i}\,(Q_E-Q_e) +\{P_E + {\rm i}\,(Q_E-Q_i)\,D^{\,2}\}\,p^{\,2}+(1+\tau)\,P_M\,D^{\,2}\,p^{\,4}}
-\right] p^{\,2}\, Y = 0.
-\end{equation}
-If the small-$p$ behavior of solution of the previous equation that is well-behaved as $p\rightarrow \infty$ is
-\begin{equation}
-Y(p) = Y_0\left[1 - c\,p+{\cal O}(p^{\,2})\right].
-\end{equation}
-then the 
-linear layer width is 
-\begin{equation}
-\frac{\delta_{\rm linear}}{r} = \frac{\pi\,|c|}{S^{\,1/3}}.
-\end{equation}
 
@@
 where
-\begin{equation}\label{e24a}
-\delta \hat{T}_k=\sum_{k'=1,K}\hat{E}_{kk'}\,\hat{\mit\Psi}_k\,\hat{\mit\Psi}_{k'}\,\sin(\varphi_k-\varphi_{k'}-\xi_{kk'})+\hat{E}_{kk}\,\hat{\mit\Psi}_k\,\hat{\chi}_k\,\sin(\varphi_k-\zeta_k).
-\end{equation}
+\begin{align}\label{e24a}
+\delta \hat{T}_k&= \sum_{k'=1,K}\hat{E}_{kk'}\left[(Y_k\,X_{k'}-X_k\,Y_{k'})\,\cos\xi_{kk'}- (X_k\,X_{k'}+Y_k\,Y_{k'})\,\sin\xi_{kk'}\right]\nonumber\\[0.5ex]
+&\phantom{=}+{\mit\Sigma}_{kw}\,(Y_k\,U_k-X_k\,V_k)+\hat{E}_{kk'}\,\hat{\chi}_k\,(Y_k\,\cos\zeta_k-X_k\,\sin\zeta_k).
+\end{align}
 Here, $Q_k = Q(r_k)$, $\hat{\rho}_k=\rho(r_k)/\rho(0)$, $\hat{\tau}_{M\,k}= r_{100}^{\,2}/[\chi_\phi(r_k)\,\tau_A]$,  $\hat{\tau}_{\theta\,k}=\tau_\theta(r_k)/\tau_A$, $\hat{\tau}_{{\rm cx}\,k} =\tau_{{\rm cx}}(r_k)/\tau_A$.
-Moreover, $\chi_\phi(r)$ is the perpendicular toroidal momentum diffusivity profile, whereas
+Moreover, 
 \begin{equation}\label{a70}
@@
 \begin{equation}\label{elin}
- \varpi_{e,k} = - n\,(\omega_E+\omega_{\ast\,e})_{r_k}.
+ \varpi_{e\,k} = - n\,(\omega_E+\omega_{\ast\,e})_{r_k}.
 \end{equation}

### 2021-09-26 Documentation/EPEC_Model.tex
Added Sphinx documetation

@@
 {\mit\Sigma}_{kw} &= \frac{2m\,(r_{100}/r_w)^{\,m}}{1-(r_{100}/r_w)^{\,2m}}\,\frac{\psi_{pw}(r_{100})}{\psi_{pw}(r_k)},\\[0.5ex]
-{\mit\Delta}_{kw} &= -\frac{{\mit\Sigma}_{kw}^{\,2}}{{\mit\Delta}^{nw}_k-{\mit\Delta}^{pw}_k},\\[0.5ex]
+{\mit\Delta}_{kw} &= -\left(\frac{{\mit\Sigma}_{kw}^{\,2}}{{\mit\Delta}^{nw}_k-{\mit\Delta}^{pw}_k}\right),\\[0.5ex]
 B_k &= -\left(\frac{r^{\,2}\,q\,\hat{J}_\phi''}{s}\right)_{r_k},
 \end{align}
-where $\hat{J}_\phi'' \equiv d^2\hat{J}_\phi/dr^{\,2}$.
+where $\hat{J}_\phi'' \equiv d^{\,2}\hat{J}_\phi/dr^{\,2}$.
 
@@
 \subsection{Plasma Species}\label{a3}
-The plasma is assumed to consist of three (charged) species; namely,  electrons ($e$), majority ions ($i$), and impurity ions
+The plasma is assumed to consist of three (charged) species (with Maxwellian distribution functions); namely,  electrons ($e$), majority ions ($i$), and impurity ions
 ($I$).  The charges of the  three species are $e_e=-e$, $e_i= e$, and $e_I=Z_I\,e$, respectively, where
@@
 \tau_H(r) &= \frac{R_0}{B_0\,g}\,\frac{\sqrt{\mu_0\,\rho}}{n\,s},\\[0.5ex]
+\rho(r)&= m_i\left[n_i(r) + n_b(r)\right] + m_I\,n_I(r),\\[0.5ex]
 \tau_E(r) &= \frac{r^{\,2}}{D_\perp + (2/3)\,\chi_e},\\[0.5ex]
@@
 Here, $\chi_e(r)$, $D_\perp(r)$, and $\chi_\phi(r)$ are the perpendicular electron energy, particle,
-and toroidal momentum diffusivity profiles, respectively. 
+and toroidal momentum diffusivity profiles, respectively. Moreover, $n_b(r)$ is the number density of fast (as opposed to thermal) majority ions. 
 The constant-$\psi$ linear layer width is determined from the solution of
@@
 \chi_{\parallel\,e}^{\rm brag} &= \frac{1.55\,\tau_{ee}\,v_{T\,e}^{\,2}}{1+0.38\,Z_{\rm eff}},\\[0.5ex]
-\chi_{\parallel\,e}^{\rm max} &= \frac{2\,R_0\,v_{T\,e}}{n\,s}\,\frac{r_k}{W_{T_e\,k}}.
+\chi_{\parallel\,e}^{\rm max} &= \frac{2\,R_0\,v_{T\,e}}{n\,s}\,\frac{r_k}{W_{T_e\,k}}\label{e64d}
 \end{align}
-Equation~(\ref{e64g}) must be solved iteratively for $W_{T_e\,k}/r_k$.
+Equations~(\ref{e64g})--(\ref{e64d}) must be solved iteratively for $W_{T_e\,k}/r_k$.
 
@@
 \chi_{\parallel\,i}^{\rm brag} &= 1.95\,\tau_{ii}\,v_{T\,i}^{\,2},\\[0.5ex]
-\chi_{\parallel\,i}^{\rm max} &= \frac{2\,R_0\,v_{T\,i}}{n\,s}\,\frac{r_k}{W_{T_i\,k}}.
+\chi_{\parallel\,i}^{\rm max} &= \frac{2\,R_0\,v_{T\,i}}{n\,s}\,\frac{r_k}{W_{T_i\,k}}.\label{e64rr}
 \end{align}
-Equation~(\ref{e64gg}) must be solved iteratively for $W_{T_i\,k}/r_k$.
+Equations~(\ref{e64gg})--(\ref{e64rr}) must be solved iteratively for $W_{T_i\,k}/r_k$.
 
@@
 \chi_{\parallel\,i}^{\rm brag} &= 1.95\,\tau_{ii}\,v_{T\,i}^{\,2},\\[0.5ex]
-\chi_{\parallel\,i}^{\rm max} &= \frac{2\,R_0\,v_{T\,i}}{n\,s}\,\frac{r_k}{W_{n_e\,k}}.
+\chi_{\parallel\,i}^{\rm max} &= \frac{2\,R_0\,v_{T\,i}}{n\,s}\,\frac{r_k}{W_{n_e\,k}}.\label{e64fff}
 \end{align}
-Equation~(\ref{e64ggg}) must be solved iteratively for $W_{n_e\,k}/r_k$.
+Equations~(\ref{e64ggg})--(\ref{e64fff}) must be solved iteratively for $W_{n_e\,k}/r_k$.
 
@@
 \end{align}
-Here, ${\cal I} = 0.8227$, $\epsilon_{100}=r_{100}/R_0$, $\hat{r}=r/r_{100}$, $\hat{r}_k=r_k/r_{100}$, $\hat{t}=t/\tau_A$, and $\rho(r)$ is the plasma
-mass density profile.
+Here, ${\cal I} = 0.8227$, $\epsilon_{100}=r_{100}/R_0$, $\hat{r}=r/r_{100}$, $\hat{r}_k=r_k/r_{100}$, and $\hat{t}=t/\tau_A$. Note that the EPEC resonant plasma response model interpolates smoothly
+between the linear regime and the
+nonlinear Rutherford regime. The linear regime corresponds to $\hat{W}_k\ll\hat{\delta}_k$, whereas the nonlinear
+region corresponds to $\hat{W}_k\gg\hat{\delta}_k$.
 
-The perturbed bootstrap current terms take the form
+The perturbed bootstrap current terms in the response model take the form
 \begin{align}
@@
 \end{align}
-where $I_=1.38$.
+and  $I_p=1.38$.
 
@@
 \end{align}
-
-Note that the EPEC resonant plasma response model interpolates smoothly
-between the linear regime and the
-nonlinear Rutherford regime. The linear regime corresponds to $\hat{W}_k\ll\hat{\delta}_k$, whereas the nonlinear
-region corresponds to $\hat{W}_k\gg\hat{\delta}_k$.
 
@@
 \delta \hat{T}_k&= \sum_{k'=1,K}\hat{E}_{kk'}\left[(Y_k\,X_{k'}-X_k\,Y_{k'})\,\cos\xi_{kk'}- (X_k\,X_{k'}+Y_k\,Y_{k'})\,\sin\xi_{kk'}\right]\nonumber\\[0.5ex]
-&\phantom{=}+{\mit\Sigma}_{kw}\,(Y_k\,U_k-X_k\,V_k)+\hat{E}_{kk'}\,\hat{\chi}_k\,(Y_k\,\cos\zeta_k-X_k\,\sin\zeta_k).
+&\phantom{=}+{\mit\Sigma}_{kw}\,(Y_k\,U_k-X_k\,V_k)+\hat{E}_{kk}\,\hat{\chi}_k\,(Y_k\,\cos\zeta_k-X_k\,\sin\zeta_k).
 \end{align}

### 2021-09-28 Documentation/EPEC_Model.tex
Added TOFF and electromagnetic torque plots

@@
 where $q_k= m_k/n$, and $a_{kk}(r) = \oint |\nabla r|^{-2}\,d\theta/(2\pi)$.
+
+\subsection{Glasser-Greene-Johnson Data}
+Let us write
+\begin{equation}
+{\bf B} = \nabla\phi\times\nabla\psi_p+g(\psi_p)\,\nabla\phi.
+\end{equation}
+The angle $\theta^{\,\ast}$ is defined such that
+\begin{equation}
+\nabla\phi\times\nabla\psi_p\cdot\nabla\theta^{\,\ast} = \gamma(\psi_p)\,B.
+\end{equation}
+Let
+\begin{align}
+J_1(\psi_p) &= \oint\frac{1}{B}\,\frac{d\theta^{\,\ast}}{2\pi},\\[0.5ex]
+J_2(\psi_p) &= \oint B\,\frac{d\theta^{\,\ast}}{2\pi},\\[0.5ex]
+J_3(\psi_p) &= \oint\frac{1}{B^{\,3}}\,\frac{d\theta^{\,\ast}}{2\pi},\\[0.5ex]
+J_4(\psi_p) &= \oint\frac{1}{B\,|\nabla\psi_p|^{\,2}}\,\frac{d\theta^{\,\ast}}{2\pi},\\[0.5ex]
+J_5(\psi_p) &= \oint\frac{B}{|\nabla\psi_p|^{\,2}}\,\frac{d\theta^{\,\ast}}{2\pi},\\[0.5ex]
+J_6(\psi_p) &= \oint\frac{1}{B^{\,3}\,|\nabla\psi_p|^{\,2}}\,\frac{d\theta^{\,\ast}}{2\pi}.
+\end{align}
+It follows that
+\begin{align}
+E(\psi_p) &= - \frac{dP/d\psi_p}{(dq/d\psi_p)^{\,2}}\,\frac{1}{\gamma}\left[\frac{d}{d\psi_p}\!\left(\frac{J_1}{\gamma}\right) - g\,\frac{dq}{d\psi_p}\,\frac{J_1}{J_2}\right]J_5,\\[0.5ex]
+F(\psi_p) &= \frac{(dP/d\psi_p)^{\,2}}{(dq/d\psi_p)^{\,2}}\,\frac{1}{\gamma^{\,2}}\left[g^{\,2}\left(J_5\,J_6- J_4^{\,2}\right)+ J_5\,J_3\right],
+\\[0.5ex]
+H(\psi_p)&= \frac{dP/d\psi_p}{dq/d\psi_p}\,\frac{g}{\gamma}\left(J_4 - \frac{J_1\,J_5}{J_2}\right),
+\end{align}
+where $P(\psi_p)$ is the total plasma pressure. 
+Finally,
+\begin{equation}
+D_R(\psi_p)= E + F + H^{\,2}.
+\end{equation}
 

### 2021-09-28 Flux/Source/Stage2.cpp

@@ -178,11 +178,11 @@ void Flux::WriteStage2Netcdfc ()
   
   // Basic parameters
   int para_d, para;
-  double parameters[11] = {R0, B0, RLEFT, ZLOW, RRIGHT, ZHIGH, Raxis, Zaxis, q95, PSILIM, PSIRAT};
-  err += nc_def_dim (dataFile, "index", 11, &para_d);
+  double parameters[12] = {R0, B0, RLEFT, ZLOW, RRIGHT, ZHIGH, Raxis, Zaxis, q95, PSILIM, PSIRAT, PSIPED};
+  err += nc_def_dim (dataFile, "index", 12, &para_d);
   err += nc_def_var (dataFile, "Parameters", NC_DOUBLE, 1, &para_d, &para);
-  nc_put_att_text   (dataFile, para, "Contents", strlen ("R0 B0 RLEFT ZLOW RRIGH ZHIGH RAXIS ZAXIS q95 PSILIM PSIRAT"),
-		     "R0 B0 RLEFT ZLOW RRIGH ZHIGH RAXIS ZAXIS q95 PSILIM PSIRAT");
+  nc_put_att_text   (dataFile, para, "Contents", strlen ("R0 B0 RLEFT ZLOW RRIGH ZHIGH RAXIS ZAXIS q95 PSILIM PSIRAT PSIPED"),
+		     "R0 B0 RLEFT ZLOW RRIGH ZHIGH RAXIS ZAXIS q95 PSILIM PSIRAT PSIPED");
   
   // Plasma boundary
   int bound_d, bound_r, bound_z;

### 2021-09-28 Neoclassical/Source/fFileInterpolate.cpp

@@ -131,14 +131,14 @@ void Neoclassical::fFileInterpolateLinear (char* fFile1, double time1, char* fFi
   int             NPSI_1, NTOR_1, nres_1;
   Array<double,1> v1_1, v2_1, v3_1;
   Array<int, 1>   mres_1;
-  Array<double,1> u1_1, u2_1, u3_1, u4_1, u5_1, u6_1, u7_1, u8_1, u9_1, u10_1, u11_1, u12_1, u13_1, u14_1, u15_1, u16_1, u17_1, u18_1, u19_1, u20_1;
+  Array<double,1> u1_1, u2_1, u3_1, u4_1, u5_1, u6_1, u7_1, u8_1, u9_1, u10_1, u11_1, u12_1, u13_1, u14_1, u15_1, u16_1, u17_1, u18_1, u19_1, u20_1, u21_1, u22_1;
   Array<double,2> Freal_1, Fimag_1, Ereal_1, Eimag_1;
   
   double          r1_0, r2_0, r3_0, r4_0, r5_0, r6_0, r7_0, r8_0, r9_0, r10_0, r11_0, r12_0, r13_0;
   int             NPSI_0, NTOR_0, nres_0;
   Array<double,1> v1_0, v2_0, v3_0;
   Array<int, 1>   mres_0;
-  Array<double,1> u1_0, u2_0, u3_0, u4_0, u5_0, u6_0, u7_0, u8_0, u9_0, u10_0, u11_0, u12_0, u13_0, u14_0, u15_0, u16_0, u17_0, u18_0, u19_0, u20_0;
+  Array<double,1> u1_0, u2_0, u3_0, u4_0, u5_0, u6_0, u7_0, u8_0, u9_0, u10_0, u11_0, u12_0, u13_0, u14_0, u15_0, u16_0, u17_0, u18_0, u19_0, u20_0, u21_0, u22_0;
   Array<double,2> Freal_0, Fimag_0, Ereal_0, Eimag_0;
 
   // ................
@@ -171,14 +171,15 @@ void Neoclassical::fFileInterpolateLinear (char* fFile1, double time1, char* fFi
   u10_1.resize  (nres_1); u11_1.resize (nres_1); u12_1.resize (nres_1);
   u13_1.resize  (nres_1); u14_1.resize (nres_1); u15_1.resize (nres_1);
[…]

### 2021-09-28 Phase/Source/Phase.cpp

@@ -148,6 +148,9 @@ void Phase::Read_Data ()
   CHIR   = 1.;
   HIGH   = 1;
   RATS   = 1;
+
+  TAUW   = 1.;
+  TOFF   = 0.;
   
   // Read input data from namelists (Inputs/Phase.nml, Inputs/Waveform.nml)
   printf ("........................................................................................\n");
@@ -159,8 +162,8 @@ void Phase::Read_Data ()
   PCTRL = new double[MAXCONTROLPOINTNUMBER];
 
   NameListRead (&NFLOW, &STAGE5, &INTF, &INTN, &INTU, &NATS, &OLD, &FREQ, &LIN, &MID, &COPT,
-		&DT, &TSTART, &TEND, &SCALE, &PMAX, &CHIR, &HIGH, &RATS, &CORE, &FFAC, 
-		&CXD, &BOOT, &CURV, &POLZ, &NCTRL, TCTRL, ICTRL, PCTRL);
+		&DT, &TSTART, &TEND, &TOFF, &SCALE, &PMAX, &CHIR, &HIGH, &RATS, &CORE, &FFAC, 
+		&CXD, &BOOT, &CURV, &POLZ, &TAUW, &NCTRL, TCTRL, ICTRL, PCTRL);
 
   TT.resize (NCTRL);
   
@@ -202,27 +205,37 @@ void Phase::Read_Data ()
       printf ("PHASE:: Invalid MID value\n");
       exit (1);
     }
-
+  if (TAUW < 0.)
+    {
+      printf ("PHASE:: Invalid TAUW value\n");
+      exit (1);
+    }
+  if (TOFF < 0.)
+    {
+      printf ("PHASE:: Invalid TOFF value\n");
+      exit (1);
+    }
+  
   for (int i = 0; i < NCTRL; i++)
-    printf ("T = %11.4e  IRMP = %11.4e  PRMP/pi = %11.4e\n", TCTRL[i], ICTRL[i], PCTRL[i]/M_PI);
+    printf ("T = %10.3e  IRMP = %10.3e  PRMP/pi = %10.3e\n", TCTRL[i], ICTRL[i], PCTRL[i]/M_PI);
 
   // .............................
   // Output calculation parameters
   // .............................
[…]

### 2021-10-01 Phase/Source/fFileInterpolate.cpp
Minor changes

@@ -1313,7 +1313,7 @@ void Phase::fFileInterpolateQuartic (char* fFile1, double time1, char* fFile2, d
   u10_4.resize  (nres_4); u11_4.resize (nres_4); u12_4.resize (nres_4);
   u13_4.resize  (nres_4); u14_4.resize (nres_4); u15_4.resize (nres_4);
   u16_4.resize  (nres_4); u17_4.resize (nres_4); u18_4.resize (nres_4);
-  u19_4.resize  (nres_4); u19_4.resize (nres_4); u21_4.resize (nres_4);
+  u19_4.resize  (nres_4); u20_4.resize (nres_4); u21_4.resize (nres_4);
   u22_4.resize  (nres_4);
   
   for (int j = 0; j < nres_4; j++)
@@ -1506,7 +1506,7 @@ void Phase::fFileInterpolateQuartic (char* fFile1, double time1, char* fFile2, d
   for (int j = 0; j < nres_0; j++)
     fprintf (file, "%d %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e %16.9e\n",
 	     mres_0(j), u1_0(j), u2_0(j), u3_0(j), u4_0(j), u5_0(j), u6_0(j), u7_0(j), u8_0(j), u9_0(j), u10_0(j), u11_0(j), u12_0(j),
-	     u13_0(j), u14_0(j), u15_0(j), u16_0(j), u17_0(j), u18_0(j), u19_0(j), u20_0(j));
+	     u13_0(j), u14_0(j), u15_0(j), u16_0(j), u17_0(j), u18_0(j), u19_0(j), u20_0(j), u21_0(j), u22_0(j));
   for (int j = 0; j < nres_0; j++)
     for (int k = 0; k < nres_0; k++)
       fprintf (file, "%d %d %16.9e %16.9e\n",

### 2021-10-07 Rescale/Source/Field.h
Improved documentation

@@ -33,13 +33,16 @@ class Field
 
   void resize (int n);
   
-  int    GetN ();
-  void   PushData (int i, double  x, double  y, double  dydx);
-  void   PullData (int i, double& x, double& y, double& dydx);
-  double GetX     (int i);
-  double GetY     (int i);
-  double GetdYdX  (int i);
-  void   Rescale  (double A1);
+  int    GetN       ();
+  void   PushData   (int i, double  x, double  y, double  dydx);
+  void   PullData   (int i, double& x, double& y, double& dydx);
+  double GetX       (int i);
+  double GetY       (int i);
+  double GetdYdX    (int i);
+  void   Rescale    (double scale);
+  void   Shift      (double shift);
+  void   ShiftScale (Field& A, double shift);
+  void   Copy       (Field& copy);
   
   // -----------------------
   // Private class functions

### 2021-10-22 Documentation/TearingModeTheory.tex
Changed definition of Waveform 2 pulse frequency

\documentclass[notitlepage,12pt]{article}
\usepackage {amsmath}
\pdfoutput = 1 
\usepackage {graphicx}
\usepackage{fullpage}
\allowdisplaybreaks
\newcommand {\bpsi} {\mbox{\boldmath$\psi$}}
\newcommand {\brho} {\mbox{\boldmath$\rho$}}
\newcommand{\bmu}{\mbox{\boldmath$\mu$}}
\newcommand{\bzeta}{\mbox{\boldmath$\zeta$}}
\newcommand{\bpi}{\mbox{\boldmath$\pi$}}
\newcommand{\bsigma}{\mbox{\boldmath$\sigma$}}
\newcommand{\bomega}{\mbox{\boldmath$\omega$}}

\begin{document}
\title{\bf Tearing Modes in Tokamak Plasmas}
\author{R.~Fitzpatrick\,\footnote{rfitzp@utexas.edu}\\
Institute for Fusion Studies,\\  Department of Physics,\\  University of Texas at Austin,\\  Austin TX 78712, USA}
\maketitle

\section{Fluid Theory}
\subsection{Fundamental Quantities}
Consider an idealized tokamak plasma consisting of an equal number of electrons, with
mass $m_e$ and charge $-e$ (here, $e$ denotes the  magnitude of the electron
charge), and ions, with  mass $m_i$ and charge $+e$. We shall employ 
the symbol
\begin{equation}
T_s = \frac{1}{3} \,m_s\, \langle v_s^{2}\rangle
\end{equation}
to denote a {\em kinetic temperature}\/   measured in units of energy.
Here, $v$ is a particle speed, and the angular brackets denote an
ensemble average (Reif 1965). The kinetic temperature of species $s$ is a measure of 
the mean kinetic energy of particles of
that species. (Here, $s$ represents either $e$ for electrons, or $i$ for ions.) In tokamak plasma physics, kinetic temperature
is invariably measured in {\em electron-volts}\/ \index{electron-volt} (1 joule is equivalent to
$6.24\times 10^{18}$\,eV).

Quasi-neutrality demands that
\begin{equation}
n_i \simeq n_e, 
\end{equation}
where $n_s$ is the {\em particle number density} (that is, the number of particles 
per cubic meter) of species $s$ (Fitzpatrick 2015).

We can
estimate typical particle speeds in terms of the so-called {\em thermal speed}, 
\begin{equation}\label{e1.3}
v_{t\,s} = \left(\frac{2\,T_s}{m_s}\right)^{1/2}.
\end{equation}

In a tokamak plasma,  the ambient magnetic field, 
${\bf B}$,  is strong enough to significantly alter charged particle
trajectories. In particular,
magnetized plasmas are highly  anisotropic, responding differently to
forces that are parallel and perpendicular to the direction
of ${\bf B}$. As is well known, charged particles respond to the Lorentz force
by freely streaming in the direction of ${\bf B}$, while executing
circular  {\em gyro-orbits} in the plane perpendicular to ${\bf B}$ (Fitzpatrick 2008). 
The typical   {\em gyroradius}\/ of a charged particle 
gyrating in a
magnetic field is given by
\begin{equation}
\rho_s = \frac{v_{t\,s}}{{\mit\Omega}_s},
\end{equation}
where
\begin{equation}
{\mit\Omega}_s = \frac{e\,B}{m_s}
\end{equation}
is the  {\em gyrofrequency}\/ associated with the
gyration.

The electron-ion and ion-ion {\em collision times}\/ are
written
\begin{equation}\label{e3.74}
\tau_e = \frac{6\sqrt{2}\pi^{3/2}\,\epsilon_0^{2}\,\sqrt{m_e}\,\,T_e^{3/2}}
{\ln{\mit\Lambda}_c\, e^4\, n_e},
\end{equation}
and\index{collision!time!ion-ion}
\begin{equation}\label{e3.75}
\tau_i = \frac{ 12\pi^{3/2}\,\epsilon_0^{2}\,\sqrt{m_i}\,\,T_i^{3/2}}
{\ln{\mit\Lambda}_c\, e^4\, n_e},
\end{equation}
respectively (Fitzpatrick 2015). 
Here, $\ln{\mit\Lambda}_c\simeq 15$ is 
the  {\em Coulomb logarithm}\/ (Richardson 2019). Note that $\tau_e$ is the typical time required for the cumulative effect of electron-ion collisions to
deviate the path of an electron through $90^\circ$. Likewise, $\tau_i$ is the typical time required for the cumulative effect of ion-ion collisions to
deviate the path of an ion through $90^\circ$.

\subsection{Braginskii Equations}
The electron and ion fluid equations in a collisional plasma
take the form:
\begin{align}\label{e3.79a}
\frac{dn}{dt} + n\,\nabla\cdot{\bf V}_e &= 0,\\[0.5ex]
m_e \,n\,\frac{d {\bf V}_e}{dt} + \nabla p_e+ \nabla\cdot \bpi_e + e\, n\,
({\bf E} + {\bf V}_e\times {\bf B})& = {\bf F},\\[0.5ex]
\frac{3}{2}\frac{d p_e}{dt} + \frac{5}{2}\,p_e\,\nabla\cdot{\bf V}_e
+ \bpi_e:\nabla{\bf V}_e+ \nabla\cdot{\bf q}_e &= w_e,\label{e3.79c}
\end{align}
and
\begin{align}\label{e3.80a}
\frac{dn}{dt} + n\,\nabla\cdot{\bf V}_i &= 0,\\[0.5ex]
m_i \,n\,\frac{d {\bf V}_i}{dt} + \nabla p_i + \nabla\cdot \bpi_i - e\, n\,
({\bf E} + {\bf V}_i\times {\bf B})& =- {\bf F},\\[0.5ex]
\frac{3}{2}\frac{d p_i}{dt} + \frac{5}{2}\,p_i\,\nabla\cdot{\bf V}_i
+ \bpi_i:\nabla{\bf V}_i+ \nabla\cdot{\bf q}_i &= w_i,\label{e3.80c}
\end{align}
respectively. 
Equations (\ref{e3.79a})--(\ref{e3.79c}) and (\ref{e3.80a})--(\ref{e3.80c})  are called the {\em Braginskii equations}, because they were first obtained
in a celebrated article by S.I.~Braginskii (Braginskii 1965). Here, ${\bf V}_s$ is the species-$s$ flow velocity, $p_s=n\,T_s$ is the 
species-$s$ scalar
pressure, $\bpi_s$ is the species-$s$ viscosity tensor, ${\bf F}$ is the collisional friction force density, ${\bf q}_s$ is the species-$s$ heat flux density, $w_s$ is the species-$s$ collisional heating rate density, and ${\bf E}$ is the ambient electric field strength. Moreover, $d/dt\equiv \partial/\partial t + {\bf V}_e\cdot\nabla$ in the electron fluid equations, (\ref{e3.79a})--(\ref{e3.79c}), whereas  $d/dt\equiv \partial/\partial t + {\bf V}_i\cdot\nabla$ in the ion fluid equations,  (\ref{e3.80a})--(\ref{e3.80c}).

A tokamak plasma is highly magnetized. In other words, 
\begin{equation}
{\mit\Omega}_i\,\tau_i, \,\,\,{\mit\Omega}_e\, \tau_e \gg 1,
\end{equation}
 which implies that the electron and ion gyroradii are much  smaller than the
corresponding mean-free-paths between $90^\circ$ collisional scattering events. In this limit, a standard two-Laguerre-polynomial
Chapman-Enskog closure scheme (Chapman \& Cowling 1953) yields
\begin{align}\label{e3.91a}
{\bf F}&= n\,e\left(\frac{{\bf j}_\parallel}{\sigma_\parallel}
+\frac{{\bf j}_\perp}{\sigma_\perp}\right) -0.71\,n\,\nabla_\parallel T_e
-\frac{3\,n}{2\,{\mit\Omega}_e\,\tau_e}\,{\bf b}\times\nabla_\perp T_e,
\\[0.5ex]
w_i &= \frac{3\,m_e}{m_i} \frac{n\,(T_e-T_i)}{\tau_e},\\[0.5ex]
w_e &= -w_i + \frac{ {\bf j}\cdot {\bf F} }{n \,e}.
\end{align}
Here, ${\bf b}={\bf B}/B$ is a unit vector parallel to the magnetic field, and ${\bf j}= n\,e\,({\bf V}_i-{\bf V}_e)$ is the net plasma current density. 
Moreover, the {\em parallel electrical conductivity}, $\sigma_\parallel$,  is given by
\begin{equation}\label{e3.83}
\sigma_\parallel = 1.96\,\frac{n \,e^2\,\tau_e}{m_e}.
\end{equation} 
whereas the {\em perpendicular electrical conductivity}, $\sigma_\perp$,  takes the form
\begin{equation}\label{e3.92}
\sigma_\perp = 0.51\,\sigma_\parallel = \frac{n\,e^2\,\tau_e}{m_e}.
\end{equation}
Note that $\nabla_\parallel(\cdots) \equiv [{\bf b}\cdot\nabla
(\cdots)]\,{\bf b}$ denotes a
gradient parallel to the magnetic field, whereas $\nabla_\perp \equiv
 \nabla-\nabla_\parallel$ denotes a gradient perpendicular to the magnetic
field. Likewise, ${\bf j}_\parallel \equiv ({\bf b}\cdot{\bf j})\,{\bf b}$
represents the component of the plasma current flowing parallel to the
magnetic field, whereas ${\bf j}_\perp \equiv {\bf j} - {\bf j}_\parallel$
represents the perpendicular component of the plasma current.

In a highly magnetized plasma, the electron and ion heat flux densities are written 
\begin{align}
{\bf q}_e &= -\kappa_\parallel^e\,\nabla_\parallel T_e -\kappa_\perp^e\,
\nabla_\perp T_e
-\kappa_\times^e\,{\bf b}\times\nabla_\perp T_e- 0.71\,\frac{T_e}{e}\,{\bf j}_\parallel-
\frac{3\,T_e}{2\,{\mit\Omega}_e\,\tau_e\,e}\,{\bf b}\times{\bf j}_\perp,\label{e3.94a}\\[0.5ex]
{\bf q}_i &= -\kappa_\parallel^i\,\nabla_\parallel T_i -\kappa_\perp^i\,
\nabla_\perp T_i
+\kappa_\times^i\,{\bf b}\times\nabla_\perp T_i,\label{e3.94b}
\end{align}
respectively. Here, the {\em parallel thermal conductivities}, which control the diffusion of heat parallel to magnetic field-lines, are 
given by
\begin{align}\label{e3.87a}
\kappa_\parallel^e &= 3.2\,\,\frac{n\,\tau_e\,T_e}{m_e},\\[0.5ex]
\kappa_\parallel^i &= 3.9\,\,\frac{n\,\tau_i\,T_i}{m_i},\label{e3.87b}
\end{align} 
whereas the {\em perpendicular thermal conductivities}, which control the diffusion of heat perpendicular to magnetic flux-surfaces, take the form
\begin{align}
\kappa_\perp^e &= 4.7\,\frac{n\,T_e}{m_e\,{\mit\Omega}_e^{\,2}\,\tau_e},\\[0.5ex]
\kappa_\perp^i &= 2\, \frac{n\,T_i}{m_i\,{\mit\Omega}_i^{\,2}\,\tau_i}.
\end{align}
Finally, the {\em cross thermal conductivities}, which control the flow of heat within magnetic flux-surfaces,  are written
\begin{align}
\kappa_\times^e &= \frac{5\,n\,T_e}{2\,m_e\,{\mit\Omega}_e},\\[0.5ex]
\kappa_\times^i &=\frac{5\,n\,T_i}{2\,m_i\,{\mit\Omega}_i}.
\end{align}

In order to describe the viscosity tensor in a magnetized plasma, it is
helpful to define the {\em rate-of-strain tensor} \index{rate-of-strain tensor} 
\begin{equation}
W_{\alpha\beta} = \frac{\partial V_\alpha}{\partial r_\beta}
+ \frac{\partial V_\beta}{\partial r_\alpha} - \frac{2}{3} \,\nabla\cdot{\bf V}\,
\delta_{\alpha\beta}.
\end{equation}
Obviously, there is a separate rate-of-strain tensor for the electron and ion
fluids. It is easily demonstrated that this tensor is zero if the plasma
translates, or rotates as a rigid body, or if it undergoes isotropic
compression. Thus, the rate-of-strain tensor measures the  deformation  of
plasma volume elements.

In a highly magnetized plasma, the viscosity tensor is best described as the
sum of  five component tensors,
\begin{equation}
\bpi  = \sum_{n=0,4} \bpi_n,
\end{equation}
where 
\begin{equation}
\bpi_0 = - 3\,\eta_0\,\left({\bf b}{\bf b} - \frac{1}{3}\,{\bf I}\right)
\left({\bf b}{\bf b} - \frac{1}{3}\,{\bf I}\right): \nabla {\bf V},
\end{equation}
with
\begin{equation}
\bpi_1 =- \eta_1\left[{\bf I}_\perp \cdot{\bf W}\cdot{\bf I}_\perp
+ \frac{1}{2}\,{\bf I}_\perp\,({\bf b}\cdot{\bf W}\cdot{\bf b})\right],
\end{equation}
and
\begin{equation}
\bpi_2 = -4\,\eta_1\,\left({\bf I}_\perp\cdot
{\bf W}\cdot{\bf b}{\bf b}
+ {\bf b}{\bf b}\cdot{\bf W} \cdot{\bf I}_\perp\right).
\end{equation}
plus
\begin{equation}
\bpi_3 = \frac{\eta_3}{2}\,\left( {\bf b}\times 
{\bf W}\cdot{\bf I}_\perp - {\bf I}_\perp\cdot{\bf W}\times{\bf b}
\right),
\end{equation}
and
\begin{equation}
\bpi_4 = 2\,\eta_3\,\left({\bf b} \times{\bf W} \cdot {\bf b}{\bf b}
- {\bf b}{\bf b} \cdot{\bf W} \times{\bf b}\right).
\end{equation}
Here, ${\bf I}$ is the identity tensor, and 
${\bf I}_\perp = {\bf I} - {\bf b}{\bf b}$. The previous 
expressions are valid for both electrons and ions.

The tensor $\bpi_0$ describes what is known as {\em parallel viscosity}.
This is a viscosity that controls the variation along magnetic field-lines of the
velocity component parallel to  field-lines.
 The parallel
viscosity coefficients are given by 
\begin{align}\label{e3.89a}
\eta_0^e &= 0.73\,n\,\tau_e\,T_e,\\[0.5ex]
\eta_0^i &= 0.96\,n\,\tau_i\,T_i,\label{e3.89b}
\end{align}

The tensors $\bpi_1$ and $\bpi_2$ describe what is known
as {\em perpendicular viscosity}. This is a viscosity
that controls the variation perpendicular to magnetic field-lines
of the velocity components perpendicular to field-lines. The perpendicular
viscosity coefficients are given by
\begin{align}
\eta_1^e &= 0.51\, \frac{n\,T_e}{{\mit\Omega}_e^{\,2}\,\tau_e},\\[0.5ex]
\eta_1^i &= \frac{3\, n\,T_i}{10\,{\mit\Omega}_i^{\,2}\,\tau_i}.
\end{align}

Finally, the tensors $\bpi_3$ and $\bpi_4$ describe what is known
as {\em gyroviscosity}. This is not really viscosity at all, because the
associated viscous stresses are always perpendicular to the velocity, implying that
there is no dissipation ({\rm i.e.}, viscous heating) associated with
this effect. The gyroviscosity coefficients are given by 
\begin{align}
\eta_3^e &= -\frac{n\,T_e}{2\,{\mit\Omega}_e} ,\\[0.5ex]
\eta_3^i &= \frac{n\,T_i}{2\,{\mit\Omega}_i}.
\end{align}

\subsection{Normalization of Braginskii Equations}\label{s3.9}
As we have just seen, the Braginskii equations contain terms that describe a
very wide range of different physical phenomena. For this reason, they are
extremely complicated. Fortunately, however, it is not generally 
necessary to retain all of
the terms in these equations when investigating tearing mode dynamics in tokamak plasmas. In this section, we shall attempt to construct a systematic
normalization scheme for the Braginskii equations that will, hopefully, enable us
to determine which terms to keep, and which to discard, when investigating
tearing mode dynamics.

 It is convenient to split the friction force
${\bf F}$ into a component ${\bf F}_U$ corresponding to resistivity, and a
component ${\bf F}_T$ corresponding to the thermal force. Thus,
\begin{equation}
{\bf F} = {\bf F}_U+{\bf F}_T,
\end{equation}
where
\begin{align}
{\bf F}_U&= n\,e\left(\frac{{\bf j}_\parallel}{\sigma_\parallel}
+\frac{{\bf j}_\perp}{\sigma_\perp}\right), \\[0.5ex]
{\bf F}_T &= - 0.71\,n\,\nabla_\parallel T_e
-\frac{3\,n}{2\,{\mit\Omega}_e\,\tau_e}\,{\bf b}\times\nabla_\perp T_e.
\end{align}
Likewise, the electron collisional energy gain term $w_e$ is split
into a component $-w_i$ corresponding to the energy lost to the ions (in the
ion rest frame), a component $w_U$ corresponding to work done by the friction
force ${\bf F}_U$, and a component $w_T$ corresponding to work done by the
thermal force ${\bf F}_T$. Thus,
\begin{equation}
w_e = -w_i + w_U + w_T,
\end{equation}
where
\begin{align}
w_U &= \frac{{\bf j}\cdot{\bf F}_U}{n\,e},\\[0.5ex]
w_T&= \frac{{\bf j}\cdot{\bf F}_T}{n\,e}.
\end{align}
Finally, it is helpful to split the electron heat flux density ${\bf q}_e$ into
a diffusive component ${\bf q}_{Te}$ and a convective component ${\bf q}_{Ue}$. 
Thus,
\begin{equation}
{\bf q}_e = {\bf q}_{Te} + {\bf q}_{Ue},
\end{equation}
where
\begin{align}
{\bf q}_{Te} &=-\kappa_\parallel^e\,\nabla_\parallel T_e -\kappa_\perp^e\,
\nabla_\perp T_e
-\kappa_\times^e\,{\bf b}\times\nabla_\perp T_e,\\[0.5ex]
{\bf q}_{Ue}&=  0.71\,\frac{T_e}{e}\,{\bf j}_\parallel-
\frac{3\,T_e}{2\,{\mit\Omega}_e\,\tau_e\,e}\,{\bf b}\times{\bf j}_\perp.
\end{align}

Let us, first of all, consider the electron fluid equations, which can
be written:
\begin{align}
\frac{dn}{dt} + n\,\nabla\cdot{\bf V}_e &= 0,\\[0.5ex]
m_e\, n\,\frac{d {\bf V}_e}{dt} + \nabla p_e+ \nabla\cdot \bpi_e + e\, n\,
({\bf E} + {\bf V}_e\times {\bf B})& = {\bf F}_U +{\bf F}_T,\\[0.5ex]
\frac{3}{2}\frac{d p_e}{dt} + \frac{5}{2}\,p_e\,\nabla\cdot{\bf V}_e
+ \bpi_e:\nabla{\bf V}_e+ \nabla\cdot{\bf q}_{Te} 
+ \nabla\cdot{\bf q}_{Ue} &= -w_i+w_U + w_T.
\end{align}
Let $\bar{n}$, $\bar{v}_e$, $\bar{\tau}_e$, $\bar{l}_e=\bar{v}_e\,\bar{\tau}_e$, $\bar{B}$,
and $\bar{\rho}_e =\bar{ v}_e/(e\bar{B}/m_e)$,  be typical values
of the particle density, the electron thermal velocity, the electron collision time, the electron
mean-free-path between collisions,  the magnetic field-strength, and the
electron gyroradius,  respectively. 
Suppose that the typical spatial variation lengthscale of fluid variables is $L$. Let
 \begin{align}
\delta_e &=\frac{\bar{\rho}_e}{L},\\[0.5ex]
\zeta_e &= \frac{\bar{\rho}_e}{\bar{l}_e},\\[0.5ex]
\mu &= \sqrt{\frac{m_e}{m_i}}.
\end{align}
All three of these parameters are assumed to be  small
compared to unity. Finally, the typical electron flow velocity is assumed to be of order $\delta_e\,\bar{v}_e$. This corresponds
to the so-called {\em drift ordering}\/ in which the flow velocity is comparable to the curvature and grad-B particle
drift velocities (Fitzpatrick 2015). The drift ordering is appropriate to tearing modes in tokamak plasmas, which are comparatively
slowly growing instabilities.

 We
define the following normalized quantities: {\small
\begin{align}
\hat{n} &= \frac{n}{\bar{n}},&
\hat{v}_e &= \frac{v_e}{\bar{v}_e}, &
\hat{\bf r} &= \frac{{\bf r}}{ L},\nonumber\\[0.5ex]
\widehat{\nabla} &= L\,\nabla, &
\hat{t} &= \frac{\delta_e\,\bar{v}_e\,t}{L}, &
\widehat{\bf V}_e &= \frac{{\bf V}_e}{\delta_e\,\bar{v}_e}, \nonumber\\[0.5ex]
\widehat{\bf B}&= \frac{{\bf B}}{\bar{B}}, &
\widehat{\bf E}& = \frac{{\bf E}}{ \delta_e\,\bar{v}_e\,\bar{B}},&
\widehat{\bf j}& =\frac{{\bf j} }{n\,e\,\delta_e\,\bar{v}_e}, \nonumber\\[0.5ex]
\hat{p}_e &= \frac{p_e}{m_e\,\bar{n}\,\bar{v}_e^{2}}, &
\widehat{\bpi}_e&= \frac{\bpi_e}{\delta_e^{\,2}\,\zeta_e^{-1}\,m_e\,\bar{n}\,\bar{v}_e^{2}}, &
\widehat{\bf q}_{Te}& = \frac{{\bf q}_{Te} }{ \delta_e\,\zeta_e^{-1}\,m_e\,\bar{n}\,\bar{v}_e^{3}}, \nonumber\\[0.5ex]
\widehat{\bf q}_{Ue} &= \frac{{\bf q}_{Ue} }{\delta_e\,m_e\,\bar{n}\,\bar{v}_e^{3}}, &
\widehat{\bf F}_U &= \frac{{\bf F}_U}{\zeta_e\,m_e\,\bar{n}\,\bar{v}_e^{2}/L}, &
\widehat{\bf F}_T &= \frac{{\bf F}_T}{m_e\,\bar{n}\,\bar{v}_e^{2}/L},\nonumber\\[0.5ex]
\widehat{w}_i &= \frac{w_i}{\delta_e^{-1}\,\zeta_e\,\mu^2\, m_e\,\bar{n}\,\bar{v}_e^{3}/L},&
\widehat{w}_U &= \frac{w_U}{\delta_e\,\zeta_e\, m_e\,\bar{n}\,\bar{v}_e^{3}/L},&
\widehat{w}_T &= \frac{w_T}{\delta_e\, m_e\,\bar{n}\,\bar{v}_e^{3}/L}.\nonumber
\end{align}}

The normalization procedure is designed to make all hatted quantities ${\cal O}(1)$.
The normalization of the electric field is chosen 
 such that the ${\bf E}\times{\bf B}$
velocity is of  similar magnitude to the electron fluid velocity. Note that the parallel viscosity
makes an ${\cal O}(1)$ contribution to $\widehat{\bpi}_e$, whereas the gyroviscosity
makes an ${\cal O}(\zeta_e)$ contribution, and the perpendicular viscosity only 
makes an ${\cal O}(\zeta_e^{2})$ contribution. Likewise, the parallel thermal
conductivity 
makes an ${\cal O}(1)$ contribution to $\widehat{\bf q}_{Te}$, whereas the cross
conductivity 
makes an ${\cal O}(\zeta_e)$ contribution, and the perpendicular conductivity only 
makes an ${\cal O}(\zeta_e^{2})$ contribution. Similarly, the parallel components
of ${\bf F}_T$ and ${\bf q}_{Ue}$ are ${\cal O}(1)$, whereas the perpendicular
components are ${\cal O}(\zeta_e)$.

The normalized electron fluid equations take the form:
\begin{align}
\frac{d\hat{n}}{d\hat{t}} + \hat{n}\,\widehat{\nabla}\cdot\widehat{\bf V}_e &=0,\label{e3.113a}\\[0.5ex]
\hat{n}\,\frac{d\widehat{\bf V}_e}{d\hat{t}} +
\delta_e^{-2}\,\widehat{\nabla}\hat{p}_e +\zeta_e^{-1}\,\widehat{\nabla}
\cdot\widehat{\bpi}_e  
+ \delta_e^{-2}\,\hat{n}\,(\widehat{\bf E} + \widehat{\bf V}_e
\times\widehat{\bf B}) &= \delta_e^{-2}\,\zeta_e\,\widehat{\bf F}_U +\delta_e^{-2}\,\widehat{\bf F}_T, \\[0.5ex]
\frac{3}{2}\frac{d\hat{p}_e}{d\hat{t}} + \frac{5}{2}\,
\hat{p}_e\,\widehat{\nabla}\cdot\widehat{\bf V}_e + \delta_e^{2}\,
\zeta_e^{-1}\,\widehat{\bpi}_e : \widehat{\nabla}\cdot\widehat{\bf V}_e&\nonumber\label{e3.113c}\\[0.5ex] 
+\zeta_e^{-1} \,\widehat{\nabla}\cdot\widehat{\bf q}_{Te}
 +\widehat{\nabla}\cdot\widehat{\bf q}_{Ue} 
&= -\delta_e^{-2}\,\zeta_e\,\mu^2\,\widehat{w}_i + \zeta_e\,
\widehat{w}_U +\widehat{w}_T.
\end{align}
The only large or small (compared to unity) quantities in these equations are the
parameters $\delta_e$, $\zeta_e$, and $\mu$. 
Here, $d/d\hat{t}\equiv\partial /\partial\hat{t} +
 \widehat{\bf V}_e\cdot\widehat{\nabla}$. It is assumed that $T_e\sim T_i$.

Let us now consider the ion fluid equations, which can be written:
\begin{align}
\frac{dn}{dt} + n\,\nabla\cdot{\bf V}_i &= 0,\\[0.5ex]
m_i\, n\,\frac{d {\bf V}_i}{dt} + \nabla p_i + \nabla\cdot \bpi_i - e\, n\,
({\bf E} + {\bf V}_i\times {\bf B})& =- {\bf F}_U -{\bf F}_T,\\[0.5ex]
\frac{3}{2}\frac{d p_i}{dt} + \frac{5}{2}\,p_i\,\nabla \cdot {\bf V}_i
+ \bpi_i:\nabla{\bf V}_i+ \nabla\cdot{\bf q}_i & =w_i.
\end{align}
It is convenient to adopt a normalization scheme for the ion equations
which is similar to, but independent of, that employed to normalize the
electron equations. Let  $\bar{n}$, $\bar{v}_i$, $\bar{l}_i$, $\bar{B}$,
and $\bar{\rho}_i =\bar{ v}_i/(e\bar{B}/m_i)$,  be typical values
of the particle density, the ion  thermal velocity, the ion
mean-free-path between collisions,  the magnetic field-strength, and the
ion gyroradius,  respectively. 
Suppose that 
the typical spatial variation lengthscale of fluid quantities is $L$. Let
 \begin{align}
\delta_i &= \frac{\bar{\rho}_i}{L},\\[0.5ex]
\zeta_i &= \frac{\bar{\rho}_i}{\bar{l}_i},\\[0.5ex]
\mu &= \sqrt{\frac{m_e}{m_i}}.
\end{align}
All three of these parameters are assumed to be  small 
compared to unity.  As before, we adopt the drift ordering in which the typical ion flow velocity is assumed to be of order $\delta_i\,\bar{v}_i$.

We
define the following normalized quantities: 
\begin{align}
\hat{n} &=\frac{ n}{\bar{n}},&
\hat{v}_i &= \frac{v_i}{\bar{v}_i},& 
\hat{\bf r} &= \frac{{\bf r}}{ L}, \nonumber\\[0.5ex]
\widehat{\nabla} &= L\,\nabla, &
\hat{t} &= \frac{\delta_i\,\bar{v}_i\,t}{L}, &
\widehat{\bf V}_i &= \frac{{\bf V}_i}{\delta_i\,\bar{v}_i}, \nonumber\\[0.5ex]
\widehat{\bf B}&= \frac{{\bf B}}{\bar{B}}, &
\widehat{\bf E} &= \frac{{\bf E}}{ \delta_i\,\bar{v}_i\,\bar{B}},&
\widehat{\bf j} &=\frac{{\bf j} }{ n\,e\,\delta_i\,\bar{v}_i},\nonumber\\[0.5ex]
 \hat{p}_i &=\frac{ p_i}{m_i\,\bar{n}\,\bar{v}_i^{2}}, &
 \widehat{\bpi}_i&= \frac{\bpi_i}{\delta_i^{\,2}\,\zeta_i^{-1}\,m_i\,\bar{n}\,\bar{v}_i^{2}}, &
\widehat{\bf q}_{i} &= \frac{{\bf q}_{i} }{ \delta_i\,\zeta_i^{-1}\,m_i\,\bar{n}\,\bar{v}_i^{3}},  \nonumber\\[0.5ex]
\widehat{\bf F}_U &= \frac{{\bf F}_U}{ \zeta_i\,\mu\,m_i\,\bar{n}\,\bar{v}_i^{2}/L}, &
\widehat{\bf F}_T &=\frac{ {\bf F}_T}{m_i\,\bar{n}\,\bar{v}_i^{2}/L},&
\widehat{w}_i& = \frac{w_i}{\delta_i^{-1}\,\zeta_i\,\mu\, m_i\,\bar{n}\,\bar{v}_i^{3}/L}.\nonumber
\end{align}

As before, the normalization procedure is designed to make all hatted quantities ${\cal O}(1)$.
The normalization of the electric field is chosen 
 such that the ${\bf E}\times{\bf B}$
velocity is of similar  magnitude to the ion fluid velocity. Note that the parallel viscosity
makes an ${\cal O}(1)$ contribution to $\widehat{\bpi}_i$, whereas the gyroviscosity
makes an ${\cal O}(\zeta_i)$ contribution, and the perpendicular viscosity only 
makes an ${\cal O}(\zeta_i^{2})$ contribution. Likewise, the parallel thermal
conductivity 
makes an ${\cal O}(1)$ contribution to $\widehat{\bf q}_{i}$, whereas the cross
conductivity 
makes an ${\cal O}(\zeta_i)$ contribution, and the perpendicular conductivity only 
makes an ${\cal O}(\zeta_i^{2})$ contribution. Similarly, the parallel component
of ${\bf F}_T$ is  ${\cal O}(1)$, whereas the perpendicular
component is  ${\cal O}(\zeta_i\,\mu)$.

The normalized ion fluid equations take the form:
\begin{align}\label{e3.116a}
\frac{d\hat{n}}{d\hat{t}} + \hat{n}\,\widehat{\nabla}\cdot\widehat{\bf V}_i &=0,\\[0.5ex]
\hat{n}\,\frac{d\widehat{\bf V}_i}{d\hat{t}} +
\delta_i^{-2}\,\widehat{\nabla}\hat{p}_i+\zeta_i^{-1}\,\widehat{\nabla}
\cdot\widehat{\bpi}_i  
-\delta_i^{-2}\,\hat{n}\,(\widehat{\bf E} + \widehat{\bf V}_i
\times\widehat{\bf B}) &=-\delta_i^{-2}\,\zeta_i\,\mu\,\widehat{\bf F}_U
 - \delta_i^{-2}\,\widehat{\bf F}_T, \\[0.5ex]
\frac{3}{2}\frac{d\hat{p}_i}{d\hat{t}} + \frac{5}{2}\,
\hat{p}_i\,\widehat{\nabla}\cdot\widehat{\bf V}_i + \delta_i^{2}\,
\zeta_i^{-1}\,\widehat{\bpi}_i : \widehat{\nabla}\cdot\widehat{\bf V}_i
+\zeta_i^{-1} \,\widehat{\nabla}\cdot\widehat{\bf q}_{i}
&= \delta_i^{-2}\,\zeta_i\,\mu\,\widehat{w}_i. \label{e3.116c}
\end{align}
The only large or small (compared to unity) quantities in these equations are the
parameters $\delta_i$, $\zeta_i$, and $\mu$. 
Here, $d/d\hat{t}\equiv\partial /\partial\hat{t} +
 \widehat{\bf V}_i\cdot\widehat{\nabla}$.

\subsection{Lowest-Order Fluid Equations}
If we restore dimensions to the Braginskii equations then we can write them in the form
\begin{align}
\frac{\partial n}{\partial t} + \nabla\cdot(n\,{\bf V}_e) &= 0,\label{e3.151a}\\[0.5ex]
m_e\, n\,\frac{\partial  {\bf V}_e}{\partial t} +
m_e\, n\,({\bf V}_e\cdot\nabla){\bf V}_e+
 [\delta_e^{-2}]\,\nabla p_e+
[\zeta_e^{-1}]\, \nabla\cdot \bpi_e &\label{e3.151b}\\[0.5ex]
 +[\delta_e^{-2}]\,e\, n\,
({\bf E} + {\bf V}_e\times {\bf B})& =[\delta_e^{-2}\,\zeta_e]\, {\bf F}_U + [\delta_e^{-2}]\,
{\bf F}_T,\nonumber\\[0.5ex]
\frac{3}{2}\frac{\partial  p_e}{\partial t} + \frac{3}{2}
 \,({\bf V}_e\cdot\nabla)\, p_e 
+ \frac{5}{2}\,p_e\,\nabla\cdot{\bf V}_e+[\delta_e^{\,2}\,\zeta_e^{-1}]\, \bpi_e:\nabla{\bf V}_e&\label{e3.151c}\\[0.5ex]
+ [\zeta_e^{-1}]\,\nabla\cdot{\bf q}_{Te} +\nabla\cdot{\bf q}_{Ue}  &=-[\delta_e^{-2}\,\zeta_e\,\mu^2]\,
 w_i+ [\zeta_e]\,w_U + w_T,\nonumber
\end{align}
and
\begin{align}\label{e3.152a}
\frac{\partial n}{\partial t} +\nabla\cdot(n\,{\bf V}_i) &= 0,\\[0.5ex]
m_i \,n\,\frac{\partial  {\bf V}_i}{\partial t} +
m_i \,n\,({\bf V}_i\cdot\nabla) {\bf V}_i +
 [\delta_i^{-2}]\,\nabla p_i + 
[\zeta_i^{-1}]\,\nabla\cdot \bpi_i &\label{e3.152b}\\[0.5ex]
- [\delta_i^{-2}]\,e \,n\,
({\bf E} + {\bf V}_i\times {\bf B})& =-[\delta_i^{-2}\,\zeta_i\,\mu]\, {\bf F}_U - [\delta_i^{-2}]\,{\bf F}_T,
\nonumber\\[0.5ex]
\frac{3}{2}\frac{\partial  p_i}{\partial t} +   \frac{3}{2}
 \,({\bf V}_i\cdot\nabla) \,p_i
+ \frac{5}{2}\,p_i\,\nabla\cdot{\bf V}_i+[\delta_i^{\,2}\,\zeta_i^{-1}]\, \bpi_i:\nabla{\bf V}_i\nonumber\\[0.5ex]
+ [\zeta_i^{-1}]\,\nabla\cdot{\bf q}_i &= [\delta_i^{-2}\,\zeta_i\,\mu]\,w_i.\label{e3.152c}
\end{align}
The terms in square brackets are just to remind us that the terms they precede are smaller or larger than the
other terms in the equations (by the corresponding terms within the brackets).

If we assume that $\delta_e\sim \zeta_e\sim \mu$ then the dominant terms in the electron energy conservation equation
(\ref{e3.151c}) yield
\begin{equation}
\nabla\cdot{\bf q}_{T_e}\simeq \nabla\cdot(-\kappa_\parallel^e\,\nabla_\parallel T_e)\simeq 0,
\end{equation}
which implies that 
\begin{equation}
{\bf B}\cdot\nabla T_e=0. \label{e75}
\end{equation}
In other words, the parallel electron heat conductivity in a tokamak plasma is usually
sufficiently large that it forces the electron temperature to be constant on magnetic flux-surfaces. 
Likewise, if we assume that $\delta_i\sim \zeta_i\sim \mu$ then the dominant terms in the ion energy conservation equation
(\ref{e3.152c}) yield
\begin{equation}
\nabla\cdot{\bf q}_{T_i}\simeq \nabla\cdot(-\kappa_\parallel^i\,\nabla_\parallel T_i)\simeq 0,
\end{equation}
which implies that 
\begin{equation}
{\bf B}\cdot\nabla T_i=0.\label{e77}
\end{equation}
In other words, the parallel ion heat conductivity in a tokamak plasma is usually
sufficiently large that it forces the ion temperature to be constant on magnetic flux-surfaces.

 The dominant terms in the electron and ion momentum conservation equations,
(\ref{e3.151b}) and (\ref{e3.152b}), respectively, yield
\begin{align}\label{e78}
\nabla p_e + n\,e\,({\bf E}+{\bf V}_e\times {\bf B}) &\simeq 0,\\[0.5ex]
\nabla p_i - n\,e\,({\bf E}+{\bf V}_i\times {\bf B}) &\simeq 0.\label{e79}
\end{align}
The sum of the preceding two equations gives
\begin{equation}\label{e80}
 {\bf j}\times {\bf B} \simeq-\nabla p,
\end{equation}
where $p=p_e+p_i$. In other words, a conventional tokamak plasma exists in a state in which electromagnetic
forces exactly balance the  total scalar pressure force. 
It follows from the previous equation that 
\begin{equation}
{\bf B}\cdot\nabla p\simeq 0.
\end{equation}
In other words, the pressure in a conventional tokamak plasma is constant on magnetic flux-surfaces. 
 However, given that $p=n\,(T_e+T_i)$, and making use of Eqs.~(\ref{e75}) and (\ref{e77}), we deduce that 
\begin{equation}
{\bf B}\cdot\nabla n\simeq 0.
\end{equation}
In other words, the particle density in a conventional tokamak plasma is also  constant on
magnetic flux-surfaces.

 Taking the difference of the electron and ion particle
conservation equations, (\ref{e3.151a}) and (\ref{e3.152a}), respectively, we obtain
\begin{equation}\label{e82}
\nabla\cdot {\bf j} = 0.
\end{equation}
 Equations~(\ref{e80}) and (\ref{e82}) can be combined to give
\begin{equation}\label{e84}
({\bf B}\cdot\nabla)\,{\bf j } - ({\bf j}\cdot\nabla)\,{\bf B} \simeq {\bf 0}.
\end{equation}

Finally, Equations~(\ref{e78}) and (\ref{e79}) imply that
\begin{align}
{\bf V}_{\perp\,e} &\simeq {\bf V}_E + {\bf V}_{\ast\,e},\\[0.5ex]
{\bf V}_{\perp\,i} &\simeq {\bf V}_E + {\bf V}_{\ast\,i},
\end{align}
where
\begin{equation}
{\bf V}_e = \frac{{\bf E}\times {\bf B}}{B^2}
\end{equation}
is the {\em E-cross-B drift velocity}, and
\begin{align}
{\bf V}_{\ast\,e}&= \frac{\nabla p_e\times {\bf B}}{e\,n\,B^2},\\[0.5ex]
{\bf V}_{\ast\,i}&=- \frac{\nabla p_i\times {\bf B}}{e\,n\,B^2},
\end{align}
are termed the {\em electron diamagnetic velocity}\/ and the {\em ion diamagnetic velocity}, respectively.

\section{Cylindrical Tearing Mode Theory}
\subsection{Tokamak Equilibrium}
Consider a large aspect-ratio tokamak plasma equilibrium with whose magnetic flux-surfaces map out (almost) concentric circles in the poloidal plane. 
Let us employ a conventional set of right-handed cylindrical coordinates, $r$, $\theta$, $z$. The
equilibrium magnetic flux-surfaces lie on surfaces of constant $r$. The system is
assumed to be periodic in the $z$ (`toroidal') direction, with periodicity length $2\pi\,R_0$, 
where $R_0$ is the simulated {\em major radius}\/ of the plasma. The {\em safety-factor}\/ profile takes the form
\begin{equation}\label{e90}
q(r)= \frac{r\,B_z}{R_0\,B_\theta(r)},
\end{equation}
where $B_z$ is the constant `toroidal' magnetic field-strength, and $B_\theta(r)$ is
the poloidal magnetic field-strength. It is assumed that $q\sim{\cal O}(1)$. 
The equilibrium `toroidal' current density
satisfies
\begin{equation}
\mu_0\,j_z(r) = \frac{(r\,B_\theta)'}{r},
\end{equation}
where $'$ denotes $d/dr$. Finally, the standard large aspect-ratio
tokamak orderings,  
\begin{equation}\label{e92}
\frac{r}{R_0}\ll 1,~~~ \frac{B_\theta}{B_z}\ll 1,
\end{equation}
are adopted (Fitzpatrick 1993).

\subsection{Perturbed Magnetic Field}
Consider a tearing mode perturbation that has $m$ periods in the poloidal direction,
and $n$ periods in the `toroidal' direction, where $m/n\sim {\cal O}(1)$.  We can write the perturbed magnetic field in the form
\begin{equation}\label{e93}
\delta{\bf B} \simeq \nabla\times (\psi\,{\bf e}_z),
\end{equation}
where
\begin{equation}\label{e93a}
\psi(r,\theta,\phi,t)= \psi(r,t)\,\exp[{\rm i}\,(m\,\theta-n\,\phi)].
\end{equation}
Here, $\phi=z/R_0$ is a simulated toroidal angle. The perturbed current density becomes
\begin{equation}\label{e94}
\mu_0\,\delta {\bf j} \simeq - \nabla^2\psi\,{\bf e}_z.
\end{equation}

\subsection{Cylindrical Tearing Mode Equation}
The tearing perturbation is governed by the linearized version of Equation~(\ref{e84}), which yields
\begin{equation}\label{e96}
(\delta{\bf B}\cdot \nabla)\,{\bf j} + ({\bf B}\cdot\nabla)\,\delta{\bf j} - (\delta{\bf j}\cdot\nabla)\,{\bf B} - 
({\bf j}\cdot\nabla)\,\delta {\bf B}\simeq {\bf 0}.
\end{equation}
Making use of Equations~(\ref{e90})--(\ref{e94}), the $z$-component of the previous equation gives
the {\em cylindrical tearing mode equation}\/ (Fitzpatrick 1993),
\begin{equation}
\frac{\partial^2\psi}{dr^2} + \frac{1}{r}\,\frac{\partial\psi}{\partial r}-\frac{m^2}{r^2}\,\psi - \frac{J_z'\,\psi}{r\,(1/q-n/m)}\simeq 0,
\end{equation}
where 
\begin{equation}
J_z(r)= \frac{R_0\,\mu_0\,j_z(r)}{B_z}.
\end{equation}

\subsection{Solution in Presence of Perfectly-Conducting Wall}\label{perfect}
Suppose that the plasma occupies the region $0\leq r\leq a$, where $a$ is the plasma {\em minor radius}. It follows that
$J_z(r)=0$ for $r>a$. Suppose that the plasma is surrounded by a concentric perfectly-conducting wall of radius $r_w>a$. An appropriate
physical solution of the cylindrical tearing mode equation takes the form
\begin{equation}\label{e99}
\psi(r,t)= {\mit\Psi}_s(t)\,\hat{\psi}_s(r),
\end{equation}
where the real function $\hat{\psi}_s(r)$ is a solution of 
\begin{equation}\label{e100}
\frac{d^2\hat{\psi}_s}{dr^2} + \frac{1}{r}\,\frac{d\hat{\psi}_s}{dr}-\frac{m^2}{r^2}\,\hat{\psi}_s - \frac{J_z'\,\hat{\psi}_s}{r\,(1/q-n/m)}\simeq 0
\end{equation}
that satisfies
\begin{align}\label{e101}
\hat{\psi}_s(0) &= 0,\\[0.5ex]
\hat{\psi}_s(r_s) &= 1,\label{e102}\\[0.5ex]
\hat{\psi}_s(r\geq r_w) &= 0.\label{e103}
\end{align}

Note that Equation~(\ref{e100}) is singular at the so-called {\em resonant}\/ magnetic flux-surface, radius $r=r_s$, at which 
\begin{equation}\label{e104}
q(r_s)= \frac{m}{n}.
\end{equation}
At the resonant surface, ${\bf k}\cdot{\bf B}=0$, where ${\bf k} = (0,\,m/r,\,-n/R_0)$ is the wavevector of the tearing perturbation. 
The value of $\psi(r,t)$ at the resonant surface---namely, ${\mit\Psi}_s(t)$---is known as the {\em reconnected magnetic flux}. 
Note that ${\mit\Psi}_s$ is, in general, a complex quantity. 
Let $\rho=(r-r_s)/r_s$. 
The solution of Equation~(\ref{e100}) in the vicinity of the resonant surface is
\begin{equation}\label{e105}
\hat{\psi}_s(\rho) = 1 + {\mit\Delta}_{s+}\,\rho + \alpha_s\,\rho\,\ln|\rho| + {\cal O}(\rho^2)
\end{equation}
for $\rho>0$, and
\begin{equation}\label{e106}
\hat{\psi}_s(\rho) = 1 + {\mit\Delta}_{s-}\,\rho + \alpha_s\,\rho\,\ln|\rho| + {\cal O}(\rho^2)
\end{equation}
for $\rho<0$. Here, 
\begin{align}
\alpha_s& =- \left(\frac{r\,q\,J_z'}{s}\right)_{r=r_s},\\[0.5ex]
s(r) &= \frac{r\,q'}{q}.
\end{align}
Moreover,  the real parameters ${\mit\Delta}_{s+}$ and  ${\mit\Delta}_{s-}$ are fully determined by Equation~(\ref{e100})
and the boundary conditions (\ref{e101})--(\ref{e103}). Note that, in general, $\psi$ is continuous across the resonant surface,
whereas $\partial\psi/\partial r$ is discontinuous. The discontinuity in $\partial \psi/\partial r$ implies the presence of a radially
thin current sheet  at the resonant surface. This current sheet can only be resolved by retaining more terms in the perturbed plasma equation of motion, (\ref{e96}).

The complex quantity
\begin{equation}
{\mit\Delta\Psi}_s = \left[r\,\frac{\partial \psi}{\partial r}\right]_{r_{s-}}^{r_{s+}}
\end{equation}
parameterizes the amplitude and phase of the current sheet flowing at the resonant surface. Matching the solutions
in the so-called {\em inner region}\/ (i.e., the region of the plasma in the immediate vicinity of the resonant surface)
and the so-called {\em outer region}\/ (i.e., everywhere in the plasma other than the inner region) with the help
of Equations~(\ref{e99}), (\ref{e105}), and ({\ref{e106}), we obtain
\begin{equation}
{\mit\Delta\Psi}_s = E_{ss}\,{\mit\Psi}_s,
\end{equation}
where $E_{ss}= {\mit\Delta}_{s+}-{\mit\Delta}_{s-}$ is a real quantity determined by the solution in the outer region.

\subsection{Solution in Presence of Resistive Wall}\label{resistive}
Suppose, now, that the wall at $r=r_w$ possesses a finite resistivity, but is surrounded by a second perfectly-conducting wall
located at radius $r_c>r_w$.
The solution in the outer region can be written
\begin{equation}\label{e111}
\psi(r,t) = {\mit\Psi}_s(t)\,\hat{\psi}_s(r) + {\mit\Psi}_w(t)\,\hat{\psi}_w(r),
\end{equation}
where the real function $\hat{\psi}_s(r)$ is specified in the previous section, and the real function  $\hat{\psi}_w(r)$ is a solution of 
\begin{equation}\label{e100a}
\frac{d^2\hat{\psi}_w}{dr^2} + \frac{1}{r}\,\frac{d\hat{\psi}_w}{dr}-\frac{m^2}{r^2}\,\hat{\psi}_w - \frac{J_z'\,\hat{\psi}_w}{r\,(1/q-n/m)}\simeq 0
\end{equation}
that satisfies
\begin{align}\label{e101a}
\hat{\psi}_w(r\leq r_s) &= 0,\\[0.5ex]
\hat{\psi}_w(r_w) &= 1,\label{e102a}\\[0.5ex]
\hat{\psi}_w(r\geq r_c) &= 0.\label{e103a}
\end{align}
It is easily seen that
\begin{equation}\label{e117}
\hat{\psi}_w(r_w< r < r_c) = \frac{(r/r_c)^{-m} - (r/r_c)^m}{(r_w/r_c)^{-m} - (r_w/r_c)^m}.
\end{equation}

In general, $\psi$ is continuous across the wall, whereas $\partial\psi/\partial r$ is discontinuous. The discontinuity in $\partial\psi/\partial r$ is caused by the currents induced in the wall. The complex quantity ${\mit\Psi}_w(t)$ determines the amplitude and
phase of the perturbed magnetic flux that penetrates the wall. The complex quantity
\begin{equation}\label{e118}
{\mit\Delta\Psi}_w = \left[r\,\frac{\partial\psi}{\partial r}\right]_{r_{w-}}^{r_{w+}}
\end{equation}
parameterizes the amplitude and phase of the current sheet flowing in the wall.
Simultaneously matching the outer solution (\ref{e111}) across the resonant surface and the wall yields
\begin{align}
{\mit\Delta\Psi}_s &= E_{ss}\,{\mit\Psi}_s + E_{sw}\,{\mit\Psi}_w,\\[0.5ex]
{\mit\Delta\Psi}_w &= E_{ws}\,{\mit\Psi}_s+ E_{ww}\,{\mit\Psi}_w
\end{align}
(Fitzpatrick 1993).
Here,
\begin{align}
E_{ww}&= \left[r\,\frac{d\hat{\psi}_w}{dr}\right]_{r_{w-}}^{r_{w+}},\\[0.5ex]
E_{sw} &=\left[r\,\frac{{d\hat\psi}_w}{dr}\right]_{r=r_{s+}},\label{e121}\\[0.5ex]
E_{ws} &=-\left[r\,\frac{{d\hat\psi}_s}{dr}\right]_{r=r_{w-}}\label{e122}
\end{align}
are real quantities determined by the solution in the outer region.

Equations~(\ref{e100}) and (\ref{e100a}) can be combined to give
\begin{equation}
\frac{d}{dr}\!\left(\hat{\psi}_s\,r\,\frac{d\hat{\psi}_w}{dr} - \hat{\psi}_w\,r\,\frac{d\hat{\psi}_s}{dr}\right) = 0.
\end{equation}
If we integrate the previous equation from $r=r_{s+}$ to $r=r_{w-}$, making use of Equations~(\ref{e102}), (\ref{e103}), (\ref{e101a}), (\ref{e102a}), (\ref{e121}),
and (\ref{e122}), then we obtain
\begin{equation}\label{e123}
E_{sw} = E_{ws}
\end{equation}
(Fitzpatrick 1993).

\subsection{Resistive Wall Physics}
It is clear from Equation~(\ref{e93}) that
\begin{equation}
\delta {\bf A} \simeq \psi\,{\bf e}_z,
\end{equation}
where $\delta {\bf A}$ is the perturbed magnetic vector potential. 
Hence, the perturbed electric field can be written
\begin{equation}
\delta {\bf E} \simeq -\nabla\delta{\mit\Phi} - \frac{\partial\psi}{\partial t}\,{\bf e}_z,
\end{equation}
where $\delta{\mit\Phi}$ is the perturbed electric scalar potential. 
Assuming that $|\nabla\delta{\mit\Phi}|\sim |\partial\psi/\partial t|$, the $z$-component of the previous
equation yields
\begin{equation}
\delta E_z\simeq -\frac{\partial\psi}{\partial t},
\end{equation}
where use has been made of the large aspect-ratio orderings (\ref{e92}). Within the wall, we
can write
\begin{equation}
\delta E_z \simeq -\frac{d{\mit\Psi}_w}{dt}.
\end{equation}
Here, we are making use of the so-called {\em thin wall approximation}, according to which $\psi$ is assumed to only vary weakly in $r$ across
the wall. Ohm's law implies that
\begin{equation}
\delta j_z = \frac{\delta E_z}{\eta_w} = -\frac{1}{\eta_w}\,\frac{d{\mit\Psi}_w}{dt}
\end{equation}
within the wall, where $\eta_w$ is the wall resistivity. Equations~(\ref{e94}) and (\ref{e118}) yield
\begin{equation}\label{e132}
{\mit\Delta\Psi}_w = -\mu_0\int_{r_{w-}}^{r_{w+}}r\,\delta j_z\,dr.
\end{equation}
Suppose that the radial thickness of the wall is $\delta_w\ll r_w$. The previous two equations yield
\begin{equation}\label{e133}
{\mit\Delta\Psi}_w = \tau_w\,\frac{d{\mit\Psi}_w}{dt},
\end{equation}
where
\begin{equation}
\tau_w = \frac{\mu_0\,r_w\,\delta_w}{\eta_w}
\end{equation}
is the so-called {\em time constant}\/ of the wall (Fitzpatrick 1993). The thin wall approximation is
valid as long as
\begin{equation}
\frac{r_w}{\delta_w}\gg \tau_w\left|\frac{d\ln{\mit\Psi}_w}{dt}\right|.
\end{equation}

\subsection{Resonant Layer Physics}
By analogy with Equation~(\ref{e133}), we can write
\begin{equation}
{\mit\Delta\Psi}_s = \tau_s\left(\frac{d{\mit\Psi}_w}{dt} + {\rm i}\,\varpi_s\,{\mit\Psi}_s\right).
\end{equation}
Here, $\tau_s$ is the {\em reconnection time}, whereas $\varpi_s$ is the so-called {\em natural frequency}. 
The natural frequency is the phase velocity of the tearing mode when the wall is perfectly conducting. The
natural frequency is non-zero because the reconnected flux in the resonant layer is convected by the local plasma
flow (Fitzpatrick 1993).

\subsection{Solution in Presence of External Magnetic Field-Coil}
Suppose that the perfectly-conducting wall at $r=r_c$ is replaced by a magnetic field-coil that carries a
helical current possesing $m$ periods in the poloidal direction, and $n$ periods in the `toroidal' direction. Let the current density in the coil
take the form
\begin{equation}\label{e135}
\delta j_z = -\frac{I_c(t)}{r_c}\,\delta(r-r_c)\,{\rm e}^{\,{\rm i}\,(m\,\theta-n\,\phi)}.
\end{equation}
Here, the complex quantity $I_c(t)$ parameterizes the amplitude and phase of the helical current flowing in the field-coil.

The solution in the outer region can be written
\begin{equation}
\psi(r,t) = {\mit\Psi}_s(t)\,\hat{\psi}_s(r) + {\mit\Psi}_w(t)\,\hat{\psi}_w(r) + {\mit\Psi}_c\,\hat{\psi}_c(r),
\end{equation}
where the real functions $\hat{\psi}_s(r)$ and $\hat{\psi}_w(r)$ are specified in Sections~\ref{perfect} and \ref{resistive}, respectively. 
Moreover, 
the real function  $\hat{\psi}_c(r)$ is a solution of 
\begin{equation}\label{e100b}
\frac{d^2\hat{\psi}_c}{dr^2} + \frac{1}{r}\,\frac{d\hat{\psi}_c}{dr}-\frac{m^2}{r^2}\,\hat{\psi}_c\simeq 0
\end{equation}
that satisfies
\begin{align}
\hat{\psi}_c(r\leq r_w) &= 0,\\[0.5ex]
\hat{\psi}_c(r_c) &= 1,\\[0.5ex]
\hat{\psi}_c(\infty) &= 0.
\end{align}
It is easily seen that
\begin{align}
\hat{\psi}_c(r\leq r_w) &= 0,\\[0.5ex]
\hat{\psi}_c(r_w<r \leq r_c) &= \frac{(r/r_w)^m-(r/r_w)^{-m}}{(r_c/r_w)^m - (r_c/r_w)^{-m}},\label{e142}\\[0.5ex]
\hat{\psi}_c(r> r_c) &=\left(\frac{r}{r_c}\right)^{-m}.\label{e143}
\end{align}

In general, $\psi$ is continuous across the field-coil, whereas $\partial\psi/\partial r$ is discontinuous. The discontinuity in $\partial\psi/\partial r$ is caused by the currents flowing in the coil. The complex quantity ${\mit\Psi}_c(t)$ determines the amplitude and
phase of the perturbed magnetic flux at the coil. The complex quantity
\begin{equation}\label{e118a}
{\mit\Delta\Psi}_c = \left[r\,\frac{\partial\psi}{\partial r}\right]_{r_{c-}}^{r_{c+}}
\end{equation}
parameterizes the amplitude and phase of the current sheet flowing in the coil.
It follows from Equations~(\ref{e93a}), (\ref{e94}), and (\ref{e135})  that
\begin{equation}
{\mit\Delta\Psi}_c = \mu_0\,I_c.
\end{equation}

Simultaneously matching the outer solution across the resonant surface, the wall, and the field-coil, we
obtain
\begin{align}\label{e146}
{\mit\Delta\Psi}_s &= E_{ss}\,{\mit\Psi}_s + E_{sw}\,{\mit\Psi}_w,\\[0.5ex]
{\mit\Delta\Psi}_w &= E_{ws}\,{\mit\Psi}_s + E_{ww}\,{\mit\Psi}_w + E_{wc}\,{\mit\Psi}_c,\\[0.5ex]
{\mit\Delta\Psi}_c&= E_{cw}\,{\mit\Psi}_w + E_{cc}\,{\mit\Psi}_c. \label{e148}
\end{align}
Here,  
\begin{align}
E_{cc} &= \left[r\,\frac{d\hat{\psi}_c}{dr}\right]_{r_{c-}}^{r_{c+}}=- \frac{2m}{1-(r_w/r_c)^{2m}},\\[0.5ex]
E_{wc}&= \left[r\,\frac{d\hat{\psi}_c}{dr}\right]_{r_{w+}} = \frac{2m\,(r_w/r_c)^m}{1-(r_w/r_c)^{2m}},\label{e150a}\\[0.5ex]
E_{cw}&=- \left[r\,\frac{d\hat{\psi}_w}{dr}\right]_{r_{c-}} = \frac{2m\,(r_w/r_c)^m}{1-(r_w/r_c)^{2m}},\label{e151}
\end{align}
where use has been made of Equations~(\ref{e117}), (\ref{e142}), and (\ref{e143}).

\subsection{Electromagnetic Torques}
The flux-surface integrated poloidal and `toroidal' electromagnetic torque densities acting on the plasma
can be written
\begin{align}
T_\theta(r) &= \oint\oint R_0\,r^{\,2}\,{\bf j}\times {\bf B}\cdot {\bf e}_\theta\,d\theta\,d\phi,\\[0.5ex]
T_\phi(r) &= \oint\oint R_0^{\,2}\,r\,{\bf j}\times {\bf B}\cdot {\bf e}_z\,d\theta\,d\phi,
\end{align}
respectively. However, according to Equation~(\ref{e80}),
\begin{equation}\label{e150}
{\bf j}\times {\bf B} \simeq -\nabla p.
\end{equation}
Given that the scalar pressure is a single-valued function of $\theta$ and $\phi$, it immediately follows
that $T_\theta=T_\phi = 0$ throughout the plasma. The only exception to this rule occurs in the immediate vicinity of the
resonant surface, where Equation~(\ref{e150}) breaks down. It follows that we can write
\begin{align}
T_\theta(r) &= T_{\theta\,s}\,\delta(r-r_s),\\[0.5ex]
T_\phi(r) &= T_{\phi\,s}\,\delta(r-r_s),
\end{align}
where
\begin{align}\label{e153}
T_{\theta\,s} &=  \frac{1}{4}\int_{r_{s-}}^{r_{s+}}\oint\oint R_0\,r^{\,2}\,(\delta j_z\,\delta B_r^{\,\ast} + \delta j_z^{\,\ast}\,\delta B_r)\,dr\,d\theta\,d\phi,\\[0.5ex]
T_{\phi\,s} &=  -\frac{1}{4}\int_{r_{s-}}^{r_{s+}}\oint\oint R_0^{\,2}\,r\,(\delta j_\theta\,\delta B_r^{\,\ast} + \delta j_\theta^{\,\ast}\,\delta B_r)\,dr\,d\theta\,d\phi
\end{align}
are the net poloidal and `toroidal' torques, respectively, acting at the resonant surface. 
Note that the equilibrium torques are zero because $B_r=0$. Furthermore, the linear (in perturbed quantities) torques 
average to zero over the flux-surface. Hence, the largest non-zero torques  are quadratic in perturbed quantities. 
According to Equation~(\ref{e82}), 
\begin{equation}
\nabla \cdot \delta {\bf j} = {\rm i}\left(\frac{m}{r}\,\delta j_\theta - \frac{n}{R_0}\,\delta j_z\right) = 0,
\end{equation}
where $\delta{\bf j}$ is the density of the current sheet flowing at the resonant surface, and we have made use
of the fact that $\delta j_r\simeq 0$. 
 It follows from the previous three equations that
\begin{equation}\label{e156}
T_{\phi\,s} = - \frac{n}{m}\,T_{\theta\,s}.
\end{equation}
Finally, Equations~(\ref{e93}), (\ref{e94}), (\ref{e153}), and (\ref{e156}) imply that
\begin{align}\label{e157}
T_{\theta\,s} &= -\frac{2\pi^2\,R_0\,m}{\mu_0}\,{\rm Im}({\mit\Delta\Psi}_s\,{\mit\Psi}_s^{\,\ast}),\\[0.5ex]
T_{\phi\,s} &= \frac{2\pi^2\,R_0\,n}{\mu_0}\,{\rm Im}({\mit\Delta\Psi}_s\,{\mit\Psi}_s^{\,\ast})
\end{align}
(Fitzpatrick 1993).

By analogy with the previous analysis,  the net poloidal and `toroidal' electromagnetic torques acting on the
resistive wall are 
\begin{align}
T_{\theta\,w} &= -\frac{2\pi^2\,R_0\,m}{\mu_0}\,{\rm Im}({\mit\Delta\Psi}_w\,{\mit\Psi}_w^{\,\ast}),\\[0.5ex]
T_{\phi\,w} &= \frac{2\pi^2\,R_0\,n}{\mu_0}\,{\rm Im}({\mit\Delta\Psi}_w\,{\mit\Psi}_w^{\,\ast}),
\end{align}
respectively. 
Finally, 
the net poloidal and `toroidal' electromagnetic torques acting on the
magnetic field-coil are 
\begin{align}
T_{\theta\,c} &= -\frac{2\pi^2\,R_0\,m}{\mu_0}\,{\rm Im}({\mit\Delta\Psi}_c\,{\mit\Psi}_c^{\,\ast}),\\[0.5ex]
T_{\phi\,c} &= \frac{2\pi^2\,R_0\,n}{\mu_0}\,{\rm Im}({\mit\Delta\Psi}_c\,{\mit\Psi}_c^{\,\ast}),\label{e166}
\end{align}
respectively.

It follows from Equations~(\ref{e146})--(\ref{e148}) that
\begin{align}
{\rm Im}({\mit\Delta\Psi}_s\,{\mit\Psi}_s^{\,\ast}) &= E_{sw}\,{\rm Im}({\mit\Psi}_w\,{\mit\Psi}_s^{\,\ast}),\\[0.5ex]
{\rm Im}({\mit\Delta\Psi}_w\,{\mit\Psi}_w^{\,\ast}) &= E_{ws}\,{\rm Im}({\mit\Psi}_s\,{\mit\Psi}_w^{\,\ast})+E_{wc}\,{\rm Im}({\mit\Psi}_c\,{\mit\Psi}_w^{\,\ast}),\\[0.5ex]
 {\rm Im}({\mit\Delta\Psi}_c\,{\mit\Psi}_c^{\,\ast}) &=E_{cw}\,{\rm Im}({\mit\Psi}_w\,{\mit\Psi}_c^{\,\ast}).
 \end{align}
 Thus,
 \begin{align}
 {\rm Im}({\mit\Delta\Psi}_s\,{\mit\Psi}_s^{\,\ast})+ {\rm Im}({\mit\Delta\Psi}_w\,{\mit\Psi}_w^{\,\ast}) + {\rm Im}({\mit\Delta\Psi}_c\,{\mit\Psi}_c^{\,\ast}) & = (E_{sw}-E_{ws})\,{\rm Im}({\mit\Psi}_w\,{\mit\Psi}_s^{\,\ast}) \nonumber\\[0.5ex]
 &\phantom{=}+ (E_{wc}-E_{cw})\,{\rm Im}({\mit\Psi}_c\,{\mit\Psi}_w^{\,\ast}).
 \end{align}
 However, according to Equations~(\ref{e123}), (\ref{e150a}), and (\ref{e151}), $E_{sw}=E_{ws}$ and $E_{wc}=E_{cw}$. 
We deduce that
 \begin{equation} 
  {\rm Im}({\mit\Delta\Psi}_s\,{\mit\Psi}_s^{\,\ast})+ {\rm Im}({\mit\Delta\Psi}_w\,{\mit\Psi}_w^{\,\ast}) + {\rm Im}({\mit\Delta\Psi}_c\,{\mit\Psi}_c^{\,\ast})=0.
  \end{equation}
Hence, Equations~(\ref{e157})--(\ref{e166})   yield
\begin{align}
T_{\theta\,s} + T_{\theta\,w}+T_{\theta\,c} &= 0,\\[0.5ex]
T_{\phi\,s} + T_{\phi\,w}+T_{\phi\,c} &= 0.
\end{align}
In other words, the plasma/wall/field-coil system exerts zero net poloidal electromagnetic torque and zero net toroidal electromagnetic
torque on itself.

\subsection{Plasma Angular Equations of Motion}
We can write
\begin{align}
{\mit\Omega}_\theta(r,t)&= {\mit\Omega}_{\theta\,0}(r) + {\mit\Delta\Omega}_\theta(r,t),\\[0.5ex]
{\mit\Omega}_\phi(r,t)&= {\mit\Omega}_{\phi\,0}(r) + {\mit\Delta\Omega}_\phi(r,t),
\end{align}
where ${\mit\Omega}_\theta(r,t)$ and ${\mit\Omega}_\phi(r,t)$ are the poloidal and 	`toroidal' plasma angular velocity profiles, respectively. [To be more exact,  ${\mit\Omega}_\theta(r,t)$ and ${\mit\Omega}_\phi(r,t)$ are the ion fluid angular velocity
profiles.] Moreover, ${\mit\Omega}_{\theta\,0}(r)$ and ${\mit\Omega}_{\phi\,0}(r)$ are the corresponding unperturbed profiles,
and ${\mit\Delta\Omega}_{\theta}(r,t)$ and ${\mit\Delta\Omega}_{\phi}(r,t)$ are the respective modifications to the profiles
induced by the electromagnetic torques that develop at the resonant surface. The modifications to the angular
velocity profiles are governed by the poloidal and toroidal angular equations of motion of the plasma, which
take the respective forms
\begin{align}
4\pi^2\,R_0\left[(1+2\,q^2)\,\rho\,r^{\,3}\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial t}-\frac{\partial}{\partial r}\!\left(
\mu\,r^{\,3}\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial r}\right) + \frac{\rho}{\tau_\theta}\,r^{\,3}\,{\mit\Delta\Omega}_\theta\right] = T_{\theta\,s}\,\delta(r-r_s),\\[0.5ex]
4\pi^2\,R_0^{\,3}\left[\rho\,r\,\frac{\partial{\mit\Delta\Omega}_\phi}{\partial t}-\frac{\partial}{\partial r}\!\left(
\mu\,r\,\frac{\partial{\mit\Delta\Omega}_\phi}{\partial r}\right) \right] = T_{\phi\,s}\,\delta(r-r_s).
\end{align}
Here, $\rho(r)$ is the plasma mass density profile, $\mu(r)$ is the anomalous plasma perpendicular ion viscosity
(due to plasma turbulence), and $\tau_\theta(r)$ is the characteristic time at which neoclassical
parallel viscosity relaxes the plasma poloidal angular velocity profile.

\section*{Bibliography}
\begin{description}
\item Braginskii, S.I.\ 1965. {\em Transport Processes in a Plasma}. In {\em Reviews of Plasma Physics}. Consultants Bureau. Volume~1, 205.
\item Chapman, S., and Cowling, T.G.\ 1953. {\em The Mathematical Theory of Non-Uniform Gases}. Cambridge.
\item Fitzpatrick, R.\ 1993. {\em Interaction of Tearing Modes with External Structures in Cylindrical Geometry}, Nucl.\ Fusion {\bf 33}, 1049 (1993). 
\item Fitzpatrick, R.\ 2008. {\em Maxwell's Equations and the Principles of Electromagnetism}. Jones \& Bartlett.
\item Fitzpatrick, R.\ 2015. {\em Plasma Physics: An Introduction}. Taylor \& Francis, CRC Press. 
\item Reif, F.\ 1965. {\em Fundamentals of Statistical and Thermal Physics}. McGraw-Hill.
\item Richardson, A.S.\ 2019. {\em 2019 NRL Plasma Formulary}.  Naval Research Laboratory.
\end{description}

\end{document}

### 2021-10-25 Documentation/TearingModeTheory.tex
Added to tearing mode theory report

@@
 \begin{equation}\label{e80}
- {\bf j}\times {\bf B} \simeq-\nabla p,
+ {\bf j}\times {\bf B} \simeq\nabla p,
 \end{equation}
@@
 \subsection{Tokamak Equilibrium}
-Consider a large aspect-ratio tokamak plasma equilibrium with whose magnetic flux-surfaces map out (almost) concentric circles in the poloidal plane. 
+Consider a large aspect-ratio, toroidal,  tokamak plasma equilibrium whose magnetic flux-surfaces map out (almost) concentric circles in the poloidal plane. 
 Let us employ a conventional set of right-handed cylindrical coordinates, $r$, $\theta$, $z$. The
@@
 \end{equation}
+It is assumed that $|\delta{\bf B}|\ll |{\bf B}|$.
 
 \subsection{Cylindrical Tearing Mode Equation}
-The tearing perturbation is governed by the linearized version of Equation~(\ref{e84}), which yields
+To lowest order, the tearing perturbation is governed by the linearized version of Equation~(\ref{e84}), which yields
 \begin{equation}\label{e96}
@@
 Moreover,  the real parameters ${\mit\Delta}_{s+}$ and  ${\mit\Delta}_{s-}$ are fully determined by Equation~(\ref{e100})
-and the boundary conditions (\ref{e101})--(\ref{e103}). Note that, in general, $\psi$ is continuous across the resonant surface,
+and the boundary conditions (\ref{e101})--(\ref{e103}). Note that, in general, $\psi$ is continuous across the resonant surface (in accordance with Maxwell's equations),
 whereas $\partial\psi/\partial r$ is discontinuous. The discontinuity in $\partial \psi/\partial r$ implies the presence of a radially
-thin current sheet  at the resonant surface. This current sheet can only be resolved by retaining more terms in the perturbed plasma equation of motion, (\ref{e96}).
+thin, helical,  current sheet  at the resonant surface. This current sheet can only be resolved by retaining more terms in the perturbed plasma equation of motion, (\ref{e96}).
 
@@
 
-In general, $\psi$ is continuous across the wall, whereas $\partial\psi/\partial r$ is discontinuous.
+In general, $\psi$ is continuous across the wall (in accordance with Maxwell's equations), whereas $\partial\psi/\partial r$ is discontinuous.
 The discontinuity in $\partial\psi/\partial r$ is caused by the currents induced in the wall.
@@
 \end{equation}
-parameterizes the amplitude and phase of the current sheet flowing in the wall.
+parameterizes the amplitude and phase of the helical current sheet flowing in the wall.
 Simultaneously matching the outer solution (\ref{e111}) across the resonant surface and the wall yields
@@
 \end{equation}
-Suppose that the radial thickness of the wall is $\delta_w\ll r_w$. The previous two equations yield
+Suppose that the radial thickness of the wall is $\delta_w\ll r_w$. The previous two equations give
 \begin{equation}\label{e133}
@@
 \end{equation}
-Here, $\tau_s$ is the {\em reconnection time}, whereas $\varpi_s$ is the so-called {\em natural frequency}. 
+Here, $\tau_s$ is the {\em reconnection time}\/ (i.e., the typical timescale on which magnetic reconnection takes place in the
+resonant layer surrounding the resonant surface), whereas $\varpi_s$ is the so-called {\em natural frequency}. 
 The natural frequency is the phase velocity of the tearing mode when the wall is perfectly conducting. The
@@
 Suppose that the perfectly-conducting wall at $r=r_c$ is replaced by a magnetic field-coil that carries a
-helical current possesing $m$ periods in the poloidal direction, and $n$ periods in the `toroidal' direction. Let the current density in the coil
+helical current possesing $m$ periods in the poloidal direction, and $n$ periods in the `toroidal' direction. Let the current density in the field-coil
 take the form
@@
 
-In general, $\psi$ is continuous across the field-coil, whereas $\partial\psi/\partial r$ is discontinuous.
+In general, $\psi$ is continuous across the field-coil (in accordance with Maxwell's equations), whereas $\partial\psi/\partial r$ is discontinuous.
 The discontinuity in $\partial\psi/\partial r$ is caused by the currents flowing in the coil.
@@
 
-\subsection{Electromagnetic Torques}
+\subsection{Electromagnetic Torques}\label{storque}
 The flux-surface integrated poloidal and `toroidal' electromagnetic torque densities acting on the plasma
 can be written
-\begin{align}
-T_\theta(r) &= \oint\oint R_0\,r^{\,2}\,{\bf j}\times {\bf B}\cdot {\bf e}_\theta\,d\theta\,d\phi,\\[0.5ex]
-T_\phi(r) &= \oint\oint R_0^{\,2}\,r\,{\bf j}\times {\bf B}\cdot {\bf e}_z\,d\theta\,d\phi,
+\begin{align}\label{e152}
+T_\theta(r) &= \left\langle r\,{\bf j}\times {\bf B}\cdot {\bf e}_\theta\right\rangle\\[0.5ex]
+T_\phi(r) &= \left\langle R_0\,{\bf j}\times {\bf B}\cdot {\bf e}_z\right\rangle,
 \end{align}
-respectively. However, according to Equation~(\ref{e80}),
+respectively, 
+where
+\begin{equation}
+\left\langle\cdots\right\rangle \equiv \oint\oint r\,R_0\,(\cdots)\,d\theta\,d\phi
+\end{equation}
+is the flux-surface average operator. 
+ However, according to Equation~(\ref{e80}),
 \begin{equation}\label{e150}
-{\bf j}\times {\bf B} \simeq -\nabla p.
+{\bf j}\times {\bf B} \simeq \nabla p.
 \end{equation}
@@
 resonant surface, where Equation~(\ref{e150}) breaks down. It follows that we can write
-\begin{align}
+\begin{align}\label{e156a}
 T_\theta(r) &= T_{\theta\,s}\,\delta(r-r_s),\\[0.5ex]
@@
 \end{align}
-In other words, the plasma/wall/field-coil system exerts zero net poloidal electromagnetic torque and zero net toroidal electromagnetic
-torque on itself.
+In other words, the plasma/wall/field-coil system exerts zero net poloidal electromagnetic torque, and zero net toroidal electromagnetic
+torque, on itself.
 
 \subsection{Plasma Angular Equations of Motion}
+The sum of the electron fluid equation of motion, (\ref{e3.151b}), and the ion fluid equation of motion, (\ref{e3.152b}), yields the plasma equation of motion, 
+\begin{equation}
+\rho\,\frac{\partial  {\bf V}_i}{\partial t} +
+\rho\,({\bf V}_i\cdot\nabla) {\bf V}_i +
+ [\delta_i^{-2}]\,\nabla p + 
+[\zeta_i^{-1}]\,\nabla\cdot \bpi_i-[\delta_i^{-2}]\,{\bf j}\times {\bf B} =0,\label{e175}
+\end{equation}
+where $\rho=m_i\,n$ is the plasma mass density.
+Here, we have neglected electron inertial terms with respect to ion inertial terms (because the
+former are order $m_e/m_i$ smaller than the latter). We have also neglected electron viscosity terms
+with respect to ion viscosity terms (because the
+former are order $\sqrt{m_e/m_i}$ smaller than the latter). Recall that the terms in square brackets are to remind us that the terms they precede are larger than the
+other terms in the equations (by the corresponding terms within the brackets).
+
+Taking the flux-surface average of the scalar product of $r\,{\bf e}_\theta$ with the plasma equation of motion, (\ref{e175}), we obtain 
+\begin{equation}
+\left\langle\rho\,\frac{\partial (r\,V_{\theta\,i})}{\partial t} \right\rangle 
++\left\langle \rho\left[V_{r\,i}\,\frac{\partial (r\,V_{\theta\,i})}{\partial r} + V_{z\,i}\,\frac{\partial(r\, V_{\theta\,i})}{\partial z}
+\right]\right\rangle + [\zeta_i^{-1}]\,\langle r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\rangle
+= [\delta_i^{-2}]\,T_{\theta\,s}\,\delta(r-r_s),
+\end{equation}
+where use has been made of Equations~(\ref{e152}) and (\ref{e156a}). Note that the dominant $\nabla p$ term
+has averaged to zero.
+Moreover, because $T_{\theta\,s}$ is quadratic in perturbed quantities (see Section~\ref{storque}), it is plausible that the right-hand side of the previous equation is not a dominant term [i.e., it is not ${\cal O}(\delta_i^{-2})$ larger than the
+other terms in the equation].
+
 We can write

### 2021-10-30 Documentation/TearingModeTheory.tex
Added to tearing mode writeup

@@
 \begin{document}
-\title{\bf Tearing Modes in Tokamak Plasmas}
+\title{\bf Tearing Mode Dynamics in Tokamak Plasmas}
 \author{R.~Fitzpatrick\,\footnote{rfitzp@utexas.edu}\\
@@
 \section{Fluid Theory}
+\subsection{Introduction}
+The aim of this section is to introduce the fundamental plasma fluid theory that underpins the analysis of tearing mode dynamics in tokamak
+plasmas.
+
 \subsection{Fundamental Quantities}
@@
 ${\bf B}$,  is strong enough to significantly alter charged particle
-trajectories. In particular,
-magnetized plasmas are highly  anisotropic, responding differently to
+trajectories. Consequently,
+tokamak plasmas are highly  anisotropic, responding differently to
 forces that are parallel and perpendicular to the direction
@@
 
-\subsection{Braginskii Equations}
+\subsection{Braginskii Equations}\label{sbrag}
 The electron and ion fluid equations in a collisional plasma
@@
 m_e \,n\,\frac{d {\bf V}_e}{dt} + \nabla p_e+ \nabla\cdot \bpi_e + e\, n\,
-({\bf E} + {\bf V}_e\times {\bf B})& = {\bf F},\\[0.5ex]
+({\bf E} + {\bf V}_e\times {\bf B})& = {\bf F},\label{e3.79b}\\[0.5ex]
 \frac{3}{2}\frac{d p_e}{dt} + \frac{5}{2}\,p_e\,\nabla\cdot{\bf V}_e
@@
 m_i \,n\,\frac{d {\bf V}_i}{dt} + \nabla p_i + \nabla\cdot \bpi_i - e\, n\,
-({\bf E} + {\bf V}_i\times {\bf B})& =- {\bf F},\\[0.5ex]
+({\bf E} + {\bf V}_i\times {\bf B})& =- {\bf F},\label{e3.80b}\\[0.5ex]
 \frac{3}{2}\frac{d p_i}{dt} + \frac{5}{2}\,p_i\,\nabla\cdot{\bf V}_i
@@
 respectively. 
-Equations (\ref{e3.79a})--(\ref{e3.79c}) and (\ref{e3.80a})--(\ref{e3.80c})  are called the {\em Braginskii equations}, because they were first obtained
-in a celebrated article by S.I.~Braginskii (Braginskii 1965). Here, ${\bf V}_s$ is the species-$s$ flow velocity, $p_s=n\,T_s$ is the 
+Equations (\ref{e3.79a})--(\ref{e3.80c})  are called the {\em Braginskii equations}, because they were first obtained
+in a celebrated article by S.I.~Braginskii (Braginskii 1965). Here, $n$ is the electron number density, ${\bf V}_s$ is the species-$s$ flow velocity, $p_s=n\,T_s$ is the 
 species-$s$ scalar
@@
 Obviously, there is a separate rate-of-strain tensor for the electron and ion
-fluids. It is easily demonstrated that this tensor is zero if the plasma
+fluids. It is easily demonstrated that this tensor is zero if the fluid
 translates, or rotates as a rigid body, or if it undergoes isotropic
 compression. Thus, the rate-of-strain tensor measures the  deformation  of
-plasma volume elements.
+fluid volume elements.
 
@@
 
-\subsection{Lowest-Order Fluid Equations}
+\subsection{Lowest-Order Fluid Equations}\label{lowest}
 If we restore dimensions to the Braginskii equations then we can write them in the form
@@
  [\delta_e^{-2}]\,\nabla p_e+
-[\zeta_e^{-1}]\, \nabla\cdot \bpi_e &\label{e3.151b}\\[0.5ex]
+[\zeta_e^{-1}]\, \nabla\cdot \bpi_e &\nonumber\\[0.5ex]
  +[\delta_e^{-2}]\,e\, n\,
 ({\bf E} + {\bf V}_e\times {\bf B})& =[\delta_e^{-2}\,\zeta_e]\, {\bf F}_U + [\delta_e^{-2}]\,
-{\bf F}_T,\nonumber\\[0.5ex]
+{\bf F}_T,\label{e3.151b}\\[0.5ex]
 \frac{3}{2}\frac{\partial  p_e}{\partial t} + \frac{3}{2}
- \,({\bf V}_e\cdot\nabla)\, p_e 
+ \,{\bf V}_e\cdot\nabla p_e 
 + \frac{5}{2}\,p_e\,\nabla\cdot{\bf V}_e+[\delta_e^{\,2}\,\zeta_e^{-1}]\, \bpi_e:\nabla{\bf V}_e&\label{e3.151c}\\[0.5ex]
@@
  [\delta_i^{-2}]\,\nabla p_i + 
-[\zeta_i^{-1}]\,\nabla\cdot \bpi_i &\label{e3.152b}\\[0.5ex]
+[\zeta_i^{-1}]\,\nabla\cdot \bpi_i &\nonumber\\[0.5ex]
 - [\delta_i^{-2}]\,e \,n\,
 ({\bf E} + {\bf V}_i\times {\bf B})& =-[\delta_i^{-2}\,\zeta_i\,\mu]\, {\bf F}_U - [\delta_i^{-2}]\,{\bf F}_T,
-\nonumber\\[0.5ex]
+\label{e3.152b}\\[0.5ex]
 \frac{3}{2}\frac{\partial  p_i}{\partial t} +   \frac{3}{2}
- \,({\bf V}_i\cdot\nabla) \,p_i
+ \,{\bf V}_i\cdot\nabla p_i
 + \frac{5}{2}\,p_i\,\nabla\cdot{\bf V}_i+[\delta_i^{\,2}\,\zeta_i^{-1}]\, \bpi_i:\nabla{\bf V}_i\nonumber\\[0.5ex]
@@
 \end{align}
-The terms in square brackets are just to remind us that the terms they precede are smaller or larger than the
+The terms in square brackets are there to remind us that the terms they precede are smaller or larger than the
 other terms in the equations (by the corresponding terms within the brackets).
 
-If we assume that $\delta_e\sim \zeta_e\sim \mu$ then the dominant terms in the electron energy conservation equation
+If we assume that $\delta_e\sim \zeta_e\sim \mu\ll 1$ then the dominant terms in the electron energy conservation equation
 (\ref{e3.151c}) yield
@@
 sufficiently large that it forces the electron temperature to be constant on magnetic flux-surfaces. 
-Likewise, if we assume that $\delta_i\sim \zeta_i\sim \mu$ then the dominant terms in the ion energy conservation equation
+Likewise, if we assume that $\delta_i\sim \zeta_i\sim \mu\ll 1$ then the dominant terms in the ion energy conservation equation
 (\ref{e3.152c}) yield
@@
 \end{equation}
-In other words, the particle density in a conventional tokamak plasma is also  constant on
+In other words, the electron number density in a conventional tokamak plasma is also  constant on
 magnetic flux-surfaces.
@@
 \end{equation}
+Here, we have made use of the fact that $\nabla\cdot{\bf B}=0$.
 
@@
 \begin{equation}
-{\bf V}_e = \frac{{\bf E}\times {\bf B}}{B^2}
-\end{equation}
-is the {\em E-cross-B drift velocity}, and
-\begin{align}
-{\bf V}_{\ast\,e}&= \frac{\nabla p_e\times {\bf B}}{e\,n\,B^2},\\[0.5ex]
-{\bf V}_{\ast\,i}&=- \frac{\nabla p_i\times {\bf B}}{e\,n\,B^2},
-\end{align}
-are termed the {\em electron diamagnetic velocity}\/ and the {\em ion diamagnetic velocity}, respectively.
+{\bf V}_E = \frac{{\bf E}\times {\bf B}}{B^{\,2}}
+\end{equation}
+is the {\em E-cross-B drift velocity}\/ (otherwise known as  the ${\bf E}\times {\bf B}$ velocity), and
+\begin{align}
+{\bf V}_{\ast\,e}&= \frac{\nabla p_e\times {\bf B}}{e\,n\,B^{\,2}},\\[0.5ex]
+{\bf V}_{\ast\,i}&=- \frac{\nabla p_i\times {\bf B}}{e\,n\,B^{\,2}},
+\end{align}
+are termed the {\em electron diamagnetic velocity}\/ and the {\em ion diamagnetic velocity}, respectively (Fitzpatrick 2015).
 
 \section{Cylindrical Tearing Mode Theory}
+\subsection{Introduction}
+The aim of this section is to describe the simplest theory of tearing mode dynamics in tokamak plasmas, according to which the plasma
+equilibrium is approximated as a periodic cylinder.
+
 \subsection{Tokamak Equilibrium}
 Consider a large aspect-ratio, toroidal,  tokamak plasma equilibrium whose magnetic flux-surfaces map out (almost) concentric circles in the poloidal plane.
+Such an equilibrium can be approximated as a periodic cylinder (Wesson 1978).
 Let us employ a conventional set of right-handed cylindrical coordinates, $r$, $\theta$, $z$. The
@@
 Consider a tearing mode perturbation that has $m$ periods in the poloidal direction,
-and $n$ periods in the `toroidal' direction, where $m/n\sim {\cal O}(1)$.  We can write the perturbed magnetic field in the form
+and $n$ periods in the toroidal direction, where $m/n\sim {\cal O}(1)$.  We can write the perturbed magnetic field in the form
 \begin{equation}\label{e93}
@@
 \begin{equation}\label{e93a}
-\psi(r,\theta,\phi,t)= \psi(r,t)\,\exp[{\rm i}\,(m\,\theta-n\,\phi)].
-\end{equation}
-Here, $\phi=z/R_0$ is a simulated toroidal angle. The perturbed current density becomes
+\psi(r,\theta,\varphi,t)= \psi(r,t)\,\exp[{\rm i}\,(m\,\theta-n\,\varphi)].
+\end{equation}
+Here, $\varphi=z/R_0$ is a simulated toroidal angle. The perturbed current density becomes
 \begin{equation}\label{e94}
@@
 \begin{equation}
-\frac{\partial^2\psi}{dr^2} + \frac{1}{r}\,\frac{\partial\psi}{\partial r}-\frac{m^2}{r^2}\,\psi - \frac{J_z'\,\psi}{r\,(1/q-n/m)}\simeq 0,
+\frac{\partial^2\psi}{\partial r^2} + \frac{1}{r}\,\frac{\partial\psi}{\partial r}-\frac{m^2}{r^2}\,\psi - \frac{J_z'\,\psi}{r\,(1/q-n/m)}\simeq 0,
 \end{equation}
@@
 Suppose that the plasma occupies the region $0\leq r\leq a$, where $a$ is the plasma {\em minor radius}. It follows that
-$J_z(r)=0$ for $r>a$. Suppose that the plasma is surrounded by a concentric perfectly-conducting wall of radius $r_w>a$. An appropriate
+$J_z(r)=0$ for $r>a$. Let the plasma be surrounded by a concentric perfectly-conducting wall of radius $r_w>a$. 
+(By definition, $a\ll R_0$ in a large aspect-ratio tokamak.) An appropriate
 physical solution of the cylindrical tearing mode equation takes the form
@@
 At the resonant surface, ${\bf k}\cdot{\bf B}=0$, where ${\bf k} = (0,\,m/r,\,-n/R_0)$ is the wavevector of the tearing perturbation. 
-The value of $\psi(r,t)$ at the resonant surface---namely, ${\mit\Psi}_s(t)$---is known as the {\em reconnected magnetic flux}. 
+The value of $\psi(r,t)$ at the resonant surface---namely, ${\mit\Psi}_s(t)$---is known as the {\em reconnected magnetic flux}\/ (Fitzpatrick 1993). 
 Note that ${\mit\Psi}_s$ is, in general, a complex quantity. 
@@
 \begin{equation}\label{e105}
-\hat{\psi}_s(\rho) = 1 + {\mit\Delta}_{s+}\,\rho + \alpha_s\,\rho\,\ln|\rho| + {\cal O}(\rho^2)
+\hat{\psi}_s(\rho) = 1 + {\mit\Delta}_{s+}\,\rho + \alpha_s\,\rho\,\ln|\rho| + {\cal O}(\rho^{\,2})
 \end{equation}
@@
 \begin{equation}\label{e106}
-\hat{\psi}_s(\rho) = 1 + {\mit\Delta}_{s-}\,\rho + \alpha_s\,\rho\,\ln|\rho| + {\cal O}(\rho^2)
+\hat{\psi}_s(\rho) = 1 + {\mit\Delta}_{s-}\,\rho + \alpha_s\,\rho\,\ln|\rho| + {\cal O}(\rho^{\,2})
 \end{equation}
@@
 and the so-called {\em outer region}\/ (i.e., everywhere in the plasma other than the inner region) with the help
-of Equations~(\ref{e99}), (\ref{e105}), and ({\ref{e106}), we obtain
+of Equations~(\ref{e99}), (\ref{e105}), and (\ref{e106}), we obtain
 \begin{equation}
@@
 \end{equation}
-where $E_{ss}= {\mit\Delta}_{s+}-{\mit\Delta}_{s-}$ is a real quantity determined by the solution in the outer region.
+where $E_{ss}= {\mit\Delta}_{s+}-{\mit\Delta}_{s-}$ is a real quantity that is known as the {\em tearing stability index}\/ (Furth, et al., 1963).
 
@@
 In general, $\psi$ is continuous across the wall (in accordance with Maxwell's equations), whereas $\partial\psi/\partial r$ is discontinuous.
-The discontinuity in $\partial\psi/\partial r$ is caused by the currents induced in the wall.
+The discontinuity in $\partial\psi/\partial r$ is caused by a helical current sheet induced in the wall.
 The complex quantity ${\mit\Psi}_w(t)$ determines the amplitude and
@@
 \end{align}
-are real quantities determined by the solution in the outer region.
+are real quantities determined by the solutions of Equations~(\ref{e100}) and (\ref{e100a}) in the outer region.
 
@@
 \end{equation}
-Here, we are making use of the so-called {\em thin wall approximation}, according to which $\psi$ is assumed to only vary weakly in $r$ across
+Here, we are making use of the so-called {\em thin wall approximation}, according to which $\psi$ is assumed to only vary weakly in $r$ inside 
 the wall. Ohm's law implies that
@@
 \end{equation}
-is the so-called {\em time constant}\/ of the wall (Fitzpatrick 1993). The thin wall approximation is
+is the so-called {\em time constant}\/ of the wall (Nave \& Wesson 1990; Fitzpatrick 1993). The thin wall approximation is
 valid as long as
@@
 
-\subsection{Resonant Layer Physics}
+\subsection{Resonant Layer Physics}\label{sres}
 By analogy with Equation~(\ref{e133}), we can write
-\begin{equation}
-{\mit\Delta\Psi}_s = \tau_s\left(\frac{d{\mit\Psi}_w}{dt} + {\rm i}\,\varpi_s\,{\mit\Psi}_s\right).
+\begin{equation}\label{e134}
+{\mit\Delta\Psi}_s = \tau_s\left(\frac{d{\mit\Psi}_s}{dt} + {\rm i}\,\varpi_s\,{\mit\Psi}_s\right).
 \end{equation}
@@
 Suppose that the perfectly-conducting wall at $r=r_c$ is replaced by a magnetic field-coil that carries a
-helical current possesing $m$ periods in the poloidal direction, and $n$ periods in the `toroidal' direction. Let the current density in the field-coil
+helical current possesing $m$ periods in the poloidal direction, and $n$ periods in the toroidal direction. Let the current density in the field-coil
 take the form
 \begin{equation}\label{e135}
-\delta j_z = -\frac{I_c(t)}{r_c}\,\delta(r-r_c)\,{\rm e}^{\,{\rm i}\,(m\,\theta-n\,\phi)}.
+\delta j_z = \frac{I_c(t)}{r_c}\,\delta(r-r_c)\,{\rm e}^{\,{\rm i}\,(m\,\theta-n\,\varphi)}.
 \end{equation}
@@
 In general, $\psi$ is continuous across the field-coil (in accordance with Maxwell's equations), whereas $\partial\psi/\partial r$ is discontinuous.
-The discontinuity in $\partial\psi/\partial r$ is caused by the currents flowing in the coil.
+The discontinuity in $\partial\psi/\partial r$ is caused by the helical currents flowing in the coil.
 The complex quantity ${\mit\Psi}_c(t)$ determines the amplitude and
@@
 \end{equation}
-parameterizes the amplitude and phase of the current sheet flowing in the coil.
+parameterizes the amplitude and phase of the helical  current sheet flowing in the coil.
 It follows from Equations~(\ref{e93a}), (\ref{e94}), and (\ref{e135})  that
-\begin{equation}
-{\mit\Delta\Psi}_c = \mu_0\,I_c.
+\begin{equation}\label{e145}
+{\mit\Delta\Psi}_c = -\mu_0\,I_c.
 \end{equation}
@@
 \subsection{Electromagnetic Torques}\label{storque}
-The flux-surface integrated poloidal and `toroidal' electromagnetic torque densities acting on the plasma
+The flux-surface integrated poloidal and toroidal electromagnetic torque densities acting on the plasma
 can be written
@@
 T_\theta(r) &= \left\langle r\,{\bf j}\times {\bf B}\cdot {\bf e}_\theta\right\rangle\\[0.5ex]
-T_\phi(r) &= \left\langle R_0\,{\bf j}\times {\bf B}\cdot {\bf e}_z\right\rangle,
+T_\varphi(r) &= \left\langle R_0\,{\bf j}\times {\bf B}\cdot {\bf e}_z\right\rangle,
 \end{align}
@@
 \begin{equation}
-\left\langle\cdots\right\rangle \equiv \oint\oint r\,R_0\,(\cdots)\,d\theta\,d\phi
-\end{equation}
-is the flux-surface average operator. 
+\left\langle\cdots\right\rangle \equiv \oint\oint r\,R_0\,(\cdots)\,d\theta\,d\varphi
+\end{equation}
+is a flux-surface integration  operator. 
  However, according to Equation~(\ref{e80}),
@@
 \end{equation}
-Given that the scalar pressure is a single-valued function of $\theta$ and $\phi$, it immediately follows
-that $T_\theta=T_\phi = 0$ throughout the plasma. The only exception to this rule occurs in the immediate vicinity of the
+Given that the scalar pressure is a single-valued function of $\theta$ and $\varphi$, it immediately follows
+that $T_\theta=T_\varphi = 0$ throughout the plasma (Fitzpatrick 1993). The only exception to this rule occurs in the immediate vicinity of the
 resonant surface, where Equation~(\ref{e150}) breaks down. It follows that we can write
@@
 T_\theta(r) &= T_{\theta\,s}\,\delta(r-r_s),\\[0.5ex]
-T_\phi(r) &= T_{\phi\,s}\,\delta(r-r_s),
+T_\varphi(r) &= T_{\varphi\,s}\,\delta(r-r_s),
 \end{align}
@@
 \begin{align}\label{e153}
-T_{\theta\,s} &=  \frac{1}{4}\int_{r_{s-}}^{r_{s+}}\oint\oint R_0\,r^{\,2}\,(\delta j_z\,\delta B_r^{\,\ast} + \delta j_z^{\,\ast}\,\delta B_r)\,dr\,d\theta\,d\phi,\\[0.5ex]
-T_{\phi\,s} &=  -\frac{1}{4}\int_{r_{s-}}^{r_{s+}}\oint\oint R_0^{\,2}\,r\,(\delta j_\theta\,\delta B_r^{\,\ast} + \delta j_\theta^{\,\ast}\,\delta B_r)\,dr\,d\theta\,d\phi
-\end{align}
-are the net poloidal and `toroidal' torques, respectively, acting at the resonant surface. 
-Note that the equilibrium torques are zero because $B_r=0$. Furthermore, the linear (in perturbed quantities) torques 
+T_{\theta\,s} &=  \frac{1}{4}\int_{r_{s-}}^{r_{s+}}\oint\oint R_0\,r^{\,2}\,(\delta j_z\,\delta B_r^{\,\ast} + \delta j_z^{\,\ast}\,\delta B_r)\,dr\,d\theta\,d\varphi,\\[0.5ex]
+T_{\varphi\,s} &=  -\frac{1}{4}\int_{r_{s-}}^{r_{s+}}\oint\oint R_0^{\,2}\,r\,(\delta j_\theta\,\delta B_r^{\,\ast} + \delta j_\theta^{\,\ast}\,\delta B_r)\,dr\,d\theta\,d\varphi
+\end{align}
+are the net poloidal and toroidal torques, respectively, acting at the resonant surface. 
+Note that the zeroth-order (in perturbed quantities) torques are zero because $B_r=0$. Furthermore, the linear (in perturbed quantities) torques 
 average to zero over the flux-surface. Hence, the largest non-zero torques  are quadratic in perturbed quantities. 
@@
 \begin{equation}\label{e156}
-T_{\phi\,s} = - \frac{n}{m}\,T_{\theta\,s}.
+T_{\varphi\,s} = - \frac{n}{m}\,T_{\theta\,s}.
 \end{equation}
@@
 T_{\theta\,s} &= -\frac{2\pi^2\,R_0\,m}{\mu_0}\,{\rm Im}({\mit\Delta\Psi}_s\,{\mit\Psi}_s^{\,\ast}),\\[0.5ex]
-T_{\phi\,s} &= \frac{2\pi^2\,R_0\,n}{\mu_0}\,{\rm Im}({\mit\Delta\Psi}_s\,{\mit\Psi}_s^{\,\ast})
+T_{\varphi\,s} &= \frac{2\pi^2\,R_0\,n}{\mu_0}\,{\rm Im}({\mit\Delta\Psi}_s\,{\mit\Psi}_s^{\,\ast})\label{e158}
 \end{align}
@@
 
-By analogy with the previous analysis,  the net poloidal and `toroidal' electromagnetic torques acting on the
+By analogy with the previous analysis,  the net poloidal and toroidal electromagnetic torques acting on the
 resistive wall are 
@@
 T_{\theta\,w} &= -\frac{2\pi^2\,R_0\,m}{\mu_0}\,{\rm Im}({\mit\Delta\Psi}_w\,{\mit\Psi}_w^{\,\ast}),\\[0.5ex]
-T_{\phi\,w} &= \frac{2\pi^2\,R_0\,n}{\mu_0}\,{\rm Im}({\mit\Delta\Psi}_w\,{\mit\Psi}_w^{\,\ast}),
+T_{\varphi\,w} &= \frac{2\pi^2\,R_0\,n}{\mu_0}\,{\rm Im}({\mit\Delta\Psi}_w\,{\mit\Psi}_w^{\,\ast}),
 \end{align}
@@
 Finally, 
-the net poloidal and `toroidal' electromagnetic torques acting on the
+the net poloidal and toroidal electromagnetic torques acting on the
 magnetic field-coil are 
@@
 T_{\theta\,c} &= -\frac{2\pi^2\,R_0\,m}{\mu_0}\,{\rm Im}({\mit\Delta\Psi}_c\,{\mit\Psi}_c^{\,\ast}),\\[0.5ex]
-T_{\phi\,c} &= \frac{2\pi^2\,R_0\,n}{\mu_0}\,{\rm Im}({\mit\Delta\Psi}_c\,{\mit\Psi}_c^{\,\ast}),\label{e166}
+T_{\varphi\,c} &= \frac{2\pi^2\,R_0\,n}{\mu_0}\,{\rm Im}({\mit\Delta\Psi}_c\,{\mit\Psi}_c^{\,\ast}),\label{e166}
 \end{align}
@@
  \end{align}
- However, according to Equations~(\ref{e123}), (\ref{e150a}), and (\ref{e151}), $E_{sw}=E_{ws}$ and $E_{wc}=E_{cw}$. 
+ However, according to Equations~(\ref{e123}), (\ref{e150a}), and (\ref{e151}), $E_{sw}=E_{ws}$ and 
+ $E_{wc}=E_{cw}$.
 We deduce that
@@
 T_{\theta\,s} + T_{\theta\,w}+T_{\theta\,c} &= 0,\\[0.5ex]
-T_{\phi\,s} + T_{\phi\,w}+T_{\phi\,c} &= 0.
+T_{\varphi\,s} + T_{\varphi\,w}+T_{\varphi\,c} &= 0.
 \end{align}
@@
 with respect to ion viscosity terms (because the
-former are order $\sqrt{m_e/m_i}$ smaller than the latter). Recall that the terms in square brackets are to remind us that the terms they precede are larger than the
-other terms in the equations (by the corresponding terms within the brackets).
-
-Taking the flux-surface average of the scalar product of $r\,{\bf e}_\theta$ with the plasma equation of motion, (\ref{e175}), we obtain 
-\begin{equation}
+former are order $\sqrt{m_e/m_i}$ smaller than the latter).
+(See Sections~\ref{sbrag} and \ref{s3.9}.) Recall that the terms in square brackets are there to remind us that the terms they precede are larger than the
+other terms in the equation (by the corresponding terms within the brackets).
+
+Taking  the scalar product of $r\,{\bf e}_\theta$ with the plasma equation of motion, (\ref{e175}), and integrating around magnetic
+flux-surfaces, we obtain 
+\begin{equation}\label{e176}
 \left\langle\rho\,\frac{\partial (r\,V_{\theta\,i})}{\partial t} \right\rangle 
@@
 has averaged to zero.
-Moreover, because $T_{\theta\,s}$ is quadratic in perturbed quantities (see Section~\ref{storque}), it is plausible that the right-hand side of the previous equation is not a dominant term [i.e., it is not ${\cal O}(\delta_i^{-2})$ larger than the
+Moreover, because $T_{\theta\,s}$ is quadratic in perturbed quantities (see Section~\ref{storque}), it is plausible that the right-hand side of the previous equation is no longer a dominant term [i.e., it is not ${\cal O}(\delta_i^{-2})$ larger than the
+other terms in the equation]. To be more exact, if $|\delta {\bf B}|/|{\bf B}|\sim \delta_i$ then the right-hand side ceases to be a dominant term in the equation.
+
+The largest contribution to $\langle r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\rangle$
+comes from the ion parallel viscosity tensor acting on the zeroth-order (in perturbed quantities) ion flow.
+(See Section~\ref{sbrag}.)  However, this contribution averages to zero in a cylindrical plasma in which $B_z$
+is constant on magnetic flux-surfaces. Of course, in reality, in a large aspect-ratio tokamak plasma, 
+$B_z$ varies slightly around magnetic flux-surfaces, being larger on the inboard side of the torus than on the outboard side (Wesson 2011).
+This variation gives rise to a residual contribution to $\langle r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\rangle$.
+It is plausible that this contribution is not a dominant term in Equation~(\ref{e176})  [i.e., it is not ${\cal O}(\zeta_i^{-1})$ larger than the
 other terms in the equation].
-
+To be more exact, if the residual contribution is ${\cal O}(\zeta_i)$ times smaller than the original contribution then  $\langle r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\rangle$ ceases to be a dominant term in the equation.
+
+According to the previous discussion, it is plausible that all terms appearing in Equation~(\ref{e176}) are of approximately equal
+magnitude when the inertial and viscous terms are evaluated with the zeroth-order ion flow, which can be written
+\begin{equation}
+{\bf V}_i = r\,{\mit\Omega}_\theta(r,t)\,{\bf e}_\theta + R_0\,{\mit\Omega}_\varphi(r,t)\,{\bf e}_z.
+\end{equation}
+Here, ${\mit\Omega}_\theta(r,t)$ and ${\mit\Omega}_\varphi(r,t)$ are the ion poloidal and toroidal angular velocity
+profiles, respectively. When $\langle r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\rangle$ is evaluated with  the ion parallel viscosity tensor, and the zeroth-order
+ion flow, it gives rise to a term that acts to relax the ion poloidal angular velocity profile toward a so-called {\em neoclassical
+profile}\/ determined by ion density and temperature gradients (Stix 1973; Hirshman \& Sigmar 1981). In principle, the
+contribution of the ion perpendicular viscosity tensor to $\langle r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\rangle$ 
+is ${\cal O}(\zeta_i^{\,2})$ smaller than the contribution of the ion parallel viscosity tensor. (See Section~\ref{sbrag}.) In practice, the magnitude of the ion perpendicular
+viscosity tensor is greatly enhanced above the value predicted by the Braginskii equations by the action of small-scale
+plasma turbulence (Wesson 2011). Hence, it is reasonable to include the contribution of the enhanced perpendicular
+viscosity tensor to $\langle r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\rangle$. Our model form for $\langle r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\rangle$ is written
+\begin{equation}\label{e178}
+\langle r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\rangle = 4\pi^2\,R_0\left[ \frac{\rho}{\tau_\theta}\,r^{\,3}\,({\mit\Omega}_\theta-{\mit\Omega}_{\theta\,{\rm nc}}) -\frac{\partial}{\partial r}\!\left(\mu\,r^{\,3}\,\frac{\partial{\mit\Omega}_\theta}{\partial r}\right)\right].
+\end{equation}
+Here, $\rho(r)$ is the equilibrium plasma mass density profile, $\tau_\theta(r)$ is the {\em poloidal flow-damping time}\/ (which
+is generally of order $\tau_i$), ${\mit\Omega}_{\theta\,{\rm nc}}(r)$ is the neoclassical poloidal angular velocity profile, and
+$\mu(r)$ is a phenomenological perpendicular viscosity due to plasma turbulence.
+
+When evaluated with the zeroth-order ion flow, Equation~(\ref{e176}) reduces to 
+\begin{equation}\label{e179}
+4\pi^2\,R_0\left[\rho\,r^{\,3}\,\frac{\partial {\mit\Omega}_\theta}{\partial t}+ \frac{\rho}{\tau_\theta}\,r^{\,3}\,({\mit\Omega}_\theta-{\mit\Omega}_{\theta\,{\rm nc}}) -\frac{\partial}{\partial r}\!\left(\mu\,r^{\,3}\,\frac{\partial{\mit\Omega}_\theta}{\partial r}\right)\right]
+=T_{\theta\,s}\,\delta(r-r_s)+ S_\theta,
+\end{equation}
+where use has been made of Equation~(\ref{e178}). 
+Here, we have added a source term, $S_\theta(r)$, to the equation. Let ${\mit\Omega}_{\theta\,0}(r)$ be the 
+unperturbed (by the tearing mode) ion poloidal angular velocity profile. It follows that 
+\begin{equation}
+S_\theta = 4\pi^2\,R_0\left[ \frac{\rho}{\tau_\theta}\,r^{\,3}\,({\mit\Omega}_{\theta\,0}-{\mit\Omega}_{\theta\,{\rm nc}}) -\frac{d}{d r}\!\left(\mu\,r^{\,3}\,\frac{d{\mit\Omega}_{\theta\,0}}{d r}\right)\right].
+\end{equation}
+Hence, writing
+\begin{equation}
+{\mit\Omega}_\theta(r,t)= {\mit\Omega}_{\theta\,0}(r) + {\mit\Delta\Omega}_\theta(r,t),
+\end{equation}
+where ${\mit\Delta\Omega}_{\theta}(r,t)$ is the  modification to the ion poloidal angular velocity profile
+induced by the poloidal electromagnetic torque that develops at the resonant surface, Equation~(\ref{e179})
+yields 
+\begin{equation}
+4\pi^2\,R_0\left[\rho\,r^{\,3}\,\frac{\partial {\mit\Delta\Omega}_\theta}{\partial t}+ \frac{\rho}{\tau_\theta}\,r^{\,3}\,{\mit\Delta\Omega}_\theta-\frac{\partial}{\partial r}\!\left(\mu\,r^{\,3}\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial r}\right)\right]
+=T_{\theta\,s}\,\delta(r-r_s).
+\end{equation}
+There is one further refinement that we can make to the previous equation. It turns out that neoclassical poloidal
+flow damping gives rise to an enhancement of poloidal ion inertia by a factor of $1+2\,q^{\,2}$ (Hirshman 1978). Hence,
+our final version of the perturbed plasma poloidal angular equation of motion becomes 
+\begin{equation}\label{e182}
+4\pi^2\,R_0\left[(1+2\,q^{\,2})\,\rho\,r^{\,3}\,\frac{\partial {\mit\Delta\Omega}_\theta}{\partial t}+ \frac{\rho}{\tau_\theta}\,r^{\,3}\,{\mit\Delta\Omega}_\theta-\frac{\partial}{\partial r}\!\left(\mu\,r^{\,3}\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial r}\right)\right]
+=T_{\theta\,s}\,\delta(r-r_s).
+\end{equation}
+
+Taking the scalar product of  $R_0\,{\bf e}_z$ with the plasma equation of motion, (\ref{e175}), and integrating around magnetic
+flux-surfaces, similar arguments to those just employed for the ion poloidal flow allow us to write the zeroth-order ion toroidal angular velocity profile in the form
+\begin{equation}
+{\mit\Omega}_\varphi(r,t)= {\mit\Omega}_{\varphi\,0}(r) + {\mit\Delta\Omega}_\varphi(r,t),
+\end{equation}
+where ${\mit\Omega}_{\varphi\,0}(r)$ is the 
+unperturbed (by the tearing mode) ion toroidal angular velocity profile, and ${\mit\Delta\Omega}_{\theta}(r,t)$ is the  modification to  this  profile
+induced by the toroidal electromagnetic torque that develops at the resonant surface. The perturbed ion toroidal angular
+equation of motion is written
+\begin{equation}\label{e185}
+4\pi^2\,R_0^{\,3}\left[\rho\,r\,\frac{\partial {\mit\Delta\Omega}_\varphi}{\partial t}-\frac{\partial}{\partial r}\!\left(\mu\,r\,\frac{\partial{\mit\Delta\Omega}_\varphi}{\partial r}\right)\right]
+=T_{\varphi\,s}\,\delta(r-r_s).
+\end{equation}
+Note that the ion parallel viscosity tensor does not give rise to damping of the toroidal flow profile. Furthermore, there is  no
+neoclassical enhancement of the plasma toroidal ion inertia.
+
+Equations~(\ref{e182}) and (\ref{e185}) are subject to the boundary conditions
+\begin{align}\label{e186}
+\frac{\partial{\mit\Delta\Omega}_\theta(0,t)}{\partial r} &= \frac{\partial{\mit\Delta\Omega}_\varphi(0,t)}{\partial r} =0,\\[0.5ex]
+{\mit\Delta\Omega}_\theta(a,t) &= {\mit\Delta\Omega}_\varphi(a,t)=0.\label{e187}
+\end{align}
+The boundary conditions (\ref{e186}) merely ensure that the ion angular velocities remain finite at the magnetic axis. 
+On the other  hand, the boundary conditions (\ref{e187}) are a consequence of the action of charge exchange with neutrals emitted isotropically from the wall  in the edge regions of the plasma
+(Brau, et al., 1983; Fitzpatrick 1993; Monier-Garbet, et al., 1997). Charge exchange with neutrals gives rise to 
+dominant damping torques acting at the edge of the plasma that relaxes the edge ion angular velocities  toward  particular values. Moreover, the
+electromagnetic torques that develop at the resonant surface are not large enough, compared with the charge-exchange torques,
+to modify the edge ion angular velocities (Fitzpatrick 1993).
+
+\subsection{Solution of Plasma Angular Equations of Motion}
+In general, the perturbed angular velocity profiles, ${\mit\Delta\Omega}_\theta(r,t)$ and ${\mit\Delta\Omega}_\varphi(r,t)$, are
+localized in the vicinity of the resonant surface (Fitzpatrick 1993). Hence, it is reasonable to write the perturbed angular
+equations of motion, (\ref{e182}) and (\ref{e185}), in the simplified  forms
+\begin{align}\label{e188}
+4\pi^2\,R_0\left[(1+2\,q_s^{\,2})\,\rho_s\,r^{\,3}\,\frac{\partial {\mit\Delta\Omega}_\theta}{\partial t}+ \frac{\rho_s}{\tau_{\theta\,s}}\,r^{\,3}\,{\mit\Delta\Omega}_\theta-\mu_s\frac{\partial}{\partial r}\!\left(r^{\,3}\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial r}\right)\right]
+&=T_{\theta\,s}\,\delta(r-r_s),\\[0.5ex]
+4\pi^2\,R_0^{\,3}\left[\rho_s\,r\,\frac{\partial {\mit\Delta\Omega}_\varphi}{\partial t}-\mu_s\frac{\partial}{\partial r}\!\left(r\,\frac{\partial{\mit\Delta\Omega}_\varphi}{\partial r}\right)\right]
+=T_{\varphi\,s}\,\delta(r-r_s),\label{e189}
+\end{align}
+where $q_s=q(r_s)$, $\rho_s=\rho(r_s)$, $\tau_{\theta\,s}=\tau_\theta(r_s)$, and $\mu_s=\mu(r_s)$.
+
+Let us write
+\begin{align}\label{e190}
+{\mit\Delta\Omega}_\theta(r,t) &= - \frac{1}{m}\sum_{p=1,\infty} \alpha_p(t)\,\frac{y_p(r/a)}{y_p(r_s/a)},\\[0.5ex]
+{\mit\Delta\Omega}_\varphi(r,t) &=  \frac{1}{n}\sum_{p=1,\infty} \beta_p(t)\,\frac{z_p(r/a)}{z_p(r_s/a)},\label{e191}
+\end{align}
+where
+\begin{align}
+y_p(r) &= \frac{J_1(j_{1\,p}\,r/a)}{r/a},\\[0.5ex]
+z_p(r) &= J_0(j_{0\,p}\,r/a).\label{e194}
+\end{align}
+Here, $J_m(z)$ is a Bessel function, and $j_{m,p}$ denotes its $p$th zero. Note that
+Equations~(\ref{e190})--(\ref{e194}) automatically satisfy the boundary conditions (\ref{e186}) and (\ref{e187}).
+
+It is easily demonstrated that 
+\begin{align}
+\frac{d}{dr}\!\left(r^{3}\,\frac{dy_p}{dr}\right)&= -\frac{j_{1\,p}^{\,2}\,r^{3}\,y_p}{a^{2}},\\[0.5ex]
+\frac{d}{dr}\!\left(r\,\frac{dz_p}{dr}\right)&= -\frac{j_{0\,p}^{\,2}\,r\,z_p}{a^{2}},
+\end{align}
+and
+\begin{align}
+\int_0^a r^{3}\,y_p(r)\,y_q(r)\,dr &= \frac{a^{4}}{2}\,[J_2(j_{1\,p})]^{\,2}\,\delta_{p,q},\\[0.5ex]
+\int_0^a r\,z_p(r)\,z_q(r)\,dr &= \frac{a^{2}}{2}\,[J_1(j_{0\,p})]^{\,2}\,\delta_{p,q}.\label{e197}
+\end{align}
+
+Equations~(\ref{e188}) and (\ref{e189}) yield
+\begin{align}\label{e198}
+(1+2\,q_k^{\,2})\,\frac{d\alpha_p}{dt} + \left(\frac{1}{\tau_{\theta\,s}}+\frac{j_{1,p}^{\,2}}{\tau_{M\,s}}\right)\alpha_p
+&= \frac{m^{2}\,[y_p(r_s/a)]^{\,2}}{\tau_A^{\,2}\,\epsilon^{\,2}\,[J_2(j_{1,p})]^{\,2}}\,
+{\rm Im}({\mit\Delta\hat{\Psi}_s}\,\hat{\mit\Psi}_s^{\,\ast}),\\[0.5ex]
+\frac{d\beta_p}{dt} + \frac{j_{0,p}^{\,2}}{\tau_{M\,s}}\,\beta_p
+&= \frac{n^{2}\,[z_p(r_s/a)]^{\,2}}{\tau_A^{\,2}\,[J_1(j_{0,p})]^{\,2}}\,
+{\rm Im}({\mit\Delta\hat{\Psi}_s}\,\hat{\mit\Psi}_s^{\,\ast}).\label{e199}
+\end{align}
+Here, $\tau_{M\,s} =\rho_s\,a^{\,2}/\mu_s$ is the {\em momentum confinement time}, $\tau_A = (\mu_0\,\rho_s\,a^{\,2}/B_z^{\,2})^{1/2}$ is the {\em Alfv\'{e}n time}, $\epsilon=a/R_0\ll 1$ is the {\em inverse aspect-ratio}\/ of the plasma,
+${\mit\Delta\Psi}_s = R_0\,B_z\,{\mit\Delta\hat{\Psi}}_s$, and ${\mit\Psi}_s = R_0\,B_z\,\hat{\mit\Psi}_s$. Moreover,
+use has been made of Equations~(\ref{e157}), (\ref{e158}), and (\ref{e190})--(\ref{e197}).
+
+\subsection{No-Slip Constraint}
+The reconnected magnetic flux at the resonant surface is assumed to convected by the local plasma flow. (See Section~\ref{sres}.) Hence, changes in the
+plasma flow at the resonant surface induced by the electromagnetic torques that develop in the vicinity of this
+surface will modify the convection velocity. Consequently, the natural frequency of the reconnected flux can be written
+\begin{equation}
+ \varpi_s(t) = \varpi_{s\,0} + ({\bf k}\cdot {\mit\Delta}{\bf V}_i)_{r=r_s}=
+ \varpi_{s\,0} + m\,{\mit\Delta\Omega}_\theta(r_s,t) - n\,{\mit\Delta\Omega}_\varphi(r_s,t),
+\end{equation}
+where $\varpi_{s\,0}$ is the unperturbed natural frequency.
+The previous expression is known as the {\em no-slip constraint}\/ (Fitzpatrick 1993), and has been verified experimentally (Vahala, et al., 1980).
+It follows from Equations~(\ref{e190})
+and (\ref{e191}) that
+\begin{equation}\label{e201}
+\varpi_s(t) = \varpi_{s\,0} - \sum_{p=1,\infty}\left[\alpha_p(t)+\beta_p(t)\right].
+\end{equation}
+
+\subsection{Final Equations}
+Equations~(\ref{e123}), (\ref{e133}), (\ref{e134}),  (\ref{e145})--(\ref{e151}), (\ref{e198}), (\ref{e199}), and (\ref{e201})
+can be combined to give the following complete set of equations that determine the time evolution of the reconnected 
+magnetic flux at the resonant surface:
+\begin{align}\label{e202}
+\tau_s\left(\frac{d\hat{\mit\Psi}_s}{dt} + {\rm i}\,\varpi_s\,\hat{\mit\Psi}_s\right) &= E_{ss}\,\hat{\mit\Psi}_s + E_{sw}\,\hat{\mit\Psi}_w,\\[0.5ex]
+\tau_w\,\frac{d\hat{\mit\Psi}_w}{dt} &= E_{sw}\,\hat{\mit\Psi}_s +\tilde{E}_{ww}\,\hat{\mit\Psi}_w
++\hat{I}_c,\\[0.5ex]
+\varpi_s(t)& = \varpi_{s\,0} - \sum_{p=1,\infty}\left[\alpha_p(t)+\beta_p(t)\right],\\[0.5ex]
+(1+2\,q_k^{\,2})\,\frac{d\alpha_p}{dt} + \left(\frac{1}{\tau_{\theta\,s}}+\frac{j_{1,p}^{\,2}}{\tau_{M\,s}}\right)\alpha_p
+&= \frac{m^{2}\,[y_p(r_s/a)]^{\,2}}{\tau_A^{\,2}\,\epsilon^{\,2}\,[J_2(j_{1,p})]^{\,2}}
+\,E_{sw}\,{\rm Im}(\hat{\mit\Psi}_w\,\hat{\mit\Psi}_s^{\,\ast}),\\[0.5ex]
+\frac{d\beta_p}{dt} + \frac{j_{0,p}^{\,2}}{\tau_{M\,s}}\,\beta_p
+&= \frac{n^{2}\,[z_p(r_s/a)]^{\,2}}{\tau_A^{\,2}\,[J_1(j_{0,p})]^{\,2}}\,
+E_{sw}\,{\rm Im}(\hat{\mit\Psi}_w\,\hat{\mit\Psi}_s^{\,\ast}).
+\end{align}
+Here, 
+\begin{align}
+\hat{I}_c &= \frac{\mu_0\,I_c}{R_0\,B_z}\left(\frac{r_w}{r_c}\right)^m,\\[0.5ex]
+\tilde{E}_{ww} &= E_{ww} + \frac{2m\,(r_w/r_c)^{2m}}{1-(r_w/r_c)^{2m}}.\label{e208}
+\end{align}
+
+\section{Reduced Drift-Magnetohydrodyamical Model}
+\subsection{Introduction}
+Equations~(\ref{e202})--(\ref{e208}) contain two quantities---namely, the reconnection time, $\tau_s$, and the unperturbed
+natural frequency, $\varpi_{s\,0}$---that can only be determined by solving for the plasma response in the radially thin resonant layer surrounding the resonant surface.
+Unfortunately, determining the resonant plasma response is not a straightforward task.
+The
+problem is that the small characteristic lengthscale in the resonant region (i.e., the resonant layer width) causes the ordering parameters
+$\delta_e$ and $\delta_i$ (see Section~\ref{s3.9}) to take values that are of order unity. Consequently, most of the simplifications described in
+Section~\ref{lowest} are not applicable in the resonant layer.
+In particular, many of the terms in the Braginskii equations (see Section~\ref{sbrag}) that are negligible in the outer region (e.g., plasma resistivity) have to be taken into account in the resonant layer.
+
+A tearing mode is a modified shear-Alfv\'{e}n wave (Hazeltine \& Meiss 1985), and has very little connection with the compressible-Alfv\'{e}n wave.
+For instance, the resonance condition, ${\bf k}\cdot{\bf B}=0$, which determines the position of the resonant
+surface, is identical to the resonance condition for a  shear-Alfv\'{e}n wave, but differs substantially from that of a  compressible-Alfv\'{e}n wave (Fitzpatrick 2015).
+Hence, one very effective way of simplifying the resonant layer equations is to remove the
+physics of a compressible-Alfv\'{e}n wave from them, in the process converting a drift-magnetohydrodynamical (MHD) model
+into a so-called {\em reduced drift-MHD model}\/ (Strauss 1976; Hazeltine, et al.\ 1985; Furuya, et al.\ 2003). The aim of
+this section is to describe the reduction process (which essentially boils down to arguing that the divergence of the
+plasma flow is small), and to derive the reduced drift-MHD equations that will subsequently be used to model the resonant
+response of the plasma.
+
+\subsection{Drift-MHD Equations}
+ It is helpful to define
+the following parameters:
+\begin{align}
+n_0 &= n(r_s),\\[0.5ex]
+p_0&= p(r_s),\\[0.5ex]
+\eta_e &=\left.\frac{d\ln T_e}{d\ln n}\right|_{r=r_s},\label{e211}\\[0.5ex]
+\eta_i &= \left.\frac{d\ln T_i}{d\ln n}\right|_{r=r_s},\\[0.5ex]
+\tau &= \left(\frac{T_e}{T_i}\right)_{r=r_s}\left(\frac{1+\eta_e}{1+\eta_i}\right),\label{e213}
+\end{align}
+where $n(r)$, $p(r)$, $T_e(r)$, and $T_i(r)$ refer to density, pressure, and temperature profiles that are unperturbed by the tearing mode.
+
+Let us assume, for the sake of simplicity, that the perturbed electron and ion temperature profiles in the vicinity of the resonant
+layer are functions of the perturbed electron number density profile. In other words, $T_e=T_e(n)$ and $T_i=T_i(n)$. 
+It follows that the perturbed total pressure profile is also a function of the perturbed electron number density profile: that is,
+$p=p(n)$. Let us define
+\begin{equation}
+{\bf V}_\ast = \frac{{\bf b}\times \nabla p}{e\,n_0\,B_z}.
+\end{equation}
+To lowest order, the electron and ion diamagnetic velocities take the respective forms
+\begin{align}
+{\bf V}_{\ast\,e} &= -\left(\frac{\tau}{1+\tau}\right){\bf V}_\ast,\\[0.5ex]
+{\bf V}_{\ast\,i} &= \left(\frac{1}{1+\tau}\right){\bf V}_\ast.
+\end{align}
+(See Section~\ref{lowest}.)
+The so-called {\em MHD velocity}\/ is defined
+\begin{equation}
+{\bf V} = {\bf V}_E + V_{\parallel\,i}\,{\bf b},
+\end{equation}
+where ${\bf V}_E$ is the ${\bf E}\times {\bf B}$ velocity, and $V_{\parallel\,i}$ is the parallel component of the ion
+fluid velocity. The lowest order electron and ion fluid velocities take the respective forms:
+\begin{align}
+{\bf V}_e &= {\bf V} +{\bf V}_{\ast\,i}-\frac{{\bf j}}{n_0\,e},\\[0.5ex]
+{\bf V}_i &= {\bf V} + {\bf V}_{\ast\,i}.
+\end{align}
+(See Section~\ref{lowest}.)
+
+Following Hazeltine \& Meiss 1992, if we neglect electron inertia and electron viscosity  in the electron equation of motion, (\ref{e3.79b}), then
+we obtain the {\em generalized Ohm's law}: 
+\begin{equation}\label{e220}
+{\bf E} + {\bf V}\times {\bf B} + \frac{1}{e\,n_0}\left[\nabla p + \frac{1}{1+\tau}\left(\frac{0.71\,\eta_e\,\tau}{1+\eta_e}-1\right)({\bf b}\cdot\nabla p)\,{\bf b} -{\bf j}\times{\bf b}\right] \simeq \eta_\parallel\,{\bf j}_\parallel + \eta_\perp\,{\bf j}_\perp.
+\end{equation}
+Here, $\eta_\parallel=1/\sigma_\parallel$ and $\eta_\theta=1/\sigma_\perp$ are the parallel and perpendicular plasma
+resistivities,  respectively. (See Section~\ref{sbrag}.) We have neglected the cross term in Equation~(\ref{e3.91a})
+because it is a factor $({\mit\Omega}_e\,\tau_e)^{-1}$  smaller than $\nabla p$.
+
+Next, we can add the electron and ion equations of motion, (\ref{e3.79b}) and (\ref{e3.80b}), again neglecting electron inertia and electron viscosity, 
+to give the {\em plasma equation of motion}: 
+\begin{equation}
+n_0\,m_i\left[\frac{\partial {\bf V}}{\partial t} + ({\bf V}\cdot\nabla ){\bf V} + \frac{1}{1+\tau}\,({\bf V}_\ast\cdot\nabla){\bf V}_E\right]
++ \nabla p + \nabla\cdot\bpi_i - {\bf j}\times {\bf B}\simeq 0.
+\end{equation}
+Here, $\nabla\cdot\bpi_i$ includes the contribution from the anomalous perpendicular viscosity tensor. The contribution from the gyroviscosity tensor,
+which is the same size as the ion inertial terms, has already been incorporated into the equation (Hazeltine \& Meiss 1992).
+We are neglecting the contribution of the parallel viscosity tensor  because we
+expect it to be much smaller than its nominal magnitude in a large aspect-ratio tokamak
+plasma.
+
+Finally, we can combine the electron and ion energy evolution equations, (\ref{e3.79c}) and (\ref{e3.80c}), to obtain
+a {\em plasma energy evolution equation}:
+\begin{equation}
+\frac{\partial p}{\partial t} + {\bf V}\cdot\nabla p + {\mit\Gamma}\,p\,\nabla\cdot{\bf V} + \frac{2}{3}\,\nabla\cdot {\bf q}\simeq 0, 
+\label{e223}
+\end{equation}
+where ${\mit\Gamma}=5/3$. Here, we have neglected a number of  terms (e.g., the ohmic heating terms) because they
+are, at least, factors $({\mit\Omega}_e\,\tau_e)^{-1}$ or  $({\mit\Omega}_i\,\tau_i)^{-1}$ smaller than $\nabla\cdot{\bf q}$. We have also neglected the viscous heating term because we
+expect the dominant contribution, which comes from the parallel viscosity, to be much smaller than its nominal magnitude in a large aspect-ratio tokamak
+plasma.
+
+Equations~(\ref{e220})---(\ref{e223}) are known collectively as the {\em drift-MHD equations}, and contain both shear-Alfv\'{e}n
+and compressible-Alfv\'{e}n wave dynamics. The system of equations is completed by Maxwell's equations:
+\begin{align}
+\nabla\cdot{\bf B} &= 0,\\[0.5ex]
+\nabla\times {\bf E} &= - \frac{\partial {\bf B}}{\partial t},\\[0.5ex]
+\mu_0\,{\bf j} &= \nabla \times {\bf B}.\label{e226}
+\end{align}
+
+\subsection{Normalization Scheme}
+Let $L$ be a typical variation lengthscale in the resonant layer. The {\em Alfv\'{e}n velocity}, which is the typical phase
+velocity of compressible Alfv\'{e}n waves, is defined
+\begin{equation}
+V_A = \frac{B_z}{\sqrt{\mu_0\,n_0\,m_i}}.
+\end{equation}
+It is helpful to define the  {\em collisionless ion skin-depth}: 
+\begin{equation}
+d_i = \left(\frac{m_i}{n_0\,e^{\,2}\,\mu_0}\right)^{1/2}.
+\end{equation}
+
+It is convenient to adopt the following normalization scheme that renders all quantities in the drift-MHD equations dimensionless: 
+$\hat{\nabla} = L\,\nabla$, $\hat{d}_i=d_i/L$, $\hat{t} = t/(L/V_A)$, $\hat{\bf B} = {\bf B}/B_z$, $\hat{\bf E} = {\bf E}/(B_z\,V_A)$,
+$\hat{\bf j} = {\bf j}/(B_z/\mu_0\,L)$, $\hat{\eta}_{\parallel,\perp} = \eta_{\parallel,\perp}/(\mu_0\,V_A\,L)$, $\hat{\bf V} = {\bf V}/V_A$,
+$\hat{{\bf V}}_{\ast,i}= {\bf V}_{\ast,i}/V_A$, $\hat{V}_{\parallel\,i}= V_{\parallel\,i}/V_A$, $\hat{p} = p/(B_z^{\,2}/\mu_0)$, $\hat{p}_0 = p_0/(B_z^{\,2}/\mu_0)$, $\hat{\bpi}_{i} = \bpi_{i}/(B_z^{\,2}/\mu_0)$,
+$\hat{\bf q} = {\bf q} /(B_z^{\,2}\,V_A/\mu_0)$. Equations~(\ref{e220})--(\ref{e226}) yield
+\begin{align}\label{e227}
+\hat{\bf E} + \hat{\bf V}\times \hat{\bf B} + \hat{d}_i\left[\hat{\nabla} \hat{p} + \frac{1}{1+\tau}\left(\frac{0.71\,\eta_e\,\tau}{1+\eta_e}-1\right)({\bf b}\cdot\hat{\nabla} \hat{p})\,{\bf b} + \hat{\nabla}\cdot\hat{\bpi}_e-\hat{\bf j}\times\hat{\bf b}\right] &\simeq \hat{\eta}_\parallel\,\hat{\bf j}_\parallel+ \hat{\eta}_\perp\,\hat{\bf j}_\perp,\\[0.5ex]
+\frac{\partial \hat{\bf V}}{\partial \hat{t}} 
++ (\hat{\bf V}\cdot\hat{\nabla} )\hat{\bf V} + 
+\frac{1}{1+\tau}\,(\hat{\bf V}_\ast\cdot\hat{\nabla})\hat{\bf V}_E
++ \hat{\nabla} \hat{p} + \hat{\nabla}\cdot\hat{\bpi}_i -
+ \hat{\bf j}\times \hat{\bf B} &\simeq 0,
+ \\[0.5ex]
+\frac{\partial \hat{p}}{\partial \hat{t}} + \hat{\bf V}\cdot\hat{\nabla} \hat{p} + {\mit\Gamma}\,\hat{p}\,\hat{\nabla}\cdot\hat{\bf V} + \frac{2}{3}\,\hat{\nabla}\cdot \hat{\bf q}&\simeq 0,\label{e229}
+\end{align}
+and
+\begin{align}
+\hat{\nabla}\cdot\hat{\bf B} &= 0,\label{e230}\\[0.5ex]
+\hat{\nabla}\times \hat{\bf E} &= - \frac{\partial \hat{\bf B}}{\partial \hat{t}},\label{e231}\\[0.5ex]
+\hat{\bf j} &= \hat{\nabla} \times \hat{\bf B}.\label{e232}
+\end{align}
+Finally,
+\begin{align}
+\hat{\bf V}_E &= \hat{\bf E}\times {\bf b},\\[0.5ex]
+\hat{\bf V} &= \hat{\bf V}_E + \hat{V}_{\parallel\,i}\,{\bf b},\\[0.5ex]
+\hat{\bf V}_\ast &= \hat{d}_i\,{\bf b}\times \hat{\nabla} \hat{p},\\[0.5ex]
+\hat{\bf V}_i &= \hat{\bf V} + \frac{\hat{\bf V}_{\ast\,i}}{1+\tau}.
+\end{align}
+
+\subsection{Reduction Process} 
+All variables in the resonant layer are assumed to be functions of $\hat{x}=(r-r_s)/L$ and $\zeta=m\,\theta-n\,\varphi$. 
+Let ${\bf n} = (0,\,\epsilon_s/q_s,\,1)$. It follows that ${\bf n}\cdot\nabla A$ for any $A(\hat{x},\zeta)$. 
+Let us write
+\begin{equation}\label{e238}
+\hat{\bf B} \simeq (1+ \delta b)\,{\bf n} + \hat{\nabla}\psi\times {\bf n},
+\end{equation}
+which automatically satisfies Equation~(\ref{e230}). Here, $\delta b(\hat{x},\zeta)$ and $\psi(\hat{x},\zeta)$ are assumed to be small
+compared to unity, which merely indicates that the perturbed magnetic field due to the tearing mode is small compared to the
+equilibrium magnetic field.  We can write
+\begin{equation}
+\hat{\bf E} \simeq \left(\hat{E}_\parallel- \frac{\partial \psi}{\partial \hat{t}}\right){\bf n} + \hat{\nabla}\left(\frac{\partial\chi}{\partial \hat{t}}\right)\times {\bf n} + \hat{\nabla}\phi,
+\end{equation}
+which automatically satisfies Equation~(\ref{e231}) provided that
+\begin{equation}
+\hat{\nabla}^2\chi =\delta b.
+\end{equation}
+Here, $\hat{E}_\parallel = E_\parallel/(B_z\,V_A)$ represents the constant inductive electric field that drives the equilibrium plasma current in the vicinity of the resonant surface.
+Now, $\partial/\partial \hat{t}$ and $\phi(\hat{x},\zeta)$
+are 
+assumed to be first order in small quantities, whereas $\hat{E}_\parallel$ is assumed to be second order. 
+It follows that
+\begin{align}
+\hat{\bf V}_E &\simeq \hat{\nabla}\phi\times {\bf n},\\[0.5ex]
+\hat{\bf V} &\simeq \hat{V}_{\parallel\,i}\,{\bf n}+  \hat{\nabla}\phi\times {\bf n}+\hat{\nabla}{\mit\Xi},
+\end{align}
+where $\hat{V}_{\parallel\,i}(\hat{x},\zeta)$ is assumed to be first order in small quantities, whereas ${\mit\Xi}(\hat{x},\zeta)$ is assumed to be
+second order. 
 We can write
-\begin{align}
-{\mit\Omega}_\theta(r,t)&= {\mit\Omega}_{\theta\,0}(r) + {\mit\Delta\Omega}_\theta(r,t),\\[0.5ex]
-{\mit\Omega}_\phi(r,t)&= {\mit\Omega}_{\phi\,0}(r) + {\mit\Delta\Omega}_\phi(r,t),
-\end{align}
-where ${\mit\Omega}_\theta(r,t)$ and ${\mit\Omega}_\phi(r,t)$ are the poloidal and 	`toroidal' plasma angular velocity profiles, respectively.
-[To be more exact,  ${\mit\Omega}_\theta(r,t)$ and ${\mit\Omega}_\phi(r,t)$ are the ion fluid angular velocity
-profiles.] Moreover, ${\mit\Omega}_{\theta\,0}(r)$ and ${\mit\Omega}_{\phi\,0}(r)$ are the corresponding unperturbed profiles,
-and ${\mit\Delta\Omega}_{\theta}(r,t)$ and ${\mit\Delta\Omega}_{\phi}(r,t)$ are the respective modifications to the profiles
-induced by the electromagnetic torques that develop at the resonant surface. The modifications to the angular
-velocity profiles are governed by the poloidal and toroidal angular equations of motion of the plasma, which
-take the respective forms
-\begin{align}
-4\pi^2\,R_0\left[(1+2\,q^2)\,\rho\,r^{\,3}\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial t}-\frac{\partial}{\partial r}\!\left(
-\mu\,r^{\,3}\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial r}\right) + \frac{\rho}{\tau_\theta}\,r^{\,3}\,{\mit\Delta\Omega}_\theta\right] = T_{\theta\,s}\,\delta(r-r_s),\\[0.5ex]
-4\pi^2\,R_0^{\,3}\left[\rho\,r\,\frac{\partial{\mit\Delta\Omega}_\phi}{\partial t}-\frac{\partial}{\partial r}\!\left(
-\mu\,r\,\frac{\partial{\mit\Delta\Omega}_\phi}{\partial r}\right) \right] = T_{\phi\,s}\,\delta(r-r_s).
-\end{align}
-Here, $\rho(r)$ is the plasma mass density profile, $\mu(r)$ is the anomalous plasma perpendicular ion viscosity
-(due to plasma turbulence), and $\tau_\theta(r)$ is the characteristic time at which neoclassical
-parallel viscosity relaxes the plasma poloidal angular velocity profile.
+\begin{equation}
+\hat{p}\simeq  \frac{\beta}{{\mit\Gamma}} + \delta p,
+\end{equation}
+where 
+\begin{equation}
+\beta= {\mit\Gamma}\,\hat{p}_0= \frac{{\mit\Gamma}\,p_0\,\mu_0}{B_z^{\,2}}.
+\end{equation}
+ Here, $\delta p(\hat{x},\zeta)$ is assumed to be first order in small
+quantities. 
+It follows that
+\begin{align}
+\hat{\bf V}_\ast &=\simeq \hat{d}_i\,{\bf n}\times \hat{\nabla} \delta p,\\[0.5ex]
+\hat{\bf V}_i&\simeq  \hat{V}_{\parallel\,i} \,{\bf n}+ \hat{\nabla}\left(\phi - \frac{\hat{d}_i\,\delta p}{1+\tau}\right)\times {\bf n}.
+\end{align}
+
+ The normalized drift-MHD equations, (\ref{e227})--(\ref{e229}), yield 
+ \begin{align}\label{e247}
+ \hat{d}_i\,\hat{\nabla}(\delta p + \delta b)\nonumber\\[0.5ex]+ \left(\hat{E}_{\parallel}-\frac{\partial\psi}{\partial \hat{t}} - [\psi,\phi]+ \frac{\hat{d}_i\,[\psi,\delta p]}{1+\tau}\left(1-\frac{0.71\,\eta_e\,\tau}{1+\eta_e}\right)
+ + \hat{d}_i\,[\psi,\delta b]+ \hat{\eta}_\parallel\,\hat{\nabla}^2\psi\right){\bf n}\nonumber\\[0.5ex]
+ +\hat{\nabla}\!\left(\frac{\partial\chi}{\partial \hat{t}} + {\mit\Xi} -\hat{\eta}_\perp\,\delta b\right)\times {\bf n} - b_z\,\hat{\nabla}\phi + \hat{V}_{\parallel\,i}\,\hat{\nabla}\psi
+ + \hat{d}_i\,\delta b\,\hat{\nabla}\delta b+ \hat{d}_i\,\hat{\nabla}^2\psi\,\hat{\nabla}\psi \simeq 0,\\[0.5ex]
+ \hat{\nabla}(\delta p + \delta b) + \left(\frac{\partial \hat{V}_{\parallel\,i}}{\partial \hat{t}} + [\hat{V}_{\parallel\,i},\phi] + [\psi,\delta b]\right){\bf n}\nonumber\\[0.5ex]
+ +\hat{\nabla}\!\left(\frac{\partial\phi}{\partial \hat{t}} - \frac{\hat{d}_i\,[\phi,\delta p]}{2\,(1+\tau)}\right)\times {\bf n} 
+ + \frac{1}{2}\,\hat{\nabla}\!
+ \left(\hat{V}_\perp^{\,2}+ \frac{\hat{\bf V}_\ast\cdot\hat{\bf V}_E }{1+\tau}+ \delta b^{\,2}\right)  \nonumber\\[0.5ex]
+-\hat{\nabla}^2\phi\,\hat{\nabla}\phi + \frac{\hat{d}_i}{2\,(1+\tau)}\left(\hat{\nabla}^2\phi\,\hat{\nabla}\delta p +\hat{\nabla}^2\delta p\,\hat{\nabla}\phi\right) + \hat{\nabla}^2\psi\,\hat{\nabla}\psi + \hat{\nabla}\cdot\hat{\bpi}_i \simeq 0,\label{e248}\\[0.5ex]
+\frac{\partial \delta p}{\partial \hat{t}} + [\delta p,\phi] +\beta\,\hat{\nabla}^2{\mit\Xi} + \frac{2}{3}\,\hat{\nabla}\cdot \hat{\bf q}\simeq 0,\label{e249}
+ \end{align}
+ where use has been made of Equation~(\ref{e232}), and
+ \begin{equation}
+ [A,B] \equiv \hat{\nabla} A\times \hat{\nabla} B\cdot{\bf n}.
+ \end{equation}
+ Here, $\hat{d}_i$ and $\beta$ are assumed to be zeroth order in small quantities, $\hat{\eta}_\parallel$ and $\hat{\eta}_\perp$ are assumed to be first order, while $\hat{\nabla}\cdot \hat{\bpi}_{i}$ and $\hat{\nabla}\cdot\hat{\bf q}$ are assumed to be second order.
+
+ To first order in small quantities, both Equations~(\ref{e247}) and (\ref{e248}) yield
+ \begin{equation}
+ \delta b \simeq - \delta p,
+ \end{equation}
+ which is an expression of lowest-order force balance. The scalar product of Equation~(\ref{e247}) with ${\bf n}$ gives
+ \begin{equation}\label{e252}
+ \frac{\partial\psi}{\partial\hat{t}}\simeq [\phi,\psi] +\hat{d}_i\left(\frac{\tau}{1+\tau}\right)\left(1+\frac{0.71\,\eta_e}{1+\eta_e}\right)
+ [\delta p,\psi] + \hat{\eta}_\parallel\,J + \hat{E}_\parallel,
+ \end{equation}
+ where
+ \begin{equation}
+ J = \hat{\nabla}^2\psi.
+ \end{equation}
+ The scalar product of Equation~(\ref{e248}) with ${\bf n}$ yields
+ \begin{equation}\label{e254}
+ \frac{\partial\hat{V}_{\parallel\,i}}{\partial\hat{t}}\simeq [\phi,\hat{V}_{\parallel\,i}]-[\delta p,\psi] -{\bf n}\cdot\hat{\nabla}\cdot\hat{\bpi}_i.
+ \end{equation}
+ The scalar product of the curl of Equation~(\ref{e247}) with ${\bf n}$ gives
+ \begin{equation}
+ \frac{\partial\delta p}{\partial\hat{t}}\simeq [\phi,\delta p]+\hat{\nabla}^2{\mit\Xi}-[\hat{V}_{\parallel\,i},\psi]
+ -\hat{d}_i\,[J,\psi] +\hat{\eta}_\perp\,\hat{\nabla}^{\,2}\delta p.
+ \end{equation}
+ Eliminating $\hat{\nabla}^2{\mit\Xi}$ between Equation~(\ref{e249}) and the previous equation, we obtain
+ \begin{align}\label{e256}
+ \frac{\partial\delta p}{\partial\hat{t}}\simeq [\phi,\delta p]-c_\beta^{\,2}\,[\hat{V}_{\parallel\,i},\psi]-c_\beta^{\,2}\,\hat{d}_i\,[J,\psi]
+ -\frac{2}{3}\,(1-c_\beta^{\,2})\,\hat{\nabla}\cdot\hat{\bf q} +c_\beta^{\,2}\,\hat{\eta}_\perp \hat{\nabla}^2\delta p,
+ \end{align}
+ where
+ \begin{equation}
+ c_\beta = \sqrt{\frac{\beta}{1+\beta}}.
+ \end{equation}
+ Finally, the scalar product of the curl of Equation~(\ref{e248}) with ${\bf n}$ gives 
+ \begin{align}\label{e258}
+ \frac{\partial U}{\partial\hat{t}}& \simeq [\phi,U] + \frac{\hat{d}_i}{2\,(1+\tau)}\left(
+ \hat{\nabla}^2[\phi,\delta p] + [\hat{\nabla}^2\phi,\delta p] + [\hat{\nabla}^2 \delta p,\phi]\right)
+ + [J,\psi] \nonumber\\[0.5ex]&\phantom{=} + {\bf n}\cdot\hat{\nabla}\times \hat{\nabla}\cdot\hat{\bpi}_i,
+ \end{align}
+ where 
+ \begin{equation}
+ U = \hat{\nabla}^{2}\phi.
+ \end{equation}
+
+We can write
+\begin{align}
+\hat{\nabla}\cdot \hat{\bf q} &\simeq- \left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\parallel\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\parallel\,i}\right)[[\delta p,\psi],\psi]\nonumber\\[0.5ex]
+&\phantom{=} - \left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\perp\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\perp\,i}\right)\nabla_\perp^{\,2} \delta p,\label{e260}
+\end{align}
+where $\chi_{\parallel\,e,i} = \kappa_{\parallel\,e,i}/n_0$, $\chi_{\perp\,e,i} = \kappa_{\perp\,e,i}/n_0$, $\hat{\chi}_{\parallel\,e,i}=
+\chi_{\parallel\,e,i}/(L\,V_A)$,  $\hat{\chi}_{\perp\,e,i}=
+\chi_{\perp\,e,i}/(L\,V_A)$, and use has been made of Equations~(\ref{e3.94a}),  (\ref{e3.94b}), (\ref{e211})--(\ref{e213}), and (\ref{e238}). 
+We can also
+write
+\begin{equation}
+\hat{\nabla}\cdot\hat{\bpi}_i \simeq - \hat{\chi}_\phi\,\hat{\nabla}^2\hat{\bf V}_i,
+\end{equation}
+where $\chi_\phi = \mu_{\perp\,i}/(n_0\,m_i)$, $\hat{\chi}_\phi = \chi_\phi/(L\,V_A)$, and $\mu_\perp$ is the anomalous
+ion perpendicular viscosity. It is easily seen that
+\begin{align}\label{e262}
+{\bf n}\cdot\hat{\nabla}\cdot\hat{\bpi}_i&\simeq -\hat{\chi}_\phi\,\hat{\nabla}^{2}\hat{V}_{\parallel\,i},\\[0.5ex]
+{\bf n}\cdot\hat{\nabla}\times \hat{\nabla}\cdot\hat{\bpi}_i&\simeq \hat{\chi}_\perp \,\hat{\nabla}^4\!\left(\phi - \frac{\hat{d}_i\,\delta p}{1+\tau}\right).\label{e263}
+\end{align}
+
+Let us define $V=\hat{V}_{\parallel\,i}$ and $N=c_\beta\,\delta p$.
+Equations~(\ref{e252})--(\ref{e254}), (\ref{e256}), (\ref{e258})--(\ref{e260}), (\ref{e262}), and (\ref{e263}) yield the following closed set of equations:
+\begin{align}
+\frac{\partial\psi}{\partial\hat{t}}&\simeq [\phi,\psi] + \hat{d}_\beta\left(\frac{\tau}{1+\tau}\right)\left(1+\frac{0.71\,\eta_e}{1+\eta_e}\right)[N,\psi]
++\hat{\eta}_\parallel\,J + \hat{E}_\parallel,\\[0.5ex]
+\frac{\partial U}{\partial \hat{t}}&\simeq [\phi,U] + \frac{\hat{d}_\beta}{2\,(1+\tau)}\left(\hat{\nabla}^2[\phi,N] + [\hat{\nabla}^2\phi,N] + [\hat{\nabla}^2 N,\phi]\right) + [J,\psi] \nonumber\\[0.5ex]&\phantom{=}+\hat{\chi}_\perp  \,\hat{\nabla}^4\!\left(\phi - \frac{\hat{d}_\beta\,N}{1+\tau}\right), \\[0.5ex]
+\frac{\partial N}{\partial \hat{t}}&\simeq [\phi,N] -c_\beta\,[V,\psi] -\hat{d}_\beta\,[J,\psi] + \hat{D}_\parallel\,[[N,\psi],\psi]
++ \hat{D}_\perp\,\hat{\nabla}^{\,2}N,\\[0.5ex]
+\frac{\partial V}{\partial\hat{t}}&\simeq [\phi,V] - c_\beta\,[N,\psi] + \hat{\chi}_\phi\,\hat{\nabla}^2 V,\\[0.5ex]
+J &=\hat{\nabla}^2\psi,\\[0.5ex]
+U &=\hat{\nabla}^2 \phi.
+\end{align}
+Here, 
+\begin{equation}
+d_\beta = c_\beta\,d_i,
+\end{equation}
+and $\hat{d}_\beta=d_\beta/L$. 
+Moreover,
+\begin{align}
+\hat{D}_\parallel&= \frac{2}{3}\,(1-c_\beta^{\,2})\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\parallel\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\parallel\,i}\right),\\[0.5ex]
+\hat{D}_\perp &= c_\beta^{\,2}\,\hat{\eta}_\perp +  \frac{2}{3}\,(1-c_\beta^{\,2})\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\perp\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\perp\,i}\right).
+\end{align}
 
@@
 \begin{description}
-\item Braginskii, S.I.\ 1965. {\em Transport Processes in a Plasma}. In {\em Reviews of Plasma Physics}. Consultants Bureau. Volume~1, 205.
-\item Chapman, S., and Cowling, T.G.\ 1953. {\em The Mathematical Theory of Non-Uniform Gases}. Cambridge.
-\item Fitzpatrick, R.\ 1993. {\em Interaction of Tearing Modes with External Structures in Cylindrical Geometry}, Nucl.\ Fusion {\bf 33}, 1049 (1993). 
+\item Braginskii, S.I.\ 1965. {\em Transport Processes in a Plasma}. In {\em Reviews of Plasma Physics}. Consultants Bureau. Vol.~1, 205.
+\item Brau, K., et al.\ 1983. {\em Plasma Rotation in the PDX Tokamak}. Nucl.\ Fusion {\bf 23}, 1643.
+\item Chapman, S., and Cowling, T.G.\ 1953. {\em The Mathematical Theory of Non-Uniform Gases}. Cambridge University Press.
+\item Fitzpatrick, R.\ 1993. {\em Interaction of Tearing Modes with External Structures in Cylindrical Geometry}. Nucl.\ Fusion {\bf 33}, 1049. 
 \item Fitzpatrick, R.\ 2008. {\em Maxwell's Equations and the Principles of Electromagnetism}. Jones \& Bartlett.
 \item Fitzpatrick, R.\ 2015. {\em Plasma Physics: An Introduction}. Taylor \& Francis, CRC Press. 
+\item Fitzpatrick, R.\ and Waelbroeck, F.L.\ 2005. {\em Two-Fluid Magnetic Island Dynamics in Slab Geometry. I. Isolated Islands}.
+Phys.\ Plasmas {\bf 12}, 022307. 
+\item Fitzpatrick, R.\ and Waelbroeck, F.L.\ 2009. {\em Effect of Flow Damping on Drift-Tearing Magnetic Islands in Tokamak Plasmas}.
+Phys.\ Plasmas {\bf 16}, 072507.
+\item Furth, H.P., Killeen, J., and Rosenbluth, M.N.\ 1963. {\em Finite-Resistivity Instabilities of a Sheet Pinch}. Phys.\ Fluids {\bf 6}, 459.
+\item Furuya, A., Yagi, M., and Itoh, S.-I.\ 2003. {\em Linear Analysis of Neoclassical Tearing Mode
+Based on the Four-Field Reduced Neoclassical MHD Equation}. J.\ Phys.\ Soc. Japan {\bf 72}, 313.
+\item Hazeltine, R.D., Kotschenreuther, M., and Morrison, P.G.\ 1985. {\em A Four-Field Model for Tokamak Plasma Dynamics}.
+ Phys.\ Fluids {\bf 28}, 2466.
+\item Hazeltine, R.D., and Meiss, J.D.\ 1985. {\em Shear-Alfv\'{e}n Dynamcis of Toroidally Confined Plasmas}. Physics Reports {\bf 121}, 1.
+\item Hazeltine, R.D., and Meiss, J.D.\ 1992. {\em Plasma Confinement}. Addison-Wesley. 
+\item Hirshman, S.P.\ 1978. {\em The Ambipolarity Paradox in Toroidal Diffusion, Revisited}. Nucl.\ Fusion {\bf 18}, 917.
+\item Hirshman, S.P., and Sigmar, D.J.\ 1981.\ {\em Neoclassical Transport of Impurities in Tokamak Plasmas}. Nucl.\ Fusion {\bf 21}, 1079.
+\item Nave, M.F.F., and Wesson, J.A., 1990. {\em Mode Locking in Tokamaks}. Nucl.\ Fusion {\bf 30}, 2575. 
+\item Monier-Garbet, P., et al.\ 1997. {\em Effects of Neutrals on Plasma Rotation in DIII-D}. Nucl.\ Fusion {\bf 37}, 403.
 \item Reif, F.\ 1965. {\em Fundamentals of Statistical and Thermal Physics}. McGraw-Hill.
 \item Richardson, A.S.\ 2019. {\em 2019 NRL Plasma Formulary}.  Naval Research Laboratory.
+\item Stix, T.H.\ 1973. {\em Decay of Poloidal Rotation in a Tokamak Plasma}. Phys.\ Fluids {\bf 16}, 1260.
+\item Stauss, H.R.\ 1976. {\em Nonlinear, Three-Dimensional Magnetohydrodynamics of  Noncircular Tokamaks}. Phys.\ Fluids {\bf 19}  134.
+\item Vahala, G., et al., 1980. {\em Perturbed Magnetic-Field Phase Slip for Tokamaks}. Nucl.\ Fusion {\bf 20}, 17.
+\item Wesson, J.\  1978. {\em Hydrodynamic Stability of Tokamaks}. Nucl.\ Fusion {\bf 18}, 87.
+\item Wesson, J.\ 2011. {\em Tokamaks}. Oxford University Press. 
 \end{description}

### 2021-11-01 Documentation/TearingModeTheory.tex
Added to tearing writeup

@@
 
-\section{Fluid Theory}
+\section{Introduction}
+
+\section{Plasma Fluid Theory}
 \subsection{Introduction}
@@
 \begin{align}\label{e3.79a}
-\frac{dn}{dt} + n\,\nabla\cdot{\bf V}_e &= 0,\\[0.5ex]
-m_e \,n\,\frac{d {\bf V}_e}{dt} + \nabla p_e+ \nabla\cdot \bpi_e + e\, n\,
+\frac{d_en}{dt} + n\,\nabla\cdot{\bf V}_e &= 0,\\[0.5ex]
+m_e \,n\,\frac{d_e {\bf V}_e}{dt} + \nabla p_e+ \nabla\cdot \bpi_e + e\, n\,
 ({\bf E} + {\bf V}_e\times {\bf B})& = {\bf F},\label{e3.79b}\\[0.5ex]
-\frac{3}{2}\frac{d p_e}{dt} + \frac{5}{2}\,p_e\,\nabla\cdot{\bf V}_e
+\frac{3}{2}\frac{d_e p_e}{dt} + \frac{5}{2}\,p_e\,\nabla\cdot{\bf V}_e
 + \bpi_e:\nabla{\bf V}_e+ \nabla\cdot{\bf q}_e &= w_e,\label{e3.79c}
@@
 \begin{align}\label{e3.80a}
-\frac{dn}{dt} + n\,\nabla\cdot{\bf V}_i &= 0,\\[0.5ex]
-m_i \,n\,\frac{d {\bf V}_i}{dt} + \nabla p_i + \nabla\cdot \bpi_i - e\, n\,
+\frac{d_i n}{dt} + n\,\nabla\cdot{\bf V}_i &= 0,\\[0.5ex]
+m_i \,n\,\frac{d_i {\bf V}_i}{dt} + \nabla p_i + \nabla\cdot \bpi_i - e\, n\,
 ({\bf E} + {\bf V}_i\times {\bf B})& =- {\bf F},\label{e3.80b}\\[0.5ex]
-\frac{3}{2}\frac{d p_i}{dt} + \frac{5}{2}\,p_i\,\nabla\cdot{\bf V}_i
+\frac{3}{2}\frac{d_i p_i}{dt} + \frac{5}{2}\,p_i\,\nabla\cdot{\bf V}_i
 + \bpi_i:\nabla{\bf V}_i+ \nabla\cdot{\bf q}_i &= w_i,\label{e3.80c}
@@
 species-$s$ scalar
-pressure, $\bpi_s$ is the species-$s$ viscosity tensor, ${\bf F}$ is the collisional friction force density, ${\bf q}_s$ is the species-$s$ heat flux density, $w_s$ is the species-$s$ collisional heating rate density, and ${\bf E}$ is the ambient electric field strength.
-Moreover, $d/dt\equiv \partial/\partial t + {\bf V}_e\cdot\nabla$ in the electron fluid equations, (\ref{e3.79a})--(\ref{e3.79c}), whereas  $d/dt\equiv \partial/\partial t + {\bf V}_i\cdot\nabla$ in the ion fluid equations,  (\ref{e3.80a})--(\ref{e3.80c}).
+pressure, $\bpi_s$ is the species-$s$ viscosity tensor, ${\bf F}$ is the collisional friction force density, ${\bf q}_s$ is the species-$s$ heat flux density, $w_s$ is the species-$s$ collisional heating rate density, and ${\bf E}$ is the ambient electric field-strength.
+Moreover, $d_e/dt\equiv \partial/\partial t + {\bf V}_e\cdot\nabla$ in the electron fluid equations, (\ref{e3.79a})--(\ref{e3.79c}), whereas  $d_i/dt\equiv \partial/\partial t + {\bf V}_i\cdot\nabla$ in the ion fluid equations,  (\ref{e3.80a})--(\ref{e3.80c}).
 
@@
 
- It is convenient to split the friction force
+ It is convenient to split the friction force density
 ${\bf F}$ into a component ${\bf F}_U$ corresponding to resistivity, and a
-component ${\bf F}_T$ corresponding to the thermal force. Thus,
+component ${\bf F}_T$ corresponding to the so-called {\em thermal force}. Thus,
 \begin{equation}
@@
 \begin{align}
-\frac{dn}{dt} + n\,\nabla\cdot{\bf V}_e &= 0,\\[0.5ex]
-m_e\, n\,\frac{d {\bf V}_e}{dt} + \nabla p_e+ \nabla\cdot \bpi_e + e\, n\,
+\frac{d_e n}{dt} + n\,\nabla\cdot{\bf V}_e &= 0,\\[0.5ex]
+m_e\, n\,\frac{d_e {\bf V}_e}{dt} + \nabla p_e+ \nabla\cdot \bpi_e + e\, n\,
 ({\bf E} + {\bf V}_e\times {\bf B})& = {\bf F}_U +{\bf F}_T,\\[0.5ex]
-\frac{3}{2}\frac{d p_e}{dt} + \frac{5}{2}\,p_e\,\nabla\cdot{\bf V}_e
+\frac{3}{2}\frac{d_e p_e}{dt} + \frac{5}{2}\,p_e\,\nabla\cdot{\bf V}_e
 + \bpi_e:\nabla{\bf V}_e+ \nabla\cdot{\bf q}_{Te} 
@@
 \begin{align}
-\frac{d\hat{n}}{d\hat{t}} + \hat{n}\,\widehat{\nabla}\cdot\widehat{\bf V}_e &=0,\label{e3.113a}\\[0.5ex]
-\hat{n}\,\frac{d\widehat{\bf V}_e}{d\hat{t}} +
+\frac{d_e \hat{n}}{d\hat{t}} + \hat{n}\,\widehat{\nabla}\cdot\widehat{\bf V}_e &=0,\label{e3.113a}\\[0.5ex]
+\hat{n}\,\frac{d_e \widehat{\bf V}_e}{d\hat{t}} +
 \delta_e^{-2}\,\widehat{\nabla}\hat{p}_e +\zeta_e^{-1}\,\widehat{\nabla}
@@
 \times\widehat{\bf B}) &= \delta_e^{-2}\,\zeta_e\,\widehat{\bf F}_U +\delta_e^{-2}\,\widehat{\bf F}_T, \\[0.5ex]
-\frac{3}{2}\frac{d\hat{p}_e}{d\hat{t}} + \frac{5}{2}\,
+\frac{3}{2}\frac{d_e \hat{p}_e}{d\hat{t}} + \frac{5}{2}\,
 \hat{p}_e\,\widehat{\nabla}\cdot\widehat{\bf V}_e + \delta_e^{2}\,
@@
 parameters $\delta_e$, $\zeta_e$, and $\mu$. 
-Here, $d/d\hat{t}\equiv\partial /\partial\hat{t} +
+Here, $d_e/d\hat{t}\equiv\partial /\partial\hat{t} +
  \widehat{\bf V}_e\cdot\widehat{\nabla}$. It is assumed that $T_e\sim T_i$.
@@
 \begin{align}
-\frac{dn}{dt} + n\,\nabla\cdot{\bf V}_i &= 0,\\[0.5ex]
-m_i\, n\,\frac{d {\bf V}_i}{dt} + \nabla p_i + \nabla\cdot \bpi_i - e\, n\,
+\frac{d_i n}{dt} + n\,\nabla\cdot{\bf V}_i &= 0,\\[0.5ex]
+m_i\, n\,\frac{d_i {\bf V}_i}{dt} + \nabla p_i + \nabla\cdot \bpi_i - e\, n\,
 ({\bf E} + {\bf V}_i\times {\bf B})& =- {\bf F}_U -{\bf F}_T,\\[0.5ex]
-\frac{3}{2}\frac{d p_i}{dt} + \frac{5}{2}\,p_i\,\nabla \cdot {\bf V}_i
+\frac{3}{2}\frac{d_i p_i}{dt} + \frac{5}{2}\,p_i\,\nabla \cdot {\bf V}_i
 + \bpi_i:\nabla{\bf V}_i+ \nabla\cdot{\bf q}_i & =w_i.
@@
 \begin{align}\label{e3.116a}
-\frac{d\hat{n}}{d\hat{t}} + \hat{n}\,\widehat{\nabla}\cdot\widehat{\bf V}_i &=0,\\[0.5ex]
-\hat{n}\,\frac{d\widehat{\bf V}_i}{d\hat{t}} +
+\frac{d_i \hat{n}}{d\hat{t}} + \hat{n}\,\widehat{\nabla}\cdot\widehat{\bf V}_i &=0,\\[0.5ex]
+\hat{n}\,\frac{d_i \widehat{\bf V}_i}{d\hat{t}} +
 \delta_i^{-2}\,\widehat{\nabla}\hat{p}_i+\zeta_i^{-1}\,\widehat{\nabla}
@@
  - \delta_i^{-2}\,\widehat{\bf F}_T, \\[0.5ex]
-\frac{3}{2}\frac{d\hat{p}_i}{d\hat{t}} + \frac{5}{2}\,
+\frac{3}{2}\frac{d_i \hat{p}_i}{d\hat{t}} + \frac{5}{2}\,
 \hat{p}_i\,\widehat{\nabla}\cdot\widehat{\bf V}_i + \delta_i^{2}\,
@@
 parameters $\delta_i$, $\zeta_i$, and $\mu$. 
-Here, $d/d\hat{t}\equiv\partial /\partial\hat{t} +
+Here, $d_i/d\hat{t}\equiv\partial /\partial\hat{t} +
  \widehat{\bf V}_i\cdot\widehat{\nabla}$.
@@
 Note that the zeroth-order (in perturbed quantities) torques are zero because $B_r=0$. Furthermore, the linear (in perturbed quantities) torques 
-average to zero over the flux-surface. Hence, the largest non-zero torques  are quadratic in perturbed quantities. 
+average to zero over the flux-surface. Hence, the largest non-zero torques  are {\em quadratic}\/ in perturbed quantities. 
 According to Equation~(\ref{e82}), 
@@
 where $\delta{\bf j}$ is the density of the current sheet flowing at the resonant surface, and we have made use
-of the fact that $\delta j_r\simeq 0$. 
+of the fact that $\delta j_r\simeq 0$ in a radially thin current sheet. 
  It follows from the previous three equations that
@@
 The boundary conditions (\ref{e186}) merely ensure that the ion angular velocities remain finite at the magnetic axis. 
-On the other  hand, the boundary conditions (\ref{e187}) are a consequence of the action of charge exchange with neutrals emitted isotropically from the wall  in the edge regions of the plasma
+On the other  hand, the boundary conditions (\ref{e187}) are a consequence of the action of {\em charge exchange}\/ with electrically neutral particles emitted isotropically from the wall  in the edge regions of the plasma
 (Brau, et al., 1983; Fitzpatrick 1993; Monier-Garbet, et al., 1997). Charge exchange with neutrals gives rise to 
-dominant damping torques acting at the edge of the plasma that relaxes the edge ion angular velocities  toward  particular values. Moreover, the
+dominant damping torques acting at the edge of the plasma that relax the edge ion angular velocities  toward  particular values. Moreover, the
 electromagnetic torques that develop at the resonant surface are not large enough, compared with the charge-exchange torques,
-to modify the edge ion angular velocities (Fitzpatrick 1993).
+to significantly modify the edge ion angular velocities (Fitzpatrick 1993).
 
@@
 
-\section{Reduced Drift-Magnetohydrodyamical Model}
+\section{Reduced Drift-MHD Resonant Plasma Response Model}
 \subsection{Introduction}
@@
 The
-problem is that the small characteristic lengthscale in the resonant region (i.e., the resonant layer width) causes the ordering parameters
+problem is that the small characteristic lengthscale in the resonant region (i.e., the resonant layer width) causes the fundamental ordering parameters
 $\delta_e$ and $\delta_i$ (see Section~\ref{s3.9}) to take values that are of order unity. Consequently, most of the simplifications described in
@@
 Hence, one very effective way of simplifying the resonant layer equations is to remove the
-physics of a compressible-Alfv\'{e}n wave from them, in the process converting a drift-magnetohydrodynamical (MHD) model
-into a so-called {\em reduced drift-MHD model}\/ (Strauss 1976; Hazeltine, et al.\ 1985; Furuya, et al.\ 2003). The aim of
+physics of a compressible-Alfv\'{e}n wave from them altogether, in the process converting a drift-magnetohydrodynamical (MHD) response model
+into a so-called {\em reduced}\/ drift-MHD response model (Strauss 1976; Hazeltine, et al.\ 1985; Furuya, et al.\ 2003). The aim of
 this section is to describe the reduction process (which essentially boils down to arguing that the divergence of the
@@
 (See Section~\ref{lowest}.)
-The so-called {\em MHD velocity}\/ is defined
+The so-called {\em MHD velocity}, which is the velocity of a fictional `MHD fluid',  is defined
 \begin{equation}
@@
 \end{equation}
-Here, $\eta_\parallel=1/\sigma_\parallel$ and $\eta_\theta=1/\sigma_\perp$ are the parallel and perpendicular plasma
+Here, $\eta_\parallel=1/\sigma_\parallel$ and $\eta_\perp=1/\sigma_\perp$ are the parallel and perpendicular plasma
 resistivities,  respectively. (See Section~\ref{sbrag}.) We have neglected the cross term in Equation~(\ref{e3.91a})
@@
 \end{equation}
-Here, $\nabla\cdot\bpi_i$ includes the contribution from the anomalous perpendicular viscosity tensor. The contribution from the gyroviscosity tensor,
+Here, $\nabla\cdot\bpi_i$ includes the contribution from the anomalous (i.e., enhanced due to the action of small-scale plasma turbulence) perpendicular viscosity tensor.
+The contribution from the gyroviscosity tensor,
 which is the same size as the ion inertial terms, has already been incorporated into the equation (Hazeltine \& Meiss 1992).
@@
 
-Equations~(\ref{e220})---(\ref{e223}) are known collectively as the {\em drift-MHD equations}, and contain both shear-Alfv\'{e}n
+Equations~(\ref{e220})--(\ref{e223}) are known collectively as the {\em drift-MHD equations}, and contain both shear-Alfv\'{e}n
 and compressible-Alfv\'{e}n wave dynamics. The system of equations is completed by Maxwell's equations:
@@
 \subsection{Normalization Scheme}
-Let $L$ be a typical variation lengthscale in the resonant layer. The {\em Alfv\'{e}n velocity}, which is the typical phase
+Let $l$ be a typical variation lengthscale in the resonant layer. The {\em Alfv\'{e}n velocity}, which is the typical phase
 velocity of compressible Alfv\'{e}n waves, is defined
@@
 \end{equation}
+Note that $d_i=c/\omega_{p\,i}$, where $c$ is the velocity of light, and $\omega_{p\,i}$ is the ion plasma
+frequency (Fitzpatrick 2015).
 
 It is convenient to adopt the following normalization scheme that renders all quantities in the drift-MHD equations dimensionless: 
-$\hat{\nabla} = L\,\nabla$, $\hat{d}_i=d_i/L$, $\hat{t} = t/(L/V_A)$, $\hat{\bf B} = {\bf B}/B_z$, $\hat{\bf E} = {\bf E}/(B_z\,V_A)$,
-$\hat{\bf j} = {\bf j}/(B_z/\mu_0\,L)$, $\hat{\eta}_{\parallel,\perp} = \eta_{\parallel,\perp}/(\mu_0\,V_A\,L)$, $\hat{\bf V} = {\bf V}/V_A$,
+$\hat{\nabla} = l\,\nabla$, $\hat{d}_i=d_i/l$, $\hat{t} = t/(l/V_A)$, $\hat{\bf B} = {\bf B}/B_z$, $\hat{\bf E} = {\bf E}/(B_z\,V_A)$,
+$\hat{\bf j} = {\bf j}/(B_z/\mu_0\,l)$, $\hat{\eta}_{\parallel,\perp} = \eta_{\parallel,\perp}/(\mu_0\,V_A\,l)$, $\hat{\bf V} = {\bf V}/V_A$,
 $\hat{{\bf V}}_{\ast,i}= {\bf V}_{\ast,i}/V_A$, $\hat{V}_{\parallel\,i}= V_{\parallel\,i}/V_A$, $\hat{p} = p/(B_z^{\,2}/\mu_0)$, $\hat{p}_0 = p_0/(B_z^{\,2}/\mu_0)$, $\hat{\bpi}_{i} = \bpi_{i}/(B_z^{\,2}/\mu_0)$,
@@
 \subsection{Reduction Process} 
-All variables in the resonant layer are assumed to be functions of $\hat{x}=(r-r_s)/L$ and $\zeta=m\,\theta-n\,\varphi$. 
-Let ${\bf n} = (0,\,\epsilon_s/q_s,\,1)$. It follows that ${\bf n}\cdot\nabla A$ for any $A(\hat{x},\zeta)$. 
-Let us write
+All variables in the resonant layer are assumed to be functions of $\hat{x}=(r-r_s)/l$ and $\zeta=m\,\theta-n\,\varphi$ only. 
+Let ${\bf n} = (0,\,\epsilon/q_s,\,1)$, where $\epsilon=r/R_0$ and $q_s=m/n$. It follows that ${\bf n}\cdot\nabla A=0$ for any $A(\hat{x},\zeta)$. 
+Let us write (Fitzpatrick \& Waelbroeck 2009)
 \begin{equation}\label{e238}
@@
 \end{equation}
-which automatically satisfies Equation~(\ref{e230}). Here, $\delta b(\hat{x},\zeta)$ and $\psi(\hat{x},\zeta)$ are assumed to be small
+which automatically satisfies Equation~(\ref{e230}).
+(Here, we are assuming that $|r-r_s|\ll a$ inside the resonant layer.) Here, $\delta b(\hat{x},\zeta)$ and $\psi(\hat{x},\zeta)$ are assumed to be small
 compared to unity, which merely indicates that the perturbed magnetic field due to the tearing mode is small compared to the
@@
 \begin{equation}
-\hat{\bf E} \simeq \left(\hat{E}_\parallel- \frac{\partial \psi}{\partial \hat{t}}\right){\bf n} + \hat{\nabla}\left(\frac{\partial\chi}{\partial \hat{t}}\right)\times {\bf n} + \hat{\nabla}\phi,
+\hat{\bf E} \simeq \left(\hat{E}_\parallel- \frac{\partial \psi}{\partial \hat{t}}\right){\bf n} + \hat{\nabla}\!\left(\frac{\partial\chi}{\partial \hat{t}}\right)\times {\bf n} + \hat{\nabla}\phi,
 \end{equation}
@@
 Here, $\hat{E}_\parallel = E_\parallel/(B_z\,V_A)$ represents the constant inductive electric field that drives the equilibrium plasma current in the vicinity of the resonant surface.
-Now, $\partial/\partial \hat{t}$ and $\phi(\hat{x},\zeta)$
+Moreover, $\partial/\partial \hat{t}$ and $\phi(\hat{x},\zeta)$
 are 
@@
 \begin{align}
-\hat{\bf V}_\ast &=\simeq \hat{d}_i\,{\bf n}\times \hat{\nabla} \delta p,\\[0.5ex]
-\hat{\bf V}_i&\simeq  \hat{V}_{\parallel\,i} \,{\bf n}+ \hat{\nabla}\left(\phi - \frac{\hat{d}_i\,\delta p}{1+\tau}\right)\times {\bf n}.
+\hat{\bf V}_\ast &\simeq \hat{d}_i\,{\bf n}\times \hat{\nabla} \delta p,\\[0.5ex]
+\hat{\bf V}_i&\simeq  \hat{V}_{\parallel\,i} \,{\bf n}+ \hat{\nabla}\!\left(\phi - \frac{\hat{d}_i\,\delta p}{1+\tau}\right)\times {\bf n}.
 \end{align}
@@
  + \hat{d}_i\,[\psi,\delta b]+ \hat{\eta}_\parallel\,\hat{\nabla}^2\psi\right){\bf n}\nonumber\\[0.5ex]
- +\hat{\nabla}\!\left(\frac{\partial\chi}{\partial \hat{t}} + {\mit\Xi} -\hat{\eta}_\perp\,\delta b\right)\times {\bf n} - b_z\,\hat{\nabla}\phi + \hat{V}_{\parallel\,i}\,\hat{\nabla}\psi
- + \hat{d}_i\,\delta b\,\hat{\nabla}\delta b+ \hat{d}_i\,\hat{\nabla}^2\psi\,\hat{\nabla}\psi \simeq 0,\\[0.5ex]
+ +\hat{\nabla}\!\left(\frac{\partial\chi}{\partial \hat{t}} + {\mit\Xi} -\hat{\eta}_\perp\,\delta b\right)\times {\bf n} + \frac{\hat{d}_i}{2}\,\hat{\nabla}\delta b^{\,2}- b_z\,\hat{\nabla}\phi + \hat{V}_{\parallel\,i}\,\hat{\nabla}\psi
++  \hat{d}_i\,\hat{\nabla}^2\psi\,\hat{\nabla}\psi \simeq 0,\\[0.5ex]
  \hat{\nabla}(\delta p + \delta b) + \left(\frac{\partial \hat{V}_{\parallel\,i}}{\partial \hat{t}} + [\hat{V}_{\parallel\,i},\phi] + [\psi,\delta b]\right){\bf n}\nonumber\\[0.5ex]
@@
  \end{equation}
- which is an expression of lowest-order force balance. The scalar product of Equation~(\ref{e247}) with ${\bf n}$ gives
+ which is simply an expression of lowest-order equilibrium force balance. The scalar product of Equation~(\ref{e247}) with ${\bf n}$ gives
  \begin{equation}\label{e252}
@@
 \end{align}
-where $\chi_{\parallel\,e,i} = \kappa_{\parallel\,e,i}/n_0$, $\chi_{\perp\,e,i} = \kappa_{\perp\,e,i}/n_0$, $\hat{\chi}_{\parallel\,e,i}=
-\chi_{\parallel\,e,i}/(L\,V_A)$,  $\hat{\chi}_{\perp\,e,i}=
-\chi_{\perp\,e,i}/(L\,V_A)$, and use has been made of Equations~(\ref{e3.94a}),  (\ref{e3.94b}), (\ref{e211})--(\ref{e213}), and (\ref{e238}). 
+where $\hat{\nabla}_\perp^{\,2}\equiv \hat{\nabla}\cdot\hat{\nabla}_\perp$, $\chi_{\parallel\,e,i} = \kappa_{\parallel\,e,i}/n_0$, $\chi_{\perp\,e,i} = \kappa_{\perp\,e,i}/n_0$, $\hat{\chi}_{\parallel\,e,i}=
+\chi_{\parallel\,e,i}/(l\,V_A)$,  $\hat{\chi}_{\perp\,e,i}=
+\chi_{\perp\,e,i}/(l\,V_A)$, and use has been made of Equations~(\ref{e3.94a}),  (\ref{e3.94b}), (\ref{e211})--(\ref{e213}), and (\ref{e238}). 
 We can also
@@
 \end{equation}
-where $\chi_\phi = \mu_{\perp\,i}/(n_0\,m_i)$, $\hat{\chi}_\phi = \chi_\phi/(L\,V_A)$, and $\mu_\perp$ is the anomalous
-ion perpendicular viscosity. It is easily seen that
+where $\chi_\phi = \mu_{\perp}/(n_0\,m_i)$, $\hat{\chi}_\phi = \chi_\phi/(l\,V_A)$, and $\mu_\perp$ is the anomalous
+ion perpendicular viscosity. Note that the previous equation is entirely phenomenological in nature.  It is easily seen that
 \begin{align}\label{e262}
@@
 
-Let us define $V=\hat{V}_{\parallel\,i}$ and $N=c_\beta\,\delta p$.
-Equations~(\ref{e252})--(\ref{e254}), (\ref{e256}), (\ref{e258})--(\ref{e260}), (\ref{e262}), and (\ref{e263}) yield the following closed set of equations:
-\begin{align}
+Let us define $V=\hat{V}_{\parallel\,i}$ and $N=\delta p/c_\beta$.
+Equations~(\ref{e252})--(\ref{e254}), (\ref{e256}), (\ref{e258})--(\ref{e260}), (\ref{e262}), and (\ref{e263}) yield the following closed set of equations (Fitzpatrick \& Waelbroeck 2005):
+\begin{align}\label{e264}
 \frac{\partial\psi}{\partial\hat{t}}&\simeq [\phi,\psi] + \hat{d}_\beta\left(\frac{\tau}{1+\tau}\right)\left(1+\frac{0.71\,\eta_e}{1+\eta_e}\right)[N,\psi]
 +\hat{\eta}_\parallel\,J + \hat{E}_\parallel,\\[0.5ex]
-\frac{\partial U}{\partial \hat{t}}&\simeq [\phi,U] + \frac{\hat{d}_\beta}{2\,(1+\tau)}\left(\hat{\nabla}^2[\phi,N] + [\hat{\nabla}^2\phi,N] + [\hat{\nabla}^2 N,\phi]\right) + [J,\psi] \nonumber\\[0.5ex]&\phantom{=}+\hat{\chi}_\perp  \,\hat{\nabla}^4\!\left(\phi - \frac{\hat{d}_\beta\,N}{1+\tau}\right), \\[0.5ex]
+\frac{\partial U}{\partial \hat{t}}&\simeq [\phi,U] + \frac{\hat{d}_\beta}{2\,(1+\tau)}\left(\hat{\nabla}^2[\phi,N] + [\hat{\nabla}^2\phi,N] + [\hat{\nabla}^2 N,\phi]\right) + [J,\psi] \nonumber\\[0.5ex]&\phantom{=}+\hat{\chi}_\perp  \,\hat{\nabla}^4\!\left(\phi - \frac{\hat{d}_\beta\,N}{1+\tau}\right),\label{e265} \\[0.5ex]
 \frac{\partial N}{\partial \hat{t}}&\simeq [\phi,N] -c_\beta\,[V,\psi] -\hat{d}_\beta\,[J,\psi] + \hat{D}_\parallel\,[[N,\psi],\psi]
-+ \hat{D}_\perp\,\hat{\nabla}^{\,2}N,\\[0.5ex]
-\frac{\partial V}{\partial\hat{t}}&\simeq [\phi,V] - c_\beta\,[N,\psi] + \hat{\chi}_\phi\,\hat{\nabla}^2 V,\\[0.5ex]
++ \hat{D}_\perp\,\hat{\nabla}_\perp^{\,2}N,\label{e266}\\[0.5ex]
+\frac{\partial V}{\partial\hat{t}}&\simeq [\phi,V] - c_\beta\,[N,\psi] + \hat{\chi}_\phi\,\hat{\nabla}^2 V,\label{e267}\\[0.5ex]
 J &=\hat{\nabla}^2\psi,\\[0.5ex]
-U &=\hat{\nabla}^2 \phi.
+U &=\hat{\nabla}^2 \phi.\label{e269}
 \end{align}
 Here, 
-\begin{equation}
-d_\beta = c_\beta\,d_i,
-\end{equation}
-and $\hat{d}_\beta=d_\beta/L$. 
+\begin{align}
+d_\beta &= c_\beta\,d_i = \left(\frac{{\mit\Gamma}}{1+\beta}\right)^{1/2}\rho_s,\\[0.5ex]
+ \rho_s &= \frac{v_t}{{\mit\Omega}_i},\\[0.5ex]
+v_t &= \left(\frac{T_e+T_i}{m_i}\right)^{1/2}_{r_s},
+\end{align}
+and $\hat{d}_\beta=d_\beta/l$. The quantity $\rho_s$ is usually referred to as the {\em ion sound radius}. 
 Moreover,
@@
 \end{align}
+
+\subsection{Discussion}
+Equations~(\ref{e264})--(\ref{e269}) constitute our reduced, four-field, drift-MHD, resonant, plasma response model. Our model is very similar
+to the original four-field model derived by Hazeltine, et al.\ (Hazeltine, et al.\ 1985). Equation~(\ref{e264}) is the {\em generalized
+Ohm's law}\/ that governs the time evolution of the helical magnetic flux, $\psi$. Equation~(\ref{e265}) is the {\em parallel
+ion vorticity equation}\/ that governs the  time evolution of the parallel ion vorticity, $U$. 
+Equation~(\ref{e266}) is the {\em electron number density continuity equation}\/ that 
+governs the time evolution of the electron number density, $N$. Finally, Equation~(\ref{e267}) is the
+{\em ion parallel equation of motion}\/ that governs the time evolution of the  parallel ion velocity, $V$.
+
+If we neglect $d_\beta$ in our reduced drift-MHD model, which is equivalent to saying that the ion sound
+radius is much smaller than the radial extent of the resonant layer, then our four-field resonant response model
+decouples into two independent two-field models. The first two-field model takes the form:
+\begin{align}\label{e275}
+\frac{\partial\psi}{\partial\hat{t}}&\simeq [\phi,\psi]+\hat{\eta}_\parallel\,J + \hat{E}_\parallel,\\[0.5ex]
+\frac{\partial U}{\partial \hat{t}}&\simeq [\phi,U]  + [J,\psi]+\hat{\chi}_\perp  \,\hat{\nabla}^4\phi.\label{e276}
+\end{align}
+Of course, this is a {\em reduced MHD model}\/ that describes shear-Alfv\'{e}n dynamics perpendicular to
+magnetic field-lines (Strauss 1976). The second two-field model takes the form:
+\begin{align}
+\frac{\partial N}{\partial \hat{t}}&\simeq [\phi,N] -c_\beta\,[V,\psi] + \hat{D}_\parallel\,[[N,\psi],\psi]
++ \hat{D}_\perp\,\hat{\nabla}_\perp^{\,2}N,\\[0.5ex]
+\frac{\partial V}{\partial\hat{t}}&\simeq [\phi,V] - c_\beta\,[N,\psi] + \hat{\chi}_\phi\,\hat{\nabla}^2 V,
+\end{align}
+where $\psi$ is assumed to take its unperturbed value. 
+This model describes ion sound wave dynamics parallel to magnetic field-lines. It should be noted that the
+ion sound radius is {\em not}\/ negligibly small compared to the radial extents of resonant layers in present-day
+tokamak plasmas. Hence, the `single-fluid' reduced MHD model, (\ref{e275})--(\ref{e276}), provides  a very poor description
+of the response of  resonant layers in tokamak plasmas.
+
+Finally, the crucial element of the reduction process, by which our original drift-MHD response model is converted into a
+reduced drift-MHD model, is the set of ordering assumptions that render $\hat{\nabla}\cdot \hat{\bf V}=\hat{\nabla}^2{\mit\Xi}$
+a second-order quantity while leaving $\hat{\bf V}$ a first-order quantity. This ordering implies that the  MHD fluid is
+{\em incompressible}\/ to lowest-order. It should be noted, however, that the small, but finite, compressibility of the
+MHD fluid has a significant influence on the form of the continuity equation (\ref{e266}).
+
+\section{Linear Resonant Plasma Response Model}
+\subsection{Introduction}
+The aim of this section is to employ the reduced, drift-MHD, resonant, plasma response model derived in the
+previous section to determine the {\em linear}\/ response of the resonant layer to external perturbations.
 
@@
 \item Furuya, A., Yagi, M., and Itoh, S.-I.\ 2003. {\em Linear Analysis of Neoclassical Tearing Mode
-Based on the Four-Field Reduced Neoclassical MHD Equation}. J.\ Phys.\ Soc. Japan {\bf 72}, 313.
+Based on the Four-Field Reduced Neoclassical MHD Equation}. J.\ Phys.\ Soc.\ Japan {\bf 72}, 313.
 \item Hazeltine, R.D., Kotschenreuther, M., and Morrison, P.G.\ 1985. {\em A Four-Field Model for Tokamak Plasma Dynamics}.
  Phys.\ Fluids {\bf 28}, 2466.
-\item Hazeltine, R.D., and Meiss, J.D.\ 1985. {\em Shear-Alfv\'{e}n Dynamcis of Toroidally Confined Plasmas}. Physics Reports {\bf 121}, 1.
+\item Hazeltine, R.D., and Meiss, J.D.\ 1985. {\em Shear-Alfv\'{e}n Dynamics of Toroidally Confined Plasmas}. Physics Reports {\bf 121}, 1.
 \item Hazeltine, R.D., and Meiss, J.D.\ 1992. {\em Plasma Confinement}. Addison-Wesley. 
@@
 \item Stix, T.H.\ 1973. {\em Decay of Poloidal Rotation in a Tokamak Plasma}. Phys.\ Fluids {\bf 16}, 1260.
-\item Stauss, H.R.\ 1976. {\em Nonlinear, Three-Dimensional Magnetohydrodynamics of  Noncircular Tokamaks}. Phys.\ Fluids {\bf 19}  134.
+\item Strauss, H.R.\ 1976. {\em Nonlinear, Three-Dimensional Magnetohydrodynamics of  Noncircular Tokamaks}. Phys.\ Fluids {\bf 19},  134.
 \item Vahala, G., et al., 1980. {\em Perturbed Magnetic-Field Phase Slip for Tokamaks}. Nucl.\ Fusion {\bf 20}, 17.

### 2021-11-06 Documentation/TearingModeTheory.tex
Added more to tearing mode writeup

@@
 \usepackage{fullpage}
+\usepackage{amsmath}
+\usepackage{amssymb}
 \allowdisplaybreaks
@@
 the mean kinetic energy of particles of
-that species. (Here, $s$ represents either $e$ for electrons, or $i$ for ions.) In tokamak plasma physics, kinetic temperature
-is invariably measured in {\em electron-volts}\/ \index{electron-volt} (1 joule is equivalent to
-$6.24\times 10^{18}$\,eV).
+that species. (Here, $s$ represents either $e$ for electrons, or $i$ for ions.)
 
@@
 Equations (\ref{e3.79a})--(\ref{e3.80c})  are called the {\em Braginskii equations}, because they were first obtained
-in a celebrated article by S.I.~Braginskii (Braginskii 1965). Here, $n$ is the electron number density, ${\bf V}_s$ is the species-$s$ flow velocity, $p_s=n\,T_s$ is the 
+in a celebrated article by S.I.~Braginskii (Braginskii 1965). Here, $n$ is the electron number density, ${\bf V}_s$ the species-$s$ flow velocity, $p_s=n\,T_s$ the 
 species-$s$ scalar
-pressure, $\bpi_s$ is the species-$s$ viscosity tensor, ${\bf F}$ is the collisional friction force density, ${\bf q}_s$ is the species-$s$ heat flux density, $w_s$ is the species-$s$ collisional heating rate density, and ${\bf E}$ is the ambient electric field-strength.
-Moreover, $d_e/dt\equiv \partial/\partial t + {\bf V}_e\cdot\nabla$ in the electron fluid equations, (\ref{e3.79a})--(\ref{e3.79c}), whereas  $d_i/dt\equiv \partial/\partial t + {\bf V}_i\cdot\nabla$ in the ion fluid equations,  (\ref{e3.80a})--(\ref{e3.80c}).
-
-A tokamak plasma is highly magnetized. In other words, 
+pressure, $\bpi_s$ the species-$s$ viscosity tensor, ${\bf F}$ the collisional friction force density, ${\bf q}_s$  the species-$s$ heat flux density, $w_s$ the species-$s$ collisional heating rate density, and ${\bf E}$  the ambient electric field-strength.
+Moreover, $d_e/dt\equiv \partial/\partial t + {\bf V}_e\cdot\nabla$ and   $d_i/dt\equiv \partial/\partial t + {\bf V}_i\cdot\nabla$.
+
+A tokamak plasma is {\em highly magnetized}. In other words, 
 \begin{equation}
@@
 \end{align}
-Here, ${\bf b}={\bf B}/B$ is a unit vector parallel to the magnetic field, and ${\bf j}= n\,e\,({\bf V}_i-{\bf V}_e)$ is the net plasma current density. 
-Moreover, the {\em parallel electrical conductivity}, $\sigma_\parallel$,  is given by
+Here, ${\bf b}={\bf B}/B$ is a unit vector parallel to the magnetic field, and ${\bf j}= n\,e\,({\bf V}_i-{\bf V}_e)$ is the plasma current density. 
+Moreover, the {\em parallel electrical conductivity}\/ is given by
 \begin{equation}\label{e3.83}
@@
 \end{equation} 
-whereas the {\em perpendicular electrical conductivity}, $\sigma_\perp$,  takes the form
+whereas the {\em perpendicular electrical conductivity}\/ takes the form
 \begin{equation}\label{e3.92}
@@
 field. Likewise, ${\bf j}_\parallel \equiv ({\bf b}\cdot{\bf j})\,{\bf b}$
-represents the component of the plasma current flowing parallel to the
+represents the component of the plasma current density  flowing parallel to the
 magnetic field, whereas ${\bf j}_\perp \equiv {\bf j} - {\bf j}_\parallel$
-represents the perpendicular component of the plasma current.
+represents the perpendicular component of the plasma current density.
 
@@
 \begin{align}
-{\bf q}_e &= -\kappa_\parallel^e\,\nabla_\parallel T_e -\kappa_\perp^e\,
+{\bf q}_e &= -\kappa_{\parallel\,e}\,\nabla_\parallel T_e -\kappa_{\perp\,e}\,
 \nabla_\perp T_e
--\kappa_\times^e\,{\bf b}\times\nabla_\perp T_e- 0.71\,\frac{T_e}{e}\,{\bf j}_\parallel-
+-\kappa_{\times\,e}\,{\bf b}\times\nabla_\perp T_e- 0.71\,\frac{T_e}{e}\,{\bf j}_\parallel-
 \frac{3\,T_e}{2\,{\mit\Omega}_e\,\tau_e\,e}\,{\bf b}\times{\bf j}_\perp,\label{e3.94a}\\[0.5ex]
-{\bf q}_i &= -\kappa_\parallel^i\,\nabla_\parallel T_i -\kappa_\perp^i\,
+{\bf q}_i &= -\kappa_{\parallel\,i}\,\nabla_\parallel T_i -\kappa_{\perp\,i}\,
 \nabla_\perp T_i
-+\kappa_\times^i\,{\bf b}\times\nabla_\perp T_i,\label{e3.94b}
++\kappa_{\times\,i}\,{\bf b}\times\nabla_\perp T_i,\label{e3.94b}
 \end{align}
@@
 \begin{align}\label{e3.87a}
-\kappa_\parallel^e &= 3.2\,\,\frac{n\,\tau_e\,T_e}{m_e},\\[0.5ex]
-\kappa_\parallel^i &= 3.9\,\,\frac{n\,\tau_i\,T_i}{m_i},\label{e3.87b}
+\kappa_{\parallel\,e} &= 3.2\,\,\frac{n\,\tau_e\,T_e}{m_e},\\[0.5ex]
+\kappa_{\parallel\,i} &= 3.9\,\,\frac{n\,\tau_i\,T_i}{m_i},\label{e3.87b}
 \end{align} 
@@
 \begin{align}
-\kappa_\perp^e &= 4.7\,\frac{n\,T_e}{m_e\,{\mit\Omega}_e^{\,2}\,\tau_e},\\[0.5ex]
-\kappa_\perp^i &= 2\, \frac{n\,T_i}{m_i\,{\mit\Omega}_i^{\,2}\,\tau_i}.
+\kappa_{\perp\,e} &= 4.7\,\frac{n\,T_e}{m_e\,{\mit\Omega}_e^{\,2}\,\tau_e},\\[0.5ex]
+\kappa_{\perp\,i} &= 2\, \frac{n\,T_i}{m_i\,{\mit\Omega}_i^{\,2}\,\tau_i}.
 \end{align}
@@
 \begin{align}
-\kappa_\times^e &= \frac{5\,n\,T_e}{2\,m_e\,{\mit\Omega}_e},\\[0.5ex]
-\kappa_\times^i &=\frac{5\,n\,T_i}{2\,m_i\,{\mit\Omega}_i}.
+\kappa_{\times\,e} &= \frac{5\,n\,T_e}{2\,m_e\,{\mit\Omega}_e},\\[0.5ex]
+\kappa_{\times\,i} &=\frac{5\,n\,T_i}{2\,m_i\,{\mit\Omega}_i}.
 \end{align}
@@
 \begin{align}\label{e3.89a}
-\eta_0^e &= 0.73\,n\,\tau_e\,T_e,\\[0.5ex]
-\eta_0^i &= 0.96\,n\,\tau_i\,T_i,\label{e3.89b}
+\eta_{0\,e} &= 0.73\,n\,\tau_e\,T_e,\\[0.5ex]
+\eta_{0\,i} &= 0.96\,n\,\tau_i\,T_i.\label{e3.89b}
 \end{align}
@@
 \begin{align}
-\eta_1^e &= 0.51\, \frac{n\,T_e}{{\mit\Omega}_e^{\,2}\,\tau_e},\\[0.5ex]
-\eta_1^i &= \frac{3\, n\,T_i}{10\,{\mit\Omega}_i^{\,2}\,\tau_i}.
+\eta_{1\,e} &= 0.51\, \frac{n\,T_e}{{\mit\Omega}_e^{\,2}\,\tau_e},\\[0.5ex]
+\eta_{1\,i} &= \frac{3\, n\,T_i}{10\,{\mit\Omega}_i^{\,2}\,\tau_i}.
 \end{align}
@@
 \begin{align}
-\eta_3^e &= -\frac{n\,T_e}{2\,{\mit\Omega}_e} ,\\[0.5ex]
-\eta_3^i &= \frac{n\,T_i}{2\,{\mit\Omega}_i}.
+\eta_{3\,e} &= -\frac{n\,T_e}{2\,{\mit\Omega}_e} ,\\[0.5ex]
+\eta_{3\,i} &= \frac{n\,T_i}{2\,{\mit\Omega}_i}.
 \end{align}
@@
 very wide range of different physical phenomena. For this reason, they are
-extremely complicated. Fortunately, however, it is not generally 
+extremely complicated in nature. Fortunately, however, it is not generally 
 necessary to retain all of
-the terms in these equations when investigating tearing mode dynamics in tokamak plasmas. In this section, we shall attempt to construct a systematic
-normalization scheme for the Braginskii equations that will, hopefully, enable us
+the terms in these equations when investigating tearing mode dynamics in tokamak plasmas. In this section, we shall construct a systematic
+normalization scheme for the Braginskii equations that will enable us
 to determine which terms to keep, and which to discard, when investigating
@@
 
- It is convenient to split the friction force density
-${\bf F}$ into a component ${\bf F}_U$ corresponding to resistivity, and a
-component ${\bf F}_T$ corresponding to the so-called {\em thermal force}. Thus,
+ It is convenient to split the friction force density,
+${\bf F}$, into a component, ${\bf F}_U$, corresponding to resistivity, and a
+component, ${\bf F}_T$, corresponding to the so-called {\em thermal force density}. Thus,
 \begin{equation}
@@
 {\bf F}_T &= - 0.71\,n\,\nabla_\parallel T_e
--\frac{3\,n}{2\,{\mit\Omega}_e\,\tau_e}\,{\bf b}\times\nabla_\perp T_e.
-\end{align}
-Likewise, the electron collisional energy gain term $w_e$ is split
-into a component $-w_i$ corresponding to the energy lost to the ions (in the
-ion rest frame), a component $w_U$ corresponding to work done by the friction
-force ${\bf F}_U$, and a component $w_T$ corresponding to work done by the
-thermal force ${\bf F}_T$. Thus,
+-\frac{3\,n}{2\,{\mit\Omega}_e\,\tau_e}\,{\bf b}\times\nabla_\perp T_e.\label{e43}
+\end{align}
+Likewise, the electron collisional energy gain term, $w_e$, is split
+into a component, $-w_i$, corresponding to the energy lost per unit volume to the ions (in the
+ion rest frame), a component, $w_U$, corresponding to work done by the friction
+force density, ${\bf F}_U$, and a component, $w_T$, corresponding to work done by the
+thermal force density, ${\bf F}_T$. Thus,
 \begin{equation}
@@
 \end{align}
-Finally, it is helpful to split the electron heat flux density ${\bf q}_e$ into
-a diffusive component ${\bf q}_{Te}$ and a convective component ${\bf q}_{Ue}$. 
+Finally, it is helpful to split the electron heat flux density, ${\bf q}_e$, into
+a diffusive component, ${\bf q}_{Te}$, and a convective component, ${\bf q}_{Ue}$. 
 Thus,
@@
 \begin{align}
-{\bf q}_{Te} &=-\kappa_\parallel^e\,\nabla_\parallel T_e -\kappa_\perp^e\,
+{\bf q}_{Te} &=-\kappa_{\parallel\,e}\,\nabla_\parallel T_e -\kappa_{\perp\,e}\,
 \nabla_\perp T_e
--\kappa_\times^e\,{\bf b}\times\nabla_\perp T_e,\\[0.5ex]
+-\kappa_{\times\,e}\,{\bf b}\times\nabla_\perp T_e,\\[0.5ex]
 {\bf q}_{Ue}&=  0.71\,\frac{T_e}{e}\,{\bf j}_\parallel-
@@
  such that the ${\bf E}\times{\bf B}$
-velocity is of  similar magnitude to the electron fluid velocity. Note that the parallel viscosity
+velocity is of  similar magnitude to the electron diamagnetic velocity.  (See Section~\ref{lowest}.) Note that the parallel viscosity
 makes an ${\cal O}(1)$ contribution to $\widehat{\bpi}_e$, whereas the gyroviscosity
@@
  such that the ${\bf E}\times{\bf B}$
-velocity is of similar  magnitude to the ion fluid velocity. Note that the parallel viscosity
+velocity is of similar  magnitude to the ion diamagnetic velocity. Note that the parallel viscosity
 makes an ${\cal O}(1)$ contribution to $\widehat{\bpi}_i$, whereas the gyroviscosity
@@
 \end{align}
-The terms in square brackets are there to remind us that the terms they precede are smaller or larger than the
-other terms in the equations (by the corresponding terms within the brackets).
+The factors in square brackets are there to remind us that the terms they precede are smaller or larger than the
+other terms in the equations (by the corresponding factors within the brackets).
 
@@
 \begin{equation}
-\nabla\cdot{\bf q}_{T_e}\simeq \nabla\cdot(-\kappa_\parallel^e\,\nabla_\parallel T_e)\simeq 0,
+\nabla\cdot{\bf q}_{T_e}\simeq \nabla\cdot(-\kappa_{\parallel\,e}\,\nabla_\parallel T_e)\simeq 0,
 \end{equation}
@@
 \begin{equation}
-\nabla\cdot{\bf q}_{T_i}\simeq \nabla\cdot(-\kappa_\parallel^i\,\nabla_\parallel T_i)\simeq 0,
+\nabla\cdot{\bf q}_{T_i}\simeq \nabla\cdot(-\kappa_{\parallel\,i}\,\nabla_\parallel T_i)\simeq 0,
 \end{equation}
@@
 \end{equation}
-where $p=p_e+p_i$. In other words, a conventional tokamak plasma exists in a state in which electromagnetic
-forces exactly balance the  total scalar pressure force. 
+where $p=p_e+p_i$. In other words, a conventional tokamak plasma exists in a state in which the magnetic force density exactly balances the  total scalar pressure force density. 
 It follows from the previous equation that 
@@
 \end{equation}
-In other words, the pressure in a conventional tokamak plasma is constant on magnetic flux-surfaces. 
+In other words, the total pressure in a conventional tokamak plasma is constant on magnetic flux-surfaces. 
  However, given that $p=n\,(T_e+T_i)$, and making use of Eqs.~(\ref{e75}) and (\ref{e77}), we deduce that 
@@
 
-\section{Cylindrical Tearing Mode Theory}
+\section{Cylindrical Tearing Mode Theory}\label{cyl}
 \subsection{Introduction}
@@
 Consider a tearing mode perturbation that has $m$ periods in the poloidal direction,
-and $n$ periods in the toroidal direction, where $m/n\sim {\cal O}(1)$.  We can write the perturbed magnetic field in the form
+and $n$ periods in the toroidal direction, where $m/n\sim {\cal O}(1)$.  We can write the perturbed magnetic field in the divergence-free form
 \begin{equation}\label{e93}
@@
 Making use of Equations~(\ref{e90})--(\ref{e94}), the $z$-component of the previous equation gives
-the {\em cylindrical tearing mode equation}\/ (Fitzpatrick 1993),
+the {\em cylindrical tearing mode equation}\/ (Wesson 1978; Fitzpatrick 1993),
 \begin{equation}
@@
 Suppose that the plasma occupies the region $0\leq r\leq a$, where $a$ is the plasma {\em minor radius}. It follows that
-$J_z(r)=0$ for $r>a$. Let the plasma be surrounded by a concentric perfectly-conducting wall of radius $r_w>a$. 
-(By definition, $a\ll R_0$ in a large aspect-ratio tokamak.) An appropriate
-physical solution of the cylindrical tearing mode equation takes the form
+$J_z(r)=0$ for $r>a$. Let the plasma be surrounded by a concentric, rigid, radially-thin, perfectly-conducting, wall of radius $r_w>a$. 
+(By definition, $a\ll R_0$ in a large aspect-ratio tokamak. In most circumstances, the wall represents the metal vacuum vessel that surrounds  the plasma.) An appropriate
+physical solution of the cylindrical tearing mode equation takes the separable form
 \begin{equation}\label{e99}
@@
 \alpha_s& =- \left(\frac{r\,q\,J_z'}{s}\right)_{r=r_s},\\[0.5ex]
-s(r) &= \frac{r\,q'}{q}.
+s(r) &= \frac{r\,q'}{q}.\label{shear}
 \end{align}
@@
 and the boundary conditions (\ref{e101})--(\ref{e103}). Note that, in general, $\psi$ is continuous across the resonant surface (in accordance with Maxwell's equations),
-whereas $\partial\psi/\partial r$ is discontinuous. The discontinuity in $\partial \psi/\partial r$ implies the presence of a radially
-thin, helical,  current sheet  at the resonant surface. This current sheet can only be resolved by retaining more terms in the perturbed plasma equation of motion, (\ref{e96}).
+whereas $\partial\psi/\partial r$ is discontinuous.
+The discontinuity in $\partial \psi/\partial r$ implies the presence of a radially-thin, helical,  current sheet  at the resonant surface.
+This current sheet can only be resolved by retaining more terms in the perturbed plasma equation of motion, (\ref{e96}).
+(See Section~\ref{linear}.)
 
 The complex quantity
-\begin{equation}
+\begin{equation}\label{e109}
 {\mit\Delta\Psi}_s = \left[r\,\frac{\partial \psi}{\partial r}\right]_{r_{s-}}^{r_{s+}}
@@
 of Equations~(\ref{e99}), (\ref{e105}), and (\ref{e106}), we obtain
-\begin{equation}
+\begin{equation}\label{e110}
 {\mit\Delta\Psi}_s = E_{ss}\,{\mit\Psi}_s,
 \end{equation}
-where $E_{ss}= {\mit\Delta}_{s+}-{\mit\Delta}_{s-}$ is a real quantity that is known as the {\em tearing stability index}\/ (Furth, et al., 1963).
+where $E_{ss}= {\mit\Delta}_{s+}-{\mit\Delta}_{s-}$ is a real quantity that is known as the {\em tearing stability index}\/ (Furth, et al.\ 1963).
 
 \subsection{Solution in Presence of Resistive Wall}\label{resistive}
-Suppose, now, that the wall at $r=r_w$ possesses a finite resistivity, but is surrounded by a second perfectly-conducting wall
+Suppose, now, that the wall at $r=r_w$ possesses a finite electrical resistivity, but is surrounded by a second perfectly-conducting wall
 located at radius $r_c>r_w$.
@@
 \end{equation}
-Here, we are making use of the so-called {\em thin wall approximation}, according to which $\psi$ is assumed to only vary weakly in $r$ inside 
+Here, we are making use of the so-called {\em thin wall approximation}, according to which $\psi$ is assumed to only vary weakly in $r$ across 
 the wall. Ohm's law implies that
@@
 \subsection{Solution in Presence of External Magnetic Field-Coil}
-Suppose that the perfectly-conducting wall at $r=r_c$ is replaced by a magnetic field-coil that carries a
-helical current possesing $m$ periods in the poloidal direction, and $n$ periods in the toroidal direction. Let the current density in the field-coil
+Suppose that the perfectly-conducting wall at $r=r_c$ is replaced by a radially-thin, magnetic field-coil that carries a
+helical current possessing $m$ periods in the poloidal direction, and $n$ periods in the toroidal direction. Let the current density in the field-coil
 take the form
@@
 where $\delta{\bf j}$ is the density of the current sheet flowing at the resonant surface, and we have made use
-of the fact that $\delta j_r\simeq 0$ in a radially thin current sheet. 
+of the fact that $\delta j_r$ is negligible in a radially-thin current sheet (Fitzpatrick 1993). 
  It follows from the previous three equations that
@@
 former are order $\sqrt{m_e/m_i}$ smaller than the latter).
-(See Sections~\ref{sbrag} and \ref{s3.9}.) Recall that the terms in square brackets are there to remind us that the terms they precede are larger than the
-other terms in the equation (by the corresponding terms within the brackets).
+(See Sections~\ref{sbrag} and \ref{s3.9}.) Recall that the factors in square brackets are there to remind us that the terms they precede are larger than the
+other terms in the equation (by the corresponding factors within the brackets).
 
@@
 comes from the ion parallel viscosity tensor acting on the zeroth-order (in perturbed quantities) ion flow.
-(See Section~\ref{sbrag}.)  However, this contribution averages to zero in a cylindrical plasma in which $B_z$
+(See Section~\ref{sbrag}.)  However, this contribution averages to zero in a cylindrical plasma, in which $B_z$
 is constant on magnetic flux-surfaces. Of course, in reality, in a large aspect-ratio tokamak plasma, 
@@
 other terms in the equation].
-To be more exact, if the residual contribution is ${\cal O}(\zeta_i)$ times smaller than the original contribution then  $\langle r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\rangle$ ceases to be a dominant term in the equation.
+To be more exact, if the residual contribution is ${\cal O}(\zeta_i)$ times smaller than the non-averaged  contribution then  $\langle r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\rangle$ ceases to be a dominant term in the equation.
 
@@
 \begin{equation}\label{e178}
-\langle r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\rangle = 4\pi^2\,R_0\left[ \frac{\rho}{\tau_\theta}\,r^{\,3}\,({\mit\Omega}_\theta-{\mit\Omega}_{\theta\,{\rm nc}}) -\frac{\partial}{\partial r}\!\left(\mu\,r^{\,3}\,\frac{\partial{\mit\Omega}_\theta}{\partial r}\right)\right].
+\langle r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\rangle = 4\pi^2\,R_0\left[ \frac{\rho}{\tau_\theta}\,r^{\,3}\,({\mit\Omega}_\theta-{\mit\Omega}_{\theta\,{\rm nc}}) -\frac{\partial}{\partial r}\!\left(\mu_\perp\,r^{\,3}\,\frac{\partial{\mit\Omega}_\theta}{\partial r}\right)\right].
 \end{equation}
@@
 is generally of order $\tau_i$), ${\mit\Omega}_{\theta\,{\rm nc}}(r)$ is the neoclassical poloidal angular velocity profile, and
-$\mu(r)$ is a phenomenological perpendicular viscosity due to plasma turbulence.
+$\mu_\perp(r)$ is a phenomenological perpendicular viscosity due to plasma turbulence.
 
@@
 \begin{equation}\label{e179}
-4\pi^2\,R_0\left[\rho\,r^{\,3}\,\frac{\partial {\mit\Omega}_\theta}{\partial t}+ \frac{\rho}{\tau_\theta}\,r^{\,3}\,({\mit\Omega}_\theta-{\mit\Omega}_{\theta\,{\rm nc}}) -\frac{\partial}{\partial r}\!\left(\mu\,r^{\,3}\,\frac{\partial{\mit\Omega}_\theta}{\partial r}\right)\right]
+4\pi^2\,R_0\left[\rho\,r^{\,3}\,\frac{\partial {\mit\Omega}_\theta}{\partial t}+ \frac{\rho}{\tau_\theta}\,r^{\,3}\,({\mit\Omega}_\theta-{\mit\Omega}_{\theta\,{\rm nc}}) -\frac{\partial}{\partial r}\!\left(\mu_\perp\,r^{\,3}\,\frac{\partial{\mit\Omega}_\theta}{\partial r}\right)\right]
 =T_{\theta\,s}\,\delta(r-r_s)+ S_\theta,
@@
 where use has been made of Equation~(\ref{e178}). 
-Here, we have added a source term, $S_\theta(r)$, to the equation. Let ${\mit\Omega}_{\theta\,0}(r)$ be the 
+Here, we have added a source term, $S_\theta(r)$, to the equation in order to account for the equilibrium poloidal flow. Let ${\mit\Omega}_{\theta\,0}(r)$ be the 
 unperturbed (by the tearing mode) ion poloidal angular velocity profile. It follows that 
 \begin{equation}
-S_\theta = 4\pi^2\,R_0\left[ \frac{\rho}{\tau_\theta}\,r^{\,3}\,({\mit\Omega}_{\theta\,0}-{\mit\Omega}_{\theta\,{\rm nc}}) -\frac{d}{d r}\!\left(\mu\,r^{\,3}\,\frac{d{\mit\Omega}_{\theta\,0}}{d r}\right)\right].
+S_\theta = 4\pi^2\,R_0\left[ \frac{\rho}{\tau_\theta}\,r^{\,3}\,({\mit\Omega}_{\theta\,0}-{\mit\Omega}_{\theta\,{\rm nc}}) -\frac{d}{d r}\!\left(\mu_\perp\,r^{\,3}\,\frac{d{\mit\Omega}_{\theta\,0}}{d r}\right)\right].
 \end{equation}
@@
 \begin{equation}
-4\pi^2\,R_0\left[\rho\,r^{\,3}\,\frac{\partial {\mit\Delta\Omega}_\theta}{\partial t}+ \frac{\rho}{\tau_\theta}\,r^{\,3}\,{\mit\Delta\Omega}_\theta-\frac{\partial}{\partial r}\!\left(\mu\,r^{\,3}\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial r}\right)\right]
+4\pi^2\,R_0\left[\rho\,r^{\,3}\,\frac{\partial {\mit\Delta\Omega}_\theta}{\partial t}+ \frac{\rho}{\tau_\theta}\,r^{\,3}\,{\mit\Delta\Omega}_\theta-\frac{\partial}{\partial r}\!\left(\mu_\perp\,r^{\,3}\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial r}\right)\right]
 =T_{\theta\,s}\,\delta(r-r_s).
@@
 \begin{equation}\label{e182}
-4\pi^2\,R_0\left[(1+2\,q^{\,2})\,\rho\,r^{\,3}\,\frac{\partial {\mit\Delta\Omega}_\theta}{\partial t}+ \frac{\rho}{\tau_\theta}\,r^{\,3}\,{\mit\Delta\Omega}_\theta-\frac{\partial}{\partial r}\!\left(\mu\,r^{\,3}\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial r}\right)\right]
+4\pi^2\,R_0\left[(1+2\,q^{\,2})\,\rho\,r^{\,3}\,\frac{\partial {\mit\Delta\Omega}_\theta}{\partial t}+ \frac{\rho}{\tau_\theta}\,r^{\,3}\,{\mit\Delta\Omega}_\theta-\frac{\partial}{\partial r}\!\left(\mu_\perp\,r^{\,3}\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial r}\right)\right]
 =T_{\theta\,s}\,\delta(r-r_s).
@@
 \begin{equation}\label{e185}
-4\pi^2\,R_0^{\,3}\left[\rho\,r\,\frac{\partial {\mit\Delta\Omega}_\varphi}{\partial t}-\frac{\partial}{\partial r}\!\left(\mu\,r\,\frac{\partial{\mit\Delta\Omega}_\varphi}{\partial r}\right)\right]
+4\pi^2\,R_0^{\,3}\left[\rho\,r\,\frac{\partial {\mit\Delta\Omega}_\varphi}{\partial t}-\frac{\partial}{\partial r}\!\left(\mu_\perp\,r\,\frac{\partial{\mit\Delta\Omega}_\varphi}{\partial r}\right)\right]
 =T_{\varphi\,s}\,\delta(r-r_s).
@@
 On the other  hand, the boundary conditions (\ref{e187}) are a consequence of the action of {\em charge exchange}\/ with electrically neutral particles emitted isotropically from the wall  in the edge regions of the plasma
-(Brau, et al., 1983; Fitzpatrick 1993; Monier-Garbet, et al., 1997). Charge exchange with neutrals gives rise to 
+(Brau, et al.\ 1983; Fitzpatrick 1993; Monier-Garbet, et al.\ 1997). Charge exchange with neutrals gives rise to 
 dominant damping torques acting at the edge of the plasma that relax the edge ion angular velocities  toward  particular values. Moreover, the
@@
 In general, the perturbed angular velocity profiles, ${\mit\Delta\Omega}_\theta(r,t)$ and ${\mit\Delta\Omega}_\varphi(r,t)$, are
-localized in the vicinity of the resonant surface (Fitzpatrick 1993). Hence, it is reasonable to write the perturbed angular
+localized in the vicinity of the resonant surface (Fitzpatrick 1993). Hence, it is reasonable to express  the perturbed angular
 equations of motion, (\ref{e182}) and (\ref{e185}), in the simplified  forms
@@
 \end{align}
-where $q_s=q(r_s)$, $\rho_s=\rho(r_s)$, $\tau_{\theta\,s}=\tau_\theta(r_s)$, and $\mu_s=\mu(r_s)$.
+where $q_s=q(r_s)$, $\rho_s=\rho(r_s)$, $\tau_{\theta\,s}=\tau_\theta(r_s)$, and $\mu_s=\mu_\perp(r_s)$.
 
@@
 \begin{align}\label{e198}
-(1+2\,q_k^{\,2})\,\frac{d\alpha_p}{dt} + \left(\frac{1}{\tau_{\theta\,s}}+\frac{j_{1,p}^{\,2}}{\tau_{M\,s}}\right)\alpha_p
-&= \frac{m^{2}\,[y_p(r_s/a)]^{\,2}}{\tau_A^{\,2}\,\epsilon^{\,2}\,[J_2(j_{1,p})]^{\,2}}\,
+(1+2\,q_k^{\,2})\,\frac{d\alpha_p}{dt} + \left(\frac{1}{\tau_{\theta\,s}}+\frac{j_{1,p}^{\,2}}{\tau_{M}}\right)\alpha_p
+&= \frac{m^{2}\,[y_p(r_s/a)]^{\,2}}{\tau_A^{\,2}\,\epsilon_a^{\,2}\,[J_2(j_{1,p})]^{\,2}}\,
 {\rm Im}({\mit\Delta\hat{\Psi}_s}\,\hat{\mit\Psi}_s^{\,\ast}),\\[0.5ex]
-\frac{d\beta_p}{dt} + \frac{j_{0,p}^{\,2}}{\tau_{M\,s}}\,\beta_p
+\frac{d\beta_p}{dt} + \frac{j_{0,p}^{\,2}}{\tau_{M}}\,\beta_p
 &= \frac{n^{2}\,[z_p(r_s/a)]^{\,2}}{\tau_A^{\,2}\,[J_1(j_{0,p})]^{\,2}}\,
@@
 \end{align}
-Here, $\tau_{M\,s} =\rho_s\,a^{\,2}/\mu_s$ is the {\em momentum confinement time}, $\tau_A = (\mu_0\,\rho_s\,a^{\,2}/B_z^{\,2})^{1/2}$ is the {\em Alfv\'{e}n time}, $\epsilon=a/R_0\ll 1$ is the {\em inverse aspect-ratio}\/ of the plasma,
+Here, $\tau_{M} =\rho_s\,a^{\,2}/\mu_s$ is the {\em momentum confinement time}, $\tau_A = (\mu_0\,\rho_s\,a^{\,2}/B_z^{\,2})^{1/2}$ is the {\em Alfv\'{e}n time}, $\epsilon_a=a/R_0\ll 1$ is the {\em inverse aspect-ratio}\/ of the plasma,
 ${\mit\Delta\Psi}_s = R_0\,B_z\,{\mit\Delta\hat{\Psi}}_s$, and ${\mit\Psi}_s = R_0\,B_z\,\hat{\mit\Psi}_s$. Moreover,
@@
 where $\varpi_{s\,0}$ is the unperturbed natural frequency.
-The previous expression is known as the {\em no-slip constraint}\/ (Fitzpatrick 1993), and has been verified experimentally (Vahala, et al., 1980).
+The previous expression is known as the {\em no-slip constraint}\/ (Fitzpatrick 1993), and has been verified experimentally (Vahala, et al.\ 1980).
 It follows from Equations~(\ref{e190})
@@
 \varpi_s(t)& = \varpi_{s\,0} - \sum_{p=1,\infty}\left[\alpha_p(t)+\beta_p(t)\right],\\[0.5ex]
-(1+2\,q_k^{\,2})\,\frac{d\alpha_p}{dt} + \left(\frac{1}{\tau_{\theta\,s}}+\frac{j_{1,p}^{\,2}}{\tau_{M\,s}}\right)\alpha_p
-&= \frac{m^{2}\,[y_p(r_s/a)]^{\,2}}{\tau_A^{\,2}\,\epsilon^{\,2}\,[J_2(j_{1,p})]^{\,2}}
+(1+2\,q_k^{\,2})\,\frac{d\alpha_p}{dt} + \left(\frac{1}{\tau_{\theta\,s}}+\frac{j_{1,p}^{\,2}}{\tau_{M}}\right)\alpha_p
+&= \frac{m^{2}\,[y_p(r_s/a)]^{\,2}}{\tau_A^{\,2}\,\epsilon_a^{\,2}\,[J_2(j_{1,p})]^{\,2}}
 \,E_{sw}\,{\rm Im}(\hat{\mit\Psi}_w\,\hat{\mit\Psi}_s^{\,\ast}),\\[0.5ex]
-\frac{d\beta_p}{dt} + \frac{j_{0,p}^{\,2}}{\tau_{M\,s}}\,\beta_p
+\frac{d\beta_p}{dt} + \frac{j_{0,p}^{\,2}}{\tau_{M}}\,\beta_p
 &= \frac{n^{2}\,[z_p(r_s/a)]^{\,2}}{\tau_A^{\,2}\,[J_1(j_{0,p})]^{\,2}}\,
-E_{sw}\,{\rm Im}(\hat{\mit\Psi}_w\,\hat{\mit\Psi}_s^{\,\ast}).
+E_{sw}\,{\rm Im}(\hat{\mit\Psi}_w\,\hat{\mit\Psi}_s^{\,\ast}).\label{e206}
 \end{align}
@@
 
-\section{Reduced Drift-MHD Resonant Plasma Response Model}
+\section{Reduced Drift-MHD Resonant  Response Model}
 \subsection{Introduction}
-Equations~(\ref{e202})--(\ref{e208}) contain two quantities---namely, the reconnection time, $\tau_s$, and the unperturbed
+Equations~(\ref{e202})--(\ref{e206}) contain two quantities---namely, the reconnection time, $\tau_s$, and the unperturbed
 natural frequency, $\varpi_{s\,0}$---that can only be determined by solving for the plasma response in the radially thin resonant layer surrounding the resonant surface.
@@
 
-A tearing mode is a modified shear-Alfv\'{e}n wave (Hazeltine \& Meiss 1985), and has very little connection with the compressible-Alfv\'{e}n wave.
+A tearing mode is a modified shear-Alfv\'{e}n wave (Hazeltine \& Meiss 1985), and has very little connection with a compressible-Alfv\'{e}n wave.
 For instance, the resonance condition, ${\bf k}\cdot{\bf B}=0$, which determines the position of the resonant
@@
 n_0 &= n(r_s),\\[0.5ex]
-p_0&= p(r_s),\\[0.5ex]
+p_0&= p(r_s),\label{e210}\\[0.5ex]
 \eta_e &=\left.\frac{d\ln T_e}{d\ln n}\right|_{r=r_s},\label{e211}\\[0.5ex]
@@
 The so-called {\em MHD velocity}, which is the velocity of a fictional `MHD fluid',  is defined
-\begin{equation}
+\begin{equation}\label{e217}
 {\bf V} = {\bf V}_E + V_{\parallel\,i}\,{\bf b},
@@
 where ${\bf V}_E$ is the ${\bf E}\times {\bf B}$ velocity, and $V_{\parallel\,i}$ is the parallel component of the ion
-fluid velocity. The lowest order electron and ion fluid velocities take the respective forms:
+fluid velocity. The lowest-order electron and ion fluid velocities take the respective forms:
 \begin{align}
@@
 \begin{equation}\label{e220}
-{\bf E} + {\bf V}\times {\bf B} + \frac{1}{e\,n_0}\left[\nabla p + \frac{1}{1+\tau}\left(\frac{0.71\,\eta_e\,\tau}{1+\eta_e}-1\right)({\bf b}\cdot\nabla p)\,{\bf b} -{\bf j}\times{\bf b}\right] \simeq \eta_\parallel\,{\bf j}_\parallel + \eta_\perp\,{\bf j}_\perp.
+{\bf E} + {\bf V}\times {\bf B} + \frac{1}{e\,n_0}\!\left[\nabla p + \frac{1}{1+\tau}\left(\frac{0.71\,\eta_e\,\tau}{1+\eta_e}-1\right)({\bf b}\cdot\nabla p)\,{\bf b} -{\bf j}\times{\bf b}\right] \simeq \eta_\parallel\,{\bf j}_\parallel + \eta_\perp\,{\bf j}_\perp.
 \end{equation}
@@
 \begin{equation}
-n_0\,m_i\left[\frac{\partial {\bf V}}{\partial t} + ({\bf V}\cdot\nabla ){\bf V} + \frac{1}{1+\tau}\,({\bf V}_\ast\cdot\nabla){\bf V}_E\right]
+n_0\,m_i\!\left[\frac{\partial {\bf V}}{\partial t} + ({\bf V}\cdot\nabla ){\bf V} + \frac{1}{1+\tau}\,({\bf V}_\ast\cdot\nabla){\bf V}_E\right]
 + \nabla p + \nabla\cdot\bpi_i - {\bf j}\times {\bf B}\simeq 0.
@@
 which is the same size as the ion inertial terms, has already been incorporated into the equation (Hazeltine \& Meiss 1992).
-We are neglecting the contribution of the parallel viscosity tensor  because we
-expect it to be much smaller than its nominal magnitude in a large aspect-ratio tokamak
-plasma.
+For the moment, we are neglecting the contribution of the parallel viscosity tensor.
 
@@
 velocity of compressible Alfv\'{e}n waves, is defined
-\begin{equation}
+\begin{equation}\label{e226a}
 V_A = \frac{B_z}{\sqrt{\mu_0\,n_0\,m_i}}.
@@
 \begin{align}\label{e227}
-\hat{\bf E} + \hat{\bf V}\times \hat{\bf B} + \hat{d}_i\left[\hat{\nabla} \hat{p} + \frac{1}{1+\tau}\left(\frac{0.71\,\eta_e\,\tau}{1+\eta_e}-1\right)({\bf b}\cdot\hat{\nabla} \hat{p})\,{\bf b} + \hat{\nabla}\cdot\hat{\bpi}_e-\hat{\bf j}\times\hat{\bf b}\right] &\simeq \hat{\eta}_\parallel\,\hat{\bf j}_\parallel+ \hat{\eta}_\perp\,\hat{\bf j}_\perp,\\[0.5ex]
+\hat{\bf E} + \hat{\bf V}\times \hat{\bf B} + \hat{d}_i\!\left[\hat{\nabla} \hat{p} + \frac{1}{1+\tau}\left(\frac{0.71\,\eta_e\,\tau}{1+\eta_e}-1\right)({\bf b}\cdot\hat{\nabla} \hat{p})\,{\bf b} + \hat{\nabla}\cdot\hat{\bpi}_e-\hat{\bf j}\times\hat{\bf b}\right] &\simeq \hat{\eta}_\parallel\,\hat{\bf j}_\parallel+ \hat{\eta}_\perp\,\hat{\bf j}_\perp,\\[0.5ex]
 \frac{\partial \hat{\bf V}}{\partial \hat{t}} 
@@
 which automatically satisfies Equation~(\ref{e230}).
-(Here, we are assuming that $|r-r_s|\ll a$ inside the resonant layer.) Here, $\delta b(\hat{x},\zeta)$ and $\psi(\hat{x},\zeta)$ are assumed to be small
+(Recall that we are assuming that $|r-r_s|\ll r_s$ inside the resonant layer.) Here, $\delta b(\hat{x},\zeta)$ and $\psi(\hat{x},\zeta)$ are assumed to be small
 compared to unity, which merely indicates that the perturbed magnetic field due to the tearing mode is small compared to the
@@
 \begin{equation}
-\hat{\bf E} \simeq \left(\hat{E}_\parallel- \frac{\partial \psi}{\partial \hat{t}}\right){\bf n} + \hat{\nabla}\!\left(\frac{\partial\chi}{\partial \hat{t}}\right)\times {\bf n} + \hat{\nabla}\phi,
+\hat{\bf E} \simeq \left(\hat{E}_\parallel- \frac{\partial \psi}{\partial \hat{t}}\right)\!{\bf n} + \hat{\nabla}\!\left(\frac{\partial\chi}{\partial \hat{t}}\right)\times {\bf n} + \hat{\nabla}\phi,
 \end{equation}
@@
 where 
-\begin{equation}
+\begin{equation}\label{e244}
 \beta= {\mit\Gamma}\,\hat{p}_0= \frac{{\mit\Gamma}\,p_0\,\mu_0}{B_z^{\,2}}.
@@
  \hat{d}_i\,\hat{\nabla}(\delta p + \delta b)\nonumber\\[0.5ex]+ \left(\hat{E}_{\parallel}-\frac{\partial\psi}{\partial \hat{t}} - [\psi,\phi]+ \frac{\hat{d}_i\,[\psi,\delta p]}{1+\tau}\left(1-\frac{0.71\,\eta_e\,\tau}{1+\eta_e}\right)
- + \hat{d}_i\,[\psi,\delta b]+ \hat{\eta}_\parallel\,\hat{\nabla}^2\psi\right){\bf n}\nonumber\\[0.5ex]
+ + \hat{d}_i\,[\psi,\delta b]+ \hat{\eta}_\parallel\,J\right){\bf n}\nonumber\\[0.5ex]
  +\hat{\nabla}\!\left(\frac{\partial\chi}{\partial \hat{t}} + {\mit\Xi} -\hat{\eta}_\perp\,\delta b\right)\times {\bf n} + \frac{\hat{d}_i}{2}\,\hat{\nabla}\delta b^{\,2}- b_z\,\hat{\nabla}\phi + \hat{V}_{\parallel\,i}\,\hat{\nabla}\psi
-+  \hat{d}_i\,\hat{\nabla}^2\psi\,\hat{\nabla}\psi \simeq 0,\\[0.5ex]
++  \hat{d}_i\,J\,\hat{\nabla}\psi \simeq 0,\\[0.5ex]
  \hat{\nabla}(\delta p + \delta b) + \left(\frac{\partial \hat{V}_{\parallel\,i}}{\partial \hat{t}} + [\hat{V}_{\parallel\,i},\phi] + [\psi,\delta b]\right){\bf n}\nonumber\\[0.5ex]
@@
  \left(\hat{V}_\perp^{\,2}+ \frac{\hat{\bf V}_\ast\cdot\hat{\bf V}_E }{1+\tau}+ \delta b^{\,2}\right)  \nonumber\\[0.5ex]
--\hat{\nabla}^2\phi\,\hat{\nabla}\phi + \frac{\hat{d}_i}{2\,(1+\tau)}\left(\hat{\nabla}^2\phi\,\hat{\nabla}\delta p +\hat{\nabla}^2\delta p\,\hat{\nabla}\phi\right) + \hat{\nabla}^2\psi\,\hat{\nabla}\psi + \hat{\nabla}\cdot\hat{\bpi}_i \simeq 0,\label{e248}\\[0.5ex]
+-\hat{\nabla}^2\phi\,\hat{\nabla}\phi + \frac{\hat{d}_i}{2\,(1+\tau)}\left(\hat{\nabla}^2\phi\,\hat{\nabla}\delta p +\hat{\nabla}^2\delta p\,\hat{\nabla}\phi\right) + J\,\hat{\nabla}\psi + \hat{\nabla}\cdot\hat{\bpi}_i \simeq 0,\label{e248}\\[0.5ex]
 \frac{\partial \delta p}{\partial \hat{t}} + [\delta p,\phi] +\beta\,\hat{\nabla}^2{\mit\Xi} + \frac{2}{3}\,\hat{\nabla}\cdot \hat{\bf q}\simeq 0,\label{e249}
@@
  where use has been made of Equation~(\ref{e232}), and
- \begin{equation}
- [A,B] \equiv \hat{\nabla} A\times \hat{\nabla} B\cdot{\bf n}.
- \end{equation}
- Here, $\hat{d}_i$ and $\beta$ are assumed to be zeroth order in small quantities, $\hat{\eta}_\parallel$ and $\hat{\eta}_\perp$ are assumed to be first order, while $\hat{\nabla}\cdot \hat{\bpi}_{i}$ and $\hat{\nabla}\cdot\hat{\bf q}$ are assumed to be second order.
+ \begin{align}
+ [A,B] &\equiv \hat{\nabla} A\times \hat{\nabla} B\cdot{\bf n},\\[0.5ex]
+ J &= -\frac{2}{q_s\,\hat{R}_0}+ \hat{\nabla}^2\psi,\label{eJ}
+ \end{align}
+ with $R_0=R_0/l$. 
+ Here, $\hat{d}_i$ and $\beta$ are assumed to be zeroth order in small quantities, $J$, $1/\hat{R}_0$, $\hat{\eta}_\parallel$, and $\hat{\eta}_\perp$ are assumed to be first order, while $\hat{\nabla}\cdot \hat{\bpi}_{i}$ and $\hat{\nabla}\cdot\hat{\bf q}$ are assumed to be second order.
 
@@
  \begin{equation}\label{e252}
- \frac{\partial\psi}{\partial\hat{t}}\simeq [\phi,\psi] +\hat{d}_i\left(\frac{\tau}{1+\tau}\right)\left(1+\frac{0.71\,\eta_e}{1+\eta_e}\right)
- [\delta p,\psi] + \hat{\eta}_\parallel\,J + \hat{E}_\parallel,
- \end{equation}
- where
- \begin{equation}
- J = \hat{\nabla}^2\psi.
+ \frac{\partial\psi}{\partial\hat{t}}\simeq [\phi,\psi] +\hat{d}_i\!\left(\frac{\tau}{1+\tau}\right)\left(1+\frac{0.71\,\eta_e}{1+\eta_e}\right)
+ [\delta p,\psi] + \hat{\eta}_\parallel\,J + \hat{E}_\parallel.
  \end{equation}
@@
  where
- \begin{equation}
+ \begin{equation}\label{e257}
  c_\beta = \sqrt{\frac{\beta}{1+\beta}}.
@@
 \begin{equation}
-\hat{\nabla}\cdot\hat{\bpi}_i \simeq - \hat{\chi}_\phi\,\hat{\nabla}^2\hat{\bf V}_i,
-\end{equation}
-where $\chi_\phi = \mu_{\perp}/(n_0\,m_i)$, $\hat{\chi}_\phi = \chi_\phi/(l\,V_A)$, and $\mu_\perp$ is the anomalous
+\hat{\nabla}\cdot\hat{\bpi}_i \simeq - \hat{\chi}_\varphi\,\hat{\nabla}^2\hat{\bf V}_i,
+\end{equation}
+where $\chi_\varphi = \mu_{\perp}/(n_0\,m_i)$, $\hat{\chi}_\varphi = \chi_\varphi/(l\,V_A)$, and $\mu_\perp$ is the anomalous
 ion perpendicular viscosity. Note that the previous equation is entirely phenomenological in nature.  It is easily seen that
 \begin{align}\label{e262}
-{\bf n}\cdot\hat{\nabla}\cdot\hat{\bpi}_i&\simeq -\hat{\chi}_\phi\,\hat{\nabla}^{2}\hat{V}_{\parallel\,i},\\[0.5ex]
-{\bf n}\cdot\hat{\nabla}\times \hat{\nabla}\cdot\hat{\bpi}_i&\simeq \hat{\chi}_\perp \,\hat{\nabla}^4\!\left(\phi - \frac{\hat{d}_i\,\delta p}{1+\tau}\right).\label{e263}
+{\bf n}\cdot\hat{\nabla}\cdot\hat{\bpi}_i&\simeq -\hat{\chi}_\varphi\,\hat{\nabla}^{2}\hat{V}_{\parallel\,i},\\[0.5ex]
+{\bf n}\cdot\hat{\nabla}\times \hat{\nabla}\cdot\hat{\bpi}_i&\simeq \hat{\chi}_\varphi \,\hat{\nabla}^4\!\left(\phi - \frac{\hat{d}_i\,\delta p}{1+\tau}\right).\label{e263}
 \end{align}
@@
 Let us define $V=\hat{V}_{\parallel\,i}$ and $N=\delta p/c_\beta$.
-Equations~(\ref{e252})--(\ref{e254}), (\ref{e256}), (\ref{e258})--(\ref{e260}), (\ref{e262}), and (\ref{e263}) yield the following closed set of equations (Fitzpatrick \& Waelbroeck 2005):
+Equations~(\ref{eJ}), (\ref{e252})--(\ref{e254}), (\ref{e256}), (\ref{e258})--(\ref{e260}), (\ref{e262}), and (\ref{e263}) yield the following closed set of equations (Fitzpatrick \& Waelbroeck 2005):
 \begin{align}\label{e264}
-\frac{\partial\psi}{\partial\hat{t}}&\simeq [\phi,\psi] + \hat{d}_\beta\left(\frac{\tau}{1+\tau}\right)\left(1+\frac{0.71\,\eta_e}{1+\eta_e}\right)[N,\psi]
+\frac{\partial\psi}{\partial\hat{t}}&\simeq [\phi,\psi] + \hat{d}_\beta\!\left(\frac{\tau}{1+\tau}\right)\left(1+\frac{0.71\,\eta_e}{1+\eta_e}\right)[N,\psi]
 +\hat{\eta}_\parallel\,J + \hat{E}_\parallel,\\[0.5ex]
-\frac{\partial U}{\partial \hat{t}}&\simeq [\phi,U] + \frac{\hat{d}_\beta}{2\,(1+\tau)}\left(\hat{\nabla}^2[\phi,N] + [\hat{\nabla}^2\phi,N] + [\hat{\nabla}^2 N,\phi]\right) + [J,\psi] \nonumber\\[0.5ex]&\phantom{=}+\hat{\chi}_\perp  \,\hat{\nabla}^4\!\left(\phi - \frac{\hat{d}_\beta\,N}{1+\tau}\right),\label{e265} \\[0.5ex]
+\frac{\partial U}{\partial \hat{t}}&\simeq [\phi,U] + \frac{\hat{d}_\beta}{2\,(1+\tau)}\left(\hat{\nabla}^2[\phi,N] + [\hat{\nabla}^2\phi,N] + [\hat{\nabla}^2 N,\phi]\right) + [J,\psi] \nonumber\\[0.5ex]&\phantom{=}+\hat{\chi}_\varphi  \,\hat{\nabla}^4\!\left(\phi - \frac{\hat{d}_\beta\,N}{1+\tau}\right),\label{e265} \\[0.5ex]
 \frac{\partial N}{\partial \hat{t}}&\simeq [\phi,N] -c_\beta\,[V,\psi] -\hat{d}_\beta\,[J,\psi] + \hat{D}_\parallel\,[[N,\psi],\psi]
 + \hat{D}_\perp\,\hat{\nabla}_\perp^{\,2}N,\label{e266}\\[0.5ex]
-\frac{\partial V}{\partial\hat{t}}&\simeq [\phi,V] - c_\beta\,[N,\psi] + \hat{\chi}_\phi\,\hat{\nabla}^2 V,\label{e267}\\[0.5ex]
-J &=\hat{\nabla}^2\psi,\\[0.5ex]
+\frac{\partial V}{\partial\hat{t}}&\simeq [\phi,V] - c_\beta\,[N,\psi] + \hat{\chi}_\varphi\,\hat{\nabla}^2 V,\label{e267}\\[0.5ex]
+J &=-\frac{2}{q_s\,\hat{R}_0}+\hat{\nabla}^2\psi,\\[0.5ex]
 U &=\hat{\nabla}^2 \phi.\label{e269}
@@
 Here, 
-\begin{align}
+\begin{align}\label{e270}
 d_\beta &= c_\beta\,d_i = \left(\frac{{\mit\Gamma}}{1+\beta}\right)^{1/2}\rho_s,\\[0.5ex]
@@
 \begin{align}
-\hat{D}_\parallel&= \frac{2}{3}\,(1-c_\beta^{\,2})\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\parallel\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\parallel\,i}\right),\\[0.5ex]
-\hat{D}_\perp &= c_\beta^{\,2}\,\hat{\eta}_\perp +  \frac{2}{3}\,(1-c_\beta^{\,2})\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\perp\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\perp\,i}\right).
+\hat{D}_\parallel&= \frac{2}{3}\,(1-c_\beta^{\,2})\!\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\parallel\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\parallel\,i}\right),\\[0.5ex]
+\hat{D}_\perp &= c_\beta^{\,2}\,\hat{\eta}_\perp +  \frac{2}{3}\,(1-c_\beta^{\,2})\!\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\perp\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\perp\,i}\right).
 \end{align}
@@
 
-If we neglect $d_\beta$ in our reduced drift-MHD model, which is equivalent to saying that the ion sound
+If we neglect $\hat{d}_\beta$ in our reduced drift-MHD model, which is equivalent to saying that the ion sound
 radius is much smaller than the radial extent of the resonant layer, then our four-field resonant response model
@@
 This model describes ion sound wave dynamics parallel to magnetic field-lines. It should be noted that the
-ion sound radius is {\em not}\/ negligibly small compared to the radial extents of resonant layers in present-day
+ion sound radius is {\em not}\/ negligibly small compared to the radial extents of resonant layers in conventional 
 tokamak plasmas. Hence, the `single-fluid' reduced MHD model, (\ref{e275})--(\ref{e276}), provides  a very poor description
-of the response of  resonant layers in tokamak plasmas.
+of the response of  resonant layers in such plasmas.
 
@@
 a second-order quantity while leaving $\hat{\bf V}$ a first-order quantity. This ordering implies that the  MHD fluid is
-{\em incompressible}\/ to lowest-order. It should be noted, however, that the small, but finite, compressibility of the
+{\em incompressible}\/ to lowest order. It should be noted, however, that the small, but finite, compressibility of the
 MHD fluid has a significant influence on the form of the continuity equation (\ref{e266}).
 
-\section{Linear Resonant Plasma Response Model}
+\section{Linear Resonant  Response Model}\label{linear}
 \subsection{Introduction}
-The aim of this section is to employ the reduced, drift-MHD, resonant, plasma response model derived in the
+The aim of this section is to employ the reduced, drift-MHD, four-field, resonant, plasma response model derived in the
 previous section to determine the {\em linear}\/ response of the resonant layer to external perturbations.
+
+It is convenient to set the normalization scale-length, $l$, in our four-field response model equal to the minor radius of the resonant surface, $r_s$. 
+Recall that the four fields in question---namely, $\psi$, $\phi$, $N$, and $V$---have the following
+definitions:
+\begin{align}\label{e279}
+\nabla\psi &= \frac{{\bf n}\times{\bf B}} {r_s\,B_z},\\[0.5ex]
+\nabla\phi &= \frac{{\bf n}\times {\bf V}}{r_s\,V_A},\\[0.5ex]
+N &= \frac{p-p_0}{c_\beta\,B_z^{\,2}/\mu_0},\\[0.5ex]
+V &= \frac{{\bf n}\cdot {\bf V}}{V_A},
+\end{align}
+where  ${\bf V}$ is the MHD velocity defined in Equation~(\ref{e217}),  $p$ is the total plasma pressure, $p_0$ is defined in Equation~(\ref{e210}), $V_A$ is the
+Alfv\'{e}n speed defined in Equation~(\ref{e226a}), and $c_\beta$ is defined in Equations~(\ref{e244}) and (\ref{e257}). Our
+model also employs the auxiliary fields $J=-2\,\epsilon_s/q_s+r_s^2\,\nabla^2 \psi$ and  $U=r_s^2\,\nabla^2 \phi$. Here, $\epsilon_s=r_s/R_0$.
+
+\subsection{Plasma Equilibrium}
+The unperturbed plasma equilibrium is such that
+\begin{align}
+{\bf B} &= (0,\,B_\theta(r),\,B_z),\\[0.5ex]
+p &= p(r),\\[0.5ex]
+{\bf V} &= (0,\,V_E(r),\,V_z(r)),\label{e282}
+\end{align}
+where 
+\begin{equation}
+V_E(r)\simeq \frac{E_r}{B_z}
+\end{equation}
+ is the (dominant $\theta$-component of the) ${\bf E}\times {\bf B}$ velocity. Now, the resonant layer is assumed to have a radial thickness that is
+much smaller than $r_s$. (See Section~\ref{s5.3}.) Hence, we only need to evaluate plasma equilibrium quantities in the immediate vicinity of the resonant
+surface. Equations~(\ref{e279})--(\ref{e282}) suggest that 
+\begin{align}\label{e287}
+\psi &= \frac{\hat{x}^{\,2}}{2\,\hat{L}_s},\\[0.5ex]
+\phi &= - \hat{V}_E\,\hat{x},\\[0.5ex]
+N &= \frac{\hat{V}_\ast\,\hat{x}}{\hat{d}_\beta},\\[0.5ex]
+V &= \hat{V}_\parallel,\label{e290}
+\end{align}
+where $\hat{x}=(r-r_s)/r_s$, $\hat{L}_s=L_s/r_s$, $L_s=(R_0\,q/s)_{r_s}$ is the {\em magnetic shear length},  the {\em magnetic shear}, $s(r)$, is defined in Equation~(\ref{shear}), $\hat{V}_E= V_E(r_s)/V_A$,
+$\hat{V}_\ast= V_\ast(r_s)/V_A$,
+\begin{equation}
+V_\ast(r) = \frac{1}{e\,n_0\,B_z}\,\frac{dp}{dr}
+\end{equation}
+is the (dominant $\theta$-component of the) diamagnetic velocity, $\hat{d}_\beta=d_\beta/r_s$, $d_\beta$ is the modified  ion sound radius defined in 
+Equation~(\ref{e270}), and 
+ $\hat{V}_\parallel= V_z(r_s)/V_A$. We also have
+ \begin{align}\label{e292}
+ J &= -\left(\frac{2}{s_s}-1\right)\frac{1}{\hat{L}_s},\\[0.5ex]
+ U &= 0,\label{e293}\\[0.5ex]
+ \hat{E}_\parallel &=\left(\frac{2}{s_s}-1\right) \frac{\hat{\eta}_\parallel(r_s)}{\hat{L}_s},\label{e294}
+\end{align}
+where $s_s=s(r_s)$. 
+Note that we are neglecting the radial shear of the equilibrium MHD velocity because, in conventional tokamak plasmas, such shear does not significantly affect the linear response of a  resonant
+layer, due to the fact that the shear is comparatively weak (i.e., $|dV/dr|\ll V_A/a$) combined with the fact that a linear  resonant layer is
+very narrow (Chen \& Morrison 1990).
+
+\subsection{Derivation of Linear Layer Equations}\label{s5.3}
+Suppose that the system is perturbed by a tearing mode with $m$ periods in the poloidal direction, and
+$n$ periods in the toroidal direction. In accordance with Equations~(\ref{e287})--(\ref{e290}), and (\ref{e292})--(\ref{e293}), we can write
+\begin{align}
+\psi(\hat{x},\zeta,t) &= \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
+\phi(\hat{x},\zeta,t) &=-\hat{V}_E\,\hat{x}+ \tilde{\phi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
+N(\hat{x},\zeta,t) &= \frac{\hat{V}_\ast\,\hat{x}}{\hat{d}_\beta}-\frac{1}{\hat{d}_\beta}\!\left(\frac{1+\tau}{\tau}\right)\!\tilde{N}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
+V(\hat{x},\zeta,t) &= \hat{V}_\parallel + \frac{c_\beta}{\hat{d}_\beta}\!\left(\frac{1+\tau}{\tau}\right)\!\tilde{V}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
+J(\hat{x},\zeta,t) &=-\left(\frac{2}{s_s}-1\right)\!\frac{1}{\hat{L}_s}+ \hat{\nabla}^2\tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
+U(\hat{x},\zeta,t) &=  \hat{\nabla}^2\tilde{\phi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\label{e300}
+\end{align}
+where $\zeta=m\,\theta-n\,\varphi$, $\hat{t}=V_A\,t/r_s$, $\hat{\omega}=r_s\,\omega/V_A$, and $\omega$ is the frequency of the tearing mode in the laboratory frame. 
+Substituting Equations~(\ref{e294})--(\ref{e300}) into the four-field model, (\ref{e264})--(\ref{e269}), and only retaining terms that
+are first order in perturbed quantities, we obtain the following set of linear layer equations:
+\begin{align}\label{e301}
+-{\rm i}\,[\omega-\omega_E -(1+\lambda_e)\,\omega_{\ast\,e}]\,\tau_H\,\tilde{\psi} &= -{\rm i} \,\hat{x}\,[\tilde{\phi}-(1+\lambda_e)\,\tilde{N}) + S^{-1}\,\hat{\nabla}^2\tilde{\psi},\\[0.5ex]
+-{\rm i}\,(\omega-\omega_E-\omega_{\ast\,i})\,\tau_H\,\hat{\nabla}^2\tilde{\psi} &= -{\rm i}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi}+S^{-1}\,P_\varphi\,\hat{\nabla}^4\!\left(\tilde{\phi} + \frac{\tilde{N}}{\tau}\right),\\[0.5ex]
+-{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{N} &= -{\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\phi} - {\rm i}\!\left(\frac{\tau}{1+\tau}\right)\hat{d}_\beta^{\,2}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi} -{\rm i}\,c_\beta^2\,\hat{x}\,\tilde{V}\\[0.5ex]
+&\phantom{=}
++S^{-1}\,P_\parallel\!\left(m\,\omega_{\ast\,e}\,\tau_H\,\hat{x}\,\tilde{\psi}-\frac{m}{\hat{L}_s}\,\hat{x}^2\,\tilde{N}\right)
++ S^{-1}\,P_\perp\,\hat{\nabla}^2 \tilde{N},\nonumber\\[0.5ex]
+-{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{V} &= {\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\psi} - {\rm i}\,\hat{x}\,\tilde{N}
++ S^{-1}\,P_\varphi\,\hat{\nabla}^2\tilde{V}.\label{e304}
+\end{align}
+Here, $\tau_H = L_s/(m\,V_A)$ is the {\em hydromagnetic time}, $\omega_E = (m/r_s)\,V_E(r_s)$  the 
+{\em E-cross-B frequency}, $\omega_{\ast\,e} = -[\tau/(1+\tau)]\,(m/r_s)\,V_\ast(r_s)$  the {\em electron diamagnetic
+frequency}, $\lambda_e = 0.71\,[\eta_e/(1+\eta_e)]\,[\tau/(1+\tau)]$, $\omega_{\ast\,i} = [1/(1+\tau)]\,(m/r_s)\,V_\ast(r_s)$  the {\em ion diamagnetic
+frequency}, $S=\tau_R/\tau_H$ the {\em Lundquist number}, $\tau_R = \mu_0\,r_s^{\,2}/\eta_\parallel(r_s)$  the
+{\em resistive diffusion time}, $P_\varphi = \tau_R/\tau_\varphi$ the {\em magnetic Prandtl number}, $\tau_\varphi
+= r_s^{\,2}/\chi_\varphi(r_s)$  the {\em toroidal momentum confinement time}, $P_\perp = \tau_R/\tau_\perp$, 
+$\tau_\perp = r_s^{\,2}/D_\perp(r_s)$  the {\em particle/energy confinement time}, 
+$P_\parallel=\tau_R/\tau_\parallel$, and $\tau_\parallel =r_s^{\,2}/D_\parallel(r_s)$.
+
+In conventional tokamak plasmas, the Lundquist number, $S$, which is the ratio of the resistive diffusion and plasma inertia terms in the plasma Ohm's law, is very much greater than unity.
+In fact, $S$ typically exceeds $10^8$ (Wesson 2011).
+However, a resonant layer is
+characterized by a balance between plasma inertia and resistive diffusion (Furth, et al.\ 1963). Such a balance is
+only possible if the layer is very narrow in the radial direction (because a narrow layer enhances radial derivatives, and, thereby, enhances
+resistive diffusion). Let us define the stretched radial variable (Ara, et al.\ 1978)
+\begin{equation}
+X = S^{1/3}\,\hat{x}.
+\end{equation}
+Assuming that $X\sim{\cal O}(1)$ in the layer (i.e., assuming that the layer thickness is of order $S^{-1/3}\,r_s$),
+and making use of the fact that $S\gg 1$, we deduce that $\hat{\nabla}^2\simeq \hat{\nabla}_\perp^2\simeq S^{\,2/3}\,d^{\,2}/dX^2$.
+Hence, the linear layer equations, (\ref{e301})--(\ref{e304}), reduce to (Cole \& Fitzpatrick 2006)
+\begin{align}\label{e306}
+-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_{e}]\,\tilde{\psi}&= - {\rm i}\,X\left[\tilde{\phi}-(1+\lambda_e)\,\tilde{N}\right] + \frac{d^{\,2}\tilde{\psi}}{d X^2},\\[0.5ex]
+-{\rm i}\,(Q-Q_E -Q_{i})\,\frac{d^{\,2}\tilde{\phi}}{dX^2}&= - {\rm i}\,X\,\frac{d^{\,2}\tilde{\psi}}{dX^2}+ P_\varphi\,\frac{d^{\,4}}{dX^4}\!\left(\tilde{\phi} + \frac{\tilde{N}}{\tau}\right),\\[0.5ex]
+-{\rm i}\,(Q-Q_E)\tilde{N} &= - {\rm i}\,Q_{e}\,\tilde{\phi} - {\rm i} \,D^{2}\,X\,\frac{d^{\,2}\tilde{\psi}}{dX^{2}}
+ - {\rm i}\,c_\beta^{\,2}\,X\,\tilde{V} + P_\perp\,\frac{d^{\,2} \tilde{N}}{dX^{2}},\label{e308}\\[0.5ex]
+ -{\rm i}\,(Q-Q_E)\,\tilde{V} &= {\rm i}\,Q_{e}\,\tilde{\psi} - {\rm i}\,X\,\tilde{N} + P_\varphi\,\frac{d^{\,2}\tilde{V}}{dX^{2}}.\label{e309}
+\end{align}
+Here, $Q=S^{\,1/3}\,\omega\,\tau_H$, $Q_E = S^{\,1/3}\,\omega_E\,\tau_H$, $Q_{e,i} = S^{\,1/3}\,\omega_{\ast\,e,i}\,\tau_H$,
+and $D = S^{\,1/3}\,[\tau/(1+\tau)]^{1/2}\,\hat{d}_\beta$. Note that the terms involving parallel transport have dropped out of
+Equation~(\ref{e308}). The neglect of these terms is justified provided that the layer width is much less than the critical value,
+\begin{equation}
+\delta_c = \left(\frac{1}{\epsilon\,s\,n}\sqrt{\frac{D_\perp}{D_\parallel}}\right)^{1/2}_{r_s} r_s,
+\end{equation}
+below which parallel transport is unable to constrain the electron number density (and, by implication, the electron and
+ion temperatures) to be constant along magnetic field-lines (Fitzpatrick 1995). This condition is well satisfied in conventional
+tokamak plasmas. 
+Note that all of the terms appearing in the 
+normalized layer equations, (\ref{e306})--(\ref{e309}), are assumed to be roughly the same order of magnitude.
+
+\subsection{Asymptotic Matching}
+The normalized linear layer equations, (\ref{e306})--(\ref{e309}), possess independent {\em tearing parity}\/ solutions,
+characterized by the symmetry $\tilde{\psi}(-X)=\tilde\psi(X)$, $\tilde{\phi}(-X)=-\tilde{\phi}(X)$, 
+$\tilde{N}(-X)= - \tilde{N}(X)$, $\tilde{V}(-X)=\tilde{V}(X)$, and {\em twisting parity}\/ solutions, characterized by the symmetry 
+$\tilde{\psi}(-X)=-\tilde\psi(X)$, $\tilde{\phi}(-X)=\tilde{\phi}(X)$, 
+$\tilde{N}(-X)=  \tilde{N}(X)$, $\tilde{V}(-X)=-\tilde{V}(X)$ (Fitzpatrick \& Hender 1994). However, only the tearing parity
+solutions can be asymptotically matched to tearing mode solutions in the outer region. If we assume that
+the asymptotic behavior of the tearing parity layer solutions is
+\begin{equation}\label{e311}
+\tilde{\psi}\rightarrow  \psi_0\!\left[1+ \frac{\hat{\mit\Delta}}{2}\,|X| + {\cal O}(X^2)\right]
+\end{equation}
+as $|X|\rightarrow\infty$, where $\psi_0$ is an arbitrary constant, then asymptotic matching to the outer solution yields
+\begin{equation}\label{e312}
+{\mit\Delta\Psi}_s= S^{1/3}\,\hat{\mit\Delta}\,\,{\mit\Psi}_s.
+\end{equation}
+[See Equations~(\ref{e109}) and (\ref{e134}).]
+
+\subsection{Fourier Transformation}
+Equations~(\ref{e306})--(\ref{e309}) are most conveniently solved in Fourier transform space (Cole \& Fitzpatrick 2006). 
+Let
+\begin{equation}
+\bar{\phi}(p) = \int_{-\infty}^\infty \tilde{\phi}(X)\,{\rm e}^{-{\rm i}\,p\,X}\,dX,
+\end{equation}
+et cetera. The Fourier transformed linear layer equations become
+\begin{align}\label{e314}
+-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_{e}]\,\bar{\psi}&=\frac{d}{dp}\!\left[\bar{\phi}-(1+\lambda_e)\,\bar{N}\right] -p^2\,\bar{\psi},\\[0.5ex]
+-{\rm i}\,(Q-Q_E -Q_{i})\,p^2\,\bar{\phi}&=  \frac{d(p^2\,\bar{\psi})}{dp}- P_\varphi\,p^4\!\left(\bar{\phi} + \frac{\bar{N}}{\tau}\right),\\[0.5ex]
+-{\rm i}\,(Q-Q_E)\bar{N} &= - {\rm i}\,Q_{e}\,\bar{\phi} -D^{2}\,\frac{d(p^2\,\bar{\psi})}{dp}
+ + c_\beta^{\,2}\,\frac{d\bar{V}}{dp} - P_\perp\,p^2\bar{N},\label{e316}\\[0.5ex]
+ -{\rm i}\,(Q-Q_E)\,\bar{V} &= {\rm i}\,Q_{e}\,\bar{\psi} +\frac{d\bar{N}}{dp}- P_\varphi\,p^2\,\bar{V},\label{e317}
+\end{align}
+where, for a tearing parity solution, 
+\begin{equation}
+\bar{\phi}(p)\rightarrow \bar{\phi}_0\!\left[\frac{\hat{\mit\Delta}}{\pi\,p} + 1+ {\cal O}(p)\right]
+\end{equation}
+as $p\rightarrow 0$.
+
+Let us ignore the term $c_\beta^{\,2}\,d\bar{V}/dp$ in Equation~(\ref{e316}). This approximation can
+be justified {\em a posteriori}. It is equivalent to the neglect of the contribution of ion parallel dynamics to the linear  plasma
+response in the resonant layer, and effectively decouples Equation~(\ref{e317}) from Equations~(\ref{e314})--(\ref{e316}) (Waelbroeck, et al.\ 2012).
+Equations~(\ref{e314})--(\ref{e317}) reduce to (Cole \& Fitzpatrick 2006)
+\begin{equation}\label{e320}
+\frac{d}{dp}\!\left[G(p)\,\frac{dY}{dp}\right] - H(p)\,p^{2}\,Y = 0,
+\end{equation}
+where
+\begin{align}
+G(p)&= \frac{p^2}{-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e] + p^2},\\[0.5ex]
+H(p) &=\frac{A(p)}{B(p)},\\[0.5ex]
+ A(p) &= -(Q-Q_E)\,(Q-Q_E-Q_i)-{\rm i}\,(Q-Q_E-Q_i)\,(P_\varphi+P_\perp)\,p^2 + P_\varphi\,P_\perp\,p^4,\\[0.5ex]
+ B(p) &= 
+-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e] +\{P_\perp - {\rm i}\,(1+\lambda_e)\,(Q-Q_E-Q_i)\,D^2\}p^2\nonumber\\[0.5ex]
+&\phantom{=}+[(1+\lambda_e)+1/\tau]\,P_\varphi\,D^2\,p^4,
+\end{align}
+and $Y=\bar{\phi} - (1+\lambda_e)\,\bar{N}$. The boundary conditions are that $Y(p)$ is bounded as $p\rightarrow\infty$, and
+\begin{equation}\label{e325}
+Y(p)\rightarrow Y_0\!\left[\frac{\hat{\mit\Delta}}{\pi\,p} + 1+ {\cal O}(p)\right]
+\end{equation}
+as $p\rightarrow 0$. In the following, we shall assume that $|Q|\sim |Q_E|\sim |Q_e|\sim |Q_i|$, $P_\varphi\sim P_\perp \sim P$, $\tau\sim {\cal O}(1)$, and $\lambda_e\sim{\cal O}(1)$,  for the
+sake of simplicity.
+
+\subsection{Constant-$\psi$ Approximation}\label{s5.6}
+Let us suppose that there are two layers in $p$ space. In the small-$p$ layer, suppose that Equation~(\ref{e320}) reduces to
+\begin{equation}
+\frac{d}{dp}\!\left[\frac{p^2}{-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e] + p^2}\,\frac{dY}{dp}\right]\simeq 0
+\end{equation}
+when $p\sim Q^{1/2}$. Integrating directly, we find that
+\begin{equation}
+Y(p) \simeq Y_0 \left[\frac{\hat{\mit\Delta}}{\pi}\left(\frac{1}{p} + \frac{p}{{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e]}\right) + 1 + {\cal O}(p^2)\right]
+\end{equation}
+for $p\lesssim {\cal O}(Q^{1/2})$, where use has been made of Equation~(\ref{e325}). The two-layer  approximation, which is
+equivalent to the well-known {\em constant-$\psi$ approximation}\/ (Furth, et al.\ 1963), is valid provided
+\begin{equation}
+\frac{Q^3\,(1+P)}{1+Q\,D^2}\ll 1.
+\end{equation}
+In the large-$p$ layer, for  $p\gg {\cal O}(Q^{1/2})$, we obtain 
+\begin{equation}\label{e329}
+\frac{d^{\,2} Y}{dp^2} - H(p)\,p^2\,Y\simeq 0,
+\end{equation}
+with $Y$ bounded as $p\rightarrow \infty$. Asymptotic matching to the small-$p$ layer yields the boundary
+condition 
+\begin{equation}\label{e330}
+Y(p)\simeq Y_0\left\{1+ \frac{\hat{\mit\Delta}}{\pi}\,\frac{p}{{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e]}+ {\cal O}(p^2)\right\}
+\end{equation}
+as $p\rightarrow 0$.
+
+In the various constant-$\psi$ linear response regimes considered in Section~\ref{scp}, Equation~(\ref{e329}) reduces to an
+equation of the form
+\begin{equation}\label{e330a}
+\frac{d^{\,2}Y}{dp^2}- C\,p^m\,Y\simeq 0,
+\end{equation}
+where $m$ is real and non-negative, and $C$ is a complex constant. Let $Y=\sqrt{p}\,Z$ and $q=\sqrt{C}\,p^n/n$, where
+$n=(m+2)/2$. The previous equation transforms into a modified Bessel equation of general order, 
+\begin{equation}
+q^2\,\frac{d^{\,2}Z}{dq^2} + q\,\frac{dZ}{dq} - (q^2+\nu^2)\,Z =0,
+\end{equation}
+where $\nu=1/(m+2)$. The solution that is bounded as $q\rightarrow \infty$ has the small-$q$
+expansion
+\begin{equation}\label{e332}
+K_\nu(z)= \frac{1}{{\mit\Gamma}(1-\nu)}\left(\frac{2}{q}\right)^\nu - \frac{1}{{\mit\Gamma}(1+\nu)}\left(\frac{q}{2}\right)^\nu + {\cal O}(q^{2-\nu}),
+\end{equation}
+where ${\mit\Gamma}(z)$ is a gamma function. 
+A comparison of this expression with Equation~(\ref{e330}) reveals that
+\begin{equation}
+\hat{\mit\Delta} = \pi\,(-{\rm i}\,\left[Q-Q_E-(1+\lambda_e)\,Q_e\right])\, \frac{{\mit\Gamma}(1-\nu)}{{\mit\Gamma}(\nu)}\,\nu^{2\nu-1}\,C^{\,\nu}.
+\end{equation}
+Note, finally, that $p_\ast\sim |C|^{-\nu}$, where $p_\ast$ denotes the width of the large-$p$ layer in $p$ space.
+
+\subsection{Constant-$\psi$ Linear Response Regimes}\label{scp}
+Suppose that $Q\gg P\,p^2$ and $D^2\,p^2 \ll 1$. It follows that $\nu=1/4$ and
+\begin{equation}
+C = \frac{[-{\rm i}\,(Q-Q_E)]\,[-{\rm i}\,(Q-Q_E-Q_i)]}{-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e]}.
+\end{equation}
+Hence, we deduce that
+\begin{equation}\label{ri}
+\hat{\mit\Delta} = \frac{2\pi\,{\mit\Gamma}(3/4)}{{\mit\Gamma}(1/4)}\,(-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e])^{3/4}\,[-{\rm i}\,(Q-Q_E)]^{1/4}\,[-{\rm i}\,(Q-Q_E-Q_i)]^{1/4}.
+\end{equation}
+This response regime is known as the {\em resistive-inertial regime}, because the layer response is dominated by
+resistivity and ion inertia (Furth, et al.\ 1963; Ara, et al.\ 1976; Fitzpatrick 1998). The characteristic layer width is $p_\ast \sim Q^{-1/4}$,
+which implies that the regime is valid when $P\ll Q^{3/2}$, $Q\gg D^4$, and $Q\ll 1$.
+
+Suppose that $Q\ll P\,p^2$ and $D^2\,p^2\ll 1$. It follows that $\nu=1/6$ and $C=P_\varphi$. 
+Hence, we deduce that
+\begin{equation}\label{vr}
+\hat{\mit\Delta} = \frac{6^{2/3}\,\pi\,{\mit\Gamma}(5/6)}{{\mit\Gamma}(1/6)}\, (-{\rm i}\,\left[Q-Q_E-(1+\lambda_e)\,Q_e\right])\,P_\varphi^{1/6}.
+\end{equation}
+This response regime is known as the {\em visco-resistive regime}, because the layer response is dominated by
+resistivity and viscosity. (Fitzpatrick 1998). The characteristic layer width is $p_\ast \sim P^{-1/6}$, which implies that
+the regime is valid when  $P\gg Q^{3/2}$, $P\gg D^6$, and $P\ll Q^{-3}$.
+
+Suppose that $Q\gg P\,p^2$ and $D^2\,p^2\gg 1$. It follows that $\nu=1/2$ and
+\begin{equation}
+C = \frac{-{\rm i}\,(Q-Q_E)}{(1+\lambda_e)\,D^2}.
+\end{equation}
+Hence, we deduce that
+\begin{equation}\label{sc}
+\hat{\mit\Delta}= \frac{\pi\,(-{\rm i}\,\left[Q-Q_E-(1+\lambda_e)\,Q_e\right])\,[-{\rm i}\,(Q-Q_E)]^{1/2}}{\sqrt{1+\lambda_e}\,D}.
+\end{equation}
+This response regime is known as the {\em semi-collisional regime}\/ (Drake \& Lee 1977; Waelbroeck 2003). The characteristic
+layer width is $p_\ast\sim D\,Q^{-1/2}$. which implies that the regime is valid when $Q\ll D^4$,
+ $P\ll Q^2/D^2$, and $Q\ll D$.
+
+Suppose, finally, that $Q\ll P\,p^2$ and $D^2\,p^2\gg 1$. It follows that $\nu=1/4$ and
+\begin{equation}
+C = \frac{P_\perp}{[(1+\lambda_e)+1/\tau]\,D^2}.
+\end{equation}
+Hence, we deduce that 
+\begin{equation}\label{hr}
+\hat{\mit\Delta}= \frac{2\pi\,{\mit\Gamma}(3/4)}{{\mit\Gamma}(1/4)}\,\frac{(-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e])\,P_\perp^{1/4}}{[(1+\lambda_e)+1/\tau]^{1/4}\,D^{1/2}}.
+\end{equation}
+This response regime is known as the {\em Hall-resistive regime}\/ (Cole \& Fitzpatrick 2006). The characteristic
+layer width is $p_\ast \sim D^{1/2}\,P^{-1/4}$, which implies that the regime is valid when $P\gg Q^2/D^2$,
+$P\ll D^6$, and $P\ll D^2/Q^2$.
+
+\subsection{Nonconstant-$\psi$ Regimes}
+Suppose that $p\ll Q^{-1/2}$. In this limit, Equation~(\ref{e320}) reduces to 
+\begin{equation}
+\frac{d}{dp}\!\left(p^2\,\frac{dY}{dp}\right)-(-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e])\,H(p)\,p^2\,Y=0.
+\end{equation}
+
+In the various nonconstant-$\psi$ regimes considered in this section, the previous equation takes the form
+\begin{equation}
+\frac{d}{dp}\!\left(p^2\,\frac{dY}{dp}\right)-C\,p^{m+2}\,Y = 0,
+\end{equation}
+where $m$ is real and non-negative, and $C$ is a complex constant. Let $U=p\,Y$. The previous equation
+yields
+\begin{equation}
+\frac{d^{\,2} U}{dp^2} - C\,p^m\,U = 0.
+\end{equation}
+This equation is identical in form to Equation~(\ref{e330a}), which we have already solved. Indeed, the solution that
+is bounded as $p\rightarrow\infty$ has the small-$p$ expansion (\ref{e332}), where $z=\sqrt{C}\,p^n/n$, 
+$n=(m+2)/2$, and $\nu=1/(m+2)$. The layer width in $p$-space again scales as $p_\ast\sim |C|^{-\nu}$. 
+Matching to Equation~(\ref{e325}) yields
+\begin{equation}
+\hat{\mit\Delta} = -\pi\,\frac{{\mit\Gamma}(\nu)}{{\mit\Gamma}(1-\nu)}\,\nu^{1-2\nu}\,C^{-\nu}.
+\end{equation}
+
+\begin{figure}
+\centerline{\includegraphics[width=0.9\textwidth]{RegimeI.pdf}}
+\caption{Linear resonant plasma response regimes in $Q$-$P$ space for the case $D=0.9$. The various regimes are
+the Hall-resisitive (HR), the semi-collisional (SC), the resistive-inertial (RI), the visco-resistive (VR), the visco-inertial
+(VI), and the inertial (I).}\label{f1}
+\end{figure}
+
+Suppose that $Q\gg P\,p^2$ and $D^2\,p^2 \ll 1$. It follows that $\nu=1/2$ and
+\begin{equation}
+C = [-{\rm i}\,(Q-Q_E)]\,[-{\rm i}\,(Q-Q_E-Q_i)].
+\end{equation}
+Hence, we deduce that
+\begin{equation}
+\hat{\mit\Delta} = -\frac{\pi}{[-{\rm i}\,(Q-Q_E)]^{1/2}\,[-{\rm i}\,(Q-Q_E-Q_i)]^{1/2}}.
+\end{equation}
+This response regime is known as the {\em inertial regime}, because the layer response is dominated by
+ ion inertia (Ara, et al.\ 1976; Fitzpatrick 1998). Note that the plasma response in the inertial regime is
+ equivalent to that of two closely spaced Alfv\'{e}n resonances that straddle the resonant surface (Boozer 1996). 
+ The characteristic layer width is $p_\ast \sim Q^{-1}$,
+which implies that the regime is valid when $P\ll Q^3$, $Q\gg D$, and $Q\gg 1$.
+
+Suppose that $Q\ll P\,p^2$ and $D^2\,p^2 \ll 1$. It follows that $\nu=1/4$ and
+\begin{equation}
+C = (-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e])\,P_\varphi.
+\end{equation}
+Hence, we deduce that
+\begin{equation}
+\hat{\mit\Delta} =- \frac{\pi}{2}\,\frac{{\mit\Gamma}(1/4)}{{\mit\Gamma}(3/4)}\, (-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e])^{-1/4}\,P_\varphi^{-1/4}.
+\end{equation}
+This response regime is known as the {\em visco-inertial regime}, because the layer response is dominated by
+viscosity and ion inertia (Fitzpatrick 1998). 
+ The characteristic layer width is $p_\ast \sim Q^{-1/4}\,P^{-1/4}$,
+which implies that the regime is valid when $P\gg Q^3$, $P\gg D^4/Q$, and $P\gg Q^{-3}$.
+
+Suppose, finally, that $Q\ll P\,p^2$ and $D^2\,p^2\gg 1$. It follows that $\nu=1/2$ and
+\begin{equation}
+C = \frac{(-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e)]\,P_\perp}{[(1+\lambda_e)+1/\tau]\,D^2}.
+\end{equation}
+Hence, we deduce that
+\begin{equation}
+\hat{\mit\Delta}= -\frac{\pi\,[(1+\lambda_e)+1/\tau]^{1/2}\,D}{(-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e)])^{1/2}\,P_\perp^{1/2}}.
+\end{equation}
+This response regime is known as the {\em Hall-viscous regime}. The characteristic layer width is $p_\ast\sim
+D\,Q^{-1/2}\,P^{-1/2}$, which implies that the regime is valid when $Q\ll D$, $P\ll D^4/Q$, and $P\gg D^2/Q^2$.
+
+\begin{figure}
+\centerline{\includegraphics[width=0.9\textwidth]{RegimeII.pdf}}
+\caption{Linear resonant plasma response regimes in $Q$-$P$ space for the case $D=1.2$. The various regimes are
+the Hall-resisitive (HR), the semi-collisional (SC), the Hall-viscous (HV), the visco-resistive (VR), the visco-inertial
+(VI), and the inertial (I).}\label{f2}
+\end{figure}
+
+Figures~\ref{f1} and \ref{f2} show the extents of the various different response regimes in the $Q$-$P$ plane for the
+cases $D<1$ and $D>1$, respectively.
+
+\section{Linear Tearing Mode Stability}
+\subsection{Introduction}
+The aim of this section is to combine the analysis of Sections~\ref{cyl} and \ref{linear} to determine the linear stability
+of tearing modes in tokamak plasmas. In this study, we shall assume that the wall is perfectly conducting.
+
+\subsection{Linear Dispersion Relation}
+Let us write
+\begin{equation}
+\omega = \gamma+{\rm i}\,\omega_r,
+\end{equation}
+where $\gamma$ is the growth-rate of the tearing mode, whereas $\omega_r$ is the real
+phase velocity of the mode in the laboratory frame. We shall assume that $|\gamma|\ll |\omega_r|$. This assumption can
+easily be verified {\em a posteriori}. Asymptotic matching between the solution in the outer region and that in the
+thin linear layer surrounding the resonant surface yields a linear tearing mode dispersion relation of the form
+\begin{equation}\label{e352}
+S^{1/3}\,\hat{\mit\Delta}(\gamma,\omega_r) = E_{ss},
+\end{equation}
+where use has been made of Equations~(\ref{e110}) and (\ref{e312}). Here, $E_{ss}$ is the real tearing stability index, 
+whereas the complex layer matching parameter, $\hat{\mit\Delta}$, is defined in Equation~(\ref{e311}).
+
+In a conventional tokamak plasma, $E_{ss}\sim {\cal O}(1)$,\footnote{Note that we are neglecting $m=1$ modes, for which $|E_{ss}|\gg 1$,
+because these are not really tearing modes
+(Wesson 1978).} and $S^{1/3}\gg 1$. Hence, the previous dispersion relation can only be satisfied if $\omega_r$ takes a
+value that renders $|\hat{\mit\Delta}|\ll 1$. It is clear from Equations~(\ref{ri}), (\ref{vr}), (\ref{sc}), and (\ref{hr}) that this goal
+can be achieved in all of the constant-$\psi$ linear response regimes if
+\begin{equation}\label{e353}
+\omega_r = \omega_{\perp\,e},
+\end{equation}
+where
+\begin{equation}\label{e354}
+\omega_{\perp\,e} = \omega_E+(1+\lambda_e)\,\omega_{\ast\,e}.
+\end{equation}
+According to Equations~(\ref{e353}) and (\ref{e354}), the tearing mode co-rotates with the electron fluid at the resonant
+ surface.\footnote{In fact, it
+rotates slightly faster than the electron fluid because of the influence of the thermal force, ${\bf F}_T$ [see Equation~(\ref{e43})],
+which generates the factor $\lambda_e$ in Equation~(\ref{e354}).}
+
+\subsection{Determination of Growth-Rates}
+Reusing the analysis of Sections~\ref{s5.6} and \ref{scp}, there are two layers in $p$ space (i.e., Fourier space). The
+small-$p$ layer is of width $|\hat{\gamma}|^{1/2}$, where $\hat{\gamma} = S^{1/3}\,\gamma\,\tau_H$. Given that we are effectively assuming that
+$|\hat{\gamma}|\ll 1$, the condition for the separation of the layer solution into two layers (i.e., that the width of the small-$p$ layer is less than that of the large-$p$ layer) is always satisfied.
+The large-$p$ layer is governed by the equation
+\begin{equation}\label{e355}
+\frac{d^{\,2} Y}{dp^2} - \frac{A(p)}{C(p)} \,Y =0,
+\end{equation}
+where 
+\begin{align}
+A(p) &= (1+\lambda_e)\left(\frac{\tau}{1+\tau}\right)\left(1+ \frac{\lambda_e\,\tau}{1+\tau}\right)Q_\ast^{\,2}
++{\rm i}\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)Q_\ast\,(P_\varphi+P_\perp)\,p^2\nonumber\\[0.5ex]
+&\phantom{=} + P_\varphi\,P_\perp\,p^4,\\[0.5ex]
+C(p)&= P_\perp - {\rm i}\,(1+\lambda_e)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)Q_\ast\,D^2 +\left(\frac{1+\tau}{\tau}\right)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right) D^2\,P_\varphi\,p^2.
+\end{align}
+Here, $Q_\ast = S^{1/3}\,\omega_\ast\,\tau_H$, where
+\begin{equation}
+\omega_\ast = -\frac{m}{r_s}\frac{1}{e\,n_0\,B_z}\left.\frac{dp}{dr}\right|_{r_s}.
+\end{equation}
+In the following, $\omega_\ast$ is assumed to be positive. The boundary conditions on Equation~(\ref{e355}) are
+that $Y$ is bounded as $p\rightarrow\infty$, and
+\begin{equation}\label{e359}
+Y(p)= Y_0\left[1+\frac{\hat{\mit\Delta}\,p}{\pi\,\hat{\gamma}} + {\cal O}(p^2)\right]
+\end{equation}
+as $p\rightarrow 0$.
+
+In the various constant-$\psi$ linear response regimes considered in this section, Equation~(\ref{e355}) reduces to an equation of the form
+\begin{equation}
+\frac{d^{\,2} Y}{dp^2} - C\,p^m\,Y = 0,
+\end{equation}
+where $m$ is real and non-negative, and $C$ is a complex constant. As described in Section~\ref{s5.6}, the solution of this
+equation that is bounded as $p\rightarrow \infty$ can be matched to the small-$p$ asymptotic form (\ref{e359}) to give 
+\begin{equation}
+{\mit\Delta} = \pi\,\hat{\gamma}\,\frac{{\mit\Gamma}(1-\nu)}{{\mit\Gamma}(\nu)}\,\nu^{2\nu-1}\,C^\nu,
+\end{equation}
+where $\nu=1/(m+2)$. The width of the large-$p$ layer in $p$ space is $C^{-\nu}$.
+
+As before, we shall assume that. $P_\varphi\sim P_\perp \sim P$, $\lambda_e\sim{\cal O}(1)$, and $\tau\sim {\cal O}(2)$, for
+the sake of simplicity. 
+Suppose that $Q_\ast\gg P\,p^2$ and $P\gg Q_\ast\,D^2$. It follows that $\nu=1/2$ and
+\begin{equation}
+C = (1+\lambda_e)\left(\frac{\tau}{1+\tau}\right)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)\frac{Q_\ast}{P_\perp^{1/2}}.
+\end{equation}
+Hence, 
+\begin{equation}
+{\mit\Delta} = \pi\,\hat{\gamma}\left[ (1+\lambda_e)\left(\frac{\tau}{1+\tau}\right)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)\right]^{1/2}\,\frac{Q_\ast}{P_\perp^{1/2}},
+\end{equation}
+and $p_\ast\sim P^{1/2}/Q_\ast$. This so-called {\em resisrtive-inertial regime}\/ is valid when $P\ll Q_\ast^{3/2}$ and
+$P\gg Q_\ast\,D^2$. 
+Making use of Equation~(\ref{e352}), the corresponding tearing mode growth-rate is
+\begin{equation}
+\gamma = \frac{E_{ss}}{\pi\left[ (1+\lambda_e)\left(\frac{\tau}{1+\tau}\right)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)\right]^{1/2}\,}\,\frac{1}{\omega_\ast\,\tau_H\,\tau_R^{1/2}\,\tau_\perp^{1/2}}.
+\end{equation}
+
+Suppose that $Q_\ast \ll P\,p^2$ and $D^2\,p^2\ll 1$. 
+It follows that $\nu=1/6$ and
+$C = P_\varphi$. 
+Hence, 
+\begin{equation}
+{\mit\Delta} = \frac{6^{2/3}\,\pi\,\hat{\gamma}\, {\mit\Gamma}(5/6)}{\Gamma(1/6)}\,P_\varphi^{1/6}, 
+\end{equation}
+and $p_\ast\sim P^{-1/6}$. This so-called {\em visco-resistive regime}\/ is valid when $P\gg Q_\ast^{3/2}$ and
+$P\gg D^6$. 
+The corresponding tearing mode growth-rate is
+\begin{equation}
+\gamma = \frac{E_{ss}}{6^{2/3}\,\pi\,[{\mit\Gamma}(5/6)/{\mit\Gamma}(1/6)]}\,\frac{\tau_\varphi^{1/6}}{\tau_R^{5/6}\,\tau_H^{1/3}}.
+\end{equation}
+
+Suppose that $Q_\ast\gg P\,p^2$ and $P\ll Q_\ast\,D^2$. It follows that $\nu=1/2$ and
+\begin{equation}
+C = {\rm i}\left(\frac{\tau}{1+\tau}\right)\frac{Q_\ast}{D^2}.
+\end{equation} 
+Hence, 
+\begin{equation}
+{\mit\Delta} = \pi\,\hat{\gamma}\left(\frac{\tau}{1+\tau}\right)^{1/2}\,\frac{Q_\ast^{1/2}}{D},
+\end{equation}
+and $p_\ast\sim D/Q_\ast^{1/2}$. This so-called {\em semi-collisional regime}\/ is valid when $P\ll Q_\ast^{\,2}/D^2$ and
+$P\ll Q_\ast\,D^2$. 
+The corresponding tearing mode growth-rate is
+\begin{equation}
+\gamma = \frac{E_{ss}\,{\rm e}^{-{\rm i}\,\pi/4}}{\pi}\,\frac{d_\beta/r_s}{\omega_\ast^{1/2}\,\tau_H\,\tau_R^{1/2}}.
+\end{equation}
+
+Suppose, finally, that $Q_\ast \ll P\,p^2$ and $D^2\,p^2\gg 1$. It follows that $\nu=1/4$ and
+\begin{equation}
+C = \frac{P_\perp\,[\tau/(1+\tau)]}{[1+\lambda_e\,\tau/(1+\tau)]\,D^2}.
+\end{equation}
+Hence,
+\begin{equation} 
+\hat{\Delta} = 2\pi\,\hat{\gamma}\,\frac{{\mit\Gamma}(3/4)}{\Gamma(1/4)}\,\frac{[\tau/(1+\tau)]^{1/4}\,P_\perp^{1/4}}{[1+\lambda_e\,\tau/(1+\tau)]^{1/4}\,D^{1/2}},
+\end{equation}
+and $p_\ast \sim D^{1/2}/P^{1/4}$. This so-called {\em Hall-resistive regime}\/ is valid when $P\gg Q_\ast^2/D^2$ and
+$P\ll D^6$. The corresponding tearing mode growth rate is 
+\begin{equation}
+\gamma= \frac{E_{ss}}{2\pi\,[{\mit\Gamma}(3/4)/{\mit\Gamma}(1/4)]\,[1+\lambda_e\,\tau/(1+\tau)]^{-1/4}}\,\frac{(d_\beta/r_s)^{1/4}\,\tau_\perp^{1/4}}{\tau_H^{1/3}\,\tau_R^{11/12}}.
+\end{equation}
+
+\subsection{Discussion}
+
+\begin{figure}
+\centerline{\includegraphics[width=0.9\textwidth]{RegimeIII.pdf}}
+\caption{Linear tearing mode growth-rate regimes  in $Q_\ast$-$P$ space for the case $D=1$. The various regimes are
+the Hall-resisitive (HR), the semi-collisional (SC),  the visco-resistive (VR), and the resistive-inertia (RI).}\label{f3}
+\end{figure}
 
@@
 \begin{description}
+\item Ara, A., et al.\ 1978. {\em Magnetic Reconnection and m = 1 Oscillations in Current Carrying Plasmas}. Ann.\ Physics (NY) 
+{\bf 112}, 443. 
+\item Boozer, A.H.\ 1996. {\em Shielding of Resonant Magnetic Perturbations by Rotation}. Phys.\ Plasmas {\bf 3}, 4620.
 \item Braginskii, S.I.\ 1965. {\em Transport Processes in a Plasma}. In {\em Reviews of Plasma Physics}. Consultants Bureau. Vol.~1, 205.
@@
 \item Chapman, S., and Cowling, T.G.\ 1953. {\em The Mathematical Theory of Non-Uniform Gases}. Cambridge University Press.
+\item Chen, X.L.\ and Morrison, P.J.\ 1990. {\em Resistive Tearing Instability with Equilibrium Shear Flow}. Phys.\ Plasmas {\bf 2}, 495. 
+\item Cole, A.\ and Fitzpatrick, R.\ 2006. {\em Drift-Magnetohydrodynamical Model of Error-Field Penetration in Tokamak
+Plasmas}. Phys.\ Plasmas {\bf 13}, 032503. 
+\item Drake, J.F.\ and Lee, Y.C.\ 1977. {\em Kinetic Theory of Tearing Instabilities}. Phys.\ Fluids {\bf 20}, 1341.
 \item Fitzpatrick, R.\ 1993. {\em Interaction of Tearing Modes with External Structures in Cylindrical Geometry}. Nucl.\ Fusion {\bf 33}, 1049. 
+\item Fitzpatrick, R.\ 1995. {\em Helical Temperature Perturbations Associated with Tearing Modes in Tokamak Plasmas}. Phys.\ Plasmas {\bf 2}, 825. 
+\item Fitzpatrick, R.\ 1998. {\em Bifurcated States of a Rotating Tokamak Plasma in the Presence of a Static Error-Field}. Phys.\ Plasmas {\bf 5}, 3325. 
 \item Fitzpatrick, R.\ 2008. {\em Maxwell's Equations and the Principles of Electromagnetism}. Jones \& Bartlett.
 \item Fitzpatrick, R.\ 2015. {\em Plasma Physics: An Introduction}. Taylor \& Francis, CRC Press. 
+\item Fitzpatrick, R.\ and Hender, T.C.\ 1994. {\em Effect of a Static External Magnetic Perturbation on Resistive Mode Stability in Tokamaks}. Phys.\ Plasmas {\bf 1}, 3337. 
 \item Fitzpatrick, R.\ and Waelbroeck, F.L.\ 2005. {\em Two-Fluid Magnetic Island Dynamics in Slab Geometry. I. Isolated Islands}.
@@
 \item Strauss, H.R.\ 1976. {\em Nonlinear, Three-Dimensional Magnetohydrodynamics of  Noncircular Tokamaks}. Phys.\ Fluids {\bf 19},  134.
-\item Vahala, G., et al., 1980. {\em Perturbed Magnetic-Field Phase Slip for Tokamaks}. Nucl.\ Fusion {\bf 20}, 17.
+\item Vahala, G., et al.\ 1980. {\em Perturbed Magnetic-Field Phase Slip for Tokamaks}. Nucl.\ Fusion {\bf 20}, 17.
+\item Waelbroeck, F.L.\ 2003. {\em Shielding of Resonant Magnetic Perturbations in the Long Mean-Free Path Regime}. Phys.\ Plasmas {\bf 10}, 4040.
+\item Waelbroeck, F.L., et al.\ 2012. {\em Role of Singular Layers in the Plasma Response to Resonant Magnetic Perturbations}.
+Nucl.\ Fusion {\bf 52}, 074004.
 \item Wesson, J.\  1978. {\em Hydrodynamic Stability of Tokamaks}. Nucl.\ Fusion {\bf 18}, 87.

### 2021-11-06 Documentation/RegimeI.py

@@ -1,0 +1,55 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+D = 0.9
+
+D2 = D*D
+D4 = D2*D2
+D6 = D4*D2
+
+def f1(q):
+    return q*q/D2
+
+def f2(q):
+    return q**1.5
+
+def f3(q):
+    return q**3.
+
+def f4(q):
+    return 1./q**3.
+
+t1 = np.arange(0., D4, 1.e-3)
+t2 = np.arange(D4, 1., 1.e-3)
+t3 = np.arange(1., 2.**(1./3.), 1.e-3)
+t4 = np.arange(2.**(-1./3.), 1., 1.e-3)
+
+plt.hlines(y=D6, xmin=0, xmax=D4, linewidth=2, color='blue')
+plt.vlines(x=D4, ymin=0, ymax=D6, linewidth=2, color='blue')
+plt.vlines(x=1., ymin=0, ymax=1., linewidth=2, color='blue')
+plt.plot(t1, f1(t1), linewidth=2, color='blue')
+plt.plot(t2, f2(t2), linewidth=2, color='blue')
+plt.plot(t3, f3(t3), linewidth=2, color='blue')
+plt.plot(t4, f4(t4), linewidth=2, color='blue')
+
+plt.text(0.4, 1.4, 'VR',  fontsize=20)
+plt.text(0.975, 1.4, 'VI',  fontsize=20)
+plt.text(1.2, 0.5, 'I',  fontsize=20)
+plt.text(0.8, 0.5, 'RI',  fontsize=20)
+plt.text(0.2, 0.3, 'HR',  fontsize=20)
+plt.text(0.5, 0.1, 'SC',  fontsize=20)
+
+plt.text(1.17, 1.5, '$P=Q^3$', fontsize=20, color='red')
+plt.text(0.63, 1.5, '$P=Q^{-3}$', fontsize=20, color='red')
+plt.text(0.63, 0.75, '$P=Q^{3/2}$', fontsize=20, color='red')
+plt.text(0.665, 0.15, '$Q=D^4$', fontsize=20, color='red')
+plt.text(0.25, 0.56, '$P=D^6$', fontsize=20, color='red')
+plt.text(0.01, 0.07, '$P=Q^2\!D^{-2}$', fontsize=20, color='red')
+plt.text(1.01, 0.15, '$Q=1$', fontsize=20, color='red')
+
[…]

### 2021-11-06 Documentation/RegimeII.py

@@ -1,0 +1,61 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+D = 1.2
+
+D2 = D*D
+DM2 = 1./D2
+D3 = D2*D
+D4 = D2*D2
+D6 = D4*D2
+
+def f1(q):
+    return q*q/D2
+
+def f2(q):
+    return D2/q/q
+
+def f3(q):
+    return q**3.
+
+def f4(q):
+    return 1./q**3.
+
+def f5(q):
+    return D4/q
+
+t1 = np.arange(0., D, 1.e-3)
+t2 = np.arange(DM2, D, 1.e-3)
+t3 = np.arange(D, 4.**(1./3.), 1.e-3)
+t4 = np.arange(4.**(-1./3.), DM2, 1.e-3)
+t5 = np.arange(DM2, D, 1.e-3)
+
+plt.hlines(y=D6, xmin=0, xmax=DM2, linewidth=2, color='blue')
+plt.vlines(x=D, ymin=0, ymax=D3, linewidth=2, color='blue')
+plt.plot(t1, f1(t1), linewidth=2, color='blue')
+plt.plot(t2, f2(t2), linewidth=2, color='blue')
+plt.plot(t3, f3(t3), linewidth=2, color='blue')
+plt.plot(t4, f4(t4), linewidth=2, color='blue')
+plt.plot(t5, f5(t5), linewidth=2, color='blue')
+
+plt.text(0.3, 3.5, 'VR',  fontsize=20)
+plt.text(1.1, 3.5, 'VI',  fontsize=20)
+plt.text(1.4, 1.0, 'I',  fontsize=20)
+plt.text(1.025, 1.5, 'HV',  fontsize=20)
+plt.text(0.4, 1.0, 'HR',  fontsize=20)
+plt.text(0.9, 0.2, 'SC',  fontsize=20)
+
+plt.text(1.34, 2.25, '$P=Q^3$', fontsize=20, color='red')
+plt.text(0.665, 3.5, '$P=Q^{-3}$', fontsize=20, color='red')
+plt.text(0.58, 1.5, '$P=D^2\!Q^{-2}$', fontsize=20, color='red')
+plt.text(1.21, 0.5, '$Q=D$', fontsize=20, color='red')
+plt.text(0.25, 3.04, '$P=D^6$', fontsize=20, color='red')
[…]

### 2021-11-06 Documentation/RegimeIII.py

@@ -1,0 +1,43 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+D = 1.
+
+D2 = D*D
+D4 = D2*D2
+D6 = D4*D2
+
+def f1(q):
+    return q*q/D2
+
+def f2(q):
+    return q**1.5
+
+def f3(q):
+    return q*D2
+
+t1 = np.arange(0., D4, 1.e-3)
+t2 = np.arange(D4, 2., 1.e-3)
+t3 = np.arange(D4, 2., 1.e-3)
+
+plt.hlines(y=D6, xmin=0, xmax=D4, linewidth=2, color='blue')
+plt.plot(t1, f1(t1), linewidth=2, color='blue')
+plt.plot(t2, f2(t2), linewidth=2, color='blue')
+plt.plot(t3, f3(t3), linewidth=2, color='blue')
+
+plt.text(0.4, 2.0, 'VR',  fontsize=20)
+plt.text(1.5, 0.5, 'SC',  fontsize=20)
+plt.text(0.2, 0.5, 'HR',  fontsize=20)
+plt.text(1.75, 2.0, 'RI',  fontsize=20)
+
+plt.text(1.29, 2.0, r'$P=Q_\ast^{3/2}$', fontsize=20, color='red')
+plt.text(0.35, 1.03, '$P=D^6$', fontsize=20, color='red')
+plt.text(0.741, 0.4, r'$P=Q_\ast^2 D^{-2}$', fontsize=20, color='red')
+plt.text(1.525, 1.4, r'$P=Q_\ast D^2$', fontsize=20, color='red')
+
+plt.xlabel(r'$Q_\ast$', fontsize=16)
+plt.ylabel('$P$', fontsize=16)
+
+plt.savefig("RegimeIII.pdf")
+
+#plt.show()

### 2021-11-08 Documentation/TearingModeTheory.tex
Additions to tearing mode writeup

@@
 forces that are parallel and perpendicular to the direction
-of ${\bf B}$. As is well known, charged particles respond to the Lorentz force
+of ${\bf B}$. As is well known, charged particles react to the Lorentz force
 by freely streaming in the direction of ${\bf B}$, while executing
@@
 \begin{equation}
-\frac{\partial^2\psi}{\partial r^2} + \frac{1}{r}\,\frac{\partial\psi}{\partial r}-\frac{m^2}{r^2}\,\psi - \frac{J_z'\,\psi}{r\,(1/q-n/m)}\simeq 0,
+\frac{\partial^2\psi}{\partial r^2} + \frac{1}{r}\,\frac{\partial\psi}{\partial r}-\frac{m^2}{r^2}\,\psi - \frac{J_z'\,\psi}{r\,(1/q-n/m)}=  0,
 \end{equation}
@@
 \begin{equation}\label{e100}
-\frac{d^2\hat{\psi}_s}{dr^2} + \frac{1}{r}\,\frac{d\hat{\psi}_s}{dr}-\frac{m^2}{r^2}\,\hat{\psi}_s - \frac{J_z'\,\hat{\psi}_s}{r\,(1/q-n/m)}\simeq 0
+\frac{d^2\hat{\psi}_s}{dr^2} + \frac{1}{r}\,\frac{d\hat{\psi}_s}{dr}-\frac{m^2}{r^2}\,\hat{\psi}_s - \frac{J_z'\,\hat{\psi}_s}{r\,(1/q-n/m)}= 0
 \end{equation}
@@
 \begin{equation}\label{e100a}
-\frac{d^2\hat{\psi}_w}{dr^2} + \frac{1}{r}\,\frac{d\hat{\psi}_w}{dr}-\frac{m^2}{r^2}\,\hat{\psi}_w - \frac{J_z'\,\hat{\psi}_w}{r\,(1/q-n/m)}\simeq 0
+\frac{d^2\hat{\psi}_w}{dr^2} + \frac{1}{r}\,\frac{d\hat{\psi}_w}{dr}-\frac{m^2}{r^2}\,\hat{\psi}_w - \frac{J_z'\,\hat{\psi}_w}{r\,(1/q-n/m)}= 0
 \end{equation}
@@
 \begin{equation}\label{e100b}
-\frac{d^2\hat{\psi}_c}{dr^2} + \frac{1}{r}\,\frac{d\hat{\psi}_c}{dr}-\frac{m^2}{r^2}\,\hat{\psi}_c\simeq 0
+\frac{d^2\hat{\psi}_c}{dr^2} + \frac{1}{r}\,\frac{d\hat{\psi}_c}{dr}-\frac{m^2}{r^2}\,\hat{\psi}_c=  0
 \end{equation}
@@
 where ${\mit\Omega}_{\varphi\,0}(r)$ is the 
-unperturbed (by the tearing mode) ion toroidal angular velocity profile, and ${\mit\Delta\Omega}_{\theta}(r,t)$ is the  modification to  this  profile
+unperturbed (by the tearing mode) ion toroidal angular velocity profile, and ${\mit\Delta\Omega}_{\varphi}(r,t)$ is the  modification to  this  profile
 induced by the toroidal electromagnetic torque that develops at the resonant surface. The perturbed ion toroidal angular
@@
 \begin{align}\label{e188}
-4\pi^2\,R_0\left[(1+2\,q_s^{\,2})\,\rho_s\,r^{\,3}\,\frac{\partial {\mit\Delta\Omega}_\theta}{\partial t}+ \frac{\rho_s}{\tau_{\theta\,s}}\,r^{\,3}\,{\mit\Delta\Omega}_\theta-\mu_s\frac{\partial}{\partial r}\!\left(r^{\,3}\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial r}\right)\right]
+4\pi^2\,R_0\left[(1+2\,q_s^{\,2})\,\rho_s\,r^{\,3}\,\frac{\partial {\mit\Delta\Omega}_\theta}{\partial t}+ \frac{\rho_s}{\tau_{\theta\,s}}\,r^{\,3}\,{\mit\Delta\Omega}_\theta-\mu_{\perp,s}\frac{\partial}{\partial r}\!\left(r^{\,3}\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial r}\right)\right]
 &=T_{\theta\,s}\,\delta(r-r_s),\\[0.5ex]
-4\pi^2\,R_0^{\,3}\left[\rho_s\,r\,\frac{\partial {\mit\Delta\Omega}_\varphi}{\partial t}-\mu_s\frac{\partial}{\partial r}\!\left(r\,\frac{\partial{\mit\Delta\Omega}_\varphi}{\partial r}\right)\right]
+4\pi^2\,R_0^{\,3}\left[\rho_s\,r\,\frac{\partial {\mit\Delta\Omega}_\varphi}{\partial t}-\mu_{\perp\,s}\frac{\partial}{\partial r}\!\left(r\,\frac{\partial{\mit\Delta\Omega}_\varphi}{\partial r}\right)\right]
 =T_{\varphi\,s}\,\delta(r-r_s),\label{e189}
 \end{align}
-where $q_s=q(r_s)$, $\rho_s=\rho(r_s)$, $\tau_{\theta\,s}=\tau_\theta(r_s)$, and $\mu_s=\mu_\perp(r_s)$.
+where $q_s=q(r_s)$, $\rho_s=\rho(r_s)$, $\tau_{\theta\,s}=\tau_\theta(r_s)$, and $\mu_{\perp\,s}=\mu_\perp(r_s)$.
 
@@
 \begin{equation}\label{e220}
-{\bf E} + {\bf V}\times {\bf B} + \frac{1}{e\,n_0}\!\left[\nabla p + \frac{1}{1+\tau}\left(\frac{0.71\,\eta_e\,\tau}{1+\eta_e}-1\right)({\bf b}\cdot\nabla p)\,{\bf b} -{\bf j}\times{\bf b}\right] \simeq \eta_\parallel\,{\bf j}_\parallel + \eta_\perp\,{\bf j}_\perp.
+{\bf E} + {\bf V}\times {\bf B} + \frac{1}{e\,n_0}\!\left[\nabla p + \frac{1}{1+\tau}\left(\frac{0.71\,\eta_e\,\tau}{1+\eta_e}-1\right)({\bf b}\cdot\nabla p)\,{\bf b} -{\bf j}\times{\bf b}\right] = \eta_\parallel\,{\bf j}_\parallel + \eta_\perp\,{\bf j}_\perp.
 \end{equation}
@@
 n_0\,m_i\!\left[\frac{\partial {\bf V}}{\partial t} + ({\bf V}\cdot\nabla ){\bf V} + \frac{1}{1+\tau}\,({\bf V}_\ast\cdot\nabla){\bf V}_E\right]
-+ \nabla p + \nabla\cdot\bpi_i - {\bf j}\times {\bf B}\simeq 0.
++ \nabla p + \nabla\cdot\bpi_i - {\bf j}\times {\bf B}= 0.
 \end{equation}
@@
 \begin{equation}
-\frac{\partial p}{\partial t} + {\bf V}\cdot\nabla p + {\mit\Gamma}\,p\,\nabla\cdot{\bf V} + \frac{2}{3}\,\nabla\cdot {\bf q}\simeq 0, 
+\frac{\partial p}{\partial t} + {\bf V}\cdot\nabla p + {\mit\Gamma}\,p\,\nabla\cdot{\bf V} + \frac{2}{3}\,\nabla\cdot {\bf q}=0, 
 \label{e223}
@@
 \begin{align}\label{e227}
-\hat{\bf E} + \hat{\bf V}\times \hat{\bf B} + \hat{d}_i\!\left[\hat{\nabla} \hat{p} + \frac{1}{1+\tau}\left(\frac{0.71\,\eta_e\,\tau}{1+\eta_e}-1\right)({\bf b}\cdot\hat{\nabla} \hat{p})\,{\bf b} + \hat{\nabla}\cdot\hat{\bpi}_e-\hat{\bf j}\times\hat{\bf b}\right] &\simeq \hat{\eta}_\parallel\,\hat{\bf j}_\parallel+ \hat{\eta}_\perp\,\hat{\bf j}_\perp,\\[0.5ex]
+\hat{\bf E} + \hat{\bf V}\times \hat{\bf B} + \hat{d}_i\!\left[\hat{\nabla} \hat{p} + \frac{1}{1+\tau}\left(\frac{0.71\,\eta_e\,\tau}{1+\eta_e}-1\right)({\bf b}\cdot\hat{\nabla} \hat{p})\,{\bf b} + \hat{\nabla}\cdot\hat{\bpi}_e-\hat{\bf j}\times\hat{\bf b}\right] &= \hat{\eta}_\parallel\,\hat{\bf j}_\parallel+ \hat{\eta}_\perp\,\hat{\bf j}_\perp,\\[0.5ex]
 \frac{\partial \hat{\bf V}}{\partial \hat{t}} 
@@
 + \hat{\nabla} \hat{p} + \hat{\nabla}\cdot\hat{\bpi}_i -
- \hat{\bf j}\times \hat{\bf B} &\simeq 0,
+ \hat{\bf j}\times \hat{\bf B} &= 0,
  \\[0.5ex]
-\frac{\partial \hat{p}}{\partial \hat{t}} + \hat{\bf V}\cdot\hat{\nabla} \hat{p} + {\mit\Gamma}\,\hat{p}\,\hat{\nabla}\cdot\hat{\bf V} + \frac{2}{3}\,\hat{\nabla}\cdot \hat{\bf q}&\simeq 0,\label{e229}
+\frac{\partial \hat{p}}{\partial \hat{t}} + \hat{\bf V}\cdot\hat{\nabla} \hat{p} + {\mit\Gamma}\,\hat{p}\,\hat{\nabla}\cdot\hat{\bf V} + \frac{2}{3}\,\hat{\nabla}\cdot \hat{\bf q}&= 0,\label{e229}
 \end{align}
@@
 \begin{equation}\label{e238}
-\hat{\bf B} \simeq (1+ \delta b)\,{\bf n} + \hat{\nabla}\psi\times {\bf n},
+\hat{\bf B} \simeq (1+ \delta b)\,{\bf n} + \hat{\nabla}\hat{\psi}\times {\bf n},
 \end{equation}
 which automatically satisfies Equation~(\ref{e230}).
-(Recall that we are assuming that $|r-r_s|\ll r_s$ inside the resonant layer.) Here, $\delta b(\hat{x},\zeta)$ and $\psi(\hat{x},\zeta)$ are assumed to be small
+(Recall that we are assuming that $|r-r_s|\ll r_s$ inside the resonant layer.) Note that $\hat{\psi}=\psi/r_s$, where $\psi$ is defined in Equation~(\ref{e93}).
+ Here, $\delta b(\hat{x},\zeta)$ and $\hat{\psi}(\hat{x},\zeta)$ are assumed to be small
 compared to unity, which merely indicates that the perturbed magnetic field due to the tearing mode is small compared to the
@@
 \begin{equation}
-\hat{\bf E} \simeq \left(\hat{E}_\parallel- \frac{\partial \psi}{\partial \hat{t}}\right)\!{\bf n} + \hat{\nabla}\!\left(\frac{\partial\chi}{\partial \hat{t}}\right)\times {\bf n} + \hat{\nabla}\phi,
+\hat{\bf E} \simeq \left(\hat{E}_\parallel- \frac{\partial \hat{\psi}}{\partial \hat{t}}\right)\!{\bf n} + \hat{\nabla}\!\left(\frac{\partial\chi}{\partial \hat{t}}\right)\times {\bf n} + \hat{\nabla}\phi,
 \end{equation}
@@
 \end{equation}
-Here, $\hat{E}_\parallel = E_\parallel/(B_z\,V_A)$ represents the constant inductive electric field that drives the equilibrium plasma current in the vicinity of the resonant surface.
+Here, $\hat{E}_\parallel = E_\parallel/(B_z\,V_A)$, where $E_\parallel$ represents the constant inductive electric field that drives the equilibrium plasma current in the vicinity of the resonant surface.
 Moreover, $\partial/\partial \hat{t}$ and $\phi(\hat{x},\zeta)$
@@
 \begin{equation}
-\hat{p}\simeq  \frac{\beta}{{\mit\Gamma}} + \delta p,
+\hat{p}= \frac{\beta}{{\mit\Gamma}} + \delta p,
 \end{equation}
@@
  \begin{align}\label{e247}
- \hat{d}_i\,\hat{\nabla}(\delta p + \delta b)\nonumber\\[0.5ex]+ \left(\hat{E}_{\parallel}-\frac{\partial\psi}{\partial \hat{t}} - [\psi,\phi]+ \frac{\hat{d}_i\,[\psi,\delta p]}{1+\tau}\left(1-\frac{0.71\,\eta_e\,\tau}{1+\eta_e}\right)
- + \hat{d}_i\,[\psi,\delta b]+ \hat{\eta}_\parallel\,J\right){\bf n}\nonumber\\[0.5ex]
- +\hat{\nabla}\!\left(\frac{\partial\chi}{\partial \hat{t}} + {\mit\Xi} -\hat{\eta}_\perp\,\delta b\right)\times {\bf n} + \frac{\hat{d}_i}{2}\,\hat{\nabla}\delta b^{\,2}- b_z\,\hat{\nabla}\phi + \hat{V}_{\parallel\,i}\,\hat{\nabla}\psi
-+  \hat{d}_i\,J\,\hat{\nabla}\psi \simeq 0,\\[0.5ex]
- \hat{\nabla}(\delta p + \delta b) + \left(\frac{\partial \hat{V}_{\parallel\,i}}{\partial \hat{t}} + [\hat{V}_{\parallel\,i},\phi] + [\psi,\delta b]\right){\bf n}\nonumber\\[0.5ex]
+ \hat{d}_i\,\hat{\nabla}(\delta p + \delta b)\nonumber\\[0.5ex]+ \left(\hat{E}_{\parallel}-\frac{\partial\hat{\psi}}{\partial \hat{t}} - [\hat{\psi},\phi]+ \frac{\hat{d}_i\,[\hat{\psi},\delta p]}{1+\tau}\left(1-\frac{0.71\,\eta_e\,\tau}{1+\eta_e}\right)
+ + \hat{d}_i\,[\hat{\psi},\delta b]+ \hat{\eta}_\parallel\,J\right){\bf n}\nonumber\\[0.5ex]
+ +\hat{\nabla}\!\left(\frac{\partial\chi}{\partial \hat{t}} + {\mit\Xi} -\hat{\eta}_\perp\,\delta b\right)\times {\bf n} + \frac{\hat{d}_i}{2}\,\hat{\nabla}\delta b^{\,2}- b_z\,\hat{\nabla}\phi + \hat{V}_{\parallel\,i}\,\hat{\nabla}\hat{\psi}
++  \hat{d}_i\,J\,\hat{\nabla}\hat{\psi}= 0,\\[0.5ex]
+ \hat{\nabla}(\delta p + \delta b) + \left(\frac{\partial \hat{V}_{\parallel\,i}}{\partial \hat{t}} + [\hat{V}_{\parallel\,i},\phi] + [\hat{\psi},\delta b]\right){\bf n}\nonumber\\[0.5ex]
  +\hat{\nabla}\!\left(\frac{\partial\phi}{\partial \hat{t}} - \frac{\hat{d}_i\,[\phi,\delta p]}{2\,(1+\tau)}\right)\times {\bf n} 
@@
  \left(\hat{V}_\perp^{\,2}+ \frac{\hat{\bf V}_\ast\cdot\hat{\bf V}_E }{1+\tau}+ \delta b^{\,2}\right)  \nonumber\\[0.5ex]
--\hat{\nabla}^2\phi\,\hat{\nabla}\phi + \frac{\hat{d}_i}{2\,(1+\tau)}\left(\hat{\nabla}^2\phi\,\hat{\nabla}\delta p +\hat{\nabla}^2\delta p\,\hat{\nabla}\phi\right) + J\,\hat{\nabla}\psi + \hat{\nabla}\cdot\hat{\bpi}_i \simeq 0,\label{e248}\\[0.5ex]
-\frac{\partial \delta p}{\partial \hat{t}} + [\delta p,\phi] +\beta\,\hat{\nabla}^2{\mit\Xi} + \frac{2}{3}\,\hat{\nabla}\cdot \hat{\bf q}\simeq 0,\label{e249}
+-\hat{\nabla}^2\phi\,\hat{\nabla}\phi + \frac{\hat{d}_i}{2\,(1+\tau)}\left(\hat{\nabla}^2\phi\,\hat{\nabla}\delta p +\hat{\nabla}^2\delta p\,\hat{\nabla}\phi\right) + J\,\hat{\nabla}\hat{\psi} + \hat{\nabla}\cdot\hat{\bpi}_i = 0,\label{e248}\\[0.5ex]
+\frac{\partial \delta p}{\partial \hat{t}} + [\delta p,\phi] +\beta\,\hat{\nabla}^2{\mit\Xi} + \frac{2}{3}\,\hat{\nabla}\cdot \hat{\bf q}= 0,\label{e249}
  \end{align}
@@
  [A,B] &\equiv \hat{\nabla} A\times \hat{\nabla} B\cdot{\bf n},\\[0.5ex]
- J &= -\frac{2}{q_s\,\hat{R}_0}+ \hat{\nabla}^2\psi,\label{eJ}
+ J &= -\frac{2}{q_s\,\hat{R}_0}+ \hat{\nabla}^2\hat{\psi},\label{eJ}
  \end{align}
@@
  \begin{equation}
- \delta b \simeq - \delta p,
+ \delta b =- \delta p,
  \end{equation}
@@
  \begin{equation}\label{e252}
- \frac{\partial\psi}{\partial\hat{t}}\simeq [\phi,\psi] +\hat{d}_i\!\left(\frac{\tau}{1+\tau}\right)\left(1+\frac{0.71\,\eta_e}{1+\eta_e}\right)
- [\delta p,\psi] + \hat{\eta}_\parallel\,J + \hat{E}_\parallel.
+ \frac{\partial\hat{\psi}}{\partial\hat{t}}= [\phi,\hat{\psi}] +\hat{d}_i\!\left(\frac{\tau}{1+\tau}\right)\left(1+\frac{0.71\,\eta_e}{1+\eta_e}\right)
+ [\delta p,\hat{\psi}] + \hat{\eta}_\parallel\,J + \hat{E}_\parallel.
  \end{equation}
@@
  \begin{equation}\label{e254}
- \frac{\partial\hat{V}_{\parallel\,i}}{\partial\hat{t}}\simeq [\phi,\hat{V}_{\parallel\,i}]-[\delta p,\psi] -{\bf n}\cdot\hat{\nabla}\cdot\hat{\bpi}_i.
+ \frac{\partial\hat{V}_{\parallel\,i}}{\partial\hat{t}}= [\phi,\hat{V}_{\parallel\,i}]-[\delta p,\hat{\psi}] -{\bf n}\cdot\hat{\nabla}\cdot\hat{\bpi}_i.
  \end{equation}
@@
  \begin{equation}
- \frac{\partial\delta p}{\partial\hat{t}}\simeq [\phi,\delta p]+\hat{\nabla}^2{\mit\Xi}-[\hat{V}_{\parallel\,i},\psi]
- -\hat{d}_i\,[J,\psi] +\hat{\eta}_\perp\,\hat{\nabla}^{\,2}\delta p.
+ \frac{\partial\delta p}{\partial\hat{t}}= [\phi,\delta p]+\hat{\nabla}^2{\mit\Xi}-[\hat{V}_{\parallel\,i},\hat{\psi}]
+ -\hat{d}_i\,[J,\hat{\psi}] +\hat{\eta}_\perp\,\hat{\nabla}^{\,2}\delta p.
  \end{equation}
@@
  \begin{align}\label{e256}
- \frac{\partial\delta p}{\partial\hat{t}}\simeq [\phi,\delta p]-c_\beta^{\,2}\,[\hat{V}_{\parallel\,i},\psi]-c_\beta^{\,2}\,\hat{d}_i\,[J,\psi]
+ \frac{\partial\delta p}{\partial\hat{t}}= [\phi,\delta p]-c_\beta^{\,2}\,[\hat{V}_{\parallel\,i},\hat{\psi}]-c_\beta^{\,2}\,\hat{d}_i\,[J,\hat{\psi}]
  -\frac{2}{3}\,(1-c_\beta^{\,2})\,\hat{\nabla}\cdot\hat{\bf q} +c_\beta^{\,2}\,\hat{\eta}_\perp \hat{\nabla}^2\delta p,
@@
  \begin{align}\label{e258}
- \frac{\partial U}{\partial\hat{t}}& \simeq [\phi,U] + \frac{\hat{d}_i}{2\,(1+\tau)}\left(
+ \frac{\partial U}{\partial\hat{t}}& = [\phi,U] + \frac{\hat{d}_i}{2\,(1+\tau)}\left(
  \hat{\nabla}^2[\phi,\delta p] + [\hat{\nabla}^2\phi,\delta p] + [\hat{\nabla}^2 \delta p,\phi]\right)
- + [J,\psi] \nonumber\\[0.5ex]&\phantom{=} + {\bf n}\cdot\hat{\nabla}\times \hat{\nabla}\cdot\hat{\bpi}_i,
+ + [J,\hat{\psi}] \nonumber\\[0.5ex]&\phantom{=} + {\bf n}\cdot\hat{\nabla}\times \hat{\nabla}\cdot\hat{\bpi}_i,
  \end{align}
@@
 \begin{align}
-\hat{\nabla}\cdot \hat{\bf q} &\simeq- \left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\parallel\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\parallel\,i}\right)[[\delta p,\psi],\psi]\nonumber\\[0.5ex]
+\hat{\nabla}\cdot \hat{\bf q} &=- \left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\parallel\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\parallel\,i}\right)[[\delta p,\hat{\psi}],\hat{\psi}]\nonumber\\[0.5ex]
 &\phantom{=} - \left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\perp\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\perp\,i}\right)\nabla_\perp^{\,2} \delta p,\label{e260}
@@
 \begin{equation}
-\hat{\nabla}\cdot\hat{\bpi}_i \simeq - \hat{\chi}_\varphi\,\hat{\nabla}^2\hat{\bf V}_i,
+\hat{\nabla}\cdot\hat{\bpi}_i =- \hat{\chi}_\varphi\,\hat{\nabla}^2\hat{\bf V}_i,
 \end{equation}
@@
 \begin{align}\label{e262}
-{\bf n}\cdot\hat{\nabla}\cdot\hat{\bpi}_i&\simeq -\hat{\chi}_\varphi\,\hat{\nabla}^{2}\hat{V}_{\parallel\,i},\\[0.5ex]
-{\bf n}\cdot\hat{\nabla}\times \hat{\nabla}\cdot\hat{\bpi}_i&\simeq \hat{\chi}_\varphi \,\hat{\nabla}^4\!\left(\phi - \frac{\hat{d}_i\,\delta p}{1+\tau}\right).\label{e263}
+{\bf n}\cdot\hat{\nabla}\cdot\hat{\bpi}_i&= -\hat{\chi}_\varphi\,\hat{\nabla}^{2}\hat{V}_{\parallel\,i},\\[0.5ex]
+{\bf n}\cdot\hat{\nabla}\times \hat{\nabla}\cdot\hat{\bpi}_i&= \hat{\chi}_\varphi \,\hat{\nabla}^4\!\left(\phi - \frac{\hat{d}_i\,\delta p}{1+\tau}\right).\label{e263}
 \end{align}
@@
 \begin{align}\label{e264}
-\frac{\partial\psi}{\partial\hat{t}}&\simeq [\phi,\psi] + \hat{d}_\beta\!\left(\frac{\tau}{1+\tau}\right)\left(1+\frac{0.71\,\eta_e}{1+\eta_e}\right)[N,\psi]
+\frac{\partial\hat{\psi}}{\partial\hat{t}}&= [\phi,\hat{\psi}] + \hat{d}_\beta\!\left(\frac{\tau}{1+\tau}\right)\left(1+\frac{0.71\,\eta_e}{1+\eta_e}\right)[N,\hat{\psi}]
 +\hat{\eta}_\parallel\,J + \hat{E}_\parallel,\\[0.5ex]
-\frac{\partial U}{\partial \hat{t}}&\simeq [\phi,U] + \frac{\hat{d}_\beta}{2\,(1+\tau)}\left(\hat{\nabla}^2[\phi,N] + [\hat{\nabla}^2\phi,N] + [\hat{\nabla}^2 N,\phi]\right) + [J,\psi] \nonumber\\[0.5ex]&\phantom{=}+\hat{\chi}_\varphi  \,\hat{\nabla}^4\!\left(\phi - \frac{\hat{d}_\beta\,N}{1+\tau}\right),\label{e265} \\[0.5ex]
-\frac{\partial N}{\partial \hat{t}}&\simeq [\phi,N] -c_\beta\,[V,\psi] -\hat{d}_\beta\,[J,\psi] + \hat{D}_\parallel\,[[N,\psi],\psi]
+\frac{\partial U}{\partial \hat{t}}&= [\phi,U] + \frac{\hat{d}_\beta}{2\,(1+\tau)}\left(\hat{\nabla}^2[\phi,N] + [\hat{\nabla}^2\phi,N] + [\hat{\nabla}^2 N,\phi]\right) + [J,\hat{\psi}] \nonumber\\[0.5ex]&\phantom{=}+\hat{\chi}_\varphi  \,\hat{\nabla}^4\!\left(\phi - \frac{\hat{d}_\beta\,N}{1+\tau}\right),\label{e265} \\[0.5ex]
+\frac{\partial N}{\partial \hat{t}}&= [\phi,N] -c_\beta\,[V,\hat{\psi}] -\hat{d}_\beta\,[J,\hat{\psi}] + \hat{D}_\parallel\,[[N,\hat{\psi}],\hat{\psi}]
 + \hat{D}_\perp\,\hat{\nabla}_\perp^{\,2}N,\label{e266}\\[0.5ex]
-\frac{\partial V}{\partial\hat{t}}&\simeq [\phi,V] - c_\beta\,[N,\psi] + \hat{\chi}_\varphi\,\hat{\nabla}^2 V,\label{e267}\\[0.5ex]
-J &=-\frac{2}{q_s\,\hat{R}_0}+\hat{\nabla}^2\psi,\\[0.5ex]
+\frac{\partial V}{\partial\hat{t}}&= [\phi,V] - c_\beta\,[N,\hat{\psi}] + \hat{\chi}_\varphi\,\hat{\nabla}^2 V,\label{e267}\\[0.5ex]
+J &=-\frac{2}{q_s\,\hat{R}_0}+\hat{\nabla}^2\hat{\psi},\\[0.5ex]
 U &=\hat{\nabla}^2 \phi.\label{e269}
@@
  \rho_s &= \frac{v_t}{{\mit\Omega}_i},\\[0.5ex]
-v_t &= \left(\frac{T_e+T_i}{m_i}\right)^{1/2}_{r_s},
+v_t &= \left(\frac{T_e+T_i}{m_i}\right)^{1/2},
 \end{align}
@@
 to the original four-field model derived by Hazeltine, et al.\ (Hazeltine, et al.\ 1985). Equation~(\ref{e264}) is the {\em generalized
-Ohm's law}\/ that governs the time evolution of the helical magnetic flux, $\psi$. Equation~(\ref{e265}) is the {\em parallel
-ion vorticity equation}\/ that governs the  time evolution of the parallel ion vorticity, $U$. 
+Ohm's law}\/ that governs the time evolution of the (normalized) helical magnetic flux, $\hat{\psi}$. Equation~(\ref{e265}) is the {\em parallel
+ion vorticity equation}\/ that governs the  time evolution of the (normalized) parallel ion vorticity, $U$. 
 Equation~(\ref{e266}) is the {\em electron number density continuity equation}\/ that 
-governs the time evolution of the electron number density, $N$. Finally, Equation~(\ref{e267}) is the
-{\em ion parallel equation of motion}\/ that governs the time evolution of the  parallel ion velocity, $V$.
+governs the time evolution of the (normalized) electron number density, $N$. Finally, Equation~(\ref{e267}) is the
+{\em ion parallel equation of motion}\/ that governs the time evolution of the  (normalized) parallel ion velocity, $V$.
 
@@
 \begin{align}\label{e275}
-\frac{\partial\psi}{\partial\hat{t}}&\simeq [\phi,\psi]+\hat{\eta}_\parallel\,J + \hat{E}_\parallel,\\[0.5ex]
-\frac{\partial U}{\partial \hat{t}}&\simeq [\phi,U]  + [J,\psi]+\hat{\chi}_\perp  \,\hat{\nabla}^4\phi.\label{e276}
+\frac{\partial\hat{\psi}}{\partial\hat{t}}&= [\phi,\hat{\psi}]+\hat{\eta}_\parallel\,J + \hat{E}_\parallel,\\[0.5ex]
+\frac{\partial U}{\partial \hat{t}}&= [\phi,U]  + [J,\hat{\psi}]+\hat{\chi}_\perp  \,\hat{\nabla}^4\phi.\label{e276}
 \end{align}
@@
 \begin{align}
-\frac{\partial N}{\partial \hat{t}}&\simeq [\phi,N] -c_\beta\,[V,\psi] + \hat{D}_\parallel\,[[N,\psi],\psi]
+\frac{\partial N}{\partial \hat{t}}&= [\phi,N] -c_\beta\,[V,\hat{\psi}] + \hat{D}_\parallel\,[[N,\hat{\psi}],\hat{\psi}]
 + \hat{D}_\perp\,\hat{\nabla}_\perp^{\,2}N,\\[0.5ex]
-\frac{\partial V}{\partial\hat{t}}&\simeq [\phi,V] - c_\beta\,[N,\psi] + \hat{\chi}_\phi\,\hat{\nabla}^2 V,
-\end{align}
-where $\psi$ is assumed to take its unperturbed value. 
+\frac{\partial V}{\partial\hat{t}}&= [\phi,V] - c_\beta\,[N,\hat{\psi}] + \hat{\chi}_\phi\,\hat{\nabla}^2 V,
+\end{align}
+where $\hat{\psi}$ is assumed to take its unperturbed value. 
 This model describes ion sound wave dynamics parallel to magnetic field-lines. It should be noted that the
@@
 It is convenient to set the normalization scale-length, $l$, in our four-field response model equal to the minor radius of the resonant surface, $r_s$. 
-Recall that the four fields in question---namely, $\psi$, $\phi$, $N$, and $V$---have the following
+Recall that the four fields in question---namely, $\hat{\psi}$, $\phi$, $N$, and $V$---have the following
 definitions:
 \begin{align}\label{e279}
-\nabla\psi &= \frac{{\bf n}\times{\bf B}} {r_s\,B_z},\\[0.5ex]
+\nabla\hat{\psi} &= \frac{{\bf n}\times{\bf B}} {r_s\,B_z},\\[0.5ex]
 \nabla\phi &= \frac{{\bf n}\times {\bf V}}{r_s\,V_A},\\[0.5ex]
@@
 Alfv\'{e}n speed defined in Equation~(\ref{e226a}), and $c_\beta$ is defined in Equations~(\ref{e244}) and (\ref{e257}). Our
-model also employs the auxiliary fields $J=-2\,\epsilon_s/q_s+r_s^2\,\nabla^2 \psi$ and  $U=r_s^2\,\nabla^2 \phi$. Here, $\epsilon_s=r_s/R_0$.
+model also employs the auxiliary fields $J=-2\,\epsilon_s/q_s+r_s^2\,\nabla^2 \hat{\psi}$ and  $U=r_s^2\,\nabla^2 \phi$. Here, $\epsilon_s=r_s/R_0$.
 
@@
 \begin{align}\label{e287}
-\psi &= \frac{\hat{x}^{\,2}}{2\,\hat{L}_s},\\[0.5ex]
+\hat{\psi} &= \frac{\hat{x}^{\,2}}{2\,\hat{L}_s},\\[0.5ex]
 \phi &= - \hat{V}_E\,\hat{x},\\[0.5ex]
-N &= \frac{\hat{V}_\ast\,\hat{x}}{\hat{d}_\beta},\\[0.5ex]
+N &= \frac{\hat{V}_\ast\,\hat{x}}{\hat{d}_s},\\[0.5ex]
 V &= \hat{V}_\parallel,\label{e290}
@@
 \end{equation}
-is the (dominant $\theta$-component of the) diamagnetic velocity, $\hat{d}_\beta=d_\beta/r_s$, $d_\beta$ is the modified  ion sound radius defined in 
+is the (dominant $\theta$-component of the) diamagnetic velocity, $\hat{d}_s=d_s/r_s$,  $d_s=d_\beta(r_s)$, $d_\beta$ is the modified  ion sound radius defined in 
 Equation~(\ref{e270}), and 
@@
 \begin{align}
-\psi(\hat{x},\zeta,t) &= \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
+\hat{\psi}(\hat{x},\zeta,t) &= \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
 \phi(\hat{x},\zeta,t) &=-\hat{V}_E\,\hat{x}+ \tilde{\phi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
-N(\hat{x},\zeta,t) &= \frac{\hat{V}_\ast\,\hat{x}}{\hat{d}_\beta}-\frac{1}{\hat{d}_\beta}\!\left(\frac{1+\tau}{\tau}\right)\!\tilde{N}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
-V(\hat{x},\zeta,t) &= \hat{V}_\parallel + \frac{c_\beta}{\hat{d}_\beta}\!\left(\frac{1+\tau}{\tau}\right)\!\tilde{V}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
+N(\hat{x},\zeta,t) &= \frac{\hat{V}_\ast\,\hat{x}}{\hat{d}_s}-\frac{1}{\hat{d}_s}\!\left(\frac{1+\tau}{\tau}\right)\!\tilde{N}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
+V(\hat{x},\zeta,t) &= \hat{V}_\parallel + \frac{c_\beta}{\hat{d}_s}\!\left(\frac{1+\tau}{\tau}\right)\!\tilde{V}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
 J(\hat{x},\zeta,t) &=-\left(\frac{2}{s_s}-1\right)\!\frac{1}{\hat{L}_s}+ \hat{\nabla}^2\tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
@@
 -{\rm i}\,[\omega-\omega_E -(1+\lambda_e)\,\omega_{\ast\,e}]\,\tau_H\,\tilde{\psi} &= -{\rm i} \,\hat{x}\,[\tilde{\phi}-(1+\lambda_e)\,\tilde{N}) + S^{-1}\,\hat{\nabla}^2\tilde{\psi},\\[0.5ex]
--{\rm i}\,(\omega-\omega_E-\omega_{\ast\,i})\,\tau_H\,\hat{\nabla}^2\tilde{\psi} &= -{\rm i}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi}+S^{-1}\,P_\varphi\,\hat{\nabla}^4\!\left(\tilde{\phi} + \frac{\tilde{N}}{\tau}\right),\\[0.5ex]
--{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{N} &= -{\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\phi} - {\rm i}\!\left(\frac{\tau}{1+\tau}\right)\hat{d}_\beta^{\,2}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi} -{\rm i}\,c_\beta^2\,\hat{x}\,\tilde{V}\\[0.5ex]
+-{\rm i}\,(\omega-\omega_E-\omega_{\ast\,i})\,\tau_H\,\hat{\nabla}^2\tilde{\phi} &= -{\rm i}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi}+S^{-1}\,P_\varphi\,\hat{\nabla}^4\!\left(\tilde{\phi} + \frac{\tilde{N}}{\tau}\right),\\[0.5ex]
+-{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{N} &= -{\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\phi} - {\rm i}\!\left(\frac{\tau}{1+\tau}\right)\hat{d}_s^{\,2}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi} -{\rm i}\,c_\beta^2\,\hat{x}\,\tilde{V}\\[0.5ex]
 &\phantom{=}
@@
 Here, $Q=S^{\,1/3}\,\omega\,\tau_H$, $Q_E = S^{\,1/3}\,\omega_E\,\tau_H$, $Q_{e,i} = S^{\,1/3}\,\omega_{\ast\,e,i}\,\tau_H$,
-and $D = S^{\,1/3}\,[\tau/(1+\tau)]^{1/2}\,\hat{d}_\beta$. Note that the terms involving parallel transport have dropped out of
+and $D = S^{\,1/3}\,[\tau/(1+\tau)]^{1/2}\,\hat{d}_s$. Note that the terms involving parallel transport have dropped out of
 Equation~(\ref{e308}). The neglect of these terms is justified provided that the layer width is much less than the critical value,
@@
 \begin{equation}\label{e320}
-\frac{d}{dp}\!\left[G(p)\,\frac{dY}{dp}\right] - H(p)\,p^{2}\,Y = 0,
+\frac{d}{dp}\!\left[G(p)\,\frac{dY}{dp}\right] - \frac{A(p)}{B(p)}\,p^{2}\,Y = 0,
 \end{equation}
@@
 G(p)&= \frac{p^2}{-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e] + p^2},\\[0.5ex]
-H(p) &=\frac{A(p)}{B(p)},\\[0.5ex]
  A(p) &= -(Q-Q_E)\,(Q-Q_E-Q_i)-{\rm i}\,(Q-Q_E-Q_i)\,(P_\varphi+P_\perp)\,p^2 + P_\varphi\,P_\perp\,p^4,\\[0.5ex]
@@
 \end{equation}
+
 In the large-$p$ layer, for  $p\gg {\cal O}(Q^{1/2})$, we obtain 
 \begin{equation}\label{e329}
-\frac{d^{\,2} Y}{dp^2} - H(p)\,p^2\,Y\simeq 0,
+\frac{d^{\,2} Y}{dp^2} - \frac{A(p)}{B(p)}\,p^2\,Y\simeq 0,
 \end{equation}
@@
 This response regime is known as the {\em semi-collisional regime}\/ (Drake \& Lee 1977; Waelbroeck 2003). The characteristic
-layer width is $p_\ast\sim D\,Q^{-1/2}$. which implies that the regime is valid when $Q\ll D^4$,
+layer width is $p_\ast\sim D\,Q^{-1/2}$, which implies that the regime is valid when $Q\ll D^4$,
  $P\ll Q^2/D^2$, and $Q\ll D$.
@@
 \begin{equation}
-\frac{d}{dp}\!\left(p^2\,\frac{dY}{dp}\right)-(-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e])\,H(p)\,p^2\,Y=0.
+\frac{d}{dp}\!\left(p^2\,\frac{dY}{dp}\right)-(-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e])\,\frac{A(p)}{B(p)}\,p^2\,Y=0.
 \end{equation}
@@
 This response regime is known as the {\em visco-inertial regime}, because the layer response is dominated by
-viscosity and ion inertia (Fitzpatrick 1998). 
+perpendicular viscosity and ion inertia (Fitzpatrick 1998). 
  The characteristic layer width is $p_\ast \sim Q^{-1/4}\,P^{-1/4}$,
@@
 
+\subsection{Discussion}\label{dis1}
 Figures~\ref{f1} and \ref{f2} show the extents of the various different response regimes in the $Q$-$P$ plane for the
 cases $D<1$ and $D>1$, respectively.
+
+Let $\hat{\delta}\sim p_\ast^{-1}$ be the normalized radial thickness of the resonant layer.  Of course, the true thickness is
+$\delta = S^{-1/3}\,\hat{\delta}\,r_s$.  It follows from
+Equation~(\ref{e311}) that the relative change in the perturbed helical flux, $\tilde{\psi}$, across the layer
+is
+\begin{equation}
+\left.\frac{d\ln\tilde{\psi}}{dX}\right|_{-\hat{\delta}/2}^{+\hat{\delta}/2} = \hat{\mit\Delta}\,\,\hat{\delta}\sim \hat{\mit\Delta}\,\,p_\ast^{-1},
+\end{equation}
+According to the previous analysis, $\hat{\mit\Delta}\,p_\ast^{-1}$ takes the respective values $Q^{1/2}$, $Q\,P^{1/3}$, 
+$Q^2/D^2$, and $Q\,P^{1/2}/D$ in the resistive-inertial, visco-resistive, semi-collisional, and
+Hall-resistive response regimes. Moreover, it is clear from Figures~\ref{f1} and \ref{f2} that these values are all
+much less than unity. In other words, it is indeed the case that $\tilde{\psi}$ does not vary substantially across a
+`constant-$\psi$' resonant layer. On the other hand, $\hat{\mit\Delta}\,p_\ast^{-1}\sim 1$ in the inertial,
+visco-inertial, and Hall-viscous response regimes, which implies that $\tilde{\psi}$ does vary substantially
+across a `nonconstant-$\psi$' layer.
 
@@
 
-\subsection{Linear Dispersion Relation}
+\subsection{Linear Dispersion Relation}\label{s6.2}
 Let us write
-\begin{equation}
+\begin{equation}\label{e350}
 \omega = \gamma+{\rm i}\,\omega_r,
@@
 
-In a conventional tokamak plasma, $E_{ss}\sim {\cal O}(1)$,\footnote{Note that we are neglecting $m=1$ modes, for which $|E_{ss}|\gg 1$,
-because these are not really tearing modes
+In a conventional tokamak plasma, assuming that $m\sim {\cal O}(1)$, $E_{ss}\sim {\cal O}(1)$,\footnote{Note that we are neglecting $m=1$ modes, for which $|E_{ss}|\gg 1$,
+because such modes are not really tearing modes
 (Wesson 1978).} and $S^{1/3}\gg 1$. Hence, the previous dispersion relation can only be satisfied if $\omega_r$ takes a
@@
 rotates slightly faster than the electron fluid because of the influence of the thermal force, ${\bf F}_T$ [see Equation~(\ref{e43})],
-which generates the factor $\lambda_e$ in Equation~(\ref{e354}).}
-
-\subsection{Determination of Growth-Rates}
+which generates the additional  factor $\lambda_e$ in Equation~(\ref{e354}).}
+
+\subsection{Determination of Linear Growth-Rates}\label{s6.3}
 Reusing the analysis of Sections~\ref{s5.6} and \ref{scp}, there are two layers in $p$ space (i.e., Fourier space). The
@@
 \begin{equation}\label{e355}
-\frac{d^{\,2} Y}{dp^2} - \frac{A(p)}{C(p)} \,Y =0,
+\frac{d^{\,2} Y}{dp^2} - \frac{A(p)}{\tilde{B}(p)} \,Y =0,
 \end{equation}
@@
 A(p) &= (1+\lambda_e)\left(\frac{\tau}{1+\tau}\right)\left(1+ \frac{\lambda_e\,\tau}{1+\tau}\right)Q_\ast^{\,2}
-+{\rm i}\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)Q_\ast\,(P_\varphi+P_\perp)\,p^2\nonumber\\[0.5ex]
-&\phantom{=} + P_\varphi\,P_\perp\,p^4,\\[0.5ex]
-C(p)&= P_\perp - {\rm i}\,(1+\lambda_e)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)Q_\ast\,D^2 +\left(\frac{1+\tau}{\tau}\right)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right) D^2\,P_\varphi\,p^2.
+-{\rm i}\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)Q_\ast\,(P_\varphi+P_\perp)\,p^2\nonumber\\[0.5ex]
+\phantom{=} &+ P_\varphi\,P_\perp\,p^4,\\[0.5ex]
+\tilde{B}(p)&= P_\perp - {\rm i}\,(1+\lambda_e)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)Q_\ast\,D^2 +\left(\frac{1+\tau}{\tau}\right)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right) D^2\,P_\varphi\,p^2.
 \end{align}
@@
 \begin{equation}
-{\mit\Delta} = \pi\,\hat{\gamma}\,\frac{{\mit\Gamma}(1-\nu)}{{\mit\Gamma}(\nu)}\,\nu^{2\nu-1}\,C^\nu,
+\hat{\mit\Delta} = \pi\,\hat{\gamma}\,\frac{{\mit\Gamma}(1-\nu)}{{\mit\Gamma}(\nu)}\,\nu^{2\nu-1}\,C^{\,\nu},
 \end{equation}
@@
 
-As before, we shall assume that. $P_\varphi\sim P_\perp \sim P$, $\lambda_e\sim{\cal O}(1)$, and $\tau\sim {\cal O}(2)$, for
+As before, we shall assume that $P_\varphi\sim P_\perp \sim P$, $\lambda_e\sim{\cal O}(1)$, and $\tau\sim {\cal O}(1)$, for
 the sake of simplicity. 
@@
 \begin{equation}
-C = (1+\lambda_e)\left(\frac{\tau}{1+\tau}\right)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)\frac{Q_\ast}{P_\perp^{1/2}}.
+C = (1+\lambda_e)\left(\frac{\tau}{1+\tau}\right)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)\frac{Q_\ast^{2}}{P_\perp}.
 \end{equation}
@@
 \begin{equation}
-{\mit\Delta} = \pi\,\hat{\gamma}\left[ (1+\lambda_e)\left(\frac{\tau}{1+\tau}\right)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)\right]^{1/2}\,\frac{Q_\ast}{P_\perp^{1/2}},
-\end{equation}
-and $p_\ast\sim P^{1/2}/Q_\ast$. This so-called {\em resisrtive-inertial regime}\/ is valid when $P\ll Q_\ast^{3/2}$ and
+\hat{\mit\Delta} = \pi\,\hat{\gamma}\left[ (1+\lambda_e)\left(\frac{\tau}{1+\tau}\right)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)\right]^{1/2}\,\frac{Q_\ast}{P_\perp^{1/2}},
+\end{equation}
+and $p_\ast\sim P^{1/2}/Q_\ast$. This so-called {\em resistive-inertial regime}\/ is valid when $P\ll Q_\ast^{3/2}$ and
 $P\gg Q_\ast\,D^2$. 
 Making use of Equation~(\ref{e352}), the corresponding tearing mode growth-rate is
-\begin{equation}
+\begin{equation}\label{e363}
 \gamma = \frac{E_{ss}}{\pi\left[ (1+\lambda_e)\left(\frac{\tau}{1+\tau}\right)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)\right]^{1/2}\,}\,\frac{1}{\omega_\ast\,\tau_H\,\tau_R^{1/2}\,\tau_\perp^{1/2}}.
@@
 \begin{equation}
-{\mit\Delta} = \frac{6^{2/3}\,\pi\,\hat{\gamma}\, {\mit\Gamma}(5/6)}{\Gamma(1/6)}\,P_\varphi^{1/6}, 
+\hat{\mit\Delta} = 6^{2/3}\,\pi\,\hat{\gamma}\, \frac{{\mit\Gamma}(5/6)}{{\mit\Gamma}(1/6)}\,P_\varphi^{1/6}, 
 \end{equation}
@@
 The corresponding tearing mode growth-rate is
-\begin{equation}
-\gamma = \frac{E_{ss}}{6^{2/3}\,\pi\,[{\mit\Gamma}(5/6)/{\mit\Gamma}(1/6)]}\,\frac{\tau_\varphi^{1/6}}{\tau_R^{5/6}\,\tau_H^{1/3}}.
+\begin{equation}\label{e365}
+\gamma = \frac{E_{ss}}{6^{2/3}\,\pi\,[{\mit\Gamma}(5/6)/{\mit\Gamma}(1/6)]}\,\frac{\tau_\varphi^{1/6}}{\tau_H^{1/3}\,\tau_R^{5/6}}.
 \end{equation}
@@
 \begin{equation}
-{\mit\Delta} = \pi\,\hat{\gamma}\left(\frac{\tau}{1+\tau}\right)^{1/2}\,\frac{Q_\ast^{1/2}}{D},
+\hat{\mit\Delta} = {\rm e}^{{\rm i}\,\pi/4}\,\pi\,\hat{\gamma}\left(\frac{\tau}{1+\tau}\right)^{1/2}\,\frac{Q_\ast^{1/2}}{D},
 \end{equation}
@@
 The corresponding tearing mode growth-rate is
-\begin{equation}
-\gamma = \frac{E_{ss}\,{\rm e}^{-{\rm i}\,\pi/4}}{\pi}\,\frac{d_\beta/r_s}{\omega_\ast^{1/2}\,\tau_H\,\tau_R^{1/2}}.
-\end{equation}
+\begin{equation}\label{e368}
+\gamma = \frac{E_{ss}}{\sqrt{2}\,\pi}\,\frac{d_s/r_s}{\omega_\ast^{1/2}\,\tau_H\,\tau_R^{1/2}}.
+\end{equation}
+Here, we have neglected the imaginary component of $\gamma$ because it merely gives rise to a small correction to the
+propagation frequency of the mode.
 
@@
 \begin{equation} 
-\hat{\Delta} = 2\pi\,\hat{\gamma}\,\frac{{\mit\Gamma}(3/4)}{\Gamma(1/4)}\,\frac{[\tau/(1+\tau)]^{1/4}\,P_\perp^{1/4}}{[1+\lambda_e\,\tau/(1+\tau)]^{1/4}\,D^{1/2}},
+\hat{\mit\Delta} = 2\pi\,\hat{\gamma}\,\frac{{\mit\Gamma}(3/4)}{{\mit\Gamma}(1/4)}\,\frac{[\tau/(1+\tau)]^{1/4}\,P_\perp^{1/4}}{[1+\lambda_e\,\tau/(1+\tau)]^{1/4}\,D^{1/2}},
 \end{equation}
 and $p_\ast \sim D^{1/2}/P^{1/4}$. This so-called {\em Hall-resistive regime}\/ is valid when $P\gg Q_\ast^2/D^2$ and
-$P\ll D^6$. The corresponding tearing mode growth rate is 
-\begin{equation}
-\gamma= \frac{E_{ss}}{2\pi\,[{\mit\Gamma}(3/4)/{\mit\Gamma}(1/4)]\,[1+\lambda_e\,\tau/(1+\tau)]^{-1/4}}\,\frac{(d_\beta/r_s)^{1/4}\,\tau_\perp^{1/4}}{\tau_H^{1/3}\,\tau_R^{11/12}}.
-\end{equation}
-
-\subsection{Discussion}
+$P\ll D^6$. The corresponding tearing mode growth-rate is 
+\begin{equation}\label{e371}
+\gamma= \frac{E_{ss}}{2\pi\,[{\mit\Gamma}(3/4)/{\mit\Gamma}(1/4)]\,[1+\lambda_e\,\tau/(1+\tau)]^{-1/4}}\,\frac{(d_s/r_s)^{1/2}\,\tau_\perp^{1/4}}{\tau_H^{1/4}\,\tau_R^{3/4}}.
+\end{equation}
 
@@
 \caption{Linear tearing mode growth-rate regimes  in $Q_\ast$-$P$ space for the case $D=1$. The various regimes are
-the Hall-resisitive (HR), the semi-collisional (SC),  the visco-resistive (VR), and the resistive-inertia (RI).}\label{f3}
+the Hall-resisitive (HR), the semi-collisional (SC),  the visco-resistive (VR), and the resistive-inertial (RI).}\label{f3}
 \end{figure}
+
+\subsection{Discussion}
+According to Equations~(\ref{e350}), (\ref{e353}), (\ref{e363}), (\ref{e365}), (\ref{e368}), and (\ref{e371}), a linear tearing mode is unstable when the tearing stability index, $E_{ss}$, is positive, and is stable otherwise (Furth, et al.\ 1963).
+Moreover, the perturbed magnetic field associated with the mode corotates with the electron fluid at the resonant surface (Ara, et al.\ 1978). Finally,
+the mode grows on a hybrid timescale that is much greater than the hydrodynamical timescale, $\tau_H$,
+but much less than the resistive evolution timescale, $\tau_R$.
+
+There are three main factors that
+affect the growth-rate of a tearing mode in a conventional tokamak plasma. First, the strength of diamagnetic flows in the plasma, which is parameterized by the
+diamagnetic frequency, $\omega_\ast$ (and by the normalized diamagnetic frequency, $Q_\ast$).
+Second, the  anomalous perpendicular diffusion of momentum and particles, which is parameterized by the momentum and particle confinement
+timescales, $\tau_\varphi$ and $\tau_\perp$ (and by the magnetic Prandtl number, $P$). Third, the
+finite gyroradii of ions, which is parameterized by the modified ion sound radius, $d_s$ (and by the normalized
+sound radius $D$).
+
+ There are four growth-rate regimes---the resistive-inertial, the visco-resistive, the semi-collisional, and the Hall-resistive---and their extents in $Q_\ast$-$P$-$D$ space are illustrated in Figure~\ref{f3}.
+Note that Figure~\ref{f3} differs somewhat from Figures~\ref{f1} and \ref{f2} because in the latter two
+figures it was assumed that $|Q-Q_E-(1+\lambda_e)\,Q_e|\sim |Q-Q_E|\sim |Q-Q_E-Q_i|$ whereas
+in the former figure it was assumed that $|Q-Q_E-(1+\lambda_e)\,Q_e|\ll |Q-Q_E|\sim |Q-Q_E-Q_i|$.
+This refined ordering eliminates the nonconstant-$\psi$ response regimes, and significantly modifies the
+resistive-inertial response regime.
+
+The absence of nonconstant-$\psi$ response regimes in Figure~\ref{f3}
+should come as no surprise. As we saw in Section~\ref{dis1}, nonconstant-$\psi$ resonant layers
+are characterized by $\hat{\mit\Delta}\sim\hat{\delta}^{-1}= S^{-1/3}\,(r_s/\delta)$, where $\delta$
+is the layer thickness. Hence, according to Equation~(\ref{e352}), asymptotic matching of such a
+layer to the outer solution is only possible if $|E_{ss}|\sim r_s/\delta \gg 1$ (given that resonant
+layers in tokamak plasmas are invariably very thin compared to the minor radius of the plasma). However,
+low-$m$ tearing modes in conventional tokamak plasmas are characterized by $|E_{ss}|\sim 1$ rather than
+$|E_{ss}|\gg 1$. (As before, we are neglecting $m=1$ modes, which are characterized by
+$|E_{ss}|\gg 1$, because they are not really tearing modes.)
+
+Diamagnetic flows modify the tearing mode growth-rate in the resistive-inertial and semi-collisional
+growth-rate regimes, but not in the Hall-resistive and visco-resistive regimes. Anomalous perpendicular
+transport modifies the growth-rate in all regimes except the semi-collisional regime. Finally, finite ion gyroradius
+effects modify the growth-rate in the Hall-resistive and semi-collisional regimes, but not in the other two
+regimes.
+
+Increasing  the diamagnetic flow strength decreases the tearing mode growth-rate such that it
+eventually scales as $\omega_\ast^{-1/2}$. Increasing the anomalous perpendicular transport increases the
+growth-rate such that it  eventually scales as $P_\varphi^{1/6}$. Increasing the ion gyroradius
+increases the tearing mode growth-rate, but the increase eventually saturates (i.e., the
+growth-rate ends up scaling as $d_s^{\,0}$).
+
+Finally, it is clear from Equation~(\ref{e352}) that the layer solution can only be matched to the
+outer solution when $\omega_r$ takes a value that renders $|\hat{\mit\Delta}|\ll 1$. We have seen that this
+is possible in all constant-$\psi$ response regimes when $\omega_r= \omega_E+(1+\lambda_e)\,\omega_{\ast\,e}$
+(i.e., when the tearing perturbation corotates with the electron fluid at the resonant surface.) However, Equation~(\ref{ri})
+seems to suggest that in the resistive-inertial regime it might be possible to successfully match the
+layer solution to the outer solution when $\omega_r=\omega_E$, or when $\omega_r=\omega_E+\omega_{\ast\,i}$,
+giving tearing mode perturbations that corotate with the MHD fluid and the ion fluid, respectfully, at the resonant
+surface.
+In fact, we can see that this is not the case, because if we set $\omega_r=\omega_E$, or $\omega_r=\omega_E+\omega_{\ast\,i}$,  then Equation~(\ref{e329}) does not lead to a layer solution characterized by  $|\hat{\mit\Delta}|\ll 1$,
+as a consequence of finite anomalous perpendicular transport. Likewise, Equation~(\ref{sc}) seems to suggest that in the semi-collisional response regime it might be possible to successfully match the
+layer solution to the outer solution when $\omega_r=\omega_E$, giving rise to a tearing perturbation that corotates with the MHD fluid at the resonant surface.
+In fact, this possibility is also ruled out by finite anomalous
+perpendicular transport.
 
@@
 \item Chapman, S., and Cowling, T.G.\ 1953. {\em The Mathematical Theory of Non-Uniform Gases}. Cambridge University Press.
-\item Chen, X.L.\ and Morrison, P.J.\ 1990. {\em Resistive Tearing Instability with Equilibrium Shear Flow}. Phys.\ Plasmas {\bf 2}, 495. 
-\item Cole, A.\ and Fitzpatrick, R.\ 2006. {\em Drift-Magnetohydrodynamical Model of Error-Field Penetration in Tokamak
+\item Chen, X.L., and Morrison, P.J.\ 1990. {\em Resistive Tearing Instability with Equilibrium Shear Flow}. Phys.\ Plasmas {\bf 2}, 495. 
+\item Cole, A., and Fitzpatrick, R.\ 2006. {\em Drift-Magnetohydrodynamical Model of Error-Field Penetration in Tokamak
 Plasmas}. Phys.\ Plasmas {\bf 13}, 032503. 
-\item Drake, J.F.\ and Lee, Y.C.\ 1977. {\em Kinetic Theory of Tearing Instabilities}. Phys.\ Fluids {\bf 20}, 1341.
+\item Drake, J.F., and Lee, Y.C.\ 1977. {\em Kinetic Theory of Tearing Instabilities}. Phys.\ Fluids {\bf 20}, 1341.
 \item Fitzpatrick, R.\ 1993. {\em Interaction of Tearing Modes with External Structures in Cylindrical Geometry}. Nucl.\ Fusion {\bf 33}, 1049. 
@@
 \item Fitzpatrick, R.\ 2015. {\em Plasma Physics: An Introduction}. Taylor \& Francis, CRC Press. 
-\item Fitzpatrick, R.\ and Hender, T.C.\ 1994. {\em Effect of a Static External Magnetic Perturbation on Resistive Mode Stability in Tokamaks}. Phys.\ Plasmas {\bf 1}, 3337. 
-\item Fitzpatrick, R.\ and Waelbroeck, F.L.\ 2005. {\em Two-Fluid Magnetic Island Dynamics in Slab Geometry. I. Isolated Islands}.
+\item Fitzpatrick, R., and Hender, T.C.\ 1994. {\em Effect of a Static External Magnetic Perturbation on Resistive Mode Stability in Tokamaks}. Phys.\ Plasmas {\bf 1}, 3337. 
+\item Fitzpatrick, R., and Waelbroeck, F.L.\ 2005. {\em Two-Fluid Magnetic Island Dynamics in Slab Geometry. I. Isolated Islands}.
 Phys.\ Plasmas {\bf 12}, 022307. 
-\item Fitzpatrick, R.\ and Waelbroeck, F.L.\ 2009. {\em Effect of Flow Damping on Drift-Tearing Magnetic Islands in Tokamak Plasmas}.
+\item Fitzpatrick, R., and Waelbroeck, F.L.\ 2009. {\em Effect of Flow Damping on Drift-Tearing Magnetic Islands in Tokamak Plasmas}.
 Phys.\ Plasmas {\bf 16}, 072507.

### 2021-11-13 Documentation/TearingModeTheory.tex
Finished error field penetration section

@@
 \author{R.~Fitzpatrick\,\footnote{rfitzp@utexas.edu}\\
-Institute for Fusion Studies,\\  Department of Physics,\\  University of Texas at Austin,\\  Austin TX 78712, USA}
+Institute for Fusion St udies,\\  Department of Physics,\\  University of Texas at Austin,\\  Austin TX 78712, USA}
+\date{}
 \maketitle
 
+\tableofcontents
+
+\newpage
 \section{Introduction}
@@
 corresponding mean-free-paths between $90^\circ$ collisional scattering events. In this limit, a standard two-Laguerre-polynomial
-Chapman-Enskog closure scheme (Chapman \& Cowling 1953) yields
+Chapman-Enskog closure scheme (Chapman \& Cowling 1953; Braginskii 1965) yields
 \begin{align}\label{e3.91a}
@@
 
-In a highly magnetized plasma, the viscosity tensor is best described as the
+In a highly magnetized plasma, the viscosity tensor is conveniently  described as the
 sum of  five component tensors,
@@
 Let $\bar{n}$, $\bar{v}_e$, $\bar{\tau}_e$, $\bar{l}_e=\bar{v}_e\,\bar{\tau}_e$, $\bar{B}$,
-and $\bar{\rho}_e =\bar{ v}_e/(e\bar{B}/m_e)$,  be typical values
+and $\bar{\rho}_e =\bar{ v}_e/(e\bar{B}/m_e)$  be typical values
 of the particle density, the electron thermal velocity, the electron collision time, the electron
@@
 electron equations. Let  $\bar{n}$, $\bar{v}_i$, $\bar{l}_i$, $\bar{B}$,
-and $\bar{\rho}_i =\bar{ v}_i/(e\bar{B}/m_i)$,  be typical values
+and $\bar{\rho}_i =\bar{ v}_i/(e\bar{B}/m_i)$  be typical values
 of the particle density, the ion  thermal velocity, the ion
@@
 At the resonant surface, ${\bf k}\cdot{\bf B}=0$, where ${\bf k} = (0,\,m/r,\,-n/R_0)$ is the wavevector of the tearing perturbation. 
-The value of $\psi(r,t)$ at the resonant surface---namely, ${\mit\Psi}_s(t)$---is known as the {\em reconnected magnetic flux}\/ (Fitzpatrick 1993). 
+The value of $\psi(r,t)$ at the resonant surface---namely, ${\mit\Psi}_s(t)$---is known as the {\em reconnected magnetic flux}\/ (Fitzpatrick 1993). (See Section~\ref{dis1}.)
 Note that ${\mit\Psi}_s$ is, in general, a complex quantity. 
@@
 \end{equation}
-where $E_{ss}= {\mit\Delta}_{s+}-{\mit\Delta}_{s-}$ is a real quantity that is known as the {\em tearing stability index}\/ (Furth, et al.\ 1963).
+where $E_{ss}= {\mit\Delta}_{s+}-{\mit\Delta}_{s-}$ is a real dimensionless quantity that is known as the {\em tearing stability index}\/ (Furth, et al.\ 1963).
 
@@
 \end{equation}
-where the real function $\hat{\psi}_s(r)$ is specified in the previous section, and the real function  $\hat{\psi}_w(r)$ is a solution of 
+where the real function $\hat{\psi}_s(r)$ is specified in Section~\ref{perfect}, and the real function  $\hat{\psi}_w(r)$ is a solution of 
 \begin{equation}\label{e100a}
@@
 
-\subsection{Resistive Wall Physics}
+\subsection{Resistive Wall Physics}\label{tauw}
 It is clear from Equation~(\ref{e93}) that
@@
 \begin{equation}\label{e134}
-{\mit\Delta\Psi}_s = \tau_s\left(\frac{d{\mit\Psi}_s}{dt} + {\rm i}\,\varpi_s\,{\mit\Psi}_s\right).
+{\mit\Delta\Psi}_s = \tau_s\left(\frac{d{\mit\Psi}_s}{dt} + {\rm i}\,\omega_s\,{\mit\Psi}_s\right).
 \end{equation}
 Here, $\tau_s$ is the {\em reconnection time}\/ (i.e., the typical timescale on which magnetic reconnection takes place in the
-resonant layer surrounding the resonant surface), whereas $\varpi_s$ is the so-called {\em natural frequency}. 
+resonant layer surrounding the resonant surface), whereas $\omega_s$ is the so-called {\em natural frequency}. 
 The natural frequency is the phase velocity of the tearing mode when the wall is perfectly conducting. The
 natural frequency is non-zero because the reconnected flux in the resonant layer is convected by the local plasma
-flow (Fitzpatrick 1993).
-
-\subsection{Solution in Presence of External Magnetic Field-Coil}
+flow (Fitzpatrick 1993). (See Section~\ref{s6.2}.)
+
+\subsection{Solution in Presence of External Magnetic Field-Coil}\label{sfc}
 Suppose that the perfectly-conducting wall at $r=r_c$ is replaced by a radially-thin, magnetic field-coil that carries a
@@
 \end{equation}
-Here, $\rho(r)$ is the equilibrium plasma mass density profile, $\tau_\theta(r)$ is the {\em poloidal flow-damping time}\/ (which
-is generally of order $\tau_i$), ${\mit\Omega}_{\theta\,{\rm nc}}(r)$ is the neoclassical poloidal angular velocity profile, and
+Here, $\rho(r)$ is the equilibrium plasma mass density profile, $\tau_\theta(r)$ is the {\em poloidal flow-damping time}\/ [which
+is generally of order $(a/q\,R_0)^2\,\tau_i$], ${\mit\Omega}_{\theta\,{\rm nc}}(r)$ is the neoclassical poloidal angular velocity profile, and
 $\mu_\perp(r)$ is a phenomenological perpendicular viscosity due to plasma turbulence.
@@
 \begin{align}\label{e188}
-4\pi^2\,R_0\left[(1+2\,q_s^{\,2})\,\rho_s\,r^{\,3}\,\frac{\partial {\mit\Delta\Omega}_\theta}{\partial t}+ \frac{\rho_s}{\tau_{\theta\,s}}\,r^{\,3}\,{\mit\Delta\Omega}_\theta-\mu_{\perp,s}\frac{\partial}{\partial r}\!\left(r^{\,3}\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial r}\right)\right]
+4\pi^2\,R_0\left[(1+2\,q_s^{\,2})\,\rho_s\,r^{\,3}\,\frac{\partial {\mit\Delta\Omega}_\theta}{\partial t}+ \frac{\rho_s}{\tau_{\theta\,s}}\,r^{\,3}\,{\mit\Delta\Omega}_\theta-\mu_{\perp\,s}\frac{\partial}{\partial r}\!\left(r^{\,3}\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial r}\right)\right]
 &=T_{\theta\,s}\,\delta(r-r_s),\\[0.5ex]
@@
 \begin{align}
-y_p(r) &= \frac{J_1(j_{1\,p}\,r/a)}{r/a},\\[0.5ex]
+y_p(r) &= \frac{J_1(j_{1\,p}\,r/a)}{r/a},\label{e193}\\[0.5ex]
 z_p(r) &= J_0(j_{0\,p}\,r/a).\label{e194}
 \end{align}
-Here, $J_m(z)$ is a Bessel function, and $j_{m,p}$ denotes its $p$th zero. Note that
+Here, $J_m(z)$ is a Bessel function, and $j_{m\,p}$ denotes its $p$th zero. Note that
 Equations~(\ref{e190})--(\ref{e194}) automatically satisfy the boundary conditions (\ref{e186}) and (\ref{e187}).
@@
 \begin{align}\label{e198}
-(1+2\,q_k^{\,2})\,\frac{d\alpha_p}{dt} + \left(\frac{1}{\tau_{\theta\,s}}+\frac{j_{1,p}^{\,2}}{\tau_{M}}\right)\alpha_p
-&= \frac{m^{2}\,[y_p(r_s/a)]^{\,2}}{\tau_A^{\,2}\,\epsilon_a^{\,2}\,[J_2(j_{1,p})]^{\,2}}\,
+(1+2\,q_s^{\,2})\,\frac{d\alpha_p}{dt} + \left(\frac{1}{\tau_{\theta\,s}}+\frac{j_{1\,p}^{\,2}}{\tau_{M}}\right)\alpha_p
+&= \frac{m^{2}\,[y_p(r_s/a)]^{\,2}}{\tau_A^{\,2}\,\epsilon_a^{\,2}\,[J_2(j_{1\,p})]^{\,2}}\,
 {\rm Im}({\mit\Delta\hat{\Psi}_s}\,\hat{\mit\Psi}_s^{\,\ast}),\\[0.5ex]
-\frac{d\beta_p}{dt} + \frac{j_{0,p}^{\,2}}{\tau_{M}}\,\beta_p
-&= \frac{n^{2}\,[z_p(r_s/a)]^{\,2}}{\tau_A^{\,2}\,[J_1(j_{0,p})]^{\,2}}\,
+\frac{d\beta_p}{dt} + \frac{j_{0\,p}^{\,2}}{\tau_{M}}\,\beta_p
+&= \frac{n^{2}\,[z_p(r_s/a)]^{\,2}}{\tau_A^{\,2}\,[J_1(j_{0\,p})]^{\,2}}\,
 {\rm Im}({\mit\Delta\hat{\Psi}_s}\,\hat{\mit\Psi}_s^{\,\ast}).\label{e199}
 \end{align}
-Here, $\tau_{M} =\rho_s\,a^{\,2}/\mu_s$ is the {\em momentum confinement time}, $\tau_A = (\mu_0\,\rho_s\,a^{\,2}/B_z^{\,2})^{1/2}$ is the {\em Alfv\'{e}n time}, $\epsilon_a=a/R_0\ll 1$ is the {\em inverse aspect-ratio}\/ of the plasma,
-${\mit\Delta\Psi}_s = R_0\,B_z\,{\mit\Delta\hat{\Psi}}_s$, and ${\mit\Psi}_s = R_0\,B_z\,\hat{\mit\Psi}_s$. Moreover,
+Here, 
+\begin{equation}
+\tau_{M} =\frac{\rho_s\,a^{\,2}}{\mu_{\perp\,s}},
+\end{equation} 
+is the {\em momentum confinement time}, 
+\begin{equation}
+\tau_A = \left(\frac{\mu_0\,\rho_s\,a^{\,2}}{B_z^{\,2}}\right)^{1/2}
+\end{equation}
+ is the {\em Alfv\'{e}n time}, 
+ \begin{equation}
+ \epsilon_a=\frac{a}{R_0}\ll 1
+ \end{equation}
+ is the {\em inverse aspect-ratio}\/ of the plasma, and
+ \begin{align}
+{\mit\Delta\hat{\Psi}}_s &=\frac{{\mit\Delta\Psi}_s}{R_0\,B_z},\\[0.5ex]
+ \hat{\mit\Psi}_s &=\frac{{\mit\Psi}_s}{R_0\,B_z}.
+ \end{align}
+  Moreover,
 use has been made of Equations~(\ref{e157}), (\ref{e158}), and (\ref{e190})--(\ref{e197}).
 
-\subsection{No-Slip Constraint}
+\subsection{No-Slip Constraint}\label{sns}
 The reconnected magnetic flux at the resonant surface is assumed to convected by the local plasma flow. (See Section~\ref{sres}.) Hence, changes in the
@@
 surface will modify the convection velocity. Consequently, the natural frequency of the reconnected flux can be written
-\begin{equation}
- \varpi_s(t) = \varpi_{s\,0} + ({\bf k}\cdot {\mit\Delta}{\bf V}_i)_{r=r_s}=
- \varpi_{s\,0} + m\,{\mit\Delta\Omega}_\theta(r_s,t) - n\,{\mit\Delta\Omega}_\varphi(r_s,t),
-\end{equation}
-where $\varpi_{s\,0}$ is the unperturbed natural frequency.
+\begin{equation}\label{e200}
+ \omega_s(t) = \omega_{s\,0} + ({\bf k}\cdot {\mit\Delta}{\bf V}_i)_{r=r_s}=
+ \omega_{s\,0} + m\,{\mit\Delta\Omega}_\theta(r_s,t) - n\,{\mit\Delta\Omega}_\varphi(r_s,t),
+\end{equation}
+where $\omega_{s\,0}$ is the unperturbed natural frequency.
 The previous expression is known as the {\em no-slip constraint}\/ (Fitzpatrick 1993), and has been verified experimentally (Vahala, et al.\ 1980).
@@
 \begin{equation}\label{e201}
-\varpi_s(t) = \varpi_{s\,0} - \sum_{p=1,\infty}\left[\alpha_p(t)+\beta_p(t)\right].
-\end{equation}
+\omega_s(t) = \omega_{s\,0} - \sum_{p=1,\infty}\left[\alpha_p(t)+\beta_p(t)\right].
+\end{equation}
+(See Section~\ref{stb}.)
 
@@
 \begin{align}\label{e202}
-\tau_s\left(\frac{d\hat{\mit\Psi}_s}{dt} + {\rm i}\,\varpi_s\,\hat{\mit\Psi}_s\right) &= E_{ss}\,\hat{\mit\Psi}_s + E_{sw}\,\hat{\mit\Psi}_w,\\[0.5ex]
+{\mit\Delta\hat{\Psi}}_s\equiv \tau_s\left(\frac{d\hat{\mit\Psi}_s}{dt} + {\rm i}\,\omega_s\,\hat{\mit\Psi}_s\right) &= E_{ss}\,\hat{\mit\Psi}_s + E_{sw}\,\hat{\mit\Psi}_w,\\[0.5ex]
 \tau_w\,\frac{d\hat{\mit\Psi}_w}{dt} &= E_{sw}\,\hat{\mit\Psi}_s +\tilde{E}_{ww}\,\hat{\mit\Psi}_w
-+\hat{I}_c,\\[0.5ex]
-\varpi_s(t)& = \varpi_{s\,0} - \sum_{p=1,\infty}\left[\alpha_p(t)+\beta_p(t)\right],\\[0.5ex]
-(1+2\,q_k^{\,2})\,\frac{d\alpha_p}{dt} + \left(\frac{1}{\tau_{\theta\,s}}+\frac{j_{1,p}^{\,2}}{\tau_{M}}\right)\alpha_p
-&= \frac{m^{2}\,[y_p(r_s/a)]^{\,2}}{\tau_A^{\,2}\,\epsilon_a^{\,2}\,[J_2(j_{1,p})]^{\,2}}
-\,E_{sw}\,{\rm Im}(\hat{\mit\Psi}_w\,\hat{\mit\Psi}_s^{\,\ast}),\\[0.5ex]
-\frac{d\beta_p}{dt} + \frac{j_{0,p}^{\,2}}{\tau_{M}}\,\beta_p
-&= \frac{n^{2}\,[z_p(r_s/a)]^{\,2}}{\tau_A^{\,2}\,[J_1(j_{0,p})]^{\,2}}\,
-E_{sw}\,{\rm Im}(\hat{\mit\Psi}_w\,\hat{\mit\Psi}_s^{\,\ast}).\label{e206}
++\hat{I}_c,\label{e203}\\[0.5ex]
+\omega_s(t)& = \omega_{s\,0} - \sum_{p=1,\infty}\left[\alpha_p(t)+\beta_p(t)\right],\\[0.5ex]
+(1+2\,q_s^{\,2})\,\frac{d\alpha_p}{dt} + \left(\frac{1}{\tau_{\theta\,s}}+\frac{j_{1\,p}^{\,2}}{\tau_{M}}\right)\alpha_p
+&= \frac{m^{2}\,[y_p(r_s/a)]^{\,2}}{\tau_A^{\,2}\,\epsilon_a^{\,2}\,[J_2(j_{1\,p})]^{\,2}}
+\,{\rm Im}({\mit\Delta\hat{\Psi}}_s\,\hat{\mit\Psi}_s^{\,\ast}),\label{e205}\\[0.5ex]
+\frac{d\beta_p}{dt} + \frac{j_{0\,p}^{\,2}}{\tau_{M}}\,\beta_p
+&= \frac{n^{2}\,[z_p(r_s/a)]^{\,2}}{\tau_A^{\,2}\,[J_1(j_{0\,p})]^{\,2}}\,
+{\rm Im}({\mit\Delta\hat{\Psi}}_s\,\hat{\mit\Psi}_s^{\,\ast}).\label{e206}
 \end{align}
@@
 \begin{align}
-\hat{I}_c &= \frac{\mu_0\,I_c}{R_0\,B_z}\left(\frac{r_w}{r_c}\right)^m,\\[0.5ex]
+\hat{I}_c &= \left(\frac{r_w}{r_c}\right)^m\frac{\mu_0\,I_c}{R_0\,B_z},\\[0.5ex]
 \tilde{E}_{ww} &= E_{ww} + \frac{2m\,(r_w/r_c)^{2m}}{1-(r_w/r_c)^{2m}}.\label{e208}
@@
 Equations~(\ref{e202})--(\ref{e206}) contain two quantities---namely, the reconnection time, $\tau_s$, and the unperturbed
-natural frequency, $\varpi_{s\,0}$---that can only be determined by solving for the plasma response in the radially thin resonant layer surrounding the resonant surface.
+natural frequency, $\omega_{s\,0}$---that can only be determined by solving for the plasma response in the radially-thin resonant layer surrounding the resonant surface.
 Unfortunately, determining the resonant plasma response is not a straightforward task.
@@
 {\bf V}_e &= {\bf V} +{\bf V}_{\ast\,i}-\frac{{\bf j}}{n_0\,e},\\[0.5ex]
-{\bf V}_i &= {\bf V} + {\bf V}_{\ast\,i}.
+{\bf V}_i &= {\bf V} + {\bf V}_{\ast\,i}.\label{e219}
 \end{align}
@@
 resistivities,  respectively. (See Section~\ref{sbrag}.) We have neglected the cross term in Equation~(\ref{e3.91a})
-because it is a factor $({\mit\Omega}_e\,\tau_e)^{-1}$  smaller than $\nabla p$.
+because it is a factor $({\mit\Omega}_e\,\tau_e)^{-1}$  smaller than $\nabla p$. Incidentally, if we assume that all
+flow velocities are similar in magnitude to the diamagnetic velocity then the neglect of
+electron inertia and electron viscosity in the previous equation is justified because the corresponding terms are factors
+$(\rho_e/r_s)^2$ and $({\mit\Omega}_e\,\tau_e)\,(\rho_e/r_s)^2$, respectively, smaller than the leading order terms
+in the equation.
 
@@
 For the moment, we are neglecting the contribution of the parallel viscosity tensor.
+The neglect of electron inertia and electron viscosity in the previous equation is justified because
+the corresponding terms are factors $m_e/m_i$ and $(m_e/m_i)^{1/2}$, respectively, smaller than the leading order
+terms in the equation.
 
@@
 
-Equations~(\ref{e220})--(\ref{e223}) are known collectively as the {\em drift-MHD equations}, and contain both shear-Alfv\'{e}n
-and compressible-Alfv\'{e}n wave dynamics. The system of equations is completed by Maxwell's equations:
+Equations~(\ref{e220})--(\ref{e223}) are known collectively as the {\em drift-MHD equations},\footnote{The 'drift' appellation  merely indicates that we are taking diamagnetic flows into account.} and contain both shear-Alfv\'{e}n
+and compressible-Alfv\'{e}n wave dynamics. The system of equations is completed by a subset of Maxwell's equations:
 \begin{align}
@@
 \end{equation}
-Note that $d_i=c/\omega_{p\,i}$, where $c$ is the velocity of light, and $\omega_{p\,i}$ is the ion plasma
+Note that $d_i=c/\omega_{p\,i}$, where $c$ is the velocity of light in vacuum, and $\omega_{p\,i}$ is the ion plasma
 frequency (Fitzpatrick 2015).
@@
 \subsection{Reduction Process} 
-All variables in the resonant layer are assumed to be functions of $\hat{x}=(r-r_s)/l$ and $\zeta=m\,\theta-n\,\varphi$ only. 
-Let ${\bf n} = (0,\,\epsilon/q_s,\,1)$, where $\epsilon=r/R_0$ and $q_s=m/n$. It follows that ${\bf n}\cdot\nabla A=0$ for any $A(\hat{x},\zeta)$. 
+All variables in the resonant layer are assumed to be functions of 
+$\hat{x}=(r-r_s)/l$,
+ and 
+ \begin{equation}
+ \zeta=m\,\theta-n\,\varphi
+ \end{equation}
+ only. 
+Let ${\bf n} = (0,\,\epsilon/q_s,\,1)$, where $\epsilon=r/R_0$ and 
+\begin{equation}
+q_s=q(r_s)= \frac{m}{n}.
+\end{equation}
+ It follows that ${\bf n}\cdot\nabla A=0$ for any $A(\hat{x},\zeta)$. 
 Let us write (Fitzpatrick \& Waelbroeck 2009)
@@
 which automatically satisfies Equation~(\ref{e230}).
-(Recall that we are assuming that $|r-r_s|\ll r_s$ inside the resonant layer.) Note that $\hat{\psi}=\psi/r_s$, where $\psi$ is defined in Equation~(\ref{e93}).
+(Recall that we are assuming that $|r-r_s|\ll r_s$ inside the resonant layer.) Note that $\hat{\psi}=\psi/(r_s\,B_z)$, where $\psi$ is defined in Equation~(\ref{e93}).
  Here, $\delta b(\hat{x},\zeta)$ and $\hat{\psi}(\hat{x},\zeta)$ are assumed to be small
@@
  \end{align}
- with $R_0=R_0/l$. 
+ with $\hat{R}_0=R_0/l$. 
  Here, $\hat{d}_i$ and $\beta$ are assumed to be zeroth order in small quantities, $J$, $1/\hat{R}_0$, $\hat{\eta}_\parallel$, and $\hat{\eta}_\perp$ are assumed to be first order, while $\hat{\nabla}\cdot \hat{\bpi}_{i}$ and $\hat{\nabla}\cdot\hat{\bf q}$ are assumed to be second order.
@@
 \end{align}
+(Here, we are neglecting any $\hat{x}$ dependence of the various $\chi$ parameters for ease of notation.)
 
@@
 \begin{align}
-\hat{D}_\parallel&= \frac{2}{3}\,(1-c_\beta^{\,2})\!\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\parallel\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\parallel\,i}\right),\\[0.5ex]
-\hat{D}_\perp &= c_\beta^{\,2}\,\hat{\eta}_\perp +  \frac{2}{3}\,(1-c_\beta^{\,2})\!\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\perp\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\perp\,i}\right).
+\hat{D}_\parallel&= \frac{2}{3}\left(1-c_\beta^{\,2}\right)\!\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\parallel\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\parallel\,i}\right),\\[0.5ex]
+\hat{D}_\perp &= c_\beta^{\,2}\,\hat{\eta}_\perp +  \frac{2}{3}\left(1-c_\beta^{\,2}\right)\!\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\perp\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\perp\,i}\right).
 \end{align}
@@
 
+Strictly speaking, the analysis
+presented in this section is only valid when the ion gyroradius is smaller than the typical variation lengthscale in the resonant layer. 
+If this is not the case then it is necessary to adopt a so-called {\em gyrofluid}\/ approach in which the ion response is
+averaged over the ion gyro-orbits (Cowley, Kulsrud \& Hahm 1986; Hammett, Dorland \& Perkins 1992; Waelbroeck, Hazeltine \& Morrison 2009).
+Of course, if the ions are cold (i.e., $T_i\ll T_e$) then the ion gyroradius tends to zero,  which means that the
+analysis is valid. 
+Note, however, that the ion sound radius is finite even when the ions are cold. In the following, we shall assume that the
+analysis is valid even when the ions are hot.
+
 If we neglect $\hat{d}_\beta$ in our reduced drift-MHD model, which is equivalent to saying that the ion sound
@@
 N &= \frac{p-p_0}{c_\beta\,B_z^{\,2}/\mu_0},\\[0.5ex]
-V &= \frac{{\bf n}\cdot {\bf V}}{V_A},
-\end{align}
-where  ${\bf V}$ is the MHD velocity defined in Equation~(\ref{e217}),  $p$ is the total plasma pressure, $p_0$ is defined in Equation~(\ref{e210}), $V_A$ is the
-Alfv\'{e}n speed defined in Equation~(\ref{e226a}), and $c_\beta$ is defined in Equations~(\ref{e244}) and (\ref{e257}). Our
-model also employs the auxiliary fields $J=-2\,\epsilon_s/q_s+r_s^2\,\nabla^2 \hat{\psi}$ and  $U=r_s^2\,\nabla^2 \phi$. Here, $\epsilon_s=r_s/R_0$.
+V &= \frac{{\bf n}\cdot {\bf V}}{V_A}.
+\end{align}
+ Our
+model also employs the auxiliary fields $J=-2\,\epsilon_s/q_s+r_s^2\,\nabla^2 \hat{\psi}$ and  $U=r_s^2\,\nabla^2 \phi$. Here, 
+\begin{equation}
+\epsilon_s=\frac{r_s}{R_0}\ll 1. 
+\end{equation}
 
@@
 \end{align}
-where $\hat{x}=(r-r_s)/r_s$, $\hat{L}_s=L_s/r_s$, $L_s=(R_0\,q/s)_{r_s}$ is the {\em magnetic shear length},  the {\em magnetic shear}, $s(r)$, is defined in Equation~(\ref{shear}), $\hat{V}_E= V_E(r_s)/V_A$,
+where 
+\begin{equation}
+\hat{x}=\frac{r-r_s}{r_s},
+\end{equation}
+ $\hat{L}_s=L_s/r_s$, 
+ \begin{equation}
+ L_s=\left(\frac{R_0\,q}{s}\right)_{r_s}
+ \end{equation}
+  is the {\em magnetic shear length},  $\hat{V}_E= V_E(r_s)/V_A$,
 $\hat{V}_\ast= V_\ast(r_s)/V_A$,
@@
 \end{equation}
-is the (dominant $\theta$-component of the) diamagnetic velocity, $\hat{d}_s=d_s/r_s$,  $d_s=d_\beta(r_s)$, $d_\beta$ is the modified  ion sound radius defined in 
-Equation~(\ref{e270}), and 
+is the (dominant $\theta$-component of the) diamagnetic velocity, $\hat{d}_s=d_s/r_s$,  
+\begin{equation}
+d_s=d_\beta(r_s),
+\end{equation}
+  and 
  $\hat{V}_\parallel= V_z(r_s)/V_A$. We also have
@@
  U &= 0,\label{e293}\\[0.5ex]
- \hat{E}_\parallel &=\left(\frac{2}{s_s}-1\right) \frac{\hat{\eta}_\parallel(r_s)}{\hat{L}_s},\label{e294}
-\end{align}
-where $s_s=s(r_s)$. 
+ \hat{E}_\parallel &=\left(\frac{2}{s_s}-1\right) \frac{\hat{\eta}_\parallel(r_s)}{\hat{L}_s},\label{e294}\\[0.5ex]
+s_s&=s(r_s).
+\end{align} 
 Note that we are neglecting the radial shear of the equilibrium MHD velocity because, in conventional tokamak plasmas, such shear does not significantly affect the linear response of a  resonant
@@
 $n$ periods in the toroidal direction. In accordance with Equations~(\ref{e287})--(\ref{e290}), and (\ref{e292})--(\ref{e293}), we can write
-\begin{align}
+\begin{align}\label{e295}
 \hat{\psi}(\hat{x},\zeta,t) &= \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
@@
 \end{align}
-where $\zeta=m\,\theta-n\,\varphi$, $\hat{t}=V_A\,t/r_s$, $\hat{\omega}=r_s\,\omega/V_A$, and $\omega$ is the frequency of the tearing mode in the laboratory frame. 
+where $\hat{t}=V_A\,t/r_s$, $\hat{\omega}=r_s\,\omega/V_A$, and $\omega$ is the frequency of the tearing mode in the laboratory frame. 
 Substituting Equations~(\ref{e294})--(\ref{e300}) into the four-field model, (\ref{e264})--(\ref{e269}), and only retaining terms that
@@
 \begin{align}\label{e301}
--{\rm i}\,[\omega-\omega_E -(1+\lambda_e)\,\omega_{\ast\,e}]\,\tau_H\,\tilde{\psi} &= -{\rm i} \,\hat{x}\,[\tilde{\phi}-(1+\lambda_e)\,\tilde{N}) + S^{-1}\,\hat{\nabla}^2\tilde{\psi},\\[0.5ex]
+-{\rm i}\,[\omega-\omega_E -(1+\lambda_e)\,\omega_{\ast\,e}]\,\tau_H\,\tilde{\psi} &= -{\rm i} \,\hat{x}\,[\tilde{\phi}-(1+\lambda_e)\,\tilde{N}] + S^{-1}\,\hat{\nabla}^2\tilde{\psi},\\[0.5ex]
 -{\rm i}\,(\omega-\omega_E-\omega_{\ast\,i})\,\tau_H\,\hat{\nabla}^2\tilde{\phi} &= -{\rm i}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi}+S^{-1}\,P_\varphi\,\hat{\nabla}^4\!\left(\tilde{\phi} + \frac{\tilde{N}}{\tau}\right),\\[0.5ex]
@@
 +S^{-1}\,P_\parallel\!\left(m\,\omega_{\ast\,e}\,\tau_H\,\hat{x}\,\tilde{\psi}-\frac{m}{\hat{L}_s}\,\hat{x}^2\,\tilde{N}\right)
-+ S^{-1}\,P_\perp\,\hat{\nabla}^2 \tilde{N},\nonumber\\[0.5ex]
++ S^{-1}\,P_\perp\,\hat{\nabla}_\perp^2 \tilde{N},\nonumber\\[0.5ex]
 -{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{V} &= {\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\psi} - {\rm i}\,\hat{x}\,\tilde{N}
@@
 \end{align}
-Here, $\tau_H = L_s/(m\,V_A)$ is the {\em hydromagnetic time}, $\omega_E = (m/r_s)\,V_E(r_s)$  the 
-{\em E-cross-B frequency}, $\omega_{\ast\,e} = -[\tau/(1+\tau)]\,(m/r_s)\,V_\ast(r_s)$  the {\em electron diamagnetic
-frequency}, $\lambda_e = 0.71\,[\eta_e/(1+\eta_e)]\,[\tau/(1+\tau)]$, $\omega_{\ast\,i} = [1/(1+\tau)]\,(m/r_s)\,V_\ast(r_s)$  the {\em ion diamagnetic
-frequency}, $S=\tau_R/\tau_H$ the {\em Lundquist number}, $\tau_R = \mu_0\,r_s^{\,2}/\eta_\parallel(r_s)$  the
-{\em resistive diffusion time}, $P_\varphi = \tau_R/\tau_\varphi$ the {\em magnetic Prandtl number}, $\tau_\varphi
-= r_s^{\,2}/\chi_\varphi(r_s)$  the {\em toroidal momentum confinement time}, $P_\perp = \tau_R/\tau_\perp$, 
-$\tau_\perp = r_s^{\,2}/D_\perp(r_s)$  the {\em particle/energy confinement time}, 
-$P_\parallel=\tau_R/\tau_\parallel$, and $\tau_\parallel =r_s^{\,2}/D_\parallel(r_s)$.
-
-In conventional tokamak plasmas, the Lundquist number, $S$, which is the ratio of the resistive diffusion and plasma inertia terms in the plasma Ohm's law, is very much greater than unity.
+Here, 
+\begin{equation}
+\tau_H = \frac{L_s}{m\,V_A}
+\end{equation}
+is the {\em hydromagnetic time}, 
+\begin{equation}
+\omega_E = \left(\frac{m}r_s\right)V_E(r_s)
+\end{equation}
+  the 
+{\em E-cross-B frequency}, 
+\begin{equation}
+\omega_{\ast\,e} = -\left(\frac{\tau}{1+\tau}\right)\left(\frac{m}{r_s}\right)V_\ast(r_s)
+\end{equation}
+  the {\em electron diamagnetic
+frequency},
+\begin{align}
+  \omega_{\ast\,i} &= \left(\frac{1}{1+\tau}\right)\left(\frac{m}{r_s}\right)V_\ast(r_s)
+  \end{align}
+    the {\em ion diamagnetic
+frequency}, 
+\begin{equation}
+S=\frac{\tau_R}{\tau_H}
+\end{equation}
+ the {\em Lundquist number}, 
+\begin{equation}
+\tau_R = \frac{\mu_0\,r_s^{\,2}}{\eta_\parallel(r_s)}
+\end{equation}
+ the
+{\em resistive diffusion time}, 
+\begin{equation}
+\tau_\varphi
+= \frac{r_s^{\,2}}{\chi_\varphi(r_s)}=\frac{r_s^{\,2}\,n_0\,m_i}{\mu_\perp(r_s)}
+\end{equation} 
+the {\em toroidal momentum confinement time}, and 
+\begin{equation}
+\tau_\perp = \frac{r_s^{\,2}}{D_\perp(r_s)}
+\end{equation}
+ the {\em particle/energy confinement time}. Furthermore, $P_\varphi = \tau_R/\tau_\varphi$, $P_\perp = \tau_R/\tau_\perp$, 
+$P_\parallel=\tau_R/\tau_\parallel$, $\tau_\parallel =r_s^{\,2}/D_\parallel(r_s)$, and
+\begin{equation}
+ \lambda_e = 0.71\left(\frac{\eta_e}{1+\eta_e}\right)\left(\frac{\tau}{1+\tau}\right).
+\end{equation}
+
+In conventional tokamak plasmas, the Lundquist number, $S$, which is the nominal ratio of the plasma inertia to the   resistive diffusion  terms in the plasma Ohm's law, is very much greater than unity.
 In fact, $S$ typically exceeds $10^8$ (Wesson 2011).
@@
 and $D = S^{\,1/3}\,[\tau/(1+\tau)]^{1/2}\,\hat{d}_s$. Note that the terms involving parallel transport have dropped out of
-Equation~(\ref{e308}). The neglect of these terms is justified provided that the layer width is much less than the critical value,
+Equation~(\ref{e308}). The neglect of these terms is justified provided that the linear layer width is much less than the critical value,
 \begin{equation}
@@
 response in the resonant layer, and effectively decouples Equation~(\ref{e317}) from Equations~(\ref{e314})--(\ref{e316}) (Waelbroeck, et al.\ 2012).
-Equations~(\ref{e314})--(\ref{e317}) reduce to (Cole \& Fitzpatrick 2006)
+Equations~(\ref{e314})--(\ref{e316}) reduce to (Cole \& Fitzpatrick 2006)
 \begin{equation}\label{e320}
@@
 \end{equation}
-for $p\lesssim {\cal O}(Q^{1/2})$, where use has been made of Equation~(\ref{e325}). The two-layer  approximation, which is
-equivalent to the well-known {\em constant-$\psi$ approximation}\/ (Furth, et al.\ 1963), is valid provided
-\begin{equation}
-\frac{Q^3\,(1+P)}{1+Q\,D^2}\ll 1.
-\end{equation}
+for $p\lesssim {\cal O}(Q^{1/2})$, where use has been made of Equation~(\ref{e325}). The two-layer  approximation is
+equivalent to the well-known {\em constant-$\psi$ approximation}\/ (Furth, et al.\ 1963).
 
@@
 Note, finally, that $p_\ast\sim |C|^{-\nu}$, where $p_\ast$ denotes the width of the large-$p$ layer in $p$ space.
+This width must be larger than $Q^{1/2}$ (i.e., the width of the small-$p$ layer) in order for the constant-$\psi$ approximation to hold.
 
@@
 This response regime is known as the {\em visco-resistive regime}, because the layer response is dominated by
-resistivity and viscosity. (Fitzpatrick 1998). The characteristic layer width is $p_\ast \sim P^{-1/6}$, which implies that
+resistivity and  perpendicular viscosity. (Fitzpatrick 1998). The characteristic layer width is $p_\ast \sim P^{-1/6}$, which implies that
 the regime is valid when  $P\gg Q^{3/2}$, $P\gg D^6$, and $P\ll Q^{-3}$.
@@
 
-\subsection{Nonconstant-$\psi$ Regimes}
-Suppose that $p\ll Q^{-1/2}$. In this limit, Equation~(\ref{e320}) reduces to 
+\subsection{Nonconstant-$\psi$ Regimes}\label{sncp}
+Suppose that $p\ll Q^{1/2}$. In this limit, Equation~(\ref{e320}) reduces to 
 \begin{equation}
@@
 \end{equation}
-
 In the various nonconstant-$\psi$ regimes considered in this section, the previous equation takes the form
@@
 is bounded as $p\rightarrow\infty$ has the small-$p$ expansion (\ref{e332}), where $z=\sqrt{C}\,p^n/n$, 
-$n=(m+2)/2$, and $\nu=1/(m+2)$. The layer width in $p$-space again scales as $p_\ast\sim |C|^{-\nu}$. 
-Matching to Equation~(\ref{e325}) yields
+$n=(m+2)/2$, and $\nu=1/(m+2)$. Matching to Equation~(\ref{e325}) yields
 \begin{equation}
@@
 \end{equation}
-
-\begin{figure}
+The layer width in $p$-space again scales as $p_\ast\sim |C|^{-\nu}$. This width must be
+less that $Q^{1/2}$.
+
+\begin{figure}[t]
 \centerline{\includegraphics[width=0.9\textwidth]{RegimeI.pdf}}
@@
 
-\begin{figure}
+\begin{figure}[t]
 \centerline{\includegraphics[width=0.9\textwidth]{RegimeII.pdf}}
@@
 \subsection{Discussion}\label{dis1}
-Figures~\ref{f1} and \ref{f2} show the extents of the various different response regimes in the $Q$-$P$ plane for the
+Figures~\ref{f1} and \ref{f2} show the extents of the various different response regimes in $Q$-$P$ space for the
 cases $D<1$ and $D>1$, respectively.
 
-Let $\hat{\delta}\sim p_\ast^{-1}$ be the normalized radial thickness of the resonant layer.  Of course, the true thickness is
-$\delta = S^{-1/3}\,\hat{\delta}\,r_s$.  It follows from
+Let $\hat{\delta}_\ast\sim p_\ast^{-1}$ be the normalized radial thickness of the resonant layer.  Of course, the true thickness is
+$\delta = S^{-1/3}\,\hat{\delta}_\ast\,r_s$.  It follows from
 Equation~(\ref{e311}) that the relative change in the perturbed helical flux, $\tilde{\psi}$, across the layer
@@
 \begin{equation}
-\left.\frac{d\ln\tilde{\psi}}{dX}\right|_{-\hat{\delta}/2}^{+\hat{\delta}/2} = \hat{\mit\Delta}\,\,\hat{\delta}\sim \hat{\mit\Delta}\,\,p_\ast^{-1},
-\end{equation}
-According to the previous analysis, $\hat{\mit\Delta}\,p_\ast^{-1}$ takes the respective values $Q^{1/2}$, $Q\,P^{1/3}$, 
+\left.\frac{d\ln\tilde{\psi}}{dX}\right|_{-\hat{\delta}/2}^{+\hat{\delta}/2} = \hat{\mit\Delta}\,\,\hat{\delta}_\ast\sim \hat{\mit\Delta}\,\,p_\ast^{-1},
+\end{equation}
+According to the  analysis of Section~\ref{scp}, $\hat{\mit\Delta}\,p_\ast^{-1}$ takes the respective values $Q^{1/2}$, $Q\,P^{1/3}$, 
 $Q^2/D^2$, and $Q\,P^{1/2}/D$ in the resistive-inertial, visco-resistive, semi-collisional, and
@@
 much less than unity. In other words, it is indeed the case that $\tilde{\psi}$ does not vary substantially across a
-`constant-$\psi$' resonant layer. On the other hand, $\hat{\mit\Delta}\,p_\ast^{-1}\sim 1$ in the inertial,
+`constant-$\psi$' resonant layer. On the other hand, according to the analysis of Section~\ref{sncp}, $\hat{\mit\Delta}\,p_\ast^{-1}\sim 1$ in the inertial,
 visco-inertial, and Hall-viscous response regimes, which implies that $\tilde{\psi}$ does vary substantially
 across a `nonconstant-$\psi$' layer.
+
+\begin{figure}[t]
+\centerline{\includegraphics[width=0.9\textwidth]{Island.pdf}}
+\caption{Equally-spaced contours of $\psi(\hat{x},\xi)$. The magnetic separatrix is shown in red. }\label{f2a}
+\end{figure}
+
+Suppose that the resonant layer lies in a constant-$\psi$ response regime. According to Equation~(\ref{e295}),
+the perturbed magnetic flux in the layer takes the form:
+\begin{equation}
+\hat{\psi}(\hat{x},\zeta,t) = \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},
+\end{equation}
+where $\tilde{\psi}$ is a complex constant. Of course, the physical flux is the real part of the previous expression; that is,
+\begin{equation}\label{e352a}
+\hat{\psi}(\hat{x},\xi)= \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ |\tilde{\psi}|\,\cos\xi,
+\end{equation}
+where
+\begin{equation}
+\xi = \zeta +{\rm arg}(\tilde{\psi})-\hat{\omega}\,\hat{t} = m\,\theta-n\,\varphi +{\rm arg}(\tilde{\psi}) -\omega\,t.
+\end{equation}
+Now, it is clear from Equation~(\ref{e279}) that ${\bf B}\cdot\hat{\nabla}\hat{\psi}=0$. In other words, the contours of
+$\hat{\psi}(\hat{x},\xi)$ map out the perturbed magnetic flux-surfaces in the vicinity of the resonant layer. 
+Let $\hat{W} = 4\,(|\tilde{\psi}|\,\hat{L}_s)^{1/2}$. Equation~(\ref{e352a}) can be written
+\begin{equation}
+\frac{\psi(\hat{x},\xi)}{|\tilde{\psi}|} = 8\left(\frac{\hat{x}}{\hat{W}}\right)^2 + \cos\xi.
+\end{equation}
+Figure~\ref{f2a} shows the contours of $\psi(\hat{x},\xi)$ specified by the previous equation. It can be seen that the
+tearing mode has reconnected magnetic field-lines to produce a {\em helical magnetic island chain}\/ centered on the resonant
+surface. The chain has $m$ periods in the poloidal direction, $n$ periods in the toroidal direction, and propagates at the
+helical phase velocity $\omega$. The maximum full (as opposed to half) radial width of the magnetic separatrix is 
+\begin{equation}\label{e355s}
+W =  \hat{W}\,r_s= 4\,(|\tilde{\psi}|\,\hat{L}_s)^{1/2}\,r_s = 4\left(\frac{q_s}{s_s}\,|\hat{\mit\Psi}_s|\right)^{1/2}R_0,
+\end{equation}
+where ${\mit\Psi}_s = r_s\,B_z\,\tilde{\psi}$ is the reconnected magnetic flux defined in Equation~(\ref{e99}), and
+$\hat{\mit\Psi}_s= {\mit\Psi}_s/(R_0\,B_z)$.
+
+Finally, our four-field resonant plasma response model, (\ref{e264})--(\ref{e269}), contains many term of the general form $[\hat{\psi},\tilde{A}]$,
+where $\tilde{A}(\hat{x},\zeta)$ is a perturbed quantity. According to Equation~(\ref{e352a}), such terms
+can be written
+\begin{equation}
+[\hat{\psi},\tilde{A}] = {\rm i}\,\frac{m}{r_s}\left(\frac{\hat{x}}{\hat{L}_s}\,\tilde{A} - \tilde{\psi}\,\frac{\partial \tilde{A}}{\partial\hat{x}}\right)
+\sim {\rm i}\,\frac{m}{r_s}\,\frac{\hat{\delta}}{\hat{L}_s}\,\tilde{A} - {\rm i}\,\frac{m}{r_s}\,\frac{\tilde{\psi}}{\hat{\delta}}\,\tilde{A}, 
+\end{equation}
+where $\delta = \hat{\delta}\,r_s$ is the width of the linear layer. Now, linear layer theory is only valid when the second
+term on the extreme right side of the previous equation is negligible compared to the first (because the second term is quadratic in perturbed quantities, whereas the first is linear). In other words,
+we require $\hat{\delta}^{\,2}\gg |\tilde{\psi}|\,\hat{L}_s$, which reduces to 
+\begin{equation}
+\delta \gg W.
+\end{equation}
+[See Equation~(\ref{e355s}).]
+We conclude that the linear resonant response theory presented in this section is only valid when the radial width of the magnetic
+island chain that develops in the vicinity of the resonant surface is {\em much less}\/ than the radial width of the linear layer. 
+Given that linear layers are very narrow in conventional tokamak plasmas, this is a stringent constraint.
 
@@
 
-In a conventional tokamak plasma, assuming that $m\sim {\cal O}(1)$, $E_{ss}\sim {\cal O}(1)$,\footnote{Note that we are neglecting $m=1$ modes, for which $|E_{ss}|\gg 1$,
+In a conventional tokamak plasma [assuming that $m\sim {\cal O}(1)$], $E_{ss}\sim {\cal O}(1)$,\footnote{Note that we are neglecting $m=1$ modes, for which $|E_{ss}|\gg 1$,
 because such modes are not really tearing modes
@@
 According to Equations~(\ref{e353}) and (\ref{e354}), the tearing mode co-rotates with the electron fluid at the resonant
- surface.\footnote{In fact, it
+ surface.\footnote{In fact, the mode 
 rotates slightly faster than the electron fluid because of the influence of the thermal force, ${\bf F}_T$ [see Equation~(\ref{e43})],
@@
 \subsection{Determination of Linear Growth-Rates}\label{s6.3}
-Reusing the analysis of Sections~\ref{s5.6} and \ref{scp}, there are two layers in $p$ space (i.e., Fourier space). The
-small-$p$ layer is of width $|\hat{\gamma}|^{1/2}$, where $\hat{\gamma} = S^{1/3}\,\gamma\,\tau_H$. Given that we are effectively assuming that
+Reusing the analysis of Sections~\ref{s5.6} and \ref{scp}, let us again suppose that there are two layers in $p$ space (i.e., Fourier space). The
+small-$p$ layer turns out to be of width $|\hat{\gamma}|^{1/2}$, where $\hat{\gamma} = S^{1/3}\,\gamma\,\tau_H$. Given that we are effectively assuming that
 $|\hat{\gamma}|\ll 1$, the condition for the separation of the layer solution into two layers (i.e., that the width of the small-$p$ layer is less than that of the large-$p$ layer) is always satisfied.
@@
 \begin{equation}\label{e371}
-\gamma= \frac{E_{ss}}{2\pi\,[{\mit\Gamma}(3/4)/{\mit\Gamma}(1/4)]\,[1+\lambda_e\,\tau/(1+\tau)]^{-1/4}}\,\frac{(d_s/r_s)^{1/2}\,\tau_\perp^{1/4}}{\tau_H^{1/4}\,\tau_R^{3/4}}.
-\end{equation}
-
-\begin{figure}
+\gamma= \frac{E_{ss}}{2\pi\,[{\mit\Gamma}(3/4)/{\mit\Gamma}(1/4)]\,[1+\lambda_e\,\tau/(1+\tau)]^{-1/4}}\,\frac{(d_s/r_s)^{1/2}\,\tau_\perp^{1/4}}{\tau_H^{1/2}\,\tau_R^{3/4}}.
+\end{equation}
+
+\begin{figure}[t]
 \centerline{\includegraphics[width=0.9\textwidth]{RegimeIII.pdf}}
-\caption{Linear tearing mode growth-rate regimes  in $Q_\ast$-$P$ space for the case $D=1$. The various regimes are
+\caption{Linear tearing mode growth-rate regimes  in $Q_\ast$-$P$ space. The various regimes are
 the Hall-resisitive (HR), the semi-collisional (SC),  the visco-resistive (VR), and the resistive-inertial (RI).}\label{f3}
@@
 the mode grows on a hybrid timescale that is much greater than the hydrodynamical timescale, $\tau_H$,
-but much less than the resistive evolution timescale, $\tau_R$.
+but much less than the resistive evolution timescale, $\tau_R$. Note that, in all cases, the growth-rate goes to zero as
+$\tau_R\rightarrow \infty$. This is not surprising because, as is clear from Equation~(\ref{e301}), the perturbed
+helical magnetic flux at the resonant surface,  $\tilde{\psi}(\hat{x}=0,\zeta)$, is constrained to take the value zero
+in the limit that $S\rightarrow\infty$. In other words, magnetic reconnection at the resonant surface (which corresponds to a finite
+$\tilde{\psi}$ at $\hat{x}=0$) is impossible in the absence of plasma resistivity (Furth, et al.\ 1963).
 
@@
 Second, the  anomalous perpendicular diffusion of momentum and particles, which is parameterized by the momentum and particle confinement
-timescales, $\tau_\varphi$ and $\tau_\perp$ (and by the magnetic Prandtl number, $P$). Third, the
-finite gyroradii of ions, which is parameterized by the modified ion sound radius, $d_s$ (and by the normalized
+timescales, $\tau_\varphi$ and $\tau_\perp$ (and by the magnetic Prandtl number, $P$).
+Third, finite ion sound radius effects,  which are parameterized by the modified ion sound radius, $d_s$ (and by the normalized
 sound radius $D$).
 
- There are four growth-rate regimes---the resistive-inertial, the visco-resistive, the semi-collisional, and the Hall-resistive---and their extents in $Q_\ast$-$P$-$D$ space are illustrated in Figure~\ref{f3}.
+ There are four tearing-mode growth-rate regimes---the resistive-inertial, the visco-resistive, the semi-collisional, and the Hall-resistive---and their extents in $Q_\ast$-$P$-$D$ space are illustrated in Figure~\ref{f3}.
 Note that Figure~\ref{f3} differs somewhat from Figures~\ref{f1} and \ref{f2} because in the latter two
-figures it was assumed that $|Q-Q_E-(1+\lambda_e)\,Q_e|\sim |Q-Q_E|\sim |Q-Q_E-Q_i|$ whereas
-in the former figure it was assumed that $|Q-Q_E-(1+\lambda_e)\,Q_e|\ll |Q-Q_E|\sim |Q-Q_E-Q_i|$.
+figures it is assumed that $|Q-Q_E-(1+\lambda_e)\,Q_e|\sim |Q-Q_E|\sim |Q-Q_E-Q_i|$ whereas
+in the former figure it is assumed that $|Q-Q_E-(1+\lambda_e)\,Q_e|\ll |Q-Q_E|\sim |Q-Q_E-Q_i|$.
 This refined ordering eliminates the nonconstant-$\psi$ response regimes, and significantly modifies the
@@
 should come as no surprise. As we saw in Section~\ref{dis1}, nonconstant-$\psi$ resonant layers
-are characterized by $\hat{\mit\Delta}\sim\hat{\delta}^{-1}= S^{-1/3}\,(r_s/\delta)$, where $\delta$
+are characterized by $\hat{\mit\Delta}\sim\hat{\delta}_\ast^{-1}= S^{-1/3}\,(r_s/\delta)$, where $\delta$
 is the layer thickness. Hence, according to Equation~(\ref{e352}), asymptotic matching of such a
@@
 growth-rate regimes, but not in the Hall-resistive and visco-resistive regimes. Anomalous perpendicular
-transport modifies the growth-rate in all regimes except the semi-collisional regime. Finally, finite ion gyroradius
+transport modifies the growth-rate in all regimes except the semi-collisional regime. Finally, finite ion sound radius 
 effects modify the growth-rate in the Hall-resistive and semi-collisional regimes, but not in the other two
@@
 eventually scales as $\omega_\ast^{-1/2}$. Increasing the anomalous perpendicular transport increases the
-growth-rate such that it  eventually scales as $P_\varphi^{1/6}$. Increasing the ion gyroradius
+growth-rate such that it  eventually scales as $P_\varphi^{1/6}$. Increasing the ion sound radius 
 increases the tearing mode growth-rate, but the increase eventually saturates (i.e., the
@@
 seems to suggest that in the resistive-inertial regime it might be possible to successfully match the
-layer solution to the outer solution when $\omega_r=\omega_E$, or when $\omega_r=\omega_E+\omega_{\ast\,i}$,
-giving tearing mode perturbations that corotate with the MHD fluid and the ion fluid, respectfully, at the resonant
+layer solution to the outer solution when $\omega_r=\omega_E$ (i.e., $Q=Q_E$), or when 
+$\omega_r=\omega_E+\omega_{\ast\,i}$
+(i.e., $Q=Q_E+Q_i$),
+giving tearing mode perturbations that corotate with the MHD fluid and the ion fluid, respectively, at the resonant
 surface.
-In fact, we can see that this is not the case, because if we set $\omega_r=\omega_E$, or $\omega_r=\omega_E+\omega_{\ast\,i}$,  then Equation~(\ref{e329}) does not lead to a layer solution characterized by  $|\hat{\mit\Delta}|\ll 1$,
+In fact, we can see that this is not the case, because if we set $\omega_r=\omega_E$ or $\omega_r=\omega_E+\omega_{\ast\,i}$  then Equation~(\ref{e329}) does not lead to a layer solution characterized by  $|\hat{\mit\Delta}|\ll 1$,
 as a consequence of finite anomalous perpendicular transport. Likewise, Equation~(\ref{sc}) seems to suggest that in the semi-collisional response regime it might be possible to successfully match the
@@
 perpendicular transport.
+
+\section{Error-Field Penetration in Tokamak Plasmas}
+\subsection{Introduction}
+Tokamak plasmas are invariably subject to small amplitude, static, resonant magnetic pert\-urbations---known as
+{\em error-fields}---which are primarily generated by field-coil misalignments and uncompensated coil feeds. 
+Error-fields can drive magnetic reconnection, resulting in the formation of {\em locked}\/ (i.e., non-rotating in the laboratory
+frame) magnetic island chains, in intrinsically tearing-stable plasmas. Low-density, ohmically-heated tokamak plasmas
+containing locked magnetic island chains often terminate in sudden violent events known as {\em disruptions}\/ (Wesson, et al.\ 1989; Wesson 2011) (usually triggered when the
+external heating is turned on). Fortunately, error-field driven magnetic reconnection is strongly
+suppressed by the naturally occurring rotation of ohmic plasmas. However, when the error-field amplitude rises
+above a certain critical amplitude, the rotation at the resonant surface is suddenly arrested, and error-field driven reconnection proceeds
+unhindered. This phenomenon is known as {\em error-field penetration}\/ (Fitzpatrick 1993; Fitzpatrick 1998). The scenario
+just outlined has been observed in a number of tokamak experiments (Scoville, et al.\ 1991; Hender, et al.\ 1992; Fishpool
+\& Haynes 1994; Wolfe, et al.\ 2005; Wolf, et al.\ 2005; Howell, Hender, \& Cunningham 2007; Menard, et al.\ 2010; Wang, et al.\ 2014; Wang, et al.\ 2018).
+
+In this section, we shall calculate the critical error-field amplitude required to trigger penetration on the assumption that,
+prior to penetration, the rotational suppression of error-field driven magnetic reconnection is sufficiently strong that
+the resonant plasma response is governed by linear layer physics (Fitzpatrick 1993; Fitzpatrick 1998; Cole \& Fitzpatrick 2006).
+
+\subsection{Asymptotic Matching}
+It is convenient to parametrize the error-field in terms of the static current, $I_c$, that must be run through the magnetic
+field-coil introduced in Section~\ref{sfc} in order to generate it. Setting $d/dt=0$ in Equations~(\ref{e202}) and (\ref{e203}),
+we get
+\begin{equation}\label{e400}
+{\mit\Delta\hat{\Psi}}_s = {\mit\Delta}_{nw}\,\hat{\mit\Psi}_s+\tilde{I}_c,
+\end{equation}
+where
+\begin{equation}
+{\mit\Delta}_{nw} = {\mit\Delta}_{pw} + \frac{E_{sw}^{\,2}}{(-\tilde{E}_{ww})}
+\end{equation}
+is the (real) tearing stability index in the absence of a wall, ${\mit\Delta}_{pw}= E_{ss}$ is the
+(real) tearing stability index in the presence of a perfectly conducting wall at $r=r_w$, and
+\begin{equation}
+\tilde{I}_c =\left(\frac{{\mit\Delta}_{nw} - {\mit\Delta}_{pw}}{E_{sw}}\right)\left(
+\frac{r_w}{r_c}\right)^m\left(\frac{\mu_0\,I_c}{R_0\,B_z}\right).
+\end{equation}
+Here, the plasma-wall coupling parameter, $E_{sw}>0$, is defined in Section~\ref{resistive}. We expect $0>{\mit\Delta}_{nw}>
+{\mit\Delta}_{pw}$ because the plasma is assumed to be tearing stable, and $\tilde{E}_{ww}<0$.
+
+In the resonant layer, Equation~(\ref{e312}) yields
+\begin{equation}\label{e383}
+{\mit\Delta\hat{\Psi}}_s = {\mit\Delta}\,\,\hat{\mit\Psi}_s,
+\end{equation}
+where ${\mit\Delta} = S^{1/3}\,\hat{\mit\Delta}$, and the complex layer matching parameter, $\hat{\mit\Delta}$, is defined in 
+Equation~(\ref{e312}). 
+Hence, asymptotic matching between the inner and the outer regions yields
+\begin{equation}\label{e384}
+\hat{\mit\Psi}_s = \frac{\tilde{I}}{(-{\mit\Delta}_{nw}) + {\mit\Delta}},
+\end{equation}
+where use has been made of Equations~(\ref{e400}) and (\ref{e383}). 
+The previous equation specifies the (normalized) reconnected magnetic flux, $\hat{\mit\Psi}_s$, driven at the resonant surface by the (normalized) 
+error-field coil current, $\tilde{I}_c$. The complex layer parameter, ${\mit\Delta}$, specifies the strength of a shielding current
+that is induced in the resonant layer, and acts to prevent driven magnetic reconnection.
+
+\subsection{Resonant Layer Response}
+Generally speaking, in an ohmically-heated tokamak, we do not expect the plasma flow at the resonant surface to be sufficiently
+large to cause a breakdown of the constant-$\psi$ approximation. We also expect $P_\varphi, P_\perp \gg 1$. In other
+words, we expect the resistive evolution timescale to significantly exceed both the momentum and energy/particle
+confinement timescales (which it generally does by, at least, a factor of 10). Hence, consulting Figures~\ref{f1} and \ref{f2},
+we can see that the appropriate linear resonant response regime is either the visco-resistive regime or the Hall-resistive
+regime.
+
+According to the analysis of Section~\ref{scp}, and making use of the fact that $\omega=Q=0$ for a static perturbation, 
+in the visco-resistive response regime we have
+\begin{equation}
+{\mit\Delta}_{\rm VR} = {\rm i}\,\tau_{\rm VR}\,(\omega_{\perp\,e}+{\mit\Delta}\omega_E),
+\end{equation}
+where $\tau_{\rm VR} = \tau_R\,\hat{\delta}_{\rm VR}$, and
+\begin{equation}
+\hat{\delta}_{\rm VR} = \frac{6^{2/3}\,\pi\,{\mit\Gamma}(5/6)}{{\mit\Gamma}(1/6)}\,\frac{\tau_H^{1/3}}{\tau_R^{1/6}\,\tau_\varphi^{1/6}}
+\end{equation}
+is the visco-resistive layer width (normalized to $r_s$). Here, $\omega_{\perp\,e}$ is defined in Equation~(\ref{e354}), and
+${\mit\Delta}\omega_E$ is the modification to the ${\bf E}\times{\bf B}$ frequency generated at the resonant surface by
+the electromagnetic torques that develop there in response to the error-field. Likewise, in the
+Hall-resistive regime we have
+\begin{equation}
+{\mit\Delta}_{\rm HR} = {\rm i}\,\tau_{\rm HR}\,(\omega_{\perp\,e}+{\mit\Delta}\omega_E),
+\end{equation}
+where $\tau_{\rm HR} = \tau_R\,\hat{\delta}_{\rm HR}$, and
+\begin{equation}
+\hat{\delta}_{\rm HR} = \frac{2\pi\,{\mit\Gamma}(3/4)}{{\mit\Gamma}(1/4)\,[1+\lambda_e\,\tau/(1+\tau)]^{1/4}}\,
+\frac{\tau_H^{1/2}}{(d_s/r_s)^{1/2}\,\tau_R^{1/4}\,\tau_\perp^{1/4}}
+\end{equation}
+is the Hall-resistive layer width (normalized to $r_s$).
+
+We can combine the previous two results to give the composite layer response equation
+\begin{equation}\label{e389}
+{\mit\Delta} = {\rm i}\,\tau_s\,(\omega_{s\,0}+ {\mit\Delta}\omega_E),
+\end{equation}
+where $\tau_s=\tau_R\,\hat{\delta}$, 
+\begin{equation}
+\hat{\delta} = \frac{\hat{\delta}_{\rm VR}\,\hat{\delta}_{\rm HR}}{\hat{\delta}_{\rm VR} + \hat{\delta}_{\rm HR}},
+\end{equation}
+and 
+\begin{equation}
+\omega_{s\,0}= \omega_{\perp\,e}.
+\end{equation}
+
+It can be seen, by comparison with the analysis of Section~\ref{tauw}, that the resonant layer responds to the error-field
+perturbation in an analogous manner to a thin, rigid, resistive wall whose resistivity matches that of the plasma at the
+resonant surface, and whose radial thickness is $\delta=r_s\,\hat{\delta}$. Note, however, that the effective wall corotates with the
+electron fluid at the resonant surface. Moreover, it is the rotation of the effective wall that generates the shielding current.
+
+Incidentally, the reason that a shielding current only develops in the vicinity of the resonant surface is that the plasma is
+not a rigid body. Under normal circumstances, the plasma responds to the error-field by displacing radially in such a
+manner as to eliminate the shielding current. The requisite displacement is (Freidberg 1987)
+\begin{equation}
+\xi_r(r,\zeta) = \frac{\tilde{\psi}(r,\zeta)}{B_\theta(r)\,[1-q(r)/q_s]}.
+\end{equation}
+However, this displacement becomes infinite at the resonant surface, where $q(r)=q_s$, which explains why a shielding
+current is only excited in the immediate vicinity of this surface.
+
+Equations~(\ref{e384}) and (\ref{e389}) yield
+\begin{equation}\label{e392}
+\hat{\mit\Psi}_s=\frac{\tilde{I}_c}{(-{\mit\Delta}_{nw})+ {\rm i}\,\tau_s\,(\omega_{s\,0}+ {\mit\Delta}\omega_E)}.
+\end{equation}
+Now, in a conventional ohmically-heated tokamak plasma, $\tau_s\,\omega_{s\,0}\gg (-{\mit\Delta}_{nw})$. Consequently, the
+shielding current that develops at the resonant surface, in response to the local plasma rotation, is strong enough to largely
+suppress error-field-driven magnetic reconnection [i.e., $|\hat{\mit\Psi}_s|\ll |\tilde{I}_c|/(-{\mit\Delta}_{nw})$]. However, the shielding current also gives rise to a localized electromagnetic
+torque at the resonant surface (see Section~\ref{storque}) that acts to slow the plasma rotation.
+
+\subsection{Torque Balance}\label{stb}
+According to Equations~(\ref{e200}) and (\ref{e201}),
+\begin{equation}\label{e393}
+{\mit\Delta}\omega_E = ({\bf k}\cdot{\mit\Delta}{\bf V}_i)_{r=r_s} = -\sum_{p=1,\infty}(\alpha_p+ \beta_p).
+\end{equation}
+In other words, the shift in the ${\bf E}\times {\bf B}$ velocity at the resonant surface, in response to the electromagnetic
+torques that develop there, is mirrored by an equal  shift in the ion fluid velocity. This is the
+essence of the no-slip constraint discussed in Section~\ref{sns}. The no-slip constaint follows from Equations~(\ref{e217}) and (\ref{e219})
+because the torques do not modify the diamagnetic velocity at the resonant surface.
+
+Making use of Equations~(\ref{e193}), (\ref{e194}), (\ref{e205}) and (\ref{e206}) (with $d/dt=0$), (\ref{e383}), (\ref{e389}), (\ref{e392}),
+and (\ref{e393}), we arrive at the following torque balance equation (Fitzpatrick 1993; Fitzpatrick 1998):
+\begin{equation}\label{e394}
+T_{\rm VS}(v)= T_{\rm EM}(v),
+\end{equation}
+where 
+\begin{align}
+v&=\frac{\omega_{s\,0}+{\mit\Delta}\omega_E}{\omega_{s\,0}},\\[0.5ex]
+T_{\rm VS}(v) &= 1- v,\\[0.5ex]
+T_{\rm EM}(v) &= \frac{1}{4}\,\frac{v}{\zeta_s^{\,2}+v^2}
+\left(\frac{|\tilde{I}_c|}{\tilde{I}_{c\,{\rm crit}}}\right)^2,\\[0.5ex]
+\zeta_s &= \frac{(-{\mit\Delta}_{nw})}{\tau_s\,\omega_{s\,0}}\ll 1,\\[0.5ex]
+\tilde{I}_{c\,{\rm crit}}&= (\epsilon_s\,s_s)\,(\omega_{s\,0}\,\tau_H)\left/
+\left[\frac{q_s}{\epsilon_s}\left(\frac{\sqrt{\tau_\varphi\,\tau_{i\,s}/\mu_{00\,s}^i}}{\tau_s}\right)+2\left(\frac{\tau_\varphi}{\tau_s}\right) \ln\!\left(\frac{a}{r_s}\right)\right]^{1/2}\right..\label{e420}
+\end{align}
+Here, use has been made of the identities
+\begin{align}
+\lim_{\epsilon\rightarrow 0}\sum_{p=1,\infty} \frac{\sqrt{\epsilon}\,[J_1(j_{1\,p}\,x)]^{2}}{[J_2(j_{1\,p})]^2\,(1+\epsilon\,j_{1\,p}^2)}
+&=\frac{1}{4\,x},\\[0.5ex]
+\sum_{p=1,\infty} \frac{[J_0(j_{0\,p}\,x)]^2}{[J_1(j_{0\,p}\,x)]^2\,j_{0\,p}^{\,2}} =\frac{1}{2}\,\ln\!\left(\frac{1}{x}\right).
+\end{align}
+We have also written 
+\begin{equation}
+\frac{1}{\tau_{\theta\,s}} = \left(\frac{q_s}{\epsilon_s}\right)^2\,\left(\frac{\mu_{00\,s}^i}{\tau_{i\,s}}\right),
+\end{equation}
+ where
+ \begin{align}
+\tau_{i\,s}&= \tau_i(r_s),\\[0.5ex]
+ \mu_{00\,s}^i&=\mu_{00}^i(r_s), 
+ \end{align}
+ and $\mu_{00}^i(r)$ is a dimensionless neoclassical viscosity coefficient defined in Fitzpatrick \& Nelson 2020. Furthermore,
+ we have assumed that $\tau_{i\,s}/(\tau_\varphi\,\mu_{00\,s}^i)\ll (q_s/\epsilon_s)^2$ (this
+turns out to be  
+a very good approximation because the ion collision time, $\tau_{i\,s}$, is much less than the momentum confinement
+time, $\tau_\varphi$, in conventional tokamak plasmas).
+
+\begin{figure}[t]
+\centerline{\includegraphics[width=0.9\textwidth]{Torque.pdf}}
+\caption{Torque balance. The red curve shows the normalized viscous restoring torque, $T_{\rm VS}(v)$. The
+solid and dashed blue curves show the normalized electromagnetic locking torque, $T_{\rm EM}(v)$,
+evaluated with $\zeta_s=0.05$, and
+ $|\tilde{I}_c|/\tilde{I}_{c\,{\rm crit}}=0.8$ and $1.0$, respectively. }\label{f5}
+\end{figure}
+
+In Equation~(\ref{e394}), the dimensionless
+parameter $v$ takes the value unity when the plasma (i.e., electron fluid) rotation at the resonant surface is unmodified by
+the electromagnetic locking torque, and zero when the electromagnetic locking torque has reduced the rotation to zero. The electromagnetic torque itself
+is represented  by the function $T_{\rm EM}(v)$, whereas the viscous restoring toque that acts to oppose changes in the plasma rotation is represented
+by the function $T_{\rm VS}(v)$. It can be seen from Figure~\ref{f5} that, while the viscous restoring torque varies linearly with $v$,
+the electromagnetic locking torque varies with $v$ in a nonmonotonic manner. The electromagnetic torque is
+zero when $v=0$, because there is no plasma rotation to induce a shielding current. As $v$ increases from zero, the
+torque initially increases linearly with $v$. However, the shielding current eventually becomes strong enough to expel
+the reconnected magnetic flux from the resonant layer. Consequently, because the torque
+is proportional to the product of the shielding current and the reconnected flux, the torque peaks, and ends up falling off as $1/v$ 
+with increasing $v$ (Gimbett \& Peckover 1979; Fitzpatrick 1993).
+
+The solutions of the torque balance equation (\ref{e394}) correspond to the crossing points of the viscous and electromagnetic torque
+curves. As is clear from Figure~\ref{f5}, if the normalized magnitude of the error-field coil current, $|\tilde{I}_c|$, lies below
+the critical value $\tilde{I}_{c\,{\rm crit}}$ then there are three crossing points. However, the intermediate crossing point corresponds to
+a dynamically unstable equilibrium. Hence, we deduce that there are two physical solution branches of the torque
+balance equation. The large-$v$ solution branch corresponds to  so-called {\em shielded}\/ solutions in which the plasma
+rotation at the resonant surface is large enough to strongly suppress driven magnetic reconnection. The small-$v$
+solution branch corresponds to so-called {\em unshielded}\/ solutions  in which the plasma rotation at the resonant surface is
+too weak to suppress driven magnetic reconnection. 
+On the shielded solution branch, Equation~(\ref{e394}) possesses the approximate solution
+\begin{equation}
+v \simeq \frac{1}{2}\left(1-\left[1-\left(\frac{|\tilde{I}_c|}{\tilde{I}_{c\,{\rm crit}}}\right)^2\right]^{1/2}.
+\right)
+\end{equation}
+It can be seen that as the error-field coil current increases  the plasma rotation at the resonant surface decreases. However, when
+$|\tilde{I}_c|$ attains the critical value $\tilde{I}_{c\,{\rm crit}}$, and the rotation is reduced to half of its
+original value, the shielded solution branch ceases to exist, and there is a bifurcation to the unshielded solution branch (Fitzpatrick 1993;
+Fitzpatrick 1998). (See Figure~\ref{f5}.)
+The bifurcation is associated with a sudden decrease in the plasma rotation at the resonant surface, and a sudden
+increase in the driven reconnected magnetic flux, and is identified with the error-field penetration phenomenon observed in tokamak
+experiments. As is clear from Equation~(\ref{e420}), the critical error-field coil current needed to trigger error-field
+penetration increases linearly with the unperturbed plasma rotation at the resonant surface, which is parameterized by $\omega_{s\,0}$. 
+Once error-field penetration has occurred, the magnitude of the error-field coil current must be reduced to a value
+that is substantially less than $\tilde{I}_{c\,{\rm crit}}$ in order to trigger a reverse bifurcation to the unshielded solution branch (Fitzpatrick 1998).
+
+Finally, the criterion for the validity of the theory presented in this section is that the width of the magnetic island
+chain driven at the resonant surface, just prior to mode penetration, is much less than the linear layer width (so that the resonant
+plasma response is governed by linear physics). This is the case provided that (Fitzpatrick 1998)
+\begin{equation}
+\hat{\delta}\gg 4\,S^{-2/5}\left(\frac{q_s}{\epsilon_s}\right)^{2/5}\left[\frac{q_s}{\epsilon_s}\left(\frac{\sqrt{\tau_\varphi\,\tau_{i\,s}/\mu_{00\,s}^i}}{\tau_R}\right)+2\left(\frac{\tau_\varphi}{\tau_R}\right) \ln\!\left(\frac{a}{r_s}\right)\right]^{-1/5}.
+\end{equation}
+
+\subsection{Scaling Analysis}
+The aim of this section is to use the previous analysis to predict the scaling of the error-field penetration
+threshold with the standard dimensionless scaling parameters (Connor \& Taylor 1977)
+\begin{align}
+\rho_\ast &= \frac{T_0^{1/2}\,m_i^{1/2}}{e\,B_z\,L_s},\label{e428}\\[0.5ex]
+\nu_\ast &= \frac{L_s\,n_0\,e^2\,\eta_\parallel(r_s)}{m_e^{1/2}\,T_0^{1/2}},\\[0.5ex]
+\beta&=\frac{\mu_0\,n_0\,T_0}{B_z^{\,2}},\label{e430}
+\end{align}
+where $T_0=p_0/n_0$. In the following, for the sake of simplicity, we
+shall assume that $T_i=T_e=T_0$, $\omega_{s\,0}=\omega_\ast$, and $-(d\ln p/dr)_{r_s} = 1/r_s$. We shall also neglect ${\cal O}(1)$
+constants such as $s_s$, $\eta_e$, $\eta_i$, $\lambda_e$, $\tau$, $\pi$, $\ln(r_s/a)$, et cetera.
+
+ Now, in an ohmically-heated tokamak
+plasma, the energy confinement timescale, $\tau_E$, satisfies the constraint
+\begin{equation}
+\frac{n_0\,T_0}{\tau_E} = \eta_\parallel(r_s)\left(\frac{B_z}{\mu_0\,L_s}\right)^2,
+\end{equation}
+which is obtained by equating the energy loss rate to the ohmic heating rate. Let us assume that the momentum confinement
+time, $\tau_\varphi$, and the particle/energy confinement time, $\tau_\perp$, are both equal to $\tau_E$, as is generally
+(approximately) the case in ohmically-heated tokamak plasmas (ITER Physics Basis Editors 1999).
+
+It is easily demonstrated that
+\begin{align}
+\omega_{s\,0}\,\tau_H&\simeq \left(\frac{q_s}{\epsilon_s}\right)^2\rho_\ast\,\beta^{\,1/2},\\[0.5ex]
+\frac{\tau_H}{\tau_R}&\simeq \left(\frac{q_s}{\epsilon_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/2}\rho_\ast^{\,2}\,\nu_\ast\,\beta^{-1/2},\\[0.5ex]
+\frac{\tau_\varphi}{\tau_R} = \frac{\tau_\perp}{\tau_R} &\simeq \left(\frac{q_s}{\epsilon_s}\right)^2\beta,\\[0.5ex]
+\frac{\tau_{i\,s}}{\tau_R} &\simeq  \left(\frac{q_s}{\epsilon_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/2}\rho_\ast^{\,2}\,\beta^{-1},\\[0.5ex]
+\frac{d_s}{r_s} &\simeq \left(\frac{q_s}{\epsilon_s}\right)\rho_\ast.
+\end{align} 
+Hence, we deduce that 
+\begin{align}
+\hat{\delta}_{\rm VR} = \left(\frac{\tau_{\rm VR}}{\tau_R}\right) \simeq\left(\frac{\tau_H}{\tau_R}\right)^{1/3}\left(\frac{\tau_R}{\tau_\varphi}\right)^{1/6}&\simeq \left(\frac{q_s}{\epsilon_s}\right)^{1/3}\left(\frac{m_e}{m_i}\right)^{1/6}\rho_\ast^{\,2/3}\,\nu_\ast^{\,1/3}\,\beta^{-1/3},\\[0.5ex]
+\hat{\delta}_{\rm HR} = \left(\frac{\tau_{\rm HR}}{\tau_R}\right) \simeq \left(\frac{\tau_H}{\tau_R}\right)^{1/2}\left(\frac{\tau_R}{\tau_\perp}\right)^{1/4}\left(\frac{r_s}{d_s}\right)^{1/2}&\simeq \left(\frac{m_e}{m_i}\right)^{1/4}\rho_\ast^{\,1/2}\,\nu_\ast^{\,1/2}\,\beta^{-1/2},\\[0.5ex]
+\frac{\sqrt{\tau_\varphi\, \tau_{i\,s}/\mu_{00\,s}^i}}{\tau_R}&\simeq \left(\frac{q_s}{r_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/4}\,\rho_\ast.
+\end{align}
+Here, we have treated $\mu_{00\,s}^i$ as an ignorable ${\cal O}(1)$ constant that is independent of $\rho_\ast$, $\nu_\ast$, and
+$\beta$ [as is indeed the case provided that the plasma at the resonant surface lies in the banana collisionality regime (Hirshman \& Sigmar 1981)].
+
+\begin{figure}[t]
+\centerline{\includegraphics[width=0.9\textwidth]{Scaling.pdf}}
+\caption{Error-field penetration regimes in $\hat{\nu}_\ast$-$\hat{\rho}_\ast$ space. The various regimes are the
+visco-resistive-toroidal (${\rm VR}$-$\varphi$), the visco-resistive-poloidal (${\rm VR}$-$\theta$), the Hall-resistive-poloidal (${\rm HR}$-$\theta$), and the  Hall-resistive-toroidal (${\rm HR}$-$\varphi$).
+}\label{f6}
+\end{figure}
+
+There are four error-field penetration regimes depending on whether the plasma response in the resonant layer is
+in the visco-resistive or the Hall-resistive regime, and depending on whether the change in the ion rotation at the resonant surface, induced by the electromagnetic locking torque,  is
+predominately toroidal or poloidal in nature. The plasma response in the resonant layer is in the
+visco-resisitive, rather than the Hall resistive, regime when $\tau_{\rm VR}<\tau_{\rm HR}$, or
+\begin{equation}
+\rho_\ast < \left(\frac{\epsilon_s}{q_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/2}\nu_\ast\,\beta^{-1},
+\end{equation}
+and vice versa. The change in the ion rotation at the resonant surface is predominately toroidal, rather than poloidal, when
+\begin{equation}
+\rho_\ast < \left(\frac{\epsilon_s}{q_s}\right)\left(\frac{m_i}{m_e}\right)^{1/4}\beta,
+\end{equation}
+and vice vera.
+
+Let us define 
+\begin{align}
+\hat{\rho}_\ast&= \left(\frac{q_s}{\epsilon_s}\right)\left(\frac{m_e}{m_i}\right)^{1/4}\rho_\ast,\\[0.5ex]
+\hat{\nu}_\ast&=\left(\frac{\epsilon_s}{q_s}\right)\left(\frac{m_e}{m_i}\right)^{3/4}\nu_\ast.
+\end{align}
+As is illustrated in Figure~\ref{f6}, the {\em visco-resistive-toroidal regime}\/ (i.e., a visco-resistive layer response
+combined with a predominately toroidal change in the ion rotation) corresponds to $\hat{\rho}_\ast < \beta^{-1}\,\nu_\ast$ 
+and $\hat{\rho}_\ast <\beta$, the {\em visco-resisitive-poloidal regime}\/ corresponds to 
+ $\hat{\rho}_\ast<\beta^{-1}\,\nu_\ast$ and $\hat{\rho}_\ast > \beta$, the {\em Hall-resisitive-poloidal regime}\/ corresponds to  
+ $\hat{\rho}_\ast>\beta^{-1}\,\nu_\ast$ and $\hat{\rho}_\ast > \beta$, and the {\em Hall-resistive-toroidal regime}\/ corresponds to   
+ $\hat{\rho}_\ast>\beta^{-1}\,\nu_\ast$ and $\hat{\rho}_\ast < \beta$.
+It can be seen that higher/lower plasma collisionality (i.e., $\nu_\ast$) favors the visco-resistive/Hall-resistive response regime, whereas a
+larger/smaller ion sound radius (i.e., $\rho_\ast$) favors poloidal/toroidal changes in the ion rotation. Finally, higher/lower plasma
+pressure (i.e., $\beta$) 
+favors the Hall-resistive/visco-resistive response regime and toroidal/poloidal changes in the ion rotation.
+
+In the visco-resistive-toroidal response regime, the critical vacuum (i.e., in the absence of shielding currents) radial magnetic
+field at the resonant surface required to
+trigger error-field penetration is
+\begin{equation}\label{e444}
+\left(\frac{b_{r}}{B_z}\right)_{{\rm VR}-\varphi} \simeq \epsilon_s^{-1}\tilde{I}_{c\,{\rm crit}}\simeq \left(\frac{q_s}{\epsilon_s}\right)^{7/6}\left(\frac{m_e}{m_i}\right)^{1/12}
+\rho_\ast^{\,4/3}\,\nu_\ast^{\,1/6}\,\beta^{-1/6},
+\end{equation}
+where we have treated $-{\mit\Delta}_{nw}$ as an ignorable ${\cal O}(1)$ parameter. Likewise,  the critical
+field required to trigger penetration in the visco-resistive-poloidal regime is
+\begin{equation}
+\left(\frac{b_{r}}{B_z}\right)_{{\rm VR}-\theta} \simeq  \left(\frac{q_s}{\epsilon_s}\right)^{2/3}\left(\frac{m_e}{m_i}\right)^{-1/24}
+\rho_\ast^{\,5/6}\,\nu_\ast^{\,1/6}\,\beta^{\,1/3}.
+\end{equation}
+The critical field required to trigger penetration in the Hall-resistive-poloidal regime is
+\begin{equation}
+\left(\frac{b_{r}}{B_z}\right)_{{\rm HR}-\theta} \sim  \left(\frac{q_s}{\epsilon_s}\right)^{1/2}\left(\frac{m_e}{m_i}\right)^{0}
+\rho_\ast^{\,3/4}\,\nu_\ast^{\,1/4}\,\beta^{\,1/4}.
+\end{equation}
+Finally, the critical field 
+required to  trigger penetration in the Hall-resistive-toroidal regime is
+\begin{equation}
+\left(\frac{b_{r}}{B_z}\right)_{{\rm HR}-\varphi} \sim  \left(\frac{q_s}{\epsilon_s}\right)^{}\left(\frac{m_e}{m_i}\right)^{1/8}
+\rho_\ast^{\,5/4}\,\nu_\ast^{\,1/4}\,\beta^{-1/4}.\label{e447}
+\end{equation}
+Generally speaking, ohmically-heated tokamak plasmas all  have similar $\beta$ values. However,
+both $\nu_\ast$ and $\rho_\ast$ are smaller in devices of larger physical size. Hence, Equations~(\ref{e444})--(\ref{e447})
+imply that the error-field penetration threshold is smaller in larger devices.
+
+Let $n$, $T$, $B$, and $R$ represent the typical electron number density, plasma temperature, toroidal magnetic field-strength,
+and physical dimension (i.e., major radius) of an ohmically-heated tokamak. Using $\rho_\ast\sim T^{1/2}\,B^{-1}\,R^{-1}$, 
+$\nu_\ast\sim n\,T^{-2}\,R$, and $\beta\sim n\,T\,B^{-1}$ [see Equations~(\ref{e3.74}), (\ref{e3.83}), and (\ref{e428})--(\ref{e430})],
+we deduce that
+\begin{align}
+\left(\frac{b_{r}}{B_z}\right)_{{\rm VR}-\varphi} &\propto n^{0}\,T^{\,1/6}\,B^{-1}\,R^{-7/6},\\[0.5ex]
+\left(\frac{b_{r}}{B_z}\right)_{{\rm VR}-\theta} &\propto n^{1/2}\,T^{\,5/12}\,B^{-3/2}\,R^{-2/3},\\[0.5ex]
+\left(\frac{b_{r}}{B_z}\right)_{{\rm HR}-\theta} &\propto n^{1/2}\,T^{\,1/8}\,B^{-5/4}\,R^{-1/2},\\[0.5ex]
+\left(\frac{b_{r}}{B_z}\right)_{{\rm HR}-\varphi} &\propto n^{0}\,T^{-1/8}\,B^{-3/4}\,R^{-1}.
+\end{align}
+It can be seen that the error-field penetration threshold exhibits no explicit dependence on the plasma
+density in regimes in which the change in the ion rotation at the resonant surface is predominately toroidal
+in nature (Fitzpatrick 1998; Cole \& Fitzpatrick 2006). On the other hand, the penetration threshold
+scales as $n^{1/2}$ in regimes in which the change in the ion rotation at the resonant surface is predominately poloidal 
+in nature. An $n^{1/2}$ scaling of the penetration threshold has been observed in a number of tokamak
+experiments (Hender, et al.\ 1999; Lazzaro, et al.\ 2002; Park, et al.\ 2012; Wang, et al.\ 2014; Wang, et al.\ 2018). 
+On the other hand, some experiments have reported a linear scaling of the penetration threshold with $n$ (Scoville, et al.\ 1991; Buttery, et al.\ 1999; Wolfe, et al.\ 2005; Wolf, et al.\ 2005; Howell, Hender, \& Cunningham 2007; Menard, et al.\ 2010).
+The latter
+scaling is difficult to account for on the basis of the theory presented in this section.
+
+In order to make further progress, we need to adopt a specific scaling model for the energy confinement timescale, $\tau_E$. Let us adopt
+the following slightly modified version of the well-known neo-Alcator scaling law for low-density ohmically-heated tokamak plasmas (Goldston 1984; Simmet, et al.\ 1996; Fitzpatrick 2012): 
+\begin{equation}
+\tau_E\propto n\,R^{\,13/4}.
+\end{equation}
+[The modification is to ensure that the scaling law is consonant with the Connor-Taylor constraints (Connor \& Taylor 1977).]
+It follows that
+\begin{align}
+\nu_\ast&\propto \rho_\ast^{\,2/3}\,\beta,\\[0.5ex]
+T&\propto B^{\,4/5}\,R^{\,1/2}.
+\end{align}
+Hence, we deduce that 
+\begin{align}\label{e455}
+\left(\frac{b_{r}}{B_z}\right)_{{\rm VR}-\varphi} &\propto n^{0}\,B^{-13/15}\,R^{-13/12},\\[0.5ex]
+\left(\frac{b_{r}}{B_z}\right)_{{\rm VR}-\theta} &\propto n^{1/2}\,B^{-7/6}\,R^{-11/24},\\[0.5ex]
+\left(\frac{b_{r}}{B_z}\right)_{{\rm HR}-\theta} &\propto n^{1/2}\,B^{-23/20}\,R^{-7/16},\\[0.5ex]
+\left(\frac{b_{r}}{B_z}\right)_{{\rm HR}-\varphi} &\propto n^{0}\,B^{-17/20}\,R^{-17/16}.\label{e458}
+\end{align}
+Equations~(\ref{e455})--(\ref{e458}) confirm the $n^{0}$ scaling of the error-field penetration threshold in regimes in which the change in the ion rotation at the resonant surface is predominately toroidal
+in nature, and the $n^{1/2}$ scaling when the change is predominately poloidal.
+All regimes exhibit a roughly linear inverse scaling with increasing magnetic field-strength.
+On the other hand, the regimes in which the threshold scales as $n^{1/2}$ exhibit a
+weaker inverse scaling with machine size (roughly $R^{-1/2}$) than the regimes in which the threshold scales as $n^0$ (which
+exhibit an approximate $R^{-1}$ scaling),
+
+Note, finally, that the analysis presented in this section is only valid provided that the width of the driven magnetic
+island, $W$, at the resonant surface, just prior to error-field penetration, is less than the linear layer width, $\delta$. 
+The ratio of $W$ to $\delta$, just prior to penetration, in the four regimes discussed previously is
+\begin{align}
+\left(\frac{W}{\delta}\right)_{{\rm VR}-\varphi} &\simeq \left(\frac{q_s}{\epsilon_s}\right)^{7/12}\left(\frac{m_e}{m_i}\right)^{1/24}\rho_\ast^{\,1/6}\,\nu_\ast^{\,1/12}\,\beta^{-1/12},\\[0.5ex]
+\left(\frac{W}{\delta}\right)_{{\rm VR}-\theta} &\simeq \left(\frac{q_s}{\epsilon_s}\right)^{1/3}\left(\frac{m_i}{m_e}\right)^{1/48}\rho_\ast^{-1/12}\,\nu_\ast^{\,1/12}\,\beta^{\,1/6},\\[0.5ex]
+\left(\frac{W}{\delta}\right)_{{\rm HR}-\theta} &\simeq \left(\frac{q_s}{\epsilon_s}\right)^{3/4}\left(\frac{m_i}{m_e}\right)^{1/8}\rho_\ast^{\,1/8}\,\nu_\ast^{-1/8}\,\beta^{\,3/8},\\[0.5ex]
+\left(\frac{W}{\delta}\right)_{{\rm HR}-\varphi} &\simeq \left(\frac{q_s}{\epsilon_s}\right)\left(\frac{m_i}{m_e}\right)^{1/16}\rho_\ast^{\,3/8}\,\nu_\ast^{-1/8}\,\beta^{\,1/8}.
+\end{align}
 
@@
 \item Boozer, A.H.\ 1996. {\em Shielding of Resonant Magnetic Perturbations by Rotation}. Phys.\ Plasmas {\bf 3}, 4620.
-\item Braginskii, S.I.\ 1965. {\em Transport Processes in a Plasma}. In {\em Reviews of Plasma Physics}. Consultants Bureau. Vol.~1, 205.
+\item Buttery, R.J., et al.\ 1999. {\em Error Field Mode Studies on JET, COMPASS-D and DIII-D, and Implications for ITER}. Nucl.\ Fusion {\bf 39}, 1827. 
+\item Braginskii, S.I.\ 1965. {\em Transport Processes in a Plasma}. In {\em Reviews of Plasma Physics}.  Vol.~1, 205. Consultants Bureau, New York NY. 
 \item Brau, K., et al.\ 1983. {\em Plasma Rotation in the PDX Tokamak}. Nucl.\ Fusion {\bf 23}, 1643.
-\item Chapman, S., and Cowling, T.G.\ 1953. {\em The Mathematical Theory of Non-Uniform Gases}. Cambridge University Press.
+\item Chapman, S., and Cowling, T.G.\ 1953. {\em The Mathematical Theory of Non-Uniform Gases}. Cambridge University Press, Cambridge UK. 
 \item Chen, X.L., and Morrison, P.J.\ 1990. {\em Resistive Tearing Instability with Equilibrium Shear Flow}. Phys.\ Plasmas {\bf 2}, 495. 
@@
 Plasmas}. Phys.\ Plasmas {\bf 13}, 032503. 
+\item Connor, J.W., and Taylor, J.B.\ 1977. {\em Scaling Laws for Plasma Confinement}. Nucl.\ Fusion {\bf 17}, 1047.
+\item Cowley, S.C.,  Kulsrud, R.M., and Hahm, T.S.\ 1986. {\em Linear Stability of Tearing Modes}. Phys.\ Fluids {\bf 29}, 3230. 
 \item Drake, J.F., and Lee, Y.C.\ 1977. {\em Kinetic Theory of Tearing Instabilities}. Phys.\ Fluids {\bf 20}, 1341.
+\item Fishpool, G.M., and Haynes, P.S.\ 1994. {\em Field Error Instabilities in JET}. Nucl.\ Fusion {\bf 34}, 109. 
 \item Fitzpatrick, R.\ 1993. {\em Interaction of Tearing Modes with External Structures in Cylindrical Geometry}. Nucl.\ Fusion {\bf 33}, 1049. 
@@
 \item Fitzpatrick, R.\ 1998. {\em Bifurcated States of a Rotating Tokamak Plasma in the Presence of a Static Error-Field}. Phys.\ Plasmas {\bf 5}, 3325. 
-\item Fitzpatrick, R.\ 2008. {\em Maxwell's Equations and the Principles of Electromagnetism}. Jones \& Bartlett.
-\item Fitzpatrick, R.\ 2015. {\em Plasma Physics: An Introduction}. Taylor \& Francis, CRC Press. 
+\item Fitzpatrick, R.\ 2008. {\em Maxwell's Equations and the Principles of Electromagnetism}. Jones \& Bartlett, Burlington MA.
+\item Fitzpatrick, R.\ 2012. {\em Nonlinear Error-Field Penetration in Low Density Ohmically Heated Tokamak Plasmas}. Plasma Phys.\ Control.\ Fusion {\bf 54}, 094002.
+\item Fitzpatrick, R.\ 2015. {\em Plasma Physics: An Introduction}. Taylor \& Francis, CRC Press, Boca Raton FL.
 \item Fitzpatrick, R., and Hender, T.C.\ 1994. {\em Effect of a Static External Magnetic Perturbation on Resistive Mode Stability in Tokamaks}. Phys.\ Plasmas {\bf 1}, 3337. 
+\item Fitzpatrick, R., and Nelson, A.O.\ 2020.
+{\em An Improved Theory of the Response of DIII-D H-mode Discharges to Static Resonant Magnetic Perturbations and its Implications for the Suppression of Edge Localized Modes}.
+Phys.\ Plasmas {\bf 27}, 072501.
 \item Fitzpatrick, R., and Waelbroeck, F.L.\ 2005. {\em Two-Fluid Magnetic Island Dynamics in Slab Geometry. I. Isolated Islands}.
@@
 Phys.\ Plasmas {\bf 16}, 072507.
+\item Freidberg, J.P.\ 1987. {\em Ideal Magnetohydrodynamics}. Plenum, New York NY. 
 \item Furth, H.P., Killeen, J., and Rosenbluth, M.N.\ 1963. {\em Finite-Resistivity Instabilities of a Sheet Pinch}. Phys.\ Fluids {\bf 6}, 459.
@@
 Based on the Four-Field Reduced Neoclassical MHD Equation}. J.\ Phys.\ Soc.\ Japan {\bf 72}, 313.
+\item Gimblett, C.G., and Peckover, R.S.\ 1979. {\em On the Mutual Interaction Between Rotation and Magnetic Fields
+for Axisymmetric Bodies.} Proc.\ Roy.\ Soc.\ London {\bf 369}, 1732. 
+\item Goldston, R.J. 1984. {\em Energy Confinement Scaling in Tokamaks: Some Implications of Recent Experiments with Ohmic and Strong Auxiliary Heating}. Plasma Phys.\ Control.\ Fusion {\bf 26}, 87. 
+\item Hammett, G.W., Dorland, W., and Perkins, F.W.\ 1992.  {\em Fluid Models of Phase Mixing, Landau Damping, and Nonlinear Gyrokinetic Dynamics}. Phys.\ Fluids B {\bf 4}, 2052. 
 \item Hazeltine, R.D., Kotschenreuther, M., and Morrison, P.G.\ 1985. {\em A Four-Field Model for Tokamak Plasma Dynamics}.
@@
 \item Hazeltine, R.D., and Meiss, J.D.\ 1985. {\em Shear-Alfv\'{e}n Dynamics of Toroidally Confined Plasmas}. Physics Reports {\bf 121}, 1.
-\item Hazeltine, R.D., and Meiss, J.D.\ 1992. {\em Plasma Confinement}. Addison-Wesley. 
+\item Hazeltine, R.D., and Meiss, J.D.\ 1992. {\em Plasma Confinement}. Addison-Wesley, Redwood City CA. 
+\item Hender, T.C., et al.\ 1992. {\em Effect of Resonant Magnetic Perturbations on COMPASS-C Tokamak Discharges}. Nucl.\ Fusion
+{\bf 32}, 2091.  
 \item Hirshman, S.P.\ 1978. {\em The Ambipolarity Paradox in Toroidal Diffusion, Revisited}. Nucl.\ Fusion {\bf 18}, 917.
 \item Hirshman, S.P., and Sigmar, D.J.\ 1981.\ {\em Neoclassical Transport of Impurities in Tokamak Plasmas}. Nucl.\ Fusion {\bf 21}, 1079.
+\item Howell, D.F., Hender, T.C., and Cunningham, G.\ 2007. {\em Locked mode Thresholds on the MAST Spherical Tokamak}. Nucl.\ Fusion {\bf 47}, 1336. 
+\item ITER Physics Basis Editors 1999. {\em Plasma Confinement and Transport}. Nucl.\ Fusion {\bf 39}, 2175. 
+\item Lazzaro, E., et al.\ 2002. {\em Error Field Locked Modes Thresholds in Rotating Plasmas, Anomalous Braking and Spin-Up}. Phys.\ Plasmas {\bf 9}, 3906. 
+\item Menard, J.E., et al.\ 2010. {\em Progress in Understanding Error-Field Physics in NSTX Spherical Torus Plasmas}. Nucl.\ Fusion {\bf 50}, 045008.
+\item Monier-Garbet, P., et al.\ 1997. {\em Effects of Neutrals on Plasma Rotation in DIII-D}. Nucl.\ Fusion {\bf 37}, 403.
 \item Nave, M.F.F., and Wesson, J.A., 1990. {\em Mode Locking in Tokamaks}. Nucl.\ Fusion {\bf 30}, 2575. 
-\item Monier-Garbet, P., et al.\ 1997. {\em Effects of Neutrals on Plasma Rotation in DIII-D}. Nucl.\ Fusion {\bf 37}, 403.
-\item Reif, F.\ 1965. {\em Fundamentals of Statistical and Thermal Physics}. McGraw-Hill.
-\item Richardson, A.S.\ 2019. {\em 2019 NRL Plasma Formulary}.  Naval Research Laboratory.
+\item Park, J.-K., et al.\ 2012. {\em  Sensitivity to Error Fields in NSTX High $\beta$ Plasmas}. Nucl.\ Fusion {\bf 52}, 023004. 
+\item Reif, F.\ 1965. {\em Fundamentals of Statistical and Thermal Physics}. McGraw-Hill, New York NY. 
+\item Richardson, A.S.\ 2019. {\em 2019 NRL Plasma Formulary}.  Naval Research Laboratory, Washington DC. 
+\item Scoville, J.T., et al.\ 1991. {\em Locked Modes in DIII-D and a Method for Prevention of the Low Density Mode}. Nucl.\ Fusion {\bf 31}, 875. 
+\item Simmet, E.E., et al.\ 1996. {\em Statistical Analysis of the Global Energy Confinement Time in Ohmic Discharges in the ASDEX Tokamak}. Plasma Phys.\ Control.\ Fusion {\bf 38}, 689.
 \item Stix, T.H.\ 1973. {\em Decay of Poloidal Rotation in a Tokamak Plasma}. Phys.\ Fluids {\bf 16}, 1260.
@@
 \item Waelbroeck, F.L.\ 2003. {\em Shielding of Resonant Magnetic Perturbations in the Long Mean-Free Path Regime}. Phys.\ Plasmas {\bf 10}, 4040.
+\item Waelbroeck, F.L., Hazeltine, R.D., and Morrison, P.J.\ 2009. {\em A Hamiltonian Electromagnetic Gyrofluid Model}. Phys.\ Plasmas {\bf 16}, 032109. 
 \item Waelbroeck, F.L., et al.\ 2012. {\em Role of Singular Layers in the Plasma Response to Resonant Magnetic Perturbations}.
 Nucl.\ Fusion {\bf 52}, 074004.
-\item Wesson, J.\  1978. {\em Hydrodynamic Stability of Tokamaks}. Nucl.\ Fusion {\bf 18}, 87.
-\item Wesson, J.\ 2011. {\em Tokamaks}. Oxford University Press. 
+\item Wang, H.-H., et al.\ 2018. {\em Density Scaling on $n=1$ Error Field Penetration in Ohmically Heated Discharges in EAST}. 
+Nucl.\ Fusion {\bf 58}, 056024. 
+\item Wang, N., et al.\ 2014. {\em Study of the Penetration of Resonant Magnetic Perturbations in J-TEXT}. Nucl.\ Fusion {\bf 54}, 064014. 
+\item Wesson, J.A.\  1978. {\em Hydrodynamic Stability of Tokamaks}. Nucl.\ Fusion {\bf 18}, 87.
+\item Wesson, J.A.\ 2011. {\em Tokamaks}. Oxford University Press, Oxford UK.
+\item Wesson, J.A., et al.\ 1989. {\em Disruptions in JET}. Nucl.\ Fusion {\bf 29}, 641. 
+\item Wolf, R.C., et al.\ 2005. {\em Effect of the Dynamic Ergodic Divertor in the TEXTOR Tokamak on MHD Stability, Plasma Rotation and Transport}. Nucl.\ Fusion {\bf 45}, 1700. 
+\item Wolfe, S.M., et al.\ 2005. {\em Nonaxisymmetric Field Effects on Alcator C-Mod}. Phys.\ Plasmas {\bf 12}, 056110. 
 \end{description}

### 2021-11-13 Documentation/Bessel.py

@@ -1,0 +1,70 @@
+import scipy.special as sc
+import matplotlib.pyplot as plt
+import numpy as np
+import math
+
+N = 1000
+eps = 0.01
+
+j0p = sc.jn_zeros(0, N)
+j1p = sc.jn_zeros(1, N)
+
+def Sum1(x):
+
+    sum = 0.
+    for i in range(0, N):
+        sum = sum + sc.jn(0, j0p[i]*x) * sc.jn(0, j0p[i]*x) /sc.jn(1, j0p[i])/sc.jn(1, j0p[i]) /j0p[i]/j0p[i]
+
+    return sum
+
+sum1 = np.vectorize(Sum1)
+
+def Log(x):
+
+    return 0.5*math.log(1./x)
+
+logg = np.vectorize(Log)
+
+def Sum2(x):
+
+    sum = 0.
+    for i in range(0, N):
+        sum = sum + sc.jn(1, j1p[i]*x) * sc.jn(1, j1p[i]*x) /sc.jn(2, j1p[i])/sc.jn(2, j1p[i]) /(1. + eps*j1p[i]*j1p[i])
+
+    return sum*eps**0.5
+
+sum2 = np.vectorize(Sum2)
+
+def Exp(x):
+
+    return 0.25/x
+
+expp = np.vectorize(Exp)
+
+x1 = np.arange (0.01, 1., 1.e-3)
+np.append(x1, 1.)
+
+plt.plot(x1, sum1(x1), linewidth=2, color='blue')
+plt.plot(x1, logg(x1), linewidth=2, linestyle='dashed', color='red')
+
+x2 = np.arange (0.01, 1., 1.e-3)
+np.append(x2, 1.)
+
+plt.xlim(0.,1.)
+plt.ylim(0.,3.)
+plt.xlabel(r'$r_s/a$', fontsize=16)
+plt.ylabel(r'$F_\theta,\, F_\varphi$', fontsize=16)
+
+eps = 1.e-3
+#plt.plot(x2, sum2(x2), linewidth=2, color='green')
+
+eps = 1.e-4
+plt.plot(x2, sum2(x2), linewidth=2, color='green')
+
+eps = 1.e-5
+plt.plot(x2, expp(x2), linewidth=2, linestyle='dashed', color='red')
+
+#plt.savefig("Bessel.pdf")
+
+plt.show()
+

### 2021-11-13 Documentation/Island.py

@@ -24,9 +24,10 @@ def xxm(t):
 
 XXminus= np.vectorize(xxm)
 
-t1 = np.arange(0., 4., 1.e-3)
+t1 = np.arange(0., 6., 1.e-3)
 t2 = np.arange(0.5000000001, 1.49999999999, 1.e-4)
 t3 = t2 + 2.
+t4 = t3 + 2.
 
 F = 1.
 plt.plot(t1, Xplus(t1), linewidth=2, color='red')
@@ -60,23 +61,76 @@ F = 8.0
 plt.plot(t1, Xplus(t1), linewidth=2, color='blue')
 plt.plot(t1, Xminus(t1), linewidth=2, color='blue')
 
+F = 9.0
+plt.plot(t1, Xplus(t1), linewidth=2, color='blue')
+plt.plot(t1, Xminus(t1), linewidth=2, color='blue')
+
+F = 10.
+plt.plot(t1, Xplus(t1), linewidth=2, color='blue')
+plt.plot(t1, Xminus(t1), linewidth=2, color='blue')
+
+F = 11.
+plt.plot(t1, Xplus(t1), linewidth=2, color='blue')
+plt.plot(t1, Xminus(t1), linewidth=2, color='blue')
+
+F = 12.
+plt.plot(t1, Xplus(t1), linewidth=2, color='blue')
+plt.plot(t1, Xminus(t1), linewidth=2, color='blue')
+
+F = 13.
+plt.plot(t1, Xplus(t1), linewidth=2, color='blue')
+plt.plot(t1, Xminus(t1), linewidth=2, color='blue')
+
+F = 14.
+plt.plot(t1, Xplus(t1), linewidth=2, color='blue')
+plt.plot(t1, Xminus(t1), linewidth=2, color='blue')
+
+F = 15.
+plt.plot(t1, Xplus(t1), linewidth=2, color='blue')
+plt.plot(t1, Xminus(t1), linewidth=2, color='blue')
+
+F = 16.
+plt.plot(t1, Xplus(t1), linewidth=2, color='blue')
+plt.plot(t1, Xminus(t1), linewidth=2, color='blue')
+
+F = 17.
+plt.plot(t1, Xplus(t1), linewidth=2, color='blue')
+plt.plot(t1, Xminus(t1), linewidth=2, color='blue')
+
+F = 18.
+plt.plot(t1, Xplus(t1), linewidth=2, color='blue')
+plt.plot(t1, Xminus(t1), linewidth=2, color='blue')
[…]

### 2021-11-16 Documentation/TearingModeTheory.tex
Latest version

@@
 
-If we assume that $\delta_e\sim \zeta_e\sim \mu\ll 1$ then the dominant terms in the electron energy conservation equation
-(\ref{e3.151c}) yield
+If we assume that $\delta_e\sim \zeta_e\sim \mu\ll 1$ then the dominant term in the electron energy conservation equation
+(\ref{e3.151c}) yields
 \begin{equation}
@@
 sufficiently large that it forces the electron temperature to be constant on magnetic flux-surfaces. 
-Likewise, if we assume that $\delta_i\sim \zeta_i\sim \mu\ll 1$ then the dominant terms in the ion energy conservation equation
-(\ref{e3.152c}) yield
+Likewise, if we assume that $\delta_i\sim \zeta_i\sim \mu\ll 1$ then the dominant term in the ion energy conservation equation
+(\ref{e3.152c}) yields
 \begin{equation}
@@
 It follows from the previous equation that 
-\begin{equation}
+\begin{equation}\label{e81}
 {\bf B}\cdot\nabla p\simeq 0.
@@
 magnetic flux-surfaces.
+
+Let us make the reasonable assumption that Equation~(\ref{e81}) implies that ${\bf B}\cdot\nabla p_e={\bf B}\cdot\nabla
+p_i=0$.
+In other words, the electron and ion pressures are separately constant on magnetic flux-surfaces.
+If we assume that, to lowest order, ${\bf E}=-\nabla{\mit\Phi}$, where ${\mit\Phi}$ is the electrostatic potential, then Equations~(\ref{e78})
+and (\ref{e79}) yield
+\begin{equation}
+{\bf B}\cdot\nabla{\mit\Phi}=0.
+\end{equation}
+In other words,  the electrostatic potential is also constant on magnetic flux-surfaces.
 
@@
 \subsection{Solution in Presence of Perfectly-Conducting Wall}\label{perfect}
-Suppose that the plasma occupies the region $0\leq r\leq a$, where $a$ is the plasma {\em minor radius}. It follows that
+Suppose that the plasma occupies the region $0\leq r\leq a$, where $a$ is the plasma {\em minor radius}. (By definition, $a\ll R_0$ in a large aspect-ratio tokamak.( It follows that
 $J_z(r)=0$ for $r>a$. Let the plasma be surrounded by a concentric, rigid, radially-thin, perfectly-conducting, wall of radius $r_w>a$. 
-(By definition, $a\ll R_0$ in a large aspect-ratio tokamak. In most circumstances, the wall represents the metal vacuum vessel that surrounds  the plasma.) An appropriate
+(In most circumstances, the wall represents the metal vacuum vessel that surrounds  the plasma.) An appropriate
 physical solution of the cylindrical tearing mode equation takes the separable form
@@
 \end{equation}
-where $E_{ss}= {\mit\Delta}_{s+}-{\mit\Delta}_{s-}$ is a real dimensionless quantity that is known as the {\em tearing stability index}\/ (Furth, et al.\ 1963).
+where $E_{ss}= {\mit\Delta}_{s+}-{\mit\Delta}_{s-}$ is a real dimensionless quantity that is known as the {\em tearing stability index}\/ (Furth, Killeen \& Rosenbluth 1963).
 
@@
 \subsection{Solution of Plasma Angular Equations of Motion}
-In general, the perturbed angular velocity profiles, ${\mit\Delta\Omega}_\theta(r,t)$ and ${\mit\Delta\Omega}_\varphi(r,t)$, are
+In most situations of interest, the perturbed angular velocity profiles, ${\mit\Delta\Omega}_\theta(r,t)$ and ${\mit\Delta\Omega}_\varphi(r,t)$, are
 localized in the vicinity of the resonant surface (Fitzpatrick 1993). Hence, it is reasonable to express  the perturbed angular
@@
 
-Equations~(\ref{e220})--(\ref{e223}) are known collectively as the {\em drift-MHD equations},\footnote{The 'drift' appellation  merely indicates that we are taking diamagnetic flows into account.} and contain both shear-Alfv\'{e}n
+Equations~(\ref{e220})--(\ref{e223}) are known collectively as the {\em drift-MHD equations},\footnote{The  `drift' appellation  merely indicates that we are taking diamagnetic flows into account.} and contain both shear-Alfv\'{e}n
 and compressible-Alfv\'{e}n wave dynamics. The system of equations is completed by a subset of Maxwell's equations:
@@
 
-Strictly speaking, the analysis
+Strictly speaking, the four-field fluid model 
 presented in this section is only valid when the ion gyroradius is smaller than the typical variation lengthscale in the resonant layer. 
@@
 analysis is valid. 
-Note, however, that the ion sound radius is finite even when the ions are cold. In the following, we shall assume that the
-analysis is valid even when the ions are hot.
+Note, however, that the ion sound radius is finite even when the ions are cold. In the following, we shall assume that our model remains valid even when the ions are hot.
 
@@
 However, a resonant layer is
-characterized by a balance between plasma inertia and resistive diffusion (Furth, et al.\ 1963). Such a balance is
+characterized by a balance between plasma inertia and resistive diffusion (Furth, Killeen \& Rosenbluth 1963). Such a balance is
 only possible if the layer is very narrow in the radial direction (because a narrow layer enhances radial derivatives, and, thereby, enhances
@@
 for $p\lesssim {\cal O}(Q^{1/2})$, where use has been made of Equation~(\ref{e325}). The two-layer  approximation is
-equivalent to the well-known {\em constant-$\psi$ approximation}\/ (Furth, et al.\ 1963).
+equivalent to the well-known {\em constant-$\psi$ approximation}\/ (Furth, Killeen \& Rosenbluth 1963).
 
@@
 This response regime is known as the {\em resistive-inertial regime}, because the layer response is dominated by
-resistivity and ion inertia (Furth, et al.\ 1963; Ara, et al.\ 1976; Fitzpatrick 1998). The characteristic layer width is $p_\ast \sim Q^{-1/4}$,
+resistivity and ion inertia (Furth, Killeen \& Rosenbluth 1963; Ara, et al.\ 1976; Fitzpatrick 1998). The characteristic layer width is $p_\ast \sim Q^{-1/4}$,
 which implies that the regime is valid when $P\ll Q^{3/2}$, $Q\gg D^4$, and $Q\ll 1$.
@@
 tearing mode has reconnected magnetic field-lines to produce a {\em helical magnetic island chain}\/ centered on the resonant
-surface. The chain has $m$ periods in the poloidal direction, $n$ periods in the toroidal direction, and propagates at the
+surface ($\hat{x}=0$). The chain has $m$ periods in the poloidal direction, $n$ periods in the toroidal direction, and propagates at the
 helical phase velocity $\omega$. The maximum full (as opposed to half) radial width of the magnetic separatrix is 
@@
 \subsection{Discussion}
-According to Equations~(\ref{e350}), (\ref{e353}), (\ref{e363}), (\ref{e365}), (\ref{e368}), and (\ref{e371}), a linear tearing mode is unstable when the tearing stability index, $E_{ss}$, is positive, and is stable otherwise (Furth, et al.\ 1963).
+According to Equations~(\ref{e350}), (\ref{e353}), (\ref{e363}), (\ref{e365}), (\ref{e368}), and (\ref{e371}), a linear tearing mode is unstable when the tearing stability index, $E_{ss}$, is positive, and is stable otherwise (Furth, Killeen \& Rosnebluth 1963).
 Moreover, the perturbed magnetic field associated with the mode corotates with the electron fluid at the resonant surface (Ara, et al.\ 1978). Finally,
@@
 in the limit that $S\rightarrow\infty$. In other words, magnetic reconnection at the resonant surface (which corresponds to a finite
-$\tilde{\psi}$ at $\hat{x}=0$) is impossible in the absence of plasma resistivity (Furth, et al.\ 1963).
+$\tilde{\psi}$ at $\hat{x}=0$) is impossible in the absence of plasma resistivity (Furth, Killeen \& Rosenbluth 1963).
 
@@
 layers in tokamak plasmas are invariably very thin compared to the minor radius of the plasma). However,
-low-$m$ tearing modes in conventional tokamak plasmas are characterized by $|E_{ss}|\sim 1$ rather than
+low-$m$ tearing modes in conventional tokamak plasmas are characterized by $|E_{ss}|\sim {\cal O}(1)$ rather than
 $|E_{ss}|\gg 1$. (As before, we are neglecting $m=1$ modes, which are characterized by
@@
 \begin{equation}\label{e384}
-\hat{\mit\Psi}_s = \frac{\tilde{I}}{(-{\mit\Delta}_{nw}) + {\mit\Delta}},
+\hat{\mit\Psi}_s = \frac{\tilde{I}_c}{(-{\mit\Delta}_{nw}) + {\mit\Delta}},
 \end{equation}
@@
 \begin{equation}
-v \simeq \frac{1}{2}\left(1-\left[1-\left(\frac{|\tilde{I}_c|}{\tilde{I}_{c\,{\rm crit}}}\right)^2\right]^{1/2}.
-\right)
+v \simeq \frac{1}{2}\left(1-\left[1-\left(\frac{|\tilde{I}_c|}{\tilde{I}_{c\,{\rm crit}}}\right)^2\right]^{1/2}
+\right).
 \end{equation}
@@
 field at the resonant surface required to
-trigger error-field penetration is
+trigger error-field penetration is (Cole \& Fitzpatrick 2006)
 \begin{equation}\label{e444}
@@
 weaker inverse scaling with machine size (roughly $R^{-1/2}$) than the regimes in which the threshold scales as $n^0$ (which
-exhibit an approximate $R^{-1}$ scaling),
+exhibit an approximate $R^{-1}$ scaling). [In fact, it is easily demonstrated that if 
+$b_r/B_z\propto n^{\,\alpha_n}\,B^{\,\alpha_B}\,R^{\,\alpha_R}$ then $\alpha_R = 2\,\alpha_n+1.25\,\alpha_B$. (Buttery, et al.\ 1999).]
 

### 2021-11-20 Documentation/TearingModeTheory.tex
Started Section 8

@@
 \author{R.~Fitzpatrick\,\footnote{rfitzp@utexas.edu}\\
-Institute for Fusion St udies,\\  Department of Physics,\\  University of Texas at Austin,\\  Austin TX 78712, USA}
+Institute for Fusion Studies,\\  Department of Physics,\\  University of Texas at Austin,\\  Austin TX 78712, USA}
 \date{}
@@
 \subsection{Solution in Presence of Perfectly-Conducting Wall}\label{perfect}
-Suppose that the plasma occupies the region $0\leq r\leq a$, where $a$ is the plasma {\em minor radius}. (By definition, $a\ll R_0$ in a large aspect-ratio tokamak.( It follows that
+Suppose that the plasma occupies the region $0\leq r\leq a$, where $a$ is the plasma {\em minor radius}. (By definition, $a\ll R_0$ in a large aspect-ratio tokamak.) It follows that
 $J_z(r)=0$ for $r>a$. Let the plasma be surrounded by a concentric, rigid, radially-thin, perfectly-conducting, wall of radius $r_w>a$. 
@@
 \begin{align}\label{e188}
-4\pi^2\,R_0\left[(1+2\,q_s^{\,2})\,\rho_s\,r^{\,3}\,\frac{\partial {\mit\Delta\Omega}_\theta}{\partial t}+ \frac{\rho_s}{\tau_{\theta\,s}}\,r^{\,3}\,{\mit\Delta\Omega}_\theta-\mu_{\perp\,s}\frac{\partial}{\partial r}\!\left(r^{\,3}\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial r}\right)\right]
+4\pi^2\,R_0\left[(1+2\,q_s^{\,2})\,\rho_s\,r^{\,3}\,\frac{\partial {\mit\Delta\Omega}_\theta}{\partial t}+ \frac{\rho_s}{\tau_{\theta\,s}}\,r^{\,3}\,{\mit\Delta\Omega}_\theta-\mu_{\perp\,s}\,\frac{\partial}{\partial r}\!\left(r^{\,3}\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial r}\right)\right]
 &=T_{\theta\,s}\,\delta(r-r_s),\\[0.5ex]
-4\pi^2\,R_0^{\,3}\left[\rho_s\,r\,\frac{\partial {\mit\Delta\Omega}_\varphi}{\partial t}-\mu_{\perp\,s}\frac{\partial}{\partial r}\!\left(r\,\frac{\partial{\mit\Delta\Omega}_\varphi}{\partial r}\right)\right]
+4\pi^2\,R_0^{\,3}\left[\rho_s\,r\,\frac{\partial {\mit\Delta\Omega}_\varphi}{\partial t}-\mu_{\perp\,s}\,\frac{\partial}{\partial r}\!\left(r\,\frac{\partial{\mit\Delta\Omega}_\varphi}{\partial r}\right)\right]
 =T_{\varphi\,s}\,\delta(r-r_s),\label{e189}
@@
 
-\section{Reduced Drift-MHD Resonant  Response Model}
+\section{Reduced Drift-MHD Resonant  Response Model}\label{ff}
 \subsection{Introduction}
@@
 Hence, one very effective way of simplifying the resonant layer equations is to remove the
-physics of a compressible-Alfv\'{e}n wave from them altogether, in the process converting a drift-magnetohydrodynamical (MHD) response model
-into a so-called {\em reduced}\/ drift-MHD response model (Strauss 1976; Hazeltine, et al.\ 1985; Furuya, et al.\ 2003). The aim of
+physics of  compressible-Alfv\'{e}n waves from them altogether, in the process converting a drift-magnetohydrodynamical (MHD) response model
+into a so-called {\em reduced}\/ drift-MHD response model (Strauss 1976; Hazeltine, Kotschenreuther \& Morrison 1985; 
+Furuya, Yagi \& Itoh 2003). The aim of
 this section is to describe the reduction process (which essentially boils down to arguing that the divergence of the
@@
 \end{equation}
-Here, $\eta_\parallel=1/\sigma_\parallel$ and $\eta_\perp=1/\sigma_\perp$ are the parallel and perpendicular plasma
-resistivities,  respectively. (See Section~\ref{sbrag}.) We have neglected the cross term in Equation~(\ref{e3.91a})
+Here, $\eta_\parallel=1/\sigma_\parallel(r_s)$ and $\eta_\perp=1/\sigma_\perp(r_s)$ are the parallel and perpendicular plasma
+resistivities,  respectively, at the resonant surface. (See Section~\ref{sbrag}.) We have neglected the cross term in Equation~(\ref{e3.91a})
 because it is a factor $({\mit\Omega}_e\,\tau_e)^{-1}$  smaller than $\nabla p$. Incidentally, if we assume that all
@@
 \end{equation}
-which automatically satisfies Equation~(\ref{e230}).
-(Recall that we are assuming that $|r-r_s|\ll r_s$ inside the resonant layer.) Note that $\hat{\psi}=\psi/(r_s\,B_z)$, where $\psi$ is defined in Equation~(\ref{e93}).
+which automatically satisfies Equation~(\ref{e230}). Note that $\hat{\psi}=\psi/(r_s\,B_z)$, where $\psi$ is defined in Equation~(\ref{e93}).
  Here, $\delta b(\hat{x},\zeta)$ and $\hat{\psi}(\hat{x},\zeta)$ are assumed to be small
@@
 \end{align}
-where $\hat{\nabla}_\perp^{\,2}\equiv \hat{\nabla}\cdot\hat{\nabla}_\perp$, $\chi_{\parallel\,e,i} = \kappa_{\parallel\,e,i}/n_0$, $\chi_{\perp\,e,i} = \kappa_{\perp\,e,i}/n_0$, $\hat{\chi}_{\parallel\,e,i}=
+where $\hat{\nabla}_\perp^{\,2}\equiv \hat{\nabla}\cdot\hat{\nabla}_\perp$, $\chi_{\parallel\,e,i} = \kappa_{\parallel\,e,i}(r_s)/n_0$, $\chi_{\perp\,e,i} = \kappa_{\perp\,e,i}(r_s)/n_0$, $\hat{\chi}_{\parallel\,e,i}=
 \chi_{\parallel\,e,i}/(l\,V_A)$,  $\hat{\chi}_{\perp\,e,i}=
@@
 \end{equation}
-where $\chi_\varphi = \mu_{\perp}/(n_0\,m_i)$, $\hat{\chi}_\varphi = \chi_\varphi/(l\,V_A)$, and $\mu_\perp$ is the anomalous
+where $\chi_\varphi = \mu_{\perp}(r_s)/(n_0\,m_i)$, $\hat{\chi}_\varphi = \chi_\varphi/(l\,V_A)$, and $\mu_\perp(r)$ is the anomalous
 ion perpendicular viscosity. Note that the previous equation is entirely phenomenological in nature.  It is easily seen that
@@
 \end{align}
-(Here, we are neglecting any $\hat{x}$ dependence of the various $\chi$ parameters for ease of notation.)
-
-Let us define $V=\hat{V}_{\parallel\,i}$ and $N=\delta p/c_\beta$.
+
+\subsection{Four-Field Model}\label{fourf}
+Let us define $V=\hat{d}_i\,\hat{V}_{\parallel\,i}$ and $N=-\hat{d}_i\,\delta p$.
 Equations~(\ref{eJ}), (\ref{e252})--(\ref{e254}), (\ref{e256}), (\ref{e258})--(\ref{e260}), (\ref{e262}), and (\ref{e263}) yield the following closed set of equations (Fitzpatrick \& Waelbroeck 2005):
 \begin{align}\label{e264}
-\frac{\partial\hat{\psi}}{\partial\hat{t}}&= [\phi,\hat{\psi}] + \hat{d}_\beta\!\left(\frac{\tau}{1+\tau}\right)\left(1+\frac{0.71\,\eta_e}{1+\eta_e}\right)[N,\hat{\psi}]
+\frac{\partial\hat{\psi}}{\partial\hat{t}}&= [\phi,\hat{\psi}] -\left(\frac{\tau}{1+\tau}\right)(1+\lambda_e)\,[N,\hat{\psi}]
 +\hat{\eta}_\parallel\,J + \hat{E}_\parallel,\\[0.5ex]
-\frac{\partial U}{\partial \hat{t}}&= [\phi,U] + \frac{\hat{d}_\beta}{2\,(1+\tau)}\left(\hat{\nabla}^2[\phi,N] + [\hat{\nabla}^2\phi,N] + [\hat{\nabla}^2 N,\phi]\right) + [J,\hat{\psi}] \nonumber\\[0.5ex]&\phantom{=}+\hat{\chi}_\varphi  \,\hat{\nabla}^4\!\left(\phi - \frac{\hat{d}_\beta\,N}{1+\tau}\right),\label{e265} \\[0.5ex]
-\frac{\partial N}{\partial \hat{t}}&= [\phi,N] -c_\beta\,[V,\hat{\psi}] -\hat{d}_\beta\,[J,\hat{\psi}] + \hat{D}_\parallel\,[[N,\hat{\psi}],\hat{\psi}]
+\frac{\partial U}{\partial \hat{t}}&= [\phi,U] - \frac{1}{2\,(1+\tau)}\left(\hat{\nabla}^2[\phi,N] + [\hat{\nabla}^2\phi,N] + [\hat{\nabla}^2 N,\phi]\right) + [J,\hat{\psi}] \nonumber\\[0.5ex]&\phantom{=}+\hat{\chi}_\varphi  \,\hat{\nabla}^4\!\left(\phi + \frac{N}{1+\tau}\right),\label{e265} \\[0.5ex]
+\frac{\partial N}{\partial \hat{t}}&= [\phi,N] +c_\beta^{\,2}\,[V,\hat{\psi}] +\hat{d}_\beta^{\,2}\,[J,\hat{\psi}] + \hat{D}_\parallel\,[[N,\hat{\psi}],\hat{\psi}]
 + \hat{D}_\perp\,\hat{\nabla}_\perp^{\,2}N,\label{e266}\\[0.5ex]
-\frac{\partial V}{\partial\hat{t}}&= [\phi,V] - c_\beta\,[N,\hat{\psi}] + \hat{\chi}_\varphi\,\hat{\nabla}^2 V,\label{e267}\\[0.5ex]
+\frac{\partial V}{\partial\hat{t}}&= [\phi,V] +[N,\hat{\psi}] + \hat{\chi}_\varphi\,\hat{\nabla}^2 V,\label{e267}\\[0.5ex]
 J &=-\frac{2}{q_s\,\hat{R}_0}+\hat{\nabla}^2\hat{\psi},\\[0.5ex]
@@
 \end{align}
-Here, 
-\begin{align}\label{e270}
-d_\beta &= c_\beta\,d_i = \left(\frac{{\mit\Gamma}}{1+\beta}\right)^{1/2}\rho_s,\\[0.5ex]
- \rho_s &= \frac{v_t}{{\mit\Omega}_i},\\[0.5ex]
-v_t &= \left(\frac{T_e+T_i}{m_i}\right)^{1/2},
-\end{align}
-and $\hat{d}_\beta=d_\beta/l$. The quantity $\rho_s$ is usually referred to as the {\em ion sound radius}. 
+Here, the quantity 
+\begin{equation}\label{e270}
+d_\beta = c_\beta\,d_i 
+\end{equation}
+ is usually referred to as the {\em ion sound radius}, and $\hat{d}_\beta =d_\beta/l$. 
 Moreover,
-\begin{align}
-\hat{D}_\parallel&= \frac{2}{3}\left(1-c_\beta^{\,2}\right)\!\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\parallel\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\parallel\,i}\right),\\[0.5ex]
-\hat{D}_\perp &= c_\beta^{\,2}\,\hat{\eta}_\perp +  \frac{2}{3}\left(1-c_\beta^{\,2}\right)\!\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\perp\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\perp\,i}\right).
+\begin{equation}
+ \lambda_e = 0.71\left(\frac{\eta_e}{1+\eta_e}\right),
+\end{equation}
+and
+\begin{align}
+\hat{D}_\parallel&=\frac{D_{\parallel}}{l\,V_A}= \frac{2}{3}\left(1-c_\beta^{\,2}\right)\!\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\parallel\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\parallel\,i}\right),\\[0.5ex]
+\hat{D}_\perp &=\frac{D_{\perp}}{l\,V_A}= c_\beta^{\,2}\,\hat{\eta}_\perp +  \frac{2}{3}\left(1-c_\beta^{\,2}\right)\!\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\perp\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\perp\,i}\right).
 \end{align}
@@
 averaged over the ion gyro-orbits (Cowley, Kulsrud \& Hahm 1986; Hammett, Dorland \& Perkins 1992; Waelbroeck, Hazeltine \& Morrison 2009).
-Of course, if the ions are cold (i.e., $T_i\ll T_e$) then the ion gyroradius tends to zero,  which means that the
-analysis is valid. 
-Note, however, that the ion sound radius is finite even when the ions are cold. In the following, we shall assume that our model remains valid even when the ions are hot.
-
-If we neglect $\hat{d}_\beta$ in our reduced drift-MHD model, which is equivalent to saying that the ion sound
-radius is much smaller than the radial extent of the resonant layer, then our four-field resonant response model
-decouples into two independent two-field models. The first two-field model takes the form:
-\begin{align}\label{e275}
-\frac{\partial\hat{\psi}}{\partial\hat{t}}&= [\phi,\hat{\psi}]+\hat{\eta}_\parallel\,J + \hat{E}_\parallel,\\[0.5ex]
-\frac{\partial U}{\partial \hat{t}}&= [\phi,U]  + [J,\hat{\psi}]+\hat{\chi}_\perp  \,\hat{\nabla}^4\phi.\label{e276}
-\end{align}
-Of course, this is a {\em reduced MHD model}\/ that describes shear-Alfv\'{e}n dynamics perpendicular to
-magnetic field-lines (Strauss 1976). The second two-field model takes the form:
-\begin{align}
-\frac{\partial N}{\partial \hat{t}}&= [\phi,N] -c_\beta\,[V,\hat{\psi}] + \hat{D}_\parallel\,[[N,\hat{\psi}],\hat{\psi}]
-+ \hat{D}_\perp\,\hat{\nabla}_\perp^{\,2}N,\\[0.5ex]
-\frac{\partial V}{\partial\hat{t}}&= [\phi,V] - c_\beta\,[N,\hat{\psi}] + \hat{\chi}_\phi\,\hat{\nabla}^2 V,
-\end{align}
-where $\hat{\psi}$ is assumed to take its unperturbed value. 
-This model describes ion sound wave dynamics parallel to magnetic field-lines. It should be noted that the
-ion sound radius is {\em not}\/ negligibly small compared to the radial extents of resonant layers in conventional 
-tokamak plasmas. Hence, the `single-fluid' reduced MHD model, (\ref{e275})--(\ref{e276}), provides  a very poor description
-of the response of  resonant layers in such plasmas.
 
@@
 \subsection{Introduction}
-The aim of this section is to employ the reduced, drift-MHD, four-field, resonant, plasma response model derived in the
-previous section to determine the {\em linear}\/ response of the resonant layer to external perturbations.
+The aim of this section is to employ the reduced, drift-MHD, four-field, resonant, plasma response model derived in Section~\ref{ff} to determine the {\em linear}\/ response of the resonant layer to external perturbations.
 
@@
 \nabla\phi &= \frac{{\bf n}\times {\bf V}}{r_s\,V_A},\\[0.5ex]
-N &= \frac{p-p_0}{c_\beta\,B_z^{\,2}/\mu_0},\\[0.5ex]
-V &= \frac{{\bf n}\cdot {\bf V}}{V_A}.
+N &=-\hat{d}_i\left(\frac{p-p_0}{B_z^{\,2}/\mu_0}\right),\\[0.5ex]
+V &= \hat{d}_i\left(\frac{{\bf n}\cdot {\bf V}}{V_A}\right).
 \end{align}
@@
 \phi &= - \hat{V}_E\,\hat{x},\\[0.5ex]
-N &= \frac{\hat{V}_\ast\,\hat{x}}{\hat{d}_s},\\[0.5ex]
+N &= -\hat{V}_\ast\,\hat{x},\\[0.5ex]
 V &= \hat{V}_\parallel,\label{e290}
@@
  \begin{equation}
- L_s=\left(\frac{R_0\,q}{s}\right)_{r_s}
+ L_s=\frac{R_0\,q_s}{s_s}
  \end{equation}
@@
 \end{equation}
-is the (dominant $\theta$-component of the) diamagnetic velocity, $\hat{d}_s=d_s/r_s$,  
-\begin{equation}
-d_s=d_\beta(r_s),
-\end{equation}
+is the (dominant $\theta$-component of the) diamagnetic velocity,
   and 
- $\hat{V}_\parallel= V_z(r_s)/V_A$. We also have
+ $\hat{V}_\parallel=\hat{d}_i\, V_z(r_s)/V_A$. We also have
  \begin{align}\label{e292}
@@
  U &= 0,\label{e293}\\[0.5ex]
- \hat{E}_\parallel &=\left(\frac{2}{s_s}-1\right) \frac{\hat{\eta}_\parallel(r_s)}{\hat{L}_s},\label{e294}\\[0.5ex]
+ \hat{E}_\parallel &=\left(\frac{2}{s_s}-1\right) \frac{\hat{\eta}_\parallel}{\hat{L}_s},\label{e294}\\[0.5ex]
 s_s&=s(r_s).
@@
 \phi(\hat{x},\zeta,t) &=-\hat{V}_E\,\hat{x}+ \tilde{\phi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
-N(\hat{x},\zeta,t) &= \frac{\hat{V}_\ast\,\hat{x}}{\hat{d}_s}-\frac{1}{\hat{d}_s}\!\left(\frac{1+\tau}{\tau}\right)\!\tilde{N}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
-V(\hat{x},\zeta,t) &= \hat{V}_\parallel + \frac{c_\beta}{\hat{d}_s}\!\left(\frac{1+\tau}{\tau}\right)\!\tilde{V}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
+N(\hat{x},\zeta,t) &= -\hat{V}_\ast\,\hat{x}+\left(\frac{1+\tau}{\tau}\right)\!\tilde{N}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
+V(\hat{x},\zeta,t) &= \hat{V}_\parallel + \left(\frac{1+\tau}{\tau}\right)\!\tilde{V}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
 J(\hat{x},\zeta,t) &=-\left(\frac{2}{s_s}-1\right)\!\frac{1}{\hat{L}_s}+ \hat{\nabla}^2\tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
@@
 -{\rm i}\,(\omega-\omega_E-\omega_{\ast\,i})\,\tau_H\,\hat{\nabla}^2\tilde{\phi} &= -{\rm i}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi}+S^{-1}\,P_\varphi\,\hat{\nabla}^4\!\left(\tilde{\phi} + \frac{\tilde{N}}{\tau}\right),\\[0.5ex]
--{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{N} &= -{\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\phi} - {\rm i}\!\left(\frac{\tau}{1+\tau}\right)\hat{d}_s^{\,2}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi} -{\rm i}\,c_\beta^2\,\hat{x}\,\tilde{V}\\[0.5ex]
+-{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{N} &= -{\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\phi}-{\rm i}\,c_\beta^{\,2}\,\hat{x}\,\tilde{V} - {\rm i}\!\left(\frac{\tau}{1+\tau}\right)\hat{d}_\beta^{\,2}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi} \\[0.5ex]
 &\phantom{=}
@@
 \begin{equation}
-\omega_E = \left(\frac{m}r_s\right)V_E(r_s)
+\omega_E = \left(\frac{m}{r_s}\right)V_E(r_s)
 \end{equation}
@@
 \begin{equation}
-\tau_R = \frac{\mu_0\,r_s^{\,2}}{\eta_\parallel(r_s)}
+\tau_R = \frac{\mu_0\,r_s^{\,2}}{\eta_\parallel}
 \end{equation}
@@
 \tau_\varphi
-= \frac{r_s^{\,2}}{\chi_\varphi(r_s)}=\frac{r_s^{\,2}\,n_0\,m_i}{\mu_\perp(r_s)}
+= \frac{r_s^{\,2}}{\chi_\varphi}=\frac{r_s^{\,2}\,n_0\,m_i}{\mu_\perp(r_s)}
 \end{equation} 
@@
 \begin{equation}
-\tau_\perp = \frac{r_s^{\,2}}{D_\perp(r_s)}
+\tau_\perp = \frac{r_s^{\,2}}{D_\perp}
 \end{equation}
  the {\em particle/energy confinement time}. Furthermore, $P_\varphi = \tau_R/\tau_\varphi$, $P_\perp = \tau_R/\tau_\perp$, 
-$P_\parallel=\tau_R/\tau_\parallel$, $\tau_\parallel =r_s^{\,2}/D_\parallel(r_s)$, and
-\begin{equation}
- \lambda_e = 0.71\left(\frac{\eta_e}{1+\eta_e}\right)\left(\frac{\tau}{1+\tau}\right).
-\end{equation}
+$P_\parallel=\tau_R/\tau_\parallel$, and $\tau_\parallel =r_s^{\,2}/D_\parallel$.
 
@@
 -{\rm i}\,(Q-Q_E -Q_{i})\,\frac{d^{\,2}\tilde{\phi}}{dX^2}&= - {\rm i}\,X\,\frac{d^{\,2}\tilde{\psi}}{dX^2}+ P_\varphi\,\frac{d^{\,4}}{dX^4}\!\left(\tilde{\phi} + \frac{\tilde{N}}{\tau}\right),\\[0.5ex]
--{\rm i}\,(Q-Q_E)\tilde{N} &= - {\rm i}\,Q_{e}\,\tilde{\phi} - {\rm i} \,D^{2}\,X\,\frac{d^{\,2}\tilde{\psi}}{dX^{2}}
- - {\rm i}\,c_\beta^{\,2}\,X\,\tilde{V} + P_\perp\,\frac{d^{\,2} \tilde{N}}{dX^{2}},\label{e308}\\[0.5ex]
+-{\rm i}\,(Q-Q_E)\tilde{N} &= - {\rm i}\,Q_{e}\,\tilde{\phi} - {\rm i}\,c_\beta^{\,2}\,X\,\tilde{V}  - {\rm i} \,D^{2}\,X\,\frac{d^{\,2}\tilde{\psi}}{dX^{2}}
++ P_\perp\,\frac{d^{\,2} \tilde{N}}{dX^{2}},\label{e308}\\[0.5ex]
  -{\rm i}\,(Q-Q_E)\,\tilde{V} &= {\rm i}\,Q_{e}\,\tilde{\psi} - {\rm i}\,X\,\tilde{N} + P_\varphi\,\frac{d^{\,2}\tilde{V}}{dX^{2}}.\label{e309}
@@
 Here, $Q=S^{\,1/3}\,\omega\,\tau_H$, $Q_E = S^{\,1/3}\,\omega_E\,\tau_H$, $Q_{e,i} = S^{\,1/3}\,\omega_{\ast\,e,i}\,\tau_H$,
-and $D = S^{\,1/3}\,[\tau/(1+\tau)]^{1/2}\,\hat{d}_s$. Note that the terms involving parallel transport have dropped out of
+and $D = S^{\,1/3}\,[\tau/(1+\tau)]^{1/2}\,\hat{d}_\beta$. Note that the terms involving parallel transport have dropped out of
 Equation~(\ref{e308}). The neglect of these terms is justified provided that the linear layer width is much less than the critical value,
-\begin{equation}
-\delta_c = \left(\frac{1}{\epsilon\,s\,n}\sqrt{\frac{D_\perp}{D_\parallel}}\right)^{1/2}_{r_s} r_s,
+\begin{equation}\label{wcdef}
+w_c = \left(\frac{1}{\epsilon_s\,s_s\,n}\right)^{1/2}\left(\frac{D_\perp}{D_\parallel}\right)^{1/4}r_s,
 \end{equation}
@@
 -{\rm i}\,(Q-Q_E -Q_{i})\,p^2\,\bar{\phi}&=  \frac{d(p^2\,\bar{\psi})}{dp}- P_\varphi\,p^4\!\left(\bar{\phi} + \frac{\bar{N}}{\tau}\right),\\[0.5ex]
--{\rm i}\,(Q-Q_E)\bar{N} &= - {\rm i}\,Q_{e}\,\bar{\phi} -D^{2}\,\frac{d(p^2\,\bar{\psi})}{dp}
- + c_\beta^{\,2}\,\frac{d\bar{V}}{dp} - P_\perp\,p^2\bar{N},\label{e316}\\[0.5ex]
+-{\rm i}\,(Q-Q_E)\bar{N} &= - {\rm i}\,Q_{e}\,\bar{\phi} + c_\beta^{\,2}\,\frac{d\bar{V}}{dp}-D^{2}\,\frac{d(p^2\,\bar{\psi})}{dp}
+  - P_\perp\,p^2\bar{N},\label{e316}\\[0.5ex]
  -{\rm i}\,(Q-Q_E)\,\bar{V} &= {\rm i}\,Q_{e}\,\bar{\psi} +\frac{d\bar{N}}{dp}- P_\varphi\,p^2\,\bar{V},\label{e317}
@@
 This response regime is known as the {\em visco-resistive regime}, because the layer response is dominated by
-resistivity and  perpendicular viscosity. (Fitzpatrick 1998). The characteristic layer width is $p_\ast \sim P^{-1/6}$, which implies that
+resistivity and  ion perpendicular viscosity (Bondeson \& Persson 1986; Fitzpatrick 1993). The characteristic layer width is $p_\ast \sim P^{-1/6}$, which implies that
 the regime is valid when  $P\gg Q^{3/2}$, $P\gg D^6$, and $P\ll Q^{-3}$.
@@
 This equation is identical in form to Equation~(\ref{e330a}), which we have already solved. Indeed, the solution that
-is bounded as $p\rightarrow\infty$ has the small-$p$ expansion (\ref{e332}), where $z=\sqrt{C}\,p^n/n$, 
+is bounded as $p\rightarrow\infty$ has the small-$p$ expansion (\ref{e332}), where $q=\sqrt{C}\,p^n/n$, 
 $n=(m+2)/2$, and $\nu=1/(m+2)$. Matching to Equation~(\ref{e325}) yields
@@
 This response regime is known as the {\em visco-inertial regime}, because the layer response is dominated by
-perpendicular viscosity and ion inertia (Fitzpatrick 1998). 
+ion perpendicular viscosity and ion inertia (Fitzpatrick 1998). 
  The characteristic layer width is $p_\ast \sim Q^{-1/4}\,P^{-1/4}$,
@@
 \begin{equation}
-\frac{\psi(\hat{x},\xi)}{|\tilde{\psi}|} = 8\left(\frac{\hat{x}}{\hat{W}}\right)^2 + \cos\xi.
+\frac{\hat{\psi}(\hat{x},\xi)}{|\tilde{\psi}|} = 8\left(\frac{\hat{x}}{\hat{W}}\right)^2 + \cos\xi.
 \end{equation}
@@
 \begin{equation}\label{e350}
-\omega = \gamma+{\rm i}\,\omega_r,
+\omega = {\rm i}\,\gamma+\omega_r,
 \end{equation}
@@
 -{\rm i}\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)Q_\ast\,(P_\varphi+P_\perp)\,p^2\nonumber\\[0.5ex]
-\phantom{=} &+ P_\varphi\,P_\perp\,p^4,\\[0.5ex]
+&\phantom{=} + P_\varphi\,P_\perp\,p^4,\\[0.5ex]
 \tilde{B}(p)&= P_\perp - {\rm i}\,(1+\lambda_e)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)Q_\ast\,D^2 +\left(\frac{1+\tau}{\tau}\right)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right) D^2\,P_\varphi\,p^2.
@@
 \begin{equation}\label{e359}
-Y(p)= Y_0\left[1+\frac{\hat{\mit\Delta}\,p}{\pi\,\hat{\gamma}} + {\cal O}(p^2)\right]
+Y(p)= Y_0\left[1-\frac{\hat{\mit\Delta}\,p}{\pi\,\hat{\gamma}} + {\cal O}(p^2)\right]
 \end{equation}
@@
 \begin{equation}
-C = (1+\lambda_e)\left(\frac{\tau}{1+\tau}\right)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)\frac{Q_\ast^{2}}{P_\perp}.
+C =\left(\frac{\tau}{1+\tau}\right) (1+\lambda_e)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)\frac{Q_\ast^{2}}{P_\perp}.
 \end{equation}
@@
 \begin{equation}
-\hat{\mit\Delta} = \pi\,\hat{\gamma}\left[ (1+\lambda_e)\left(\frac{\tau}{1+\tau}\right)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)\right]^{1/2}\,\frac{Q_\ast}{P_\perp^{1/2}},
+\hat{\mit\Delta} = \pi\,\hat{\gamma}\left[ \left(\frac{\tau}{1+\tau}\right)(1+\lambda_e)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)\right]^{1/2}\,\frac{Q_\ast}{P_\perp^{1/2}},
 \end{equation}
@@
 \begin{equation}\label{e363}
-\gamma = \frac{E_{ss}}{\pi\left[ (1+\lambda_e)\left(\frac{\tau}{1+\tau}\right)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)\right]^{1/2}\,}\,\frac{1}{\omega_\ast\,\tau_H\,\tau_R^{1/2}\,\tau_\perp^{1/2}}.
+\gamma = \frac{E_{ss}}{\pi\left[ \left(\frac{\tau}{1+\tau}\right)(1+\lambda_e)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)\right]^{1/2}\,}\,\frac{1}{\omega_\ast\,\tau_H\,\tau_R^{1/2}\,\tau_\perp^{1/2}}.
 \end{equation}
@@
 \begin{equation}\label{e368}
-\gamma = \frac{E_{ss}}{\sqrt{2}\,\pi}\,\frac{d_s/r_s}{\omega_\ast^{1/2}\,\tau_H\,\tau_R^{1/2}}.
+\gamma = \frac{E_{ss}}{\sqrt{2}\,\pi}\,\frac{d_\beta/r_s}{\omega_\ast^{1/2}\,\tau_H\,\tau_R^{1/2}}.
 \end{equation}
@@
 \begin{equation}\label{e371}
-\gamma= \frac{E_{ss}}{2\pi\,[{\mit\Gamma}(3/4)/{\mit\Gamma}(1/4)]\,[1+\lambda_e\,\tau/(1+\tau)]^{-1/4}}\,\frac{(d_s/r_s)^{1/2}\,\tau_\perp^{1/4}}{\tau_H^{1/2}\,\tau_R^{3/4}}.
+\gamma= \frac{E_{ss}}{2\pi\,[{\mit\Gamma}(3/4)/{\mit\Gamma}(1/4)]\,[1+\lambda_e\,\tau/(1+\tau)]^{-1/4}}\,\frac{(d_\beta/r_s)^{1/2}\,\tau_\perp^{1/4}}{\tau_H^{1/2}\,\tau_R^{3/4}}.
 \end{equation}
@@
 timescales, $\tau_\varphi$ and $\tau_\perp$ (and by the magnetic Prandtl number, $P$).
-Third, finite ion sound radius effects,  which are parameterized by the modified ion sound radius, $d_s$ (and by the normalized
+Third, finite ion sound radius effects,  which are parameterized by the ion sound radius, $d_\beta$ (and by the normalized ion
 sound radius $D$).
 
- There are four tearing-mode growth-rate regimes---the resistive-inertial, the visco-resistive, the semi-collisional, and the Hall-resistive---and their extents in $Q_\ast$-$P$-$D$ space are illustrated in Figure~\ref{f3}.
+ There are four tearing-mode growth-rate regimes---the resistive-inertial, the visco-resistive, the semi-collisional, and the Hall-resistive---and their extents in $Q_\ast$-$P$ space are illustrated in Figure~\ref{f3}.
 Note that Figure~\ref{f3} differs somewhat from Figures~\ref{f1} and \ref{f2} because in the latter two
@@
 increases the tearing mode growth-rate, but the increase eventually saturates (i.e., the
-growth-rate ends up scaling as $d_s^{\,0}$).
+growth-rate ends up scaling as $d_\beta^{\,0}$).
 
@@
 \hat{\delta}_{\rm HR} = \frac{2\pi\,{\mit\Gamma}(3/4)}{{\mit\Gamma}(1/4)\,[1+\lambda_e\,\tau/(1+\tau)]^{1/4}}\,
-\frac{\tau_H^{1/2}}{(d_s/r_s)^{1/2}\,\tau_R^{1/4}\,\tau_\perp^{1/4}}
+\frac{\tau_H^{1/2}}{(d_\beta/r_s)^{1/2}\,\tau_R^{1/4}\,\tau_\perp^{1/4}}
 \end{equation}
@@
 \tilde{I}_{c\,{\rm crit}}&= (\epsilon_s\,s_s)\,(\omega_{s\,0}\,\tau_H)\left/
-\left[\frac{q_s}{\epsilon_s}\left(\frac{\sqrt{\tau_\varphi\,\tau_{i\,s}/\mu_{00\,s}^i}}{\tau_s}\right)+2\left(\frac{\tau_\varphi}{\tau_s}\right) \ln\!\left(\frac{a}{r_s}\right)\right]^{1/2}\right..\label{e420}
+\left[\frac{q_s}{\epsilon_s}\left(\frac{\sqrt{\tau_\varphi\,\tau_i/\mu_{00}^i}}{\tau_s}\right)+2\left(\frac{\tau_\varphi}{\tau_s}\right) \ln\!\left(\frac{a}{r_s}\right)\right]^{1/2}\right..\label{e420}
 \end{align}
@@
 \begin{equation}
-\frac{1}{\tau_{\theta\,s}} = \left(\frac{q_s}{\epsilon_s}\right)^2\,\left(\frac{\mu_{00\,s}^i}{\tau_{i\,s}}\right),
+\frac{1}{\tau_{\theta\,s}} = \left(\frac{q_s}{\epsilon_s}\right)^2\,\left(\frac{\mu_{00}^i}{\tau_{i}}\right),
 \end{equation}
  where
- \begin{align}
-\tau_{i\,s}&= \tau_i(r_s),\\[0.5ex]
- \mu_{00\,s}^i&=\mu_{00}^i(r_s), 
- \end{align}
- and $\mu_{00}^i(r)$ is a dimensionless neoclassical viscosity coefficient defined in Fitzpatrick \& Nelson 2020. Furthermore,
- we have assumed that $\tau_{i\,s}/(\tau_\varphi\,\mu_{00\,s}^i)\ll (q_s/\epsilon_s)^2$ (this
+$\tau_i$ is the ion collision time and $\mu_{00}^i$ is a dimensionless neoclassical viscosity coefficient defined in Fitzpatrick \& Nelson 2020.
+Both quantities are evaluated at the resonant surface.
+Furthermore,
+ we have assumed that $\tau_i/(\tau_\varphi\,\mu_{00}^i)\ll (q_s/\epsilon_s)^2$ (this
 turns out to be  
-a very good approximation because the ion collision time, $\tau_{i\,s}$, is much less than the momentum confinement
+a very good approximation because the ion collision time, $\tau_i$, is much less than the momentum confinement
 time, $\tau_\varphi$, in conventional tokamak plasmas).
@@
 the electromagnetic locking torque, and zero when the electromagnetic locking torque has reduced the rotation to zero. The electromagnetic torque itself
-is represented  by the function $T_{\rm EM}(v)$, whereas the viscous restoring toque that acts to oppose changes in the plasma rotation is represented
+is represented  by the function $T_{\rm EM}(v)$, whereas the viscous restoring torque that acts to oppose changes in the plasma rotation is represented
 by the function $T_{\rm VS}(v)$. It can be seen from Figure~\ref{f5} that, while the viscous restoring torque varies linearly with $v$,
@@
 is proportional to the product of the shielding current and the reconnected flux, the torque peaks, and ends up falling off as $1/v$ 
-with increasing $v$ (Gimbett \& Peckover 1979; Fitzpatrick 1993).
+with increasing $v$ (Gimblett \& Peckover 1979; Fitzpatrick 1993).
 
@@
 \begin{equation}
-\hat{\delta}\gg 4\,S^{-2/5}\left(\frac{q_s}{\epsilon_s}\right)^{2/5}\left[\frac{q_s}{\epsilon_s}\left(\frac{\sqrt{\tau_\varphi\,\tau_{i\,s}/\mu_{00\,s}^i}}{\tau_R}\right)+2\left(\frac{\tau_\varphi}{\tau_R}\right) \ln\!\left(\frac{a}{r_s}\right)\right]^{-1/5}.
+\hat{\delta}\gg 4\,S^{-2/5}\left(\frac{q_s}{\epsilon_s}\right)^{2/5}\left[\frac{q_s}{\epsilon_s}\left(\frac{\sqrt{\tau_\varphi\,\tau_i/\mu_{00}^i}}{\tau_R}\right)+2\left(\frac{\tau_\varphi}{\tau_R}\right) \ln\!\left(\frac{a}{r_s}\right)\right]^{-1/5}.
 \end{equation}
@@
 \frac{\tau_\varphi}{\tau_R} = \frac{\tau_\perp}{\tau_R} &\simeq \left(\frac{q_s}{\epsilon_s}\right)^2\beta,\\[0.5ex]
-\frac{\tau_{i\,s}}{\tau_R} &\simeq  \left(\frac{q_s}{\epsilon_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/2}\rho_\ast^{\,2}\,\beta^{-1},\\[0.5ex]
-\frac{d_s}{r_s} &\simeq \left(\frac{q_s}{\epsilon_s}\right)\rho_\ast.
+\frac{\tau_i}{\tau_R} &\simeq  \left(\frac{q_s}{\epsilon_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/2}\rho_\ast^{\,2}\,\beta^{-1},\\[0.5ex]
+\frac{d_\beta}{r_s} &\simeq \left(\frac{q_s}{\epsilon_s}\right)\rho_\ast.
 \end{align} 
@@
 \hat{\delta}_{\rm VR} = \left(\frac{\tau_{\rm VR}}{\tau_R}\right) \simeq\left(\frac{\tau_H}{\tau_R}\right)^{1/3}\left(\frac{\tau_R}{\tau_\varphi}\right)^{1/6}&\simeq \left(\frac{q_s}{\epsilon_s}\right)^{1/3}\left(\frac{m_e}{m_i}\right)^{1/6}\rho_\ast^{\,2/3}\,\nu_\ast^{\,1/3}\,\beta^{-1/3},\\[0.5ex]
-\hat{\delta}_{\rm HR} = \left(\frac{\tau_{\rm HR}}{\tau_R}\right) \simeq \left(\frac{\tau_H}{\tau_R}\right)^{1/2}\left(\frac{\tau_R}{\tau_\perp}\right)^{1/4}\left(\frac{r_s}{d_s}\right)^{1/2}&\simeq \left(\frac{m_e}{m_i}\right)^{1/4}\rho_\ast^{\,1/2}\,\nu_\ast^{\,1/2}\,\beta^{-1/2},\\[0.5ex]
-\frac{\sqrt{\tau_\varphi\, \tau_{i\,s}/\mu_{00\,s}^i}}{\tau_R}&\simeq \left(\frac{q_s}{r_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/4}\,\rho_\ast.
-\end{align}
-Here, we have treated $\mu_{00\,s}^i$ as an ignorable ${\cal O}(1)$ constant that is independent of $\rho_\ast$, $\nu_\ast$, and
+\hat{\delta}_{\rm HR} = \left(\frac{\tau_{\rm HR}}{\tau_R}\right) \simeq \left(\frac{\tau_H}{\tau_R}\right)^{1/2}\left(\frac{\tau_R}{\tau_\perp}\right)^{1/4}\left(\frac{r_s}{d_\beta}\right)^{1/2}&\simeq \left(\frac{m_e}{m_i}\right)^{1/4}\rho_\ast^{\,1/2}\,\nu_\ast^{\,1/2}\,\beta^{-1/2},\\[0.5ex]
+\frac{\sqrt{\tau_\varphi\, \tau_i/\mu_{00}^i}}{\tau_R}&\simeq \left(\frac{q_s}{r_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/4}\,\rho_\ast.
+\end{align}
+Here, we have treated $\mu_{00}^i$ as an ignorable ${\cal O}(1)$ constant that is independent of $\rho_\ast$, $\nu_\ast$, and
 $\beta$ [as is indeed the case provided that the plasma at the resonant surface lies in the banana collisionality regime (Hirshman \& Sigmar 1981)].
@@
 weaker inverse scaling with machine size (roughly $R^{-1/2}$) than the regimes in which the threshold scales as $n^0$ (which
-exhibit an approximate $R^{-1}$ scaling). [In fact, it is easily demonstrated that if 
+exhibit an approximate $R^{-1}$ scaling). [In fact, it is easily demonstrated, from the previous analysis, that if 
 $b_r/B_z\propto n^{\,\alpha_n}\,B^{\,\alpha_B}\,R^{\,\alpha_R}$ then $\alpha_R = 2\,\alpha_n+1.25\,\alpha_B$. (Buttery, et al.\ 1999).]
 
-Note, finally, that the analysis presented in this section is only valid provided that the width of the driven magnetic
-island, $W$, at the resonant surface, just prior to error-field penetration, is less than the linear layer width, $\delta$. 
+Note, finally, that the analysis presented in this section is only valid provided that the width of the  magnetic
+island chain, $W$,  driven at the resonant surface, just prior to error-field penetration, is less than the linear layer width, $\delta$. 
 The ratio of $W$ to $\delta$, just prior to penetration, in the four regimes discussed previously is
@@
 
+\section{Nonlinear Resonant Response Model}
+\subsection{Introduction}
+As was discussed in Section~\ref{dis1}, the linear resonant response model derived in Section~\ref{linear} is only
+valid when the width of the magnetic island chain at the resonant surface is much less than the linear layer width. 
+In the opposite limit, in which the island width greatly exceeds the layer width, a nonlinear approach is required. 
+The aim of this section  is to employ the reduced, drift-MHD, four-field, resonant, plasma response model derived in Section~\ref{ff} to 
+construct a nonlinear resonant response model.
+
+It is convenient to set the normalization scale-length, $l$, in our four-field response model equal to the minor radius of the resonant surface, $r_s$.
+It is also convenient to work in a frame of reference that corotates with the island chain.
+In this reference frame, the
+normalized reconnected flux, $\hat{\mit\Psi}_s(\hat{t})$, is assumed to be a positive real quantity. 
+Furthermore, the four fields,
+$\hat{\psi}$, $\phi$, $N$, and $V$, as well as the auxiliary field, $J$, are assumed to only be functions of the
+normalized time, $\hat{t}= t\,V_A/r_s$, the normalized radial coordinate $\hat{x} = (r-r_s)/r_s$, and the
+helical angle $\zeta= m\,\theta-n\,\varphi$.
+
+It is helpful to define the reduced island width
+\begin{equation}
+w = \frac{W}{4} = (L_s\,R_0\,{\mit\Psi}_s)^{1/2}.
+\end{equation}
+It is assumed that $\delta\ll w\ll r_s$, where $\delta$ is the linear layer width. Let $\hat{w}= w/r_s$.  Reusing the analysis of Section~\ref{linear},
+in the limit $|\hat{x}|/\hat{w}\gg 1$ (i.e., many island widths from the resonant surface), we expect 
+\begin{align}
+\hat{\psi} &\rightarrow \frac{\hat{x}^{\,2}}{2\,\hat{L}_s} + \hat{R}_0\,\hat{\mit\Psi}_s\,\cos\zeta,\\[0.5ex]
+\phi &\rightarrow \left(\frac{\hat{\omega}}{m}- \hat{V}_E\right)\hat{x} - \frac{s}{4}\,\hat{V}_E'\,\hat{x}^{\,2},\\[0.5ex]
+N &\rightarrow -\hat{V}_\ast\,\hat{x},\\[0.5ex]
+V&\rightarrow \hat{V}_\parallel,\\[0.5ex]
+J& \rightarrow -\frac{2}{q_s\,\hat{R}_0} + \frac{1}{\hat{L}_s}.
+\end{align}
+Here, 
+\begin{equation}
+s = {\rm sgn}(\hat{x}),
+\end{equation}
+and 
+\begin{equation}
+\hat{V}_E' = \frac{1}{V_A}\left[r\,\frac{dV_E}{dr}\right]_{r_{s-}}^{r_{s+}}.
+\end{equation}
+The parameter $\hat{V}_E'$ is included in the analysis to take into account the fact that the plasma rotation profile in the outer region develops a
+gradient discontinuity at the resonant surface in response to the nonlinear localized electromagnetic torque that develops
+there.
+
+\subsection{Rescaled Four-Field Model}
+Let
+\begin{align}
+X &= \frac{\hat{x}}{\hat{w}},\\[0.5ex]
+T &= \omega_\ast\,t.
+\end{align}
+Thus, $|X|\sim {\cal O}(1)$ in the immediate vicinity of the island chain. It is helpful to define the
+rescaled fields ${\mit\Psi}(X,\zeta,T)$, ${\mit\Phi}(X,\zeta,T)$, ${\cal N}(X,\zeta,T)$,
+${\cal V}(X,\zeta,T)$, and ${\cal J}(X,\zeta,T)$, where
+\begin{align}
+\hat{\psi} &= \left(\frac{\hat{w}^{\,2}}{\hat{L}_s}\right){\mit\Psi},\\[0.5ex]
+\phi &=\left(\frac{\hat{\omega}_\ast\,\hat{w}}{m}\right){\mit\Phi},\\[0.5ex]
+N &= \left(\frac{\hat{\omega}_\ast\,\hat{w}}{m}\right){\cal N},\\[0.5ex]
+V&= \hat{V}_\parallel + \left(\frac{\hat{L}_s\,\hat{\omega}_\ast^{\,2}}{m^2\,c_\beta^{\,2}}\right){\cal V},\\[0.5ex]
+J & =-\frac{2}{q_s\,\hat{R}_0} + \frac{1}{\hat{L}_s} + \left(\frac{\hat{L}_s\,\hat{\omega}_\ast^{\,2}}{m^2\,\hat{w}^{\,2}}\right){\cal J}.
+\end{align}
+The four-field model introduced in Section~\ref{fourf} rescales to give
+\begin{align}\label{e469}
+\frac{d(\ln \hat{w}^2)}{dT}\,\cos\zeta &= \left\{{\mit\Phi}-\left(\frac{\tau}{1+\tau}\right)(1+\lambda_e)\,{\cal N}, {\mit\Psi}\right\}
++ \epsilon_\beta\,\epsilon_d\,\epsilon_\eta\,{\cal J},\\[0.5ex]
+\frac{\partial(\partial_X^{\,2}\,{\mit\Phi})}{\partial T} &= \partial_X\!\!\left\{{\mit\Phi} + \frac{{\cal N}}{1+\tau},{\mit\Psi}\right\}
++ [{\cal J},{\mit\Psi}]+ \epsilon_\chi \,\partial_X^{\,4}\!\left({\mit\Phi} + \frac{{\cal N}}{1+\tau}\right),\\[0.5ex]
+\frac{\partial {\cal N}}{\partial T} &= \{{\mit\Phi}, {\cal N}\} + \{{\cal V},{\mit\Psi}\} + \epsilon_d\,\epsilon_n\,\{{\cal J},{\mit\Psi}\}\nonumber\\[0.5ex]&\phantom{=}
++ \epsilon_D \!\left[\left(\frac{w}{w_c}\right)^4\,\{\{{\cal N},{\mit\Psi}\}, {\mit\Psi}\}+\partial_X^{\,2}{\cal N}\right],\\[0.5ex]
+\epsilon_d\,\frac{\partial {\cal V}}{\partial T} &= \epsilon_d\,\{{\mit\Phi},{\cal V}\}+\{{\cal N}, {\mit\Psi}\} + \epsilon_d\,\epsilon_\chi\,\partial_X^{\,2} {\cal V},\\[0.5ex]
+\partial_X^{\,2}{\mit\Psi} &= 1+ \epsilon_\beta\,\epsilon_d\,{\cal J}.\label{e473}
+\end{align}
+Here, $\partial_X\equiv \partial/\partial X$, 
+\begin{equation}
+\{A,B\} \equiv \frac{\partial A}{\partial X}\,\frac{\partial B}{\partial\zeta} - \frac{\partial A}{\partial \zeta}\,\frac{\partial B}{\partial X},
+\end{equation}
+and we have set
+\begin{equation}
+\hat{E}_\parallel = \left(\frac{2}{q_s\hat{R}_0}-\frac{1}{\hat{L}_s}\right)\eta_\parallel.
+\end{equation}
+Furthermore,
+\begin{align}
+\epsilon_d &= \left(\frac{L_s}{L_n}\right)\left(\frac{d_\beta}{w}\right)^2,\\[0.5ex]
+\epsilon_\beta &= c_\beta^{\,2},\\[0.5ex]
+\epsilon_n&= \left(\frac{L_n}{L_s}\right)^2,\\[0.5ex]
+\epsilon_\eta &= \frac{\eta_\parallel}{\mu_0\,\omega_\ast\,w^2},\\[0.5ex]
+\epsilon_\chi &= \frac{\chi_\phi}{\omega_\ast\,w^2},\\[0.5ex]
+\epsilon_D &= \frac{D_\perp}{\omega_\ast\,w^2}.
+\end{align}
+Finally,
+\begin{equation}
+\frac{1}{L_n}= -\frac{1}{{\mit\Gamma}\,(1-c_\beta^{\,2})}\left(\frac{d\ln n}{dr}\right)_{r_s}
+\end{equation}
+is the {\em density gradient scalelength}, 
+and the critical island width, $w_c$, is defined in Equation~(\ref{wcdef}).
+
+Equations~(\ref{e469})--(\ref{e473}) must be solved subject to the boundary conditions
+\begin{align}
+{\mit\Psi}&\rightarrow \frac{X^{\,2}}{2} + \cos\zeta,\label{e483}\\[0.5ex]
+{\mit\Phi} &\rightarrow v\,X +\frac{ s\,v'\,X^{\,2}}{2},\\[0.5ex]
+{\cal N}&\rightarrow X,\\[0.5ex]
+{\cal V}&\rightarrow 0,\\[0.5ex]
+{\cal J}& \rightarrow 0,\label{e487}
+\end{align}
+as $|X|\rightarrow\infty$. Here,
+\begin{align}
+v &= \frac{\omega-\omega_E}{\omega_\ast},\\[0.5ex]
+v' &= -\frac{\hat{w}}{2\,\omega_\ast}\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}}.
+\end{align}
+In the following, it is assumed that $v\sim{\cal O}(1)$ and $|v'|\ll 1$. Note that the boundary conditions (\ref{e483})--(\ref{e487}),
+as well as the symmetry of the rescaled four-field equations,  (\ref{e469})--(\ref{e473}), ensure that ${\mit\Psi}$, ${\cal V}$, and
+${\cal J}$ are even functions of $X$, whereas ${\mit\Phi}$ and ${\cal N}$ are odd functions.
+
 \section*{Bibliography}
@@
 {\bf 112}, 443. 
+\item Bondeson, A., and Persson, M.\ 1986. {\em Resistive Tearing Modes in the Presence of Equilibrium Flows}. Phys.\ Fluids
+{\bf 29}, 2997. 
 \item Boozer, A.H.\ 1996. {\em Shielding of Resonant Magnetic Perturbations by Rotation}. Phys.\ Plasmas {\bf 3}, 4620.

### 2021-11-22 Documentation/TearingModeTheory.tex
Lastest version

@@
 
-\section{Reduced Drift-MHD Resonant  Response Model}\label{ff}
+\section{Reduced Resonant  Response Model}\label{ff}
 \subsection{Introduction}
@@
 Hence, one very effective way of simplifying the resonant layer equations is to remove the
-physics of  compressible-Alfv\'{e}n waves from them altogether, in the process converting a drift-magnetohydrodynamical (MHD) response model
-into a so-called {\em reduced}\/ drift-MHD response model (Strauss 1976; Hazeltine, Kotschenreuther \& Morrison 1985; 
-Furuya, Yagi \& Itoh 2003). The aim of
+physics of  compressible-Alfv\'{e}n waves from them altogether, in the process converting a 
+drift-magnetohydrodynamical\footnote{The  `drift' appellation  merely indicates that we are taking diamagnetic flows into account.
+However, this necessarily entails treating the ion and electron flow separately.
+In other words, a
+drift-MHD model is also a `two-fluid' model. }(MHD) response model  
+into a so-called {\em reduced}\/ drift-MHD response model (Strauss 1976; Hazeltine, Kotschenreuther \& Morrison 1985). The aim of
 this section is to describe the reduction process (which essentially boils down to arguing that the divergence of the
@@
 \begin{equation}\label{e220}
-{\bf E} + {\bf V}\times {\bf B} + \frac{1}{e\,n_0}\!\left[\nabla p + \frac{1}{1+\tau}\left(\frac{0.71\,\eta_e\,\tau}{1+\eta_e}-1\right)({\bf b}\cdot\nabla p)\,{\bf b} -{\bf j}\times{\bf b}\right] = \eta_\parallel\,{\bf j}_\parallel + \eta_\perp\,{\bf j}_\perp.
+{\bf E} + {\bf V}\times {\bf B} + \frac{1}{e\,n_0}\!\left[\nabla p + \frac{1}{1+\tau}\left(\frac{0.71\,\eta_e\,\tau}{1+\eta_e}-1\right)({\bf b}\cdot\nabla p)\,{\bf b} -{\bf j}\times{\bf B}\right] = \eta_\parallel\,{\bf j}_\parallel + \eta_\perp\,{\bf j}_\perp.
 \end{equation}
@@
 
-Equations~(\ref{e220})--(\ref{e223}) are known collectively as the {\em drift-MHD equations},\footnote{The  `drift' appellation  merely indicates that we are taking diamagnetic flows into account.} and contain both shear-Alfv\'{e}n
+Equations~(\ref{e220})--(\ref{e223}) are known collectively as the {\em drift-MHD equations}, and contain both shear-Alfv\'{e}n
 and compressible-Alfv\'{e}n wave dynamics. The system of equations is completed by a subset of Maxwell's equations:
@@
 \begin{align}\label{e227}
-\hat{\bf E} + \hat{\bf V}\times \hat{\bf B} + \hat{d}_i\!\left[\hat{\nabla} \hat{p} + \frac{1}{1+\tau}\left(\frac{0.71\,\eta_e\,\tau}{1+\eta_e}-1\right)({\bf b}\cdot\hat{\nabla} \hat{p})\,{\bf b} + \hat{\nabla}\cdot\hat{\bpi}_e-\hat{\bf j}\times\hat{\bf b}\right] &= \hat{\eta}_\parallel\,\hat{\bf j}_\parallel+ \hat{\eta}_\perp\,\hat{\bf j}_\perp,\\[0.5ex]
+\hat{\bf E} + \hat{\bf V}\times \hat{\bf B} + \hat{d}_i\!\left[\hat{\nabla} \hat{p} + \frac{1}{1+\tau}\left(\frac{0.71\,\eta_e\,\tau}{1+\eta_e}-1\right)({\bf b}\cdot\hat{\nabla} \hat{p})\,{\bf b} + \hat{\nabla}\cdot\hat{\bpi}_e-\hat{\bf j}\times\hat{\bf B}\right] &= \hat{\eta}_\parallel\,\hat{\bf j}_\parallel+ \hat{\eta}_\perp\,\hat{\bf j}_\perp,\\[0.5ex]
 \frac{\partial \hat{\bf V}}{\partial \hat{t}} 
@@
 \hat{\bf V}_\ast &= \hat{d}_i\,{\bf b}\times \hat{\nabla} \hat{p},\\[0.5ex]
-\hat{\bf V}_i &= \hat{\bf V} + \frac{\hat{\bf V}_{\ast\,i}}{1+\tau}.
+\hat{\bf V}_i &= \hat{\bf V} + \frac{\hat{\bf V}_{\ast}}{1+\tau}.
 \end{align}
@@
 \subsection{Discussion}
-Equations~(\ref{e264})--(\ref{e269}) constitute our reduced, four-field, drift-MHD, resonant, plasma response model. Our model is very similar
-to the original four-field model derived by Hazeltine, et al.\ (Hazeltine, et al.\ 1985). Equation~(\ref{e264}) is the {\em generalized
+Equations~(\ref{e264})--(\ref{e269}) constitute our reduced drift-MHD resonant plasma response model. Our model is very similar
+to the original four-field model derived by Hazeltine, et al.\ (Hazeltine, Kotschenreuther \& Morrison 1985). Equation~(\ref{e264}) is the {\em generalized
 Ohm's law}\/ that governs the time evolution of the (normalized) helical magnetic flux, $\hat{\psi}$. Equation~(\ref{e265}) is the {\em parallel
@@
 \subsection{Introduction}
-The aim of this section is to employ the reduced, drift-MHD, four-field, resonant, plasma response model derived in Section~\ref{ff} to determine the {\em linear}\/ response of the resonant layer to external perturbations.
+The aim of this section is to employ the reduced resonant plasma response model derived in Section~\ref{ff} to determine the {\em linear}\/ response of the resonant layer to external perturbations.
 
@@
 \begin{align}\label{e295}
-\hat{\psi}(\hat{x},\zeta,t) &= \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
-\phi(\hat{x},\zeta,t) &=-\hat{V}_E\,\hat{x}+ \tilde{\phi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
-N(\hat{x},\zeta,t) &= -\hat{V}_\ast\,\hat{x}+\left(\frac{1+\tau}{\tau}\right)\!\tilde{N}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
-V(\hat{x},\zeta,t) &= \hat{V}_\parallel + \left(\frac{1+\tau}{\tau}\right)\!\tilde{V}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
-J(\hat{x},\zeta,t) &=-\left(\frac{2}{s_s}-1\right)\!\frac{1}{\hat{L}_s}+ \hat{\nabla}^2\tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
-U(\hat{x},\zeta,t) &=  \hat{\nabla}^2\tilde{\phi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\label{e300}
+\hat{\psi}(\hat{x},\zeta,\hat{t}) &= \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
+\phi(\hat{x},\zeta,\hat{t}) &=-\hat{V}_E\,\hat{x}+ \tilde{\phi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
+N(\hat{x},\zeta,\hat{t}) &= -\hat{V}_\ast\,\hat{x}+\left(\frac{1+\tau}{\tau}\right)\!\tilde{N}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
+V(\hat{x},\zeta,\hat{t}) &= \hat{V}_\parallel + \left(\frac{1+\tau}{\tau}\right)\!\tilde{V}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
+J(\hat{x},\zeta,\hat{t}) &=-\left(\frac{2}{s_s}-1\right)\!\frac{1}{\hat{L}_s}+ \hat{\nabla}^2\tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
+U(\hat{x},\zeta,\hat{t}) &=  \hat{\nabla}^2\tilde{\phi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\label{e300}
 \end{align}
@@
 \begin{equation}
-\hat{\psi}(\hat{x},\zeta,t) = \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},
+\hat{\psi}(\hat{x},\zeta,\hat{t}) = \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},
 \end{equation}
@@
 $\hat{\psi}(\hat{x},\xi)$ map out the perturbed magnetic flux-surfaces in the vicinity of the resonant layer. 
-Let $\hat{W} = 4\,(|\tilde{\psi}|\,\hat{L}_s)^{1/2}$. Equation~(\ref{e352a}) can be written
+Let $\hat{W} = 4\,(\hat{L}_s|\,\tilde{\psi}|)^{1/2}$. Equation~(\ref{e352a}) can be written
 \begin{equation}
@@
 \begin{equation}\label{e355s}
-W =  \hat{W}\,r_s= 4\,(|\tilde{\psi}|\,\hat{L}_s)^{1/2}\,r_s = 4\left(\frac{q_s}{s_s}\,|\hat{\mit\Psi}_s|\right)^{1/2}R_0,
+W =  \hat{W}\,r_s= 4\,(\hat{L}_s\,|\tilde{\psi}|)^{1/2}\,r_s = 4\left(L_s\,R_0\,|\hat{\mit\Psi}_s|\right)^{1/2},
 \end{equation}
@@
 \rho_\ast &= \frac{T_0^{1/2}\,m_i^{1/2}}{e\,B_z\,L_s},\label{e428}\\[0.5ex]
-\nu_\ast &= \frac{L_s\,n_0\,e^2\,\eta_\parallel(r_s)}{m_e^{1/2}\,T_0^{1/2}},\\[0.5ex]
+\nu_\ast &= \frac{L_s\,n_0\,e^2\,\eta_\parallel}{m_e^{1/2}\,T_0^{1/2}},\\[0.5ex]
 \beta&=\frac{\mu_0\,n_0\,T_0}{B_z^{\,2}},\label{e430}
@@
 \begin{equation}
-\frac{n_0\,T_0}{\tau_E} = \eta_\parallel(r_s)\left(\frac{B_z}{\mu_0\,L_s}\right)^2,
+\frac{n_0\,T_0}{\tau_E} = \eta_\parallel\left(\frac{B_z}{\mu_0\,L_s}\right)^2,
 \end{equation}
@@
 As was discussed in Section~\ref{dis1}, the linear resonant response model derived in Section~\ref{linear} is only
-valid when the width of the magnetic island chain at the resonant surface is much less than the linear layer width. 
+valid when the width of the magnetic island chain that develops at the resonant surface is much less than the linear layer width. 
 In the opposite limit, in which the island width greatly exceeds the layer width, a nonlinear approach is required. 
-The aim of this section  is to employ the reduced, drift-MHD, four-field, resonant, plasma response model derived in Section~\ref{ff} to 
-construct a nonlinear resonant response model.
-
-It is convenient to set the normalization scale-length, $l$, in our four-field response model equal to the minor radius of the resonant surface, $r_s$.
+The aim of this section  is to employ the reduced four-field resonant plasma response model derived in Section~\ref{ff} to 
+construct a suitable nonlinear resonant response model.
+
+It is convenient to set the normalization scale-length, $l$, in the four-field  model equal to the minor radius of the resonant surface, $r_s$.
 It is also convenient to work in a frame of reference that corotates with the island chain.
@@
 Furthermore, the four fields,
-$\hat{\psi}$, $\phi$, $N$, and $V$, as well as the auxiliary field, $J$, are assumed to only be functions of the
-normalized time, $\hat{t}= t\,V_A/r_s$, the normalized radial coordinate $\hat{x} = (r-r_s)/r_s$, and the
-helical angle $\zeta= m\,\theta-n\,\varphi$.
+$\hat{\psi}$, $\phi$, $N$, and $V$, as well as the auxiliary field, $J$, are assumed to only be functions of  the normalized radial coordinate, $\hat{x} = (r-r_s)/r_s$, the
+helical angle, $\zeta= m\,\theta-n\,\varphi$, and the
+normalized time, $\hat{t}= t\,V_A/r_s$.
 
@@
 \end{equation}
+[See Equation~(\ref{e355s}).]
 It is assumed that $\delta\ll w\ll r_s$, where $\delta$ is the linear layer width. Let $\hat{w}= w/r_s$.  Reusing the analysis of Section~\ref{linear},
-in the limit $|\hat{x}|/\hat{w}\gg 1$ (i.e., many island widths from the resonant surface), we expect 
+in the limit $|\hat{x}|/\hat{w}\gg 1$ (i.e., many island widths from the resonant surface), we find that 
 \begin{align}
@@
 V&\rightarrow \hat{V}_\parallel,\\[0.5ex]
-J& \rightarrow -\frac{2}{q_s\,\hat{R}_0} + \frac{1}{\hat{L}_s}.
-\end{align}
-Here, 
+J& \rightarrow -\frac{2}{q_s\hat{R}_0} + \frac{1}{\hat{L}_s}.
+\end{align}
+Here, $\omega = \hat{\omega}\,V_A/r_s$ is the helical phase velocity of the island chain in the
+laboratory frame,
 \begin{equation}
@@
 \end{equation}
-The parameter $\hat{V}_E'$ is included in the analysis to take into account the fact that the plasma rotation profile in the outer region develops a
+The parameter $\hat{V}_E'$ is introduced  into the analysis in order to take into account the fact that the plasma rotation profile in the outer region develops a
 gradient discontinuity at the resonant surface in response to the nonlinear localized electromagnetic torque that develops
@@
 \end{align}
-Thus, $|X|\sim {\cal O}(1)$ in the immediate vicinity of the island chain. It is helpful to define the
+It follows that $|X|\sim {\cal O}(1)$ in the immediate vicinity of the island chain. It is helpful to define the
 rescaled fields ${\mit\Psi}(X,\zeta,T)$, ${\mit\Phi}(X,\zeta,T)$, ${\cal N}(X,\zeta,T)$,
@@
 V&= \hat{V}_\parallel + \left(\frac{\hat{L}_s\,\hat{\omega}_\ast^{\,2}}{m^2\,c_\beta^{\,2}}\right){\cal V},\\[0.5ex]
-J & =-\frac{2}{q_s\,\hat{R}_0} + \frac{1}{\hat{L}_s} + \left(\frac{\hat{L}_s\,\hat{\omega}_\ast^{\,2}}{m^2\,\hat{w}^{\,2}}\right){\cal J}.
-\end{align}
-The four-field model introduced in Section~\ref{fourf} rescales to give
+J & =-\frac{2}{q_s \hat{R}_0} + \frac{1}{\hat{L}_s} + \left(\frac{\hat{L}_s\,\hat{\omega}_\ast^{\,2}}{m^2\,\hat{w}^{\,2}}\right){\cal J}.
+\end{align}
+The four-field model specified in Section~\ref{fourf} rescales to give
 \begin{align}\label{e469}
@@
 + \epsilon_\beta\,\epsilon_d\,\epsilon_\eta\,{\cal J},\\[0.5ex]
-\frac{\partial(\partial_X^{\,2}\,{\mit\Phi})}{\partial T} &= \partial_X\!\!\left\{{\mit\Phi} + \frac{{\cal N}}{1+\tau},{\mit\Psi}\right\}
-+ [{\cal J},{\mit\Psi}]+ \epsilon_\chi \,\partial_X^{\,4}\!\left({\mit\Phi} + \frac{{\cal N}}{1+\tau}\right),\\[0.5ex]
+\frac{\partial(\partial_X^{\,2}\,{\mit\Phi})}{\partial T} &= \partial_X\!\!\left\{{\mit\Phi} + \frac{{\cal N}}{1+\tau},\partial_X{\mit\Phi}\right\}
++ \{{\cal J},{\mit\Psi}\}+ \epsilon_\chi \,\partial_X^{\,4}\!\left({\mit\Phi} + \frac{{\cal N}}{1+\tau}\right),\label{e470}\\[0.5ex]
 \frac{\partial {\cal N}}{\partial T} &= \{{\mit\Phi}, {\cal N}\} + \{{\cal V},{\mit\Psi}\} + \epsilon_d\,\epsilon_n\,\{{\cal J},{\mit\Psi}\}\nonumber\\[0.5ex]&\phantom{=}
-+ \epsilon_D \!\left[\left(\frac{w}{w_c}\right)^4\,\{\{{\cal N},{\mit\Psi}\}, {\mit\Psi}\}+\partial_X^{\,2}{\cal N}\right],\\[0.5ex]
-\epsilon_d\,\frac{\partial {\cal V}}{\partial T} &= \epsilon_d\,\{{\mit\Phi},{\cal V}\}+\{{\cal N}, {\mit\Psi}\} + \epsilon_d\,\epsilon_\chi\,\partial_X^{\,2} {\cal V},\\[0.5ex]
++ \epsilon_D \!\left[\left(\frac{w}{w_c}\right)^4\,\{\{{\cal N},{\mit\Psi}\}, {\mit\Psi}\}+\partial_X^{\,2}{\cal N}\right],\label{e471}\\[0.5ex]
+\epsilon_d\,\frac{\partial {\cal V}}{\partial T} &= \epsilon_d\,\{{\mit\Phi},{\cal V}\}+\{{\cal N}, {\mit\Psi}\} + \epsilon_d\,\epsilon_\chi\,\partial_X^{\,2} {\cal V},\label{e472}\\[0.5ex]
 \partial_X^{\,2}{\mit\Psi} &= 1+ \epsilon_\beta\,\epsilon_d\,{\cal J}.\label{e473}
@@
 is the {\em density gradient scalelength}, 
-and the critical island width, $w_c$, is defined in Equation~(\ref{wcdef}).
+and the critical reduced island width, $w_c$, is defined in Equation~(\ref{wcdef}).
 
@@
 \begin{align}
-{\mit\Psi}&\rightarrow \frac{X^{\,2}}{2} + \cos\zeta,\label{e483}\\[0.5ex]
-{\mit\Phi} &\rightarrow v\,X +\frac{ s\,v'\,X^{\,2}}{2},\\[0.5ex]
-{\cal N}&\rightarrow X,\\[0.5ex]
+{\mit\Psi}&\rightarrow \frac{X^{2}}{2} + \cos\zeta,\label{e483}\\[0.5ex]
+{\mit\Phi} &\rightarrow v\,X +\frac{ s\,v'\,X^{2}}{2},\label{e484}\\[0.5ex]
+{\cal N}&\rightarrow X,\label{e486}\\[0.5ex]
 {\cal V}&\rightarrow 0,\\[0.5ex]
@@
 \end{align}
-In the following, it is assumed that $v\sim{\cal O}(1)$ and $|v'|\ll 1$. Note that the boundary conditions (\ref{e483})--(\ref{e487}),
+In the following, it is assumed that $v\sim{\cal O}(1)$ and $|v'|\ll 1$. Note that ${\mit\Psi}$, ${\mit\Phi}$, ${\cal N}$, ${\cal V}$, and ${\cal J}$ are all ${\cal O}(1)$ quantities.
+Note, further,  that the boundary conditions (\ref{e483})--(\ref{e487}),
 as well as the symmetry of the rescaled four-field equations,  (\ref{e469})--(\ref{e473}), ensure that ${\mit\Psi}$, ${\cal V}$, and
 ${\cal J}$ are even functions of $X$, whereas ${\mit\Phi}$ and ${\cal N}$ are odd functions.
+
+\subsection{Ordering Scheme}
+In the following, the dimensionless parameters $\epsilon_d$, $\epsilon_\beta$, $\epsilon_n$, $\epsilon_\eta$, $\epsilon_\chi$,
+and $\epsilon_D$ are all assumed to be of similar size, but much smaller than unity. The orderings $\epsilon_n\ll 1$ and $\epsilon_\beta\ll 1$
+are consistent with the standard large-aspect ratio, low-$\beta$ orderings used to describe conventional tokamak
+plasmas (Freidberg 1987). As will become apparent, the ordering $\epsilon_d\ll 1$ ensures that the island chain is
+sufficiently wide that ion acoustic waves propagating parallel to the magnetic field are able to smooth out any
+variations in the normalized electron number density, ${\cal N}$, around magnetic flux-surfaces (Scott, Hassam \& Drake 1985).
+The orderings $\epsilon_\eta\ll 1$, $\epsilon_\chi\ll 1$, and $\epsilon_D\ll 1$ ensure that the island
+chain is sufficiently wide that the perpendicular diffusion of magnetic flux, momentum, and particles are not dominant
+effects in the rescaled four-field equations. We shall also assume that $w/w_c\sim{\cal O}(1)$. In other words, the
+island chain is sufficiently wide for the parallel diffusion of particles to compete with perpendicular diffusion.
+
+Let 
+\begin{align}
+\frac{\partial}{\partial T}&\sim {\cal O}(\epsilon_d^3),\\[0.5ex]
+{\mit\Psi}&= {\mit\Psi}_0+\epsilon_d^2\,{\mit\Psi}_2+ \epsilon_d^3\,{\mit\Psi}_3 + \cdots,\\[0.5ex]
+{\mit\Phi}&= {\mit\Phi}_0+\epsilon_d^2\,{\mit\Phi}_2+ \epsilon_d^3\,{\mit\Phi}_3 + \cdots,\\[0.5ex]
+{\cal N}&= {\cal N}_0+\epsilon_d^2\,{\cal N}_2+ \epsilon_d^3\,{\cal N}_3 + \cdots,\\[0.5ex]
+{\cal V} & ={\cal V}_0. +\epsilon_d\,{\cal V}_1 +\cdots,\\[0.5ex]
+{\cal J} &= {\cal J}_0 + \epsilon_d\,{\cal J}_1 +\cdots. 
+\end{align}
+Here, ${\mit\Psi}_0$, ${\mit\Psi}_1$, et cetera are assumed to be ${\cal O}(1)$.
+
+\subsection{Lowest-Order Solution}
+To lowest order in $\epsilon_d$, Equation~(\ref{e473}) yields
+\begin{equation}
+\partial_X^{\,2}{\mit\Psi}_0 = 1.
+\end{equation} 
+Solving this equation subject to the boundary condition (\ref{e483}), we obtain
+\begin{equation}\label{e498}
+{\mit\Psi}_0 = {\mit\Omega}(X,\zeta)\equiv \frac{X^2}{2} + \cos\zeta.
+\end{equation}
+Thus, we conclude that, to lowest order in our expansion, the magnetic flux-surfaces in the island region have the constant-$\psi$
+structure pictured in Figure~\ref{f2a}. The island O-points correspond to ${\mit\Omega}=-1$ and $\zeta=(2k-1)\,\pi$ (where $k$ is an integer), the
+X-points correspond to ${\mit\Omega}=+1$ and $\zeta = 2k\,\pi$, and the magnetic separatrix corresponds to 
+${\mit\Omega}=+1$.
+
+To lowest order in $\epsilon_d$, Equation~(\ref{e472}) yields
+\begin{equation}
+\{{\cal N}_0, {\mit\Omega}\}= 0,
+\end{equation}
+where use has been made of Equation~(\ref{e498}). Given that ${\cal N}$ is an odd function of $X$, it
+follows that
+\begin{equation}\label{e500}
+{\cal N}_0 = s\, {\cal N}_{(0)}({\mit\Omega}).
+\end{equation}
+We conclude that parallel
+ion acoustic waves, whose dynamics are described by Equation~(\ref{e473}), have smoothed out
+any variations in the lowest-order electron number density, ${\cal N}_0$,  around magnetic flux-surfaces. 
+By symmetry, ${\cal N}_{0}=0$ inside the magnetic separatrix of the island chain. In other words, the electron number
+density profile (and, by implication, the electron and ion temperature profile) has been completely flattened inside 
+the  separatrix.
+
+It is helpful to define
+\begin{equation}\label{e501}
+L({\mit\Omega}) = \frac{d{\cal N}_{(0)}}{d{\mit\Omega}}.
+\end{equation}
+It follows that $L({\mit\Omega}<1)=0$. Also, Equations~(\ref{e486}) and (\ref{e498}) imply that
+\begin{equation}
+L({\mit\Omega}\rightarrow\infty) = \frac{1}{\sqrt{2\,{\mit\Omega}}}.
+\end{equation}
+
+To lowest order in $\epsilon_d$, Equation~(\ref{e469}) gives
+\begin{equation}
+\{{\mit\Phi}_0,{\mit\Omega}\}=0,
+\end{equation}
+where use has been made of Equations~(\ref{e498}) and (\ref{e500}). Given that
+${\mit\Phi}$ is an odd function of $X$, it follows that 
+\begin{equation}\label{e503}
+{\mit\Phi}_0 = s\, {\mit\Phi}_{(0)}({\mit\Omega}).
+\end{equation}
+ We conclude that the lowest-order normalized
+electrostatic potential (in the island rest frame), ${\mit\Phi}_{0}$, is also constant on magnetic flux-surfaces. 
+By symmetry, ${\mit\Phi}_{0}=0$ inside the magnetic separatrix of the island chain. In other words, the electrostatic
+potential profile has been completely flattened inside the separatrix.
+
+It is helpful to define
+\begin{equation}\label{e505}
+M({\mit\Omega}) = \frac{d{\mit\Phi}_{(0)}}{d{\mit\Omega}}.
+\end{equation}
+It follows that $M({\mit\Omega}<1)=0$. Also, Equations~(\ref{e484}) and (\ref{e498}) imply that
+\begin{equation}
+M({\mit\Omega}\rightarrow\infty) = \frac{v}{\sqrt{2\,{\mit\Omega}}}+ v'.
+\end{equation}
+
+To lowest-order in $\epsilon_d$, Equation~(\ref{e471}) yields
+\begin{equation}
+\{{\cal V}_0,{\mit\Omega}\} = 0,
+\end{equation}
+where use has been made of Equations~(\ref{e498}), (\ref{e500}), and (\ref{e503}). Given that
+${\cal V}$ is an even function of $X$, we can write
+\begin{equation}
+{\cal V}_0 = {\cal V}_{(0)}({\mit\Omega}).
+\end{equation}
+In other words, the lowest-order normalized parallel ion velocity, ${\cal V}_0$, is also constant on
+magnetic flux-surfaces.
+
+Finally, to lowest order in $\epsilon_d$, Equation~(\ref{e470}) yields
+\begin{equation}\label{e509}
+\{{\cal J}_0,{\mit\Omega}\} = -\partial_X\!\left({\mit\Phi}_0+\frac{{\cal N}_0}{1+\tau}, \partial_X {\mit\Phi}_0\right)=
+\frac{1}{2}\left\{d_{\mit\Omega}\!\left[M\left(M+\frac{L}{1+\tau}\right)\right]X^2, {\mit\Omega}\right\},
+\end{equation}
+where use has been made of Equations~(\ref{e498}), (\ref{e501}), and (\ref{e505}). Moreover, $d_{\mit\Omega}\equiv
+\partial/\partial{\mit\Omega}$.
+
+\subsection{Discussion}
+To lowest order, the rescaled four-field model, (\ref{e469})--(\ref{e473}), requires the density, temperature, 
+electrostatic potential, and ion parallel velocity profiles to be magnetic flux-surface functions. This should come as no surprise. In essence,
+a magnetic island chain is a helical magnetic equilibrium that evolves (in its local rest frame) on the very
+slow resistive timescale (Rutherford 1973). Hence, we would expect all of the results derived in Section~\ref{lowest}
+to apply to the plasma in the region of the island chain, as is indeed the case. Note, however, that
+while solving the  rescaled four-field model, (\ref{e469})--(\ref{e473}), tells us that
+${\cal N}=s\,{\cal N}_{(0)}({\mit\Omega})$, ${\mit\Phi}_0 =s\,{\mit\Psi}_{(0)}({\mit\Omega})$, and
+${\cal V}_0 = {\cal V}_{(0)}({\mit\Omega})$, the solution leaves the forms of the  functions ${\cal N}_{(0)}({\mit\Omega})$,
+${\mit\Phi}_{(0)}({\mit\Omega})$, and ${\cal V}_{(0)}({\mit\Omega})$ undetermined. In order to determine
+the forms of these functions, we must solve the rescaled four-field model to higher order. In particular,
+we must include the terms that describe the perpendicular diffusion of magnetic flux, ion momentum, and
+particles in the analysis (Fitzpatrick \& Waelbroeck 2005). The essential point is that the magnetic island
+chain persists in the plasma for a sufficiently long time for the relatively small perpendicular diffusion
+terms to relax the lowest-order profiles across the island region (and, in fact, across the whole plasma).
+
+\subsection{Flux-Surface Average Operator}
+The {\em flux-surface average operator}, $\langle\cdots\rangle$, is defined (Rutherford 1973)
+\begin{equation}
+\langle A(s,{\mit\Omega},\zeta)\rangle
+\equiv \left\{
+\begin{array}{lll}
+\int_{\zeta_0}^{2\pi-\zeta_0}\frac{A(s,{\mit\Omega}\,\zeta)+A(-s,{\mit\Omega},\zeta)}{2\,[2\,({\mit\Omega}-\cos\zeta)]^{1/2}}\,\frac{d\zeta}{2\pi}&~~~~~&0\leq {\mit\Omega}<1\\[2ex]
+\oint \frac{A(s,{\mit\Omega}\,\zeta)}{[2\,({\mit\Omega}-\cos\zeta)]^{1/2}}\,\frac{d\zeta}{2\pi}
+&&{\mit\Omega}\geq 1
+\end{array}
+\right.
+\end{equation}
+It follows that
+\begin{equation}
+\langle\{A,{\mit\Omega}\}\rangle = 0
+\end{equation}
+for any $A(s,{\mit\Omega},\zeta)$. It is helpful to define
+\begin{equation}
+\tilde{A}  \equiv A - \frac{\langle A\rangle}{\langle 1\rangle}.
+\end{equation}
+It follows that $\langle \tilde{A}\rangle =0$ for any $A(s,{\mit\Omega},\zeta)$.
+
+Equation~(\ref{e509}) yields 
+\begin{equation}
+{\cal J}_0({\mit\Omega},\zeta)= 
+\frac{1}{2}\,d_{\mit\Omega}\!\left[M\left(M+\frac{L}{1+\tau}\right)\right]\!\tilde{X}^2 + \bar{\cal J}_0({\mit\Omega}),
+\end{equation}
+where $\bar{{\cal J}}_0({\mit\Omega})$ is an undetermined function.
 
@@
 \item Furth, H.P., Killeen, J., and Rosenbluth, M.N.\ 1963. {\em Finite-Resistivity Instabilities of a Sheet Pinch}. Phys.\ Fluids {\bf 6}, 459.
-\item Furuya, A., Yagi, M., and Itoh, S.-I.\ 2003. {\em Linear Analysis of Neoclassical Tearing Mode
-Based on the Four-Field Reduced Neoclassical MHD Equation}. J.\ Phys.\ Soc.\ Japan {\bf 72}, 313.
+%\item Furuya, A., Yagi, M., and Itoh, S.-I.\ 2003. {\em Linear Analysis of Neoclassical Tearing Mode
+%Based on the Four-Field Reduced Neoclassical MHD Equation}. J.\ Phys.\ Soc.\ Japan {\bf 72}, 313.
 \item Gimblett, C.G., and Peckover, R.S.\ 1979. {\em On the Mutual Interaction Between Rotation and Magnetic Fields
@@
 \item Richardson, A.S.\ 2019. {\em 2019 NRL Plasma Formulary}.  Naval Research Laboratory, Washington DC. 
+\item Rutherford, P.H.\ 1973. {\em Nonlinear Growth of the Tearing Mode}. Phys.\ Fluids {\bf 16}, 1903. 
+\item Scott, B.D., Hassam, A.B., and Drake, J.F.\ 1985. {\em Nonlinear Evolution of Drift-Tearing Modes}. Phys.\ Fluids
+{\bf 28}, 275. 
 \item Scoville, J.T., et al.\ 1991. {\em Locked Modes in DIII-D and a Method for Prevention of the Low Density Mode}. Nucl.\ Fusion {\bf 31}, 875. 

### 2021-11-24 Documentation/TearingModeTheory.tex
Latest version

@@
  \begin{align}
-{\mit\Delta\hat{\Psi}}_s &=\frac{{\mit\Delta\Psi}_s}{R_0\,B_z},\\[0.5ex]
+{\mit\Delta\hat{\Psi}}_s &=\frac{{\mit\Delta\Psi}_s}{R_0\,B_z},\label{e204}\\[0.5ex]
  \hat{\mit\Psi}_s &=\frac{{\mit\Psi}_s}{R_0\,B_z}.
@@
 drift-magnetohydrodynamical\footnote{The  `drift' appellation  merely indicates that we are taking diamagnetic flows into account.
-However, this necessarily entails treating the ion and electron flow separately.
+However, this necessarily entails treating the ion and electron flows separately.
 In other words, a
-drift-MHD model is also a `two-fluid' model. }(MHD) response model  
+drift-MHD model is,  by definition, also a `two-fluid' model. }(MHD) response model  
 into a so-called {\em reduced}\/ drift-MHD response model (Strauss 1976; Hazeltine, Kotschenreuther \& Morrison 1985). The aim of
@@
 
-\subsection{Drift-MHD Equations}
+\subsection{Drift-MHD Equations}\label{s4.2}
  It is helpful to define
@@
 
-\subsection{Normalization Scheme}
+\subsection{Normalization Scheme}\label{s4.3}
 Let $l$ be a typical variation lengthscale in the resonant layer. The {\em Alfv\'{e}n velocity}, which is the typical phase
@@
 $\hat{x}=(r-r_s)/l$,
- and 
- \begin{equation}
- \zeta=m\,\theta-n\,\varphi
- \end{equation}
+ \begin{equation}
+ \zeta=m\,\theta-n\,\varphi,
+ \end{equation}
+ and $\hat{t}$, 
  only. 
@@
 \end{equation}
- It follows that ${\bf n}\cdot\nabla A=0$ for any $A(\hat{x},\zeta)$. 
+ It follows that ${\bf n}\cdot\nabla A=0$ for any $A(\hat{x},\zeta,\hat{t})$. 
 Let us write (Fitzpatrick \& Waelbroeck 2009)
@@
 \end{equation}
-which automatically satisfies Equation~(\ref{e230}). Note that $\hat{\psi}=\psi/(r_s\,B_z)$, where $\psi$ is defined in Equation~(\ref{e93}).
- Here, $\delta b(\hat{x},\zeta)$ and $\hat{\psi}(\hat{x},\zeta)$ are assumed to be small
+which automatically satisfies Equation~(\ref{e230}). Note that 
+\begin{equation}\label{e247a}
+\hat{\psi}=\frac{\psi}{r_s\,B_z},
+\end{equation}
+ where $\psi$ is defined in Equation~(\ref{e93}).
+ Here, $\delta b(\hat{x},\zeta,
+ \hat{t})$ and $\hat{\psi}(\hat{x},\zeta,\hat{t})$ are assumed to be small
 compared to unity, which merely indicates that the perturbed magnetic field due to the tearing mode is small compared to the
@@
 \end{equation}
-Here, $\hat{E}_\parallel = E_\parallel/(B_z\,V_A)$, where $E_\parallel$ represents the constant inductive electric field that drives the equilibrium plasma current in the vicinity of the resonant surface.
-Moreover, $\partial/\partial \hat{t}$ and $\phi(\hat{x},\zeta)$
+Here, $\hat{E}_\parallel = E_\parallel/(B_z\,V_A)$, where $E_\parallel$ represents the constant inductive parallel electric field that drives the equilibrium plasma current in the vicinity of the resonant surface.
+Moreover, $\partial/\partial \hat{t}$ and $\phi(\hat{x},\zeta,\hat{t})$
 are 
@@
 \end{align}
-where $\hat{V}_{\parallel\,i}(\hat{x},\zeta)$ is assumed to be first order in small quantities, whereas ${\mit\Xi}(\hat{x},\zeta)$ is assumed to be
+where $\hat{V}_{\parallel\,i}(\hat{x},\zeta,\hat{t})$ is assumed to be first order in small quantities, whereas ${\mit\Xi}(\hat{x},\zeta,\hat{t})$ is assumed to be
 second order. 
@@
 \end{equation}
- Here, $\delta p(\hat{x},\zeta)$ is assumed to be first order in small
+ Here, $\delta p(\hat{x},\zeta,\hat{t})$ is assumed to be first order in small
 quantities. 
@@
 \begin{align}
-\hat{D}_\parallel&=\frac{D_{\parallel}}{l\,V_A}= \frac{2}{3}\left(1-c_\beta^{\,2}\right)\!\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\parallel\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\parallel\,i}\right),\\[0.5ex]
-\hat{D}_\perp &=\frac{D_{\perp}}{l\,V_A}= c_\beta^{\,2}\,\hat{\eta}_\perp +  \frac{2}{3}\left(1-c_\beta^{\,2}\right)\!\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\perp\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\perp\,i}\right).
+\hat{D}_\parallel&\equiv\frac{D_{\parallel}}{l\,V_A}= \frac{2}{3}\left(1-c_\beta^{\,2}\right)\!\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\parallel\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\parallel\,i}\right),\\[0.5ex]
+\hat{D}_\perp &\equiv \frac{D_{\perp}}{l\,V_A}= c_\beta^{\,2}\,\hat{\eta}_\perp +  \frac{2}{3}\left(1-c_\beta^{\,2}\right)\!\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\perp\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\perp\,i}\right).
 \end{align}
@@
  the {\em Lundquist number}, 
-\begin{equation}
+\begin{equation}\label{e317a}
 \tau_R = \frac{\mu_0\,r_s^{\,2}}{\eta_\parallel}
@@
 {\em resistive diffusion time}, 
-\begin{equation}
+\begin{equation}\label{e318a}
 \tau_\varphi
@@
 
-In conventional tokamak plasmas, the Lundquist number, $S$, which is the nominal ratio of the plasma inertia to the   resistive diffusion  terms in the plasma Ohm's law, is very much greater than unity.
+In conventional tokamak plasmas, the Lundquist number, $S$, which is the nominal ratio of the plasma inertia term to the   resistive diffusion  term in the plasma Ohm's law, is very much greater than unity.
 In fact, $S$ typically exceeds $10^8$ (Wesson 2011).
@@
 \begin{equation}\label{e320}
-\frac{d}{dp}\!\left[G(p)\,\frac{dY}{dp}\right] - \frac{A(p)}{B(p)}\,p^{2}\,Y = 0,
+\frac{d}{dp}\!\left[G(p)\,\frac{dY_e}{dp}\right] - \frac{A(p)}{B(p)}\,p^{2}\,Y_e = 0,
 \end{equation}
@@
 \end{align}
-and $Y=\bar{\phi} - (1+\lambda_e)\,\bar{N}$. The boundary conditions are that $Y(p)$ is bounded as $p\rightarrow\infty$, and
+and $Y_e=\bar{\phi} - (1+\lambda_e)\,\bar{N}$. The boundary conditions are that $Y_e(p)$ is bounded as $p\rightarrow\infty$, and
 \begin{equation}\label{e325}
-Y(p)\rightarrow Y_0\!\left[\frac{\hat{\mit\Delta}}{\pi\,p} + 1+ {\cal O}(p)\right]
+Y_e(p)\rightarrow Y_0\!\left[\frac{\hat{\mit\Delta}}{\pi\,p} + 1+ {\cal O}(p)\right]
 \end{equation}
@@
 \begin{equation}
-\frac{d}{dp}\!\left[\frac{p^2}{-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e] + p^2}\,\frac{dY}{dp}\right]\simeq 0
+\frac{d}{dp}\!\left[\frac{p^2}{-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e] + p^2}\,\frac{dY_e}{dp}\right]\simeq 0
 \end{equation}
@@
 \begin{equation}
-Y(p) \simeq Y_0 \left[\frac{\hat{\mit\Delta}}{\pi}\left(\frac{1}{p} + \frac{p}{{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e]}\right) + 1 + {\cal O}(p^2)\right]
+Y_e(p) \simeq Y_0 \left[\frac{\hat{\mit\Delta}}{\pi}\left(\frac{1}{p} + \frac{p}{{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e]}\right) + 1 + {\cal O}(p^2)\right]
 \end{equation}
@@
 \begin{equation}\label{e329}
-\frac{d^{\,2} Y}{dp^2} - \frac{A(p)}{B(p)}\,p^2\,Y\simeq 0,
-\end{equation}
-with $Y$ bounded as $p\rightarrow \infty$. Asymptotic matching to the small-$p$ layer yields the boundary
+\frac{d^{\,2} Y_e}{dp^2} - \frac{A(p)}{B(p)}\,p^2\,Y_e\simeq 0,
+\end{equation}
+with $Y_e$ bounded as $p\rightarrow \infty$. Asymptotic matching to the small-$p$ layer yields the boundary
 condition 
 \begin{equation}\label{e330}
-Y(p)\simeq Y_0\left\{1+ \frac{\hat{\mit\Delta}}{\pi}\,\frac{p}{{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e]}+ {\cal O}(p^2)\right\}
+Y_e(p)\simeq Y_0\left\{1+ \frac{\hat{\mit\Delta}}{\pi}\,\frac{p}{{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e]}+ {\cal O}(p^2)\right\}
 \end{equation}
@@
 \begin{equation}\label{e330a}
-\frac{d^{\,2}Y}{dp^2}- C\,p^m\,Y\simeq 0,
-\end{equation}
-where $m$ is real and non-negative, and $C$ is a complex constant. Let $Y=\sqrt{p}\,Z$ and $q=\sqrt{C}\,p^n/n$, where
+\frac{d^{\,2}Y_e}{dp^2}- C\,p^m\,Y_e\simeq 0,
+\end{equation}
+where $m$ is real and non-negative, and $C$ is a complex constant. Let $Y_e=\sqrt{p}\,Z$ and $q=\sqrt{C}\,p^n/n$, where
 $n=(m+2)/2$. The previous equation transforms into a modified Bessel equation of general order, 
@@
 \begin{equation}
-\frac{d}{dp}\!\left(p^2\,\frac{dY}{dp}\right)-(-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e])\,\frac{A(p)}{B(p)}\,p^2\,Y=0.
+\frac{d}{dp}\!\left(p^2\,\frac{dY_e}{dp}\right)-(-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e])\,\frac{A(p)}{B(p)}\,p^2\,Y_e=0.
 \end{equation}
@@
 \begin{equation}
-\frac{d}{dp}\!\left(p^2\,\frac{dY}{dp}\right)-C\,p^{m+2}\,Y = 0,
-\end{equation}
-where $m$ is real and non-negative, and $C$ is a complex constant. Let $U=p\,Y$. The previous equation
+\frac{d}{dp}\!\left(p^2\,\frac{dY_e}{dp}\right)-C\,p^{m+2}\,Y_e = 0,
+\end{equation}
+where $m$ is real and non-negative, and $C$ is a complex constant. Let $U=p\,Y_e$. The previous equation
 yields
@@
  ion inertia (Ara, et al.\ 1976; Fitzpatrick 1998). Note that the plasma response in the inertial regime is
- equivalent to that of two closely spaced Alfv\'{e}n resonances that straddle the resonant surface (Boozer 1996). 
+ equivalent to that of two closely-spaced Alfv\'{e}n resonances that straddle the resonant surface (Boozer 1996). 
  The characteristic layer width is $p_\ast \sim Q^{-1}$,
@@
 Finally, our four-field resonant plasma response model, (\ref{e264})--(\ref{e269}), contains many term of the general form $[\hat{\psi},\tilde{A}]$,
-where $\tilde{A}(\hat{x},\zeta)$ is a perturbed quantity. According to Equation~(\ref{e352a}), such terms
+where $\tilde{A}(\hat{x},\zeta,\hat{t})$ is a perturbed quantity. According to Equation~(\ref{e352a}), such terms
 can be written
@@
 \begin{equation}\label{e355}
-\frac{d^{\,2} Y}{dp^2} - \frac{A(p)}{\tilde{B}(p)} \,Y =0,
+\frac{d^{\,2} Y_e}{dp^2} - \frac{A(p)}{\tilde{B}(p)} \,Y_e =0,
 \end{equation}
@@
 In the following, $\omega_\ast$ is assumed to be positive. The boundary conditions on Equation~(\ref{e355}) are
-that $Y$ is bounded as $p\rightarrow\infty$, and
+that $Y_e$ is bounded as $p\rightarrow\infty$, and
 \begin{equation}\label{e359}
-Y(p)= Y_0\left[1-\frac{\hat{\mit\Delta}\,p}{\pi\,\hat{\gamma}} + {\cal O}(p^2)\right]
+Y_e(p)= Y_0\left[1-\frac{\hat{\mit\Delta}\,p}{\pi\,\hat{\gamma}} + {\cal O}(p^2)\right]
 \end{equation}
@@
 \begin{equation}
-\frac{d^{\,2} Y}{dp^2} - C\,p^m\,Y = 0,
+\frac{d^{\,2} Y_e}{dp^2} - C\,p^m\,Y_e = 0,
 \end{equation}
@@
 It is helpful to define the reduced island width
-\begin{equation}
-w = \frac{W}{4} = (L_s\,R_0\,{\mit\Psi}_s)^{1/2}.
+\begin{equation}\label{e456}
+w = \frac{W}{4} = (L_s\,R_0\,\hat{\mit\Psi}_s)^{1/2}.
 \end{equation}
@@
 It is assumed that $\delta\ll w\ll r_s$, where $\delta$ is the linear layer width. Let $\hat{w}= w/r_s$.  Reusing the analysis of Section~\ref{linear},
-in the limit $|\hat{x}|/\hat{w}\gg 1$ (i.e., many island widths from the resonant surface), we find that 
+in the limit $|\hat{x}|/\hat{w}\gg 1$ (i.e., many island widths from the resonant surface) we find that 
 \begin{align}
@@
 
-\subsection{Rescaled Four-Field Model}
+\subsection{Rescaled Four-Field Model}\label{s8.2}
 Let
@@
 \begin{align}
-\hat{\psi} &= \left(\frac{\hat{w}^{\,2}}{\hat{L}_s}\right){\mit\Psi},\\[0.5ex]
+\hat{\psi} &= \left(\frac{\hat{w}^{\,2}}{\hat{L}_s}\right){\mit\Psi},\label{e466}\\[0.5ex]
 \phi &=\left(\frac{\hat{\omega}_\ast\,\hat{w}}{m}\right){\mit\Phi},\\[0.5ex]
@@
 \epsilon_n&= \left(\frac{L_n}{L_s}\right)^2,\\[0.5ex]
-\epsilon_\eta &= \frac{\eta_\parallel}{\mu_0\,\omega_\ast\,w^2},\\[0.5ex]
-\epsilon_\chi &= \frac{\chi_\phi}{\omega_\ast\,w^2},\\[0.5ex]
+\epsilon_\eta &= \frac{\eta_\parallel}{\mu_0\,\omega_\ast\,w^2},\label{e481}\\[0.5ex]
+\epsilon_\chi &= \frac{\chi_\phi}{\omega_\ast\,w^2},\label{e482}\\[0.5ex]
 \epsilon_D &= \frac{D_\perp}{\omega_\ast\,w^2}.
@@
 \end{equation}
-is the {\em density gradient scalelength}, 
+is the {\em density gradient scalelength}\/  at the resonant surface, 
 and the critical reduced island width, $w_c$, is defined in Equation~(\ref{wcdef}).
@@
 {\cal N}&\rightarrow X,\label{e486}\\[0.5ex]
-{\cal V}&\rightarrow 0,\\[0.5ex]
+{\cal V}&\rightarrow 0,\label{e486a}\\[0.5ex]
 {\cal J}& \rightarrow 0,\label{e487}
@@
 \begin{align}
-v &= \frac{\omega-\omega_E}{\omega_\ast},\\[0.5ex]
-v' &= -\frac{\hat{w}}{2\,\omega_\ast}\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}}.
+v(T) &= \frac{\omega-\omega_E}{\omega_\ast},\\[0.5ex]
+v'(T) &= -\frac{\hat{w}}{2\,\omega_\ast}\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}}.
 \end{align}
@@
 
-Let 
-\begin{align}
-\frac{\partial}{\partial T}&\sim {\cal O}(\epsilon_d^3),\\[0.5ex]
-{\mit\Psi}&= {\mit\Psi}_0+\epsilon_d^2\,{\mit\Psi}_2+ \epsilon_d^3\,{\mit\Psi}_3 + \cdots,\\[0.5ex]
+Suppose that 
+\begin{align}
+\frac{\partial}{\partial T}&\sim {\cal O}(\epsilon_d^3).
+\end{align}
+Let us expand the various fields in our model as follows:
+\begin{align}
+{\mit\Psi}&= {\mit\Psi}_0+\epsilon_d^2\,{\mit\Psi}_2+ \epsilon_d^3\,{\mit\Psi}_3 + \cdots,\label{e429}\\[0.5ex]
 {\mit\Phi}&= {\mit\Phi}_0+\epsilon_d^2\,{\mit\Phi}_2+ \epsilon_d^3\,{\mit\Phi}_3 + \cdots,\\[0.5ex]
-{\cal N}&= {\cal N}_0+\epsilon_d^2\,{\cal N}_2+ \epsilon_d^3\,{\cal N}_3 + \cdots,\\[0.5ex]
+{\cal N}&= {\cal N}_0+\epsilon_d^2\,{\cal N}_2+ \epsilon_d^3\,{\cal N}_3 + \cdots,\label{e431}\\[0.5ex]
 {\cal V} & ={\cal V}_0. +\epsilon_d\,{\cal V}_1 +\cdots,\\[0.5ex]
-{\cal J} &= {\cal J}_0 + \epsilon_d\,{\cal J}_1 +\cdots. 
+{\cal J} &= {\cal J}_0 + \epsilon_d\,{\cal J}_1 +\cdots. \label{e496}
 \end{align}
@@
 \begin{equation}\label{e500}
-{\cal N}_0 = s\, {\cal N}_{(0)}({\mit\Omega}).
+{\cal N}_0(X,\zeta,T) = s\, {\cal N}_{(0)}({\mit\Omega},T).
 \end{equation}
 We conclude that parallel
-ion acoustic waves, whose dynamics are described by Equation~(\ref{e473}), have smoothed out
+ion acoustic waves, whose dynamics are described by Equation~(\ref{e472}), have smoothed out
 any variations in the lowest-order electron number density, ${\cal N}_0$,  around magnetic flux-surfaces. 
 By symmetry, ${\cal N}_{0}=0$ inside the magnetic separatrix of the island chain. In other words, the electron number
-density profile (and, by implication, the electron and ion temperature profile) has been completely flattened inside 
+density profile (and, by implication, the electron and ion temperature profile) is completely flattened inside 
 the  separatrix.
@@
 \begin{equation}\label{e501}
-L({\mit\Omega}) = \frac{d{\cal N}_{(0)}}{d{\mit\Omega}}.
-\end{equation}
-It follows that $L({\mit\Omega}<1)=0$. Also, Equations~(\ref{e486}) and (\ref{e498}) imply that
-\begin{equation}
-L({\mit\Omega}\rightarrow\infty) = \frac{1}{\sqrt{2\,{\mit\Omega}}}.
+L({\mit\Omega},T) = \frac{d{\cal N}_{(0)}}{d{\mit\Omega}}.
+\end{equation}
+It follows that $L({\mit\Omega}<1,T)=0$. Furthermore, Equations~(\ref{e486}) and (\ref{e498}) imply that
+\begin{equation}\label{e502}
+L({\mit\Omega}\rightarrow\infty,T) = \frac{1}{\sqrt{2\,{\mit\Omega}}}.
 \end{equation}
@@
 \begin{equation}\label{e503}
-{\mit\Phi}_0 = s\, {\mit\Phi}_{(0)}({\mit\Omega}).
+{\mit\Phi}_0(X,\zeta,T) = s\, {\mit\Phi}_{(0)}({\mit\Omega},T).
 \end{equation}
@@
 By symmetry, ${\mit\Phi}_{0}=0$ inside the magnetic separatrix of the island chain. In other words, the electrostatic
-potential profile has been completely flattened inside the separatrix.
+potential profile is  completely flattened inside the separatrix.
 
@@
 \begin{equation}\label{e505}
-M({\mit\Omega}) = \frac{d{\mit\Phi}_{(0)}}{d{\mit\Omega}}.
+M({\mit\Omega},T) = \frac{d{\mit\Phi}_{(0)}}{d{\mit\Omega}}.
 \end{equation}
 It follows that $M({\mit\Omega}<1)=0$. Also, Equations~(\ref{e484}) and (\ref{e498}) imply that
-\begin{equation}
-M({\mit\Omega}\rightarrow\infty) = \frac{v}{\sqrt{2\,{\mit\Omega}}}+ v'.
+\begin{equation}\label{e506}
+M({\mit\Omega}\rightarrow\infty,T) = \frac{v}{\sqrt{2\,{\mit\Omega}}}+ v'.
 \end{equation}
@@
 ${\cal V}$ is an even function of $X$, we can write
-\begin{equation}
-{\cal V}_0 = {\cal V}_{(0)}({\mit\Omega}).
+\begin{equation}\label{e508}
+{\cal V}_0(X,\zeta,T) = {\cal V}_{(0)}({\mit\Omega},T).
 \end{equation}
@@
 
-\subsection{Discussion}
-To lowest order, the rescaled four-field model, (\ref{e469})--(\ref{e473}), requires the density, temperature, 
-electrostatic potential, and ion parallel velocity profiles to be magnetic flux-surface functions. This should come as no surprise. In essence,
+\subsection{Flux-Surface Average Operator}
+The {\em flux-surface average operator}, $\langle\cdots\rangle$, is defined (Rutherford 1973)
+\begin{equation}
+\langle A(s,{\mit\Omega},\zeta)\rangle
+\equiv \left\{
+\begin{array}{llr}
+\int_{\zeta_0}^{2\pi-\zeta_0}\frac{A(s,{\mit\Omega}\,\zeta)+A(-s,{\mit\Omega},\zeta)}{2\,[2\,({\mit\Omega}-\cos\zeta)]^{1/2}}\,\frac{d\zeta}{2\pi}&~~~~~&0\leq {\mit\Omega}\leq 1\\[2ex]
+\oint \frac{A(s,{\mit\Omega}\,\zeta)}{[2\,({\mit\Omega}-\cos\zeta)]^{1/2}}\,\frac{d\zeta}{2\pi}
+&&{\mit\Omega}> 1
+\end{array}
+\right.,
+\end{equation}
+where $\zeta_0=\cos^{-1}({\mit\Omega})$ and $0\leq\zeta_0\leq\pi$. 
+It follows that
+\begin{equation}\label{e5111}
+\langle\{A,{\mit\Omega}\}\rangle = 0
+\end{equation}
+for {\em any}\/ $A(s,{\mit\Omega},\zeta,T)$. It is helpful to define
+\begin{equation}
+\tilde{A}  \equiv A - \frac{\langle A\rangle}{\langle 1\rangle}.
+\end{equation}
+It follows that 
+\begin{equation}\label{e512}
+\langle \tilde{A}\rangle =0
+\end{equation}
+ for {\em any}\/ $A(s,{\mit\Omega},\zeta,T)$.
+
+Equation~(\ref{e509}) yields 
+\begin{equation}\label{e513}
+{\cal J}_0({\mit\Omega},\zeta,T)= 
+\frac{1}{2}\,d_{\mit\Omega}\!\left[M\left(M+\frac{L}{1+\tau}\right)\right]\!\widetilde{X}^2 + \overline{\cal J}_0({\mit\Omega},T),
+\end{equation}
+where $\overline{{\cal J}}_0({\mit\Omega},T)$ is an undetermined flux-surface function.
+
+\subsection{Fluid Velocities}\label{s8.6}
+The flux-surface functions $M({\mit\Omega},T)$ and $L({\mit\Omega},T)$ are directly related to the lowest-order perpendicular
+velocities of the various fluid species in the island rest frame. In fact, as is clear from Sections~\ref{s4.2}, \ref{s4.3}, and \ref{s8.2}, 
+\begin{align}
+V_\theta(x,\zeta,T) &= -\frac{\omega_\ast}{m}\,x\,M({\mit\Omega},T),\\[0.5ex]
+V_{\theta\,i}(x,\zeta,T)& = -\frac{\omega_\ast}{m}\,x\,Y_i({\mit\Omega},T)\\[0.5ex]
+V_{\theta\,e}(x,\zeta,T)& = -\frac{\omega_\ast}{m}\,x\,Y_e({\mit\Omega},T),
+\end{align}
+where
+\begin{align}
+Y_i({\mit\Omega},T)&= M+\left(\frac{1}{1+\tau}\right)L,\label{e518}\\[0.5ex]
+Y_e({\mit\Omega},T)&= Y_i- L.
+\end{align}
+Here, $V_\theta$, $V_{\theta\,i}$, and $V_{\theta\,e}$ refer to velocity components of the MHD, ion, and
+electron fluid, respectively. Note that $Y_i$ and $Y_e$ are both zero inside the magnetic separatrix of the island chain.
+
+\subsection{Need for Higher-Order Solution}
+To lowest order in our expansion scheme, the rescaled four-field model, (\ref{e469})--(\ref{e473}), requires the density, temperature, and  
+electrostatic potential profiles to be magnetic flux-surface functions. This should come as no surprise. In essence,
 a magnetic island chain is a helical magnetic equilibrium that evolves (in its local rest frame) on the very
 slow resistive timescale (Rutherford 1973). Hence, we would expect all of the results derived in Section~\ref{lowest}
-to apply to the plasma in the region of the island chain, as is indeed the case. Note, however, that
-while solving the  rescaled four-field model, (\ref{e469})--(\ref{e473}), tells us that
-${\cal N}=s\,{\cal N}_{(0)}({\mit\Omega})$, ${\mit\Phi}_0 =s\,{\mit\Psi}_{(0)}({\mit\Omega})$, and
-${\cal V}_0 = {\cal V}_{(0)}({\mit\Omega})$, the solution leaves the forms of the  functions ${\cal N}_{(0)}({\mit\Omega})$,
-${\mit\Phi}_{(0)}({\mit\Omega})$, and ${\cal V}_{(0)}({\mit\Omega})$ undetermined. In order to determine
-the forms of these functions, we must solve the rescaled four-field model to higher order. In particular,
-we must include the terms that describe the perpendicular diffusion of magnetic flux, ion momentum, and
-particles in the analysis (Fitzpatrick \& Waelbroeck 2005). The essential point is that the magnetic island
-chain persists in the plasma for a sufficiently long time for the relatively small perpendicular diffusion
-terms to relax the lowest-order profiles across the island region (and, in fact, across the whole plasma).
-
-\subsection{Flux-Surface Average Operator}
-The {\em flux-surface average operator}, $\langle\cdots\rangle$, is defined (Rutherford 1973)
-\begin{equation}
-\langle A(s,{\mit\Omega},\zeta)\rangle
-\equiv \left\{
-\begin{array}{lll}
-\int_{\zeta_0}^{2\pi-\zeta_0}\frac{A(s,{\mit\Omega}\,\zeta)+A(-s,{\mit\Omega},\zeta)}{2\,[2\,({\mit\Omega}-\cos\zeta)]^{1/2}}\,\frac{d\zeta}{2\pi}&~~~~~&0\leq {\mit\Omega}<1\\[2ex]
-\oint \frac{A(s,{\mit\Omega}\,\zeta)}{[2\,({\mit\Omega}-\cos\zeta)]^{1/2}}\,\frac{d\zeta}{2\pi}
-&&{\mit\Omega}\geq 1
-\end{array}
-\right.
-\end{equation}
-It follows that
-\begin{equation}
-\langle\{A,{\mit\Omega}\}\rangle = 0
-\end{equation}
-for any $A(s,{\mit\Omega},\zeta)$. It is helpful to define
-\begin{equation}
-\tilde{A}  \equiv A - \frac{\langle A\rangle}{\langle 1\rangle}.
-\end{equation}
-It follows that $\langle \tilde{A}\rangle =0$ for any $A(s,{\mit\Omega},\zeta)$.
-
-Equation~(\ref{e509}) yields 
-\begin{equation}
+to apply to the plasma in the immediate region of the island chain, as is indeed the case. Note, however, that, 
+while solving the  rescaled four-field model (\ref{e469})--(\ref{e473}) to lowest order  tells us that
+${\cal N}=s\,{\cal N}_{(0)}({\mit\Omega},T)$, ${\mit\Phi}_0 =s\,{\mit\Psi}_{(0)}({\mit\Omega},T)$, and
+${\cal V}_0 = {\cal V}_{(0)}({\mit\Omega},T)$, and that the lowest-order current density profile has the form (\ref{e513}), the lowest-order solution leaves the  flux-surface functions ${\cal N}_{(0)}({\mit\Omega},T)$,
+${\mit\Phi}_{(0)}({\mit\Omega},T)$,  ${\cal V}_{(0)}({\mit\Omega},T)$, and $\overline{\cal J}_0({\mit\Omega},T)$ undetermined. In fact, in order to determine
+the forms of these  four flux-surface functions we need to solve the rescaled four-field model to higher order in our expansion. In particular,
+we need to include the terms that describe the perpendicular diffusion of magnetic flux, ion momentum, and
+particles in our analysis (Fitzpatrick \& Waelbroeck 2005). The essential point is that the magnetic island
+chain persists in the plasma for a sufficiently long time that  the relatively small perpendicular diffusion
+terms are able to relax the lowest-order profiles across the island region (and, in fact, across the whole plasma).
+
+\subsection{Higher-Order Solution}
+We need to evaluate Equation~(\ref{e469}) to third order in $\epsilon_d$ in order to include the perpendicular transport term. Doing so,
+we obtain
+\begin{equation}\label{e514}
+\frac{d(\ln \hat{w}^{\,2})}{dT}\,\cos\zeta = \{F, {\mit\Omega}\} + \epsilon_\beta\,\epsilon_d\,\epsilon_\eta\,{\cal J}_0,
+\end{equation}
+where
+\begin{equation}
+F ({\mit\Omega},\zeta,T)= \epsilon_d^2\,({\mit\Phi}_2+\epsilon_d\,{\mit\Phi}_3)-\epsilon_d^{\,2}\left(\frac{\tau}{1+\tau}\right)({\cal N}_2+\epsilon_d\,{\cal N}_3)
+- \epsilon_d^2\,s\,Y_e({\mit\Psi}_2+\epsilon_d\,{\mit\Psi}_3),
+\end{equation}
+and use has been made of Equations~(\ref{e429})--(\ref{e431}), (\ref{e500}), (\ref{e501}), (\ref{e503}), and (\ref{e505}). 
+The flux-surface average of Equation~(\ref{e514}) yields
+\begin{equation}
+\overline{\cal J}_0({\mit\Omega},T) = \frac{1}{\epsilon_\beta\,\epsilon_d\,\epsilon_\eta}\frac{d(\ln \hat{w}^{\,2})}{dT}\,\frac{\langle\cos\zeta\rangle}{\langle 1\rangle},
+\end{equation}
+where use has been made of Equations~(\ref{e5111}), (\ref{e512}), and (\ref{e513}). Hence, we
+can write
+\begin{equation}\label{e524a}
 {\cal J}_0({\mit\Omega},\zeta)= 
-\frac{1}{2}\,d_{\mit\Omega}\!\left[M\left(M+\frac{L}{1+\tau}\right)\right]\!\tilde{X}^2 + \bar{\cal J}_0({\mit\Omega}),
-\end{equation}
-where $\bar{{\cal J}}_0({\mit\Omega})$ is an undetermined function.
+\frac{1}{2}\,d_{\mit\Omega}\!\left(M\,Y_i\right)\widetilde{X}^2+ \frac{1}{\epsilon_\beta\,\epsilon_d\,\epsilon_\eta}\frac{d(\ln \hat{w}^{\,2})}{dT}\,\frac{\langle\cos\zeta\rangle}{\langle 1\rangle},
+\end{equation}
+where use has been made of Equation~(\ref{e518}). 
+The first term on the right-hand side of the previous equation represents the parallel return current driven by the perpendicular {\em polarization current}\/ associated with the
+acceleration of the ion fluid around the magnetic separatrix of the island chain (Smolyakov 1993; Smolyakov, et al.\ 1995). 
+In fact, it is easily seen that if the ion fluid could pass freely through the separatrix (i.e., ${\mit\Phi}_0\propto X$ and ${\cal N}_0\propto X$) then the term in question would be zero.
+The second term on the right-hand side of the previous equation represents the parallel current driven
+inductively when the reconnected flux at the resonant surfaces varies in time.
+
+We need to evaluate Equation~(\ref{e471}) to first order in $\epsilon_d$ in order to include the perpendicular transport term. Doing so,
+we obtain
+\begin{equation}
+0= \epsilon_d\,\{{\cal V}_1, {\mit\Omega}\} + \epsilon_D\,(X^2\,d_{\mit\Omega} L + L),
+\end{equation}
+where use has been made of Equations~(\ref{e498}), (\ref{e500}),  and (\ref{e501}). The flux-surface average of the
+previous equation yields
+\begin{equation}
+\langle X^2\rangle\,d_{\mit\Omega} L +\langle 1\rangle\,L = 0,
+\end{equation}
+where use has been made of Equation~(\ref{e5111}). 
+We can solve the previous equation, subject to the boundary condition (\ref{e502}), to give
+\begin{equation}\label{e526}
+L({\mit\Omega})=\left\{
+\begin{array}{llr}
+0&&-1\leq {\mit\Omega}\leq 1\\[0.5ex]
+1/\langle X^2\rangle&~~&{\mit\Omega}>1
+\end{array}\right..
+\end{equation}
+Here, we have taken into account the previously mentioned fact that $L=0$ within the island separatrix.
+
+We need to evaluate Equation~(\ref{e470}) to first order in $\epsilon_d$ in order to include the perpendicular transport term. Doing so,
+we obtain
+\begin{equation}\label{e528a}
+0 =\epsilon_d\,\{{\cal J}_1,{\mit\Omega}\} +\epsilon_\chi\,X\,d_{{\mit\Omega}}\!\left[d_{\mit\Omega}\!\left(X^3\,d_{\mit\Omega} Y_i\right)\right].
+\end{equation}
+where use has been made of Equations~(\ref{e498}), (\ref{e500}), (\ref{e501}), (\ref{e503}), (\ref{e505}), and (\ref{e518}). The flux-surface average of the previous equation yields 
+\begin{equation}
+d_{\mit\Omega}^{\,2}\!\left(\langle X^4\rangle\,d_{\mit\Omega} Y_i\right)= 0.
+\end{equation}
+We can solve the previous equation, subject to the boundary conditions (\ref{e502}) and (\ref{e506}), to give
+\begin{equation}\label{e530}
+Y_i({\mit\Omega},T)=\frac{v'(T)}{\int_1^\infty \!\frac{d{\mit\Omega}}{\langle X^4\rangle}}\left\{
+\begin{array}{llr}
+0&&-1\leq {\mit\Omega}\leq 1\\[0.5ex]
+\int_1^{\mit\Omega}\! \frac{d{\mit\Omega}'}{\langle X^4\rangle}&~~&{\mit\Omega}>1
+\end{array}\right.
+\end{equation}
+(Fitzpatrick \& Waelbroeck 2005).
+Here, we have made use of the fact that $Y_i=0$ within the magnetic separatrix of the island chain. We have also demanded that the ion
+fluid velocity, and, hence, the function $Y_i$,  be continuous across the separatrix, because the ion fluid possesses finite perpendicular viscosity. 
+Note, however, that the discontinuity in the function $L({\mit\Omega})$ across the separatrix [see Equation~(\ref{e526})] implies that the
+MHD and electron fluid velocities are  discontinuous across the separatrix. (See Section~\ref{s8.6}.)
+
+We need to evaluate Equation~(\ref{e472}) to second order in $\epsilon_d$ in order to include the perpendicular transport term. Doing so,
+we obtain
+\begin{equation}
+0=\epsilon_d\,\{{\cal V}_1,{\mit\Omega}\} + \epsilon_\chi\,(X^2\,d_{\mit\Omega} {\cal V}_{(0)} + {\cal V}_{(0)}),
+\end{equation}
+where use has been made of Equations~(\ref{e498}) and (\ref{e508}). The flux-surface average of the
+previous equation yields
+\begin{equation}
+\langle X^2\rangle\,d_{\mit\Omega} {\cal V}_{(0)} +\langle 1\rangle \,{\cal V}_{(0)}= 0.
+\end{equation}
+ This equation can be solved, subject to the boundary condition (\ref{e486a}) to
+give
+\begin{equation}
+{\cal V}_{(0)}({\mit\Omega}, T) = 0.
+\end{equation}
+Hence, we conclude that the lowest-order ion parallel flow is unaffected by the presence of the island chain.
+
+\subsection{Asymptotic Matching}
+Now that we have solved the four-field model in the immediate vicinity of the magnetic island chain, it is
+necessary to asymptotically match this solution to the solution in the outer region. 
+In the island rest frame, the reconnected magnetic flux, defined in Equation~(\ref{e99}), can be written
+\begin{equation}
+{\mit\Psi}_s = R_0\,B_z\,\hat{\mit\Psi}_s\,(\cos\zeta + {\rm i}\,\sin\zeta),
+\end{equation}
+where $\hat{\mit\Psi}_s$ is real and positive. It follows from
+Equations~(\ref{e110}), (\ref{e204}), and (\ref{e247a}) that
+\begin{align}
+{\rm Re}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)&= \frac{2\,r_s}{R_0\,B_z\,\hat{\mit\Psi}_s}\int_{r_{s-}}^{r_{s+}}\oint
+\frac{\partial^2\psi}{\partial r^2}\,\cos\zeta\,\frac{d\zeta}{2\pi}\,dx\nonumber\\[0.5ex]&=\frac{2}{\hat{w}\,\hat{R}_0\,\hat{\mit\Psi}_s}\int_{-\infty}^{\infty}\oint
+\frac{\partial^2\hat{\psi}}{\partial X^2}\,\cos\zeta\,\frac{d\zeta}{2\pi}\,dX,\\[0.5ex]
+{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)&= -\frac{2\,r_s}{R_0\,B_z\,\hat{\mit\Psi}_s}\int_{r_{s-}}^{r_{s+}}\oint
+\frac{\partial^2\psi}{\partial r^2}\,\sin\zeta\,\frac{d\zeta}{2\pi}\,dx\nonumber\\[0.5ex]&=-\frac{2}{\hat{w}\,\hat{R}_0\,\hat{\mit\Psi}_s}\int_{-\infty}^{\infty}\oint
+\frac{\partial^2\hat{\psi}}{\partial X^2}\,\sin\zeta\,\frac{d\zeta}{2\pi}\,dX.
+\end{align}
+Making use of Equations~(\ref{e456}), and (\ref{e466}), we obtain
+\begin{align}
+{\rm Re}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)&=\frac{2}{\hat{w}}\int_{-\infty}^{\infty}\oint
+\partial_X^{\,2}{\mit\Psi}\,\cos\zeta\,\frac{d\zeta}{2\pi}\,dX,\\[0.5ex]
+{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)&=-\frac{2}{\hat{w}}\int_{-\infty}^{\infty}\oint
+\partial_X^{\,2}{\mit\Psi}\,\sin\zeta\,\frac{d\zeta}{2\pi}\,dX.
+\end{align}
+However, according to Equations~(\ref{e473}) and (\ref{e496}),
+\begin{equation}
+\partial_X^{\,2}{\mit\Psi} = 1 + \epsilon_\beta\,\epsilon_d\,{\cal J}_0 + \epsilon_\beta\,\epsilon_d^{\,2}\,{\cal J}_1.
+\end{equation}
+Moreover, it is clear from Equations~(\ref{e524a}) and (\ref{e528a}) that ${\cal J}_0$ has the symmetry of $\cos\zeta$,
+whereas ${\cal J}_1$ has the symmetry of $\sin\zeta$. 
+Hence, we deduce that
+\begin{align}
+{\rm Re}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)&=\frac{2\,\epsilon_\beta\,\epsilon_d}{\hat{w}}\int_{-\infty}^{\infty}\oint
+{\cal J}_0\,\cos\zeta\,\frac{d\zeta}{2\pi}\,dX,\\[0.5ex]
+{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)&=-\frac{2\,\epsilon_\beta\,\epsilon_d^{\,2}}{\hat{w}}\int_{-\infty}^{\infty}\oint
+{\cal J}_1\,\sin\zeta\,\frac{d\zeta}{2\pi}\,dX.
+\end{align}
+The previous two equations can also be written
+\begin{align}
+{\rm Re}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)&=\frac{4\,\epsilon_\beta\,\epsilon_d}{\hat{w}}\int_{-1}^\infty
+\langle {\cal J}_0\,\cos\zeta\rangle\,d{\mit\Omega},\label{e542}\\[0.5ex]
+{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)&=-\frac{4\,\epsilon_\beta\,\epsilon_d^{\,2}}{\hat{w}}\int_{-1}^\infty
+\langle {\cal J}_1\,\sin\zeta\rangle\,d{\mit\Omega}=-\frac{4\,\epsilon_\beta\,\epsilon_d^{\,2}}{\hat{w}}\int_{-1}^\infty
+\langle X\,\{{\cal J}_1,{\mit\Omega}\}\rangle\,d{\mit\Omega}.\label{e543}
+\end{align}
+
+Equations~(\ref{e528a}) and (\ref{e543}) can be combined to give (Fitzpatrick \& Waelbroeck 2005)
+\begin{align}
+{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right) &=\frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi}{\hat{w}}\int_0^\infty
+\left\langle X^{2}\,d_{\mit\Omega}\!\left[d_{\mit\Omega}(X^3\,d_{\mit\Omega}Y_i)\right]\right\rangle d{\mit\Omega}\nonumber\\[0.5ex]
+&=\frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi}{\hat{w}}\int_1^\infty d_{\mit\Omega}\!\left(-\langle X\rangle\,Y_i
++2\,\langle X^3\rangle\,d_{\mit\Omega} Y_i + \langle X^5\rangle\,d_{\mit\Omega}^{\,2} Y_i\right)d{\mit\Omega}\nonumber\\[0.5ex]
+&= \frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi}{\hat{w}}\,\lim_{\mit\Omega\rightarrow\infty}\left(-\langle X\rangle\,Y_i
++2\,\langle X^3\rangle\,d_{\mit\Omega} Y_i + \langle X^5\rangle\,d_{\mit\Omega}^{\,2} Y_i\right),
+\end{align}
+where use has been made of the fact that $Y_i$ is continuous across the island separatrix. 
+Combining the previous equation with Equation~(\ref{e530}), we obtain (Fitzpatrick \& Waelbroeck 2005)
+\begin{equation}\label{e545}
+{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)  =- \frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi\,v'}{\hat{w}}.
+\end{equation}
+
+Equations~(\ref{e524a}) and (\ref{e542}) can be combined to give
+\begin{align}
+{\rm Re}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)&= \frac{2\,\epsilon_\beta\,\epsilon_d}{\hat{w}}
+\int_1^\infty d_{\mit\Omega}(M\,Y_i)\left\langle\widetilde{X^2}\,\cos\zeta\right\rangle d{\mit\Omega}
++\frac{4}{\epsilon_\eta\,\hat{w}}\,\frac{d(\ln \hat{w}^2)}{dT}\int_{-1}^\infty \frac{\langle \cos\zeta\rangle^2}{\langle 1\rangle}\,d{\mit\Omega}
+\end{align}
+Making use of Equations~(\ref{e518}), (\ref{e526}), and (\ref{e530}), the previous equation yields
+\begin{align}
+{\rm Re}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)&= -\frac{2\,\epsilon_\beta\,\epsilon_d\,v'}{(1+\tau)\,\hat{w}}
+\int_1^\infty d_{\mit\Omega}\!\left(\frac{F_i}{\langle X^2\rangle}\right)\left\langle\widetilde{X^2}\,\cos\zeta\right\rangle d{\mit\Omega}
+\nonumber\\[0.5ex]&\phantom{=}+\frac{4}{\epsilon_\eta\,\hat{w}}\,\frac{d(\ln \hat{w}^2)}{dT}\int_{-1}^\infty \frac{\langle \cos\zeta\rangle^2}{\langle 1\rangle}\,d{\mit\Omega},\label{e547}
+\end{align}
+where
+\begin{equation}
+F_i({\mit\Omega})=\left.\int_1^{\mit\Omega}\frac{d{\mit\Omega}'}{\langle X^4\rangle}\right/\int_1^\infty\frac{d{\mit\Omega}}{\langle X^4\rangle}
+\end{equation}
+Here, we have neglected terms that are quadratic in the small parameter $v'$. Finally, Equations~(\ref{e545}) and (\ref{e547})
+can be combined to give (Waelbroeck \& Fitzpatrick 1997)
+\begin{equation}
+{\rm Re}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)= I_1\,\tau_R\,\frac{d}{dt}\!\left(\frac{W}{r_s}\right)
++ I_2\left(\frac{\omega_\ast\,\tau_\varphi}{1+\tau}\right)\left(\frac{W}{r_s}\right)^2 {\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right),
+\end{equation}
+where
+\begin{align}
+I_1 &= 2\int_{-1}^\infty \frac{\langle \cos\zeta\rangle^2}{\langle 1\rangle}\,d{\mit\Omega},\\[0.5ex]
+I_2 &= \frac{1}{32}\int_1^\infty d_{\mit\Omega}\!\left(\frac{F_i}{\langle X^2\rangle}\right)\left\langle\widetilde{X^2}\,\cos\zeta\right\rangle d{\mit\Omega}.
+\end{align}
+Here, use has been made of Equations~(\ref{e317a}), (\ref{e318a}), (\ref{e481}), and (\ref{e482}).
 
@@
 \item Simmet, E.E., et al.\ 1996. {\em Statistical Analysis of the Global Energy Confinement Time in Ohmic Discharges in the ASDEX Tokamak}. Plasma Phys.\ Control.\ Fusion {\bf 38}, 689.
+\item Smolyakov, A.I.\ 1993. {\em Nonlinear Evolution of Tearing Modes in Inhomogeneous Plasmas}. Plasma Phys.\ Contol.\ Fusion 
+{\bf 35}, 657. 
+\item Smolyakov, A.I., et al.\ 1995. {\em Rotating Nonlinear Magnetic islands in a Tokamak Plasma}. Phys.\ Plasmas {\bf 2}, 1581.
 \item Stix, T.H.\ 1973. {\em Decay of Poloidal Rotation in a Tokamak Plasma}. Phys.\ Fluids {\bf 16}, 1260.
@@
 \item Waelbroeck, F.L.\ 2003. {\em Shielding of Resonant Magnetic Perturbations in the Long Mean-Free Path Regime}. Phys.\ Plasmas {\bf 10}, 4040.
+\item Waelbroeck, F.L., and Fitzpatrick, R.\ 1997. {\em Rotation and Locking of Magnetic Islands}. Phys.\ Rev.\ Lett.\ {\bf 78}, 1703. 
 \item Waelbroeck, F.L., Hazeltine, R.D., and Morrison, P.J.\ 2009. {\em A Hamiltonian Electromagnetic Gyrofluid Model}. Phys.\ Plasmas {\bf 16}, 032109. 

### 2021-11-25 Documentation/TearingModeTheory.tex
Latest version

@@
 frequency},
-\begin{align}
+\begin{align}\label{omegai}
   \omega_{\ast\,i} &= \left(\frac{1}{1+\tau}\right)\left(\frac{m}{r_s}\right)V_\ast(r_s)
@@
 Here, $Q_\ast = S^{1/3}\,\omega_\ast\,\tau_H$, where
-\begin{equation}
-\omega_\ast = -\frac{m}{r_s}\frac{1}{e\,n_0\,B_z}\left.\frac{dp}{dr}\right|_{r_s}.
+\begin{equation}\label{omega}
+\omega_\ast = -\frac{m}{r_s}\,V_\ast(r_s)= -\frac{m}{r_s}\frac{1}{e\,n_0\,B_z}\left.\frac{dp}{dr}\right|_{r_s}.
 \end{equation}
@@
 gradient discontinuity at the resonant surface in response to the nonlinear localized electromagnetic torque that develops
-there.
+at the surface.
 
@@
 \begin{align}
-\epsilon_d &= \left(\frac{L_s}{L_n}\right)\left(\frac{d_\beta}{w}\right)^2,\\[0.5ex]
-\epsilon_\beta &= c_\beta^{\,2},\\[0.5ex]
+\epsilon_d &= \left(\frac{L_s}{L_n}\right)^2\left(\frac{d_\beta}{w}\right)^2,\label{e479}\\[0.5ex]
+\epsilon_\beta &= c_\beta^{\,2},\label{e480}\\[0.5ex]
 \epsilon_n&= \left(\frac{L_n}{L_s}\right)^2,\\[0.5ex]
@@
 \begin{align}
-v(T) &= \frac{\omega-\omega_E}{\omega_\ast},\\[0.5ex]
+v(T) &= \frac{\omega-\omega_E}{\omega_\ast},\label{e488}\\[0.5ex]
 v'(T) &= -\frac{\hat{w}}{2\,\omega_\ast}\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}}.
@@
 We conclude that parallel
-ion acoustic waves, whose dynamics are described by Equation~(\ref{e472}), have smoothed out
+ion acoustic waves, whose dynamics are described by Equation~(\ref{e472}),  smooth  out
 any variations in the lowest-order electron number density, ${\cal N}_0$,  around magnetic flux-surfaces. 
@@
  We conclude that the lowest-order normalized
-electrostatic potential (in the island rest frame), ${\mit\Phi}_{0}$, is also constant on magnetic flux-surfaces. 
+electrostatic potential (in the island rest frame), ${\mit\Phi}_{0}$, is  constant on magnetic flux-surfaces. 
 By symmetry, ${\mit\Phi}_{0}=0$ inside the magnetic separatrix of the island chain. In other words, the electrostatic
@@
 \end{equation}
-It follows that $M({\mit\Omega}<1)=0$. Also, Equations~(\ref{e484}) and (\ref{e498}) imply that
+It follows that $M({\mit\Omega}<1,T)=0$. Furthermore, Equations~(\ref{e484}) and (\ref{e498}) imply that
 \begin{equation}\label{e506}
@@
 where use has been made of Equations~(\ref{e498}), (\ref{e501}), and (\ref{e505}). Moreover, $d_{\mit\Omega}\equiv
-\partial/\partial{\mit\Omega}$.
+d/d{\mit\Omega}$.
 
@@
 ${\mit\Phi}_{(0)}({\mit\Omega},T)$,  ${\cal V}_{(0)}({\mit\Omega},T)$, and $\overline{\cal J}_0({\mit\Omega},T)$ undetermined. In fact, in order to determine
-the forms of these  four flux-surface functions we need to solve the rescaled four-field model to higher order in our expansion. In particular,
+the forms of these  four  functions we need to solve the rescaled four-field model to higher order in our expansion. In particular,
 we need to include the terms that describe the perpendicular diffusion of magnetic flux, ion momentum, and
@@
 \begin{equation}\label{e514}
-\frac{d(\ln \hat{w}^{\,2})}{dT}\,\cos\zeta = \{F, {\mit\Omega}\} + \epsilon_\beta\,\epsilon_d\,\epsilon_\eta\,{\cal J}_0,
+\frac{d(\ln \hat{w}^{\,2})}{dT}\,\cos\zeta = \{F_e, {\mit\Omega}\} + \epsilon_\beta\,\epsilon_d\,\epsilon_\eta\,{\cal J}_0,
 \end{equation}
@@
 \begin{equation}
-F ({\mit\Omega},\zeta,T)= \epsilon_d^2\,({\mit\Phi}_2+\epsilon_d\,{\mit\Phi}_3)-\epsilon_d^{\,2}\left(\frac{\tau}{1+\tau}\right)({\cal N}_2+\epsilon_d\,{\cal N}_3)
+F_e({\mit\Omega},\zeta,T)= \epsilon_d^2\,({\mit\Phi}_2+\epsilon_d\,{\mit\Phi}_3)-\epsilon_d^{\,2}\left(\frac{\tau}{1+\tau}\right)({\cal N}_2+\epsilon_d\,{\cal N}_3)
 - \epsilon_d^2\,s\,Y_e({\mit\Psi}_2+\epsilon_d\,{\mit\Psi}_3),
@@
 
+In the limit ${\mit\Omega}\gg 1$, the previous equation yields
+\begin{equation}
+Y_i\simeq v' -\left. \frac{v'}{\sqrt{2\,{\mit\Omega}}}\right/\int_1^\infty \frac{d{\mit\Omega}}{\langle X^4\rangle}.
+\end{equation}
+Hence, it follows from Equations~(\ref{e518}) and (\ref{e526}) that
+\begin{equation}
+M\simeq v' -\left. \frac{v'}{\sqrt{2\,{\mit\Omega}}}\right/\int_1^\infty \frac{d{\mit\Omega}}{\langle X^4\rangle} -\left(\frac{1}{1+\tau}\right)
+\frac{1}{\sqrt{2\,{\mit\Omega}}}
+\end{equation}
+in the same limit. A comparison with Equation~(\ref{e506}) reveals that
+\begin{equation}
+v = -\frac{1}{1+\tau} - v'\left/\int_1^\infty \frac{d{\mit\Omega}}{\langle X^4\rangle}\right.,
+\end{equation}
+or 
+\begin{equation}\label{e534}
+\omega = \omega_{\perp\,i} -v'\,\omega_\ast\left/\int_1^\infty \frac{d{\mit\Omega}}{\langle X^4\rangle}\right.,
+\end{equation}
+where
+\begin{equation}
+\omega_{\perp\,i} = \omega_E + \omega_{\ast\,i},
+\end{equation}
+and use has been made of Equations~(\ref{omegai}), (\ref{omega}), and (\ref{e488}).
+
 We need to evaluate Equation~(\ref{e472}) to second order in $\epsilon_d$ in order to include the perpendicular transport term. Doing so,
@@
 where $\hat{\mit\Psi}_s$ is real and positive. It follows from
-Equations~(\ref{e110}), (\ref{e204}), and (\ref{e247a}) that
+Equations~(\ref{e109}), (\ref{e204}), and (\ref{e247a}) that
 \begin{align}
 {\rm Re}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)&= \frac{2\,r_s}{R_0\,B_z\,\hat{\mit\Psi}_s}\int_{r_{s-}}^{r_{s+}}\oint
-\frac{\partial^2\psi}{\partial r^2}\,\cos\zeta\,\frac{d\zeta}{2\pi}\,dx\nonumber\\[0.5ex]&=\frac{2}{\hat{w}\,\hat{R}_0\,\hat{\mit\Psi}_s}\int_{-\infty}^{\infty}\oint
+\frac{\partial^2\psi}{\partial r^2}\,\cos\zeta\,\frac{d\zeta}{2\pi}\,dr\nonumber\\[0.5ex]&=\frac{2}{\hat{w}\,\hat{R}_0\,\hat{\mit\Psi}_s}\int_{-\infty}^{\infty}\oint
 \frac{\partial^2\hat{\psi}}{\partial X^2}\,\cos\zeta\,\frac{d\zeta}{2\pi}\,dX,\\[0.5ex]
 {\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)&= -\frac{2\,r_s}{R_0\,B_z\,\hat{\mit\Psi}_s}\int_{r_{s-}}^{r_{s+}}\oint
-\frac{\partial^2\psi}{\partial r^2}\,\sin\zeta\,\frac{d\zeta}{2\pi}\,dx\nonumber\\[0.5ex]&=-\frac{2}{\hat{w}\,\hat{R}_0\,\hat{\mit\Psi}_s}\int_{-\infty}^{\infty}\oint
+\frac{\partial^2\psi}{\partial r^2}\,\sin\zeta\,\frac{d\zeta}{2\pi}\,dr\nonumber\\[0.5ex]&=-\frac{2}{\hat{w}\,\hat{R}_0\,\hat{\mit\Psi}_s}\int_{-\infty}^{\infty}\oint
 \frac{\partial^2\hat{\psi}}{\partial X^2}\,\sin\zeta\,\frac{d\zeta}{2\pi}\,dX.
 \end{align}
-Making use of Equations~(\ref{e456}), and (\ref{e466}), we obtain
+Making use of Equations~(\ref{e456}) and (\ref{e466}), we obtain
 \begin{align}
@@
 \begin{align}
-{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right) &=\frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi}{\hat{w}}\int_0^\infty
+{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right) &=\frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi}{\hat{w}}\int_1^\infty
 \left\langle X^{2}\,d_{\mit\Omega}\!\left[d_{\mit\Omega}(X^3\,d_{\mit\Omega}Y_i)\right]\right\rangle d{\mit\Omega}\nonumber\\[0.5ex]
@@
 \end{align}
-where use has been made of the fact that $Y_i$ is continuous across the island separatrix. 
+where use has been made of the facts that $Y_i$ is zero inside the island separatrix, and $Y_i$ is continuous across the separatrix.
 Combining the previous equation with Equation~(\ref{e530}), we obtain (Fitzpatrick \& Waelbroeck 2005)
@@
 \end{equation}
+Finally, the previous equation can be combined with Equation~(\ref{e534}) to give
+\begin{equation}
+\omega=\omega_{\perp\,i} + I_1\left(\frac{\tau_\varphi}{\tau_H^{\,2}}\right)\left(\frac{W}{r_s}\right)^5{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right),
+\end{equation}
+where
+\begin{equation}
+I_1 = 2^{-12}\left/\int_1^{\infty} \frac{d{\mit\Omega}}{\langle X^4\rangle}\right. =3.584\times 10^{-4}. 
+\end{equation}
+Here, use has been made of Equations~(\ref{e479}), (\ref{e480}), and (\ref{e482}).
 
@@
 {\rm Re}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)&= \frac{2\,\epsilon_\beta\,\epsilon_d}{\hat{w}}
-\int_1^\infty d_{\mit\Omega}(M\,Y_i)\left\langle\widetilde{X^2}\,\cos\zeta\right\rangle d{\mit\Omega}
+\int_{1+}^\infty d_{\mit\Omega}(M\,Y_i)\left\langle\widetilde{X^2}\,\cos\zeta\right\rangle d{\mit\Omega}
 +\frac{4}{\epsilon_\eta\,\hat{w}}\,\frac{d(\ln \hat{w}^2)}{dT}\int_{-1}^\infty \frac{\langle \cos\zeta\rangle^2}{\langle 1\rangle}\,d{\mit\Omega}
@@
 \begin{equation}
-{\rm Re}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)= I_1\,\tau_R\,\frac{d}{dt}\!\left(\frac{W}{r_s}\right)
-+ I_2\left(\frac{\omega_\ast\,\tau_\varphi}{1+\tau}\right)\left(\frac{W}{r_s}\right)^2 {\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right),
+{\rm Re}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)= I_2\,\tau_R\,\frac{d}{dt}\!\left(\frac{W}{r_s}\right)
+- I_3\left(\frac{c_\beta}{1+\tau}\right)\left(\frac{d_\beta}{r_s}\right)\left(\frac{L_s}{L_n}\right)\left(\frac{\tau_\varphi}{\tau_H}\right)\left(\frac{W}{r_s}\right)^2 {\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right),
 \end{equation}
@@
 \begin{align}
-I_1 &= 2\int_{-1}^\infty \frac{\langle \cos\zeta\rangle^2}{\langle 1\rangle}\,d{\mit\Omega},\\[0.5ex]
-I_2 &= \frac{1}{32}\int_1^\infty d_{\mit\Omega}\!\left(\frac{F_i}{\langle X^2\rangle}\right)\left\langle\widetilde{X^2}\,\cos\zeta\right\rangle d{\mit\Omega}.
+I_2 &= 2\int_{-1}^\infty \frac{\langle \cos\zeta\rangle^2}{\langle 1\rangle}\,d{\mit\Omega} =0.8227,\\[0.5ex]
+I_3&= 2^{-6}\int_1^\infty d_{\mit\Omega}\!\left(\frac{F_i}{\langle X^2\rangle}\right)\left(\langle X^4\rangle - \frac{\langle X^2\rangle^2}{\langle 1\rangle}\right)d{\mit\Omega} = 3.055\times 10^{-3}.
 \end{align}

### 2021-11-26 Documentation/TearingModeTheory.tex
Started isolated islands

@@
 \end{equation}
-is the (real) tearing stability index in the absence of a wall, ${\mit\Delta}_{pw}= E_{ss}$ is the
+is the (real) tearing stability index in the absence of a wall, 
+\begin{equation}\label{epw}
+{\mit\Delta}_{pw}= E_{ss}
+\end{equation}
+ is the
 (real) tearing stability index in the presence of a perfectly conducting wall at $r=r_w$, and
@@
 v(T) &= \frac{\omega-\omega_E}{\omega_\ast},\label{e488}\\[0.5ex]
-v'(T) &= -\frac{\hat{w}}{2\,\omega_\ast}\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}}.
-\end{align}
-In the following, it is assumed that $v\sim{\cal O}(1)$ and $|v'|\ll 1$. Note that ${\mit\Psi}$, ${\mit\Phi}$, ${\cal N}$, ${\cal V}$, and ${\cal J}$ are all ${\cal O}(1)$ quantities.
+v'(T) &= -\frac{\hat{w}}{2\,\omega_\ast}\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}}.\label{e489}
+\end{align}
+Note that ${\mit\Psi}$, ${\mit\Phi}$, ${\cal N}$, ${\cal V}$, and ${\cal J}$ are all ${\cal O}(1)$ quantities.
 Note, further,  that the boundary conditions (\ref{e483})--(\ref{e487}),
@@
 sufficiently wide that ion acoustic waves propagating parallel to the magnetic field are able to smooth out any
-variations in the normalized electron number density, ${\cal N}$, around magnetic flux-surfaces (Scott, Hassam \& Drake 1985).
+variations in the normalized electron number density, ${\cal N}$, around magnetic flux-surfaces (Scott, Hassam \& Drake 1985). The fact that $\epsilon_d\ll 1$ implies that
+\begin{equation}
+w \gg \rho_\beta,
+\end{equation}
+where
+\begin{equation}
+\rho_\beta = \left(\frac{L_s}{L_n}\right)d_\beta
+\end{equation}
+is a characteristic lengthscale that is of order the ion poloidal gyroradius. 
  The orderings $\epsilon_\eta\ll 1$, $\epsilon_\chi\ll 1$, and $\epsilon_D\ll 1$ ensure that the island
@@
 \begin{equation}\label{e509}
-\{{\cal J}_0,{\mit\Omega}\} = -\partial_X\!\left({\mit\Phi}_0+\frac{{\cal N}_0}{1+\tau}, \partial_X {\mit\Phi}_0\right)=
+\{{\cal J}_0,{\mit\Omega}\} = -\partial_X\!\left\{{\mit\Phi}_0+\frac{{\cal N}_0}{1+\tau}, \partial_X {\mit\Phi}_0\right\}=
 \frac{1}{2}\left\{d_{\mit\Omega}\!\left[M\left(M+\frac{L}{1+\tau}\right)\right]X^2, {\mit\Omega}\right\},
@@
 \begin{align}
-V_\theta(x,\zeta,T) &= -\frac{\omega_\ast}{m}\,x\,M({\mit\Omega},T),\\[0.5ex]
-V_{\theta\,i}(x,\zeta,T)& = -\frac{\omega_\ast}{m}\,x\,Y_i({\mit\Omega},T)\\[0.5ex]
-V_{\theta\,e}(x,\zeta,T)& = -\frac{\omega_\ast}{m}\,x\,Y_e({\mit\Omega},T),
+V_\theta(x,\zeta,T) &= -\frac{r_s\,\omega_\ast}{m}\,|X|\,M({\mit\Omega},T),\\[0.5ex]
+V_{\theta\,i}(x,\zeta,T)& = -\frac{r_s\,\omega_\ast}{m}\,|X|\,Y_i({\mit\Omega},T)\\[0.5ex]
+V_{\theta\,e}(x,\zeta,T)& = -\frac{r_s\,\omega_\ast}{m}\,|X|\,Y_e({\mit\Omega},T),
 \end{align}
@@
 Here, we have taken into account the previously mentioned fact that $L=0$ within the island separatrix.
+Note that $L$ is discontinuous across the island separatrix, which implies that the density gradient, and, hence,
+the diamagnetic velocity, are both also discontinuous across the separatrix. Of course, there is not a real
+discontinuity. Given that the discontinuity in $L$ is mandated by the ordering $\epsilon_d=(\rho_\beta/w)^2\ll 1$, which
+requires $L$ to be a flux-surface function, and, hence, zero by symmetry inside the separatrix, it follows that the discontinuity is resolved by a thin layer of characteristic thickness $\rho_\beta$ on the island
+separatrix.
 
@@
 (Fitzpatrick \& Waelbroeck 2005).
-Here, we have made use of the fact that $Y_i=0$ within the magnetic separatrix of the island chain. We have also demanded that the ion
+Here, we have rejected, as unphysical, the solution that blows up as ${\mit\Omega}^{\,1/2}$ as ${\mit\Omega}\rightarrow\infty$. 
+We have also made use of the fact that $Y_i=0$ within the magnetic separatrix of the island chain. Finally, we have  demanded that the ion
 fluid velocity, and, hence, the function $Y_i$,  be continuous across the separatrix, because the ion fluid possesses finite perpendicular viscosity. 
 Note, however, that the discontinuity in the function $L({\mit\Omega})$ across the separatrix [see Equation~(\ref{e526})] implies that the
-MHD and electron fluid velocities are  discontinuous across the separatrix. (See Section~\ref{s8.6}.)
-
-In the limit ${\mit\Omega}\gg 1$, the previous equation yields
-\begin{equation}
-Y_i\simeq v' -\left. \frac{v'}{\sqrt{2\,{\mit\Omega}}}\right/\int_1^\infty \frac{d{\mit\Omega}}{\langle X^4\rangle}.
-\end{equation}
-Hence, it follows from Equations~(\ref{e518}) and (\ref{e526}) that
-\begin{equation}
-M\simeq v' -\left. \frac{v'}{\sqrt{2\,{\mit\Omega}}}\right/\int_1^\infty \frac{d{\mit\Omega}}{\langle X^4\rangle} -\left(\frac{1}{1+\tau}\right)
-\frac{1}{\sqrt{2\,{\mit\Omega}}}
-\end{equation}
-in the same limit. A comparison with Equation~(\ref{e506}) reveals that
-\begin{equation}
-v = -\frac{1}{1+\tau} - v'\left/\int_1^\infty \frac{d{\mit\Omega}}{\langle X^4\rangle}\right.,
-\end{equation}
-or 
-\begin{equation}\label{e534}
-\omega = \omega_{\perp\,i} -v'\,\omega_\ast\left/\int_1^\infty \frac{d{\mit\Omega}}{\langle X^4\rangle}\right.,
-\end{equation}
-where
-\begin{equation}
-\omega_{\perp\,i} = \omega_E + \omega_{\ast\,i},
-\end{equation}
-and use has been made of Equations~(\ref{omegai}), (\ref{omega}), and (\ref{e488}).
+MHD and electron fluid velocities are  discontinuous across the separatrix. (See Section~\ref{s8.6}.) As previously
+mentioned, these discontinuities are resolved in a layer of characteristic thickness $\rho_\beta$.
 
@@
 \end{equation}
-Finally, the previous equation can be combined with Equation~(\ref{e534}) to give
-\begin{equation}
-\omega=\omega_{\perp\,i} + I_1\left(\frac{\tau_\varphi}{\tau_H^{\,2}}\right)\left(\frac{W}{r_s}\right)^5{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right),
-\end{equation}
-where
-\begin{equation}
-I_1 = 2^{-12}\left/\int_1^{\infty} \frac{d{\mit\Omega}}{\langle X^4\rangle}\right. =3.584\times 10^{-4}. 
-\end{equation}
-Here, use has been made of Equations~(\ref{e479}), (\ref{e480}), and (\ref{e482}).
+The previous equation yields
+\begin{equation}
+\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}} = \left(\frac{\tau_\varphi\,\hat{w}^{\,4}}{2\,\tau_H^{\,2}}{\rm Im}\!\right)\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right),
+\end{equation}
+where use has been made of Equation~(\ref{e489}).
+The same relation can be obtained by integrating Equation~(\ref{e182}) across the resonant surface, making use of Equation~(\ref{e157}), as well as the
+identification
+\begin{equation}
+\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}} = m\left[r\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial r}\right]_{r_{s-}}^{r_{s+}}.
+\end{equation}
+The latter result merely states that the  discontinuity in the MHD fluid velocity gradient that develop at the resonant
+surface is mirrored by an equal discontinuity in the ion fluid velocity gradient (because the discontinuity is ultimately due to 
+a discontinuity in the ${\bf E}\times {\bf B}$ velocity gradient).
 
@@
 \int_1^\infty d_{\mit\Omega}\!\left(\frac{F_i}{\langle X^2\rangle}\right)\left\langle\widetilde{X^2}\,\cos\zeta\right\rangle d{\mit\Omega}
-\nonumber\\[0.5ex]&\phantom{=}+\frac{4}{\epsilon_\eta\,\hat{w}}\,\frac{d(\ln \hat{w}^2)}{dT}\int_{-1}^\infty \frac{\langle \cos\zeta\rangle^2}{\langle 1\rangle}\,d{\mit\Omega},\label{e547}
+\nonumber\\[0.5ex]
+&\phantom{=}+ \frac{2\,\epsilon_\beta\,\epsilon_d\,v'^{\,2}}{\hat{w}} \,\int_1^\infty d_{\mit\Omega}\!\left(F_i^{\,2}\right)\left\langle\widetilde{X^2}\,\cos\zeta\right\rangle d{\mit\Omega}\nonumber\\[0.5ex]
+&\phantom{=}+\frac{4}{\epsilon_\eta\,\hat{w}}\,\frac{d(\ln \hat{w}^2)}{dT}\int_{-1}^\infty \frac{\langle \cos\zeta\rangle^2}{\langle 1\rangle}\,d{\mit\Omega},\label{e547}
 \end{align}
@@
 \end{equation}
-Here, we have neglected terms that are quadratic in the small parameter $v'$. Finally, Equations~(\ref{e545}) and (\ref{e547})
-can be combined to give (Waelbroeck \& Fitzpatrick 1997)
-\begin{equation}
-{\rm Re}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)= I_2\,\tau_R\,\frac{d}{dt}\!\left(\frac{W}{r_s}\right)
-- I_3\left(\frac{c_\beta}{1+\tau}\right)\left(\frac{d_\beta}{r_s}\right)\left(\frac{L_s}{L_n}\right)\left(\frac{\tau_\varphi}{\tau_H}\right)\left(\frac{W}{r_s}\right)^2 {\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right),
-\end{equation}
+Finally, Equations~(\ref{e545}) and (\ref{e547})
+can be combined to give (Waelbroeck \& Fitzpatrick 1997; Fitzpatrick \& Waelbroeck 2005a)
+\begin{align}\label{e559}
+{\rm Re}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)&= I_1\,\tau_R\,\frac{d}{dt}\!\left(\frac{4\,w}{r_s}\right)
+- I_2\left(\frac{c_\beta}{1+\tau}\right)\left(\frac{\rho_\beta}{r_s}\right)\left(\frac{\tau_\varphi}{\tau_H}\right)\left(\frac{w}{r_s}\right)^2 {\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)\nonumber\\[0.5ex]
+&\phantom{=} -I_3\left(\frac{\tau_\varphi}{\tau_H}\right)^2 \left(\frac{w}{r_s}\right)^7\left[{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)\right]^2, 
+\end{align}
 where
 \begin{align}
-I_2 &= 2\int_{-1}^\infty \frac{\langle \cos\zeta\rangle^2}{\langle 1\rangle}\,d{\mit\Omega} =0.8227,\\[0.5ex]
-I_3&= 2^{-6}\int_1^\infty d_{\mit\Omega}\!\left(\frac{F_i}{\langle X^2\rangle}\right)\left(\langle X^4\rangle - \frac{\langle X^2\rangle^2}{\langle 1\rangle}\right)d{\mit\Omega} = 3.055\times 10^{-3}.
+I_1 &= 2\int_{-1}^\infty \frac{\langle \cos\zeta\rangle^2}{\langle 1\rangle}\,d{\mit\Omega} =0.8227,\\[0.5ex]
+I_2&= \frac{1}{4}\int_1^\infty d_{\mit\Omega}\!\left(\frac{F_i}{\langle X^2\rangle}\right)\left(\langle X^4\rangle - \frac{\langle X^2\rangle^2}{\langle 1\rangle}\right)d{\mit\Omega} =4.889\times 10^{-2},\\[0.5ex]
+I_3&= \frac{1}{16}\int_1^\infty d_{\mit\Omega}\!\left(F_i^{\,2}\right)\left(\langle X^4\rangle - \frac{\langle X^2\rangle^2}{\langle 1\rangle}\right)d{\mit\Omega} =2.944\times 10^{-2}.
 \end{align}
 Here, use has been made of Equations~(\ref{e317a}), (\ref{e318a}), (\ref{e481}), and (\ref{e482}).
+
+\section{Isolated Magnetic Island Chain}
+\subsection{Introduction}
+Suppose that the wall surrounding the plasma is perfectly conducting (i.e.\, $\tau_w\rightarrow\infty$), and that there is no current
+flowing through the external magnetic-field coil (i.e., $\hat{I}_c=0$). In this case, assuming that $d/dt = -{\rm i}\,\omega$, Equations~(\ref{e202}), 
+(\ref{e203}), and (\ref{epw}),  yield 
+\begin{equation}\label{e563}
+\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right) ={\mit\Delta}_{pw},
+\end{equation}
+where ${\mit\Delta}_{pw}$ is the (real) perfect-wall tearing stability index.
+
+\subsection{Rutherford Island Width Evolution Equation}
+It is clear from the previous equation that
+\begin{equation}
+{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right) = 0,
+\end{equation}
+which implies that no electromagnetic torque is exerted at the resonant surface. (See Section~\ref{storque}.) 
+Hence, Equations~(\ref{e559}) and (\ref{e563}) yield the {\em Rutherford island width evolution equation}\/ (Rutherford 1973):
+\begin{equation}
+I_2\,\tau_R\,\frac{d}{dt}\!\left(\frac{4\,w}{r_s}\right)= {\mit\Delta}_{nw}.
+\end{equation}
+According to this equation, if the perfect-wall tearing stability index is positive then the width of the magnetic
+island chain at the resonant surface grows algebraically on the resistive evolution timescale, $\tau_R$.
 
@@
 \item Fitzpatrick, R., and Waelbroeck, F.L.\ 2005. {\em Two-Fluid Magnetic Island Dynamics in Slab Geometry. I. Isolated Islands}.
-Phys.\ Plasmas {\bf 12}, 022307. 
+\item Fitzpatrick, R., and Waelbroeck, F.L.\ 2005a. {\em Two-Fluid Magnetic Island Dynamics in Slab Geometry. II. Islands Interacting with Resistive Walls or Resonant Magnetic Perturbations}.
+Phys.\ Plasmas {\bf 12}, 022308. 
 \item Fitzpatrick, R., and Waelbroeck, F.L.\ 2009. {\em Effect of Flow Damping on Drift-Tearing Magnetic Islands in Tokamak Plasmas}.

### 2021-11-26 Documentation/Section8/Integrals.h

@@ -49,9 +49,7 @@ class Integrals
 
   // Useful functions
   double Ak  (double k);
-  double Bk  (double k);
   double Ck  (double k);
-  double Dk  (double k);
   double Ek  (double k);
 
   // Evaluate right-hand sides of differential equations

### 2021-11-28 Documentation/TearingModeTheory.tex
Latest version
Started isolated islands

@@
 {\cal J}_0({\mit\Omega},\zeta,T)= 
-\frac{1}{2}\,d_{\mit\Omega}\!\left[M\left(M+\frac{L}{1+\tau}\right)\right]\!\widetilde{X}^2 + \overline{\cal J}_0({\mit\Omega},T),
+\frac{1}{2}\,d_{\mit\Omega}\!\left[M\left(M+\frac{L}{1+\tau}\right)\right]\!\widetilde{X^2} + \overline{\cal J}_0({\mit\Omega},T),
 \end{equation}
@@
 \begin{align}
-V_\theta(x,\zeta,T) &= -\frac{r_s\,\omega_\ast}{m}\,|X|\,M({\mit\Omega},T),\\[0.5ex]
-V_{\theta\,i}(x,\zeta,T)& = -\frac{r_s\,\omega_\ast}{m}\,|X|\,Y_i({\mit\Omega},T)\\[0.5ex]
-V_{\theta\,e}(x,\zeta,T)& = -\frac{r_s\,\omega_\ast}{m}\,|X|\,Y_e({\mit\Omega},T),
+V_{\theta\,e}(X,\zeta,T)& = -\frac{r_s\,\omega_\ast}{m}\,|X|\,Y_e({\mit\Omega},T),\\[0.5ex]
+V_\theta(X,\zeta,T) &= -\frac{r_s\,\omega_\ast}{m}\,|X|\,M({\mit\Omega},T),\\[0.5ex]
+V_{\theta\,i}(X,\zeta,T)& = -\frac{r_s\,\omega_\ast}{m}\,|X|\,Y_i({\mit\Omega},T),
 \end{align}
@@
 \begin{align}
-Y_i({\mit\Omega},T)&= M+\left(\frac{1}{1+\tau}\right)L,\label{e518}\\[0.5ex]
-Y_e({\mit\Omega},T)&= Y_i- L.
-\end{align}
-Here, $V_\theta$, $V_{\theta\,i}$, and $V_{\theta\,e}$ refer to velocity components of the MHD, ion, and
-electron fluid, respectively. Note that $Y_i$ and $Y_e$ are both zero inside the magnetic separatrix of the island chain.
+Y_e({\mit\Omega},T)&= M- \left(\frac{\tau}{1+\tau}\right)L,\\[0.5ex]
+Y_i({\mit\Omega},T)&= M+\left(\frac{1}{1+\tau}\right)L,\label{e518}
+\end{align}
+Here,  $V_{\theta\,e}$, $V_\theta$, and $V_{\theta\,i}$  refer to velocity components of the electron, MHD, and ion 
+ fluid, respectively. Note that $Y_e$ and $Y_i$ are both zero inside the magnetic separatrix of the island chain.
 
@@
 \begin{equation}
-F_e({\mit\Omega},\zeta,T)= \epsilon_d^2\,({\mit\Phi}_2+\epsilon_d\,{\mit\Phi}_3)-\epsilon_d^{\,2}\left(\frac{\tau}{1+\tau}\right)({\cal N}_2+\epsilon_d\,{\cal N}_3)
+F_e({\mit\Omega},\zeta,T)= \epsilon_d^2\,({\mit\Phi}_2+\epsilon_d\,{\mit\Phi}_3)-\epsilon_d^{2}\left(\frac{\tau}{1+\tau}\right)({\cal N}_2+\epsilon_d\,{\cal N}_3)
 - \epsilon_d^2\,s\,Y_e({\mit\Psi}_2+\epsilon_d\,{\mit\Psi}_3),
@@
 \begin{equation}
-\overline{\cal J}_0({\mit\Omega},T) = \frac{1}{\epsilon_\beta\,\epsilon_d\,\epsilon_\eta}\frac{d(\ln \hat{w}^{\,2})}{dT}\,\frac{\langle\cos\zeta\rangle}{\langle 1\rangle},
+\overline{\cal J}_0({\mit\Omega},T) = \frac{1}{\epsilon_\beta\,\epsilon_d\,\epsilon_\eta}\frac{d(\ln \hat{w}^{2})}{dT}\,\frac{\langle\cos\zeta\rangle}{\langle 1\rangle},
 \end{equation}
@@
 {\cal J}_0({\mit\Omega},\zeta)= 
-\frac{1}{2}\,d_{\mit\Omega}\!\left(M\,Y_i\right)\widetilde{X}^2+ \frac{1}{\epsilon_\beta\,\epsilon_d\,\epsilon_\eta}\frac{d(\ln \hat{w}^{\,2})}{dT}\,\frac{\langle\cos\zeta\rangle}{\langle 1\rangle},
+\frac{1}{2}\,d_{\mit\Omega}\!\left(M\,Y_i\right)\widetilde{X^2}+ \frac{1}{\epsilon_\beta\,\epsilon_d\,\epsilon_\eta}\frac{d(\ln \hat{w}^{2})}{dT}\,\frac{\langle\cos\zeta\rangle}{\langle 1\rangle},
 \end{equation}
@@
 Here, we have taken into account the previously mentioned fact that $L=0$ within the island separatrix.
-Note that $L$ is discontinuous across the island separatrix, which implies that the density gradient, and, hence,
-the diamagnetic velocity, are both also discontinuous across the separatrix. Of course, there is not a real
+Note that $L$ is discontinuous across the island separatrix, which implies that the density gradient---and, hence,
+the diamagnetic velocity---are both also discontinuous across the separatrix. Of course, there is not a real
 discontinuity. Given that the discontinuity in $L$ is mandated by the ordering $\epsilon_d=(\rho_\beta/w)^2\ll 1$, which
-requires $L$ to be a flux-surface function, and, hence, zero by symmetry inside the separatrix, it follows that the discontinuity is resolved by a thin layer of characteristic thickness $\rho_\beta$ on the island
+requires $L$ to be a flux-surface function---and, hence, zero, by symmetry, inside the separatrix---it is plausible that the discontinuity is resolved by a thin layer of characteristic thickness $\rho_\beta$ on the island
 separatrix.
@@
 We have also made use of the fact that $Y_i=0$ within the magnetic separatrix of the island chain. Finally, we have  demanded that the ion
-fluid velocity, and, hence, the function $Y_i$,  be continuous across the separatrix, because the ion fluid possesses finite perpendicular viscosity. 
+fluid velocity---and, hence, the function $Y_i$---is continuous across the separatrix, because the ion fluid possesses finite perpendicular viscosity. 
 Note, however, that the discontinuity in the function $L({\mit\Omega})$ across the separatrix [see Equation~(\ref{e526})] implies that the
-MHD and electron fluid velocities are  discontinuous across the separatrix. (See Section~\ref{s8.6}.) As previously
+electron and MHD  fluid velocities are  discontinuous across the separatrix. (See Section~\ref{s8.6}.) As previously
 mentioned, these discontinuities are resolved in a layer of characteristic thickness $\rho_\beta$.
@@
 \end{equation}
- This equation can be solved, subject to the boundary condition (\ref{e486a}) to
+ The previous equation can be solved, subject to the boundary condition (\ref{e486a}) to
 give
@@
 \begin{equation}
-\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}} = \left(\frac{\tau_\varphi\,\hat{w}^{\,4}}{2\,\tau_H^{\,2}}{\rm Im}\!\right)\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right),
+\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}} = \left(\frac{\tau_\varphi\,\hat{w}^{\,4}}{2\,\tau_H^{\,2}}\right){\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right),
 \end{equation}
@@
 \end{equation}
-The latter result merely states that the  discontinuity in the MHD fluid velocity gradient that develop at the resonant
+The previous identification  merely states that the  discontinuity in the MHD fluid velocity gradient that develop at the resonant
 surface is mirrored by an equal discontinuity in the ion fluid velocity gradient (because the discontinuity is ultimately due to 
@@
 \begin{equation}\label{e563}
-\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right) ={\mit\Delta}_{pw},
+\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s} ={\mit\Delta}_{pw},
 \end{equation}
@@
 It is clear from the previous equation that
-\begin{equation}
+\begin{equation}\label{e559}
 {\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right) = 0,
 \end{equation}
-which implies that no electromagnetic torque is exerted at the resonant surface. (See Section~\ref{storque}.) 
-Hence, Equations~(\ref{e559}) and (\ref{e563}) yield the {\em Rutherford island width evolution equation}\/ (Rutherford 1973):
-\begin{equation}
-I_2\,\tau_R\,\frac{d}{dt}\!\left(\frac{4\,w}{r_s}\right)= {\mit\Delta}_{nw}.
+which implies that zero electromagnetic torque is exerted at the resonant surface. (See Section~\ref{storque}.) 
+Moreover, 
+\begin{equation}
+{\rm Re}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right) = {\mit\Delta}_{pw}.
+\end{equation}
+Hence, Equations~(\ref{e456}), (\ref{e559}), and (\ref{e559}) yield the {\em Rutherford island width evolution equation}\/ (Rutherford 1973):
+\begin{equation}
+I_1\,\tau_R\,\frac{d}{dt}\!\left(\frac{W}{r_s}\right)= {\mit\Delta}_{pw}.
 \end{equation}

### 2021-12-02 Documentation/TearingModeTheory.tex
Finished first part of tearing mode write up

@@
 \title{\bf Tearing Mode Dynamics in Tokamak Plasmas}
-\author{R.~Fitzpatrick\,\footnote{rfitzp@utexas.edu}\\
+\author{R.~Fitzpatrick\,\footnote{rfitzp@utexas.edu}\\[0.5ex]
 Institute for Fusion Studies,\\  Department of Physics,\\  University of Texas at Austin,\\  Austin TX 78712, USA}
@@
 the {\em cylindrical tearing mode equation}\/ (Wesson 1978; Fitzpatrick 1993),
-\begin{equation}
+\begin{equation}\label{e97}
 \frac{\partial^2\psi}{\partial r^2} + \frac{1}{r}\,\frac{\partial\psi}{\partial r}-\frac{m^2}{r^2}\,\psi - \frac{J_z'\,\psi}{r\,(1/q-n/m)}=  0,
@@
 for $\rho<0$. Here, 
-\begin{align}
+\begin{align}\label{e108}
 \alpha_s& =- \left(\frac{r\,q\,J_z'}{s}\right)_{r=r_s},\\[0.5ex]
@@
 \begin{equation}\label{e134}
-{\mit\Delta\Psi}_s = \tau_s\left(\frac{d{\mit\Psi}_s}{dt} + {\rm i}\,\omega_s\,{\mit\Psi}_s\right).
+{\mit\Delta\Psi}_s = \tau_s\left(\frac{d{\mit\Psi}_s}{dt} + {\rm i}\,\omega\,{\mit\Psi}_s\right).
 \end{equation}
 Here, $\tau_s$ is the {\em reconnection time}\/ (i.e., the typical timescale on which magnetic reconnection takes place in the
-resonant layer surrounding the resonant surface), whereas $\omega_s$ is the so-called {\em natural frequency}. 
-The natural frequency is the phase velocity of the tearing mode when the wall is perfectly conducting. The
-natural frequency is non-zero because the reconnected flux in the resonant layer is convected by the local plasma
-flow (Fitzpatrick 1993). (See Section~\ref{s6.2}.)
+resonant layer surrounding the resonant surface), whereas $\omega$ is the phase velocity 
+of the tearing mode when the wall is perfectly conducting. The
+phase velocity  is non-zero because the reconnected flux in the resonant layer is convected by the local plasma
+flow (Fitzpatrick 1993). (See Sections~\ref{s6.2} and \ref{sphase1}.)
 
@@
 In general, $\psi$ is continuous across the field-coil (in accordance with Maxwell's equations), whereas $\partial\psi/\partial r$ is discontinuous.
-The discontinuity in $\partial\psi/\partial r$ is caused by the helical currents flowing in the coil.
+The discontinuity in $\partial\psi/\partial r$ is caused by the helical current flowing in the coil.
 The complex quantity ${\mit\Psi}_c(t)$ determines the amplitude and
@@
 \begin{align}\label{e152}
-T_\theta(r) &= \left\langle r\,{\bf j}\times {\bf B}\cdot {\bf e}_\theta\right\rangle\\[0.5ex]
-T_\varphi(r) &= \left\langle R_0\,{\bf j}\times {\bf B}\cdot {\bf e}_z\right\rangle,
+T_\theta(r) &= \left\{ r\,{\bf j}\times {\bf B}\cdot {\bf e}_\theta\right\}\\[0.5ex]
+T_\varphi(r) &= \left\{ R_0\,{\bf j}\times {\bf B}\cdot {\bf e}_z\right\},
 \end{align}
@@
 \begin{equation}
-\left\langle\cdots\right\rangle \equiv \oint\oint r\,R_0\,(\cdots)\,d\theta\,d\varphi
+\left\{\cdots\right\} \equiv \oint\oint r\,R_0\,\cdots\,d\theta\,d\varphi
 \end{equation}
@@
 \begin{equation}\label{e176}
-\left\langle\rho\,\frac{\partial (r\,V_{\theta\,i})}{\partial t} \right\rangle 
-+\left\langle \rho\left[V_{r\,i}\,\frac{\partial (r\,V_{\theta\,i})}{\partial r} + V_{z\,i}\,\frac{\partial(r\, V_{\theta\,i})}{\partial z}
-\right]\right\rangle + [\zeta_i^{-1}]\,\langle r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\rangle
+\left\{\rho\,\frac{\partial (r\,V_{\theta\,i})}{\partial t} \right\} 
++\left\{ \rho\left[V_{r\,i}\,\frac{\partial (r\,V_{\theta\,i})}{\partial r} + V_{z\,i}\,\frac{\partial(r\, V_{\theta\,i})}{\partial z}
+\right]\right\} + [\zeta_i^{-1}]\,\{ r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\}
 = [\delta_i^{-2}]\,T_{\theta\,s}\,\delta(r-r_s),
@@
 
-The largest contribution to $\langle r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\rangle$
+The largest contribution to $\{ r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\}$
 comes from the ion parallel viscosity tensor acting on the zeroth-order (in perturbed quantities) ion flow.
@@
 $B_z$ varies slightly around magnetic flux-surfaces, being larger on the inboard side of the torus than on the outboard side (Wesson 2011).
-This variation gives rise to a residual contribution to $\langle r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\rangle$.
+This variation gives rise to a residual contribution to $\{r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\}$.
 It is plausible that this contribution is not a dominant term in Equation~(\ref{e176})  [i.e., it is not ${\cal O}(\zeta_i^{-1})$ larger than the
 other terms in the equation].
-To be more exact, if the residual contribution is ${\cal O}(\zeta_i)$ times smaller than the non-averaged  contribution then  $\langle r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\rangle$ ceases to be a dominant term in the equation.
+To be more exact, if the residual contribution is ${\cal O}(\zeta_i)$ times smaller than the non-averaged  contribution then  $\{ r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\}$ ceases to be a dominant term in the equation.
 
@@
 Here, ${\mit\Omega}_\theta(r,t)$ and ${\mit\Omega}_\varphi(r,t)$ are the ion poloidal and toroidal angular velocity
-profiles, respectively. When $\langle r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\rangle$ is evaluated with  the ion parallel viscosity tensor, and the zeroth-order
+profiles, respectively. When $\{ r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\}$ is evaluated with  the ion parallel viscosity tensor, and the zeroth-order
 ion flow, it gives rise to a term that acts to relax the ion poloidal angular velocity profile toward a so-called {\em neoclassical
 profile}\/ determined by ion density and temperature gradients (Stix 1973; Hirshman \& Sigmar 1981). In principle, the
-contribution of the ion perpendicular viscosity tensor to $\langle r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\rangle$ 
+contribution of the ion perpendicular viscosity tensor to $\{ r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\}$ 
 is ${\cal O}(\zeta_i^{\,2})$ smaller than the contribution of the ion parallel viscosity tensor. (See Section~\ref{sbrag}.) In practice, the magnitude of the ion perpendicular
@@
 plasma turbulence (Wesson 2011). Hence, it is reasonable to include the contribution of the enhanced perpendicular
-viscosity tensor to $\langle r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\rangle$. Our model form for $\langle r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\rangle$ is written
+viscosity tensor to $\{ r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\}$. Our model form for $\{ r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\}$ is written
 \begin{equation}\label{e178}
-\langle r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\rangle = 4\pi^2\,R_0\left[ \frac{\rho}{\tau_\theta}\,r^{\,3}\,({\mit\Omega}_\theta-{\mit\Omega}_{\theta\,{\rm nc}}) -\frac{\partial}{\partial r}\!\left(\mu_\perp\,r^{\,3}\,\frac{\partial{\mit\Omega}_\theta}{\partial r}\right)\right].
+\{ r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\} = 4\pi^2\,R_0\left[ \frac{\rho}{\tau_\theta}\,r^{\,3}\,({\mit\Omega}_\theta-{\mit\Omega}_{\theta\,{\rm nc}}) -\frac{\partial}{\partial r}\!\left(\mu_\perp\,r^{\,3}\,\frac{\partial{\mit\Omega}_\theta}{\partial r}\right)\right].
 \end{equation}
@@
 plasma flow at the resonant surface induced by the electromagnetic torques that develop in the vicinity of this
-surface will modify the convection velocity. Consequently, the natural frequency of the reconnected flux can be written
+surface will modify the convection velocity. Consequently, the phase velocity of the tearing mode can be written
 \begin{equation}\label{e200}
- \omega_s(t) = \omega_{s\,0} + ({\bf k}\cdot {\mit\Delta}{\bf V}_i)_{r=r_s}=
- \omega_{s\,0} + m\,{\mit\Delta\Omega}_\theta(r_s,t) - n\,{\mit\Delta\Omega}_\varphi(r_s,t),
-\end{equation}
-where $\omega_{s\,0}$ is the unperturbed natural frequency.
+ \omega(t) = \omega_{0} + ({\bf k}\cdot {\mit\Delta}{\bf V}_i)_{r=r_s}=
+ \omega_{0} + m\,{\mit\Delta\Omega}_\theta(r_s,t) - n\,{\mit\Delta\Omega}_\varphi(r_s,t),
+\end{equation}
+where $\omega_{0}$ is the unperturbed phase velocity.
 The previous expression is known as the {\em no-slip constraint}\/ (Fitzpatrick 1993), and has been verified experimentally (Vahala, et al.\ 1980).
@@
 \begin{equation}\label{e201}
-\omega_s(t) = \omega_{s\,0} - \sum_{p=1,\infty}\left[\alpha_p(t)+\beta_p(t)\right].
+\omega(t) = \omega_{0} - \sum_{p=1,\infty}\left[\alpha_p(t)+\beta_p(t)\right].
 \end{equation}
@@
 \begin{align}\label{e202}
-{\mit\Delta\hat{\Psi}}_s\equiv \tau_s\left(\frac{d\hat{\mit\Psi}_s}{dt} + {\rm i}\,\omega_s\,\hat{\mit\Psi}_s\right) &= E_{ss}\,\hat{\mit\Psi}_s + E_{sw}\,\hat{\mit\Psi}_w,\\[0.5ex]
+{\mit\Delta\hat{\Psi}}_s\equiv \tau_s\left(\frac{d\hat{\mit\Psi}_s}{dt} + {\rm i}\,\omega\,\hat{\mit\Psi}_s\right) &= E_{ss}\,\hat{\mit\Psi}_s + E_{sw}\,\hat{\mit\Psi}_w,\\[0.5ex]
 \tau_w\,\frac{d\hat{\mit\Psi}_w}{dt} &= E_{sw}\,\hat{\mit\Psi}_s +\tilde{E}_{ww}\,\hat{\mit\Psi}_w
 +\hat{I}_c,\label{e203}\\[0.5ex]
-\omega_s(t)& = \omega_{s\,0} - \sum_{p=1,\infty}\left[\alpha_p(t)+\beta_p(t)\right],\\[0.5ex]
+\omega(t)& = \omega_{0} - \sum_{p=1,\infty}\left[\alpha_p(t)+\beta_p(t)\right],\label{e210a}\\[0.5ex]
 (1+2\,q_s^{\,2})\,\frac{d\alpha_p}{dt} + \left(\frac{1}{\tau_{\theta\,s}}+\frac{j_{1\,p}^{\,2}}{\tau_{M}}\right)\alpha_p
@@
 Equations~(\ref{e202})--(\ref{e206}) contain two quantities---namely, the reconnection time, $\tau_s$, and the unperturbed
-natural frequency, $\omega_{s\,0}$---that can only be determined by solving for the plasma response in the radially-thin resonant layer surrounding the resonant surface.
+phase velocity, $\omega_{0}$---that can only be determined by solving for the plasma response in the radially-thin resonant layer surrounding the resonant surface.
 Unfortunately, determining the resonant plasma response is not a straightforward task.
@@
 \begin{equation}\label{e226a}
-V_A = \frac{B_z}{\sqrt{\mu_0\,n_0\,m_i}}.
+V_A =\frac{a}{\tau_A}= \frac{B_z}{\sqrt{\mu_0\,n_0\,m_i}}.
 \end{equation}
@@
 \end{align}
-where $\hat{t}=V_A\,t/r_s$, $\hat{\omega}=r_s\,\omega/V_A$, and $\omega$ is the frequency of the tearing mode in the laboratory frame. 
+where $\hat{t}=V_A\,t/r_s$, $\hat{\omega}=r_s\,\omega/V_A$, and $\omega$ is the phase velocity of the tearing mode in the laboratory frame. 
 Substituting Equations~(\ref{e294})--(\ref{e300}) into the four-field model, (\ref{e264})--(\ref{e269}), and only retaining terms that
@@
 Here, 
-\begin{equation}
+\begin{equation}\label{e313a}
 \tau_H = \frac{L_s}{m\,V_A}
@@
 \begin{figure}[t]
-\centerline{\includegraphics[width=0.9\textwidth]{RegimeI.pdf}}
+\centerline{\includegraphics[width=0.95\textwidth]{RegimeI.pdf}}
 \caption{Linear resonant plasma response regimes in $Q$-$P$ space for the case $D=0.9$. The various regimes are
@@
 \begin{figure}[t]
-\centerline{\includegraphics[width=0.9\textwidth]{RegimeII.pdf}}
+\centerline{\includegraphics[width=0.95\textwidth]{RegimeII.pdf}}
 \caption{Linear resonant plasma response regimes in $Q$-$P$ space for the case $D=1.2$. The various regimes are
@@
 \begin{figure}[t]
-\centerline{\includegraphics[width=0.9\textwidth]{Island.pdf}}
-\caption{Equally-spaced contours of $\psi(\hat{x},\xi)$. The magnetic separatrix is shown in red. }\label{f2a}
+\centerline{\includegraphics[width=0.95\textwidth]{Island.pdf}}
+\caption{Equally-spaced contours of $\hat{\psi}(\hat{x},\xi)$. The magnetic separatrix is shown in red. }\label{f2a}
 \end{figure}
@@
 $\hat{\psi}(\hat{x},\xi)$ map out the perturbed magnetic flux-surfaces in the vicinity of the resonant layer. 
-Let $\hat{W} = 4\,(\hat{L}_s|\,\tilde{\psi}|)^{1/2}$. Equation~(\ref{e352a}) can be written
+Let $\hat{W} = 4\,(\hat{L}_s\,|\tilde{\psi}|)^{1/2}$. Equation~(\ref{e352a}) can be written
 \begin{equation}
@@
 \end{equation}
-Figure~\ref{f2a} shows the contours of $\psi(\hat{x},\xi)$ specified by the previous equation. It can be seen that the
+Figure~\ref{f2a} shows the contours of $\hat{\psi}(\hat{x},\xi)$ specified by the previous equation. It can be seen that the
 tearing mode has reconnected magnetic field-lines to produce a {\em helical magnetic island chain}\/ centered on the resonant
-surface ($\hat{x}=0$). The chain has $m$ periods in the poloidal direction, $n$ periods in the toroidal direction, and propagates at the
-helical phase velocity $\omega$. The maximum full (as opposed to half) radial width of the magnetic separatrix is 
+surface ($\hat{x}=0$).
+The chain has $m$ periods in the poloidal direction, $n$ periods in the toroidal direction, and propagates at the phase velocity $\omega$.
+The maximum full (as opposed to half) radial width of the magnetic separatrix is
 \begin{equation}\label{e355s}
@@
 Here, we have neglected the imaginary component of $\gamma$ because it merely gives rise to a small correction to the
-propagation frequency of the mode.
+phase velocity  of the mode.
 
@@
 \begin{figure}[t]
-\centerline{\includegraphics[width=0.9\textwidth]{RegimeIII.pdf}}
+\centerline{\includegraphics[width=0.95\textwidth]{RegimeIII.pdf}}
 \caption{Linear tearing mode growth-rate regimes  in $Q_\ast$-$P$ space. The various regimes are
@@
 \subsection{Discussion}
-According to Equations~(\ref{e350}), (\ref{e353}), (\ref{e363}), (\ref{e365}), (\ref{e368}), and (\ref{e371}), a linear tearing mode is unstable when the tearing stability index, $E_{ss}$, is positive, and is stable otherwise (Furth, Killeen \& Rosnebluth 1963).
+According to Equations~(\ref{e350}), (\ref{e353}), (\ref{e363}), (\ref{e365}), (\ref{e368}), and (\ref{e371}), a linear tearing mode is unstable when the tearing stability index, $E_{ss}$, is positive, and is stable otherwise (Furth, Killeen \& Rosenbluth 1963).
 Moreover, the perturbed magnetic field associated with the mode corotates with the electron fluid at the resonant surface (Ara, et al.\ 1978). Finally,
@@
 In fact, we can see that this is not the case, because if we set $\omega_r=\omega_E$ or $\omega_r=\omega_E+\omega_{\ast\,i}$  then Equation~(\ref{e329}) does not lead to a layer solution characterized by  $|\hat{\mit\Delta}|\ll 1$,
-as a consequence of finite anomalous perpendicular transport. Likewise, Equation~(\ref{sc}) seems to suggest that in the semi-collisional response regime it might be possible to successfully match the
+as a consequence of finite anomalous perpendicular transport (Waelbroeck, et al.\ 2012).
+Likewise, Equation~(\ref{sc}) seems to suggest that in the semi-collisional response regime it might be possible to successfully match the
 layer solution to the outer solution when $\omega_r=\omega_E$, giving rise to a tearing perturbation that corotates with the MHD fluid at the resonant surface.
@@
 where
-\begin{equation}
+\begin{equation}\label{enw}
 {\mit\Delta}_{nw} = {\mit\Delta}_{pw} + \frac{E_{sw}^{\,2}}{(-\tilde{E}_{ww})}
@@
 \begin{equation}\label{e389}
-{\mit\Delta} = {\rm i}\,\tau_s\,(\omega_{s\,0}+ {\mit\Delta}\omega_E),
+{\mit\Delta} = {\rm i}\,\tau_s\,(\omega_{0}+ {\mit\Delta}\omega_E),
 \end{equation}
@@
 \begin{equation}
-\omega_{s\,0}= \omega_{\perp\,e}.
+\omega_{0}= \omega_{\perp\,e}.
 \end{equation}
@@
 \begin{equation}\label{e392}
-\hat{\mit\Psi}_s=\frac{\tilde{I}_c}{(-{\mit\Delta}_{nw})+ {\rm i}\,\tau_s\,(\omega_{s\,0}+ {\mit\Delta}\omega_E)}.
-\end{equation}
-Now, in a conventional ohmically-heated tokamak plasma, $\tau_s\,\omega_{s\,0}\gg (-{\mit\Delta}_{nw})$. Consequently, the
+\hat{\mit\Psi}_s=\frac{\tilde{I}_c}{(-{\mit\Delta}_{nw})+ {\rm i}\,\tau_s\,(\omega_{0}+ {\mit\Delta}\omega_E)}.
+\end{equation}
+Now, in a conventional ohmically-heated tokamak plasma, $\tau_s\,\omega_{0}\gg (-{\mit\Delta}_{nw})$. Consequently, the
 shielding current that develops at the resonant surface, in response to the local plasma rotation, is strong enough to largely
@@
 \begin{align}
-v&=\frac{\omega_{s\,0}+{\mit\Delta}\omega_E}{\omega_{s\,0}},\\[0.5ex]
+v&=\frac{\omega_{0}+{\mit\Delta}\omega_E}{\omega_{0}},\\[0.5ex]
 T_{\rm VS}(v) &= 1- v,\\[0.5ex]
@@
 \left(\frac{|\tilde{I}_c|}{\tilde{I}_{c\,{\rm crit}}}\right)^2,\\[0.5ex]
-\zeta_s &= \frac{(-{\mit\Delta}_{nw})}{\tau_s\,\omega_{s\,0}}\ll 1,\\[0.5ex]
-\tilde{I}_{c\,{\rm crit}}&= (\epsilon_s\,s_s)\,(\omega_{s\,0}\,\tau_H)\left/
+\zeta_s &= \frac{(-{\mit\Delta}_{nw})}{\tau_s\,\omega_{0}}\ll 1,\\[0.5ex]
+\tilde{I}_{c\,{\rm crit}}&= (\epsilon_s\,s_s)\,(\omega_{0}\,\tau_H)\left/
 \left[\frac{q_s}{\epsilon_s}\left(\frac{\sqrt{\tau_\varphi\,\tau_i/\mu_{00}^i}}{\tau_s}\right)+2\left(\frac{\tau_\varphi}{\tau_s}\right) \ln\!\left(\frac{a}{r_s}\right)\right]^{1/2}\right..\label{e420}
@@
 Here, use has been made of the identities
-\begin{align}
+\begin{align}\label{e417a}
 \lim_{\epsilon\rightarrow 0}\sum_{p=1,\infty} \frac{\sqrt{\epsilon}\,[J_1(j_{1\,p}\,x)]^{2}}{[J_2(j_{1\,p})]^2\,(1+\epsilon\,j_{1\,p}^2)}
 &=\frac{1}{4\,x},\\[0.5ex]
-\sum_{p=1,\infty} \frac{[J_0(j_{0\,p}\,x)]^2}{[J_1(j_{0\,p}\,x)]^2\,j_{0\,p}^{\,2}} =\frac{1}{2}\,\ln\!\left(\frac{1}{x}\right).
+\sum_{p=1,\infty} \frac{[J_0(j_{0\,p}\,x)]^2}{[J_1(j_{0\,p}\,x)]^2\,j_{0\,p}^{\,2}} =\frac{1}{2}\,\ln\!\left(\frac{1}{x}\right).\label{e418a}
 \end{align}
@@
 \begin{figure}[t]
-\centerline{\includegraphics[width=0.9\textwidth]{Torque.pdf}}
+\centerline{\includegraphics[width=0.95\textwidth]{Torque.pdf}}
 \caption{Torque balance. The red curve shows the normalized viscous restoring torque, $T_{\rm VS}(v)$. The
@@
 It can be seen that as the error-field coil current increases  the plasma rotation at the resonant surface decreases. However, when
-$|\tilde{I}_c|$ attains the critical value $\tilde{I}_{c\,{\rm crit}}$, and the rotation is reduced to half of its
+$|\tilde{I}_c|$ attains the critical value $\tilde{I}_{c\,{\rm crit}}$, and the rotation is reduced to {\em half}\/ of its
 original value, the shielded solution branch ceases to exist, and there is a bifurcation to the unshielded solution branch (Fitzpatrick 1993;
@@
 experiments. As is clear from Equation~(\ref{e420}), the critical error-field coil current needed to trigger error-field
-penetration increases linearly with the unperturbed plasma rotation at the resonant surface, which is parameterized by $\omega_{s\,0}$. 
+penetration increases linearly with the unperturbed plasma rotation at the resonant surface, which is parameterized by $\omega_{0}$. 
 Once error-field penetration has occurred, the magnitude of the error-field coil current must be reduced to a value
@@
 \nu_\ast &= \frac{L_s\,n_0\,e^2\,\eta_\parallel}{m_e^{1/2}\,T_0^{1/2}},\\[0.5ex]
-\beta&=\frac{\mu_0\,n_0\,T_0}{B_z^{\,2}},\label{e430}
+\beta_\ast&=\frac{\mu_0\,n_0\,T_0}{B_z^{\,2}},\label{e430}
 \end{align}
 where $T_0=p_0/n_0$. In the following, for the sake of simplicity, we
-shall assume that $T_i=T_e=T_0$, $\omega_{s\,0}=\omega_\ast$, and $-(d\ln p/dr)_{r_s} = 1/r_s$. We shall also neglect ${\cal O}(1)$
+shall assume that $T_i=T_e=T_0$, $\omega_{0}=\omega_\ast$, and $-(d\ln p/dr)_{r_s} = 1/r_s$. We shall also neglect ${\cal O}(1)$
 constants such as $s_s$, $\eta_e$, $\eta_i$, $\lambda_e$, $\tau$, $\pi$, $\ln(r_s/a)$, et cetera.
@@
 \begin{align}
-\omega_{s\,0}\,\tau_H&\simeq \left(\frac{q_s}{\epsilon_s}\right)^2\rho_\ast\,\beta^{\,1/2},\\[0.5ex]
-\frac{\tau_H}{\tau_R}&\simeq \left(\frac{q_s}{\epsilon_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/2}\rho_\ast^{\,2}\,\nu_\ast\,\beta^{-1/2},\\[0.5ex]
-\frac{\tau_\varphi}{\tau_R} = \frac{\tau_\perp}{\tau_R} &\simeq \left(\frac{q_s}{\epsilon_s}\right)^2\beta,\\[0.5ex]
-\frac{\tau_i}{\tau_R} &\simeq  \left(\frac{q_s}{\epsilon_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/2}\rho_\ast^{\,2}\,\beta^{-1},\\[0.5ex]
+\omega_{0}\,\tau_H&\simeq \left(\frac{q_s}{\epsilon_s}\right)^2\rho_\ast\,\beta_\ast^{\,1/2},\\[0.5ex]
+\frac{\tau_H}{\tau_R}&\simeq \left(\frac{q_s}{\epsilon_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/2}\rho_\ast^{\,2}\,\nu_\ast\,\beta_\ast^{-1/2},\\[0.5ex]
+\frac{\tau_\varphi}{\tau_R} = \frac{\tau_\perp}{\tau_R} &\simeq \left(\frac{q_s}{\epsilon_s}\right)^2\beta_\ast,\\[0.5ex]
+\frac{\tau_i}{\tau_R} &\simeq  \left(\frac{q_s}{\epsilon_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/2}\rho_\ast^{\,2}\,\beta_\ast^{-1},\\[0.5ex]
 \frac{d_\beta}{r_s} &\simeq \left(\frac{q_s}{\epsilon_s}\right)\rho_\ast.
@@
 \begin{align}
-\hat{\delta}_{\rm VR} = \left(\frac{\tau_{\rm VR}}{\tau_R}\right) \simeq\left(\frac{\tau_H}{\tau_R}\right)^{1/3}\left(\frac{\tau_R}{\tau_\varphi}\right)^{1/6}&\simeq \left(\frac{q_s}{\epsilon_s}\right)^{1/3}\left(\frac{m_e}{m_i}\right)^{1/6}\rho_\ast^{\,2/3}\,\nu_\ast^{\,1/3}\,\beta^{-1/3},\\[0.5ex]
-\hat{\delta}_{\rm HR} = \left(\frac{\tau_{\rm HR}}{\tau_R}\right) \simeq \left(\frac{\tau_H}{\tau_R}\right)^{1/2}\left(\frac{\tau_R}{\tau_\perp}\right)^{1/4}\left(\frac{r_s}{d_\beta}\right)^{1/2}&\simeq \left(\frac{m_e}{m_i}\right)^{1/4}\rho_\ast^{\,1/2}\,\nu_\ast^{\,1/2}\,\beta^{-1/2},\\[0.5ex]
+\hat{\delta}_{\rm VR} = \left(\frac{\tau_{\rm VR}}{\tau_R}\right) \simeq\left(\frac{\tau_H}{\tau_R}\right)^{1/3}\left(\frac{\tau_R}{\tau_\varphi}\right)^{1/6}&\simeq \left(\frac{q_s}{\epsilon_s}\right)^{1/3}\left(\frac{m_e}{m_i}\right)^{1/6}\rho_\ast^{\,2/3}\,\nu_\ast^{\,1/3}\,\beta_\ast^{-1/3},\\[0.5ex]
+\hat{\delta}_{\rm HR} = \left(\frac{\tau_{\rm HR}}{\tau_R}\right) \simeq \left(\frac{\tau_H}{\tau_R}\right)^{1/2}\left(\frac{\tau_R}{\tau_\perp}\right)^{1/4}\left(\frac{r_s}{d_\beta}\right)^{1/2}&\simeq \left(\frac{m_e}{m_i}\right)^{1/4}\rho_\ast^{\,1/2}\,\nu_\ast^{\,1/2}\,\beta_\ast^{-1/2},\\[0.5ex]
 \frac{\sqrt{\tau_\varphi\, \tau_i/\mu_{00}^i}}{\tau_R}&\simeq \left(\frac{q_s}{r_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/4}\,\rho_\ast.
@@
 Here, we have treated $\mu_{00}^i$ as an ignorable ${\cal O}(1)$ constant that is independent of $\rho_\ast$, $\nu_\ast$, and
-$\beta$ [as is indeed the case provided that the plasma at the resonant surface lies in the banana collisionality regime (Hirshman \& Sigmar 1981)].
+$\beta_\ast$ [as is indeed the case provided that the plasma at the resonant surface lies in the banana collisionality regime (Hirshman \& Sigmar 1981)].
 
 \begin{figure}[t]
-\centerline{\includegraphics[width=0.9\textwidth]{Scaling.pdf}}
+\centerline{\includegraphics[width=0.95\textwidth]{Scaling.pdf}}
 \caption{Error-field penetration regimes in $\hat{\nu}_\ast$-$\hat{\rho}_\ast$ space. The various regimes are the
@@
 
-There are four error-field penetration regimes depending on whether the plasma response in the resonant layer is
+There are four error-field penetration regimes, depending on whether the plasma response in the resonant layer is
 in the visco-resistive or the Hall-resistive regime, and depending on whether the change in the ion rotation at the resonant surface, induced by the electromagnetic locking torque,  is
@@
 \begin{equation}
-\rho_\ast < \left(\frac{\epsilon_s}{q_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/2}\nu_\ast\,\beta^{-1},
+\rho_\ast < \left(\frac{\epsilon_s}{q_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/2}\nu_\ast\,\beta_\ast^{-1},
 \end{equation}
@@
 \begin{equation}
-\rho_\ast < \left(\frac{\epsilon_s}{q_s}\right)\left(\frac{m_i}{m_e}\right)^{1/4}\beta,
+\rho_\ast < \left(\frac{\epsilon_s}{q_s}\right)\left(\frac{m_i}{m_e}\right)^{1/4}\beta_\ast,
 \end{equation}
@@
 As is illustrated in Figure~\ref{f6}, the {\em visco-resistive-toroidal regime}\/ (i.e., a visco-resistive layer response
-combined with a predominately toroidal change in the ion rotation) corresponds to $\hat{\rho}_\ast < \beta^{-1}\,\nu_\ast$ 
-and $\hat{\rho}_\ast <\beta$, the {\em visco-resisitive-poloidal regime}\/ corresponds to 
- $\hat{\rho}_\ast<\beta^{-1}\,\nu_\ast$ and $\hat{\rho}_\ast > \beta$, the {\em Hall-resisitive-poloidal regime}\/ corresponds to  
- $\hat{\rho}_\ast>\beta^{-1}\,\nu_\ast$ and $\hat{\rho}_\ast > \beta$, and the {\em Hall-resistive-toroidal regime}\/ corresponds to   
- $\hat{\rho}_\ast>\beta^{-1}\,\nu_\ast$ and $\hat{\rho}_\ast < \beta$.
+combined with a predominately toroidal change in the ion rotation) corresponds to $\hat{\rho}_\ast < \beta_\ast^{-1}\,\nu_\ast$ 
+and $\hat{\rho}_\ast <\beta_\ast$, the {\em visco-resisitive-poloidal regime}\/ corresponds to 
+ $\hat{\rho}_\ast<\beta_\ast^{-1}\,\nu_\ast$ and $\hat{\rho}_\ast > \beta_\ast$, the {\em Hall-resisitive-poloidal regime}\/ corresponds to  
+ $\hat{\rho}_\ast>\beta_\ast^{-1}\,\nu_\ast$ and $\hat{\rho}_\ast > \beta_\ast$, and the {\em Hall-resistive-toroidal regime}\/ corresponds to   
+ $\hat{\rho}_\ast>\beta_\ast^{-1}\,\nu_\ast$ and $\hat{\rho}_\ast < \beta_\ast$.
 It can be seen that higher/lower plasma collisionality (i.e., $\nu_\ast$) favors the visco-resistive/Hall-resistive response regime, whereas a
 larger/smaller ion sound radius (i.e., $\rho_\ast$) favors poloidal/toroidal changes in the ion rotation. Finally, higher/lower plasma
-pressure (i.e., $\beta$) 
+pressure (i.e., $\beta_\ast$) 
 favors the Hall-resistive/visco-resistive response regime and toroidal/poloidal changes in the ion rotation.
@@
 \left(\frac{b_{r}}{B_z}\right)_{{\rm VR}-\varphi} \simeq \epsilon_s^{-1}\tilde{I}_{c\,{\rm crit}}\simeq \left(\frac{q_s}{\epsilon_s}\right)^{7/6}\left(\frac{m_e}{m_i}\right)^{1/12}
-\rho_\ast^{\,4/3}\,\nu_\ast^{\,1/6}\,\beta^{-1/6},
+\rho_\ast^{\,4/3}\,\nu_\ast^{\,1/6}\,\beta_\ast^{-1/6},
 \end{equation}
@@
 \left(\frac{b_{r}}{B_z}\right)_{{\rm VR}-\theta} \simeq  \left(\frac{q_s}{\epsilon_s}\right)^{2/3}\left(\frac{m_e}{m_i}\right)^{-1/24}
-\rho_\ast^{\,5/6}\,\nu_\ast^{\,1/6}\,\beta^{\,1/3}.
+\rho_\ast^{\,5/6}\,\nu_\ast^{\,1/6}\,\beta_\ast^{\,1/3}.
 \end{equation}
@@
 \left(\frac{b_{r}}{B_z}\right)_{{\rm HR}-\theta} \sim  \left(\frac{q_s}{\epsilon_s}\right)^{1/2}\left(\frac{m_e}{m_i}\right)^{0}
-\rho_\ast^{\,3/4}\,\nu_\ast^{\,1/4}\,\beta^{\,1/4}.
+\rho_\ast^{\,3/4}\,\nu_\ast^{\,1/4}\,\beta_\ast^{\,1/4}.
 \end{equation}
@@
 \left(\frac{b_{r}}{B_z}\right)_{{\rm HR}-\varphi} \sim  \left(\frac{q_s}{\epsilon_s}\right)^{}\left(\frac{m_e}{m_i}\right)^{1/8}
-\rho_\ast^{\,5/4}\,\nu_\ast^{\,1/4}\,\beta^{-1/4}.\label{e447}
-\end{equation}
-Generally speaking, ohmically-heated tokamak plasmas all  have similar $\beta$ values. However,
+\rho_\ast^{\,5/4}\,\nu_\ast^{\,1/4}\,\beta_\ast^{-1/4}.\label{e447}
+\end{equation}
+Generally speaking, ohmically-heated tokamak plasmas all  have similar $\beta_\ast$ values. However,
 both $\nu_\ast$ and $\rho_\ast$ are smaller in devices of larger physical size. Hence, Equations~(\ref{e444})--(\ref{e447})
@@
 and physical dimension (i.e., major radius) of an ohmically-heated tokamak. Using $\rho_\ast\sim T^{1/2}\,B^{-1}\,R^{-1}$, 
-$\nu_\ast\sim n\,T^{-2}\,R$, and $\beta\sim n\,T\,B^{-1}$ [see Equations~(\ref{e3.74}), (\ref{e3.83}), and (\ref{e428})--(\ref{e430})],
+$\nu_\ast\sim n\,T^{-2}\,R$, and $\beta_\ast\sim n\,T\,B^{-1}$ [see Equations~(\ref{e3.74}), (\ref{e3.83}), and (\ref{e428})--(\ref{e430})],
 we deduce that
@@
 \begin{align}
-\nu_\ast&\propto \rho_\ast^{\,2/3}\,\beta,\\[0.5ex]
+\nu_\ast&\propto \rho_\ast^{\,2/3}\,\beta_\ast,\\[0.5ex]
 T&\propto B^{\,4/5}\,R^{\,1/2}.
@@
 \begin{align}
-\left(\frac{W}{\delta}\right)_{{\rm VR}-\varphi} &\simeq \left(\frac{q_s}{\epsilon_s}\right)^{7/12}\left(\frac{m_e}{m_i}\right)^{1/24}\rho_\ast^{\,1/6}\,\nu_\ast^{\,1/12}\,\beta^{-1/12},\\[0.5ex]
-\left(\frac{W}{\delta}\right)_{{\rm VR}-\theta} &\simeq \left(\frac{q_s}{\epsilon_s}\right)^{1/3}\left(\frac{m_i}{m_e}\right)^{1/48}\rho_\ast^{-1/12}\,\nu_\ast^{\,1/12}\,\beta^{\,1/6},\\[0.5ex]
-\left(\frac{W}{\delta}\right)_{{\rm HR}-\theta} &\simeq \left(\frac{q_s}{\epsilon_s}\right)^{3/4}\left(\frac{m_i}{m_e}\right)^{1/8}\rho_\ast^{\,1/8}\,\nu_\ast^{-1/8}\,\beta^{\,3/8},\\[0.5ex]
-\left(\frac{W}{\delta}\right)_{{\rm HR}-\varphi} &\simeq \left(\frac{q_s}{\epsilon_s}\right)\left(\frac{m_i}{m_e}\right)^{1/16}\rho_\ast^{\,3/8}\,\nu_\ast^{-1/8}\,\beta^{\,1/8}.
+\left(\frac{W}{\delta}\right)_{{\rm VR}-\varphi} &\simeq \left(\frac{q_s}{\epsilon_s}\right)^{7/12}\left(\frac{m_e}{m_i}\right)^{1/24}\rho_\ast^{\,1/6}\,\nu_\ast^{\,1/12}\,\beta_\ast^{-1/12},\\[0.5ex]
+\left(\frac{W}{\delta}\right)_{{\rm VR}-\theta} &\simeq \left(\frac{q_s}{\epsilon_s}\right)^{1/3}\left(\frac{m_i}{m_e}\right)^{1/48}\rho_\ast^{-1/12}\,\nu_\ast^{\,1/12}\,\beta_\ast^{\,1/6},\\[0.5ex]
+\left(\frac{W}{\delta}\right)_{{\rm HR}-\theta} &\simeq \left(\frac{q_s}{\epsilon_s}\right)^{3/4}\left(\frac{m_i}{m_e}\right)^{1/8}\rho_\ast^{\,1/8}\,\nu_\ast^{-1/8}\,\beta_\ast^{\,3/8},\\[0.5ex]
+\left(\frac{W}{\delta}\right)_{{\rm HR}-\varphi} &\simeq \left(\frac{q_s}{\epsilon_s}\right)\left(\frac{m_i}{m_e}\right)^{1/16}\rho_\ast^{\,3/8}\,\nu_\ast^{-1/8}\,\beta_\ast^{\,1/8}.
 \end{align}
@@
 \end{align}
-Here, $\omega = \hat{\omega}\,V_A/r_s$ is the helical phase velocity of the island chain in the
+Here, $\omega = \hat{\omega}\,V_A/r_s$ is the phase velocity of the island chain in the
 laboratory frame,
@@
 The parameter $\hat{V}_E'$ is introduced  into the analysis in order to take into account the fact that the plasma rotation profile in the outer region develops a
-gradient discontinuity at the resonant surface in response to the nonlinear localized electromagnetic torque that develops
+gradient discontinuity at the resonant surface in response to the nonlinear localized electromagnetic torque that emerges 
 at the surface.
@@
  We conclude that the lowest-order normalized
-electrostatic potential (in the island rest frame), ${\mit\Phi}_{0}$, is  constant on magnetic flux-surfaces. 
+electrostatic potential, ${\mit\Phi}_{0}$, is  constant on magnetic flux-surfaces. 
 By symmetry, ${\mit\Phi}_{0}=0$ inside the magnetic separatrix of the island chain. In other words, the electrostatic
@@
 
-To lowest-order in $\epsilon_d$, Equation~(\ref{e471}) yields
+To lowest order in $\epsilon_d$, Equation~(\ref{e471}) yields
 \begin{equation}
@@
 velocities of the various fluid species in the island rest frame. In fact, as is clear from Sections~\ref{s4.2}, \ref{s4.3}, and \ref{s8.2}, 
-\begin{align}
+\begin{align}\label{e519a}
 V_{\theta\,e}(X,\zeta,T)& = -\frac{r_s\,\omega_\ast}{m}\,|X|\,Y_e({\mit\Omega},T),\\[0.5ex]
 V_\theta(X,\zeta,T) &= -\frac{r_s\,\omega_\ast}{m}\,|X|\,M({\mit\Omega},T),\\[0.5ex]
-V_{\theta\,i}(X,\zeta,T)& = -\frac{r_s\,\omega_\ast}{m}\,|X|\,Y_i({\mit\Omega},T),
+V_{\theta\,i}(X,\zeta,T)& = -\frac{r_s\,\omega_\ast}{m}\,|X|\,Y_i({\mit\Omega},T),\label{e521a}
 \end{align}
 where
-\begin{align}
+\begin{align}\label{e517}
 Y_e({\mit\Omega},T)&= M- \left(\frac{\tau}{1+\tau}\right)L,\\[0.5ex]
@@
 ${\mit\Phi}_{(0)}({\mit\Omega},T)$,  ${\cal V}_{(0)}({\mit\Omega},T)$, and $\overline{\cal J}_0({\mit\Omega},T)$ undetermined. In fact, in order to determine
-the forms of these  four  functions we need to solve the rescaled four-field model to higher order in our expansion. In particular,
+the forms of these  four  functions it is necessary to solve the rescaled four-field model to higher order in our expansion. In particular,
 we need to include the terms that describe the perpendicular diffusion of magnetic flux, ion momentum, and
@@
 We have also made use of the fact that $Y_i=0$ within the magnetic separatrix of the island chain. Finally, we have  demanded that the ion
-fluid velocity---and, hence, the function $Y_i$---is continuous across the separatrix, because the ion fluid possesses finite perpendicular viscosity. 
+fluid velocity---and, hence, the function $Y_i$---be continuous across the separatrix, because the ion fluid possesses finite perpendicular viscosity. 
 Note, however, that the discontinuity in the function $L({\mit\Omega})$ across the separatrix [see Equation~(\ref{e526})] implies that the
@@
 \end{equation}
- The previous equation can be solved, subject to the boundary condition (\ref{e486a}) to
+ The previous equation can be solved, subject to the boundary condition (\ref{e486a}), to
 give
@@
 {\rm Re}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)&= I_1\,\tau_R\,\frac{d}{dt}\!\left(\frac{4\,w}{r_s}\right)
-- I_2\left(\frac{c_\beta}{1+\tau}\right)\left(\frac{\rho_\beta}{r_s}\right)\left(\frac{\tau_\varphi}{\tau_H}\right)\left(\frac{w}{r_s}\right)^2 {\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)\nonumber\\[0.5ex]
-&\phantom{=} -I_3\left(\frac{\tau_\varphi}{\tau_H}\right)^2 \left(\frac{w}{r_s}\right)^7\left[{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)\right]^2, 
+- \frac{I_2}{4}\left(\frac{c_\beta}{1+\tau}\right)\left(\frac{\rho_\beta}{r_s}\right)\left(\frac{\tau_\varphi}{\tau_H}\right)\left(\frac{w}{r_s}\right)^2 {\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)\nonumber\\[0.5ex]
+&\phantom{=} -\frac{I_3}{16}\left(\frac{\tau_\varphi}{\tau_H}\right)^2 \left(\frac{w}{r_s}\right)^7\left[{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)\right]^2, 
 \end{align}
@@
 I_1 &= 2\int_{-1}^\infty \frac{\langle \cos\zeta\rangle^2}{\langle 1\rangle}\,d{\mit\Omega} =0.8227,\\[0.5ex]
-I_2&= \frac{1}{4}\int_1^\infty d_{\mit\Omega}\!\left(\frac{F_i}{\langle X^2\rangle}\right)\left(\langle X^4\rangle - \frac{\langle X^2\rangle^2}{\langle 1\rangle}\right)d{\mit\Omega} =4.889\times 10^{-2},\\[0.5ex]
-I_3&= \frac{1}{16}\int_1^\infty d_{\mit\Omega}\!\left(F_i^{\,2}\right)\left(\langle X^4\rangle - \frac{\langle X^2\rangle^2}{\langle 1\rangle}\right)d{\mit\Omega} =2.944\times 10^{-2}.
-\end{align}
-Here, use has been made of Equations~(\ref{e317a}), (\ref{e318a}), (\ref{e481}), and (\ref{e482}).
-
-\section{Isolated Magnetic Island Chain}
+I_2&= \int_1^\infty d_{\mit\Omega}\!\left(\frac{F_i}{\langle X^2\rangle}\right)\left(\langle X^4\rangle - \frac{\langle X^2\rangle^2}{\langle 1\rangle}\right)d{\mit\Omega} =0.1955,\\[0.5ex]
+I_3&= \int_1^\infty d_{\mit\Omega}\!\left(F_i^{\,2}\right)\left(\langle X^4\rangle - \frac{\langle X^2\rangle^2}{\langle 1\rangle}\right)d{\mit\Omega} =0.4711.
+\end{align}
+Here, use has been made of Equations~(\ref{e317a}), (\ref{e318a}), (\ref{e481}), and (\ref{e482}). Note that $d/dt$ in Equation~(\ref{e559}) represents a time derivative in the island rest frame.
+
+\section{Isolated Magnetic Island Chains}
 \subsection{Introduction}
 Suppose that the wall surrounding the plasma is perfectly conducting (i.e.\, $\tau_w\rightarrow\infty$), and that there is no current
-flowing through the external magnetic-field coil (i.e., $\hat{I}_c=0$). In this case, assuming that $d/dt = -{\rm i}\,\omega$, Equations~(\ref{e202}), 
+flowing through the external magnetic field-coil (i.e., $\hat{I}_c=0$). In this case, Equations~(\ref{e202}), 
 (\ref{e203}), and (\ref{epw}),  yield 
@@
 \end{equation}
-where ${\mit\Delta}_{pw}$ is the (real) perfect-wall tearing stability index.
+where ${\mit\Delta}_{pw}$ is the (real) perfect-wall tearing stability index. It is clear from the previous equation that
+\begin{equation}\label{e559x}
+{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right) = 0,
+\end{equation}
+which implies that zero electromagnetic torque is exerted at the resonant surface.
+(See Section~\ref{storque}.) In this respect, the magnetic island chain that develops at the resonant surface can be termed `isolated'.
 
 \subsection{Rutherford Island Width Evolution Equation}
-It is clear from the previous equation that
-\begin{equation}\label{e559}
-{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right) = 0,
-\end{equation}
-which implies that zero electromagnetic torque is exerted at the resonant surface. (See Section~\ref{storque}.) 
-Moreover, 
-\begin{equation}
+Equation~(\ref{e563}) implies that 
+\begin{equation}\label{e560x}
 {\rm Re}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right) = {\mit\Delta}_{pw}.
 \end{equation}
-Hence, Equations~(\ref{e456}), (\ref{e559}), and (\ref{e559}) yield the {\em Rutherford island width evolution equation}\/ (Rutherford 1973):
-\begin{equation}
-I_1\,\tau_R\,\frac{d}{dt}\!\left(\frac{W}{r_s}\right)= {\mit\Delta}_{pw}.
-\end{equation}
-According to this equation, if the perfect-wall tearing stability index is positive then the width of the magnetic
-island chain at the resonant surface grows algebraically on the resistive evolution timescale, $\tau_R$.
-
+Equations~(\ref{e456}), (\ref{e559}), (\ref{e559x}), and (\ref{e560x}) yield the {\em Rutherford island width evolution equation}\/ (Rutherford 1973):
+\begin{equation}\label{e561}
+I_1\,\tau_R\,\frac{d}{dt}\!\left(\frac{W}{r_s}\right)= {\mit\Delta}_{pw},
+\end{equation}
+where $d/dt$ represents a time derivative in the island rest frame. 
+According to the Rutherford equation, if the perfect-wall tearing stability index is positive then the width of the magnetic
+island chain at the resonant surface grows {\em algebraically}\/ on the resistive evolution timescale, $\tau_R$.
+
+\subsection{Saturated Island Width}\label{sat}
+Equation~(\ref{e561}) gives the impression that if ${\mit\Delta}_{pw}>0$ then the width of the magnetic island chain 
+grows without limit. In fact, this is not the case. Instead, the width of the island chain eventually stops growing, and the
+tearing mode attains a saturated steady state. In order to model this effect, it is necessary to perform the
+asymptotic matching between the inner and outer regions to higher order, taking into account the finite
+width of the island chain (White, et al.\ 1977; Thyagaraja 1981; Escande \& Ottaviani 2004; Militello \& Porcelli
+2004).
+
+For the case of an island chain that is sufficiently wide to flatten  the density and temperature profiles within its magnetic separatrix, the appropriate saturation theory is given in Hastie, Militello, and Porcelli 2005.
+According to this theory, ${\mit\Delta}_{pw}$ in Equation~(\ref{e561}) must be replaced by
+\begin{equation}\label{e562}
+{\mit\Delta}_{pw}(0) - \left(0.8\,\alpha_s^{2}-0.27\,\beta_s - 0.09\,\alpha_s\right)\frac{W}{r_s},
+\end{equation}
+where ${\mit\Delta}_{pw}(0)$ denotes the zero-island-width tearing stability index, $\alpha_s$ is defined in  Equation~(\ref{e108}),
+and
+\begin{equation}
+\beta_s = -\left(\frac{r\,q\,J_z''}{s}\right)_{r=r_s}.
+\end{equation}
+
+\begin{figure}[t]
+\centerline{\includegraphics[width=0.95\textwidth]{m2n1.pdf}}
+\caption{Saturated island width of the $m=2/n=1$ tearing mode for a Wesson equilibrium in which $q(0)=0.8$ and
+$q(a)$ is varied. The blue, green, and red curves correspond to $r_w/a= 1.0$, 1.1, and 1.2, respectively.}\label{f7}
+\end{figure}
+
+Equations~(\ref{e561}) and (\ref{e562}) can be combined to give
+\begin{equation}\label{e564}
+I_1\,\tau_R\,\frac{d}{dt}\!\left(\frac{W}{r_s}\right)= {\mit\Delta}_{pw}(0)- \left(0.8\,\alpha_s^{2}-0.27\,\beta_s - 0.09\,\alpha_s\right)\frac{W}{r_s}.
+\end{equation}
+If we define
+\begin{align}
+W_{\rm sat} &= \frac{{\mit\Delta}_{pw}(0)\,r_s}{0.8\,\alpha_s^{2}-0.27\,\beta_s - 0.09\,\alpha_s},\\[0.5ex]
+\tau_{\rm sat} &= \frac{I_1\,\tau_R}{{\mit\Delta}_{pw}(0)}\,\frac{W_{\rm sat}}{r_s},
+\end{align}
+then Equation~(\ref{e564}) reduces to
+\begin{equation}
+\tau_{\rm sat} \,\frac{d}{dt}\!\left(\frac{W}{W_{\rm sat}}\right) = 1-\frac{W}{W_{\rm sat}}.
+\end{equation}
+The previous equation can be solved to give
+\begin{equation}
+W(t) = W_{\rm sat}\left(1-{\rm e}^{-t/\tau_{\rm sat}}\right),
+\end{equation}
+assuming that the island width is zero at $t=0$. It follows that the width of the island chain does not grow without limit, 
+but instead eventually attains the saturated 
+value $W_{\rm sat}$. Moreover, the time required to attain saturation, $\tau_{\rm sat}$, is of order $\tau_R\,(W_{\rm sat}/r_s)$.
+
+Figure~\ref{f7} shows the saturated island width of an $m=2/n=1$ tearing mode\footnote{This is, generally, the most unstable tearing mode in conventional tokamak plasmas (Wesson 1978).}  in a so-called `Wesson' equilibrium (Wesson 1978) characterized by
+\begin{align}
+J_z(r) &= \frac{2}{q(0)}\left(1-\frac{r^2}{a^2}\right)^\nu,\\[0.5ex]
+q(r) &= \frac{q(a)\,(r/a)^2}{1-(1-r^2/a^2)^{1+\nu}},
+\end{align}
+where $\nu = q(a)/q(0)-1$.  Here, $q(0)$ and $q(a)$ are the safety-factor values at the magnetic axis and the plasma
+boundary, respectively. In the calculation shown in Figure~\ref{f7}, ${\mit\Delta}_{pw}(0)$ is determined by solving the cylindrical tearing mode
+equation, subject to suitable boundary conditions, as described in Section~\ref{perfect}.  Moreover, $q(0)$ is given the plausible value 0.8 (Wesson 2011), while
+$q(a)$ is varied in order to shift the position of the resonant surface within the plasma. It can be seen that if the resonant
+surface lies far from the plasma boundary then the 2/1 island chain saturates at relatively small width (i.e., $W_{\rm sat}/a\ll 1$). 
+On the other hand, if the resonant surface lies close to the plasma boundary then the island chain
+saturates at a much higher width. However, the presence of a close-fitting perfectly conducting wall can mitigate this
+effect to some extent.
+
+\subsection{Island Phase Velocity}\label{sphase1}
+Equations~(\ref{e545}) and (\ref{e559x}) imply that 
+\begin{equation}\label{evz}
+v'=0 
+\end{equation}
+for an isolated magnetic island chain. It follows from
+Equations~(\ref{e517}), (\ref{e518}), (\ref{e526}), and (\ref{e530}) that the stream functions for the
+electron, MHD, and ion fluids take the respective forms
+\begin{align}\label{e571}
+Y_e({\mit\Omega} )&= \left\{ \begin{array}{llr} 0&~~~~~~~~~~~~~~\,&-1\leq{\mit\Omega}\leq 1\\[0.5ex]
+-1/\langle X^2\rangle&&{\mit\Omega}>1\end{array}\right.,\\[0.5ex]
+M({\mit\Omega} )&= \left(\frac{1}{1+\tau}\right)\left\{ \begin{array}{llr} 0&~~&-1\leq{\mit\Omega}\leq 1\\[0.5ex]
+-1/\langle X^2\rangle&&{\mit\Omega}>1\end{array}\right.,\label{e572}\\[0.5ex]
+Y_i({\mit\Omega}) &= 0,\label{e573}
+\end{align}
+in the vicinity of the island chain. Equations~(\ref{e488}), (\ref{e506}), (\ref{evz}), and (\ref{e572}) yield $v=-1/(1+\tau)$, or
+\begin{equation}\label{e574}
+\omega= \omega_{\perp\,i},
+\end{equation}
+where
+\begin{equation}
+\omega_{\perp\,i} = \omega_E + \omega_{\ast\,i},
+\end{equation}
+and
+\begin{equation}
+\omega_{\ast\,i} = -\left(\frac{1}{1+\tau}\right)\omega_\ast.
+\end{equation}
+We conclude that, unlike a linear tearing mode, which is convected by the electron fluid at the resonant surface (see Section~\ref{s6.2}), a nonlinear
+tearing mode is convected by the {\em ion}\/ fluid  (Fitzpatrick \& Waelbroeck 2005).
+
+\begin{figure}[t]
+\centerline{\includegraphics[width=0.95\textwidth]{velocity.pdf}}
+\caption{Normalized velocity profiles across the O-point of an isolated magnetic island chain in the island rest frame. The red, black, and
+blue curves correspond to the electron, MHD, and ion fluid, respectively. Here, $\tau=1$. }\label{f8}
+\end{figure}
+
+Figure~\ref{f8} shows the normalized velocity profiles of the electron, MHD, and ion fluids across the O-point of an isolated magnetic island
+chain in the island rest frame, as determined from Equations~(\ref{e519a})--(\ref{e521a}) and
+(\ref{e571})--(\ref{e573}) (Fitzpatrick \& Waelbroeck 2005). Here, $\hat{V}_\theta =(m/r_s)\,V_\theta/\omega_\ast$. It can be seen that all three fluids co-rotate with the island
+chain inside the magnetic separatrix. The ion fluid velocity profile is completely unaffected by the presence of the  chain. 
+On the other hand, the electron and the MHD fluid velocity profiles are modified by the island chain. In particular, both profiles
+are discontinuous across the magnetic separatrix.  As has already been mentioned, these discontinuities are resolved in a thin layer of
+thickness $\rho_\beta$ on the separatrix. It is clear from the figure that the island chain rotates in the ion (i.e., negative) direction with respect to
+the unperturbed ${\bf E}\times {\bf B}$ frame at the resonant surface (Fitzpatrick \& Waelbroeck 2005).
+
+\subsection{Discussion}
+The phase velocity of an isolated tearing mode is determined by the
+equilibrium plasma flow at the resonant surface. Now, a magnetic
+island chain is a helical pattern in the magnetic field generated by a
+helical current perturbation that is localized in the vicinity of the resonant surface. Given that plasma current is predominately carried by
+the electrons, it is natural to suppose that a magnetic island chain (as
+well as the magnetic perturbation away from the resonant surface)
+is convected by the electron fluid in the immediate vicinity of the resonant surface. This is indeed the case in the linear regime. 
+(See~Section~\ref{s6.2}.) Of course, as a consequence of diamagnetic flows, if the island chain is convected by the electron fluid at the resonant surface then it propagates with respect to the local ion fluid.
+However, this is not a problem because a linear layer is sufficiently thin that the magnetic field can diffuse through the plasma very rapidly, which implies that the ion fluid is not tied to the magnetic structure of the island chain (Fitzpatrick 2020).
+
+The situation is very different in the nonlinear regime. The region
+inside the magnetic separatrix of a sufficiently wide nonlinear magnetic island chain is
+governed by a combination of flux-freezing and perturbed force balance. This implies that both the electron and the ion fluids are trapped
+inside the separatrix, and are, therefore, forced to co-rotate with the
+island chain. There is no such constraint outside the separatrix, so the
+electron and ion fluids rotate at different speeds in this region, as a
+consequence of diamagnetism. It follows that one or other of the electron and the ion fluid rotation profiles must exhibit a strong gradient
+across the separatrix. The island phase velocity is determined by
+which of the two fluids is most resistant to the formation of such a gradient. Of course, it is the ion fluid which is more resistant because of
+its much greater perpendicular viscosity.
+Hence, a nonlinear magnetic island chain is convected by the ion fluid in the vicinity of the resonant surface, because this choice of phase velocity minimizes the ion fluid velocity gradient across the separatrix (Fitzpatrick 2000).
+Incidentally, there is clear experimental evidence that wide magnetic island chains in tokamak plasmas rotate in the ion
+diamagnetic direction relative to the unperturbed ${\bf E}\times {\bf B}$ frame at the resonant surface (La Haye, et al.\ 2003;
+Burratti, et al.\ 2016).
+
+Finally, it is reasonable to suppose that the critical island width that must be exceeded before a magnetic island chain switches from rotating in the electron
+direction, with respect to the unperturbed local ${\bf E}\times{\bf B}$ frame, to rotating in the ion direction, is  that
+above which the density and temperature profiles flatten within the separatrix (Scott, Hassam \& Drake 1985).
+
+\section{Mode Locking in Tokamak Plasmas}
+\subsection{Introduction}
+{\em Mode locking}\/ is a process by which the rotation of a slowly growing  tearing mode is braked  due to electromagnetic interaction with the 
+resistive wall surrounding the plasma, causing the mode to eventually {\em lock}\/ (i.e., become stationary in the laboratory frame) to an error-field
+(Nave \& Wesson 1990; Berge, Sandal \& Wesson 1989; Zohm, et al.\ 1990; Fitzpatrick 1993; Waelbroeck \& Fitzpatrick 1997).
+Locked tearing modes are one of the principal causes of disruptions in tokamaks (de\,Vries, et al.\ 2011).
+
+\subsection{Resistive-Wall Rotation Braking}\label{wall}
+Let us, first of all, investigate the braking of tearing mode rotation due to electromagnetic interaction with the resistive wall, in the absence of the error-field. 
+Assuming that the tearing mode possesses the phase velocity $\omega$, and that $\hat{I}_c=0$, 
+Equation~(\ref{e203}) yields
+\begin{equation}
+\hat{\mit\Psi}_w = \frac{E_{sw}/(-\tilde{E}_{ww})}{1-{\rm i}\,\omega\,\tau_{LR}},
+\end{equation}
+where
+\begin{equation}
+\tau_{LR} = \frac{\tau_w}{(-\tilde{E}_{ww})}
+\end{equation}
+is the effective $L/R$ time of the wall. Equation~(\ref{e202}) then gives
+\begin{equation}
+\frac{{\mit\Delta\hat{\Psi}}_s}{\hat{\mit\Psi}_s} = {\mit\Delta}_{pw} + ({\mit\Delta}_{nw}-{\mit\Delta}_{pw})\left(\frac{1+{\rm i}\,\omega\,\tau_{LR}}{1+\omega^2\,\tau_{LR}^{\,2}}\right),
+\end{equation}
+where use has been made of Equations~(\ref{enw}) and (\ref{epw}). It follows that
+\begin{align}
+{\rm Re}\left(\frac{{\mit\Delta\hat{\Psi}}_s}{\hat{\mit\Psi}_s}\right)&= {\mit\Delta}_{pw} + ({\mit\Delta}_{nw}-{\mit\Delta}_{pw})\left(\frac{1}{1+\omega^2\,\tau_{LR}^{\,2}}\right),\\[0.5ex]
+{\rm Im}\left(\frac{{\mit\Delta\hat{\Psi}}_s}{\hat{\mit\Psi}_s}\right)&=({\mit\Delta}_{nw}-{\mit\Delta}_{pw})\left(\frac{\omega\,\tau_{LR}}{1+\omega^2\,\tau_{LR}^{\,2}}\right).
+\end{align} 
+Finally, making use of the island saturation theory presented in Section~\ref{sat}, we obtain
+\begin{align}\label{e583}
+{\rm Re}\left(\frac{{\mit\Delta\hat{\Psi}}_s}{\hat{\mit\Psi}_s}\right)&= {\mit\Delta}_{pw}(0)\left(1-\frac{w}{w_{pw}}\right) + [{\mit\Delta}_{nw}(0)-{\mit\Delta}_{pw}(0)]\left(\frac{1}{1+\omega^2\,\tau_{LR}^{\,2}}\right),\\[0.5ex]
+{\rm Im}\left(\frac{{\mit\Delta\hat{\Psi}}_s}{\hat{\mit\Psi}_s}\right)&=[{\mit\Delta}_{nw}(0)-{\mit\Delta}_{pw}(0)]\left(\frac{\omega\,\tau_{LR}}{1+\omega^2\,\tau_{LR}^{\,2}}\right),\label{e584}
+\end{align} 
+where $w_{pw}=W_{pw}/4$, and
+\begin{equation}
+W_{pw} = \frac{{\mit\Delta}_{pw}(0)\,r_s}{0.8\,\alpha_s^2 -0.27\,\beta_s-0.09\,\alpha_s}
+\end{equation}
+is the saturated island width when the wall is perfectly conducting.
+
+Equations~(\ref{e559}), (\ref{e583}), and (\ref{e584}) yield the following modified Rutherford island width evolution equation: 
+\begin{align}\label{e586}
+I_1\,\tau_R\,\frac{d}{dt}\!\left(\frac{4\,w}{r_s}\right) &= {\mit\Delta}_{pw}(0)\left(1-\frac{w}{w_{pw}}\right) + [{\mit\Delta}_{nw}(0)-{\mit\Delta}_{pw}(0)]\left(\frac{1}{1+\omega^2\,\tau_{LR}^{\,2}}\right)\nonumber\\[0.5ex]
+&\phantom{=} +\frac{I_2}{4}\,[{\mit\Delta}_{nw}(0)-{\mit\Delta}_{pw}(0)]\left(\frac{c_\beta}{1+\tau}\right)\left(\frac{\rho_\beta}{r_s}\right)
+\left(\frac{\tau_\varphi}{\tau_H}\right)\left(\frac{w}{r_s}\right)^2\left(\frac{\omega\,\tau_{LR}}{1+\omega^2\,\tau_{LR}^{\,2}}\right)\nonumber\\[0.5ex]&\phantom{=}+\frac{I_3}{16}\,[{\mit\Delta}_{nw}(0)-{\mit\Delta}_{pw}(0)]^2\left(\frac{\tau_\varphi}{\tau_H}\right)^2\left(\frac{w}{r_s}\right)^7\left(\frac{\omega\,\tau_{LR}}{1+\omega^2\,\tau_{LR}^{\,2}}\right)^2.
+\end{align}
+The first term on the right-hand side of the previous equation governs the growth and saturation of the tearing mode when the wall
+is perfectly conducting. The second term describes  the loss of wall
+stabilization when the phase velocity of the mode is sufficiently small that the associated perturbed magnetic field  can penetrate through the wall.
+The third and fourth terms represent the destabilizing effect of the ion polarization
+current induced in the vicinity of the island chain when the ion fluid flows around the chain's magnetic separatrix (Waelbroeck \& Fitzpatrick 1997; Fitzpatrick \& Waelbroeck 2005a).
+Unlike the case of an isolated island chain, the polarization effect
+is non-zero because, according to Equation~(\ref{e521a}), (\ref{e530}), (\ref{e545}), and (\ref{e584}), the electromagnetic
+braking torque exerted on the plasma in the immediate vicinity of the island chain, due to interaction with the resistive wall, 
+generates finite ion flow in the island rest frame.
+
+Equations~(\ref{e210a}) and (\ref{e574}) imply that
+\begin{equation}
+\omega = \omega_{0} -\sum_{p=1,\infty}(\alpha_p+\beta_p),
+\end{equation}
+where $\omega_0=\omega_{\perp\,i}$ is the island phase velocity in the absence of the resistive wall. In the following, $\omega_0$ is
+assumed to be positive for the sake of definiteness. The modifications to the analysis when $\omega_0$ is
+negative are trivial. 
+The previous equation can be combined with Equations~(\ref{e205}), (\ref{e206}), (\ref{e417a}), (\ref{e418a}), (\ref{e456}),
+and (\ref{e584}) to give the following torque balance equation:
+\begin{equation}\label{e588}
+\omega_0 - \omega = \frac{1}{4}\,[{\mit\Delta}_{nw}(0)-{\mit\Delta}_{pw}(0)]
+\left(\frac{\epsilon_s}{q_s}\right)^2\left(\frac{\tau_V}{\tau_H^{\,2}}\right)\left(\frac{w}{r_s}\right)^4\left(\frac{\omega\,\tau_{LR}}{1+\omega^2\,\tau_{LR}^{\,2}}\right),
+\end{equation}
+where
+\begin{equation}
+\tau_V = 2\,\ln\!\left(\frac{a}{r_s}\right)\tau_\varphi + \left(\frac{q_s}{\epsilon_s}\right)\left(\frac{\tau_i\,\tau_\varphi}{\mu_{00}^i}\right)^{1/2}.
+\end{equation}
+The left-hand side of Equation~(\ref{e588}) represents the viscous restoring torque that acts to prevent changes in the
+island chain's phase velocity. The right-hand side represents the electromagnetic braking torque acting on the island chain due to eddy currents induced in the
+resistive wall.
+
+Let
+\begin{align}
+x &= \frac{x}{x_{pw}},\\[0.5ex]
+y &= \frac{\omega}{\omega_0},\\[0.5ex]
+T &= \frac{t}{\tau_{pw}},\\[0.5ex]
+\tau_{pw}&= \frac{I_1\,\tau_R}{{\mit\Delta}_{pw}(0)}\,\frac{W_{pw}}{r_s}.
+\end{align}
+The modified Rutherford equation, (\ref{e586}), and the torque balance equation, (\ref{e588}), can be
+written in the nondimensional forms (Waelbroeck \& Fitzpatrick 1997)
+\begin{align}\label{e594}
+\frac{dx}{dT} &= 1 - x +\beta_l\left(\frac{1}{1+\alpha_l^2\,y^2}\right) + \gamma_l\left(\frac{1-y}{x^2}\right)
++\delta_l \left[\frac{(1-y)^2}{x}\right],\\[0.5ex]
+1- y &= \epsilon_l\left(\frac{x^4\,y}{1+\alpha_l^2\,y^2}\right),\label{e595}
+\end{align}
+respectively, 
+where
+\begin{align}
+\alpha_l & = \omega_0\,\tau_{LR},\\[0.5ex]
+\beta_l &= 1 - \frac{{\mit\Delta}_{pw}(0)}{{\mit\Delta}_{nw}(0)},\\[0.5ex]
+\gamma_l&= \frac{I_2}{{\mit\Delta}_{nw}(0)}\left(\frac{q_s}{\epsilon_s}\right)^2\left(\frac{c_\beta}{1+\tau}\right)
+\left(\frac{\rho_\beta}{r_s}\right)\left(\frac{\tau_\varphi\,\tau_H\,\omega_0}{\tau_V}\right)\left(\frac{r_s}{w_{pw}}\right)^2,\\[0.5ex]
+\delta_l&= \frac{I_3}{{\mit\Delta}_{nw}(0)}\left(\frac{q_s}{\epsilon_s}\right)^4\left(\frac{\tau_\varphi\,\tau_H\,\omega_0}{\tau_V}\right)^2\left(\frac{r_s}{w_{pw}}\right),\\[0.5ex]
+\epsilon_l &= \frac{\beta_l}{4\,{\mit\Delta}_{pw}(0)}\left(\frac{\epsilon_s}{q_s}\right)^2\left(\frac{\tau_{LR}\,\tau_V}{\tau_H^{\,2}}\right)\left(\frac{w_{pw}}{r_s}\right)^4.
+\end{align}
+
+In conventional tokamaks, it is generally the case that $\alpha_l\gg 1$. In other words, in the absence of wall braking,
+tearing modes rotate sufficiently rapidly that the associated perturbed magnetic fields do not
+penetrate through the wall. It is easily demonstrated that if $\alpha_l$ exceed the critical value $\sqrt{27}$ then the
+normalized torque balance equation, (\ref{e595}), possesses two branches of solutions (Fitzpatrick 1993). The
+{\em high-rotation solution branch}\/ is characterized by $1/2\leq y\leq 1$, and is such that
+\begin{equation}
+y \simeq \frac{1}{2}\left(1-\left[1-\left(\frac{x}{x_h}\right)^4\right]^{1/2}\right),
+\end{equation}
+where
+\begin{equation}
+x_h =\left(\frac{\alpha_l^2}{4\,\epsilon_l}\right)^{1/4}.
+\end{equation}
+The high-rotation solution branch ceases to exist when the normalized island width, $x$, exceeds the
+critical value, $x_h$---at which point the island phase velocity has been reduced to {\em half}\/ of its original value---and
+there is a bifurcation to the low-rotation solution branch. 
+The low-rotation solution branch is characterized by $0\leq y\leq 1/\alpha_l$, and is such that
+\begin{equation}
+y \simeq \frac{1}{\alpha_l}\left\{\left(\frac{x}{x_l}\right)^4-\left[\left(\frac{x}{x_l}\right)^8-1\right]^{1/2}\right\},
+\end{equation}
+where
+\begin{equation}
+x_l=\left(\frac{2\,\alpha_l}{\epsilon_l}\right)^{1/4}.
+\end{equation}
+The low-rotation solution branch ceases to exist when the normalized island width falls below the critical value
+$x_l$, and there is a bifurcation to the high-rotation solution branch. Note that $x_h\gg x_l$, which indicates that once the
+island chain has grown sufficiently to trigger a high-rotation to low-rotation bifurcation it is unlikely to ever attain a
+high-rotation state again (because it would have to shrink by a considerable factor to trigger the reverse bifurcation). 
+Note that, in the presence of a resistive wall, there is a forbidden band of island phase velocities: $\omega_0/\alpha_l < \omega< \omega_0/2$.
+The existence of this forbidden band has been verified experimentally (Gates \& Hender 1996).
+
+It is clear from Equation~(\ref{e594}) that rotation braking due to eddy currents induced in the
+resistive wall has a {\em destabilizing}\/ effect on a tearing mode. In fact, if there is no
+substantial braking then the normalized modified Rutherford equation (\ref{e594}) reduces to
+\begin{equation}
+\frac{dx}{dT} \simeq 1 - x,
+\end{equation}
+indicating that the normalized island width, $x$, saturates at its perfect-wall value, unity. On the other hand, on the low-rotation
+solution branch, Equation~(\ref{e594}) reduces to
+\begin{equation}\label{e606}
+\frac{dx}{dT} \simeq 1 - x + \beta_l +\frac{\gamma_l}{x^2}+\frac{\delta_l}{x},
+\end{equation}
+indicating that the normalized island width saturates at a value that is greater than unity. (Because $\beta_l$, $\gamma_l$, and $\delta_l$ are all positive.) The tearing mode is
+destabilized by the loss of wall stabilization, and also by the ion polarization effect associated with rotation braking.
+
+\subsection{Locking to Static Error-Field}\label{error}
+Rotation braking due to interaction with a resistive wall can reduce the phase velocity of a tearing mode
+by a large factor, but it cannot reduce the velocity to zero (because the braking torque is zero when $\omega=0$).
+The later goal can be achieved by locking to a static error-field, a process that is greatly facilitated once the phase
+velocity of the tearing mode has been reduced to a comparatively small value by wall braking.
+
+Suppose that the
+tearing mode has locked to a static error-field generated by running a steady current $I_c$ in the external field-coil. Without loss of
+generality, we can suppose that $I_c$ is a real quantity. 
+Because
+the mode is locked (i.e., $\omega=0$), Equations~(\ref{e202}) and (\ref{e203}) yield
+\begin{equation}
+\frac{{\mit\Delta\hat{\Psi}}_s}{\hat{\mit\Psi}_s} = {\mit\Delta}_{pw} + ({\mit\Delta}_{nw}-{\mit\Delta}_{pw}) +
+\left(\frac{{\mit\Delta}_{nw} - {\Delta}_{pw}}{E_{sw}}\right)\frac{\hat{I}_c}{\hat{\mit\Psi}_s}.
+\end{equation}
+Let ${\mit\Psi}_s = |{\mit\Psi}_s|\,{\rm e}^{-{\rm i}\,\varphi_s}$. It is convenient to define the normalized vacuum
+flux,
+\begin{equation}
+\hat{\mit\Psi}_v = \frac{\beta_l}{E_{sw}}\left(\frac{r_w}{r_c}\right)^m\frac{\mu_0\,I_c}{R_0\,B_z},
+\end{equation}
+and the reduced vacuum island width,
+\begin{equation}
+w_v = (L_s\,R_0\,\hat{\mit\Psi}_v)^{1/2}.
+\end{equation}
+[See Equation~(\ref{e456}).] The vacuum island width $W_v = 4\,w_v$ is the width of the magnetic island chain that
+would be driven at the resonant surface by the error-field in the absence of shielding. The quantity $\varphi_s$ is the
+helical phase shift between the actual magnetic island chain  at the resonant surface and the vacuum magnetic island
+chain. Making use of the island saturation theory presented in Section~\ref{sat}, we deduce that
+\begin{align}
+{\rm Re}\!\left(\frac{{\mit\Delta\hat{\Psi}}_s}{\hat{\mit\Psi}_s}\right)&= {\mit\Delta}_{pw}(0)\left[1-\frac{w}{w_{pw}}
++\beta_l + \left(\frac{w_v}{w}\right)^2\cos\varphi_s\right],\\[0.5ex]
+{\rm Im}\!\left(\frac{{\mit\Delta\hat{\Psi}}_s}{\hat{\mit\Psi}_s}\right)&={\mit\Delta}_{pw}(0)\left(\frac{w_v}{w}\right)^2\sin\varphi_s.
+\end{align}
+
+Using similar analysis to that employed in Section~\ref{wall}, we obtain the nondimensional modified Rutherford equation,
+\begin{equation}\label{e612}
+\frac{dx}{dT} = 1-x+\beta_l + \frac{\gamma_l}{x^2} + \frac{\delta_l}{x} + \left(\frac{x_v}{x}\right)^2\cos\varphi_s,
+\end{equation}
+and the nondimensional torque balance equation,
+\begin{equation}\label{e613}
+x_u^{4} = x_v^{2}\,x^2\,\sin\varphi_s.
+\end{equation}
+Here, $x_u = w_u/w_{pw}$, and
+\begin{equation}
+w_u = \left[\frac{4}{{\mit\Delta}_{pw}(0)}\left(\frac{q_s}{\epsilon_s}\right)^2\left(\frac{\tau_H^{\,2}\,\omega_0}{\tau_V}\right)\right]^{1/4}r_s.
+\end{equation}
+The left-hand side of Equation~(\ref{e613}) represents the viscous restoring torque that acts to prevent changes in the island
+chain's phase velocity. The right-hand side represents the electromagnetic locking torque exerted on the island chain by
+the error-field. It is clear from Equation~(\ref{e613}) that the error-field is only able to lock the island chain when
+$x_v\,x> x_u^2$, or, equivalently, 
+\begin{equation}
+w_v\,w > w_u^2.
+\end{equation}
+When the previous criterion is satisfied, the relative phase of the island chain lies in the range $0\leq \varphi_s\leq \pi/2$. Note that the island
+chain unlocks from the error-field, and spins up under the influence of the viscous restoring force, if $\varphi_s$
+exceeds the critical value $\pi/2$.
+Finally, a comparison between Equations~(\ref{e606}) and (\ref{e612}) reveals that when the island chain locks to
+the error-field it is further destabilized (because $\cos\varphi_s>0$).
+
+\subsection{Discussion}
+Magnetic island chains in tokamak plasmas that remain rotating tend to be fairly benign.
+On the other hand, magnetic island chains that slow down, due to interaction with a resistive wall, and lock to an error-field, often
+attain sufficiently large widths to trigger disruptions (de Vries, et al.\ 2011). As described in Sections~\ref{wall} and \ref{error}, 
+the slowing down and locking of a magnetic island chain gives rise to three additional destabilizing terms in the chain's
+island width evolution equation. The first is due to the loss of wall stabilization. The second is due to the ion polarization
+current generated by by the velocity gradient discontinuity that develops at the resonant surface when the island chain
+slows down. The third is due to the error-field. Hence, we can understand why tokamak plasmas containing
+locked magnetic island chains are more disruption-prone than those that contain rotating island chains.
+
+\newpage
 \section*{Bibliography}
@@
 {\bf 112}, 443. 
+\item Berge, G., Sandal, L.K., and Wesson, J.A.\ 1989. {\em Rotation and Mode Locking in Tokamaks}. Phys.\ Scr.\ {\bf 40}, 173.
 \item Bondeson, A., and Persson, M.\ 1986. {\em Resistive Tearing Modes in the Presence of Equilibrium Flows}. Phys.\ Fluids
@@
 \item Brau, K., et al.\ 1983. {\em Plasma Rotation in the PDX Tokamak}. Nucl.\ Fusion {\bf 23}, 1643.
+\item Buratti, P., et al.\ 2016. {\em Diagnostic Application of Magnetic Islands Rotation in JET}.  Nucl.\ Fusion {\bf 56}. 076004. 
 \item Chapman, S., and Cowling, T.G.\ 1953. {\em The Mathematical Theory of Non-Uniform Gases}. Cambridge University Press, Cambridge UK. 
@@
 \item Cowley, S.C.,  Kulsrud, R.M., and Hahm, T.S.\ 1986. {\em Linear Stability of Tearing Modes}. Phys.\ Fluids {\bf 29}, 3230. 
+\item de\,Vries, P.C., et al.\ 2011. {\em Survey of Disruption Causes at JET}. Nucl.\ Fusion {\bf 51}, 053018.
 \item Drake, J.F., and Lee, Y.C.\ 1977. {\em Kinetic Theory of Tearing Instabilities}. Phys.\ Fluids {\bf 20}, 1341.
+\item Escande, D.F., and Ottaviani, M.\ 2004. {\em Simple and Rigorous Solution for the Nonlinear Tearing Mode}. Phys.\ Lett.\ A {\bf 323}, 278. 
 \item Fishpool, G.M., and Haynes, P.S.\ 1994. {\em Field Error Instabilities in JET}. Nucl.\ Fusion {\bf 34}, 109. 
@@
 \item Fitzpatrick, R.\ 2015. {\em Plasma Physics: An Introduction}. Taylor \& Francis, CRC Press, Boca Raton FL.
+\item Fitzpatrick, R.\ 2020. {\em Modeling q95 Windows for the Suppression of Edge Localized Modes by Resonant Magnetic Perturbations in the DIII-D Tokamak}. Phys.\ Plasmas {\bf 27}, 102511.
 \item Fitzpatrick, R., and Hender, T.C.\ 1994. {\em Effect of a Static External Magnetic Perturbation on Resistive Mode Stability in Tokamaks}. Phys.\ Plasmas {\bf 1}, 3337. 
@@
 %Based on the Four-Field Reduced Neoclassical MHD Equation}. J.\ Phys.\ Soc.\ Japan {\bf 72}, 313.
+\item Gates, D.A., and Hender, T.C.\ 1996. {\em Resistive Wall Induced Forbidden Bands of Mode Rotation Frequency on the COMPASS-D Tokamak}. Nucl.\ Fusion {\bf 36}, 273. 
 \item Gimblett, C.G., and Peckover, R.S.\ 1979. {\em On the Mutual Interaction Between Rotation and Magnetic Fields
@@
 \item Hammett, G.W., Dorland, W., and Perkins, F.W.\ 1992.  {\em Fluid Models of Phase Mixing, Landau Damping, and Nonlinear Gyrokinetic Dynamics}. Phys.\ Fluids B {\bf 4}, 2052. 
+\item Hastie, R.J., Militello, F., and Porcelli, F.\ 2005. {\em Nonlinear Saturation of Tearing Mode Islands}. Phys.\ Rev.\ Lett.\ {\bf 95}, 065001. 
 \item Hazeltine, R.D., Kotschenreuther, M., and Morrison, P.G.\ 1985. {\em A Four-Field Model for Tokamak Plasma Dynamics}.
@@
 \item Hirshman, S.P., and Sigmar, D.J.\ 1981.\ {\em Neoclassical Transport of Impurities in Tokamak Plasmas}. Nucl.\ Fusion {\bf 21}, 1079.
-\item Howell, D.F., Hender, T.C., and Cunningham, G.\ 2007. {\em Locked mode Thresholds on the MAST Spherical Tokamak}. Nucl.\ Fusion {\bf 47}, 1336. 
+\item Howell, D.F., Hender, T.C., and Cunningham, G.\ 2007. {\em Locked Mode Thresholds on the MAST Spherical Tokamak}. Nucl.\ Fusion {\bf 47}, 1336. 
 \item ITER Physics Basis Editors 1999. {\em Plasma Confinement and Transport}. Nucl.\ Fusion {\bf 39}, 2175. 
+\item La\,Haye, R.J., et al.\ 2003. {\em Propagation of Magnetic Islands in the  $E_r=0$ Frame of Co-Injected Neutral Beam Driven Discharges in the DIII-D Tokamak}. Phys.\ Plasmas {\bf 10}, 3644. 
 \item Lazzaro, E., et al.\ 2002. {\em Error Field Locked Modes Thresholds in Rotating Plasmas, Anomalous Braking and Spin-Up}. Phys.\ Plasmas {\bf 9}, 3906. 
 \item Menard, J.E., et al.\ 2010. {\em Progress in Understanding Error-Field Physics in NSTX Spherical Torus Plasmas}. Nucl.\ Fusion {\bf 50}, 045008.
+\item Militello, F., and Porcelli, F.\ 2004. {\em Simple Analysis of the Nonlinear Saturation of the Tearing Mode}. Phys.\ Plasmas {\bf 11}, L13. 
 \item Monier-Garbet, P., et al.\ 1997. {\em Effects of Neutrals on Plasma Rotation in DIII-D}. Nucl.\ Fusion {\bf 37}, 403.
@@
 {\bf 35}, 657. 
-\item Smolyakov, A.I., et al.\ 1995. {\em Rotating Nonlinear Magnetic islands in a Tokamak Plasma}. Phys.\ Plasmas {\bf 2}, 1581.
+\item Smolyakov, A.I., et al.\ 1995. {\em Rotating Nonlinear Magnetic Islands in a Tokamak Plasma}. Phys.\ Plasmas {\bf 2}, 1581.
 \item Stix, T.H.\ 1973. {\em Decay of Poloidal Rotation in a Tokamak Plasma}. Phys.\ Fluids {\bf 16}, 1260.
 \item Strauss, H.R.\ 1976. {\em Nonlinear, Three-Dimensional Magnetohydrodynamics of  Noncircular Tokamaks}. Phys.\ Fluids {\bf 19},  134.
+\item Thyagaraja, A.\ 1981. {\em Perturbation Analysis of a Simple Model of Magnetic Island Structures}. Phys.\ Fluids {\bf 24}, 1716. 
 \item Vahala, G., et al.\ 1980. {\em Perturbed Magnetic-Field Phase Slip for Tokamaks}. Nucl.\ Fusion {\bf 20}, 17.
@@
 \item Wesson, J.A., et al.\ 1989. {\em Disruptions in JET}. Nucl.\ Fusion {\bf 29}, 641. 
+\item White, R.A., et al.\ 1977. {\em Saturation of the Tearing Mode}. Phys.\ Fluids {\bf 20}, 800.
 \item Wolf, R.C., et al.\ 2005. {\em Effect of the Dynamic Ergodic Divertor in the TEXTOR Tokamak on MHD Stability, Plasma Rotation and Transport}. Nucl.\ Fusion {\bf 45}, 1700. 
 \item Wolfe, S.M., et al.\ 2005. {\em Nonaxisymmetric Field Effects on Alcator C-Mod}. Phys.\ Plasmas {\bf 12}, 056110. 
+\item Zohm, H., et al.\ 1990. {\em Plasma Angular-Momentum Loss by MHD Mode Locking}. Europhys.\ Lett.\ {\bf 11}, 745.
 \end{description}

### 2021-12-02 Documentation/Section9/Velocity/Velocity.cpp

@@ -1,0 +1,27 @@
+// Program to determine velocity profiles around isolated magnetic island chain
+
+#include <stdio.h>
+#include <math.h>
+#include <gsl/gsl_sf_ellint.h>
+
+int main ()
+{
+  FILE* file = fopen("Velocity.out", "w");
+
+  double Xmax = 8.;
+  int    N    = 2000;
+
+  for (int i = 0; i <= N; i++)
+    {
+      double X = - Xmax + (double (i) /double (N)) * 2. * Xmax;
+      double V;
+      if (fabs(X) <= 2.)
+	V = 0.;
+      else
+	V = (M_PI/2.) /gsl_sf_ellint_Ecomp (2./fabs(X), GSL_PREC_DOUBLE);
+
+      fprintf (file, "%e %e\n", X, V);
+    }
+  
+  fclose (file);
+}

### 2021-12-02 Documentation/Section9/Wesson/main.cpp

@@ -1,0 +1,13 @@
+// main.cpp
+
+// Main function for program Wesson
+
+#include "Wesson.h"
+
+int main ()
+{
+  Wesson wesson;
+
+  wesson.Solve();
+}
+

### 2021-12-03 Documentation/TearingModeTheory.tex
Corrections

@@
 \begin{equation}\label{e134}
-{\mit\Delta\Psi}_s = \tau_s\left(\frac{d{\mit\Psi}_s}{dt} + {\rm i}\,\omega\,{\mit\Psi}_s\right).
+{\mit\Delta\Psi}_s = \tau_s\left(\frac{d{\mit\Psi}_s}{dt} + {\rm i}\,\omega_s\,{\mit\Psi}_s\right).
 \end{equation}
 Here, $\tau_s$ is the {\em reconnection time}\/ (i.e., the typical timescale on which magnetic reconnection takes place in the
-resonant layer surrounding the resonant surface), whereas $\omega$ is the phase velocity 
-of the tearing mode when the wall is perfectly conducting. The
-phase velocity  is non-zero because the reconnected flux in the resonant layer is convected by the local plasma
+resonant layer surrounding the resonant surface), whereas $\omega_s$ is the {\em natural frequency}\/ of the tearing mode.
+The natural frequency is defined as oscillation frequency of a naturally unstable tearing mode.
+The
+natural frequency  is non-zero because the reconnected flux in the resonant layer is convected by the local plasma
 flow (Fitzpatrick 1993). (See Sections~\ref{s6.2} and \ref{sphase1}.)
@@
 plasma flow at the resonant surface induced by the electromagnetic torques that develop in the vicinity of this
-surface will modify the convection velocity. Consequently, the phase velocity of the tearing mode can be written
+surface will modify the convection velocity. Consequently, the natural frequency of the tearing mode can be written
 \begin{equation}\label{e200}
- \omega(t) = \omega_{0} + ({\bf k}\cdot {\mit\Delta}{\bf V}_i)_{r=r_s}=
- \omega_{0} + m\,{\mit\Delta\Omega}_\theta(r_s,t) - n\,{\mit\Delta\Omega}_\varphi(r_s,t),
-\end{equation}
-where $\omega_{0}$ is the unperturbed phase velocity.
+ \omega_s(t) = \omega_{s\,0} + ({\bf k}\cdot {\mit\Delta}{\bf V}_i)_{r=r_s}=
+ \omega_{s\,0} + m\,{\mit\Delta\Omega}_\theta(r_s,t) - n\,{\mit\Delta\Omega}_\varphi(r_s,t),
+\end{equation}
+where $\omega_{s\,0}$ is the unperturbed natural frequency.
 The previous expression is known as the {\em no-slip constraint}\/ (Fitzpatrick 1993), and has been verified experimentally (Vahala, et al.\ 1980).
@@
 \begin{equation}\label{e201}
-\omega(t) = \omega_{0} - \sum_{p=1,\infty}\left[\alpha_p(t)+\beta_p(t)\right].
+\omega_s(t) = \omega_{s\,0} - \sum_{p=1,\infty}\left[\alpha_p(t)+\beta_p(t)\right].
 \end{equation}
@@
 \begin{align}\label{e202}
-{\mit\Delta\hat{\Psi}}_s\equiv \tau_s\left(\frac{d\hat{\mit\Psi}_s}{dt} + {\rm i}\,\omega\,\hat{\mit\Psi}_s\right) &= E_{ss}\,\hat{\mit\Psi}_s + E_{sw}\,\hat{\mit\Psi}_w,\\[0.5ex]
+{\mit\Delta\hat{\Psi}}_s\equiv \tau_s\left(\frac{d\hat{\mit\Psi}_s}{dt} + {\rm i}\,\omega_s\,\hat{\mit\Psi}_s\right) &= E_{ss}\,\hat{\mit\Psi}_s + E_{sw}\,\hat{\mit\Psi}_w,\\[0.5ex]
 \tau_w\,\frac{d\hat{\mit\Psi}_w}{dt} &= E_{sw}\,\hat{\mit\Psi}_s +\tilde{E}_{ww}\,\hat{\mit\Psi}_w
 +\hat{I}_c,\label{e203}\\[0.5ex]
-\omega(t)& = \omega_{0} - \sum_{p=1,\infty}\left[\alpha_p(t)+\beta_p(t)\right],\label{e210a}\\[0.5ex]
+\omega_s(t)& = \omega_{s\,0} - \sum_{p=1,\infty}\left[\alpha_p(t)+\beta_p(t)\right],\label{e210a}\\[0.5ex]
 (1+2\,q_s^{\,2})\,\frac{d\alpha_p}{dt} + \left(\frac{1}{\tau_{\theta\,s}}+\frac{j_{1\,p}^{\,2}}{\tau_{M}}\right)\alpha_p
@@
 Equations~(\ref{e202})--(\ref{e206}) contain two quantities---namely, the reconnection time, $\tau_s$, and the unperturbed
-phase velocity, $\omega_{0}$---that can only be determined by solving for the plasma response in the radially-thin resonant layer surrounding the resonant surface.
+natural frequency, $\omega_{s\,0}$---that can only be determined by solving for the plasma response in the radially-thin resonant layer surrounding the resonant surface.
 Unfortunately, determining the resonant plasma response is not a straightforward task.
@@
 \end{align}
-where $\hat{t}=V_A\,t/r_s$, $\hat{\omega}=r_s\,\omega/V_A$, and $\omega$ is the phase velocity of the tearing mode in the laboratory frame. 
+where $\hat{t}=V_A\,t/r_s$, $\hat{\omega}=r_s\,\omega/V_A$, and $\omega$ is the natural frequency of the tearing mode in the laboratory frame. 
 Substituting Equations~(\ref{e294})--(\ref{e300}) into the four-field model, (\ref{e264})--(\ref{e269}), and only retaining terms that
@@
 surface ($\hat{x}=0$).
-The chain has $m$ periods in the poloidal direction, $n$ periods in the toroidal direction, and propagates at the phase velocity $\omega$.
+The chain has $m$ periods in the poloidal direction, $n$ periods in the toroidal direction, and propagates at the helical phase velocity $\omega$.
 The maximum full (as opposed to half) radial width of the magnetic separatrix is
@@
 where $\gamma$ is the growth-rate of the tearing mode, whereas $\omega_r$ is the real
-phase velocity of the mode in the laboratory frame. We shall assume that $|\gamma|\ll |\omega_r|$. This assumption can
+frequency of the mode in the laboratory frame. We shall assume that $|\gamma|\ll |\omega_r|$. This assumption can
 easily be verified {\em a posteriori}. Asymptotic matching between the solution in the outer region and that in the
@@
 Here, we have neglected the imaginary component of $\gamma$ because it merely gives rise to a small correction to the
-phase velocity  of the mode.
+real frequency of the mode.
 
@@
 \begin{equation}\label{e389}
-{\mit\Delta} = {\rm i}\,\tau_s\,(\omega_{0}+ {\mit\Delta}\omega_E),
+{\mit\Delta} = {\rm i}\,\tau_s\,(\omega_{s\,0}+ {\mit\Delta}\omega_E),
 \end{equation}
@@
 \begin{equation}
-\omega_{0}= \omega_{\perp\,e}.
-\end{equation}
+\omega_{s\,0}= \omega_{\perp\,e}.
+\end{equation} 
+Here, $\omega_{\perp\,e}$ is understood to take its unperturbed (by any electromagnetic torques that
+develop in the resonant layer) value.
 
@@
 \begin{equation}\label{e392}
-\hat{\mit\Psi}_s=\frac{\tilde{I}_c}{(-{\mit\Delta}_{nw})+ {\rm i}\,\tau_s\,(\omega_{0}+ {\mit\Delta}\omega_E)}.
-\end{equation}
-Now, in a conventional ohmically-heated tokamak plasma, $\tau_s\,\omega_{0}\gg (-{\mit\Delta}_{nw})$. Consequently, the
+\hat{\mit\Psi}_s=\frac{\tilde{I}_c}{(-{\mit\Delta}_{nw})+ {\rm i}\,\tau_s\,(\omega_{s\,0}+ {\mit\Delta}\omega_E)}.
+\end{equation}
+Now, in a conventional ohmically-heated tokamak plasma, $\tau_s\,\omega_{s\,0}\gg (-{\mit\Delta}_{nw})$. Consequently, the
 shielding current that develops at the resonant surface, in response to the local plasma rotation, is strong enough to largely
@@
 \begin{align}
-v&=\frac{\omega_{0}+{\mit\Delta}\omega_E}{\omega_{0}},\\[0.5ex]
+v&=\frac{\omega_{s\,0}+{\mit\Delta}\omega_E}{\omega_{s\,0}},\\[0.5ex]
 T_{\rm VS}(v) &= 1- v,\\[0.5ex]
@@
 \left(\frac{|\tilde{I}_c|}{\tilde{I}_{c\,{\rm crit}}}\right)^2,\\[0.5ex]
-\zeta_s &= \frac{(-{\mit\Delta}_{nw})}{\tau_s\,\omega_{0}}\ll 1,\\[0.5ex]
-\tilde{I}_{c\,{\rm crit}}&= (\epsilon_s\,s_s)\,(\omega_{0}\,\tau_H)\left/
+\zeta_s &= \frac{(-{\mit\Delta}_{nw})}{\tau_s\,\omega_{s\,0}}\ll 1,\\[0.5ex]
+\tilde{I}_{c\,{\rm crit}}&= (\epsilon_s\,s_s)\,(\omega_{s\,0}\,\tau_H)\left/
 \left[\frac{q_s}{\epsilon_s}\left(\frac{\sqrt{\tau_\varphi\,\tau_i/\mu_{00}^i}}{\tau_s}\right)+2\left(\frac{\tau_\varphi}{\tau_s}\right) \ln\!\left(\frac{a}{r_s}\right)\right]^{1/2}\right..\label{e420}
@@
 experiments. As is clear from Equation~(\ref{e420}), the critical error-field coil current needed to trigger error-field
-penetration increases linearly with the unperturbed plasma rotation at the resonant surface, which is parameterized by $\omega_{0}$. 
+penetration increases linearly with the unperturbed plasma rotation at the resonant surface, which is parameterized by $\omega_{s\,0}$. 
 Once error-field penetration has occurred, the magnitude of the error-field coil current must be reduced to a value
@@
 where $T_0=p_0/n_0$. In the following, for the sake of simplicity, we
-shall assume that $T_i=T_e=T_0$, $\omega_{0}=\omega_\ast$, and $-(d\ln p/dr)_{r_s} = 1/r_s$. We shall also neglect ${\cal O}(1)$
+shall assume that $T_i=T_e=T_0$, $\omega_{s\,0}=\omega_\ast$, and $-(d\ln p/dr)_{r_s} = 1/r_s$. We shall also neglect ${\cal O}(1)$
 constants such as $s_s$, $\eta_e$, $\eta_i$, $\lambda_e$, $\tau$, $\pi$, $\ln(r_s/a)$, et cetera.
@@
 \begin{align}
-\omega_{0}\,\tau_H&\simeq \left(\frac{q_s}{\epsilon_s}\right)^2\rho_\ast\,\beta_\ast^{\,1/2},\\[0.5ex]
+\omega_{s\,0}\,\tau_H&\simeq \left(\frac{q_s}{\epsilon_s}\right)^2\rho_\ast\,\beta_\ast^{\,1/2},\\[0.5ex]
 \frac{\tau_H}{\tau_R}&\simeq \left(\frac{q_s}{\epsilon_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/2}\rho_\ast^{\,2}\,\nu_\ast\,\beta_\ast^{-1/2},\\[0.5ex]
@@
 \end{align}
-Here, $\omega = \hat{\omega}\,V_A/r_s$ is the phase velocity of the island chain in the
+Here, $\omega = \hat{\omega}\,V_A/r_s$ is the frequency of the tearing mode  in the
 laboratory frame,
@@
 \begin{equation}\label{e561}
-I_1\,\tau_R\,\frac{d}{dt}\!\left(\frac{W}{r_s}\right)= {\mit\Delta}_{pw},
-\end{equation}
-where $d/dt$ represents a time derivative in the island rest frame. 
+I_1\,\tau_R\,\frac{d}{dt}\!\left(\frac{W}{r_s}\right)= {\mit\Delta}_{pw}.
+\end{equation}
  According to the Rutherford equation, if the perfect-wall tearing stability index is positive then the width of the magnetic
@@
 
-\subsection{Island Phase Velocity}\label{sphase1}
+\subsection{Natural Frequency}\label{sphase1}
 Equations~(\ref{e545}) and (\ref{e559x}) imply that 
@@
 \subsection{Discussion}
-The phase velocity of an isolated tearing mode is determined by the
+The rotation frequency of an isolated tearing mode is determined by the
 equilibrium plasma flow at the resonant surface. Now, a magnetic
@@
 consequence of diamagnetism. It follows that one or other of the electron and the ion fluid rotation profiles must exhibit a strong gradient
-across the separatrix. The island phase velocity is determined by
+across the separatrix. The island rotation frequency is determined by
 which of the two fluids is most resistant to the formation of such a gradient. Of course, it is the ion fluid which is more resistant because of
 its much greater perpendicular viscosity.
-Hence, a nonlinear magnetic island chain is convected by the ion fluid in the vicinity of the resonant surface, because this choice of phase velocity minimizes the ion fluid velocity gradient across the separatrix (Fitzpatrick 2000).
+Hence, a nonlinear magnetic island chain is convected by the ion fluid in the vicinity of the resonant surface, because this choice of frequency minimizes the ion fluid velocity gradient across the separatrix (Fitzpatrick 2000).
 Incidentally, there is clear experimental evidence that wide magnetic island chains in tokamak plasmas rotate in the ion
@@
 Let us, first of all, investigate the braking of tearing mode rotation due to electromagnetic interaction with the resistive wall, in the absence of the error-field. 
-Assuming that the tearing mode possesses the phase velocity $\omega$, and that $\hat{I}_c=0$, 
+Assuming that the tearing mode possesses the frequency $\omega$ in the laboratory frame, and that $\hat{I}_c=0$, 
 Equation~(\ref{e203}) yields
@@
 is perfectly conducting. The second term describes  the loss of wall
-stabilization when the phase velocity of the mode is sufficiently small that the associated perturbed magnetic field  can penetrate through the wall.
+stabilization when the rotation frequency of the mode is sufficiently small that the associated perturbed magnetic field  can penetrate through the wall.
 The third and fourth terms represent the destabilizing effect of the ion polarization
@@
 
-Equations~(\ref{e210a}) and (\ref{e574}) imply that
-\begin{equation}
-\omega = \omega_{0} -\sum_{p=1,\infty}(\alpha_p+\beta_p),
-\end{equation}
-where $\omega_0=\omega_{\perp\,i}$ is the island phase velocity in the absence of the resistive wall. In the following, $\omega_0$ is
-assumed to be positive for the sake of definiteness. The modifications to the analysis when $\omega_0$ is
+Assuming that the tearing mode oscillates at its natural frequency, Equations~(\ref{e210a}) and (\ref{e574}) imply that
+\begin{equation}
+\omega = \omega_{s\,0} -\sum_{p=1,\infty}(\alpha_p+\beta_p),
+\end{equation}
+where $\omega_{s\,0}=\omega_{\perp\,i}$ is the unperturbed natural frequency. Note that $\omega_{\perp\,i}$ is
+assumed to take its unperturbed (by any electromagnetic torques that develop in the resonant region) value. Furthermore, in the following, $\omega_{s\,0}$ is
+assumed to be positive for the sake of definiteness. The modifications to the analysis when $\omega_{s\,0}$ is
 negative are trivial. 
@@
 \begin{equation}\label{e588}
-\omega_0 - \omega = \frac{1}{4}\,[{\mit\Delta}_{nw}(0)-{\mit\Delta}_{pw}(0)]
+\omega_{s\,0} - \omega = \frac{1}{4}\,[{\mit\Delta}_{nw}(0)-{\mit\Delta}_{pw}(0)]
 \left(\frac{\epsilon_s}{q_s}\right)^2\left(\frac{\tau_V}{\tau_H^{\,2}}\right)\left(\frac{w}{r_s}\right)^4\left(\frac{\omega\,\tau_{LR}}{1+\omega^2\,\tau_{LR}^{\,2}}\right),
@@
 \end{equation}
-The left-hand side of Equation~(\ref{e588}) represents the viscous restoring torque that acts to prevent changes in the
-island chain's phase velocity. The right-hand side represents the electromagnetic braking torque acting on the island chain due to eddy currents induced in the
+The left-hand side of Equation~(\ref{e588}) represents the viscous restoring torque that acts to prevent changes in plasma rotation at the resonant surface.
+The right-hand side represents the electromagnetic braking torque acting on the island chain due to eddy currents induced in the
 resistive wall.
@@
 x &= \frac{x}{x_{pw}},\\[0.5ex]
-y &= \frac{\omega}{\omega_0},\\[0.5ex]
+y &= \frac{\omega}{\omega_{s\,0} },\\[0.5ex]
 T &= \frac{t}{\tau_{pw}},\\[0.5ex]
@@
 \begin{align}
-\alpha_l & = \omega_0\,\tau_{LR},\\[0.5ex]
+\alpha_l & = \omega_{s\,0}\,\tau_{LR},\\[0.5ex]
 \beta_l &= 1 - \frac{{\mit\Delta}_{pw}(0)}{{\mit\Delta}_{nw}(0)},\\[0.5ex]
 \gamma_l&= \frac{I_2}{{\mit\Delta}_{nw}(0)}\left(\frac{q_s}{\epsilon_s}\right)^2\left(\frac{c_\beta}{1+\tau}\right)
-\left(\frac{\rho_\beta}{r_s}\right)\left(\frac{\tau_\varphi\,\tau_H\,\omega_0}{\tau_V}\right)\left(\frac{r_s}{w_{pw}}\right)^2,\\[0.5ex]
-\delta_l&= \frac{I_3}{{\mit\Delta}_{nw}(0)}\left(\frac{q_s}{\epsilon_s}\right)^4\left(\frac{\tau_\varphi\,\tau_H\,\omega_0}{\tau_V}\right)^2\left(\frac{r_s}{w_{pw}}\right),\\[0.5ex]
+\left(\frac{\rho_\beta}{r_s}\right)\left(\frac{\tau_\varphi\,\tau_H\,\omega_{s\,0}}{\tau_V}\right)\left(\frac{r_s}{w_{pw}}\right)^2,\\[0.5ex]
+\delta_l&= \frac{I_3}{{\mit\Delta}_{nw}(0)}\left(\frac{q_s}{\epsilon_s}\right)^4\left(\frac{\tau_\varphi\,\tau_H\,\omega_{s\,0}}{\tau_V}\right)^2\left(\frac{r_s}{w_{pw}}\right),\\[0.5ex]
 \epsilon_l &= \frac{\beta_l}{4\,{\mit\Delta}_{pw}(0)}\left(\frac{\epsilon_s}{q_s}\right)^2\left(\frac{\tau_{LR}\,\tau_V}{\tau_H^{\,2}}\right)\left(\frac{w_{pw}}{r_s}\right)^4.
@@
 The high-rotation solution branch ceases to exist when the normalized island width, $x$, exceeds the
-critical value, $x_h$---at which point the island phase velocity has been reduced to {\em half}\/ of its original value---and
+critical value, $x_h$---at which point the island rotation frequency has been reduced to {\em half}\/ of its original value---and
 there is a bifurcation to the low-rotation solution branch. 
@@
 high-rotation state again (because it would have to shrink by a considerable factor to trigger the reverse bifurcation). 
-Note that, in the presence of a resistive wall, there is a forbidden band of island phase velocities: $\omega_0/\alpha_l < \omega< \omega_0/2$.
+Note that, in the presence of a resistive wall, there is a forbidden band of tearing mode frequencies: $\omega_{s\,0}/\alpha_l < \omega< \omega_{s\,0}/2$.
 The existence of this forbidden band has been verified experimentally (Gates \& Hender 1996).
@@
 \subsection{Locking to Static Error-Field}\label{error}
-Rotation braking due to interaction with a resistive wall can reduce the phase velocity of a tearing mode
-by a large factor, but it cannot reduce the velocity to zero (because the braking torque is zero when $\omega=0$).
+Rotation braking due to interaction with a resistive wall can reduce the rotation frequency of a tearing mode
+by a large factor, but it cannot reduce the frequency to zero (because the braking torque is zero when $\omega=0$).
 The later goal can be achieved by locking to a static error-field, a process that is greatly facilitated once the phase
@@
 \frac{{\mit\Delta\hat{\Psi}}_s}{\hat{\mit\Psi}_s} = {\mit\Delta}_{pw} + ({\mit\Delta}_{nw}-{\mit\Delta}_{pw}) +
-\left(\frac{{\mit\Delta}_{nw} - {\Delta}_{pw}}{E_{sw}}\right)\frac{\hat{I}_c}{\hat{\mit\Psi}_s}.
+\left(\frac{{\mit\Delta}_{nw} - {\mit\Delta}_{pw}}{E_{sw}}\right)\frac{\hat{I}_c}{\hat{\mit\Psi}_s}.
 \end{equation}
@@
 \begin{equation}
-w_u = \left[\frac{4}{{\mit\Delta}_{pw}(0)}\left(\frac{q_s}{\epsilon_s}\right)^2\left(\frac{\tau_H^{\,2}\,\omega_0}{\tau_V}\right)\right]^{1/4}r_s.
-\end{equation}
-The left-hand side of Equation~(\ref{e613}) represents the viscous restoring torque that acts to prevent changes in the island
-chain's phase velocity. The right-hand side represents the electromagnetic locking torque exerted on the island chain by
+w_u = \left[\frac{4}{{\mit\Delta}_{pw}(0)}\left(\frac{q_s}{\epsilon_s}\right)^2\left(\frac{\tau_H^{\,2}\,\omega_{s\,0}}{\tau_V}\right)\right]^{1/4}r_s.
+\end{equation}
+The left-hand side of Equation~(\ref{e613}) represents the viscous restoring torque that acts to prevent changes in the plasma rotation at the resonant surface.
+The right-hand side represents the electromagnetic locking torque exerted on the island chain by
 the error-field. It is clear from Equation~(\ref{e613}) that the error-field is only able to lock the island chain when

### 2021-12-04 Documentation/TearingModeTheory.tex
More corrections

@@
 \begin{equation}\label{e178}
-\{ r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\} = 4\pi^2\,R_0\left[ \frac{\rho}{\tau_\theta}\,r^{\,3}\,({\mit\Omega}_\theta-{\mit\Omega}_{\theta\,{\rm nc}}) -\frac{\partial}{\partial r}\!\left(\mu_\perp\,r^{\,3}\,\frac{\partial{\mit\Omega}_\theta}{\partial r}\right)\right].
+\{ r\,\nabla\cdot \bpi_i\cdot{\bf e}_\theta\} = 4\pi^2\,R_0\left[ \frac{\rho}{\tau_\theta}\,r^3\,({\mit\Omega}_\theta-{\mit\Omega}_{\theta\,{\rm nc}}) -\frac{\partial}{\partial r}\!\left(\mu_\perp\,r^3\,\frac{\partial{\mit\Omega}_\theta}{\partial r}\right)\right].
 \end{equation}
@@
 \begin{equation}\label{e179}
-4\pi^2\,R_0\left[\rho\,r^{\,3}\,\frac{\partial {\mit\Omega}_\theta}{\partial t}+ \frac{\rho}{\tau_\theta}\,r^{\,3}\,({\mit\Omega}_\theta-{\mit\Omega}_{\theta\,{\rm nc}}) -\frac{\partial}{\partial r}\!\left(\mu_\perp\,r^{\,3}\,\frac{\partial{\mit\Omega}_\theta}{\partial r}\right)\right]
+4\pi^2\,R_0\left[\rho\,r^3\,\frac{\partial {\mit\Omega}_\theta}{\partial t}+ \frac{\rho}{\tau_\theta}\,r^3\,({\mit\Omega}_\theta-{\mit\Omega}_{\theta\,{\rm nc}}) -\frac{\partial}{\partial r}\!\left(\mu_\perp\,r^3\,\frac{\partial{\mit\Omega}_\theta}{\partial r}\right)\right]
 =T_{\theta\,s}\,\delta(r-r_s)+ S_\theta,
@@
 \begin{equation}
-S_\theta = 4\pi^2\,R_0\left[ \frac{\rho}{\tau_\theta}\,r^{\,3}\,({\mit\Omega}_{\theta\,0}-{\mit\Omega}_{\theta\,{\rm nc}}) -\frac{d}{d r}\!\left(\mu_\perp\,r^{\,3}\,\frac{d{\mit\Omega}_{\theta\,0}}{d r}\right)\right].
+S_\theta = 4\pi^2\,R_0\left[ \frac{\rho}{\tau_\theta}\,r^3\,({\mit\Omega}_{\theta\,0}-{\mit\Omega}_{\theta\,{\rm nc}}) -\frac{d}{d r}\!\left(\mu_\perp\,r^3\,\frac{d{\mit\Omega}_{\theta\,0}}{d r}\right)\right].
 \end{equation}
@@
 \begin{equation}
-4\pi^2\,R_0\left[\rho\,r^{\,3}\,\frac{\partial {\mit\Delta\Omega}_\theta}{\partial t}+ \frac{\rho}{\tau_\theta}\,r^{\,3}\,{\mit\Delta\Omega}_\theta-\frac{\partial}{\partial r}\!\left(\mu_\perp\,r^{\,3}\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial r}\right)\right]
+4\pi^2\,R_0\left[\rho\,r^3\,\frac{\partial {\mit\Delta\Omega}_\theta}{\partial t}+ \frac{\rho}{\tau_\theta}\,r^3\,{\mit\Delta\Omega}_\theta-\frac{\partial}{\partial r}\!\left(\mu_\perp\,r^3\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial r}\right)\right]
 =T_{\theta\,s}\,\delta(r-r_s).
@@
 There is one further refinement that we can make to the previous equation. It turns out that neoclassical poloidal
-flow damping gives rise to an enhancement of poloidal ion inertia by a factor of $1+2\,q^{\,2}$ (Hirshman 1978). Hence,
+flow damping gives rise to an enhancement of poloidal ion inertia by a factor of $1+2\,q^2$ (Hirshman 1978). Hence,
 our final version of the perturbed plasma poloidal angular equation of motion becomes 
 \begin{equation}\label{e182}
-4\pi^2\,R_0\left[(1+2\,q^{\,2})\,\rho\,r^{\,3}\,\frac{\partial {\mit\Delta\Omega}_\theta}{\partial t}+ \frac{\rho}{\tau_\theta}\,r^{\,3}\,{\mit\Delta\Omega}_\theta-\frac{\partial}{\partial r}\!\left(\mu_\perp\,r^{\,3}\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial r}\right)\right]
+4\pi^2\,R_0\left[(1+2\,q^2)\,\rho\,r^3\,\frac{\partial {\mit\Delta\Omega}_\theta}{\partial t}+ \frac{\rho}{\tau_\theta}\,r^3\,{\mit\Delta\Omega}_\theta-\frac{\partial}{\partial r}\!\left(\mu_\perp\,r^3\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial r}\right)\right]
 =T_{\theta\,s}\,\delta(r-r_s).
@@
 \begin{align}\label{e188}
-4\pi^2\,R_0\left[(1+2\,q_s^{\,2})\,\rho_s\,r^{\,3}\,\frac{\partial {\mit\Delta\Omega}_\theta}{\partial t}+ \frac{\rho_s}{\tau_{\theta\,s}}\,r^{\,3}\,{\mit\Delta\Omega}_\theta-\mu_{\perp\,s}\,\frac{\partial}{\partial r}\!\left(r^{\,3}\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial r}\right)\right]
+4\pi^2\,R_0\left[(1+2\,q_s^{\,2})\,\rho_s\,r^3\,\frac{\partial {\mit\Delta\Omega}_\theta}{\partial t}+ \frac{\rho_s}{\tau_{\theta\,s}}\,r^3\,{\mit\Delta\Omega}_\theta-\mu_{\perp\,s}\,\frac{\partial}{\partial r}\!\left(r^3\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial r}\right)\right]
 &=T_{\theta\,s}\,\delta(r-r_s),\\[0.5ex]
@@
 \end{align}
-where $\hat{t}=V_A\,t/r_s$, $\hat{\omega}=r_s\,\omega/V_A$, and $\omega$ is the natural frequency of the tearing mode in the laboratory frame. 
+where $\hat{t}=V_A\,t/r_s$, $\hat{\omega}=r_s\,\omega/V_A$, and $\omega$ is the frequency of the tearing mode in the laboratory frame. 
 Substituting Equations~(\ref{e294})--(\ref{e300}) into the four-field model, (\ref{e264})--(\ref{e269}), and only retaining terms that
@@
 T_{\rm VS}(v) &= 1- v,\\[0.5ex]
-T_{\rm EM}(v) &= \frac{1}{4}\,\frac{v}{\zeta_s^{\,2}+v^2}
+T_{\rm EM}(v) &= \frac{1}{4}\,\frac{v}{\zeta_s^{2}+v^2}
 \left(\frac{|\tilde{I}_c|}{\tilde{I}_{c\,{\rm crit}}}\right)^2,\\[0.5ex]
 \zeta_s &= \frac{(-{\mit\Delta}_{nw})}{\tau_s\,\omega_{s\,0}}\ll 1,\\[0.5ex]
-\tilde{I}_{c\,{\rm crit}}&= (\epsilon_s\,s_s)\,(\omega_{s\,0}\,\tau_H)\left/
-\left[\frac{q_s}{\epsilon_s}\left(\frac{\sqrt{\tau_\varphi\,\tau_i/\mu_{00}^i}}{\tau_s}\right)+2\left(\frac{\tau_\varphi}{\tau_s}\right) \ln\!\left(\frac{a}{r_s}\right)\right]^{1/2}\right..\label{e420}
+\tilde{I}_{c\,{\rm crit}}&=\epsilon_s\,s_s\left(\frac{\tau_s\,\tau_H\,\omega_{s\,0}}{\tau_V}\right),\label{e420}
+\\[0.5ex]
+\tau_V&= \frac{q_s}{\epsilon_s}\left(\frac{\tau_\varphi\,\tau_i}{\mu_{00}^i}\right)^{1/2}+ 2\ \ln\!\left(\frac{a}{r_s}\right)\tau_\varphi.\label{e421a}
 \end{align}
@@
 \begin{equation}
-\hat{\delta}\gg 4\,S^{-2/5}\left(\frac{q_s}{\epsilon_s}\right)^{2/5}\left[\frac{q_s}{\epsilon_s}\left(\frac{\sqrt{\tau_\varphi\,\tau_i/\mu_{00}^i}}{\tau_R}\right)+2\left(\frac{\tau_\varphi}{\tau_R}\right) \ln\!\left(\frac{a}{r_s}\right)\right]^{-1/5}.
+\hat{\delta}\gg 4\left(\frac{q_s}{\epsilon_s}\right)^{2/5}\left(\frac{\tau_H^{\,2}}{\tau_R\,\tau_V}\right)^{1/5}.
 \end{equation}
@@
 \end{equation}
-and vice vera.
+and vice versa.
 
@@
 \end{align}
-Here, $\omega = \hat{\omega}\,V_A/r_s$ is the frequency of the tearing mode  in the
+Here, $\omega = \hat{\omega}\,V_A/r_s$ is the rotation frequency of the tearing mode  in the
 laboratory frame,
@@
 \begin{equation}
-\frac{1}{L_n}= -\frac{1}{{\mit\Gamma}\,(1-c_\beta^{\,2})}\left(\frac{d\ln n}{dr}\right)_{r_s}
+L_n= \left[-\frac{1}{{\mit\Gamma}\,(1-c_\beta^{\,2})}\left(\frac{d\ln n}{dr}\right)_{r_s}\right]^{-1}
 \end{equation}
@@
 \end{align}
-Here, use has been made of Equations~(\ref{e317a}), (\ref{e318a}), (\ref{e481}), and (\ref{e482}). Note that $d/dt$ in Equation~(\ref{e559}) represents a time derivative in the island rest frame.
+Here, use has been made of Equations~(\ref{e317a}), (\ref{e318a}), (\ref{e481}), and (\ref{e482}).
 
@@
 
-Assuming that the tearing mode oscillates at its natural frequency, Equations~(\ref{e210a}) and (\ref{e574}) imply that
+Assuming that the tearing mode rotates at its natural frequency, Equations~(\ref{e210a}) and (\ref{e574}) imply that
 \begin{equation}
@@
 negative are trivial. 
-The previous equation can be combined with Equations~(\ref{e205}), (\ref{e206}), (\ref{e417a}), (\ref{e418a}), (\ref{e456}),
+The previous equation can be combined with Equations~(\ref{e205}), (\ref{e206}), (\ref{e421a}), (\ref{e417a}), (\ref{e418a}), (\ref{e456}),
 and (\ref{e584}) to give the following torque balance equation:
@@
 \omega_{s\,0} - \omega = \frac{1}{4}\,[{\mit\Delta}_{nw}(0)-{\mit\Delta}_{pw}(0)]
-\left(\frac{\epsilon_s}{q_s}\right)^2\left(\frac{\tau_V}{\tau_H^{\,2}}\right)\left(\frac{w}{r_s}\right)^4\left(\frac{\omega\,\tau_{LR}}{1+\omega^2\,\tau_{LR}^{\,2}}\right),
-\end{equation}
-where
-\begin{equation}
-\tau_V = 2\,\ln\!\left(\frac{a}{r_s}\right)\tau_\varphi + \left(\frac{q_s}{\epsilon_s}\right)\left(\frac{\tau_i\,\tau_\varphi}{\mu_{00}^i}\right)^{1/2}.
+\left(\frac{\epsilon_s}{q_s}\right)^2\left(\frac{\tau_V}{\tau_H^{\,2}}\right)\left(\frac{w}{r_s}\right)^4\left(\frac{\omega\,\tau_{LR}}{1+\omega^2\,\tau_{LR}^{\,2}}\right).
 \end{equation}
@@
 \begin{align}
-x &= \frac{x}{x_{pw}},\\[0.5ex]
+x &= \frac{w}{w_{pw}},\\[0.5ex]
 y &= \frac{\omega}{\omega_{s\,0} },\\[0.5ex]
@@
 \alpha_l & = \omega_{s\,0}\,\tau_{LR},\\[0.5ex]
-\beta_l &= 1 - \frac{{\mit\Delta}_{pw}(0)}{{\mit\Delta}_{nw}(0)},\\[0.5ex]
-\gamma_l&= \frac{I_2}{{\mit\Delta}_{nw}(0)}\left(\frac{q_s}{\epsilon_s}\right)^2\left(\frac{c_\beta}{1+\tau}\right)
+\beta_l &= \frac{{\mit\Delta}_{nw}(0)}{{\mit\Delta}_{pw}(0)}-1,\\[0.5ex]
+\gamma_l&= \frac{I_2}{{\mit\Delta}_{pw}(0)}\left(\frac{q_s}{\epsilon_s}\right)^2\left(\frac{c_\beta}{1+\tau}\right)
 \left(\frac{\rho_\beta}{r_s}\right)\left(\frac{\tau_\varphi\,\tau_H\,\omega_{s\,0}}{\tau_V}\right)\left(\frac{r_s}{w_{pw}}\right)^2,\\[0.5ex]
-\delta_l&= \frac{I_3}{{\mit\Delta}_{nw}(0)}\left(\frac{q_s}{\epsilon_s}\right)^4\left(\frac{\tau_\varphi\,\tau_H\,\omega_{s\,0}}{\tau_V}\right)^2\left(\frac{r_s}{w_{pw}}\right),\\[0.5ex]
-\epsilon_l &= \frac{\beta_l}{4\,{\mit\Delta}_{pw}(0)}\left(\frac{\epsilon_s}{q_s}\right)^2\left(\frac{\tau_{LR}\,\tau_V}{\tau_H^{\,2}}\right)\left(\frac{w_{pw}}{r_s}\right)^4.
+\delta_l&= \frac{I_3}{{\mit\Delta}_{pw}(0)}\left(\frac{q_s}{\epsilon_s}\right)^4\left(\frac{\tau_\varphi\,\tau_H\,\omega_{s\,0}}{\tau_V}\right)^2\left(\frac{r_s}{w_{pw}}\right),\\[0.5ex]
+\epsilon_l &= \frac{[{\mit\Delta}_{nw}(0)-{\mit\Delta}_{pw}(0)]}{4}\left(\frac{\epsilon_s}{q_s}\right)^2\left(\frac{\tau_{LR}\,\tau_V}{\tau_H^{\,2}}\right)\left(\frac{w_{pw}}{r_s}\right)^4.
 \end{align}

### 2021-12-04 Research/LinearTearingModeTheory/LinearTearingModeTheory.tex
Reorganized files

--- 2020-11-05 Papers/Paper2/Submit/Paper.tex
@@
 \usepackage {graphicx}
-\newcommand {\bomega}{\mbox{\boldmath$\omega$}}
-\newcommand {\bpi}{\mbox{\boldmath$\pi$}}
 
@@
 
-\title {Further Modeling of $q_{95}$ Windows for the Suppression of Edge Localized Modes by Resonant Magnetic Perturbations in the DIII-D Tokamak}
+\title{Further drift-magnetohydrodynamic modeling of linear tearing mode dynamics in tokamak plasmas}
 
-\author{R.~Fitzpatrick\,\footnote{rfitzp@farside.ph.utexas.edu}}
+\author{R.~Fitzpatrick\,\footnote{rfitzp@utexas.edu}}
 \affiliation{Institute for Fusion Studies,  Department of Physics,  University of Texas at Austin,  Austin TX, 78712, USA}
@@
 \begin{abstract}
-An improved resonant plasma response model that describes the interaction between a tokamak plasma and a resonant magnetic perturbation  (RMP) is developed. 
-The model interpolates between the linear and the nonlinear response regimes, and takes into account the fact that the slip-frequency
-is non-zero in the nonlinear regime. The improved model is incorporated into the {\tt EPEC} toroidal asymptotic matching code.
-The modified {\tt EPEC} code is used to investigate RMP-induced edge-localized-mode (ELM) suppression in DIII-D H-mode discharge \#145380. 
-Somewhat surprisingly, allowing for a finite slip-frequency (i.e., relaxing the so-called no-slip constraint) is found to only slightly facilitate the locking of
-driven magnetic island chains to the RMP, and, hence, to only slightly facilitate RMP-induced ELM suppression.  The previously obtained conclusion 
-that the response of a typical H-mode tokamak plasma to an RMP cannot be accurately modeled by linear theory is confirmed.
-The previously obtained conclusion that the best agreement between theory and observations is achieved by assuming that the
-natural frequencies of tearing modes, in the absence of the RMP, are determined by the local equilibrium ${\bf E}\times{\bf B}$ frequency is also confirmed.
+An improved 
 \end{abstract}
@@
 
-\section{Introduction}
-In the context of tokamak plasmas, a resonant magnetic perturbation (RMP) refers to an externally
-generated, (usually) static, helical magnetic perturbation that resonates at
-one or more ``rational'' magnetic flux-surfaces within the plasma. Resonant magnetic perturbations have been successfully
-employed to compensate error fields (i.e., accidentally produced RMPs), and, thereby,  to prevent the associated formation of
-locked modes, in a wide variety of different types of tokamak discharge. \cite{error1,error2,error3} RMPs have also been  successfully used to either  
-mitigate or completely suppress  edge-localized-modes (ELMs) in H-mode tokamak discharges.\cite{elm1,elm2,elm3,elm4,elm5,elm6}
-
-``Asymptotic matching'' is by far the most efficient method for modeling the response of a tokamak plasma to an RMP.\cite{fkr,coppi,ruth,ara,pletz,rfa, am1,tokuda,brennan,am2,am3} 
-According to the asymptotic matching approach, the response of the plasma to the applied RMP is governed by a combination of flux-freezing and
-perturbed force balance---this combination is usually referred to as ``marginally-stable ideal-magnetohydrodynamics (MHD)"---everywhere in the plasma apart from a number of relatively narrow (in the radial direction) regions in which the applied
-perturbation resonates with the equilibrium magnetic field. Magnetic reconnection can take place within the resonant regions to
-produce relatively narrow magnetic island chains. Within the resonant regions, the plasma response is governed by  linear or nonlinear 
- two-fluid resistive-MHD, depending on whether the induced magnetic island widths are smaller or larger, respectively, than the corresponding linear layer widths. 
- Thus, when employing the asymptotic matching approach, the equations of marginally-stable ideal-MHD
-are solved in the so-called ``outer region'' that comprises most of the plasma (and the surrounding vacuum), the equations of 
-linear/nonlinear two-fluid resistive-MHD are solved in the various resonant layers that constitute the so-called ``inner region'', and the two
-sets of solutions are then asymptotically matched to one another.
-
-In the nonlinear resonant response regime, the evolution of the island chain width in a given resonant layer is governed by the familiar ``Rutherford island width evolution equation''.\cite{ruth,ruth1}
-On the other hand, the phase evolution of the island chain is conventionally governed by the well-known ``no-slip constraint''.\cite{rfa} According to this constraint,  plasma is trapped inside the
-magnetic separatrix of the island chain,
-which forces the chain to co-rotate with the local plasma flow. In reality, however, the plasma
-is able to diffuse resistively across the separatrix to some extent.\cite{slip1,slip2}
-
-The recently developed, toroidal, asymptotic matching code {\tt EPEC} (Extended Perturbed Equilibrium Code) has been used to simulate 
-RMP-induced ELM suppression in DIII-D H-mode plasmas.\cite{rftor,rftor1}
-The original {\tt EPEC} model incorporates the no-slip constraint.
-The first aim of this paper is to investigate 
-what happens when the no-slip constraint is relaxed in the aforementioned {\tt EPEC} simulations.
- The second aim is to examine what happens when an improvement is made to the manner in which the resonant
-plasma response component of the {\tt EPEC} model interpolates between the linear and the nonlinear regimes.
-
-\section{Cylindrical Resonant Response Model}\label{s2}
-\subsection{Introduction}
-For the sake of simplicity, and also to make a better connection with previous research, let us commence our investigation by discussing
-the resonant response of a tokamak plasma to an RMP in cylindrical geometry.
-
-\subsection{Plasma Equilibrium}
-Consider a large aspect-ratio, low-$\beta$, circular cross-section, tokamak plasma.
-Such a plasma is well approximated as a periodic cylinder.  Suppose that the minor radius of the plasma
-is $a$. Standard cylindrical coordinates ($r$, $\theta$, $z$) are adopted. The system is assumed to
-be periodic in the $z$-direction, with periodicity length $2\pi\,R_0$, where $R_0\gg a$ is the simulated
-plasma major radius. It is convenient to define the simulated toroidal angle $\phi=z/R_0$. 
-The equilibrium magnetic field is written ${\bf B} = [0,B_\theta(r), B_\phi]$.  The
-so-called ``safety-factor'', $q(r)=r\,B_\phi/(R_0\,B_\theta)$, parameterizes the helical pitches of equilibrium magnetic
-field-lines.
-
-\subsection{Plasma Response to RMP}
-Consider the response of the plasma to an externally generated, static, helical, RMP. 
-Suppose that the RMP has $m$ periods in the poloidal direction, and $n$ periods in the toroidal direction.
-It is convenient to express the perturbed magnetic field and the perturbed plasma current density in
-terms of a perturbed poloidal magnetic flux (divided by $2\pi\,R_0$), $\psi(r,\theta,\phi,t)$. In fact, $\delta{\bf B} = \nabla\psi\times \nabla z$, 
-where $\psi(r,\theta,\phi,t) = \hat{\psi}(r,t)\,\exp[{\rm i}\,(m\,\theta-n\,\phi)]$, and $\hat{\psi}$ is real. This particular representation
-is valid provided that $m/n\gg a/R_0$.\cite{rfa}
-
-The response of the plasma to the RMP is governed by the equations of marginally-stable, ideal-MHD everywhere in the
-plasma, apart from a relatively narrow (in $r$) region in the vicinity of the so-called  ``rational surface'', minor radius $r_s$, 
-at which $q(r_s)=m/n$.\cite{rfa}
-
-It is convenient to parameterize the RMP in terms of the so-called ``vacuum magnetic flux'', ${\mit\Psi}_v(t) = |{\mit\Psi}_v|\,{\rm e}^{-{\rm i}\,\varphi_v}$,
-which is defined to be the value of $\hat{\psi}(r,t)$ at radius $r_s$ in the presence of the RMP, but in the absence of plasma. Here,
-$\varphi_v$ is the helical phase of the RMP. Likewise, the response of the plasma in the vicinity of the rational
-surface is parameterized in terms of the so-called ``reconnected magnetic flux'', ${\mit\Psi}_s(t)=|{\mit\Psi}_s|\,{\rm e}^{\,{\rm i}\,\varphi_s}$, 
-which is the actual value of $\hat{\psi}(r,t)$ at radius $r_s$. Here, $\varphi_s$ is the helical phase of
-the reconnected magnetic flux.
-
-The intrinsic stability of the $m$, $n$ tearing mode is governed by the dimensionless parameter
-$E_{ss}= [d\hat{\psi}_s/d\ln r]_{r_{s-}}^{r_{s+}}$, where $\hat{\psi}_s(r)$
-is a solution of the marginally-stable, ideal-MHD equations, for the case of an $m$, $n$ helical
-perturbation, that satisfies physical boundary conditions at $r=0$ and $r=a$, in the absence of the
-RMP, and is such that $\hat{\psi}_s(r_s)=1$.\cite{fkr,am1} According to resistive-MHD theory,\cite{fkr,ruth}
-if $E_{ss}>0$ then the $m$, $n$ tearing mode spontaneously reconnects magnetic flux at the rational
-surface to form a helical magnetic island chain. In this paper, it is assumed that $E_{ss}<0$, so that the
-$m$, $n$ tearing mode is intrinsically stable. In this case, any magnetic reconnection that takes place
-at the rational surface is due solely to the action of the RMP.
-
-The ideal-MHD response of the plasma to the RMP is governed by the dimensionless parameter
-$E_{sv}= [d\hat{\psi}_v/d\ln r]_{r_{s-}}^{r_{s+}}$, where $\hat{\psi}_v(r)$
-is a solution of the marginally-stable, ideal-MHD equations, for the case of an $m$, $n$ helical
-perturbation, that satisfies physical boundary conditions at $r=0$ and $r=a$, in the presence of the
-RMP, and is such that $\hat{\psi}_v(r_s)=0$.\cite{am1}
-
-\subsection{Linear Response Regime}
-In the linear response regime, the reconnected magnetic flux induced by the RMP at the
-rational surface is governed by\,\cite{rfa,rfb,rfc}
-\begin{equation}\label{e1}
-\frac{\delta_s}{r_s}\,\tau_R\left(\frac{d}{dt}+{\rm i}\,\omega_s\right){\mit\Psi}_s= E_{ss}\,{\mit\Psi}_s+E_{sv}\,{\mit\Psi}_v,
-\end{equation}
-where $\delta_s$ is the linear layer width, $\tau_R=\mu_0\,r_s^{\,2}\,\sigma(r_s)$ the global resistive diffusion timescale,
- and
-\begin{equation}
-\omega_s (t)=m\,{\mit\Omega}_\theta(r_s,t)-n\,{\mit\Omega}_\phi(r_s,t).
-\end{equation}
-Here, $\sigma(r)$, ${\mit\Omega}_\theta(r,t)$, and ${\mit\Omega}_\phi(r,t)$ are the 
-plasma electrical conductivity, poloidal angular velocity, and toroidal angular velocity profiles, respectively. 
-Note that, in this paper, we are assuming that the constant-$\psi$ approximation\,\cite{fkr} holds at the rational surface. (It is demonstrated in
-Ref.~\onlinecite{rf1} that the appropriate linear response regime for an RMP resonant in the pedestal of a typical DIII-D H-mode discharge
-is the so-called  ``first semi-collisional regime'', which is indeed a constant-$\psi$ response regime. Moreover, if the appropriate linear response regime
-is constant-$\psi$ then so is the appropriate nonlinear response regime, because the constant-$\psi$ constraint is
-easier to satisfy in the nonlinear regime than in the linear regime.\cite{rfb,rffig})
-
-Equation~(\ref{e1}) can be rewritten as an ``amplitude evolution equation'',
-\begin{equation}\label{e3}
-\frac{\delta_s}{r_s}\,\tau_R\,\frac{d|{\mit\Psi}_s|}{dt}= E_{ss}\,|{\mit\Psi}_s| + E_{sv}\,|{\mit\Psi}_v|\,\cos(\varphi_s-\varphi_v),
-\end{equation}
-combined with a ``phase evolution equation'', 
-\begin{equation}\label{e4}
-\frac{d\varphi_s}{dt} = \omega_s - \frac{E_{sv}}{\tau_R}\,\frac{r_s}{\delta_s}\,\frac{|{\mit\Psi}_v|}{|{\mit\Psi}_s|}\,\sin(\varphi_s-\varphi_v).
-\end{equation}
-The final term on the right-hand side of Eq.~(\ref{e4}) is termed the ``slip-frequency'', and is the difference between the helical phase velocity of
-the reconnected magnetic flux and that expected on the  assumption that the flux is convected by the plasma flow at the
-rational surface (i.e., $d\varphi_s/dt=\omega_s$). In general, the slip-frequency is non-zero because the plasma in the vicinity of the rational surface is capable of diffusing resistively 
-through the linear layer structure.
-
-\subsection{Nonlinear Response Regime}
-In the nonlinear response regime, Eq.~(\ref{e3}) generalizes to the ``Rutherford island width evolution equation'':\,\cite{ruth,ruth1}
-\begin{equation}\label{e5}
-\frac{({\cal I}/2)\,W_s}{r_s}\,\tau_R\,\frac{d|{\mit\Psi}_s|}{dt} = E_{ss}\,|{\mit\Psi}_s| + E_{sv}\,|{\mit\Psi}_v|\,\cos(\varphi_s-\varphi_v),
-\end{equation}
-where
-\begin{equation}
-W_s = 4\left(\frac{|{\mit\Psi}_s|}{s_s\,r_s\,B_\theta(r_s)}\right)^{1/2} r_s
-\end{equation}
-is the full radial width of the magnetic island chain, ${\cal I} = 0.8227$, $s(r) = d\ln q/d\ln r$, and $s_s=s(r_s)$. The
-nonlinear regime holds when $W_s\gg \delta_s$, whereas the linear regime holds when $\delta_s\ll W_s$.
-
-Equation~(\ref{e5}) is usually coupled with the so-called ``no-slip constraint'':\,\cite{rfa}
-\begin{equation}\label{e6}
-\frac{d\varphi_s}{dt} = \omega_s.
-\end{equation}
-The reasoning behind the imposition of this constraint is that  plasma is trapped inside the
-magnetic separatrix of the  island chain that forms in the vicinity of the rational surface,
-which forces the chain to co-rotate with the local plasma flow. However, in reality, the plasma
-is able to diffuse resistively across the separatrix to some extent. Hence, by analogy with Eqs.~(\ref{e3}), (\ref{e4}), and (\ref{e5}), and 
-in accordance with Refs.~\onlinecite{slip1} and \onlinecite{slip2}, in this paper we shall modify Eq.~(\ref{e6}) such that
-\begin{equation}\label{e7}
-\frac{d\varphi_s}{dt} = \omega_s - \frac{E_{sv}}{\tau_R}\,\frac{r_s}{({\cal I}/2)\,W_s}\,\frac{|{\mit\Psi}_v|}{|{\mit\Psi}_s|}\,\sin(\varphi_s-\varphi_v).
-\end{equation}
-The final term on the right-hand side of the previous equation is the ``nonlinear slip-frequency''. In general,
-we would expect this frequency to be relatively small (because it is usually the case that $|\omega_s|\,\tau_R\,(W_s/r_s)\gg 1$
-for fully-developed magnetic islands in high-temperature tokamak plasmas\,\cite{rf1,slip2}). Nevertheless, the
-nonlinear slip-frequency may be non-negligible for developing island chains, which is why we are including it in our analysis.
-
-\subsection{Composite Model}
-If we define $X_s = |{\mit\Psi}_s|\,\cos\varphi_s$, $Y_s = |{\mit\Psi}_s|\,\sin\varphi_s$, $X_v = |{\mit\Psi}_v|\,\cos\varphi_v$, and $Y_v = |{\mit\Psi}_v|\,\sin\varphi_v$ 
-then we can combine Eqs.~(\ref{e3}), (\ref{e4}), (\ref{e5}), and (\ref{e7}) to give the following
-composite resonant response model that interpolates between the linear and the nonlinear
-regimes:\,\cite{slip1,slip2,slip3}
-\begin{align}\label{e11}
-\left(\frac{({\cal I}/2)\,W_s+\delta_s}{r_s}\right)\tau_R\left(\frac{dX_s}{dt}+\omega_s\,Y_s\right)&= E_{ss}\,X_s + E_{sv}\,X_v,\\[0.5ex]
-\left(\frac{({\cal I}/2)\,W_s+\delta_s}{r_s}\right)\tau_R\left(\frac{dY_s}{dt}-\omega_s\,X_s\right)& = E_{ss}\,Y_s + E_{sv}\,Y_v,\label{e12}
-\end{align}
-where
-\begin{equation}\label{e23x}
-W_s = 4\left(\frac{\sqrt{X_s^{\,2}+Y_s^{\,2}}}{s_s\,r_s\,B_\theta(r_s)}\right)^{1/2} r_s.
-\end{equation}
-With the benefit of hindsight, Eqs.~(\ref{e11}) and (\ref{e12}) could have been derived more directly from the
-following heuristic generalization of Eq.~(\ref{e1}):\,\cite{slip2}
-\begin{equation}
-\left(\frac{({\cal I}/2)\,W_s+\delta_s}{r_s}\right)\tau_R\left(\frac{d}{dt}+{\rm i}\,\omega_s\right){\mit\Psi}_s= E_{ss}\,{\mit\Psi}_s+E_{sv}\,{\mit\Psi}_v.
-\end{equation}
-
-\section{Modified Toroidal Resonant Response Model}\label{s3}
-Let us now generalize our investigation to toroidal geometry.
-
-The toroidal model of the response of a tokamak plasma to a static, externally generated, RMP that is implemented in the {\tt EPEC} code\,\cite{rftor1} is described in
-detail in Ref.~\onlinecite{rftor}. In the light of the composite cylindrical resonant response model developed in Sect.~\ref{s2}, we propose to 
-modify the resonant  response component of the {\tt EPEC} model (this component is described in Appendix~D of Ref.~\onlinecite{rftor}).
-
-Equations~(D1) and (D2) in Ref.~\onlinecite{rftor} are modified such that 
-\begin{align}\label{e15}
-\left(\hat{W}_k + \hat{\delta}_k\right){\cal S}_k\,\frac{d\hat{\mit\Psi}_k}{d\hat{t}} &= \sum_{k'=1,K}\hat{E}_{kk'}\,\hat{\mit\Psi}_{k'}\,\cos(\varphi_k-\varphi_{k'}-\xi_{kk'})
-+\hat{E}_{kk}\,\hat{\chi}_k\,\cos(\varphi_k-\zeta_k),\\[0.5ex]
-{\cal S}_k&=\frac{\tau_R(\hat{r}_k)}{\tau_A},
-\end{align}
-respectively. Here, 
-\begin{align}
-\hat{W}_k &=\frac{2\,{\cal I}}{\hat{a}\,\hat{r}_k}\left(\frac{q}{g\,s}\right)_{\hat{r}_k}^{1/2} |\hat{\mit\Psi}_k|^{\,1/2},\\[0.5ex]
-\hat{\delta}_k &= \frac{\delta_{\rm SC}(\hat{r}_k)}{R_0\,\hat{a}\,\hat{r}_k},
-\end{align}
-where $\delta_{\rm SC}(\hat{r})$ is the semi-collisional linear layer width specified in Ref.~\onlinecite{rf1}.
-
-In the previous expressions, $R_0$ is the major radius of the magnetic axis, $r$ is a magnetic flux-surface label with dimensions of length (which, roughly speaking, is the average minor radius of the
-flux-surface), $q(r)$ is the safety-factor profile, $s(r)=d\ln q/d\ln r$, 
-$g(r)\,B_0$ is the toroidal magnetic field-strength at major radius $R_0$, $B_0$ is the vacuum
-toroidal magnetic field-strength on the magnetic axis, $a$ is the value of $r$ on the last closed magnetic flux-surface, $r_k$ is the value of $r$ on the $k$th rational
-surface (resonant with poloidal mode number $m_k$, and toroidal mode number $n$), $\hat{a}=a/R_0$, $\hat{r}=r/a$, and $\hat{r}_k=r_k/a$. 
-Furthermore, $\tau_R(\hat{r})= \mu_0\,r^{\,2}\,\sigma_{ee}\,Q_{00}^{\,ee}$, where $\sigma_{ee}$ is the classical plasma parallel electrical conductivity, and
-$Q_{00}^{\,ee}$ describes the corrections to this conductivity due to neoclassical effects and the presence of plasma impurities. Also, $\tau_A$ is a convenient
-scale time, and $\hat{t}=t/\tau_A$. Finally, ${\mit\Psi}_k = B_0\,R_0\,\hat{\mit\Psi}_k\,{\rm e}^{-{\rm i}\,\varphi_k}$ is the reconnected magnetic flux
-at the $k$th rational surface, ${\mit\chi}_k = B_0\,R_0\,\hat{\mit\chi}_k\,{\rm e}^{-{\rm i}\,\zeta_k}$ is a measure of the vacuum magnetic flux at the $k$th
-rational surface (in fact, $\hat{E}_{kk}\,\chi_k$ is equivalent to $E_{sv}\,{\mit\Psi}_v$ in Sect.~\ref{s2}), and $E_{kk'} =\hat{E}_{kk'}\,{\rm e}^{-{\rm i}\,\xi_{kk'}}$ is the toroidal tearing stability matrix.\cite{am1} Here, $\hat{\mit\Psi}_k>0$, $\varphi_k$, $\hat{\chi}_k>0$,
-$\zeta_k$, $\hat{E}_{kk'}>0$, and $\xi_{kk'}$ are all real quantities.
-
-Equation~(\ref{e15}) represents a {\em minor}\/ improvement to Eq.~(D1) of Ref.~\onlinecite{rftor} in which the interpolation between the
-linear and nonlinear regimes is performed in a slightly more accurate manner.
-
-Equation~(D6) of Ref.~\onlinecite{rftor} is modified such that
-\begin{align}\label{e19}
-\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{d\varphi_k}{d\hat{t}}-\hat{\varpi}_k\right)&=
-- \sum_{k'=1,K}\hat{E}_{kk'}\,\hat{\mit\Psi}_{k'}\,\sin(\varphi_k-\varphi_{k'}-\xi_{kk'})-\hat{E}_{kk}\,\hat{\chi}_k\,\sin(\varphi_k-\zeta_k),
-\end{align}
-where
-\begin{equation}
-\hat{\varpi}_k= \hat{\varpi}_{k\,0}+m_k\,{\mit\Delta}\hat{\mit\Omega}_\theta(\hat{r}_k,\hat{t})-n\,{\mit\Delta}\hat{\mit\Omega}_\phi(\hat{r}_k,\hat{t}),
-\end{equation}
-and $\hat{\varpi}_{k\,0}= \varpi_{k\,0}\,\tau_A$, $\hat{\mit\Omega}_\theta= {\mit\Delta}{\mit\Omega}_\theta\,\tau_A$, and $\hat{\mit\Omega}_\phi= {\mit\Delta}{\mit\Omega}_\phi\,\tau_A$.
-Here, $\varpi_{k\,0}$
-is the so-called ``natural frequency''  (in the absence of the RMP) at the $k$th rational surface; this quantity is defined as the helical phase velocity of a naturally unstable island chain, resonant at the surface, in the
-absence of an RMP (or any other island chains). On the other hand,  ${\mit\Delta}{\mit\Omega}_\theta$ and ${\mit\Delta}{\mit\Omega}_\phi$ are the changes in the plasma
-poloidal and toroidal velocity profiles, respectively, induced by the electromagnetic torques that develop in the vicinities of the various rational surfaces in the plasma in response to the RMP.
-
-Equation~(\ref{e19}) represents
-a {\em major}\/ improvement to Eq.~(D6) of Ref.~\onlinecite{rftor} that takes into  account the finite slip-frequencies of the magnetic island chains induced at
-the various rational surfaces in the plasma. In the absence of a finite slip-frequency, the right-hand side of Eq.~(\ref{e19}) would be zero.
-
-If we define $X_k = \hat{\mit\Psi}_k\,\cos\varphi_k$ and $Y_k=\hat{\mit\Psi}_k\,\sin\varphi_k$ then Eqs.~(\ref{e15}) and (\ref{e19}) are
-more conveniently written in the non-singular (when $\hat{\mit\Psi}_k=0$) forms
-\begin{align}\label{e21}
-\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{dX_k}{d\hat{t}} 
-+\hat{\varpi}_k\,Y_k\right)= \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,X_{k'}  -\sin\xi_{kk'}\,Y_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\cos\zeta_k,\\[0.5ex]
-\left(\hat{W}_k +\hat{\delta}_k\right){\cal S}_k\left(\frac{dY_k}{d\hat{t}} -\hat{\varpi}_k\,X_k\right)
-= \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,Y_{k'}
-+\sin\xi_{kk'}\,X_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\sin\zeta_k,\label{e22}
-\end{align}
-where
-\begin{equation}\label{e23}
-\hat{W}_k =\frac{2\,{\cal I}}{\hat{a}\,\hat{r}_k}\left(\frac{q}{g\,s}\right)^{1/2}_{\hat{r}_k} (X_k^{\,2} + Y_k^{\,2})^{\,1/4}.
-\end{equation}
-Equationsv (\ref{e21}), (\ref{e22}) and (\ref{e23}) are the toroidal generalizations of Eqs.~(\ref{e11}), (\ref{e12}), and (\ref{e23x}), respectively.
-
-\section{{\tt EPEC} Modeling of DIII-D Discharge \#145380}\label{s4}
-\subsection{Introduction}
-DIII-D discharge \#145380 is an ITER-Similar-Shape (ISS), ELMing, H-mode discharge in which the
-plasma current is slowly ramped in order to scan the magnetic safety-factor.\cite{d3d,d3d2} This discharge is described in more detail in Sect.~III.B of Ref.~\onlinecite{rftor1}.
-A static RMP is applied to the plasma by running steady $n=3$ currents through the I-coil system.\cite{icoil}
-Three windows of ELM suppression  are evident: the first occurs when $t\simeq 2900$ ms and $q_{95}\simeq 3.91$; the
-second occurs when $t=3400$ ms and $q_{95}\simeq 3.66$; and the third occurs when $t\simeq 4000$ ms and $q_{95}\simeq 3.41$.  Here, $q_{95}$ is the safety-factor at the 95\% flux-surface.
-
-\subsection{Relaxation of No-Slip Constraint}\label{s4a}
-As is discussed in Ref.~\onlinecite{rftor1}, the best agreement between the predictions of the {\tt EPEC} code and experimental observations is
-obtained by assuming that the unperturbed natural frequencies at the various rational surfaces in the plasma are determined by the
-local equilibrium ${\bf E}\times {\bf B}$ frequencies. In other words, 
-\begin{equation}\label{e24}
-\varpi_{k\,0} =-n\,\omega_E({\mit\Psi}_{p\,k}),
-\end{equation}
-where 
-$\omega_E({\mit\Psi}_p) = -d{\mit\Phi}/d{\mit\Psi}_p$.
-Here, ${\mit\Phi}({\mit\Psi}_p)$ is the equilibrium scalar electric potential (in the absence of the RMP), ${\mit\Psi}_p$ the equilibrium poloidal magnetic flux (divided by $2\pi$), 
-and ${\mit\Psi}_{p\,k}$  the value of ${\mit\Psi}_p$ at the $k$th rational surface.  Equation~(\ref{e24}) holds at
-every rational surface in all of the simulations discussed in Sect.~\ref{s4a}.
-
-\subsubsection{No-Slip Constraint Imposed}
-In our first simulation, the no-slip constraint is imposed at all rational surfaces in the plasma. This implies that the resonant response
-model at the $k$th rational surface consists of Eq.~(\ref{e15}) and Eq.~(\ref{e19}), with the right-hand side of the latter equation
-set to zero; in other words,  the slip-frequency is set to zero at the $k$th rational surface.
-
-The upper panel of Fig.~\ref{fig2} shows the natural frequencies, in the absence of the RMP, of the various  $n=3$ tearing modes 
- that are resonant in the pedestal of DIII-D discharge \#145380, whereas  
-  the lower panel of Fig.~\ref{fig2} shows the same frequencies  in the presence of the RMP.
-   It is apparent that if the magnitude of the natural frequency in the absence of the RMP falls below about
-$3\,{\rm krad/s}$ then the associated tearing mode locks to the RMP (i.e., its true natural frequency becomes zero).
-
-The upper panel of Fig.~\ref{fig3} shows the widths of the various  magnetic island chains driven by the applied $n=3$ RMP in the
-absence of shielding due to plasma flow, whereas the lower panel
-shows the same widths in the presence of shielding. It is apparent 
-that the predicted island widths are generally much smaller than the ``vacuum'' island widths (i.e., the widths in the absence of shielding), as a consequence of the shielding of driven magnetic
-reconnection by plasma flow. However, this shielding breaks down at various rational surfaces when the associated natural frequency is zero (see the lower panel of
-Fig.~\ref{fig3}). In this situation, the driven island width is similar to the vacuum island width.
-
-According to the prevailing hypothesis, RMP-induced ELM mitigation/suppression in an H-mode tokamak discharge occurs when a comparatively wide, locked, magnetic
-island chain is generated at the top of the pedestal.\cite{hu} The temperature and density flattening associated with the chain
-is presumed to limit the radial expansion of the
-pedestal, and, thereby, prevent it from attaining a width sufficient to destabilize peeling-ballooning modes\,\cite{connor}  (which are thought to trigger ELMs).\cite{d3d}
-
-According to Fig.~\ref{fig3},  
- the comparatively wide, $m=11$ (brown),  $m=10$ (magenta), and  $m=9$ (cyan), locked magnetic island chains which are predicted to be driven by the RMP in the pedestal of DIII-D discharge \#145380 line up
-fairly well with the first, second, and third, ELM-suppression windows, respectively. To be more exact, the island chains are located at
-the top of the pedestal (i.e., ${\mit\Psi}_N=0.925$), and also occur in roughly the correct time intervals. This is consistent with the hypothesis that the formation of locked
-magnetic island chains at the top of the pedestal causes ELM mitigation/suppression.
-
-In principle, the calculation shown in Figs.~\ref{fig2} and \ref{fig3} is a repeat of one performed in Ref.~\onlinecite{rftor1}. In practice, there is a slight difference between
-the two calculations because the expression for the linear layer width used in Eq.~(D1) of Ref.~\onlinecite{rftor} (which specifies the island width evolution
-equation employed in Ref.~\onlinecite{rftor1}), which was only intended to be approximate,  is slightly inaccurate [because it contains a spurious factor of ($2\,{\cal I}/\hat{a})\,(q/g\,s)^{1/2}_{\hat{r}_k}$].
-This accounts for the very minor differences between Figs.~\ref{fig2} and \ref{fig3} in this
-paper, and Figs.~8 and 9 in Ref.~\onlinecite{rftor1}.
-
-\subsubsection{No-Slip Constraint Relaxed}
-In our second simulation, the no-slip constraint is relaxed at all rational surfaces in the plasma. This implies that the resonant response
-model at the $k$th rational surface consists of Eqs.~(\ref{e21}) and (\ref{e22}). Figures~\ref{fig4} and \ref{fig5} show analogous 
-data to Figs.~\ref{fig2} and \ref{fig3}, respectively. Figure~\ref{fig6} shows details of the bottom panels of Figs.~\ref{fig2} and \ref{fig4},
-in order to better illustrate the island chain dynamics when the  RMP-modified natural frequencies of the various $n=3$ tearing modes in  plasma
-are comparatively small.
-
-A comparison of Figs.~\ref{fig2} and \ref{fig4}, as well as an examination of Fig.~\ref{fig6}, reveals that the relaxation of the
-no-slip constraint facilitates the locking of magnetic island chains to the RMP to a relatively modest degree. (Here, by locking, we mean a reduction in the
-RMP-modified natural frequency to a value close to zero.) 
-This is not surprising, because 
-relaxation of the no-slip constraint clearly weakens the coupling between a given magnetic island chain and the local plasma flow (which is ultimately responsible
-for the shielding of driven magnetic reconnection). 
-It can be seen from Fig.~\ref{fig6} that if the no-slip constraint is imposed then the RMP-modified natural frequencies of locked magnetic
-island chains are exactly zero. On the other hand, if the no-slip constraint is relaxed then locked magnetic island chains possess
- small but finite RMP-modified natural frequencies, because the local plasma flow is able to slip through the  stationary chains to some
- extent. However, the degree of slippage for a fully developed locked magnetic island chain is comparatively small (i.e., no more than
- $0.5\,{\rm krad/s}$), which helps explain
- why the no-slip constraint can be used to accurately predict the dynamics of wide magnetic island chains in tokamaks and reversed field pinches.\cite{rfp}
-
-It is remarkable that the results shown in Figs.~\ref{fig2}--\ref{fig4} are so similar, given that the relaxation of the no-slip constraint leads to a
-{\em radical}\/ modification of the dynamics of non-locked magnetic island chains. When the no-slip constraint is imposed, the widths of magnetic island chains that are
-unable to lock to the RMP are forced to pulsate, periodically falling to zero, because the helical phases of the chains are forced to
-continuously increase (or decrease) by their non-zero natural frequencies.\cite{rfb,rfc,rf1,pulse} On the other hand, when the no-slip
-constraint is relaxed, the widths of magnetic island chains that are unable to lock to the RMP have steady values, because the  chains can
-slip with respect to the local plasma flow, which means that they can have fixed helical phases despite the fact that their natural
-frequencies are non-zero.
-
-\subsection{Improved Interpolation between Linear and Nonlinear Resonant Response Regimes}\label{s4b}
-According to linear tearing mode theory, in the absence of the RMP, the natural frequency of the tearing mode resonant at the $k$th rational surface is given by\,\cite{ara,lin1,lin2,lin3}
-\begin{equation}\label{elin}
-\varpi_{k\,0} = \varpi_{{\rm ln}\,k} \equiv - n\,(\omega_E+\omega_{\ast\,e})_{{\mit\Psi}_{p\,k}},
-\end{equation}
-where
-$\omega_{\ast\,e}({\mit\Psi}_p)=(T_e/e)\,d\ln p_e/d{\mit\Psi}_p$.
- Here,  $e$ is the magnitude of the electron charge,  $p_e({\mit\Psi}_p)$  the equilibrium (i.e., in the absence of the RMP)
-electron pressure, and $T_e({\mit\Psi}_p)$ the equilibrium
-electron temperature.
-
-According to nonlinear tearing mode theory, in the absence of the RMP, 
-the natural frequency of the tearing mode resonant at the $k$th rational surface is given by\,\cite{rftor}
-\begin{equation}
-\varpi_{k\,0} = \varpi_{{\rm nl}\,k}\equiv  -n\left(\omega_E +\left[1-L_{00}^{\,ii}+L_{01}^{\,ii}\left(\frac{\eta_i}{1+\eta_i}\right)\right]
-\omega_{\ast\,i}
--\left[L_{00}^{\,iI}- L_{01}^{\,iI}\left(\frac{\eta_I}{1+\eta_I}\right)\right]\omega_{\ast\,I}\right)_{{\mit\Psi}_{p\,k}},
-\end{equation}
-where
-$\omega_{\ast\,a}({\mit\Psi}_p) =-(T_a/Z_a\,e)\,d\ln p_a/d{\mit\Psi}_p$,
-$\eta_a({\mit\Psi}_p)=d\ln T_a/d\ln n_a$,
-for $a=i, I$. 
-Here, $Z_i$, $n_i({\mit\Psi}_p)$, $T_i({\mit\Psi}_p)$, and $p_i({\mit\Psi}_p)=n_i\,T_i$   are the charge number, 
-equilibrium number density, 
-equilibrium temperature, and equilibrium pressure
-of the majority (thermal) ions, respectively,
-whereas  $Z_I$, $n_I$, $T_I$, $p_I = n_I\,T_I$
-are the corresponding quantities for the impurity ions.  
-Furthermore, $L_{00}^{ii}({\mit\Psi}_p)$, $L_{01}^{ii}({\mit\Psi}_p)$,  $L_{00}^{II}({\mit\Psi}_p)$, and $L_{01}^{II}({\mit\Psi}_p)$ are neoclassical parameters that are defined
-in Sect.~B of Ref.~\onlinecite{rftor}.
-
-Finally, the best agreement between theory and experiment is obtained by assuming that, in the absence of the RMP, the 
- natural frequency of the tearing mode resonant at the $k$th rational surface is given by Eq.~(\ref{e24}).\cite{rftor1,heyn}
-
-\subsubsection{Linear Calculation}
-For the sake of comparison, we shall first perform a purely linear calculation. Thus, the
-resonant plasma response model at the $k$th rational surface consists of Eqs.~(\ref{e21}) and (\ref{e22}), with
-$\hat{W}_k$ set to zero. Moreover, in the absence of the RMP, the natural frequency at the $k$th rational surface is specified by Eq.~(\ref{elin}).
-Figures~\ref{fig7} and \ref{fig8} show the natural frequencies in the absence, and in the presence, of the RMP, as well as the vacuum
-islands widths and the actual island widths.
-
-\subsubsection{Composite Linear/Nonlinear Calculation}
-In our composite linear/nonlinear calculation, the resonant plasma response model at the $k$th rational surface consists of Eqs.~(\ref{e21}) and (\ref{e22}).
-Moreover, in the absence of the RMP, the natural frequency at the $k$th rational surface is specified
-by 
-\begin{equation}\label{ecomp}
-\varpi_{k\,0} = \frac{\varpi_{{\rm ln}\,k} +(\varpi_{{\rm eb}\,k} -\varpi_{{\rm ln}\,k}-\varpi_{{\rm nl}\,k})\,x_k + \varpi_{{\rm nl}\,k}\,x_k^{\,2}}{1-x_k +x_k^{\,2}},
-\end{equation}
-where $x_k = \hat{W}_k/\hat{\delta}_k$.
-It follows that $\varpi_{k\,0}=\varpi_{{\rm ln}\,k}$ in the linear regime, $x_k\ll 1$;  $\varpi_{k\,0}=\varpi_{{\rm nl}\,k}$ in the nonlinear regime, $x_k\gg 1$;
-and $\varpi_{k\,0}=\varpi_{{\rm eb}\,k}$  when $x_k=1$.
-(Note that $\varpi_{{\rm eb}\,k}$ generally lies between $\varpi_{{\rm ln}\,k}$ and $\varpi_{{\rm nl}\,k}$.) Figures~\ref{fig9} and \ref{fig10} show the natural frequencies in the absence, and in the presence, of the RMP, as well as the vacuum
-islands widths and the actual island widths.
-
-It can be seen, by a comparison of Figs.~\ref{fig7}--\ref{fig10}, that the linear calculation very significantly overestimates how easy it is for magnetic
-island chains to lock to the RMP. The reason for this is that the linear slip-frequency is comparatively high, because the linear layer width is
-comparatively narrow. The true slip-frequency becomes less than the linear slip-frequency as soon as the island width exceeds the
-linear layer width. The fact that the linear calculation is highly inaccurate confirms the conclusion reached in Ref.~\onlinecite{rf1}
-that the response of a typical H-mode tokamak plasma to an RMP is not governed by linear theory, because the driven
-island widths exceed the very narrow linear layer widths, even when driven reconnection is strongly suppressed by plasma flow.
-
-Intriguingly, the composite linear/nonlinear model fairly accurately predicts the temporal extends of the three ELM mitigation/suppression windows (assuming that the
-windows correspond to the formation of wide locked magnetic island chains at the top of the pedestal). 
-However, the windows do not occur in the correct time intervals. We conclude that Eq.~(\ref{e24}) gives a more accurate prediction for the
-natural frequencies, in the absence of the RMP, than Eq.~(\ref{ecomp}). However, the reason for this is, as yet, unclear.
-
-\section{Summary}
-We have developed an improved resonant plasma response model that describes the interaction between a tokamak plasma and an RMP. 
-The model interpolates between the linear and the nonlinear response regimes, and takes into account the fact that the slip-frequency
-is non-zero in the nonlinear regime. Our improved model has been incorporated into the {\tt EPEC} toroidal asymptotic matching code.\cite{rftor1}
-The modified {\tt EPEC} code is used to model RMP-induced ELM mitigation/suppression in DIII-D H-mode discharge \#145380.
-
-We find that allowing for a finite slip-frequency (i.e., relaxing the so-called no-slip constraint) slightly facilitates the locking of
-driven magnetic island chains to the RMP. (Here, by locking, we mean the reduction of the true natural frequency of a given chain to
-a value that is very close to zero.) In fact, there is surprisingly little difference between {\tt EPEC} simulations that impose the
-no-slip constraint at the various rational surfaces in the plasma and those in which the constraint is relaxed. This is true despite
-the fact that the nature of non-locked island solutions is {\em radically}\/ different in the two cases (in the first case, the widths of the island
-chains driven at the rational surfaces pulsate, in the second they remain steady).
-
-Our calculations  confirm the conclusion reached in Ref.~\onlinecite{rf1}
-that the response of a typical H-mode tokamak plasma to an RMP cannot be accurately modeled by linear theory. Our calculations also
-confirm the conclusion reached in Ref.~\onlinecite{rftor1} that the best agreement between theory and observations is obtained by assuming that the
-natural frequencies of tearing modes, in the absence of the RMP, are determined by the local ${\bf E}\times{\bf B}$ frequency.
-
 \section*{Acknowledgements}
-This research was directly funded by the U.S.\ Department of Energy, Office of Science, Office of Fusion Energy Sciences,  under contract DE-FG02-04ER54742, and
-incorporates work funded by the U.S.\ Department of Energy, Office of Science, Office of Fusion Energy Sciences, using the DIII-D National Fusion Facility, a DOE Office of Science user facility, under contract DE-FC02-04ER54698.
-
-\section*{Disclaimer} This report was prepared as an account of work sponsored by an agency of the United States Government.
-Neither the United States Government nor any agency thereof, nor any of their employees, makes any warranty, express or implied, or assumes any legal liability or responsibility for the accuracy, completeness, or usefulness of any information, apparatus, product, or process disclosed, or represents that its use would not infringe privately owned rights.
-Reference herein to any specific commercial product, process, or service by trade name, trademark, manufacturer, or otherwise does not necessarily constitute or imply its endorsement, recommendation, or favoring by the United States Government or any agency thereof.
-The views and opinions of authors expressed herein do not necessarily state or reflect those of the United States Government or any agency thereof.
-
-\section*{Data Availability Statement}
-The data that support the findings of this study are available from the corresponding author upon reasonable request.
+This research was directly funded by the U.S.\ Department of Energy, Office of Science, Office of Fusion Energy Sciences,  under contract DE-FG02-04ER54742,
 
@@
 \bibitem{error1} J.T.~Scoville, and R.J.~La\,Haye, Nucl.\ Fusion {\bf 43}, 250 (2003).
-
-\bibitem{error2}  J.-K.~Park, M.J.~Schaffer, J.E.~Menard, and A.H.~Boozer  Phys.\  Rev.\  Lett.\  {\bf 99}, 195003 (2007).
-
-\bibitem{error3} N.M.~Ferraro, J.-K.~Park, C.E.~Myers, A.~Brooks, S.P.~Gerhardt, J.E.~Menard, S.~Munaretto, and M.L.~Reinke, Nucl.\ Fusion {\bf 59}, 086021 (2019).
-
-\bibitem{elm1}  T.E.~Evans, R.A.~Moyer, J.G.~Watkins, P.R.~Thomas, T.H.~Osborne, J.A.~Boedo, M.E.~Fenstermacher, K.H.~Finken, R.J.~Groebner, M.~Groth, {\it et al.},  
-Phys.\ Rev.\ Lett.\ {\bf 92}, 235003 (2004).
-
-\bibitem{elm2} Y.~Liang,  H.R.~Koslowski, P.R.~Thomas, E.~Nardon, B.~Alper, P.~Andrew, Y.~Andrew, G.~Arnoux,  Y.~Baranov, M.~B\'{e}coulet, {\it et al.},  
-Phys.\ Rev.\ Lett.\ {\bf 98}, 265004 (2007).
-
-\bibitem{elm3} W.~Suttrop,  T.~Eich, J.C.~Fuchs, S.~G\"{u}nter, A.~Janzer, A.~Herrmann, A.~Kallenbach, P.T.~Lang, T.~Lunt, M.~Maraschek, {\it et al.},   
-Phys.\ Rev.\ Lett.\ {\bf 106}, 225004 (2011).
-
-\bibitem{elm4} Y.M.~Jeon,  J.-K.~Park, S.W.~Yoon, W.H.~Ko, S.G.~Lee, K.D.~Lee, G.S.~Yun, Y.U.~Nam, W.C.~Kim, J.-G.~Kwak, K.S.~Lee, H.K.~Kim, and H.L.~Yang, {\it et al.}, 
-Phys.\ Rev.\ Lett.\ {\bf 109}, 035004 (2012).
-
-\bibitem{elm5} A.~Kirk, I.T.~Chapman, Y.~Liu, P.~Cahyna, P.~Denner, G.~Fishpool, C.J.~Ham, J.R.~Harrison, Y.~Liang, E.~Nardon, S.~Saarelma, R.~Scannell, A.J.~Thornton, and  MAST Team, 
-Nucl.\  Fusion {\bf 53}, 043007 (2013).
-
-\bibitem{elm6} T.~Sun,  Y.~Liang, Y.Q.~Liu, S.~Gu, X.~Yang, W.~Guo, T.~Shi, M.~Jia, L.~Wang, B.~Lyu, {\it et al.},  
-Phys.\ Rev.\ Lett.\  {\bf 117}, 115001 (2016).
-
-\bibitem{fkr} H.P.~Furth,  J.~Killeen, and M.N.~Rosenbluth,  Phys.\ Fluids {\bf 6}, 459 (1963).
-
-\bibitem{coppi} B.~Coppi, J.M.~Greene, and J.L.~Johnson, Nucl.\ Fusion {\bf 6}, 101 (1966).
-
-\bibitem{ruth} P.H.~Rutherford,  Phys.\ Fluids  {\bf 16}, 1903 (1973).
-
-\bibitem{ara} G.~Ara,  B.~Basu, B.~Coppi, G.~Laval, M.N.~Rosenbluth, and B.V.~Waddell, Ann.\ Phys.\ (N.Y.) {\bf 112}, 443 (1978).
-
-\bibitem{pletz} A.~Pletzer, and R.L.~Dewar, J.\ Plasma Physics {\bf 45}, 427 (1991).
-
-\bibitem{rfa} R.~Fitzpatrick, Nucl.\ Fusion {\bf 33}, 1049 (1993).
-
-\bibitem{am1} R.~Fitzpatrick, R.J.~Hastie, T.J.~Martin, and C.M.~Roach, Nucl.\ Fusion {\bf 33}, 1533 (1993).
-
-\bibitem{tokuda} S.~Tokuda, Nucl.\ Fusion {\bf 41}, 1037 (2001).
-
-\bibitem{brennan} D.P.~Brennan, R.J.~La Haye, A.D.~Turnbull, M.S.~Chu, T.H.~Jensen, L.L.~Lao, T.C.~Luce, P.A.~Politzer, and E.J.~Strait,
-Phys.\ Plasmas {\bf 10}, 1643 (2003).
-
-\bibitem{am2} A.H.~Glasser, Z.R.~Wang, and J.-K.~Park, Phys.\ Plasmas {\bf 23}, 112506 (2016).
-
-\bibitem{am3} R.~Fitzpatrick, Phys.\ Plasmas {\bf 24}, 072506 (2017).
-
-\bibitem{ruth1} P.H.~Rutherford, in  {\it Basic Physical Processes of
-Toroidal Fusion Plasmas}, Proc.\ Course and Workshop, Varenna, 1985. (Commission of the European Communities, Brussels, 1985.) Vol.~2, p.~531.
-
-\bibitem{slip1} L.G.~Eliseev, N.V.~Ivanov, A.M.~Kakurin, A.V.~Melnikov, and S.V.~Perfilov, Phys.\ Plasmas {\bf 22}, 052504 (2015).
-
-\bibitem{slip2} W.~Huang, and P.~Zhu, Phys.\ Plasmas {\bf 27}, 022514 (2020).
-
-\bibitem{rftor} R.~Fitzpatrick, and A.O.~Nelson, Phys.\ Plasmas {\bf 27}, 072501 (2020).
-
-\bibitem{rftor1} R.~Fitzpatrick,  Phys.\ Plasmas {\bf 27}, 102511 (2020).
-
-\bibitem{rfb} R.~Fitzpatrick, Phys.\ Plasmas {\bf 5}, 3325 (1998).
-
-\bibitem{rfc} R.~Fitzpatrick, Phys.\ Plasmas {\bf 21}, 092513 (2014).
-
-\bibitem{rf1} R.~Fitzpatrick, Phys.\ Plasmas {\bf 27}, 042506 (2020).
-
-\bibitem{rffig} R.~Fitzpatrick, Phys.\ Plasmas {\bf 10}, 2304 (2003).
-
-%\bibitem{rfisland} R.~Fitzpatrick, Phys.\ Plasmas {\bf 25}, 082513 (2018).
-
-\bibitem{slip3} A.N.~Chudnovskiy, Y.V.~Gvozdkov, N.V.~Ivanov, A.M.~Kakurin,
-A.A.~Medvedev, I.I.~Orlovskiy, Y.D.~Pavlov, V.V.~Piterskiy, V.D.~Pustovitov,
-M.B.~Safonova, V.V.~Volkov, and the T-10 Team, Nucl.\ Fusion {\bf 43} 681 (2003).
-
-\bibitem{d3d} P.B.~Snyder, T.H.~Osboune, K.H.~Burrell, R.J.~Groebner, A.W.~Leonard, R.~Nazikian, D.M.~Orlov, O.~Schmitz, M.R.~Wade, and H.R.~Wilson, 
- Phys.\ Plasmas {\bf 19}, 056115 (2012).
-
-\bibitem{d3d2} Q.M.~Hu, R.~Nazikian, B.A.~Grierson, N.C.~Logan, D.M.~Orlov, C.~Paz-Solden, and Q.~Yu, 
-Phys.\ Rev.\ Lett.\ {\bf 125}, 045001 (2020).
-
-\bibitem{icoil} G.L.~Jackson, P.M.~Anderson, J.~Bialek, W.P.~Cary, G.L.~Campbell, A.M.~Garofalo,  R.~Hatcher, A.G.~Kellman, R.J.~La\,Haye, A.~Nagy, {\em et al.},  
-Proc.\ 30th EPS Conf.\ on Controlled Fusion and Plasma Physics. (St.\ Petersburg, Russia, 2003) CD-ROM, P-4.47.
-
-\bibitem{hu} Q.M.~Hu,  R.~Nazikian,  B.A.~Grierson,  N.C.~Logan,  J.-K.~Park,  C.~Paz-Soldan, and Q.~Yu, Phys.\ Plasmas {\bf 26}, 120702 (2019).
-
-%\bibitem{flat} R.~Fitzpatrick, Phys.\ Plasmas {\bf 2}, 825 (1995).
-
-\bibitem{connor} J.W.~Connor,  R.J.~Hastie, H.R.~Wilson, and R.L.~Miller, Phys.\ Plasmas  {\bf 5}, 2687 (1998).
-
-\bibitem{rfp} B.E.~Chapman, R.~Fitzpatrick, D.~Craig, P.~Martin, and G.~Spizzo, Phys.\ Plasmas {\bf 11}, 2156 (2004).
-
-\bibitem{pulse} R.~Fitzpatrick, Phys.\ Plasmas {\bf 25}, 112505 (2018).
-
-\bibitem{lin1} M.~B\'{e}coulet, F.~Orain, P.~Maget, N.~Mellet, X.~Garbet, E.~Nardon, G.T.A.~Huysmans, T.~Caspar, A.~Loarte,  P.~Cayna, {\em et al.}, 
-Nucl.\ Fusion {\bf 52}, 054003  (2012).
-
-\bibitem{lin2} N.M.~Ferraro, Phys.\ Plasmas {\bf 19}, 056105  (2012).
-
-\bibitem{lin3} F.~Orain, M.~B\'{e}coulet, G.~Dif-Pradalier, G.T.A.~Huysmans, S.~Pamela,   E.~Nardon, C.~Passeron, G.~Latu, V.~Grandgirard, A.~Fil, {\em et al.}, 
-Phys.\ Plasmas {\bf 20}, 102510 (2013).
-
-\bibitem{heyn} M.F.~Heyn, I.B.~Ivanov, S.V.~Kasilov, W.~Kernbichler, I.~Joseph, R.A.~Moyer,  and A.M.~Runov, Nucl.\ Fusion {\bf 48}, 024005 (2008).
-
 \end{thebibliography}
 
-\newpage
-
 %\begin{figure}
-%\includegraphics[height=5in]{fig1.pdf}
-%\caption{Overview of DIII-D discharge \#145380.
-%(a) Safety factor at  ${\mit\Psi}_N=0.95$. 
-%(b) $D_\alpha$ (i.e., Deuterium Balmer-alpha) signal, as well as $n=3$ current flowing in upper and lower sections of I-coil. 
-%(c) Pedestal (i.e., ${\mit\Psi}_N=0.94$)
-%electron pressure.
-(The red curve is the running average over 10 ms.) (d) Pedestal electron number density.
-The common vertical yellow bands indicate the ELM-suppression/mitigation windows.}\label{fig1}
+%\includegraphics[height=6in]{fig2.pdf}
+%\caption{}
 %\end{figure}
-
-\begin{figure}
-\includegraphics[height=6in]{fig2.pdf}
-\caption{Composite linear/nonlinear calculation with the no-slip constraint imposed at all rational surfaces, and the natural frequencies
-in the absence of the RMP determined by the local  ${\bf E}\times {\bf B}$
-frequency.
-Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
-in   DIII-D discharge \#145380. Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
-in   DIII-D discharge \#145380. The red, green, blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig2}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=6in]{fig3.pdf}
-\caption{Composite linear/nonlinear calculation with the no-slip constraint imposed at all rational surfaces, and the natural frequencies
-in the absence of the RMP determined by the local  ${\bf E}\times {\bf B}$
-frequency. Top Panel: Full  $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time 
-in   DIII-D discharge \#145380.
-Bottom Panel:  Full $n=3$ island widths as functions of time
-in   DIII-D discharge \#145380. The yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=8$, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression/mitigation windows. 
-The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig3}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=6in]{fig4.pdf}
-\caption{Composite linear/nonlinear calculation with the no-slip constraint relaxed at all rational surfaces, and the natural frequencies
-in the absence of the RMP determined by the local  ${\bf E}\times {\bf B}$
-frequency.
-Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
-in   DIII-D discharge \#145380.
-Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
-in   DIII-D discharge \#145380. The red, green, blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig4}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=6in]{fig5.pdf}
-\caption{Composite linear/nonlinear calculation with the no-slip constraint relaxed at all rational surfaces, and the natural frequencies
-in the absence of the RMP determined by the local  ${\bf E}\times {\bf B}$
-frequency. Top Panel: Full  $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time 
-in   DIII-D discharge \#145380.
-Bottom Panel:  Full $n=3$ island widths as functions of time
-in   DIII-D discharge \#145380. The yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=8$, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
-The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig5}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=6in]{fig6.pdf}
-\caption{Top Panel: Detail of the bottom panel of Fig.~\ref{fig2}. Bottom Panel: Detail of the bottom panel of Fig.~\ref{fig4}. } \label{fig6}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=6in]{fig7.pdf}
-\caption{Linear calculation with the no-slip constraint relaxed at all rational surfaces, and  the natural frequencies
-in the absence of the RMP determined by linear theory. 
- Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
-in   DIII-D discharge \#145380.
-Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
-in   DIII-D discharge \#145380. The red, green, blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig7}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=6in]{fig8.pdf}
-\caption{Linear calculation with the no-slip constraint relaxed at all rational surfaces, and  the natural frequencies
-in the absence of the RMP determined by linear theory. Top Panel: Full  $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time 
-in   DIII-D discharge \#145380.
-Bottom Panel:  Full $n=3$ island widths as functions of time
-in   DIII-D discharge \#145380. The yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=8$, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
-The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig8}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=6in]{fig9.pdf}
-\caption{Composite linear/nonlinear calculation with the no-slip constraint relaxed at all rational surfaces, and  the natural frequencies
-in the absence of the RMP determined by composite linear/nonlinear theory. Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
-in   DIII-D discharge \#145380.
-Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
-in   DIII-D discharge \#145380. The red, green, blue, yellow, cyan, magenta, brown, pink,
-purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig9}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=6in]{fig10.pdf}
-\caption{Composite linear/nonlinear calculation with the no-slip constraint relaxed at all rational surfaces, and  the natural frequencies
-in the absence of the RMP determined by composite linear/nonlinear theory. Top Panel: Full  $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time 
-in   DIII-D discharge \#145380.
-Bottom Panel:  Full $n=3$ island widths as functions of time
-in   DIII-D discharge \#145380. The yellow, cyan, magenta, brown, pink,
-purple, and orange  areas correspond to $m=8$, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
-The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig10}
-\end{figure}
 \end{document}

### 2021-12-06 Research/LinearTearingModeTheory/LinearTearingModeTheory.tex
Started linear paper

@@
 
+\section{Introduction}
+Tearing modes are slowly growing instabilities of ideally-stable tokamak plasmas that reconnect magnetic field-lines
+at various resonant surfaces within the plasma, in the process degrading the plasma confinement.\cite{wes}
+If tearing modes gorw to sufficiently large amplitude then they can trigger major disruptions.\cite{wes1}  Tokamak
+plasma are observed to be particularly disruption prone when tearing modes {\em lock}\/ (i.e., become stationary in the
+laboratory frame) to externally generated, resonant magnetic perturbations.\cite{vries}
+
+It is well known that single-fluid resistive magnetohydrodynamics (MHD) offers a very poor description of
+tearing mode dynamics in tokamak plasmas. 
+For instance, the strong {\em diamagnetic}\/ flows present in such plasmas decouple the electron and ion fluid dynamics,
+necessitating a two-fluid treatment.\cite{ara} Moreover, resistive-MHD does not take  the important {\em ion sound radius lengthscale}, below which electron and ion dynamics are further decoupled, 
+into account.\cite{drake,wal} Previously, Cole \& Fitzpatrick\,\cite{cole} used the four-field model
+of Fitzpatrick \& Waelbroeck\,\cite{fw} (which is based on the original four-field model of Hazeltine, et al.\cite{haz}),
+to determine the two-fluid response of a linear tearing layer in a tokamak plasma to an externally generated, 
+resonant magnetic perturbation. However, the treatment of Cole \& Fitzpatrick failed to take into account the
+strong anomalous perpendicular transport of particles and energy present in tokamak plasmas. The
+aim of this paper is to correct this deficiency.
+
+\section{Four-Field Model}
+
 \section*{Acknowledgements}
-This research was directly funded by the U.S.\ Department of Energy, Office of Science, Office of Fusion Energy Sciences,  under contract DE-FG02-04ER54742,
+This research was directly funded by the U.S.\ Department of Energy, Office of Science, Office of Fusion Energy Sciences,  under  contracts DE-FG02-04ER54742 and DE-SC0021156.
 
@@
 
-\bibitem{error1} J.T.~Scoville, and R.J.~La\,Haye, Nucl.\ Fusion {\bf 43}, 250 (2003).
+\bibitem{wes} J.A.~Wesson, Nucl.\ Fusion {\bf 18}, 87 (1978).
+
+\bibitem{wes1} J.A.~Wesson, et al.\ Nucl.\ Fusion {\bf 29}, 641 (1989).
+
+\bibitem{vries} P.C. de Vries, et al.\ Nucl.\ Fusion {\bf 51}, 053018 (2011).
+
+\bibitem{ara} G.~Ara, B.~Basu, B.~Coppi, G.~Laval, M.N.~Rosenbluth, and B.V.~Waddell, Ann.\ Phys.\ (NY) {\bf 112}, 443 (1978).
+
+\bibitem{drake} J.F.~Drake, and Y.C.~Lee, Phys.\ Fluids {\bf 20}, 1341 (1977).
+
+\bibitem{wal} F.L.~Waelbroeck, Phys.\ Plasmas {\bf 10}, 4040 (2003).
+
+\bibitem{cole} A.~Cole, and R.~Fitzpatrick, Phys.\ Plasmas {\bf 13}, 032503 (2006).
+
+\bibitem{fw} R.~Fitzpatrick, and F.L.~Waelbroeck, Phys. Plasmas {\bf 12}, 022307 (2005).
+
+\bibitem{haz} R.D.~Hazeltine, M.~Kotschenreuther, and P.G.~Morrison, Phys.\ Fluids {\bf 28}, 2466 (1985).
+
 \end{thebibliography}

### 2021-12-11 Research/LinearTearingModeTheory/LinearTearingModeTheory.tex
Started writing linear and nonlinear papers

--- 2021-12-04 Research/LinearTearingModeTheory/LinearTearingModeTheory.tex
@@
 
-\title{Further drift-magnetohydrodynamic modeling of linear tearing mode dynamics in tokamak plasmas}
+\title{Influence of anomalous perpendicular transport on linear tearing mode dynamics in tokamak plasmas}
 
@@
 \begin{abstract}
-An improved 
+The analysis of a previous paper [A.~Cole, and R.~Fitzpatrick, Phys.\ Plasmas {\bf 13}, 032503 (2006)] that maps out all of the
+two-fluid response regimes of a  linear tearing layer interacting with an externally generated resonant magnetic perturbation, in a large aspect-ratio tokamak plasma,  is generalized to
+take into account realistic levels of perpendicular particle transport. A new response-regime map is obtained that differs substantially, in many
+respects, from the old one.
+The improved analysis is first employed to find all of the two-fluid growth-rate regimes of a non-interacting low-mode-number tearing mode in a large aspect-ratio tokamak plasma.
+The analysis is then used to determine the scaling of the error-field penetration threshold with machine
+parameters in large aspect-ratio, ohmically heated, tokamak plasmas . A number of penetration regimes are found in which the threshold scales as $n^{1/2}$, where $n$ is the line-averaged
+electron number density. A similar scaling has been reported in some experiments. 
 \end{abstract}
@@
 
+\section{Introduction}
+Tearing modes are slowly growing instabilities of ideally-stable tokamak plasmas that reconnect magnetic field-lines
+at various resonant surfaces within the plasma, in the process forming magnetic island chains that degrade the plasma confinement.\cite{wes}
+If tearing modes grow to sufficiently large amplitude then they can trigger major disruptions.\cite{wes1}  Tokamak
+plasmas are observed to be particularly disruption-prone when tearing modes {\em lock}\/ (i.e., become stationary in the
+laboratory frame) to externally generated, resonant magnetic perturbations.\cite{vries}
+
+It is well known that single-fluid, resistive magnetohydrodynamics (MHD) offers a very poor description of
+tearing mode dynamics in tokamak plasmas. 
+For instance, the strong {\em diamagnetic}\/ flows present in such plasmas decouple the electron and ion flows to some extent,
+necessitating a two-fluid treatment.\cite{ara} Moreover, resistive-MHD does not take  the important {\em ion sound radius lengthscale}, below which electron and ion dynamics are further decoupled, 
+into account.\cite{drake,wal} Previously, Cole \& Fitzpatrick\,\cite{cole} used the four-field model
+of Fitzpatrick \& Waelbroeck\,\cite{fw} (which is based on the original four-field model of Hazeltine, et al.\cite{haz}) 
+to determine the two-fluid response of a linear tearing layer to an externally generated, 
+resonant magnetic perturbation  in a large aspect-ratio tokamak plasma. However, the treatment of Cole \& Fitzpatrick fails to take into account the
+ anomalously large perpendicular  particle diffusivity  present in tokamak plasmas. The
+aim of this paper is to correct this deficiency.
+
+This paper is organized as follows. After some preliminary analysis in Sect.~\ref{sect1}, our fundamental four-field resonant
+plasma response model is introduced in Sect.~\ref{sfour}.
+This model is a slightly improved version of the model derived in Ref.~\onlinecite{fw} that takes the thermal force into account.
+The model is converted into a set of linear layer equations in
+Sect.~\ref{layer}. These layer equations are then solved in Sect.~\ref{linear} in order to map out all of the linear response regimes
+of a resonant layer to an externally generated resonant magnetic perturbation in a large aspect-ratio tokamak plasma. In Sect.~\ref{stab}, we reuse the analysis of Sect.~\ref{linear} to map out all
+of the growth-rate regimes for a low-mode-number (but not $m=1$) tearing mode in a large aspect-ratio tokamak plasma. Finally,
+in Sect.~\ref{error}, we employ the results of Sect.~\ref{linear} to determine the scaling of the error-field penetration threshold with machine parameters
+ in large aspect-ratio, ohmically heated, tokamak plasmas.
+
+\section{Preliminary Analysis}\label{sect1}
+\subsection{Plasma Equilibrium}
+Consider a large aspect-ratio tokamak plasma equilibrium whose magnetic flux-surfaces map out
+(almost) concentric circles in the poloidal plane. Such an equilibrium can be approximated as a
+periodic cylinder.\cite{rf1993} Let $r$, $\theta$, $z$ be right-handed cylindrical coordinates. 
+The magnetic axis corresponds to $r=0$, and the plasma boundary to $r=a$. The system is assumed to be periodic in the $z$
+direction with periodicity length $2\pi\,R_0$, where $R_0$ is the simulated major radius of the plasma. The
+safety-factor profile takes the form $q(r)=r\,B_z/[R_0\,B_\theta(r)]$, where $B_z$ is the constant
+`toroidal' magnetic field-strength, and $B_\theta(r)$ is the poloidal magnetic field-strength. The standard
+large aspect-ratio orderings, $r/R_0\ll 1$ and $B_\theta/B_z\ll 1$, are adopted.
+
+\subsection{Asymptotic Matching}\label{cyl}
+Consider a tearing mode perturbation that has $m$ periods in the poloidal direction, and
+$n$ periods in the toroidal direction. 
+As is well known, the response of the plasma to the tearing mode is
+governed by marginally stable, ideal-MHD everywhere in the plasma, apart from a (radially) narrow
+layer centered on the so-called {\em resonant surface}, minor radius $r_s$, at which $q(r_s)=m/n$.\cite{fkr}
+
+The perturbed magnetic field associated with the tearing mode is written $\delta{\bf B} \simeq \nabla\delta\psi\times{\bf e}_z$,  
+where
+$\delta\psi(r,\theta,\varphi,t)= \delta\psi(r,t)\,\exp[\,{\rm i}\,(m\,\theta-n\,\varphi)]$, 
+and $\varphi=z/R_0$ is a simulated toroidal angle.
+
+In the so-called {\em outer region}\/ (i.e., everywhere in the plasma
+apart from the resonant layer), the perturbed helical magnetic flux, $\delta\psi(r,t)$, satisfies the
+{\em cylindrical tearing mode equation}:\cite{wes}
+\begin{equation}\label{e3}
+\frac{\partial^2\delta\psi}{\partial r^2} + \frac{1}{r}\,\frac{\partial\delta\psi}{\partial r}-\frac{m^2}{r^2}\,\delta\psi - \frac{J_z'\,\delta\psi}{r\,(1/q-n/m)}=  0,
+\end{equation}
+where 
+$J_z(r)= R_0\,\mu_0\,j_z(r)/B_z$,
+and $j_z(r)$ is the equilibrium `toroidal' current density. Here, $'\equiv d/dr$. In general, the solution of Eq.~(\ref{e3}) that satisfies physical
+boundary conditions at the magnetic axis and the plasma boundary is such that $\delta\psi$ is continuous
+across the resonant surface, whereas $\partial\delta\psi/\partial r$ is discontinuous. The discontinuity of
+ $\partial\delta\psi/\partial r$ across the resonant surface is indicative of the presence of a helical current
+ sheet at the surface.  The complex quantity ${\mit\Psi}_s(t)= \delta\psi(r_s,t)$ determines the amplitude
+ and phase of the reconnected helical magnetic flux at the resonant surface, whereas the complex quantity\,\cite{rf1993}
+ \begin{equation}
+{\mit\Delta\Psi}_s = \left[r\,\frac{\partial \delta\psi}{\partial r}\right]_{r_{s-}}^{r_{s+}}
+\end{equation}
+parameterizes the amplitude and phase of the helical current sheet flowing at the surface. The solution of
+the cylindrical tearing mode equation in the outer region, in the presence of an externally generated, resonant magnetic perturbation 
+of the same helicity as the tearing mode, leads to the relation\,\cite{rf1993,fkr}
+\begin{equation}\label{e110}
+{\mit\Delta\Psi}_s= {\mit\Delta}_s'\,{\mit\Psi}_s + (-{\mit\Delta}_s')\,{\mit\Psi}_v,
+\end{equation}
+where ${\mit\Delta}_s'$ is a real dimensionless quantity known as the {\em tearing stability index}. Moreover,
+${\mit\Psi}_v$ is the so-called {\em vacuum flux}, and is defined as the reconnected magnetic flux
+that would be driven at the resonant surface by the resonant magnetic perturbation were the
+plasma intrinsically tearing stable (i.e., ${\mit\Delta}_s' <0$), and were there no current sheet at the resonant surface
+(i.e., ${\mit\Delta\Psi}_s=0$).
+
+The current sheet at the resonant surface can only be resolved by solving  a two-fluid, resistive-MHD, plasma response model
+in the so-called {\em inner region}\/ (i.e., the region of the plasma in the immediate vicinity of the resonant surface), 
+and asymptotically matching the solution so obtained to the ideal-MHD solution in the outer region. The particular 
+plasma response model used in this paper is
+described in the following section.
+
+\section{Four-Field Resonant Plasma Response Model}\label{sfour}
+\subsection{Useful Definitions}
+The plasma is assumed to consist of two species. First, electrons of mass $m_e$, electrical charge $-e$, 
+number density $n$, and temperature $T_e$.  Second, ions of mass $m_i$, electrical charge $+e$,  
+number density $n$, and temperature $T_i$. Let $p=n\,(T_e+T_i)$ be the total plasma pressure.
+
+It is helpful to define $n_0 = n(r_s)$, $p_0= p(r_s)$,
+\begin{align}
+\eta_e &=\left.\frac{d\ln T_e}{d\ln n}\right|_{r=r_s},\label{e211}\\[0.5ex]
+\eta_i &= \left.\frac{d\ln T_i}{d\ln n}\right|_{r=r_s},\\[0.5ex]
+\tau &= \left(\frac{T_e}{T_i}\right)_{r=r_s}\left(\frac{1+\eta_e}{1+\eta_i}\right),\label{e213}
+\end{align}
+where $n(r)$, $p(r)$, $T_e(r)$, and $T_i(r)$ refer to
+density, pressure, and temperature profiles that are unperturbed by the tearing mode.
+
+For the sake of simplicity, the perturbed electron and ion temperature profiles are assumed to be functions of
+the perturbed electron number density profile in the immediate vicinity of the resonant surface. In other words, $T_e=T_e(n)$ and $T_i=T_i(n)$. This
+implies that $p=p(n)$. 
+The {\em MHD velocity}, which is the velocity of a
+fictional MHD fluid, is defined ${\bf V}={\bf V}_E + V_{\parallel\,i}\,{\bf b}$, where ${\bf V}_E$ is the
+${\bf E}\times{\bf B}$ drift velocity, $V_{\parallel\,i}$ is the parallel component of the ion fluid
+velocity, ${\bf b}= {\bf B}/|{\bf B}|$, and ${\bf B}$ is the magnetic field-strength.
+
+\subsection{Fundamental Fields}
+The four fundamental fields in our four-field model---namely, $\psi$, $\phi$, $N$, and $V$---have the following
+definitions:
+\begin{align}\label{e10}
+\nabla\psi &= \frac{{\bf n}\times{\bf B}} {r_s\,B_z},\\[0.5ex]
+\nabla\phi &= \frac{{\bf n}\times {\bf V}}{r_s\,V_A},\\[0.5ex]
+N &=-\hat{d}_i\left(\frac{p-p_0}{B_z^{\,2}/\mu_0}\right),\\[0.5ex]
+V &= \hat{d}_i\left(\frac{{\bf n}\cdot {\bf V}}{V_A}\right).\label{e13}
+\end{align}
+Here,   ${\bf n} = (0,\,\epsilon/q_s,\,1)$, $\epsilon = r/R_0$, $q_s=m/n$, 
+$V_A =B_z/\sqrt{\mu_0\,n_0\,m_i}$, 
+$d_i = \sqrt{m_i/(n_0\,e^{\,2}\,\mu_0)}$,
+and $\hat{d}_i=d_i/r_s$. 
+ Our
+model also employs the auxiliary field
+\begin{align}\label{e16}
+J=-\frac{2\,\epsilon_s}{q_s}+\hat{\nabla}^2\psi,
+\end{align}
+where 
+$\epsilon_s=r_s/R_0$, and $\hat{\nabla} = r_s\,\nabla$.
+
+\subsection{Fundamental Equations}
+The four-field model takes the form:\cite{fw}
+\begin{align}
+\frac{\partial\psi}{\partial\hat{t}}&= [\phi,\psi] -\left(\frac{\tau}{1+\tau}\right)(1+\lambda_e)\,[N,\psi]
++\hat{\eta}_\parallel\,J + \hat{E}_\parallel,\\[0.5ex]
+\frac{\partial \hat{\nabla}^2\phi}{\partial \hat{t}}&= [\phi,\hat{\nabla}^2\phi] - \frac{1}{2\,(1+\tau)}\left(\hat{\nabla}^2[\phi,N] + [\hat{\nabla}^2\phi,N] + [\hat{\nabla}^2 N,\phi]\right) + [J,\psi] \nonumber\\[0.5ex]&\phantom{=}+\hat{\chi}_\varphi  \,\hat{\nabla}^4\!\left(\phi + \frac{N}{1+\tau}\right), \\[0.5ex]
+\frac{\partial N}{\partial \hat{t}}&= [\phi,N] +c_\beta^{\,2}\,[V,\hat{\psi}] +\hat{d}_\beta^{\,2}\,[J,\psi]
++ \hat{D}_\perp\,\hat{\nabla}_\perp^{\,2}N,\\[0.5ex]
+\frac{\partial V}{\partial\hat{t}}&= [\phi,V] +[N,\psi] + \hat{\chi}_\varphi\,\hat{\nabla}^2 V.\label{e21}
+\end{align}
+Here, $[A,B]\equiv \hat{\nabla} A\times \hat{\nabla} B\cdot {\bf n}$, $\hat{t} = t/(r_s/V_A)$, $\hat{\eta}_{\parallel,\perp} = \eta_{\parallel,\perp}/(\mu_0\,r_s\,V_A)$, $\hat{E}_\parallel = E_\parallel/(B_z\,V_A)$,
+$\hat{\chi}_\varphi= \chi_\varphi/(r_s\,V_A)$, where $\eta_{\parallel,\perp}$ is the parallel/perpendicular plasma electrical
+resistivity at the resonant surface, $E_\parallel$ the parallel inductive electric field that maintains the equilibrium toroidal
+plasma current in the vicinity of the resonant surface, and $\chi_\varphi$  the anomalous perpendicular ion momentum
+diffusivity at the resonant surface. 
+Moreover, $d_\beta=c_\beta\,d_i$, and $\hat{d}_\beta=d_\beta/r_s$, where $c_\beta = \sqrt{\beta/(1+\beta)}$, and
+$\beta=(5/3)\,\mu_0\,p_0/B_z^{\,2}$. Here, $d_\beta$ is usually referred to as the {\em ion sound radius}. Furthermore,
+$\lambda_e=0.71\,\eta_e/(1+\eta_e)$. Finally,\cite{fw}
+\begin{equation}
+\hat{D}_\perp \equiv \frac{D_{\perp}}{r_s\,V_A}= c_\beta^{\,2}\,\hat{\eta}_\perp +  \frac{2}{3}\left(1-c_\beta^{\,2}\right)\!\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\perp\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\perp\,i}\right),
+\end{equation}
+where $\hat{\chi}_{\perp\,e,i}=\chi_{\perp\,e,i}/(r_s\,V_A)$, and $\chi_{\perp\,e,i}$ is the anomalous
+electron/ion perpendicular energy diffusivity in the vicinity of the resonant surface. 
+Note that Cole \& Fitzpatrick (2006) neglects the contribution of $\chi_{\perp\,e,i}$ to the perpendicular particle
+diffusivity, $D_\perp$, leading to an anomalously small estimate for $D_\perp$. It is this deficiency that we aim to
+correct in the present paper.
+
+\subsection{Matching to Plasma Equilibrium}
+The unperturbed plasma equilibrium is such that
+${\bf B} = (0,\,B_\theta(r),\,B_z)$,  $p = p(r)$,
+${\bf V} = (0,\,V_E(r),\,V_z(r))$,
+where 
+$V_E(r)\simeq E_r/B_z$
+ is the (dominant $\theta$-component of the) ${\bf E}\times {\bf B}$ velocity. Now, the resonant layer is assumed to have a radial thickness that is
+much smaller than $r_s$.   Hence, we only need to evaluate plasma equilibrium quantities in the immediate vicinity of the resonant
+surface. Equations~(\ref{e10})--(\ref{e13}) suggest that 
+\begin{align}
+\psi&= \frac{\hat{x}^{\,2}}{2\,\hat{L}_s},\label{e23}\\[0.5ex]
+\phi &= - \hat{V}_E\,\hat{x},\\[0.5ex]
+N &= -\hat{V}_\ast\,\hat{x},\\[0.5ex]
+V &= \hat{V}_\parallel,\label{e26}
+\end{align}
+where 
+$\hat{x}=(r-r_s)/r_s$,
+ $\hat{L}_s=L_s/r_s$,  $L_s=R_0\,q_s/s_s$, 
+  $\hat{V}_E= V_E(r_s)/V_A$,
+$\hat{V}_\ast= V_\ast(r_s)/V_A$,
+$V_\ast(r) = (dp/dr)/(e\,n_0\,B_z)$ 
+is the (dominant $\theta$-component of the) diamagnetic velocity,
+  and 
+ $\hat{V}_\parallel=\hat{d}_i\, V_z(r_s)/V_A$. Here, $s_s=s(r_s)$ and $s(r)=d\ln q/d\ln r$. We also have
+ \begin{align}\label{e28}
+ J &= -\left(\frac{2}{s_s}-1\right)\frac{1}{\hat{L}_s},
+\end{align} 
+and $ \hat{E}_\parallel =(2/s_s-1) (\hat{\eta}_\parallel/\hat{L}_s)$.
+
+\section{Linear Resonant Plasma Response Model}\label{layer}
+\subsection{Introduction}
+The aim of this section is to obtain a set of linear layer equations from the four-field model
+introduced in Sect.~\ref{sfour}.
+
+\subsection{Derivation of Linear Layer Equations}
+In accordance with Eqs.~(\ref{e23})--(\ref{e28}), let us write
+\begin{align}\label{e31}
+\hat{\psi}(\hat{x},\zeta,\hat{t}) &= \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
+\phi(\hat{x},\zeta,\hat{t}) &=-\hat{V}_E\,\hat{x}+ \tilde{\phi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
+N(\hat{x},\zeta,\hat{t}) &= -\hat{V}_\ast\,\hat{x}+\left(\frac{1+\tau}{\tau}\right)\!\tilde{N}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
+V(\hat{x},\zeta,\hat{t}) &= \hat{V}_\parallel + \left(\frac{1+\tau}{\tau}\right)\!\tilde{V}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
+J(\hat{x},\zeta,\hat{t}) &=-\left(\frac{2}{s_s}-1\right)\!\frac{1}{\hat{L}_s}+ \hat{\nabla}^2\tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\label{e36}
+\end{align}
+where $\zeta=m\,\theta-n\,\varphi$, $\hat{\omega}=r_s\,\omega/V_A$, and $\omega$ is the frequency of the tearing mode in the laboratory frame. 
+Substituting Eqs.~(\ref{e31})--(\ref{e36}) into Eqs.~(\ref{e16})--(\ref{e21}), 
+ and only retaining terms that
+are first order in perturbed quantities, we obtain the following set of linear equations:
+\begin{align}\label{e37}
+-{\rm i}\,[\omega-\omega_E -(1+\lambda_e)\,\omega_{\ast\,e}]\,\tau_H\,\tilde{\psi} &= -{\rm i} \,\hat{x}\,[\tilde{\phi}-(1+\lambda_e)\,\tilde{N}] + S^{-1}\,\hat{\nabla}^2\tilde{\psi},\\[0.5ex]
+-{\rm i}\,(\omega-\omega_E-\omega_{\ast\,i})\,\tau_H\,\hat{\nabla}^2\tilde{\phi} &= -{\rm i}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi}+S^{-1}\,P_\varphi\,\hat{\nabla}^4\!\left(\tilde{\phi} + \frac{\tilde{N}}{\tau}\right),\\[0.5ex]
+-{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{N} &= -{\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\phi}-{\rm i}\,c_\beta^{\,2}\,\hat{x}\,\tilde{V} - {\rm i}\!\left(\frac{\tau}{1+\tau}\right)\hat{d}_\beta^{\,2}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi}\nonumber\\[0.5ex]
+&\phantom{=} + S^{-1}\,P_\perp\,\hat{\nabla}_\perp^2 \tilde{N},\\[0.5ex]
+-{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{V} &= {\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\psi} - {\rm i}\,\hat{x}\,\tilde{N}
++ S^{-1}\,P_\varphi\,\hat{\nabla}^2\tilde{V}.\label{e40}
+\end{align}
+Here, 
+$\tau_H = L_s/(m\,V_A)$ 
+is the  hydromagnetic time, 
+$\omega_E =(m/r_s)\,V_E(r_s)$
+  the 
+ ${\bf E}\times {\bf B}$ frequency, 
+$\omega_{\ast\,e} = -[\tau/(1+\tau)](m/r_s)V_\ast(r_s)$
+the 
+   electron diamagnetic
+frequency,
+$\omega_{\ast\,i} =[1/(1+\tau)](m/r_s)V_\ast(r_s)$
+ the  ion diamagnetic
+frequency, 
+$S=\tau_R/\tau_H$
+ the  Lundquist number, 
+$\tau_R = \mu_0\,r_s^{\,2}/\eta_\parallel$
+ the
+ resistive diffusion time, 
+$\tau_\varphi
+= r_s^{\,2}/\chi_\varphi$
+the  toroidal momentum confinement time, and 
+$\tau_\perp = r_s^{\,2}/D_\perp$.
+  Furthermore, $P_\varphi = \tau_R/\tau_\varphi$ and $P_\perp = \tau_R/\tau_\perp$ are magnetic Prandtl numbers.
+
+ Let us define the stretched radial variable $X = S^{1/3}\,\hat{x}$.
+Assuming that $X\sim{\cal O}(1)$ in the layer (i.e., assuming that the layer thickness is roughly of order $S^{-1/3}\,r_s$),
+and making use of the fact that $S\gg 1$ in conventional tokamak plasmas,  Eqs.~(\ref{e37})--(\ref{e40}) reduce to the following
+set of linear layer equations:\,\cite{cole}
+\begin{align}\label{e43}
+-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_{e}]\,\tilde{\psi}&= - {\rm i}\,X\left[\tilde{\phi}-(1+\lambda_e)\,\tilde{N}\right] + \frac{d^{\,2}\tilde{\psi}}{d X^2},\\[0.5ex]
+-{\rm i}\,(Q-Q_E -Q_{i})\,\frac{d^{\,2}\tilde{\phi}}{dX^2}&= - {\rm i}\,X\,\frac{d^{\,2}\tilde{\psi}}{dX^2}+ P_\varphi\,\frac{d^{\,4}}{dX^4}\!\left(\tilde{\phi} + \frac{\tilde{N}}{\tau}\right),\\[0.5ex]
+-{\rm i}\,(Q-Q_E)\tilde{N} &= - {\rm i}\,Q_{e}\,\tilde{\phi} - {\rm i}\,c_\beta^{\,2}\,X\,\tilde{V}  - {\rm i} \,D^{2}\,X\,\frac{d^{\,2}\tilde{\psi}}{dX^{2}}
++ P_\perp\,\frac{d^{\,2} \tilde{N}}{dX^{2}},\\[0.5ex]
+ -{\rm i}\,(Q-Q_E)\,\tilde{V} &= {\rm i}\,Q_{e}\,\tilde{\psi} - {\rm i}\,X\,\tilde{N} + P_\varphi\,\frac{d^{\,2}\tilde{V}}{dX^{2}}.\label{e46}
+\end{align}
+Here, $Q=S^{\,1/3}\,\omega\,\tau_H$, $Q_E = S^{\,1/3}\,\omega_E\,\tau_H$, $Q_{e,i} = S^{\,1/3}\,\omega_{\ast\,e,i}\,\tau_H$,
+and $D = S^{\,1/3}\,[\tau/(1+\tau)]^{1/2}\,\hat{d}_\beta$.
+
+\subsection{Asymptotic Matching}
+The  linear layer equations, (\ref{e43})--(\ref{e46}), possess tearing parity solutions
+characterized by the symmetry $\tilde{\psi}(-X)=\tilde\psi(X)$, $\tilde{\phi}(-X)=-\tilde{\phi}(X)$, 
+$\tilde{N}(-X)= - \tilde{N}(X)$, $\tilde{V}(-X)=\tilde{V}(X)$. If we assume that
+the asymptotic behavior of the tearing parity layer solutions is such that 
+\begin{equation}\label{e47}
+\tilde{\psi}\rightarrow  \psi_0\!\left[1+ \frac{\hat{\mit\Delta}}{2}\,|X| + {\cal O}(X^2)\right]
+\end{equation}
+as $|X|\rightarrow\infty$, where $\psi_0$ is an arbitrary constant, then asymptotic matching to the outer solution yields
+\begin{equation}\label{e48}
+{\mit\Delta\Psi}_s= S^{1/3}\,\hat{\mit\Delta}\,\,{\mit\Psi}_s.
+\end{equation}
+
+\section{Linear Resonant Plasma Response Regimes}\label{linear}
+\subsection{Introduction}
+The aim of this section is to solve the linear layer equations derived in Sect.~\ref{layer} to determine the
+response of a resonant layer to an external perturbation.
+
+\subsection{Fourier Transformation}
+Equations~(\ref{e43})--(\ref{e46}) are most conveniently solved in Fourier transform space.\cite{cole} 
+Let
+\begin{equation}
+\bar{\phi}(p) = \int_{-\infty}^\infty \tilde{\phi}(X)\,{\rm e}^{-{\rm i}\,p\,X}\,dX,
+\end{equation}
+et cetera. The Fourier transformed linear layer equations become
+\begin{align}\label{e314}
+-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_{e}]\,\bar{\psi}&=\frac{d}{dp}\!\left[\bar{\phi}-(1+\lambda_e)\,\bar{N}\right] -p^2\,\bar{\psi},\\[0.5ex]
+-{\rm i}\,(Q-Q_E -Q_{i})\,p^2\,\bar{\phi}&=  \frac{d(p^2\,\bar{\psi})}{dp}- P_\varphi\,p^4\!\left(\bar{\phi} + \frac{\bar{N}}{\tau}\right),\\[0.5ex]
+-{\rm i}\,(Q-Q_E)\bar{N} &= - {\rm i}\,Q_{e}\,\bar{\phi} + c_\beta^{\,2}\,\frac{d\bar{V}}{dp}-D^{2}\,\frac{d(p^2\,\bar{\psi})}{dp}
+  - P_\perp\,p^2\bar{N},\label{e316}\\[0.5ex]
+ -{\rm i}\,(Q-Q_E)\,\bar{V} &= {\rm i}\,Q_{e}\,\bar{\psi} +\frac{d\bar{N}}{dp}- P_\varphi\,p^2\,\bar{V},\label{e317}
+\end{align}
+where, for a tearing parity solution, 
+\begin{equation}
+\bar{\phi}(p)\rightarrow \bar{\phi}_0\!\left[\frac{\hat{\mit\Delta}}{\pi\,p} + 1+ {\cal O}(p)\right]
+\end{equation}
+as $p\rightarrow 0$.
+
+Let us ignore the term $c_\beta^{\,2}\,d\bar{V}/dp$ in Eq.~(\ref{e316}). This approximation can
+be justified {\em a posteriori}. It is equivalent to the neglect of the contribution of ion parallel dynamics to the linear  plasma
+response in the resonant layer, and effectively decouples Eq.~(\ref{e317}) from Eqs.~(\ref{e314})--(\ref{e316}).\cite{cole,ber} Equations~(\ref{e314})--(\ref{e316}) reduce to\,\cite{cole}
+\begin{equation}\label{e320}
+\frac{d}{dp}\!\left[G(p)\,\frac{dY_e}{dp}\right] - \frac{A(p)}{B(p)}\,p^{2}\,Y_e = 0,
+\end{equation}
+where
+\begin{align}
+G(p)&= \frac{p^2}{-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e] + p^2},\\[0.5ex]
+ A(p) &= -(Q-Q_E)\,(Q-Q_E-Q_i)-{\rm i}\,(Q-Q_E-Q_i)\,(P_\varphi+P_\perp)\,p^2 + P_\varphi\,P_\perp\,p^4,\\[0.5ex]
+ B(p) &= 
+-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e] +\{P_\perp - {\rm i}\,(1+\lambda_e)\,(Q-Q_E-Q_i)\,D^2\}p^2\nonumber\\[0.5ex]
+&\phantom{=}+[(1+\lambda_e)+1/\tau]\,P_\varphi\,D^2\,p^4,
+\end{align}
+and $Y_e=\bar{\phi} - (1+\lambda_e)\,\bar{N}$. The boundary conditions are that $Y_e(p)$ is bounded as $p\rightarrow\infty$, and
+\begin{equation}\label{e325}
+Y_e(p)\rightarrow Y_0\!\left[\frac{\hat{\mit\Delta}}{\pi\,p} + 1+ {\cal O}(p)\right]
+\end{equation}
+as $p\rightarrow 0$. In the following, we shall assume that $|Q|\sim |Q_E|\sim |Q_e|\sim |Q_i|$, $P_\varphi\sim P_\perp \sim P$, $\tau\sim {\cal O}(1)$, and $\lambda_e\sim{\cal O}(1)$,  for the
+sake of simplicity.
+
+\subsection{Constant-$\psi$ Approximation}\label{s5.6}
+Let us suppose that there are two layers in $p$ space. In the small-$p$ layer, suppose that Eq.~(\ref{e320}) reduces to
+\begin{equation}
+\frac{d}{dp}\!\left[\frac{p^2}{-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e] + p^2}\,\frac{dY_e}{dp}\right]\simeq 0
+\end{equation}
+when $p\sim Q^{1/2}$. Integrating directly, we find that
+\begin{equation}
+Y_e(p) \simeq Y_0 \left[\frac{\hat{\mit\Delta}}{\pi}\left(\frac{1}{p} + \frac{p}{{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e]}\right) + 1 + {\cal O}(p^2)\right]
+\end{equation}
+for $p\lesssim {\cal O}(Q^{1/2})$, where use has been made of Eq.~(\ref{e325}). The two-layer  approximation is
+equivalent to the well-known {\em constant-$\psi$ approximation}.\cite{fkr}
+
+In the large-$p$ layer, for  $p\gg {\cal O}(Q^{1/2})$, we obtain 
+\begin{equation}\label{e329}
+\frac{d^{\,2} Y_e}{dp^2} - \frac{A(p)}{B(p)}\,p^2\,Y_e\simeq 0,
+\end{equation}
+with $Y_e$ bounded as $p\rightarrow \infty$. Asymptotic matching to the small-$p$ layer yields the boundary
+condition 
+\begin{equation}\label{e330}
+Y_e(p)\simeq Y_0\left\{1+ \frac{\hat{\mit\Delta}}{\pi}\,\frac{p}{{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e]}+ {\cal O}(p^2)\right\}
+\end{equation}
+as $p\rightarrow 0$.
+
+In the various constant-$\psi$ linear response regimes considered in Sect.~\ref{scp}, Eq.~(\ref{e329}) reduces to an
+equation of the form
+\begin{equation}\label{e330a}
+\frac{d^{\,2}Y_e}{dp^2}- C\,p^m\,Y_e\simeq 0,
+\end{equation}
+where $m$ is real and non-negative, and $C$ is a complex constant. Let $Y_e=\sqrt{p}\,Z$ and $q=\sqrt{C}\,p^n/n$, where
+$n=(m+2)/2$. The previous equation transforms into a modified Bessel equation of general order, 
+\begin{equation}
+q^2\,\frac{d^{\,2}Z}{dq^2} + q\,\frac{dZ}{dq} - (q^2+\nu^2)\,Z =0,
+\end{equation}
+where $\nu=1/(m+2)$. The solution that is bounded as $q\rightarrow \infty$ has the small-$q$
+expansion
+\begin{equation}\label{e332}
+K_\nu(z)= \frac{1}{{\mit\Gamma}(1-\nu)}\left(\frac{2}{q}\right)^\nu - \frac{1}{{\mit\Gamma}(1+\nu)}\left(\frac{q}{2}\right)^\nu + {\cal O}(q^{2-\nu}),
+\end{equation}
+where ${\mit\Gamma}(z)$ is a gamma function. 
+A comparison of this expression with Eq.~(\ref{e330}) reveals that
+\begin{equation}
+\hat{\mit\Delta} = \pi\,(-{\rm i}\,\left[Q-Q_E-(1+\lambda_e)\,Q_e\right])\, \frac{{\mit\Gamma}(1-\nu)}{{\mit\Gamma}(\nu)}\,\nu^{2\nu-1}\,C^{\,\nu}.
+\end{equation}
+Note, finally, that $p_\ast\sim |C|^{-\nu}$, where $p_\ast$ denotes the width of the large-$p$ layer in $p$ space.
+This width must be larger than $Q^{1/2}$ (i.e., the width of the small-$p$ layer) in order for the constant-$\psi$ approximation to hold.
+
+\subsection{Constant-$\psi$ Linear Response Regimes}\label{scp}
+Suppose that $Q\gg P\,p^2$ and $D^2\,p^2 \ll 1$. It follows that $\nu=1/4$ and
+\begin{equation}
+C = \frac{[-{\rm i}\,(Q-Q_E)]\,[-{\rm i}\,(Q-Q_E-Q_i)]}{-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e]}.
+\end{equation}
+Hence, we deduce that
+\begin{equation}\label{ri}
+\hat{\mit\Delta} = \frac{2\pi\,{\mit\Gamma}(3/4)}{{\mit\Gamma}(1/4)}\,(-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e])^{3/4}\,[-{\rm i}\,(Q-Q_E)]^{1/4}\,[-{\rm i}\,(Q-Q_E-Q_i)]^{1/4}.
+\end{equation}
+This response regime is known as the {\em resistive-inertial regime}, because the layer response is dominated by
+plasma resistivity and ion inertia.\cite{fkr,ara,rf1998}. The characteristic layer width is $p_\ast \sim Q^{-1/4}$,
+which implies that the regime is valid when $P\ll Q^{3/2}$, $Q\gg D^4$, and $Q\ll 1$.
+
+Suppose that $Q\ll P\,p^2$ and $D^2\,p^2\ll 1$. It follows that $\nu=1/6$ and $C=P_\varphi$. 
+Hence, we deduce that
+\begin{equation}\label{vr}
+\hat{\mit\Delta} = \frac{6^{2/3}\,\pi\,{\mit\Gamma}(5/6)}{{\mit\Gamma}(1/6)}\, (-{\rm i}\,\left[Q-Q_E-(1+\lambda_e)\,Q_e\right])\,P_\varphi^{1/6}.
+\end{equation}
+This response regime is known as the {\em viscous-resistive regime}, because the layer response is dominated by
+  ion perpendicular viscosity and plasma resistivity.\cite{rf1993,bond} The characteristic layer width is $p_\ast \sim P^{-1/6}$, which implies that
+the regime is valid when  $P\gg Q^{3/2}$, $P\gg D^6$, and $P\ll Q^{-3}$.
+
+Suppose that $Q\gg P\,p^2$ and $D^2\,p^2\gg 1$. It follows that $\nu=1/2$ and
+\begin{equation}
+C = \frac{-{\rm i}\,(Q-Q_E)}{(1+\lambda_e)\,D^2}.
+\end{equation}
+Hence, we deduce that
+\begin{equation}\label{sc}
+\hat{\mit\Delta}= \frac{\pi\,(-{\rm i}\,\left[Q-Q_E-(1+\lambda_e)\,Q_e\right])\,[-{\rm i}\,(Q-Q_E)]^{1/2}}{\sqrt{1+\lambda_e}\,D}.
+\end{equation}
+This response regime is known as the {\em semi-collisional regime}.\cite{drake,wal} The characteristic
+layer width is $p_\ast\sim D\,Q^{-1/2}$, which implies that the regime is valid when $Q\ll D^4$,
+ $P\ll Q^2/D^2$, and $Q\ll D$.
+
+Suppose, finally, that $Q\ll P\,p^2$ and $D^2\,p^2\gg 1$. It follows that $\nu=1/4$ and
+\begin{equation}
+C = \frac{P_\perp}{[(1+\lambda_e)+1/\tau]\,D^2}.
+\end{equation}
+Hence, we deduce that 
+\begin{equation}\label{hr}
+\hat{\mit\Delta}= \frac{2\pi\,{\mit\Gamma}(3/4)}{{\mit\Gamma}(1/4)}\,\frac{(-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e])\,P_\perp^{1/4}}{[(1+\lambda_e)+1/\tau]^{1/4}\,D^{1/2}}.
+\end{equation}
+This response regime is known as the {\em diffusive-resistive regime}, because the layer
+response is dominated by perpendicular particle diffusion and plasma resistivity. The characteristic
+layer width is $p_\ast \sim D^{1/2}\,P^{-1/4}$, which implies that the regime is valid when $P\gg Q^2/D^2$,
+$P\ll D^6$, and $P\ll D^2/Q^2$.
+
+\subsection{Nonconstant-$\psi$ Linear Response Regimes}\label{sncp}
+Suppose that $p\ll Q^{1/2}$. In this limit, Eq.~(\ref{e320}) reduces to 
+\begin{equation}
+\frac{d}{dp}\!\left(p^2\,\frac{dY_e}{dp}\right)-(-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e])\,\frac{A(p)}{B(p)}\,p^2\,Y_e=0.
+\end{equation}
+In the various nonconstant-$\psi$ regimes considered in this section, the previous equation takes the form
+\begin{equation}
+\frac{d}{dp}\!\left(p^2\,\frac{dY_e}{dp}\right)-C\,p^{m+2}\,Y_e = 0,
+\end{equation}
+where $m$ is real and non-negative, and $C$ is a complex constant. Let $U=p\,Y_e$. The previous equation
+yields
+$d^{\,2} U/dp^2- C\,p^m\,U = 0$.
+This equation is identical in form to Eq.~(\ref{e330a}), which we have already solved. Indeed, the solution that
+is bounded as $p\rightarrow\infty$ has the small-$p$ expansion (\ref{e332}), where $q=\sqrt{C}\,p^n/n$, 
+$n=(m+2)/2$, and $\nu=1/(m+2)$. Matching to Eq.~(\ref{e325}) yields
+\begin{equation}
+\hat{\mit\Delta} = -\pi\,\frac{{\mit\Gamma}(\nu)}{{\mit\Gamma}(1-\nu)}\,\nu^{1-2\nu}\,C^{-\nu}.
+\end{equation}
+The layer width in $p$-space again scales as $p_\ast\sim |C|^{-\nu}$. This width must be
+less that $Q^{1/2}$.
+
+Suppose that $Q\gg P\,p^2$ and $D^2\,p^2 \ll 1$. It follows that $\nu=1/2$ and
+\begin{equation}
+C = [-{\rm i}\,(Q-Q_E)]\,[-{\rm i}\,(Q-Q_E-Q_i)].
+\end{equation}
+Hence, we deduce that
+\begin{equation}
+\hat{\mit\Delta} = -\frac{\pi}{[-{\rm i}\,(Q-Q_E)]^{1/2}\,[-{\rm i}\,(Q-Q_E-Q_i)]^{1/2}}.
+\end{equation}
+This response regime is known as the {\em inertial regime}, because the layer response is dominated by
+ ion inertia.\cite{ara,rf1993} Note that the plasma response in the inertial regime is
+ equivalent to that of two closely-spaced Alfv\'{e}n resonances that straddle the resonant surface,\cite{boozer} 
+ In fact, it is easily demonstrated that in real space,
+ \begin{equation}
+ \hat{\mit\Delta} = \int_{-\infty}^\infty \frac{dX}{(Q-Q_E)\,(Q-Q_E-Q_i)-X^{\,2}},
+ \end{equation}
+ which suggests that the resonances lie at $X=\pm \sqrt{(Q-Q_E)\,(Q-Q_E-Q_i)}$. 
+ The characteristic layer width is $p_\ast \sim Q^{-1}$,
+which implies that the regime is valid when $P\ll Q^3$, $Q\gg D$, and $Q\gg 1$.
+
+Suppose that $Q\ll P\,p^2$ and $D^2\,p^2 \ll 1$. It follows that $\nu=1/4$ and
+\begin{equation}
+C = (-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e])\,P_\varphi.
+\end{equation}
+Hence, we deduce that
+\begin{equation}
+\hat{\mit\Delta} =- \frac{\pi}{2}\,\frac{{\mit\Gamma}(1/4)}{{\mit\Gamma}(3/4)}\, (-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e])^{-1/4}\,P_\varphi^{-1/4}.
+\end{equation}
+This response regime is known as the {\em viscous-inertial regime}, because the layer response is dominated by
+ion perpendicular viscosity and ion inertia.\cite{rf1998} 
+ The characteristic layer width is $p_\ast \sim Q^{-1/4}\,P^{-1/4}$,
+which implies that the regime is valid when $P\gg Q^3$, $P\gg D^4/Q$, and $P\gg Q^{-3}$.
+
+Suppose, finally, that $Q\ll P\,p^2$ and $D^2\,p^2\gg 1$. It follows that $\nu=1/2$ and
+\begin{equation}
+C = \frac{(-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e)]\,P_\perp}{[(1+\lambda_e)+1/\tau]\,D^2}.
+\end{equation}
+Hence, we deduce that
+\begin{equation}
+\hat{\mit\Delta}= -\frac{\pi\,[(1+\lambda_e)+1/\tau]^{1/2}\,D}{(-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e)])^{1/2}\,P_\perp^{1/2}}.
+\end{equation}
+This response regime is known as the {\em diffusive-inertial regime},  because the
+layer response is dominated by perpendicular particle diffusivity and ion inertia. The characteristic layer width is $p_\ast\sim
+D\,Q^{-1/2}\,P^{-1/2}$, which implies that the regime is valid when $Q\ll D$, $P\ll D^4/Q$, and $P\gg D^2/Q^2$.
+
+\subsection{Discussion}\label{dis1}
+Figures~\ref{f1} and \ref{f2} show the extents of the various different linear resonant response regimes in $Q$-$P$ space for the
+cases $D<1$ and $D>1$, respectively. It can be seen, by comparison with Figs.~1--3 in Ref.~\onlinecite{cole}, that
+adopting a more realistic ordering for the perpendicular particle diffusivity, $D_\perp$, leads to a significant
+modification to the system of response regimes. We can identify the
+resistive-inertial, viscous-resistive, semi-collisional, diffusive-resistive, inertial, and viscous-inertial response regimes, found in this paper, with
+the RIi, VRii, SCii, HRii, I, and VI response regimes found in Ref.~\onlinecite{cole}. Some of the response regimes
+found in Ref.~\onlinecite{cole}---namely, the RIii, VRi, SCi, and HRi---no longer exist. On the other hand, we have
+found one new response regime---namely, the diffusive-inertial. On the whole, the system of response regimes shown
+in Figs.~\ref{f1} and \ref{f2} is much simpler than that shown in Figs.~1--3 of Ref.~\onlinecite{cole}.
+
+Let $\hat{\delta}_\ast\sim p_\ast^{-1}$ be the normalized radial thickness of the resonant layer.  Of course, the true thickness is
+$\delta = S^{-1/3}\,\hat{\delta}_\ast\,r_s$.  It follows from
+Eq.~(\ref{e47}) that the relative change in the perturbed helical flux, $\tilde{\psi}$, across the layer
+is
+\begin{equation}
+\left.\frac{d\ln\tilde{\psi}}{dX}\right|_{-\hat{\delta}/2}^{+\hat{\delta}/2} = \hat{\mit\Delta}\,\,\hat{\delta}_\ast\sim \hat{\mit\Delta}\,\,p_\ast^{-1},
+\end{equation}
+According to the  analysis of Sect.~\ref{scp}, $\hat{\mit\Delta}\,p_\ast^{-1}$ takes the respective values $Q^{1/2}$, $Q\,P^{1/3}$, 
+$Q^2/D^2$, and $Q\,P^{1/2}/D$ in the resistive-inertial, viscous-resistive, semi-collisional, and
+diffusive-resistive response regimes. Moreover, it is clear from Figs.~\ref{f1} and \ref{f2} that these values are all
+much less than unity. In other words, it is indeed the case that $\tilde{\psi}$ does not vary substantially across a
+`constant-$\psi$' resonant layer. On the other hand, according to the analysis of Sect.~\ref{sncp}, $\hat{\mit\Delta}\,p_\ast^{-1}\sim 1$ in the inertial,
+viscous-inertial, and diffusive-inertial response regimes, which implies that $\tilde{\psi}$ does vary substantially
+across a `nonconstant-$\psi$' layer.
+
+\section{Linear Tearing Mode Stability}\label{stab}
+\subsection{Introduction}
+The aim of this section is to combine the analysis of Sects~\ref{cyl} and \ref{linear} to determine the linear stability
+of tearing modes in larger aspect-ratio  tokamak plasmas. In this study, we shall assume that there is no externally generated, resonant
+magnetic perturbation (i.e., ${\mit\Psi}_v=0$).
+
+\subsection{Linear Dispersion Relation}\label{s6.2}
+Let us write
+$\omega = {\rm i}\,\gamma+\omega_r$, where $\gamma$ is the growth-rate of the tearing mode, whereas $\omega_r$ is the real
+frequency of the mode in the laboratory frame. We shall assume that $|\gamma|\ll |\omega_r|$. This assumption can
+easily be verified {\em a posteriori}. Asymptotic matching between the solution in the outer region and that in the
+thin linear layer surrounding the resonant surface yields a linear tearing mode dispersion relation of the form
+\begin{equation}\label{e352}
+S^{1/3}\,\hat{\mit\Delta}(\gamma,\omega_r) = {\mit\Delta}_s',
+\end{equation}
+where use has been made of Eqs.~(\ref{e110}) and (\ref{e48}). Here, ${\mit\Delta}_s'$ is the real tearing stability index, 
+whereas the complex layer matching parameter, $\hat{\mit\Delta}$, is defined in Eq.~(\ref{e47}).
+
+In a conventional tokamak plasma, ${\mit\Delta}_s' \sim {\cal O}(1)$, and $S^{1/3}\gg 1$. (Here, we are neglecting $m=1$ modes, which
+are not really tearing modes.)
+Hence, the previous dispersion relation can only be satisfied if $\omega_r$ takes a
+value that renders $|\hat{\mit\Delta}|\ll 1$. It is clear from Eqs.~(\ref{ri}), (\ref{vr}), (\ref{sc}), and (\ref{hr}) that this goal
+can be achieved in all of the constant-$\psi$ linear response regimes if
+$\omega_r = \omega_{\perp\,e}$, where
+\begin{equation}\label{e354}
+\omega_{\perp\,e} = \omega_E+(1+\lambda_e)\,\omega_{\ast\,e}.
+\end{equation}
+We conclude that the tearing mode co-rotates with the electron fluid at the resonant
+ surface.\cite{ara} [In fact, the mode 
+rotates slightly faster than the electron fluid because of the influence of the thermal force, 
+which generates the additional  factor $\lambda_e$ in Eq.~(\ref{e354}).]
+
+\subsection{Determination of Linear Growth-Rates}\label{s6.3}
+Reusing the analysis of Sects.~\ref{s5.6} and \ref{scp}, let us again suppose that there are two layers in $p$ space (i.e., Fourier space). The
+small-$p$ layer turns out to be of width $|\hat{\gamma}|^{1/2}$, where $\hat{\gamma} = S^{1/3}\,\gamma\,\tau_H$. Given that we are effectively assuming that
+$|\hat{\gamma}|\ll 1$, the condition for the separation of the layer solution into two layers (i.e., that the width of the small-$p$ layer is less than that of the large-$p$ layer) is always satisfied.
+The large-$p$ layer is governed by the equation
+\begin{equation}\label{e355}
+\frac{d^{\,2} Y_e}{dp^2} - \frac{A(p)}{\tilde{B}(p)} \,Y_e =0,
+\end{equation}
+where 
+\begin{align}
+A(p) &= (1+\lambda_e)\left(\frac{\tau}{1+\tau}\right)\left(1+ \frac{\lambda_e\,\tau}{1+\tau}\right)Q_\ast^{\,2}
+-{\rm i}\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)Q_\ast\,(P_\varphi+P_\perp)\,p^2\nonumber\\[0.5ex]
+&\phantom{=} + P_\varphi\,P_\perp\,p^4,\\[0.5ex]
+\tilde{B}(p)&= P_\perp - {\rm i}\,(1+\lambda_e)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)Q_\ast\,D^2 +\left(\frac{1+\tau}{\tau}\right)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right) D^2\,P_\varphi\,p^2.
+\end{align}
+Here, $Q_\ast = S^{1/3}\,\omega_\ast\,\tau_H$, where
+$\omega_\ast =-(m/r_s)\,(1/e\,n_0\,B_z)\,(dp/dr)_{r_s}$.
+In the following, $\omega_\ast$ is assumed to be positive. The boundary conditions on Eq.~(\ref{e355}) are
+that $Y_e$ is bounded as $p\rightarrow\infty$, and
+\begin{equation}\label{e359}
+Y_e(p)= Y_0\left[1-\frac{\hat{\mit\Delta}\,p}{\pi\,\hat{\gamma}} + {\cal O}(p^2)\right]
+\end{equation}
+as $p\rightarrow 0$.
+
+In the various constant-$\psi$ linear growth-rate regimes considered in this section, Eq.~(\ref{e355}) reduces to an equation of the form
+$d^{\,2} Y_e/dp^2 - C\,p^m\,Y_e = 0$,
+where $m$ is real and non-negative, and $C$ is a complex constant. As described in Sect.~\ref{s5.6}, the solution of this
+equation that is bounded as $p\rightarrow \infty$ can be matched to the small-$p$ asymptotic form (\ref{e359}) to give 
+\begin{equation}
+\hat{\mit\Delta} = \pi\,\hat{\gamma}\,\frac{{\mit\Gamma}(1-\nu)}{{\mit\Gamma}(\nu)}\,\nu^{2\nu-1}\,C^{\,\nu},
+\end{equation}
+where $\nu=1/(m+2)$. The width of the large-$p$ layer in $p$ space is $C^{-\nu}$.
+
+As before, we shall assume that $P_\varphi\sim P_\perp \sim P$, $\lambda_e\sim{\cal O}(1)$, and $\tau\sim {\cal O}(1)$, for
+the sake of simplicity. 
+Suppose that $Q_\ast\gg P\,p^2$ and $P\gg Q_\ast\,D^2$. It follows that $\nu=1/2$ and
+\begin{equation}
+C =\left(\frac{\tau}{1+\tau}\right) (1+\lambda_e)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)\frac{Q_\ast^{2}}{P_\perp}.
+\end{equation}
+Hence, 
+\begin{equation}
+\hat{\mit\Delta} = \pi\,\hat{\gamma}\left[ \left(\frac{\tau}{1+\tau}\right)(1+\lambda_e)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)\right]^{1/2}\,\frac{Q_\ast}{P_\perp^{1/2}},
+\end{equation}
+and $p_\ast\sim P^{1/2}/Q_\ast$. This {\em resistive-inertial  growth-rate regime}\/ is valid when $P\ll Q_\ast^{3/2}$ and
+$P\gg Q_\ast\,D^2$. 
+Making use of Eq.~(\ref{e352}), the corresponding tearing mode growth-rate is
+\begin{equation}\label{e363}
+\gamma = \frac{{\mit\Delta}_s'}{\pi\left[ \left(\frac{\tau}{1+\tau}\right)(1+\lambda_e)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)\right]^{1/2}\,}\,\frac{1}{\omega_\ast\,\tau_H\,\tau_R^{1/2}\,\tau_\perp^{1/2}}.
+\end{equation}
+Note that this growth-rate is significantly different from 
+the classical resistive-inertial growth-rate derived in Ref.~\onlinecite{fkr},  as a consequence of finite perpendicular particle diffusivity.
+
+Suppose that $Q_\ast \ll P\,p^2$ and $D^2\,p^2\ll 1$. 
+It follows that $\nu=1/6$ and
+$C = P_\varphi$. 
+Hence, 
+\begin{equation}
+\hat{\mit\Delta} = 6^{2/3}\,\pi\,\hat{\gamma}\, \frac{{\mit\Gamma}(5/6)}{{\mit\Gamma}(1/6)}\,P_\varphi^{1/6}, 
+\end{equation}
+and $p_\ast\sim P^{-1/6}$. This  {\em viscous-resistive growth-rate regime}\/ is valid when $P\gg Q_\ast^{3/2}$ and
+$P\gg D^6$. 
+The corresponding tearing mode growth-rate is
+\begin{equation}\label{e365}
+\gamma = \frac{{\mit\Delta}_s'}{6^{2/3}\,\pi\,[{\mit\Gamma}(5/6)/{\mit\Gamma}(1/6)]}\,\frac{\tau_\varphi^{1/6}}{\tau_H^{1/3}\,\tau_R^{5/6}}.
+\end{equation}
+
+Suppose that $Q_\ast\gg P\,p^2$ and $P\ll Q_\ast\,D^2$. It follows that $\nu=1/2$ and
+\begin{equation}
+C = {\rm i}\left(\frac{\tau}{1+\tau}\right)\frac{Q_\ast}{D^2}.
+\end{equation} 
+Hence, 
+\begin{equation}
+\hat{\mit\Delta} = {\rm e}^{{\rm i}\,\pi/4}\,\pi\,\hat{\gamma}\left(\frac{\tau}{1+\tau}\right)^{1/2}\,\frac{Q_\ast^{1/2}}{D},
+\end{equation}
+and $p_\ast\sim D/Q_\ast^{1/2}$. This  {\em semi-collisional growth-rate}\/ regime is valid when $P\ll Q_\ast^{\,2}/D^2$ and
+$P\ll Q_\ast\,D^2$. 
+The corresponding tearing mode growth-rate is
+\begin{equation}\label{e368}
+\gamma = \frac{{\mit\Delta}_s'}{\sqrt{2}\,\pi}\,\frac{d_\beta/r_s}{\omega_\ast^{1/2}\,\tau_H\,\tau_R^{1/2}}.
+\end{equation}
+Here, we have neglected the imaginary component of $\gamma$ because it merely gives rise to a small correction to the
+real frequency of the mode.
+
+Suppose, finally, that $Q_\ast \ll P\,p^2$ and $D^2\,p^2\gg 1$. It follows that $\nu=1/4$ and
+\begin{equation}
+C = \frac{P_\perp\,[\tau/(1+\tau)]}{[1+\lambda_e\,\tau/(1+\tau)]\,D^2}.
+\end{equation} 
+Hence,
+\begin{equation} 
+\hat{\mit\Delta} = 2\pi\,\hat{\gamma}\,\frac{{\mit\Gamma}(3/4)}{{\mit\Gamma}(1/4)}\,\frac{[\tau/(1+\tau)]^{1/4}\,P_\perp^{1/4}}{[1+\lambda_e\,\tau/(1+\tau)]^{1/4}\,D^{1/2}},
+\end{equation}
+and $p_\ast \sim D^{1/2}/P^{1/4}$. This {\em diffusive-resistive growth-rate regime}\/ is valid when $P\gg Q_\ast^2/D^2$ and
+$P\ll D^6$. The corresponding tearing mode growth-rate is 
+\begin{equation}\label{e371}
+\gamma= \frac{{\mit\Delta}_s'}{2\pi\,[{\mit\Gamma}(3/4)/{\mit\Gamma}(1/4)]\,[1+\lambda_e\,\tau/(1+\tau)]^{-1/4}}\,\frac{(d_\beta/r_s)^{1/2}\,\tau_\perp^{1/4}}{\tau_H^{1/2}\,\tau_R^{3/4}}.
+\end{equation}
+
+\subsection{Discussion}
+According to Eqs.~(\ref{e363}), (\ref{e365}), (\ref{e368}), and (\ref{e371}), a linear tearing mode is unstable when the tearing stability index, ${\mit\Delta}_s'$, is positive, and is stable otherwise.\cite{fkr}
+Moreover, the perturbed magnetic field associated with the mode corotates with the electron fluid at the resonant surface.\cite{ara}
+
+There are three main factors that
+affect the growth-rate of a tearing mode in a conventional tokamak plasma. First, the strength of diamagnetic flows in the plasma, which is parameterized by the
+diamagnetic frequency, $\omega_\ast$ (and by the normalized diamagnetic frequency, $Q_\ast$).
+Second, the  anomalous perpendicular diffusion of momentum and particles, which is parameterized by the momentum and particle confinement
+timescales, $\tau_\varphi$ and $\tau_\perp$ (and by the magnetic Prandtl number, $P$).
+Third, finite ion sound radius effects,  which are parameterized by the ion sound radius, $d_\beta$ (and by the normalized ion
+sound radius $D$).
+
+ There are four tearing-mode growth-rate regimes---the resistive-inertial, the viscous-resistive, the semi-collisional, and the diffusive-resistive---and their extents in $Q_\ast$-$P$ space are illustrated in Fig.~\ref{f3}.
+Note that Fig.~\ref{f3} differs somewhat from Figs.~\ref{f1} and \ref{f2} because in the latter two
+figures it is assumed that $|Q-Q_E-(1+\lambda_e)\,Q_e|\sim |Q-Q_E|\sim |Q-Q_E-Q_i|$ whereas
+in the former figure it is assumed that $|Q-Q_E-(1+\lambda_e)\,Q_e|\ll |Q-Q_E|\sim |Q-Q_E-Q_i|$.
+This refined ordering eliminates the nonconstant-$\psi$ response regimes, and significantly modifies the
+extent of the resistive-inertial response regime.
+
+The absence of nonconstant-$\psi$ response regimes in Fig.~\ref{f3}
+should come as no surprise. As we saw in Sect.~\ref{dis1}, nonconstant-$\psi$ resonant layers
+are characterized by $\hat{\mit\Delta}\sim\hat{\delta}_\ast^{-1}= S^{-1/3}\,(r_s/\delta)$, where $\delta$
+is the layer thickness. Hence, according to Eq.~(\ref{e352}), asymptotic matching of such a
+layer to the outer solution is only possible if $|{\mit\Delta}_s'|\sim r_s/\delta \gg 1$ (given that resonant
+layers in tokamak plasmas are invariably very thin compared to the minor radius of the plasma). However,
+low-$m$ tearing modes in conventional tokamak plasmas are characterized by $|{\mit\Delta}_s'|\sim {\cal O}(1)$ rather than
+$|{\mit\Delta}_s'|\gg 1$.
+
+Diamagnetic flows modify the tearing mode growth-rate in the resistive-inertial and semi-collisional
+growth-rate regimes, but not in the diffusive-resistive and viscous-resistive regimes. Anomalous perpendicular
+transport modifies the growth-rate in all regimes except the semi-collisional regime. Finally, finite ion sound radius 
+effects modify the growth-rate in the diffusive-resistive and semi-collisional regimes, but not in the other two
+regimes.
+
+Increasing  the diamagnetic flow strength decreases the tearing mode growth-rate such that it
+eventually scales as $\omega_\ast^{-1/2}$. Increasing the anomalous perpendicular transport increases the
+growth-rate such that it  eventually scales as $P_\varphi^{1/6}$. Increasing the ion sound radius 
+increases the tearing mode growth-rate, but the increase eventually saturates (i.e., the
+growth-rate ends up scaling as $d_\beta^{\,0}$).
+
+Finally, it is clear from Eq.~(\ref{e352}) that the layer solution can only be matched to the
+outer solution when $\omega_r$ takes a value that renders $|\hat{\mit\Delta}|\ll 1$. We have seen that this
+is possible in all constant-$\psi$ response regimes when $\omega_r= \omega_E+(1+\lambda_e)\,\omega_{\ast\,e}$
+(i.e., when the tearing perturbation corotates with the electron fluid at the resonant surface.) However, Eq.~(\ref{ri})
+seems to suggest that in the resistive-inertial regime it might be possible to successfully match the
+layer solution to the outer solution when $\omega_r=\omega_E$ (i.e., $Q=Q_E$), or when 
+$\omega_r=\omega_E+\omega_{\ast\,i}$
+(i.e., $Q=Q_E+Q_i$),
+giving tearing mode perturbations that corotate with the MHD fluid and the ion fluid, respectively, at the resonant
+surface.
+In fact, we can see that this is not the case, because if we set $\omega_r=\omega_E$ or $\omega_r=\omega_E+\omega_{\ast\,i}$  then Eq.~(\ref{e329}) does not lead to a layer solution characterized by  $|\hat{\mit\Delta}|\ll 1$,
+as a consequence of finite anomalous perpendicular transport.\cite{ber} Likewise, Eq.~(\ref{sc}) seems to suggest that in the semi-collisional response regime it might be possible to successfully match the
+layer solution to the outer solution when $\omega_r=\omega_E$, giving rise to a tearing perturbation that corotates with the MHD fluid at the resonant surface.
+In fact, this possibility is also ruled out by finite anomalous
+perpendicular transport.
+
+\section{Error-Field Penetration}\label{error}
+\subsection{Introduction}
+Tokamak plasmas are invariably subject to small amplitude, static, resonant magnetic perturbations---known as
+{\em error-fields}---which are primarily generated by field-coil misalignments and uncompensated coil feeds. 
+Error-fields can drive magnetic reconnection, resulting in the formation of  locked (i.e., non-rotating in the laboratory
+frame) magnetic island chains, in intrinsically tearing-stable plasmas. Low-density, ohmically-heated tokamak plasmas
+containing locked magnetic island chains often terminate in disruptions\,\cite{wes1} (usually triggered when the
+external heating is turned on). Fortunately, error-field driven magnetic reconnection is strongly
+suppressed by the naturally occurring rotation of ohmic plasmas. However, when the error-field amplitude rises
+above a certain critical amplitude, the rotation at the resonant surface is suddenly arrested, and error-field driven reconnection proceeds
+unhindered. This phenomenon is known as {\em error-field penetration}.\cite{rf1993,rf1998} The scenario
+just outlined has been observed in a number of tokamak experiments.\cite{scoville, hender,
+fishpool,wolf, wolfe,howell,menard,wang1,wang2}.
+
+In this section, we shall calculate the critical error-field amplitude required to trigger penetration on the assumption that,
+prior to penetration, the rotational suppression of error-field driven magnetic reconnection is sufficiently strong that
+the resonant plasma response is governed by linear layer physics.\cite{rf1993,rf1998,cole}
+
+\subsection{Asymptotic Matching}
+It is convenient to parametrize the error-field in terms of the vacuum magnetic flux, ${\mit\Psi}_v$, that it generates at the resonant surface. 
+Equations~(\ref{e110}) and (\ref{e48}) can be combined to give
+\begin{equation}\label{e383}
+{\mit\Psi}_s= \frac{{\mit\Psi}_v}{1+{\mit\Delta}/(-{\mit\Delta}_s')},
+\end{equation}
+where ${\mit\Delta} = S^{1/3}\,\hat{\mit\Delta}$. 
+The previous equation specifies the reconnected magnetic flux, ${\mit\Psi}_s$, driven at the resonant surface by the error-field.
+The complex layer parameter, ${\mit\Delta}$, specifies the strength of a shielding current
+that is induced in the resonant layer, and acts to prevent driven magnetic reconnection. Note that ${\mit\Delta}_s'<0$, because the
+plasma is assumed to be intrinsically tearing stable.
+
+\subsection{Resonant Layer Response}
+Generally speaking, in an ohmically-heated tokamak, we do not expect the plasma flow at the resonant surface to be sufficiently
+large to cause a breakdown of the constant-$\psi$ approximation. We also expect $P_\varphi, P_\perp \gg 1$. In other
+words, we expect the resistive evolution timescale to significantly exceed both the momentum and energy/particle
+confinement timescales (which it generally does by, at least, a factor of 10). Hence, consulting Figs.~\ref{f1} and \ref{f2},
+we can see that the appropriate linear resonant response regime is either the viscous-resistive regime or the diffusive-resistive
+regime.
+
+According to the analysis of Section~\ref{scp}, and making use of the fact that $\omega=Q=0$ for a static perturbation, 
+in the viscous-resistive response regime we have
+\begin{equation}
+{\mit\Delta}_{\rm VR} = {\rm i}\,\tau_{\rm VR}\,(\omega_{\perp\,e}+{\mit\Delta}\omega_E),
+\end{equation}
+where $\tau_{\rm VR} = \tau_R\,\hat{\delta}_{\rm VR}$, and
+\begin{equation}
+\hat{\delta}_{\rm VR} = \frac{6^{2/3}\,\pi\,{\mit\Gamma}(5/6)}{{\mit\Gamma}(1/6)}\,\frac{\tau_H^{1/3}}{\tau_R^{1/6}\,\tau_\varphi^{1/6}}
+\end{equation}
+is the viscous-resistive layer width (normalized to $r_s$). Here, $\omega_{\perp\,e}$ is defined in Eq.~(\ref{e354}), and
+${\mit\Delta}\omega_E$ is the modification to the ${\bf E}\times{\bf B}$ frequency generated at the resonant surface by
+the electromagnetic torques that develop there in response to the error-field. Likewise, in the
+diffusive-resistive regime we have
+\begin{equation}
+{\mit\Delta}_{\rm DR} = {\rm i}\,\tau_{\rm DR}\,(\omega_{\perp\,e}+{\mit\Delta}\omega_E),
+\end{equation}
+where $\tau_{\rm DR} = \tau_R\,\hat{\delta}_{\rm DR}$, and
+\begin{equation}
+\hat{\delta}_{\rm DR} = \frac{2\pi\,{\mit\Gamma}(3/4)}{{\mit\Gamma}(1/4)\,[1+\lambda_e\,\tau/(1+\tau)]^{1/4}}\,
+\frac{\tau_H^{1/2}}{(d_\beta/r_s)^{1/2}\,\tau_R^{1/4}\,\tau_\perp^{1/4}}
+\end{equation}
+is the diffusive-resistive layer width (normalized to $r_s$).
+
+We can combine the previous two results to give the composite layer response equation
+\begin{equation}\label{e389}
+{\mit\Delta} = {\rm i}\,\tau_s\,(\omega_{s\,0}+ {\mit\Delta}\omega_E),
+\end{equation}
+where $\tau_s=\tau_R\,\hat{\delta}$, 
+\begin{equation}
+\hat{\delta} = \frac{\hat{\delta}_{\rm VR}\,\hat{\delta}_{\rm DR}}{\hat{\delta}_{\rm VR} + \hat{\delta}_{\rm DR}},
+\end{equation}
+and 
+$\omega_{s\,0}= \omega_{\perp\,e}$.
+Here, $\omega_{\perp\,e}$ is understood to take its unperturbed (by any electromagnetic torques that
+develop in the resonant layer) value.
+
+According to Eq.~(\ref{e389}), the resonant layer responds to the error-field
+perturbation in an analogous manner to a thin, rigid, resistive wall whose resistivity matches that of the plasma at the
+resonant surface, and whose radial thickness is $\delta=r_s\,\hat{\delta}$. Note, however, that the effective wall corotates with the
+electron fluid at the resonant surface. Moreover, it is the rotation of the effective wall that generates the shielding current.
+
+Equations~(\ref{e110}), (\ref{e383}) and (\ref{e389}) yield
+\begin{equation}\label{e391}
+{\mit\Delta\Psi}_s ={\rm i}\,\tau_s\,(\omega_{s\,0}+{\mit\Delta}\omega_E)\,{\mit\Psi}_s,
+\end{equation}
+and 
+\begin{equation}\label{e392}
+{\mit\Psi}_s=\frac{{\mit\Psi}_v}{1+ {\rm i}\,\tau_s\,(\omega_{s\,0}+ {\mit\Delta}\omega_E)/(-{\mit\Delta}_s')}.
+\end{equation}
+Now, in a conventional ohmically-heated tokamak plasma, $\tau_s\,\omega_{s\,0}\gg (-{\mit\Delta}_s')$. Consequently, according to the previous equation, the
+shielding current that develops at the resonant surface, in response to the local plasma rotation, is strong enough to largely
+suppress error-field-driven magnetic reconnection (i.e., $|{\mit\Psi}_s|\ll |{\mit\Psi}_v|$). However, the shielding current also gives rise to a localized electromagnetic
+locking torque at the resonant surface  that acts to slow the plasma rotation.
+
+\subsection{Torque Balance}
+According to the analysis of Ref.~\onlinecite{nelson} (see, in particular, Appendix C), the shift in the ${\bf E}\times{\bf B}$ frequency at the resonant
+surface induced by the error-field locking torque can be written
+\begin{equation}\label{e108}
+{\mit\Delta}\omega_E = -\sum_{p=1,\infty}(\alpha_p + \beta_p),
+\end{equation}
+where
+\begin{align}
+\alpha_p &= \frac{(r_s/a)^2\,[J_1(j_{1\,p}\,r_s/a)]^{\,2}}{[J_2(j_{1\,p})]^2\,[1+(\tau_\theta/\tau_\varphi)\,(r_s/a)^2\,j_{1\,p}^{\,2}]}
+\left(\frac{\tau_\theta}{\tau_H^{\,2}}\right){\rm Im}\!\left(\frac{{\mit\Delta\Psi}_s}{{\mit\Psi}_s}\right)|{\mit\Psi}_s|^2\left(\frac{L_s}{B_z\,r_s^{\,2}}\right)^2,\\[0.5ex]
+\beta_p &= \left(\frac{\epsilon_s}{q_s}\right)^2\frac{[J_0(j_{0\,p}\,r_s/a)]^{\,2}}{[J_1(j_{0\,p})]^2\,j_{0\,p}^{\,2}}\left(\frac{\tau_\varphi}{\tau_H^{\,2}}\right){\rm Im}\!\left(\frac{{\mit\Delta\Psi}_s}{{\mit\Psi}_s}\right)|{\mit\Psi}_s|^2\left(\frac{L_s}{B_z\,r_s^{\,2}}\right)^2
+.\label{e110dx}
+\end{align}
+Here, $\tau_\theta$ is the neoclassical poloidal flow-damping time evaluated at the resonant surface, $J_m(z)$ is a Bessel function, 
+and $j_{m\,p}$ denotes the $p$th zero of $J_m(z)$. Making use of Eqs.~(\ref{e391}), (\ref{e389}), and the previous two equations,
+we obtain
+\begin{align}\label{e109d}
+\alpha_p &= \frac{(r_s/a)^2\,[J_1(j_{1\,p}\,r_s/a)]^{\,2}}{[J_2(j_{1\,p})]^2\,[1+(\tau_\theta/\tau_\varphi)\,(r_s/a)^2\,j_{1\,p}^{\,2}]}
+\left(\frac{\tau_\theta}{\tau_H^{\,2}}\right)\frac{\tau_s\,(\omega_{s\,0}+{\mit\Delta}\omega_E)}{1+\tau_s^{\,2}\,(\omega_{s\,0}+{\mit\Delta}\omega_E)^2/(-{\mit\Delta}_s')^2}\left(\frac{w_v}{r_s}\right)^4,\\[0.5ex]
+\beta_p &= \left(\frac{\epsilon_s}{q_s}\right)^2\frac{[J_0(j_{0\,p}\,r_s/a)]^{\,2}}{[J_1(j_{0\,p})]^2\,j_{0\,p}^{\,2}}
+\left(\frac{\tau_\varphi}{\tau_H^{\,2}}\right)\frac{\tau_s\,(\omega_{s\,0}+{\mit\Delta}\omega_E)}{1+\tau_s^{\,2}\,(\omega_{s\,0}+{\mit\Delta}\omega_E)^2/(-{\mit\Delta}_s')^2}\left(\frac{w_v}{r_s}\right)^4,\label{e110d}
+\end{align}
+where
+\begin{equation}
+w_v = \left(\frac{L_s\,|{\mit\Psi}_v|}{B_z}\right)^{1/2}
+\end{equation}
+is one quarter of the full width of the vacuum magnetic island chain that the error-field would drive at the resonant surface were there no
+shielding current. In Eq.~(\ref{e108}), the term $\sum_{p=1,\infty}(-\alpha_p)$ denote the shift in the ${\bf E}\times{\bf B}$ frequency at the resonant surface that is
+ induced by changes in the {\em poloidal}\/ ion fluid velocity, whereas  $\sum_{p=1,\infty}(-\beta_p)$ denote the shift that induced by  changes in the {\em toroidal}\/  ion fluid velocity.
+
+Making use of the identities 
+\begin{align}\label{e417a}
+\lim_{\epsilon\rightarrow 0}\sum_{p=1,\infty} \frac{\sqrt{\epsilon}\,[J_1(j_{1\,p}\,x)]^{2}}{[J_2(j_{1\,p})]^2\,(1+\epsilon\,j_{1\,p}^2)}
+&=\frac{1}{4\,x},\\[0.5ex]
+\sum_{p=1,\infty} \frac{[J_0(j_{0\,p}\,x)]^2}{[J_1(j_{0\,p}\,x)]^2\,j_{0\,p}^{\,2}} =\frac{1}{2}\,\ln\!\left(\frac{1}{x}\right),\label{e418a}
+\end{align}
+Eqs.~(\ref{e108}), (\ref{e109d}), and (\ref{e110d}) yield
+\begin{equation}\label{torque}
+{\mit\Delta}\omega_E = \frac{1}{4}\left(\frac{\epsilon_s}{q_s}\right)^2\left(\frac{\tau_V}{\tau_H^{\,2}}\right)\frac{\tau_s\,(\omega_{s\,0}+{\mit\Delta}\omega_E)}{1+\tau_s^{\,2}\,(\omega_{s\,0}+{\mit\Delta}\omega_E)^2/(-{\mit\Delta}_s')^2}\left(\frac{w_v}{r_s}\right)^4,
+\end{equation}
+where
+\begin{equation}
+\tau_V = \left(\frac{q_s}{\epsilon_s}\right)^2\,(\tau_\theta\,\tau_\varphi)^{1/2} + 2\,\ln\!\left(\frac{a}{r_s}\right)\tau_\varphi.
+\end{equation}
+Here, we have assumed that $\tau_\theta\ll \tau_\varphi$ (as is invariably the case in tokamak plasmas).
+
+The torque balance equation, (\ref{torque}), can be written in the nondimensional form 
+\begin{equation}\label{e394}
+T_{VS}(v)= T_{EM}(v),
+\end{equation}
+where
+\begin{align}
+v&=\frac{\omega_{s\,0}+{\mit\Delta}\omega_E}{\omega_{s\,0}},\\[0.5ex]
+T_{\rm VS}(v) &= 1- v,\\[0.5ex]
+T_{\rm EM}(v) &= \frac{1}{4}\,\frac{v}{\zeta_s^{2}+v^2}
+\left(\frac{w_v}{w_{v\,{\rm crit}}}\right)^4,\\[0.5ex]
+\zeta_s &= \frac{(-{\mit\Delta}'_s)}{\tau_s\,\omega_{s\,0}}\ll 1,\\[0.5ex]
+\frac{w_{v\,{\rm crit}}}{r_s}&= \left[\frac{1}{(-{\mit\Delta}'_s)}\left(\frac{q_s}{\epsilon_s}\right)\left(\frac{\tau_s}{\tau_V}\right)^{1/2}(\omega_{s\,0}\,\tau_H)\right]^{1/2}.
+\end{align}
+
+In Eq.~(\ref{e394}), the dimensionless
+parameter $v$ takes the value unity when the plasma (i.e., electron fluid) rotation at the resonant surface is unmodified by
+the electromagnetic locking torque, and zero when the electromagnetic locking torque has reduced the rotation to zero. The electromagnetic torque itself
+is represented  by the function $T_{\rm EM}(v)$, whereas the viscous restoring torque that acts to oppose changes in the plasma rotation is represented
+by the function $T_{\rm VS}(v)$. Note that the viscous restoring torque varies linearly with $v$,
+whereas the electromagnetic locking torque varies with $v$ in a nonmonotonic manner.
+
+The solutions of the torque balance equation (\ref{e394}) correspond to the crossing points of the viscous and electromagnetic torque
+curves. If reduced vacuum island width, $w_v$, lies below
+the critical value $w_{v\,{\rm crit}}$ then there are three crossing points. However, the intermediate crossing point corresponds to
+a dynamically unstable equilibrium. Hence, we deduce that there are two physical solution branches of the torque
+balance equation. The large-$v$ solution branch corresponds to  so-called {\em shielded}\/ solutions in which the plasma
+rotation at the resonant surface is large enough to strongly suppress driven magnetic reconnection. The small-$v$
+solution branch corresponds to so-called {\em unshielded}\/ solutions  in which the plasma rotation at the resonant surface is
+too weak to suppress driven magnetic reconnection.\cite{rf1993,rf1998} 
+On the shielded solution branch, Eq.~(\ref{e394}) possesses the approximate solution
+\begin{equation}
+v \simeq \frac{1}{2}\left(1-\left[1-\left(\frac{w_v}{w_{v\,{\rm crit}}}\right)^4\right]^{1/2}
+\right).
+\end{equation}
+It can be seen that as the vacuum island width increases, the plasma rotation at the resonant surface decreases. However, when
+$w_v$ attains the critical value $w_{v\,{\rm crit}}$, and the rotation is reduced to  half of its
+original value, the shielded solution branch ceases to exist, and there is a bifurcation to the unshielded solution branch.\cite{rf1993,rf1998} The bifurcation is associated with a sudden decrease in the plasma rotation at the resonant surface, and a sudden
+increase in the driven reconnected magnetic flux, and is identified with the error-field penetration phenomenon observed in tokamak
+experiments.
+
+It is convenient to parameterize the critical error-field required to trigger  penetration in terms of the critical
+vacuum radial magnetic field, $b_r$, that must be driven at the resonant surface. It is easily demonstrated that
+\begin{equation}
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)= (n\,\epsilon_s\,s_s)\left(\frac{w_{v\,{\rm crit}}}{r_s}\right)^2,
+\end{equation}
+which implies that
+\begin{equation}
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)= \frac{m\,s_s}{(-{\mit\Delta}_s')}\left(\frac{\tau_s}{\tau_V}\right)^{1/2}\,(\omega_{s\,0}\,\tau_H).
+\end{equation}
+Note that the critical radial field needed to trigger error-field
+penetration increases linearly with the unperturbed plasma rotation at the resonant surface, which is parameterized by $\omega_{s\,0}$.
+
+\subsection{Scaling Analysis}
+The aim of this section is to use the previous analysis to predict the scaling of the error-field penetration
+threshold with the standard dimensionless scaling parameters\,\cite{connor}
+\begin{align}
+\rho_\ast &= \frac{T_0^{1/2}\,m_i^{1/2}}{e\,B_z\,L_s},\label{e428}\\[0.5ex]
+\nu_\ast &= \frac{L_s\,n_0\,e^2\,\eta_\parallel}{m_e^{1/2}\,T_0^{1/2}},\\[0.5ex]
+\beta_\ast&=\frac{\mu_0\,n_0\,T_0}{B_z^{\,2}},\label{e430}
+\end{align}
+where $T_0=p_0/n_0$. In the following, for the sake of simplicity, we
+shall assume that $T_i=T_e=T_0$, $\omega_{s\,0}=\omega_\ast$, and $-(d\ln p/dr)_{r_s} = 1/r_s$. We shall also neglect ${\cal O}(1)$
+constants such as $m$, $s_s$, $\eta_e$, $\eta_i$, $\lambda_e$, $\tau$, $\pi$, $\ln(r_s/a)$, et cetera.
+
+We can  write 
+\begin{equation}
+\frac{1}{\tau_{\theta}} = \left(\frac{q_s}{\epsilon_s}\right)^2\,\left(\frac{\mu_{00}^i}{\tau_{i}}\right),
+\end{equation}
+ where
+$\tau_i$ is the Braginskii ion collision time, and $\mu_{00}^i$ is a dimensionless neoclassical viscosity coefficient defined in Ref.~\onlinecite{nelson}.
+Both quantities are evaluated at the resonant surface.
+
+In an ohmically-heated tokamak
+plasma, the energy confinement timescale, $\tau_E$, satisfies the constraint
+\begin{equation}
+\frac{n_0\,T_0}{\tau_E} = \eta_\parallel\left(\frac{B_z}{\mu_0\,L_s}\right)^2,
+\end{equation}
+which is obtained by equating the energy loss rate to the ohmic heating rate. Let us assume that the momentum confinement
+time, $\tau_\varphi$, and the particle/energy confinement time, $\tau_\perp$, are both equal to $\tau_E$, as is generally
+(approximately) the case in ohmically-heated tokamak plasmas.\cite{iter}
+
+It is easily demonstrated that
+\begin{align}
+\omega_{s\,0}\,\tau_H&\simeq \left(\frac{q_s}{\epsilon_s}\right)^2\rho_\ast\,\beta_\ast^{\,1/2},\\[0.5ex]
+\frac{\tau_H}{\tau_R}&\simeq \left(\frac{q_s}{\epsilon_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/2}\rho_\ast^{\,2}\,\nu_\ast\,\beta_\ast^{-1/2},\\[0.5ex]
+\frac{\tau_\varphi}{\tau_R} = \frac{\tau_\perp}{\tau_R} &\simeq \left(\frac{q_s}{\epsilon_s}\right)^2\beta_\ast,\\[0.5ex]
+\frac{\tau_i}{\tau_R} &\simeq  \left(\frac{q_s}{\epsilon_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/2}\rho_\ast^{\,2}\,\beta_\ast^{-1},\\[0.5ex]
+\frac{d_\beta}{r_s} &\simeq \left(\frac{q_s}{\epsilon_s}\right)\rho_\ast.
+\end{align} 
+Hence, we deduce that 
+\begin{align}
+\hat{\delta}_{\rm VR} = \left(\frac{\tau_{\rm VR}}{\tau_R}\right) \simeq\left(\frac{\tau_H}{\tau_R}\right)^{1/3}\left(\frac{\tau_R}{\tau_\varphi}\right)^{1/6}&\simeq \left(\frac{q_s}{\epsilon_s}\right)^{1/3}\left(\frac{m_e}{m_i}\right)^{1/6}\rho_\ast^{\,2/3}\,\nu_\ast^{\,1/3}\,\beta_\ast^{-1/3},\\[0.5ex]
+\hat{\delta}_{\rm DR} = \left(\frac{\tau_{\rm DR}}{\tau_R}\right) \simeq \left(\frac{\tau_H}{\tau_R}\right)^{1/2}\left(\frac{\tau_R}{\tau_\perp}\right)^{1/4}\left(\frac{r_s}{d_\beta}\right)^{1/2}&\simeq \left(\frac{m_e}{m_i}\right)^{1/4}\rho_\ast^{\,1/2}\,\nu_\ast^{\,1/2}\,\beta_\ast^{-1/2},\\[0.5ex]
+\frac{\sqrt{\tau_\varphi\, \tau_i/\mu_{00}^i}}{\tau_R}&\simeq \left(\frac{q_s}{\epsilon_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/4}\,\rho_\ast.
+\end{align}
+Here, we have treated $\mu_{00}^i$ as an ignorable ${\cal O}(1)$ constant that is independent of $\rho_\ast$, $\nu_\ast$, and
+$\beta_\ast$ (as is indeed the case provided that the plasma at the resonant surface lies in the banana collisionality regime).\cite{hs}
+
+There are four error-field penetration regimes, depending on whether the plasma response in the resonant layer lies 
+in the viscous-resistive or the diffusive-resistive regime, and depending on whether the change in the ${\bf E}\times{\bf B}$
+frequency at the resonant surface, induced by the electromagnetic locking torque,  is
+predominately due to a toroidal or a poloidal shift in the local ion fluid velocity. The plasma response in the resonant layer is in the
+viscous-resisitive, rather than the diffusive-resistive, regime when $\tau_{\rm VR}<\tau_{\rm DR}$, or
+\begin{equation}
+\rho_\ast < \left(\frac{\epsilon_s}{q_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/2}\nu_\ast\,\beta_\ast^{-1},
+\end{equation}
+and vice versa. The change in the ${\bf E}\times{\bf B}$ frequency at the resonant surface is predominately due to a toroidal, rather than poloidal, ion fluid velocity shift when
+\begin{equation}
+\rho_\ast < \left(\frac{\epsilon_s}{q_s}\right)\left(\frac{m_i}{m_e}\right)^{1/4}\beta_\ast,
+\end{equation}
+and vice versa.
+
+Let us define 
+\begin{align}
+\hat{\rho}_\ast&= \left(\frac{q_s}{\epsilon_s}\right)\left(\frac{m_e}{m_i}\right)^{1/4}\rho_\ast,\\[0.5ex]
+\hat{\nu}_\ast&=\left(\frac{\epsilon_s}{q_s}\right)\left(\frac{m_e}{m_i}\right)^{3/4}\nu_\ast.
+\end{align}
+As is illustrated in Fig.~\ref{f6}, the {\em viscous-resistive-toroidal regime}\/ (i.e., a viscous-resistive layer response
+combined with a predominately toroidal change in the ion fluid velocity) corresponds to $\hat{\rho}_\ast < \beta_\ast^{-1}\,\nu_\ast$ 
+and $\hat{\rho}_\ast <\beta_\ast$, the {\em viscous-resisitive-poloidal regime}\/ corresponds to 
+ $\hat{\rho}_\ast<\beta_\ast^{-1}\,\nu_\ast$ and $\hat{\rho}_\ast > \beta_\ast$, the {\em diffusive-resisitive-poloidal regime}\/ corresponds to  
+ $\hat{\rho}_\ast>\beta_\ast^{-1}\,\nu_\ast$ and $\hat{\rho}_\ast > \beta_\ast$, and the {\em diffusive-resistive-toroidal regime}\/ corresponds to   
+ $\hat{\rho}_\ast>\beta_\ast^{-1}\,\nu_\ast$ and $\hat{\rho}_\ast < \beta_\ast$.
+It can be seen that higher/lower plasma collisionality (i.e., $\nu_\ast$) favors the viscous-resistive/diffusive-resistive response regime, whereas a
+larger/smaller ion sound radius (i.e., $\rho_\ast$) favors poloidal/toroidal changes in the ion fluid velocity. Finally, higher/lower plasma
+pressure (i.e., $\beta_\ast$) 
+favors the diffusive-resistive/viscous-resistive response regime and toroidal/poloidal changes in the ion fluid velocity.
+
+In the viscous-resistive-toroidal response regime, the critical vacuum radial magnetic
+field at the resonant surface required to
+trigger error-field penetration is\,\cite{cole}
+\begin{equation}\label{e444}
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm VR}-\varphi} \simeq \left(\frac{q_s}{\epsilon_s}\right)^{7/6}\left(\frac{m_e}{m_i}\right)^{1/12}
+\rho_\ast^{\,4/3}\,\nu_\ast^{\,1/6}\,\beta_\ast^{-1/6},
+\end{equation}
+where we have treated $-{\mit\Delta}_s'$ as an ignorable ${\cal O}(1)$ parameter. Likewise,  the critical
+field required to trigger penetration in the viscous-resistive-poloidal regime is
+\begin{equation}
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm VR}-\theta} \simeq  \left(\frac{q_s}{\epsilon_s}\right)^{2/3}\left(\frac{m_e}{m_i}\right)^{-1/24}
+\rho_\ast^{\,5/6}\,\nu_\ast^{\,1/6}\,\beta_\ast^{\,1/3}.
+\end{equation}
+The critical field required to trigger penetration in the diffusive-resistive-poloidal regime is
+\begin{equation}
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm DR}-\theta} \simeq  \left(\frac{q_s}{\epsilon_s}\right)^{1/2}\left(\frac{m_e}{m_i}\right)^{0}
+\rho_\ast^{\,3/4}\,\nu_\ast^{\,1/4}\,\beta_\ast^{\,1/4}.
+\end{equation}
+Finally, the critical field 
+required to  trigger penetration in the diffusive-resistive-toroidal regime is
+\begin{equation}
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm DR}-\varphi} \simeq  \left(\frac{q_s}{\epsilon_s}\right)^{}\left(\frac{m_e}{m_i}\right)^{1/8}
+\rho_\ast^{\,5/4}\,\nu_\ast^{\,1/4}\,\beta_\ast^{-1/4}.\label{e447}
+\end{equation}
+Generally speaking, ohmically-heated tokamak plasmas all  have similar $\beta_\ast$ values. However,
+both $\nu_\ast$ and $\rho_\ast$ are smaller in devices of larger physical size. Hence, Eqs.~(\ref{e444})--(\ref{e447})
+imply that the error-field penetration threshold is smaller in larger devices.
+
+Let $n$, $T$, $B$, and $R$ represent the typical electron number density, plasma temperature, toroidal magnetic field-strength,
+and physical dimension (i.e., major radius) of an ohmically-heated tokamak. Using $\rho_\ast\sim T^{1/2}\,B^{-1}\,R^{-1}$, 
+$\nu_\ast\sim n\,T^{-2}\,R$, and $\beta_\ast\sim n\,T\,B^{-1}$,
+we deduce that
+\begin{align}
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm VR}-\varphi} &\propto n^{0}\,T^{\,1/6}\,B^{-1}\,R^{-7/6},\\[0.5ex]
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm VR}-\theta} &\propto n^{1/2}\,T^{\,5/12}\,B^{-3/2}\,R^{-2/3},\\[0.5ex]
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm DR}-\theta} &\propto n^{1/2}\,T^{\,1/8}\,B^{-5/4}\,R^{-1/2},\\[0.5ex]
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm DR}-\varphi} &\propto n^{0}\,T^{-1/8}\,B^{-3/4}\,R^{-1}.
+\end{align}
+It can be seen that the error-field penetration threshold exhibits no explicit dependence on the plasma
+density in regimes in which the change in the ${\bf E}\times {\bf B}$ frequency at the resonant surface is predominately due to a toroidal ion fluid 
+velocity shift.\cite{rf1998,cole}. On the other hand, the penetration threshold
+scales as $n^{1/2}$ in regimes in which the change in the ${\bf E}\times{\bf B}$ frequency at the resonant surface is predominately due to a  poloidal ion fluid velocity shift.
+An $n^{1/2}$ scaling of the penetration threshold has been observed in a number of tokamak
+experiments.\cite{hender,wang1,wang2,lazzaro,park} 
+On the other hand, some experiments have reported a linear scaling of the penetration threshold with $n$.\cite{scoville,wolf,wolfe,howell,menard,buttery} The latter
+scaling is difficult to account for on the basis of the theory presented in this section.
+
+In order to make further progress, we need to adopt a specific scaling model for the energy confinement timescale, $\tau_E$. Let us adopt
+the following slightly modified version of the well-known neo-Alcator scaling law for low-density ohmically-heated tokamak plasmas:\cite{goldston,simmet,rf2012} 
+\begin{equation}
+\tau_E\propto n\,R^{\,13/4}.
+\end{equation}
+(The modification is to ensure that the scaling law is consonant with the Connor-Taylor constraints.\cite{connor})
+It follows that
+\begin{align}
+\nu_\ast&\propto \rho_\ast^{\,2/3}\,\beta_\ast,\\[0.5ex]
+T&\propto B^{\,4/5}\,R^{\,1/2}.
+\end{align}
+Hence, we deduce that 
+\begin{align}\label{e455}
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm VR}-\varphi} &\propto n^{0}\,B^{-13/15}\,R^{-13/12},\\[0.5ex]
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm VR}-\theta} &\propto n^{1/2}\,B^{-7/6}\,R^{-11/24},\\[0.5ex]
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm DR}-\theta} &\propto n^{1/2}\,B^{-23/20}\,R^{-7/16},\\[0.5ex]
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm DR}-\varphi} &\propto n^{0}\,B^{-17/20}\,R^{-17/16}.\label{e458}
+\end{align}
+Equations~(\ref{e455})--(\ref{e458}) confirm the $n^{0}$ scaling of the error-field penetration threshold in regimes in which the change in the ${\bf E}\times{\bf B}$ frequency at the resonant surface is predominately due to a toroidal
+ion fluid velocity shift, and the $n^{1/2}$ scaling when the change is predominately due to a poloidal ion fluid velocity shift.
+All regimes exhibit a roughly linear inverse scaling with increasing magnetic field-strength.
+On the other hand, the regimes in which the threshold scales as $n^{1/2}$ exhibit a
+weaker inverse scaling with machine size (roughly $R^{-1/2}$) than the regimes in which the threshold scales as $n^0$ (which
+exhibit an approximate $R^{-1}$ scaling). (In fact, it is easily demonstrated, from the previous analysis, that if 
+$b_{r\,{\rm crit}}/B_z\propto n^{\,\alpha_n}\,B^{\,\alpha_B}\,R^{\,\alpha_R}$ then $\alpha_R = 2\,\alpha_n+1.25\,\alpha_B$.\cite{buttery})
+
+\section{Summary and Discussion}
+We have employed a slightly improved version of the four-field model derived in Ref.~\onlinecite{fw} to map out  all of the
+two-fluid response regimes of a  linear tearing layer that interacts with an externally generated resonant magnetic perturbation,  in a large aspect-ratio tokamak plasma, 
+taking into account realistic levels of perpendicular particle transport. This analysis is a generalization of that
+presented in Ref.~\onlinecite{cole}. Our results are summarized in Figs.~\ref{f1} and
+\ref{f2}. We find that there are four constant-$\psi$ response regimes: the resistive-inertial, the viscous-resistive, the
+semi-collisional, and the diffusive-resistive. In addition, there are three nonconstant-$\psi$ response regimes: the inertial, the
+viscous-inertial, and the diffusive-inertial. In general, both the number and the mutual arrangement of the various response regimes shown
+in Figs.~\ref{f1} and \ref{f2} are different from those reported in Ref.~\onlinecite{cole}. Moreover, these differences are a direct 
+consequence of including realistic levels of perpendicular particle transport in the analysis. In particular, perpendicular particle
+diffusivity plays an explicit role in the diffusive-resistive and the diffusive-inertial response regimes.
+
+We have employed our improved analysis to map out all of the growth-rate regimes of a non-interacting low-mode-number
+(but not $m=1$) tearing mode in a large aspect-ratio tokamak plasma. We find that there are four growth-rate regimes:
+the resistive-inertial, the viscous-resistive, the semi-collisional, and the diffusive-resistive. The extents of these regimes are illustrated in Fig.~\ref{f3}. 
+Realistic levels of perpendicular particle diffusion significantly modify the growth-rate in the resistive-inertial
+regime (which is the original Furth, Killeen, and Rosenbluth regime), and also affect the growth-rate in the diffusive-resistive regime. 
+Perpendicular transport also suppresses spurious tearing mode branches in which the mode co-rotates with the MHD, or with the ion,
+fluid at the resonant surface, rather than with the electron fluid.
+
+Finally, we have used our improved analysis to determine the scaling of the error-field penetration threshold with machine parameters in 
+large aspect-ratio, ohmically heated, tokamak plasmas. We find that if the change in the ${\bf E}\times {\bf B}$ frequency at the the resonant surface that permits the
+driven mode to lock to the error-field is predominately caused by a  shift in the  {\em poloidal}\/ ion fluid velocity (which is entirely possible,
+even in the presence of strong poloidal flow damping) then the threshold exhibits an $n^{1/2}$ scaling with particle
+number density. Such a scaling is consistent with some experimental observations.
+
 \section*{Acknowledgements}
-This research was directly funded by the U.S.\ Department of Energy, Office of Science, Office of Fusion Energy Sciences,  under contract DE-FG02-04ER54742,
+This research was directly funded by the U.S.\ Department of Energy, Office of Science, Office of Fusion Energy Sciences,  under  contracts DE-FG02-04ER54742 and DE-SC0021156.
+
+\section*{Disclaimer} This report was prepared as an account of work sponsored by an agency of the United States Government.
+Neither the United States Government nor any agency thereof, nor any of their employees, makes any warranty, express or implied, or assumes any legal liability or responsibility for the accuracy, completeness, or usefulness of any information, apparatus, product, or process disclosed, or represents that its use would not infringe privately owned rights.
+Reference herein to any specific commercial product, process, or service by trade name, trademark, manufacturer, or otherwise does not necessarily constitute or imply its endorsement, recommendation, or favoring by the United States Government or any agency thereof.
+The views and opinions of authors expressed herein do not necessarily state or reflect those of the United States Government or any agency thereof.
+
+\section*{Data Availability Statement}
+The data that support the findings of this study are available from the corresponding author upon reasonable request.
 
@@
 
-\bibitem{error1} J.T.~Scoville, and R.J.~La\,Haye, Nucl.\ Fusion {\bf 43}, 250 (2003).
+\bibitem{wes} J.A.~Wesson, Nucl.\ Fusion {\bf 18}, 87 (1978).
+
+\bibitem{wes1} J.A.~Wesson, R.D.~Gill, M.~Hugon, F.C.~Sch\"{u}ller, J.A.~Snipes, D.J.~Ward, et al., Nucl.\ Fusion {\bf 29}, 641 (1989).
+
+\bibitem{vries} P.C.~de\,Vries, M.F.~Johnson, B.~Alper, P.~Buratti, T.C.~Hender, H.R.~Koslowski, et al., Nucl.\ Fusion {\bf 51}, 053018 (2011).
+
+\bibitem{ara} G.~Ara, B.~Basu, B.~Coppi, G.~Laval, M.N.~Rosenbluth, and B.V.~Waddell, Ann.\ Phys.\ (NY) {\bf 112}, 443 (1978).
+
+\bibitem{drake} J.F.~Drake, and Y.C.~Lee, Phys.\ Fluids {\bf 20}, 1341 (1977).
+
+\bibitem{wal} F.L.~Waelbroeck, Phys.\ Plasmas {\bf 10}, 4040 (2003).
+
+\bibitem{cole} A.~Cole, and R.~Fitzpatrick, Phys.\ Plasmas {\bf 13}, 032503 (2006).
+
+\bibitem{fw} R.~Fitzpatrick, and F.L.~Waelbroeck, Phys. Plasmas {\bf 12}, 022307 (2005).
+
+\bibitem{haz} R.D.~Hazeltine, M.~Kotschenreuther, and P.G.~Morrison, Phys.\ Fluids {\bf 28}, 2466 (1985).
+
+\bibitem{rf1993} R.~Fitzpatrick, Nucl.\ Fusion {\bf 33}, 1049 (1993).
+
+\bibitem{fkr} H.P.~Furth, J.~Killeen, and M.N.~Rosenbluth, Phys.\ Fluids {\bf 6}, 459 (1963).
+
+\bibitem{ber} F.L.~Waelbroeck,  I.~Joseph, E.~Nardon, M.~B\'{e}coulet, and R.~Fitzpatrick, Nucl.\ Fusion {\bf 52}, 074004 (2012).
+
+\bibitem{rf1998} R.~Fitzpatrick, Phys.\ Plasmas {\bf 5}, 3325 (1998).
+
+\bibitem{bond} A.~Bondeson, and M.~Persson, Phys.\ Fluids {\bf 29}, 2997 (1986).
+
+\bibitem{boozer} A.H.~Boozer, Phys.\ Plasmas {\bf 3}, 4620 (1996).
+
+\bibitem{scoville} J.T.~Scoville, R.J.~La\,Haye, A.G.~Kellman, T.H.~Osborne, R.D.~Stambaugh, E.J.~Strait, and T.S.~Taylor, Nucl.\ Fusion {\bf 31}, 875 (1991).
+
+\bibitem{hender} T.C.~Hender, R.~Fitzpatrick, A.W.~Morris, P.G.~Carolan, R.D.~Durst, T.~Edlington, et  al., Nucl.\ Fusion {\bf 32}, 2091 (1992).
+
+\bibitem{fishpool} G.M.~Fishpool, and P.S.~Haynes, Nucl.\ Fusion {\bf 34}, 109 (1994).
+
+\bibitem{wolf} R.C.~Wolf, W~Biel, M.F.M.~de\,Bock, K.H.~Finken, S.~G\"{u}nter, G.M.D.~Hogeweijet, et al., Nucl.\ Fusion {\bf 45}, 1700 (2005).
+
+\bibitem{wolfe} S.M.~Wolfe,  I.H.~Hutchinson, R.S.~Granetz, J.~Rice, and A.~Hubbard, Phys.\ Plasmas {\bf 12}, 056110 (2005).
+
+\bibitem{howell} D.F.~Howell, T.C.~Hender, and G.~Cunningham, Nucl.\ Fusion {\bf 47}, 1336 (2007).
+
+\bibitem{menard} J.E.~Menard, R.E.~Bell, D.A.~Gates, S.P.~Gerhardt, J.-K.~Park, S.A.~Sabbagh, et al., Nucl.\ Fusion {\bf 50}, 045008 (2010).
+
+\bibitem{wang1} N.~Wang, B.~Rao, Q.~Hu, Y.~Ding, Z.~Chen1, L.~Gao, et al., Nucl.\ Fusion {\bf 54}, 064014 (2014).
+
+\bibitem{wang2} H.-H.~Wang, Y.-W.~Sun, T.-H.~Shi, Q.~Zang, Y.-Q.~Liu, X.~Yang, et al., Nucl.\ Fusion {\bf 58}, 056024 (2018).
+
+\bibitem{nelson} R.~Fitzpatrick, and A.O.~Nelson,  Phys.\ Plasmas {\bf 27}, 072501 (2020).
+
+\bibitem{connor} J.W.~Connor, and J.B.~Taylor, Nucl.\ Fusion {\bf 17}, 1047 (1977).
+
+\bibitem{iter} ITER Physics Basis Editors, Nucl.\ Fusion {\bf 39}, 2175 (1999).
+
+\bibitem{hs} S.P.~Hirshman, and D.J.~Sigmar, Nucl.\ Fusion {\bf 21}, 1079 (1981).
+
+\bibitem{lazzaro} E.~Lazzaro, R.J.~Buttery, T.C.~Hender, P.~Zanca, R.~Fitzpatrick, 
+M.~Bigi, et al., Phys.\ Plasmas {\bf 9}, 3906 (2002).
+
+\bibitem{park} J.-K.~Park, J.E.~Menard, S.P.~Gerhardt, R.J.~Buttery, S.A.~Sabbagh, R.E.~Bell, and B.P.~LeBlanc, Nucl.\ Fusion {\bf 52}, 023004 (2012).
+
+\bibitem{buttery} R.J.~Buttery, M.~De'\,Benedetti, D.A.~Gates, Y.~Gribov, T.C.~Hender, R.J.~La\,Haye, et al., Nucl.\ Fusion {\bf 39}, 1827 (1999).
+
+\bibitem{goldston} R.J.~Goldston, Plasma Phys.\ Control.\ Fusion {\bf 26}, 87 (1984).
+
+\bibitem{simmet} E.E.~Simmet, and the ASDEX Team, Plasma Phys.\ Control.\ Fusion {\bf 38}, 689 (1996).
+
+\bibitem{rf2012} R.~Fitzpatrick, Plasma Phys.\ Control.\ Fusion {\bf 54}, 094002 (2012).
+
 \end{thebibliography}
 
-%\begin{figure}
-%\includegraphics[height=6in]{fig2.pdf}
-%\caption{}
-%\end{figure}
+\newpage 
+\begin{figure}
+\centerline{\includegraphics[width=0.95\textwidth]{RegimeI.pdf}}
+\caption{Linear resonant plasma response regimes in $Q$-$P$ space for the case $D=0.9$. The various regimes are
+the diffusive-resisitive (DR), the semi-collisional (SC), the resistive-inertial (RI), the viscous-resistive (VR), the viscous-inertial
+(VI), and the inertial (I).}\label{f1}
+\end{figure}
+
+\begin{figure}
+\centerline{\includegraphics[width=0.95\textwidth]{RegimeII.pdf}}
+\caption{Linear resonant plasma response regimes in $Q$-$P$ space for the case $D=1.2$. The various regimes are
+the diffusive-resisitive (DR), the semi-collisional (SC), the diffusive-inertial (DI), the viscous-resistive (VR), the viscous-inertial
+(VI), and the inertial (I).}\label{f2}
+\end{figure}
+
+\begin{figure}
+\centerline{\includegraphics[width=0.95\textwidth]{RegimeIII.pdf}}
+\caption{Linear tearing mode growth-rate regimes  in $Q_\ast$-$P$ space. The various regimes are
+the diffusive-resisitive (DR), the semi-collisional (SC),  the viscous-resistive (VR), and the resistive-inertial (RI).}\label{f3}
+\end{figure}
+
+\begin{figure}
+\centerline{\includegraphics[width=0.95\textwidth]{Scaling.pdf}}
+\caption{Error-field penetration regimes in $\hat{\nu}_\ast$-$\hat{\rho}_\ast$ space. The various regimes are the
+viscous-resistive-toroidal (${\rm VR}$-$\varphi$), the viscous-resistive-poloidal (${\rm VR}$-$\theta$), the diffusive-resistive-poloidal (${\rm DR}$-$\theta$), and the  diffusive-resistive-toroidal (${\rm DR}$-$\varphi$).
+}\label{f6}
+\end{figure}
+
 \end{document}

### 2021-12-11 Research/NonlinearTearingModeTheory/NonlinearTearingModeTheory.tex
Started writing linear and nonlinear papers

\documentclass[12pt,prb,aps]{revtex4-1}
\usepackage {amsmath}
\pdfoutput = 1 
\usepackage {graphicx}

\begin{document}

\title{Rotation of Magnetic Islands in Tokamak Plasmas}

\author{R.~Fitzpatrick\,\footnote{rfitzp@utexas.edu}}
\affiliation{Institute for Fusion Studies,  Department of Physics,  University of Texas at Austin,  Austin TX, 78712, USA}

\begin{abstract}
\end{abstract}

\maketitle

\section{Introduction}
Tearing modes are slowly growing instabilities of ideally-stable tokamak plasmas that reconnect magnetic field-lines
at various resonant surfaces within the plasma, in the process forming magnetic island chains that degrade the plasma confinement.\cite{wes} {\em Mode locking}\/ is a process by which the rotation of a magnetic island chain is braked  due to electromagnetic interaction with the resistive 
vacuum vessel surrounding the plasma, causing the chain to eventually {\em lock}\/ (i.e., become stationary in the laboratory frame) to an error-field.\cite{nave}
 Locked magnetic island chains are one of the principal causes of disruptions in tokamaks.\cite{vries}

It is well known that single-fluid, resistive magnetohydrodynamics (MHD) offers a very poor description of
tearing mode dynamics in tokamak plasmas. 
For instance, the strong {\em diamagnetic}\/ flows present in such plasmas decouple the electron and ion flows to some extent,
necessitating a two-fluid treatment.\cite{ara} Previously, Fitzpatrick \& Waelbroeck\,\cite{fw,fw1} used a generalized version of the four-field model of Hazeltine, et al.\cite{haz})
to determine the two-fluid response of a nonlinear magnetic island chain to a resistive vacuum vessel  in a large aspect-ratio tokamak plasma. The aim of this paper is to revisit this analysis in the light of certain refinements to magnetic island theory
introduced in Ref.~\onlinecite{rf2021}.

\section{Preliminary Analysis}\label{sect1}
\subsection{Plasma Equilibrium}
Consider a large aspect-ratio tokamak plasma equilibrium whose magnetic flux-surfaces map out
(almost) concentric circles in the poloidal plane. Such an equilibrium can be approximated as a
periodic cylinder.\cite{rf1993} Let $r$, $\theta$, $z$ be right-handed cylindrical coordinates. 
The magnetic axis corresponds to $r=0$. The system is assumed to be periodic in the $z$
direction with periodicity length $2\pi\,R_0$, where $R_0$ is the simulated major radius of the plasma. The
safety-factor profile takes the form $q(r)=r\,B_z/[R_0\,B_\theta(r)]$, where $B_z$ is the constant
`toroidal' magnetic field-strength, and $B_\theta(r)$ is the poloidal magnetic field-strength. The standard
large aspect-ratio orderings, $r/R_0\ll 1$ and $B_\theta/B_z\ll 1$, are adopted.

\subsection{Perturbed Magnetic Field}\label{cyl}
Consider a tearing mode perturbation that has $m$ periods in the poloidal direction, and
$n$ periods in the toroidal direction. 
The perturbed magnetic field associated with the tearing mode is written $\delta{\bf B} \simeq \nabla\delta\psi\times{\bf e}_z$,  
where
$\delta\psi(r,\theta,\varphi,t)= \delta\psi(r,t)\,\exp[\,{\rm i}\,(m\,\theta-n\,\varphi)]$, 
and $\varphi=z/R_0$ is a simulated toroidal angle. 
Throughout most of the plasma $\delta\psi(r,t)$ satisfies the
{\em cylindrical tearing mode equation}:\cite{wes}
\begin{equation}\label{e3}
\frac{\partial^2\delta\psi}{\partial r^2} + \frac{1}{r}\,\frac{\partial\delta\psi}{\partial r}-\frac{m^2}{r^2}\,\delta\psi - \frac{J_z'\,\delta\psi}{r\,(1/q-n/m)}=  0,
\end{equation}
where 
$J_z(r)= R_0\,\mu_0\,j_z(r)/B_z$,
and $j_z(r)$ is the equilibrium `toroidal' current density. Here, $'\equiv d/dr$.

\subsection{Outer Solution}\label{perfect}
Suppose that the plasma occupies the region $0\leq r\leq a$, where $a$ is the plasma  minor radius. It follows that
$J_z(r)=0$ for $r>a$. Let the plasma be surrounded by a concentric, rigid, radially-thin, resistive wall of radius $r_w>a$.  (Of course, the resistive wall represents the vacuum vessel.) 
 An appropriate
physical solution of the cylindrical tearing mode equation takes the separable form
$\delta\psi(r,t) = {\mit\Psi}_s(t)\,\hat{\psi}_s(r) + {\mit\Psi}_w(t)\,\hat{\psi}_w(r)$,
where the real function $\hat{\psi}_s(r)$ is a solution of 
\begin{equation}\label{e100}
\frac{d^2\hat{\psi}_s}{dr^2} + \frac{1}{r}\,\frac{d\hat{\psi}_s}{dr}-\frac{m^2}{r^2}\,\hat{\psi}_s - \frac{J_z'\,\hat{\psi}_s}{r\,(1/q-n/m)}= 0
\end{equation}
that satisfies
$\hat{\psi}_s(0) = 0$, 
$\hat{\psi}_s(r_s) = 1$, and
$\hat{\psi}_s(r\geq r_w) = 0$, and the real function  $\hat{\psi}_w(r)$ is a solution of 
\begin{equation}\label{e100a}
\frac{d^2\hat{\psi}_w}{dr^2} + \frac{1}{r}\,\frac{d\hat{\psi}_w}{dr}-\frac{m^2}{r^2}\,\hat{\psi}_w - \frac{J_z'\,\hat{\psi}_w}{r\,(1/q-n/m)}= 0
\end{equation}
that satisfies
$\hat{\psi}_w(r\leq r_s) = 0$,
$\hat{\psi}_w(r_w) = 1$,
and $\hat{\psi}_w(\infty) = 0$.

Note that Eq.~(\ref{e100}) is singular at the so-called {\em resonant}\/ magnetic flux-surface, radius $r=r_s$, at which 
$q(r_s)= m/n$. 
As is well-known, the general solution of Eq.~(\ref{e100} is such that $\delta\psi$ is continuous across the resonant surface,
whereas $\partial\delta\psi/\partial r$ is discontinuous. The discontinuity in $\partial \delta\psi/\partial r$ implies the presence of a helical  current sheet  at the resonant surface. 
The complex quantity 
\begin{equation}
{\mit\Psi}_s(t)= \delta\psi(r_s,t) 
\end{equation}
parameterizes the amplitude and phase of the
reconnected magnetic flux at the resonant surface.\cite{rf1993}
The complex quantity
\begin{equation}\label{e109}
{\mit\Delta\Psi}_s = \left[r\,\frac{\partial \delta\psi}{\partial r}\right]_{r_{s-}}^{r_{s+}}
\end{equation}
parameterizes the amplitude and phase of the current sheet flowing at the resonant surface.

In general, $\delta\psi$ is continuous across the wall, whereas $\partial\delta\psi/\partial r$ is discontinuous. The discontinuity in $\partial\delta\psi/\partial r$ is caused by a helical current sheet induced in the wall. The complex quantity ${\mit\Psi}_w(t)$ determines the amplitude and
phase of the perturbed magnetic flux that penetrates the wall. The complex quantity
\begin{equation}\label{e118}
{\mit\Delta\Psi}_w = \left[r\,\frac{\partial\delta\psi}{\partial r}\right]_{r_{w-}}^{r_{w+}}
\end{equation}
parameterizes the amplitude and phase of the helical current sheet flowing in the wall.

Simultaneously matching our separable solution of Eq.~(\ref{e3})  across the resonant surface and the wall yields\,\cite{rf1993}
\begin{align}
{\mit\Delta\Psi}_s& = E_{ss}\,{\mit\Psi}_s + E_{sw}\,{\mit\Psi}_w,\\[0.5ex]
{\mit\Delta\Psi}_w& = E_{ws}\,{\mit\Psi}_s+ E_{ww}\,{\mit\Psi}_w.
\end{align}
Here, $E_{ss}= [r\,d\hat{\psi}_s/dr]_{r_{s-}}^{r_{s+}}$,
$E_{ww}= [r\,d\hat{\psi}_w/dr]_{r_{w-}}^{r_{w+}}$,
$E_{sw} =[r\,{d\hat\psi}_w/dr]_{r=r_{s+}}$, and 
$E_{ws} =-[r\,{d\hat\psi}_s/dr]_{r=r_{w-}}$
are real quantities determined by the solutions of Eqs.~(\ref{e100}) and (\ref{e100a}) in the outer region.
It is easily demonstrated that 
$E_{sw} = E_{ws}$.\cite{rf1993}

Standard electromagnetic theory applied to the resistive wall reveals that\,\cite{nave,rf1993}
\begin{equation}
{\mit\Delta\Psi}_w = \tau_w\,\frac{d{\mit\Psi}_w}{dt},
\end{equation}
where
$\tau_w= \mu_0\,r_w\,\delta_w/\eta_w$.
Here, $\eta_w$ and $\delta_w$ are the electrical resistivity and radial thickness  of the wall, respectively.

Assuming an $\exp(-{\rm i}\,\omega\,t)$ time dependence of perturbed quantities, the previous four equations
can be combined to give
\begin{equation}
\frac{{\mit\Delta\Psi}_s}{{\mit\Psi}_s}= {\mit\Delta}_{pw} + \frac{{\mit\Delta}_{nw}-{\mit\Delta}_{pw}}{1-{\rm i}\,\omega\,\tau_{LR}},
\end{equation}
where ${\mit\Delta}_{pw}= E_{ss}$ is the  tearing stability index\cite{fkr} when the wall is perfectly conducting,
${\mit\Delta}_{nw} = E_{ss} + E_{sw}^{\,2}/(-E_{ww})$ is the  tearing stability index when there is no wall,
and $\tau_{LR}= \tau_w/(-E_{ww})$ is the effective L/R time of the wall. (Note that $E_{ww}<0$.)

\section{Resonant Plasma Response Model}\label{sfour}
\subsection{Introduction}
The helical current sheet at the resonant surface can only be resolved by solving  a two-fluid, resistive-MHD, plasma response model
in the inner region (i.e., the region of the plasma in the immediate vicinity of the resonant surface), 
and asymptotically matching the solution so obtained to the ideal-MHD solution in the outer region (i.e., everywhere else in the plasma). The particular 
plasma response model used in this paper is
described in this section.

\subsection{Useful Definitions}
The plasma is assumed to consist of two species. First, electrons of mass $m_e$, electrical charge $-e$, 
number density $n$, and temperature $T_e$.  Second, ions of mass $m_i$, electrical charge $+e$,  
number density $n$, and temperature $T_i$. Let $p=n\,(T_e+T_i)$ be the total plasma pressure.

It is helpful to define $n_0 = n(r_s)$, $p_0= p(r_s)$,
\begin{align}
\eta_e &=\left.\frac{d\ln T_e}{d\ln n}\right|_{r=r_s},\label{e211}\\[0.5ex]
\eta_i &= \left.\frac{d\ln T_i}{d\ln n}\right|_{r=r_s},\\[0.5ex]
\tau &= \left(\frac{T_e}{T_i}\right)_{r=r_s}\left(\frac{1+\eta_e}{1+\eta_i}\right),\label{e213}
\end{align}
where $n(r)$, $p(r)$, $T_e(r)$, and $T_i(r)$ refer to
density, pressure, and temperature profiles that are unperturbed by the tearing mode.

For the sake of simplicity, the perturbed electron and ion temperature profiles are assumed to be functions of
the perturbed electron number density profile in the immediate vicinity of the resonant surface. In other words, $T_e=T_e(n)$ and $T_i=T_i(n)$. This
implies that $p=p(n)$. 
The {\em MHD velocity}, which is the velocity of a
fictional MHD fluid, is defined ${\bf V}={\bf V}_E + V_{\parallel\,i}\,{\bf b}$, where ${\bf V}_E$ is the
${\bf E}\times{\bf B}$ drift velocity, $V_{\parallel\,i}$ is the parallel component of the ion fluid
velocity, ${\bf b}= {\bf B}/|{\bf B}|$, and ${\bf B}$ is the magnetic field-strength.

\subsection{Resonant Response Model}\label{resonant}
The fundamental fields in our resonant plasma reponse model---namely, $\psi$, $\phi$, $N$, $V$, and $J$---have the following
definitions:
\begin{align}\label{e10}
\nabla\psi &= \frac{{\bf n}\times{\bf B}} {r_s\,B_z},\\[0.5ex]
\nabla\phi &= \frac{{\bf n}\times {\bf V}}{r_s\,V_A},\\[0.5ex]
N &=-\hat{d}_i\left(\frac{p-p_0}{B_z^{\,2}/\mu_0}\right),\\[0.5ex]
V &= \hat{d}_i\left(\frac{{\bf n}\cdot {\bf V}}{V_A}\right),\label{e13}\\[0.5ex]
J&=-\frac{2\,\epsilon_s}{q_s}+\hat{\nabla}^2\psi.
\end{align}
Here,   ${\bf n} = (0,\,\epsilon/q_s,\,1)$, $\epsilon = r/R_0$, $q_s=m/n$, 
$V_A =B_z/\sqrt{\mu_0\,n_0\,m_i}$, 
$d_i = \sqrt{m_i/(n_0\,e^{\,2}\,\mu_0)}$,  $\hat{d}_i=d_i/r_s$, 
$\epsilon_s=r_s/R_0$, and $\hat{\nabla} = r_s\,\nabla$.

Our resonant plasma response model takes the form:\cite{fw}
\begin{align}
\frac{\partial\psi}{\partial\hat{t}}&= [\phi,\psi] -\left(\frac{\tau}{1+\tau}\right)(1+\lambda_e)\,[N,\psi]
+\hat{\eta}_\parallel\,J + \hat{E}_\parallel,\\[0.5ex]
\frac{\partial \hat{\nabla}^2\phi}{\partial \hat{t}}&= [\phi,\hat{\nabla}^2\phi] - \frac{1}{2\,(1+\tau)}\left(\hat{\nabla}^2[\phi,N] + [\hat{\nabla}^2\phi,N] + [\hat{\nabla}^2 N,\phi]\right) + [J,\psi] \nonumber\\[0.5ex]&\phantom{=}+\hat{\chi}_\varphi  \,\hat{\nabla}^4\!\left(\phi + \frac{N}{1+\tau}\right), \\[0.5ex]
\frac{\partial N}{\partial \hat{t}}&= [\phi,N] +c_\beta^{\,2}\,[V,\hat{\psi}] +\hat{d}_\beta^{\,2}\,[J,\psi]
+ \hat{D}_\parallel \,[[N,\hat{\psi}],\hat{\psi}]+ \hat{D}_\perp\,\hat{\nabla}_\perp^{\,2}N,\\[0.5ex]
\frac{\partial V}{\partial\hat{t}}&= [\phi,V] +[N,\psi] + \hat{\chi}_\varphi\,\hat{\nabla}^2 V.\label{e21}
\end{align}
Here, $[A,B]\equiv \hat{\nabla} A\times \hat{\nabla} B\cdot {\bf n}$, $\hat{t} = t/(r_s/V_A)$, $\hat{\eta}_{\parallel,\perp} = \eta_{\parallel,\perp}/(\mu_0\,r_s\,V_A)$, $\hat{E}_\parallel = E_\parallel/(B_z\,V_A)$, 
$\hat{\chi}_\varphi= \chi_\varphi/(r_s\,V_A)$, where $\eta_{\parallel,\perp}$ is the parallel/perpendicular plasma electrical
resistivity at the resonant surface, $E_\parallel$ the parallel inductive electric field that maintains the equilibrium toroidal
plasma current in the vicinity of the resonant surface, and $\chi_\varphi$  the anomalous perpendicular ion momentum
diffusivity at the resonant surface. 
Moreover, $d_\beta=c_\beta\,d_i$, and $\hat{d}_\beta=d_\beta/r_s$, where $c_\beta = \sqrt{\beta/(1+\beta)}$, and
$\beta=(5/3)\,\mu_0\,p_0/B_z^{\,2}$. Here, $d_\beta$ is usually referred to as the {\em ion sound radius}. Furthermore,
$\lambda_e=0.71\,\eta_e/(1+\eta_e)$. Finally,\cite{fw}
\begin{align}
\hat{D}_\parallel&\equiv\frac{D_{\parallel}}{r_s\,V_A}= \frac{2}{3}\left(1-c_\beta^{\,2}\right)\!\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\parallel\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\parallel\,i}\right),\\[0.5ex]
\hat{D}_\perp& \equiv \frac{D_{\perp}}{r_s\,V_A}= c_\beta^{\,2}\,\hat{\eta}_\perp +  \frac{2}{3}\left(1-c_\beta^{\,2}\right)\!\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\perp\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\perp\,i}\right),
\end{align}
where $\hat{\chi}_{\parallel\,e,i}=\chi_{\parallel\,e,i}/(r_s\,V_A)$,  $\hat{\chi}_{\perp\,e,i}=\chi_{\perp\,e,i}/(r_s\,V_A)$, 
$\chi_{\parallel\,e,i}$ is the parallel electron/ion energy diffusivity in the vicinity of the resonant surface, and 
$\chi_{\perp\,e,i}$ is the anomalous
electron/ion perpendicular energy diffusivity in the vicinity of the resonant surface.

\subsection{Boundary Conditions}
The unperturbed plasma equilibrium is such that
${\bf B} = (0,\,B_\theta(r),\,B_z)$,  $p = p(r)$,
${\bf V} = (0,\,V_E(r),\,V_z(r))$,
where 
$V_E(r)\simeq E_r/B_z$
 is the (dominant $\theta$-component of the) ${\bf E}\times {\bf B}$ velocity.

It is convenient  to work in a frame of reference that corotates with the tearing mode. In this reference frame, the
reconnected flux, ${\mit\Psi}_s$, is assumed to be a positive real
quantity. If $W$ is the full radial width of the magnetic island chain that develops at the resonant surface then it is
helpful to define the reduced island width:
\begin{equation}
w = \frac{W}{4}= \left(\frac{L_s\,{\mit\Psi}_s}{B_z}\right)^{1/2}.
\end{equation}
It is assumed that $w\ll r_s$. Let $\hat{w}=w/r_s$. 
 In the limit $|\hat{x}|/\hat{w}\gg 1$ (i.e., many island widths from the resonant surface), we have  
\begin{align}\label{e26}
\psi &\rightarrow \frac{\hat{x}^{\,2}}{2\,\hat{L}_s} + \frac{{\mit\Psi}_s}{r_s\,B_z}\,\cos\zeta,\\[0.5ex]
\phi &\rightarrow \left(\frac{\hat{\omega}}{m}- \hat{V}_E\right)\hat{x} - \frac{s}{4}\,\hat{V}_E'\,\hat{x}^{\,2},\\[0.5ex]
N &\rightarrow -\hat{V}_\ast\,\hat{x},\\[0.5ex]
V&\rightarrow \hat{V}_\parallel,\\[0.5ex]
J& \rightarrow -\frac{2}{q_s\,\hat{R}_0} + \frac{1}{\hat{L}_s}.\label{e30}
\end{align}
where 
$\hat{x}=(r-r_s)/r_s$,
 $\hat{L}_s=L_s/r_s$,  $L_s=R_0\,q_s/s_s$, $\hat{R}_0=R_0/r_s$, $\zeta=m\,\theta-n\,\varphi$, 
  $\hat{V}_E= V_E(r_s)/V_A$,
$\hat{V}_\ast= V_\ast(r_s)/V_A$,
$V_\ast(r) = (dp/dr)/(e\,n_0\,B_z)$ 
is the (dominant $\theta$-component of the) diamagnetic velocity,
 $\hat{V}_\parallel=\hat{d}_i\, V_z(r_s)/V_A$, $s_s=s(r_s)$, and $s(r)=d\ln q/d\ln r$. 
Here, $\omega = \hat{\omega}\,V_A/r_s$ is the rotation frequency of the tearing mode  in the
laboratory frame,
$s = {\rm sgn}(\hat{x})$,
and 
\begin{equation}
\hat{V}_E' = \frac{1}{V_A}\left[r\,\frac{dV_E}{dr}\right]_{r_{s-}}^{r_{s+}}.
\end{equation}
The parameter $\hat{V}_E'$ is introduced  into the analysis in order to take into account the fact that the plasma rotation profile in the outer region develops a
gradient discontinuity at the resonant surface in response to the nonlinear localized electromagnetic torque that emerges 
at the surface. Finally, 
 $\hat{E}_\parallel =(2/s_s-1) \,(\hat{\eta}_\parallel/\hat{L}_s)$.

\section{Nonlinear Solution of Resonant Plasma Response Model}
\subsection{Rescaled Response Model}\label{s8.2}
Let
$X = \hat{x}/\hat{w}$,
and
$T = \omega_\ast\,t$.
It follows that $|X|\sim {\cal O}(1)$ in the immediate vicinity of the island chain. It is helpful to define the
rescaled fields ${\mit\Psi}(X,\zeta,T)$, ${\mit\Phi}(X,\zeta,T)$, ${\cal N}(X,\zeta,T)$,
${\cal V}(X,\zeta,T)$, and ${\cal J}(X,\zeta,T)$, where
\begin{align}
\psi&= \left(\frac{\hat{w}^{\,2}}{\hat{L}_s}\right){\mit\Psi},\label{e466}\\[0.5ex]
\phi &=\left(\frac{\hat{\omega}_\ast\,\hat{w}}{m}\right){\mit\Phi},\\[0.5ex]
N &= \left(\frac{\hat{\omega}_\ast\,\hat{w}}{m}\right){\cal N},\\[0.5ex]
V&= \hat{V}_\parallel + \left(\frac{\hat{L}_s\,\hat{\omega}_\ast^{\,2}}{m^2\,c_\beta^{\,2}}\right){\cal V},\\[0.5ex]
J & =-\frac{2}{q_s\, \hat{R}_0} + \frac{1}{\hat{L}_s} + \left(\frac{\hat{L}_s\,\hat{\omega}_\ast^{\,2}}{m^2\,\hat{w}^{\,2}}\right){\cal J},
\end{align}
where $\omega_\ast = - (m/r_s)\,V_\ast(r_s)$ and $\hat{\omega}_\ast = \omega_\ast/(V_A/r_s)$. 
The resonant response model specified in Sect.~\ref{resonant} rescales to give
\begin{align}\label{e469}
\frac{d(\ln \hat{w}^2)}{dT}\,\cos\zeta &= \left\{{\mit\Phi}-\left(\frac{\tau}{1+\tau}\right)(1+\lambda_e)\,{\cal N}, {\mit\Psi}\right\}
+ \epsilon_\beta\,\epsilon_d\,\epsilon_\eta\,{\cal J},\\[0.5ex]
\frac{\partial(\partial_X^{\,2}\,{\mit\Phi})}{\partial T} &= \partial_X\!\!\left\{{\mit\Phi} + \frac{{\cal N}}{1+\tau},\partial_X{\mit\Phi}\right\}
+ \{{\cal J},{\mit\Psi}\}+ \epsilon_\chi \,\partial_X^{\,4}\!\left({\mit\Phi} + \frac{{\cal N}}{1+\tau}\right),\label{e470}\\[0.5ex]
\frac{\partial {\cal N}}{\partial T} &= \{{\mit\Phi}, {\cal N}\} + \{{\cal V},{\mit\Psi}\} + \epsilon_d\,\epsilon_n\,\{{\cal J},{\mit\Psi}\}\nonumber\\[0.5ex]&\phantom{=}
+ \epsilon_D \!\left[\left(\frac{w}{w_c}\right)^4\,\{\{{\cal N},{\mit\Psi}\}, {\mit\Psi}\}+\partial_X^{\,2}{\cal N}\right],\label{e471}\\[0.5ex]
\epsilon_d\,\frac{\partial {\cal V}}{\partial T} &= \epsilon_d\,\{{\mit\Phi},{\cal V}\}+\{{\cal N}, {\mit\Psi}\} + \epsilon_d\,\epsilon_\chi\,\partial_X^{\,2} {\cal V},\label{e472}\\[0.5ex]
\partial_X^{\,2}{\mit\Psi} &= 1+ \epsilon_\beta\,\epsilon_d\,{\cal J}.\label{e473}
\end{align}
Here,  $\partial_X\equiv \partial/\partial X$, 
\begin{equation}
\{A,B\} \equiv \frac{\partial A}{\partial X}\,\frac{\partial B}{\partial\zeta} - \frac{\partial A}{\partial \zeta}\,\frac{\partial B}{\partial X},
\end{equation}
and
\begin{equation}
w_c = \left(\frac{1}{\epsilon_s\,s_s\,n}\right)^{1/2}\left(\frac{D_\perp}{D_\parallel}\right)^{1/4}r_s.
\end{equation}
Furthermore,
\begin{align}
\epsilon_d &= \left(\frac{L_s}{L_n}\right)^2\left(\frac{d_\beta}{w}\right)^2,\label{e479}\\[0.5ex]
\epsilon_\beta &= c_\beta^{\,2},\label{e480}\\[0.5ex]
\epsilon_n&= \left(\frac{L_n}{L_s}\right)^2,\\[0.5ex]
\epsilon_\eta &= \frac{\eta_\parallel}{\mu_0\,\omega_\ast\,w^2},\label{e481}\\[0.5ex]
\epsilon_\chi &= \frac{\chi_\phi}{\omega_\ast\,w^2},\label{e482}\\[0.5ex]
\epsilon_D &= \frac{D_\perp}{\omega_\ast\,w^2}.
\end{align}
Finally,
\begin{equation}
L_n= \left[-\frac{1}{{\mit\Gamma}\,(1-c_\beta^{\,2})}\left(\frac{d\ln n}{dr}\right)_{r_s}\right]^{-1}
\end{equation}
is the {\em density gradient scalelength}\/  at the resonant surface.

Equations~(\ref{e469})--(\ref{e473}) must be solved subject to the boundary conditions [see Eqs.~(\ref{e26})--(\ref{e30})] 
\begin{align}
{\mit\Psi}&\rightarrow \frac{X^{2}}{2} + \cos\zeta,\label{e483}\\[0.5ex]
{\mit\Phi} &\rightarrow v\,X +\frac{ s\,v'\,X^{2}}{2},\label{e484}\\[0.5ex]
{\cal N}&\rightarrow X,\label{e486}\\[0.5ex]
{\cal V}&\rightarrow 0,\label{e486a}\\[0.5ex]
{\cal J}& \rightarrow 0,\label{e487}
\end{align}
as $|X|\rightarrow\infty$.  Here,
\begin{align}
v(T) &= \frac{\omega-\omega_E}{\omega_\ast},\label{e488}\\[0.5ex]
v'(T) &= -\frac{\hat{w}}{2\,\omega_\ast}\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}}.\label{e489}
\end{align}
Note that ${\mit\Psi}$, ${\mit\Phi}$, ${\cal N}$, ${\cal V}$, and ${\cal J}$ are all ${\cal O}(1)$ quantities.
Note, further,  that the boundary conditions (\ref{e483})--(\ref{e487}),
as well as the symmetry of Eqs.~(\ref{e469})--(\ref{e473}), ensure that ${\mit\Psi}$, ${\cal V}$, and
${\cal J}$ are even functions of $X$, whereas ${\mit\Phi}$ and ${\cal N}$ are odd functions.

\subsection{Ordering Scheme}
In the following, the dimensionless parameters $\epsilon_d$, $\epsilon_\beta$, $\epsilon_n$, $\epsilon_\eta$, $\epsilon_\chi$,
and $\epsilon_D$ are all assumed to be of similar size, but much smaller than unity. The orderings $\epsilon_n\ll 1$ and $\epsilon_\beta\ll 1$
are consistent with the standard large-aspect ratio, low-$\beta$ orderings used to describe conventional tokamak
plasmas. As will become apparent, the ordering $\epsilon_d\ll 1$ ensures that the island chain is
sufficiently wide that ion acoustic waves propagating parallel to the magnetic field are able to smooth out any
variations in the normalized electron number density, ${\cal N}$, around magnetic flux-surfaces.\cite{scott} The fact that $\epsilon_d\ll 1$ implies that
\begin{equation}
w \gg \rho_\beta,
\end{equation}
where
\begin{equation}
\rho_\beta = \left(\frac{L_s}{L_n}\right)d_\beta
\end{equation}
is a characteristic lengthscale that is of order the ion poloidal gyroradius. 
 The orderings $\epsilon_\eta\ll 1$, $\epsilon_\chi\ll 1$, and $\epsilon_D\ll 1$ ensure that the island
chain is sufficiently wide that the perpendicular diffusion of magnetic flux, momentum, and particles are not dominant
effects in the rescaled four-field equations. We shall also assume that $w/w_c\sim{\cal O}(1)$. In other words, the
island chain is sufficiently wide for the parallel diffusion of particles to compete with perpendicular diffusion.\cite{rff}

Suppose that 
\begin{align}
\frac{\partial}{\partial T}&\sim {\cal O}(\epsilon_d^3).
\end{align}
Let us expand the various fields in our model as follows:
\begin{align}
{\mit\Psi}&= {\mit\Psi}_0+\epsilon_d^2\,{\mit\Psi}_2+ \epsilon_d^3\,{\mit\Psi}_3 + \cdots,\label{e429}\\[0.5ex]
{\mit\Phi}&= {\mit\Phi}_0+\epsilon_d^2\,{\mit\Phi}_2+ \epsilon_d^3\,{\mit\Phi}_3 + \cdots,\\[0.5ex]
{\cal N}&= {\cal N}_0+\epsilon_d^2\,{\cal N}_2+ \epsilon_d^3\,{\cal N}_3 + \cdots,\label{e431}\\[0.5ex]
{\cal V} & ={\cal V}_0. +\epsilon_d\,{\cal V}_1 +\cdots,\\[0.5ex]
{\cal J} &= {\cal J}_0 + \epsilon_d\,{\cal J}_1 +\cdots. \label{e496}
\end{align}
Here, ${\mit\Psi}_0$, ${\mit\Psi}_1$, et cetera are assumed to be ${\cal O}(1)$.

\subsection{Lowest-Order Solution}
To lowest order in $\epsilon_d$, Eq.~(\ref{e473}) yields
\begin{equation}
\partial_X^{\,2}{\mit\Psi}_0 = 1.
\end{equation} 
Solving this equation subject to the boundary condition (\ref{e483}), we obtain
\begin{equation}\label{e498}
{\mit\Psi}_0 = {\mit\Omega}(X,\zeta)\equiv \frac{X^2}{2} + \cos\zeta.
\end{equation}
Thus, we conclude that, to lowest order in our expansion, the magnetic flux-surfaces in the island region map out a helical magnetic island
chain. The island O-points correspond to ${\mit\Omega}=-1$ and $\zeta=(2k-1)\,\pi$ (where $k$ is an integer), the
X-points correspond to ${\mit\Omega}=+1$ and $\zeta = 2k\,\pi$, and the magnetic separatrix corresponds to 
${\mit\Omega}=+1$.

To lowest order in $\epsilon_d$, Eq.~(\ref{e472}) yields
\begin{equation}
\{{\cal N}_0, {\mit\Omega}\}= 0,
\end{equation}
where use has been made of Eq.~(\ref{e498}). Given that ${\cal N}$ is an odd function of $X$, it
follows that
\begin{equation}\label{e500}
{\cal N}_0(X,\zeta,T) = s\, {\cal N}_{(0)}({\mit\Omega},T).
\end{equation}
We conclude that parallel
ion acoustic waves, whose dynamics are described by Eq.~(\ref{e472}),  smooth  out
any variations in the lowest-order electron number density, ${\cal N}_0$,  around magnetic flux-surfaces. 
By symmetry, ${\cal N}_{0}=0$ inside the magnetic separatrix of the island chain. In other words, the electron number
density profile (and, by implication, the electron and ion temperature profile) is completely flattened inside 
the  separatrix.

It is helpful to define
\begin{equation}\label{e501}
L({\mit\Omega},T) = \frac{d{\cal N}_{(0)}}{d{\mit\Omega}}.
\end{equation}
It follows that $L({\mit\Omega}<1,T)=0$. Furthermore, Eqs.~(\ref{e486}) and (\ref{e498}) imply that
\begin{equation}\label{e502}
L({\mit\Omega}\rightarrow\infty,T) = \frac{1}{\sqrt{2\,{\mit\Omega}}}.
\end{equation}

To lowest order in $\epsilon_d$, Eq.~(\ref{e469}) gives
\begin{equation}
\{{\mit\Phi}_0,{\mit\Omega}\}=0,
\end{equation}
where use has been made of Eqs.~(\ref{e498}) and (\ref{e500}). Given that
${\mit\Phi}$ is an odd function of $X$, it follows that 
\begin{equation}\label{e503}
{\mit\Phi}_0(X,\zeta,T) = s\, {\mit\Phi}_{(0)}({\mit\Omega},T).
\end{equation}
 We conclude that the lowest-order normalized
electrostatic potential, ${\mit\Phi}_{0}$, is  constant on magnetic flux-surfaces. 
By symmetry, ${\mit\Phi}_{0}=0$ inside the magnetic separatrix of the island chain. In other words, the electrostatic
potential profile is  completely flattened inside the separatrix.

It is helpful to define
\begin{equation}\label{e505}
M({\mit\Omega},T) = \frac{d{\mit\Phi}_{(0)}}{d{\mit\Omega}}.
\end{equation}
It follows that $M({\mit\Omega}<1,T)=0$. Furthermore, Eqs.~(\ref{e484}) and (\ref{e498}) imply that
\begin{equation}\label{e506}
M({\mit\Omega}\rightarrow\infty,T) = \frac{v}{\sqrt{2\,{\mit\Omega}}}+ v'.
\end{equation}

To lowest order in $\epsilon_d$, Eq.~(\ref{e471}) yields
\begin{equation}
\{{\cal V}_0,{\mit\Omega}\} = 0,
\end{equation}
where use has been made of Eqs.~(\ref{e498}), (\ref{e500}), and (\ref{e503}). Given that
${\cal V}$ is an even function of $X$, we can write
\begin{equation}\label{e508}
{\cal V}_0(X,\zeta,T) = {\cal V}_{(0)}({\mit\Omega},T).
\end{equation}
In other words, the lowest-order normalized parallel ion velocity, ${\cal V}_0$, is also constant on
magnetic flux-surfaces.

Finally, to lowest order in $\epsilon_d$, Eq.~(\ref{e470}) yields
\begin{equation}\label{e509}
\{{\cal J}_0,{\mit\Omega}\} = -\partial_X\!\left\{{\mit\Phi}_0+\frac{{\cal N}_0}{1+\tau}, \partial_X {\mit\Phi}_0\right\}=
\frac{1}{2}\left\{d_{\mit\Omega}\!\left[M\left(M+\frac{L}{1+\tau}\right)\right]X^2, {\mit\Omega}\right\},
\end{equation}
where use has been made of Eqs.~(\ref{e498}), (\ref{e501}), and (\ref{e505}). Moreover, $d_{\mit\Omega}\equiv
d/d{\mit\Omega}$.

\subsection{Flux-Surface Average Operator}
The {\em flux-surface average operator}, $\langle\cdots\rangle$, is defined\,\cite{rutherford}
\begin{equation}
\langle A(s,{\mit\Omega},\zeta)\rangle
\equiv \left\{
\begin{array}{llr}
\int_{\zeta_0}^{2\pi-\zeta_0}\frac{A(s,{\mit\Omega}\,\zeta)+A(-s,{\mit\Omega},\zeta)}{2\,[2\,({\mit\Omega}-\cos\zeta)]^{1/2}}\,\frac{d\zeta}{2\pi}&~~~~~&0\leq {\mit\Omega}\leq 1\\[2ex]
\oint \frac{A(s,{\mit\Omega}\,\zeta)}{[2\,({\mit\Omega}-\cos\zeta)]^{1/2}}\,\frac{d\zeta}{2\pi}
&&{\mit\Omega}> 1
\end{array}
\right.,
\end{equation}
where $\zeta_0=\cos^{-1}({\mit\Omega})$ and $0\leq\zeta_0\leq\pi$. 
It follows that
$\langle\{A,{\mit\Omega}\}\rangle = 0$
for {\em any}\/ $A(s,{\mit\Omega},\zeta,T)$. It is helpful to define
$\tilde{A}  \equiv A - \langle A\rangle/\langle 1\rangle$.
It follows that 
$\langle \tilde{A}\rangle =0$
 for {\em any}\/ $A(s,{\mit\Omega},\zeta,T)$.

Equation~(\ref{e509}) yields 
\begin{equation}\label{e513}
{\cal J}_0({\mit\Omega},\zeta,T)= 
\frac{1}{2}\,d_{\mit\Omega}\!\left[M\left(M+\frac{L}{1+\tau}\right)\right]\!\widetilde{X^2} + \overline{\cal J}_0({\mit\Omega},T),
\end{equation}
where $\overline{{\cal J}}_0({\mit\Omega},T)$ is an undetermined flux-surface function.

\subsection{Higher-Order Solution}
To lowest order in our expansion scheme, the rescaled resonant response model, (\ref{e469})--(\ref{e473}), specifies the
island solution in terms of four flux-surface functions: 
 ${\cal N}_{(0)}({\mit\Omega},T)$,
${\mit\Phi}_{(0)}({\mit\Omega},T)$,  ${\cal V}_{(0)}({\mit\Omega},T)$, and $\overline{\cal J}_0({\mit\Omega},T)$. In order to determine
the forms of these  four  functions,  it is necessary to solve the rescaled model to higher order in our expansion. In particular,
we need to include the terms that describe the perpendicular diffusion of magnetic flux, ion momentum, and
particles in our analysis.

We need to evaluate Eq.~(\ref{e469}) to third order in $\epsilon_d$ in order to include the perpendicular transport term. Doing so,
we obtain
\begin{equation}\label{e514}
\frac{d(\ln \hat{w}^{\,2})}{dT}\,\cos\zeta = \{F_e, {\mit\Omega}\} + \epsilon_\beta\,\epsilon_d\,\epsilon_\eta\,{\cal J}_0,
\end{equation}
where
\begin{equation}
F_e({\mit\Omega},\zeta,T)= \epsilon_d^2\,({\mit\Phi}_2+\epsilon_d\,{\mit\Phi}_3)-\epsilon_d^{2}\left(\frac{\tau}{1+\tau}\right)({\cal N}_2+\epsilon_d\,{\cal N}_3)
- \epsilon_d^2\,s\,Y_e({\mit\Psi}_2+\epsilon_d\,{\mit\Psi}_3),
\end{equation}
and use has been made of Eqs.~(\ref{e429})--(\ref{e431}), (\ref{e500}), (\ref{e501}), (\ref{e503}), and (\ref{e505}). 
The flux-surface average of Eq.~(\ref{e514}) yields
\begin{equation}
\overline{\cal J}_0({\mit\Omega},T) = \frac{1}{\epsilon_\beta\,\epsilon_d\,\epsilon_\eta}\frac{d(\ln \hat{w}^{2})}{dT}\,\frac{\langle\cos\zeta\rangle}{\langle 1\rangle}.
\end{equation}
 Hence, we
can write
\begin{equation}\label{e524a}
{\cal J}_0({\mit\Omega},\zeta)= 
\frac{1}{2}\,d_{\mit\Omega}\!\left(M\,Y_i\right)\widetilde{X^2}+ \frac{1}{\epsilon_\beta\,\epsilon_d\,\epsilon_\eta}\frac{d(\ln \hat{w}^{2})}{dT}\,\frac{\langle\cos\zeta\rangle}{\langle 1\rangle},
\end{equation}
where use has been made of Eq.~(\ref{e513}). Here, $Y_i= M + [1/(1+\tau)]\,L$. 
The first term on the right-hand side of the previous equation represents the parallel return current driven by the perpendicular {\em polarization current}\/ associated with the
acceleration of the ion fluid around the magnetic separatrix of the island chain.\cite{smol1,smol2} 
In fact, it is easily seen that if the ion fluid could pass freely through the separatrix (i.e., ${\mit\Phi}_0\propto X$ and ${\cal N}_0\propto X$) then the term in question would be zero. The second term on the right-hand side of the previous equation represents the parallel current driven
inductively when the reconnected flux at the resonant surfaces varies in time.

We need to evaluate Eq.~(\ref{e471}) to first order in $\epsilon_d$ in order to include the perpendicular transport term. Doing so,
we obtain
\begin{equation}
0= \epsilon_d\,\{{\cal V}_1, {\mit\Omega}\} + \epsilon_D\,(X^2\,d_{\mit\Omega} L + L),
\end{equation}
where use has been made of Eqs.~(\ref{e498}), (\ref{e500}),  and (\ref{e501}). The flux-surface average of the
previous equation yields
\begin{equation}
\langle X^2\rangle\,d_{\mit\Omega} L +\langle 1\rangle\,L = 0.
\end{equation}
We can solve the previous equation, subject to the boundary condition (\ref{e502}), to give
\begin{equation}\label{e526}
L({\mit\Omega})=\left\{
\begin{array}{llr}
0&&-1\leq {\mit\Omega}\leq 1\\[0.5ex]
1/\langle X^2\rangle&~~&{\mit\Omega}>1
\end{array}\right..
\end{equation}
Here, we have taken into account the previously mentioned fact that $L=0$ within the island separatrix.
Note that $L$ is discontinuous across the island separatrix, which implies that the density gradient---and, hence,
the diamagnetic velocity---are both also discontinuous across the separatrix. Of course, there is not a real
discontinuity. Given that the discontinuity in $L$ is mandated by the ordering $\epsilon_d=(\rho_\beta/w)^2\ll 1$, which
requires $L$ to be a flux-surface function---and, hence, zero, by symmetry, inside the separatrix---it is plausible that the discontinuity is resolved by a thin layer of characteristic thickness $\rho_\beta$ on the island
separatrix.

We need to evaluate Eq.~(\ref{e470}) to first order in $\epsilon_d$ in order to include the perpendicular transport term. Doing so,
we obtain
\begin{equation}\label{e528a}
0 =\epsilon_d\,\{{\cal J}_1,{\mit\Omega}\} +\epsilon_\chi\,X\,d_{{\mit\Omega}}\!\left[d_{\mit\Omega}\!\left(X^3\,d_{\mit\Omega} Y_i\right)\right].
\end{equation}
where use has been made of Eqs.~(\ref{e498}), (\ref{e500}), (\ref{e501}), (\ref{e503}), and (\ref{e505}). The flux-surface average of the previous equation yields 
\begin{equation}
d_{\mit\Omega}^{\,2}\!\left(\langle X^4\rangle\,d_{\mit\Omega} Y_i\right)= 0.
\end{equation}
We can solve the previous equation, subject to the boundary conditions (\ref{e502}) and (\ref{e506}), to give\,\cite{fw}
\begin{equation}\label{e530}
Y_i({\mit\Omega},T)=\frac{v'(T)}{\int_1^\infty \!\frac{d{\mit\Omega}}{\langle X^4\rangle}}\left\{
\begin{array}{llr}
0&&-1\leq {\mit\Omega}\leq 1\\[0.5ex]
\int_1^{\mit\Omega}\! \frac{d{\mit\Omega}'}{\langle X^4\rangle}&~~&{\mit\Omega}>1
\end{array}\right.
\end{equation}
Here, we have rejected, as unphysical, the solution that blows up as ${\mit\Omega}^{\,1/2}$ as ${\mit\Omega}\rightarrow\infty$. 
We have also made use of the fact that $Y_i=0$ within the magnetic separatrix of the island chain. Finally, we have  demanded that the ion
fluid velocity---and, hence, the function $Y_i$---be continuous across the separatrix, because the ion fluid possesses finite perpendicular viscosity. 
Note, however, that the discontinuity in the function $L({\mit\Omega})$ across the separatrix [see Equation~(\ref{e526})] implies that the
electron and MHD  fluid velocities are  discontinuous across the separatrix.  As previously
mentioned, these discontinuities are resolved in a layer of characteristic thickness $\rho_\beta$.

We need to evaluate Eq.~(\ref{e472}) to second order in $\epsilon_d$ in order to include the perpendicular transport term. Doing so,
we obtain
\begin{equation}
0=\epsilon_d\,\{{\cal V}_1,{\mit\Omega}\} + \epsilon_\chi\,(X^2\,d_{\mit\Omega} {\cal V}_{(0)} + {\cal V}_{(0)}),
\end{equation}
where use has been made of Eqs.~(\ref{e498}) and (\ref{e508}). The flux-surface average of the
previous equation yields
\begin{equation}
\langle X^2\rangle\,d_{\mit\Omega} {\cal V}_{(0)} +\langle 1\rangle \,{\cal V}_{(0)}= 0.
\end{equation}
 The previous equation can be solved, subject to the boundary condition (\ref{e486a}), to
give
\begin{equation}
{\cal V}_{(0)}({\mit\Omega}, T) = 0.
\end{equation}
Hence, we conclude that the lowest-order ion parallel flow is unaffected by the presence of the island chain.

\subsection{Asymptotic Matching}
Now that we have solved the resonant response model in the immediate vicinity of the magnetic island chain, it is
necessary to asymptotically match this solution to the solution in the outer region. 
It is easily seen that  
\begin{align}
{\rm Re}\!\left(\frac{{\mit\Delta}{\mit\Psi}_s}{{\mit\Psi}_s}\right)&=\frac{2}{\hat{w}}\int_{-\infty}^{\infty}\oint
\partial_X^{\,2}{\mit\Psi}\,\cos\zeta\,\frac{d\zeta}{2\pi}\,dX,\\[0.5ex]
{\rm Im}\!\left(\frac{{\mit\Delta}{\mit\Psi}_s}{{\mit\Psi}_s}\right)&=-\frac{2}{\hat{w}}\int_{-\infty}^{\infty}\oint
\partial_X^{\,2}{\mit\Psi}\,\sin\zeta\,\frac{d\zeta}{2\pi}\,dX.
\end{align}
However, according to Eqs.~(\ref{e473}) and (\ref{e496}),
\begin{equation}
\partial_X^{\,2}{\mit\Psi} = 1 + \epsilon_\beta\,\epsilon_d\,{\cal J}_0 + \epsilon_\beta\,\epsilon_d^{\,2}\,{\cal J}_1.
\end{equation}
Moreover, it is clear from Eqs.~(\ref{e524a}) and (\ref{e528a}) that ${\cal J}_0$ has the symmetry of $\cos\zeta$,
whereas ${\cal J}_1$ has the symmetry of $\sin\zeta$. 
Hence, we deduce that
\begin{align}
{\rm Re}\!\left(\frac{{\mit\Delta}{\mit\Psi}_s}{{\mit\Psi}_s}\right)&=\frac{2\,\epsilon_\beta\,\epsilon_d}{\hat{w}}\int_{-\infty}^{\infty}\oint
{\cal J}_0\,\cos\zeta\,\frac{d\zeta}{2\pi}\,dX,\\[0.5ex]
{\rm Im}\!\left(\frac{{\mit\Delta}{\mit\Psi}_s}{{\mit\Psi}_s}\right)&=-\frac{2\,\epsilon_\beta\,\epsilon_d^{\,2}}{\hat{w}}\int_{-\infty}^{\infty}\oint
{\cal J}_1\,\sin\zeta\,\frac{d\zeta}{2\pi}\,dX.
\end{align}
The previous two equations can also be written
\begin{align}
{\rm Re}\!\left(\frac{{\mit\Delta\Psi}_s}{{\mit\Psi}_s}\right)&=\frac{4\,\epsilon_\beta\,\epsilon_d}{\hat{w}}\int_{-1}^\infty
\langle {\cal J}_0\,\cos\zeta\rangle\,d{\mit\Omega},\label{e542}\\[0.5ex]
{\rm Im}\!\left(\frac{{\mit\Delta\Psi}_s}{{\mit\Psi}_s}\right)&=-\frac{4\,\epsilon_\beta\,\epsilon_d^{\,2}}{\hat{w}}\int_{-1}^\infty
\langle {\cal J}_1\,\sin\zeta\rangle\,d{\mit\Omega}=-\frac{4\,\epsilon_\beta\,\epsilon_d^{\,2}}{\hat{w}}\int_{-1}^\infty
\langle X\,\{{\cal J}_1,{\mit\Omega}\}\rangle\,d{\mit\Omega}.\label{e543}
\end{align}

Equations~(\ref{e528a}) and (\ref{e543}) can be combined to give\,\cite{fw,fw1}
\begin{align}
{\rm Im}\!\left(\frac{{\mit\Delta\Psi}_s}{\hat{\mit\Psi}_s}\right) &=\frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi}{\hat{w}}\int_1^\infty
\left\langle X^{2}\,d_{\mit\Omega}\!\left[d_{\mit\Omega}(X^3\,d_{\mit\Omega}Y_i)\right]\right\rangle d{\mit\Omega}\nonumber\\[0.5ex]
&=\frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi}{\hat{w}}\int_1^\infty d_{\mit\Omega}\!\left(-\langle X\rangle\,Y_i
+2\,\langle X^3\rangle\,d_{\mit\Omega} Y_i + \langle X^5\rangle\,d_{\mit\Omega}^{\,2} Y_i\right)d{\mit\Omega}\nonumber\\[0.5ex]
&= \frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi}{\hat{w}}\,\lim_{\mit\Omega\rightarrow\infty}\left(-\langle X\rangle\,Y_i
+2\,\langle X^3\rangle\,d_{\mit\Omega} Y_i + \langle X^5\rangle\,d_{\mit\Omega}^{\,2} Y_i\right),
\end{align}
where use has been made of the facts that $Y_i$ is zero inside the island separatrix, and $Y_i$ is continuous across the separatrix.
Combining the previous equation with Eq.~(\ref{e530}), we obtain\,\cite{fw}
\begin{equation}\label{e545}
{\rm Im}\!\left(\frac{{\mit\Delta}{\mit\Psi}_s}{{\mit\Psi}_s}\right)  =- \frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi\,v'}{\hat{w}}.
\end{equation}

Equations~(\ref{e524a}) and (\ref{e542}) can be combined to give
\begin{align}
{\rm Re}\!\left(\frac{{\mit\Delta}{\mit\Psi}_s}{{\mit\Psi}_s}\right)&= \frac{2\,\epsilon_\beta\,\epsilon_d}{\hat{w}}
\int_{1+}^\infty d_{\mit\Omega}(M\,Y_i)\left\langle\widetilde{X^2}\,\cos\zeta\right\rangle d{\mit\Omega}
+\frac{4}{\epsilon_\eta\,\hat{w}}\,\frac{d(\ln \hat{w}^2)}{dT}\int_{-1}^\infty \frac{\langle \cos\zeta\rangle^2}{\langle 1\rangle}\,d{\mit\Omega}
\end{align}
Making use of Eqs.~(\ref{e526}) and (\ref{e530}), the previous equation yields
\begin{align}
{\rm Re}\!\left(\frac{{\mit\Delta}{\mit\Psi}_s}{{\mit\Psi}_s}\right)&= -\frac{2\,\epsilon_\beta\,\epsilon_d\,v'}{(1+\tau)\,\hat{w}}
\int_1^\infty d_{\mit\Omega}\!\left(\frac{F_i}{\langle X^2\rangle}\right)\left\langle\widetilde{X^2}\,\cos\zeta\right\rangle d{\mit\Omega}
\nonumber\\[0.5ex]
&\phantom{=}+ \frac{2\,\epsilon_\beta\,\epsilon_d\,v'^{\,2}}{\hat{w}} \,\int_1^\infty d_{\mit\Omega}\!\left(F_i^{\,2}\right)\left\langle\widetilde{X^2}\,\cos\zeta\right\rangle d{\mit\Omega}\nonumber\\[0.5ex]
&\phantom{=}+\frac{4}{\epsilon_\eta\,\hat{w}}\,\frac{d(\ln \hat{w}^2)}{dT}\int_{-1}^\infty \frac{\langle \cos\zeta\rangle^2}{\langle 1\rangle}\,d{\mit\Omega},\label{e547}
\end{align}
where
\begin{equation}
F_i({\mit\Omega})=\left.\int_1^{\mit\Omega}\frac{d{\mit\Omega}'}{\langle X^4\rangle}\right/\int_1^\infty\frac{d{\mit\Omega}}{\langle X^4\rangle}
\end{equation}
Finally, Eqs.~(\ref{e545}) and (\ref{e547})
can be combined to give\,\cite{fw,fw1}
\begin{align}\label{e559}
{\rm Re}\!\left(\frac{{\mit\Delta}{\mit\Psi}_s}{{\mit\Psi}_s}\right)&= I_1\,\tau_R\,\frac{d}{dt}\!\left(\frac{4\,w}{r_s}\right)
- \frac{I_2}{4}\left(\frac{c_\beta}{1+\tau}\right)\left(\frac{\rho_\beta}{r_s}\right)\left(\frac{\tau_\varphi}{\tau_H}\right)\left(\frac{w}{r_s}\right)^2 {\rm Im}\!\left(\frac{{\mit\Delta\Psi}_s}{{\mit\Psi}_s}\right)\nonumber\\[0.5ex]
&\phantom{=} -\frac{I_3}{16}\left(\frac{\tau_\varphi}{\tau_H}\right)^2 \left(\frac{w}{r_s}\right)^7\left[{\rm Im}\!\left(\frac{{\mit\Delta\Psi}_s}{{\mit\Psi}_s}\right)\right]^2, 
\end{align}
where
\begin{align}
I_1 &= 2\int_{-1}^\infty \frac{\langle \cos\zeta\rangle^2}{\langle 1\rangle}\,d{\mit\Omega} =0.8227,\\[0.5ex]
I_2&= \int_1^\infty d_{\mit\Omega}\!\left(\frac{F_i}{\langle X^2\rangle}\right)\left(\langle X^4\rangle - \frac{\langle X^2\rangle^2}{\langle 1\rangle}\right)d{\mit\Omega} =0.1955,\\[0.5ex]
I_3&= \int_1^\infty d_{\mit\Omega}\!\left(F_i^{\,2}\right)\left(\langle X^4\rangle - \frac{\langle X^2\rangle^2}{\langle 1\rangle}\right)d{\mit\Omega} =0.4711.
\end{align}

\section*{Acknowledgements}
This research was directly funded by the U.S.\ Department of Energy, Office of Science, Office of Fusion Energy Sciences,  under  contracts DE-FG02-04ER54742 and DE-SC0021156.

\section*{Disclaimer} This report was prepared as an account of work sponsored by an agency of the United States Government. Neither the United States Government nor any agency thereof, nor any of their employees, makes any warranty, express or implied, or assumes any legal liability or responsibility for the accuracy, completeness, or usefulness of any information, apparatus, product, or process disclosed, or represents that its use would not infringe privately owned rights. Reference herein to any specific commercial product, process, or service by trade name, trademark, manufacturer, or otherwise does not necessarily constitute or imply its endorsement, recommendation, or favoring by the United States Government or any agency thereof. The views and opinions of authors expressed herein do not necessarily state or reflect those of the United States Government or any agency thereof.

\section*{Data Availability Statement}
The data that support the findings of this study are available from the corresponding author upon reasonable request.

\section*{References}
\begin{thebibliography}{99}\baselineskip 5ex

\bibitem{wes} J.A.~Wesson, Nucl.\ Fusion {\bf 18}, 87 (1978).

\bibitem{nave} M.F.F.~Nave, and J.A.~Wesson, Nucl.\ Fusion {\bf 30}, 2575 (1990).

\bibitem{vries} P.C.~de\,Vries, M.F.~Johnson, B.~Alper, P.~Buratti, T.C.~Hender, H.R.~Koslowski, et al., Nucl.\ Fusion {\bf 51}, 053018 (2011).
\bibitem{ara} G.~Ara, B.~Basu, B.~Coppi, G.~Laval, M.N.~Rosenbluth, and B.V.~Waddell, Ann.\ Phys.\ (NY) {\bf 112}, 443 (1978).

\bibitem{fw} R.~Fitzpatrick, and F.L.~Waelbroeck, Phys. Plasmas {\bf 12}, 022307 (2005).

\bibitem{fw1} R.~Fitzpatrick, and F.L.~Waelbroeck, Phys. Plasmas {\bf 12}, 022308 (2005).

\bibitem{haz} R.D.~Hazeltine, M.~Kotschenreuther, and P.G.~Morrison, Phys.\ Fluids {\bf 28}, 2466 (1985).

\bibitem{rf2021} R.~Fitzpatrick, Phys.\ Plasmas {\bf 28}, 022503 (2021).

\bibitem{rf1993} R.~Fitzpatrick, Nucl.\ Fusion {\bf 33}, 1049 (1993).

\bibitem{fkr} H.P.~Furth, J.~Killeen, and M.N.~Rosenbluth, Phys.\ Fluids {\bf 6}, 459 (1963).

\bibitem{scott} B.D.~Scott,  A.B.~Hassam, and J.F.~Drake, Phys.\ Fluids {\bf 28}, 275 (1985).

\bibitem{rff} R.~Fitzpatrick, Phys.\ Plasmas {\bf 2}, 825 (1995).

\bibitem{rutherford} P.H.~Rutherford, Phys.\ Fluids {\bf 16}, 1903 (1985).

\bibitem{smol1} A.I.~Smolyakov, Plasma Phys.\ Control.\ Fusion {\bf 35}, 657 (1993).

\bibitem{smol2} A.I.~Smolyakov, A.~Hirose E.~Lazzaro, G.B.~Re, and  J.D.~Callen, Phys.\ Plasmas {\bf 2}, 1581 (1995).

\bibitem{wf} F.L.~Waelbroeck, and R.~Fitzpatrick, Phys.\ Rev.\ Lett.\ {\bf 78}, 1703 (1997).

\end{thebibliography}

\end{document}

### 2021-12-11 Research/TearingModeTheory/TearingModeTheory.tex
Started writing linear and nonlinear papers

--- 2021-12-04 Documentation/TearingModeTheory.tex
@@
 and $\bar{\rho}_e =\bar{ v}_e/(e\bar{B}/m_e)$  be typical values
-of the particle density, the electron thermal velocity, the electron collision time, the electron
+of the particle number density, the electron thermal velocity, the electron collision time, the electron
 mean-free-path between collisions,  the magnetic field-strength, and the
@@
 and $\bar{\rho}_i =\bar{ v}_i/(e\bar{B}/m_i)$  be typical values
-of the particle density, the ion  thermal velocity, the ion
+of the particle number density, the ion  thermal velocity, the ion
 mean-free-path between collisions,  the magnetic field-strength, and the
@@
 \end{equation}
-In other words, the parallel electron heat conductivity in a tokamak plasma is usually
+In other words, the parallel electron heat conductivity in a tokamak plasma equilibrium is usually
 sufficiently large that it forces the electron temperature to be constant on magnetic flux-surfaces. 
@@
 \end{equation}
-In other words, the parallel ion heat conductivity in a tokamak plasma is usually
+In other words, the parallel ion heat conductivity in a tokamak plasma equilibrium is usually
 sufficiently large that it forces the ion temperature to be constant on magnetic flux-surfaces.
@@
 \end{equation}
-where $p=p_e+p_i$. In other words, a conventional tokamak plasma exists in a state in which the magnetic force density exactly balances the  total scalar pressure force density. 
+where $p=p_e+p_i$. In other words, a  tokamak plasma equilibrium exists in a state in which the magnetic force density exactly balances the  total scalar pressure force density. 
 It follows from the previous equation that 
@@
 \end{equation}
-In other words, the total pressure in a conventional tokamak plasma is constant on magnetic flux-surfaces. 
+In other words, the total pressure in a  tokamak plasma equilibrium is constant on magnetic flux-surfaces. 
  However, given that $p=n\,(T_e+T_i)$, and making use of Eqs.~(\ref{e75}) and (\ref{e77}), we deduce that 
@@
 \end{equation}
-In other words, the electron number density in a conventional tokamak plasma is also  constant on
+In other words, the electron number density in a  tokamak plasma equilibrium is also  constant on
 magnetic flux-surfaces.
@@
 \end{equation}
-In other words,  the electrostatic potential is also constant on magnetic flux-surfaces.
+In other words,  the electrostatic potential in a tokamak plasma equilibrium  is also constant on magnetic flux-surfaces.
 
@@
 \begin{equation}\label{e93}
-\delta{\bf B} \simeq \nabla\times (\psi\,{\bf e}_z),
+\delta{\bf B} \simeq \nabla\times (\delta\psi\,{\bf e}_z),
 \end{equation}
@@
 \begin{equation}\label{e93a}
-\psi(r,\theta,\varphi,t)= \psi(r,t)\,\exp[{\rm i}\,(m\,\theta-n\,\varphi)].
+\delta\psi(r,\theta,\varphi,t)= \delta\psi(r,t)\,\exp[{\rm i}\,(m\,\theta-n\,\varphi)].
 \end{equation}
@@
 \begin{equation}\label{e94}
-\mu_0\,\delta {\bf j} \simeq - \nabla^2\psi\,{\bf e}_z.
+\mu_0\,\delta {\bf j} \simeq - \nabla^2\delta\psi\,{\bf e}_z.
 \end{equation}
@@
 \begin{equation}\label{e97}
-\frac{\partial^2\psi}{\partial r^2} + \frac{1}{r}\,\frac{\partial\psi}{\partial r}-\frac{m^2}{r^2}\,\psi - \frac{J_z'\,\psi}{r\,(1/q-n/m)}=  0,
+\frac{\partial^2\delta\psi}{\partial r^2} + \frac{1}{r}\,\frac{\partial\delta\psi}{\partial r}-\frac{m^2}{r^2}\,\delta\psi - \frac{J_z'\,\delta\psi}{r\,(1/q-n/m)}=  0,
 \end{equation}
@@
 \begin{equation}\label{e99}
-\psi(r,t)= {\mit\Psi}_s(t)\,\hat{\psi}_s(r),
+\delta\psi(r,t)= {\mit\Psi}_s(t)\,\hat{\psi}_s(r),
 \end{equation}
@@
 At the resonant surface, ${\bf k}\cdot{\bf B}=0$, where ${\bf k} = (0,\,m/r,\,-n/R_0)$ is the wavevector of the tearing perturbation. 
-The value of $\psi(r,t)$ at the resonant surface---namely, ${\mit\Psi}_s(t)$---is known as the {\em reconnected magnetic flux}\/ (Fitzpatrick 1993). (See Section~\ref{dis1}.)
+The value of $\delta\psi(r,t)$ at the resonant surface---namely, ${\mit\Psi}_s(t)$---is known as the {\em reconnected magnetic flux}\/ (Fitzpatrick 1993). (See Section~\ref{dis1}.)
 Note that ${\mit\Psi}_s$ is, in general, a complex quantity. 
@@
 Moreover,  the real parameters ${\mit\Delta}_{s+}$ and  ${\mit\Delta}_{s-}$ are fully determined by Equation~(\ref{e100})
-and the boundary conditions (\ref{e101})--(\ref{e103}). Note that, in general, $\psi$ is continuous across the resonant surface (in accordance with Maxwell's equations),
-whereas $\partial\psi/\partial r$ is discontinuous.
-The discontinuity in $\partial \psi/\partial r$ implies the presence of a radially-thin, helical,  current sheet  at the resonant surface.
+and the boundary conditions (\ref{e101})--(\ref{e103}). Note that, in general, $\delta\psi$ is continuous across the resonant surface (in accordance with Maxwell's equations),
+whereas $\partial\delta\psi/\partial r$ is discontinuous.
+The discontinuity in $\partial \delta\psi/\partial r$ implies the presence of a radially-thin, helical,  current sheet  at the resonant surface.
 This current sheet can only be resolved by retaining more terms in the perturbed plasma equation of motion, (\ref{e96}).
@@
 \begin{equation}\label{e109}
-{\mit\Delta\Psi}_s = \left[r\,\frac{\partial \psi}{\partial r}\right]_{r_{s-}}^{r_{s+}}
+{\mit\Delta\Psi}_s = \left[r\,\frac{\partial \delta\psi}{\partial r}\right]_{r_{s-}}^{r_{s+}}
 \end{equation}
@@
 \begin{equation}\label{e111}
-\psi(r,t) = {\mit\Psi}_s(t)\,\hat{\psi}_s(r) + {\mit\Psi}_w(t)\,\hat{\psi}_w(r),
+\delta\psi(r,t) = {\mit\Psi}_s(t)\,\hat{\psi}_s(r) + {\mit\Psi}_w(t)\,\hat{\psi}_w(r),
 \end{equation}
@@
 
-In general, $\psi$ is continuous across the wall (in accordance with Maxwell's equations), whereas $\partial\psi/\partial r$ is discontinuous.
-The discontinuity in $\partial\psi/\partial r$ is caused by a helical current sheet induced in the wall.
+In general, $\delta\psi$ is continuous across the wall (in accordance with Maxwell's equations), whereas $\partial\delta\psi/\partial r$ is discontinuous.
+The discontinuity in $\partial\delta\psi/\partial r$ is caused by a helical current sheet induced in the wall.
 The complex quantity ${\mit\Psi}_w(t)$ determines the amplitude and
@@
 \begin{equation}\label{e118}
-{\mit\Delta\Psi}_w = \left[r\,\frac{\partial\psi}{\partial r}\right]_{r_{w-}}^{r_{w+}}
+{\mit\Delta\Psi}_w = \left[r\,\frac{\partial\delta\psi}{\partial r}\right]_{r_{w-}}^{r_{w+}}
 \end{equation}
@@
 \begin{equation}
-\delta {\bf A} \simeq \psi\,{\bf e}_z,
+\delta {\bf A} \simeq \delta\psi\,{\bf e}_z,
 \end{equation}
@@
 \begin{equation}
-\delta {\bf E} \simeq -\nabla\delta{\mit\Phi} - \frac{\partial\psi}{\partial t}\,{\bf e}_z,
+\delta {\bf E} \simeq -\nabla\delta{\mit\Phi} - \frac{\partial\delta\psi}{\partial t}\,{\bf e}_z,
 \end{equation}
 where $\delta{\mit\Phi}$ is the perturbed electric scalar potential. 
-Assuming that $|\nabla\delta{\mit\Phi}|\sim |\partial\psi/\partial t|$, the $z$-component of the previous
+Assuming that $|\nabla\delta{\mit\Phi}|\sim |\partial\delta\psi/\partial t|$, the $z$-component of the previous
 equation yields
 \begin{equation}
-\delta E_z\simeq -\frac{\partial\psi}{\partial t},
+\delta E_z\simeq -\frac{\partial\delta\psi}{\partial t},
 \end{equation}
@@
 \end{equation}
-Here, we are making use of the so-called {\em thin wall approximation}, according to which $\psi$ is assumed to only vary weakly in $r$ across 
+Here, we are making use of the so-called {\em thin wall approximation}, according to which $\delta\psi$ is assumed to only vary weakly in $r$ across 
 the wall. Ohm's law implies that
@@
 resonant layer surrounding the resonant surface), whereas $\omega_s$ is the {\em natural frequency}\/ of the tearing mode.
-The natural frequency is defined as oscillation frequency of a naturally unstable tearing mode.
+The natural frequency is defined as the oscillation frequency of a naturally unstable tearing mode.
 The
@@
 \begin{equation}
-\psi(r,t) = {\mit\Psi}_s(t)\,\hat{\psi}_s(r) + {\mit\Psi}_w(t)\,\hat{\psi}_w(r) + {\mit\Psi}_c\,\hat{\psi}_c(r),
+\delta\psi(r,t) = {\mit\Psi}_s(t)\,\hat{\psi}_s(r) + {\mit\Psi}_w(t)\,\hat{\psi}_w(r) + {\mit\Psi}_c\,\hat{\psi}_c(r),
 \end{equation}
@@
 
-In general, $\psi$ is continuous across the field-coil (in accordance with Maxwell's equations), whereas $\partial\psi/\partial r$ is discontinuous.
-The discontinuity in $\partial\psi/\partial r$ is caused by the helical current flowing in the coil.
+In general, $\delta\psi$ is continuous across the field-coil (in accordance with Maxwell's equations), whereas $\partial\delta\psi/\partial r$ is discontinuous.
+The discontinuity in $\partial\delta\psi/\partial r$ is caused by the helical current flowing in the coil.
 The complex quantity ${\mit\Psi}_c(t)$ determines the amplitude and
@@
 \begin{equation}\label{e118a}
-{\mit\Delta\Psi}_c = \left[r\,\frac{\partial\psi}{\partial r}\right]_{r_{c-}}^{r_{c+}}
+{\mit\Delta\Psi}_c = \left[r\,\frac{\partial\delta\psi}{\partial r}\right]_{r_{c-}}^{r_{c+}}
 \end{equation}
@@
 
-\subsection{No-Slip Constraint}\label{sns}
+\subsection{Modification of Natural Frequency}\label{sns}
 The reconnected magnetic flux at the resonant surface is assumed to convected by the local plasma flow. (See Section~\ref{sres}.) Hence, changes in the
@@
 where $\omega_{s\,0}$ is the unperturbed natural frequency. 
-The previous expression is known as the {\em no-slip constraint}\/ (Fitzpatrick 1993), and has been verified experimentally (Vahala, et al.\ 1980).
+%The previous expression is known as the {\em no-slip constraint}\/ (Fitzpatrick 1993), and has been verified experimentally (Vahala, et al.\ 1980). 
 It follows from Equations~(\ref{e190})
@@
 \end{equation}
-Here, $\nabla\cdot\bpi_i$ includes the contribution from the anomalous (i.e., enhanced due to the action of small-scale plasma turbulence) perpendicular viscosity tensor.
-The contribution from the gyroviscosity tensor,
+Here, $\nabla\cdot\bpi_i$ includes the contribution from the anomalous (i.e., enhanced due to the action of small-scale plasma turbulence) ion perpendicular viscosity tensor.
+The contribution from the ion gyroviscosity tensor,
 which is the same size as the ion inertial terms, has already been incorporated into the equation (Hazeltine \& Meiss 1992).
-For the moment, we are neglecting the contribution of the parallel viscosity tensor.
+For the moment, we are neglecting the contribution of the ion parallel viscosity tensor.
 The neglect of electron inertia and electron viscosity in the previous equation is justified because
@@
 \begin{equation}\label{e247a}
-\hat{\psi}=\frac{\psi}{r_s\,B_z},
-\end{equation}
- where $\psi$ is defined in Equation~(\ref{e93}).
+\hat{\psi}=\frac{\psi_0+\delta\psi}{r_s\,B_z},
+\end{equation}
+ where $\psi_0(r) = \int_{r_s}^r r'(1/q_s-1/q)\,(B_z/R_0)\,dr'$, and $\delta\psi$ is defined in Equation~(\ref{e93}).
  Here, $\delta b(\hat{x},\zeta,
@@
  \frac{\partial\delta p}{\partial\hat{t}}= [\phi,\delta p]+\hat{\nabla}^2{\mit\Xi}-[\hat{V}_{\parallel\,i},\hat{\psi}]
- -\hat{d}_i\,[J,\hat{\psi}] +\hat{\eta}_\perp\,\hat{\nabla}^{\,2}\delta p.
+ -\hat{d}_i\,[J,\hat{\psi}] +\hat{\eta}_\perp\,\hat{\nabla}^{2}\delta p.
  \end{equation}
@@
 \end{equation}
-Assuming that $X\sim{\cal O}(1)$ in the layer (i.e., assuming that the layer thickness is of order $S^{-1/3}\,r_s$),
+Assuming that $X\sim{\cal O}(1)$ in the layer (i.e., assuming that the layer thickness is roughly of order $S^{-1/3}\,r_s$),
 and making use of the fact that $S\gg 1$, we deduce that $\hat{\nabla}^2\simeq \hat{\nabla}_\perp^2\simeq S^{\,2/3}\,d^{\,2}/dX^2$.
@@
 This response regime is known as the {\em resistive-inertial regime}, because the layer response is dominated by
-resistivity and ion inertia (Furth, Killeen \& Rosenbluth 1963; Ara, et al.\ 1976; Fitzpatrick 1998). The characteristic layer width is $p_\ast \sim Q^{-1/4}$,
+plasma resistivity and ion inertia (Furth, Killeen \& Rosenbluth 1963; Ara, et al.\ 1976; Fitzpatrick 1998). The characteristic layer width is $p_\ast \sim Q^{-1/4}$,
 which implies that the regime is valid when $P\ll Q^{3/2}$, $Q\gg D^4$, and $Q\ll 1$.
@@
 \end{equation}
-This response regime is known as the {\em visco-resistive regime}, because the layer response is dominated by
-resistivity and  ion perpendicular viscosity (Bondeson \& Persson 1986; Fitzpatrick 1993). The characteristic layer width is $p_\ast \sim P^{-1/6}$, which implies that
+This response regime is known as the {\em viscous-resistive regime}, because the layer response is dominated by
+ion perpendicular viscosity and plasma resistivity  (Bondeson \& Persson 1986; Fitzpatrick 1993). The characteristic layer width is $p_\ast \sim P^{-1/6}$, which implies that
 the regime is valid when  $P\gg Q^{3/2}$, $P\gg D^6$, and $P\ll Q^{-3}$.
@@
 \end{equation}
-This response regime is known as the {\em Hall-resistive regime}\/ (Cole \& Fitzpatrick 2006). The characteristic
+This response regime is known as the {\em diffusive-resistive regime}, because the layer 
+response is dominated by perpendicular particle diffusivity and plasma resistivity. The characteristic
 layer width is $p_\ast \sim D^{1/2}\,P^{-1/4}$, which implies that the regime is valid when $P\gg Q^2/D^2$,
@@
 
-\subsection{Nonconstant-$\psi$ Regimes}\label{sncp}
+\subsection{Nonconstant-$\psi$ Linear Response Regimes}\label{sncp}
 Suppose that $p\ll Q^{1/2}$. In this limit, Equation~(\ref{e320}) reduces to 
@@
 \caption{Linear resonant plasma response regimes in $Q$-$P$ space for the case $D=0.9$. The various regimes are
-the Hall-resisitive (HR), the semi-collisional (SC), the resistive-inertial (RI), the visco-resistive (VR), the visco-inertial
+the diffusive-resisitive (DR), the semi-collisional (SC), the resistive-inertial (RI), the viscous-resistive (VR), the viscous-inertial
 (VI), and the inertial (I).}\label{f1}
@@
  equivalent to that of two closely-spaced Alfv\'{e}n resonances that straddle the resonant surface (Boozer 1996). 
+ In fact, it is easily demonstrated that in real space,
+ \begin{equation}
+ \hat{\mit\Delta} = \int_{-\infty}^\infty \frac{dX}{(Q-Q_E)\,(Q-Q_E-Q_i)-X^{\,2}},
+ \end{equation}
+ which suggests that the resonances lie at $X=\pm \sqrt{(Q-Q_E)\,(Q-Q_E-Q_i)}$. 
  The characteristic layer width is $p_\ast \sim Q^{-1}$,
@@
 \end{equation}
-This response regime is known as the {\em visco-inertial regime}, because the layer response is dominated by
+This response regime is known as the {\em viscous-inertial regime}, because the layer response is dominated by
 ion perpendicular viscosity and ion inertia (Fitzpatrick 1998). 
@@
 \end{equation}
-This response regime is known as the {\em Hall-viscous regime}. The characteristic layer width is $p_\ast\sim
+This response regime is known as the {\em diffusive-inertial regime}, because the
+layer response is dominated by perpendicular particle diffusivity and ion inertia. The characteristic layer width is $p_\ast\sim
 D\,Q^{-1/2}\,P^{-1/2}$, which implies that the regime is valid when $Q\ll D$, $P\ll D^4/Q$, and $P\gg D^2/Q^2$.
@@
 \caption{Linear resonant plasma response regimes in $Q$-$P$ space for the case $D=1.2$. The various regimes are
-the Hall-resisitive (HR), the semi-collisional (SC), the Hall-viscous (HV), the visco-resistive (VR), the visco-inertial
+the diffusive-resisitive (DR), the semi-collisional (SC), the diffusive-inertial (DI), the viscous-resistive (VR), the viscous-inertial
 (VI), and the inertial (I).}\label{f2}
@@
 According to the  analysis of Section~\ref{scp}, $\hat{\mit\Delta}\,p_\ast^{-1}$ takes the respective values $Q^{1/2}$, $Q\,P^{1/3}$, 
-$Q^2/D^2$, and $Q\,P^{1/2}/D$ in the resistive-inertial, visco-resistive, semi-collisional, and
-Hall-resistive response regimes. Moreover, it is clear from Figures~\ref{f1} and \ref{f2} that these values are all
+$Q^2/D^2$, and $Q\,P^{1/2}/D$ in the resistive-inertial, viscous-resistive, semi-collisional, and
+diffusive-resistive response regimes. Moreover, it is clear from Figures~\ref{f1} and \ref{f2} that these values are all
 much less than unity. In other words, it is indeed the case that $\tilde{\psi}$ does not vary substantially across a
 `constant-$\psi$' resonant layer. On the other hand, according to the analysis of Section~\ref{sncp}, $\hat{\mit\Delta}\,p_\ast^{-1}\sim 1$ in the inertial,
-visco-inertial, and Hall-viscous response regimes, which implies that $\tilde{\psi}$ does vary substantially
+viscous-inertial, and diffusive-inertial response regimes, which implies that $\tilde{\psi}$ does vary substantially
 across a `nonconstant-$\psi$' layer.
@@
 
-In the various constant-$\psi$ linear response regimes considered in this section, Equation~(\ref{e355}) reduces to an equation of the form
+In the various constant-$\psi$ linear growth-rate regimes considered in this section, Equation~(\ref{e355}) reduces to an equation of the form
 \begin{equation}
@@
 \end{equation}
-and $p_\ast\sim P^{1/2}/Q_\ast$. This so-called {\em resistive-inertial regime}\/ is valid when $P\ll Q_\ast^{3/2}$ and
+and $p_\ast\sim P^{1/2}/Q_\ast$. This so-called {\em resistive-inertial growth-rate regime}\/ is valid when $P\ll Q_\ast^{3/2}$ and
 $P\gg Q_\ast\,D^2$. 
@@
 \end{equation}
-and $p_\ast\sim P^{-1/6}$. This so-called {\em visco-resistive regime}\/ is valid when $P\gg Q_\ast^{3/2}$ and
+and $p_\ast\sim P^{-1/6}$. This so-called {\em viscous-resistive growth-rate regime}\/ is valid when $P\gg Q_\ast^{3/2}$ and
 $P\gg D^6$. 
@@
 \end{equation}
-and $p_\ast\sim D/Q_\ast^{1/2}$. This so-called {\em semi-collisional regime}\/ is valid when $P\ll Q_\ast^{\,2}/D^2$ and
+and $p_\ast\sim D/Q_\ast^{1/2}$. This so-called {\em semi-collisional growth-rate regime}\/ is valid when $P\ll Q_\ast^{\,2}/D^2$ and
 $P\ll Q_\ast\,D^2$. 
@@
 \end{equation}
-and $p_\ast \sim D^{1/2}/P^{1/4}$. This so-called {\em Hall-resistive regime}\/ is valid when $P\gg Q_\ast^2/D^2$ and
+and $p_\ast \sim D^{1/2}/P^{1/4}$. This so-called {\em diffusive-resistive growth-rate regime}\/ is valid when $P\gg Q_\ast^2/D^2$ and
 $P\ll D^6$. The corresponding tearing mode growth-rate is 
@@
 \caption{Linear tearing mode growth-rate regimes  in $Q_\ast$-$P$ space. The various regimes are
-the Hall-resisitive (HR), the semi-collisional (SC),  the visco-resistive (VR), and the resistive-inertial (RI).}\label{f3}
+the diffusive-resisitive (DR), the semi-collisional (SC),  the viscous-resistive (VR), and the resistive-inertial (RI).}\label{f3}
 \end{figure}
@@
 
- There are four tearing-mode growth-rate regimes---the resistive-inertial, the visco-resistive, the semi-collisional, and the Hall-resistive---and their extents in $Q_\ast$-$P$ space are illustrated in Figure~\ref{f3}.
+ There are four tearing-mode growth-rate regimes---the resistive-inertial, the viscous-resistive, the semi-collisional, and the diffusive-resistive---and their extents in $Q_\ast$-$P$ space are illustrated in Figure~\ref{f3}.
 Note that Figure~\ref{f3} differs somewhat from Figures~\ref{f1} and \ref{f2} because in the latter two
@@
 This refined ordering eliminates the nonconstant-$\psi$ response regimes, and significantly modifies the
-resistive-inertial response regime.
+extent of the resistive-inertial growth-rate regime.
 
@@
 Diamagnetic flows modify the tearing mode growth-rate in the resistive-inertial and semi-collisional
-growth-rate regimes, but not in the Hall-resistive and visco-resistive regimes. Anomalous perpendicular
+growth-rate regimes, but not in the diffusive-resistive and viscous-resistive regimes. Anomalous perpendicular
 transport modifies the growth-rate in all regimes except the semi-collisional regime. Finally, finite ion sound radius 
-effects modify the growth-rate in the Hall-resistive and semi-collisional regimes, but not in the other two
+effects modify the growth-rate in the diffusive-resistive and semi-collisional regimes, but not in the other two
 regimes.
@@
 confinement timescales (which it generally does by, at least, a factor of 10). Hence, consulting Figures~\ref{f1} and \ref{f2},
-we can see that the appropriate linear resonant response regime is either the visco-resistive regime or the Hall-resistive
+we can see that the appropriate linear resonant response regime is either the viscous-resistive regime or the diffusive-resistive
 regime.
@@
 According to the analysis of Section~\ref{scp}, and making use of the fact that $\omega=Q=0$ for a static perturbation, 
-in the visco-resistive response regime we have
+in the viscous-resistive response regime we have
 \begin{equation}
@@
 \end{equation}
-is the visco-resistive layer width (normalized to $r_s$). Here, $\omega_{\perp\,e}$ is defined in Equation~(\ref{e354}), and
+is the viscous-resistive layer width (normalized to $r_s$). Here, $\omega_{\perp\,e}$ is defined in Equation~(\ref{e354}), and
 ${\mit\Delta}\omega_E$ is the modification to the ${\bf E}\times{\bf B}$ frequency generated at the resonant surface by
 the electromagnetic torques that develop there in response to the error-field. Likewise, in the
-Hall-resistive regime we have
-\begin{equation}
-{\mit\Delta}_{\rm HR} = {\rm i}\,\tau_{\rm HR}\,(\omega_{\perp\,e}+{\mit\Delta}\omega_E),
-\end{equation}
-where $\tau_{\rm HR} = \tau_R\,\hat{\delta}_{\rm HR}$, and
-\begin{equation}
-\hat{\delta}_{\rm HR} = \frac{2\pi\,{\mit\Gamma}(3/4)}{{\mit\Gamma}(1/4)\,[1+\lambda_e\,\tau/(1+\tau)]^{1/4}}\,
+diffusive-resistive regime we have
+\begin{equation}
+{\mit\Delta}_{\rm DR} = {\rm i}\,\tau_{\rm DR}\,(\omega_{\perp\,e}+{\mit\Delta}\omega_E),
+\end{equation}
+where $\tau_{\rm DR} = \tau_R\,\hat{\delta}_{\rm DR}$, and
+\begin{equation}
+\hat{\delta}_{\rm DR} = \frac{2\pi\,{\mit\Gamma}(3/4)}{{\mit\Gamma}(1/4)\,[1+\lambda_e\,\tau/(1+\tau)]^{1/4}}\,
 \frac{\tau_H^{1/2}}{(d_\beta/r_s)^{1/2}\,\tau_R^{1/4}\,\tau_\perp^{1/4}}
 \end{equation}
-is the Hall-resistive layer width (normalized to $r_s$).
+is the diffusive-resistive layer width (normalized to $r_s$).
 
@@
 \begin{equation}
-\hat{\delta} = \frac{\hat{\delta}_{\rm VR}\,\hat{\delta}_{\rm HR}}{\hat{\delta}_{\rm VR} + \hat{\delta}_{\rm HR}},
+\hat{\delta} = \frac{\hat{\delta}_{\rm VR}\,\hat{\delta}_{\rm DR}}{\hat{\delta}_{\rm VR} + \hat{\delta}_{\rm DR}},
 \end{equation}
@@
 torques that develop there, is mirrored by an equal  shift in the ion fluid velocity. This is the
-essence of the no-slip constraint discussed in Section~\ref{sns}. The no-slip constaint follows from Equations~(\ref{e217}) and (\ref{e219})
+essence of  Equation~(\ref{e200}), which follows from Equations~(\ref{e217}) and (\ref{e219})
 because the torques do not modify the diamagnetic velocity at the resonant surface.
@@
 \zeta_s &= \frac{(-{\mit\Delta}_{nw})}{\tau_s\,\omega_{s\,0}}\ll 1,\\[0.5ex]
-\tilde{I}_{c\,{\rm crit}}&=\epsilon_s\,s_s\left(\frac{\tau_s\,\tau_H\,\omega_{s\,0}}{\tau_V}\right),\label{e420}
+\tilde{I}_{c\,{\rm crit}}&=(\epsilon_s\,s_s)\left(\frac{\tau_s}{\tau_V}\right)^{1/2}(\omega_{s\,0}\,\tau_H), \label{e420}
 \\[0.5ex]
@@
 \hat{\delta}_{\rm VR} = \left(\frac{\tau_{\rm VR}}{\tau_R}\right) \simeq\left(\frac{\tau_H}{\tau_R}\right)^{1/3}\left(\frac{\tau_R}{\tau_\varphi}\right)^{1/6}&\simeq \left(\frac{q_s}{\epsilon_s}\right)^{1/3}\left(\frac{m_e}{m_i}\right)^{1/6}\rho_\ast^{\,2/3}\,\nu_\ast^{\,1/3}\,\beta_\ast^{-1/3},\\[0.5ex]
-\hat{\delta}_{\rm HR} = \left(\frac{\tau_{\rm HR}}{\tau_R}\right) \simeq \left(\frac{\tau_H}{\tau_R}\right)^{1/2}\left(\frac{\tau_R}{\tau_\perp}\right)^{1/4}\left(\frac{r_s}{d_\beta}\right)^{1/2}&\simeq \left(\frac{m_e}{m_i}\right)^{1/4}\rho_\ast^{\,1/2}\,\nu_\ast^{\,1/2}\,\beta_\ast^{-1/2},\\[0.5ex]
-\frac{\sqrt{\tau_\varphi\, \tau_i/\mu_{00}^i}}{\tau_R}&\simeq \left(\frac{q_s}{r_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/4}\,\rho_\ast.
+\hat{\delta}_{\rm DR} = \left(\frac{\tau_{\rm DR}}{\tau_R}\right) \simeq \left(\frac{\tau_H}{\tau_R}\right)^{1/2}\left(\frac{\tau_R}{\tau_\perp}\right)^{1/4}\left(\frac{r_s}{d_\beta}\right)^{1/2}&\simeq \left(\frac{m_e}{m_i}\right)^{1/4}\rho_\ast^{\,1/2}\,\nu_\ast^{\,1/2}\,\beta_\ast^{-1/2},\\[0.5ex]
+\frac{\sqrt{\tau_\varphi\, \tau_i/\mu_{00}^i}}{\tau_R}&\simeq \left(\frac{q_s}{\epsilon_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/4}\,\rho_\ast.
 \end{align}
@@
 \caption{Error-field penetration regimes in $\hat{\nu}_\ast$-$\hat{\rho}_\ast$ space. The various regimes are the
-visco-resistive-toroidal (${\rm VR}$-$\varphi$), the visco-resistive-poloidal (${\rm VR}$-$\theta$), the Hall-resistive-poloidal (${\rm HR}$-$\theta$), and the  Hall-resistive-toroidal (${\rm HR}$-$\varphi$).
+viscous-resistive-toroidal (${\rm VR}$-$\varphi$), the viscous-resistive-poloidal (${\rm VR}$-$\theta$), the diffusive-resistive-poloidal (${\rm DR}$-$\theta$), and the  diffusive-resistive-toroidal (${\rm DR}$-$\varphi$).
 }\label{f6}
@@
 There are four error-field penetration regimes, depending on whether the plasma response in the resonant layer is
-in the visco-resistive or the Hall-resistive regime, and depending on whether the change in the ion rotation at the resonant surface, induced by the electromagnetic locking torque,  is
+in the viscous-resistive or the diffusive-resistive regime, and depending on whether the change in the ion fluid rotation at the resonant surface, induced by the electromagnetic locking torque,  is
 predominately toroidal or poloidal in nature. The plasma response in the resonant layer is in the
-visco-resisitive, rather than the Hall resistive, regime when $\tau_{\rm VR}<\tau_{\rm HR}$, or
+viscous-resisitive, rather than the diffusive-resistive, regime when $\tau_{\rm VR}<\tau_{\rm DR}$, or
 \begin{equation}
@@
 \end{align}
-As is illustrated in Figure~\ref{f6}, the {\em visco-resistive-toroidal regime}\/ (i.e., a visco-resistive layer response
-combined with a predominately toroidal change in the ion rotation) corresponds to $\hat{\rho}_\ast < \beta_\ast^{-1}\,\nu_\ast$ 
-and $\hat{\rho}_\ast <\beta_\ast$, the {\em visco-resisitive-poloidal regime}\/ corresponds to 
- $\hat{\rho}_\ast<\beta_\ast^{-1}\,\nu_\ast$ and $\hat{\rho}_\ast > \beta_\ast$, the {\em Hall-resisitive-poloidal regime}\/ corresponds to  
- $\hat{\rho}_\ast>\beta_\ast^{-1}\,\nu_\ast$ and $\hat{\rho}_\ast > \beta_\ast$, and the {\em Hall-resistive-toroidal regime}\/ corresponds to   
+As is illustrated in Figure~\ref{f6}, the {\em viscous-resistive-toroidal regime}\/ (i.e., a viscous-resistive layer response
+combined with a predominately toroidal change in the ion fluid rotation) corresponds to $\hat{\rho}_\ast < \beta_\ast^{-1}\,\nu_\ast$ 
+and $\hat{\rho}_\ast <\beta_\ast$, the {\em viscous-resisitive-poloidal regime}\/ corresponds to 
+ $\hat{\rho}_\ast<\beta_\ast^{-1}\,\nu_\ast$ and $\hat{\rho}_\ast > \beta_\ast$, the {\em diffusive-resisitive-poloidal regime}\/ corresponds to  
+ $\hat{\rho}_\ast>\beta_\ast^{-1}\,\nu_\ast$ and $\hat{\rho}_\ast > \beta_\ast$, and the {\em diffusive-resistive-toroidal regime}\/ corresponds to   
  $\hat{\rho}_\ast>\beta_\ast^{-1}\,\nu_\ast$ and $\hat{\rho}_\ast < \beta_\ast$.
-It can be seen that higher/lower plasma collisionality (i.e., $\nu_\ast$) favors the visco-resistive/Hall-resistive response regime, whereas a
-larger/smaller ion sound radius (i.e., $\rho_\ast$) favors poloidal/toroidal changes in the ion rotation. Finally, higher/lower plasma
+It can be seen that higher/lower plasma collisionality (i.e., $\nu_\ast$) favors the viscous-resistive/diffusive-resistive response regime, whereas a
+larger/smaller ion sound radius (i.e., $\rho_\ast$) favors poloidal/toroidal changes in the ion fluid rotation. Finally, higher/lower plasma
 pressure (i.e., $\beta_\ast$) 
-favors the Hall-resistive/visco-resistive response regime and toroidal/poloidal changes in the ion rotation.
-
-In the visco-resistive-toroidal response regime, the critical vacuum (i.e., in the absence of shielding currents) radial magnetic
+favors the diffusive-resistive/viscous-resistive response regime and toroidal/poloidal changes in the ion fluid rotation.
+
+In the viscous-resistive-toroidal response regime, the critical vacuum (i.e., in the absence of shielding currents) radial magnetic
 field at the resonant surface required to
@@
 where we have treated $-{\mit\Delta}_{nw}$ as an ignorable ${\cal O}(1)$ parameter. Likewise,  the critical
-field required to trigger penetration in the visco-resistive-poloidal regime is
+field required to trigger penetration in the viscous-resistive-poloidal regime is
 \begin{equation}
@@
 \end{equation}
-The critical field required to trigger penetration in the Hall-resistive-poloidal regime is
-\begin{equation}
-\left(\frac{b_{r}}{B_z}\right)_{{\rm HR}-\theta} \sim  \left(\frac{q_s}{\epsilon_s}\right)^{1/2}\left(\frac{m_e}{m_i}\right)^{0}
+The critical field required to trigger penetration in the diffusive-resistive-poloidal regime is
+\begin{equation}
+\left(\frac{b_{r}}{B_z}\right)_{{\rm DR}-\theta} \simeq  \left(\frac{q_s}{\epsilon_s}\right)^{1/2}\left(\frac{m_e}{m_i}\right)^{0}
 \rho_\ast^{\,3/4}\,\nu_\ast^{\,1/4}\,\beta_\ast^{\,1/4}.
@@
 Finally, the critical field 
-required to  trigger penetration in the Hall-resistive-toroidal regime is
-\begin{equation}
-\left(\frac{b_{r}}{B_z}\right)_{{\rm HR}-\varphi} \sim  \left(\frac{q_s}{\epsilon_s}\right)^{}\left(\frac{m_e}{m_i}\right)^{1/8}
+required to  trigger penetration in the diffusive-resistive-toroidal regime is
+\begin{equation}
+\left(\frac{b_{r}}{B_z}\right)_{{\rm DR}-\varphi} \simeq  \left(\frac{q_s}{\epsilon_s}\right)^{}\left(\frac{m_e}{m_i}\right)^{1/8}
 \rho_\ast^{\,5/4}\,\nu_\ast^{\,1/4}\,\beta_\ast^{-1/4}.\label{e447}
@@
 \left(\frac{b_{r}}{B_z}\right)_{{\rm VR}-\theta} &\propto n^{1/2}\,T^{\,5/12}\,B^{-3/2}\,R^{-2/3},\\[0.5ex]
-\left(\frac{b_{r}}{B_z}\right)_{{\rm HR}-\theta} &\propto n^{1/2}\,T^{\,1/8}\,B^{-5/4}\,R^{-1/2},\\[0.5ex]
-\left(\frac{b_{r}}{B_z}\right)_{{\rm HR}-\varphi} &\propto n^{0}\,T^{-1/8}\,B^{-3/4}\,R^{-1}.
+\left(\frac{b_{r}}{B_z}\right)_{{\rm DR}-\theta} &\propto n^{1/2}\,T^{\,1/8}\,B^{-5/4}\,R^{-1/2},\\[0.5ex]
+\left(\frac{b_{r}}{B_z}\right)_{{\rm DR}-\varphi} &\propto n^{0}\,T^{-1/8}\,B^{-3/4}\,R^{-1}.
 \end{align}
 It can be seen that the error-field penetration threshold exhibits no explicit dependence on the plasma
-density in regimes in which the change in the ion rotation at the resonant surface is predominately toroidal
+density in regimes in which the change in the ion fluid rotation at the resonant surface is predominately toroidal
 in nature (Fitzpatrick 1998; Cole \& Fitzpatrick 2006). On the other hand, the penetration threshold
-scales as $n^{1/2}$ in regimes in which the change in the ion rotation at the resonant surface is predominately poloidal 
+scales as $n^{1/2}$ in regimes in which the change in the ion fluid rotation at the resonant surface is predominately poloidal 
 in nature. An $n^{1/2}$ scaling of the penetration threshold has been observed in a number of tokamak
@@
 \left(\frac{b_{r}}{B_z}\right)_{{\rm VR}-\theta} &\propto n^{1/2}\,B^{-7/6}\,R^{-11/24},\\[0.5ex]
-\left(\frac{b_{r}}{B_z}\right)_{{\rm HR}-\theta} &\propto n^{1/2}\,B^{-23/20}\,R^{-7/16},\\[0.5ex]
-\left(\frac{b_{r}}{B_z}\right)_{{\rm HR}-\varphi} &\propto n^{0}\,B^{-17/20}\,R^{-17/16}.\label{e458}
-\end{align}
-Equations~(\ref{e455})--(\ref{e458}) confirm the $n^{0}$ scaling of the error-field penetration threshold in regimes in which the change in the ion rotation at the resonant surface is predominately toroidal
+\left(\frac{b_{r}}{B_z}\right)_{{\rm DR}-\theta} &\propto n^{1/2}\,B^{-23/20}\,R^{-7/16},\\[0.5ex]
+\left(\frac{b_{r}}{B_z}\right)_{{\rm DR}-\varphi} &\propto n^{0}\,B^{-17/20}\,R^{-17/16}.\label{e458}
+\end{align}
+Equations~(\ref{e455})--(\ref{e458}) confirm the $n^{0}$ scaling of the error-field penetration threshold in regimes in which the change in the ion fluid rotation at the resonant surface is predominately toroidal
 in nature, and the $n^{1/2}$ scaling when the change is predominately poloidal.
@@
 \left(\frac{W}{\delta}\right)_{{\rm VR}-\theta} &\simeq \left(\frac{q_s}{\epsilon_s}\right)^{1/3}\left(\frac{m_i}{m_e}\right)^{1/48}\rho_\ast^{-1/12}\,\nu_\ast^{\,1/12}\,\beta_\ast^{\,1/6},\\[0.5ex]
-\left(\frac{W}{\delta}\right)_{{\rm HR}-\theta} &\simeq \left(\frac{q_s}{\epsilon_s}\right)^{3/4}\left(\frac{m_i}{m_e}\right)^{1/8}\rho_\ast^{\,1/8}\,\nu_\ast^{-1/8}\,\beta_\ast^{\,3/8},\\[0.5ex]
-\left(\frac{W}{\delta}\right)_{{\rm HR}-\varphi} &\simeq \left(\frac{q_s}{\epsilon_s}\right)\left(\frac{m_i}{m_e}\right)^{1/16}\rho_\ast^{\,3/8}\,\nu_\ast^{-1/8}\,\beta_\ast^{\,1/8}.
+\left(\frac{W}{\delta}\right)_{{\rm DR}-\theta} &\simeq \left(\frac{q_s}{\epsilon_s}\right)^{3/4}\left(\frac{m_i}{m_e}\right)^{1/8}\rho_\ast^{\,1/8}\,\nu_\ast^{-1/8}\,\beta_\ast^{\,3/8},\\[0.5ex]
+\left(\frac{W}{\delta}\right)_{{\rm DR}-\varphi} &\simeq \left(\frac{q_s}{\epsilon_s}\right)\left(\frac{m_i}{m_e}\right)^{1/16}\rho_\ast^{\,3/8}\,\nu_\ast^{-1/8}\,\beta_\ast^{\,1/8}.
 \end{align}
@@
 V&\rightarrow \hat{V}_\parallel,\\[0.5ex]
-J& \rightarrow -\frac{2}{q_s\hat{R}_0} + \frac{1}{\hat{L}_s}.
+J& \rightarrow -\frac{2}{q_s\,\hat{R}_0} + \frac{1}{\hat{L}_s}.
 \end{align}
@@
 V&= \hat{V}_\parallel + \left(\frac{\hat{L}_s\,\hat{\omega}_\ast^{\,2}}{m^2\,c_\beta^{\,2}}\right){\cal V},\\[0.5ex]
-J & =-\frac{2}{q_s \hat{R}_0} + \frac{1}{\hat{L}_s} + \left(\frac{\hat{L}_s\,\hat{\omega}_\ast^{\,2}}{m^2\,\hat{w}^{\,2}}\right){\cal J}.
-\end{align}
+J & =-\frac{2}{q_s \hat{R}_0} + \frac{1}{\hat{L}_s} + \left(\frac{\hat{L}_s\,\hat{\omega}_\ast^{\,2}}{m^2\,\hat{w}^{\,2}}\right){\cal J},
+\end{align}
+where $\hat{\omega}_\ast = \omega_\ast/(V_A/r_s)$. 
 The four-field model specified in Section~\ref{fourf} rescales to give
@@
 Phys.\ Plasmas {\bf 27}, 072501.
-\item Fitzpatrick, R., and Waelbroeck, F.L.\ 2005. {\em Two-Fluid Magnetic Island Dynamics in Slab Geometry. I. Isolated Islands}.
+\item Fitzpatrick, R., and Waelbroeck, F.L.\ 2005. {\em Two-Fluid Magnetic Island Dynamics in Slab Geometry. I. Isolated Islands}. Phys.\ Plasmas {\bf 12}, 022307. 
 \item Fitzpatrick, R., and Waelbroeck, F.L.\ 2005a. {\em Two-Fluid Magnetic Island Dynamics in Slab Geometry. II. Islands Interacting with Resistive Walls or Resonant Magnetic Perturbations}.
@@
 \item Thyagaraja, A.\ 1981. {\em Perturbation Analysis of a Simple Model of Magnetic Island Structures}. Phys.\ Fluids {\bf 24}, 1716. 
-\item Vahala, G., et al.\ 1980. {\em Perturbed Magnetic-Field Phase Slip for Tokamaks}. Nucl.\ Fusion {\bf 20}, 17.
+%\item Vahala, G., et al.\ 1980. {\em Perturbed Magnetic-Field Phase Slip for Tokamaks}. Nucl.\ Fusion {\bf 20}, 17.
 \item Waelbroeck, F.L.\ 2003. {\em Shielding of Resonant Magnetic Perturbations in the Long Mean-Free Path Regime}. Phys.\ Plasmas {\bf 10}, 4040.

### 2021-12-12 Research/LinearTearingModeTheory/LinearTearingModeTheory.tex
Latest version

@@
 
-\section*{Disclaimer} This report was prepared as an account of work sponsored by an agency of the United States Government.
-Neither the United States Government nor any agency thereof, nor any of their employees, makes any warranty, express or implied, or assumes any legal liability or responsibility for the accuracy, completeness, or usefulness of any information, apparatus, product, or process disclosed, or represents that its use would not infringe privately owned rights.
-Reference herein to any specific commercial product, process, or service by trade name, trademark, manufacturer, or otherwise does not necessarily constitute or imply its endorsement, recommendation, or favoring by the United States Government or any agency thereof.
-The views and opinions of authors expressed herein do not necessarily state or reflect those of the United States Government or any agency thereof.
-
 \section*{Data Availability Statement}

### 2021-12-12 Research/NonlinearTearingModeTheory/NonlinearTearingModeTheory.tex
Latest version

@@
 and $\varphi=z/R_0$ is a simulated toroidal angle. 
-Throughout most of the plasma $\delta\psi(r,t)$ satisfies the
+Throughout most of the plasma, $\delta\psi(r,t)$ satisfies the
 {\em cylindrical tearing mode equation}:\cite{wes}
@@
 $J_z(r)= R_0\,\mu_0\,j_z(r)/B_z$,
-and $j_z(r)$ is the equilibrium `toroidal' current density. Here, $'\equiv d/dr$.
+and $j_z(r)$ is the equilibrium `toroidal' current density.
+Here, $'\equiv d/dr$.
+Note that Eq.~(\ref{e3}) is singular at the so-called {\em resonant}\/ magnetic flux-surface, radius $r=r_s$, at which
+$q(r_s)= m/n$.
 
@@
 
-Note that Eq.~(\ref{e100}) is singular at the so-called {\em resonant}\/ magnetic flux-surface, radius $r=r_s$, at which 
-$q(r_s)= m/n$. 
-As is well-known, the general solution of Eq.~(\ref{e100} is such that $\delta\psi$ is continuous across the resonant surface,
+As is well known, the general solution of Eq.~(\ref{e100}) is such that $\delta\psi$ is continuous across the resonant surface,
 whereas $\partial\delta\psi/\partial r$ is discontinuous. The discontinuity in $\partial \delta\psi/\partial r$ implies the presence of a helical  current sheet  at the resonant surface. 
 The complex quantity 
-\begin{equation}
+\begin{equation}\label{e108}
 {\mit\Psi}_s(t)= \delta\psi(r_s,t) 
@@
 $E_{ws} =-[r\,{d\hat\psi}_s/dr]_{r=r_{w-}}$
-are real quantities determined by the solutions of Eqs.~(\ref{e100}) and (\ref{e100a}) in the outer region.
+are real quantities determined by the solutions of Eqs.~(\ref{e100}) and (\ref{e100a}).
 It is easily demonstrated that 
@@
 Standard electromagnetic theory applied to the resistive wall reveals that\,\cite{nave,rf1993}
-\begin{equation}
+\begin{equation}\label{e9}
 {\mit\Delta\Psi}_w = \tau_w\,\frac{d{\mit\Psi}_w}{dt},
@@
 Here, $\eta_w$ and $\delta_w$ are the electrical resistivity and radial thickness  of the wall, respectively. 
+In deriving Eq.~(\ref{e9}), we have made use of the so-called {\em thin wall}\/ approximation, according to
+which the radial variation of $\delta\psi$ across the wall is negligible.  The thin wall approximation is
+valid as long as
+\begin{equation}
+\frac{r_w}{\delta_w}\gg \tau_w\left|\frac{d\ln{\mit\Psi}_w}{dt}\right|.
+\end{equation}
 
@@
 can be combined to give
-\begin{equation}
+\begin{equation}\label{e11}
 \frac{{\mit\Delta\Psi}_s}{{\mit\Psi}_s}= {\mit\Delta}_{pw} + \frac{{\mit\Delta}_{nw}-{\mit\Delta}_{pw}}{1-{\rm i}\,\omega\,\tau_{LR}},
@@
 
-Our resonant plasma response model takes the form:\cite{fw}
+Our resonant plasma response model takes the form:\,\cite{fw}
 \begin{align}
@@
 resistivity at the resonant surface, $E_\parallel$ the parallel inductive electric field that maintains the equilibrium toroidal
-plasma current in the vicinity of the resonant surface, and $\chi_\varphi$  the anomalous perpendicular ion momentum
+plasma current in the vicinity of the resonant surface, and $\chi_\varphi$  the (anomalous) perpendicular ion momentum
 diffusivity at the resonant surface. 
@@
 helpful to define the reduced island width:
-\begin{equation}
+\begin{equation}\label{e26a}
 w = \frac{W}{4}= \left(\frac{L_s\,{\mit\Psi}_s}{B_z}\right)^{1/2}.
@@
 gradient discontinuity at the resonant surface in response to the nonlinear localized electromagnetic torque that emerges 
-at the surface. Finally, 
+at the surface.\cite{fw} Finally, 
  $\hat{E}_\parallel =(2/s_s-1) \,(\hat{\eta}_\parallel/\hat{L}_s)$.
@@
 
-Equations~(\ref{e469})--(\ref{e473}) must be solved subject to the boundary conditions [see Eqs.~(\ref{e26})--(\ref{e30})] 
+Equations~(\ref{e469})--(\ref{e473}) must be solved subject to the boundary conditions [cf.\ Eqs.~(\ref{e26})--(\ref{e30})] 
 \begin{align}
@@
 \begin{align}
-v(T) &= \frac{\omega-\omega_E}{\omega_\ast},\label{e488}\\[0.5ex]
-v'(T) &= -\frac{\hat{w}}{2\,\omega_\ast}\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}}.\label{e489}
+v &= \frac{\omega-\omega_E}{\omega_\ast},\label{e488}\\[0.5ex]
+v' &= -\frac{\hat{w}}{2\,\omega_\ast}\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}}.\label{e489}
 \end{align}
@@
 variations in the normalized electron number density, ${\cal N}$, around magnetic flux-surfaces.\cite{scott} The fact that $\epsilon_d\ll 1$ implies that
-\begin{equation}
-w \gg \rho_\beta,
-\end{equation}
+$w \gg \rho_\beta$,
 where
@@
 chain is sufficiently wide that the perpendicular diffusion of magnetic flux, momentum, and particles are not dominant
-effects in the rescaled four-field equations. We shall also assume that $w/w_c\sim{\cal O}(1)$. In other words, the
+effects in the rescaled resonant response equations. We shall also assume that $w/w_c\sim{\cal O}(1)$. In other words, the
 island chain is sufficiently wide for the parallel diffusion of particles to compete with perpendicular diffusion.\cite{rff}
@@
 $\langle\{A,{\mit\Omega}\}\rangle = 0$
-for {\em any}\/ $A(s,{\mit\Omega},\zeta,T)$. It is helpful to define
+for any $A(s,{\mit\Omega},\zeta,T)$. It is helpful to define
 $\tilde{A}  \equiv A - \langle A\rangle/\langle 1\rangle$.
@@
 $\langle \tilde{A}\rangle =0$
- for {\em any}\/ $A(s,{\mit\Omega},\zeta,T)$.
+ for any $A(s,{\mit\Omega},\zeta,T)$.
 
@@
 \end{equation}
-where use has been made of Eq.~(\ref{e513}). Here, $Y_i= M + [1/(1+\tau)]\,L$. 
+where use has been made of Eq.~(\ref{e513}). Here, 
+\begin{equation}\label{yi}
+Y_i= M + \left(\frac{1}{1+\tau}\right)L.
+\end{equation} 
 The first term on the right-hand side of the previous equation represents the parallel return current driven by the perpendicular {\em polarization current}\/ associated with the
@@
 \int_1^{\mit\Omega}\! \frac{d{\mit\Omega}'}{\langle X^4\rangle}&~~&{\mit\Omega}>1
-\end{array}\right.
+\end{array}\right..
 \end{equation}
@@
 necessary to asymptotically match this solution to the solution in the outer region. 
-It is easily seen that  
+It is easily seen from Eqs.~(\ref{e108}) and (\ref{e109}) that  
 \begin{align}
@@
 \begin{align}
-{\rm Im}\!\left(\frac{{\mit\Delta\Psi}_s}{\hat{\mit\Psi}_s}\right) &=\frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi}{\hat{w}}\int_1^\infty
+{\rm Im}\!\left(\frac{{\mit\Delta\Psi}_s}{{\mit\Psi}_s}\right) &=\frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi}{\hat{w}}\int_1^\infty
 \left\langle X^{2}\,d_{\mit\Omega}\!\left[d_{\mit\Omega}(X^3\,d_{\mit\Omega}Y_i)\right]\right\rangle d{\mit\Omega}\nonumber\\[0.5ex]
@@
 \int_{1+}^\infty d_{\mit\Omega}(M\,Y_i)\left\langle\widetilde{X^2}\,\cos\zeta\right\rangle d{\mit\Omega}
-+\frac{4}{\epsilon_\eta\,\hat{w}}\,\frac{d(\ln \hat{w}^2)}{dT}\int_{-1}^\infty \frac{\langle \cos\zeta\rangle^2}{\langle 1\rangle}\,d{\mit\Omega}
++\frac{4}{\epsilon_\eta\,\hat{w}}\,\frac{d(\ln \hat{w}^2)}{dT}\int_{-1}^\infty \frac{\langle \cos\zeta\rangle^2}{\langle 1\rangle}\,d{\mit\Omega}. 
 \end{align}
@@
 
+\section{Isolated Magnetic Island Chains}
+\subsection{Introduction}
+Suppose, for the sake of argument,  that the wall surrounding the plasma is perfectly conducting (i.e.\, $\tau_{LR}\rightarrow\infty$). In this case, Eq.~(\ref{e11}) yields 
+\begin{equation}\label{e563}
+\frac{{\mit\Delta\Psi}_s}{{\mit\Psi}_s} ={\mit\Delta}_{pw},
+\end{equation}
+where ${\mit\Delta}_{pw}$ is the (real) perfect-wall tearing stability index. It is clear from the previous equation that
+\begin{equation}\label{e559x}
+{\rm Im}\!\left(\frac{{\mit\Delta\Psi}_s}{{\mit\Psi}_s}\right) = 0,
+\end{equation}
+which implies that zero electromagnetic torque is exerted at the resonant surface. In this respect, the magnetic island chain that develops at the resonant surface can be termed `isolated'.
+
+\subsection{Rutherford Island Width Evolution Equation}
+Equation~(\ref{e563}) implies that 
+\begin{equation}\label{e560x}
+{\rm Re}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right) = {\mit\Delta}_{pw}.
+\end{equation}
+Equations~(\ref{e26a}), (\ref{e559}), (\ref{e559x}), and (\ref{e560x}) yield the {\em Rutherford island width evolution equation}:\,\cite{rutherford}
+\begin{equation}\label{e561}
+I_1\,\tau_R\,\frac{d}{dt}\!\left(\frac{W}{r_s}\right)= {\mit\Delta}_{pw}.
+\end{equation}
+ According to the Rutherford equation, if the perfect-wall tearing stability index is positive then the width of the magnetic
+island chain at the resonant surface grows  algebraically on the resistive evolution timescale, $\tau_R$.
+
+\subsection{Saturated Island Width}\label{sat}
+Equation~(\ref{e561}) gives the impression that if ${\mit\Delta}_{pw}>0$ then the width of the magnetic island chain 
+grows without limit. In fact, this is not the case. Instead, the width of the island chain eventually stops growing, and the
+tearing mode attains a saturated steady state. In order to model this effect, it is necessary to perform the
+asymptotic matching between the inner and outer regions to higher order, taking into account the finite
+width of the island chain.\cite{white,thy,esc,mit}
+
+For the case of an island chain that is sufficiently wide to flatten  the density and temperature profiles within its magnetic separatrix, the appropriate saturation theory is given in Ref.~\onlinecite{has}.
+According to this theory, ${\mit\Delta}_{pw}$ in Eq.~(\ref{e561}) must be replaced by
+\begin{equation}\label{e562}
+{\mit\Delta}_{pw}(0) - \left(0.8\,\alpha_s^{2}-0.27\,\beta_s - 0.09\,\alpha_s\right)\frac{W}{r_s},
+\end{equation}
+where ${\mit\Delta}_{pw}(0)$ denotes the zero-island-width tearing stability index, $\alpha_s$ is defined in  Eq.~(\ref{e108}),
+and
+\begin{equation}
+\beta_s = -\left(\frac{r\,q\,J_z''}{s}\right)_{r=r_s}.
+\end{equation}
+
+Equations~(\ref{e561}) and (\ref{e562}) can be combined to give
+\begin{equation}\label{e564}
+I_1\,\tau_R\,\frac{d}{dt}\!\left(\frac{W}{r_s}\right)= {\mit\Delta}_{pw}(0)- \left(0.8\,\alpha_s^{2}-0.27\,\beta_s - 0.09\,\alpha_s\right)\frac{W}{r_s}.
+\end{equation}
+If we define
+\begin{align}
+W_{\rm sat} &= \frac{{\mit\Delta}_{pw}(0)\,r_s}{0.8\,\alpha_s^{2}-0.27\,\beta_s - 0.09\,\alpha_s},\\[0.5ex]
+\tau_{\rm sat} &= \frac{I_1\,\tau_R}{{\mit\Delta}_{pw}(0)}\,\frac{W_{\rm sat}}{r_s},
+\end{align}
+then Eq.~(\ref{e564}) reduces to
+\begin{equation}
+\tau_{\rm sat} \,\frac{d}{dt}\!\left(\frac{W}{W_{\rm sat}}\right) = 1-\frac{W}{W_{\rm sat}}.
+\end{equation}
+The previous equation can be solved to give
+\begin{equation}
+W(t) = W_{\rm sat}\left(1-{\rm e}^{-t/\tau_{\rm sat}}\right),
+\end{equation}
+assuming that the island width is zero at $t=0$. It follows that the width of the island chain does not grow without limit, 
+but instead eventually attains the saturated 
+value $W_{\rm sat}$. Moreover, the time required to attain saturation, $\tau_{\rm sat}$, is of order $\tau_R\,(W_{\rm sat}/r_s)$.
+
+\subsection{Natural Frequency}\label{sphase1}
+Equations~(\ref{e545}) and (\ref{e559x}) imply that 
+\begin{equation}\label{evz}
+v'=0 
+\end{equation}
+for an isolated magnetic island chain. It follows from
+ Equations~(\ref{e488}), (\ref{e506}), (\ref{yi}), (\ref{e526}), (\ref{e530}), and (\ref{evz}) yield $v=-1/(1+\tau)$, or
+\begin{equation}\label{e574}
+\omega= \omega_{\perp\,i},
+\end{equation}
+where
+\begin{equation}
+\omega_{\perp\,i} = \omega_E + \omega_{\ast\,i},
+\end{equation}
+and
+\begin{equation}
+\omega_{\ast\,i} = -\left(\frac{1}{1+\tau}\right)\omega_\ast.
+\end{equation}
+We conclude that, unlike a linear tearing mode, which is convected by the electron fluid at the resonant surface,\cite{ara} a nonlinear
+tearing mode is convected by the  ion  fluid.\cite{fw}
+
 \section*{Acknowledgements}
 This research was directly funded by the U.S.\ Department of Energy, Office of Science, Office of Fusion Energy Sciences,  under  contracts DE-FG02-04ER54742 and DE-SC0021156.
-
-\section*{Disclaimer} This report was prepared as an account of work sponsored by an agency of the United States Government.
-Neither the United States Government nor any agency thereof, nor any of their employees, makes any warranty, express or implied, or assumes any legal liability or responsibility for the accuracy, completeness, or usefulness of any information, apparatus, product, or process disclosed, or represents that its use would not infringe privately owned rights.
-Reference herein to any specific commercial product, process, or service by trade name, trademark, manufacturer, or otherwise does not necessarily constitute or imply its endorsement, recommendation, or favoring by the United States Government or any agency thereof.
-The views and opinions of authors expressed herein do not necessarily state or reflect those of the United States Government or any agency thereof.
 
@@
 
+\bibitem{white} R.A.~White, D.A.~Monticello, M.N.~Rosenbluth, and B.V.~Waddell, Phys.\ Fluids {\bf 20}, 800 (1977).
+
+\bibitem{thy} A.~Thyagaraja, Phys.\ Fluids {\bf 24}, 1716 (1981).
+
+\bibitem{esc} D.F.~Escande, and M.~Ottaviani, Phys. Lett.\ A {\bf 323}, 278 (2004).
+
+\bibitem{mit} F.~Militello, and F.~Porcelli, Phys.\ Plasmas {\bf 1}, L13 (2004).
+
+\bibitem{has} R.J.~Hastie, F.~Militello, and F.~Porcelli, Phys.\ Rev.\ Lett.\ {\bf 95}, 065001 (2005).
+
 \end{thebibliography}

### 2022-01-27 Research/LinearTearingModeTheory/Version1/Paper1.tex
Latest version

--- 2021-12-12 Research/LinearTearingModeTheory/LinearTearingModeTheory.tex
@@
 The analysis is then used to determine the scaling of the error-field penetration threshold with machine
-parameters in large aspect-ratio, ohmically heated, tokamak plasmas . A number of penetration regimes are found in which the threshold scales as $n^{1/2}$, where $n$ is the line-averaged
+parameters in large aspect-ratio, ohmically heated, tokamak plasmas. A number of penetration regimes are found in which the threshold scales as $n^{1/2}$, where $n$ is the line-averaged
 electron number density. A similar scaling has been reported in some experiments. 
@@
 \frac{\partial \hat{\nabla}^2\phi}{\partial \hat{t}}&= [\phi,\hat{\nabla}^2\phi] - \frac{1}{2\,(1+\tau)}\left(\hat{\nabla}^2[\phi,N] + [\hat{\nabla}^2\phi,N] + [\hat{\nabla}^2 N,\phi]\right) + [J,\psi] \nonumber\\[0.5ex]&\phantom{=}+\hat{\chi}_\varphi  \,\hat{\nabla}^4\!\left(\phi + \frac{N}{1+\tau}\right), \\[0.5ex]
-\frac{\partial N}{\partial \hat{t}}&= [\phi,N] +c_\beta^{\,2}\,[V,\hat{\psi}] +\hat{d}_\beta^{\,2}\,[J,\psi]
+\frac{\partial N}{\partial \hat{t}}&= [\phi,N] +c_\beta^{\,2}\,[V,\psi] +\hat{d}_\beta^{\,2}\,[J,\psi]
 + \hat{D}_\perp\,\hat{\nabla}_\perp^{\,2}N,\\[0.5ex]
@@
 \end{equation}
-where $\hat{\chi}_{\perp\,e,i}=\chi_{\perp\,e,i}/(r_s\,V_A)$, and $\chi_{\perp\,e,i}$ is the anomalous
-electron/ion perpendicular energy diffusivity in the vicinity of the resonant surface. 
+where $\hat{\chi}_{\perp\,e,i}=\chi_{\perp\,e,i}/(r_s\,V_A)$, and $\chi_{\perp\,e,i}$ is the (anomalous)
+perpendicular electron/ion  energy diffusivity in the vicinity of the resonant surface. 
 Note that Cole \& Fitzpatrick (2006) neglects the contribution of $\chi_{\perp\,e,i}$ to the perpendicular particle
@@
 \begin{align}\label{e31}
-\hat{\psi}(\hat{x},\zeta,\hat{t}) &= \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
+\psi(\hat{x},\zeta,\hat{t}) &= \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
 \phi(\hat{x},\zeta,\hat{t}) &=-\hat{V}_E\,\hat{x}+ \tilde{\phi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
@@
 \begin{equation}\label{torque}
-{\mit\Delta}\omega_E = \frac{1}{4}\left(\frac{\epsilon_s}{q_s}\right)^2\left(\frac{\tau_V}{\tau_H^{\,2}}\right)\frac{\tau_s\,(\omega_{s\,0}+{\mit\Delta}\omega_E)}{1+\tau_s^{\,2}\,(\omega_{s\,0}+{\mit\Delta}\omega_E)^2/(-{\mit\Delta}_s')^2}\left(\frac{w_v}{r_s}\right)^4,
+{\mit\Delta}\omega_E =- \frac{1}{4}\left(\frac{\epsilon_s}{q_s}\right)^2\left(\frac{\tau_V}{\tau_H^{\,2}}\right)\frac{\tau_s\,(\omega_{s\,0}+{\mit\Delta}\omega_E)}{1+\tau_s^{\,2}\,(\omega_{s\,0}+{\mit\Delta}\omega_E)^2/(-{\mit\Delta}_s')^2}\left(\frac{w_v}{r_s}\right)^4,
 \end{equation}
@@
 
-\bibitem{wes1} J.A.~Wesson, R.D.~Gill, M.~Hugon, F.C.~Sch\"{u}ller, J.A.~Snipes, D.J.~Ward, et al., Nucl.\ Fusion {\bf 29}, 641 (1989).
-
-\bibitem{vries} P.C.~de\,Vries, M.F.~Johnson, B.~Alper, P.~Buratti, T.C.~Hender, H.R.~Koslowski, et al., Nucl.\ Fusion {\bf 51}, 053018 (2011).
+\bibitem{wes1} J.A.~Wesson, R.D.~Gill, M.~Hugon, F.C.~Sch\"{u}ller, J.A.~Snipes, D.J.~Ward, D.V.~Bartlett, 
+D.J.~Campbell, P.A.~Duperrex, A.W.~Edwards, et al., Nucl.\ Fusion {\bf 29}, 641 (1989).
+
+\bibitem{vries} P.C.~de\,Vries, M.F.~Johnson, B.~Alper, P.~Buratti, T.C.~Hender, H.R.~Koslowski, V.~Riccardo, and JET-EFDA Contributors, Nucl.\ Fusion {\bf 51}, 053018 (2011).
 
@@
 
-\bibitem{hender} T.C.~Hender, R.~Fitzpatrick, A.W.~Morris, P.G.~Carolan, R.D.~Durst, T.~Edlington, et  al., Nucl.\ Fusion {\bf 32}, 2091 (1992).
+\bibitem{hender} T.C.~Hender, R.~Fitzpatrick, A.W.~Morris, P.G.~Carolan, R.D.~Durst, T.~Edlington, J.~Ferreira, 
+S.J.~Fielding, P.S.~Haynes, J.~Hugill, et al., Nucl.\ Fusion {\bf 32}, 2091 (1992).
 
@@
 
-\bibitem{wolf} R.C.~Wolf, W~Biel, M.F.M.~de\,Bock, K.H.~Finken, S.~G\"{u}nter, G.M.D.~Hogeweijet, et al., Nucl.\ Fusion {\bf 45}, 1700 (2005).
+\bibitem{wolf} R.C.~Wolf, W~Biel, M.F.M.~de\,Bock, K.H.~Finken, S.~G\"{u}nter, G.M.D.~Hogeweijet,  S.~Jachmich, M.W.~Jakubowski, R.J.E.~Jaspers, A.~Kr\"{a}mer-Flecken, et al., Nucl.\ Fusion {\bf 45}, 1700 (2005).
 
@@
 
-\bibitem{menard} J.E.~Menard, R.E.~Bell, D.A.~Gates, S.P.~Gerhardt, J.-K.~Park, S.A.~Sabbagh, et al., Nucl.\ Fusion {\bf 50}, 045008 (2010).
-
-\bibitem{wang1} N.~Wang, B.~Rao, Q.~Hu, Y.~Ding, Z.~Chen1, L.~Gao, et al., Nucl.\ Fusion {\bf 54}, 064014 (2014).
-
-\bibitem{wang2} H.-H.~Wang, Y.-W.~Sun, T.-H.~Shi, Q.~Zang, Y.-Q.~Liu, X.~Yang, et al., Nucl.\ Fusion {\bf 58}, 056024 (2018).
+\bibitem{menard} J.E.~Menard, R.E.~Bell, D.A.~Gates, S.P.~Gerhardt, J.-K.~Park, S.A.~Sabbagh, J.W.~Berkery,
+A.~Egan, J.~Kallman, S.M.~Kaye, et al., Nucl.\ Fusion {\bf 50}, 045008 (2010).
+
+\bibitem{wang1} N.~Wang, B.~Rao, Q.~Hu, Y.~Ding, Z.~Chen, L.~Gao, W.~Jin, B.~Yi, W.~Zeng, Q.~Li, et al., Nucl.\ Fusion {\bf 54}, 064014 (2014).
+
+\bibitem{wang2} H.-H.~Wang, Y.-W.~Sun, T.-H.~Shi, Q.~Zang, Y.-Q.~Liu, X.~Yang, 
+S.~Gu, K.-Y.~He, X.~Gu, J.-P.~Qian, et al., Nucl.\ Fusion {\bf 58}, 056024 (2018).
 
@@
 \bibitem{lazzaro} E.~Lazzaro, R.J.~Buttery, T.C.~Hender, P.~Zanca, R.~Fitzpatrick, 
-M.~Bigi, et al., Phys.\ Plasmas {\bf 9}, 3906 (2002).
+M.~Bigi, T.~Bolzonella, R.~Coelho, M.~DeBenedetti S.~Nowak, et al., Phys.\ Plasmas {\bf 9}, 3906 (2002).
 
@@
 
-\bibitem{buttery} R.J.~Buttery, M.~De'\,Benedetti, D.A.~Gates, Y.~Gribov, T.C.~Hender, R.J.~La\,Haye, et al., Nucl.\ Fusion {\bf 39}, 1827 (1999).
+\bibitem{buttery} R.J.~Buttery, M.~De'\,Benedetti, D.A.~Gates, Y.~Gribov, T.C.~Hender, R.J.~La\,Haye, P.~Leahy, 
+J.A.~Leuer, A.W.~Morris, A.~Santagiustina, et al., Nucl.\ Fusion {\bf 39}, 1827 (1999).
 
@@
 \begin{figure}
-\centerline{\includegraphics[width=0.95\textwidth]{RegimeI.pdf}}
+\centerline{\includegraphics[width=0.95\textwidth]{Figure1.pdf}}
 \caption{Linear resonant plasma response regimes in $Q$-$P$ space for the case $D=0.9$. The various regimes are
@@
 \begin{figure}
-\centerline{\includegraphics[width=0.95\textwidth]{RegimeII.pdf}}
+\centerline{\includegraphics[width=0.95\textwidth]{Figure2.pdf}}
 \caption{Linear resonant plasma response regimes in $Q$-$P$ space for the case $D=1.2$. The various regimes are
@@
 \begin{figure}
-\centerline{\includegraphics[width=0.95\textwidth]{RegimeIII.pdf}}
+\centerline{\includegraphics[width=0.95\textwidth]{Figure3.pdf}}
 \caption{Linear tearing mode growth-rate regimes  in $Q_\ast$-$P$ space. The various regimes are
@@
 \begin{figure}
-\centerline{\includegraphics[width=0.95\textwidth]{Scaling.pdf}}
+\centerline{\includegraphics[width=0.95\textwidth]{Figure4.pdf}}
 \caption{Error-field penetration regimes in $\hat{\nu}_\ast$-$\hat{\rho}_\ast$ space. The various regimes are the

### 2022-01-27 Research/LinearTearingModeTheory/Version2/Paper2.tex
Latest version

--- 2022-01-27 Research/LinearTearingModeTheory/Version1/Paper1.tex
@@
 The analysis is then used to determine the scaling of the error-field penetration threshold with machine
-parameters in large aspect-ratio, ohmically heated, tokamak plasmas. A number of penetration regimes are found in which the threshold scales as $n^{1/2}$, where $n$ is the line-averaged
-electron number density. A similar scaling has been reported in some experiments. 
+parameters in large aspect-ratio tokamak plasmas. 
 \end{abstract}
@@
 For instance, the strong {\em diamagnetic}\/ flows present in such plasmas decouple the electron and ion flows to some extent,
-necessitating a two-fluid treatment.\cite{ara} Moreover, resistive-MHD does not take  the important {\em ion sound radius lengthscale}, below which electron and ion dynamics are further decoupled, 
+necessitating a two-fluid treatment.\cite{ara} Moreover, resistive-MHD does not take  the important {\em ion sound radius} lengthscale, below which electron and ion dynamics are further decoupled, 
 into account.\cite{drake,wal} Previously, Cole \& Fitzpatrick\,\cite{cole} used the four-field model
@@
 This model is a slightly improved version of the model derived in Ref.~\onlinecite{fw} that takes the thermal force into account.
-The model is converted into a set of linear layer equations in
+(The thermal force merely gives rise to an additional term  in the perpendicular electron fluid velocity that scales as the electron temperature gradient.) The model is converted into a set of linear layer equations in
 Sect.~\ref{layer}. These layer equations are then solved in Sect.~\ref{linear} in order to map out all of the linear response regimes
-of a resonant layer to an externally generated resonant magnetic perturbation in a large aspect-ratio tokamak plasma. In Sect.~\ref{stab}, we reuse the analysis of Sect.~\ref{linear} to map out all
+of a resonant layer to an externally generated, resonant magnetic perturbation in a large aspect-ratio tokamak plasma. In Sect.~\ref{stab}, we reuse the analysis of Sect.~\ref{linear} to map out all
 of the growth-rate regimes for a low-mode-number (but not $m=1$) tearing mode in a large aspect-ratio tokamak plasma. Finally,
 in Sect.~\ref{error}, we employ the results of Sect.~\ref{linear} to determine the scaling of the error-field penetration threshold with machine parameters
- in large aspect-ratio, ohmically heated, tokamak plasmas.
+ in large aspect-ratio tokamak plasmas.
 
@@
 \begin{equation}\label{e110}
-{\mit\Delta\Psi}_s= {\mit\Delta}_s'\,{\mit\Psi}_s + (-{\mit\Delta}_s')\,{\mit\Psi}_v,
+{\mit\Delta\Psi}_s= ({\mit\Delta}_s')\,{\mit\Psi}_s + (-{\mit\Delta}_s')\,{\mit\Psi}_v,
 \end{equation}
@@
 \begin{align}
-\frac{\partial\psi}{\partial\hat{t}}&= [\phi,\psi] -\left(\frac{\tau}{1+\tau}\right)(1+\lambda_e)\,[N,\psi]
+\frac{\partial\psi}{\partial\hat{t}}&= [\phi,\psi] -\tau_e\,(1+\lambda_e)\,[N,\psi]
 +\hat{\eta}_\parallel\,J + \hat{E}_\parallel,\\[0.5ex]
-\frac{\partial \hat{\nabla}^2\phi}{\partial \hat{t}}&= [\phi,\hat{\nabla}^2\phi] - \frac{1}{2\,(1+\tau)}\left(\hat{\nabla}^2[\phi,N] + [\hat{\nabla}^2\phi,N] + [\hat{\nabla}^2 N,\phi]\right) + [J,\psi] \nonumber\\[0.5ex]&\phantom{=}+\hat{\chi}_\varphi  \,\hat{\nabla}^4\!\left(\phi + \frac{N}{1+\tau}\right), \\[0.5ex]
+\frac{\partial \hat{\nabla}^2\phi}{\partial \hat{t}}&= [\phi,\hat{\nabla}^2\phi] - \frac{\tau_i}{2}\left(\hat{\nabla}^2[\phi,N] + [\hat{\nabla}^2\phi,N] + [\hat{\nabla}^2 N,\phi]\right) + [J,\psi] \nonumber\\[0.5ex]&\phantom{=}+\hat{\chi}_\varphi  \,\hat{\nabla}^4\!\left(\phi + \tau_i\,N\right), \\[0.5ex]
 \frac{\partial N}{\partial \hat{t}}&= [\phi,N] +c_\beta^{\,2}\,[V,\psi] +\hat{d}_\beta^{\,2}\,[J,\psi]
@@
 \end{align}
-Here, $[A,B]\equiv \hat{\nabla} A\times \hat{\nabla} B\cdot {\bf n}$, $\hat{t} = t/(r_s/V_A)$, $\hat{\eta}_{\parallel,\perp} = \eta_{\parallel,\perp}/(\mu_0\,r_s\,V_A)$, $\hat{E}_\parallel = E_\parallel/(B_z\,V_A)$,
+Here, $[A,B]\equiv \hat{\nabla} A\times \hat{\nabla} B\cdot {\bf n}$, $\tau_e=[\tau/(1+\tau)]$, $\tau_i=1/(1+\tau)$, $\hat{t} = t/(r_s/V_A)$, $\hat{\eta}_{\parallel,\perp} = \eta_{\parallel,\perp}/(\mu_0\,r_s\,V_A)$, $\hat{E}_\parallel = E_\parallel/(B_z\,V_A)$,
 $\hat{\chi}_\varphi= \chi_\varphi/(r_s\,V_A)$, where $\eta_{\parallel,\perp}$ is the parallel/perpendicular plasma electrical
@@
 $\beta=(5/3)\,\mu_0\,p_0/B_z^{\,2}$. Here, $d_\beta$ is usually referred to as the {\em ion sound radius}. Furthermore,
-$\lambda_e=0.71\,\eta_e/(1+\eta_e)$. Finally,\cite{fw}
-\begin{equation}
-\hat{D}_\perp \equiv \frac{D_{\perp}}{r_s\,V_A}= c_\beta^{\,2}\,\hat{\eta}_\perp +  \frac{2}{3}\left(1-c_\beta^{\,2}\right)\!\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\perp\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\perp\,i}\right),
+$\lambda_e=0.71\,\eta_e/(1+\eta_e)$ originates from the thermal force. Finally,\cite{fw}
+\begin{equation}
+\hat{D}_\perp \equiv \frac{D_{\perp}}{r_s\,V_A}= c_\beta^{\,2}\,\hat{\eta}_\perp +  \frac{2}{3}\left(1-c_\beta^{\,2}\right)\!\left(\frac{\eta_e\,\tau_e}{1+\eta_e}\,\hat{\chi}_{\perp\,e} + \frac{\eta_i\,\tau_i}{1+\eta_i}\,\hat{\chi}_{\perp\,i}\right),
 \end{equation}
@@
 diffusivity, $D_\perp$, leading to an anomalously small estimate for $D_\perp$. It is this deficiency that we aim to
-correct in the present paper.
+correct in the present paper. To be more exact, given that $c_\beta\ll 1$ in conventional tokamak plasmas, and
+that $\hat{\eta}_\perp\ll \hat{\chi}_{\perp\,e,i}$ (i.e., magnetic flux typically diffuses  across magnetic flux surfaces in tokamak plasmas much more
+slowly than energy), the neglect of the terms involving $\hat{\chi}_{\perp\,e,i}$ in the previous equation leads to the
+erroneous conclusion that $\hat{D}_\perp\ll \hat{\chi}_{\perp\,e,i}$ (i.e., particles diffuse across magnetic flux-surfaces in tokamak plasmas 
+much more slowly than energy). The inclusion of the terms leads to the correct conclusion that  $\hat{D}_\perp\sim \hat{\chi}_{\perp\,e,i}$ (i.e., particles diffuse across magnetic flux-surfaces 
+at a similar rate to energy).
 
@@
 \phi(\hat{x},\zeta,\hat{t}) &=-\hat{V}_E\,\hat{x}+ \tilde{\phi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
-N(\hat{x},\zeta,\hat{t}) &= -\hat{V}_\ast\,\hat{x}+\left(\frac{1+\tau}{\tau}\right)\!\tilde{N}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
-V(\hat{x},\zeta,\hat{t}) &= \hat{V}_\parallel + \left(\frac{1+\tau}{\tau}\right)\!\tilde{V}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
+N(\hat{x},\zeta,\hat{t}) &= -\hat{V}_\ast\,\hat{x}+\tau_e\,\tilde{N}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
+V(\hat{x},\zeta,\hat{t}) &= \hat{V}_\parallel +\tau_e\,\tilde{V}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
 J(\hat{x},\zeta,\hat{t}) &=-\left(\frac{2}{s_s}-1\right)\!\frac{1}{\hat{L}_s}+ \hat{\nabla}^2\tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\label{e36}
@@
 -{\rm i}\,(\omega-\omega_E-\omega_{\ast\,i})\,\tau_H\,\hat{\nabla}^2\tilde{\phi} &= -{\rm i}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi}+S^{-1}\,P_\varphi\,\hat{\nabla}^4\!\left(\tilde{\phi} + \frac{\tilde{N}}{\tau}\right),\\[0.5ex]
--{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{N} &= -{\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\phi}-{\rm i}\,c_\beta^{\,2}\,\hat{x}\,\tilde{V} - {\rm i}\!\left(\frac{\tau}{1+\tau}\right)\hat{d}_\beta^{\,2}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi}\nonumber\\[0.5ex]
+-{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{N} &= -{\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\phi}-{\rm i}\,c_\beta^{\,2}\,\hat{x}\,\tilde{V} - {\rm i}\,\tau_e\,\hat{d}_\beta^{\,2}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi}\nonumber\\[0.5ex]
 &\phantom{=} + S^{-1}\,P_\perp\,\hat{\nabla}_\perp^2 \tilde{N},\\[0.5ex]
@@
  ${\bf E}\times {\bf B}$ frequency, 
-$\omega_{\ast\,e} = -[\tau/(1+\tau)](m/r_s)V_\ast(r_s)$
+$\omega_{\ast\,e} = -\tau_e\,(m/r_s)V_\ast(r_s)$
 the 
@@
 frequency,
-$\omega_{\ast\,i} =[1/(1+\tau)](m/r_s)V_\ast(r_s)$
+$\omega_{\ast\,i} =\tau_i\,(m/r_s)V_\ast(r_s)$
  the  ion diamagnetic
@@
 Here, $Q=S^{\,1/3}\,\omega\,\tau_H$, $Q_E = S^{\,1/3}\,\omega_E\,\tau_H$, $Q_{e,i} = S^{\,1/3}\,\omega_{\ast\,e,i}\,\tau_H$,
-and $D = S^{\,1/3}\,[\tau/(1+\tau)]^{1/2}\,\hat{d}_\beta$.
+and $D = S^{\,1/3}\,\tau_e^{1/2}\,\hat{d}_\beta$.
 
@@
 \begin{equation}\label{e48}
-{\mit\Delta\Psi}_s= S^{1/3}\,\hat{\mit\Delta}\,\,{\mit\Psi}_s.
+{\mit\Delta\Psi}_s= (S^{1/3}\,\hat{\mit\Delta})\,\,{\mit\Psi}_s.
 \end{equation}
@@
 G(p)&= \frac{p^2}{-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_e] + p^2},\\[0.5ex]
- A(p) &= -(Q-Q_E)\,(Q-Q_E-Q_i)-{\rm i}\,(Q-Q_E-Q_i)\,(P_\varphi+P_\perp)\,p^2 + P_\varphi\,P_\perp\,p^4,\\[0.5ex]
+ A(p) &= -(Q-Q_E)\,(Q-Q_E-Q_i)-{\rm i}\,(Q-Q_E-Q_i)\,(P_\varphi+P_\perp)\,p^2 + P_\varphi\,P_\perp\,p^4,\label{e45}\\[0.5ex]
  B(p) &= 
@@
 \begin{equation}\label{e332}
-K_\nu(z)= \frac{1}{{\mit\Gamma}(1-\nu)}\left(\frac{2}{q}\right)^\nu - \frac{1}{{\mit\Gamma}(1+\nu)}\left(\frac{q}{2}\right)^\nu + {\cal O}(q^{2-\nu}),
+K_\nu(q)= \frac{1}{{\mit\Gamma}(1-\nu)}\left(\frac{2}{q}\right)^\nu - \frac{1}{{\mit\Gamma}(1+\nu)}\left(\frac{q}{2}\right)^\nu + {\cal O}(q^{2-\nu}),
 \end{equation}
@@
 Figures~\ref{f1} and \ref{f2} show the extents of the various different linear resonant response regimes in $Q$-$P$ space for the
-cases $D<1$ and $D>1$, respectively. It can be seen, by comparison with Figs.~1--3 in Ref.~\onlinecite{cole}, that
+cases $D<1$ and $D>1$, respectively. Note that
+\begin{align}
+Q&\simeq 1.02\times 10^2\left[\frac{r_s^{2/3}({\rm m})\,L_s^{\,2/3}({\rm m})\,T_0^{\,1/2}({\rm keV})\,n_0^{\,1/2}(10^{19}\,{\rm m}^{-3})\,\omega({\rm krad/s})}{m^{\,2/3}\,B_z^{\,2/3}({\rm T})}\right],\label{e73}\\[0.5ex]
+P&\simeq 5.04\times 10^1\left[\chi_\perp({\rm m^2/s})\,T_0^{\,3/2}({\rm keV})\right],\\[0.5ex]
+D&\simeq 4.15\left[\frac{\tau_e^{\,1/2}\,m^{\,1/3}\,T_0({\rm keV})}{r_s^{\,1/2}({\rm m})\,L_s^{\,1/2}({\rm m})\,B_z^{\,1/6}({\rm T})\,n_0^{\,1/6}(10^{19}\,{\rm m}^{-3})}\right],
+\end{align}
+where $T_0$ and $\chi_\perp$ are the electron/ion temperatures and the particle/energy diffusivities at the resonant
+surface.
+ It can be seen, by comparison with Figs.~1--3 in Ref.~\onlinecite{cole}, that
 adopting a more realistic ordering for the perpendicular particle diffusivity, $D_\perp$, leads to a significant
@@
 \begin{align}
-A(p) &= (1+\lambda_e)\left(\frac{\tau}{1+\tau}\right)\left(1+ \frac{\lambda_e\,\tau}{1+\tau}\right)Q_\ast^{\,2}
--{\rm i}\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)Q_\ast\,(P_\varphi+P_\perp)\,p^2\nonumber\\[0.5ex]
-&\phantom{=} + P_\varphi\,P_\perp\,p^4,\\[0.5ex]
-\tilde{B}(p)&= P_\perp - {\rm i}\,(1+\lambda_e)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)Q_\ast\,D^2 +\left(\frac{1+\tau}{\tau}\right)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right) D^2\,P_\varphi\,p^2.
+A(p) &= (1+\lambda_e)\,\tau_e\left(1+ \lambda_e\,\tau_e\right)Q_\ast^{\,2}
+-{\rm i}\left(1+\lambda_e\,\tau_e\right)Q_\ast\,(P_\varphi+P_\perp)\,p^2+ P_\varphi\,P_\perp\,p^4,\\[0.5ex]
+\tilde{B}(p)&= P_\perp - {\rm i}\,(1+\lambda_e)\left(1+\lambda_e\,\tau_e\right)Q_\ast\,D^2 +\tau_e\left(1+\lambda_e\,\tau_e\right) D^2\,P_\varphi\,p^2.
 \end{align}
@@
 \begin{equation}
-C =\left(\frac{\tau}{1+\tau}\right) (1+\lambda_e)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)\frac{Q_\ast^{2}}{P_\perp}.
+C =\tau_e\, (1+\lambda_e)\left(1+\lambda_e\,\tau_e\right)\frac{Q_\ast^{2}}{P_\perp}.
 \end{equation}
@@
 \begin{equation}
-\hat{\mit\Delta} = \pi\,\hat{\gamma}\left[ \left(\frac{\tau}{1+\tau}\right)(1+\lambda_e)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)\right]^{1/2}\,\frac{Q_\ast}{P_\perp^{1/2}},
+\hat{\mit\Delta} = \pi\,\hat{\gamma}\left[ \tau_e\,(1+\lambda_e)\left(1+\lambda_e\,\tau_e\right)\right]^{1/2}\,\frac{Q_\ast}{P_\perp^{1/2}},
 \end{equation}
@@
 \begin{equation}\label{e363}
-\gamma = \frac{{\mit\Delta}_s'}{\pi\left[ \left(\frac{\tau}{1+\tau}\right)(1+\lambda_e)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)\right]^{1/2}\,}\,\frac{1}{\omega_\ast\,\tau_H\,\tau_R^{1/2}\,\tau_\perp^{1/2}}.
+\gamma = \frac{{\mit\Delta}_s'}{\pi\left[ \tau_e\,(1+\lambda_e)\left(1+\lambda_e\,\tau_e\right)\right]^{1/2}\,}\,\frac{1}{\omega_\ast\,\tau_H\,\tau_R^{1/2}\,\tau_\perp^{1/2}}.
 \end{equation}
@@
 \begin{equation}
-C = {\rm i}\left(\frac{\tau}{1+\tau}\right)\frac{Q_\ast}{D^2}.
+C = {\rm i}\,\tau_e\,\frac{Q_\ast}{D^2}.
 \end{equation} 
@@
 \begin{equation}
-\hat{\mit\Delta} = {\rm e}^{{\rm i}\,\pi/4}\,\pi\,\hat{\gamma}\left(\frac{\tau}{1+\tau}\right)^{1/2}\,\frac{Q_\ast^{1/2}}{D},
+\hat{\mit\Delta} = {\rm e}^{{\rm i}\,\pi/4}\,\pi\,\hat{\gamma}\,\tau_e^{1/2}\,\frac{Q_\ast^{1/2}}{D},
 \end{equation}
@@
 \begin{equation}
-C = \frac{P_\perp\,[\tau/(1+\tau)]}{[1+\lambda_e\,\tau/(1+\tau)]\,D^2}.
+C = \frac{P_\perp\,\tau_e}{(1+\lambda_e\,\tau_e)\,D^2}.
 \end{equation} 
@@
 \begin{equation} 
-\hat{\mit\Delta} = 2\pi\,\hat{\gamma}\,\frac{{\mit\Gamma}(3/4)}{{\mit\Gamma}(1/4)}\,\frac{[\tau/(1+\tau)]^{1/4}\,P_\perp^{1/4}}{[1+\lambda_e\,\tau/(1+\tau)]^{1/4}\,D^{1/2}},
+\hat{\mit\Delta} = 2\pi\,\hat{\gamma}\,\frac{{\mit\Gamma}(3/4)}{{\mit\Gamma}(1/4)}\,\frac{\tau_e^{1/4}\,P_\perp^{1/4}}{(1+\lambda_e\,\tau_e)^{1/4}\,D^{1/2}},
 \end{equation}
@@
 \begin{equation}\label{e371}
-\gamma= \frac{{\mit\Delta}_s'}{2\pi\,[{\mit\Gamma}(3/4)/{\mit\Gamma}(1/4)]\,[1+\lambda_e\,\tau/(1+\tau)]^{-1/4}}\,\frac{(d_\beta/r_s)^{1/2}\,\tau_\perp^{1/4}}{\tau_H^{1/2}\,\tau_R^{3/4}}.
+\gamma= \frac{{\mit\Delta}_s'}{2\pi\,[{\mit\Gamma}(3/4)/{\mit\Gamma}(1/4)]\,(1+\lambda_e\,\tau_e)^{-1/4}}\,\frac{(d_\beta/r_s)^{1/2}\,\tau_\perp^{1/4}}{\tau_H^{1/2}\,\tau_R^{3/4}}.
 \end{equation}
@@
  There are four tearing-mode growth-rate regimes---the resistive-inertial, the viscous-resistive, the semi-collisional, and the diffusive-resistive---and their extents in $Q_\ast$-$P$ space are illustrated in Fig.~\ref{f3}.
+The value of $Q_\ast$
+ can be estimated from Eq.~(\ref{e73}), with $\omega$ replaced by $\omega_\ast$. 
 Note that Fig.~\ref{f3} differs somewhat from Figs.~\ref{f1} and \ref{f2} because in the latter two
@@
 In fact, this possibility is also ruled out by finite anomalous
-perpendicular transport.
+perpendicular transport. To be more exact, the spurious resonances at  $\omega_r=\omega_E$ and $\omega_r=\omega_E+\omega_{\ast\,i}$  originate from the fact that, in the absence of finite
+perpendicular transport (i.e., $P_\varphi=P_\perp=0$), the function $A(p)$, specified in Eq.~(\ref{e45}), takes the value
+zero when $Q=Q_E+Q_i$ or $Q=Q_E$. However, in the presence of finite perpendicular transport, the function
+remains finite at  $Q=Q_E+Q_i$ and $Q=Q_E$, and the spurious resonances are eliminated.
 
@@
 Error-fields can drive magnetic reconnection, resulting in the formation of  locked (i.e., non-rotating in the laboratory
-frame) magnetic island chains, in intrinsically tearing-stable plasmas. Low-density, ohmically-heated tokamak plasmas
-containing locked magnetic island chains often terminate in disruptions\,\cite{wes1} (usually triggered when the
-external heating is turned on). Fortunately, error-field driven magnetic reconnection is strongly
-suppressed by the naturally occurring rotation of ohmic plasmas. However, when the error-field amplitude rises
+frame) magnetic island chains, in intrinsically tearing-stable plasmas. Tokamak plasmas
+containing locked magnetic island chains often terminate in disruptions.\cite{wes1} Fortunately, error-field driven magnetic reconnection is strongly
+suppressed by the naturally occurring rotation of such plasmas. However, when the error-field amplitude rises
 above a certain critical amplitude, the rotation at the resonant surface is suddenly arrested, and error-field driven reconnection proceeds
@@
 \subsection{Resonant Layer Response}
-Generally speaking, in an ohmically-heated tokamak, we do not expect the plasma flow at the resonant surface to be sufficiently
+Generally speaking, we do not expect the plasma flow at the resonant surface to be sufficiently
 large to cause a breakdown of the constant-$\psi$ approximation. We also expect $P_\varphi, P_\perp \gg 1$. In other
@@
 \begin{equation}
-\hat{\delta}_{\rm DR} = \frac{2\pi\,{\mit\Gamma}(3/4)}{{\mit\Gamma}(1/4)\,[1+\lambda_e\,\tau/(1+\tau)]^{1/4}}\,
+\hat{\delta}_{\rm DR} = \frac{2\pi\,{\mit\Gamma}(3/4)}{{\mit\Gamma}(1/4)\,(1+\lambda_e\,\tau_e)^{1/4}}\,
 \frac{\tau_H^{1/2}}{(d_\beta/r_s)^{1/2}\,\tau_R^{1/4}\,\tau_\perp^{1/4}}
@@
 
-Making use of the identities 
+Making use of the identities (which have been verified numerically)
 \begin{align}\label{e417a}
@@
 \begin{align}
-\rho_\ast &= \frac{T_0^{1/2}\,m_i^{1/2}}{e\,B_z\,L_s},\label{e428}\\[0.5ex]
-\nu_\ast &= \frac{L_s\,n_0\,e^2\,\eta_\parallel}{m_e^{1/2}\,T_0^{1/2}},\\[0.5ex]
-\beta_\ast&=\frac{\mu_0\,n_0\,T_0}{B_z^{\,2}},\label{e430}
+\rho_\ast &= \frac{T_0^{1/2}\,m_i^{1/2}}{e\,B_z\,L_s}= 3.23\times 10^{-3}\,\frac{T_0^{\,1/2}({\rm keV})}{B_z({\rm T})\,L_s({\rm m})},\label{e428}\\[0.5ex]
+\nu_\ast &= \frac{L_s\,n_0\,e^2\,\eta_\parallel}{m_e^{1/2}\,T_0^{1/2}}= 5.30\times 10^{-4}\,\frac{L_s({\rm m})\,n_0(10^{19}\,{\rm m}^{-3})}{T_0^{\,2}({\rm keV})},\\[0.5ex]
+\beta_\ast&=\frac{\mu_0\,n_0\,T_0}{B_z^{\,2}}= 2.01\times 10^{-3}\,\frac{n_0(10^{19}\,{\rm m}^{-3})\,T_0({\rm keV})}{B_z^{\,2}({\rm T})},\label{e430}
 \end{align}
@@
 
-In an ohmically-heated tokamak
+In a tokamak
 plasma, the energy confinement timescale, $\tau_E$, satisfies the constraint
 \begin{equation}
-\frac{n_0\,T_0}{\tau_E} = \eta_\parallel\left(\frac{B_z}{\mu_0\,L_s}\right)^2,
-\end{equation}
-which is obtained by equating the energy loss rate to the ohmic heating rate. Let us assume that the momentum confinement
+\frac{n_0\,T_0}{\tau_E} = \eta_\parallel\left(\frac{B_z}{\mu_0\,L_s}\right)^2\,{\cal P},
+\end{equation}
+which is obtained by equating the energy loss rate to the heating rate.
+Here, ${\cal P}$ is the ratio of the total heating rate to the ohmic heating rate.
+(Thus, ${\cal P}=1$ in an ohmically heated tokamak.)
+ Let us assume that the momentum confinement
 time, $\tau_\varphi$, and the particle/energy confinement time, $\tau_\perp$, are both equal to $\tau_E$, as is generally
-(approximately) the case in ohmically-heated tokamak plasmas.\cite{iter}
+(approximately) the case in  tokamak plasmas.\cite{iter}
 
@@
 \frac{\tau_H}{\tau_R}&\simeq \left(\frac{q_s}{\epsilon_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/2}\rho_\ast^{\,2}\,\nu_\ast\,\beta_\ast^{-1/2},\\[0.5ex]
-\frac{\tau_\varphi}{\tau_R} = \frac{\tau_\perp}{\tau_R} &\simeq \left(\frac{q_s}{\epsilon_s}\right)^2\beta_\ast,\\[0.5ex]
+\frac{\tau_\varphi}{\tau_R} = \frac{\tau_\perp}{\tau_R} &\simeq \left(\frac{q_s}{\epsilon_s}\right)^2\beta_\ast\,{\cal P}^{-1},\\[0.5ex]
 \frac{\tau_i}{\tau_R} &\simeq  \left(\frac{q_s}{\epsilon_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/2}\rho_\ast^{\,2}\,\beta_\ast^{-1},\\[0.5ex]
@@
 \begin{align}
-\hat{\delta}_{\rm VR} = \left(\frac{\tau_{\rm VR}}{\tau_R}\right) \simeq\left(\frac{\tau_H}{\tau_R}\right)^{1/3}\left(\frac{\tau_R}{\tau_\varphi}\right)^{1/6}&\simeq \left(\frac{q_s}{\epsilon_s}\right)^{1/3}\left(\frac{m_e}{m_i}\right)^{1/6}\rho_\ast^{\,2/3}\,\nu_\ast^{\,1/3}\,\beta_\ast^{-1/3},\\[0.5ex]
-\hat{\delta}_{\rm DR} = \left(\frac{\tau_{\rm DR}}{\tau_R}\right) \simeq \left(\frac{\tau_H}{\tau_R}\right)^{1/2}\left(\frac{\tau_R}{\tau_\perp}\right)^{1/4}\left(\frac{r_s}{d_\beta}\right)^{1/2}&\simeq \left(\frac{m_e}{m_i}\right)^{1/4}\rho_\ast^{\,1/2}\,\nu_\ast^{\,1/2}\,\beta_\ast^{-1/2},\\[0.5ex]
-\frac{\sqrt{\tau_\varphi\, \tau_i/\mu_{00}^i}}{\tau_R}&\simeq \left(\frac{q_s}{\epsilon_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/4}\,\rho_\ast.
+\hat{\delta}_{\rm VR} = \left(\frac{\tau_{\rm VR}}{\tau_R}\right) \simeq\left(\frac{\tau_H}{\tau_R}\right)^{1/3}\left(\frac{\tau_R}{\tau_\varphi}\right)^{1/6}&\simeq \left(\frac{q_s}{\epsilon_s}\right)^{1/3}\left(\frac{m_e}{m_i}\right)^{1/6}\rho_\ast^{\,2/3}\,\nu_\ast^{\,1/3}\,\beta_\ast^{-1/3}\,{\cal P}^{1/6},\\[0.5ex]
+\hat{\delta}_{\rm DR} = \left(\frac{\tau_{\rm DR}}{\tau_R}\right) \simeq \left(\frac{\tau_H}{\tau_R}\right)^{1/2}\left(\frac{\tau_R}{\tau_\perp}\right)^{1/4}\left(\frac{r_s}{d_\beta}\right)^{1/2}&\simeq \left(\frac{m_e}{m_i}\right)^{1/4}\rho_\ast^{\,1/2}\,\nu_\ast^{\,1/2}\,\beta_\ast^{-1/2}\,{\cal P}^{1/4},\\[0.5ex]
+\frac{\sqrt{\tau_\varphi\, \tau_i/\mu_{00}^i}}{\tau_R}&\simeq \left(\frac{q_s}{\epsilon_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/4}\,\rho_\ast\,{\cal P}^{-1/2}.
 \end{align}
@@
 \begin{equation}
-\rho_\ast < \left(\frac{\epsilon_s}{q_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/2}\nu_\ast\,\beta_\ast^{-1},
+\rho_\ast < \left(\frac{\epsilon_s}{q_s}\right)^2\left(\frac{m_e}{m_i}\right)^{1/2}\nu_\ast\,\beta_\ast^{-1}\,{\cal P}^{1/2},
 \end{equation}
@@
 \begin{equation}
-\rho_\ast < \left(\frac{\epsilon_s}{q_s}\right)\left(\frac{m_i}{m_e}\right)^{1/4}\beta_\ast,
+\rho_\ast < \left(\frac{\epsilon_s}{q_s}\right)\left(\frac{m_i}{m_e}\right)^{1/4}\beta_\ast\,{\cal P}^{-1/2},
 \end{equation}
@@
 \begin{align}
-\hat{\rho}_\ast&= \left(\frac{q_s}{\epsilon_s}\right)\left(\frac{m_e}{m_i}\right)^{1/4}\rho_\ast,\\[0.5ex]
-\hat{\nu}_\ast&=\left(\frac{\epsilon_s}{q_s}\right)\left(\frac{m_e}{m_i}\right)^{3/4}\nu_\ast.
+\hat{\rho}_\ast&= \left(\frac{q_s}{\epsilon_s}\right)\left(\frac{m_e}{m_i}\right)^{1/4}\rho_\ast\,{\cal P}^{1/2}= 0.245\left(\frac{B_z}{B_\theta}\right)
+{\cal P}^{1/2}\,\frac{B_z({\rm T})}{L_s({\rm m})\,n_0(10^{19}\,{\rm m}^{-3})\,T_0^{\,1/2}({\rm keV})},
+\\[0.5ex]
+\hat{\nu}_\ast&=\left(\frac{\epsilon_s}{q_s}\right)\left(\frac{m_e}{m_i}\right)^{3/4}\nu_\ast\,{\cal P}= 0.467\left(\frac{B_\theta}{B_z}\right)
+{\cal P}\,\frac{L_s({\rm m})\,B_z^{\,4}({\rm T})}{n_0(10^{19}\,{\rm m}^{-3})\,T_0^{\,4}({\rm keV})},.
 \end{align}
@@
 \left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm VR}-\varphi} \simeq \left(\frac{q_s}{\epsilon_s}\right)^{7/6}\left(\frac{m_e}{m_i}\right)^{1/12}
-\rho_\ast^{\,4/3}\,\nu_\ast^{\,1/6}\,\beta_\ast^{-1/6},
+\rho_\ast^{\,4/3}\,\nu_\ast^{\,1/6}\,\beta_\ast^{-1/6}\,{\cal P}^{\,7/12},
 \end{equation}
@@
 \left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm VR}-\theta} \simeq  \left(\frac{q_s}{\epsilon_s}\right)^{2/3}\left(\frac{m_e}{m_i}\right)^{-1/24}
-\rho_\ast^{\,5/6}\,\nu_\ast^{\,1/6}\,\beta_\ast^{\,1/3}.
+\rho_\ast^{\,5/6}\,\nu_\ast^{\,1/6}\,\beta_\ast^{\,1/3}\,{\cal P}^{\,1/3}.
 \end{equation}
@@
 \left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm DR}-\theta} \simeq  \left(\frac{q_s}{\epsilon_s}\right)^{1/2}\left(\frac{m_e}{m_i}\right)^{0}
-\rho_\ast^{\,3/4}\,\nu_\ast^{\,1/4}\,\beta_\ast^{\,1/4}.
+\rho_\ast^{\,3/4}\,\nu_\ast^{\,1/4}\,\beta_\ast^{\,1/4}\,{\cal P}^{\,3/8}.
 \end{equation}
@@
 \left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm DR}-\varphi} \simeq  \left(\frac{q_s}{\epsilon_s}\right)^{}\left(\frac{m_e}{m_i}\right)^{1/8}
-\rho_\ast^{\,5/4}\,\nu_\ast^{\,1/4}\,\beta_\ast^{-1/4}.\label{e447}
+\rho_\ast^{\,5/4}\,\nu_\ast^{\,1/4}\,\beta_\ast^{-1/4}\,{\cal P}^{\,5/8}.\label{e447}
 \end{equation}
@@
 and physical dimension (i.e., major radius) of an ohmically-heated tokamak. Using $\rho_\ast\sim T^{1/2}\,B^{-1}\,R^{-1}$, 
-$\nu_\ast\sim n\,T^{-2}\,R$, and $\beta_\ast\sim n\,T\,B^{-1}$,
+$\nu_\ast\sim n\,T^{-2}\,R$, and $\beta_\ast\sim n\,T\,B^{-2}$,
 we deduce that
 \begin{align}
-\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm VR}-\varphi} &\propto n^{0}\,T^{\,1/6}\,B^{-1}\,R^{-7/6},\\[0.5ex]
-\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm VR}-\theta} &\propto n^{1/2}\,T^{\,5/12}\,B^{-3/2}\,R^{-2/3},\\[0.5ex]
-\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm DR}-\theta} &\propto n^{1/2}\,T^{\,1/8}\,B^{-5/4}\,R^{-1/2},\\[0.5ex]
-\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm DR}-\varphi} &\propto n^{0}\,T^{-1/8}\,B^{-3/4}\,R^{-1}.
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm VR}-\varphi} &\propto n^{0}\,T^{\,1/6}\,B^{-1}\,R^{-7/6}\,{\cal P}^{\,7/12},\\[0.5ex]
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm VR}-\theta} &\propto n^{1/2}\,T^{\,5/12}\,B^{-3/2}\,R^{-2/3}\,{\cal P}^{\,1/3},\\[0.5ex]
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm DR}-\theta} &\propto n^{1/2}\,T^{\,1/8}\,B^{-5/4}\,R^{-1/2}\,{\cal P}^{\,3/8},\\[0.5ex]
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm DR}-\varphi} &\propto n^{0}\,T^{-1/8}\,B^{-3/4}\,R^{-1}\,{\cal P}^{\,5/8}.
 \end{align}
@@
 
-In order to make further progress, we need to adopt a specific scaling model for the energy confinement timescale, $\tau_E$. Let us adopt
+\subsection{Ohmic Plasmas}
+In order to make further progress, we need to adopt a specific scaling model for the energy confinement timescale, $\tau_E$. Consider ohmic plasmas for which ${\cal P}=1$. Let us adopt
 the following slightly modified version of the well-known neo-Alcator scaling law for low-density ohmically-heated tokamak plasmas:\cite{goldston,simmet,rf2012} 
@@
 \end{equation}
-(The modification is to ensure that the scaling law is consonant with the Connor-Taylor constraints.\cite{connor})
+(The modification is to ensure that the scaling law is consonant with the Connor-Taylor constraints, which
+require that ${\mit\Omega}_i\,\tau_E\propto n^{\alpha_n}\,B^{\,\alpha_B}\,R^{\,2\,\alpha_n+(5/4)\,\alpha_B}$.\cite{connor})
 It follows that
@@
 \begin{align}\label{e455}
-\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm VR}-\varphi} &\propto n^{0}\,B^{-13/15}\,R^{-13/12},\\[0.5ex]
-\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm VR}-\theta} &\propto n^{1/2}\,B^{-7/6}\,R^{-11/24},\\[0.5ex]
-\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm DR}-\theta} &\propto n^{1/2}\,B^{-23/20}\,R^{-7/16},\\[0.5ex]
-\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm DR}-\varphi} &\propto n^{0}\,B^{-17/20}\,R^{-17/16}.\label{e458}
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm VR}-\varphi} &\propto n^{\,0}\,B^{-13/15}\,R^{-13/12}= n^{\,0.00}\,B^{-0.87}\,R^{-1.08},\\[0.5ex]
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm VR}-\theta} &\propto n^{\,1/2}\,B^{-7/6}\,R^{-11/24}= n^{\,0.50}\,B^{-1.17}
+\,R^{-0.46},\\[0.5ex]
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm DR}-\theta} &\propto n^{\,1/2}\,B^{-23/20}\,R^{-7/16}=n^{\,0.50}\,B^{-1.15}\,R^{-0.44},\\[0.5ex]
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm DR}-\varphi} &\propto n^{\,0}\,B^{-17/20}\,R^{-17/16}= n^{\,0.00}\,B^{-0.85}\,R^{-1.06}.\label{e458}
 \end{align}
@@
 $b_{r\,{\rm crit}}/B_z\propto n^{\,\alpha_n}\,B^{\,\alpha_B}\,R^{\,\alpha_R}$ then $\alpha_R = 2\,\alpha_n+1.25\,\alpha_B$.\cite{buttery})
+
+\subsection{L/H-Mode Plasmas}
+For externally heated (i.e., ${\cal P}>1$) L/H-mode plasmas, we adopt the ITER89-P scaling law,\cite{yush}
+which yields
+\begin{equation}
+T\propto n^{-18/35}\,B^{\,41/35}\,R^{\,27/35}\,{\cal P}^{\,2/7}.
+\end{equation}
+(Note that we are assuming that the plasma rotation remains diamagnetic, which means that we are not taking into
+account any significant injection of toroidal momentum into the plasma as a consequence of the external
+heating scheme. This assumption is reasonable for ITER.)
+Hence, we deduce that 
+\begin{align}\label{e141}
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm VR}-\varphi} &\propto n^{-3/35}\,B^{-169/210}\,R^{-218/210}\,{\cal P}^{\,53/84}= n^{-0.09}\,B^{-0.80}\,R^{-1.04}\,{\cal P}^{\,0.63},\\[0.5ex]
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm VR}-\theta} &\propto n^{\,2/7}\,B^{-85/84}\,R^{-29/84}\,{\cal P}^{\,19/42}= n^{\,0.29}\,B^{-1.01}
+\,R^{-0.35}\,{\cal P}^{\,0.45},\\[0.5ex]
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm DR}-\theta} &\propto n^{\,61/140}\,B^{-309/280}\,R^{-113/280}\,{\cal P}^{\,23/56}=n^{\,0.44}\,B^{-1.10}\,R^{-0.40}\,{\cal P}^{\,0.41},\\[0.5ex]
+\left(\frac{b_{r\,{\rm crit}}}{B_z}\right)_{{\rm DR}-\varphi} &\propto n^{\,9/140}\,B^{-251/280}\,R^{-307/280}\,{\cal P}^{\,33/56}= n^{\,0.06}\,B^{-0.90}\,R^{-1.09}\,{\cal P}^{\,0.59}.\label{e144}
+\end{align}
+It can be seen, by comparison with Eqs.~(\ref{e455})--(\ref{e458}), that the ITER89-P scaling law leads to a
+somewhat weaker scaling of the penetration threshold with density compared to that predicted by the neo-Alcator scaling law. On the other hand, the scalings of the
+penetration threshold with magnetic field-strength and machine size predicted by the two scaling laws are
+remarkably similar.
+
+\subsection{Comparison with Experimental Data}
+The most up to date and comprehensive study of the empirical scaling of the error-field penetration threshold
+with machine parameters in tokamak plasmas is that of Ref.~\onlinecite{logan}. For $n=1$ modes in L/H-mode plasmas,
+it is found that
+\begin{equation}
+\frac{b_{r\,{\rm crit}}}{B_z}\propto n^{\,0.58\pm 0.06}\,B^{-1.13\pm 0.07}\,R^{+0.10\pm0.07}.
+\end{equation}
+It can be seen, by comparison with Eqs.~(\ref{e141})--(\ref{e144}), that the experimental density and magnetic field-strength scalings of the penetration threshold are reasonably compatible with those predicted in the theoretical diffusive-resistive-poloidal (DR-$\theta$) regime.
+On the other hand, the scaling with machine size is significantly different.
+All of the theoretical
+error-field penetration regimes lead to a {\em negative}\/ scaling of the penetration threshold with machine size.
+On the other hand, the experimental scaling features a {\em positive}\/ scaling with machine size. This discrepancy has
+significant consequences for ITER, which is much larger than present-day tokamaks. It should
+be noted that the experimental scaling with machine size is the most uncertain of all of the empirical scalings, because it is
+not possible to modify the major radius of a given tokamak. Hence, there are only as many effective data
+points as there are different machines in the data set.
+However, since most modern-day machines (e.g., DIII-D, EAST, JET) are of similar size, the size scaling of the penetration threshold is hypersensitive to data obtained from small
+tokamaks.
 
@@
 Finally, we have used our improved analysis to determine the scaling of the error-field penetration threshold with machine parameters in 
-large aspect-ratio, ohmically heated, tokamak plasmas. We find that if the change in the ${\bf E}\times {\bf B}$ frequency at the the resonant surface that permits the
-driven mode to lock to the error-field is predominately caused by a  shift in the  {\em poloidal}\/ ion fluid velocity (which is entirely possible,
-even in the presence of strong poloidal flow damping) then the threshold exhibits an $n^{1/2}$ scaling with particle
-number density. Such a scaling is consistent with some experimental observations.
+large aspect-ratio tokamak plasmas. We find that one particular error-field penetration regime (i.e., the diffusive-resistive-poloidal)
+leads to predicted scalings of the error-field penetration threshold with plasma density and magnetic field-strength
+that are reasonably consistent with the empirical scaling deduced from experimental data. On the other hand,
+all of the theoretical scalings predict a negative scaling of the penetration threshold with machine size, 
+whereas the experimental data indicates a positive scaling. This discrepancy has
+significant consequences for ITER, which is much larger than present-day tokamaks.
 
@@
 \bibitem{rf2012} R.~Fitzpatrick, Plasma Phys.\ Control.\ Fusion {\bf 54}, 094002 (2012).
+
+\bibitem{yush} P.N.~Yushmanov, T.~Takizuka, K.S.~Reidel, O.J.W.F.~Kardaun, J.G.~Cordey, S.M.~Kaye,
+and D.E.~Post, Nucl.\ Fusion {\bf 30}, 1999 (1990).
+
+\bibitem{logan} N.C.~Logan, J.-K.~Park, Q.~Hu, C.~Paz-Soldan, T.~Markovic, H.~Wang,
+Y.~In, L.~Piron, P.~Piovesan, C.E.~Myers, et al., Nucl.\ Fusion {\bf 60}, 086010 (2020).
 

### 2022-01-27 Research/LinearTearingModeTheory/Version2/reply.tex
Latest version

\documentclass{article}[12pt]
\usepackage{fullpage}

\begin{document}
\begin{center}
{\em  Influence of Anomalous Perpendicular Transport on Linear Tearing Mode Dynamics in Tokamak Plasmas}\\[1ex]
by R.~Fitzpatrick\\[1ex]
{\bf Reply to Referees' Comments}
\end{center}
Let me thank the  referees for their helpful and insightful comments on my paper. In response to the
comments, I have made the following changes:
\begin{enumerate}
\item In Sect.~V, I have expressed the dimensionless parameters $Q$, $P$, and $D$ in terms of
physical quantities. This should make it easier to determine which particular resonant response regime is
appropriate to a given plasma discharge. 
\item In Sect.~VII, I have expressed the dimensionless parameters $\rho_\ast$,
$\nu_\ast$, $\beta_\ast$, $\hat{\rho}_\ast$, and $\hat{\nu}_\ast$ in terms of physical quantities. 
This should made it easer to determine which particular error-field penetration regime is appropriate to
a given plasma discharge.
\item I have added a discussion of L/H-mode scaling based on the ITER89-P scaling law to Section~VII. This discussion facilitates comparison with
experimental data. I find that I can account for the density and magnetic field-strength scalings of
the penetration threshold (in a particular response regime). However, there is a serious discrepancy between
the theoretical and experimental scalings of the penetration threshold with machine size. This
discrepancy has obvious implications for ITER. Clearly, more research is needed to resolve this discrepancy.
\item I have added a comment to the effect that the thermal force merely gives rise to an additional term
in the expression for the perpendicular electron fluid velocity that is proportional to the temperature gradient.
\item I have added a comment that clarifies that the neglect of the $\chi_{\perp\,e,i}$ contributions to
$D_\perp$ leads to the erroneous prediction that the perpendicular particle diffusivity is much smaller than the
perpendicular energy diffusivity. 
\item I have defined the new parameters $\tau_e$ and $\tau_i$ to avoid excessive repetition
of $\tau/(1+\tau)$ and $1/(1+\tau)$ factors.
\item I have corrected Eq.~(54), and the incorrect scaling $\beta_\ast\sim n\,T/B$. 
\item I cannot actually find a reference for the identities (107) and (108). However, I have added a
comment to the effect that these identities have been verified numerically.
\item I have added some parenthesis, where appropriate, so that ${\mit\Delta\Psi}_s$ is not confused with
${\mit\Delta}\,\,{\mit\Psi}_s$.
\item I have made clear, in the abstract, that the error-field scaling involves the plasma density at the
resonant surface, rather than the line-averaged density. 
\item I have tried to improve the discussion of the elimination of spurious resonances by finite perpendicular transport. 
\end{enumerate}

My additional responses to the referees' comments are as follows:
\begin{enumerate}
\item Eqs.~(112)--(116) follow very directly from Eq.~(109). 
\item The neoclassical drive only applies to relatively wide islands (i.e., islands wide enough to flatten the
temperature profile). Hence, it does not seem relevant to error-field penetration, which involves the loss
of torque balance of a very thin island. 
\item I cannot think of any obvious interpolation formula that would link all of the possible layer response regimes.
\end{enumerate}
\end{document}

### 2022-01-27 Research/NonlinearTearingModeTheory/NonlinearTearingModeTheory.tex
Latest version

@@
 Tearing modes are slowly growing instabilities of ideally-stable tokamak plasmas that reconnect magnetic field-lines
-at various resonant surfaces within the plasma, in the process forming magnetic island chains that degrade the plasma confinement.\cite{wes} {\em Mode locking}\/ is a process by which the rotation of a magnetic island chain is braked  due to electromagnetic interaction with the resistive
+at various resonant surfaces within the plasma leading to the formation of magnetic island chains that degrade the plasma confinement.\cite{wes} {\em Mode locking}\/ is a process by which the rotation of a magnetic island chain is braked  due to electromagnetic interaction with the resistive
 vacuum vessel surrounding the plasma, causing the chain to eventually {\em lock}\/ (i.e., become stationary in the laboratory frame) to an error-field.\cite{nave}
@@
 tearing mode dynamics in tokamak plasmas. 
-For instance, the strong {\em diamagnetic}\/ flows present in such plasmas decouple the electron and ion flows to some extent,
+For instance, the strong {\em diamagnetic}\/ flows present in such plasmas decouple the electron and ion flows,
 necessitating a two-fluid treatment.\cite{ara} Previously, Fitzpatrick \& Waelbroeck\,\cite{fw,fw1} used a generalized version of the four-field model of Hazeltine, et al.\cite{haz})
@@
 As is well known, the general solution of Eq.~(\ref{e100}) is such that $\delta\psi$ is continuous across the resonant surface,
-whereas $\partial\delta\psi/\partial r$ is discontinuous. The discontinuity in $\partial \delta\psi/\partial r$ implies the presence of a helical  current sheet  at the resonant surface. 
+whereas $\partial\delta\psi/\partial r$ is discontinuous.\cite{fkr} The discontinuity in $\partial \delta\psi/\partial r$ implies the presence of a helical  current sheet  at the resonant surface. 
 The complex quantity 
@@
 Simultaneously matching our separable solution of Eq.~(\ref{e3})  across the resonant surface and the wall yields\,\cite{rf1993}
-\begin{align}
+\begin{align}\label{e9a}
 {\mit\Delta\Psi}_s& = E_{ss}\,{\mit\Psi}_s + E_{sw}\,{\mit\Psi}_w,\\[0.5ex]
@@
 where
-$\tau_w= \mu_0\,r_w\,\delta_w/\eta_w$.
+$\tau_w= \mu_0\,r_w\,\delta_w/\eta_w$ is known as the {\em time constant}\/ of the wall.
 Here, $\eta_w$ and $\delta_w$ are the electrical resistivity and radial thickness  of the wall, respectively. 
@@
 valid as long as
-\begin{equation}
+\begin{equation}\label{e10}
 \frac{r_w}{\delta_w}\gg \tau_w\left|\frac{d\ln{\mit\Psi}_w}{dt}\right|.
@@
 
-Assuming an $\exp(-{\rm i}\,\omega\,t)$ time dependence of perturbed quantities, the previous four equations
+Assuming an $\exp(-{\rm i}\,\omega\,t)$ time dependence of perturbed quantities,  Eqs.~(\ref{e9a})--(\ref{e9}) 
 can be combined to give
 \begin{equation}\label{e11}
-\frac{{\mit\Delta\Psi}_s}{{\mit\Psi}_s}= {\mit\Delta}_{pw} + \frac{{\mit\Delta}_{nw}-{\mit\Delta}_{pw}}{1-{\rm i}\,\omega\,\tau_{LR}},
+\frac{{\mit\Delta\Psi}_s}{{\mit\Psi}_s}= {\mit\Delta}_{pw} + \frac{{\mit\Delta}_{nw}-{\mit\Delta}_{pw}}{1-{\rm i}\,\tau_{LR}\,\omega},
 \end{equation}
-where ${\mit\Delta}_{pw}= E_{ss}$ is the  tearing stability index\cite{fkr} when the wall is perfectly conducting,
+where ${\mit\Delta}_{pw}= E_{ss}$ is the  so-called {\em tearing stability index}\,\cite{fkr} when the wall is perfectly conducting,
 ${\mit\Delta}_{nw} = E_{ss} + E_{sw}^{\,2}/(-E_{ww})$ is the  tearing stability index when there is no wall,
@@
 \subsection{Introduction}
-The helical current sheet at the resonant surface can only be resolved by solving  a two-fluid, resistive-MHD, plasma response model
+In order to proceed further, we need a relationship between ${\mit\Delta\Psi}_s$ and ${\mit\Psi}_s$ that
+is analogous in form to Eq.~(\ref{e9}). Such a relationship specifies how the helical current sheet that
+flows at the resonant surface is related to the reconnected magnetic flux. 
+We can obtain the desired relationship  by solving  a two-fluid, resistive-MHD, plasma response model
 in the inner region (i.e., the region of the plasma in the immediate vicinity of the resonant surface), 
@@
 \subsection{Resonant Response Model}\label{resonant}
-The fundamental fields in our resonant plasma reponse model---namely, $\psi$, $\phi$, $N$, $V$, and $J$---have the following
+The fundamental (dimensionless) fields in our resonant plasma reponse model---namely, $\psi$, $\phi$, $N$, $V$, and $J$---have the following
 definitions:
@@
 $\chi_{\parallel\,e,i}$ is the parallel electron/ion energy diffusivity in the vicinity of the resonant surface, and 
-$\chi_{\perp\,e,i}$ is the anomalous
-electron/ion perpendicular energy diffusivity in the vicinity of the resonant surface.
+$\chi_{\perp\,e,i}$ is the (anomalous) perpendicular
+electron/ion  energy diffusivity in the vicinity of the resonant surface.
 
@@
 reconnected flux, ${\mit\Psi}_s$, is assumed to be a positive real
-quantity. If $W$ is the full radial width of the magnetic island chain that develops at the resonant surface then it is
+quantity. Let $W$ be the full radial width of the magnetic island chain that develops at the resonant surface. It
+is
 helpful to define the reduced island width:
 \begin{equation}\label{e26a}
-w = \frac{W}{4}= \left(\frac{L_s\,{\mit\Psi}_s}{B_z}\right)^{1/2}.
+w \equiv \frac{W}{4}= \left(\frac{L_s\,{\mit\Psi}_s}{B_z}\right)^{1/2}.
 \end{equation}
@@
 \psi &\rightarrow \frac{\hat{x}^{\,2}}{2\,\hat{L}_s} + \frac{{\mit\Psi}_s}{r_s\,B_z}\,\cos\zeta,\\[0.5ex]
-\phi &\rightarrow \left(\frac{\hat{\omega}}{m}- \hat{V}_E\right)\hat{x} - \frac{s}{4}\,\hat{V}_E'\,\hat{x}^{\,2},\\[0.5ex]
+\phi &\rightarrow \left(\frac{\hat{\omega}}{m}- \hat{V}_E\right)\hat{x} - \frac{\varsigma}{4}\,\hat{V}_E'\,\hat{x}^{\,2},\\[0.5ex]
 N &\rightarrow -\hat{V}_\ast\,\hat{x},\\[0.5ex]
 V&\rightarrow \hat{V}_\parallel,\\[0.5ex]
-J& \rightarrow -\frac{2}{q_s\,\hat{R}_0} + \frac{1}{\hat{L}_s}.\label{e30}
+J& \rightarrow -\frac{2}{q_s\,\hat{R}_0} + \frac{1}{\hat{L}_s},\label{e30}
 \end{align}
@@
 laboratory frame,
-$s = {\rm sgn}(\hat{x})$,
+$\varsigma = {\rm sgn}(\hat{x})$,
 and 
@@
 \end{equation}
-The parameter $\hat{V}_E'$ is introduced  into the analysis in order to take into account the fact that the plasma rotation profile in the outer region develops a
+The parameter $\hat{V}_E'$ is introduced  into our analysis in order to take into account the fact that the plasma rotation profile in the outer region develops a
 gradient discontinuity at the resonant surface in response to the nonlinear localized electromagnetic torque that emerges 
-at the surface.\cite{fw} Finally, 
+at the surface due to interaction with the resistive wall.\cite{fw} Finally, 
  $\hat{E}_\parallel =(2/s_s-1) \,(\hat{\eta}_\parallel/\hat{L}_s)$.
@@
 and
-$T = \omega_\ast\,t$.
+$T = \omega_\ast\,t$,  where $\omega_\ast = - (m/r_s)\,V_\ast(r_s)$. 
 It follows that $|X|\sim {\cal O}(1)$ in the immediate vicinity of the island chain. It is helpful to define the
@@
 \end{align}
-where $\omega_\ast = - (m/r_s)\,V_\ast(r_s)$ and $\hat{\omega}_\ast = \omega_\ast/(V_A/r_s)$. 
+and  $\hat{\omega}_\ast = \omega_\ast/(V_A/r_s)$. 
 The resonant response model specified in Sect.~\ref{resonant} rescales to give
@@
 {\mit\Psi}&\rightarrow \frac{X^{2}}{2} + \cos\zeta,\label{e483}\\[0.5ex]
-{\mit\Phi} &\rightarrow v\,X +\frac{ s\,v'\,X^{2}}{2},\label{e484}\\[0.5ex]
+{\mit\Phi} &\rightarrow v\,X +\frac{\varsigma\,v'\,X^{2}}{2},\label{e484}\\[0.5ex]
 {\cal N}&\rightarrow X,\label{e486}\\[0.5ex]
@@
 v &= \frac{\omega-\omega_E}{\omega_\ast},\label{e488}\\[0.5ex]
-v' &= -\frac{\hat{w}}{2\,\omega_\ast}\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}}.\label{e489}
+v' &= -\frac{\hat{w}}{2\,\omega_\ast}\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}},\label{e489}
 \end{align}
+where $\omega_E= (m/r_s)\,V_E(r_s)$. 
 Note that ${\mit\Psi}$, ${\mit\Phi}$, ${\cal N}$, ${\cal V}$, and ${\cal J}$ are all ${\cal O}(1)$ quantities.
@@
 are consistent with the standard large-aspect ratio, low-$\beta$ orderings used to describe conventional tokamak
-plasmas. As will become apparent, the ordering $\epsilon_d\ll 1$ ensures that the island chain is
+plasmas.\cite{rf1993} As will become apparent, the ordering $\epsilon_d\ll 1$ ensures that the island chain is
 sufficiently wide that ion acoustic waves propagating parallel to the magnetic field are able to smooth out any
@@
 \begin{equation}\label{e500}
-{\cal N}_0(X,\zeta,T) = s\, {\cal N}_{(0)}({\mit\Omega},T).
+{\cal N}_0(X,\zeta,T) =\varsigma\, {\cal N}_{(0)}({\mit\Omega},T).
 \end{equation}
@@
 \begin{equation}\label{e503}
-{\mit\Phi}_0(X,\zeta,T) = s\, {\mit\Phi}_{(0)}({\mit\Omega},T).
+{\mit\Phi}_0(X,\zeta,T) = \varsigma\, {\mit\Phi}_{(0)}({\mit\Omega},T).
 \end{equation}
@@
 \begin{equation}
-\langle A(s,{\mit\Omega},\zeta)\rangle
+\langle A(\varsigma,{\mit\Omega},\zeta)\rangle
 \equiv \left\{
 \begin{array}{llr}
-\int_{\zeta_0}^{2\pi-\zeta_0}\frac{A(s,{\mit\Omega}\,\zeta)+A(-s,{\mit\Omega},\zeta)}{2\,[2\,({\mit\Omega}-\cos\zeta)]^{1/2}}\,\frac{d\zeta}{2\pi}&~~~~~&0\leq {\mit\Omega}\leq 1\\[2ex]
-\oint \frac{A(s,{\mit\Omega}\,\zeta)}{[2\,({\mit\Omega}-\cos\zeta)]^{1/2}}\,\frac{d\zeta}{2\pi}
+\int_{\zeta_0}^{2\pi-\zeta_0}\frac{A(\varsigma,{\mit\Omega}\,\zeta)+A(-\varsigma,{\mit\Omega},\zeta)}{2\,[2\,({\mit\Omega}-\cos\zeta)]^{1/2}}\,\frac{d\zeta}{2\pi}&~~~~~&0\leq {\mit\Omega}\leq 1\\[2ex]
+\oint \frac{A(\varsigma,{\mit\Omega}\,\zeta)}{[2\,({\mit\Omega}-\cos\zeta)]^{1/2}}\,\frac{d\zeta}{2\pi}
 &&{\mit\Omega}> 1
@@
 $\langle\{A,{\mit\Omega}\}\rangle = 0$
-for any $A(s,{\mit\Omega},\zeta,T)$. It is helpful to define
+for any $A(\varsigma,{\mit\Omega},\zeta,T)$. It is helpful to define
 $\tilde{A}  \equiv A - \langle A\rangle/\langle 1\rangle$.
@@
 $\langle \tilde{A}\rangle =0$
- for any $A(s,{\mit\Omega},\zeta,T)$.
+ for any $A(\varsigma,{\mit\Omega},\zeta,T)$.
 
@@
 \begin{equation}\label{yi}
-Y_i= M + \left(\frac{1}{1+\tau}\right)L.
+Y_i({\mit\Omega},T)= M + \left(\frac{1}{1+\tau}\right)L
 \end{equation} 
-The first term on the right-hand side of the previous equation represents the parallel return current driven by the perpendicular {\em polarization current}\/ associated with the
+parameterizes the ion fluid velocity. In fact, $V_{\theta\,i}\propto |X|\,Y_i$. 
+The first term on the right-hand side of Eq.~(\ref{e524a}) represents the parallel return current driven by the perpendicular {\em polarization current}\/ associated with the
 acceleration of the ion fluid around the magnetic separatrix of the island chain.\cite{smol1,smol2} 
 In fact, it is easily seen that if the ion fluid could pass freely through the separatrix (i.e., ${\mit\Phi}_0\propto X$ and ${\cal N}_0\propto X$) then the term in question would be zero.
-The second term on the right-hand side of the previous equation represents the parallel current driven
+The second term on the right-hand side of Eq.~(\ref{e524a}) represents the parallel current driven
 inductively when the reconnected flux at the resonant surfaces varies in time.
@@
 discontinuity. Given that the discontinuity in $L$ is mandated by the ordering $\epsilon_d=(\rho_\beta/w)^2\ll 1$, which
-requires $L$ to be a flux-surface function---and, hence, zero, by symmetry, inside the separatrix---it is plausible that the discontinuity is resolved by a thin layer of characteristic thickness $\rho_\beta$ on the island
+requires $L$ to be a flux-surface function---and, hence, zero, by symmetry, inside the magnetic separatrix---it is plausible that the discontinuity is resolved by a thin layer of characteristic thickness $\rho_\beta$ on the island chain's magnetic
 separatrix.
@@
 fluid velocity---and, hence, the function $Y_i$---be continuous across the separatrix, because the ion fluid possesses finite perpendicular viscosity. 
-Note, however, that the discontinuity in the function $L({\mit\Omega})$ across the separatrix [see Equation~(\ref{e526})] implies that the
+Note, however, that the discontinuity in the function $L({\mit\Omega})$ across the separatrix [see Eq.~(\ref{e526})] implies that the
 electron and MHD  fluid velocities are  discontinuous across the separatrix.  As previously
-mentioned, these discontinuities are resolved in a layer of characteristic thickness $\rho_\beta$.
+mentioned, these discontinuities are resolved in a layer of characteristic thickness $\rho_\beta$ on the island separatrix.
 
@@
 necessary to asymptotically match this solution to the solution in the outer region. 
-It is easily seen from Eqs.~(\ref{e108}) and (\ref{e109}) that  
+It is easily seen from Eqs.~(\ref{e108}) and (\ref{e109}) that\,\cite{fw} 
 \begin{align}
@@
 \end{align}
-where
+where $\tau_R=\mu_0\,r_s^{\,2}/\eta_\parallel$, $\tau_H=L_s/(m\,V_A)$, $\tau_\varphi=r_s^{\,2}/\chi_\varphi$, 
 \begin{align}
@@
 
-\section{Isolated Magnetic Island Chains}
+\section{Isolated Magnetic Island Chain}
 \subsection{Introduction}
@@
 \begin{equation}\label{e560x}
-{\rm Re}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right) = {\mit\Delta}_{pw}.
+{\rm Re}\!\left(\frac{{\mit\Delta\Psi}_s}{{\mit\Psi}_s}\right) = {\mit\Delta}_{pw}.
 \end{equation}
@@
 \begin{equation}\label{e564}
-I_1\,\tau_R\,\frac{d}{dt}\!\left(\frac{W}{r_s}\right)= {\mit\Delta}_{pw}(0)- \left(0.8\,\alpha_s^{2}-0.27\,\beta_s - 0.09\,\alpha_s\right)\frac{W}{r_s}.
+I_1\,\tau_R\,\frac{d}{dt}\!\left(\frac{W}{r_s}\right)= {\mit\Delta}_{pw}(0)\left(1-\frac{W}{W_{pw}}\right),
 \end{equation}
-If we define
+where
 \begin{align}
-W_{\rm sat} &= \frac{{\mit\Delta}_{pw}(0)\,r_s}{0.8\,\alpha_s^{2}-0.27\,\beta_s - 0.09\,\alpha_s},\\[0.5ex]
-\tau_{\rm sat} &= \frac{I_1\,\tau_R}{{\mit\Delta}_{pw}(0)}\,\frac{W_{\rm sat}}{r_s},
+W_{pw} = \frac{{\mit\Delta}_{pw}(0)\,r_s}{0.8\,\alpha_s^{2}-0.27\,\beta_s - 0.09\,\alpha_s}.
 \end{align}
-then Eq.~(\ref{e564}) reduces to
+Equation~(\ref{e564}) can be solved to give
 \begin{equation}
-\tau_{\rm sat} \,\frac{d}{dt}\!\left(\frac{W}{W_{\rm sat}}\right) = 1-\frac{W}{W_{\rm sat}}.
+W(t) = W_{pw}\left(1-{\rm e}^{-t/\tau_{pw}}\right),
 \end{equation}
-The previous equation can be solved to give
+assuming that the island width is zero at $t=0$,
+where
 \begin{equation}
-W(t) = W_{\rm sat}\left(1-{\rm e}^{-t/\tau_{\rm sat}}\right),
+\tau_{pw} = \frac{I_1\,\tau_R}{{\mit\Delta}_{pw}(0)}\,\frac{W_{pw}}{r_s}.
 \end{equation}
-assuming that the island width is zero at $t=0$. It follows that the width of the island chain does not grow without limit, 
+It follows that the width of the island chain does not grow without limit, 
 but instead eventually attains the saturated 
-value $W_{\rm sat}$. Moreover, the time required to attain saturation, $\tau_{\rm sat}$, is of order $\tau_R\,(W_{\rm sat}/r_s)$.
+value $W_{pw}$. Moreover, the time required to attain saturation is of order $\tau_R\,(W_{pw}/r_s)$.
 
@@
 Equations~(\ref{e545}) and (\ref{e559x}) imply that 
-\begin{equation}\label{evz}
-v'=0 
-\end{equation}
+$v'=0$ 
 for an isolated magnetic island chain. It follows from
- Equations~(\ref{e488}), (\ref{e506}), (\ref{yi}), (\ref{e526}), (\ref{e530}), and (\ref{evz}) yield $v=-1/(1+\tau)$, or
-\begin{equation}\label{e574}
+ Eqs.~(\ref{e488}), (\ref{e506}), (\ref{yi}), (\ref{e526}), and (\ref{e530}) that $v=-1/(1+\tau)$, or
+ \begin{equation}
 \omega= \omega_{\perp\,i},
@@
 and
-\begin{equation}
-\omega_{\ast\,i} = -\left(\frac{1}{1+\tau}\right)\omega_\ast.
-\end{equation}
+$\omega_{\ast\,i} = -[1/(1+\tau)]\,\omega_\ast$.
 We conclude that, unlike a linear tearing mode, which is convected by the electron fluid at the resonant surface,\cite{ara} a nonlinear
 tearing mode is convected by the  ion  fluid.\cite{fw}
+
+\subsection{Nonlinear Tearing Mode Dispersion Relation}\label{enl}
+According to the previous analysis, asymptotic matching between the
+inner and outer regions leads to
+\begin{equation}\label{e124}
+\frac{{\mit\Delta\Psi}_s}{{\mit\Psi}_s} = {\mit\Delta}_{pw}(0)\left(1-\frac{W}{W_{pw}}\right).
+\end{equation}
+Moreover, the physics of the inner region yields
+\begin{align}\label{e125}
+I_1\,\tau_R\,\frac{d}{dt}\!\left(\frac{W}{r_s}\right)&= {\mit\Delta}_{pw}(0)\left(1-\frac{W}{W_{pw}}\right),\\[0.5ex]
+\omega&=\omega_{\perp\,i}.\label{e126}
+\end{align}
+
+We can simultaneously account for the previous two equations by writing\,\cite{rf2021}
+\begin{equation}\label{e127}
+{\mit\Delta\Psi}_s = \tau_s\left(\frac{d}{dt}+{\rm i}\,\omega_{\perp\,i}\right){\mit\Psi}_s,
+\end{equation}
+where
+\begin{equation}
+\tau_s = \frac{I_1}{2}\,\tau_R\,\frac{W}{r_s}.
+\end{equation}
+In order to see how this works, let us write 
+\begin{equation}\label{e128}
+{\mit\Psi}_s(t)=|{\mit\Psi}_s(t)|\,{\rm e}^{-{\rm i}\,\omega\,t}.
+\end{equation} 
+It follows that
+\begin{equation}
+\frac{{\mit\Delta\Psi}_s}{{\mit\Psi}_s}= \tau_s\,\frac{d\,\ln|{\mit\Psi}_s|}{dt} + {\rm i}\,\tau_s\,(\omega_{\perp\,i}-\omega)= 
+2\,\tau_s\,\frac{d\,\ln W}{dt} + {\rm i}\,\tau_s\,(\omega_{\perp\,i}-\omega).
+\end{equation}
+Combining the previous equation with Eq.~(\ref{e124}), and taking real and imaginary parts, we obtain
+\begin{align}
+2\,\tau_s\,\frac{d\,\ln W}{dt} &= \frac{2\,\tau_s\,r_s}{W}\frac{d}{dt}\!\left(\frac{W}{r_s}\right)= I_1\,\tau_R\,\frac{d}{dt}\!\left(\frac{W}{r_s}\right)= {\mit\Delta}_{pw}(0)\left(1-\frac{W}{W_{pw}}\right),\\[0.5ex]
+\tau_s\,(\omega_{\perp\,i} -\omega) &= 0.
+\end{align}
+Thus, we have indeed accounted for Eqs.~(\ref{e125}) and (\ref{e126}).
+
+It we compare the nonlinear tearing mode dispersion relation, (\ref{e127}), with the 
+resistive wall dispersion relation, (\ref{e9}), then we can see that the plasma in the immediate vicinity of the
+resonant surface responds to external perturbations in an analogous fashion to a thin resistive wall of
+time constant $\tau_s$, that rotates at the angular frequency $\omega_{\perp\,i}$. Note, however, that
+the effective time constant of the wall, $\tau_s$, is proportional to the island width. This constitutes  the essential
+nonlinearity of the plasma response in the inner region.
+
+\section{Magnetic Island Chain Interacting with Resistive Wall}
+\subsection{Introduction}
+Let us now take the finite resistivity of the wall into account. Equation~(\ref{e10}), combined with the analysis
+of Sect.~\ref{sat}, implies that
+\begin{align}
+{\rm Re}\!\left(\frac{{\mit\Delta}{\mit\Psi}_s}{{\mit\Psi}_s}\right)&={\mit\Delta}_{pw}(0)\left(1-\frac{W}{W_{pw}}\right) + [{\mit\Delta}_{nw}(0)-{\mit\Delta}_{pw}(0)]\left(\frac{1}{1+\tau_{LR}^{\,2}\,\omega^{\,2}}\right),\\[0.5ex]
+{\rm Im}\!\left(\frac{{\mit\Delta}{\mit\Psi}_s}{{\mit\Psi}_s}\right)&=[{\mit\Delta}_{nw}(0)-{\mit\Delta}_{pw}(0)]\left(\frac{\tau_{LR}\,\omega}{1+\tau_{LR}^{\,2}\,\omega^{\,2}}\right).\label{e133}
+\end{align}
+Note that ${\rm Im}({\mit\Delta\Psi}_s/{\mit\Psi}_s)\neq 0$ as a consequence of the electromagnetic braking
+torque that develops at the resonant surface due to interaction with the resistive wall.
+
+\subsection{Nonlinear Tearing Mode Dispersion Relation}
+Equation~(\ref{e559}) yields
+\begin{align}\label{e559a}
+{\rm Re}\!\left(\frac{{\mit\Delta}{\mit\Psi}_s}{{\mit\Psi}_s}\right)&= I_1\,\tau_R\,\frac{d}{dt}\!\left(\frac{W}{r_s}\right)
+- \frac{I_2}{4}\left(\frac{c_\beta}{1+\tau}\right)\left(\frac{\rho_\beta}{r_s}\right)\left(\frac{\tau_\varphi}{\tau_H}\right)\left(\frac{W}{4\,r_s}\right)^2 {\rm Im}\!\left(\frac{{\mit\Delta\Psi}_s}{{\mit\Psi}_s}\right)\nonumber\\[0.5ex]
+&\phantom{=} -\frac{I_3}{16}\left(\frac{\tau_\varphi}{\tau_H}\right)^2 \left(\frac{W}{4\,r_s}\right)^7\left[{\rm Im}\!\left(\frac{{\mit\Delta\Psi}_s}{{\mit\Psi}_s}\right)\right]^2.
+\end{align}
+Using similar arguments to those employed in Sect.~\ref{enl}, we can account for the previous equation
+by writing
+\begin{align}
+{\mit\Delta\Psi}_s &= \tau_s\left(\frac{d}{dt}+{\rm i}\,\omega_{\perp\,i}\right){\mit\Psi}_s
+- \frac{I_2}{4}\left(\frac{c_\beta}{1+\tau}\right)\left(\frac{\rho_\beta}{r_s}\right)\left(\frac{\tau_\varphi}{\tau_H}\right)\left(\frac{W}{4\,r_s}\right)^2 {\rm Im}\!\left(\frac{{\mit\Delta\Psi}_s}{{\mit\Psi}_s}\right){\mit\Psi}_s\nonumber\\[0.5ex]
+&\phantom{=} -\frac{I_3}{16}\left(\frac{\tau_\varphi}{\tau_H}\right)^2 \left(\frac{W}{4\,r_s}\right)^7\left[{\rm Im}\!\left(\frac{{\mit\Delta\Psi}_s}{{\mit\Psi}_s}\right)\right]^2{\mit\Psi}_s.
+\end{align}
+Expressing ${\mit\Psi}_s$ in the form (\ref{e128}), dividing by ${\mit\Psi}_s$, and taking real and imaginary parts, we obtain Eq.~(\ref{e559a})
+and 
+\begin{equation}
+\tau_s\,(\omega_{\perp\,i}-\omega) = {\rm Im}\!\left(\frac{{\mit\Delta}{\mit\Psi}_s}{{\mit\Psi}_s}\right).
+\end{equation}
+According to the previous equation, if the resonant region is subject to an electromagnetic torque then the magnetic island
+chain slips to some extent with respect to the local ion fluid. Combining Eq.~(\ref{e133}) with the previous equation, we
+get 
+\begin{equation}
+\tau_s\,(\omega_{\perp\,i}-\omega) = [{\mit\Delta}_{nw}(0)-{\mit\Delta}_{pw}(0)]\left(\frac{\tau_{LR}\,\omega}{1+\tau_{LR}^{\,2}\,\omega^{\,2}}\right).
+\end{equation}
+Given that the maximum size of the right-hand side of the previous equation is of order unity, we can
+see that the maximum slip frequency is ${\mit\Delta}\omega \equiv \omega_{\perp\,i}-\omega
+\sim {\cal O}(1/\tau_s)$. The island chain is able to slip with respect to the ion fluid because the ion fluid
+is capable of diffusing across the chain's magnetic separatrix as a consequence of plasma resistivity.\cite{slip1,slip2,rf2021} However, because $\tau_s\propto W$, we conclude that wide island chains slip with respect to the ion
+fluid to a much lesser extent than narrow island chains.
 
@@
 
+\bibitem{slip1} L.G.~Eliseev, N.V.~Ivanov, A.M.~Kakurin, A.V.~Melnikov, and S.V.~Perfilov,
+Phys.\ Plasmas {\bf 22}, 052504 (2015).
+
+\bibitem{slip2} W.~Huang, and P.~Zhu, Phys.\ Plasmas {\bf 27}, 022514 (2020).
+
 \end{thebibliography}

### 2022-01-27 Research/TearingModeTheory/TearingModeTheory.tex
Latest version

@@
 \end{equation}
+Note that Equation~(\ref{e97}) is singular at the so-called {\em resonant}\/ magnetic flux-surface, radius $r=r_s$, at which 
+\begin{equation}\label{e104}
+q(r_s)= \frac{m}{n}.
+\end{equation}
+At the resonant surface, ${\bf k}\cdot{\bf B}=0$, where ${\bf k} = (0,\,m/r,\,-n/R_0)$ is the wavevector of the tearing perturbation.
 
@@
 
-Note that Equation~(\ref{e100}) is singular at the so-called {\em resonant}\/ magnetic flux-surface, radius $r=r_s$, at which 
-\begin{equation}\label{e104}
-q(r_s)= \frac{m}{n}.
-\end{equation}
-At the resonant surface, ${\bf k}\cdot{\bf B}=0$, where ${\bf k} = (0,\,m/r,\,-n/R_0)$ is the wavevector of the tearing perturbation. 
-The value of $\delta\psi(r,t)$ at the resonant surface---namely, ${\mit\Psi}_s(t)$---is known as the {\em reconnected magnetic flux}\/ (Fitzpatrick 1993). (See Section~\ref{dis1}.)
-Note that ${\mit\Psi}_s$ is, in general, a complex quantity. 
 Let $\rho=(r-r_s)/r_s$. 
@@
 
+The value of $\delta\psi(r,t)$ at the resonant surface---namely, ${\mit\Psi}_s(t)$---is known as the {\em reconnected magnetic flux}\/ (Fitzpatrick 1993). (See Section~\ref{dis1}.)
+Note that ${\mit\Psi}_s$ is, in general, a complex quantity. 
 The complex quantity
@@
 \begin{equation}\label{e238}
-\hat{\bf B} \simeq (1+ \delta b)\,{\bf n} + \hat{\nabla}\hat{\psi}\times {\bf n},
+\hat{\bf B} \simeq (1+ \delta b)\,{\bf n} + \hat{\nabla}\psi\times {\bf n},
 \end{equation}
@@
 \begin{equation}\label{e247a}
-\hat{\psi}=\frac{\psi_0+\delta\psi}{r_s\,B_z},
+\psi=\frac{\psi_0+\delta\psi}{r_s\,B_z},
 \end{equation}
@@
  Here, $\delta b(\hat{x},\zeta,
- \hat{t})$ and $\hat{\psi}(\hat{x},\zeta,\hat{t})$ are assumed to be small
+ \hat{t})$ and $\psi(\hat{x},\zeta,\hat{t})$ are assumed to be small
 compared to unity, which merely indicates that the perturbed magnetic field due to the tearing mode is small compared to the
@@
 \begin{equation}
-\hat{\bf E} \simeq \left(\hat{E}_\parallel- \frac{\partial \hat{\psi}}{\partial \hat{t}}\right)\!{\bf n} + \hat{\nabla}\!\left(\frac{\partial\chi}{\partial \hat{t}}\right)\times {\bf n} + \hat{\nabla}\phi,
+\hat{\bf E} \simeq \left(\hat{E}_\parallel- \frac{\partial \psi}{\partial \hat{t}}\right)\!{\bf n} + \hat{\nabla}\!\left(\frac{\partial\chi}{\partial \hat{t}}\right)\times {\bf n} + \hat{\nabla}\phi,
 \end{equation}
@@
  \begin{align}\label{e247}
- \hat{d}_i\,\hat{\nabla}(\delta p + \delta b)\nonumber\\[0.5ex]+ \left(\hat{E}_{\parallel}-\frac{\partial\hat{\psi}}{\partial \hat{t}} - [\hat{\psi},\phi]+ \frac{\hat{d}_i\,[\hat{\psi},\delta p]}{1+\tau}\left(1-\frac{0.71\,\eta_e\,\tau}{1+\eta_e}\right)
- + \hat{d}_i\,[\hat{\psi},\delta b]+ \hat{\eta}_\parallel\,J\right){\bf n}\nonumber\\[0.5ex]
- +\hat{\nabla}\!\left(\frac{\partial\chi}{\partial \hat{t}} + {\mit\Xi} -\hat{\eta}_\perp\,\delta b\right)\times {\bf n} + \frac{\hat{d}_i}{2}\,\hat{\nabla}\delta b^{\,2}- b_z\,\hat{\nabla}\phi + \hat{V}_{\parallel\,i}\,\hat{\nabla}\hat{\psi}
-+  \hat{d}_i\,J\,\hat{\nabla}\hat{\psi}= 0,\\[0.5ex]
- \hat{\nabla}(\delta p + \delta b) + \left(\frac{\partial \hat{V}_{\parallel\,i}}{\partial \hat{t}} + [\hat{V}_{\parallel\,i},\phi] + [\hat{\psi},\delta b]\right){\bf n}\nonumber\\[0.5ex]
+ \hat{d}_i\,\hat{\nabla}(\delta p + \delta b)\nonumber\\[0.5ex]+ \left(\hat{E}_{\parallel}-\frac{\partial\psi}{\partial \hat{t}} - [\psi,\phi]+ \frac{\hat{d}_i\,[\psi,\delta p]}{1+\tau}\left(1-\frac{0.71\,\eta_e\,\tau}{1+\eta_e}\right)
+ + \hat{d}_i\,[\psi,\delta b]+ \hat{\eta}_\parallel\,J\right){\bf n}\nonumber\\[0.5ex]
+ +\hat{\nabla}\!\left(\frac{\partial\chi}{\partial \hat{t}} + {\mit\Xi} -\hat{\eta}_\perp\,\delta b\right)\times {\bf n} + \frac{\hat{d}_i}{2}\,\hat{\nabla}\delta b^{\,2}- b_z\,\hat{\nabla}\phi + \hat{V}_{\parallel\,i}\,\hat{\nabla}\psi
++  \hat{d}_i\,J\,\hat{\nabla}\psi= 0,\\[0.5ex]
+ \hat{\nabla}(\delta p + \delta b) + \left(\frac{\partial \hat{V}_{\parallel\,i}}{\partial \hat{t}} + [\hat{V}_{\parallel\,i},\phi] + [\psi,\delta b]\right){\bf n}\nonumber\\[0.5ex]
  +\hat{\nabla}\!\left(\frac{\partial\phi}{\partial \hat{t}} - \frac{\hat{d}_i\,[\phi,\delta p]}{2\,(1+\tau)}\right)\times {\bf n} 
@@
  \left(\hat{V}_\perp^{\,2}+ \frac{\hat{\bf V}_\ast\cdot\hat{\bf V}_E }{1+\tau}+ \delta b^{\,2}\right)  \nonumber\\[0.5ex]
--\hat{\nabla}^2\phi\,\hat{\nabla}\phi + \frac{\hat{d}_i}{2\,(1+\tau)}\left(\hat{\nabla}^2\phi\,\hat{\nabla}\delta p +\hat{\nabla}^2\delta p\,\hat{\nabla}\phi\right) + J\,\hat{\nabla}\hat{\psi} + \hat{\nabla}\cdot\hat{\bpi}_i = 0,\label{e248}\\[0.5ex]
+-\hat{\nabla}^2\phi\,\hat{\nabla}\phi + \frac{\hat{d}_i}{2\,(1+\tau)}\left(\hat{\nabla}^2\phi\,\hat{\nabla}\delta p +\hat{\nabla}^2\delta p\,\hat{\nabla}\phi\right) + J\,\hat{\nabla}\psi + \hat{\nabla}\cdot\hat{\bpi}_i = 0,\label{e248}\\[0.5ex]
 \frac{\partial \delta p}{\partial \hat{t}} + [\delta p,\phi] +\beta\,\hat{\nabla}^2{\mit\Xi} + \frac{2}{3}\,\hat{\nabla}\cdot \hat{\bf q}= 0,\label{e249}
@@
  [A,B] &\equiv \hat{\nabla} A\times \hat{\nabla} B\cdot{\bf n},\\[0.5ex]
- J &= -\frac{2}{q_s\,\hat{R}_0}+ \hat{\nabla}^2\hat{\psi},\label{eJ}
+ J &= -\frac{2}{q_s\,\hat{R}_0}+ \hat{\nabla}^2\psi,\label{eJ}
  \end{align}
@@
  \begin{equation}\label{e252}
- \frac{\partial\hat{\psi}}{\partial\hat{t}}= [\phi,\hat{\psi}] +\hat{d}_i\!\left(\frac{\tau}{1+\tau}\right)\left(1+\frac{0.71\,\eta_e}{1+\eta_e}\right)
- [\delta p,\hat{\psi}] + \hat{\eta}_\parallel\,J + \hat{E}_\parallel.
+ \frac{\partial\psi}{\partial\hat{t}}= [\phi,\psi] +\hat{d}_i\!\left(\frac{\tau}{1+\tau}\right)\left(1+\frac{0.71\,\eta_e}{1+\eta_e}\right)
+ [\delta p,\psi] + \hat{\eta}_\parallel\,J + \hat{E}_\parallel.
  \end{equation}
@@
  \begin{equation}\label{e254}
- \frac{\partial\hat{V}_{\parallel\,i}}{\partial\hat{t}}= [\phi,\hat{V}_{\parallel\,i}]-[\delta p,\hat{\psi}] -{\bf n}\cdot\hat{\nabla}\cdot\hat{\bpi}_i.
+ \frac{\partial\hat{V}_{\parallel\,i}}{\partial\hat{t}}= [\phi,\hat{V}_{\parallel\,i}]-[\delta p,\psi] -{\bf n}\cdot\hat{\nabla}\cdot\hat{\bpi}_i.
  \end{equation}
@@
  \begin{equation}
- \frac{\partial\delta p}{\partial\hat{t}}= [\phi,\delta p]+\hat{\nabla}^2{\mit\Xi}-[\hat{V}_{\parallel\,i},\hat{\psi}]
- -\hat{d}_i\,[J,\hat{\psi}] +\hat{\eta}_\perp\,\hat{\nabla}^{2}\delta p.
+ \frac{\partial\delta p}{\partial\hat{t}}= [\phi,\delta p]+\hat{\nabla}^2{\mit\Xi}-[\hat{V}_{\parallel\,i},\psi]
+ -\hat{d}_i\,[J,\psi] +\hat{\eta}_\perp\,\hat{\nabla}^{2}\delta p.
  \end{equation}
@@
  \begin{align}\label{e256}
- \frac{\partial\delta p}{\partial\hat{t}}= [\phi,\delta p]-c_\beta^{\,2}\,[\hat{V}_{\parallel\,i},\hat{\psi}]-c_\beta^{\,2}\,\hat{d}_i\,[J,\hat{\psi}]
+ \frac{\partial\delta p}{\partial\hat{t}}= [\phi,\delta p]-c_\beta^{\,2}\,[\hat{V}_{\parallel\,i},\psi]-c_\beta^{\,2}\,\hat{d}_i\,[J,\psi]
  -\frac{2}{3}\,(1-c_\beta^{\,2})\,\hat{\nabla}\cdot\hat{\bf q} +c_\beta^{\,2}\,\hat{\eta}_\perp \hat{\nabla}^2\delta p,
@@
  \hat{\nabla}^2[\phi,\delta p] + [\hat{\nabla}^2\phi,\delta p] + [\hat{\nabla}^2 \delta p,\phi]\right)
- + [J,\hat{\psi}] \nonumber\\[0.5ex]&\phantom{=} + {\bf n}\cdot\hat{\nabla}\times \hat{\nabla}\cdot\hat{\bpi}_i,
+ + [J,\psi] \nonumber\\[0.5ex]&\phantom{=} + {\bf n}\cdot\hat{\nabla}\times \hat{\nabla}\cdot\hat{\bpi}_i,
  \end{align}
@@
 \begin{align}
-\hat{\nabla}\cdot \hat{\bf q} &=- \left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\parallel\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\parallel\,i}\right)[[\delta p,\hat{\psi}],\hat{\psi}]\nonumber\\[0.5ex]
+\hat{\nabla}\cdot \hat{\bf q} &=- \left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\parallel\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\parallel\,i}\right)[[\delta p,\psi],\psi]\nonumber\\[0.5ex]
 &\phantom{=} - \left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\perp\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\perp\,i}\right)\nabla_\perp^{\,2} \delta p,\label{e260}
@@
 \begin{align}\label{e264}
-\frac{\partial\hat{\psi}}{\partial\hat{t}}&= [\phi,\hat{\psi}] -\left(\frac{\tau}{1+\tau}\right)(1+\lambda_e)\,[N,\hat{\psi}]
+\frac{\partial\psi}{\partial\hat{t}}&= [\phi,\psi] -\left(\frac{\tau}{1+\tau}\right)(1+\lambda_e)\,[N,\psi]
 +\hat{\eta}_\parallel\,J + \hat{E}_\parallel,\\[0.5ex]
-\frac{\partial U}{\partial \hat{t}}&= [\phi,U] - \frac{1}{2\,(1+\tau)}\left(\hat{\nabla}^2[\phi,N] + [\hat{\nabla}^2\phi,N] + [\hat{\nabla}^2 N,\phi]\right) + [J,\hat{\psi}] \nonumber\\[0.5ex]&\phantom{=}+\hat{\chi}_\varphi  \,\hat{\nabla}^4\!\left(\phi + \frac{N}{1+\tau}\right),\label{e265} \\[0.5ex]
-\frac{\partial N}{\partial \hat{t}}&= [\phi,N] +c_\beta^{\,2}\,[V,\hat{\psi}] +\hat{d}_\beta^{\,2}\,[J,\hat{\psi}] + \hat{D}_\parallel\,[[N,\hat{\psi}],\hat{\psi}]
+\frac{\partial U}{\partial \hat{t}}&= [\phi,U] - \frac{1}{2\,(1+\tau)}\left(\hat{\nabla}^2[\phi,N] + [\hat{\nabla}^2\phi,N] + [\hat{\nabla}^2 N,\phi]\right) + [J,\psi] \nonumber\\[0.5ex]&\phantom{=}+\hat{\chi}_\varphi  \,\hat{\nabla}^4\!\left(\phi + \frac{N}{1+\tau}\right),\label{e265} \\[0.5ex]
+\frac{\partial N}{\partial \hat{t}}&= [\phi,N] +c_\beta^{\,2}\,[V,\psi] +\hat{d}_\beta^{\,2}\,[J,\psi] + \hat{D}_\parallel\,[[N,\psi],\psi]
 + \hat{D}_\perp\,\hat{\nabla}_\perp^{\,2}N,\label{e266}\\[0.5ex]
-\frac{\partial V}{\partial\hat{t}}&= [\phi,V] +[N,\hat{\psi}] + \hat{\chi}_\varphi\,\hat{\nabla}^2 V,\label{e267}\\[0.5ex]
-J &=-\frac{2}{q_s\,\hat{R}_0}+\hat{\nabla}^2\hat{\psi},\\[0.5ex]
+\frac{\partial V}{\partial\hat{t}}&= [\phi,V] +[N,\psi] + \hat{\chi}_\varphi\,\hat{\nabla}^2 V,\label{e267}\\[0.5ex]
+J &=-\frac{2}{q_s\,\hat{R}_0}+\hat{\nabla}^2\psi,\\[0.5ex]
 U &=\hat{\nabla}^2 \phi.\label{e269}
@@
 to the original four-field model derived by Hazeltine, et al.\ (Hazeltine, Kotschenreuther \& Morrison 1985). Equation~(\ref{e264}) is the {\em generalized
-Ohm's law}\/ that governs the time evolution of the (normalized) helical magnetic flux, $\hat{\psi}$. Equation~(\ref{e265}) is the {\em parallel
+Ohm's law}\/ that governs the time evolution of the (normalized) helical magnetic flux, $\psi$. Equation~(\ref{e265}) is the {\em parallel
 ion vorticity equation}\/ that governs the  time evolution of the (normalized) parallel ion vorticity, $U$. 
@@
 It is convenient to set the normalization scale-length, $l$, in our four-field response model equal to the minor radius of the resonant surface, $r_s$. 
-Recall that the four fields in question---namely, $\hat{\psi}$, $\phi$, $N$, and $V$---have the following
+Recall that the four fields in question---namely, $\psi$, $\phi$, $N$, and $V$---have the following
 definitions:
 \begin{align}\label{e279}
-\nabla\hat{\psi} &= \frac{{\bf n}\times{\bf B}} {r_s\,B_z},\\[0.5ex]
+\nabla\psi &= \frac{{\bf n}\times{\bf B}} {r_s\,B_z},\\[0.5ex]
 \nabla\phi &= \frac{{\bf n}\times {\bf V}}{r_s\,V_A},\\[0.5ex]
@@
  Our
-model also employs the auxiliary fields $J=-2\,\epsilon_s/q_s+r_s^2\,\nabla^2 \hat{\psi}$ and  $U=r_s^2\,\nabla^2 \phi$. Here, 
+model also employs the auxiliary fields $J=-2\,\epsilon_s/q_s+r_s^2\,\nabla^2 \psi$ and  $U=r_s^2\,\nabla^2 \phi$. Here, 
 \begin{equation}
@@
 \begin{align}\label{e287}
-\hat{\psi} &= \frac{\hat{x}^{\,2}}{2\,\hat{L}_s},\\[0.5ex]
+\psi &= \frac{\hat{x}^{\,2}}{2\,\hat{L}_s},\\[0.5ex]
 \phi &= - \hat{V}_E\,\hat{x},\\[0.5ex]
@@
 \begin{align}\label{e295}
-\hat{\psi}(\hat{x},\zeta,\hat{t}) &= \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
+\psi(\hat{x},\zeta,\hat{t}) &= \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
 \phi(\hat{x},\zeta,\hat{t}) &=-\hat{V}_E\,\hat{x}+ \tilde{\phi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
@@
 \centerline{\includegraphics[width=0.95\textwidth]{Island.pdf}}
-\caption{Equally-spaced contours of $\hat{\psi}(\hat{x},\xi)$. The magnetic separatrix is shown in red. }\label{f2a}
+\caption{Equally-spaced contours of $\psi(\hat{x},\xi)$. The magnetic separatrix is shown in red. }\label{f2a}
 \end{figure}
@@
 \begin{equation}
-\hat{\psi}(\hat{x},\zeta,\hat{t}) = \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},
+\psi(\hat{x},\zeta,\hat{t}) = \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},
 \end{equation}
@@
 \begin{equation}\label{e352a}
-\hat{\psi}(\hat{x},\xi)= \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ |\tilde{\psi}|\,\cos\xi,
+\psi(\hat{x},\xi)= \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ |\tilde{\psi}|\,\cos\xi,
 \end{equation}
@@
 \end{equation}
-Now, it is clear from Equation~(\ref{e279}) that ${\bf B}\cdot\hat{\nabla}\hat{\psi}=0$. In other words, the contours of
-$\hat{\psi}(\hat{x},\xi)$ map out the perturbed magnetic flux-surfaces in the vicinity of the resonant layer. 
+Now, it is clear from Equation~(\ref{e279}) that ${\bf B}\cdot\hat{\nabla}\psi=0$. In other words, the contours of
+$\psi(\hat{x},\xi)$ map out the perturbed magnetic flux-surfaces in the vicinity of the resonant layer. 
 Let $\hat{W} = 4\,(\hat{L}_s\,|\tilde{\psi}|)^{1/2}$. Equation~(\ref{e352a}) can be written
 \begin{equation}
-\frac{\hat{\psi}(\hat{x},\xi)}{|\tilde{\psi}|} = 8\left(\frac{\hat{x}}{\hat{W}}\right)^2 + \cos\xi.
-\end{equation}
-Figure~\ref{f2a} shows the contours of $\hat{\psi}(\hat{x},\xi)$ specified by the previous equation. It can be seen that the
+\frac{\psi(\hat{x},\xi)}{|\tilde{\psi}|} = 8\left(\frac{\hat{x}}{\hat{W}}\right)^2 + \cos\xi.
+\end{equation}
+Figure~\ref{f2a} shows the contours of $\psi(\hat{x},\xi)$ specified by the previous equation. It can be seen that the
 tearing mode has reconnected magnetic field-lines to produce a {\em helical magnetic island chain}\/ centered on the resonant
@@
 
-Finally, our four-field resonant plasma response model, (\ref{e264})--(\ref{e269}), contains many term of the general form $[\hat{\psi},\tilde{A}]$,
+Finally, our four-field resonant plasma response model, (\ref{e264})--(\ref{e269}), contains many term of the general form $[\psi,\tilde{A}]$,
 where $\tilde{A}(\hat{x},\zeta,\hat{t})$ is a perturbed quantity. According to Equation~(\ref{e352a}), such terms
@@
 \begin{equation}
-[\hat{\psi},\tilde{A}] = {\rm i}\,\frac{m}{r_s}\left(\frac{\hat{x}}{\hat{L}_s}\,\tilde{A} - \tilde{\psi}\,\frac{\partial \tilde{A}}{\partial\hat{x}}\right)
+[\psi,\tilde{A}] = {\rm i}\,\frac{m}{r_s}\left(\frac{\hat{x}}{\hat{L}_s}\,\tilde{A} - \tilde{\psi}\,\frac{\partial \tilde{A}}{\partial\hat{x}}\right)
 \sim {\rm i}\,\frac{m}{r_s}\,\frac{\hat{\delta}}{\hat{L}_s}\,\tilde{A} - {\rm i}\,\frac{m}{r_s}\,\frac{\tilde{\psi}}{\hat{\delta}}\,\tilde{A}, 
@@
 Furthermore, the four fields,
-$\hat{\psi}$, $\phi$, $N$, and $V$, as well as the auxiliary field, $J$, are assumed to only be functions of  the normalized radial coordinate, $\hat{x} = (r-r_s)/r_s$, the
+$\psi$, $\phi$, $N$, and $V$, as well as the auxiliary field, $J$, are assumed to only be functions of  the normalized radial coordinate, $\hat{x} = (r-r_s)/r_s$, the
 helical angle, $\zeta= m\,\theta-n\,\varphi$, and the
@@
 \begin{equation}\label{e456}
-w = \frac{W}{4} = (L_s\,R_0\,\hat{\mit\Psi}_s)^{1/2}.
+w \equiv \frac{W}{4} = (L_s\,R_0\,\hat{\mit\Psi}_s)^{1/2}.
 \end{equation}
@@
 \begin{align}
-\hat{\psi} &\rightarrow \frac{\hat{x}^{\,2}}{2\,\hat{L}_s} + \hat{R}_0\,\hat{\mit\Psi}_s\,\cos\zeta,\\[0.5ex]
-\phi &\rightarrow \left(\frac{\hat{\omega}}{m}- \hat{V}_E\right)\hat{x} - \frac{s}{4}\,\hat{V}_E'\,\hat{x}^{\,2},\\[0.5ex]
+\psi &\rightarrow \frac{\hat{x}^{\,2}}{2\,\hat{L}_s} + \hat{R}_0\,\hat{\mit\Psi}_s\,\cos\zeta,\\[0.5ex]
+\phi &\rightarrow \left(\frac{\hat{\omega}}{m}- \hat{V}_E\right)\hat{x} - \frac{\varsigma}{4}\,\hat{V}_E'\,\hat{x}^{\,2},\\[0.5ex]
 N &\rightarrow -\hat{V}_\ast\,\hat{x},\\[0.5ex]
@@
 \begin{equation}
-s = {\rm sgn}(\hat{x}),
+\varsigma = {\rm sgn}(\hat{x}),
 \end{equation}
@@
 \begin{align}
-\hat{\psi} &= \left(\frac{\hat{w}^{\,2}}{\hat{L}_s}\right){\mit\Psi},\label{e466}\\[0.5ex]
+\psi &= \left(\frac{\hat{w}^{\,2}}{\hat{L}_s}\right){\mit\Psi},\label{e466}\\[0.5ex]
 \phi &=\left(\frac{\hat{\omega}_\ast\,\hat{w}}{m}\right){\mit\Phi},\\[0.5ex]
@@
 {\cal N}&= {\cal N}_0+\epsilon_d^2\,{\cal N}_2+ \epsilon_d^3\,{\cal N}_3 + \cdots,\label{e431}\\[0.5ex]
-{\cal V} & ={\cal V}_0. +\epsilon_d\,{\cal V}_1 +\cdots,\\[0.5ex]
+{\cal V} & ={\cal V}_0 +\epsilon_d\,{\cal V}_1 +\cdots,\\[0.5ex]
 {\cal J} &= {\cal J}_0 + \epsilon_d\,{\cal J}_1 +\cdots. \label{e496}
@@
 \begin{equation}\label{e500}
-{\cal N}_0(X,\zeta,T) = s\, {\cal N}_{(0)}({\mit\Omega},T).
+{\cal N}_0(X,\zeta,T) = \varsigma\, {\cal N}_{(0)}({\mit\Omega},T).
 \end{equation}
@@
 \end{equation}
-for {\em any}\/ $A(s,{\mit\Omega},\zeta,T)$. It is helpful to define
+for {\em any}\/ $A(\varsigma,{\mit\Omega},\zeta,T)$. It is helpful to define
 \begin{equation}
@@
 \end{equation}
- for {\em any}\/ $A(s,{\mit\Omega},\zeta,T)$.
+ for {\em any}\/ $A(\varsigma,{\mit\Omega},\zeta,T)$.
 
@@
 while solving the  rescaled four-field model (\ref{e469})--(\ref{e473}) to lowest order  tells us that
-${\cal N}=s\,{\cal N}_{(0)}({\mit\Omega},T)$, ${\mit\Phi}_0 =s\,{\mit\Psi}_{(0)}({\mit\Omega},T)$, and
+${\cal N}=\varsigma\,{\cal N}_{(0)}({\mit\Omega},T)$, ${\mit\Phi}_0 =\varsigma\,{\mit\Psi}_{(0)}({\mit\Omega},T)$, and
 ${\cal V}_0 = {\cal V}_{(0)}({\mit\Omega},T)$, and that the lowest-order current density profile has the form (\ref{e513}), the lowest-order solution leaves the  flux-surface functions ${\cal N}_{(0)}({\mit\Omega},T)$,
@@
 fluid velocity---and, hence, the function $Y_i$---be continuous across the separatrix, because the ion fluid possesses finite perpendicular viscosity. 
-Note, however, that the discontinuity in the function $L({\mit\Omega})$ across the separatrix [see Equation~(\ref{e526})] implies that the
+Note, however, that the discontinuity in the function $L({\mit\Omega})$ across the island separatrix [see Equation~(\ref{e526})] implies that the
 electron and MHD  fluid velocities are  discontinuous across the separatrix. (See Section~\ref{s8.6}.) As previously
-mentioned, these discontinuities are resolved in a layer of characteristic thickness $\rho_\beta$.
+mentioned, these discontinuities are resolved in a layer of characteristic thickness $\rho_\beta$ on the separatrix.
 
@@
 \frac{\partial^2\psi}{\partial r^2}\,\cos\zeta\,\frac{d\zeta}{2\pi}\,dr\nonumber\\[0.5ex]&=\frac{2}{\hat{w}\,\hat{R}_0\,\hat{\mit\Psi}_s}\int_{-\infty}^{\infty}\oint
-\frac{\partial^2\hat{\psi}}{\partial X^2}\,\cos\zeta\,\frac{d\zeta}{2\pi}\,dX,\\[0.5ex]
+\frac{\partial^2\psi}{\partial X^2}\,\cos\zeta\,\frac{d\zeta}{2\pi}\,dX,\\[0.5ex]
 {\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)&= -\frac{2\,r_s}{R_0\,B_z\,\hat{\mit\Psi}_s}\int_{r_{s-}}^{r_{s+}}\oint
 \frac{\partial^2\psi}{\partial r^2}\,\sin\zeta\,\frac{d\zeta}{2\pi}\,dr\nonumber\\[0.5ex]&=-\frac{2}{\hat{w}\,\hat{R}_0\,\hat{\mit\Psi}_s}\int_{-\infty}^{\infty}\oint
-\frac{\partial^2\hat{\psi}}{\partial X^2}\,\sin\zeta\,\frac{d\zeta}{2\pi}\,dX.
+\frac{\partial^2\psi}{\partial X^2}\,\sin\zeta\,\frac{d\zeta}{2\pi}\,dX.
 \end{align}
@@
 \int_{1+}^\infty d_{\mit\Omega}(M\,Y_i)\left\langle\widetilde{X^2}\,\cos\zeta\right\rangle d{\mit\Omega}
-+\frac{4}{\epsilon_\eta\,\hat{w}}\,\frac{d(\ln \hat{w}^2)}{dT}\int_{-1}^\infty \frac{\langle \cos\zeta\rangle^2}{\langle 1\rangle}\,d{\mit\Omega}
++\frac{4}{\epsilon_\eta\,\hat{w}}\,\frac{d(\ln \hat{w}^2)}{dT}\int_{-1}^\infty \frac{\langle \cos\zeta\rangle^2}{\langle 1\rangle}\,d{\mit\Omega}.
 \end{align}
@@
 \begin{align}
-W_{\rm sat} &= \frac{{\mit\Delta}_{pw}(0)\,r_s}{0.8\,\alpha_s^{2}-0.27\,\beta_s - 0.09\,\alpha_s},\\[0.5ex]
-\tau_{\rm sat} &= \frac{I_1\,\tau_R}{{\mit\Delta}_{pw}(0)}\,\frac{W_{\rm sat}}{r_s},
+W_{pw} &= \frac{{\mit\Delta}_{pw}(0)\,r_s}{0.8\,\alpha_s^{2}-0.27\,\beta_s - 0.09\,\alpha_s},\label{epwa}\\[0.5ex]
+\tau_{pw} &= \frac{I_1\,\tau_R}{{\mit\Delta}_{pw}(0)}\,\frac{W_{pw}}{r_s},\label{tpw}
 \end{align}
@@
 \begin{equation}
-\tau_{\rm sat} \,\frac{d}{dt}\!\left(\frac{W}{W_{\rm sat}}\right) = 1-\frac{W}{W_{\rm sat}}.
+\tau_{pw} \,\frac{d}{dt}\!\left(\frac{W}{W_{pw}}\right) = 1-\frac{W}{W_{pw}}.
 \end{equation}
@@
 \begin{equation}
-W(t) = W_{\rm sat}\left(1-{\rm e}^{-t/\tau_{\rm sat}}\right),
+W(t) = W_{pw}\left(1-{\rm e}^{-t/\tau_{pw}}\right),
 \end{equation}
@@
 but instead eventually attains the saturated 
-value $W_{\rm sat}$. Moreover, the time required to attain saturation, $\tau_{\rm sat}$, is of order $\tau_R\,(W_{\rm sat}/r_s)$.
+value $W_{\rm pw}$. Moreover, the time required to attain saturation, $\tau_{pw}$, is of order $\tau_R\,(W_{pw}/r_s)$.
 
@@
 $q(a)$ is varied in order to shift the position of the resonant surface within the plasma. It can be seen that if the resonant
-surface lies far from the plasma boundary then the 2/1 island chain saturates at relatively small width (i.e., $W_{\rm sat}/a\ll 1$). 
+surface lies far from the plasma boundary then the 2/1 island chain saturates at relatively small width (i.e., $W_{pw}/a\ll 1$). 
 On the other hand, if the resonant surface lies close to the plasma boundary then the island chain
@@
 \begin{equation}
-\hat{\mit\Psi}_w = \frac{E_{sw}/(-\tilde{E}_{ww})}{1-{\rm i}\,\omega\,\tau_{LR}},
+\hat{\mit\Psi}_w = \frac{E_{sw}/(-\tilde{E}_{ww})}{1-{\rm i}\,\tau_{LR}\,\omega},
 \end{equation}
@@
 \begin{equation}
-\frac{{\mit\Delta\hat{\Psi}}_s}{\hat{\mit\Psi}_s} = {\mit\Delta}_{pw} + ({\mit\Delta}_{nw}-{\mit\Delta}_{pw})\left(\frac{1+{\rm i}\,\omega\,\tau_{LR}}{1+\omega^2\,\tau_{LR}^{\,2}}\right),
+\frac{{\mit\Delta\hat{\Psi}}_s}{\hat{\mit\Psi}_s} = {\mit\Delta}_{pw} + ({\mit\Delta}_{nw}-{\mit\Delta}_{pw})\left(\frac{1+{\rm i}\,\tau_{LR}\,\omega}{1+\tau_{LR}^{\,2}\,\omega^2}\right),
 \end{equation}
@@
 \begin{align}
-{\rm Re}\left(\frac{{\mit\Delta\hat{\Psi}}_s}{\hat{\mit\Psi}_s}\right)&= {\mit\Delta}_{pw} + ({\mit\Delta}_{nw}-{\mit\Delta}_{pw})\left(\frac{1}{1+\omega^2\,\tau_{LR}^{\,2}}\right),\\[0.5ex]
-{\rm Im}\left(\frac{{\mit\Delta\hat{\Psi}}_s}{\hat{\mit\Psi}_s}\right)&=({\mit\Delta}_{nw}-{\mit\Delta}_{pw})\left(\frac{\omega\,\tau_{LR}}{1+\omega^2\,\tau_{LR}^{\,2}}\right).
+{\rm Re}\left(\frac{{\mit\Delta\hat{\Psi}}_s}{\hat{\mit\Psi}_s}\right)&= {\mit\Delta}_{pw} + ({\mit\Delta}_{nw}-{\mit\Delta}_{pw})\left(\frac{1}{1+\tau_{LR}^{\,2}\,\omega^2}\right),\\[0.5ex]
+{\rm Im}\left(\frac{{\mit\Delta\hat{\Psi}}_s}{\hat{\mit\Psi}_s}\right)&=({\mit\Delta}_{nw}-{\mit\Delta}_{pw})\left(\frac{\tau_{LR}\,\omega}{1+\tau_{LR}^{\,2}\,\omega^2}\right).
 \end{align} 
@@
 \begin{align}\label{e583}
-{\rm Re}\left(\frac{{\mit\Delta\hat{\Psi}}_s}{\hat{\mit\Psi}_s}\right)&= {\mit\Delta}_{pw}(0)\left(1-\frac{w}{w_{pw}}\right) + [{\mit\Delta}_{nw}(0)-{\mit\Delta}_{pw}(0)]\left(\frac{1}{1+\omega^2\,\tau_{LR}^{\,2}}\right),\\[0.5ex]
-{\rm Im}\left(\frac{{\mit\Delta\hat{\Psi}}_s}{\hat{\mit\Psi}_s}\right)&=[{\mit\Delta}_{nw}(0)-{\mit\Delta}_{pw}(0)]\left(\frac{\omega\,\tau_{LR}}{1+\omega^2\,\tau_{LR}^{\,2}}\right),\label{e584}
-\end{align} 
-where $w_{pw}=W_{pw}/4$, and
-\begin{equation}
-W_{pw} = \frac{{\mit\Delta}_{pw}(0)\,r_s}{0.8\,\alpha_s^2 -0.27\,\beta_s-0.09\,\alpha_s}
-\end{equation}
-is the saturated island width when the wall is perfectly conducting.
+{\rm Re}\left(\frac{{\mit\Delta\hat{\Psi}}_s}{\hat{\mit\Psi}_s}\right)&= {\mit\Delta}_{pw}(0)\left(1-\frac{w}{w_{pw}}\right) + [{\mit\Delta}_{nw}(0)-{\mit\Delta}_{pw}(0)]\left(\frac{1}{1+\tau_{LR}^{\,2}\,\omega^2}\right),\\[0.5ex]
+{\rm Im}\left(\frac{{\mit\Delta\hat{\Psi}}_s}{\hat{\mit\Psi}_s}\right)&=[{\mit\Delta}_{nw}(0)-{\mit\Delta}_{pw}(0)]\left(\frac{\tau_{LR}\,\omega}{1+\tau_{LR}^{\,2}\,\omega^2}\right),\label{e584}
+\end{align} 
+where $w_{pw}=W_{pw}/4$, and $W_{pw}$ 
+is the saturated island width when the wall is perfectly conducting. [See Equation~(\ref{epwa}).]
 
@@
 \begin{align}\label{e586}
-I_1\,\tau_R\,\frac{d}{dt}\!\left(\frac{4\,w}{r_s}\right) &= {\mit\Delta}_{pw}(0)\left(1-\frac{w}{w_{pw}}\right) + [{\mit\Delta}_{nw}(0)-{\mit\Delta}_{pw}(0)]\left(\frac{1}{1+\omega^2\,\tau_{LR}^{\,2}}\right)\nonumber\\[0.5ex]
+I_1\,\tau_R\,\frac{d}{dt}\!\left(\frac{4\,w}{r_s}\right) &= {\mit\Delta}_{pw}(0)\left(1-\frac{w}{w_{pw}}\right) + [{\mit\Delta}_{nw}(0)-{\mit\Delta}_{pw}(0)]\left(\frac{1}{1+\tau_{LR}^{\,2}\,\omega^2}\right)\nonumber\\[0.5ex]
 &\phantom{=} +\frac{I_2}{4}\,[{\mit\Delta}_{nw}(0)-{\mit\Delta}_{pw}(0)]\left(\frac{c_\beta}{1+\tau}\right)\left(\frac{\rho_\beta}{r_s}\right)
-\left(\frac{\tau_\varphi}{\tau_H}\right)\left(\frac{w}{r_s}\right)^2\left(\frac{\omega\,\tau_{LR}}{1+\omega^2\,\tau_{LR}^{\,2}}\right)\nonumber\\[0.5ex]&\phantom{=}+\frac{I_3}{16}\,[{\mit\Delta}_{nw}(0)-{\mit\Delta}_{pw}(0)]^2\left(\frac{\tau_\varphi}{\tau_H}\right)^2\left(\frac{w}{r_s}\right)^7\left(\frac{\omega\,\tau_{LR}}{1+\omega^2\,\tau_{LR}^{\,2}}\right)^2.
+\left(\frac{\tau_\varphi}{\tau_H}\right)\left(\frac{w}{r_s}\right)^2\left(\frac{\tau_{LR}\,\omega}{1+\tau_{LR}^{\,2}\,\omega^2}\right)\nonumber\\[0.5ex]&\phantom{=}+\frac{I_3}{16}\,[{\mit\Delta}_{nw}(0)-{\mit\Delta}_{pw}(0)]^2\left(\frac{\tau_\varphi}{\tau_H}\right)^2\left(\frac{w}{r_s}\right)^7\left(\frac{\tau_{LR}\,\omega}{1+\tau_{LR}^{\,2}\,\omega^2}\right)^2.
 \end{align}
@@
 \omega_{s\,0} - \omega = \frac{1}{4}\,[{\mit\Delta}_{nw}(0)-{\mit\Delta}_{pw}(0)]
-\left(\frac{\epsilon_s}{q_s}\right)^2\left(\frac{\tau_V}{\tau_H^{\,2}}\right)\left(\frac{w}{r_s}\right)^4\left(\frac{\omega\,\tau_{LR}}{1+\omega^2\,\tau_{LR}^{\,2}}\right).
+\left(\frac{\epsilon_s}{q_s}\right)^2\left(\frac{\tau_V}{\tau_H^{\,2}}\right)\left(\frac{w}{r_s}\right)^4\left(\frac{\tau_{LR}\,\omega}{1+\tau_{LR}^{\,2}\,\omega^2}\right).
 \end{equation}
@@
 y &= \frac{\omega}{\omega_{s\,0} },\\[0.5ex]
-T &= \frac{t}{\tau_{pw}},\\[0.5ex]
-\tau_{pw}&= \frac{I_1\,\tau_R}{{\mit\Delta}_{pw}(0)}\,\frac{W_{pw}}{r_s}.
-\end{align}
+T &= \frac{t}{\tau_{pw}},
+\end{align}
+where $\tau_{pw}$ is defined in Equation~(\ref{tpw}).
 The modified Rutherford equation, (\ref{e586}), and the torque balance equation, (\ref{e588}), can be
@@
 \begin{align}
-\alpha_l & = \omega_{s\,0}\,\tau_{LR},\\[0.5ex]
+\alpha_l & =\tau_{LR} \,\omega_{s\,0},\\[0.5ex]
 \beta_l &= \frac{{\mit\Delta}_{nw}(0)}{{\mit\Delta}_{pw}(0)}-1,\\[0.5ex]

### 2022-01-27 Research/TearingModeTheory/Section11/Integrals/Integrals.cpp

@@ -1,0 +1,308 @@
+// Integrals.cpp
+
+#include "Integrals.h"
+
+// ###########
+// Constructor
+// ###########
+Integrals::Integrals ()
+{
+  // --------------------------------------
+  // Set default values of class parameters
+  // --------------------------------------
+
+  xmax  = 20.;
+  eps   = 1.e-7;
+  h0    = 1.e-6;
+  acc   = 1.e-13;
+  hmin  = 1.e-10;
+}
+
+// #########################
+// Function to solve problem
+// #########################
+void Integrals::Solve ()
+{
+  // ....................
+  // Calculate  integrals
+  // ....................
+
+  double x, h, t_err;
+  int rept; count = 0;
+  Array<double,1> y(4);
+
+  x    = eps;
+  y(0) = 0.;
+  y(1) = 0.;
+  y(2) = 0.;
+  y(3) = 0.;
+  h    = h0;
+
+  do
+    {
+      RK4Adaptive (x, y, h, t_err, acc, 2., rept, 20, hmin, 1.e-1, 2, 0, NULL);
+    }
+  while (x < xmax);
+
+  printf ("\nI0 = %11.4e  I1 = %11.4e  I2 = %11.4e  I3 = %11.4e\n\n", y(0), y(2), y(2), y(3));
+
+  double K00i = y(0);
+  double K01i = y(1);
+  double K11i = y(2);
+
+  double K00e = 1. + y(1);
+  double K01e = 1. + y(2);
+  double K11e = 2. + y(3);
+
+  double mu00i = K00i;
+  double mu01i = (5./2.) * K00i - K01i;
+  double mu11i = K11i - 5. * K01i + (25./4.) * K00i;
+
+  double mu00e = K00e;
+  double mu01e = (5./2.) * K00e - K01e;
+  double mu11e = K11e - 5. * K01e + (25./4.) * K00e;
+
+  printf ("mu00i = %11.4e  mu01i = %11.4e  mu11i = %11.4e\n",   mu00i, mu01i, mu11i);
+  printf ("mu00e = %11.4e  mu01e = %11.4e  mu11e = %11.4e\n\n", mu00e, mu01e, mu11e);
+
+  double fnc  = mu01i /mu00i;
+  double fbs1 = - ((sqrt(2.) + 13./4.) * mu00e - (3./2.) * mu01e) /(1. + sqrt(2.));
[…]

### 2022-07-31 Phase/Source/Phase.h
Added WPSIMAX flag to neoclassical

@@ -85,7 +85,7 @@
 #define PHASE
 
 #define VERSION_MAJOR 3
-#define VERSION_MINOR 6
+#define VERSION_MINOR 8
 #define MAXFILENAMELENGTH 500
 #define MAXCONTROLPOINTNUMBER 500
 #define MAXULFILELINELENGTH 500

### 2024-07-19 Documentation/EPEC_Model.tex
Latest version

--- 2021-09-26 Documentation/EPEC_Model.tex
@@
  K_{jk}^{\,e} &= g_t\,\frac{4}{3\sqrt{\pi}}\int_0^\infty
-\frac{e^{-x}\,x^{\,4+j+k}\,\nu_D^{\,e}(x)\,dx}{[x^{\,2}+\nu_{\ast\,e}\,\nu_D^{\,e}(x)]\,[x^{\,2}+(5\pi/8)\,(\omega_{t\,e}\,\tau_{ee})^{\,-1}\,\nu_T^{\,e}(x)]},\\[0.5ex]
-\nu_D^{\,e}&= \frac{3\sqrt{\pi}}{4}\left[\left(1-\frac{1}{2\,x}\right)\psi(x)+\psi'(x)\right]+\frac{3\sqrt{\pi}}{4}\,Z_{\rm eff},\\[0.5ex]
+\frac{e^{-x^{\,2}}\,x^{\,5+2\,(j+k)}\,\nu_D^{\,e}(x)\,dx}{[x^{\,4}+\nu_{\ast\,e}\,\nu_D^{\,e}(x)]\,[x^{\,4}+(5\pi/8)\,(\omega_{t\,e}\,\tau_{ee})^{\,-1}\,\nu_T^{\,e}(x)]},\\[0.5ex]
+\nu_D^{\,e}&= \frac{3\sqrt{\pi}}{4}\left[\left(1-\frac{1}{2\,x^2}\right)\psi(x)+\psi'(x)\right]+\frac{3\sqrt{\pi}}{4}\,Z_{\rm eff},\\[0.5ex]
 \nu_\epsilon^{\,e}&= \frac{3\sqrt{\pi}}{2}\left[\psi(x)-\psi'(x)\right],\\[0.5ex]
@@
 \begin{align}
-\psi(x) &= \frac{2}{\sqrt{\pi}}\int_0^x{\rm e}^{-t^{\,2}}\,dt -\frac{2}{\sqrt{\pi}}\,x\,{\rm e}^{-x^{\,2}},\\[0.5ex]
+\psi(x) &= \frac{2}{\sqrt{\pi}}\int_0^{x^{\,2}}\sqrt{t}\,{\rm e}^{-t}\,dt,\\[0.5ex]
 \psi'(x)&= \frac{2}{\sqrt{\pi}}\,x\,{\rm e}^{-x^{\,2}}.
@@
  K_{jk}^{\,i} &=g_t\,\frac{4}{3\sqrt{\pi}}\int_0^\infty
-\frac{e^{-x}\,x^{\,2+j+k}\,\nu_D^{\,i}(x)\,dx}{[x+\nu_{\ast\,i}\,\nu_D^{\,i}(x)]\,[x+(5\pi/8)\,(\omega_{t\,i}\,\tau_{ii})^{\,-1}\,\nu_T^{\,i}(x)]},\\[0.5ex]
- \nu_D^{\,i}&= \frac{3\sqrt{\pi}}{4}\left[\left(1-\frac{1}{2\,x}\right)\psi(x)+\psi'(x)\right]\frac{1}{x}\nonumber\\[0.5ex]\phantom{===}
-&\phantom{=}+\frac{3\sqrt{\pi}}{4}\,\alpha_I\left[\left(1-\frac{x_{iI}}{2\,x}\right)\psi\!\left(\frac{x}{x_{iI}}\right)
+\frac{e^{-x^{\,2}}\,x^{\,4+2\,(j+k)}\,\nu_D^{\,i}(x)\,dx}{[x^{\,3}+\nu_{\ast\,i}\,\nu_D^{\,i}(x)]\,[x^{\,3}+(5\pi/8)\,(\omega_{t\,i}\,\tau_{ii})^{\,-1}\,\nu_T^{\,i}(x)]},\\[0.5ex]
+ \nu_D^{\,i}&= \frac{3\sqrt{\pi}}{4}\left[\left(1-\frac{1}{2\,x^{\,2}}\right)\psi(x)+\psi'(x)\right]\frac{1}{x}\nonumber\\[0.5ex]\phantom{===}
+&\phantom{=}+\frac{3\sqrt{\pi}}{4}\,\alpha_I\left[\left(1-\frac{x_{iI}^{\,2}}{2\,x^{\,2}}\right)\psi\!\left(\frac{x}{x_{iI}}\right)
 +\psi'\!\left(\frac{x}{x_{iI}}\right)\right]\frac{1}{x},\\[0.5ex]
@@
  K_{jk}^{\,I} &= g_t\,\frac{4}{3\sqrt{\pi}}\int_0^\infty
-\frac{e^{-x}\,x^{\,2+j+k}\,\nu_D^{\,I}(x)\,dx}{[x+\nu_{\ast\,I}\,\nu_D^{\,I}(x)]\,[x+(5\pi/8)\,(\omega_{t\,I}\,\tau_{II})^{\,-1}\,\nu_T^{\,I}(x)]},\\[0.5ex]
- \nu_D^{\,I}&= \frac{3\sqrt{\pi}}{4}\left[\left(1-\frac{1}{2\,x}\right)\psi(x)+\psi'(x)\right]\frac{1}{x}\nonumber\\[0.5ex]\phantom{===}
-&\phantom{=}+\frac{3\sqrt{\pi}}{4}\,\frac{1}{\alpha_I}\left[\left(1-\frac{x_{Ii}}{2\,x}\right)\psi\!\left(\frac{x}{x_{Ii}}\right)
+\frac{e^{-x^{\,2}}\,x^{\,4+2\,(j+k)}\,\nu_D^{\,I}(x)\,dx}{[x^{\,3}+\nu_{\ast\,I}\,\nu_D^{\,I}(x)]\,[x^{\,3}+(5\pi/8)\,(\omega_{t\,I}\,\tau_{II})^{\,-1}\,\nu_T^{\,I}(x)]},\\[0.5ex]
+ \nu_D^{\,I}&= \frac{3\sqrt{\pi}}{4}\left[\left(1-\frac{1}{2\,x^{\,2}}\right)\psi(x)+\psi'(x)\right]\frac{1}{x}\nonumber\\[0.5ex]\phantom{===}
+&\phantom{=}+\frac{3\sqrt{\pi}}{4}\,\frac{1}{\alpha_I}\left[\left(1-\frac{x_{Ii}^{\,2}}{2\,x^{\,2}}\right)\psi\!\left(\frac{x}{x_{Ii}}\right)
 +\psi'\!\left(\frac{x}{x_{Ii}}\right)\right]\frac{1}{x},\\[0.5ex]
@@
 
+\subsection{Glasser-Greene-Johnson Data}
+Let $\hat{B}=|{\bf B}|/B_0$, $\hat{\nabla}= R_0\,\nabla$, $d\psi_p/dr = f(r)/R_0$, and 
+\begin{align}
+J_1(r) &= \oint\frac{1}{\hat{B}}\,\frac{d{\mit\Theta}}{2\pi},\\[0.5ex]
+J_2(r) &= \oint \hat{B}\,\frac{d{\mit\Theta}}{2\pi},\\[0.5ex]
+J_3(r) &= \oint\frac{1}{\hat{B}^{\,3}}\,\frac{d{\mit\Theta}}{2\pi},\\[0.5ex]
+J_4(r) &= \oint\frac{1}{\hat{B}\,|\hat{\nabla}\psi_p|^{\,2}}\,\frac{d{\mit\Theta}}{2\pi},\\[0.5ex]
+J_5(r) &= \oint\frac{\hat{B}}{|\hat{\nabla}\psi_p|^{\,2}}\,\frac{d{\mit\Theta}}{2\pi},\\[0.5ex]
+J_6(r) &= \oint\frac{1}{\hat{B}^{\,3}\,|\hat{\nabla}\psi_p|^{\,2}}\,\frac{d{\mit\Theta}}{2\pi}.
+\end{align}
+It follows that
+\begin{align}
+E(r) &= - \frac{dp/d\psi_p}{(dq/d\psi_p)^{\,2}}\,\frac{1}{\gamma}\left[\frac{d}{d\psi_p}\!\left(\frac{J_1}{\gamma}\right) - g\,\frac{dq}{d\psi_p}\,\frac{J_1}{J_2}\right]J_5,\\[0.5ex]
+F(r) &= \frac{(dp/d\psi_p)^{\,2}}{(dq/d\psi_p)^{\,2}}\,\frac{1}{\gamma^{\,2}}\left[g^{\,2}\left(J_5\,J_6- J_4^{\,2}\right)+ J_5\,J_3\right],
+\\[0.5ex]
+H(r)&= \frac{dp/d\psi_p}{dq/d\psi_p}\,\frac{g}{\gamma}\left(J_4 - \frac{J_1\,J_5}{J_2}\right),
+\end{align}
+where $P(r)$ is the total plasma pressure. 
+Finally,
+\begin{equation}
+D_R(r)= E + F + H^{\,2}.
+\end{equation}
+
 \section{Plasma Response in Inner Region}
@@
 \rho(r)&= m_i\left[n_i(r) + n_b(r)\right] + m_I\,n_I(r),\\[0.5ex]
-\tau_E(r) &= \frac{r^{\,2}}{D_\perp + (2/3)\,\chi_e},\\[0.5ex]
-\tau_M(r) &= \frac{R_0^{\,2}\,q^{\,2}}{\chi_\phi},\\[0.5ex]
-\rho_s (r)&= \frac{\sqrt{m_i\,T_e}}{e\,B_0\,g},\\[0.5ex]
-\tau(r)& = -\frac{\omega_{\ast\,i}}{\omega_{\ast\,e}},\\[0.5ex]
+\tau_\perp(r) &= \frac{r^{\,2}}{D_\perp},\\[0.5ex]
+\tau_\varphi(r) &= \frac{r^{\,2}}{\chi_\phi},\\[0.5ex]
+\tau(r)& = -\frac{\omega_{\ast\,e}}{\omega_{\ast\,i}},\\[0.5ex]
+d_\beta (r)&= \frac{\sqrt{(5/3)\,m_i\,[T_e + (n_i/n_e)\,T_i + (n_I/n_e)\,T_I]}}{e\,B_0\,g},\\[0.5ex]
 S(r) &= \frac{\tau_R}{\tau_H},\\[0.5ex]
-P_M(r) &= \frac{\tau_R}{\tau_M},\\[0.5ex]
-P_E(r) &= \frac{\tau_R}{\tau_E},\\[0.5ex]
-D(r)&= \frac{5}{3}\,S^{\,1/3}\,\frac{\rho_s}{r},\\[0.5ex]
-Q_E(r)&= S^{\,1/3}\,n\,\omega_E\,\tau_H,\\[0.5ex]
+P_\varphi(r) &= \frac{\tau_R}{\tau_\varphi},\\[0.5ex]
+P_\perp(r) &= \frac{\tau_R}{\tau_\perp},\\[0.5ex]
+D(r)&= S^{\,1/3}\,\left(\frac{\tau}{1+\tau}\right)^{1/2}\,\frac{d_\beta}{r},\\[0.5ex]
+Q_E(r)&= -S^{\,1/3}\,n\,\omega_E\,\tau_H,\\[0.5ex]
 Q_{e,i}(r)&= -S^{\,1/3}\,n\,\omega_{\ast\,e,i}\,\tau_H
@@
 \begin{equation}\label{e87}
-\frac{d^{\,2}\,Y}{dp^{\,2}} -\left[\frac{-Q_E\,(Q_E-Q_i)+{\rm i}\,(Q_E-Q_i)\,(P_M+P_E)\,p^{\,2}+
-P_M\,P_E\,p^{\,4}}
-{{\rm i}\,(Q_E-Q_e) +\{P_E + {\rm i}\,(Q_E-Q_i)\,D^{\,2}\}\,p^{\,2}+(1+\tau)\,P_M\,D^{\,2}\,p^{\,4}}
+\frac{d^{\,2}\,Y}{dp^{\,2}} -\left[\frac{-Q_E\,(Q_E+Q_i)+{\rm i}\,(Q_E+Q_i)\,(P_\varphi+P_\perp)\,p^{\,2}+
+P_\varphi\,P_\perp\,p^{\,4}}
+{{\rm i}\,(Q_E+Q_e) +\{P_\perp + {\rm i}\,(Q_E+Q_i)\,D^{\,2}\}\,p^{\,2}+(1+1/\tau)\,P_\varphi\,D^{\,2}\,p^{\,4}}
 \right] p^{\,2}\, Y = 0.
@@
 \end{equation}
-Note that Eq.~(\ref{e87}) can only be solved when $1+\tau>0$.
+Note that Eq.~(\ref{e87}) can only be solved when $1+1/\tau>0$.
 

### 2024-07-19 Flux/Source/Flux.cpp

@@ -33,7 +33,7 @@ void Flux::Solve ()
   // Input Stage1 data and output Stage2 data.
   // Stage2 data output to directory Outputs/Stage2.
   // Data passed to other programs output to Outputs/fFile.
-  Stage2 ();
+  if (STAGE2) Stage2 ();
 }
 
 // #################################
@@ -62,6 +62,8 @@ void Flux::SetParameters ()
   NSMOOTH = 100;
   NEOANG  = 0;
 
+  STAGE2  = 1;
+
   H0      = 1.e-6;
   ACC     = 1.e-14;
   ETA     = 1.e-8;
@@ -70,7 +72,7 @@ void Flux::SetParameters ()
   DELTA   = 1.e-7;
   
   // Read namelist file Inputs/Flux.nml
-  NameListRead (&INTG, &NPSI, &PACK, &NTHETA, &NNC, &NTOR, &H0, &ACC, &ETA, &MMIN, &MMAX, &PSILIM, &TIME, &PSIPED, &NSMOOTH, &PSIRAT, &NEOANG, &RW);
+  NameListRead (&INTG, &NPSI, &PACK, &NTHETA, &NNC, &NTOR, &H0, &ACC, &ETA, &MMIN, &MMAX, &PSILIM, &TIME, &PSIPED, &NSMOOTH, &PSIRAT, &NEOANG, &RW, &STAGE2);
 
   // Sanity check
   if (NPSI < 1)
@@ -154,8 +156,8 @@ void Flux::SetParameters ()
    printf ("Compile time = "); printf (COMPILE_TIME); printf ("\n");
    printf ("Git Branch   = "); printf (GIT_BRANCH);   printf ("\n\n");
    printf ("Input Parameters (from Inputs/Flux.nml):\n");
-   printf ("NPSI = %4d  NTHETA = %4d  NNC = %3d  PACK = %10.3e  NEOANG = %2d\n",
-	   NPSI, NTHETA, NNC, PACK, NEOANG);
+   printf ("NPSI = %4d  NTHETA = %4d  NNC = %3d  PACK = %10.3e  NEOANG = %2d  STAGE2 = %2d\n",
+	   NPSI, NTHETA, NNC, PACK, NEOANG, STAGE2);
[…]

### 2024-07-19 Flux/Source/Flux.h

@@ -65,6 +65,7 @@
 // 2.2  - Removed command line options
 // 2.3  - Added resistive wall
 // 2.4  - Added cylindrical quantities to NETCDF file
+// 2.5  - Added STAGE2 flag
 
 // #####################################################################################
 
@@ -74,7 +75,7 @@
 #define MAXFILENAMELENGTH 500
 
 #define VERSION_MAJOR 2
-#define VERSION_MINOR 4
+#define VERSION_MINOR 5
 
 #include <stdio.h>
 #include <math.h>
@@ -106,7 +107,7 @@ extern "C" int pRhs8 (double, const double[], double[], void*);
 // Namelist reading function
 extern "C" void NameListRead (int* INTG, int* NPSI, double* PACK, int* NTHETA, int* NNC, int* NTOR, double* H0,
 			      double* ACC, double* ETA, int* MMIN, int* MMAX, double* PSILIM, double* TIME,
-			      double* PSIPED, int* NSMOOTH, double* PSIRAT, int* NEOANG, double* RW);
+			      double* PSIPED, int* NSMOOTH, double* PSIRAT, int* NEOANG, double* RW, int* STAGE2);
 
 // gFile reading function
 extern "C" void gFileRead ();
@@ -150,7 +151,9 @@ class Flux
   int    NEOANG;  // Flag for using neoclassical angle in E-matrix calculation
 
   double EPS;     // Cylindrical tearing solutions launched from magnetic axis at r = EPS 
-  double DELTA;   // Cylindrical tearing solutions integrated to r = r_s +/- DELTA 
+  double DELTA;   // Cylindrical tearing solutions integrated to r = r_s +/- DELTA
+
+  int    STAGE2;  // If false terminate calculation at end of Stage1, otherwise proceed to Stage2
   
   // Stage 1 parameters
   double          R0;       // Scale major radius (m)
